### 2021-07-22 Paper_Analyses_subj_obje_arousal.Rmd
Pupil lmers

---
title: "Paper_analyses"
author: "Helio"
date: "22/07/2021"
output: html_document
---

Code for the paper: Valence modulated “subjective-objective” arousal

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Participants section

```{r}
participants_demog <- db_full4new_stim_screen_pupil_nopract %>%
  subset(Group == "NT")%>%
  group_by(ssid, Gender)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

# gender
table(participants_demog$Gender)
colnames(participants_demog)
summary(participants_demog$Age)
sd(participants_demog$Age, na.rm = TRUE)
# table(is.na(participants_demog$Age))
```

Pupil changes and subjective arousal and valence ratings

# let's model it formally

# remember baseline corection is equivalendt to stimuli intercept

```{r} 
pupil_arousal_findings<- list()
library(lmerTest)

unique(db_full4new_stim_screen_pupil_nopract$stimIAPS)
unique(substr(db_full4new_stim_screen_pupil_nopract$stimIAPS, 1,8))
db_full4new_stim_screen_pupil_nopract$Label<- substr(db_full4new_stim_screen_pupil_nopract$stimIAPS, 1,8)

db_full4new_stim_screen_pupil_nopract<- left_join(db_full4new_stim_screen_pupil_nopract, imageJ_IAPS, by = "Label")

nrow(db_full4new_stim_screen_pupil_nopract)
# rows = 2858

db_full4new_stim_screen_pupil_nopract$Mean_gray_z<- scale(db_full4new_stim_screen_pupil_nopract$Mean, center = TRUE, scale = TRUE)[,1]

db_full4new_stim_screen_pupil_nopract$ssid_num <- as.numeric(as.character(db_full4new_stim_screen_pupil_nopract$ssid))

```

lmer pupil

```{r}
options(contrasts = c("contr.sum","contr.poly"))
options(scipen = 999)

pupil_arousal_findings$pupil_from_arousal <- lmer(pup_basCor ~ arousal_c*Mean_gray_z  +(1 +Mean_gray_z | ssid) + (0+arousal_c| ssid), REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE & ssid_num< 500 & 
                                    arousal_outler == FALSE))

summary(pupil_arousal_findings$pupil_from_arousal)
# singularity (drop arousal c slope)

# is there a correlation between mean arousal rating and meang, gray(

db_full4new_stim_screen_pupil_nopract%>%
  group_by(stimIAPS,ground_valence_lab) %>%
  summarise_at(c('arousal_c', 'Mean_gray_z'), mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_c, Mean_gray_z, color = ground_valence_lab))+
  geom_point()+
  ggpubr::stat_cor()

```

# Valence and arousal
```{r}

pupil_arousal_findings$pupil_from_ar_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
                                                    Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid),
                                                    # (0+ valence_c* arousal_c | ssid),
                                                  REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE & ssid_num< 500 & 
                                      arousal_outler == FALSE))

summary(pupil_arousal_findings$pupil_from_ar_vale)
plot(pupil_arousal_findings$pupil_from_ar_vale)

car::vif(pupil_arousal_findings$pupil_from_ar_vale) #curoff 4

interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_val_gaze , pred = arousal_c, modx = valence_c)

interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_val_gaze , pred = valence_c , modx = arousal_c)

```

same analyses as above but regress brightness out of pupil

```{r}

pupil_arousal_findings$pupil_from_brightness <- lmer(pup_basCor ~ 
                                                    Mean  +
                                                    (1  | ssid),
                                                    # (0+ valence_c* arousal_c | ssid),
                                                  REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    # pupil_outlier == FALSE & ssid_num< 500 & 
                                      # arousal_outler == FALSE
                                    ))

pupil_arousal_findings$pupil_from_brightness_lm <- lm(pup_basCor ~ 
                                                    Mean,

                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    # pupil_outlier == FALSE & ssid_num< 500 & 
                                      # arousal_outler == FALSE
                                    ))

summary(pupil_arousal_findings$pupil_from_brightness)

plot(pupil_arousal_findings$pupil_from_brightness)

# store residuals
db_full4new_stim_screen_pupil_nopract$pup_resid <- resid(pupil_arousal_findings$pupil_from_brightness)

db_full4new_stim_screen_pupil_nopract$pup_resid_lm <-
resid(pupil_arousal_findings$pupil_from_brightness_lm)

db_full4new_stim_screen_pupil_nopract%>%
  ggplot(aes(pup_resid, Mean_gray_z))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

# no correlated with IV - good

db_full4new_stim_screen_pupil_nopract%>%
  ggplot(aes(pup_resid, pup_basCor))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

# strong correlation, in this case this is good, because it means there is a large ammount of unexplain ed variane not acconted for by the predictor

# predict pupil residuals
pupil_arousal_findings$pupil_resid_from_ar_vale <- lmer(pup_resid_lm ~ (arousal_c*valence_c) +

                                                    (1+arousal_c*valence_c  | ssid),
                                                    # (0+ valence_c* arousal_c | ssid),
                                                  REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE &
                                    ssid_num< 500 
                                    &
                                      arousal_outler == FALSE
                                      )) # results hold with or withouth outliers

summary(pupil_arousal_findings$pupil_resid_from_ar_vale)

# using residuals from lmer create a singularity as they eliminate individual participants variability, this is solved by using residuals from lm

interactions::interact_plot(pupil_arousal_findings$pupil_resid_from_ar_vale , pred = arousal_c, modx = valence_c)

interactions::interact_plot(pupil_arousal_findings$pupil_resid_from_ar_vale , pred = valence_c , modx = arousal_c)

```

Predict arousal from pupil

```{r}
# with arousal as DV
pupil_arousal_findings$arousal_from_pup <- lmer(arousal_c ~ valence_c*pup_basCor  + (1| stimIAPS)+
                                                 # (1 | ssid),
                                                  (0 +valence_c+pup_basCor | ssid),
                                                REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE & ssid_num<500 & 
                                      arousal_outler == FALSE))
summary(pupil_arousal_findings$arousal_from_pup)
anova(pupil_arousal_findings$arousal_from_pup)

# expected correlation between valence and pupil is low

interactions::interact_plot(pupil_arousal_findings$arousal_from_pup , pred = valence_c, modx = pup_basCor)

interactions::interact_plot(pupil_arousal_findings$arousal_from_pup, pred =pup_basCor , modx =  valence_c) #better 
# same pattern
# pupil is more aligned with subjective arousal in the more positive trials

# flip dv to valence

pupil_arousal_findings$valence_from_pup <- lmer(valence_c ~ arousal_c*pup_basCor  + (1| stimIAPS)+
                                                 # (1 | ssid),
                                                  (0 +arousal_c +pup_basCor | ssid),
                                                REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    pupil_outlier == FALSE & ssid_num<500 & 
                                      arousal_outler == FALSE))
summary(pupil_arousal_findings$valence_from_pup)
anova(pupil_arousal_findings$valence_from_pup)

# so it's not the case that pupil is tracking valence
# it's the case that arousal pupil relation is modulated by valence, and this is true regardless of whether we use a maximal or minimal model

interactions::interact_plot(pupil_arousal_findings$valence_from_pup , pred = valence_c, modx = pup_basCor)

interactions::interact_plot(pupil_arousal_findings$valence_from_pup, pred =pup_basCor , modx =  arousal_c)

```

### 2021-07-22 Paper_Analyses_subj_obje_arousal.Rmd
Timecourse pupil
line 392
- added the timecourse model for pupil.

Todo - solve the warnings and converegence errors and make one plot with all effects. also imclue velocity

@@
                                                     Mean_gray_z  +
-                                                    (1 + Mean_gray_z | ssid),
-                                                    # (0+ valence_c* arousal_c | ssid),
+                                                    (1 + Mean_gray_z | ssid)+
+                                                    (0+ valence_c* arousal_c | ssid),
                                                   REML = FALSE,
@@
 
+# relgrad <- with(pupil_arousal_findings$pupil_from_ar_vale@optinfo$derivs,solve(Hessian,gradient))
+# max(abs(relgrad))0.0002044252
+
 summary(pupil_arousal_findings$pupil_from_ar_vale)
@@
 
-car::vif(pupil_arousal_findings$pupil_from_ar_vale) #curoff 4
+# car::vif(pupil_arousal_findings$pupil_from_ar_vale) #curoff 4
 
@@
 
+# export model table
+library(MuMIn)
+library(sjmisc)
+sjPlot::tab_model(pupil_arousal_findings$pupil_from_ar_vale)
+
 ```
+
+Linear mixed model fit by maximum likelihood . t-tests use Satterthwaite's method ['lmerModLmerTest']
+Formula: pup_basCor ~ (valence_c * arousal_c) + Mean_gray_z + (1 + Mean_gray_z |  
+    ssid) + (0 + valence_c * arousal_c | ssid)
+   Data: subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier ==      FALSE & ssid_num < 500 & arousal_outler == FALSE)
+
+     AIC      BIC   logLik deviance df.resid 
+  8493.9   8579.2  -4231.9   8463.9     2170
+
+Scaled residuals: 
+    Min      1Q  Median      3Q     Max 
+-3.6141 -0.5987  0.0067  0.5952  3.6796
+
+Random effects:
+ Groups   Name                Variance Std.Dev. Corr       
+ ssid     (Intercept)         0.78415  0.8855              
+          Mean_gray_z         0.13611  0.3689   0.55       
+ ssid.1   valence_c           0.04233  0.2057              
+          arousal_c           0.02296  0.1515    0.89      
+          valence_c:arousal_c 0.01700  0.1304   -0.19  0.01
+ Residual                     2.57999  1.6062              
+Number of obs: 2185, groups:  ssid, 43
+
+Fixed effects:
+                    Estimate Std. Error       df t value             Pr(>|t|)    
+(Intercept)         -0.66764    0.14166 44.77819  -4.713          0.000023962 ***
+valence_c            0.08546    0.06557 28.33677   1.303              0.20294    
+arousal_c            0.44137    0.06445 22.53213   6.848          0.000000619 ***
+Mean_gray_z         -0.96311    0.06622 43.35750 -14.544 < 0.0000000000000002 ***
+valence_c:arousal_c  0.15461    0.04434 24.37046   3.487              0.00187 ** 
+---
+Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+Correlation of Fixed Effects:
+            (Intr) vlnc_c arsl_c Mn_gr_
+valence_c   -0.042                     
+arousal_c   -0.031  0.746              
+Mean_gray_z  0.453 -0.013  0.028       
+vlnc_c:rsl_  0.147 -0.267 -0.128  0.035
 
@@
 ```
+
+Timecourse analyses
+
+# prepare timecourse data
+```{r prepare timecourse data}
+rm(justone_test, lucy_plots, test)
+
+# import the timecourse
+
+tmp.df4_full_stim_downs_jun2021 <- readRDS("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/tmp.df4_full_stim_downs_jun2021.rds")
+
+# merge with behavioral data
+unique(db_full4new_stim_screen_pupil_nopract$ssid)
+# colnames(db_full4new_stim_screen_pupil_nopract)
+# colnames(tmp.df4_full_stim_downs_jun2021)
+# db_full4new_stim
+# colnames(db_full4new_stim_screen_pupil_nopract)
+db_full4new_stim_subset<- db_full4new_stim_screen_pupil_nopract[,c(1:4,6:7,12:13,16,21:27, 31:56,80:81,84:96,98:114,116:124)]
+
+# match types of merging variables
+tmp.df4_full_stim_downs_jun2021_with_beh2$ssid<- as.character(tmp.df4_full_stim_downs_jun2021_with_beh2$ssid)
+db_full4new_stim_subset$ssid<- as.character(db_full4new_stim_subset$ssid)
+
+# tNo
+tmp.df4_full_stim_downs_jun2021_with_beh2$tNo <- as.character(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)
+db_full4new_stim_subset$tNo <- as.character(db_full4new_stim_subset$tNo)
+unique(db_full4new_stim_subset$tNo)
+unique(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)
+
+# merge
+nrow(tmp.df4_full_stim_downs_jun2021_with_beh2)
+# 87529
+
+table(is.na(db_full4new_stim_subset$mediansplit_self_valence))
+
+tmp.df4_full_stim_downs_jun2021_with_beh2$tNo<- as.numeric(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)
+tmp.df4_full_stim_downs_jun2021_with_beh2<- tmp.df4_full_stim_downs_jun2021_with_beh2%>%
+  arrange(ssid,tNo, timerezero3)
+
+tmp.df4_full_stim_downs_jun2021_with_beh<- left_join(tmp.df4_full_stim_downs_jun2021_with_beh2, db_full4new_stim_subset)
+
+db_full4new_stim_subset$tNo<- as.numeric(db_full4new_stim_subset$tNo)
+
+table(is.na(db_full4new_stim_subset$arousal))
+
+tmp.df4_full_stim_downs_jun2021_with_behnew<- right_join(tmp.df4_full_stim_downs_jun2021_with_beh2, db_full4new_stim_subset,
+                                                     by = c('ssid', 'tNo'))
+
+nrow(tmp.df4_full_stim_downs_jun2021_with_beh)
+# 172168 good
+
+nrow(tmp.df4_full_stim_downs_jun2021_with_beh2)
+# 87529
+nrow(tmp.df4_full_stim_downs_jun2021_with_behnew)
+
+table(is.na(tmp.df4_full_stim_downs_jun2021_with_behnew$mediansplit_self_valence))
+
+```
+
+Quick check that things make sense
+```{r}
+tmp.df4_full_stim_downs_jun2021_with_beh %>%
+  subset(!is.na(ground_arousal_lab))%>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  stat_smooth(aes(group= ground_arousal_lab, color = ground_arousal_lab), fun = mean,geom = "line",
+               se = F, alpha = .1, size = 1.5)+
+  stat_smooth(aes(group=ground_arousal_lab, color = ground_arousal_lab), size = 3)+  
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")+
+  xlim(0,6)+
+   facet_grid(~mediansplit_self_valence)
+
+# group_by(stimIAPS)%>%
+tmp.df4_full_stim_downs_jun2021_with_beh<- tmp.df4_full_stim_downs_jun2021_with_beh %>%
+  ungroup()%>%
+  mutate(mediansplit_sample_valence2 = 
+           if_else(ValenceMeanThisSample >= 
+                     median(ValenceMeanThisSample,
+                            na.rm = TRUE), 
+                   "More positive", "More negative"))%>%
+  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >=
+                                                  median(ArousalMeanThisSample,
+                                                         na.rm = TRUE), "High", "Low"))
+
+```
+
+let's test the interaction term
+```{r}
+nrow(nbins)
+nbins = 30 # number of bins
+
+# create and empty dataframe for the timecourse analyses
+timecourse_result_df_int <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
+                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))
+
+# View(timecourse_result_df)
+nbins<- nbins[1:28]
+
+i = 0 # remember to always rezero it
+# b = 10
+
+rm(i,b)
+
+nbins<- unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)
+
+for (b in 1:length(nbins)) {
+  # for (s in 1:length(nsim)) {
+
+    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
+        lmer_bin_pup  <- lmer(pup_basCor ~ arousal_c* valence+Mean_gray_z  +
+                                (1 | ssid)+
+                                (0 +arousal_c* valence | ssid),
+                                # (1|stimIAPS),
+                              REML = FALSE,
+                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
+                                    # mediansplit_self_valence == "More positive" & 
+                                    timebin_no == nbins[b]))
+
+        #store results from the simulation
+            lmer_bin_pup_summary<- summary(lmer_bin_pup)
+            lmer_bin_pup_summary
+            # lmer_bin_pup_summary[["coefficients"]][3,1]
+            timecourse_result_df_int[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
+            timecourse_result_df_int[i,2]<- lmer_bin_pup_summary[["coefficients"]][5,1] # first number is term(row), second is column
+            timecourse_result_df_int[i,3]<-lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
+            timecourse_result_df_int[i,4]<-lmer_bin_pup_summary[["coefficients"]][5,5] # p value
+            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
+            timecourse_result_df_int[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
+                                                   != 0,
+                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')
+
+     i = i+1
+}
+
+# timecourse_result_df_pos<- timecourse_result_df
+
+timecourse_result_df_int %>%
+  ggplot(aes(timebins, t))+
+  geom_line(size = 2)+
+  geom_line(aes(y = p), linetype = "dashed", size = 2)+
+  geom_hline(yintercept = .05, color = 'red', size = 1.5)
+
+```

### 2021-07-22 Paper_Analyses_subj_obje_arousal.Rmd
smooth pupil velocity
to do smooth pupil velocity

@@
 ```
+
+Velocity test
+
+```{r}
+nrow(nbins)
+nbins = 30 # number of bins
+unique(tmp.df4_full_stim_downs_jun2021_with_behnew$ssid)
+tmp.df4_full_stim_downs_jun2021_with_behnew <- tmp.df4_full_stim_downs_jun2021_with_behnew%>%
+  group_by(ssid, tNo)%>%
+  arrange(ssid,tNo, timerezero3)%>%
+  mutate(pup_vel_smooth = zoo::rollmean(pup_velocity, k = 3, fill = NA))
+
+zoo::rollmean(pup_velocity, k = 3, fill = NA)
+
+tmp.df4_full_stim_downs_jun2021_with_behnew$pup_vel_smooth
+
+# create and empty dataframe for the timecourse analyses
+timecourse_result_df_int_vel <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
+                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))
+
+# View(timecourse_result_df)
+nbins<- nbins[1:28]
+
+i = 0 # remember to always rezero it
+# b = 10
+
+rm(b)
+
+nbins<- unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)
+
+for (b in 3:length(nbins)) {
+  # for (s in 1:length(nsim)) {
+
+    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
+        lmer_bin_pup  <- lmer(pup_vel_smooth ~ arousal_c* valence+Mean_gray_z  +
+                                (1 | ssid)+
+                                (0 +arousal_c* valence | ssid),
+                                # (1|stimIAPS),
+                              REML = FALSE,
+                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
+                                    # mediansplit_self_valence == "More positive" & 
+                                    timebin_no == nbins[b]))
+
+        #store results from the simulation
+            lmer_bin_pup_summary<- summary(lmer_bin_pup)
+            lmer_bin_pup_summary
+            # lmer_bin_pup_summary[["coefficients"]][3,1]
+            timecourse_result_df_int_vel[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
+            timecourse_result_df_int_vel[i,2]<- lmer_bin_pup_summary[["coefficients"]][2,1] # first number is term(row), second is column
+            timecourse_result_df_int_vel[i,3]<-lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
+            timecourse_result_df_int_vel[i,4]<-lmer_bin_pup_summary[["coefficients"]][2,5] # p value
+            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
+            timecourse_result_df_int_vel[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
+                                                   != 0,
+                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')
+
+     i = i+1
+}
+
+# timecourse_result_df_pos<- timecourse_result_df
+
+timecourse_result_df_int_vel %>%
+  ggplot(aes(timebins, t))+
+  geom_line(size = 2)+
+  geom_line(aes(y = p), linetype = "dashed", size = 2)+
+  geom_hline(yintercept = .05, color = 'red', size = 1.5)+
+  geom_vline(xintercept = 1, color = 'red')
+  # ylim(-4,4)
+
+??ma
+?stats::filter
+tmp.df4_full_stim_downs_jun2021_with_behnew%>%
+  subset(ssid == 310 & tNo == 10)%>%
+  ggplot(aes(timerezero3,zoo::rollmean(pup_velocity, k = 3, fill = NA)))+
+  geom_line()+
+  geom_line(aes(y = pup_velocity), color = 'red')+
+  geom_smooth(se = F)
+
+tmp.df4_full_stim_downs_jun2021_with_behnew%>%
+  subset(ssid == 310 & tNo == 15)%>%
+  ggplot(aes(timerezero3,pup_basCor))+
+  geom_point()+
+  # geom_line(aes(y = pup_velocity), color = 'red')+
+  geom_smooth(se = F)
+
+```

### 2021-07-23 Old scripts/pupil_arousal_datarmd.Rmd
started working on issue #1

---
title: "R Notebook"
output: html_notebook
---

Downsample data to save space

pupiltimecourse.data is dowsnampled but doesn't have all participants < 400

but the script pupiltimecourseexp2.Rmd has what we need to do the same dowsnampling

Goal
- take pupil timecourse, dowsnample and then mrge it it behavioural data so that we can do the additional arousal pupil analyses that check for timecourse things.

check gazeR or downsampling

to do, do the same arousal correlation with valence
```{r}
library(ggplot2)
library(tidyverse)
install.packages("gazer")
library(gazer)

?gazer::downsample_gaze
?gazer::downsample_pupil

unique(X_tmp_df4_full$Condition)
# gazer::downsample_gaze%

tmp.df4_full_stim<- X_tmp_df4_full %>%
  subset(screencontent == "stim")

# create bins
# install.packages("OneR")
install.packages("OneR")
library(OneR)

?bin

tmp.df4_full_stim$timebin<- OneR::bin(tmp.df4_full_stim$timerezero3, nbin = 60)

# dowsample by averaging?
colnames(tmp.df4_full_stim)
tmp.df4_full_stim_downs <- tmp.df4_full_stim %>%
  group_by(ssid, tNo, timebin, trial,trialUnq)%>%
  summarise_at(c('timerezero3','pup_basCor', 'gaze_x_cor_pix', 'gaze_y_cor_pix'), 
               mean, na.rm = TRUE)

?saveRDS
saveRDS(tmp.df4_full_stim_downs, "tmp.df4_full_stim_downs.rds")

# create klarger bins
tmp.df4_full_stim_downs_jun2021_with_beh

range(tmp.df4_full_stim_downs$timerezero3)

tmp.df4_full_stim_downs_jun2021_with_beh$timebin2<- OneR::bin(tmp.df4_full_stim_downs_jun2021_with_beh$timerezero3, nbin = 30)

tmp.df4_full_stim_downs_jun2021_with_beh2 <- tmp.df4_full_stim_downs_jun2021_with_beh %>%
  group_by(ssid, tNo, timebin2, trial,trialUnq)%>%
  summarise_at(c('timerezero3','pup_basCor', 'gaze_x_cor_pix', 'gaze_y_cor_pix'), 
               mean, na.rm = TRUE)

nrow(tmp.df4_full_stim_downs_jun2021_with_beh2)
87529
```

pupil arousal

```{r}
library(gghalves)

# pupil tracks arousal

db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, ground_arousal_lab, Alexithymia, mediansplit_ground_valence)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_arousal_lab, pup_basCor, color = ground_arousal_lab,fill = ground_arousal_lab))+
    geom_hline(yintercept = 0, linetype = "dashed", size = 2, alpha = .2)+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
  p$graphstyle+
  xlab("Arousal")+
  ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")
  facet_grid(~mediansplit_ground_valence)
  # facet_grid(~BRIGHTNESS_mediansplit)+
  ylim(-6,2.3)

  db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, mediansplit_self_arousal, Alexithymia, mediansplit_self_valence)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_self_arousal, pup_basCor, color = mediansplit_self_arousal,fill = mediansplit_self_arousal))+
    geom_hline(yintercept = 0, linetype = "dashed", size = 2, alpha = .2)+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
  p$graphstyle+
  # xlab("Arousal")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_self_valence)
  # facet_grid(~BRIGHTNESS_mediansplit)+
  ylim(-6,2.3)

mediansplit_self_arousal_thissample

  db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, mediansplit_self_arousal_thissample, Alexithymia, mediansplit_self_valence_thissample)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_self_arousal_thissample, pup_basCor, color = mediansplit_self_arousal_thissample,fill = mediansplit_self_arousal_thissample))+
    geom_hline(yintercept = 0, linetype = "dashed", size = 2, alpha = .2)+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
  p$graphstyle+
  # xlab("Arousal")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_self_valence_thissample)
  # facet_grid(~BRIGHTNESS_mediansplit)+
  ylim(-6,2.3)

  db_full4new_stim_screen_pupil_nopract%>%

     ggplot(aes( valence,arousal))+
    geom_point()+
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 1)+
    facet_grid(~mediansplit_self_arousal)
    # geom_smooth(aes(x = arousal^2, y = valence))
   db_full4new_stim_screen_pupil_nopract%>%

    ggplot(aes( valence,arousal))+
    geom_point()+
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 1)+
    facet_grid(~mediansplit_self_valence)

   unique(db_full4new_stim_screen_pupil_nopract$ssid)
```

```{r}
# mediansplit_self_valence is duoliating the stimuli based ion peopl who choose negative and positive
unique(db_full4new_stim_screen_pupil_nopract)
db_full4new_stim_screen_pupil_nopract <- db_full4new_stim_screen_pupil_nopract%>%
  ungroup()%>%
  # group_by(stimIAPS)%>%
  mutate(mediansplit_sample_valence2 = if_else(ValenceMeanThisSample >=
                                                  median(ValenceMeanThisSample,
                                                         na.rm = TRUE), "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >=
                                                  median(ArousalMeanThisSample,
                                                         na.rm = TRUE), "High", "Low"))

  group_by(mediansplit_sample_valence2, stimIAPS,stimDescription)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

```

brightness

```{r}
tmp.df4_full_stim_downs_jun2021_with_behnew%>%
  group_by(stimIAPS)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ValenceMean, Mean_gray_z))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

tmp.df4_full_stim_downs_jun2021_with_behnew%>%
  group_by(stimIAPS)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ArousalMean, Mean_gray_z))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

tmp.df4_full_stim_downs_jun2021_with_behnew %>%
  group_by(stimIAPS,ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_lab, Mean_gray_z))+
  geom_point()+
  stat_summary(geom = 'pointrange')
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

  tmp.df4_full_stim_downs_jun2021_with_behnew %>%
  group_by(stimIAPS,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_valence, Mean_gray_z))+
  # geom_point()+
  stat_summary(geom = 'pointrange')
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

    tmp.df4_full_stim_downs_jun2021_with_behnew %>%
  group_by(stimIAPS,ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(Mean_gray_z, color = ground_valence_lab))+
      # geom_histogram()+
      geom_density()
  # geom_point()+
  stat_summary(aes(group = mediansplit_ground_valence),geom = 'line')
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

  #

tmp.df4_full_stim_downs_jun2021_with_behnew %>%
  group_by(stimIAPS,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_valence, ArousalMean))+
      # geom_histog `vram()
      # geom_density()
  # geom_point()+
  stat_summary(geom = 'pointrange')
  # geom_smooth(method = 'lm', se = F)+
  # ggpubr::stat_cor()

      ground_valence_lab
```

Participants section

```{r}
participants_demog <- db_full4new_stim_screen_pupil_nopract %>%
    # subset(pp_arousal_outler== FALSE)%>%
  subset(Group == "NT")%>%
  group_by(ssid, Gender)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

unique(participants_demog)

# gender
table(participants_demog$Gender)

colnames(participants_demog)
psych::describe(participants_demog[c("Age")])

summary(participants_demog$Age)

sd(participants_demog$Age, na.rm = TRUE)

table(is.na(participants_demog$Age))

participants_demog %>%
  group_by(Gender)%>%
  mutate(genderspecif_age = sd(TAS))%>%
  ungroup()%>%
  mutate(nongenderspecif_age = sd(TAS))%>%
  group_by(Gender)%>%
  summarise_at(c("genderspecif_age","nongenderspecif_age"), mean, na.rm = TRUE)

(10.557140+8.042743)/2

8.042743

9.299941

```

```{r}
  db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(Group == "NT")%>%
  # subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, mediansplit_ground_arousal, Alexithymia, mediansplit_ground_valence)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_arousal, pup_basCor, color = mediansplit_ground_arousal,fill = mediansplit_ground_arousal))+
    geom_hline(yintercept = 0, linetype = "dashed", size = 2, alpha = .2)+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
  p$graphstyle+
  # xlab("Arousal")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_ground_valence)
  # facet_grid(~BRIGHTNESS_mediansplit)+
  ylim(-6,2.3)
```

```{r}

    db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, mediansplit_ground_arousal, Alexithymia, mediansplit_ground_valence)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_arousal, Mean, color = mediansplit_ground_arousal,fill = mediansplit_ground_arousal))+
    geom_hline(yintercept = 0, linetype = "dashed", size = 2, alpha = .2)+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
  p$graphstyle+
  # xlab("Arousal")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_ground_valence)+
  # facet_grid(~BRIGHTNESS_mediansplit)+
  ylim(90,130)

```

  okay let's create averages frio this entire sample and use those to devide the stimuli

  self aropusal might be biased by problematic folks but averages for the entire sample should not

```{r}

db_full4new_stim_screen_pupil_nopract %>%
  group_by(stimIAPS)%>%
  mutate()

  db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(ssid_num< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, self_arousal_lab, mediansplit_self_valence)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(self_arousal_lab, pup_basCor, color = self_arousal_lab,fill = self_arousal_lab))+
    geom_hline(yintercept = 0, linetype = "dashed", size = 2, alpha = .2)+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
  p$graphstyle+
  # xlab("Arousal")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_self_valence)

sample_iaps_arousal<-  db_full4new_stim_screen_pupil_nopract %>%

    group_by(stimIAPS)%>%
    subset(ssid_num< 500)%>%
    summarise_at(c('ArousalMeanThisSample','ArousalMean'), mean, na.rm = TRUE)%>%
    ggplot(aes(ArousalMeanThisSample, ArousalMean))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    ggpubr::stat_cor()+
    theme_classic()

  sample_iaps_val<-   db_full4new_stim_screen_pupil_nopract %>%

     group_by(stimIAPS)%>%
    subset(ssid_num< 500)%>%
    summarise_at(c('ValenceMeanThisSample','ValenceMean'), mean, na.rm = TRUE)%>%
    ggplot(aes(ValenceMeanThisSample, ValenceMean))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    ggpubr::stat_cor()+
      theme_classic()

library(patchwork)
sample_iaps_arousal+
sample_iaps_val
```

```{r} 
  db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(ssid_num< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, self_arousal_lab, Alexithymia, mediansplit_self_valence)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(self_arousal_lab, pup_basCor, color = self_arousal_lab,fill = self_arousal_lab))+
    geom_hline(yintercept = 0, linetype = "dashed", size = 2, alpha = .2)+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
  p$graphstyle+
  xlab("Arousal")+
  ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_self_valence)
  # facet_grid(~BRIGHTNESS_mediansplit)+
  ylim(-6,2.3)

db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(ssid_num< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, ground_arousal_lab, Alexithymia, mediansplit_ground_valence)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_arousal_lab, pup_basCor, color = ground_arousal_lab,fill = ground_arousal_lab))+
    geom_hline(yintercept = 0, linetype = "dashed", size = 2, alpha = .2)+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
  p$graphstyle+
  xlab("Arousal")+
  ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")
  facet_grid(~mediansplit_ground_valence)
  # facet_grid(~BRIGHTNESS_mediansplit)+
  ylim(-6,2.3)

```

Resposne bias
```{r}
library(ggExtra)
arous_pup_by_val<- db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  group_by(ssid, stimIAPS, mediansplit_self_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_c, pup_basCor))+
      geom_point(alpha = .2)+
    # stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Arousal")+
  ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_self_valence)
  # ggpubr::stat_cor()
  ylim(-3.3,1.3)

  arous_pup_by_val<- arous_pup_by_val+ggside::geom_xsidedensity(aes(y=stat(density),fill = mediansplit_self_valence), alpha = .4)

  arous_pup_by_val+ggside::geom_ysidedensity(aes(x=stat(density),fill = mediansplit_self_valence), alpha = .4)

ggMarginal(arous_pup_by_val, type = "density")
```

ceiliing effect?

```{r}
db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  group_by(ssid, stimIAPS, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_c, pup_basCor))+
      geom_point()+
    # stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Arousal")+
  ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()+
  ylim(-3.3,1.3)

```

ceiling effect?
```{r}
db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  group_by(mediansplit_ground_valence)%>%
  mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  group_by(mediansplit_ground_valence)%>%
  mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, pup_basCor))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary( geom = 'pointrange', alpha = .4, size = 1, colour = "Black") +
  stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  # facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()
  ylim(-3.3,1.3)

```

```{r}  
  db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  group_by(mediansplit_ground_valence)%>%
  mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  group_by(mediansplit_ground_valence)%>%
  mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, pup_basCor))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary( geom = 'pointrange', alpha = .4, size = 1, colour = "Black") +
  stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  # facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()
  ylim(-3.3,1.3)

  db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_self_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_self_valence, pup_basCor))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary( geom = 'pointrange', alpha = .5, size = 1, colour = "Black") +
  stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  # facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()
  ylim(-3.3,1.3)

```

```{r}

# db_full4new_stim_screen_pupil_nopract$arousal_outler
  db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  group_by(ssid, mediansplit_sample_arousal2, mediansplit_sample_valence2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_sample_arousal2, arousal))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary( geom = 'pointrange', alpha = .5, size = 1, colour = "Black") +
  stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_sample_valence2)+
  ggpubr::stat_cor()

# stim
  db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  group_by(stimIAPS, mediansplit_self_valence, mediansplit_self_arousal)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_self_arousal, arousal))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary( geom = 'pointrange', alpha = .5, size = 1, colour = "Black") +
  # stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_self_valence)+
  ggpubr::stat_cor()

  # ground

  # stim

  db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  group_by(stimIAPS, mediansplit_ground_arousal, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_arousal, ArousalMean))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary( geom = 'pointrange', alpha = .5, size = 1, colour = "Black") +
  # stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()

```

otehr confounds - eye movements

```{r}
db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, mean_fix_dur))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  # facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()
  ylim(-3.3,1.3)

   unique(db_full4new_stim_screen_pupil_nopract$ValenceMeanThisSample)

   median(db_full4new_stim_screen_pupil_nopract$ValenceMeanThisSample)
    median(db_full4new_stim_screen_pupil_nopract$valence)

     median(db_full4new_stim_screen_pupil_nopract$arousal)
    median(db_full4new_stim_screen_pupil_nopract$ArousalMeanThisSample)

  db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_self_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_self_valence, mean_fix_dur))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  # facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()
  ylim(-3.3,1.3)

```

```{r}
  # data loss gaze

  db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, fix_count))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  # facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()
  ylim(-3.3,1.3)

  db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, SacAmp))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  # facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()
  ylim(-3.3,1.3)

  db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, sdevgaze))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  # facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()
  ylim(-3.3,1.3)

 db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, gaze_loss_prop))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  # facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()
  ylim(-3.3,1.3)

  db_full4new_stim_screen_pupil_nopract%>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, total_fix_dur))+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_smooth(method = 'lm', se = F)+
  p$graphstyle+
  xlab("Valence")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  # facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()

```

# let's model it formally

# remember baseline corection is equivalendt to stimuli intercept

```{r} 
pupil_arousal_findings<- list()
library(lmerTest)

unique(db_full4new_stim_screen_pupil_nopract$stimIAPS)
unique(substr(db_full4new_stim_screen_pupil_nopract$stimIAPS, 1,8))
db_full4new_stim_screen_pupil_nopract$Label<- substr(db_full4new_stim_screen_pupil_nopract$stimIAPS, 1,8)

db_full4new_stim_screen_pupil_nopract<- left_join(db_full4new_stim_screen_pupil_nopract, imageJ_IAPS, by = "Label")
nrow(db_full4new_stim_screen_pupil_nopract)
# rows = 2858

db_full4new_stim_screen_pupil_nopract$Mean_gray_z<- scale(db_full4new_stim_screen_pupil_nopract$Mean, center = TRUE, scale = TRUE)[,1]

options(contrasts = c("contr.sum","contr.poly"))
options(scipen = 999)

db_full4new_stim_screen_pupil_nopract$ssid_num <- as.numeric(as.character(db_full4new_stim_screen_pupil_nopract$ssid))

pupil_arousal_findings$pupil_from_arousal <- lmer(pup_basCor ~ arousal_c*Mean_gray_z  +(1 +Mean_gray_z | ssid) + (0+arousal_c| ssid), REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier == FALSE & ssid_num< 500 & 
                                      arousal_outler == FALSE))

summary(pupil_arousal_findings$pupil_from_arousal)
# singularity (drop arousal c slope)

# is there a coorelationbtween mean arousal rating and meagray(

db_full4new_stim_screen_pupil_nopract%>%
  group_by(stimIAPS,ground_valence_lab) %>%
  summarise_at(c('arousal_c', 'Mean_gray_z'), mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_c, Mean_gray_z, color = ground_valence_lab))+
  geom_point()+
  ggpubr::stat_cor()

# <- predict(pupil_arousal_findings$pupil_from_arousal)
db_full4new_stim_screen_pupil_nopract %>%
  group_by(stimIAPS) %>%
  # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # summarise_at(c('arousal_c', 'Mean_gray_z'), mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_c, pup))+
  geom_smooth(aes(group = ssid, alpha = ssid), method = 'lm', se = F)
# geom_smooth(aes(group = stimIAPS), method = 'lm', se = F)
  ggpubr::stat_cor()

```
cor.test(db_full4new_stim_screen_pupil_nopract$, db_full4new_stim_screen_pupil_nopract$)

```{r}
# if we put brighteness and arousal we see no interaction which means we probably don't need to worry about brighteness, it doesn't change effects of arousal self report
# db_full4new_stim_pupil$pup
pupil_arousal_findings$pupil_from_arousal <- lmer(pup_basCor ~ arousal_c+Mean_gray_z  +(1 +Mean_gray_z | ssid), REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract$pup, pupil_outlier == FALSE & ssid_num< 500& 
                                      arousal_outler == FALSE))

install.packages('usdm')

usdm::vif(as.data.frame(db_full4new_stim_screen_pupil_nopract[,c('arousal', 'valence')]))

pupil_arousal_findings$pupil_from_arousal_withval <- lmer(pup_basCor ~ arousal_c*valence_c* Mean_gray_z  +(1 +Mean_gray_z | ssid), REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier == FALSE & ssid_num< 500& 
                                      arousal_outler == FALSE))

summary(pupil_arousal_findings$pupil_from_arousal_withval)
car::vif(pupil_arousal_findings$pupil_from_arousal_withval)

lmerTest::step(pupil_arousal_findings$pupil_from_arousal_withval)

# control for baseline arousal ratings

pupil_arousal_findings$pupil_from_arousal_withval

summary(lmer(pup_basCor ~ arousal_c*valence_c+ Mean_gray_z  +(1 | ssid) + (1|stimIAPS),
               # (1|ArousalMean)+ (1|ArousalMean), REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier == FALSE & Group == "NT"  & 
                                      arousal_outler == FALSE)))

# arousal_c:valence_c                      0  35.52   35.52     1 2150.19  13.5760 0.0002348 ***

pupil_arousal_findings$arousal_from_pupil <- lmer(arousal ~ pup_basCor * Mean_gray_z  +(1+pup_basCor  | ssid), REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier == FALSE & ssid!= 610& 
                                      arousal_outler == FALSE))

summary(pupil_arousal_findings$arousal_from_pupil)
# what about valence

pupil_arousal_findings$pupil_from_valence <- lmer(pup_basCor ~ valence_c+Mean_gray_z  +(1 +Mean_gray_z | ssid) + 
                                                    (0 +valence_c | ssid), REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier == FALSE & ssid!= 610& 
                                      arousal_outler == FALSE))

summary(pupil_arousal_findings$pupil_from_arousal)
summary(pupil_arousal_findings$pupil_from_valence)

```

# Valence and arousal
```{r}

pupil_arousal_findings$pupil_from_ar_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) + Mean_gray_z  +
                                                    (1 + Mean_gray_z | ssid),
                                                    # (0+ valence_c* arousal_c | ssid),
                                                  REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier == FALSE & ssid_num< 500 & 
                                      arousal_outler == FALSE))

db_full4new_stim_screen_pupil_nopract$total_fix_dur_z<- scale(db_full4new_stim_screen_pupil_nopract$total_fix_dur, center = TRUE, scale = TRUE)[,1]

pupil_arousal_findings$pupil_from_ar_val_gaze <- lmer(pup_basCor ~ (valence_c * arousal_c * total_fix_dur_z)+ Mean_gray_z  +
                                                        +
                                                    (1 + Mean_gray_z | ssid),
                                                    # (0+  total_fix_dur_z | ssid),
                                                  REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier == FALSE & ssid_num< 500 & 
                                      arousal_outler == FALSE))

summary(pupil_arousal_findings$pupil_from_ar_val_gaze )
summary(pupil_arousal_findings$pupil_from_ar_vale)

car::vif(pupil_arousal_findings$pupil_from_ar_val_gaze)

anova(pupil_arousal_findings$pupil_from_ar_vale, pupil_arousal_findings$pupil_from_arousal)
# interaction valence and arousal

```

control for gaze

```{r}
# avg fix dur
db_full4new_stim_screen_pupil_nopract$mean_fix_dur_z<- scale(db_full4new_stim_screen_pupil_nopract$mean_fix_dur, center = TRUE, scale = TRUE)[,1]

pupil_arousal_findings$pupil_from_ar_val_gaze <- lmer(pup_basCor ~ (valence_c * arousal_c * mean_fix_dur_z)+ Mean_gray_z  +
                                                        +
                                                    (1 + Mean_gray_z | ssid),
                                                    # (0+  total_fix_dur_z | ssid),
                                                  REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier == FALSE & ssid_num< 500 & 
                                      arousal_outler == FALSE))

summary(pupil_arousal_findings$pupil_from_ar_val_gaze )
interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_val_gaze , pred = arousal_c, modx = mean_fix_dur_z)

# fix count

db_full4new_stim_screen_pupil_nopract$fix_count_z<- scale(db_full4new_stim_screen_pupil_nopract$fix_count, center = TRUE, scale = TRUE)[,1]

pupil_arousal_findings$pupil_from_ar_val_gaze <- lmer(pup_basCor ~ (valence_c * arousal_c * fix_count_z)+ Mean_gray_z  +
                                                        +
                                                    (1 + Mean_gray_z | ssid),
                                                    # (0+  total_fix_dur_z | ssid),
                                                  REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier == FALSE & ssid_num< 500 & 
                                      arousal_outler == FALSE))

summary(pupil_arousal_findings$pupil_from_ar_val_gaze )

interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_val_gaze , pred = arousal_c, modx = mean_fix_dur_z)
```

```{r}
interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale , pred = valence_c, modx = arousal_c)

interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale , pred =arousal_c , modx =  valence_c)

car::vif(pupil_arousal_findings$pupil_from_ar_vale) #curoff 2.5?

cor.test(db_full4new_stim_screen_pupil_nopract$valence_c, db_full4new_stim_screen_pupil_nopract$arousal_c)

rmcorr_valence_arousal <- rmcorr::rmcorr(participant = "ssid", measure1 = "valence_c", measure2 = "arousal_c", data = db_full4new_stim_screen_pupil_nopract)

plot(rmcorr_valence_arousal)

?rmcorr

db_full4new_stim_screen_pupil_nopract %>%
  group_by(stimIAPS)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ArousalMean, ValenceMean))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  theme_classic()

db_full4new_stim_screen_pupil_nopract %>%
  group_by(stimIAPS)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_c, valence_c))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  theme_classic()

```

```{r}
# with arousal as DV
pupil_arousal_findings$aroual_from_pup <- lmer(arousal ~ valence_c*pup_basCor *  BRIGHTNESSc  + (1| stimIAPS)+
                                                 (1 | ssid)+(0 +valence_c | ssid), REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier == FALSE & ssid!= 610& 
                                      arousal_outler == FALSE))
summary(pupil_arousal_findings$aroual_from_pup)

anova(pupil_arousal_findings$aroual_from_pup)

interactions::interact_plot(pupil_arousal_findings$aroual_from_pup , pred = valence_c, modx = pup_basCor)

interactions::interact_plot(pupil_arousal_findings$aroual_from_pup, pred =pup_basCor , modx =  valence_c)
# for positive valenced stimuli participants reporte higher arousal to more dilated pupils
#for negatively valence they report feeling negative even when they don't show strog pupil dilation
# same pattern
# pupil is more alighned with objective arousal in the positive trials

```

mixed model is consistent wth the previous plot, arousal effects on pupil is modulated by valence. in other words there is a consistent effect between pupil and self-repot of arousal more for positive emotions.

analyse the correlationla way
since we are aggregating we don't need to worry too much about brighteness as every person sees every stimuli in all brightness levels
CONCORDANCE

```{r}

db_full4new_stim_screen_pupil_nopract%>%
  group_by(mediansplit_self_valence_thissample, stimIAPS)%>%
  summarise_at(c("arousal", 'valence'), mean, na.rm = TRUE)%>%
  arrange(stimIAPS)

```

````{r}

test_anovas<- db_full4new_stim_screen_pupil_nopract %>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_sample_valence2,mediansplit_sample_arousal2)%>%
    mutate(cortest = cor(arousal_c, pup_basCor, use = "complete"))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)

 db_full4new_stim_screen_pupil_nopract %>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_sample_valence2,mediansplit_sample_arousal2)%>%
    mutate(cortest = cor(arousal_c, pup_basCor, use = "complete"))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_sample_valence2, cortest, color = mediansplit_sample_valence2))+
           geom_bar(stat="summary", fun.y = "mean", alpha = .4)+

    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange')+
          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
    ylab("R pupil vs self report arousal")+
  theme_classic()+
  geom_hline(yintercept = .2, linetype = 'dashed', alpha = .2)+
   # ggpubr::stat_compare_means(paired = TRUE)+
  ggpubr::stat_compare_means()+
  facet_grid(~mediansplit_sample_arousal2)

  # let's identify the folks that show less of a difference between conditions.

flag_pos_neg<-  db_full4new_stim_screen_pupil_nopract %>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_sample_valence2)%>%
    mutate(cortest = cor.test(arousal_c, pup_basCor)$estimate)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
    mutate(cor_pos_neg_diff = cortest[mediansplit_sample_valence2 == "More positive"] -
             cortest[mediansplit_sample_valence2 == "More negative"])%>%
    mutate(cor_pos_neg_diff_lab = if_else(cor_pos_neg_diff>0, "pos > neg", "neg > pos"))%>%
     group_by(ssid,cor_pos_neg_diff_lab)%>%
    summarise_at(c("cor_pos_neg_diff"), mean, na.rm = TRUE)

    # subset(cor_pos_neg_diff<= 0)%>%
        ggplot(aes(mediansplit_sample_valence2, cortest, color = mediansplit_sample_valence2))+
           geom_bar(stat="summary", fun.y = "mean", alpha = .4)+

    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange')+
          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
    ylab("R pupil vs self report arousal")+
  theme_classic()+
  geom_hline(yintercept = .2, linetype = 'dashed', alpha = .2)
   # ggpubr::stat_compare_means(paired = TRUE)+
  ggpubr::stat_compare_means()

```

```{r}
testcor <-cor(db_full4new_stim_screen_pupil_nopract$arousal, db_full4new_stim_screen_pupil_nopract$valence)

testcor 
db_full4new_stim_screen_pupil_nopract %>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_sample_valence2, mediansplit_sample_arousal2)%>%
    # mutate(cortest = cor.test(arousal_c, pup_basCor)$estimate)%>%
   mutate(cortest = cor(arousal_c, pup_basCor, method = 'kendall'))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_sample_valence2, cortest, color = mediansplit_sample_valence2))+
           geom_bar(stat="summary", fun.y = "mean", alpha = .4)+

    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange')+
          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
    ylab("R pupil vs self report arousal")+
  theme_classic()+
   facet_grid(~mediansplit_sample_arousal2)+
  geom_hline(yintercept = .2, linetype = 'dashed', alpha = .2)
   # ggpubr::stat_compare_means(paired = TRUE)+
  # ggpubr::stat_compare_means()

db_full4new_stim_screen_pupil_nopract %>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_sample_arousal2, mediansplit_sample_valence2)%>%
    # mutate(cortest = cor.test(arousal_c, pup_basCor)$estimate)%>%
   mutate(cortest = cor(valence_c, pup_basCor, method = 'kendall'))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_sample_arousal2, cortest, color = mediansplit_sample_arousal2))+
           geom_bar(stat="summary", fun.y = "mean", alpha = .4)+

    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange')+
          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
    ylab("R pupil vs self report arousal")+
  theme_classic()+
   facet_grid(~mediansplit_sample_valence2)+
  geom_hline(yintercept = .2, linetype = 'dashed', alpha = .2)

```

# same as plot above but with valence in the correlation
```{r}
db_full4new_stim_screen_pupil_nopract %>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_sample_arousal2)%>%
    mutate(cortest = cor.test(valence_c, pup_basCor)$estimate)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_sample_arousal2, cortest, color = mediansplit_sample_arousal2))+
           geom_bar(stat="summary", fun.y = "mean", alpha = .4)+

    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange')+
          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
    ylab("R pupil vs self report arousal")+
  theme_classic()
   # ggpubr::stat_compare_means(paired = TRUE)+
  ggpubr::stat_compare_means()

```

```{r}
# ground

 db_full4new_stim_screen_pupil_nopract %>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_ground_valence)%>%
    mutate(cortest = cor.test(arousal_c, pup_basCor, use = "complete")$estimate)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_ground_valence, cortest, color = mediansplit_ground_valence))+
           geom_bar(stat="summary", fun.y = "mean", alpha = .4)+

    geom_jitter(width = .1, alpha = .3)+
        stat_summary( geom = 'pointrange')+
        stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
    ylab("R pupil vs self report arousal")+
   # ggpubr::stat_compare_means(paired = TRUE)+
  # ggpubr::stat_compare_means()
   theme_classic()
```

```{r}
 # ground arousal with valence in the  corelation

 db_full4new_stim_screen_pupil_nopract %>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_ground_valence)%>%
    mutate(cortest = cor.test(valence_c, pup_basCor, use = "complete")$estimate)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_ground_valence, cortest, color = mediansplit_ground_valence))+
           geom_bar(stat="summary", fun.y = "mean", alpha = .4)+

    geom_jitter(width = .1, alpha = .3)+
        stat_summary( geom = 'pointrange')+
        stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
    ylab("R pupil vs self report arousal")+
   # ggpubr::stat_compare_means(paired = TRUE)+
  # ggpubr::stat_compare_means()
   theme_classic()

 db_full4new_stim_screen_pupil_nopract %>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_ground_valence, mediansplit_ground_arousal)%>%
    mutate(cortest = cor.test(arousal_c, pup_basCor, use = "complete")$estimate)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_ground_valence, cortest, color = mediansplit_ground_valence))+
           geom_bar(stat="summary", fun.y = "mean", alpha = .4)+

    geom_jitter(width = .1, alpha = .3)+
        stat_summary( geom = 'pointrange')+
        stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
    ylab("R pupil vs self report arousal")+
   # ggpubr::stat_compare_means(paired = TRUE)+
  # ggpubr::stat_compare_means()
   theme_classic()+
   facet_grid(~mediansplit_ground_arousal)

```

```{r}
db_pupil_concordance_agg_ground <-  db_full4new_stim_screen_pupil_nopract %>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_ground_valence)%>%
    mutate(cortest = cor.test(arousal_c, pup_basCor, use = "complete")$estimate)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)

afex::aov_ez(id = "ssid",
             data = db_pupil_concordance_agg,
             between = NULL,
             within = 'mediansplit_ground_valence',
             dv = 'cortest')

unique(db_full4new_stim_screen_pupil_nopract$tNo)
db_pupil_concordance_agg_self <-  db_full4new_stim_screen_pupil_nopract %>%
  subset(pupil_outlier == FALSE)%>%
  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  subset(!is.na(Alexithymia))%>%
  # subset(Group == "NT")%>%
  subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_self_arousal, mediansplit_self_valence)%>%
    mutate(cortest = cor(arousal_c, pup_basCor, use = "complete"))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)

afex::aov_ez(id = "ssid",
             data = test_anovas,
             between = NULL,
             within = 'mediansplit_sample_valence2',
             dv = 'cortest')

afex::aov_ez(id = "ssid",
             data = subset(test_anovas, mediansplit_sample_valence2 == "More positive"),
             between = NULL,
             within = 'mediansplit_sample_arousal2',
             dv = 'cortest')

afex::aov_ez(id = "ssid",
             data = db_pupil_concordance_agg_self,
             between = NULL,
             within = 'mediansplit_ground_valence',
             dv = 'cortest')

# valence and arousal

afex::aov_ez(id = "ssid",
             data = test_anovas,
             between = NULL,
             within = c('mediansplit_sample_arousal2','mediansplit_sample_valence2'),
             dv = 'cortest')

db_parsed_f_summ<- db_parsed_f %>%
  group_by(tNo, ssid)%>%
  summarise_at(c('Duration', 'mean_x', 'mean_y'), sum, na.rm = TRUE)
  ggplot(aes(tNo, Duration))+
  stat_summary(geom = 'pointrange')+
  geom_point(alpha = .1)

unique(db_parsed_f_summ$ssid)
unique(db_parsed_f_summ$tNo)
unique(db_full4new_stim_screen_pupil_nopract$tNo)
unique(db_full4new_stim_screen_pupil_nopract$ssid)
nrow(db_full4new_stim_screen_pupil_nopract)
nrow(db_parsed_f_summ)

table(is.na(db_parsed_f_summ$ssid))

db_parsed_f_summ$total_fix_dur<- db_parsed_f_summ$Duration

db_parsed_f_summ$tNo<- as.character(db_parsed_f_summ$tNo)
db_parsed_f_summ$ssid<- as.character(db_parsed_f_summ$ssid)
db_full4new_stim_screen_pupil_nopract$Duration<- NULL
db_full4new_stim_screen_pupil_nopract$total_fix_dur<- NULL

db_full4new_stim_screen_pupil_nopract<- left_join(db_full4new_stim_screen_pupil_nopract, db_parsed_f_summ)

```

I HAVE THE IMPRESSION THAT WHAT THIS ANALYSES GIVES US IS THE SAME AS THE MIXED MODEL AS THIS CONCIORDANCE CAN BE EXPRESSED IN TERMS FO THE SLOPE OF THE AOUSAL AND PUPIL RELATION

SO ION OTHER WORDS IS not that pupil tracksvalence is that arousal based pupil is modulated by valence

by why is that
- bias is responding? eg.. people response they feel negative even when they don't (ie. when we have no objective indicator that they do feel)
- is it something about the stimuli, positive arousal is sexual here?
- or arousal interferes with appraisal. high arousing stimuli are distracting??

timecourse models of pupil

Pupil tracks valence

```{r}

db_full4new_stim_screen_pupil_Anopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  subset(ssid_num<500)%>%
  group_by(ssid)%>%
  mutate(pup_basCor_z = scale(pup_basCor, center = TRUE, scale = TRUE))%>%
    group_by(ssid, ground_valence_lab, Alexithymia)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_lab, pup_basCor_z,fill = ground_valence_lab))+
 geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
      geom_jitter(width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
    # geom_ysidedensity(aes(x=stat(density),color = ground_valence_lab), alpha = .4)+
  p$graphstyle+
  xlab("valence")+
  ylab("Baseline corrected pupil")+
  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")

mediansplit_self_valence

db_full4new_stim_screen_pupil_nopract %>%
  # subset(pp_arousal_outler== FALSE)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  subset(ssid_num<500)%>%
  group_by(ssid)%>%
  # mutate(pup_basCor_z = scale(pup_basCor, center = TRUE, scale = TRUE))%>%
    group_by(ssid, self_arousal_lab, mediansplit_self_valence)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(self_arousal_lab, pup_basCor,fill = self_arousal_lab))+
 geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
      geom_jitter(width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
    # geom_ysidedensity(aes(x=stat(density),color = ground_valence_lab), alpha = .4)+
  p$graphstyle+
  xlab("arousal")+
  ylab("Baseline corrected pupil")+
  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_self_valence)

  db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler== FALSE)%>%
  subset(ssid< 500)%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
    group_by(ssid, self_arousal_lab, Alexithymia, mediansplit_self_valence)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(self_arousal_lab, pup_basCor, color = self_arousal_lab,fill = self_arousal_lab))+
    geom_hline(yintercept = 0, linetype = "dashed", size = 2, alpha = .2)+
 # geom_half_violin(colour = FALSE, alpha = .3, size = 5)+
  geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
    stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = 1, colour = "Black") +
  stat_summary(geom = 'pointrange', width =1)+
  p$graphstyle+
  xlab("Arousal")+
  ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  facet_grid(~mediansplit_self_valence)
  # facet_grid(~BRIGHTNESS_mediansplit)+
  ylim(-6,2.3)

table(is.na(db_full4new_stim_screen_pupil_nopract$mediansplit_self_valence))
```

combine timecourse

let's put pupil scr and ht prediction on subjective arousal

```{r}
rm(justone_test, lucy_plots, test)

# import the timecourse

tmp.df4_full_stim_downs_jun2021 <- readRDS("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/tmp.df4_full_stim_downs_jun2021.rds")

# merge with behavioural data
unique(db_full4new_stim_screen_pupil_nopract$ssid)
colnames(db_full4new_stim_screen_pupil_nopract)
colnames(tmp.df4_full_stim_downs_jun2021)

db_full4new_stim
colnames(db_full4new_stim_screen_pupil_nopract)
db_full4new_stim_subset<- db_full4new_stim_screen_pupil_nopract[,c(1:4,6:7,12:13,16,21:27, 31:56,80:81,84:96,98:114,116:124)]

# match types of merging variables
tmp.df4_full_stim_downs_jun2021_with_beh2$ssid<- as.character(tmp.df4_full_stim_downs_jun2021_with_beh2$ssid)

db_full4new_stim_subset$ssid<- as.character(db_full4new_stim_subset$ssid)

# tNo

tmp.df4_full_stim_downs_jun2021_with_beh2$tNo <- as.character(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)
db_full4new_stim_subset$tNo <- as.character(db_full4new_stim_subset$tNo)
unique(db_full4new_stim_subset$tNo)
unique(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)
# merge
nrow(tmp.df4_full_stim_downs_jun2021_with_beh2)
# 172168
# 87529

table(is.na(db_full4new_stim_subset$mediansplit_self_valence))

tmp.df4_full_stim_downs_jun2021_with_beh2$tNo<- as.numeric(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)
tmp.df4_full_stim_downs_jun2021_with_beh2<- tmp.df4_full_stim_downs_jun2021_with_beh2%>%
  arrange(ssid,tNo, timerezero3)

db_full4new_stim_subset$t
tmp.df4_full_stim_downs_jun2021_with_beh<- left_join(tmp.df4_full_stim_downs_jun2021_with_beh2, db_full4new_stim_subset)

unique(db_full4new_stim_subset$stimIAPS)

tmp.df4_full_stim_downs_jun2021_with_beh2$trialUnq

unique(tmp.df4_full_stim_downs_jun2021_with_beh2$ssid)
unique(db_full4new_stim_subset$ssid)

db_full4new_stim_subset$tNo<- as.numeric(db_full4new_stim_subset$tNo)

table(is.na(db_full4new_stim_subset$arousal))

tmp.df4_full_stim_downs_jun2021_with_behnew<- right_join(tmp.df4_full_stim_downs_jun2021_with_beh2, db_full4new_stim_subset,
                                                     by = c('ssid', 'tNo'))

nrow(tmp.df4_full_stim_downs_jun2021_with_beh)
# 172168 good

nrow(tmp.df4_full_stim_downs_jun2021_with_beh2)

nrow(tmp.df4_full_stim_downs_jun2021_with_behnew)
87529

table(is.na(tmp.df4_full_stim_downs_jun2021_with_behnew$mediansplit_self_valence))

subset(tmp.df4_full_stim_downs_jun2021_with_behnew, is.na(arousal))

unique(tmp.df4_full_stim_downs_jun2021_with_beh2$trialUnq)

```

```{r}
# check
tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= ground_arousal_lab, color = ground_arousal_lab), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=ground_arousal_lab, color = ground_arousal_lab), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_self_valence)

```

pupil timecourse

```{r}

tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(mediansplit_sample_arousal2))%>%
  subset(!is.na(mediansplit_sample_arousal2))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= mediansplit_sample_valence2, color = mediansplit_sample_valence2), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=mediansplit_sample_valence2, color = mediansplit_sample_valence2), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_sample_arousal2)

tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= mediansplit_ground_arousal, color = mediansplit_ground_arousal), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_ground_valence)

```

unique(tmp.df4_full_stim_downs_jun2021_with_beh$condition)

```{r}
tmp.df4_full_stim_downs_jun2021_with_beh$valencearousal_outliers<- if_else(tmp.df4_full_stim_downs_jun2021_with_beh$ArousalMean< 6.7 & 
                                                                    tmp.df4_full_stim_downs_jun2021_with_beh$mediansplit_ground_valence == "More negative", TRUE,
                                                                    if_else(tmp.df4_full_stim_downs_jun2021_with_beh$ArousalMean> 2.94 & 
                                                                    tmp.df4_full_stim_downs_jun2021_with_beh$mediansplit_ground_valence == "More positive", TRUE, FALSE))

tmp.df4_full_stim_downs_jun2021_with_beh %>%
  # subset(valencearousal_outliers == TRUE) %>%
  group_by(stimIAPS,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_valence, ArousalMean))+
  # geom_boxplot()+
  # geom_point()+
  # geom_text(aes(label = stimIAPS))+
  stat_summary(geom = 'pointrange')+
  geom_hline(yintercept = 7.2)+
    geom_hline(yintercept = 6.7)+
   geom_hline(yintercept = 2.94)

# thismplot raises question regarding wthtehr the better correlation bwteen subjective and objective arousal for positive stomuli reflects the fact that for negative we don't have many low arousal ones. But this is unlikelly because the oposite us also true for posituive stimuli, notmany positive stomuli are rated as highly arousing in sekf report, so we would not expect

# less restruct varoability
tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(mediansplit_sample_arousal2))%>%
  subset(valencearousal_outliers == TRUE) %>%
  # subset(!is.na(mediansplit_sample_arousal2))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_sample_valence2)

tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(mediansplit_sample_arousal2))%>%
  subset(valencearousal_outliers == TRUE) %>%
  # subset(!is.na(mediansplit_sample_arousal2))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(mediansplit_sample_valence2~.)+
  geom_hline(yintercept = 0)

```

unique(tmp.df4_full_stim_downs_jun2021_with_beh$timebin2)
# 30 time bins

```{r}
# pval<- cor.test(tmp.df4_full_stim_downs_jun2021_with_beh$sdevgaze_parsed, tmp.df4_full_stim_downs_jun2021_with_beh$pup_basCor)
# pval$estimate

tmp.df4_full_stim_downs_jun2021_with_beh$ssid_num<- as.numeric(as.character(tmp.df4_full_stim_downs_jun2021_with_beh$ssid))

library(purrr)

tmp.df4_full_stim_downs_jun2021_with_behnew<-tmp.df4_full_stim_downs_jun2021_with_behnew%>%
ungroup()%>%
  mutate(mediansplit_sample_valence2 = 
           if_else(ValenceMeanThisSample >= 
                     median(ValenceMeanThisSample,
                            na.rm = TRUE), 
                   "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >=
                                                  median(ArousalMeanThisSample,
                                                         na.rm = TRUE), "High", "Low"))

tmp.df4_full_stim_downs_jun2021_with_behnew$ssid_split_val_time<- paste0(tmp.df4_full_stim_downs_jun2021_with_behnew$ssid,          
paste0(tmp.df4_full_stim_downs_jun2021_with_behnew$mediansplit_sample_valence2,
       paste0(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin2)))

table(is.na(tmp.df4_full_stim_downs_jun2021_with_beh$mediansplit_self_valence))
unique(tmp.df4_full_stim_downs_jun2021_with_beh$ssid_split_val_time)
subset(tmp.df4_full_stim_downs_jun2021_with_beh, is.na(mediansplit_self_valence))

tmp.df4_full_stim_downs_jun2021_with_behnew$ssid_num<- as.numeric(tmp.df4_full_stim_downs_jun2021_with_behnew$ssid)

tmp.df4_full_stim_downs_jun2021_with_behnew <- tmp.df4_full_stim_downs_jun2021_with_behnew%>%
  subset(ssid_num<500)%>%
  # subset(ssid == 320)%>%
  ungroup()%>%
  group_by(ssid_split_val_time)%>%
  mutate(cor_arous_pup = cor.test(pup_basCor, arousal_c, use = "complete")$estimate,
         cor_arous_pup_pval = cor.test(pup_basCor, arousal_c, use = "complete")$p.value)

tmp.df4_full_stim_downs_jun2021_with_behnew<- tmp.df4_full_stim_downs_jun2021_with_behnew%>%
  group_by(timebin2)%>%
  mutate(mean_cor_pup = mean(cor_arous_pup, na.rm = TRUE), sd_cor_pup = sd(cor_arous_pup, na.rm = TRUE),
         mean_cor_pup_pva = mean(cor_arous_pup_pval, na.rm = TRUE), sd_cor_arous_pup_pval = sd(cor_arous_pup_pval, na.rm = TRUE))

tmp.df4_full_stim_downs_jun2021_with_behnew$pval_sign<- if_else(tmp.df4_full_stim_downs_jun2021_with_behnew$mean_cor_pup_pva < .05, tmp.df4_full_stim_downs_jun2021_with_behnew$mean_cor_pup_pva, NULL)

ttestcheck<- t.test(tmp.df4_full_stim_downs_jun2021_with_behnew$cor_arous_pup)
ttestcheck$p.value
ttestcheck$parameter

unique(tmp.df4_full_stim_downs_jun2021_with_behnew$ssid_split_val_time)

tmp.df4_full_stim_downs_jun2021_with_behnew$vale_timebin<- paste0(tmp.df4_full_stim_downs_jun2021_with_behnew$mediansplit_sample_valence2, paste0(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin2))

# subset(tmp.df4_full_stim_downs_jun2021_with_behnew, vale_timebin == "More negative(2.6,2.82]")

tmp.df4_full_stim_downs_jun2021_with_behnew$ssid<- as.character(tmp.df4_full_stim_downs_jun2021_with_behnew$ssid)

tmp.df4_full_stim_downs_jun2021_with_behnew %>%
    group_by(ssid, mediansplit_sample_valence2, timebin2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  group_by(mediansplit_sample_valence2,timebin2)%>%
  mutate(pval = t.test(cor_arous_pup)$p.value, df = t.test(cor_arous_pup)$parameter)%>%
  group_by(mediansplit_sample_valence2,timebin2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(timerezero3, cor_arous_pup, color = mediansplit_sample_valence2))+
  # geom_s
  stat_summary(fun = mean, geom = 'line', size = 4)+
  # stat_summary(aes(y = pval), fun = mean, geom = 'line', linetype = "dashed", alpha = .2)+
  geom_hline(yintercept = .05, linetype = "dashed")+

  geom_hline(yintercept = .1, linetype = "dotted")+
  theme_classic()

nrow(left_join(tmp.df4_full_stim_downs_jun2021_with_behnew, flag_pos_neg))
nrow(tmp.df4_full_stim_downs_jun2021_with_behnew)

tmp.df4_full_stim_downs_jun2021_with_behnew$cor_pos_neg_diff_lab<- NULL
tmp.df4_full_stim_downs_jun2021_with_behnew$cor_pos_neg_diff<-NULL
tmp.df4_full_stim_downs_jun2021_with_behnew<- left_join(tmp.df4_full_stim_downs_jun2021_with_behnew, flag_pos_neg)

tmp.df4_full_stim_downs_jun2021_with_behnew %>%
  subset(!is.na(cor_pos_neg_diff_lab))%>%
  # subset(cor_pos_neg_diff_lab == "pos > neg") %>%
  group_by(ssid, mediansplit_sample_valence2, timebin2,cor_pos_neg_diff_lab) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  group_by(mediansplit_sample_valence2,timebin2) %>%
  mutate(pval = t.test(cor_arous_pup)$p.value, df = t.test(cor_arous_pup)$parameter)%>%
  group_by(mediansplit_sample_valence2,timebin2,cor_pos_neg_diff_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  # ggplot(aes(timerezero3, cor_arous_pup, color = mediansplit_sample_valence2))+
  ggplot(aes(timerezero3, cor_arous_pup, color =  cor_pos_neg_diff_lab))+
  # geom_s
  stat_summary(fun = mean, geom = 'line', size = 4)+
  # stat_summary(aes(y = pval), fun = mean, geom = 'line', linetype = "dashed", alpha = .2)+
  geom_hline(yintercept = .05, linetype = "dashed")+

  geom_hline(yintercept = .1, linetype = "dotted")+
  geom_vline(xintercept = 1, linetype = "dotted")+
  # geom_rect(xmin = .5, xmax = 1, ymin = -.2, ymax = 1, alpha = .01, color = FALSE)+
  theme_classic()+
    facet_grid(~mediansplit_sample_valence2)

range(tmp.df4_full_stim_downs_jun2021_with_behnew$pval_sign, na.rm = TRUE)
tmp.df4_full_stim_downs_jun2021_with_behnew$ssid_split_val_time

# let's identify the people whio show the negative arousal effect

```

timecourse analyss using lmer

1- select a bin
2 - fit a lmer
3 - save statistics (estimate and p value)
3 - create clusters (p value < .05 in at least 3 consecutive bins)

```{r}

tmp.df4_full_stim_downs_jun2021_with_behnew$
i = 1

nbins<- unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin2)

tmp.df4_full_stim_downs_jun2021_with_behnew

unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin2)
lmer_bin_pup<- list()

# <- nrow(nbins)

nbins<- unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin2)

tmp.df4_full_stim_downs_jun2021_with_behnew$Label<- substr(tmp.df4_full_stim_downs_jun2021_with_behnew$stimIAPS, 1,8)

imageJ_IAPS$Label
nrow(tmp.df4_full_stim_downs_jun2021_with_behnew)
# 62921
nrow(left_join(tmp.df4_full_stim_downs_jun2021_with_behnew, imageJ_IAPS))

tmp.df4_full_stim_downs_jun2021_with_behnew<- left_join(tmp.df4_full_stim_downs_jun2021_with_behnew, imageJ_IAPS)

tmp.df4_full_stim_downs_jun2021_with_behnew$Mean_gray_z<- scale(tmp.df4_full_stim_downs_jun2021_with_behnew$Mean, scale = TRUE, center = TRUE)[,1]

test<- lmer(pup_basCor ~ arousal_c+Mean_gray_z  +(1 +Mean_gray_z | ssid), 
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    timebin2 == nbins[b]))

summary(test)

tmp.df4_full_stim_downs_jun2021_with_behnew$tNo
"(0.0411,0.261]"
subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    timebin2 == nbins[28] & ssid == 341 & tNo == 3)

test
rm(i)

i = 1 # remember to always rezero it
# b = 34
nbins<- nbins[1:28]
unique(nbins)

# nbins<- as

# positive

# create number s for time bins
tmp.df4_full_stim_downs_jun2021_with_behnew<- tmp.df4_full_stim_downs_jun2021_with_behnew%>%
  group_by(ssid, stimIAPS)%>%
  mutate(timebin_no = 1:n())

tmp.df4_full_stim_downs_jun2021_with_behnew%>%
  # group_by(ssid, stimIAPS)
  ggplot(aes(timebin_no))+
  geom_histogram()+
  geom_vline(xintercept = 28)+
  geom_hline(yintercept = 200)

```

```{r}

nrow(nbins)
nbins = 30
timecourse_result_df <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))

View(timecourse_result_df)

nbins<- nbins[1:28]

i = 1 # remember to always rezero it
# b = 34

nbins<- unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)

unique(nbins)
for (b in 1:length(nbins)) {
  # for (s in 1:length(nsim)) {

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
    # db_of7_new_JEFFE$VideoType_contrast_sample<- sample((rep(c(-.5, .5), each =  1920)), replace = FALSE) 
        #run the model on the current time bin and simulation sumber
        lmer_bin_pup  <- lmer(pup_basCor ~ arousal_c+Mean_gray_z  +(1 +Mean_gray_z | ssid) +
                                (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    mediansplit_self_valence == "More positive" & 
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            timecourse_result_df[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
            timecourse_result_df[i,2]<- lmer_bin_pup_summary[["coefficients"]][2,1] # s
            timecourse_result_df[i,3]<-lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_result_df[i,4]<-lmer_bin_pup_summary[["coefficients"]][2,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}

# timecourse_result_df_pos<- timecourse_result_df

timecourse_result_df%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

```

# negative lmer
```{r}

timecourse_result_df_neg <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))

i = 1

for (b in 1:length(nbins)) {
  # for (s in 1:length(nsim)) {

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
    # db_of7_new_JEFFE$VideoType_contrast_sample<- sample((rep(c(-.5, .5), each =  1920)), replace = FALSE) 
        #run the model on the current time bin and simulation sumber
        lmer_bin_pup  <- lmer(pup_basCor ~ arousal_c+Mean_gray_z  +(1 +Mean_gray_z | ssid) +
                                (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    mediansplit_ground_valence == "More negative" & 
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            timecourse_result_df_neg[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
            timecourse_result_df_neg[i,2]<- lmer_bin_pup_summary[["coefficients"]][2,1] # s
            timecourse_result_df_neg[i,3]<-lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_result_df_neg[i,4]<-lmer_bin_pup_summary[["coefficients"]][2,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df_neg[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}

View(timecourse_result_df_neg)

# whether I use ground valence, self valemce or this sample average valence, I get the same patterns

timecourse_result_df_neg%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .1, color = 'red', size = 1.5)

```

```{r}
timecourse_result_df$Valence <- "More negative"

timecourse_result_df_neg$Valence<- "More positive"

bind_rows(timecourse_result_df,timecourse_result_df_neg)%>%
    ggplot(aes(timebins, t, color = Valence))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

```
# use valence to pupil
```{r}
timecourse_result_df_val <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))

i = 1

for (b in 1:length(nbins)) {
  # for (s in 1:length(nsim)) {

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
    # db_of7_new_JEFFE$VideoType_contrast_sample<- sample((rep(c(-.5, .5), each =  1920)), replace = FALSE) 
        #run the model on the current time bin and simulation sumber
        lmer_bin_pup  <- lmer(pup_basCor ~ arousal_c+ valence_c+ Mean_gray_z  +(1 + Mean_gray_z | ssid) +
                                (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    # mediansplit_self_valence == "More negative" & 
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            timecourse_result_df_val[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
            timecourse_result_df_val[i,2]<- lmer_bin_pup_summary[["coefficients"]][2,1] # s
            timecourse_result_df_val[i,3]<-lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_result_df_val[i,4]<-lmer_bin_pup_summary[["coefficients"]][2,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df_val[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}

# valence to pupil
timecourse_result_df_val%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

```

# use valence to pupil

```{r}
timecourse_result_df_val_and_ar <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))

i = 1

for (b in 1:length(nbins)) {
  # for (s in 1:length(nsim)) {

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
    # db_of7_new_JEFFE$VideoType_contrast_sample<- sample((rep(c(-.5, .5), each =  1920)), replace = FALSE) 
        #run the model on the current time bin and simulation sumber
        lmer_bin_pup  <- lmer(pup_basCor ~ valence_c+ arousal+Mean_gray_z  +(1 + Mean_gray_z | ssid) +
                                (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    # mediansplit_self_valence == "More negative" & 
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            timecourse_result_df_val_and_ar[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
            timecourse_result_df_val_and_ar[i,2]<- lmer_bin_pup_summary[["coefficients"]][2,1] # s
            timecourse_result_df_val_and_ar[i,3]<-lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_result_df_val_and_ar[i,4]<-lmer_bin_pup_summary[["coefficients"]][2,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df_val_and_ar[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}

timecourse_result_df_val_and_ar%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

```

valence for high vs low
```{r}
timecourse_result_df_val_and_ar_neg <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))

i = 1

for (b in 1:length(nbins)) {
  # for (s in 1:length(nsim)) {

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
    # db_of7_new_JEFFE$VideoType_contrast_sample<- sample((rep(c(-.5, .5), each =  1920)), replace = FALSE) 
        #run the model on the current time bin and simulation sumber
        lmer_bin_pup  <- lmer(pup_basCor ~ valence_c + Mean_gray_z  +(1 + Mean_gray_z | ssid) +
                                (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    mediansplit_sample_arousal2 == "High" &
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            timecourse_result_df_val_and_ar_neg[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
            timecourse_result_df_val_and_ar_neg[i,2]<- lmer_bin_pup_summary[["coefficients"]][2,1] # s
            timecourse_result_df_val_and_ar_neg[i,3]<-lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_result_df_val_and_ar_neg[i,4]<-lmer_bin_pup_summary[["coefficients"]][2,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df_val_and_ar_neg[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}

View(timecourse_result_df_val_and_ar_neg)

timecourse_result_df_val_and_ar_neg%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)+
  ggtitle("pupil ~ valence for high arousal")

```

#

```{r}
timecourse_result_df_val_and_ar_low <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))

i = 1

for (b in 1:length(nbins)) {
  # for (s in 1:length(nsim)) {

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
    # db_of7_new_JEFFE$VideoType_contrast_sample<- sample((rep(c(-.5, .5), each =  1920)), replace = FALSE) 
        #run the model on the current time bin and simulation sumber
        lmer_bin_pup  <- lmer(pup_basCor ~ valence_c +Mean_gray_z  +(1 + Mean_gray_z | ssid) +
                                (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    mediansplit_sample_arousal2 == "Low" &
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            timecourse_result_df_val_and_ar_low[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
            timecourse_result_df_val_and_ar_low[i,2]<- lmer_bin_pup_summary[["coefficients"]][2,1] # s
            timecourse_result_df_val_and_ar_low[i,3]<-lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_result_df_val_and_ar_low[i,4]<-lmer_bin_pup_summary[["coefficients"]][2,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df_val_and_ar_low[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}

View(timecourse_result_df_val_and_ar_neg)

timecourse_result_df_val_and_ar_low%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

```

velocity analyses
```{r}
# thought maybe it has soemthing to to with the velcity, velocity is sidderent

install.packages("pspline")
library(pspline)

predict(sm.spline(tmp.df4_full_stim_downs_jun2021_with_beh$timerezero3, 
                  tmp.df4_full_stim_downs_jun2021_with_beh$pup_basCor), 
        tmp.df4_full_stim_downs_jun2021_with_beh$timerezero3, 1)

D(tmp.df4_full_stim_downs_jun2021_with_beh$pup_basCor, 'x')

tmp.df4_full_stim_downs_jun2021_with_behnew

tmp.df4_full_stim_downs_jun2021_with_behnew <- tmp.df4_full_stim_downs_jun2021_with_behnew %>%
  # subset(!is.na(mediansplit_sample_arousal2))%>%
  # subset(valencearousal_outliers == TRUE) %>%
  # subset(!is.na(mediansplit_sample_arousal2))%>%
  group_by(ssid, stimIAPS) %>%
  mutate(pup_velocity = (abs(lag(pup_basCor)-pup_basCor)/abs(lag(timerezero3)-timerezero3)))
  # mutate(pup_velocity_peak = max(pup_velocity, na.rm = TRUE))

tmp.df4_full_stim_downs_jun2021_with_behnew$pup_velocity

# global
timecourse_result_df_vel <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))

i = 1
b

tmp.df4_full_stim_downs_jun2021_with_behnew$pup_velocity

lmer_bin_pup  <- lmer(pup_velocity ~ arousal_c + Mean_gray_z  + (1 + Mean_gray_z | ssid),
                      REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    timebin_no == nbins[2]))

for (b in 2:length(nbins)) {
  # for (s in 1:length(nsim)) {

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
    # db_of7_new_JEFFE$VideoType_contrast_sample<- sample((rep(c(-.5, .5), each =  1920)), replace = FALSE) 
        #run the model on the current time bin and simulation sumber
        lmer_bin_pup  <- lmer(pup_velocity ~ arousal_c + Mean_gray_z  + (1 + Mean_gray_z | ssid),
                                # (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    # !is.na== "More negative" &
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            timecourse_result_df_vel[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
            timecourse_result_df_vel[i,2]<- lmer_bin_pup_summary[["coefficients"]][2,1] # s
            timecourse_result_df_vel[i,3]<-lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_result_df_vel[i,4]<-lmer_bin_pup_summary[["coefficients"]][2,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df_vel[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}

View(timecourse_result_df_vel)

# whether I use ground valence, self valemce or this sample average valence, I get the same patterns

timecourse_result_df_vel%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

# arousal rating is related to velocity around the recovery time 1:2is, and later around 4

```

Velocity by valence
```{r}

timecourse_result_df_vel_pos <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))

i = 1
# b

tmp.df4_full_stim_downs_jun2021_with_behnew$pup_velocity

for (b in 2:length(nbins)) {
  # for (s in 1:length(nsim)) {

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
    # db_of7_new_JEFFE$VideoType_contrast_sample<- sample((rep(c(-.5, .5), each =  1920)), replace = FALSE) 
        #run the model on the current time bin and simulation sumber
        lmer_bin_pup  <- lmer(pup_velocity ~ arousal_c + Mean_gray_z  + (1  | ssid),
                                # (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    mediansplit_sample_valence2== "More positive" &
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            timecourse_result_df_vel_pos[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
            timecourse_result_df_vel_pos[i,2]<- lmer_bin_pup_summary[["coefficients"]][2,1] # s
            timecourse_result_df_vel_pos[i,3]<-lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_result_df_vel_pos[i,4]<-lmer_bin_pup_summary[["coefficients"]][2,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df_vel_pos[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}

# 11 singularity cases

View(timecourse_result_df_vel_pos)

# whether I use ground valence, self valemce or this sample average valence, I get the same patterns

timecourse_result_df_vel_pos%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

# arousal rating is related to velocity around the recovery time 1 to 1.6

```

Negative velocity

```{r}

timecourse_result_df_vel_neg <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))

i = 1
b

tmp.df4_full_stim_downs_jun2021_with_behnew$pup_velocity

for (b in 2:length(nbins)) {
  # for (s in 1:length(nsim)) {

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
    # db_of7_new_JEFFE$VideoType_contrast_sample<- sample((rep(c(-.5, .5), each =  1920)), replace = FALSE) 
        #run the model on the current time bin and simulation sumber
        lmer_bin_pup  <- lmer(pup_velocity ~ arousal_c + Mean_gray_z  + (1 | ssid),
                                # (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
                                    mediansplit_sample_valence2== "More negative" &
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            timecourse_result_df_vel_neg[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
            timecourse_result_df_vel_neg[i,2]<- lmer_bin_pup_summary[["coefficients"]][2,1] # s
            timecourse_result_df_vel_neg[i,3]<-lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_result_df_vel_neg[i,4]<-lmer_bin_pup_summary[["coefficients"]][2,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_result_df_vel_neg[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}

# 11 singularity cases

View(timecourse_result_df_vel_neg)

# whether I use ground valence, self valemce or this sample average valence, I get the same patterns

timecourse_result_df_vel_neg%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)

# arousal rating is related to velocity around the recovery time 1 to 1.6

```

A few plots for velocity
```{r}
  ggplot(aes(x = timerezero3, y = pup_velocity))+
  stat_smooth(aes(group= mediansplit_sample_valence2, color = mediansplit_sample_valence2), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=mediansplit_sample_valence2, color = mediansplit_sample_valence2), size = 3)+  
theme_classic()+
  ylab("Pupil velocity")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   # facet_grid(~mediansplit_sample_valence2)+
     geom_vline(xintercept = 1)

tmp.df4_full_stim_downs_jun2021_with_beh$timerezero3
tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(mediansplit_sample_arousal2))%>%
  subset(timerezero3>1 ) %>%
  # subset(!is.na(mediansplit_sample_arousal2))%>%
  group_by(ssid, stimIAPS)%>%
  mutate(pup_velocity = (abs(lag(pup_basCor)-pup_basCor))/(abs(lag(timerezero3)-timerezero3)))%>%
  mutate(pup_velocity_peak = max(pup_velocity, na.rm = TRUE))%>%
  group_by(ssid,mediansplit_sample_valence2,mediansplit_sample_arousal2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(x = mediansplit_sample_valence2, y = pup_velocity))+
  # geom_jitter(width = .1, alpha = .1)+
  stat_summary(geom = 'pointrange')+
  theme_classic()+
  ggpubr::stat_compare_means()+
  ylab("Pupil velocity (z)")+
  xlab("Time (s)")+
  facet_grid(~mediansplit_sample_arousal2)

tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(mediansplit_sample_arousal2))%>%
  subset(timerezero3>1) %>%
  # subset(!is.na(mediansplit_sample_arousal2))%>%
  group_by(ssid, stimIAPS)%>%
  mutate(pup_velocity = (abs(lag(pup_basCor)-pup_basCor))/(abs(lag(timerezero3)-timerezero3)))%>%
  mutate(pup_velocity_peak = max(pup_velocity, na.rm = TRUE))%>%
  group_by(ssid,mediansplit_sample_valence2,mediansplit_sample_arousal2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(x = mediansplit_sample_valence2, y = pup_velocity_peak))+
  geom_jitter(width = .1, alpha = .1)+
  stat_summary(geom = 'pointrange')+
  theme_classic()+
  ggpubr::stat_compare_means()+
  ylab("peak Pupil velocity (z)")+
  xlab("Time (s)")+
  facet_grid(~mediansplit_sample_arousal2)

```
```{r}
tmp.df4_full_stim_downs_jun2021_with_behnew%>%
    group_by(mediansplit_self_valence, timebin2)%>%
summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(timerezero3, cor_arous_pup, color = mediansplit_self_valence))+
  # geom_s
  stat_summary(fun = mean, geom = 'pointrange')+
  stat_summary(aes(y = cor_arous_pup_pval), fun = mean, geom = 'line', linetype = "dashed")+
  geom_hline(yintercept = .1, linetype = "dashed")
  geom_rect(aes(xmin = timerezero3, xmax = dplyr::lead(timerezero3), ymin =.63 , ymax =.66 , fill = pval_sign), 
            alpha = 0.8)

  # stat_smooth(aes(group = ssid), se = F, alpha = .1)
  # mutate(
  #   model = map(data, ~lm(pup_basCor ~ arousal_c, data = .)),
  #   cor = map(data, possibly(
  #     ~tidy(cor.test(.x$pup_basCor, .x$arousal_c), 3), otherwise = data.frame())
  #   )
  # )

```

# self arousal

```{r}

tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= ground_arousal_lab, color = ground_arousal_lab), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=ground_arousal_lab, color = ground_arousal_lab), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
  facet_grid(~mediansplit_self_valence)

```

```{r}

# plot with valence
tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(ground_arousal_lab))%>%
  group_by(ssid,Alexithymia, mediansplit_ground_valence, timebin2)%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= mediansplit_ground_valence, color = mediansplit_ground_valence), fun = mean,geom = "line",
               se = F, size = 1.5)+
  # stat_smooth(aes(group=ground_valence_lab, color = ground_valence_lab), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)

test<- cor.test(db_2021_pupil_summ$hr_interp,db_2021_pupil_summ$pup_basCor)

test$p.value
tmp.df4_full_stim_downs_jun2021_with_beh$ssid_ground_valence<- paste0(tmp.df4_full_stim_downs_jun2021_with_beh$ssid, paste0(tmp.df4_full_stim_downs_jun2021_with_beh$ground_arousal_lab))

tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(self_arousal_lab))%>%

  db_full4new_stim_screen_pupil_nopract

  group_by(ssid,Alexithymia, ground_valence_lab, timebin2)%>%
    mutate(cortest = cor.test(arousal_c, pup_basCor)$estimate)%>%
  mutate(pcortest = cor.test(arousal_c, pup_basCor)$p.value)%>%
  group_by(ssid,Alexithymia, self_arousal_lab, timebin2)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(x = timerezero3, y = cortest))+

  stat_smooth(aes(group= self_arousal_lab, color = self_arousal_lab), fun = mean,geom = "line",
               se = F, size = 1.5)+
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  geom_hline(yintercept = .05, linetype = "dashed")+
  xlim(0,6)

# does arousing stimuli impairs appraisal

 tmp.df4_full_stim_downs_jun2021_with_beh %>%
   ggplot(aes(ground_arousal_lab, BRIGHTNESS))+
   geom_boxplot()+
   geom_point()+
   # stat_summary(geom = 'boxplot')+
   facet_grid(~mediansplit_self_valence)
```

```{r}
 db_full4new_stim_screen_pupil_nopract %>%
  subset(pupil_outlier == FALSE & arousal_outler == FALSE & !is.na(Alexithymia) & ssid!= 610)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid,Alexithymia, mediansplit_self_valence)%>%
    mutate(cortest = cor.test(arousal_c, pup_basCor)$estimate)%>%
   group_by(ssid,Alexithymia, mediansplit_self_valence, self_arousal_lab)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_self_valence, cortest, color = mediansplit_self_valence))+
           geom_bar(stat="summary", fun.y = "mean")+

    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange')+
          # stat_summary(aes(group = ssid), geom = 'line')+
    ylab("R pupil vs self report arousal")+
   # ggpubr::stat_compare_means(paired = TRUE)+
  # ggpubr::stat_compare_means(comparisons = my_comparisons, paired = TRUE)
      facet_grid(~self_arousal_lab)

```

SCR

```{r}

unique(db_full4new_stim_screen_pupil_nopract$ssid)
View(flag_pos_neg)
db_full4new_stim_screen_pupil_nopract$mediansplit_self_arousal <- if_else(db_full4new_stim_screen_pupil_nopract$arousal> median(db_full4new_stim_screen_pupil_nopract$arousal, na.rm = TRUE), "High", "Low")

db_full4new_stim_screen_pupil_nopract$mediansplit_self_arousal_thissample <- if_else(db_full4new_stim_screen_pupil_nopract$arousal> median(db_full4new_stim_screen_pupil_nopract$ArousalMeanThisSample, na.rm = TRUE), "High", "Low")

unique(db_full4new_stim_screen_pupil_nopract2$ssid)

db_full4new_stim_screen_pupil_nopract_nt<- subset(db_full4new_stim_screen_pupil_nopract, ssid_num<500)

nrow(db_full4new_stim_screen_pupil_nopract_nt)
# 2233
# nrow(left_join(db_full4new_stim_screen_pupil_nopract_nt, flag_pos_neg))

db_full4new_stim_screen_pupil_nopract_nt<- left_join(db_full4new_stim_screen_pupil_nopract_nt, flag_pos_neg)

unique(db_full4new_stim_screen_pupil_nopract_nt$stimDescription)
db_full4new_stim_screen_pupil_nopract_nt %>%
  subset(ssid_num< 500)%>%
    subset(pp_arousal_outler == FALSE)%>%
  subset( arousal_outler == FALSE )%>%
       subset(!is.na(Alexithymia))%>%
   group_by(ssid)%>%
  mutate(BIO_CDA.SCR_z = scale((BIO_CDA.SCR))[,1])%>%
  ungroup()%>%
    group_by(ssid,cor_pos_neg_diff_lab, mediansplit_self_valence)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_self_valence, BIO_CDA.SCR_z))+
      stat_summary(geom = 'pointrange')+

     # geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
  geom_jitter(width = .2, alpha = .2)+
  stat_summary(aes(group = ssid), geom = 'line', color = "gray", alpha = .1)+
  # geom_boxplot(alpha = .1)+
  # facet_grid(~cor_pos_neg_diff_lab)+
  ggpubr::stat_compare_means()

BIO_CDA.ISCR_z

db_full4new_stim_screen_pupil_nopract_nt %>%
  group_by(ssid)%>%
  mutate(BIO_TTP.AmpSum_z = scale(BIO_TTP.AmpSum, center = TRUE, scale = TRUE)[,1])%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_c, BIO_TTP.AmpSum_z))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

db_full4new_stim_screen_pupil_nopract_nt %>%
  group_by(ssid,mediansplit_sample_valence2)%>%
  # mutate(BIO_TTP.AmpSum_z = scale(BIO_TTP.AmpSum, center = TRUE, scale = TRUE)[,1])%>%
  # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal, BIO_CDA.ISCR_z))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  facet_grid(~mediansplit_sample_valence2)

db_full4new_stim_screen_pupil_nopract_nt %>%
  group_by(ssid,mediansplit_sample_valence2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_c, BIO_CDA.PhasicMax_z, color =mediansplit_sample_valence2))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

db_full4new_stim_screen_pupil_nopract_nt %>%
  group_by(ssid,ground_arousal_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_c, BIO_CDA.PhasicMax_z, color =ground_arousal_lab))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

```

# scr model

<!-- # average aroual and rating over all trials don't track well the expected arousal relation -->
```{r}

unique(db_full4new_stim_screen_pupil_nopract_nt$condition)
pupil_arousal_findings$arousal_scr <- lmer(log(BIO_CDA.SCR+.1) ~ arousal_c*TASc +(1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt,
                                      pp_arousal_outler == FALSE &
                                      mediansplit_self_valence == "More positive"))

summary(pupil_arousal_findings$arousal_scr)
anova(pupil_arousal_findings$arousal_phas_max)

BIO_CDA.PhasicMax

pupil_arousal_findings$arousal_scr <- lmer(BIO_CDA.PhasicMax_z ~ valence_c +(1+arousal_c|ssid),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt,
                                      pp_arousal_outler == FALSE))
                                      # mediansplit_self_valence == "More positive"))

summary(pupil_arousal_findings$arousal_scr)
anova(pupil_arousal_findings$arousal_phas_max)

db_full4new_stim_screen_pupil_nopract_nt %>%
  group_by(ssid, cor_pos_neg_diff_lab)%>%
  ggplot(aes(cor_pos_neg_diff_lab, TAS))+
  geom_point()+
  stat_summary(geom = 'pointrange')
```

summary(pupil_arousal_findings$arousal_scr)
anova(pupil_arousal_findings$arousal_phas_max)

test<- subset(db_full4new_stim_screen_pupil_nopract, pp_arousal_outler == FALSE & ssid == 310)
test$Alexithymia
table(test$mediansplit_self_valence)

# try the anova grouping
```{r}

afex::aov_ez(data = (db_full4new_stim_screen_pupil_nopract %>%
    subset(pp_arousal_outler == FALSE)%>%
      # subset(is_scr_nonresponder == FALSE )%>%
      subset(!is.na(Alexithymia))%>%
      group_by(ssid, mediansplit_ground_valence)%>%
      # group_by(ssid, Alexithymia,mediansplit_self_arousal, mediansplit_self_valence)%>%
      summarise_if(is.numeric, mean, na.rm = TRUE)),
    id = "ssid",
    between = NULL,
    within = c("mediansplit_ground_valence"),
    dv = "BIO_CDA.SCR_z")

colnames(db_full4new_stim_screen_pupil_nopract)

ggcorrplot::ggcorrplot(cor(db_full4new_stim_screen_pupil_nopract[,c(19,115,125:128,27,26)], use = "complete"))

```

BIO_CDA.SCR_z

# indovidual plots
```{r}

facet_hist_scr<- db_full4new_stim_screen_pupil_nopract %>%
  subset(ssid > 303)%>%
  subset(arousal_outler == FALSE )%>%
       subset(!is.na(Alexithymia))%>%
  ggplot(aes(log1p(BIO_CDA.SCR+1)))+
  geom_histogram(bins = )+
  facet_wrap(~ssid)

```

# what's up with non responders

# 312
# 318 only one rspinse?
# 320
# 321
# 327
# 329
# 332
# 335 (only one response)
# 342
# 343
# 600
# 603
# 606 (only one response)
# 608
# 900
# 56- 15

# that would leave us with 41 people

```{r}
unique(db_full4new_stim_screen_pupil_nopract$ssid)

range(db_full4new_stim_screen_pupil_nopract$BIO_CDA.SCR, na.rm = TRUE)

mean(db_full4new_stim_screen_pupil_nopract$BIO_CDA.SCR, na.rm = TRUE)
sd(db_full4new_stim_screen_pupil_nopract$BIO_CDA.SCR, na.rm = TRUE)

db_full4new_stim_screen_pupil_nopract%>%
  ggplot(aes(BIO_CDA.SCR))+
  geom_histogram(bins = 500)
  xlim(0,.01)

db_full4new_stim_screen_pupil_nopract%>%
  subset(ssid == 312)%>%
  ggplot(aes(BIO_CDA.AmpSum))+
  geom_histogram(bins = 500)+
  xlim(0,.05)

```

```{r}
db_full4new_stim_screen_pupil_nopract$is_scr_nonresponder<- if_else(db_full4new_stim_screen_pupil_nopract$BIO_CDA.AmpSum< .1, TRUE, FALSE)

 db_full4new_stim_screen_pupil_nopract %>%
  subset(ssid > 303)%>%
  subset(arousal_outler == FALSE )%>%
       subset(!is.na(Alexithymia))%>%
  ggplot(aes(log1p(BIO_CDA.SCR+1)))+
  geom_histogram(bins = )+
   facet_grid(~is_scr_nonresponder)
  facet_wrap(~ssid)

  db_full4new_stim_screen_pupil_nopract%>%
    group_by(ssid,is_scr_nonresponder)%>%
    mutate(scr_nonresp_prop = n())%>%
      group_by(ssid)%>%
     mutate(scr_nonresp_prop = scr_nonresp_prop/n())%>%
    ggplot(aes(as.factor(ssid), scr_nonresp_prop))+
    geom_bar(stat="summary", fun.y = "mean", alpha = .2, width = .5)

# test<-  subset(db_full4new_stim_screen_pupil_nopract, ssid == 321)

  table(db_full4new_stim_screen_pupil_nopract_nt$is_scr_nonresponder)
  db_full4new_stim_screen_pupil_nopract_nt %>%
    subset(is_scr_nonresponder != FALSE)%>%
    subset(pp_arousal_outler == FALSE)%>%
    subset(!ssid %in% c("304","321", "323", "318","339","331","325"))%>%
  # subset( arousal_outler == FALSE )%>%
       subset(!is.na(Alexithymia))%>%
   group_by(ssid)%>%
  mutate(BIO_CDA.SCR_z = scale(log1p(BIO_CDA.PhasicMax +.1))[,1])%>%
  # ungroup()%>%
    group_by(ssid, Alexithymia,mediansplit_sample_arousal2, mediansplit_sample_valence2)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
    # group_by(ssid)%>%
    # mutate(SCR_trend = BIO_CDA.SCR_z[mediansplit_ground_arousal == "Higher arousal"] -
             # BIO_CDA.SCR_z[mediansplit_ground_arousal == "Lower arousal"])
    # mutate(trendscr = if_else(SCR_trend> 0, "high to high", "high to low"))

    # group_by(ssid, Alexithymia,mediansplit_ground_arousal,trendscr)%>%
    # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_sample_arousal2, BIO_CDA.SCR_z))+
      stat_summary(geom = 'pointrange')+
     stat_summary(aes(group = ssid), geom = 'line')+

     # geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
  geom_jitter(width = .2, alpha = .2)
    facet_grid(~mediansplit_sample_valence2)
    # geom_boxplot(alpha = .1)
    # geom_text(aes(label = ssid))
    facet_grid(~trendscr)
    # ylim(-1,1)

304, 318, 339, 331,325

scr_models<- list()

db_full4new_stim_screen_pupil_nopract_nt %>%
    subset(is_scr_nonresponder == FALSE)%>%
    subset(pp_arousal_outler == FALSE)%>%
    subset(!ssid %in% c("304","321", "323", "318","339","331","325"))
  # subset( arousal_outler == FALSE )%>%

db_full4new_stim_screen_pupil_nopract_nt_scr_excluding_atypical<- db_full4new_stim_screen_pupil_nopract_nt%>%
                        subset(!ssid %in% c("304","321", "323", "318","339","331","325"))
  # subset(is_scr_nonresponder == FALSE)%>%
  group_by(ssid)%>%
  mutate(BIO_CDA.PhasicMax_z = scale(BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
 mutate(valence_z = scale(valence, center = TRUE, scale = TRUE)[,1])%>%
    mutate(arousal_z = scale(arousal, center = TRUE, scale = TRUE)[,1])

scr_models$scr_excluding_atypical<- lmer(log(BIO_CDA.PhasicMax+.1) ~ valence_z + arousal_z+
                                           (1| ssid) +
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data = db_full4new_stim_screen_pupil_nopract_nt_scr_excluding_atypical)

scr_models$scr_excluding_atypical<- lmer(log(BIO_CDA.PhasicMax+.1) ~ valence_c + arousal_c+
                                           (1| ssid) +
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data =  db_full4new_stim_screen_pupil_nopract_nt)
                        # subset(!ssid %in% c("304","321", "323", "318","339","331","325"))%>%
  subset(is_scr_nonresponder != FALSE))

summary(scr_models$scr_excluding_atypical)

(db_full4new_stim_screen_pupil_nopract_nt%>%
                        subset(!ssid %in% c("304","321", "323", "318","339","331","325"))))

summary(scr_models$scr_excluding_atypical)
```
<!-- one of the worries I had was that maybe there was a bias such that valence was confounded with arousal, but if this was true, then positive stimuli woul;d be rated as more arousing -->

    db_full4new_stim_screen_pupil_nopract %>%
    subset(is_scr_nonresponder == FALSE)%>%
    subset(pp_arousal_outler == FALSE)%>%
  subset( arousal_outler == FALSE )%>%
       subset(!is.na(Alexithymia))%>%
   group_by(ssid)%>%
  mutate(BIO_CDA.SCR_z = scale(log1p(BIO_CDA.PhasicMax +.1))[,1])%>%
      mutate(arousal_z = scale(arousal +.1))%>%
  ungroup()%>%
    # group_by(ssid, Alexithymia,mediansplit_self_arousal)%>%
    # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal_z, BIO_CDA.SCR_z))+
      geom_point()+
      # geom_smooth(aes(group = ssid),method = 'lm', se = F)+
      geom_smooth(method = 'lm', se = F)+
      facet_grid(~ground_arousal_lab)

     # geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
  geom_jitter(width = .2, alpha = .2)+
    ylim(-1,1)

  # panel for many folks
  db_full4new_stim_screen_pupil_nopract %>%
  # subset(ssid == 314)%>%
    group_by(ssid)%>%
    mutate(BIO_CDA.SCR_z = scale(log1p(BIO_CDA.PhasicMax +.1))[,1])%>%
    mutate(arousal_z = scale(arousal +.1))%>%
  ggplot(aes(arousal_z,BIO_CDA.SCR_z, color =mediansplit_ground_valence , shape =mediansplit_ground_arousal))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    facet_wrap(~ssid)+
    ggpubr::stat_cor()

    db_full4new_stim_screen_pupil_nopract %>%
  # subset(ssid == 314)%>%
    group_by(ssid)%>%
    mutate(BIO_CDA.SCR_z = scale(log1p(BIO_CDA.PhasicMax +.1))[,1])%>%
    mutate(arousal_z = scale(arousal +.1))%>%
  ggplot(aes(pup_basCor,BIO_CDA.SCR_z))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    facet_wrap(~ssid)+
    ggpubr::stat_cor()

        db_full %>%
  # subset(ssid == 314)%>%
    group_by(ssid)%>%
    mutate(BIO_Mean_HR = scale(BIO_Mean_HR, scale = FALSE)[,1])%>%
    mutate(arousal_z = scale(arousal +.1))%>%
  ggplot(aes(BIO_Mean_HR,log1p(BIO_CDA.PhasicMax+.1)))+
    geom_point()+
    geom_smooth(aes(group = ssid),method = 'lm', se = F)
    facet_wrap(~ssid)+
    ggpubr::stat_cor()

Let's try some 3 d visualisations
continue here

````{r}

db_full4new_stim_screen_pupil_nopract_nt %>%
  group_by(ssid, mediansplit_ground_arousal, mediansplit_ground_valence,scr_utl)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  subset(scr_utl == "notoutlier")%>%
  ggplot(aes(mediansplit_ground_arousal , BIO_CDA.PhasicMax_z))+
    geom_jitter(alpha = .1, width = .1)+
  stat_summary(geom = 'pointrange')+
  stat_summary(aes(group = ssid), geom = "line", alpha = .1)+
  facet_grid(~mediansplit_ground_valence)

db_full4new_stim_screen_pupil_nopract_nt%>%
  ggplot(aes(BIO_CDA.PhasicMax_z))+
  geom_histogram()

db_full4new_stim_screen_pupil_nopract_nt<- db_full4new_stim_screen_pupil_nopract_nt%>%
  mutate(scr_utl = if_else(BIO_CDA.PhasicMax_z > 5, "outlier", "notoutlier"))

```

  # + arousal_c

```{r}
scr_models$scr_excluding_atypical<- lmer(log(BIO_CDA.AmpSum_collapsed+.1) ~  arousal_c*valence_c * TASc+
                                           (1| ssid) +
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data =  subset(db_full4new_stim_screen_pupil_nopract_nt, scr_utl == "notoutlier"))

summary(scr_models$scr_excluding_atypical)
plot(scr_models$scr_excluding_atypical)

interactions::interact_plot(scr_models$scr_excluding_atypical, pred = arousal_c, modx = valence_c, mod2 = TASc)

db_full4new_stim_screen_pupil_nopract_nt%>%
  ggplot(aes())

scr_models$scr1<- lmer(log(BIO_CDA.PhasicMax_collapsed+.1) ~  arousal_c*valence_c * TASc+
                                           (1| ssid) +
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data =  subset(db_full4new_stim_screen_pupil_nopract_nt, scr_utl == "notoutlier"))

summary(scr_models$scr1)
scr_models$scr1.2<- lmer(log1p(BIO_CDA.PhasicMax+.1) ~  TASc*arousal_c * valence_c+
                                           (1 | ssid)+
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data =  subset(db_full4new_stim_screen_pupil_nopract, Group == "NT", !is.na(Alexithymia)))

unique(db_full4new_stim_screen_pupil_nopract$ssid)
summary(scr_models$scr1.2)

db_full4new_stim_screen_pupil_nopract %>%
  group_by(ssid,Group)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  subset(Group == "NT")%>%
  ggplot(aes(TAS))+
  geom_histogram()

interactions::interact_plot(scr_models$scr1, pred = arousal_c, modx = valence_c, mod2 = TASc)

scr_models$scr1.1<- lmer(CDA.PhasicMax ~  arousal_c*valence_c * TASc+
                                           (1| ssid) +
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data =  subset(db_full4new_stim_screen_pupil_nopract_nt, scr_utl == "notoutlier"))

summary(scr_models$scr1.1)

interactions::interact_plot(scr_models$scr1.1, pred = arousal_c, modx = valence_c, mod2 = TASc)

scr_models$scr2<- lmer(BIO_CDA.ISCR_collapsed ~  arousal_c*valence_c *TASc+
                                           (1| ssid) +
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data =  subset(db_full4new_stim_screen_pupil_nopract_nt, scr_utl == "notoutlier"))

summary(scr_models$scr2)

interactions::interact_plot(scr_models$scr2, pred = arousal_c, modx = valence_c)

scr_models$scr2<- lmer(BIO_CDA.SCR_collapsed ~  arousal_c* valence_c *TASc+
                                           (1| ssid) +
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data =  subset(db_full4new_stim_screen_pupil_nopract, Group = "NT"))

summary(scr_models$scr2)

interactions::interact_plot(scr_models$scr2, pred = arousal_c, modx = valence_c)

# the effect of pupil is the opposite on scr

scr_models$scr3<- lmer(BIO_CDA.ISCR_collapsed ~  arousal_c * valence_c * TASc+
                                           (1| ssid) +
                                           (1 | stimIAPS),
                        REML = FALSE,
                        data =  subset(db_full4new_stim_screen_pupil_nopract_nt, scr_utl == "notoutlier"))

summary(scr_models$scr3)

interactions::interact_plot(scr_models$scr2, pred = arousal_c, modx = valence_c, mod2 = TASc)

# the effect of pupil is the opposite on scr

```

check scr on within individuals

```{r}

lm_objtest<- lm(BIO_CDA.PhasicMax_z ~ arousal * valence, data = db_full4new_stim_screen_pupil_nopract_nt)
lm_objtest_summ<-summary(lm_objtest)
lm_objtest_summ$coefficients
db_full4new_stim_screen_pupil_nopract_nt

lm_objtest[["coefficients"]][[2]]
lm_objtest[["coefficients"]][["arousal"]]
lm_objtest[["coefficients"]][["valence"]]

regression_df <- data.frame(ssid= rep(NA, 50), Estimate_arousal= rep(NA, 50), 
                         Estimate_valence= rep(NA, 50),
                         Estimate_int= rep(NA, 50),
                         p_arousal= rep(NA, 50), 
                         p_valence= rep(NA, 50),
                         p_int= rep(NA, 50))

lm_ind_summary$coefficients[[14]]

ssid<- unique(db_full4new_stim_screen_pupil_nopract_nt$ssid)

db_full4new_stim_screen_pupil_nopract_nt<- db_full4new_stim_screen_pupil_nopract_nt%>%
  group_by(ssid)%>%
  mutate(arousal_z_ssid = scale(arousal - mean(arousal, na.rm = TRUE))[,1],
         valence_z_ssid = scale(valence - mean(valence, na.rm = TRUE))[,1])

i = 1

rm(b)

# debug
ssid_tes<- unique(db_full4new_stim_screen_pupil_nopract_nt$ssid_num)

table(is.na(db_full4new_stim_screen_pupil_nopract_nt$BIO_CDA.PhasicMax_z))
lm_ind  <- lm(BIO_CDA.PhasicMax_z ~ arousal_z_ssid *valence_z_ssid,
                      data = subset(db_full4new_stim_screen_pupil_nopract_nt, !is.na(BIO_CDA.PhasicMax_z) &
                                    ssid_num == ssid_tes[10]))

subset(db_full4new_stim_screen_pupil_nopract_nt, !is.na(BIO_CDA.PhasicMax_z) &
                                    ssid_num == ssid_tes[10])

```

```{r}
i = 1
rm(b)

for (b in 5:length(ssid_tes)) {
  # for (s in 1:length(nsim)) {

    message(sprintf("$$$$$RUNING lmer for ssid %i", ssid_tes[b]))
    # db_of7_new_JEFFE$VideoType_contrast_sample<- sample((rep(c(-.5, .5), each =  1920)), replace = FALSE) 
        #run the model on the current time bin and simulation sumber
        lm_ind  <- lm(BIO_CDA.PhasicMax_z ~ arousal_z_ssid *valence_z_ssid,
                      data = subset(db_full4new_stim_screen_pupil_nopract_nt, !is.na(BIO_CDA.PhasicMax_z) & 
                                    mediansplit_ground_valence == "More negative"&
                                     ssid_num == ssid_tes[b]))

        #store results from the simulation
            lm_ind_summary<- summary(lm_ind)
            regression_df[i,1]<- ssid_tes[b] #save ssid
            regression_df[i,2]<- lm_ind_summary$coefficients[[2]] # arousal beta
            regression_df[i,3]<-lm_ind_summary$coefficients[[3]] # valence beta
            regression_df[i,4]<-lm_ind_summary$coefficients[[4]] # inyteraction beta
            regression_df[i,4]<-lm_ind_summary$coefficients[[4]] 
            regression_df[i,5]<- lm_ind_summary$coefficients[[14]]
            regression_df[i,6]<- lm_ind_summary$coefficients[[15]]
            regression_df[i,7]<- lm_ind_summary$coefficients[[16]]

            lm_ind_summary$coefficients[[14]]
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            # timecourse_result_df_neg[i,5] <-ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
            #                                        != 0,
            #                                    lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}

View(regression_df)

 lm_ind_summary$coefficients[[4]]
# whether I use ground valence, self valemce or this sample average valence, I get the same patterns

timecourse_result_df_neg%>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .1, color = 'red', size = 1.5)

t.test(regression_df$Estimate_arousal)

ssid# just positive
regression_df <- data.frame(ssid= rep(NA, 50), Estimate_arousal= rep(NA, 50), 
                         Estimate_valence= rep(NA, 50),
                         Estimate_int= rep(NA, 50),
                         p_arousal= rep(NA, 50), 
                         p_valence= rep(NA, 50),
                         p_int= rep(NA, 50))

```

```{r}

scatter3D(x, y, z, clab = c("Sepal", "Width (cm)"))

db_full4new_stim_screen_pupil_nopract_nt

install.packages("plot3D")
install.packages("misc3d")
library(misc)

plot3D::scatter3D(db_full4new_stim_screen_pupil_nopract_nt$pup_basCor, 
          db_full4new_stim_screen_pupil_nopract_nt$arousal_c, 
          db_full4new_stim_screen_pupil_nopract_nt$valence_c)

 install.packages("plot3D", dependencies = TRUE)

  install.packages("misc3d", repo = 'https://mac.R-project.org')

install.packages(c("rgl", "car"))

library(car)

install.packages("car", dependencies = TRUE)

car::scatter3d(db_full4new_stim_screen_pupil_nopract_nt$arousal_c, 
          db_full4new_stim_screen_pupil_nopract_nt$pup_basCor, 
          db_full4new_stim_screen_pupil_nopract_nt$valence_c,
          fit = "smooth"
          # point = FALSE,

          # surface = FALSE,
          # point.col = ""
          )

```

gg = ggplot(db_full4new_stim_screen_pupil_nopract_nt, aes(BIO_CDA.PhasicMax_z, arousal_c)) +
  stat_density_2d(aes(fill = stat(db_full4new_stim_screen_pupil_nopract_nt$valence_c)), 
                  geom = "polygon",
                  n = 100,bins = 10,contour = TRUE) +
  # facet_wrap(clarity~.) +
  scale_fill_viridis_c(option = "A")

rayshader::plot_gg(gg,multicore=TRUE,width=5,height=5,scale=250)

scr<- db_full4new_stim_screen_pupil_nopract_nt$BIO_CDA.PhasicMax_z
arousal<- db_full4new_stim_screen_pupil_nopract_nt$arousal_c

valence = db_full4new_stim_screen_pupil_nopract_nt$valence_c

gg = ggplot(db_full4new_stim_screen_pupil_nopract_nt, aes(BIO_CDA.PhasicMax_z, arousal_c)) +
  stat_density_2d(aes(fill = stat(valence_c)), 
                  geom = "polygon",
                  # n = 100,bins = 10,
                  contour = TRUE) +
  # facet_wrap(clarity~.) +
  scale_fill_viridis_c(option = "A")
rayshader::plot_gg(gg,multicore=TRUE,width=5,height=5,scale=250)
gg
#No lines
pp_nolines = ggplot(db_full4new_stim_screen_pupil_nopract_nt, aes(x=BIO_CDA.PhasicMax_z, y=arousal_c)) +
  geom_point(aes(color = valence_c))
  scale_fill_viridis_c(a)

rayshader::plot_gg(pp_nolines, width = 4, height = 4, scale = 300, multicore = TRUE)
pp_nolines

?scatter3d
scatter3d(x = arousal, 
          y = valence, z = scr, 
          fit = "smooth",

          # surface = FALSE,
          point.col = "blue", 
          # point
          groups = as.factor(db_full4new_stim_screen_pupil_nopract_nt$mediansplit_sample_valence2), 
          ellipsoid = FALSE)

scatter3d(x = db_full4new_stim_screen_pupil_nopract_nt$pup_basCor, 
          y = db_full4new_stim_screen_pupil_nopract_nt$BIO_CDA.PhasicMax_z, z = db_full4new_stim_screen_pupil_nopract_nt, 
          fit = "smooth",

          # surface = FALSE,
          point.col = "blue", 
          # point
          groups = as.factor(db_full4new_stim_screen_pupil_nopract_nt$mediansplit_ground_valence), 
          ellipsoid = FALSE)

library(viridisLite)
install.packages("viridis")
library(viridis)
deathgg = ggplot(db_full4new_stim_screen_pupil_nopract_nt) +
  geom_tile(aes(x=arousal_c,y=pup_basCor,fill=valence_c))+
  # scale_x_continuous("Year",expand=c(0,0),breaks=seq(1900,2010,10)) +
  # scale_y_continuous("Age",expand=c(0,0),breaks=seq(0,100,10),limits=c(0,100)) +
  scale_fill_viridis()
  # ggtitle("Death Probability vs Age and Year for the USA") +
  # labs(caption = "Data Source: US Dept. of Social Security")

rayshader:: plot_gg(deathgg, multicore=TRUE)
height=5,width=6,scale=500

```

heart rate

```{r}

unique(db_full6new$Bio_Mean_HR)
unique(db_full6new$Bio_Mean_HR_fix)

View(db_full6new)

db_full4new_stim_screen_pupil_nopract
  db_full4new_stim_screen_pupil_nopract %>%
  # subset(ssid == 314)%>%
    group_by(ssid)%>%
    mutate(BIO_CDA.SCR_z = scale(log1p(BIO_CDA.PhasicMax +.1))[,1])%>%
    mutate(arousal_z = scale(arousal +.1))%>%
  ggplot(aes(arousal_z,BIO_CDA.SCR_z, color =mediansplit_ground_valence , shape =mediansplit_ground_arousal))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    facet_wrap(~ssid)+
    ggpubr::stat_cor()

```

```

```{r}

# keep stim and and fixation

unique(db_full6new$screencontent)
unique(db_full6new$screencontent_no)
db_full6new_hr_fix_stim<- subset(db_full6new, screencontent_no <3)
View(db_full6new_hr_fix_stim)
# fixation"    "stim"

# keep controls
unique(db_full6new_hr_fix_stim$ssid)
db_full6new_hr_fix_stim$ssid_num <- as.numeric(as.character(db_full6new_hr_fix_stim$ssid))

db_full6new_hr_fix_stim_nt<- subset(db_full6new_hr_fix_stim, Group == "NT")
unique(db_full6new_hr_fix_stim_nt$ssid_num)

db_full6new_hr_fix_stim_nt<- subset(db_full6new_hr_fix_stim, ssid_num> 303)
unique(db_full6new_hr_fix_stim_nt$ssid)

# HR differences
db_full6new_hr_fix_stim_nt$Bio_Mean_HR_fix<- if_else(db_full6new_hr_fix_stim_nt$screencontent_no ==1, db_full6new_hr_fix_stim_nt$Bio_Mean_HR, NULL)

View(db_full6new_hr_fix_stim_nt)

library(dplyr)
library(tidyverse)
db_full6new_hr_fix_stim_nt1<- db_full6new_hr_fix_stim_nt %>%
  group_by(ssid, tNo) %>%
  arrange(ssid, tNo,screencontent_no)%>%
  fill(Bio_Mean_HR_fix, .direction = "down")%>%
  subset(screencontent_no == 2)

View(db_full6new_hr_fix_stim_nt1)

db_full6new_hr_fix_stim_nt1<- db_full6new_hr_fix_stim_nt1 %>%
  mutate(Bio_Mean_HR_dif = Bio_Mean_HR - Bio_Mean_HR_fix)
# 2 1
stim - fix
db_full6new_hr_fix_stim_nt1%>%
  ggplot(aes(Bio_Mean_HR_dif))+
  geom_histogram()

?scatter3d

db_full6new_hr_fix_stim_nt1%>%
  subset(!is.na(pup_basCor))%>%
   subset(!is.na(BIO_CDA.PhasicMax_z))%>%
  subset(!is.na(Bio_Mean_HR_dif))

db_full6new_hr_fix_stim_nt1<- db_full6new_hr_fix_stim_nt1%>%
  group_by(ssid)%>%
  mutate(BIO_CDA.PhasicMax_z= scale(BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])

scatter3d(x = db_full6new_hr_fix_stim_nt1$pup_basCor, 
          y = db_full6new_hr_fix_stim_nt1$BIO_CDA.PhasicMax_z, 
          z = db_full6new_hr_fix_stim_nt1$Bio_Mean_HR_dif, 
          fit = "smooth",

          surface = FALSE,
          point.col = "blue",
          # point
          groups = as.factor(db_full6new_hr_fix_stim_nt1$mediansplit_ground_arousal),
          ellipsoid = TRUE)

cor(db_full6new_hr_fix_stim_nt1[,c("pup_basCor", "BIO_CDA.PhasicMax_z","Bio_Mean_HR_dif")], use = "complete")

db_full6new_hr_fix_stim_nt1%>%
  group_by(ssid,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(pup_basCor,BIO_CDA.PhasicMax_z, color= mediansplit_ground_valence))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ylim(0,.4)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1%>%
  # group_by(ssid)%>%
  # mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif))
  group_by(ssid,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(pup_basCor,Bio_Mean_HR_dif_z, color= mediansplit_ground_valence))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  # ylim(-7,2)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  # group_by(ssid)%>%
  # mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif))
  group_by(ssid,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(BIO_CDA.PhasicMax_z,Bio_Mean_HR_dif, color= mediansplit_ground_valence))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  # ylim(-7,2)+
  ggpubr::stat_cor()+
  facet_grid(~mediansplit_ground_valence)

```

```{r}

db_full6new_hr_fix_stim_nt1$Bio_Mean_HR_dif_outl<- if_else(abs(db_full6new_hr_fix_stim_nt1$Bio_Mean_HR_dif)>
                                                             (median(abs(db_full6new_hr_fix_stim_nt1$Bio_Mean_HR_dif),na.rm = TRUE) +                                                                                                        (4*(sd(abs(db_full6new_hr_fix_stim_nt1$Bio_Mean_HR_dif), na.rm = TRUE)))), "outlier", "not outlier")

db_full6new_hr_fix_stim_nt1%>%
  ggplot(aes(Bio_Mean_HR_dif))+
  geom_histogram()+
  facet_grid(~Bio_Mean_HR_dif_outl)

```

```{r}
db_full6new_hr_fix_stim_nt1 %>%
    subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  subset(ssid_num<500)%>%
  group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif_ssid = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
  group_by(ssid)%>%
  # mutate(Bio_Mean_HR_dif_stim = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TASc, Bio_Mean_HR_dif))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1 %>%
    subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  subset(ssid_num<500)%>%
  # group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif = abs(Bio_Mean_HR_dif))%>%
  group_by(ssid, stimIAPS)%>%
  mutate(Bio_Mean_HR_dif_stim = abs(Bio_Mean_HR_dif))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TASc, Bio_Mean_HR_dif))+
  # geom_point()

  geom_smooth(aes(group = stimIAPS, y =Bio_Mean_HR_dif_stim), method=lm, se=FALSE, colour = "gray40", alpha = .01,linetype="dashed", size = .2 )+
  geom_smooth( method=lm, se=FALSE, linetype="dashed",
             color="darkred", size = 2)+
  stat_summary(geom = 'pointrange', pch = 1)+

  # geom_point()+
  # stat_summary(aes(group =ssid, y = Bio_Mean_HR_dif),method = "line",alpha = .1)+
  # ggpubr::stat_cor()+
  p$graphstyle+
  xlab("Alexithymia (Z)")+
  ylab("HR difference")+
p$graphstyle

hr_bio <- lmer(Bio_Mean_HR_dif ~ TASc *arousal_c + (1|ssid) + (1| stimIAPS),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1, Bio_Mean_HR_dif_outl == "not outlier"))

interactions::interact_plot(hr_bio, pred = arousal_c, modx = TASc)

subset(db_full6new_hr_fix_stim_nt1, Bio_Mean_HR_dif_outl == "not outlier")

```

```{r}
db_full6new_hr_fix_stim_nt1 %>%
  subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  group_by(ssid)%>%
  mutate(cor_hrdif_ar = cor(Bio_Mean_HR_dif, arousal_c))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TAS, cor_hrdif_ar))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  p$graphstyle

db_full6new_hr_fix_stim_nt1 %>%
  subset(TAS<70)%>%
  subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  group_by(ssid,mediansplit_ground_valence)%>%
  mutate(cor_hrdif_ar = cor(Bio_Mean_HR_dif, arousal_c))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_valence, cor_hrdif_ar))+
  geom_jitter(alpha = .1, width = .1)+
  stat_summary(geom = 'pointrange')
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  p$graphstyle

```

db_full6new_hr_fix_stim_nt1 %>%
  # subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  group_by(ssid)%>%
  mutate(cor_hrdif_ar = cor(Bio_Mean_HR_dif, arousal_c))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TAS, cor_hrdif_ar))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

```{r}
db_full6new_hr_fix_stim_nt1<- db_full6new_hr_fix_stim_nt1%>%
  group_by(stimIAPS)%>%
  mutate(ValenceMeanThisSample = mean(valence, na.rm = TRUE), 
         ArousalMeanThisSample = mean(arousal, na.rm = TRUE))

db_full6new_hr_fix_stim_nt1<- db_full6new_hr_fix_stim_nt1%>%
  ungroup()%>%
  mutate(mediansplit_ground_valence = if_else(ValenceMean >=
                                                  median(ValenceMean,
                                                         na.rm = TRUE), "More positive", "More negative"))%>%
  mutate(mediansplit_ground_arousal = if_else(ArousalMean >=
                                                  median(ArousalMean,
                                                         na.rm = TRUE), "High", "Low"))%>%
    mutate(mediansplit_sample_valence2 = if_else(ValenceMeanThisSample >=
                                                  median(ValenceMeanThisSample,
                                                         na.rm = TRUE), "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >=
                                                  median(ArousalMeanThisSample,
                                                         na.rm = TRUE), "High", "Low"))

db_full6new_hr_fix_stim_nt1%>%
  subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  group_by(ssid,mediansplit_ground_arousal, mediansplit_ground_valence,)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_arousal, Bio_Mean_HR_dif))+
  geom_jitter(alpha = .2, width = .2)+
   geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
  stat_summary(geom = 'pointrange')+
  # stat_smooth(aes(group = ssid), se = F, method = 'lm', alpha = .2)+
    facet_grid(~mediansplit_ground_valence)

```

```{r}  
db_full6new_hr_fix_stim_nt1%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(Bio_Mean_HR_dif_outl== "not outlier")%>%
  group_by(ssid, mediansplit_ground_arousal,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_arousal, Bio_Mean_HR_dif, fill = mediansplit_ground_valence))+
  geom_jitter(alpha = .2, width = .2)+
   geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
  stat_summary(geom = 'pointrange')+
  stat_summary(aes(group = ssid), geom = 'line', alpha = .2)+

  facet_grid(~mediansplit_ground_valence)+
     ggpubr::stat_compare_means()
  # p$graphstyle+
  scale_fill_brewer(palette = "Dark2")+

```
  # stat_smooth(aes(group = ssid), se = F, method = 'lm', alpha = .2)

db_full6new_hr_fix_stim_nt1%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  group_by(ssid, mediansplit_ground_arousal,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_arousal, Bio_Mean_HR_dif))+
  geom_jitter(alpha = .2, width = .2)+
   geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
  stat_summary(geom = 'pointrange')+
  ggpubr::stat_compare_means()+
  facet_grid(~mediansplit_ground_valence)

# self

db_full6new_hr_fix_stim_nt1%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  group_by(ssid, mediansplit_sample_arousal2,mediansplit_sample_valence2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_sample_arousal2, Bio_Mean_HR_dif))+
  geom_jitter(alpha = .2, width = .2)+
  stat_summary(aes(group = ssid), geom = 'line', alpha = .1, size = .4, colour = "Black") +
   # geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
  stat_summary(geom = 'pointrange')+
  ggpubr::stat_compare_means()+
  facet_grid(~mediansplit_sample_valence2)

lmer(
  db_full6new_hr_fix_stim_nt1)

db_full6new_hr_fix_stim_nt1%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal))+
  geom_histogram()

```{r}
# test - analyse just positive
hr_dif_models$arousal_val <- lmer(Bio_Mean_HR_dif ~  valence_c *arousal_c+
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1, mediansplit_ground_valence == "More positive" & Bio_Mean_HR_dif_outl == "not outlier"  & Group == "NT"))

summary(hr_dif_models$arousal_val)

unique(db_full6new_hr_fix_stim_nt1$ssid)
hr_dif_models$valfrom_hr <- lmer(valence_c ~   Bio_Mean_HR_dif* arousal_c+
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1, mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier" & Group == "NT"))
arousal_c

summary(hr_dif_models$valfrom_hr)

interactions::interact_plot(hr_dif_models$valfrom_hr, pred = Bio_Mean_HR_dif, modx = arousal_c)

plot(hr_dif_models$arousal_val)

car::vif(hr_dif_models$arousal_val)
 # valence_c           arousal_c valence_c:arousal_c 
           # 1.767605            1.708642            1.070635

?step
?lmerTest::step()
lmerTest::step(hr_dif_models$arousal_val)

# favours valence

# check the response bias thing
db_full6new_hr_fix_stim_nt1 %>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  ggplot(aes(log10(arousal+10.5) ,Bio_Mean_HR_dif))+
    # geom_point(alpha = .1)+
    facet_grid(~mediansplit_ground_valence)+
  geom_smooth(method = 'lm', se = F)+
  ggside::geom_ysidedensity(aes(x=stat(density, fill = mediansplit_self_valence), alpha = .4))+
ggside::geom_xsidedensity(aes(y=stat(density, fill = mediansplit_self_valence), alpha = .4))

scatter3d(x = db_full6new_hr_fix_stim_nt1$valence_c, 
          y =db_full6new_hr_fix_stim_nt1$Bio_Mean_HR_dif, z =db_full6new_hr_fix_stim_nt1$arousal_c,
          # fit = "smooth",

          # surface = FALSE,
          point.col = "blue", 
          # point
          # ellipsoid = db_full6new_hr_fix_stim_nt1$mediansplit_sample_valence2)
          ellipsoid = TRUE)

db_full6new_hr_fix_stim_nt1%>%
  group_by(stimIAPS, mediansplit_ground_valence, mediansplit_ground_arousal)%>%
  ggplot(aes(mediansplit_ground_valence, ValenceMean))+
  geom_point()

db_full6new_hr_fix_stim_nt1%>%
  subset(Condition == "IAPS")%>%
  group_by(stimIAPS, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_valence, arousal))+
  stat_summary(geom = 'pointrange')+
  ggpubr::stat_compare_means()+
  geom_text(aes(label = stimIAPS))

```

check corelation between arousal and valence on and individual basis

```{r}

db_full6new_hr_fix_stim_nt1$arousal_c
subset(db_full6new_hr_fix_stim_nt1, mediansplit_ground_valence == "More positive" & Bio_Mean_HR_dif_outl == "not outlier") %>%
  group_by(ssid)%>%
  mutate(cor_vale_ar = cor(arousal, valence, use  = "complete"))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(cor_vale_ar))+
    geom_histogram()+
  geom_vline(xintercept = -.7)

subset(db_full6new_hr_fix_stim_nt1)%>%
  # group_by(mediansplit_ground_valence, stimIAPS)%>%
  # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes( valence, arousal))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  # geom_smooth(aes(group = ssid), se  = F, method = 'lm')+
  # facet_grid(~mediansplit_ground_valence)+
  ggpubr::stat_cor()

subset(db_full6new_hr_fix_stim_nt1)%>%
  subset(ssid == 331)%>%
  # group_by(mediansplit_ground_valence, stimIAPS)%>%
  # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes( as.numeric(tNo), arousal))+
  geom_point()+
  stat_summary(geom = "line")+
  geom_point(aes(y = valence), color = "green")+
  stat_summary(aes(y = valence),geom = "line", linetype = "dashed", color = "green")
  # geom_smooth(method = 'lm', se = F)+
  # geom_smooth(aes(group = ssid), se  = F, method = 'lm')+
  # facet_grid(~mediansplit_ground_valence)+
  # ggpubr::stat_cor()

```

# try and regress valence our oarousal_val

db_full6new_hr_fix_stim_nt2

db_full6new_hr_fix_stim_nt3<- subset(db_full6new_hr_fix_stim_nt2, !is.na(valence))

hr_dif_models$arosal_from_val <- lmer(arousal_c~  valence_c +
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt3))

hr_dif_models$val_from_arousal <- lmer(valence_c~arousal_c+
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt3))

hr_dif_models$arosal_from_val
plot(hr_dif_models$arosal_from_val)

?residuals
?resid
?residuals.merMod
db_full6new_hr_fix_stim_nt3$arous_val_resid <- residuals(hr_dif_models$arosal_from_val)

db_full6new_hr_fix_stim_nt3$val_from_arous_resid<- residuals(hr_dif_models$val_from_arousal)

# residuals.merMod(hr_dif_models$arosal_from_val)

ar_frm_val<- lm(arousal_c ~ valence_c, data = db_full6new_hr_fix_stim_nt3)

val_frm_val<- lm( valence_c~arousal_c, data = db_full6new_hr_fix_stim_nt3)

db_full6new_hr_fix_stim_nt3%>%ggplot(aes(val_from_arous_resid, arous_val_resid))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

```

resid(ar_frm_val)
resid(val_frm_val)
 #           1            2            3            4            5            6            7            8 
 # 0.149962843  0.505815507
 # 
 # -0.637512958  0.044580602

Is the residual of A~ B the same as B~A 
```{r}

hr_dif_models$val_from_arousal <- lmer(valence_c~arousal_c+
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt3))

hr_dif_models$biohr_dif_arous_res <- lmer(Bio_Mean_HR_dif~  val_from_arous_resid *arous_val_resid+
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt3, Bio_Mean_HR_dif_outl == "not outlier"))

summary(hr_dif_models$biohr_dif_arous_res)

# analyses of residuals also suggets that effects on bio_hr are related to common arousal and valence relation

```

interactions::interact_plot(hr_dif_models$arousal_val, pred= arousal_c, modx = valence_c)

# alexithjymia
db_full6new_hr_fix_stim_nt1$Bio_Mean_HR_dif_z<- scale(db_full6new_hr_fix_stim_nt1$Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1]
hr_dif_models$arousal_val_cat <- lmer(Bio_Mean_HR_dif_z ~TASc*arousal_c+
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = db_full6new_hr_fix_stim_nt1)

interactions::interact_plot(hr_dif_models$arousal_val_cat, pred= arousal_c, modx = TASc)

summary(hr_dif_models$arousal_val_cat)

plot(hr_dif_models$arousal_val)
plot(hr_dif_models$arousal_val_cat)

```
summary(hr_dif_models$arousal_val_cat)

hr_dif_models$arousal_val_cat <- lmer(Bio_Mean_HR_dif~  mediansplit_sample_arousal2* mediansplit_sample_valence2+
                                        + (1+mediansplit_sample_valence2 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = db_full6new_hr_fix_stim_nt1)

summary(hr_dif_models$arousal_val_cat)

interactions::cat_plot(hr_dif_models$arousal_val_cat, pred = mediansplit_sample_arousal2, modx = mediansplit_sample_valence2)

```
# correlation

```{r}
db_full6new_hr_fix_stim_nt1%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  group_by(ssid,mediansplit_ground_valence, mediansplit_ground_arousal)%>%
  mutate(cor_hr_arous = cor(Bio_Mean_HR_dif, arousal, use = "complete"))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_valence, cor_hr_arous))+
  # geom_jitter(alpha = .2, width = .2)+
  geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
  stat_summary(geom = 'pointrange')+
  # geom_smooth(aes(group = ssid), color = 'gray', method = 'lm', se = F)+
  ggpubr::stat_compare_means()+
  facet_grid(~mediansplit_ground_arousal)

```
  # xlim(-5,3)

```{r}
db_full6new_hr_fix_stim_nt1 %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(Age, TASc))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

hr_dif_models<- list()

hr_dif_models$arousal_val <- lmer(Bio_Mean_HR_dif~  (arousal_c*valence_c )* TASc +(1+arousal_c | ssid) + (1|stimIAPS),
     REML = FALSE,
     data = db_full6new_hr_fix_stim_nt1)

summary(hr_dif_models$arousal_val)

interactions::interact_plot(hr_dif_models$arousal_val, pred = arousal_c, modx = TASc)

hr_dif_models$arousal_val <- lmer(Bio_Mean_HR~  arousal_c* valence_c +(1+arousal_c| ssid),
                                  # + (1|stimIAPS),
     REML = FALSE,
     data = db_full6new_hr_fix_stim_nt1)

summary(hr_dif_models$arousal_val)

# plot(hr_dif_models$arousal_val)

interactions::interact_plot(hr_dif_models$arousal_val, pred = valence_c, modx = arousal_c)

```

```

import HRV resting
```{r}

Rest_HRV <- read_excel("Rest HRV.xlsx")
View(Rest_HRV)

Rest_HRV%>%
  ggplot(aes(RMSSD))+
  geom_histogram()

Rest_HRV%>%
  ggplot(aes(RMSSD))+
  geom_histogram()

Rest_HRV%>%
  ggplot(aes(MEANHR))+
  geom_histogram()

BIO_HRVanalysys$ssid<- as.character(BIO_HRVanalysys$ssid)

left_join(BIO_HRVanalysys, Rest_HRV, by = "ssid")%>%
  ggplot(aes(RMSSD, RMMSSD))+
  geom_point()+
  ggpubr::stat_cor()

# library(readxl)

Rest_practice_HRV <- read_excel("Rest + practice HRV.xlsx")
View(Rest_practice_HRV)
Rest_practice_HRV$ssid<- as.character(Rest_practice_HRV$ssid)

left_join(Rest_practice_HRV, BIO_HRVanalysys, by = "ssid")%>%
  ggplot(aes(RMSSD, RMMSSD))+
  geom_point()+
  ggpubr::stat_cor()

left_join(Rest_practice_HRV, Rest_HRV, by = "ssid")%>%
  ggplot(aes(RMSSD.x, RMSSD.y))+
  geom_point()+
  ggpubr::stat_cor()

Rest_practice_HRV%>%
  ggplot(aes(MEANHR))+
  geom_histogram()

# import hrv task
library(readxl)
hrvResultsTask <- read_excel("Summary_hrvResultsTask.xls")
View(hrvResultsTask)

```

combine with data

```{r}
Rest_HRV

Rest_HRV$subject<- NULL
nrow(db_full6new_hr_fix_stim_nt1)
# 2160

db_full6new_hr_fix_stim_nt2<- left_join(db_full6new_hr_fix_stim_nt1, Rest_HRV)

# hrv rest vs hrtaskCallbackManager(
left_join(Rest_HRV, hrvResultsTask, by = "ssid") %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(RMSSD.x, RMSSD.y))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  xlim(0,100)+
  ylim(0,100)

Rest_HRV$hrvcondition<- "rest"
hrvResultsTask$hrvcondition<- "task"

left_join(Rest_HRV, hrvResultsTask, by = "ssid") %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(RMSSD.x, RMSSD.y))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  xlim(0,100)+
  ylim(0,100)

colnames(hrvResultsTask)
bind_rows(Rest_HRV, hrvResultsTask)%>%
  subset(RMSSD<100)%>%
  ggplot(aes(hrvcondition, hfpower))+
  geom_jitter(width = .1, alpha = .1)+
  stat_summary(geom = 'pointrange')+
  stat_summary(aes(group = ssid), geom = 'line', alpha = .1)
```

```{r}
left_join(db_full6new_hr_fix_stim_nt1, hrvResultsTask) %>%
  group_by(ssid)%>%
  mutate(cor = cor(arousal, pup_basCor, use = "complete"))%>%
    group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(NN50,cor ))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  xlim(0,500)+
  ggpubr::stat_cor()

  left_join(db_full6new_hr_fix_stim_nt1, hrvResultsTask) %>%
  group_by(ssid)%>%
  mutate(cor = cor(arousal, pup_basCor, use = "complete"))%>%
    group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TASc, NN50))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
      # ylim(0,200)+
  ggpubr::stat_cor()

  hrvResultsTask%>%
    ggplot(aes(RMSSD))+
    geom_histogram()

  left_join(db_full6new_hr_fix_stim_nt1, hrvResultsTask) %>%
    subset(!is.na(mediansplit_ground_valence))%>%
  # group_by(ssid)%>%
  # mutate(cor = cor(arousal, pup_basCor, use = "complete"))%>%
    group_by(ssid,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(RMSSD,pup_basCor,color = mediansplit_ground_valence ))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  # xlim(0,100)+
  ggpubr::stat_cor()

    left_join(db_full6new_hr_fix_stim_nt1, hrvResultsTask) %>%
    subset(!is.na(mediansplit_ground_valence))%>%
  # group_by(ssid)%>%
  # mutate(cor = cor(arousal, pup_basCor, use = "complete"))%>%
    group_by(ssid,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(RMSSD,BIO_CDA.PhasicMax_z,color = mediansplit_ground_valence ))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  xlim(0,100)+
  ggpubr::stat_cor()

    left_join(db_full6new_hr_fix_stim_nt1, hrvResultsTask) %>%
    subset(!is.na(mediansplit_ground_valence))%>%
       subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  # group_by(ssid)%>%
  # mutate(cor = cor(arousal, pup_basCor, use = "complete"))%>%
    group_by(ssid,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(`LF/HF`,BIO_CDA.PhasicMax_z,color = mediansplit_ground_valence ))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  # xlim(0,5000)+
  ggpubr::stat_cor()
```

db_full6new_hr_fix_stim_nt2 %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(Bio_Mean_HR_dif, lfpower))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt2 %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(MEANHR, RMSSD))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt2 %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(MEANHR, Bio_Mean_HR))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

```

```{r}
# work on this
db_full6new_304_up$
colnames(db_full4new_stim_screen_pupil_nopract)
colnames(db_full6new_304_up)
# db_full6new
unique(db_full6new_304_up$screencontent)

View(db_full6new)

# store heart rate baseline to compute difference
db_full6new$Bio_Mean_HR_fix = if_else(db_full6new$screencontent == "fixation", db_full6new$Bio_Mean_HR, NULL)

# compute heart rate difference to fixation screen

db_full6new_304_up$Bio_Mean_HR
View(db_full6new_304_up)

db_full6new_304_up<- db_full6new_304_up%>%
  group_by(ssid)%>%
  mutate(BIO_CDA.PhasicMax_z = scale(BIO_CDA.PhasicMax)[,1])

pupulresidtest<- lmer(pup_basCor ~ BRIGHTNESSc +(1+BRIGHTNESSc|ssid), REML = FALSE,
     data = testresiddf)

summary(pupulresidtest)

plot(pupulresidtest)

resid(pupulresidtest)
tstresid <- resid(pupulresidtest)

testresiddf$puopil_resid <- tstresid

testresiddf<- subset(db_full6new_304_up, !is.na(pup_basCor))

summary(lmer(arousal ~ pupil_resid + (1|ssid), REML = FALSE,
     data = testresiddf))

summary(lmer(arousal ~ puopil_resid + Bio_Mean_HR+BIO_CDA.PhasicMax + (1|ssid),
              # (0+puopil_resid + Bio_Mean_HR+BIO_CDA.PhasicMax|ssid), 
             REML = FALSE,
     data = subset(testresiddf, as.numeric(as.character(ssid))<500)))

subset(testresiddf, as.numeric(as.character(ssid))<500)%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(arousal, BIO_CDA.PhasicMax))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

subset(testresiddf, as.numeric(as.character(ssid))<500)%>%
  mutate(median_ground_arousal = if_else(ArousalMean> median(ArousalMean, na.rm = TRUE), "High", "Low"))%>%
  mutate(median_ground_valence = if_else(ValenceMean> median(ValenceMean, na.rm = TRUE), "More positive", "More negative"))%>%
  group_by(ssid)%>%
  ungroup()%>%
  mutate(median_self_arousal = if_else(arousal> median(arousal), "High", "Low"))%>%
  mutate(median_self_valence = if_else(valence> median(valence), "Positive", "Negative"))%>%
group_by(ssid,median_self_arousal,median_self_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(median_self_arousal, puopil_resid,))+
  geom_jitter(width = .2, alpha = .2)+
   geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
  stat_summary(geom = 'pointrange')+
    facet_grid(~median_self_valence)
  ggpubr::stat_cor()

  subset(testresiddf, as.numeric(as.character(ssid))<500)%>%
  mutate(median_ground_arousal = if_else(ArousalMean> median(ArousalMean, na.rm = TRUE), "High", "Low"))%>%
  mutate(median_ground_valence = if_else(ValenceMean> median(ValenceMean, na.rm = TRUE), "More positive", "More negative"))%>%
  group_by(ssid)%>%
  mutate(median_self_arousal = if_else(arousal> median(arousal), "High", "Low"))%>%
  mutate(median_self_valence = if_else(valence> median(valence), "Positive", "Negative"))%>%
group_by(ssid,median_self_arousal)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
    subset(!is.na(median_self_arousal))%>%
  ggplot(aes(median_self_arousal, BIO_CDA.PhasicMax_z))+
  geom_jitter(width = .2, alpha = .2)+
   geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
    # geom_smooth(aes(group = ssid),method = 'lm', se = F)+
    # geom_text(aes(label = ssid))
  stat_summary(geom = 'pointrange')
    facet_grid(~median_self_valence)
  ggpubr::stat_cor()

  summary(lmer(arousal ~ log(BIO_CDA.PhasicMax+.1) + (1|ssid) + (1+log(BIO_CDA.PhasicMax+.1)|stimIAPS),
              # (0+puopil_resid + Bio_Mean_HR+BIO_CDA.PhasicMax|ssid), 
             REML = FALSE,
     data = subset(testresiddf, as.numeric(as.character(ssid))<500 &BIO_CDA.AmpSum> .1)))

```

### 2021-07-23 Paper_Analyses_subj_obje_arousal.Rmd
started working on issue #1

@@
 Code for the paper: Valence modulated “subjective-objective” arousal
+
+data<- lastopened
 
@@
 
+nrow(tmp.df4_full_stim_downs_jun2021)
+
 # import the timecourse
 
+nrow(tmp.df4_full_stim_downs_jun2021)
 tmp.df4_full_stim_downs_jun2021 <- readRDS("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/tmp.df4_full_stim_downs_jun2021.rds")
 
-# merge with behavioral data
-unique(db_full4new_stim_screen_pupil_nopract$ssid)
-# colnames(db_full4new_stim_screen_pupil_nopract)
-# colnames(tmp.df4_full_stim_downs_jun2021)
-# db_full4new_stim
-# colnames(db_full4new_stim_screen_pupil_nopract)
 db_full4new_stim_subset<- db_full4new_stim_screen_pupil_nopract[,c(1:4,6:7,12:13,16,21:27, 31:56,80:81,84:96,98:114,116:124)]
@@
 tmp.df4_full_stim_downs_jun2021_with_beh2$tNo <- as.character(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)
+
 db_full4new_stim_subset$tNo <- as.character(db_full4new_stim_subset$tNo)
-unique(db_full4new_stim_subset$tNo)
-unique(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)
+# unique(db_full4new_stim_subset$tNo)
+# unique(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)
 
@@
 tmp.df4_full_stim_downs_jun2021_with_beh2$tNo<- as.numeric(tmp.df4_full_stim_downs_jun2021_with_beh2$tNo)
+
 tmp.df4_full_stim_downs_jun2021_with_beh2<- tmp.df4_full_stim_downs_jun2021_with_beh2%>%
@@
 
-tmp.df4_full_stim_downs_jun2021_with_beh<- left_join(tmp.df4_full_stim_downs_jun2021_with_beh2, db_full4new_stim_subset)
+tmp.df4_full_stim_downs_jun2021_with_beh <- left_join(tmp.df4_full_stim_downs_jun2021_with_beh2, db_full4new_stim_subset)
 
-db_full4new_stim_subset$tNo<- as.numeric(db_full4new_stim_subset$tNo)
+```
 
-table(is.na(db_full4new_stim_subset$arousal))
+# higher sample dataset
 
-tmp.df4_full_stim_downs_jun2021_with_behnew<- right_join(tmp.df4_full_stim_downs_jun2021_with_beh2, db_full4new_stim_subset,
-                                                     by = c('ssid', 'tNo'))
+```{r}
+library(ggplot2)
+library(tidyverse)
+install.packages("gazer")
+library(gazer)
 
-nrow(tmp.df4_full_stim_downs_jun2021_with_beh)
+tmp.df4_full_stim_downs_jun2021$tNo<- as.numeric(tmp.df4_full_stim_downs_jun2021$tNo)
+
+tmp.df4_full_stim_downs_jun2021_60bins<- left_join(tmp.df4_full_stim_downs_jun2021, db_full4new_stim_subset, by = c("ssid", "tNo", "trial"))
+
+# create a dataframe version where we downsample to60 and not to 30
+tmp.df4_full_stim_downs_jun2021_60bins$Label<- substr(tmp.df4_full_stim_downs_jun2021_60bins$stimIAPS, 1,8)
+
+tmp.df4_full_stim_downs_jun2021_60bins<- left_join(tmp.df4_full_stim_downs_jun2021_60bins, imageJ_IAPS, by = "Label")
+
+tmp.df4_full_stim_downs_jun2021_60bins$Mean_gray_z<- scale(tmp.df4_full_stim_downs_jun2021_60bins$Mean, center = TRUE, scale = TRUE)[,1]
+
+nrow(tmp.df4_full_stim_downs_jun2021_60bins)
 # 172168 good
-
-nrow(tmp.df4_full_stim_downs_jun2021_with_beh2)
-# 87529
-nrow(tmp.df4_full_stim_downs_jun2021_with_behnew)
-
-table(is.na(tmp.df4_full_stim_downs_jun2021_with_behnew$mediansplit_self_valence))
 
@@
 tmp.df4_full_stim_downs_jun2021_with_beh %>%
+  subset(!is.na(ground_arousal_lab))%>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  stat_smooth(aes(group= ground_arousal_lab, color = ground_arousal_lab), fun = mean,geom = "line",
+               se = F, alpha = .1, size = 1.5)+
+  stat_smooth(aes(group=ground_arousal_lab, color = ground_arousal_lab), size = 3)+  
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")+
+  xlim(0,6)+
+   facet_grid(~mediansplit_self_valence)
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
   subset(!is.na(ground_arousal_lab))%>%
@@
 
+# higher samp[le rate]
+
+tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins %>%
+  ungroup()%>%
+  mutate(mediansplit_sample_valence2 = 
+           if_else(ValenceMeanThisSample >= 
+                     median(ValenceMeanThisSample,
+                            na.rm = TRUE), 
+                   "More positive", "More negative"))%>%
+  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >=
+                                                  median(ArousalMeanThisSample,
+                                                         na.rm = TRUE), "High", "Low"))
+
 ```
@@
 let's test the interaction term
+<!-- 30 bins -->
 ```{r}
+
+# create number s for time bins
+tmp.df4_full_stim_downs_jun2021_with_behnew<- tmp.df4_full_stim_downs_jun2021_with_behnew%>%
+  group_by(ssid, tNo)%>%
+  mutate(timebin_no = 1:n())
+
+range(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)
+nbins<- unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)
 nrow(nbins)
@@
 
-rm(i,b)
-
-nbins<- unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)
+# rm(i,b)
 
@@
         lmer_bin_pup  <- lmer(pup_basCor ~ arousal_c* valence+Mean_gray_z  +
-                                (1 | ssid)+
-                                (0 +arousal_c* valence | ssid),
+                                (1 | ssid),
+                                # (0 +arousal_c* valence | ssid),
                                 # (1|stimIAPS),
@@
 
-Velocity test
+60 bins
+
+10 hz
+each bin is an average of 100ms
+<!-- https://link.springer.com/article/10.3758/s13428-018-1075-y -->
 
 ```{r}
+
+# create number s for time bins
+tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(ssid, tNo)%>%
+  mutate(timebin_no = 1:n())
+
+# let's test the interaction term
+nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+range(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+
+unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+
+# nbins = 60 # number of bins
+
+# create and empty dataframe for the timecourse analyses
+timecourse_60bin_result_df <- data.frame(timebins= rep(NA, 60), Estimate= rep(NA, 60), 
+                                   t=rep(NA, 60), p=rep(NA, 60), cov= as.character(rep(NA,60)))
+
+# View(timecourse_result_df)
+# nbins<- nbins[1:60]
+
+i = 0 # remember to always rezero it
+# b = 10
+
+# rm(i,b)
+
+# i =1
+
+for (b in 1:length(nbins)) {
+  # for (s in 1:length(nsim)) {
+
+    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
+        lmer_bin_pup  <- lmer(pup_basCor ~ (arousal_c* valence)+Mean_gray_z  +
+                                (1 | ssid),
+                                # (0 +arousal_c* valence | ssid),
+                                # (1|stimIAPS),
+                              REML = FALSE,
+                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
+                                    # mediansplit_self_valence == "More positive" & 
+                                    timebin_no == nbins[b]))
+
+        #store results from the simulation
+            lmer_bin_pup_summary<- summary(lmer_bin_pup)
+            lmer_bin_pup_summary
+            # lmer_bin_pup_summary[["coefficients"]][3,1]
+            timecourse_60bin_result_df[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] #save the exact value of time bin
+            timecourse_60bin_result_df[i,2]<-
+              lmer_bin_pup_summary[["coefficients"]][4,1] 
+            # first number is term(row), second is column
+            timecourse_60bin_result_df[i,3]<-
+              lmer_bin_pup_summary[["coefficients"]][4,4] # t statistic
+            timecourse_60bin_result_df[i,4]<-
+              lmer_bin_pup_summary[["coefficients"]][4,5] # p value
+            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
+            timecourse_60bin_result_df[i,5] <-
+              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
+                                                   != 0,
+                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')
+
+     i = i+1
+}
+
+# timecourse_result_df_pos<- timecourse_result_df
+View(timecourse_60bin_result_df)
+
+timecourse_60bin_result_df %>%
+  ggplot(aes(timebins, t))+
+  geom_line(size = 2)+
+  geom_line(aes(y = p), linetype = "dashed", size = 2)+
+  geom_hline(yintercept = .05, color = 'red', size = 1.5)
+
+```
+
+Pupil velocity test
+
+```{r}
+
+velocity analyses
+```{r}
+# thought maybe it has soemthing to to with the velcity, velocity is sidderent
+
+install.packages("pspline")
+library(pspline)
+
+predict(sm.spline(tmp.df4_full_stim_downs_jun2021_with_beh$timerezero3, 
+                  tmp.df4_full_stim_downs_jun2021_with_beh$pup_basCor), 
+        tmp.df4_full_stim_downs_jun2021_with_beh$timerezero3, 1)
+
+D(tmp.df4_full_stim_downs_jun2021_with_beh$pup_basCor, 'x')
+
+tmp.df4_full_stim_downs_jun2021_with_behnew
+
+tmp.df4_full_stim_downs_jun2021_with_behnew <- tmp.df4_full_stim_downs_jun2021_with_behnew %>%
+  # subset(!is.na(mediansplit_sample_arousal2))%>%
+  # subset(valencearousal_outliers == TRUE) %>%
+  # subset(!is.na(mediansplit_sample_arousal2))%>%
+  group_by(ssid, stimIAPS) %>%
+  mutate(pup_velocity = (abs(lag(pup_basCor)-pup_basCor)/abs(lag(timerezero3)-timerezero3)))
+  # mutate(pup_velocity_peak = max(pup_velocity, na.rm = TRUE))
+
+tmp.df4_full_stim_downs_jun2021_with_behnew$pup_velocity
+
+# global
+
 nrow(nbins)
@@
 ```
+
+100ms
+```{r}
+unique(tmp.df4_full_stim_downs_jun2021_60bins$ssid)
+
+tmp.df4_full_stim_downs_jun2021_60bins$ssid_num<- as.numeric(as.character(tmp.df4_full_stim_downs_jun2021_60bins$ssid))
+
+tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
+  # subset(!is.na(mediansplit_sample_arousal2))%>%
+  # subset(valencearousal_outliers == TRUE) %>%
+  # subset(!is.na(mediansplit_sample_arousal2))%>%
+  group_by(ssid, tNo) %>%
+  mutate(pup_velocity = (abs(lag(pup_basCor)-pup_basCor)/abs(lag(timerezero3)-timerezero3)))
+  # mutate(pup_velocity_peak = max(pup_velocity, na.rm = TRUE))
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  subset(ssid == 325 & tNo ==38)%>%
+  ggplot(aes(timerezero3, pup_velocity))+
+  geom_line()
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  subset(ssid == 325 & tNo ==38)%>%
+  ggplot(aes(timerezero3, pup_basCor))+
+  geom_line()
+
+# compared to pupil velocity is much more jerky
+
+# smooth belocity
+# number of bins
+unique(tmp.df4_full_stim_downs_jun2021_with_behnew$ssid)
+tmp.df4_full_stim_downs_jun2021_with_behnew
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  subset(ssid == 331 & tNo ==40)%>%
+  group_by(ssid, tNo)%>%
+  arrange(ssid,tNo, timerezero3)%>%
+  mutate(pup_vel_smooth = zoo::rollmean(pup_velocity, k = 3, fill = NA))%>%
+   ggplot(aes(timerezero3, pup_velocity))+
+  geom_line()+
+  geom_line(aes(y = pup_vel_smooth), color = 'red')
+
+tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins%>%
+  # subset(ssid == 331 & tNo ==40)%>%
+  group_by(ssid, tNo)%>%
+  arrange(ssid,tNo, timerezero3)%>%
+  mutate(pup_vel_smooth = zoo::rollmean(pup_velocity, k = 3, fill = NA))
+
+```

### 2021-07-23 Paper_Analyses_subj_obje_arousal.Rmd
#1 fixed the code
the code is now working without warning, but need to split for each estimate

@@
 Pupil velocity test
+# velocity analyses
 
-```{r}
-
-velocity analyses
 ```{r}
@@
 
-100ms
+velocity 100ms
 ```{r}
@@
 ```
+
+velocity timecourse
+```{r}
+# let's test the interaction term
+nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+range(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+
+unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+
+# nbins = 60 # number of bins
+
+# create and empty dataframe for the timecourse analyses
+timecourse_60bin_result_df_vel <- data.frame(timebins= rep(NA, 60), Estimate= rep(NA, 60), 
+                                   t=rep(NA, 60), p=rep(NA, 60), cov= as.character(rep(NA,60)))
+
+# View(timecourse_result_df)
+# nbins<- nbins[1:60]
+
+i = 0 # remember to always rezero it
+# b = 10
+
+# rm(i,b)
+
+# i =1
+tmp.df4_full_stim_downs_jun2021_60bins$pup_vel_smooth
+
+tmp.df4_full_stim_downs_jun2021_60bins$pup_vel_smooth
+
+nbins<- nbins[3:56]
+
+for (b in 3:length(nbins)) {
+  # for (s in 1:length(nsim)) {
+
+    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
+        lmer_bin_pup  <- lmer(pup_vel_smooth ~ (arousal_c* valence)+Mean_gray_z  +
+                                (1 | ssid),
+                                # (0 +arousal_c* valence | ssid),
+                                # (1|stimIAPS),
+                              REML = FALSE,
+                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
+                                    !is.na(pup_vel_smooth)&
+                                    timebin_no == nbins[b]))
+
+        #store results from the simulation
+            lmer_bin_pup_summary<- summary(lmer_bin_pup)
+            lmer_bin_pup_summary
+            # lmer_bin_pup_summary[["coefficients"]][3,1]
+            timecourse_60bin_result_df_vel[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] #save the exact value of time bin
+            timecourse_60bin_result_df_vel[i,2]<-
+              lmer_bin_pup_summary[["coefficients"]][5,1] 
+            # first number is term(row), second is column
+            timecourse_60bin_result_df_vel[i,3]<-
+              lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
+            timecourse_60bin_result_df_vel[i,4]<-
+              lmer_bin_pup_summary[["coefficients"]][5,5] # p value
+            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
+            timecourse_60bin_result_df_vel[i,5] <-
+              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
+                                                   != 0,
+                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')
+
+     i = i+1
+     }
+
+# timecourse_result_df_pos<- timecourse_result_df
+View(timecourse_60bin_result_df_vel)
+
+timecourse_60bin_result_df_vel %>%
+  ggplot(aes(timebins, t))+
+  geom_line(size = 2)+
+  geom_line(aes(y = p), linetype = "dashed", size = 2)+
+  geom_hline(yintercept = .05, color = 'red', size = 1.5)
+
+```
+
+```

### 2021-07-23 Paper_Analyses_subj_obje_arousal.Rmd
pupil and velocity analyses
fixed #1  and included corrections for timeseries (holm).

next need to decide on whether significance is tested based on uncorrected values using a simple  (e.g. at least 3 consecutive samples <.05, or relying on the correction adjusted. the downside of the latter is that it might be quite conservative.

--- 2021-07-23 Paper_Analyses_subj_obje_arousal.Rmd
@@
           arousal_c           0.02296  0.1515    0.89      
-          valence_c:arousal_c 0.01700  0.1304   -0.19  0.01
+          valence_c:arousal_c 0.01700  0.1604   -0.19  0.01
  Residual                     2.57999  1.6062              
@@
 (Intercept)         -0.66764    0.14166 44.77819  -4.713          0.000023962 ***
-valence_c            0.08546    0.06557 28.33677   1.303              0.20294    
+valence_c            0.08546    0.06557 28.33677   1.603              0.20294    
 arousal_c            0.44137    0.06445 22.53213   6.848          0.000000619 ***
@@
 
-let's test the interaction term
+Pupil changes over time
 <!-- 30 bins -->
@@
 range(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)
+
 nbins<- unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin_no)
 nrow(nbins)
-nbins = 30 # number of bins
+# nbins = 30 # number of bins
 
 # create and empty dataframe for the timecourse analyses
-timecourse_result_df_int <- data.frame(timebins= rep(NA, 30), Estimate= rep(NA, 30), 
-                                   t=rep(NA, 30), p=rep(NA, 30), cov= as.character(rep(NA,30)))
+timecourse_result_df_int <- data.frame(timebins= rep(NA, 30), 
+                                       Estimate_ar= rep(NA, 30), 
+                                       t_ar=rep(NA, 30), 
+                                       p_ar=rep(NA, 30),
+                                       Estimate_vl= rep(NA, 30), 
+                                       t_vl=rep(NA, 30), 
+                                       p_vl=rep(NA, 30),
+                                       Estimate_br= rep(NA, 30), 
+                                       t_br=rep(NA, 30), 
+                                       p_br=rep(NA, 30),
+                                       Estimate_ar_vl= rep(NA, 30), 
+                                       t_ar_vl=rep(NA, 30), 
+                                       p_ar_vl=rep(NA, 30),
+                                       cov= as.character(rep(NA,30)))
 
@@
             timecourse_result_df_int[i,1]<- tmp.df4_full_stim_downs_jun2021_with_behnew$timerezero3[b] #save the exact value of time bin
+
             timecourse_result_df_int[i,2]<- lmer_bin_pup_summary[["coefficients"]][5,1] # first number is term(row), second is column
@@
 # create and empty dataframe for the timecourse analyses
-timecourse_60bin_result_df <- data.frame(timebins= rep(NA, 60), Estimate= rep(NA, 60), 
-                                   t=rep(NA, 60), p=rep(NA, 60), cov= as.character(rep(NA,60)))
+timecourse_60bin_result_df <- data.frame(timebins= rep(NA, 60), 
+                                       Estimate_ar= rep(NA, 60), 
+                                       t_ar=rep(NA, 60), 
+                                       p_ar=rep(NA, 60),
+                                       Estimate_vl= rep(NA, 60), 
+                                       t_vl=rep(NA, 60), 
+                                       p_vl=rep(NA, 60),
+                                       Estimate_br= rep(NA, 60), 
+                                       t_br=rep(NA, 60), 
+                                       p_br=rep(NA, 60),
+                                       Estimate_ar_vl= rep(NA, 60), 
+                                       t_ar_vl=rep(NA, 60), 
+                                       p_ar_vl=rep(NA, 60),
+                                       cov= as.character(rep(NA,60)))
 
@@
                       data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
-                                    # mediansplit_self_valence == "More positive" & 
                                     timebin_no == nbins[b]))
@@
             # lmer_bin_pup_summary[["coefficients"]][3,1]
-            timecourse_60bin_result_df[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] #save the exact value of time bin
+            timecourse_60bin_result_df[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
+            #save the exact value of time bin
+            # store arousal (2,parameter)            # first number is term(row), second is column
             timecourse_60bin_result_df[i,2]<-
-              lmer_bin_pup_summary[["coefficients"]][4,1] 
-            # first number is term(row), second is column
+            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
             timecourse_60bin_result_df[i,3]<-
+              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
+            timecourse_60bin_result_df[i,4]<-
+            lmer_bin_pup_summary[["coefficients"]][2,5] # p value
+
+            # valence
+
+            timecourse_60bin_result_df[i,5]<-
+            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
+            timecourse_60bin_result_df[i,6]<-
+              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
+            timecourse_60bin_result_df[i,7]<-
+              lmer_bin_pup_summary[["coefficients"]][3,5] # p value
+
+            # brighteness
+
+            timecourse_60bin_result_df[i,8]<-
+            lmer_bin_pup_summary[["coefficients"]][4,1] #estimate
+            timecourse_60bin_result_df[i,9]<-
               lmer_bin_pup_summary[["coefficients"]][4,4] # t statistic
-            timecourse_60bin_result_df[i,4]<-
+            timecourse_60bin_result_df[i,10]<-
               lmer_bin_pup_summary[["coefficients"]][4,5] # p value
-            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
-            timecourse_60bin_result_df[i,5] <-
+
+            # interaction arousal x brighteness
+
+            timecourse_60bin_result_df[i,11]<-
+            lmer_bin_pup_summary[["coefficients"]][5,1] #estimate
+            timecourse_60bin_result_df[i,12]<-
+              lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
+            timecourse_60bin_result_df[i,13]<-
+              lmer_bin_pup_summary[["coefficients"]][5,5] # p value
+
+            timecourse_60bin_result_df[i,14] <-
               ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
@@
 
+  # geom_hline(yintercept = .05, color = 'red', size = 1.5)
+
+# adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05
+?p.adjust
+timecourse_60bin_result_df$p_ar_adj<- p.adjust(timecourse_60bin_result_df$p_ar, method = "holm")
+timecourse_60bin_result_df$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df$p_ar_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df$p_vl_adj <- p.adjust(timecourse_60bin_result_df$p_vl, method = "holm")
+timecourse_60bin_result_df$p_vl_adj_TRUE<- if_else(timecourse_60bin_result_df$p_vl_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df$p_br_adj <- p.adjust(timecourse_60bin_result_df$p_br, method = "holm")
+timecourse_60bin_result_df$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df$p_br_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df$p_ar_vl_adj <- p.adjust(timecourse_60bin_result_df$p_ar_vl, method = "holm")
+timecourse_60bin_result_df$p_ar_vl_adj_TRUE<- if_else(timecourse_60bin_result_df$p_ar_vl_adj<.05, TRUE, NULL)
+
+# find the first and last true in a sequence of TRUES
+duplicated(timecourse_60bin_result_df$p_ar_adj_TRUE, na.rm = TRUE)
+
+?linetype
 timecourse_60bin_result_df %>%
-  ggplot(aes(timebins, t))+
-  geom_line(size = 2)+
-  geom_line(aes(y = p), linetype = "dashed", size = 2)+
-  geom_hline(yintercept = .05, color = 'red', size = 1.5)
+  ggplot(aes(timebins, Estimate_ar_vl))+
+  geom_line(size = 1)+
+  geom_line(aes(y = Estimate_vl), linetype = "dashed", size = 1)+
+  geom_line(aes(y = Estimate_br), linetype = "dotted", size = 1)+
+  geom_line(aes(y = Estimate_ar_vl), linetype = "dotdash", size = 1, color = "red")
+
+timecourse_60bin_result_df %>%
+  ggplot(aes(timebins, t_ar))+
+  geom_line(size = 1)+
+  geom_line(aes(y = t_vl), linetype = "dashed", size = 1)+
+  # geom_line(aes(y = t_br), linetype = "dotted", size = 1)+
+  geom_line(aes(y = t_ar_vl), linetype = "dotdash", size = 1, color = "red")
 
@@
 Pupil velocity test
+# velocity analyses
 
 ```{r}
-
-velocity analyses
-```{r}
-# thought maybe it has soemthing to to with the velcity, velocity is sidderent
-
-install.packages("pspline")
+# install.packages("pspline")
 library(pspline)
@@
 ```
+
+velocity timecourse
+```{r}
+# let's test the interaction term
+nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+range(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+
+unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+
+# nbins = 60 # number of bins
+
+# create and empty dataframe for the timecourse analyses
+timecourse_60bin_result_df_vel <- data.frame(timebins= rep(NA, 60), 
+                                       Estimate_ar= rep(NA, 60), 
+                                       t_ar=rep(NA, 60), 
+                                       p_ar=rep(NA, 60),
+                                       Estimate_vl= rep(NA, 60), 
+                                       t_vl=rep(NA, 60), 
+                                       p_vl=rep(NA, 60),
+                                       Estimate_br= rep(NA, 60), 
+                                       t_br=rep(NA, 60), 
+                                       p_br=rep(NA, 60),
+                                       Estimate_ar_vl= rep(NA, 60), 
+                                       t_ar_vl=rep(NA, 60), 
+                                       p_ar_vl=rep(NA, 60),
+                                       cov= as.character(rep(NA,60)))
+
+# View(timecourse_result_df)
+# nbins<- nbins[1:60]
+
+i = 0 # remember to always rezero it
+# b = 10
+
+# rm(i,b)
+
+# i =1
+tmp.df4_full_stim_downs_jun2021_60bins$pup_vel_smooth
+
+tmp.df4_full_stim_downs_jun2021_60bins$pup_vel_smooth
+
+nbins<- nbins[3:56]
+
+for (b in 3:length(nbins)) {
+  # for (s in 1:length(nsim)) {
+
+    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
+        lmer_bin_pup  <- lmer(pup_vel_smooth ~ (arousal_c* valence)+Mean_gray_z  +
+                                (1 | ssid),
+                                # (0 +arousal_c* valence | ssid),
+                                # (1|stimIAPS),
+                              REML = FALSE,
+                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
+                                    !is.na(pup_vel_smooth)&
+                                    timebin_no == nbins[b]))
+
+        # store results from the simulation
+            lmer_bin_pup_summary<- summary(lmer_bin_pup)
+            lmer_bin_pup_summary
+            # lmer_bin_pup_summary[["coefficients"]][3,1]
+            timecourse_60bin_result_df_vel[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
+            #save the exact value of time bin
+            # store arousal (2,parameter)            # first number is term(row), second is column
+            timecourse_60bin_result_df_vel[i,2]<-
+            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
+            timecourse_60bin_result_df_vel[i,3]<-
+              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
+            timecourse_60bin_result_df_vel[i,4]<-
+            lmer_bin_pup_summary[["coefficients"]][2,5] # p value
+
+            # valence
+
+            timecourse_60bin_result_df_vel[i,5]<-
+            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
+            timecourse_60bin_result_df_vel[i,6]<-
+              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
+            timecourse_60bin_result_df_vel[i,7]<-
+              lmer_bin_pup_summary[["coefficients"]][3,5] # p value
+
+            # brighteness
+
+            timecourse_60bin_result_df_vel[i,8]<-
+            lmer_bin_pup_summary[["coefficients"]][4,1] #estimate
+            timecourse_60bin_result_df_vel[i,9]<-
+              lmer_bin_pup_summary[["coefficients"]][4,4] # t statistic
+            timecourse_60bin_result_df_vel[i,10]<-
+              lmer_bin_pup_summary[["coefficients"]][4,5] # p value
+
+            # interaction arousal x brighteness
+
+            timecourse_60bin_result_df_vel[i,11]<-
+            lmer_bin_pup_summary[["coefficients"]][5,1] #estimate
+            timecourse_60bin_result_df_vel[i,12]<-
+              lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
+            timecourse_60bin_result_df_vel[i,13]<-
+              lmer_bin_pup_summary[["coefficients"]][5,5] # p value
+
+            timecourse_60bin_result_df_vel[i,14] <-
+              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
+                                                   != 0,
+                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')
+
+     i = i+1
+}
+# timecourse_result_df_pos<- timecourse_result_df
+View(timecourse_60bin_result_df_vel)
+
+timecourse_60bin_result_df_vel %>%
+  ggplot(aes(timebins, t))+
+  geom_line(size = 2)+
+  geom_line(aes(y = p), linetype = "dashed", size = 2)+
+  geom_hline(yintercept = .05, color = 'red', size = 1.5)
+
+View(timecourse_60bin_result_df_vel)
+timecourse_60bin_result_df_vel %>%
+  ggplot(aes(timebins, Estimate_ar))+
+  geom_line(size = 1)+
+  geom_line(aes(y = Estimate_vl), linetype = "dashed", size = 1)+
+  geom_line(aes(y = Estimate_br), linetype = "dotted", size = 1)+
+  geom_line(aes(y = Estimate_ar_vl), linetype = "dotdash", size = 1, color = "red")+
+  ylim(-.1,.25)
+
+# adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05
+?p.adjust
+timecourse_60bin_result_df_vel$p_ar_adj<- p.adjust(timecourse_60bin_result_df_vel$p_ar, method = "holm")
+timecourse_60bin_result_df_vel$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df_vel$p_ar_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df_vel$p_vl_adj <- p.adjust(timecourse_60bin_result_df_vel$p_vl, method = "holm")
+timecourse_60bin_result_df_vel$p_vl_adj_TRUE<- if_else(timecourse_60bin_result_df_vel$p_vl_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df_vel$p_br_adj <- p.adjust(timecourse_60bin_result_df_vel$p_br, method = "holm")
+timecourse_60bin_result_df_vel$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df_vel$p_br_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df_vel$p_ar_vl_adj <- p.adjust(timecourse_60bin_result_df_vel$p_ar_vl, method = "holm")
+timecourse_60bin_result_df_vel$p_ar_vl_adj_TRUE<- if_else(timecourse_60bin_result_df_vel$p_ar_vl_adj<.05, TRUE, NULL)
+
+# find the first and last true in a sequence of TRUES
+duplicated(timecourse_60bin_result_df_vel$p_ar_adj_TRUE, na.rm = TRUE)
+
+```

### 2021-07-26 Old scripts/pupil_arousal_datarmd.Rmd
Update pupil_arousal_datarmd.Rmd

@@
 colnames(tmp.df4_full_stim)
+
+tmp.df4_full_stim_downs
 tmp.df4_full_stim_downs <- tmp.df4_full_stim %>%
@@
 # create klarger bins
+
+tmp.df4_full_stim_downs_jun2021
 tmp.df4_full_stim_downs_jun2021_with_beh
@@
 
-tmp.df4_full_stim_downs_jun2021_with_beh$timebin2<- OneR::bin(tmp.df4_full_stim_downs_jun2021_with_beh$timerezero3, nbin = 30)
+tmp.df4_full_stim_downs_jun2021_with_beh$timebin2 <- OneR::bin(tmp.df4_full_stim_downs_jun2021_with_beh$timerezero3, nbin = 30)
 
@@
 # import the timecourse
+unique(tmp.df4_full_stim_downs_jun2021)
+
+tmp.df4_full_stim_downs_jun2021_with_beh2$
 

### 2021-07-26 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd
test
solved jelkas comment

@@
 
-data<- lastopened
+data<- last opened
 
@@
 ?stats::filter
-tmp.df4_full_stim_downs_jun2021_with_behnew%>%
+tmp.df4_full_stim_downs_jun2021_60bins %>%
   subset(ssid == 310 & tNo == 10)%>%
-  ggplot(aes(timerezero3,zoo::rollmean(pup_velocity, k = 3, fill = NA)))+
+  ggplot(aes(timerezero3,pup_vel_smooth))+
   geom_line()+
-  geom_line(aes(y = pup_velocity), color = 'red')+
-  geom_smooth(se = F)
+  geom_point()
+  # geom_line(aes(y = pup_velocity),Ç color = 'red')
+  # geom_smooth(se = F)
 
-tmp.df4_full_stim_downs_jun2021_with_behnew%>%
-  subset(ssid == 310 & tNo == 15)%>%
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+    subset(ssid == 320 & tNo == 20)%>%
   ggplot(aes(timerezero3,pup_basCor))+
   geom_point()+
+  geom_line()+
+  geom_line(aes(y = pup_vel_smooth), color = 'red')+
+  geom_point(aes(y = pup_vel_smooth), color = 'red')
   # geom_line(aes(y = pup_velocity), color = 'red')+
-  geom_smooth(se = F)
+  # geom_smooth(se = F)
 
@@
   group_by(ssid, tNo) %>%
-  mutate(pup_velocity = (abs(lag(pup_basCor)-pup_basCor)/abs(lag(timerezero3)-timerezero3)))
+  mutate(pup_velocity = (abs(lag(pup_basCor)-pup_basCor)/abs(lag(timerezero3)-timerezero3)))%>%
+  mutate(pup_velocity_dir = ((lag(pup_basCor)-pup_basCor) / abs(lag(timerezero3)-timerezero3)))
   # mutate(pup_velocity_peak = max(pup_velocity, na.rm = TRUE))
@@
 
-tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins%>%
-  # subset(ssid == 331 & tNo ==40)%>%
+tmp.df4_full_stim_downs_jun2021_60bins$four<- paste0(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_arousal2,
+                                                     paste0(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_valence2))
+
+paste0(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_arousal2)
+
+# unique(tmp.df4_full_stim_downs_jun2021_60bins)
+
+  tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num < 500)%>%
+  subset(!is.na(mediansplit_sample_valence2))%>%
   group_by(ssid, tNo)%>%
   arrange(ssid,tNo, timerezero3)%>%
-  mutate(pup_vel_smooth = zoo::rollmean(pup_velocity, k = 3, fill = NA))
+   ggplot(aes(timerezero3, pup_basCor, color = four))+
+  stat_smooth(se = F)
+  # geom_line(aes(y = pup_vel_smooth), color = 'red')
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num < 500)%>%
+  subset(!is.na(mediansplit_sample_valence2))%>%
+  group_by(ssid, tNo)%>%
+  arrange(ssid,tNo, timerezero3)%>%
+   ggplot(aes(timerezero3, pup_velocity, color = four))+
+  stat_smooth(se = T)
+  # stat_smooth(aes(y = pup_velocity_dir),se = F, linetype = 'dashed')
+  # geom_line(aes(y = pup_vel_smooth), color = 'red')
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num < 500)%>%
+  subset(!is.na(mediansplit_sample_valence2))%>%
+  group_by(ssid, tNo)%>%
+  arrange(ssid,tNo, timerezero3)%>%
+   ggplot(aes(timerezero3, pup_velocity_dir, color = four))+
+  # stat_summary(fun = mean, geom = 'line')
+  stat_smooth(se = T)
+  # stat_smooth(aes(y = pup_velocity_dir),se = F, linetype = 'dashed')
+  # geom_line(aes(y = pup_vel_smooth), color = 'red')
 
@@
 
+```{r}  
+  tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num < 500)%>%
+  subset(!is.na(mediansplit_sample_valence2))%>%
+  group_by(ssid, tNo)%>%
+  arrange(ssid,tNo, timerezero3)%>%
+   ggplot(aes(timerezero3, pup_basCor, color = four))+
+  stat_smooth(se = F)
+  geom_line(aes(y = pup_vel_smooth), color = 'red')
+
+  tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num < 500)%>%
+  subset(!is.na(mediansplit_sample_valence2))%>%
+  group_by(ssid, tNo)%>%
+  arrange(ssid,tNo, timerezero3)%>%
+   ggplot(aes(timerezero3, pup_vel_smooth, color = four))+
+  stat_smooth(se = F)
+  geom_line(aes(y = pup_vel_smooth), color = 'red')
+
+  tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num < 500)%>%
+  subset(!is.na(mediansplit_sample_valence2))%>%
+  group_by(ssid, tNo)%>%
+  arrange(ssid,tNo, timerezero3)%>%
+   ggplot(aes(timerezero3, pup_basCor, color = four))+
+  stat_smooth(se = F)
+  geom_line(aes(y = pup_vel_smooth), color = 'red')
+
+```
+
+is velocity correlated with puypil amplitude
+```{r}
+require(tidyverse)
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  group_by(stimIAPS)%>%
+  mutate(cor_vel_pup = cor(pup_vel_smooth,pup_basCor, use = 'complete'))%>%
+  mutate(vel_max = max(pup_vel_smooth,na.rm = TRUE))%>%
+  summarise_if(is.numeric, mean,na.rm = TRUE)%>%
+  ggplot(aes(vel_max,pup_basCor))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  ggpubr::stat_cor()
+
+```
 velocity timecourse
@@
 
+# https://masterr.org/r/how-to-find-consecutive-repeats-in-r/
+timecourse_60bin_result_df_vel$test<- NULL
+
+timecourse_60bin_result_df_vel$test <- rle(timecourse_60bin_result_df_vel$p_ar < 0.05)
+# View(runs)
+# 
+# runs[2]
+# myruns = which(runs$values == TRUE & runs$lengths >= 3)
+
 ```

### 2021-07-26 Paper_Analyses_subj_obje_arousal.Rmd
started working on #2
- created the formats for the plot
- ran additional models using real velocity (with direction) opposed to the speed which is what i had done previously.

@@
 
+View(timecourse_60bin_result_df)
+
 timecourse_60bin_result_df %>%
-  ggplot(aes(timebins, t_ar))+
-  geom_line(size = 1)+
-  geom_line(aes(y = t_vl), linetype = "dashed", size = 1)+
-  # geom_line(aes(y = t_br), linetype = "dotted", size = 1)+
-  geom_line(aes(y = t_ar_vl), linetype = "dotdash", size = 1, color = "red")
-
+  ggplot(aes(timebins, Estimate_ar))+
+  geom_line(size = 1, linetype = 'dotted', color = 1)+
+  # geom_line(aes(y = Estimate_vl), linetype = "dashed", size = 1)+
+  geom_line(aes(y = Estimate_br), size = 1, color = 2)+
+  # geom_line(aes(y = Estimate_ar_vl), linetype = "dotdash", size = 1, color = "red")+
+  geom_rect(aes(xmin = 1,
+                xmax = 5.89,
+                ymin = -2,
+                ymax = -2+.1,
+                fill = "red", linetype = 'dashed'), alpha = .01)+
+  p$graphstyle+
+  scale_color_brewer(palette="Dark2")
+  scale_color_manual(values=wes_palette(n=3, name="GrandBudapest"))
+
+library(RColorBrewer)
+
+  brewer.pal(4, "Dark2")
+  # "#1B9E77" "#D95F02" "#7570B3" "#E7298A"
+  # timecourse_60bin_result_df$
+  # Estimate_ar, Estimate_ar_vl,Estimate_br. Estimate_v
+
+  timecourse_60bin_result_df %>% 
+  select("timebins","Estimate_ar", "Estimate_vl", "Estimate_br", "Estimate_ar_vl") %>% 
+  pivot_longer(-timebins, names_to = "variable", values_to = "Estimate")%>%
+    subset(!is.na(Estimate))%>%
+  ggplot(aes(timebins, Estimate, group = variable, fill = variable, color= variable))+
+  geom_line(aes(linetype = variable), size = 1)+
+    p$graphstyle+
+    scale_color_manual(values=c("#1B9E77", "#D95F02", "#7570B3", "#E7298A"))+
+  # use correction for significance
+    # brighteness
+    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_br_adj_TRUE == TRUE]
+    annotate(geom = 'rect', 
+             xmin = .16,
+                xmax = 6,
+                ymin = -2,
+                ymax = -2+.1,
+                fill = "#7570B3", alpha = .5)+
+
+      annotate("text", 
+                x = (1+5.4)/2,
+                y = ((-2) +(-2+.1))/2,
+                label = "brightness") +
+
+    # arousal
+    # timecourse_60bin_result_df$p_ar_adj
+    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_adj_TRUE == TRUE]
+     annotate(geom = 'rect', xmin = 1,
+                xmax = 5.89,
+                ymin = -2+.1+.1,
+                ymax = -2+.1+.1+.1,
+                fill = "#1B9E77", alpha = .5)+
+        annotate("text", 
+                x = (1+5.4)/2,
+                y = ((-2+.1+.1) +(-2+.1+.1+.1))/2,
+                label = "arousal") +
+
+    # arousal-valence
+   # timecourse_60bin_result_df$p_ar_vl_adj
+    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_vl_adj_TRUE == TRUE]
+       annotate(geom = 'rect', 
+                xmin = 1,
+                xmax = 5.4,
+                ymin = -2+.1+.1+.1+.1,
+                ymax = -2+.1+.1+.1+.1+.1,
+                fill = "#D95F02", alpha = .5, label = "text")+
+    annotate("text", 
+                x = (1+5.4)/2,
+                y = ((-2+.1+.1+.1+.1) +(-2+.1+.1+.1+.1+.1))/2,
+                label = "arousal x valence") +
+        xlab("Time (s)")+
+    ylab("Effect size")+
+    xlab("Time (s)")+
+    ylab("Effect size")
+
+    # valence - no significance
+
+    # scale_fill_brewer()
+
+?annotate
 ```
@@
 
-```
+View(timecourse_60bin_result_df_vel)
+```
+
+velocity = actual velocity unlike speed (which is what I actually computed above. velocity encodes durection( constriction or dilation)
+
+```{r}
+# let's test the interaction term
+nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+range(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+
+unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+
+# nbins = 60 # number of bins
+
+# create and empty dataframe for the timecourse analyses
+timecourse_60bin_result_df_vel_dir <- data.frame(timebins= rep(NA, 60), 
+                                       Estimate_ar= rep(NA, 60), 
+                                       t_ar=rep(NA, 60), 
+                                       p_ar=rep(NA, 60),
+                                       Estimate_vl= rep(NA, 60), 
+                                       t_vl=rep(NA, 60), 
+                                       p_vl=rep(NA, 60),
+                                       Estimate_br= rep(NA, 60), 
+                                       t_br=rep(NA, 60), 
+                                       p_br=rep(NA, 60),
+                                       Estimate_ar_vl= rep(NA, 60), 
+                                       t_ar_vl=rep(NA, 60), 
+                                       p_ar_vl=rep(NA, 60),
+                                       cov= as.character(rep(NA,60)))
+
+i = 0 # remember to always rezero it
+# rm(i,b)
+
+# i =1
+
+for (b in 3:length(nbins)) {
+  # for (s in 1:length(nsim)) {
+
+    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
+        lmer_bin_pup  <- lmer(pup_velocity_dir ~ (arousal_c* valence)+Mean_gray_z  +
+                                (1 | ssid),
+                                # (0 +arousal_c* valence | ssid),
+                                # (1|stimIAPS),
+                              REML = FALSE,
+                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
+                                    ssid_num< 500&
+                                    !is.na(pup_vel_smooth) &
+                                    timebin_no == nbins[b]))
+
+        # store results from the simulation
+            lmer_bin_pup_summary<- summary(lmer_bin_pup)
+            lmer_bin_pup_summary
+            # lmer_bin_pup_summary[["coefficients"]][3,1]
+            timecourse_60bin_result_df_vel_dir[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
+            #save the exact value of time bin
+            # store arousal (2,parameter)            # first number is term(row), second is column
+            timecourse_60bin_result_df_vel_dir[i,2]<-
+            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
+            timecourse_60bin_result_df_vel_dir[i,3]<-
+              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
+            timecourse_60bin_result_df_vel_dir[i,4]<-
+            lmer_bin_pup_summary[["coefficients"]][2,5] # p value
+
+            # valence
+
+            timecourse_60bin_result_df_vel_dir[i,5]<-
+            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
+            timecourse_60bin_result_df_vel_dir[i,6]<-
+              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
+            timecourse_60bin_result_df_vel_dir[i,7]<-
+              lmer_bin_pup_summary[["coefficients"]][3,5] # p value
+
+            # brightness
+
+            timecourse_60bin_result_df_vel_dir[i,8]<-
+            lmer_bin_pup_summary[["coefficients"]][4,1] #estimate
+            timecourse_60bin_result_df_vel_dir[i,9]<-
+              lmer_bin_pup_summary[["coefficients"]][4,4] # t statistic
+            timecourse_60bin_result_df_vel_dir[i,10]<-
+              lmer_bin_pup_summary[["coefficients"]][4,5] # p value
+
+            # interaction arousal x brighteness
+
+            timecourse_60bin_result_df_vel_dir[i,11]<-
+            lmer_bin_pup_summary[["coefficients"]][5,1] #estimate
+            timecourse_60bin_result_df_vel_dir[i,12]<-
+              lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
+            timecourse_60bin_result_df_vel_dir[i,13]<-
+              lmer_bin_pup_summary[["coefficients"]][5,5] # p value
+
+            timecourse_60bin_result_df_vel_dir[i,14] <-
+              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
+                                                   != 0,
+                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')
+
+     i = i+1
+}
+# timecourse_result_df_pos<- timecourse_result_df
+View(timecourse_60bin_result_df_vel_dir)
+
+View(timecourse_60bin_result_df_vel_dir)
+
+timecourse_60bin_result_df_vel_dir %>%
+  ggplot(aes(timebins, Estimate_ar))+
+  geom_line(size = 1)+
+  geom_line(aes(y = Estimate_vl), linetype = "dashed", size = 1)+
+  geom_line(aes(y = Estimate_br), linetype = "dotted", size = 1)+
+  geom_line(aes(y = Estimate_ar_vl), linetype = "dotdash", size = 1, color = "red")
+  ylim(-.1,5)
+
+# adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05
+?p.adjust
+timecourse_60bin_result_df_vel_dir$p_ar_adj<- p.adjust(timecourse_60bin_result_df_vel_dir$p_ar, method = "holm")
+timecourse_60bin_result_df_vel_dir$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df_vel_dir$p_ar_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df_vel_dir$p_vl_adj <- p.adjust(timecourse_60bin_result_df_vel_dir$p_vl, method = "holm")
+timecourse_60bin_result_df_vel_dir$p_vl_adj_TRUE<- if_else(timecourse_60bin_result_df_vel_dir$p_vl_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df_vel_dir$p_br_adj <- p.adjust(timecourse_60bin_result_df_vel_dir$p_br, method = "holm")
+timecourse_60bin_result_df_vel_dir$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df_vel_dir$p_br_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df_vel_dir$p_ar_vl_adj <- p.adjust(timecourse_60bin_result_df_vel_dir$p_ar_vl, method = "holm")
+timecourse_60bin_result_df_vel_dir$p_ar_vl_adj_TRUE<- if_else(timecourse_60bin_result_df_vel_dir$p_ar_vl_adj<.05, TRUE, NULL)
+
+# find the first and last true in a sequence of TRUES
+duplicated(timecourse_60bin_result_df_vel_dir$p_ar_adj_TRUE, na.rm = TRUE)
+
+# https://masterr.org/r/how-to-find-consecutive-repeats-in-r/
+timecourse_60bin_result_df_vel_dir$test<- NULL
+
+timecourse_60bin_result_df_vel_dir$test <- rle(timecourse_60bin_result_df_vel_dir$p_ar < 0.05)
+```
+
+pupiul velocity and speed might better caprure arousal dynamics because the temporal dynamics are less adffected by a susrtauned effect of brighetenss.
+whereas amplitude is p[robably strongly affected by brighteness which restricts variability in input from a arousal componenets

### 2021-07-27 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 # i =1
+# unique(tmp.df4_full_stim_downs_jun2021_60bins$)
 
@@
                       data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
+                                    ssid_num< 500 &
                                     timebin_no == nbins[b]))
@@
 ?p.adjust
+
 timecourse_60bin_result_df$p_ar_adj<- p.adjust(timecourse_60bin_result_df$p_ar, method = "holm")
@@
 
-?linetype
 timecourse_60bin_result_df %>%
   ggplot(aes(timebins, Estimate_ar_vl))+
-  geom_line(size = 1)+
-  geom_line(aes(y = Estimate_vl), linetype = "dashed", size = 1)+
-  geom_line(aes(y = Estimate_br), linetype = "dotted", size = 1)+
-  geom_line(aes(y = Estimate_ar_vl), linetype = "dotdash", size = 1, color = "red")
+  geom_line(size = 1)
+  geom_line(aes(y = t_vl), linetype = "dashed", size = 1)+
+  geom_line(aes(y = t_br), linetype = "dotted", size = 1)+
+  geom_line(aes(y = t_ar), linetype = "dotdash", size = 1, color = "red")
 
@@
 
-timecourse_60bin_result_df %>%
-  ggplot(aes(timebins, Estimate_ar))+
-  geom_line(size = 1, linetype = 'dotted', color = 1)+
-  # geom_line(aes(y = Estimate_vl), linetype = "dashed", size = 1)+
-  geom_line(aes(y = Estimate_br), size = 1, color = 2)+
-  # geom_line(aes(y = Estimate_ar_vl), linetype = "dotdash", size = 1, color = "red")+
-  geom_rect(aes(xmin = 1,
-                xmax = 5.89,
-                ymin = -2,
-                ymax = -2+.1,
-                fill = "red", linetype = 'dashed'), alpha = .01)+
-  p$graphstyle+
-  scale_color_brewer(palette="Dark2")
-  scale_color_manual(values=wes_palette(n=3, name="GrandBudapest"))
-
-library(RColorBrewer)
-
-  brewer.pal(4, "Dark2")
+```
+
+# # figure preferences
+good blog in customization 
+https://www.datanovia.com/en/blog/ggplot-legend-title-position-and-labels/#rename-legend-labels-and-change-the-order-of-items
+```{r}
+p<- list()
+
+sf = 1 # scaling factor to make it easier to change sizes of everything, in which case change here
+
+p$graphstyle <-  theme(#base plot theme
+
+  # axis lines
+  axis.line.y = element_line(color="black"),
+  axis.line.x = element_line(color="black"),
+
+  axis.title.y=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
+  axis.title.x=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
+
+  # text
+  strip.text.x = element_text(size = 12*(sf+.5),  colour = "black"),
+  strip.text.y = element_text(size = 12*(sf+.5),  colour = "black"),
+
+  text=element_text(size = 14, family = "sans"),
+  axis.text.x = element_text(size = 14*(sf+.5), family = "sans", colour = "black",),
+  axis.text.y = element_text(size = 14*(sf+.5), family = "sans", colour = "black"),
+
+  # panel
+  panel.grid.major = element_blank(),
+  panel.background = element_blank(),
+  # panel.background = element_rect(fill="transparent"),
+  # panel.border = element_rect(fill="transparent"),
+  # strip shades (reco rectagles)
+   strip.background = element_blank(),
+
+  # legend
+  legend.position = "top",
+  legend.key = element_rect(colour = "transparent", fill="transparent"),
+  #legend.direction = "horizontal",
+
+  legend.text = element_text(size = 10*(sf+.3)),
+  # legend.title = element_text(size = 10*(sf+.3)),
+  # legend line tends to be really small in print so adjust here
+  legend.key.height = unit(.5, "cm"),
+  legend.key.width = unit(2, "cm"),
+
+  #legend.text = element_text(size = 10*sf),
+  legend.title=element_blank(),
+  #legend.text = element_blank(),
+  #axis.ticks = element_blank(),
+)
+
+```
+
+timecourse stats plots
+```{r}
+require(RColorBrewer) # make color friendly plots
+require(tidyverse)
+
+brewer.pal(4, "Dark2") # gives the exact names of pallets
   # "#1B9E77" "#D95F02" "#7570B3" "#E7298A"
@@
 
-  timecourse_60bin_result_df %>% 
+plots_timecourse <- list()
+
+#  let's use the order arousal, valence, arousal x valence brightness
+plots_timecourse$eff_size_pup_amp <-   timecourse_60bin_result_df %>% 
   select("timebins","Estimate_ar", "Estimate_vl", "Estimate_br", "Estimate_ar_vl") %>% 
@@
     subset(!is.na(Estimate))%>%
-  ggplot(aes(timebins, Estimate, group = variable, fill = variable, color= variable))+
+  #change the order of the coloring variable here and the name of legends
+  mutate(variable = factor(variable, c("Estimate_ar", "Estimate_vl","Estimate_ar_vl",  "Estimate_br"), labels = c("arousal", "valence", "arousal x valence", "brightness")))%>%
+  ggplot(aes(timebins, Estimate, group = variable, color= variable))+
   geom_line(aes(linetype = variable), size = 1)+
-    p$graphstyle+
-    scale_color_manual(values=c("#1B9E77", "#D95F02", "#7570B3", "#E7298A"))+
-  # use correction for significance
+
+  scale_color_brewer(palette = "Dark2")+
+    # scale_color_manual(values=c("#1B9E77", "#D95F02", "#7570B3", "#E7298A"))+
+  # use hom correction for significance
+
     # brighteness
     # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_br_adj_TRUE == TRUE]
-    annotate(geom = 'rect', 
-             xmin = .16,
+
+    annotate(geom = 'rect', # use annotate instead of geom_rect, as it is more flexible
+             xmin = .16, # got these values from the data-frame. need to fidn a way to automate this
                 xmax = 6,
-                ymin = -2,
-                ymax = -2+.1,
-                fill = "#7570B3", alpha = .5)+
+                ymin = -2.03+(sf*.3), # if I ever need to change this, use the scaling factor sf
+                ymax = -2+.1+.01+(sf*.3),
+                fill =  "#E7298A" , alpha = .5)+
 
@@
                 x = (1+5.4)/2,
-                y = ((-2) +(-2+.1))/2,
+                y = ((-2) +(-2+.1))/2+(sf*.3),
                 label = "brightness") +
@@
     # arousal
+
     # timecourse_60bin_result_df$p_ar_adj
@@
                 xmax = 5.89,
-                ymin = -2+.1+.1,
-                ymax = -2+.1+.1+.1,
+                ymin = -2.03+.1+.1+.1+.1+(sf*.3),
+                ymax = -2+.1+.1+.1+.1+.1+.01+(sf*.3),
                 fill = "#1B9E77", alpha = .5)+
@@
                   x = (1+5.4)/2,
-                y = ((-2+.1+.1) +(-2+.1+.1+.1))/2,
+                y = ((-2+.1+.1+.1+.1) +(-2+.1+.1+.1+.1+.1))/2+(sf*.3),
                  label = "arousal") +
@@
                 xmax = 5.4,
-                ymin = -2+.1+.1+.1+.1,
-                ymax = -2+.1+.1+.1+.1+.1,
-                fill = "#D95F02", alpha = .5, label = "text")+
+                ymin = -2.03+.1+.1+(sf*.3),
+                ymax = -2+.1+.1+.1+.01+(sf*.3),
+
+                fill ="#7570B3", alpha = .5, label = "text")+
     annotate("text", 
                 x = (1+5.4)/2,
-                y = ((-2+.1+.1+.1+.1) +(-2+.1+.1+.1+.1+.1))/2,
+                y = ((-2+.1+.1) +(-2+.1+.1+.1))/2+(sf*.3),
                 label = "arousal x valence") +
@@
 
+plots_timecourse$eff_size_pup_amp 
+# need to rename the label legends
+
+# Edit legend title and labels
+plots_timecourse$eff_size_pup_amp <- plots_timecourse$eff_size_pup_amp + 
+  p$graphstyle +
+    guides(colour = guide_legend(override.aes = list(size=2)))+ #the line size of the legend tends to be smaller in print
+  scale_x_continuous(limits = c(0,6), breaks = c(0,2,4,6))+
+  scale_y_continuous(limits = c(-2,.7), breaks = c(-1, -0.5, 0,0.5))
+
+plots_timecourse$eff_size_pup_amp
+
     # valence - no significance
@@
 ```
+
+I think this clustering might
 
@@
 
-# i =1
 tmp.df4_full_stim_downs_jun2021_60bins$pup_vel_smooth
 
-tmp.df4_full_stim_downs_jun2021_60bins$pup_vel_smooth
-
-nbins<- nbins[3:56]
+nbins<- nbins[3:59]
 
@@
     message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
-        lmer_bin_pup  <- lmer(pup_vel_smooth ~ (arousal_c* valence)+Mean_gray_z  +
+        lmer_bin_pup  <- lmer(pup_velocity ~ (arousal_c* valence)+Mean_gray_z  +
                                 (1 | ssid),
@@
                                     !is.na(pup_vel_smooth)&
+                                      ssid_num< 500 &
                                     timebin_no == nbins[b]))
@@
 View(timecourse_60bin_result_df_vel)
+
+range(timecourse_60bin_result_df_vel$Estimate_ar, na.rm = TRUE)
 timecourse_60bin_result_df_vel %>%
+  subset(!is.na(Estimate_ar))%>%
   ggplot(aes(timebins, Estimate_ar))+
@@
   geom_line(aes(y = Estimate_ar_vl), linetype = "dotdash", size = 1, color = "red")+
+  geom_hline(yintercept = 0.2)
   ylim(-.1,.25)
 
+```
+
+```{r}
 # adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05
@@
 
-velocity = actual velocity unlike speed (which is what I actually computed above. velocity encodes durection( constriction or dilation)
+```{r}
+#  let's use the order arousal, valence, arousal x valence brightness
+timecourse_60bin_result_df_vel %>% 
+  select("timebins","Estimate_ar", "Estimate_vl", "Estimate_br", "Estimate_ar_vl") %>% 
+  pivot_longer(-timebins, names_to = "variable", values_to = "Estimate")%>%
+    subset(!is.na(Estimate))%>%
+  #change the order of the coloring variable here and the name of legends
+  mutate(variable = factor(variable, c("Estimate_ar", "Estimate_vl","Estimate_ar_vl",  "Estimate_br"), labels = c("arousal", "valence", "arousal x valence", "brightness")))%>%
+  ggplot(aes(timebins, Estimate, group = variable, color= variable))+
+  geom_line(aes(linetype = variable), size = 1)+
+
+  scale_color_brewer(palette = "Dark2")
+    # scale_color_manual(values=c("#1B9E77", "#D95F02", "#7570B3", "#E7298A"))+
+  # use hom correction for significance
+
+    # brighteness
+    timecourse_60bin_result_df_vel$timebins[timecourse_60bin_result_df_vel$p_br_adj_TRUE == TRUE]
+
+    annotate(geom = 'rect', # use annotate instead of geom_rect, as it is more flexible
+             xmin = .16, # got these values from the data-frame. need to fidn a way to automate this
+                xmax = 6,
+                ymin = -2.03+(sf*.3), # if I ever need to change this, use the scaling factor sf
+                ymax = -2+.1+.01+(sf*.3),
+                fill =  "#E7298A" , alpha = .5)+
+
+      annotate("text", 
+                x = (1+5.4)/2,
+                y = ((-2) +(-2+.1))/2+(sf*.3),
+                label = "brightness") +
+
+    # arousal
+
+    # timecourse_60bin_result_df$p_ar_adj
+    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_adj_TRUE == TRUE]
+     annotate(geom = 'rect', xmin = 1,
+                xmax = 5.89,
+                ymin = -2.03+.1+.1+.1+.1+(sf*.3),
+                ymax = -2+.1+.1+.1+.1+.1+.01+(sf*.3),
+                fill = "#1B9E77", alpha = .5)+
+        annotate("text", 
+                  x = (1+5.4)/2,
+                y = ((-2+.1+.1+.1+.1) +(-2+.1+.1+.1+.1+.1))/2+(sf*.3),
+                 label = "arousal") +
+
+    # arousal-valence
+   # timecourse_60bin_result_df$p_ar_vl_adj
+    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_vl_adj_TRUE == TRUE]
+       annotate(geom = 'rect', 
+                xmin = 1,
+                xmax = 5.4,
+                ymin = -2.03+.1+.1+(sf*.3),
+                ymax = -2+.1+.1+.1+.01+(sf*.3),
+
+                fill ="#7570B3", alpha = .5, label = "text")+
+    annotate("text", 
+                x = (1+5.4)/2,
+                y = ((-2+.1+.1) +(-2+.1+.1+.1))/2+(sf*.3),
+                label = "arousal x valence") +
+        xlab("Time (s)")+
+    ylab("Effect size")+
+    xlab("Time (s)")+
+    ylab("Effect size")
+
+plots_timecourse$eff_size_pup_amp 
+# need to rename the label legends
+
+# Edit legend title and labels
+plots_timecourse$eff_size_pup_amp <- plots_timecourse$eff_size_pup_amp + 
+  p$graphstyle +
+    guides(colour = guide_legend(override.aes = list(size=2)))+ #the line size of the legend tends to be smaller in print
+  scale_x_continuous(limits = c(0,6), breaks = c(0,2,4,6))+
+  scale_y_continuous(limits = c(-2,.7), breaks = c(-1, -0.5, 0,0.5))
+
+plots_timecourse$eff_size_pup_amp
+
+    # valence - no significance
+
+    # scale_fill_brewer()
+
+?annotate
+
+```
+
+velocity = actual velocity unlike speed (which is what I actually computed above. velocity encodes direction( constriction or dilation)
 

### 2021-07-27 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 
+?p.adjust
+
+# flad when 3 consecutive rows have a p <.05
+require(zoo)
+
+# rle performs lenght encoding
+rletest<- rle(timecourse_60bin_result_df$p_ar<.05)
+?rle
+
+  (rletest$lengths[rletest$lengths > 3 & rletest$values== TRUE]) # length of each sequence
+
+# To get the vector with only a sequence of "TRUE" you can try
+
+rletest$values[rletest$values != TRUE] <- 0
+timecourse_60bin_result_df$p_ar_3below.5<- rep(rletest$values,  rletest$lengths)
+
+table(timecourse_60bin_result_df$p_ar_3below.5)
+?p.adjust
+
+timecourse_60bin_result_df%>%
+  group_by(p_ar_3below.5)%>%
+  mutate(p_ar_adj_clust= p.adjust(p_ar, method = "holm"))
+
+timecourse_60bin_result_df %>%
+  mutate(test=rollapply(p_ar, width=3, max, align="left", fill=NA, na.rm=TRUE))%>%
+
 ```
@@
 
-    # valence - no significance
-
-    # scale_fill_brewer()
-
-?annotate
-```
-
-I think this clustering might
+```
+
+split neutral positive and negative usign ground
+
+```{r}
+
+colnames(tmp.df4_full_stim_downs_jun2021_60bins)
+
+# create number s for time bins
+tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(ssid, tNo)%>%
+  mutate(timebin_no = 1:n())
+
+# let's test the interaction term
+nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+range(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+
+unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+
+# nbins = 60 # number of bins
+
+# create and empty dataframe for the timecourse analyses
+timecourse_60bin_result_df <- data.frame(timebins= rep(NA, 60), 
+                                       Estimate_ar= rep(NA, 60), 
+                                       t_ar=rep(NA, 60), 
+                                       p_ar=rep(NA, 60),
+                                       Estimate_vl= rep(NA, 60), 
+                                       t_vl=rep(NA, 60), 
+                                       p_vl=rep(NA, 60),
+                                       Estimate_br= rep(NA, 60), 
+                                       t_br=rep(NA, 60), 
+                                       p_br=rep(NA, 60),
+                                       Estimate_ar_vl= rep(NA, 60), 
+                                       t_ar_vl=rep(NA, 60), 
+                                       p_ar_vl=rep(NA, 60),
+                                       cov= as.character(rep(NA,60)))
+
+# View(timecourse_result_df)
+# nbins<- nbins[1:60]
+
+i = 0 # remember to always rezero it
+# b = 10
+
+# rm(i,b)
+
+# i =1
+# unique(tmp.df4_full_stim_downs_jun2021_60bins$)
+
+for (b in 1:length(nbins)) {
+  # for (s in 1:length(nsim)) {
+
+    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
+        lmer_bin_pup  <- lmer(pup_basCor ~ (arousal_c* valence)+Mean_gray_z  +
+                                (1 | ssid),
+                                # (0 +arousal_c* valence | ssid),
+                                # (1|stimIAPS),
+                              REML = FALSE,
+                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
+                                    ssid_num< 500 &
+                                    timebin_no == nbins[b]))
+
+        #store results from the simulation
+            lmer_bin_pup_summary<- summary(lmer_bin_pup)
+            lmer_bin_pup_summary
+            # lmer_bin_pup_summary[["coefficients"]][3,1]
+            timecourse_60bin_result_df[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
+            #save the exact value of time bin
+            # store arousal (2,parameter)            # first number is term(row), second is column
+            timecourse_60bin_result_df[i,2]<-
+            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
+            timecourse_60bin_result_df[i,3]<-
+              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
+            timecourse_60bin_result_df[i,4]<-
+            lmer_bin_pup_summary[["coefficients"]][2,5] # p value
+
+            # valence
+
+            timecourse_60bin_result_df[i,5]<-
+            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
+            timecourse_60bin_result_df[i,6]<-
+              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
+            timecourse_60bin_result_df[i,7]<-
+              lmer_bin_pup_summary[["coefficients"]][3,5] # p value
+
+            # brighteness
+
+            timecourse_60bin_result_df[i,8]<-
+            lmer_bin_pup_summary[["coefficients"]][4,1] #estimate
+            timecourse_60bin_result_df[i,9]<-
+              lmer_bin_pup_summary[["coefficients"]][4,4] # t statistic
+            timecourse_60bin_result_df[i,10]<-
+              lmer_bin_pup_summary[["coefficients"]][4,5] # p value
+
+            # interaction arousal x brighteness
+
+            timecourse_60bin_result_df[i,11]<-
+            lmer_bin_pup_summary[["coefficients"]][5,1] #estimate
+            timecourse_60bin_result_df[i,12]<-
+              lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
+            timecourse_60bin_result_df[i,13]<-
+              lmer_bin_pup_summary[["coefficients"]][5,5] # p value
+
+            timecourse_60bin_result_df[i,14] <-
+              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
+                                                   != 0,
+                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')
+
+     i = i+1
+}
+
+# timecourse_result_df_pos<- timecourse_result_df
+View(timecourse_60bin_result_df)
+
+  # geom_hline(yintercept = .05, color = 'red', size = 1.5)
+
+# adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05
+?p.adjust
+
+timecourse_60bin_result_df$p_ar_adj<- p.adjust(timecourse_60bin_result_df$p_ar, method = "holm")
+timecourse_60bin_result_df$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df$p_ar_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df$p_vl_adj <- p.adjust(timecourse_60bin_result_df$p_vl, method = "holm")
+timecourse_60bin_result_df$p_vl_adj_TRUE<- if_else(timecourse_60bin_result_df$p_vl_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df$p_br_adj <- p.adjust(timecourse_60bin_result_df$p_br, method = "holm")
+timecourse_60bin_result_df$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df$p_br_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df$p_ar_vl_adj <- p.adjust(timecourse_60bin_result_df$p_ar_vl, method = "holm")
+timecourse_60bin_result_df$p_ar_vl_adj_TRUE<- if_else(timecourse_60bin_result_df$p_ar_vl_adj<.05, TRUE, NULL)
+
+# find the first and last true in a sequence of TRUES
+duplicated(timecourse_60bin_result_df$p_ar_adj_TRUE, na.rm = TRUE)
+
+timecourse_60bin_result_df %>%
+  ggplot(aes(timebins, Estimate_ar_vl))+
+  geom_line(size = 1)
+  geom_line(aes(y = t_vl), linetype = "dashed", size = 1)+
+  geom_line(aes(y = t_br), linetype = "dotted", size = 1)+
+  geom_line(aes(y = t_ar), linetype = "dotdash", size = 1, color = "red")
+
+View(timecourse_60bin_result_df)
+
+?p.adjust
+
+# flad when 3 consecutive rows have a p <.05
+require(zoo)
+
+# rle performs lenght encoding
+rletest<- rle(timecourse_60bin_result_df$p_ar<.05)
+?rle
+
+  (rletest$lengths[rletest$lengths > 3 & rletest$values== TRUE]) # length of each sequence
+
+# To get the vector with only a sequence of "TRUE" you can try
+
+rletest$values[rletest$values != TRUE] <- 0
+timecourse_60bin_result_df$p_ar_3below.5<- rep(rletest$values,  rletest$lengths)
+
+table(timecourse_60bin_result_df$p_ar_3below.5)
+?p.adjust
+
+timecourse_60bin_result_df%>%
+  group_by(p_ar_3below.5)%>%
+  mutate(p_ar_adj_clust= p.adjust(p_ar, method = "holm"))
+
+timecourse_60bin_result_df %>%
+  mutate(test=rollapply(p_ar, width=3, max, align="left", fill=NA, na.rm=TRUE))%>%
+
+```
+
+```
 
@@
 # adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05
-?p.adjust
+
+```
+
+mutate(ANC=rollapply(ANC, width=3, max, align="left", fill=NA, na.rm=TRUE)) %>%
+  filter(ANC >= 0.5) %>%  
+  filter(row_number() == 1)
+
+```{r}
 timecourse_60bin_result_df_vel$p_ar_adj<- p.adjust(timecourse_60bin_result_df_vel$p_ar, method = "holm")
@@
 ```{r}
+
+View(timecourse_60bin_result_df_vel)
 #  let's use the order arousal, valence, arousal x valence brightness
+
+plots_timecourse$eff_size_pup_velocity<-
 timecourse_60bin_result_df_vel %>% 
@@
 
-  scale_color_brewer(palette = "Dark2")
+  scale_color_brewer(palette = "Dark2")+
     # scale_color_manual(values=c("#1B9E77", "#D95F02", "#7570B3", "#E7298A"))+
@@
     # brighteness
-    timecourse_60bin_result_df_vel$timebins[timecourse_60bin_result_df_vel$p_br_adj_TRUE == TRUE]
+    # timecourse_60bin_result_df_vel$timebins[timecourse_60bin_result_df_vel$p_br_adj_TRUE == TRUE]
 
     annotate(geom = 'rect', # use annotate instead of geom_rect, as it is more flexible
-             xmin = .16, # got these values from the data-frame. need to fidn a way to automate this
-                xmax = 6,
-                ymin = -2.03+(sf*.3), # if I ever need to change this, use the scaling factor sf
-                ymax = -2+.1+.01+(sf*.3),
+             xmin = .37, # got these values from the data-frame. need to fidn a way to automate this
+                xmax = .81,
+                ymin = -2.03+(sf*1.2), # if I ever need to change this, use the scaling factor sf
+                ymax = -2+.1+.01+(sf*1.2),
                 fill =  "#E7298A" , alpha = .5)+
 
-      annotate("text", 
-                x = (1+5.4)/2,
-                y = ((-2) +(-2+.1))/2+(sf*.3),
-                label = "brightness") +
+      # annotate("text", 
+      #           x = (1+5.4)/2,
+      #           y = ((-2) +(-2+.1))/2+(sf*.3),
+      #           label = "brightness") +
 
@@
     # timecourse_60bin_result_df$p_ar_adj
-    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_adj_TRUE == TRUE]
-     annotate(geom = 'rect', xmin = 1,
-                xmax = 5.89,
-                ymin = -2.03+.1+.1+.1+.1+(sf*.3),
-                ymax = -2+.1+.1+.1+.1+.1+.01+(sf*.3),
+
+    # timecourse_60bin_result_df_vel$timebins[timecourse_60bin_result_df_vel$p_ar_adj_TRUE == TRUE]
+
+    # timecourse_60bin_result_df_vel$timebins
+
+    annotate(geom = 'rect', 
+              xmin = 1.028329,
+                xmax = 1.028329+.1,
+                ymin = -2.03+.1+.1+.1+.1+(sf*1.2),
+                ymax = -2+.1+.1+.1+.1+.1+.01+(sf*1.2),
                 fill = "#1B9E77", alpha = .5)+
-        annotate("text", 
-                  x = (1+5.4)/2,
-                y = ((-2+.1+.1+.1+.1) +(-2+.1+.1+.1+.1+.1))/2+(sf*.3),
-                 label = "arousal") +
+        # annotate("text", 
+        #           x = (1+5.4)/2,
+        #         y = ((-2+.1+.1+.1+.1) +(-2+.1+.1+.1+.1+.1))/2+(sf*.3),
+        #          label = "arousal") +
 
@@
    # timecourse_60bin_result_df$p_ar_vl_adj
-    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_vl_adj_TRUE == TRUE]
+    # timecourse_60bin_result_df_vel$timebins[timecourse_60bin_result_df_vel$p_ar_vl_adj_TRUE == TRUE]
        annotate(geom = 'rect', 
-                xmin = 1,
-                xmax = 5.4,
-                ymin = -2.03+.1+.1+(sf*.3),
-                ymax = -2+.1+.1+.1+.01+(sf*.3),
+                xmin = 5.5730353,
+                xmax = 5.5730353+.1,
+                ymin = -2.03+.1+.1+(sf*1.2),
+                ymax = -2+.1+.1+.1+.01+(sf*1.2),
 
                 fill ="#7570B3", alpha = .5, label = "text")+
-    annotate("text", 
-                x = (1+5.4)/2,
-                y = ((-2+.1+.1) +(-2+.1+.1+.1))/2+(sf*.3),
-                label = "arousal x valence") +
+
+  # annotate("text", 
+  #               x = (1+5.4)/2,
+  #               y = ((-2+.1+.1) +(-2+.1+.1+.1))/2+(sf*.3),
+  #               label = "arousal x valence") +
         xlab("Time (s)")+
@@
 
-plots_timecourse$eff_size_pup_amp 
+plots_timecourse$eff_size_pup_velocity
 # need to rename the label legends
@@
 # Edit legend title and labels
-plots_timecourse$eff_size_pup_amp <- plots_timecourse$eff_size_pup_amp + 
+plots_timecourse$eff_size_pup_velocity
+
+plots_timecourse$eff_size_pup_velocity + 
   p$graphstyle +
@@
   scale_x_continuous(limits = c(0,6), breaks = c(0,2,4,6))+
-  scale_y_continuous(limits = c(-2,.7), breaks = c(-1, -0.5, 0,0.5))
+  scale_y_continuous(limits = c(-1,1.5), breaks = c(-0.5, 0,0.5,1))
 

### 2021-07-27 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 
-split neutral positive and negative usign ground
+split neutral positive and negative using IAPS validation data and fit the same
 
@@
 
-# create number s for time bins
-tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins%>%
-  group_by(ssid, tNo)%>%
-  mutate(timebin_no = 1:n())
-
-# let's test the interaction term
+tmp.df4_full_stim_downs_jun2021_60bins$ground_arousal_lab
+tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab
+
 nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
-range(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
-
-unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
-
-# nbins = 60 # number of bins
-
-# create and empty dataframe for the timecourse analyses
-timecourse_60bin_result_df <- data.frame(timebins= rep(NA, 60), 
+# create and empty data-frame for the time-course analyses
+
+View(timecourse_60bin_result_df_pos)
+timecourse_60bin_result_df_pos <- data.frame(timebins= rep(NA, 60), 
                                        Estimate_ar= rep(NA, 60), 
@@
                                        p_ar=rep(NA, 60),
-                                       Estimate_vl= rep(NA, 60), 
-                                       t_vl=rep(NA, 60), 
-                                       p_vl=rep(NA, 60),
+                                       # Estimate_vl= rep(NA, 60), 
+                                       # t_vl=rep(NA, 60), 
+                                       # p_vl=rep(NA, 60),
                                        Estimate_br= rep(NA, 60), 
@@
                                        p_br=rep(NA, 60),
-                                       Estimate_ar_vl= rep(NA, 60), 
-                                       t_ar_vl=rep(NA, 60), 
-                                       p_ar_vl=rep(NA, 60),
+                                       # Estimate_ar_vl= rep(NA, 60), 
+                                       # t_ar_vl=rep(NA, 60), 
+                                       # p_ar_vl=rep(NA, 60),
                                        cov= as.character(rep(NA,60)))
@@
     message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
-        lmer_bin_pup  <- lmer(pup_basCor ~ (arousal_c* valence)+Mean_gray_z  +
+        lmer_bin_pup  <- lmer(pup_basCor ~ arousal_c + Mean_gray_z  +
                                 (1 | ssid),
-                                # (0 +arousal_c* valence | ssid),
-                                # (1|stimIAPS),
                               REML = FALSE,
                       data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
-                                    ssid_num< 500 &
+                                    ssid_num < 500 & ground_valence_lab == "More positive" &
                                     timebin_no == nbins[b]))
@@
             # lmer_bin_pup_summary[["coefficients"]][3,1]
-            timecourse_60bin_result_df[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
+            timecourse_60bin_result_df_pos[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
             #save the exact value of time bin
             # store arousal (2,parameter)            # first number is term(row), second is column
-            timecourse_60bin_result_df[i,2]<-
+            timecourse_60bin_result_df_pos[i,2]<-
             lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
-            timecourse_60bin_result_df[i,3]<-
+            timecourse_60bin_result_df_pos[i,3]<-
               lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
-            timecourse_60bin_result_df[i,4]<-
+            timecourse_60bin_result_df_pos[i,4]<-
             lmer_bin_pup_summary[["coefficients"]][2,5] # p value
 
-            # valence
-
-            timecourse_60bin_result_df[i,5]<-
+            # brightness
+
+            timecourse_60bin_result_df_pos[i,5]<-
             lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
-            timecourse_60bin_result_df[i,6]<-
+            timecourse_60bin_result_df_pos[i,6]<-
               lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
-            timecourse_60bin_result_df[i,7]<-
+            timecourse_60bin_result_df_pos[i,7]<-
               lmer_bin_pup_summary[["coefficients"]][3,5] # p value
 
-            # brighteness
-
-            timecourse_60bin_result_df[i,8]<-
-            lmer_bin_pup_summary[["coefficients"]][4,1] #estimate
-            timecourse_60bin_result_df[i,9]<-
-              lmer_bin_pup_summary[["coefficients"]][4,4] # t statistic
-            timecourse_60bin_result_df[i,10]<-
-              lmer_bin_pup_summary[["coefficients"]][4,5] # p value
-
-            # interaction arousal x brighteness
-
-            timecourse_60bin_result_df[i,11]<-
-            lmer_bin_pup_summary[["coefficients"]][5,1] #estimate
-            timecourse_60bin_result_df[i,12]<-
-              lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
-            timecourse_60bin_result_df[i,13]<-
-              lmer_bin_pup_summary[["coefficients"]][5,5] # p value
-
-            timecourse_60bin_result_df[i,14] <-
+            timecourse_60bin_result_df_pos[i,8] <-
               ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
@@
 # timecourse_result_df_pos<- timecourse_result_df
-View(timecourse_60bin_result_df)
+View(timecourse_60bin_result_df_pos)
 
@@
 # adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05
-?p.adjust
-
-timecourse_60bin_result_df$p_ar_adj<- p.adjust(timecourse_60bin_result_df$p_ar, method = "holm")
-timecourse_60bin_result_df$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df$p_ar_adj<.05, TRUE, FALSE)
-
-timecourse_60bin_result_df$p_vl_adj <- p.adjust(timecourse_60bin_result_df$p_vl, method = "holm")
-timecourse_60bin_result_df$p_vl_adj_TRUE<- if_else(timecourse_60bin_result_df$p_vl_adj<.05, TRUE, FALSE)
-
-timecourse_60bin_result_df$p_br_adj <- p.adjust(timecourse_60bin_result_df$p_br, method = "holm")
-timecourse_60bin_result_df$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df$p_br_adj<.05, TRUE, FALSE)
-
-timecourse_60bin_result_df$p_ar_vl_adj <- p.adjust(timecourse_60bin_result_df$p_ar_vl, method = "holm")
-timecourse_60bin_result_df$p_ar_vl_adj_TRUE<- if_else(timecourse_60bin_result_df$p_ar_vl_adj<.05, TRUE, NULL)
-
-# find the first and last true in a sequence of TRUES
-duplicated(timecourse_60bin_result_df$p_ar_adj_TRUE, na.rm = TRUE)
-
-timecourse_60bin_result_df %>%
-  ggplot(aes(timebins, Estimate_ar_vl))+
-  geom_line(size = 1)
-  geom_line(aes(y = t_vl), linetype = "dashed", size = 1)+
-  geom_line(aes(y = t_br), linetype = "dotted", size = 1)+
-  geom_line(aes(y = t_ar), linetype = "dotdash", size = 1, color = "red")
-
-View(timecourse_60bin_result_df)
-
-?p.adjust
-
-# flad when 3 consecutive rows have a p <.05
-require(zoo)
-
-# rle performs lenght encoding
-rletest<- rle(timecourse_60bin_result_df$p_ar<.05)
-?rle
-
-  (rletest$lengths[rletest$lengths > 3 & rletest$values== TRUE]) # length of each sequence
-
-# To get the vector with only a sequence of "TRUE" you can try
-
-rletest$values[rletest$values != TRUE] <- 0
-timecourse_60bin_result_df$p_ar_3below.5<- rep(rletest$values,  rletest$lengths)
-
-table(timecourse_60bin_result_df$p_ar_3below.5)
-?p.adjust
-
-timecourse_60bin_result_df%>%
-  group_by(p_ar_3below.5)%>%
-  mutate(p_ar_adj_clust= p.adjust(p_ar, method = "holm"))
-
-timecourse_60bin_result_df %>%
-  mutate(test=rollapply(p_ar, width=3, max, align="left", fill=NA, na.rm=TRUE))%>%
-
-```
-
-```
-
+
+timecourse_60bin_result_df_pos$p_ar_adj<- p.adjust(timecourse_60bin_result_df_pos$p_ar, method = "holm")
+timecourse_60bin_result_df_pos$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df_pos$p_ar_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df_pos$p_br_adj <- p.adjust(timecourse_60bin_result_df_pos$p_br, method = "holm")
+timecourse_60bin_result_df_pos$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df_pos$p_br_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df_pos[1:56,] %>%
+  ggplot(aes(timebins, Estimate_ar))+
+  geom_line(size = 1)+
+  geom_line(aes(y = Estimate_br), linetype = "dashed", size = 1)
+
+# subset(tmp.df4_full_stim_downs_jun2021_60bins,
+#                                     ssid_num < 500 & ground_valence_lab == "More positive"
+#                                    )%>%
+#   # group_by(stimIAPS)%>%
+#   # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+#   # ggplot(aes(valence, Mean))+
+#   # geom_point()+
+#   # geom_smooth(method = 'lm', se = F)+
+#   # ggpubr::stat_cor()
+
+```
+neutral
+
+```{r}
+
+nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+# create and empty data-frame for the time-course analyses
+
+View(timecourse_60bin_result_df_pos)
+
+timecourse_60bin_result_df_neutral <- data.frame(timebins= rep(NA, 60), 
+                                       Estimate_ar= rep(NA, 60), 
+                                       t_ar=rep(NA, 60), 
+                                       p_ar=rep(NA, 60),
+                                       # Estimate_vl= rep(NA, 60), 
+                                       # t_vl=rep(NA, 60), 
+                                       # p_vl=rep(NA, 60),
+                                       Estimate_br= rep(NA, 60), 
+                                       t_br=rep(NA, 60), 
+                                       p_br=rep(NA, 60),
+                                       # Estimate_ar_vl= rep(NA, 60), 
+                                       # t_ar_vl=rep(NA, 60), 
+                                       # p_ar_vl=rep(NA, 60),
+                                       cov= as.character(rep(NA,60)))
+
+# View(timecourse_result_df)
+# nbins<- nbins[1:60]
+
+i = 0 # remember to always rezero it
+# b = 10
+
+# rm(i,b)
+
+# i =1
+# unique(tmp.df4_full_stim_downs_jun2021_60bins$)
+
+for (b in 1:length(nbins)) {
+  # for (s in 1:length(nsim)) {
+
+    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
+        lmer_bin_pup  <- lmer(pup_basCor ~ arousal_c + Mean_gray_z  +
+                                (1 | ssid),
+                              REML = FALSE,
+                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
+                                    ssid_num < 500 & ground_valence_lab == "Mild" &
+                                    timebin_no == nbins[b]))
+
+        #store results from the simulation
+            lmer_bin_pup_summary<- summary(lmer_bin_pup)
+            lmer_bin_pup_summary
+            # lmer_bin_pup_summary[["coefficients"]][3,1]
+            timecourse_60bin_result_df_neutral[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
+            #save the exact value of time bin
+            # store arousal (2,parameter)            # first number is term(row), second is column
+            timecourse_60bin_result_df_neutral[i,2]<-
+            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
+            timecourse_60bin_result_df_neutral[i,3]<-
+              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
+            timecourse_60bin_result_df_neutral[i,4]<-
+            lmer_bin_pup_summary[["coefficients"]][2,5] # p value
+
+            # brightness
+
+            timecourse_60bin_result_df_neutral[i,5]<-
+            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
+            timecourse_60bin_result_df_neutral[i,6]<-
+              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
+            timecourse_60bin_result_df_neutral[i,7]<-
+              lmer_bin_pup_summary[["coefficients"]][3,5] # p value
+
+            timecourse_60bin_result_df_neutral[i,8] <-
+              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
+                                                   != 0,
+                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')
+
+     i = i+1
+}
+
+# timecourse_result_df_pos<- timecourse_result_df
+View(timecourse_60bin_result_df_neutral)
+
+timecourse_60bin_result_df_neutral$p_ar_adj<- p.adjust(timecourse_60bin_result_df_neutral$p_ar, method = "holm")
+timecourse_60bin_result_df_neutral$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df_neutral$p_ar_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df_neutral$p_br_adj <- p.adjust(timecourse_60bin_result_df_neutral$p_br, method = "holm")
+timecourse_60bin_result_df_neutral$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df_neutral$p_br_adj<.05, TRUE, FALSE)
+
+View(timecourse_60bin_result_df_neutral)
+timecourse_60bin_result_df_neutral[1:56,] %>%
+  ggplot(aes(timebins, Estimate_ar))+
+  geom_line(size = 1)+
+  geom_line(aes(y = Estimate_br), linetype = "dashed", size = 1)
+
+```
+
+negative
+
+```{r}
+
+nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+# create and empty data-frame for the time-course analyses
+
+View(timecourse_60bin_result_df_pos)
+
+timecourse_60bin_result_df_neg <- data.frame(timebins= rep(NA, 60), 
+                                       Estimate_ar= rep(NA, 60), 
+                                       t_ar=rep(NA, 60), 
+                                       p_ar=rep(NA, 60),
+                                       # Estimate_vl= rep(NA, 60), 
+                                       # t_vl=rep(NA, 60), 
+                                       # p_vl=rep(NA, 60),
+                                       Estimate_br= rep(NA, 60), 
+                                       t_br=rep(NA, 60), 
+                                       p_br=rep(NA, 60),
+                                       # Estimate_ar_vl= rep(NA, 60), 
+                                       # t_ar_vl=rep(NA, 60), 
+                                       # p_ar_vl=rep(NA, 60),
+                                       cov= as.character(rep(NA,60)))
+
+# View(timecourse_result_df)
+# nbins<- nbins[1:60]
+
+i = 0 # remember to always rezero it
+# b = 10
+
+# rm(i,b)
+
+# i =1
+# unique(tmp.df4_full_stim_downs_jun2021_60bins$)
+
+for (b in 1:length(nbins)) {
+  # for (s in 1:length(nsim)) {
+
+    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
+        lmer_bin_pup  <- lmer(pup_basCor ~ arousal_c + Mean_gray_z  +
+                                (1 | ssid),
+                              REML = FALSE,
+                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
+                                    ssid_num < 500 & ground_valence_lab == "More negative" &
+                                    timebin_no == nbins[b]))
+
+        #store results from the simulation
+            lmer_bin_pup_summary<- summary(lmer_bin_pup)
+            lmer_bin_pup_summary
+            # lmer_bin_pup_summary[["coefficients"]][3,1]
+            timecourse_60bin_result_df_neg[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
+            #save the exact value of time bin
+            # store arousal (2,parameter)            # first number is term(row), second is column
+            timecourse_60bin_result_df_neg[i,2]<-
+            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
+            timecourse_60bin_result_df_neg[i,3]<-
+              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
+            timecourse_60bin_result_df_neg[i,4]<-
+            lmer_bin_pup_summary[["coefficients"]][2,5] # p value
+
+            # brightness
+
+            timecourse_60bin_result_df_neg[i,5]<-
+            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
+            timecourse_60bin_result_df_neg[i,6]<-
+              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
+            timecourse_60bin_result_df_neg[i,7]<-
+              lmer_bin_pup_summary[["coefficients"]][3,5] # p value
+
+            timecourse_60bin_result_df_neg[i,8] <-
+              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
+                                                   != 0,
+                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')
+
+     i = i+1
+}
+
+# timecourse_result_df_pos<- timecourse_result_df
+View(timecourse_60bin_result_df_neg)
+
+# adjust p values
+timecourse_60bin_result_df_neg$p_ar_adj<- p.adjust(timecourse_60bin_result_df_neg$p_ar, method = "holm")
+timecourse_60bin_result_df_neg$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df_neg$p_ar_adj<.05, TRUE, FALSE)
+
+timecourse_60bin_result_df_neg$p_br_adj <- p.adjust(timecourse_60bin_result_df_neg$p_br, method = "holm")
+timecourse_60bin_result_df_neg$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df_neg$p_br_adj<.05, TRUE, FALSE)
+
+View(timecourse_60bin_result_df_neg)
+
+timecourse_60bin_result_df_neg[1:56,] %>%
+  ggplot(aes(timebins, Estimate_ar))+
+  geom_line(size = 1)+
+  geom_line(aes(y = Estimate_br), linetype = "dashed", size = 1)
+
+```
 Pupil velocity test

### 2021-07-28 Old scripts/pupil_arousal_datarmd.Rmd
one more

@@
 timecourse_result_df%>%
-  ggplot(aes(timebins, t))+
+  ggplot(aes(timebins, Estimate))+
   geom_line(size = 2)+
@@
 
+subset(tmp.df4_full_stim_downs_jun2021_with_behnew,
+                                    mediansplit_ground_valence == "More negative" & 
+                                    timebin_no == nbins[b])%>%
+  ggplot(aes(ArousalMean))
+
 ```
@@
 timecourse_result_df_val_and_ar%>%
-  ggplot(aes(timebins, t))+
+  ggplot(aes(timebins, Estimate))+
   geom_line(size = 2)+
@@
 timecourse_result_df_val_and_ar_low%>%
-  ggplot(aes(timebins, t))+
+  ggplot(aes(timebins, Estimate))+
   geom_line(size = 2)+
@@
 
-pupil_arousal_findings$arousal_scr <- lmer(BIO_CDA.PhasicMax_z ~ valence_c +(1+arousal_c|ssid),
+pupil_arousal_findings$arousal_scr <- lmer(BIO_CDA.PhasicMax_z ~ valence_c +(1|ssid),
                         REML = FALSE,
@@
 
-scr_models$scr2<- lmer(BIO_CDA.ISCR_collapsed ~  arousal_c*valence_c *TASc+
+scr_models$scr2<- lmer(BIO_CDA.ISCR_collapsed ~  arousal_c*valence_c+
                                            (1| ssid) +
@@
 
-scr_models$scr2<- lmer(BIO_CDA.SCR_collapsed ~  arousal_c* valence_c *TASc+
+scr_models$scr2<- lmer(BIO_CDA.SCR_collapsed ~  arousal_c* valence_c +
                                            (1| ssid) +
@@
 
-```
-
 heart rate
-
 ```{r}
@@
     ggpubr::stat_cor()
-
-```
 
@@
 ```{r}
+unique(db_full6new_hr_fix_stim_nt1$Group)
 # test - analyse just positive
-hr_dif_models$arousal_val <- lmer(Bio_Mean_HR_dif ~  valence_c *arousal_c+
+hr_dif_models$arousal_val <- lmer(Bio_Mean_HR_dif ~   valence_c+
+                                        + (1 | ssid) + 
+                                    (1|stimIAPS),
+                                        # (1|mediansplit_sample_arousal2),
+     REML = FALSE,
+     data = subset(db_full6new_hr_fix_stim_nt1, 
+                   # mediansplit_ground_valence == "More negative" &
+                     Bio_Mean_HR_dif_outl == "not outlier"  & Group == "NT"))
+
+hr_dif_models$arousal_AR <- lmer(Bio_Mean_HR_dif ~   arousal_c+
+                                        + (1 | ssid) + 
+                                    (1|stimIAPS),
+                                        # (1|mediansplit_sample_arousal2),
+     REML = FALSE,
+     data = subset(db_full6new_hr_fix_stim_nt1, 
+                   # mediansplit_ground_valence == "More negative" &
+                     Bio_Mean_HR_dif_outl == "not outlier"  & Group == "NT"))
+
+summary(hr_dif_models$arousal_AR)
+
+unique(db_full6new_hr_fix_stim_nt1$ssid)
+hr_dif_models$valfrom_hr <- lmer(arousal_c ~   Bio_Mean_HR_dif* valence_c+
                                         + (1 | ssid) + (1|stimIAPS),
@@
      REML = FALSE,
-     data = subset(db_full6new_hr_fix_stim_nt1, mediansplit_ground_valence == "More positive" & Bio_Mean_HR_dif_outl == "not outlier"  & Group == "NT"))
-
-summary(hr_dif_models$arousal_val)
-
-unique(db_full6new_hr_fix_stim_nt1$ssid)
-hr_dif_models$valfrom_hr <- lmer(valence_c ~   Bio_Mean_HR_dif* arousal_c+
-                                        + (1 | ssid) + (1|stimIAPS),
+     data = subset(db_full6new_hr_fix_stim_nt1, 
+                   # mediansplit_ground_valence == "More positive" &
+                   Bio_Mean_HR_dif_outl == "not outlier" & Group == "NT"))
+arousal_c
+summary(hr_dif_models$valfrom_hr)
+
+install.packages("glmmLasso")
+require(glmmLasso)
+?glmmLasso::glmmLasso()
+
+HR_dif_forlasso<- subset(db_full6new_hr_fix_stim_nt1, 
+                   # mediansplit_ground_valence == "More positive" &
+                   Bio_Mean_HR_dif_outl == "not outlier" & Group == "NT")
+
+HR_dif_forlasso<- HR_dif_forlasso%>%subset(!is.na(valence_c))
+
+HR_dif_forlasso$ssid<- as.factor(HR_dif_forlasso$ssid)
+lassomodels<- list()
+
+lassomodels$firt<- glmmLasso(Bio_Mean_HR_dif ~ arousal_c + valence_c, rnd = list(ssid=~1), 
+       lambda=1000, data = HR_dif_forlasso, final.re=TRUE)
+
+# table(is.na(HR_dif_forlasso$arousal_c))
+# 
+# table(is.na(HR_dif_forlasso$valence_c))
+
+summary(lassomodels$firt)
+
+################# More Elegant Method ############################################
+## Idea: start with big lambda and use the estimates of the previous fit (BUT: before
+## the final re-estimation Fisher scoring is performed!) as starting values for the next fit;
+## make sure, that your lambda sequence starts at a value big enough such that all covariates are
+## shrinked to zero;
+
+## Using BIC (or AIC, respectively) to determine the optimal tuning parameter lambda
+lambda <- seq(500,0,by=-5)
+
+BIC_vec<-rep(Inf,length(lambda))
+# family = poisson(link = log)
+
+# specify starting values for the very first fit; pay attention that Delta.start has suitable length! 
+Delta.start<-as.matrix(t(rep(02)))
+Q.start<-0.1  
+HR_dif_forlasso_1<- select(HR_dif_forlasso, c(ssid, valence_c, arousal_c,Bio_Mean_HR_dif))
+table(is.na(HR_dif_forlasso$Bio_Mean_HR_dif))
+J = 1
+
+for (j in lambda) {
+
+  glm3 <- glmmLasso(Bio_Mean_HR_dif ~ arousal_c + valence_c, rnd = list(ssid=~1),  
+                    # family = family,
+                    data = HR_dif_forlasso_1, 
+                    lambda=500, 
+                    switch.NR=F,
+                    final.re=TRUE,
+                    control = list(start=Delta.start[j],
+                                   q_start=Q.start[j]))
+
+  # print(colnames(glm3$Deltamatrix)[2:7][glm3$Deltamatrix[glm3$conv.step,2:7]!=0])
+  # BIC_vec[j]<-glm3$bic
+  # Delta.start<-rbind(Delta.start,glm3$Deltamatrix[glm3$conv.step,])
+  # Q.start<-c(Q.start,glm3$Q_long[[glm3$conv.step+1]])
+  }
+
+opt3<-which.min(BIC_vec)
+
+glm3_final <- glmmLasso(points~transfer.spendings + ave.unfair.score 
+                        + ball.possession
+                        + tackles + ave.attend + sold.out, rnd = list(team=~1),  
+                        family = family, data = soccer, lambda=lambda[opt3],
+                        switch.NR=F,final.re=TRUE,
+                        control = list(start=Delta.start[opt3,],q_start=Q.start[opt3]))
+
+summary(glm3_final)
+
+## plot coefficient paths
+par(mar=c(6,6,4,4))
+plot(lambda,Delta.start[2:(length(lambda)+1),2],type="l",ylim=c(-1e-1,1e-1),ylab=expression(hat(beta[j])))
+lines(c(-1000,1000),c(0,0),lty=2)
+for(i in 3:7){
+  lines(lambda[1:length(lambda)],Delta.start[2:(length(lambda)+1),i])
+}
+abline(v=lambda[opt3],lty=2)
+```
+
+hr_dif_models$arousal_val <- lmer(Bio_Mean_HR_dif ~   valence_c* arousal_c+
+                                        + (1 | ssid),
+                                    # (1|stimIAPS),
                                         # (1|mediansplit_sample_arousal2),
      REML = FALSE,
-     data = subset(db_full6new_hr_fix_stim_nt1, mediansplit_ground_valence == "More positive" &
-                   Bio_Mean_HR_dif_outl == "not outlier" & Group == "NT"))
-arousal_c
-
-summary(hr_dif_models$valfrom_hr)
+     data = subset(db_full6new_hr_fix_stim_nt1, 
+                   # mediansplit_ground_valence == "More negative" &
+                     # Bio_Mean_HR_dif_outl == "not outlier"  & 
+                     Group == "NT"))
+
+summary(hr_dif_models$arousal_val)
+
+car::vif(hr_dif_models$arousal_val)
 
 interactions::interact_plot(hr_dif_models$valfrom_hr, pred = Bio_Mean_HR_dif, modx = arousal_c)
+
+interactions::interact_plot(hr_dif_models$arousal_val, pred =arousal_c , modx =  valence_c)
 
@@
 
-db_full6new_hr_fix_stim_nt1%>%
+db_full6new_hr_fix_stim_nt1$groung%>%
   subset(Condition == "IAPS")%>%
@@
 # try and regress valence our oarousal_val
+```{r}
 
@@
 
-```
-
 interactions::interact_plot(hr_dif_models$arousal_val, pred= arousal_c, modx = valence_c)
+
+```
 
@@
 
+```
+
+```{r}
 summary(hr_dif_models$arousal_val_cat)

### 2021-07-28 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd
one more
check

@@
 ```{r}
+
+# group_by(stimIAPS)%>%
+tmp.df4_full_stim_downs_jun2021_with_beh<- tmp.df4_full_stim_downs_jun2021_with_beh %>%
+  ungroup()%>%
+  mutate(mediansplit_sample_valence2 = 
+           if_else(ValenceMeanThisSample >= 
+                     median(ValenceMeanThisSample,
+                            na.rm = TRUE), 
+                   "More positive", "More negative"))%>%
+  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >=
+                                                  median(ArousalMeanThisSample,
+                                                         na.rm = TRUE), "High", "Low"))
+
+# higher sample rate]
+
+tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins %>%
+  ungroup()%>%
+  mutate(mediansplit_sample_valence2 = 
+           if_else(ValenceMeanThisSample > 
+                     median(ValenceMeanThisSample,
+                            na.rm = TRUE), 
+                   "More positive", "More negative"))%>%
+  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >
+                                                  median(ArousalMeanThisSample,
+                                                         na.rm = TRUE), "High", "Low"))
+
 tmp.df4_full_stim_downs_jun2021_with_beh %>%
@@
 
-# group_by(stimIAPS)%>%
-tmp.df4_full_stim_downs_jun2021_with_beh<- tmp.df4_full_stim_downs_jun2021_with_beh %>%
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(!is.na(ground_arousal_lab))%>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  stat_smooth(aes(group= mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), fun = mean,geom = "line",
+               se = F, alpha = .1, size = 1.5)+
+  stat_smooth(aes(group=mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), size = 3)+  
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")+
+  xlim(0,6)+
+   facet_grid(~mediansplit_sample_valence2)
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(!is.na(ground_arousal_lab))%>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  stat_smooth(aes(group= mediansplit_sample_valence2, color = mediansplit_sample_valence2), fun = mean,geom = "line",
+               se = F, alpha = .1, size = 1.5)+
+  stat_smooth(aes(group=, color = mediansplit_sample_valence2), size = 3)+  
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")+
+  xlim(0,6)+
+   facet_grid(~ mediansplit_sample_arousal2)
+
+# what causes 
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(!is.na(ground_arousal_lab))%>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  stat_smooth(aes(group= mediansplit_sample_valence2, color = mediansplit_sample_valence2), fun = mean,geom = "line",
+               se = F, alpha = .1, size = 1.5)+
+  stat_smooth(aes(group=, color = mediansplit_sample_valence2), size = 3)+  
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")+
+  xlim(0,6)
+   facet_grid(~ mediansplit_sample_arousal2)
+
+   tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(!is.na(ground_arousal_lab))%>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  stat_smooth(aes(color = mediansplit_sample_arousal2), fun = mean,geom = "line",
+               se = F, alpha = .1, size = 1.5)+
+  stat_smooth(aes(group=stimIAPS, color = mediansplit_sample_arousal2), size = .6, se = F)+
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+     # geom_text(aes(label = ssid))+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")+
+  xlim(0,6)+
+     geom_text(aes(label = stimIAPS))
+   facet_grid(~ mediansplit_sample_valence2)
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(!is.na(ground_arousal_lab))%>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  # stat_smooth(aes(color = mediansplit_ground_arousal), fun = mean,geom = "line",
+  #              se = F, alpha = .1, size = 1.5)+
+  stat_smooth(aes(group=stimIAPS, color = ground_arousal_lab), size = .6, se = F)+
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+     # geom_text(aes(label = ssid))+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")+
+  xlim(0,6)+
+     # geom_text(aes(label = stimIAPS))+
+   facet_grid(~ ground_valence_lab)
+
+# - use IAPS data to split valence - positive negative
+# - within that - compute arousal low mid high within each valence both for the iaps data and my study
+# do this on a participant basis or sampleÇ? try sample first
+tmp.df4_full_stim_downs_jun2021_60bins %>%
   ungroup()%>%
   mutate(mediansplit_sample_valence2 = 
-           if_else(ValenceMeanThisSample >= 
+           if_else(ValenceMeanThisSample > 
                      median(ValenceMeanThisSample,
@@
                    "More positive", "More negative"))%>%
-  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >=
-                                                  median(ArousalMeanThisSample,
-                                                         na.rm = TRUE), "High", "Low"))
-
-# higher samp[le rate]
-
-tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins %>%
-  ungroup()%>%
-  mutate(mediansplit_sample_valence2 = 
-           if_else(ValenceMeanThisSample >= 
-                     median(ValenceMeanThisSample,
-                            na.rm = TRUE), 
-                   "More positive", "More negative"))%>%
-  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >=
+  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >
                                                   median(ArousalMeanThisSample,
@@
 # unique(tmp.df4_full_stim_downs_jun2021_60bins$)
-
 for (b in 1:length(nbins)) {
@@
 
-plots_timecourse$eff_size_pup_velocity + 
+plots_timecourse$eff_size_pup_velocity<- plots_timecourse$eff_size_pup_velocity + 
   p$graphstyle +
@@
 
+plots_timecourse$eff_size_pup_velocity
 plots_timecourse$eff_size_pup_amp
-
-    # valence - no significance
-
-    # scale_fill_brewer()
-
-?annotate
 

### 2021-07-28 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
   summarise_at(c('arousal_c', 'Mean_gray_z'), mean, na.rm = TRUE)%>%
+  ggplot(aes(arousal_c, Mean_gray_z, color = ground_valence_lab))+
+  geom_point()+
+  ggpubr::stat_cor()
+
+db_full4new_stim_screen_pupil_nopract %>%
+  subset(ssid_num<500)%>%
+  group_by(ssid)%>%
+  mutate(cor_ar_vl = cor(arousal, valence, use = "complete"))%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ssid,cor_ar_vl))+
+  geom_point()+
+  geom_hline(yintercept = -.75)+
+  geom_hline(yintercept = -.90)
+  geom_histogram()
+
   ggplot(aes(arousal_c, Mean_gray_z, color = ground_valence_lab))+
@@
 
+```
+
+```{r}
 tmp.df4_full_stim_downs_jun2021_60bins %>%
@@
    facet_grid(~mediansplit_self_valence)
+
+```
+
+```{r}
 
@@
 
+```
+
+```{r Scrap this}
+
 # - use IAPS data to split valence - positive negative
@@
   ungroup()%>%
-  mutate(mediansplit_sample_valence2 = 
-           if_else(ValenceMeanThisSample > 
-                     median(ValenceMeanThisSample,
-                            na.rm = TRUE), 
-                   "More positive", "More negative"))%>%
-  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >
-                                                  median(ArousalMeanThisSample,
-                                                         na.rm = TRUE), "High", "Low"))
+  group_by(ground_valence_lab)%>%
+  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
+   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
+  group_by(stimIAPS,ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
+  ggplot(aes(ground_valence_lab, Arousal_z_by_val ))+
+  # geom_point()+
+  stat_summary(geom = 'pointrange')
+
+# hpw does this relate to the original ratigs
+
+# do this on a participant basis or sampleÇ? try sample first
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  ungroup()%>%
+  group_by(ground_valence_lab)%>%
+  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
+   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
+  # group_by(stimIAPS,ground_valence_lab)%>%
+  # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
+  ggplot(aes(ValenceMean, ArousalMean_z_by_val ))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  # geom_smooth(aes(group = ground_valence_lab), method = 'lm', se = F)
+  # stat_summary(geom = 'pointrange')+
+      ggpubr::stat_cor()
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  ungroup()%>%
+  group_by(ground_valence_lab)%>%
+  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
+   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
+  group_by(stimIAPS,ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
+  ggplot(aes(Arousal_z_by_val, valence_c))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  # geom_smooth(aes(group = ground_valence_lab), method = 'lm', se = F)
+  # stat_summary(geom = 'pointrange')+
+      ggpubr::stat_cor()
+
+?cut
+tmp.df4_full_stim_downs_jun2021_60bins$valence_self<- cut(tmp.df4_full_stim_downs_jun2021_60bins$valence, 3,
+                                                          labels = c("Negative", "Neutral", "Positive"))
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  ungroup()%>%
+  group_by(ground_valence_lab)%>%
+  # mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
+   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
+  group_by(stimIAPS,ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
+  ggplot(aes(ground_valence_lab, Arousal_z_by_val))+
+  geom_point()+
+  # geom_smooth(aes(group = ground_valence_lab), method = 'lm', se = F)
+  stat_summary(geom = 'pointrange')+
+      ggpubr::stat_cor()
+
+  # mean center within neutral positive, neutral negative
+
+tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos<- if_else(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab!= "More negative", TRUE, FALSE)
+
+tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg <- if_else(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab!= "More positive", TRUE, FALSE)
+
+tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(neutral_pos)%>%
+  mutate(neutral_pos_mean_arousal = mean(ArousalMean, na.rm = TRUE),
+                                         neutral_pos_sd_arousal = sd(ArousalMean, na.rm = TRUE))%>%
+  mutate(neutral_pos_mean_arousal_self = mean(arousal, na.rm = TRUE),
+         neutral_pos_sd_arousal_self = sd(arousal, na.rm = TRUE))%>%
+  group_by(neutral_neg)%>%
+
+  mutate(neutral_neg_mean_arousal = mean(ArousalMean, na.rm = TRUE),
+                                         neutral_sd_mean_arousal = sd(ArousalMean, na.rm = TRUE)) %>%
+  mutate(neutral_neg_mean_arousal_self = mean(arousal, na.rm = TRUE),
+         neutral_neg_sd_arousal_self = sd(arousal, na.rm = TRUE))
+
+# group_by()
+
+# replace the values when neutral_pos and neutral_neg is FALSE respectivelly
+# library(dplyr)
+# check how many nas do we have before we start
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_mean_arousal))
+ # FALSE   TRUE 
+# 158193  13975 
+tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
+    mutate_at(vars(matches('^neutral_pos_.*$')), ~ 
+                  replace(., neutral_pos == FALSE, NA))
+
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_mean_arousal))
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_sd_arousal_self))
+
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_mean_arousal_self))
+
+tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
+    mutate_at(vars(matches('^neutral_neg_.*$')), ~ 
+                  replace(., neutral_neg == FALSE, NA))
+
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_sd_arousal_self))
+
+tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_mean_arousal <- if_else(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$)
+
+```
+
+```{r}
+  tmp.df4_full_stim_downs_jun2021_60bins %>%
+  ungroup()%>%
+  group_by(ground_valence_lab)%>%
+  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
+   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
+  group_by(stimIAPS,ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
+  ggplot(aes(valence_c, ArousalMean ))+
+  geom_point()+
+  # geom_smooth(aes(group = ground_valence_lab), method = 'lm', se = F)
+  stat_summary(geom = 'pointrange')+
+  ggpubr::stat_cor()
+
+      tmp.df4_full_stim_downs_jun2021_60bins %>%
+  ungroup()%>%
+  group_by(ground_valence_lab)%>%
+  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
+
+      group_by(ground_valence_lab)%>%
+   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
+  group_by(stimIAPS,ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
+  ggplot(aes(ArousalMean_z_by_val,pup_basCor ))+
+  geom_point()+
+      geom_smooth(method = 'lm', se = F)+
+      ggpubr::stat_cor()
+
+    tmp.df4_full_stim_downs_jun2021_60bins %>%
+  ungroup()%>%
+  group_by(ground_valence_lab)%>%
+  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
+
+      group_by(ground_valence_lab)%>%
+   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
+  group_by(stimIAPS,ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
+  ggplot(aes(Arousal_z_by_val,pup_basCor ))+
+  geom_point()+
+      geom_smooth(method = 'lm', se = F)+
+      ggpubr::stat_cor()
+  # geom_smooth(aes(color = ground_valence_lab), method = 'lm', se = F)
+
+    # original variable
+
+      tmp.df4_full_stim_downs_jun2021_60bins %>%
+  ungroup()%>%
+  group_by(ground_valence_lab)%>%
+  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
+
+      group_by(ground_valence_lab)%>%
+   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
+  group_by(stimIAPS,ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
+  ggplot(aes(pup_basCor,arousal))+
+  geom_point()+
+      geom_smooth(method = 'lm', se = F)+
+      ggpubr::stat_cor()
+
+  geom_smooth(aes(color = ground_valence_lab), method = 'lm', se = F)
+        tmp.df4_full_stim_downs_jun2021_60bins %>%
+  ungroup()%>%
+  group_by(ground_valence_lab)%>%
+  mutate(ArousalMean_z_by_val = scale(ArousalMean, center = TRUE, scale = TRUE)[,1])%>%
+
+      group_by(ground_valence_lab)%>%
+   mutate(Arousal_z_by_val = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
+  group_by(stimIAPS,ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # ggplot(aes(ground_valence_lab, ArousalMean_z_by_val ))+
+  ggplot(aes(pup_basCor, ArousalMean))+
+  geom_point()+
+          geom_smooth(method = 'lm', se = F)+
+          ggpubr::stat_cor()
+  # geom_smooth(aes(group = ground_valence_lab), method = 'lm', se = F)
 

### 2021-08-02 Paper_Analyses_subj_obje_arousal.Rmd
back to it

@@
 # 158193  13975
+
+# compute new varoables where arousal is scaled to negative (negative value - mean of negative and neutral) same to positive
 tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
@@
 
-tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_mean_arousal <- if_else(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$)
+tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_mean_arousal <- if_else(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE, tmp.df4_full_stim_downs_jun2021_60bins)
+
+colnames(tmp.df4_full_stim_downs_jun2021_60bins)
 

### 2021-08-02 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
   mutate(neutral_neg_mean_arousal = mean(ArousalMean, na.rm = TRUE),
-                                         neutral_sd_mean_arousal = sd(ArousalMean, na.rm = TRUE)) %>%
+                                         neutral_neg_sd_arousal = sd(ArousalMean, na.rm = TRUE)) %>%
   mutate(neutral_neg_mean_arousal_self = mean(arousal, na.rm = TRUE),
@@
 
-# compute new varoables where arousal is scaled to negative (negative value - mean of negative and neutral) same to positive
+# compute new variables where arousal is scaled to negative (negative value - mean of negative and neutral) same to positive
 tmp.df4_full_stim_downs_jun2021_60bins <- tmp.df4_full_stim_downs_jun2021_60bins %>%
@@
 
+tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
+                                                                      tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean - tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_mean_arousal,
+                                                                    ifelse(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More negative" & tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean -
+                                                                             tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_mean_arousal, 
+                                                                           tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean - mean(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean, na.rm = TRUE)))
+
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground))
+
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground), tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab)
+
+library(tidyverse)
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(stimIAPS, ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ground_valence_lab, ArousalMean))+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(stimIAPS, ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ground_valence_lab, arousal_rel_neutral_ground))+
+  # geom_point()+
+  stat_summary(geom = 'pointrange')
+
+tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground_z <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
+                                                                      tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_sd_arousal,
+                                                                    ifelse(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More negative" & tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground /
+                                                                             tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_sd_arousal, 
+                                                                           tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ sd(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean, na.rm = TRUE)))
+
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground))
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground), tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab)
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(stimIAPS, ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ground_valence_lab, ArousalMean))+
+  # geom_point()+
+  # stat_summary(geom = 'pointrange')
+ geom_boxplot()
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  group_by(stimIAPS, ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ground_valence_lab, arousal_rel_neutral_ground_z ))+
+  # geom_point()+
+  geom_boxplot()
+  # stat_summary(geom = 'pointrange')
 ```

### 2021-08-03 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 
+# same with self report
+
+tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_self <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
+                                                                      tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$arousal - tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_mean_arousal_self,
+                                                                    ifelse(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More negative" & tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$arousal -
+                                                                             tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_mean_arousal_self, 
+                                                                           tmp.df4_full_stim_downs_jun2021_60bins$arousal - mean(tmp.df4_full_stim_downs_jun2021_60bins$arousal, na.rm = TRUE)))
+
+# visualise new ground and self report arousal baseline separetelly for positive and negative valenced stimuli (based on IAPS validation)
 table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground))
@@
 
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(stimIAPS, ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ground_valence_lab, arousal_rel_neutral_self))+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+arousal_rel_neutral_self
+```
+```{r}
+# create the new arousal corrected within positive/negative - neutral
 tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground_z <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
+                                                                      tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_sd_arousal,
+                                                                    ifelse(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More negative" & tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg == TRUE, tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground /
+                                                                             tmp.df4_full_stim_downs_jun2021_60bins$neutral_neg_sd_arousal, 
+                                                                           tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ sd(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMean, na.rm = TRUE)))
+
+# do the same with self report arousal but using ground valence?
+tmp.df4_full_stim_downs_jun2021_60bins$arousal_self_rel_neutral_ground_z <- ifelse(tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos == TRUE & 
                                                                                      tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_lab == "More positive", tmp.df4_full_stim_downs_jun2021_60bins$arousal_rel_neutral_ground/ tmp.df4_full_stim_downs_jun2021_60bins$neutral_pos_sd_arousal,
@@
   # stat_summary(geom = 'pointrange')
+
+# original valence arousal
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  group_by(stimIAPS, ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ValenceMean, ArousalMean ))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  group_by(stimIAPS, ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ValenceMean, arousal_rel_neutral_ground_z ))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()
+
 ```

### 2021-08-03 Paper_Analyses_subj_obje_arousal.Rmd
Absolluting arousal response
Given the that under some views the phrasing of the arousal question can be seen as dichotomic, we can absolute it if don't care about the direction, while preserving the intensity. This seems to work well, but need to see if it changes teh relationship with other variables of interest (e.g. correlation between subjective and objective arousal

@@
 arousal_rel_neutral_self
+
+# ?cut
+# is the cutoff for positive in the prevopis variable too large
+tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_2<- cut(tmp.df4_full_stim_downs_jun2021_60bins$ValenceMean, c(0,4,5,9), 
+                                                              labels = c("negative", "neutral", "positive"))
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(stimIAPS, ssid,ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(stimIAPS, abs(arousal), color = ground_valence))+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange')
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(stimIAPS, ssid,ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ground_valence, abs(arousal), color = ground_valence))+
+  geom_boxplot()+
+  stat_summary(funy = mean, geom = 'pointrange')
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  subset(!is.na(ground_valence))%>%
+  group_by(stimIAPS, ssid,ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ground_valence, abs(arousal), color = ground_valence))+
+  geom_boxplot()+
+  stat_summary(funy = mean, geom = 'pointrange')
+
+# absoluting
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  subset(!is.na(ground_valence))%>%
+  group_by(ssid,ground_valence)%>%
+  mutate(mean_abs_arousal = mean(abs(arousal), na.rm = TRUE))%>%
+  summarise_at(mean_abs_arousal)
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(stimIAPS, ssid,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(stimIAPS, abs(arousal), color = ground_valence_2))+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange')
+
+```
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(stimIAPS, ssid,valence_self)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(stimIAPS, arousal, color = valence_self))+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange')
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(stimIAPS, ssid,valence_self)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(stimIAPS, abs(valence), color = valence_self))+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange')
+
+tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(stimIAPS, ssid,ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(stimIAPS, abs(valence), color = ground_valence))+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange')
 ```

### 2021-08-03 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
   subset(!is.na(ground_valence))%>%
-  group_by(ssid,ground_valence)%>%
-  mutate(mean_abs_arousal = mean(abs(arousal), na.rm = TRUE))%>%
-  summarise_at(mean_abs_arousal)
+  # group_by(ground_valence)%>%
+  ungroup()%>%
+  mutate(abs_arousal = abs(arousal), na.rm = TRUE)%>%
+  mutate(abs_arousal_z = abs_arousal - mean(abs_arousal, na.rm = TRUE))%>%
+  # summarise_at(c('mean_abs_arousal'), median, na.rm = TRUE)
+  group_by(ssid,ground_valence_2)%>%
+  summarise_if(is.numeric, median, na.rm = TRUE)%>%
+  ggplot(aes(ground_valence_2, abs_arousal_z, color = ground_valence_2))+
+  geom_point()+
+  stat_summary(funy = median, geom = 'pointrange')+
+  geom_boxplot()
 
@@
 
+# does absolute arousal correlate with other variables of interest
+tmp.df4_full_stim_downs_jun2021_60bins$abs_arousal<- abs(tmp.df4_full_stim_downs_jun2021_60bins$arousal)
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num< 500)%>%
+  subset(!is.na(groun_valence))%>%
+  group_by(ssid, stimIAPS)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(pup_basCor, arousal))+
+  geom_point()+
+  stat_smooth(aes(group = ssid),method = 'lm', se = F)
+    ggpubr::stat_cor()
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(!is.na(groun_valence))%>%
+  group_by(ssid, stimIAPS)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(pup_basCor, abs_arousal))+
+  geom_point()+
+  geom_smooth(aes(group = ssid),method = 'lm', se = F)+
+  ggpubr::stat_cor()+
+  facet_grid()
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(!is.na(groun_valence))%>%
+  group_by(ssid, stimIAPS,ground_valence_lab)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  group_by(ssid,ground_valence_lab)%>%
+  mutate(corar = cor(abs_arousal, pup_basCor, use = "complete"))%>%
+  ggplot(aes(ground_valence_lab, corar))+
+  # geom_point()
+  stat_summary(geom = 'pointrange')
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  group_by(stimIAPS)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ArousalMean, ArousalMeanThisSample))+
+  geom_point()+
+  ggpubr::stat_cor()
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  group_by(stimIAPS)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ArousalMean, abs_arousal))+
+  geom_point()+
+  ggpubr::stat_cor()
+# this again suggests that there is not too much of a problem in our response format as the absolute would be the equivalent of an scale that encodes for calence (direction)
 ```

### 2021-08-03 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 ```{r}
+
+db_full4new_stim_screen_pupil_nopract$ssid<- as.factor(as.character(db_full4new_stim_screen_pupil_nopract$ssid))
 
@@
                                       arousal_outler == FALSE))
-
-# relgrad <- with(pupil_arousal_findings$pupil_from_ar_vale@optinfo$derivs,solve(Hessian,gradient))
-# max(abs(relgrad))0.0002044252
+unique(db_full4new_stim_screen_pupil_nopract$tNo)
+
+unique(db_full4new_stim_screen_pupil_nopract$ssid)
+relgrad <- with(pupil_arousal_findings$pupil_from_ar_vale@optinfo$derivs,solve(Hessian,gradient))
+max(abs(relgrad)) #0.0002044252
 
@@
 
-interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_val_gaze , pred = arousal_c, modx = valence_c)
+plots_paper$interaction_ar_vl <- interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale , pred = arousal_c, modx = valence_c, plot.points = TRUE)
 
@@
 
-interactions::interact_plot(pupil_arousal_findings$pupil_resid_from_ar_vale , pred = arousal_c, modx = valence_c)
+plots_paper<- list()
+plots_paper$interaction_ar_vl <- interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale, pred = arousal_c, modx = valence_c)
 
@@
 
+plots_paper$interaction_ar_vl+p$graphstyle
+```
+interaction plot
+
+```{r}
+sf = 1 # scaling factor to make it easier to change sizes of everything, in which case change here
+
+p$graphstyle_int <-  theme(#base plot theme
+
+  # axis lines
+  axis.line.y = element_line(color="black", size = 1.5),
+  axis.line.x = element_line(color="black", size = 1,5),
+
+  axis.title.y=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
+  axis.title.x=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
+
+  # text
+  strip.text.x = element_text(size = 12*(sf+.5),  colour = "black"),
+  strip.text.y = element_text(size = 12*(sf+.5),  colour = "black"),
+
+  text=element_text(size = 14, family = "sans"),
+  axis.text.x = element_text(size = 14*(sf+.5), family = "sans", colour = "black",),
+  axis.text.y = element_text(size = 14*(sf+.5), family = "sans", colour = "black"),
+
+  # panel
+  panel.grid.major = element_blank(),
+  panel.background = element_blank(),
+  # panel.background = element_rect(fill="transparent"),
+  # panel.border = element_rect(fill="transparent"),
+  # strip shades (reco rectagles)
+   # strip.background = element_blank(),
+
+  # legend
+  legend.position = "top",
+  legend.key = element_rect(colour = "transparent", fill="transparent"),
+  #legend.direction = "horizontal",
+
+  legend.text = element_text(size = 10*(sf+.3)),
+  # legend.title = element_text(size = 10*(sf+.3)),
+  # legend line tends to be really small in print so adjust here
+  legend.key.height = unit(.5, "cm"),
+  legend.key.width = unit(2, "cm"),
+
+  #legend.text = element_text(size = 10*sf),
+  # legend.title=element_blank(),
+  #legend.text = element_blank(),
+  #axis.ticks = element_blank(),
+)
+
+plots_paper$interaction_ar_vl<- plots_paper$interaction_ar_vl +
+  theme_classic()+
+  p$graphstyle_int+
+  xlab("Arousal (z)")+
+  ylab("Pupil change (z)")+
+  scale_y_continuous(breaks = c(-1,0,1))
+
+plots_paper$interaction_ar_vl<- plots_paper$interaction_ar_vl+   scale_y_continuous(breaks = c(-2,-1,0,1), limits = c(-2,1))
+
+ plots_paper$interaction_ar_vl +
+   theme_classic()+
+   p$graphstyle_int
+
+plots_paper[["interaction_ar_vl"]][["data"]]%>%
+  ggplot(aes(arousal_c, pup_basCor, linetype = modx_group))+
+  stat_summary(aes(color = valence_c), geom = 'line', size = 2)+
+  p$graphstyle_int
 ```
@@
 
-tmp.df4_full_stim_downs_jun2021_60bins%>%
-  group_by(stimIAPS, ssid,valence_self)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(stimIAPS, arousal, color = valence_self))+
-  # geom_point()+
-  stat_summary(funy = mean, geom = 'pointrange')
-
-tmp.df4_full_stim_downs_jun2021_60bins%>%
-  group_by(stimIAPS, ssid,valence_self)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(stimIAPS, abs(valence), color = valence_self))+
-  # geom_point()+
-  stat_summary(funy = mean, geom = 'pointrange')
-
-tmp.df4_full_stim_downs_jun2021_60bins%>%
-  group_by(stimIAPS, ssid,ground_valence)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(stimIAPS, abs(valence), color = ground_valence))+
-  # geom_point()+
-  stat_summary(funy = mean, geom = 'pointrange')
-```
+<!-- tmp.df4_full_stim_downs_jun2021_60bins%>% -->
+<!--   group_by(stimIAPS, ssid,valence_self)%>% -->
+<!--   summarise_if(is.numeric, mean, na.rm = TRUE)%>% -->
+<!--   ggplot(aes(stimIAPS, arousal, color = valence_self))+ -->
+<!--   # geom_point()+ -->
+<!--   stat_summary(funy = mean, geom = 'pointrange') -->
+
+<!-- tmp.df4_full_stim_downs_jun2021_60bins%>% -->
+<!--   group_by(stimIAPS, ssid,valence_self)%>% -->
+<!--   summarise_if(is.numeric, mean, na.rm = TRUE)%>% -->
+<!--   ggplot(aes(stimIAPS, abs(valence), color = valence_self))+ -->
+<!--   # geom_point()+ -->
+<!--   stat_summary(funy = mean, geom = 'pointrange') -->
+
+<!-- tmp.df4_full_stim_downs_jun2021_60bins%>% -->
+<!--   group_by(stimIAPS, ssid,ground_valence)%>% -->
+<!--   summarise_if(is.numeric, mean, na.rm = TRUE)%>% -->
+<!--   ggplot(aes(stimIAPS, abs(valence), color = ground_valence))+ -->
+<!--   # geom_point()+ -->
+<!--   stat_summary(funy = mean, geom = 'pointrange') -->
+
 ```{r}
@@
 
+use the same dataas timecourse to plot aggregated analyses
+aggregate arousal plot
+```{r}
+
+db_full4new_stim_screen_pupil_nopract$ground_valence_2<-
+  cut(db_full4new_stim_screen_pupil_nopract$ValenceMean, c(0,4,5,9), 
+                                                              labels = c("negative", "neutral", "positive"))
+
+db_full4new_stim_screen_pupil_nopract$sample_valence_lab2<-
+  cut(db_full4new_stim_screen_pupil_nopract$ValenceMeanThisSample, c(-10,-3,3,10), 
+                                                              labels = c("negative", "neutral", "positive"))
+
+db_full4new_stim_screen_pupil_nopract$ground_arousal_2<-
+  cut(db_full4new_stim_screen_pupil_nopract$ArousalMean, c(0,4,5,9), 
+                                                              labels = c("low", "mid", "high"))
+
+db_full4new_stim_screen_pupil_nopract$sample_arousal_lab2<-
+  cut(db_full4new_stim_screen_pupil_nopract$ArousalMeanThisSample, c(-10,-3,3,10), 
+                                                              labels = c("low", "mid", "high"))
+
+subset(db_full4new_stim_screen_pupil_nopract, 
+                                    pupil_outlier == FALSE & ssid_num<500 & 
+                                      arousal_outler == FALSE)%>%
+  ggplot(aes(sample_valence_lab2, arousal))+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+subset(db_full4new_stim_screen_pupil_nopract, 
+                                    pupil_outlier == FALSE & ssid_num<500 & 
+                                      arousal_outler == FALSE)%>%
+  group_by(ssid, mediansplit_ground_valence, mediansplit_ground_arousal)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(mediansplit_ground_valence, pup_resid_lm, color = mediansplit_ground_arousal ))+
+  # geom_point()+
+  stat_summary(geom = 'pointrange')
+
+subset(db_full4new_stim_screen_pupil_nopract, 
+                                    pupil_outlier == FALSE & ssid_num<500 & 
+                                      arousal_outler == FALSE)%>%
+  group_by(ssid, mediansplit_ground_valence, mediansplit_ground_arousal)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(mediansplit_ground_valence, pup_resid_lm, color = mediansplit_ground_arousal ))+
+  # geom_point()+
+  stat_summary(geom = 'pointrange')
+
+```
+
+```
+
 ```{r}

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
quick visualisation
quick vis of arousal sample and iaps correlation for positive negative and neutral. this shows we do have enough variance and at all levels we see a correlation between arousal

@@
   stat_summary(funy = mean, geom = 'pointrange')
+
+# Plot just positive
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 == "positive")%>%
+  group_by(stimDescription,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(stimDescription, arousal))+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange', color = "blue")+
+   stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange', color = "red")+
+  theme(axis.text.x = element_text(angle = 60))
+
+# negative
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 == "negative")%>%
+  group_by(stimDescription,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(stimDescription, arousal))+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange', color = "blue")+
+   stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange', color = "red")+
+  theme(axis.text.x = element_text(angle = 60))
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 == "positive")%>%
+  group_by(stimIAPS,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ArousalMean, arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  ggpubr::stat_cor()
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 == "negative")%>%
+  group_by(stimIAPS,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ArousalMean, arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  ggpubr::stat_cor()
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 == "neutral")%>%
+  group_by(stimIAPS,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ArousalMean, arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  ggpubr::stat_cor()
+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange', color = "blue")+
+   stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange', color = "red")+
+  theme(axis.text.x = element_text(angle = 60))
+
+```
 

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
additional plots
to check if positive arousal is being driven by sexual arousal, but it doesn't seem to be the case, so we r good

@@
 
-# negative
-tmp.df4_full_stim_downs_jun2021_60bins %>%
-  subset(ground_valence_2 == "negative")%>%
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 == "positive")%>%
   group_by(stimDescription,ground_valence_2)%>%
@@
 
-tmp.df4_full_stim_downs_jun2021_60bins %>%
-  subset(ground_valence_2 == "positive")%>%
-  group_by(stimIAPS,ground_valence_2)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(ArousalMean, arousal))+
-  geom_point()+
-  geom_smooth(method = 'lm')+
-  ggpubr::stat_cor()
-
+# if we removed the erotic ones would we have positive tracking arousal better
+
+# negative
 tmp.df4_full_stim_downs_jun2021_60bins %>%
   subset(ground_valence_2 == "negative")%>%
-  group_by(stimIAPS,ground_valence_2)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(ArousalMean, arousal))+
-  geom_point()+
-  geom_smooth(method = 'lm')+
-  ggpubr::stat_cor()
-
-tmp.df4_full_stim_downs_jun2021_60bins %>%
-  subset(ground_valence_2 == "neutral")%>%
-  group_by(stimIAPS,ground_valence_2)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(ArousalMean, arousal))+
-  geom_point()+
-  geom_smooth(method = 'lm')+
-  ggpubr::stat_cor()
-
+  group_by(stimDescription,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(stimDescription, arousal))+
   # geom_point()+
@@
 
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 == "positive")%>%
+  group_by(stimIAPS,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ArousalMean, arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  ggpubr::stat_cor()
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 == "negative")%>%
+  group_by(stimIAPS,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ArousalMean, arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  ggpubr::stat_cor()
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 == "neutral")%>%
+  group_by(stimIAPS,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ArousalMean, arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  ggpubr::stat_cor()
+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange', color = "blue")+
+   stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange', color = "red")+
+  theme(axis.text.x = element_text(angle = 60))
+
+  tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 == "positive")%>%
+  group_by(stimDescription,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(stimDescription, arousal))+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange', color = "blue")+
+   stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange', color = "red")+
+  theme(axis.text.x = element_text(angle = 60))
+
+# if we removed the erotic ones would we have positive tracking arousal better
+
+  # organise pupil by growing order of positivearousal
+  tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 == "positive")%>%
+  group_by(stimIAPS,stimDescription, ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+    arrange(arousal)%>%
+  ggplot(aes(arousal, pup_basCor))+
+    geom_text(aes(label = stimDescription))+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange', color = "blue")+
+    xlim(-7,-2)+
+    ggpubr::stat_cor()
+   stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange', color = "red")+
+  theme(axis.text.x = element_text(angle = 60))
+
+   # so arousal (ativation) sis till being tracked even if we exclude the sexual stimuli
+
+     tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 == "negative")%>%
+  group_by(stimIAPS,stimDescription, ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+    arrange(arousal)%>%
+  ggplot(aes(arousal, pup_basCor))+
+    geom_text(aes(label = stimDescription))+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange', color = "blue")+
+    # xlim(-7,-2)+
+    ggpubr::stat_cor()
+
+# if we removed the erotic ones would we have positive tracking arousal better
+
+# maybe not every emotional experience causes a detectable physiologicachangedFiles(
+# preparing ubjects might allow them to calibrate
 ```

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
another paranoid check on valence arousal scaling
did an additional set of checks to see whether arousal was captured as an absolute of valence, and it doesn't map too well,  which suggests that our scale is picking something up that is not just magnitude of valence

@@
 
+check baselining onto specific valences
 ```{r Scrap this}
@@
 
+absolutetest<- tmp.df4_full_stim_downs_jun2021_60bins%>%
+  group_by(stimDescription,ground_valence_2)%>%
+  # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  mutate(arousal_abs = abs(arousal), valence_abs = abs(valence))%>%
+
+  summarise_at(c("arousal", "ArousalMean", "ValenceMean","arousal_abs", "valence", "valence_abs", "arousal_abs_on_pos"), mean, na.rm = TRUE)
+
+absolutetest %>%
+  ggplot(aes(ValenceMean,arousal_abs))+
+  geom_point()+
+  geom_text(aes(label = stimDescription))
+
+absolutetest %>%
+  ggplot(aes(ArousalMean,arousal_abs))+
+  geom_point()+
+  geom_text(aes(label = stimDescription))
+
+# he U shape relationship seems to hold dependign on whether arousal is absolute - converting actovation to absolute
+
+# absolute arousal don't correlate with iaps arousal
+# we we taking valence absolute as intensity
+absolutetest %>%
+  ggplot(aes(ValenceMean,valence_abs))+
+  geom_point()+
+  geom_text(aes(label = stimDescription))
+
+# arousal vs absolute valence
+absolutetest %>%
+  ggplot(aes(ArousalMean,valence_abs))+
+  geom_point()+
+  geom_text(aes(label = stimDescription))+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()
+# it seems like arousal in our case is picking something that is not just intemnsity of vaence, as it correlates better with arousal Mean
+
+absolutetest %>%
+  ggplot(aes(valence,valence_abs))+
+  geom_point()+
+  geom_text(aes(label = stimDescription))+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()
+
+# try and compute correlation using valencabs(
+
 tmp.df4_full_stim_downs_jun2021_60bins%>%
-  group_by(stimIAPS, ssid,ground_valence_2)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(stimIAPS, abs(arousal), color = ground_valence_2))+
+  subset(!is.na(ground_valence_2))%>%
+  group_by(ssid, stimIAPS,ground_valence_2)%>%
+
+  mutate(arousal_abs = abs(arousal), valence_abs = abs(valence))%>%
+  group_by(ssid, ground_valence_2)%>%
+  mutate(cortest = cor(valence_abs, pup_basCor, use = "complete"))%>%
+
+  # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # summarise_at(c("arousal", "ArousalMean","ValenceMean", "arousal_abs", "valence", "valence_abs", "arousal_abs_on_pos"), mean, na.rm = TRUE) %>%
+
+  ggplot(aes(ground_valence_2, cortest, color = ground_valence_2))+
   # geom_point()+
   stat_summary(funy = mean, geom = 'pointrange')
-
+    theme(axis.text.x = element_text(angle = 60))
+
+```
+
+just positive check
+```{r}
 # Plot just positive
@@
 
-# if we removed the erotic ones would we have positive tracking arousal better
+  tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ground_valence_2 != "negative")%>%
+  group_by(stimDescription,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(stimDescription, abs(arousal), color = ground_valence_2))+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange')+
+   # stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange')+
+  theme(axis.text.x = element_text(angle = 60))
+
+  tmp.df4_full_stim_downs_jun2021_60bins$arousal_abs_on_pos<- if_else(tmp.df4_full_stim_downs_jun2021_60bins$ground_valence_2!= "negative", abs(tmp.df4_full_stim_downs_jun2021_60bins$arousal), tmp.df4_full_stim_downs_jun2021_60bins$arousal)
+
+    tmp.df4_full_stim_downs_jun2021_60bins %>%
+  # subset(ground_valence_2 != "negative")%>%
+  group_by(stimDescription,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ground_valence_2, arousal_abs_on_pos, color = ground_valence_2))+
+  geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange')+
+   # stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange')+
+  theme(axis.text.x = element_text(angle = 60))
+
+        tmp.df4_full_stim_downs_jun2021_60bins %>%
+  # subset(ground_valence_2 != "negative")%>%
+  group_by(stimDescription,ground_valence_2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(ground_valence_2, abs(arousal), color = ground_valence_2))+
+  # geom_point()+
+  stat_summary(funy = mean, geom = 'pointrange')+
+   # stat_summary(aes( y = ArousalMean), funy = mean, geom = 'pointrange')+
+  theme(axis.text.x = element_text(angle = 60))
+
+```
+
+erotica check
+```{r}
+# if we removed the erotic ones would we have positive tracking arousal better?
 
@@
 
+```{r}
 # does absolute arousal correlate with other variables of interest

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 
+a few checks on stim by ratings 
+```{r eval=FALSE, include=FALSE}
 <!-- tmp.df4_full_stim_downs_jun2021_60bins%>% -->
@@
 <!--   stat_summary(funy = mean, geom = 'pointrange') -->
+
+```
 

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 plots_paper$interaction_ar_vl+p$graphstyle
+
+plots_paper$interaction_ar_vl
 ```
@@
 #  let's use the order arousal, valence, arousal x valence brightness
-plots_timecourse$eff_size_pup_amp <-   timecourse_60bin_result_df %>% 
+View(timecourse_60bin_result_df)
+plots_timecourse$eff_size_pup_amp <-   timecourse_60bin_result_df[1:56,] %>% 
   select("timebins","Estimate_ar", "Estimate_vl", "Estimate_br", "Estimate_ar_vl") %>% 
@@
 plots_timecourse$eff_size_pup_amp
+plots_timecourse$eff_size_pup_velocity
 
@@
 
-use the same dataas timecourse to plot aggregated analyses
+use the same datas timecourse to plot aggregated analyses
 aggregate arousal plot
@@
   stat_summary(geom = 'pointrange')
+
+plots_paper$interaction_ar_vl
+
+# correlation plot
+
+plots_paper$pupil_correlation <-   db_full4new_stim_screen_pupil_nopract %>%
+    subset(ssid_num<500)%>%
+  subset(pupil_outlier == FALSE & arousal_outler == FALSE)%>%
+   group_by(ssid,Alexithymia, mediansplit_ground_valence)%>%
+    mutate(cortest = cor.test(arousal_c, pup_basCor)$estimate)%>%
+   group_by(ssid,Alexithymia, mediansplit_ground_valence)%>%
+    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+     ggplot(aes(mediansplit_ground_valence, cortest, fill = mediansplit_ground_valence))+
+     geom_bar(stat="summary", fun.y = "mean", alpha = .5)+
+     geom_jitter(width = .1, alpha = .1)+
+        stat_summary( geom = 'pointrange')+
+        stat_summary(aes(group = ssid), geom = 'line', alpha = .1)+
+    ylab("R sujective vs pupil arousal")+
+     scale_fill_brewer(palette = "Dark2")+
+     p$graphstyle+
+     theme(axis.title.x = element_blank())
+
+plots_paper$pupil_correlation
+
+# timecourse plot pupil
 

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
does neutral drive higher pupilary response than negative

@@
 
+tmp.df4_full_stim_downs_jun2021_60bins$sample_arousal_lab2<-
+  cut(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMeanThisSample, c(-10,-1,1,10), 
+                                                              labels = c("low", "mid", "high"))
+
+test<- tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num<500)%>%
+  subset(!is.na(ground_arousal_lab))%>%
+  # subset(stimIAPS!= "4573")%>%
+  # subset(pupil_outlier == FALSE)%>%
+  # subset(arousal_outler== FALSE)%>%
+  group_by(mediansplit_sample_valence2)%>%
+  mutate(mediantotes = median(ArousalMeanThisSample, na.rm = TRUE))%>%
+  ungroup()%>%
+  group_by(mediansplit_sample_valence2)%>%
+  mutate(high_lowtes = if_else(arousal> mediantotes, "high", "low"))
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num<500)%>%
+  subset(!is.na(ground_arousal_lab))%>%
+  # subset(stimIAPS!= "4573")%>%
+  # subset(pupil_outlier == FALSE)%>%
+  # subset(arousal_outler== FALSE)%>%
+  # group_by(mediansplit_sample_valence2)%>%
+  # mutate(mediantotes = median(ArousalMeanThisSample, na.rm = TRUE))%>%
+  # ungroup()%>%
+  # group_by(mediansplit_sample_valence2)%>%
+  # mutate(high_lowtes = if_else(arousal> mediantotes, "high", "low")) %>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  # stat_summary(geom = 'pointrange')+
+    # facet_grid(~mediansplit_self_valence)
+
+  # stat_smooth(aes(group= stimIAPS, color = sample_arousal_lab2), fun = mean,
+  #              se = F, alpha = .15, size = 1.5)+
+  stat_smooth(aes(group=sample_arousal_lab2, color = sample_arousal_lab2), size = 3)+
+  # stat_summary(aes(group=stimIAPS, color = high_lowtes), fun = mean, geom = "pointrange")+
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # geom_text(aes(label = stimIAPS))+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")+
+  # xlim(0,6)+
+  facet_grid(~mediansplit_sample_valence2)
+# plot separatelly
+
+# negative
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num<500)%>%
+  subset(!is.na(ground_arousal_lab))%>%
+  subset(mediansplit_sample_valence2 != "More negative")%>%
+  mutate(mediantotes = median(arousal, na.rm = TRUE))%>%
+  ungroup()%>%
+  mutate(high_lowtes = if_else(arousal> mediantotes, "high", "low")) %>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  # stat_smooth(aes(group= stimIAPS), fun = mean,
+               # se = F, alpha = .15, size = 1.5)+
+  geom_smooth(aes(group = high_lowtes))+
+  # stat_smooth(fun = mean,
+  #              se = F, alpha = .15, size = 3)+
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # geom_text(aes(label = stimIAPS))+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")
+  # xlim(0,6)+
+  facet_grid(~ high_lowtes)+
+  geom_hline(yintercept = 0)+
+  geom_hline(yintercept = -0.5)
+
+```
+
+# start wit aggregate()
+
+# tmp.df4_full_stim_downs_jun2021_60bins%>%
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num<500)%>%
+  subset(!is.na(ground_arousal_lab))%>%
+  subset(stimIAPS!= "4573")%>%
+  subset(pupil_outlier == FALSE)%>%
+  group_by(stimIAPS,stimDescription, mediansplit_sample_arousal2, mediansplit_sample_valence2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+    group_by(mediansplit_sample_valence2)%>%
+  mutate(high_lowtes = if_else(arousal> median(arousal, na.rm = TRUE), "high", "low"))%>%
+  ggplot(aes(x =high_lowtes , y = pup_basCor))+
+  stat_summary(geom = 'pointrange')+
+  facet_grid(~mediansplit_sample_valence2)+
+  geom_text(aes(label = stimDescription))
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num<500)%>%
+  subset(!is.na(ground_arousal_lab))%>%
+  subset(stimIAPS!= "4573")%>%
+  subset(pupil_outlier == FALSE)%>%
+  group_by(stimIAPS,stimDescription, mediansplit_sample_arousal2, mediansplit_sample_valence2)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+    group_by(mediansplit_sample_valence2)%>%
+  mutate(high_lowtes = if_else(arousal> median(arousal, na.rm = TRUE), "high", "low"))%>%
+  ggplot(aes(x =high_lowtes , y = Mean_gray_z))+
+  stat_summary(geom = 'pointrange')+
+  facet_grid(~mediansplit_sample_valence2)+
+  geom_text(aes(label = stimDescription))
+    # facet_grid(~mediansplit_self_valence)
+  # stat_smooth(aes(group= stimIAPS, color = sample_arousal_lab2), fun = median,geom = "line",
+               # se = F, alpha = .1, size = 1.5)+
+  stat_smooth(aes(group=mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), size = 3)+
+  # stat_summary(aes(group=sample_arousal_lab2, color = sample_arousal_lab2), fun = mean, geom = "pointrange")+
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # geom_text(aes(label = stimIAPS))+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")+
+  xlim(0,6)+
+  facet_grid(~mediansplit_self_valence)
+
 ```

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 tmp.df4_full_stim_downs_jun2021_60bins$sample_arousal_lab2<-
-  cut(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMeanThisSample, c(-10,-1,1,10), 
+  cut(tmp.df4_full_stim_downs_jun2021_60bins$ArousalMeanThisSample, 3, 
                                                               labels = c("low", "mid", "high"))
+
+tmp.df4_full_stim_downs_jun2021_60bins$sample_valence_lab2<-
+  cut(tmp.df4_full_stim_downs_jun2021_60bins$ValenceMeanThisSample, 3 , 
+                                                              labels = c("negative", "mid", "positive"))
+
+tmp.df4_full_stim_downs_jun2021_60bins$newvalence <- if_else(tmp.df4_full_stim_downs_jun2021_60bins$sample_valence_lab2 == "mid" & tmp.df4_full_stim_downs_jun2021_60bins$sample_arousal_lab2 == "mid", "neutral",
+                                                             if_else(tmp.df4_full_stim_downs_jun2021_60bins$ValenceMeanThisSample> median(tmp.df4_full_stim_downs_jun2021_60bins$ValenceMeanThisSample, na.rm = TRUE), "positive", "negative")
+                                                           )
+
+table(tmp.df4_full_stim_downs_jun2021_60bins$newvalence)
+unique(tmp.df4_full_stim_downs_jun2021_60bins$newvalence)
 
@@
   # p$graphstyle+
-  scale_color_brewer(palette = "Dark2")+
+  scale_color_brewer(palette = "Dark2")
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num<500)%>%
+  subset(!is.na(ground_arousal_lab))%>%
+  # subset(stimIAPS!= "4573")%>%
+  # subset(pupil_outlier == FALSE)%>%
+  # subset(arousal_outler== FALSE)%>%
+  # group_by(mediansplit_sample_valence2)%>%
+  # mutate(mediantotes = median(ArousalMeanThisSample, na.rm = TRUE))%>%
+  # ungroup()%>%
+  # group_by(mediansplit_sample_valence2)%>%
+  # mutate(high_lowtes = if_else(arousal> mediantotes, "high", "low")) %>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  # stat_summary(geom = 'pointrange')+
+    # facet_grid(~mediansplit_self_valence)
+
+  # stat_smooth(aes(group= stimIAPS, color = sample_valence_lab2), fun = mean,
+  #              se = F, alpha = .15, size = 1.5)+
+  stat_smooth(aes(group=newvalence, color = newvalence), size = 3)+
+  # stat_summary(aes(group=stimIAPS, color = high_lowtes), fun = mean, geom = "pointrange")+
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # geom_text(aes(label = stimIAPS))+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")
+  facet_grid(~newvalence)
+
+```
   # xlim(0,6)+
@@
 # plot separatelly
+
+test<- tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num<500)%>%
+  subset(!is.na(ground_arousal_lab))%>%
+  # subset(stimIAPS!= "4573")%>%
+  # subset(pupil_outlier == FALSE)%>%
+  # subset(arousal_outler== FALSE)%>%
+  group_by(mediansplit_sample_valence2)%>%
+  mutate(mediantotes = median(ArousalMeanThisSample, na.rm = TRUE))%>%
+  ungroup()%>%
+  group_by(mediansplit_sample_valence2)%>%
+  mutate(high_lowtes = if_else(arousal> mediantotes, "high", "low"))
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num<500)%>%
+  subset(!is.na(ground_arousal_lab))%>%
+  # subset(stimIAPS!= "4573")%>%
+  # subset(pupil_outlier == FALSE)%>%
+  # subset(arousal_outler== FALSE)%>%
+  # group_by(mediansplit_sample_valence2)%>%
+  # mutate(mediantotes = median(ArousalMeanThisSample, na.rm = TRUE))%>%
+  # ungroup()%>%
+  # group_by(mediansplit_sample_valence2)%>%
+  # mutate(high_lowtes = if_else(arousal> mediantotes, "high", "low")) %>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  # stat_summary(geom = 'pointrange')+
+    # facet_grid(~mediansplit_self_valence)
+
+  # stat_smooth(aes(group= stimIAPS, color = sample_arousal_lab2), fun = mean,
+  #              se = F, alpha = .15, size = 1.5)+
+  stat_smooth(aes(group=sample_arousal_lab2, color = sample_arousal_lab2), size = 3)+
+  # stat_summary(aes(group=stimIAPS, color = high_lowtes), fun = mean, geom = "pointrange")+
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # geom_text(aes(label = stimIAPS))+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")
+  # xlim(0,6)+
+  facet_grid(~mediansplit_sample_valence2)
+
+  tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(ssid_num<500)%>%
+  subset(!is.na(ground_arousal_lab))%>%
+  # subset(stimIAPS!= "4573")%>%
+  # subset(pupil_outlier == FALSE)%>%
+  # subset(arousal_outler== FALSE)%>%
+  # group_by(mediansplit_sample_valence2)%>%
+  # mutate(mediantotes = median(ArousalMeanThisSample, na.rm = TRUE))%>%
+  # ungroup()%>%
+  # group_by(mediansplit_sample_valence2)%>%
+  # mutate(high_lowtes = if_else(arousal> mediantotes, "high", "low")) %>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  # stat_summary(geom = 'pointrange')+
+    # facet_grid(~mediansplit_self_valence)
+
+  # stat_smooth(aes(group= stimIAPS, color = sample_arousal_lab2), fun = mean,
+  #              se = F, alpha = .15, size = 1.5)+
+  stat_smooth(aes(group=sample_arousal_lab2, color = sample_arousal_lab2), size = 3)+
+  # stat_summary(aes(group=stimIAPS, color = high_lowtes), fun = mean, geom = "pointrange")+
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # geom_text(aes(label = stimIAPS))+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")
 

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 
-# Valence and arousal
+# Valence and arousal - ridge
 ```{r}
@@
 
+# lassomodels$firt
+
+ridgemodels<-list()
+
+# ridge
+unique(db_new$exp)
+# "3b" "3b"
+db_full4new_stim_screen_pupil_nopract
+unique(db_new$exp)
+
+db_new_exp3b<- subset(db_full4new_stim_screen_pupil_nopract, 
+                                     ssid_num< 500)
+
+pp_id_3b<- unique(db_new_exp3b$ssid)
+
+db_new_exp3b$ar_x_val<- db_new_exp3b$arousal_c* db_new_exp3b$valence_c
+
+db_new_exp3b_1 <- select(db_new_exp3b, c(ssid, arousal_c, valence_c, ar_x_val, Mean_gray_z,pup_basCor))
+i = 10
+?glmnet::cv.glmnet
+set.seed(808)
+
+cv_fits_3b<- list(list())
+cv_fits<-list(list())
+library(glmnet)
+
+for (i in pp_id_3b) {
+  temp_3b <- subset(db_new_exp3b_1, ssid == 304)
+  # cv_fits <- list(i)
+  cv_fits_3b[[i]]<- list(cv.glmnet(as.matrix(temp_3b[,2:5]),temp_3b$pup_basCor, 
+                                alpha = 0, nfolds = 8))
+
+  cv_fits[[i]]<- list(glmnet(as.matrix(temp_3b[,2:5]),temp_3b$pup_basCor,
+                             family = "gaussian",
+                             alpha = 0, lambda = cv_fits_3b[[i]][[1]]$lambda.min))
+  }
+
+coef(cv_fits_3b[[i]][[1]], s = cv_fits_3b[[i]][[1]]$lambda.min)
+
+coef(cv_fits[[i]][[1]], s = cv_fits[[i]][[1]]$lambda)
+# 5 x 1 sparse Matrix of class "dgCMatrix"
+#                       1
+# (Intercept)  0.57036534
+# arousal_c    0.34759064
+# valence_c    0.34825059
+# ar_x_val    -0.03044521
+# Mean_gray_z -0.22724284
+
+my_vector_ar<- vector(mode="numeric")
+i
+
+plot(cv_fits[["306"]][[1]])
+
+plot(cv_fits[[2]][[1]])
+plot(cv_fits[[2]][[1]],xvar="lambda",label=TRUE)
+fit3=glmnet(x,g4,family="multinomial")
+plot(cv_fits[[2]][[1]],pch=19)
+
+View(my_vectors)
+for (i in pp_id_3b) {
+my_vector_ar[i]<- coef(cv_fits[[i]][[1]], s = cv_fits[[i]][[1]]$lambda)[2] # 3 is gender sd
+}
+
+my_vector_vl<- vector(mode="numeric")
+# non gender sd
+for (i in pp_id_3b) {
+my_vector_vl[i]<- coef(cv_fits[[i]][[1]], s = cv_fits[[i]][[1]]$lambda)[3] 
+}
+
+# status
+my_vector_ar_vl<- vector(mode="numeric")
+
+for (i in pp_id_3b) {
+my_vector_ar_vl[i]<- coef(cv_fits[[i]][[1]], s = cv_fits[[i]][[1]]$lambda)[4] 
+}
+
+# physical
+my_vector_gray<- vector(mode="numeric")
+
+for (i in pp_id_3b) {
+my_vector_gray[i]<- coef(cv_fits[[i]][[1]], s = cv_fits[[i]][[1]]$lambda)[5] 
+}
+
+t.test(my_vector_ar)
+# t = 41.071, df = 42, p-value < 0.00000000000000022
+t.test(my_vector_vl)
+# t = 34.501, df = 42, p-value < 0.00000000000000022
+
+t.test(my_vector_ar_vl)
+# t = -16.486, df = 42, p-value < 0.00000000000000022
+
+t.test(my_vector_gray)
+# t = -62.057, df = 42, p-value < 0.00000000000000022
 ```
@@
   facet_grid(~mediansplit_sample_valence2)
+```{r}
 # plot separatelly

### 2021-08-19 intero_study_preprocessing.Rmd
preprocessing new IAPS data

---
title: "Preprocing and mergind datasets"
author: "Helio Cuve"
date: "24/01/2020"
output:
  word_document: default
  html_document: default
---

# Loading rdhf5 
```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install(version = "3.10")

BiocManager::install("rhdf5")
library(rhdf5)

```

# Preferences
list necessary package install them if not already and load them
```{r}
# devtools::install_github("dmirman/gazer")

list.of.packages <- c("ggplot2", "data.table", 'readr', "c", 'tidyverse', "gazer", 'lmerTest')
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]

# if(length(new.packages)) install.packages(new.packages)
lapply(list.of.packages, require, character.only = TRUE)
# lapply(new.packages, require, character.only = TRUE)

# install.packages('devtools')

remotes::install_github("dmirman/gazer")
library(gazer)
library(dplyr)

# setting a workspace

#change approproatelly

setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020")
# hdf5FilesPath<- "~/Desktop/University Work/Research_Project/Data Analysis January 2020/Data Analysis Jan 2020"
setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020")
hdf5FilesPath<- "D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020"

setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Step1_GpExtractor_Output")

# 2021 data
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021")
hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021"

```

# plotting preferences

```{r, plotting}
p<- list()
```

# gp extractor function
takes gp files and returns a clean files with messages parsed and deletes unnecessary stuff

Starting from 322 we have gsr v and hr v. and Pulse is around the 30

```{r, gp extractor}
gp.extractor(hdf5FilesPath)

gp.extractor = function(hdf5FilesPath) {

  setwd(hdf5FilesPath)

  hdfFilesList = list.files(hdf5FilesPath, pattern = "\\.hdf5$")

  if (length(hdfFilesList) == 0){

    return(message('No HDF5 files found in the directory provided.'))
  }
   # f = 7
  for (f in 1:length(hdfFilesList)) {

    message(sprintf("Extracting file %i / %i - %s", f, length(hdfFilesList), hdfFilesList[f]))

    #notr this sometimes fails because e are using a notebook 
    # Extract Events from hdf5, in that case run it from command
    tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent')

    # Fixing 228
    # session 1 = IAPS
    nrow(tmp.events)
    # tmp.events<- subset(tmp.events, tmp.events$session_id == 1)

    tmp.eyetr  = h5read(hdfFilesList[f], '/data_collection/events/eyetracker/BinocularEyeSampleEvent')

    # tmp.eyetr<- subset(tmp.eyetr, tmp.eyetr$session_id == 1)

    # tmp.events<- tmp.events[245:nrow(tmp.events), ]

    # problem file
    # tmp.events

    # Get subejct id from Events
    ssid = sapply(strsplit(grep('SubjJID', tmp.events$text, value = TRUE), split = ": "), "[", 2)
    date = sapply(strsplit(grep('DATE', tmp.events$text, value = TRUE), split = ": "), "[", 2)
    session = sapply(strsplit(grep('Session:', tmp.events$text, value = TRUE), split = ":"), "[", 2)
    cali<- subset(tmp.events, grepl('Cali', tmp.events$text) == TRUE)

    # Create DF for trials data
    tmp.df = data.frame(matrix(ncol = ncol(tmp.eyetr)))
    names(tmp.df) = names(tmp.eyetr)
    colnames(tmp.df)

    # Prepare Events, keep only start/end messages
    phrases = c('tStart', 'tEnd')
    tmp.events_backup<- tmp.events
    # tmp.events<-  tmp.events_backup
    tmp.events = subset(tmp.events, grepl(paste(phrases, collapse = "|"), tmp.events$text))

    # Create start/end references
    tmp.events$tStart   = NA
    tmp.events$tEnd     = NA

    # Trial number extraction 
    tmp.events$tNo      = NA
    tmp.df$tNo          = NA
    tmp.df$Condition    = NA

    # Space for subject id
    tmp.df$ssid         = NA
    tmp.df$text<-NA

    for (l in 1:nrow(tmp.events)) {
      # sub(".*_", "", tmp.events)

      # sub("[^_]*/_", "", tmp.events$text)
      # ([^\/]+$)
      # remove everything upto to _
      # as.numeric(strsplit(tmp.events$text[l], split = '_')[[1]][3])
      # "Extracting file %i / %i - %s", f, length(hdfFilesList), hdfFilesList[f])

      message(sprintf("Grabing start messages %s", tmp.events$text[l]))

      if ((grepl('tStart', tmp.events$text[l])) == TRUE) {
        tmp.events$tStart[l] = tmp.events$time[l]

        if ((grepl('tEnd', tmp.events$text[l+1])) == TRUE){
          tmp.events$tEnd[l] = tmp.events$time[l+1]
        }

        else {
          message('trial start/end structure not valid')
        }
      }

    }
    message(sprintf("done grabbing messages"))
    # readline(prompt="Press [enter] to continue")

    tmp.events$tNo<- as.numeric(as.character(gsub(".*_","",tmp.events$text)))

    # tmp.events$tNo[is.na(tmp.events$tNo) == TRUE]<- -7

    # tmp.events$screencontent = strsplit(tmp.events$text, split = '_')[[1]][2]
    # readline(prompt="Press [enter] to continue")
     message(sprintf("making screencontent"))
    tmp.events$screencontent<- if_else(grepl('fixation', tmp.events$text), 'fixation',
                                       if_else(grepl('Valence', tmp.events$text), 'ValenceResp',
                                               if_else(grepl('rest', tmp.events$text), 'rest1', 
                                                       if_else(grepl('IntResp', tmp.events$text), 'IntResp','stim'))))

    # unique(tmp.events$screencontent)

    # first let's do condition

    tmp.events$Condition<- if_else(grepl('IAPS', tmp.events$text), 'IAPS',
                                   if_else(grepl('Example', tmp.events$text), 'Practice',
                                           if_else(grepl('rest', tmp.events$text), 'Rest', NULL)))
    tmp.events$stim<- if_else(tmp.events$Condition == 'IAPS', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text),
                              if_else(tmp.events$Condition == 'Practice', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text), 'REST'))

    # substitute periods
    tmp.events$stim<- gsub('\\.', '.jpg', tmp.events$stim)
    # tmp.events$tNo<- as.numeric(tmp.events$tNo)
    tmp.events$tNo<- if_else(tmp.events$Condition == 'Practice', (tmp.events$tNo)-6,
                             if_else(tmp.events$Condition == 'Rest',-7, tmp.events$tNo))
    # tmp.events$tNo<- tmp.events$tNo1
    tmp.events$tNo<- if_else(tmp.events$tNo> -1, tmp.events$tNo+1, tmp.events$tNo) # avoid zeros

    tmp.events1 = subset(tmp.events, grepl('tStart',tmp.events$text))
    tmp.events1$tNo1<- NULL
    tmp.events1$tNo2<- NULL

    # tmp.eyetr_backup<- tmp.eyetr
    # tmp.df_backup<- tmp.df
    # tmp.df<- tmp.df_backup
    colnames(tmp.df)
    # rm(tmp.raw.trial)
    # colnames(tmp.raw.trial)
    colnames(tmp.df)
    colnames(tmp.events1)
    colnames(tmp.eyetr)
    tmp.df$screencontent<- NA
    tmp.df$stim<- NA
    # e=10
    tmp.events1$tEnd<- if_else(tmp.events1$tNo == -7, tmp.events1$tStart+120, tmp.events1$tEnd)
    message(sprintf("subsetting eyetracking data"))

    for(e in 1:nrow(tmp.events1)) {

      # Subset the EyeTracking data based on start/end
      tmp.raw.trial = subset(tmp.eyetr, tmp.eyetr$time >= tmp.events1$tStart[e] & tmp.eyetr$time <= tmp.events1$tEnd[e])

      tmp.raw.trial$tNo = tmp.events1$tNo[e]

      tmp.raw.trial$Condition = tmp.events1$Condition[e]
      tmp.raw.trial$screencontent = tmp.events1$screencontent[e]
      tmp.raw.trial$stim = tmp.events1$stim[e]
      # tmp.raw.trial$stim = tmp.events1$[e]
      tmp.raw.trial$ssid = ssid
      tmp.raw.trial$text = tmp.events1$text[e]
       message(sprintf("binding tmp.df"))
      tmp.df= rbind(tmp.raw.trial, tmp.df)
    }
     message(sprintf("done binding"))

    # Add ssid
    # tmp.df$ssID = ssid[e]
    tmp.df<- tmp.df%>%
      arrange(time)

    # Save file
    name = sprintf("ss%s_GPdata",ssid)
    message(sprintf("saving data"))

    write_csv(tmp.df, paste(name,".csv"))
    # write_csv(tmp.df, "test.csv")
    # write calibration cali
    name2 = sprintf("ss%s_GPdata_cali", ssid)
    write_csv(cali, paste(name2,".csv"))

  }

  # write_csv(tmp.df, 'tmpdf_extracted.csv')

  message("Processing Completed.")
  tmp.df
}

tmp_full<- gp.extractor(hdf5FilesPath)

```

Problem files
```{r}
# 355  - did not finish IAPS
# adjust below manually

gp.extractor = function(hdf5FilesPath) {

  setwd(hdf5FilesPath)

  hdfFilesList = list.files(hdf5FilesPath, pattern = "\\.hdf5$")
  hdfFilesList
  if (length(hdfFilesList) == 0){

    return(message('No HDF5 files found in the directory provided.'))
  }
   f = 10# adjust here to the index for the probematic file
  for (f in 1:length(hdfFilesList)) {

    message(sprintf("Extracting file %i / %i - %s", f, length(hdfFilesList), hdfFilesList[f]))

    #ATTTENTIONNN  note this sometimes fails because we are using a notebook 
    # Extract Events from hdf5, in that case run it from command
    tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent')

    # Fixing 228
    # session 1 = IAPS
    nrow(tmp.events)
    # tmp.events<- subset(tmp.events, tmp.events$session_id == 1)

    tmp.eyetr  = h5read(hdfFilesList[f], '/data_collection/events/eyetracker/BinocularEyeSampleEvent')

    # tmp.eyetr<- subset(tmp.eyetr, tmp.eyetr$session_id == 1)

    # tmp.events<- tmp.events[245:nrow(tmp.events), ]

    # problem file
    # tmp.events

    # Get subejct id from Events
    ssid = sapply(strsplit(grep('SubjJID', tmp.events$text, value = TRUE), split = ": "), "[", 2)
    date = sapply(strsplit(grep('DATE', tmp.events$text, value = TRUE), split = ": "), "[", 2)
    session = sapply(strsplit(grep('Session:', tmp.events$text, value = TRUE), split = ":"), "[", 2)
    cali<- subset(tmp.events, grepl('Cali', tmp.events$text) == TRUE)

    # Create DF for trials data
    tmp.df = data.frame(matrix(ncol = ncol(tmp.eyetr)))
    names(tmp.df) = names(tmp.eyetr)
    colnames(tmp.df)

    # Prepare Events, keep only start/end messages
    phrases = c('tStart', 'tEnd')
    tmp.events_backup<- tmp.events
    # tmp.events<-  tmp.events_backup
    tmp.events = subset(tmp.events, grepl(paste(phrases, collapse = "|"), tmp.events$text))

    # Create start/end references
    tmp.events$tStart   = NA
    tmp.events$tEnd     = NA

    # Trial number extraction 
    tmp.events$tNo      = NA
    tmp.df$tNo          = NA
    tmp.df$Condition    = NA

    # Space for subject id
    tmp.df$ssid         = NA
    tmp.df$text<-NA

    for (l in 1:nrow(tmp.events)) {
      # sub(".*_", "", tmp.events)

      # sub("[^_]*/_", "", tmp.events$text)
      # ([^\/]+$)
      # remove everything upto to _
      # as.numeric(strsplit(tmp.events$text[l], split = '_')[[1]][3])
      # "Extracting file %i / %i - %s", f, length(hdfFilesList), hdfFilesList[f])

      message(sprintf("Grabing start messages %s", tmp.events$text[l]))

      if ((grepl('tStart', tmp.events$text[l])) == TRUE) {
        tmp.events$tStart[l] = tmp.events$time[l]

        if ((grepl('tEnd', tmp.events$text[l+1])) == TRUE){
          tmp.events$tEnd[l] = tmp.events$time[l+1]
        }

        else {
          message('trial start/end structure not valid')
        }
      }

    }
    message(sprintf("done grabbing messages"))
    # readline(prompt="Press [enter] to continue")

    tmp.events$tNo<- as.numeric(as.character(gsub(".*_","",tmp.events$text)))

    # tmp.events$tNo[is.na(tmp.events$tNo) == TRUE]<- -7

    # tmp.events$screencontent = strsplit(tmp.events$text, split = '_')[[1]][2]
    # readline(prompt="Press [enter] to continue")
     message(sprintf("making screencontent"))
    tmp.events$screencontent<- if_else(grepl('fixation', tmp.events$text), 'fixation',
                                       if_else(grepl('Valence', tmp.events$text), 'ValenceResp',
                                               if_else(grepl('rest', tmp.events$text), 'rest1', 
                                                       if_else(grepl('IntResp', tmp.events$text), 'IntResp','stim'))))

    unique(tmp.events$screencontent)

    # first let's do condition

    tmp.events$Condition<- if_else(grepl('IAPS', tmp.events$text), 'IAPS',
                                   if_else(grepl('Example', tmp.events$text), 'Practice',
                                           if_else(grepl('rest', tmp.events$text), 'Rest', NULL)))
    tmp.events$stim<- if_else(tmp.events$Condition == 'IAPS', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text),
                              if_else(tmp.events$Condition == 'Practice', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text), 'REST'))

    # substitute periods
    tmp.events$stim<- gsub('\\.', '.jpg', tmp.events$stim)
    # tmp.events$tNo<- as.numeric(tmp.events$tNo)
    tmp.events$tNo<- if_else(tmp.events$Condition == 'Practice', (tmp.events$tNo)-6,
                             if_else(tmp.events$Condition == 'Rest',-7, tmp.events$tNo))
    # tmp.events$tNo<- tmp.events$tNo1
    tmp.events$tNo<- if_else(tmp.events$tNo> -1, tmp.events$tNo+1, tmp.events$tNo) # avoid zeros

    tmp.events1 = subset(tmp.events, grepl('tStart',tmp.events$text))
    tmp.events1$tNo1<- NULL
    tmp.events1$tNo2<- NULL

    # tmp.eyetr_backup<- tmp.eyetr
    # tmp.df_backup<- tmp.df
    # tmp.df<- tmp.df_backup
    colnames(tmp.df)
    # rm(tmp.raw.trial)
    # colnames(tmp.raw.trial)
    colnames(tmp.df)
    colnames(tmp.events1)
    colnames(tmp.eyetr)
    tmp.df$screencontent<- NA
    tmp.df$stim<- NA
    # e=10
    tmp.events1$tEnd<- if_else(tmp.events1$tNo == -7, tmp.events1$tStart+120, tmp.events1$tEnd)
    message(sprintf("subsetting eyetracking data"))
    e=1
    for(e in 1:nrow(tmp.events1)) {

      # Subset the EyeTracking data based on start/end
      tmp.raw.trial = subset(tmp.eyetr, tmp.eyetr$time >= tmp.events1$tStart[e] & tmp.eyetr$time <= tmp.events1$tEnd[e])

      tmp.raw.trial$tNo = tmp.events1$tNo[e]

      tmp.raw.trial$Condition = tmp.events1$Condition[e]
      tmp.raw.trial$screencontent = tmp.events1$screencontent[e]
      tmp.raw.trial$stim = tmp.events1$stim[e]
      # tmp.raw.trial$stim = tmp.events1$[e]
      tmp.raw.trial$ssid = ssid
      tmp.raw.trial$text = tmp.events1$text[e]
       message(sprintf("binding tmp.df"))
      tmp.df= rbind(tmp.raw.trial, tmp.df)
    }
     message(sprintf("done binding"))

    # Add ssid
    # tmp.df$ssID = ssid[e]
    tmp.df<- tmp.df%>%
      arrange(time)

    # Save file
    name = sprintf("ss%s_GPdata",ssid)
    message(sprintf("saving data"))

    write_csv(tmp.df, paste(name,".csv"))
    # write_csv(tmp.df, "test.csv")
    # write calibration cali
    name2 = sprintf("ss%s_GPdata_cali", ssid)
    write_csv(cali, paste(name2,".csv"))

  }

  # write_csv(tmp.df, 'tmpdf_extracted.csv')

  message("Processing Completed.")
  tmp.df
}

# tmp_full<- gp.extractor(hdf5FilesPath)

```

now cleaning
we need to have data for ledalab
gaze path
clean and tracloss

```{r, cleaning}
# function to read all the csvs into one dataframe

rm(tmp_full)
read_plus <- function(flnm) {
  data.table::fread(flnm, select = c("session_id","event_id", "time", "left_gaze_x", "left_gaze_y","right_gaze_x", "right_gaze_y","left_pupil_measure1",
                                     "right_pupil_measure1","gsr", "gsrv", 'hr', "hrv", "hrp", "status", "tNo",  "Condition", "screencontent", "stim", "ssid", "text")) %>% 
    mutate(filename = flnm)
}

# now read them
setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Step1_GpExtractor_Output")

tmp.df2 <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_plus(.))
# rm(db_beh)

tmp.df2$ssid<- substr(tmp.df2$filename, 5,7)

unique(tmp.df2$ssid)
head(tmp.df2)

# check if we have all participants
colnames(tmp.df2)
unique(tmp.df2$ssid)

# gp preprocessing cuntion, checks for losses, averages gaze and pupil and pixelate
gp_preprocessing = function(tmp.df2) {

  message(sprintf("step1 lft gaze validity"))

  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$status != '20', tmp.df2$left_gaze_x, NULL)
  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$status != '22', tmp.df2$left_gaze_x_cor, NULL)
  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$status != '20', tmp.df2$left_gaze_y, NULL)
  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$left_gaze_y_cor, NULL)

  message(sprintf("step2 right gaze validity"))

  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$status != '2', tmp.df2$right_gaze_x, NULL)
  # 
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_x_cor, NULL)
  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_y, NULL)
  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_y_cor, NULL)

  # pupil validity
  message(sprintf("step3 pupil validity"))
  tmp.df2$left_pupil_measure1<- if_else(tmp.df2$status != '20', tmp.df2$left_pupil_measure1, NULL)
  tmp.df2$left_pupil_measure1<- if_else(tmp.df2$status != '22', tmp.df2$left_pupil_measure1, NULL)

  tmp.df2$right_pupil_measure1<- if_else(tmp.df2$status != '2', tmp.df2$right_pupil_measure1, NULL)
  tmp.df2$right_pupil_measure1<- if_else(tmp.df2$status != '22', tmp.df2$right_pupil_measure1, NULL)
  table(is.na(tmp.df2$right_pupil_measure1))

  # tmp.df2$right_pupil_measure1<- if_else(tmp.df2$pupil_meas>7, tmp.df2$right_pupil_measure1, NULL)
  message(sprintf("step 4 cutingt off screen in points and repixel"))
  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$left_gaze_x_cor >= -960 & tmp.df2$left_gaze_x_cor <= 960, tmp.df2$left_gaze_x_cor, NULL)
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$right_gaze_x_cor >= -960 & tmp.df2$right_gaze_x_cor <= 960, tmp.df2$right_gaze_x_cor, NULL)

  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$left_gaze_y_cor >= -540 & tmp.df2$left_gaze_y_cor <= 540, tmp.df2$left_gaze_y_cor, NULL)
  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$right_gaze_y_cor >= -540 & tmp.df2$right_gaze_y_cor <= 540, tmp.df2$right_gaze_y_cor, NULL)

  tmp.df2$left_gaze_x_cor_pix<- tmp.df2$left_gaze_x_cor+960
  tmp.df2$right_gaze_x_cor_pix<- tmp.df2$right_gaze_x_cor+960

  tmp.df2$left_gaze_y_cor_pix<- tmp.df2$left_gaze_y_cor+540
  tmp.df2$right_gaze_y_cor_pix<- tmp.df2$right_gaze_y_cor+540

  # is left or right and na

  tmp.df2$left_na<- is.na(tmp.df2$left_gaze_x_cor) 
  tmp.df2$right_na<- is.na(tmp.df2$right_gaze_x_cor)
  tmp.df2$both_na<- if_else(tmp.df2$left_na == TRUE & tmp.df2$right_na == TRUE, TRUE, FALSE)

  message(sprintf("step5 gaze x  means"))
  tmp.df2$gaze_x_cor<-if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_gaze_x_cor,
                              if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_gaze_x_cor,
                                      ((tmp.df2$left_gaze_x_cor + tmp.df2$right_gaze_x_cor)/2)))
  message(sprintf("step6 gaze y means"))

  tmp.df2$gaze_y_cor<-if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_gaze_y_cor,
                              if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_gaze_y_cor,
                                      ((tmp.df2$left_gaze_y_cor + tmp.df2$right_gaze_y_cor)/2)))

  message(sprintf("step6 repixel gaze means"))
  tmp.df2$gaze_x_cor_pix<- tmp.df2$gaze_x_cor + 960
  min(tmp.df2$gaze_x_cor_pix, na.rm = TRUE)

  tmp.df2$gaze_y_cor_pix<- tmp.df2$gaze_y_cor+540
  min(tmp.df2$gaze_y_cor_pix, na.rm = TRUE)

  # clean_pupil
  message(sprintf("cleaning pupil"))

  max(tmp.df2$left_pupil_measure1)

  tmp.df2$pupil<- if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_pupil_measure1,
                          if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_pupil_measure1,
                                  ((tmp.df2$left_pupil_measure1 + tmp.df2$right_pupil_measure1)/2)))
  # tmp.df2$trackloss<- if_else(tmp.df2$status > 0, TRUE, FALSE)
  tmp.df2$trialUnq<- paste(tmp.df2$tNo, paste(tmp.df2$screencontent, paste(tmp.df2$stim)))
  tmp.df2$distance = 600

  # min(tmp.df2$pupil, na.rm = TRUE)
  # max(tmp.df2$pupil, na.rm = TRUE)
  # colnames(tmp.df2)
  tmp.df2<- tmp.df2%>%
    arrange(time)
}

tmp.df2<- gp_preprocessing(tmp.df2)
 colnames(tmp.df2)

# # calculate trackloss
# (sprintf("calculating trackloss"))
#  
#   tmp.df2_trackloss<- tmp.df2%>%
#     group_by(tNo, trialUnq, ssid, trackloss)%>%
#     summarise(n = n()) %>%
#     mutate(trackloss_prop = n() / sum(n))%>%
#     mutate(mean_valid = 1- trackloss_prop)
#   
# tmp.df2_trackloss<- subset(tmp.df2_trackloss, tmp.df2_trackloss$trackloss == TRUE)
# tmp.df2_trackloss<- tmp.df2_trackloss %>%
#   group_by(trackloss)%>%
#   # summarise(mean_loss = mean(trackloss_prop))%>%
#   mutate(mean_valid = 1- trackloss_prop)
# 
# 
#   tmp.df2_trackloss$trackloss<- NULL
  # tmp.df2<- left_join(tmp.df2, tmp.df2_trackloss, by = c('tNo', 'trialUnq', 'ssid'))

```

# rezeroing

```{r}
colnames(tmp.df2)
tmp.df3<- tmp.df2

# tmp.df3<- tmp.df2
colnames(tmp.df3)

# create start at every screen content
tmp.df3<- tmp.df3%>% 
  arrange(time)%>%
  group_by(ssid)%>%
  mutate(firststart = duplicated(trialUnq))

head(tmp.df3)

# make zeros
tmp.df3$zero<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, NULL)

# fill in the zeros
tmp.df3<- tmp.df3%>%
  group_by(Condition, tNo, ssid)%>%
  # group_by(text)%>%
  fill(zero)

unique(tmp.df3$zero)

# rezero
tmp.df3<-tmp.df3%>%
  arrange(time)%>%
  group_by(ssid, tNo)%>%
  mutate(timerezero = time - zero)

min(tmp.df3$timerezero, na.rm = TRUE)

natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)

# let's check to see if it looks fine
ggplot(tmp.df3, aes(time, gsr, colour = as.factor(ssid)))+
  geom_line()
  # facet_grid(~screencontent)

  # create a new time rezero where before stim start is negative
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, Condition, screencontent)%>%
  mutate(firststartSTIM = duplicated(tNo))

#this will create a time in the stim start wich we can use to do the r=secnd rezero
tmp.df3$zero_stim<- if_else(tmp.df3$firststartSTIM == FALSE & tmp.df3$screencontent == 'stim', tmp.df3$time, NULL)

    # fill down
tmp.df3<- tmp.df3%>%
      # arrange(time)%>%
      group_by(tNo, ssid)%>%
      fill(zero_stim)

# fill up
   tmp.df3<- tmp.df3%>%
      arrange(time)%>%
     group_by(ssid, tNo)%>%
      fill(zero_stim, .direction = c('up'))
   tmp.df3$timerezero2<- tmp.df3$time-tmp.df3$zero_stim
   # check timerezero2

     min(tmp.df3$timerezero2, na.rm = TRUE)
  max(tmp.df3$timerezero2, na.rm = TRUE)

# time 3 including rest
  # simply inclues rest as is

tmp.df3$timerezero3<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$timerezero, tmp.df3$timerezero2)
min(tmp.df3$timerezero3, na.rm = TRUE)

# let's check
unique(tmp.df3$ssid)

#tmp.df3<- subset(tmp.df3, is.na(tmp.df3$ssid) == FALSE)

ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
    geom_smooth()+
    # geom_()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tmp.df3$tNo == -4) , aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tmp.df3$tNo == -7) , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

```

triggers

```{r}
unique(tmp.df3$tNo)

natest<- subset(tmp.df3, is.na(tmp.df3$tNo) == TRUE)
tmp.df3<- subset(tmp.df3, is.na(tmp.df3$tNo) == FALSE)

tmp.df3$intercept_time<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, 
                          if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$time,
                                  NULL))

# takes a bit with a group - so don't run
# ggplot(tmp.df3, aes(time, gsr))+
#   geom_line()+
#   geom_vline(aes(xintercept = intercept_time))

# should trigger be this or should I create a unique code for this based on the images

unique(tmp.df3$tNo)

tmp.df3$trigger<- as.double(tmp.df3$tNo)

tmp.df3$trigger<- if_else(tmp.df3$firststart == FALSE, tmp.df3$trigger, 
                          if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$trigger, 0))
unique(tmp.df3$trigger)

tmp.df3$trigger <- if_else(tmp.df3$screencontent == 'fixation' &tmp.df3$firststart == FALSE, 100,
                          if_else(tmp.df3$screencontent == 'ValenceResp' & tmp.df3$firststart == FALSE, 101,
                             if_else(tmp.df3$screencontent == 'IntResp' & tmp.df3$firststart == FALSE, 102, tmp.df3$trigger)))

unique(tmp.df3$trigger)

tmp.df3$trigger<- if_else(tmp.df3$firststart == TRUE, 0, tmp.df3$trigger)

unique(tmp.df3$trigger)

```

writing for ledalab

```{r}
tmp.df3<- tmp.df3%>%
  arrange(ssid, time,tNo)
# gsr baseline wil be the 1 second before tial start
# gsr to microsiemnes 1/J3*100000

options(scipen = 999)
tmp.df3$gsr_ms<- 1/tmp.df3$gsr*100000
unique(tmp.df3$ssid)
max(tmp.df3$gsr_ms)
min(tmp.df3$gsr_ms)

# gsr for leda
colnames(tmp.df3)
db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49 ))
db_GSR$tNo<- NULL
colnames(db_GSR)

unique(db_GSR$Condition)
db_GSR$Condition2<- if_else(db_GSR$Condition == 'Rest', 'Rest', 'IAPS')
unique(db_GSR$Condition2)
db_GSR$split_column<- paste0(db_GSR$Condition2,paste(db_GSR$ssid))
unique(db_GSR$split_column)
  (sprintf("writing for ledlab"))

split_column<- unique(db_GSR$split_column)

split_gsr = split(db_GSR, list(db_GSR$split_column))

    for (ssid in names(split_gsr)) {
      write_tsv(split_gsr[[ssid]][,c("time","gsr_ms", "trigger")], paste0("gpgsr_", paste0(ssid),".txt"), col_names = FALSE)
    }

```

# baselining gsr
```{r}
# use ms to baseline

tmp.df3$gsr_bas<- if_else(tmp.df3$timerezero3 >= -3 & tmp.df3$timerezero3 < 0, tmp.df3$gsr_ms, NULL)
# true if baseline within window
tmp.df3$gsr_bastrue<- if_else(tmp.df3$timerezero3 >= -3 & tmp.df3$timerezero3 < 0, TRUE, FALSE)

# create baseline median
tmp.df3$gsr_bas_mean<- NULL

tmp.df3<- tmp.df3%>%
  arrange(time)%>%
  group_by(ssid, tNo, gsr_bastrue)%>%
  mutate(gsr_bas_median = median(gsr_bas))

# fill the baseline mean
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(gsr_bas_median)

# fill up to complete
unique(tmp.df3$gsrv)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(gsr_bas_median, .direction = 'up')

# do baseline correction
# 
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  mutate(gsr_basCor = gsr_ms - gsr_bas_median)

# rest baselining
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, Condition)%>%
  mutate(gsr_restmedian = median(gsr_ms))

tmp.df3$gsr_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$gsr_ms- tmp.df3$gsr_restmedian, tmp.df3$gsr_basCor)

# plot diagnosis
ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
  # stat_summary(geom = 'line', fun.data = 'mean')+
    geom_smooth()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

 ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
  # stat_summary(geom = 'line', fun.data = 'mean')+
    geom_smooth()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2) 
  # tmp.df_norest$tNo<- as.factor(tmp.df_norest$tNo)

ggplot(subset(tmp.df3, tmp.df3$screencontent == 'stim') , aes(x = timerezero3, y= gsr_basCor, olour = as.factor(ssid)))+
    geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

# gsr respone
tmp.df3$gsr_resp_Log<- if_else(tmp.df3$timerezero3 > 1,TRUE, FALSE)
unique(tmp.df3$gsr_resp_Log)

tmp.df3 <- tmp.df3 %>%
    group_by(ssid, tNo, gsr_resp_Log )%>%
    mutate(gsr_response =   max(gsr_basCor))

# gsr response for every bit
unique(tmp.df3$screencontent)
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo, screencontent)%>%
  mutate(gsr_response_scrcont =   max(gsr_basCor))

tmp.df3$gsr_response <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)

tmp.df3<-
  tmp.df3%>%
  arrange(time)%>%
  group_by(ssid, tNo)%>%
    fill(gsr_response)

tmp.df3<-
  tmp.df3%>%
  arrange(time)%>%
  group_by(ssid, tNo)%>%
    fill(gsr_response,  .direction = c('up'))

unique(tmp.df3$gsr_response )

```

#baseline and clean pupil

```{r}
library(gazer)
min(tmp.df3$pupil, na.rm = TRUE)
max(tmp.df3$pupil, na.rm = TRUE)

tmp.df3$pupil<- if_else(tmp.df3$pupil> 7.2, tmp.df3$pupil, NULL)

tmp.df3$pupil<- if_else(tmp.df3$pupil< 45, tmp.df3$pupil, NULL)

tmp.df3<- tmp.df3 %>%
  group_by(ssid, trialUnq) %>%
  mutate(extendpupil=extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

min(tmp.df3$extendpupil, na.rm = TRUE)
max(tmp.df3$pupil, na.rm = TRUE)

# let's check

ggplot(subset(tmp.df3, tmp.df3$tNo == 3), aes(x = timerezero3, y= extendpupil , colour = as.factor(ssid)))+
      geom_line()
  # geom_line(aes(y = extendpupil), linetype = 'dashed', colour = 'red')

# Smooth and Interpolate
tmp.df3$subject<- tmp.df3$ssid
tmp.df3$trial = tmp.df3$trialUnq

# min(pup_extend$pupil, na.rm = TRUE)
tmp.df3$extendpupil
# ?smooth_interpolate_pupil

library(gazer)

tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth',
                                    maxgap=Inf, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

min(tmp.df3$pup_interp, na.rm = TRUE)
max(tmp.df3$pup_interp, na.rm = TRUE)

ggplot(subset(tmp.df3, tmp.df3$tNo == 10 & tmp.df3$ssid == 320) , aes(x = timerezero3, y= pup_interp, colour = as.factor(ssid)))+
  geom_line()+
  geom_line(aes(y = pupil), colour = 'gray')
  # facet_grid(~Condition)

# create baseline pupil mean
tmp.df3backup<- tmp.df3
tmp.df3$pup_bas<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, tmp.df3$pup_interp, NULL)
# true if bseline if baseline within widnown
tmp.df3$pup_bastrue<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, TRUE, FALSE)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo, pup_bastrue)%>%
  mutate(pup_bas_med = median(pup_bas))

# fill the baseline mean pupil
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid,tNo)%>%
  fill(pup_bas_med)

# fill up to complete pupil
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(pup_bas_med, .direction = 'up')

# do baseline correction
tmp.df3<- tmp.df3%>%
  arrange(time)%>%
  group_by(ssid, tNo)%>%
  mutate(pup_basCor = pup_interp - pup_bas_med)

# we only one the median for rest
tmp.df3<- tmp.df3%>%
  group_by(Condition)%>%
  mutate(pupilrest = median(pup_interp))

tmp.df3$pup_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$pup_interp-tmp.df3$pupilrest, tmp.df3$pup_basCor)

# MAD removal
max_pup<-tmp.df3 %>%
  dplyr::group_by(subject, trial) %>%
  dplyr::mutate(speed=speed_pupil(pup_interp,time)) %>%
  dplyr::mutate(MAD=calc_mad(speed))
  # dplyr::filter(speed < MAD)

tmp.df3<- max_pup

# instead of deleting, nus put NA
tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)

tmp.df3$pup_interp_mad<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_interp, NULL)
# tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)

ggplot(subset(tmp.df3, tmp.df3$tNo == 5 & tmp.df3$ssid == 900) , aes(x = timerezero3, y= pup_basCor))+
    # geom_smooth(se = F)+
  geom_line()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

unique(tmp.df3$ssid)

ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
    geom_smooth(se = T)+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

colnames(tmp.df3)
table(is.na(tmp.df3$gsr_ms))
table(is.na(tmp.df3$hr))

# heart rate

min(tmp.df3$hr, na.rm = TRUE)
max(tmp.df3$hr, na.rm = TRUE)
tmp.df3$hrv<- as.double(tmp.df3$hrv)
tmp.df3$hrv2<- if_else(is.na(tmp.df3$hrv) == TRUE, 999,tmp.df3$hrv)

tmp.df3$hr_clean<- tmp.df3$hr
tmp.df3$hr_clean<- as.double(tmp.df3$hr_clean)

tmp.df3$hr_clean<- if_else(tmp.df3$hrv2 >0,  tmp.df3$hr_clean, NULL)

tmp.df3$hr_clean<- if_else(tmp.df3$hr_clean > 40 & tmp.df3$hr_clean< 120, tmp.df3$hr_clean, NULL)

table(is.na(tmp.df3$hr_clean))
# interpolate, only 2 seconds 
library(zoo)
tmp.df3<- tmp.df3%>%
  arrange(ssid, time, tNo)

# tmp.df3$hr_interp =

tmp.df3<- tmp.df3%>%
  # arrange(ssid, time, tNo)%>%
  group_by(ssid, tNo,screencontent)%>%
  mutate(hr_interp = na.approx(hr_clean, na.rm=FALSE, maxgap =400))

  min(tmp.df3$hr, na.rm = TRUE)
ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 320) , aes(x = timerezero3, y= hr_interp))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_clean), linetype = 'dashed', colour = 'green', size = 0.3)+
   geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
    # geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    # geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

# na.approx(object, x = index(object), xout, ..., na.rm = TRUE, maxgap = Inf, along)
# z <- na.spline(zoo(y, x), maxgap = 2)

tmp.df3 <- tmp.df3 %>%
    group_by(ssid, tNo, gsr_resp_Log, screencontent)%>%
    mutate(gsr_response_bycond =   max(gsr_basCor))

# tmp.df3$gsr_response_bycond <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)

colnames(tmp.df3)
# tmp.df4<- select(tmp.df3, c(1:3,10:22,27:30,33:37,44,46,47,51,53:56,60))

tmp.df4<- select(tmp.df3, c("session_id", "event_id", "ssid", "subject", "text", "trial","trialUnq", "tNo","trigger", "Condition" ,"screencontent","stim",
                            "time", "timerezero", "timerezero2", "timerezero3", "status","filename",
                            "left_gaze_x_cor_pix","right_gaze_x_cor_pix","left_gaze_y_cor_pix","right_gaze_y_cor_pix",  "gaze_x_cor_pix",  "gaze_y_cor_pix",
                            "pupil", "pup_interp_mad", "extendpupil","pup_basCor",
                            "hr", "hrv", "hrp", "hr_clean", 'hr_interp', 
                            'gsr_ms', 'gsr_basCor', 'gsr_response', 'gsr_response_bycond', 
                            "distance"))
head(tmp.df4)

# calculate trackloss
unique(tmp.df4$status)

tmp.df4$trackloss<- if_else(is.na(tmp.df4$gaze_x_cor_pix) == TRUE, 0, 
                         if_else(is.na(tmp.df4$gaze_y_cor_pix) == TRUE, 0, 1))
unique(tmp.df4$trackloss)

# tmp.df4$trackloss<- if_else(tmp.df4$status> 0, 1, 0)

tmp.df4$hr_trackloss<- if_else(is.na(tmp.df4$hr_clean) == TRUE, 0, 1) # 1 means valid, 0 missing

tmp.df4 <- tmp.df4%>%
  group_by(ssid, tNo, trialUnq, text)%>%
  mutate(gaze_valid_prop = sum(trackloss)/n())%>%
  mutate(gaze_loss_prop = 1 - gaze_valid_prop)%>%
  mutate(hr_valid_prop = sum(hr_trackloss)/n())%>%
  mutate(hr_loss_prop = 1 - hr_valid_prop)

# check to see this is right
ggplot(subset(tmp.df4, tmp.df3$ssid == 324) , aes(x = tNo, y= hr_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)

ggplot(subset(tmp.df4, tmp.df3$ssid == 324) , aes(x = tNo, y= gaze_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = gaze_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)

colnames(tmp.df4)
write_csv(tmp.df4, 'interodata_clean_gp.csv')

# tmp.df4<- read_csv('intero_tsdata_clean.csv')

tmp.df4<- tmp.df4%>%
  arrange(ssid, time, tNo)

unique(tmp.df4$trigger)

# why

tmp.df4$trigger2<- tmp.df4$trigger

tmp.df4$trigger2<- if_else(tmp.df4$trigger>99, tmp.df4$trigger, as.double(tmp.df4$tNo))

unique(tmp.df4$trigger2)

tmp.df4<- tmp.df4%>%
  group_by(ssid, tNo, text)%>%
  mutate(stdev_gaze_x = sd(gaze_x_cor_pix, na.rm = TRUE))%>%
  mutate(stdev_gaze_y = sd(gaze_y_cor_pix, na.rm = TRUE))

tmp.df4$sdev_gazesum<- tmp.df4$stdev_gaze_x+ tmp.df4$stdev_gaze_y

# summarise
tmp.df4_sum<- tmp.df4%>%
  arrange(ssid, time, tNo)%>%
  group_by(ssid, subject, trial, Condition, screencontent, tNo, stim, trialUnq,text)%>%
  summarise_at(c('pup_basCor', 'gsr_response','gsr_response_bycond', 'gsr_basCor', 'hr_interp', 'hr_clean', 'time', 'gaze_loss_prop', 'gaze_valid_prop', 'hr_valid_prop', 'hr_loss_prop', 'timerezero3', 'sdev_gazesum', 'stdev_gaze_x', 'stdev_gaze_y'), mean, na.rm = TRUE)

tmp.df4_sum$trigger<-if_else(tmp.df4_sum$screencontent == 'fixation', 100,
                          if_else(tmp.df4_sum$screencontent == 'ValenceResp', 101,
                             if_else(tmp.df4_sum$screencontent == 'IntResp', 102, as.double(tmp.df4_sum$tNo))))

unique(tmp.df4_sum$trigger)

unique(tmp.df4_sum$trigger)
tmp.df4_sum<- tmp.df4_sum%>%
  arrange(time, tNo, ssid)

write_csv(tmp.df4_sum, 'intero_aggdata_clean.csv')

head(tmp.df4_sum)

unique(tmp.df4_sum$tNo)

ggplot(tmp.df4_sum, aes(tNo, gaze_valid_prop, colour = as.factor(ssid)))+
  geom_point()+
  geom_line()

ggplot(subset(tmp.df4_sum, tmp.df4_sum$screencontent == 'stim'), aes(tNo, gaze_valid_prop, colour = as.factor(ssid)))+
  geom_point()+
  geom_line()

ggplot(subset(tmp.df4_sum, tmp.df4_sum$screencontent == 'stim'), aes(gaze_valid_prop, colour = as.factor(ssid)))+
# geom_density()+
  geom_histogram()
  # geom_line()

# for gaze parsing

(sprintf("preparing for gazepath"))
  colnames(tmp.df4)

  for_gazepath<- select(tmp.df4, c(2:15,17:26, 39:40,42:43))

  for_gazepath$screencontent[for_gazepath$screencontent == 'rest1']<- 'fixation'
  for_gazepath<- for_gazepath%>%
    arrange(ssid, time, tNo)

  colnames(for_gazepath)

  for_gazepath<- subset(for_gazepath, is.na(for_gazepath$time) == FALSE)
   # View(for_gazepath)

  for_gazepath$split_column<- paste0(for_gazepath$ssid, paste0(for_gazepath$screencontent))
  splitcol<- unique(for_gazepath$split_column)
  splitcol
  # ssid<- unique(for_gazepath$ssid)
  # ssid
  split_df = split(for_gazepath, list(for_gazepath$split_column))

  (sprintf("writing for gazepath"))
  # ssid = split(for_gazepath, list(for_gazepath$ssid))
  # for (ssid in names(split_df)) {
    for (splitcol in names(split_df)) {
      # message( split_df[splitcol])
      write_csv(split_df[[splitcol]], paste0('gp_',paste0(splitcol),".csv"))
    }

```
process gazepath and ledalab
```{r}
library(gazepath)
GUI()

```

# Import Ledalab
Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 105 .01 2])
```{r}
read_leda <- function(flnm) {
  data.table::fread(flnm) %>% 
    mutate(filename = flnm)
}

# now read them
db_leda <-
  list.files(pattern = "*.txt", 
             full.names = T) %>% 
  map_df(~read_leda(.))

db_leda$trigger<- as.numeric(db_leda$Event.NID)
unique(db_leda$trigger)
db_leda$ssid<- as.numeric(substr(db_leda$filename, 13,15))
colnames(tmp.df4_sum)
colnames(db_leda)
nrow(tmp.df4_sum)
nrow(db_leda)
colnames(tmp.df4_sum)
tmp.df4_sum2<- subset(tmp.df4_sum,tmp.df4_sum$tNo != -7)
tmp.df4_sum2<- tmp.df4_sum2%>%
  arrange(ssid, time, tNo)%>%
  group_by(ssid)%>%
  mutate(order = 1:224)

db_leda2<- subset(db_leda, db_leda$trigger != -7)
db_leda2<- db_leda2%>%
  arrange(ssid, Event.Nr)%>%
  group_by(ssid)%>%
  mutate(order = 1:224)

tmp.df4_sum_fullt<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
tmp.df4_sum_full_backup<- tmp.df4_sum_full

tmp.df4_sum_full<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))

# tmp.df4_sum_full<- bind_cols(tmp.df4_sum, db_leda)

tmp.df4_sum_full<- tmp.df4_sum_full%>%
  arrange(ssid, tNo)
```

read parsed data
```{r}
read_parsed <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_parsed <- list.files(pattern = "*.csv", 
               full.names = T) %>% 
    map_df(~read_parsed(.))

# return content between spaces
# pu things in the correct order
# library(stringr)
db_parsed$screencontent<- str_extract(db_parsed$trialUnq, "(?<=\\s)(.*)(?=\\s)")
unique(db_parsed$screencontent)
db_parsed$screencontent[db_parsed$screencontent == 'rest1']<- 'fixation'

db_parsed$screencontent_no<- if_else(db_parsed$screencontent == 'fixation', 1,
                                      if_else(db_parsed$screencontent == 'stim', 2,
                                              if_else(db_parsed$screencontent == 'ValenceResp', 3,
                                                      if_else(db_parsed$screencontent == 'IntResp', 4, NULL))))

db_parsed$tNo<- as.numeric(substr(db_parsed$trialUnq, 1,2))
unique(db_parsed$screencontent_no)
db_parsed$ssid<- substr(db_parsed$Participant, 4,6)

db_parsed<- db_parsed%>%
  arrange(ssid, tNo, screencontent_no)

ggplot(db_parsed, aes(mean_x, mean_y))+
  geom_point()+
  facet_grid(ssid~screencontent)

unique(db_parsed$tNo)
# db_parsed$tNo<- if_else(db_parsed$tNo > -1, db_parsed$tNo-1, db_parsed$tNo )

db_parsed<-db_parsed%>%
  group_by(ssid, tNo, screencontent,Value)%>%
  mutate(mean_fix_dur = mean(Duration))%>%
  mutate(mean_POGsdSacAmp = mean(POGsdSacAmp))%>%
  mutate(fix_count = sum(Value == 'f'))%>%
  mutate(sac_count = sum(Value == 's'))

# this might be needed for tempoal analisys
write_csv(db_parsed, 'db_parsed.csv')

db_parsed_summarised<- db_parsed%>%
  group_by(ssid, tNo,screencontent, trialUnq, screencontent_no, Value)%>%
  summarise_at(c('fix_count', 'sac_count', 'mean_fix_dur', 'mean_POGsdSacAmp', 'RMS'), mean, na.rm = TRUE)

colnames(db_parsed_summarised)
db_parsed_summarised_fix<- subset(db_parsed_summarised, db_parsed_summarised$Value == 'f')
db_parsed_summarised_fix$sac_count<- NULL
db_parsed_summarised_fix$POGsd<- db_parsed_summarised_fix$mean_POGsdSacAmp
db_parsed_summarised_fix$mean_POGsdSacAmp<- NULL
db_parsed_summarised_fix$Value<-NULL
db_parsed_summarised_sac<- subset(db_parsed_summarised, db_parsed_summarised$Value == 's')
db_parsed_summarised_sac$fix_count<- NULL
db_parsed_summarised_sac$mean_sac_dur<-  db_parsed_summarised_sac$mean_fix_dur
db_parsed_summarised_sac$SacAmp<- db_parsed_summarised_sac$mean_POGsdSacAmp
db_parsed_summarised_sac$mean_POGsdSacAmp<- NULL
db_parsed_summarised_sac$mean_fix_dur<- NULL
db_parsed_summarised_sac$RMS<- NULL
db_parsed_summarised_sac$Value<- NULL
View(db_parsed_summarised_sac)
View(db_parsed_summarised_fix)
db_parsed_summarised_sac$Value<- NULL
db_parsed_summarised_fix$Value<- NULL
db_parsed_summarised_sac$RMS<- NULL

View(db_parsed)

colnames(db_parsed_summarised_fix)
colnames(db_parsed_summarised_sac)

db_parsed_summarised2<- left_join(db_parsed_summarised_fix,db_parsed_summarised_sac, by = (c('ssid', 'tNo', 'screencontent', "screencontent_no", "trialUnq")))

db_parsed_summarised2<- db_parsed_summarised2%>%
  arrange(ssid, tNo, screencontent_no)
# View(db_parsed_summarised2)
write_csv(db_parsed_summarised2, 'db_parsed_summarised.csv')

db_parsed_summarised2$ssid<- as.numeric(db_parsed_summarised2$ssid)
db_parsed_summarised2
tmp.df4_sum_full<- left_join(tmp.df4_sum_full,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))
rm(tmp.df4_sum_fullt)
testna<- subset(tmp.df4_sum_fullt, is.na(tmp.df4_sum_fullt$mean_fix_dur) == TRUE)

tmp.df4_sum_fullt
```

Behavioral data

```{r}
colnames(X309_2019_Dec_11_1807_01)
library(data.table) 
library(purrr)

read_plus_beh <- function(flnm, select = c("condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt")) {
  read.csv(flnm) %>% 
    mutate(filename = flnm)
}

# now read them
db_beh <-
  list.files(pattern = "*.csv",
             full.names = T) %>%
  map_df(~read_plus_beh(.))

db328$condition<-db328$ï..condition

db328 <-select(db328, c("condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))

db328$ssid<- 328

db328$filename<- db328$ssid

# files <- list.files(pattern = ".csv")
# temp <- do.call(rbind,lapply(files, read.csv), header = TRUE)

#install.packages("data.table", repos = "https://cran.rstudio.com")
library(data.table)

# Read all the files and create a FileName column to store filenames
db_beh <- rbindlist(sapply(files, fread, simplify = FALSE),
                use.names = TRUE, idcol = "filename")
db_beh$condition <- db_beh$ï..condition

db_beh<- select(db_beh, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))

db328<- select(db328, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))

# 
# db304<- rbindlist(sapply(files, fread, simplify = FALSE),
#                 use.names = TRUE, idcol = "filename")
# 
# 
# 
# db304<- select(db304, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
#                                      "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))

# db304$ssid<- 304
colnames(db_beh)
# db_beh<- bind_rows(db_beh, db304)
db_beh$ssid<- substr(db_beh$filename, 3,5)

# for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i]))

View(db_beh)

colnames(db_beh)

db_beh2<- db_beh
db328$filename<- as.character(db328$filename)
db328$ssid<- as.character(db328$ssid)

db328$ssid <- 328

db_beh2<- bind_rows(db_beh2, db328)

unique(db_beh2$ssid)
# create one column for arousl and RT

db_beh2$valence<- if_else(is.na(db_beh2$self_valence_4.response) == FALSE, db_beh2$self_valence_4.response,
                          if_else(is.na(db_beh2$self_valence_2.response) == FALSE, db_beh2$self_valence_2.response, NULL))

db_beh2$Self_intensity_3.response<- as.double(db_beh2$Self_intensity_3.response)                      
db_beh2$arousal<- if_else(is.na(db_beh2$Self_intensity_2.response) == FALSE, as.numeric(db_beh2$Self_intensity_2.response),
                          if_else(is.na(db_beh2$Self_intensity_3.response) == FALSE,
                                  as.numeric(db_beh2$Self_intensity_3.response), NULL))

db_beh2$valence_rt<- if_else(is.na(db_beh2$self_valence_4.rt) == FALSE, db_beh2$self_valence_4.rt,
                          if_else(is.na(db_beh2$self_valence_2.rt) == FALSE, db_beh2$self_valence_2.rt, NULL))

db_beh2$arousal_rt<- if_else(is.na(db_beh2$Self_intensity_2.rt) == FALSE, db_beh2$Self_intensity_2.rt,
                          if_else(is.na(db_beh2$Self_intensity_3.rt) == FALSE, db_beh2$Self_intensity_3.rt, NULL))

db_beh2$trialsPract.thisTrialN<- db_beh2$trialsPract.thisTrialN - 6

db_beh2$trialIAPS.thisTrialN<-db_beh2$trialIAPS.thisTrialN +1 
db_beh2$tNo<- if_else(is.na(db_beh2$Self_intensity_2.response) == FALSE, db_beh2$trialsPract.thisTrialN, db_beh2$trialIAPS.thisTrialN)
unique(db_beh2$tNo)
db_beh2<- subset(db_beh2, is.na(db_beh2$tNo) == FALSE)

db_beh2<- db_beh2%>%
  arrange(ssid, tNo)

ggplot(db_beh2, aes(tNo, valence, colour = ssid))+
  geom_point()+
  geom_line()

ggplot(db_beh2, aes(x = tNo, y = valence_rt))+
  geom_point()+
  geom_line()

ggplot(db_beh2, aes(x = valence, y = ValenceMean))+
  geom_point()+
  geom_smooth(method = lm, se = T)

ggplot(db_beh2, aes(x = arousal, y = ArousalMean))+
  geom_point()+
  geom_smooth(method = lm, se = T)

colnames(db_beh2)
db_beh2$triggeracq<- db_beh2$trigger
unique(db_beh2$ssid)

db_beh3<- select(db_beh2, c(2:7, 18:23))

# db_beh3<- subset(db_beh3, is.na(db_beh3$condition) == FALSE)

colnames(db_beh3)
colnames(db_beh3_301_309)
db_beh3$trigger<-NULL
db_beh3_301_309$triggeracq<- NULL

db_beh3_301_309$condition[db_beh3_301_309$condition == "Example Stimuli"]<- "Practice"
db_beh3$condition[db_beh3$condition == "Example Stimuli"]<- "Practice"

db_beh3$triggeracq<- NULL

library(readr)
db_beh300 <-  read_csv("300-309 beh/tmp.df4300_sum_full.csv")
View(tmp_df4300_sum_full)

db_beh300 <- subset(db_beh300, db_beh300$condition != "Rest")
colnames(db_beh300)

db_beh300$ssid<- 300

db_beh300<- select(db_beh300, c("condition", "stimIAPS","stimDescription","ValenceMean", "ArousalMean", "ssid", "valence","arousal","valence_rt","arousal_rt", "tNo"))

db_beh3$ssid<- as.numeric(db_beh3$ssid)
db_beh_all<- bind_rows(db_beh3, db_beh300)
db_beh_all<- bind_rows(db_beh_all, db_beh3_301_309)
# db_beh4<- db_beh3

unique(db_beh_all$ssid)

str(tmp.df4_sum)
str(db_beh_all)
tmp.df4_sum$ssid<- as.numeric(tmp.df4_sum$ssid)

db_beh3$ssid<- as.numeric(db_beh3$ssid)
# rm(tmp.df4_sum_full_t)

tmp.df4_sum_full<- left_join(tmp.df4_sum, db_beh_all, by = c('ssid', 'tNo'))

tmp.df4_sum_full<- tmp.df4_sum_full%>%
  arrange(ssid, tNo, time)

# self reports

db_selfrep <- read_csv("intero_selrep.csv")
View(intero_selrep)
tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_selfrep, by = 'ssid')

unique(tmp.df4_sum_full$ssid)
# colnames(tmp_df4300_sum_full)
# colnames(tmp.df4_sum_full)
# 
# tmp.df4_sum_full<- tmp.df4_sum_full[,1:54]
# tmp.df4_sum_full<- bind_rows(tmp.df4_sum_full, tmp_df4300_sum_full)

# db_selfrep <- read_csv("~/Documents/InteroStudy/data/Bio/Dec12/db_selfrep.csv")

# db_selfrep$ssid<- as.numeric(db_selfrep$ssid)

# tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_selfrep, by = 'ssid' )

View(tmp.df4_sum_full)
write_csv(tmp.df4_sum_full, 'intero_data_full.csv')

# tmp.df4_sum_full<- tmp.df4_sum_full%>%
#   arrange(ssid, tNo, screencontent_no)
```

check
```{r}

View(tmp.df4_sum_full)

tmp.df4_sum_full_stim<- subset( tmp.df4_sum_full,  tmp.df4_sum_full$screencontent == 'stim')

levels(as.factor(tmp.df4_sum_full_stim$Event.Name))
tmp.df4_sum_full_stim<- subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$gaze_valid_prop> .85)
colnames(tmp.df4_sum_full_stim)

# is objective arousal and self report arousal correated
tmp.df4_sum_full_stim$ValenceMean_cat<- if_else(tmp.df4_sum_full_stim$ValenceMean > 4, 'pos', 'neg')

ggplot(tmp.df4_sum_full_stim, aes(arousal, log1p(TTP.AmpSum)), color = as.factor(ssid))+
         geom_point()+
  geom_smooth(method= 'lm')+
  facet_grid(~ValenceMean_cat)
ggplot(tmp.df4_sum_full_stim, aes(arousal, log1p(TTP.AmpSum), color = as.factor(ssid)))+
         geom_point()+
  geom_smooth(method= 'lm')+
   facet_grid(~ValenceMean_cat)
  # facet_grid(~ssid) # for some subjects

color = as.factor(ssid)
ggplot(tmp.df4_sum_full_stim, aes(arousal, pup_basCor))+
         geom_point()+
  geom_smooth(method= 'lm')+
   facet_grid(~ValenceMean_cat)
  # facet_grid(~ssid)
color = as.factor(ssid)
ggplot(tmp.df4_sum_full_stim, aes(arousal, hr))+
         geom_point()+
  geom_smooth(method= 'lm')+
   facet_grid(~ValenceMean_cat)

ggplot(tmp.df4_sum_full_stim, aes(arousal, hr))+
         geom_point()+
  geom_smooth(method= 'lm')

ggplot(tmp.df4_sum_full_stim, aes(arousal, pup_basCor))+
         geom_point()+
  geom_smooth(method= 'lm')

# do our physio signals corelate with one another

ggplot(tmp.df4_sum_full_stim, aes(gsr_basCor, hr, color = as.factor(ssid)))+
         geom_point()+
  geom_smooth(method= 'lm')+
   facet_grid(~ValenceMean_cat)

ggplot(subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$CDA.AmpSum > 0), aes(TTP.AmpSum, hr))+
         geom_point()+
  geom_smooth(method= 'lm')+
   facet_grid(~ValenceMean_cat)

ggplot(tmp.df4_sum_full_stim, aes(gsr_basCor, pup_basCor))+
         geom_point()+
  geom_smooth(method= 'lm')+
   facet_grid(~ValenceMean_cat)
 colour = as.factor(ssid)
ggplot(tmp.df4_sum_full_stim, aes(hr, pup_basCor))+
         geom_point()+
  geom_smooth(method= 'lm')+
   facet_grid(~ValenceMean_cat)

ggplot(tmp.df4_sum_full_stim, aes(arousal, log1p(CDA.PhasicMax)), color = as.factor(ssid))+
         geom_point()+
  geom_smooth(method= 'lm')+
   facet_grid(~ValenceMean_cat)

# okay arousal on gaze

# is there and affect of arousal on number of fxation and saccadescolor = as.factor(ssid)
library(tibble)

is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))
}

ggplot(tmp.df4_sum_full_stim, aes(CDA.PhasicMax, fix_count))+
         geom_point()+
  geom_smooth(method= 'lm')+
   facet_grid(~ValenceMean_cat)

ggplot(tmp.df4_sum_full_stim, aes(CDA.PhasicMax, sac_count))+
         geom_point()+
  geom_smooth(method= 'lm')+
   facet_grid(~ValenceMean_cat)

ggplot(tmp.df4_sum_full_stim, aes(ValenceMean_cat, sac_count))+
  # geom_jitter()+
  stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2)
    # geom_boxplot()
  # geom_text(aes(label=ssid),hjust=0, vjust=0)

ggplot( tmp.df4_sum_full_stim, aes(IAS, cor_arousal))+
  geom_point()+
  geom_smooth(method = 'lm')
  # stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2)+
    # geom_boxplot()+
  # geom_text(aes(label=ssid),hjust=0, vjust=0)

ggplot(tmp.df4_sum_full_stim, aes(ValenceMean_cat, fix_count))+
  # geom_jitter()+
  stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2) 
    # geom_boxplot()+
  # geom_text(aes(label=ssid),hjust=0, vjust=0)

ggplot(tmp.df4_sum_full_stim, aes(ValenceMean_cat, mean_sac_dur))+
  # geom_jitter()+
  stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2)
    # geom_boxplot()
  # geom_text(aes(label=ssid),hjust=0, vjust=0)

ggplot(tmp.df4_sum_full_stim, aes(ValenceMean_cat, mean_fix_dur))+
  # geom_jitter()+
  stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2)
  geom_boxplot()
  # geom_text(aes(label=ssid),hjust=0, vjust=0)

ggplot(tmp.df4_sum_full_stim, aes(CDA.PhasicMax, fix_count, color = as.factor(ssid)))+
         geom_point()+
  geom_smooth(method= 'lm')
  # facet_grid(~ssid)+
    # geom_text(aes(label=ssid),hjust=0, vjust=0)

ggplot(subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$mean_fix_dur < 6000), aes(TTP.AmpSum, mean_fix_dur))+
         geom_point()+
  geom_smooth(method= 'lm')+
   facet_grid(~ValenceMean_cat)

ggplot(subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$mean_fix_dur < 6000 & tmp.df4_sum_full_stim$CDA.AmpSum>0 ), aes(CDA.PhasicMax, mean_fix_dur))+
         geom_point()+
  geom_smooth(method= 'lm')+
   facet_grid(~ValenceMean_cat)

ggplot(tmp.df4_sum_full_stim, aes(TAS, IAS))+
         geom_point()+
  geom_smooth(method= 'lm')

p<- list()
library(lmerTest)

tmp.df4_sum_full_stim$TAS_c<- scale(tmp.df4_sum_full_stim$TAS, center = TRUE,scale = TRUE)
tmp.df4_sum_full_stim$IAS_c<- scale(tmp.df4_sum_full_stim$IAS, center = TRUE, scale = TRUE)
tmp.df4_sum_full_stim$arousal_c<- scale(tmp.df4_sum_full_stim$arousal, center = TRUE,scale = TRUE)

tmp.df4_sum_full_stim<- tmp.df4_sum_full_stim%>%
  group_by(ssid)%>%
  mutate(cor_arousal = cor(arousal_c, hr))
tmp.df4_sum_full_stim<- tmp.df4_sum_full_stim%>%
  # mutate(ssid = as.factor(ssid))%>%
  mutate(stim = as.factor(stim))
tmp.df4_sum_full_stim$ssid<- as.factor(tmp.df4_sum_full_stim$ssid)

tmp.df4_sum_full_stim$valence_c<- scale(tmp.df4_sum_full_stim$valence, center = TRUE, scale = TRUE)
tmp.df4_sum_full_stim$TTP.AmpSum<- scale(tmp.df4_sum_full_stim$TTP.AmpSum,center = TRUE, scale = TRUE)

# test soe models
tmp.df4_sum_full_stimagg<- (tmp.df4_sum_full_stim%>%
              group_by(ssid)%>%
              summarise_at(c('IAS_c', 'TAS_c', 'AQ','cor_arousal', 'fix_count'), mean, na.rm = TRUE))

ggplot(tmp.df4_sum_full_stimagg, aes(TAS_c, cor_arousal))+
  geom_point()+
  geom_smooth(method = 'lm')

ggplot(tmp.df4_sum_full_stimagg, aes(IAS_c, cor_arousal))+
  geom_point()+
  geom_smooth(method = 'lm')

# tmp.df4_sum_full_stimagg<- subset(tmp.df4_sum_full_stimagg, is.na(tmp.df4_sum_full_stimagg$IAS_c) == FALSE)

p$a<- glmer(fix_count ~ 1 + IAS_c * CDA.ISCR *ValenceMean_cat + (1 | ssid ),
           family = poisson(), data = tmp.df4_sum_full_stim)

summary(p$a)

p$a1<- lmer(mean_fix_dur ~ 1 + IAS_c * (arousal_c + hr) * ValenceMean_cat + (1 | ssid ),
           REML = FALSE, data = tmp.df4_sum_full_stim)

summary(p$a1)

p$a1<- lmer(mean_fix_dur ~ 1 + IAS_c * + hr * ValenceMean_cat + (1 | ssid ),
           REML = FALSE, data = tmp.df4_sum_full_stim)

summary(p$a1)

p$a2<- lmer(mean_fix_dur ~ 1 + IAS_c * (arousal_c + TTP.AmpSum) + (1 | ssid ),
           REML = FALSE, data = tmp.df4_sum_full_stim)

summary(p$a2)

p$a2<- lmer(mean_fix_dur ~ 1 + cor_arousal * hr + (1 | ssid ),
           REML = FALSE, data = tmp.df4_sum_full_stim)

tmp.df4_sum_full_stim$hr_c<- scale(tmp.df4_sum_full_stim$hr, center = TRUE, scale = TRUE)

p$a3<- glmer(sac_count ~ 1 + IAS_c * hr * ValenceMean_cat  + (1 | ssid ),
           family = poisson(), data = tmp.df4_sum_full_stim)

summary(p$a3)
# p$a2<- lmer(mean_fix_dur ~ 1 + cor_arousal * ( hr)+ (1 | ssid ),
#            REML = FALSE, data = tmp.df4_sum_full_stim)
p$a4<- lmer(gsr_basCor ~ 1 + IAS_c * arousal_c + (1 | ssid ),
           REML = FALSE, data = tmp.df4_sum_full_stim)

summary(p$a4)

       tmp.df4_sum_full_stim_cor<- tmp.df4_sum_full_stim%>%
  group_by(ssid, TAS, IAS, AQ, `DASS Total`)%>%
  summarise(cor_arousal_self = cor(arousal,  log1p(CDA.PhasicMax)))

ggplot(tmp.df4_sum_full_stim_cor, aes(`DASS Total`, cor_arousal_self))+
         geom_point()+
  geom_smooth(method= 'lm')

cor(tmp.df4_sum_full_stim_cor$cor_arousal_self, tmp.df4_sum_full_stim_cor$TAS,  use = 'complete')
cor(tmp.df4_sum_full_stim_cor$cor_arousal_self, tmp.df4_sum_full_stim_cor$IAS,  use = 'complete')
cor(tmp.df4_sum_full_stim_cor$TAS, tmp.df4_sum_full_stim_cor$IAS,  use = 'complete')

tmp.df4_sum_full_stim_cor [1:8,]%>%
  summarise(cor2 = cor(cor_arousal_self, TAS, use = 'complete'))

ggplot(tmp.df4_sum_full_stim, aes(arousal_c, log1p(mean_fix_dur)))+
  geom_point()+
  geom_smooth(method = 'lm')

```

IMPORT BIOPAC

```{r}
colnames(tmp.df4_sum_full)

# import
read_leda_bio <- function(flnm) {
  data.table::fread(flnm) %>% 
    mutate(filename = flnm)
}

# now read them
db_leda_bio <-
  list.files(pattern = "*.txt", 
             full.names = T) %>% 
  map_df(~read_leda_bio(.))

db_leda_bio$trigger<- as.numeric(db_leda_bio$Event.NID)
db_leda_bio$ssid<- as.numeric(substr(db_leda_bio$filename, 3,5))

colnames(tmp.df4_sum_full)
unique(tmp.df4_sum_full$trigger)

tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full, tmp.df4_sum_full$ssid>303)
# tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full_bio, tmp.df4_sum_full_bio$trigger!= -7)

levels(as.factor(tmp.df4_sum_full_bio$ssid))
unique(tmp.df4_sum_full_bio$trigger)
levels(as.factor(db_leda_bio$ssid))

db_leda_bio$ssid<- as.factor(db_leda_bio$ssid)
db_leda_bio$trigger<- as.factor(db_leda_bio$trigger)
db_leda_bio$order<- db_leda_bio$Event.Nr
tmp.df4_sum_full_bio$ssid<- as.factor(tmp.df4_sum_full_bio$ssid)
tmp.df4_sum_full_bio$trigger<- as.factor(tmp.df4_sum_full_bio$trigger)

colnames(tmp.df4_sum_full_bio)

unique(db_leda_bio$trigger)
unique(db_leda_bio$Event.Name)
unique(tmp.df4_sum_full_bio$trigger)
unique(tmp.df4_sum_full_bio$Event.Name)

tmp.df4_sum_full_bio%>%
  arrange(ssid, tNo, order)
db_leda_bio<- db_leda_bio%>%
  arrange(ssid, order)

tmp.df4_sum_full_bio$trigger<- tmp.df4_sum_full_bio$tNo
tmp.df4_sum_full_bio$trigger<- if_else(tmp.df4_sum_full_bio$screencontent == 'fixation', 100,
                                       if_else(tmp.df4_sum_full_bio$screencontent == 'ValenceResp', 101,
                                               if_else(tmp.df4_sum_full_bio$screencontent == 'IntResp', 102, tmp.df4_sum_full_bio$tNo)))

unique(tmp.df4_sum_full_bio$trigger)

tmp.df4_sum_full_biot<-left_join(tmp.df4_sum_full_bio, db_leda_bio, by = c("order", "ssid", "trigger"))
(db_leda_bio$trigger)

nrow(tmp.df4_sum_full_bio)
nrow(db_leda_bio)

tmp.df4_sum_full<- tmp.df4_sum_full%>%
  arrange(ssid, tNo)

ggplot(tmp.df4_sum_full_biot, aes(CDA.PhasicMax.x, CDA.PhasicMax.y))+
  geom_point()+
  geom_smooth(method = 'lm')

ggplot(tmp.df4_sum_full_biot, aes(TTP.AmpSum.x, TTP.AmpSum.y))+
  geom_point()+
  geom_smooth(method = 'lm')

tmp.df4_sum_full_biot
ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308), aes(TTP.AmpSum.y, arousal, colour = ssid))+
  geom_point()+
  geom_smooth(method = 'lm', se = T)

ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308), aes(TTP.AmpSum.y, arousal))+
  geom_point()+
  geom_smooth(method = 'lm', se = T)
ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308 & tmp.df4_sum_full_biot$TTP.AmpSum.y> 0), aes( TTP.AmpSum.y, arousal))+
  geom_point()+
  geom_smooth(method = 'lm', se = T)
tmp.df4_sum_full_biot1 <-subset(tmp.df4_sum_full_biot, tmp\.df4_sum_full_biot$ssid != 308)

cor(tmp.df4_sum_full_biot1$arousal, tmp.df4_sum_full_biot1$Global.Mean.y, use = 'complete.obs')
```

import biopac heart rate
```{r}
nrow(tmp.df4_sum_full_bio)

colnames(tmp.df4_sum_full_bio)
unique(tmp.df4_sum_full_bio$ssid)

unique(db_biohr$filename)

# import
read_biohr <- function(flnm) {
  data.table::fread(flnm) %>% 
    mutate(filename = flnm)
}

# now read them
db_biohr <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_biohr(.))

db_biohr$ssid<- substr(db_biohr$filename, 6,8)
db_biohr$order<- db_biohr$Order

db_biohr$Order<- NULL
db_biohr$filename<- NULL
db_biohr$trigger<- as.factor(as.character(db_biohr$trigger))
unique(tmp.df4_sum_full_bio$ssid)
unique(db_biohr$ssid)
tmp.df4_sum_full_bio$trigger<- as.factor(as.character(tmp.df4_sum_full_bio$trigger))

db_biohr$ssid<- as.factor(as.character(db_biohr$ssid))
tmp.df4_sum_full_bio_hr<- left_join(tmp.df4_sum_full_biot, db_biohr, by = c('ssid', 'order', 'trigger'))

ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(hr, HR_BIO))+
  geom_point()+
  geom_smooth(method = 'lm')

ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(CDA.PhasicMax.x, CDA.PhasicMax.y))+
  geom_point()+
  geom_smooth(method = 'lm')
tmp.df4_sum_full_bio_hr_stim<- subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent != 'fixation')

cor(tmp.df4_sum_full_bio_hr_stim$hr, tmp.df4_sum_full_bio_hr_stim$HR_BIO, use = 'complete')

# tmp.df4_sum_full_bio_hr_stim_1<- subset(tmp.df4_sum_full_bio_hr_stim, tmp.df4_sum_full_bio_hr_stim$HR_BIO> 50)

tmp.df4_sum_full_bio_hr_stim$valence_cat<- if_else(tmp.df4_sum_full_bio_hr_stim$valence >0, 'pos',
                                                  if_else(tmp.df4_sum_full_bio_hr_stim$valence < 0, 'neg', 'neutral'))

unique(tmp.df4_sum_full_bio_hr_stim$screencontent)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
  geom_point()+
  geom_smooth(method = 'lm')
  # facet_grid(~valence_cat)

cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$arousal, use = 'complete')
cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$valence, use = 'complete')

tmp.df4_sum_full_bio_hr_stim%>%
      group_by(ssid, IAS)%>%
      summarise(corr = cor(HR_BIO, arousal, use = 'complete'))%>%
  summarise(new = cor(corr, IAS))
  # summarise_at(c('TAS'), mean)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
  geom_point()+
  geom_smooth(method = 'lm')+
  facet_grid(~valence_cat)

tmp.df4_sum_full_bio_hr_stim%>%
group_by(valence_cat)%>%
  summarise(corr = cor(HR_BIO, arousal, use = 'complete'))
ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, valence))+
  geom_point()+
  geom_smooth(method = 'lm')+
  facet_grid(~valence_cat)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, ValenceMean))+
  geom_point()+
  geom_smooth(method = 'lm')
  # facet_grid(~valence_cat)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, mean_sac_dur))+
  geom_point()+
  geom_smooth(method = 'lm')+
  facet_grid(~valence_cat)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, pup_basCor))+
  geom_point()+
  geom_smooth(method = 'lm')+
  facet_grid(~valence_cat)

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, Global.Mean.y))+
  geom_point()+
  geom_smooth(method = 'lm')

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, TAS))+
  geom_point()+
  geom_smooth(method = 'lm')

ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, `DASS Anxiety`))+
  geom_point()+
  geom_smooth(method = 'lm')

```

### 2021-08-19 intero_study_preprocessing.Rmd
Update intero_study_preprocessing.Rmd

@@
 
+# for some reason 355 is creating duplicate event ids
+library(readr)
+ss355_GPdata_ <- read_csv("ss355_GPdata .csv")
+
+View(ss355_GPdata_)
+
+ss355_GPdata_nodup <- subset(ss355_GPdata_, !duplicated(ss355_GPdata_$event_id))
+
+write_csv(ss355_GPdata_nodup, "ss355_GPdata_nodup.csv")
+
 ```
@@
 gaze path
-clean and tracloss
+clean and trackloss
 
@@
 # now read them
-setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Step1_GpExtractor_Output")
+# setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Step1_GpExtractor_Output")
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021/step1")
 
@@
   # tmp.df2$right_pupil_measure1<- if_else(tmp.df2$pupil_meas>7, tmp.df2$right_pupil_measure1, NULL)
-  message(sprintf("step 4 cutingt off screen in points and repixel"))
+  message(sprintf("step 4 cuting off screen in points and repixel"))
   tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$left_gaze_x_cor >= -960 & tmp.df2$left_gaze_x_cor <= 960, tmp.df2$left_gaze_x_cor, NULL)
@@
 
-# let's check to see if it looks fine
+# let's check to see if it looks fine - NOTE THIS IS a bit SLOW
 ggplot(tmp.df3, aes(time, gsr, colour = as.factor(ssid)))+
@@
       fill(zero_stim, .direction = c('up'))
+
 tmp.df3$timerezero2<- tmp.df3$time-tmp.df3$zero_stim
@@
 #tmp.df3<- subset(tmp.df3, is.na(tmp.df3$ssid) == FALSE)
-
-ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
-    geom_smooth()+
+tmp.df3%>%
+subset(Condition == 'IAPS' & ssid ==  353)%>%
+  ggplot(aes(x = timerezero3, y= gsr))+
+  stat_smooth()+
+    # geom_smooth()+
     # geom_()+
@@
 
-ggplot(subset(tmp.df3, tmp.df3$tNo == -4) , aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
+tmp.df3%>%
+subset( tNo == -5)%>%
+  ggplot( aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
   # geom_point()
@@
 ```{r}
+
 tmp.df3<- tmp.df3%>%
@@
 tmp.df3<- tmp.df3 %>%
-  group_by(ssid, trialUnq) %>%
+  group_by(ssid, trialUnq,tNo,screencontent) %>%
   mutate(extendpupil=extend_blinks(pupil, fillback=100, fillforward=100, hz=150))
@@
 
+?smooth_interpolate_pupil
+
 tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
-                                    extendblinks=TRUE, step.first= 'smooth',
+                                    extendblinks=TRUE, step.first= 'smooth/interpolate',
                                     maxgap=Inf, 
                                     filter = 'moving',
+                                    type="linear", hz=150, n = 5)
+
+tmp.df3<-tmp.df3 %>%
+  group_by(ssid, trialUnq,tNo,screencontent) %>%
+  smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
+                                    extendblinks=TRUE, 
+                           step.first= 'smooth',
+                                    maxgap=10, 
+                                    filter = 'moving',
+                                    type="linear", hz=20, n = 10)
+
+tmp.df3<- tmp.df3 %>%
+  group_by(ssid, trialUnq,tNo,screencontent) %>%
+  smooth_interpolate_pupil(pupil="extendpupil", extendpupil="extendpupil",
+                                    extendblinks=TRUE, step.first= 'smooth/interpolate',
+                                    maxgap=100, 
+                                    filter = 'moving',
                                     type="linear", hz=150, n = 30)
@@
 
-ggplot(subset(tmp.df3, tmp.df3$tNo == 10 & tmp.df3$ssid == 320) , aes(x = timerezero3, y= pup_interp, colour = as.factor(ssid)))+
+subset(tmp.df3, tNo == 20 & ssid == 347)%>%
+ggplot(aes(x = timerezero3, y= pup_interp))+
   geom_line()+
+   geom_line(aes(y = extendpupil), color = 'red')+
   geom_line(aes(y = pupil), colour = 'gray')
   # facet_grid(~Condition)
+
+subset(tmp.df3, tNo == -7 & ssid == 350)%>%
+ggplot(aes(x = timerezero3, y= pupil))+
+  geom_line()
+
+subset(tmp.df3, tNo == -7 & ssid == 350)%>%
+ggplot(aes(x = timerezero3, y= pup_interp))+
+  geom_line()+
+   geom_line(aes(y = extendpupil), color = 'red')
+  geom_line(aes(y = pup_interp), colour = 'gray')
+  # facet_grid(~Condition)
+```
 

### 2021-08-19 intero_study_preprocessing.Rmd
step1-2
continue on line 1231

@@
 ```{r}
+library(tidyverse)
 colnames(tmp.df2)
@@
 natest<- subset(tmp.df3, is.na(tmp.df3$tNo) == TRUE)
+
 tmp.df3<- subset(tmp.df3, is.na(tmp.df3$tNo) == FALSE)
@@
 tmp.df3<- tmp.df3%>%
-  arrange(ssid, time,tNo)
+  arrange(ssid, tNo,time)
 # gsr baseline wil be the 1 second before tial start
@@
 options(scipen = 999)
+
 tmp.df3$gsr_ms<- 1/tmp.df3$gsr*100000
@@
 unique(db_GSR$Condition)
+
 db_GSR$Condition2<- if_else(db_GSR$Condition == 'Rest', 'Rest', 'IAPS')
@@
 # use ms to baseline
+tmp.df3_backup<- tmp.df3
 
@@
 tmp.df3<- tmp.df3%>%
-  arrange(time)%>%
+  arrange(ssid, tNo,time)%>%
   group_by(ssid, tNo, gsr_bastrue)%>%
@@
 
+tmp.df3_backup<- tmp.df3
 # gsr respone
@@
 unique(tmp.df3$screencontent)
+
 tmp.df3<- tmp.df3%>%
@@
   tmp.df3%>%
-  arrange(time)%>%
+  arrange(ssid, tNo,time)%>%
   group_by(ssid, tNo)%>%
@@
 
+tmp.df3_backup<- tmp.df3
 ```
@@
 library(gazer)
+
 min(tmp.df3$pupil, na.rm = TRUE)
@@
 
+tmp.df3_backup <- tmp.df3
+
+# note that smothing and interpolating is order dependednt so order by ssid, trial and time
 tmp.df3<- tmp.df3 %>%
+  arrange(ssid, trialUnq,tNo, time)%>%
   group_by(ssid, trialUnq,tNo,screencontent) %>%
-  mutate(extendpupil=extend_blinks(pupil, fillback=100, fillforward=100, hz=150))
+  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=100, fillforward=100, hz=150))
 
@@
 
-library(gazer)
+# library(gazer)
 
@@
 
+# vert order dependent
 tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
-                                    extendblinks=TRUE, step.first= 'smooth/interpolate',
+                                    extendblinks=TRUE, step.first= 'smooth',
                                     maxgap=Inf, 
                                     filter = 'moving',
-                                    type="linear", hz=150, n = 5)
-
-tmp.df3<-tmp.df3 %>%
-  group_by(ssid, trialUnq,tNo,screencontent) %>%
-  smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
-                                    extendblinks=TRUE, 
-                           step.first= 'smooth',
-                                    maxgap=10, 
-                                    filter = 'moving',
-                                    type="linear", hz=20, n = 10)
-
-tmp.df3<- tmp.df3 %>%
-  group_by(ssid, trialUnq,tNo,screencontent) %>%
-  smooth_interpolate_pupil(pupil="extendpupil", extendpupil="extendpupil",
-                                    extendblinks=TRUE, step.first= 'smooth/interpolate',
-                                    maxgap=100, 
-                                    filter = 'moving',
                                     type="linear", hz=150, n = 30)
+
+# tmp.df3<- tmp.df3 %>%
+#   group_by(ssid, trialUnq,tNo,screencontent) %>%
+#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
+#                                     extendblinks=TRUE, 
+#                            step.first= 'smooth',
+#                                     maxgap=10, 
+#                                     filter = 'moving',
+#                                     type="linear", hz=20, n = 10)
+# 
+# 
+# tmp.df3<-
+#   tmp.df3%>%
+#   arrange(ssid,tNo,time)
+#   # group_by(ssid, tNo, timerezero3)%>%
+# 
+# tmp.df3te<- tmp.df3 %>%
+#   group_by(ssid, Condition,tNo,screencontent) %>%
+#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
+#                                     extendblinks=TRUE, 
+#                            step.first= 'smooth',
+#                                     maxgap=Inf, 
+#                                     filter = 'moving',
+#                                     type="linear", hz=100, n = 5)
 
@@
 
-subset(tmp.df3, tNo == -7 & ssid == 350)%>%
+subset(tmp.df3, tNo == 1)%>%
 ggplot(aes(x = timerezero3, y= pup_interp))+
   geom_line()+
-   geom_line(aes(y = extendpupil), color = 'red')
-  geom_line(aes(y = pup_interp), colour = 'gray')
+   geom_line(aes(y = extendpupil), color = 'red')+
+  # geom_line(aes(y = pup_interp), colour = 'gray')+
+    facet_grid(~ssid)
   # facet_grid(~Condition)
@@
 # create baseline pupil mean
+```{r}
 tmp.df3backup<- tmp.df3
@@
 tmp.df3<- tmp.df3%>%
-  arrange(time)%>%
+  arrange(ssid, tNo, time)%>% # pay attentipn to order
   group_by(ssid, tNo)%>%
@@
 # MAD removal
+library(gazer)
 max_pup<-tmp.df3 %>%
@@
 
-ggplot(subset(tmp.df3, tmp.df3$tNo == 5 & tmp.df3$ssid == 900) , aes(x = timerezero3, y= pup_basCor))+
+ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
     # geom_smooth(se = F)+
@@
     geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
-
+```
 unique(tmp.df3$ssid)
 
+```{r}
 ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
@@
 
+```
+
+```{r}
 colnames(tmp.df3)
@@
 max(tmp.df3$hr, na.rm = TRUE)
+
 tmp.df3$hrv<- as.double(tmp.df3$hrv)
@@
 library(zoo)
+
 tmp.df3<- tmp.df3%>%
-  arrange(ssid, time, tNo)
+  arrange(ssid,tNo, time)
 
@@
   min(tmp.df3$hr, na.rm = TRUE)
-ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 320) , aes(x = timerezero3, y= hr_interp))+
+ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 352) , aes(x = timerezero3, y= hr_interp))+
     # geom_smooth(se = F)+
@@
 
+```
+
+```{r}
 tmp.df3 <- tmp.df3 %>%
@@
 # check to see this is right
-ggplot(subset(tmp.df4, tmp.df3$ssid == 324) , aes(x = tNo, y= hr_valid_prop))+
+ggplot(subset(tmp.df4, tmp.df3$ssid == 353) , aes(x = tNo, y= hr_valid_prop))+
     # geom_smooth(se = F)+
@@
 
-ggplot(subset(tmp.df4, tmp.df3$ssid == 324) , aes(x = tNo, y= gaze_valid_prop))+
+ggplot(subset(tmp.df4, tmp.df3$ssid == 354) , aes(x = tNo, y= gaze_valid_prop))+
     # geom_smooth(se = F)+

### 2021-08-20 Experiment 2.Rmd
Preprocessing
This is the updated code with the correct repixelation. This was tested in the validation paper, so use it as a model

---
title: "InteroceptionStudy_GPValidation"
Author: "Helio Cuve & "
date: "8 January 2021"
output: html_document
---

# Loading rdhf5 
```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install(version = "3.10")

BiocManager::install("rhdf5")

library(rhdf5)

```

# Preferences
list necessary package install them if not already and load them
```{r}
# devtools::install_github("dmirman/gazer")

list.of.packages <- c("ggplot2", "data.table", 'readr', "rhdf5", 'tidyverse', "gazer", 'lmerTest')
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
lapply(list.of.packages, require, character.only = TRUE)
lapply(new.packages, require, character.only = TRUE)

library(purrr)
library(data.table)
library(dplyr)
library(tidyr)

# setting a workspace
# change approproatelly

setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020")
hdf5FilesPath<- "D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020"

# 2021 data
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021")
hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021"
```

# gp extractor function
takes gp files and returns a clean files with messages parsed and deletes unnecessary stuff

note that starting from 322 we have gsr-v and hr-v, and pulse

```{r, gp extractor}

# hdf5FilesPath<- "D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking"

hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021"

gp.extractor = function(hdf5FilesPath) {

  setwd(hdf5FilesPath)
  #getwd()
  hdfFilesList = list.files(hdf5FilesPath, pattern = "\\.hdf5$")

  if (length(hdfFilesList) == 0){

    return(message('No HDF5 files found in the directory provided.'))
  }
   f = 30
  for (f in 1:length(hdfFilesList)) {

    message(sprintf("Extracting file %i / %i - %s", f, length(hdfFilesList), hdfFilesList[f]))

    #note that some r-studio bug sometimes causes this to fail when runnin from notebook, 
    # in that case run it directly on command line
    tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent')

    tmp.eyetr  = h5read(hdfFilesList[f], '/data_collection/events/eyetracker/BinocularEyeSampleEvent')

    # Get subject id from Events
    ssid = sapply(strsplit(grep('SubjJID', tmp.events$text, value = TRUE), split = ": "), "[", 2)
    date = sapply(strsplit(grep('DATE', tmp.events$text, value = TRUE), split = ": "), "[", 2)
    session = sapply(strsplit(grep('Session:', tmp.events$text, value = TRUE), split = ":"), "[", 2)
    cali<- subset(tmp.events, grepl('Cali', tmp.events$text) == TRUE)

    # Create DF for trials data
    tmp.df = data.frame(matrix(ncol = ncol(tmp.eyetr)))
    names(tmp.df) = names(tmp.eyetr)
    colnames(tmp.df)

    # Prepare Events, keep only start/end messages
    phrases = c('tStart', 'tEnd')
    tmp.events_backup<- tmp.events
    # tmp.events<-  tmp.events_backup
    tmp.events = subset(tmp.events, grepl(paste(phrases, collapse = "|"), tmp.events$text))

    # Create start/end references
    tmp.events$tStart   = NA
    tmp.events$tEnd     = NA

    # Trial number extraction 
    tmp.events$tNo      = NA
    tmp.df$tNo          = NA
    tmp.df$Condition    = NA

    # Space for subject id
    tmp.df$ssid         = NA
    tmp.df$text<-NA

    for (l in 1:nrow(tmp.events)) {

      message(sprintf("Grabing start messages %s", tmp.events$text[l]))

      if ((grepl('tStart', tmp.events$text[l])) == TRUE) {
        tmp.events$tStart[l] = tmp.events$time[l]

        if ((grepl('tEnd', tmp.events$text[l+1])) == TRUE){
          tmp.events$tEnd[l] = tmp.events$time[l+1]
        }

        else {
          message('trial start/end structure not valid')
        }
      }

    }
    message(sprintf("done grabbing messages"))
    # readline(prompt="Press [enter] to continue")

    tmp.events$tNo<- as.numeric(as.character(gsub(".*_","",tmp.events$text)))

     message(sprintf("making screencontent"))

     tmp.eventsbackup<- tmp.events
    tmp.events$screencontent<- if_else(grepl('fixation', tmp.events$text), 'fixation',
                                       if_else(grepl('Valence', tmp.events$text), 'ValenceResp',
                                               if_else(grepl('rest', tmp.events$text), 'rest1', 
                                                       if_else(grepl('IntResp', tmp.events$text), 'IntResp','stim'))))

    # unique(tmp.events$screencontent)

    # atorw condition

    tmp.events$Condition<- if_else(grepl('IAPS', tmp.events$text), 'IAPS',
                                   if_else(grepl('Example', tmp.events$text), 'Practice',
                                           if_else(grepl('rest', tmp.events$text), 'Rest', NULL)))
    tmp.events$stim<- if_else(tmp.events$Condition == 'IAPS', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text),
                              if_else(tmp.events$Condition == 'Practice', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text), 'REST'))

    # substitute periods
    tmp.events$stim<- gsub('\\.', '.jpg', tmp.events$stim)

    tmp.events$tNo<- if_else(tmp.events$Condition == 'Practice', (tmp.events$tNo)-6,
                             if_else(tmp.events$Condition == 'Rest',-7, tmp.events$tNo))

    # create trial number < 0 are practice trials
    tmp.events$tNo<- if_else(tmp.events$tNo> -1, tmp.events$tNo+1, tmp.events$tNo) # avoid zeros

    tmp.events1 = subset(tmp.events, grepl('tStart',tmp.events$text))
    # tmp.events1$tNo1<- NULL
    # tmp.events1$tNo2<- NULL

    tmp.events1<- subset(tmp.events1, is.na(tmp.events1$tNo) == FALSE)

    # colnames(tmp.df)
    # colnames(tmp.df)
    # colnames(tmp.events1)
    # colnames(tmp.eyetr)

    tmp.df$screencontent<- NA
    tmp.df$stim<- NA
    tmp.events1$tEnd<- if_else(tmp.events1$tNo == -7, tmp.events1$tStart+120, tmp.events1$tEnd)

    message(sprintf("subsetting eyetracking data"))

    for(e in 1:nrow(tmp.events1)) {

      # Subset the EyeTracking data based on start/end
      tmp.raw.trial = subset(tmp.eyetr, tmp.eyetr$time >= tmp.events1$tStart[e] & tmp.eyetr$time <= tmp.events1$tEnd[e])

      tmp.raw.trial$tNo = tmp.events1$tNo[e]

      tmp.raw.trial$Condition = tmp.events1$Condition[e]
      tmp.raw.trial$screencontent = tmp.events1$screencontent[e]
      tmp.raw.trial$stim = tmp.events1$stim[e]
      # tmp.raw.trial$stim = tmp.events1$[e]
      tmp.raw.trial$ssid = ssid
      tmp.raw.trial$text = tmp.events1$text[e]

      message(sprintf("binding tmp.df"))

      tmp.df= rbind(tmp.raw.trial, tmp.df)
    }
     message(sprintf("done binding"))

    # Arrange the dataframe byu time
    tmp.df<- tmp.df%>%
      arrange(time)

    # Save file for the task with subject name
    name = sprintf("ss%s_GPdata",ssid)
    message(sprintf("saving data"))
    write_csv(tmp.df, paste(name,".csv"))

    # write calibration file
    name2 = sprintf("ss%s_GPdata_cali", ssid)
    write_csv(cali, paste(name2,".csv"))

  }

  message("Processing Completed.")
  tmp.df
}

# run function
tmp_full<- gp.extractor(hdf5FilesPath)

```

Problem files
```{r}
# 355  - did not finish IAPS
# adjust below manually

hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021"

gp.extractor = function(hdf5FilesPath) {

  setwd(hdf5FilesPath)
  #getwd()
  hdfFilesList = list.files(hdf5FilesPath, pattern = "\\.hdf5$")

  if (length(hdfFilesList) == 0){
    hdfFilesList

    return(message('No HDF5 files found in the directory provided.'))
  }
   f = 10
  for (f in 1:length(hdfFilesList)) {

    message(sprintf("Extracting file %i / %i - %s", f, length(hdfFilesList), hdfFilesList[f]))

    #note that some r-studio bug sometimes causes this to fail when runnin from notebook, 
    # in that case run it directly on command line
    tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent')

    tmp.eyetr  = h5read(hdfFilesList[f], '/data_collection/events/eyetracker/BinocularEyeSampleEvent')

    # Get subject id from Events
    ssid = sapply(strsplit(grep('SubjJID', tmp.events$text, value = TRUE), split = ": "), "[", 2)
    date = sapply(strsplit(grep('DATE', tmp.events$text, value = TRUE), split = ": "), "[", 2)
    session = sapply(strsplit(grep('Session:', tmp.events$text, value = TRUE), split = ":"), "[", 2)
    cali<- subset(tmp.events, grepl('Cali', tmp.events$text) == TRUE)

    # Create DF for trials data
    tmp.df = data.frame(matrix(ncol = ncol(tmp.eyetr)))
    names(tmp.df) = names(tmp.eyetr)
    colnames(tmp.df)

    # Prepare Events, keep only start/end messages
    phrases = c('tStart', 'tEnd')
    tmp.events_backup<- tmp.events
    # tmp.events<-  tmp.events_backup
    tmp.events = subset(tmp.events, grepl(paste(phrases, collapse = "|"), tmp.events$text))

    # Create start/end references
    tmp.events$tStart   = NA
    tmp.events$tEnd     = NA

    # Trial number extraction 
    tmp.events$tNo      = NA
    tmp.df$tNo          = NA
    tmp.df$Condition    = NA

    # Space for subject id
    tmp.df$ssid         = NA
    tmp.df$text<-NA

    for (l in 1:nrow(tmp.events)) {

      message(sprintf("Grabing start messages %s", tmp.events$text[l]))

      if ((grepl('tStart', tmp.events$text[l])) == TRUE) {
        tmp.events$tStart[l] = tmp.events$time[l]

        if ((grepl('tEnd', tmp.events$text[l+1])) == TRUE){
          tmp.events$tEnd[l] = tmp.events$time[l+1]
        }

        else {
          message('trial start/end structure not valid')
        }
      }

    }
    message(sprintf("done grabbing messages"))
    # readline(prompt="Press [enter] to continue")

    tmp.events$tNo<- as.numeric(as.character(gsub(".*_","",tmp.events$text)))

     message(sprintf("making screencontent"))

     tmp.eventsbackup<- tmp.events
    tmp.events$screencontent<- if_else(grepl('fixation', tmp.events$text), 'fixation',
                                       if_else(grepl('Valence', tmp.events$text), 'ValenceResp',
                                               if_else(grepl('rest', tmp.events$text), 'rest1', 
                                                       if_else(grepl('IntResp', tmp.events$text), 'IntResp','stim'))))

    # unique(tmp.events$screencontent)

    tmp.events$Condition<- if_else(grepl('IAPS', tmp.events$text), 'IAPS',
                                   if_else(grepl('Example', tmp.events$text), 'Practice',
                                           if_else(grepl('rest', tmp.events$text), 'Rest', NULL)))
    tmp.events$stim<- if_else(tmp.events$Condition == 'IAPS', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text),
                              if_else(tmp.events$Condition == 'Practice', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text), 'REST'))

    # substitute periods
    tmp.events$stim<- gsub('\\.', '.jpg', tmp.events$stim)

    tmp.events$tNo<- if_else(tmp.events$Condition == 'Practice', (tmp.events$tNo)-6,
                             if_else(tmp.events$Condition == 'Rest',-7, tmp.events$tNo))

    # create trial number < 0 are practice trials
    tmp.events$tNo<- if_else(tmp.events$tNo> -1, tmp.events$tNo+1, tmp.events$tNo) # avoid zeros

    tmp.events1 = subset(tmp.events, grepl('tStart',tmp.events$text))
    # tmp.events1$tNo1<- NULL
    # tmp.events1$tNo2<- NULL

    tmp.events1<- subset(tmp.events1, is.na(tmp.events1$tNo) == FALSE)

    # colnames(tmp.df)
    # colnames(tmp.df)
    # colnames(tmp.events1)
    # colnames(tmp.eyetr)

    tmp.df$screencontent<- NA
    tmp.df$stim<- NA
    tmp.events1$tEnd<- if_else(tmp.events1$tNo == -7, tmp.events1$tStart+120, tmp.events1$tEnd)

    message(sprintf("subsetting eyetracking data"))

    for(e in 1:nrow(tmp.events1)) {

      # Subset the EyeTracking data based on start/end
      tmp.raw.trial = subset(tmp.eyetr, tmp.eyetr$time >= tmp.events1$tStart[e] & tmp.eyetr$time <= tmp.events1$tEnd[e])

      tmp.raw.trial$tNo = tmp.events1$tNo[e]

      tmp.raw.trial$Condition = tmp.events1$Condition[e]
      tmp.raw.trial$screencontent = tmp.events1$screencontent[e]
      tmp.raw.trial$stim = tmp.events1$stim[e]
      # tmp.raw.trial$stim = tmp.events1$[e]
      tmp.raw.trial$ssid = ssid
      tmp.raw.trial$text = tmp.events1$text[e]

      message(sprintf("binding tmp.df"))

      tmp.df= rbind(tmp.raw.trial, tmp.df)
    }
     message(sprintf("done binding"))

    # Arrange the dataframe byu time
    tmp.df<- tmp.df%>%
      arrange(time)

    # Save file for the task with subject name
    name = sprintf("ss%s_GPdata",ssid)
    message(sprintf("saving data"))
    write_csv(tmp.df, paste(name,".csv"))

    # write calibration file
    name2 = sprintf("ss%s_GPdata_cali", ssid)
    write_csv(cali, paste(name2,".csv"))

  }

  message("Processing Completed.")
  tmp.df
}

unique(tmp.df$tNo)

```

Now cleaning gaze data and prepare data for ledalab and artifact

```{r, cleaning}
# function to read all the csvs into one dataframe

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/Step1_GpExtractor_Output/346-355")

# rm(tmp_full)
read_plus <- function(flnm) {
  data.table::fread(flnm, select = c("session_id","event_id", "time", "left_gaze_x", "left_gaze_y","right_gaze_x", "right_gaze_y","left_pupil_measure1",
                                     "right_pupil_measure1","gsr", "gsrv", 'hr', "hrv", "hrp", "status", "tNo",  "Condition", "screencontent", "stim", "ssid", "text")) %>% 
    mutate(filename = flnm)
}

# read all clean data 
tmp.df2 <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_plus(.))

unique(tmp.df2$ssid)

table(is.na(tmp.df2$ssid))
# tmp.df2$ssid<- substr(tmp.df2$filename, 5,7)
head(tmp.df2)
# check we have all participants
# unique(tmp.df2$ssid)
tmp.df2<- subset(tmp.df2, !is.na(ssid))

```

#####################################################################################
# gp preprocessing funtion, checks for losses, averages gaze, pupil and pixelate
#####################################################################################

```{r, gppreprocessing}
gp_preprocessing = function(tmp.df2) {

  message(sprintf("step1 lft gaze validity"))

  # transform invalid gaze into NA based on validity codes

  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$status != '20', tmp.df2$left_gaze_x, NULL)
  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$status != '22', tmp.df2$left_gaze_x_cor, NULL)
  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$status != '20', tmp.df2$left_gaze_y, NULL)
  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$left_gaze_y_cor, NULL)

  message(sprintf("step2 right gaze validity"))

  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$status != '2', tmp.df2$right_gaze_x, NULL)
  #
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_x_cor, NULL)
  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_y, NULL)
  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_y_cor, NULL)

  # pupil validity

  message(sprintf("step3 pupil validity"))
  tmp.df2$left_pupil_measure1<- if_else(tmp.df2$status != '20', tmp.df2$left_pupil_measure1, NULL)
  tmp.df2$left_pupil_measure1<- if_else(tmp.df2$status != '22', tmp.df2$left_pupil_measure1, NULL)

  tmp.df2$right_pupil_measure1<- if_else(tmp.df2$status != '2', tmp.df2$right_pupil_measure1, NULL)
  tmp.df2$right_pupil_measure1<- if_else(tmp.df2$status != '22', tmp.df2$right_pupil_measure1, NULL)
  table(is.na(tmp.df2$right_pupil_measure1))

  # check gazepoint out of bounds nd repixelate (1920/2 = 960 by 1200/2 = 600. add half to normalised coordinates from psychopy)

  message(sprintf("step 4 cutting off screen in points and repixelate"))

  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$left_gaze_x_cor >= -960 & tmp.df2$left_gaze_x_cor <= 960, tmp.df2$left_gaze_x_cor, NULL)
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$right_gaze_x_cor >= -960 & tmp.df2$right_gaze_x_cor <= 960, tmp.df2$right_gaze_x_cor, NULL)

  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$left_gaze_y_cor >= -600 & tmp.df2$left_gaze_y_cor <= 600, tmp.df2$left_gaze_y_cor, NULL)
  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$right_gaze_y_cor >= -600 & tmp.df2$right_gaze_y_cor <= 600, tmp.df2$right_gaze_y_cor, NULL)

  tmp.df2$left_gaze_x_cor_pix<- tmp.df2$left_gaze_x_cor+960
  tmp.df2$right_gaze_x_cor_pix<- tmp.df2$right_gaze_x_cor+960

  tmp.df2$left_gaze_y_cor_pix<- tmp.df2$left_gaze_y_cor+600
  tmp.df2$right_gaze_y_cor_pix<- tmp.df2$right_gaze_y_cor+600

  # is left or right an NA

  tmp.df2$left_na<- is.na(tmp.df2$left_gaze_x_cor) 
  tmp.df2$right_na<- is.na(tmp.df2$right_gaze_x_cor)
  tmp.df2$both_na<- if_else(tmp.df2$left_na == TRUE & tmp.df2$right_na == TRUE, TRUE, FALSE)

  message(sprintf("step5 gaze x  means"))

  tmp.df2$gaze_x_cor<-if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_gaze_x_cor,
                              if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_gaze_x_cor,
                                      ((tmp.df2$left_gaze_x_cor + tmp.df2$right_gaze_x_cor)/2)))
  message(sprintf("step6 gaze y means"))

  tmp.df2$gaze_y_cor<-if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_gaze_y_cor,
                              if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_gaze_y_cor,
                                      ((tmp.df2$left_gaze_y_cor + tmp.df2$right_gaze_y_cor)/2)))

  message(sprintf("step6 repixel gaze means"))

  tmp.df2$gaze_x_cor_pix<- tmp.df2$gaze_x_cor + 960
  min(tmp.df2$gaze_x_cor_pix, na.rm = TRUE)

  tmp.df2$gaze_y_cor_pix<- tmp.df2$gaze_y_cor+600
  min(tmp.df2$gaze_y_cor_pix, na.rm = TRUE)

  # clean_pupil

  message(sprintf("cleaning pupil"))

  max(tmp.df2$left_pupil_measure1)

  tmp.df2$pupil<- if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_pupil_measure1,
                          if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_pupil_measure1,
                                  ((tmp.df2$left_pupil_measure1 + tmp.df2$right_pupil_measure1)/2)))

  # tmp.df2$trackloss<- if_else(tmp.df2$status > 0, TRUE, FALSE)
  tmp.df2$trialUnq<- paste(tmp.df2$tNo, paste(tmp.df2$screencontent, paste(tmp.df2$stim)))
  tmp.df2$distance = 630

  # min(tmp.df2$pupil, na.rm = TRUE)
  # max(tmp.df2$pupil, na.rm = TRUE)
  # colnames(tmp.df2)
  tmp.df2<- tmp.df2%>%
    arrange(time)
}

tmp.df2<- gp_preprocessing(tmp.df2)
 colnames(tmp.df2)

min(tmp.df2$pupil, na.rm = TRUE)
max(tmp.df2$gaze_y_cor_pix, na.rm = TRUE)

```

Compute proportions outside the sccreen
repixe

# check gazepoint out of bounds nd repixelate (1920/2 = 960 by 1200/2 = 600. add half to normalised coordinates from psychopy)

  x -960 by 960
  y -600 by 600

```{r}
colnames(X_tmp_df4_full$trackloss)

range(tmp.df2$gaze_x_cor, na.rm = TRUE)

tmp.df2
range(tmp.df2$left_gaze_y, na.rm = TRUE)

range(tmp.df2$left_gaze_y, na.rm = TRUE)
range(tmp.df2$left_gaze_x, na.rm = TRUE)
tmp.df2$x_outside<- ifelse(tmp.df2$left_gaze_x < -960, TRUE,
                           ifelse(tmp.df2$left_gaze_x > 960, TRUE, FALSE))

tmp.df2$y_outside<- ifelse(tmp.df2$right_gaze_y < -600, TRUE,
                           ifelse(tmp.df2$right_gaze_y > 600, TRUE, FALSE))

table(tmp.df2$y_outside)
137/(185406+137)
0.0007383733*100

range(tmp.df, na.rm = TRUE)

```
# rezeroing times by trial, by participants

```{r}
tmp.df3<- tmp.df2

# create start at every screen content
tmp.df3<- tmp.df3%>% 
  arrange(ssid, time, tNo)%>%
  group_by(ssid)%>%
  mutate(firststart = duplicated(trialUnq))

head(tmp.df3)

# make zero-times
tmp.df3$zero<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, NULL)

# fill in the zeros
tmp.df3<- tmp.df3%>%
  group_by(ssid, Condition, tNo)%>%
  # group_by(text)%>%
  fill(zero)

unique(tmp.df3$zero)

# rezero
tmp.df3<-tmp.df3%>%
  arrange(ssid, time, tNo)%>%
  group_by(ssid, tNo)%>%
  mutate(timerezero = time - zero)

min(tmp.df3$timerezero, na.rm = TRUE)
max(tmp.df3$timerezero, na.rm = TRUE)
natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)

# let's check to see if it looks fine
ggplot(subset(tmp.df3, tmp.df3$tNo == -1), aes(timerezero, gsr, colour = as.factor(ssid)))+
  geom_line()

# create a new time rezero where before stim start, time is negative

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, Condition, screencontent)%>%
  mutate(firststartSTIM = duplicated(tNo))

#this will create a time in the stim start which we can use to do the a second rezeroing
tmp.df3$zero_stim<- if_else(tmp.df3$firststartSTIM == FALSE & tmp.df3$screencontent == 'stim', tmp.df3$time, NULL)

    # fill down
tmp.df3<- tmp.df3%>%
      arrange(time)%>%
      group_by(tNo, ssid)%>%
      fill(zero_stim, .direction = c('updown'))

   tmp.df3$timerezero2<- tmp.df3$time-tmp.df3$zero_stim

   # check timerezero2
     range(tmp.df3$timerezero2, na.rm = TRUE)

# time 3 including rest
  # simply includes rest as is

tmp.df3$timerezero3<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$timerezero, tmp.df3$timerezero2)
min(tmp.df3$timerezero3, na.rm = TRUE)

# quick check that everything is fine

ggplot(subset(tmp.df3, tmp.df3$tNo == 27 ) , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
    geom_smooth()+
    # geom_()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tmp.df3$tNo == -4) , aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tmp.df3$tNo == -7) , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

```

triggers

```{r}
unique(tmp.df3$tNo)

natest<- subset(tmp.df3, is.na(tmp.df3$tNo) == TRUE)
tmp.df3<- subset(tmp.df3, is.na(tmp.df3$tNo) == FALSE)

tmp.df3$intercept_time<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, 
                          if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$time,
                                  NULL))

# takes a bit with a group - so don't run
# ggplot(tmp.df3, aes(time, gsr))+
#   geom_line()+
#   geom_vline(aes(xintercept = intercept_time))

unique(tmp.df3$tNo)

tmp.df3$trigger<- as.double(tmp.df3$tNo)

tmp.df3$trigger<- if_else(tmp.df3$firststart == FALSE, tmp.df3$trigger, 
                          if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$trigger, 0))
unique(tmp.df3$trigger)

tmp.df3$trigger <- if_else(tmp.df3$screencontent == 'fixation' &tmp.df3$firststart == FALSE, 100,
                          if_else(tmp.df3$screencontent == 'ValenceResp' & tmp.df3$firststart == FALSE, 101,
                             if_else(tmp.df3$screencontent == 'IntResp' & tmp.df3$firststart == FALSE, 102, tmp.df3$trigger)))

unique(tmp.df3$trigger)

tmp.df3$trigger<- if_else(tmp.df3$firststart == TRUE, 0, tmp.df3$trigger)

unique(tmp.df3$trigger)

```

Calibration analysis

```{r}

# fucntion to read all calibration files into one big dataframe
read_cali <- function(flnm) {
  data.table::fread(flnm) %>%
    mutate(filename = flnm)
}

# now read them
db_cali <-
  list.files(pattern = "*.csv",
             full.names = T) %>%
  map_df(~read_cali(.))

# view the dataset
View(db_cali)
unique(db_cali$filename)

# select needed columns
db_cali$ssid <- substring(db_cali$filename, 5,7)
db_cali$valid_points <- sub(".*_", "", db_cali$text)
db_cali$valid_points <- if_else(grepl('valid', db_cali$text), db_cali$valid_points, NULL)
unique(db_cali$valid_points)

db_cali$avg_error <- sub(".*_", "", db_cali$text)
db_cali$avg_error <- if_else(grepl('AvgError', db_cali$text), db_cali$avg_error, NULL)
db_cali$cali_no <- substring(db_cali$text, 23, 24)
db_cali$cali_no <- if_else(grepl('valid', db_cali$text), db_cali$cali_no, NULL)
db_cali$cali_no<- as.numeric(sub("_", "",db_cali$cali_no))

install.packages("useful")

library(useful)
db_cali<- db_cali%>%
  fill(cali_no)%>%
  fill(valid_points)%>%
  fill(avg_error, .direction = 'up')

#find the duplicate rows (some trigger messages were sent twice)
db_cali<- db_cali %>%
  arrange(ssid)%>%
  group_by(ssid)%>%
  mutate(isduplicate = duplicated(avg_error))

db_cali1 <- subset(db_cali, isduplicate == FALSE)

db_cali1 <- select(db_cali1, c(ssid, cali_no, valid_points, avg_error))

# create a order for the calibration
db_cali1$x = row.names(db_cali1)
db_cali1$cali_order <- ave(db_cali1$x,                 # Create numbering variable
                       db_cali1$ssid,
                       FUN = seq_along)
```

# FUNCTION TO CONVERT PIXELS TO DEGREES OF VISUAL ANGLE

```{r}

pixtoAng<- function(hw,d,r,stimsize){
  #hw - height/width of the monitor(cm) - depending on the axis
  #d - distance of the participant from the monitor (cm)
  #r - vertical/horizontal resolution of the screen (px)
  #stimsize - size of the stimulus on the screen (px)
  deg_per_px = rad2deg(atan2(0.5*hw, d))/(0.5*r)
  visAng <- stimsize * deg_per_px
  return (visAng)
}
#pixtoAng - hw - height/width of the screen in cm - use height for vertical acc/prec, and width for horizontal; d - distance of the participants to the screen (we used an average distance from the logbook); r = height/width of the screen in pixels; stimsize - basically, what you wish to convert from pixels to degrees of visual angle

```

```{r}
library(ggplot2)

db_cali1$avg_error1<- as.numeric(as.character(db_cali1$avg_error))

db_cali1 %>%
  subset(ssid!= 610)%>%
ggplot(aes(x = cali_order, avg_error1))+
  geom_line(aes(group = ssid))

db_cali1 %>%
  subset(ssid!= 610)%>%
ggplot(aes(x = cali_order, cali_no, color = ssid))+
  geom_line(aes(group = ssid))

db_cali1<- db_cali1%>%
  group_by(ssid)%>%
  mutate(cali_no_resc =  cali_no - lag(cali_no))%>%
  mutate(cali_no_resc = if_else(!is.na(cali_no_resc), cali_no_resc, cali_no))

db_cali1 %>%
  subset(ssid!= 610)%>%
ggplot(aes(x = cali_order, cali_no_resc, colour = ssid))+
  geom_line(aes(group = ssid))

#how many calibrations does it take until accepting
library(lmerTest)

cali_models<- list()
db_cali1$ssid<- as.character(db_cali1$ssid)

db_cali1$cali_order <- as.numeric(as.character(db_cali1$cali_order))
db_cali1$cali_order_z<- scale(db_cali1$cali_order, center = TRUE, scale = TRUE)

cali_models$cali_toaccept<- glmer(cali_no_resc ~ (1| ssid),
                                  family = "poisson", data = db_cali1)

summary(cali_models$cali_toaccept)

summary(glm(cali_no_resc ~ cali_order_z, data = db_cali1))

summary(cali_models$cali_toaccept)

db_cali2<- subset(db_cali1, ssid < 500)
mean(subset(db_cali2, cali_order == 1)$cali_no_resc, na.rm = TRUE)
sd(subset(db_cali2, cali_order == 1)$cali_no_resc, na.rm = TRUE)

# AVG cali
mean(db_cali1$cali_no_resc, na.rm = TRUE)

sd(db_cali1$cali_no_resc)

(mean(db_cali1$avg_error1, na.rm = TRUE)) #43.40358
(median(db_cali1$avg_error1, na.rm = TRUE)) #40.13

install.packages("rCAT")
library(rCAT)

# height and widrh of the sreen in pixes and cm
# H = 32.5 cm (108 Pixels) W = (52)  1920Pix by 1200, distance 63 - 65

pixtoAng(52, 65, 1920, 43.40358) # 0.9849095
pixtoAng(52, 65, 1920, 40.13) # 0.9849095

db_cali1$avg_error1_visang<- pixtoAng(52, 65, 1920, db_cali1$avg_error1)

mean(db_cali1$avg_error1_visang)
sd(db_cali1$avg_error1_visang)
range(db_cali1$avg_error1_visang)

db_cali2_id<- db_cali2%>%
  group_by(ssid)%>%
  summarise_at(c("avg_error"), mean, na.rm = TRUE)

db_cali2$Participant<- db_cali2$ssid

db_cali2_id$avg_error<- NULL
db_cali2$Participant<- NULL

db_cali2<- left_join(db_cali2, db_cali2_id)

db_cali2$Participant<- as.character(db_cali2$Participant)
db_cali2%>%
  ggplot(aes(cali_order, avg_error1))+
  geom_line(aes(group = Participant, colour = Participant))+
  stat_summary(aes(geom = "line"))+
  geom_smooth()

```

Trackloss

data = (tmp.df4_sum)

```{r}
# get average loss
mean(tmp.df4_sum$gaze_loss_prop)*100
sd(tmp.df4_sum$gaze_loss_prop)*100
range(accuracy_dataset$gaze_loss_prop)*100

range(accuracy_dataset)*100
range(db_cali1$cali_no_resc)

tmp.df4_sum %>%
  subset(ssid < 500)%>%
  group_by(screencontent)%>%
  summarise_at(c('gaze_loss_prop'), mean, na.rm = TRUE)

# store only neurotypicals

tmp.df4_sum_below500 <- tmp.df4_sum %>%
  subset(ssid < 500)

#plot loss overtime
tmp.df4_sum_below500%>%
  ggplot(aes(tNo, gaze_loss_prop))+
  stat_summary(geom = 'pointrange')+
  geom_vline(xintercept = 26)

#merge calibration information
db_cali2_summ<- db_cali2 %>%
  group_by(ssid)%>%
  mutate(avg_error_agg = mean(avg_error1, na.rm = TRUE), cali_no_resc_agg = mean(cali_no_resc, na.rm = TRUE))

# Save an object to a file
saveRDS(db_cali2_summ, file = "db_cali2_summ.rds")
# Restore the object
accuracy_dataset_below6s<- readRDS(file = "accuracy_dataset_below6s.rds")

View(db_cali2_summ)

tmp.df4_sum_below500$cali_order<- if_else(tmp.df4_sum_below500$tNo < 0,1, if_else(tmp.df4_sum_below500$tNo > 0 & tmp.df4_sum_below500$tNo< 26, 2, 3))

unique(tmp.df4_sum_below500$cali_order)

#merge

tmp.df4_sum_below500$cali_order<- as.character(tmp.df4_sum_below500$cali_order)
tmp.df4_sum_below500 <- left_join(tmp.df4_sum_below500, db_cali2_summ)

max(tmp.df4_sum_below500$ssid)
View(tmp.df4_sum_below500)

# just create one trackloss per trial for all screens
tmp.df4_sum_below500 %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.r = TRUE)%>%
  ggplot(aes(avg_error_agg, gaze_loss_prop))+
  geom_point()+
  geom_smooth(method = 'lm')
  facet_grid(~cali_order)

 unique(tmp.df4_sum_below500$cali_order)

# mixed models

calibration_lmerdata <-  tmp.df4_sum_below500 %>%
  group_by(ssid, tNo )%>%
  summarise_at(c('avg_error_agg','gaze_loss_prop', 'cali_no_resc_agg'), mean, na.rm = TRUE)

nrow(calibration_lmerdata)

loss_lmermodels<- list()

calibration_lmerdata$ot1<- poly(calibration_lmerdata$tNo, degree = 1, raw = FALSE)
calibration_lmerdata$ot2<- poly(calibration_lmerdata$tNo, degree = 2, raw = FALSE)[,2]

View(calibration_lmerdata)
calibration_lmerdata%>%
ggplot(aes(tNo, ot1))+
  geom_line()+
  geom_line(aes(y = ot2))

cor.test(calibration_lmerdata$ot1,calibration_lmerdata$ot2 )

calibration_lmerdata1<- subset(calibration_lmerdata, ssid> 303 & tNo > 0 & tNo < 26)

calibration_lmerdata1$ot1<- poly(calibration_lmerdata1$tNo, degree = 1, raw = FALSE)
calibration_lmerdata1$ot2<- poly(calibration_lmerdata1$tNo, degree = 2, raw = FALSE)[,2]

#
loss_lmermodels$poly1<- glmer(gaze_loss_prop ~ ot1 + ot2 + (1 + ot1 + ot2 | ssid),
                             family = "binomial",
                             data = calibration_lmerdata1)

summary(loss_lmermodels$poly1)

loss_lmermodels$poly2<- glmer(gaze_loss_prop ~ tNo+ (1  | ssid),
                             family = "binomial",
                             data = calibration_lmerdata1)

summary(loss_lmermodels$poly2)

calibration_lmerdata$gaze_loss_prop

(calibration_lmerdata1)%>%
  ggplot(aes(tNo, gaze_loss_prop))+
  #geom_smooth(aes(color = ssid), se = F)
  #stat_summary(geom = 'pointrange')
 # geom_vline(xintercept = 26)+
  geom_line(aes(y = predict(loss_lmermodels$poly1), colour = ssid))

# second part

calibration_lmerdata2<- subset(calibration_lmerdata, ssid> 303 & tNo > 25)

calibration_lmerdata2$ot1<- poly(calibration_lmerdata2$tNo, degree = 1, raw = FALSE)
calibration_lmerdata2$ot2<- poly(calibration_lmerdata2$tNo, degree = 2, raw = FALSE)[,2]

# lmer models on loss

calibration_lmerdata2$avg_error_agg_z<- scale(calibration_lmerdata2$avg_error_agg, center = TRUE, scale = TRUE)

loss_lmermodels$poly2.1<- glmer(gaze_loss_prop ~ (ot1 + ot2)+ avg_error_agg_z+ (1 + ot1 + ot2 | ssid),
                             family = "binomial",
                             data = calibration_lmerdata2)

summary(loss_lmermodels$poly2.1)

loss_lmermodels$poly2.2<- glmer(gaze_loss_prop ~ tNo+ (1  | ssid),
                             family = "binomial",
                             data = calibration_lmerdata2)

summary(loss_lmermodels$poly2.2)

calibration_lmerdata$gaze_loss_prop

(calibration_lmerdata2)%>%
  ggplot(aes(tNo, gaze_loss_prop))+
  geom_smooth(aes(color = ssid), se = F)
  #stat_summary(geom = 'pointrange')
 # geom_vline(xintercept = 26)+
  geom_line(aes(y = predict(loss_lmermodels$poly2.1), colour = ssid))

#combine both
calibration_lmerdata3$part <- subset(calibration_lmerdata, ssid> 303 & tNo > 0)

calibration_lmerdata3$ot1<- poly(calibration_lmerdata3$tNo2, degree = 1, raw = FALSE)
calibration_lmerdata3$ot2<- poly(calibration_lmerdata3$tNo2, degree = 2, raw = FALSE)[,2]

#fir full model excluding pratice

calibration_lmerdata3
calibration_lmerdata3$part<- if_else(calibration_lmerdata3$tNo< 25, -.05, .05)

calibration_lmerdata3$ot1_z<- scale(calibration_lmerdata3$ot1, center = TRUE)

calibration_lmerdata3$ot2_z<- scale(calibration_lmerdata3$ot2, center = TRUE)

loss_lmermodels$poly3.1 <- glmer(gaze_loss_prop ~ (ot1_z + ot2_z) * part +(1 + ot1_z + ot2_z | ssid),
                             family = 'quasi_binomial',
                             data = calibration_lmerdata3)

loss_lmermodels$poly3.1 <- lmer(log1p(gaze_loss_prop+.5) ~ (ot1_z + ot2_z) * part +   (0 + ot1_z + ot2_z  | ssid)+(1 | ssid),
                             REML = FALSE,
                             data = calibration_lmerdata3)

loss_lmermodels$poly3.1 <- lmer(log1p(gaze_loss_prop+.5) ~ (ot1 + ot2) * part +   (0 + ot1 + ot2  | ssid)+(1 | ssid),
                             REML = FALSE,
                             data = calibration_lmerdata3)

summary(loss_lmermodels$poly3.1)

anova(loss_lmermodels$poly3.1)
library(sjstats)
library(sjPlot)

tab_model(loss_lmermodels$poly3.1)

relgrad <- with(loss_lmermodels$poly3.1@optinfo$derivs,solve(Hessian,gradient))
 max(abs(relgrad))
 #[1] 1.152891e-05

emmeans::emmeans(loss_lmermodels$poly3.1, pairwise~ part | ot2_z )

loss_lmermodels$poly3.1_rand1 <- lmer(log1p(gaze_loss_prop+.5) ~(1 | ssid),
                             REML = FALSE,
                             data = calibration_lmerdata3)

summary(loss_lmermodels$poly3.1_rand1)

loss_lmermodels$poly3.1_rand2 <- lmer(log1p(gaze_loss_prop+.5) ~( | ssid),
                             REML = FALSE,
                             data = calibration_lmerdata3)

s

# check ID

library(psych)
library(sjstats)
library(psycho)
psycho::analyze(loss_lmermodels$poly3.1)
psych
library(MuMIn)
r.squaredGLMM(loss_lmermodels$poly3.1)
r.squaredGLMM(loss_lmermodels$poly3.2)
#what if we incorporate calibration values

calibration_lmerdata3$avg_error_agg_z <- scale(calibration_lmerdata3$avg_error_agg, center = TRUE, scale = TRUE)

3$avg_error_agg_z <- scale(calibration_lmerdata3$avg_error_agg, center = TRUE, scale = TRUE)

unique(calibration_lmerdata3$ssid)
loss_lmermodels$poly3.2 <- lmer(log1p(gaze_loss_prop+.5) ~ (ot1_z + ot2_z) * part + avg_error_agg_z +   (0 + ot1_z + ot2_z  | ssid)+(1 | ssid),
                             REML = FALSE,
                             data = calibration_lmerdata3)

summary(loss_lmermodels$poly3.2)

anova(loss_lmermodels$poly3.2, loss_lmermodels$poly3.1)

calibration_lmerdata3$tNo2<- if_else(as.double(calibration_lmerdata3$tNo)< 26, as.double(calibration_lmerdata3$tNo), calibration_lmerdata3$tNo-25)

(calibration_lmerdata3)%>%
  ggplot(aes(tNo2, gaze_loss_prop))+
  #geom_smooth(aes(color = ssid), se = F)
  #stat_summary(geom = 'pointrange')
 # geom_vline(xintercept = 26)+
  geom_line(aes(y = predict(loss_lmermodels$poly3.1), colour = ssid))+
    facet_grid(~part)

(calibration_lmerdata3)%>%
  ggplot(aes(tNo2, gaze_loss_prop))+
  geom_line(aes(group = ssid,color = ssid))+
 # geom_smooth(aes(color = ssid), se = F)+
    facet_grid(~part)

# Save an object to a file
saveRDS(calibration_lmerdata3, file = "calibration_lmerdata3.rds")
# Restore the object
readRDS(file = "my_data.rds")

# is calibraton related to loss acc etc
calibration_lmerdata3$avg_error_agg_z<- as.factor(as.character(calibration_lmerdata3$part))
 %>%
  group_by(ssid, part)%>%
  summarise_at(c(avg_error1_visang))

calibration_lmerdata3$avg_error_agg_z+5

tmp.df4_sum_below500_1.2<- tmp.df4_sum_below500 %>%
   subset(cali_order!= 1)%>%
  group_by(ssid, cali_order )%>%
  summarise_at(c('avg_error1','gaze_loss_prop', 'cali_no_resc_agg'), mean, na.rm = TRUE)

 nrow(tmp.df4_sum_below500_1.2)

 #avg error
cor.test(subset(tmp.df4_sum_below500_1.2, cali_order == 2)$avg_error1, subset(tmp.df4_sum_below500_1.2, cali_order == 2)$gaze_loss_prop)

cor.test(subset(tmp.df4_sum_below500_1.2, cali_order == 3)$avg_error1, subset(tmp.df4_sum_below500_1.2, cali_order == 3)$gaze_loss_prop)

cor.test(subset(tmp.df4_sum_below500_1.2, cali_order == 2)$cali_no_resc_agg, subset(tmp.df4_sum_below500_1.2, cali_order == 2)$gaze_loss_prop)

cor.test(subset(tmp.df4_sum_below500_1.2, cali_order == 3)$cali_no_resc_agg, subset(tmp.df4_sum_below500_1.2, cali_order == 3)$gaze_loss_prop)

tmp.df4_sum_below500_1.2%>%
ggplot(aes(cali_no_resc_agg, gaze_loss_prop))+
  geom_point()+
geom_smooth(method = 'lm', se = F)+
  facet_grid(~cali_order)

   ggplot(aes(avg_error1, gaze_loss_prop))+
   geom_point()+
   facet_grid(~ cali_order)+
   geom_smooth(method = 'lm', se = F)

```

Accuracy

let's workout a few concepts
, speed velocity and aceleration

Velocity =

Velocity is a physical vector quantity; both magnitude and direction are needed to define it. The scalar absolute value (magnitude) of velocity is called speed, being a coherent derived unit whose quantity is measured in the SI (metric system) as metres per second (m/s) or as the SI base unit of (m???s???1). velocity = delta space/ delta time

Speed =  speed  = distance/ time

acceleration is the rate of change of the velocity of an object with respect to time. Accelerations are vector quantities (in that they have magnitude and direction).[1][2] acceleration = delta velocity/ delta time

For example, EyeLink (SR Research Ltd., Ontario, Canada) uses a velocity threshold of 35 deg/s and an acceleration threshold of 8000 deg/s 2 as default values, although these thresholds can be altered manually

Let's compute accuracy

ACCURACY FINAL CALCULATION
STEP 1: Calculate ABSOLUTE horizontal and vertical distance for EACH SAMPLE
STEP 2: Detect sample outliers using the median + 3 * MAD (rely only on the positive side!)
STEP 3: Remove outliers (horizontal outliers should be removed ONLY when calculating horizontal accuracy and the same for vertical outliers)
STEP 4: Mean horizontal and vertical distance (accuracy) for each participant, condition, trials
STEP 5: Calculate overall accuracy using Pitagorean theorem
STEP 6: Remove outliers in the same way as the previous (see step 2)
STEP 7: Mean accuracy per participant, condition and trial

```{r}

accuracy_dataset$y_coord<- 600
accuracy_dataset$x_coord

unique(accuracy_dataset$screencontent)
unique(accuracy_dataset$distance)
#Calculate accuracy again
library(rCAT)
# remember to ignore the last few seconds later

accuracy_dataset$distance
accuracy_dataset$y_coord
accuracy_dataset$x_coord

setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Validation")

accuracy_dataset <- readRDS("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Validation/accuracy_datasetjan16.rds")

# rm(accuracy_datasetjan16)

accuracy_dataset_below6s<- subset(accuracy_dataset, timerezero< 6)

max(accuracy_dataset_below6s$timerezero)
# STEP 1: Calculate ABSOLUTE horizontal and vertical distance for EACH SAMPLE
library(tidyverse)

accuracy_dataset_below6s <- accuracy_dataset_below6s %>%
  arrange(ssid, tNo, time) %>%
  group_by(ssid, tNo) %>%
  mutate(v_accuracy_dif = abs(y_coord - gaze_y_cor_pix)) %>%
  # mutate(v_accuracy = mean(v_accuracy_dif, na.rm = TRUE)) %>%
  mutate(h_accuracy_dif = abs(x_coord - gaze_x_cor_pix )) %>%
  # STEP 2: Detect sample outliers using the median + 3 * MAD (rely only on the positive side!)
  mutate(v_accuracy_dif_median = median(v_accuracy_dif, na.rm = TRUE),
                                        h_accuracy_dif_median = median(h_accuracy_dif, na.rm = TRUE),
                                        v_accuracy_dif_mad = mad(v_accuracy_dif, na.rm = TRUE),
                                        h_accuracy_dif_mad = mad(h_accuracy_dif, na.rm = TRUE))%>%
  mutate(v_accuracy_dif_outlier = if_else(v_accuracy_dif > (v_accuracy_dif_median + (3*v_accuracy_dif_mad)), TRUE, FALSE))%>%
  mutate(h_accuracy_dif_outlier = if_else(h_accuracy_dif > (h_accuracy_dif_median + (3*h_accuracy_dif_mad)), TRUE, FALSE))%>%
  mutate(both_acc_dif_outlier = if_else(v_accuracy_dif_outlier == TRUE & h_accuracy_dif_outlier == TRUE, TRUE, FALSE))%>%
  # create new difference columns where we don't have outliers
  mutate(v_accuracy_dif_nooutl = if_else(v_accuracy_dif_outlier == FALSE, v_accuracy_dif, NULL))%>%
  mutate(h_accuracy_dif_nooutl = if_else(h_accuracy_dif_outlier == FALSE, h_accuracy_dif, NULL))

```

```{r}

# STEP 4: Mean horizontal and vertical distance (accuracy) for each participant, condition, trials
library(rCAT)

accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
  group_by(ssid, tNo) %>%
  mutate(v_accuracy = mean(v_accuracy_dif_nooutl, na.rm = TRUE)) %>%
  mutate(h_accuracy = mean(h_accuracy_dif_nooutl, na.rm = TRUE)) %>%
  mutate(avg_accuracy = (v_accuracy + h_accuracy)/2) %>%
  mutate(v_accuracy_visang = pixtoAng(hw = 32, d = 65, r = 1200, stimsize = v_accuracy)) %>%
  mutate(h_accuracy_visang = pixtoAng(hw = 52, d = 65, r = 1920, stimsize = h_accuracy))

accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
  group_by(ssid, tNo) %>%
  mutate(avg_accuracy_visang = (v_accuracy_visang + h_accuracy_visang)/2)

accuracy_dataset_below6s %>%
  group_by(ssid,tNo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(v_accuracy_visang))+
  geom_histogram(bins = 300)+
  geom_vline(xintercept = 1.4, color = 'red')

```

```{r}

# STEP 5: Calculate overall accuracy using Pitagorean theorem
accuracy_dataset_below6s<- accuracy_dataset_below6s%>%
    arrange(ssid, tNo, time) %>%
  group_by(ssid, tNo) %>%
    mutate(accuracy_dif_pt = sqrt((x_coord - gaze_x_cor_pix)^2+ (x_coord - gaze_x_cor_pix)^2)) %>%
   mutate(accuracy_dif_pt_median = median(accuracy_dif_pt, na.rm = TRUE),accuracy_dif_pt_mad = mad(accuracy_dif_pt, na.rm = TRUE))%>%
  # check outliers
   mutate(accuracy_dif_pt_outlier = if_else(accuracy_dif_pt > (accuracy_dif_pt_median + (3*accuracy_dif_pt_mad)), TRUE, FALSE))%>%
   mutate(accuracy_dif_pt_nooutl = if_else(accuracy_dif_pt_outlier == FALSE, accuracy_dif_pt, NULL))

# mean accuracy
accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
  group_by(ssid, tNo) %>%
  mutate(accuracy_pt = mean(accuracy_dif_pt_nooutl, na.rm = TRUE)) %>%
  mutate(avg_accuracy_visang_pt = pixtoAng(hw = 52, d = 65, r = 1920, stimsize = accuracy_pt))

# report
mean(accuracy_dataset_below6s$avg_accuracy_visang_pt, na.rm = TRUE) #0.770
sd(accuracy_dataset_below6s$avg_accuracy_visang_pt, na.rm = TRUE) #0.70
median(accuracy_dataset_below6s$avg_accuracy_visang_pt, na.rm = TRUE) # 0.6382099

# mean(accuracy_dataset_below6s$avg_accuracy_visang, na.rm = TRUE)#.93
range(accuracy_dataset_below6s$avg_accuracy_visang_pt, na.rm = TRUE) # 0.2335924 13.5357490
)
# vertical
mean(accuracy_dataset_below6s$v_accuracy_visang, na.rm = TRUE) # 1.327067
median(accuracy_dataset_below6s$v_accuracy_visang, na.rm = TRUE) #1.17
sd(accuracy_dataset_below6s$v_accuracy_visang, na.rm = TRUE) # 0.725

range(accuracy_dataset_below6s$v_accuracy_visang, na.rm = TRUE) # 0.276907 9.500563

# horizontal

mean(accuracy_dataset_below6s$h_accuracy_visang, na.rm = TRUE) #0.5448298
median(accuracy_dataset_below6s$h_accuracy_visang, na.rm = TRUE) #.451
sd(accuracy_dataset_below6s$h_accuracy_visang, na.rm = TRUE) # 0.4966967

range(accuracy_dataset_below6s$accuracy_visang, na.rm = TRUE) #0.3019886 6.3431213

acc_plots<- list()

acc_plots$accuracy<- accuracy_dataset_below6s %>%
  group_by(ssid,tNo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(avg_accuracy_visang_pt))+
  geom_histogram(bins = 300)+
  geom_vline(xintercept = 1, color = 'red', linetype = "dashed", size =1.5)+p$graphstyle+
  xlab("Accuracy (deg)")+
  ylab("Density")

acc_plots$accuracy<- acc_plots$accuracy+
  scale_x_continuous(limits = c(0,10), breaks = c(0, 5, 10))

acc_plots$accuracy
saveRDS(accuracy_dataset_below6s, file = "accuracy_dataset_below6sJan16.rds")

```

fixation detection

fixations

# to detect fixations and saccades we should
compute velocity and degre of displacement by participant and trial
compute peak velcoicties as well
compute the median and sd by trial and parocipant

saccades will have occured if at least 3 consecutive samples break 6* sd of the median belocity

```{r}

# unique(fixationscreen_only1$screencontent)

# we need to compute velocity so that we can exclude samples that are likelly saccades
# exclude samples where people clearly where not looking at the center
# compute accuracy and precision

View(accuracy_dataset)

#Original calculation with the squaring

accuracy_dataset_below6s

# velocity
unique(accuracy_dataset_below6s$screencontent)
accuracy_dataset_below6s$distance

# max(accuracy_dataset_below6s$timerezero )

accuracy_dataset_below6s <-

  accuracy_dataset_below6s %>%
  arrange(ssid, tNo, timerezero)%>%
  group_by(ssid, tNo)%>%
  mutate(intdist_pix =  sqrt((gaze_x_cor_pix - lag(gaze_x_cor_pix))^2 +(gaze_y_cor_pix - lag(gaze_y_cor_pix))^2)) %>%
  mutate(inttimediff =  (timerezero)-  lag(timerezero))%>% #If time is calculated this way, it will create a mismatch between inter-sample times and inter-sample distance
  mutate(intdist_visang =  pixtoAng(hw =52, d= 65, r=1920, stimsize= intdist_pix)) %>%
  mutate(int_velocity = intdist_visang/inttimediff)%>%
  mutate(median_velocity = median(int_velocity, na.rm = TRUE,
                                  mad_velocity = mad(int_velocity, na.rm = TRUE)))%>%
  mutate(threshold_velocity = median_velocity+ (6*mad_velocity))%>%
  mutate(peak_velocity = max(int_velocity, na.rm = TRUE))%>%
  mutate(avg_velocity = mean(int_velocity, na.rm = TRUE))

accuracy_dataset_below6s %>%
  group_by(ssid, trialUnq)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(threshold_velocity))+
  geom_histogram(bins = 300)

accuracy_dataset_below6s

accuracy_dataset_below6s %>%
  group_by(ssid, trialUnq)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(peak_velocity, threshold_velocity))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)

```

```{r}

# accuracy_dataset<- accuracy_dataset %>%
#   group_by(ssid, trialUnq)%>%
#   mutate(median_velocity = median(int_velocity, na.rm = TRUE))%>% # I think his needs to be positive(absolute other wise the median will be screwed)
#   mutate(mad_velocity = mad(int_velocity, na.rm = TRUE))%>% 
#   mutate(threshold_velocity = median_velocity + (6* mad_velocity))

# mutate(threshold_velocity = median_velocity + (6* mad_velocity)) %>%

# create a boolean vector for fixationdetcation

accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
  arrange(ssid, tNo, timerezero)%>%
  group_by(ssid, tNo)%>%
  mutate(detection = if_else(abs(int_velocity)> threshold_velocity, "s", "f"))

accuracy_dataset_below6s$detection

# test<-
# accuracy_dataset_below6s %>%
#   subset(ssid == 309 &tNo == 2)%>%
#   mutate(timesaccade = if_else(detection == "s", timerezero, NULL))

accuracy_dataset_below6s %>%
  subset(ssid == 309 &tNo == 2)%>%
  mutate(timesaccade = if_else(detection == "s", timerezero, NULL))%>%
  ggplot(aes(x = timerezero, y = abs(int_velocity)))+
  geom_line()+
  geom_line(aes(y =gaze_y_cor_pix ), color = "red")+
  geom_line(aes(y =gaze_x_cor_pix ), color = "green")+
  geom_line(aes(y = threshold_velocity) , linetype = "dashed", size = 1, color = "gray")+
    ylim(0, 1000)+
  geom_vline(aes(xintercept = timesaccade), alpha  = .3)

  geom_hline(yintercept = -35, linetype = "dashed", size = 1, color = "gray")
unique(accuracy_dataset_below6s$threshold_velocity)

```

```{r}
# now find a pattern "s - f - s" and if e two saccades slit by only a few fixatiojs (up to 3) then remove the the fixations as they are likelly saccades"
# pattern 1 "s-f-s"
table(test2$detection)
accuracy_dataset_below6s$new<-NULL
accuracy_dataset_below6s$new = ifelse(accuracy_dataset_below6s$detection == "f" & 
                            lag(accuracy_dataset_below6s$detection, n = 1) == "s" & 
                                lead(accuracy_dataset_below6s$detection, n = 1) == "s", TRUE, FALSE)

r = c("s", "f", "s")
library(zoo)
test<- which(rollapply(accuracy_dataset_below6s$detection,length(r),identical,r))+0:(length(r)-1)
View(test)
test
# 
# test
test2<- accuracy_dataset_below6s[12:20,]

View(test2)

# pattern 2 "s-f-f-s"
accuracy_dataset_below6s$new1<-NULL

accuracy_dataset_below6s <- accuracy_dataset_below6s %>% 
 mutate(new1 = ifelse(detection == "f" & 
                       lead(detection, n = 1) == "f" &
                            lag(detection, n = 1) == "s" & 
                                lead(detection, n = 2) == "s", TRUE, FALSE))

r1 = c("s", "f", "f", "s")
test3<- which(rollapply(accuracy_dataset_below6s$detection,length(r1),identical,r1))+0:(length(r1)-1)

test3

test4<- accuracy_dataset_below6s[304514 :304530,]
View(test4)

# accuracy_dataset_below6s$new1[accuracy_dataset_below6s$new1 == TRUE

# if_else(accuracy_dataset_below6s$new1 == TRUE, row.names(accuracy_dataset_below6s))

View(test2)
# 
test3<- subset(accuracy_dataset_below6s[290310:290328,])

# # pattern 3 "s-f-f-"f" s"

accuracy_dataset_below6s$new2<-NULL

accuracy_dataset_below6s<- accuracy_dataset_below6s %>% 
 mutate(new2 = ifelse(detection == "f" & 
                        lead(detection, n = 1) == "f" &
                        lead(detection, n = 2) == "f" &
                        lead(detection, n = 3) == "s" &
                            lag(detection, n = 1) == "s", TRUE, FALSE))

# r1 = c("s", "f", "f", "s")

# r2 = c("s", "f", "f", "f", "s")
# 
# test1.1 <- which(rollapply(accuracy_dataset_below6s$detection,length(r1),identical,r1))+0:(length(r1)-1)

accuracy_dataset_below6s[which(accuracy_dataset_below6s$new1 == TRUE)+1, 'new1'] <- TRUE

accuracy_dataset_below6s[which(accuracy_dataset_below6s$new2 == TRUE)+1, 'new2'] <- TRUE
accuracy_dataset_below6s[which(accuracy_dataset_below6s$new2 == TRUE)+1, 'new2'] <- TRUE

# accuracy_dataset_below6s$neW2<- NULL

#mark fixations that need to be changed to saccades
accuracy_dataset_below6s$fixation_tosacade<- (rowSums(accuracy_dataset_below6s[,startsWith(names(accuracy_dataset_below6s),"new")]=="TRUE") >= 1)

table(accuracy_dataset_below6s$fixation_tosacade)

# unique(subset(accuracy_dataset_below6s, fixation_tosacade == TRUE )$new)

# replace spurious fixations when a sacade is taling pplace

accuracy_dataset_below6s<- accuracy_dataset_below6s%>%
  mutate(detection1 = if_else(fixation_tosacade == TRUE, "s", detection))

# accuracy_dataset_below6s$sac_time <- if_else(accuracy_dataset_below6s$detection1 == "s", accuracy_dataset_below6s$timerezero, NULL)
# accuracy_dataset_below6s$sac_time <- NULL

# delete spurious saccades

# create start of a saccade

accuracy_dataset_below6s$start_sacc<- NULL
accuracy_dataset_below6s$end_sacc<- NULL

# accuracy_dataset_below6s$start_sacc <- if_else(is.na(accuracy_dataset_below6s$sac_time) == FALSE & is.na(lag(accuracy_dataset_below6s$sac_time, n = 1) == TRUE),accuracy_dataset_below6s$sac_time, NULL)

# accuracy_dataset_below6s$end_sacc <- if_else(is.na(accuracy_dataset_below6s$sac_time) == FALSE & is.na(lead(accuracy_dataset_below6s$sac_time, n = 1) == TRUE),accuracy_dataset_below6s$sac_time, NULL)
# 
# max(accuracy_dataset_below6s$sac_time, na.rm = TRUE)

# #get rid os start of old spurios saccades
# accuracy_dataset_below6s$start_sacc <- if_else(accuracy_dataset_below6s$sacc_dur > 0, accuracy_dataset_below6s$start_sacc, NULL)
# accuracy_dataset_below6s$end_sacc <- if_else(accuracy_dataset_below6s$sacc_dur > 0, accuracy_dataset_below6s$end_sacc, NULL)

# accuracy_dataset_below6s <- accuracy_dataset_below6s%>%
#   arrange(ssid, tNo, timerezero)%>%
#   group_by(ssid, tNo)%>%
#   fill(end_sacc, .direction = "up")%>%
#   fill(start_sacc, .direction = "updown")%>%
#   mutate(sacc_dur = end_sacc - start_sacc)%>%
#   mutate(detection_withw_spursacc = if_else(sacc_dur == 0, "f", detection1))
#     
accuracy_dataset_below6s $detection_withw_spursacc<- NULL

accuracy_dataset_below6s %>%
subset(ssid == 309 & tNo == 2)%>%
  ggplot(aes(timerezero, abs(int_velocity)))+
  geom_line()+
  geom_point(aes(y = gaze_y_cor_pix))+
  geom_point(aes(y = gaze_x_cor_pix))+
  geom_line(aes(y = threshold_velocity), size = 1.5)
  # geom_vline(aes(xintercept = start_sacc), color = 'green')
  geom_vline(aes(xintercept = end_sacc), color = 'red')

  # annotate("rect", xmin = start_sacc, xmax = end_sacc)

# delete single sacades
rle(accuracy_dataset_below6s$detection1)

accuracy_dataset_below6s$saccade_less3 <- rle(accuracy_dataset_below6s$detection1)

accuracy_dataset_below6s <- accuracy_dataset_below6s %>%
  group_by(ssid, tNo, detection1, event_order) %>%
  mutate(keepF = if_else(detection1 == 'f' & n() >= 12, TRUE, FALSE)) %>%
  mutate(keepS = if_else(detection1 == 's' & n() >= 3, TRUE, FALSE)) %>%

# create a conter based on saca start

saveRDS(accuracy_dataset_below6s, file = "accuracy_dataset_below6sjan16.rds")

testsacc<- accuracy_dataset_below6s%>%
subset(ssid == 309 & tNo == 2)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

  # geom_vline(aes(xintercept = start_sacc), color = "red", size = 2, alpha = .03) +
  # geom_vline(aes(xintercept = end_sacc), color = "green", linetype = "dotted", alpha = .03) +
  ylim(0,1000)

mean(accuracy_dataset_below6s$end_sacc - accuracy_dataset_below6s$start_sacc, na.rm = TRUE)
min(accuracy_dataset_below6s$end_sacc - accuracy_dataset_below6s$start_sacc, na.rm = TRUE)
max(accuracy_dataset_below6s$end_sacc - accuracy_dataset_below6s$start_sacc, na.rm = TRUE)

accuracy_dataset_below6s %>%
  subset(ssid == 309 & tNo == 2)%>%
  ggplot(aes(timerezero, abs(int_velocity)))+
  geom_line()+
  geom_line(aes(y = intdist_visang_vert))+
  geom_point(aes(y = gaze_y_cor_pix))+
  # geom_point(aes(y = gaze_x_cor_pix))+
  # geom_line(aes(y = threshold_velocity), size = 1.5)+
  # geom_vline(aes(xintercept = sac_time), alpha = .03)+

  geom_vline(aes(xintercept = start_sacc), color = "green", size = 2, alpha = .3)+
  geom_vline(aes(xintercept = end_sacc), color = "red", size = 2, linetype = "dotted", alpha = .3) 
  ylim(0,100)+
  xlim(.6,2)

max(accuracy_dataset_below6s$timerezero3)

min(accuracy_dataset_below6s$timerezero)
```

Timecourse models for accuracy

```{r}

unique(accuracy_dataset_below6s$screencontent)
unique(accuracy_dataset_below6s$tNo)
unique(accuracy_dataset_below6s$ssid)

fixationscreen_only2<- accuracy_dataset_below6s%>%
  group_by(ssid, tNo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

fixationscreen_only2$ssid<- as.numeric(as.character(fixationscreen_only2$ssid))

# fixationscreen_only2$ssid< 500
# fixationscreen_only2_lmer <- fixationscreen_only2  %>%
#   subset(tNo>0 & as.numeric(ssid, na.rm = TRUE) < 500)

fixationscreen_only2_lmer<- fixationscreen_only2
fixationscreen_only2_lmer$tNo2<- if_else(as.double(fixationscreen_only2_lmer$tNo)< 25, as.double(fixationscreen_only2_lmer$tNo), fixationscreen_only2_lmer$tNo - 24)

unique(fixationscreen_only2_lmer$tNo2)

#polynomial
fixationscreen_only2_lmer$ot1<- poly(fixationscreen_only2_lmer$tNo2, degree = 1, raw =FALSE)[,1]
fixationscreen_only2_lmer$ot2<- poly(fixationscreen_only2_lmer$tNo2, degree = 2, raw =FALSE)[,2]
fixationscreen_only2_lmer$ot1_z<- scale(fixationscreen_only2_lmer$ot1, center = TRUE, scale = TRUE)[,1]
fixationscreen_only2_lmer$ot2_z<- scale(fixationscreen_only2_lmer$ot2, center = TRUE, scale = TRUE)[,1]

fixationscreen_only2_lmer%>%
  ggplot(aes(tNo2, ot1_z))+
  geom_line()+
  geom_line(aes(y = ot2_z))

fixationscreen_only2_lmer$block<- if_else(fixationscreen_only2_lmer$tNo< 25, -.5, +.5)

fixationscreen_only2_lmer$subject<- as.factor(as.character(fixationscreen_only2_lmer$ssid))                                          
# models

accurcay_models$acc_1<- lmer(avg_accuracy_visang_pt ~ (ot1_z + ot2_z) * block+
                              (0+ ot1_z+ot2_z)+ (1 | subject), REML = FALSE,
                             data = fixationscreen_only2_lmer)

summary(accurcay_models$acc_1)

anova(accurcay_models$acc_1)

```
Fixed effects:
               Estimate  Std. Error          df t value Pr(>|t|)   
ot1_z          0.044002    0.013721 2064.033249   3.207  0.00136 **
ot2_z         -0.001381    0.013899 2064.058090  -0.099  0.92087   
block          0.068205    0.027205 2064.999334   2.507  0.01225 * 
ot1_z:block    0.034924    0.027445 2064.297130   1.273  0.20333   
ot2_z:block    0.036084    0.027793 2064.388596   1.298  0.19432   
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
            ot1_z  ot2_z  block  ot1_z:
ot2_z        0.054                     
block       -0.078 -0.090              
ot1_z:block -0.123 -0.162  0.029       
ot2_z:block -0.162 -0.194  0.028  0.054

```{r}

unique(fixationscreen_only2_lmer$ssid)

plot(accurcay_models$acc_1)
qqnorm(resid(accurcay_models$acc_1)) 
qqline(resid(accurcay_models$acc_1))

fixationscreen_only2_lmer$subject<- as.factor(as.character(fixationscreen_only2_lmer$ssid))

accurcay_models$acc_1_notstand <- lmer(accuracy_visang ~ (ot1_z + ot2_z) * block+
                              (0+ ot1_z+ot2_z)+ (1 | subject), REML = FALSE,
                             data = fixationscreen_only2_lmer)

summary(accurcay_models$acc_1_notstand)
# uniq

(fixationscreen_only2_lmer) %>%
  ggplot(aes(tNo2, accuracy_visang))+
  # geom_smooth(aes(color = ssid), se = F)
 # geom_vline(xintercept = 26)+
  geom_line(aes(y = predict(accurcay_models$acc_1, fixationscreen_only2_lmer), colour = subject))+
  facet_grid(~block)

```

```{r}

# horizontal
accurcay_models$acc_1_h <- lmer(h_accuracy_visang ~ (ot1_z + ot2_z) * block+
                              (0+ ot1_z+ot2_z)+ 
                                (1 | ssid), REML = FALSE,
                             data = fixationscreen_only2_lmer)

plot(accurcay_models$acc_1_h)
qqnorm(resid(accurcay_models$acc_1_h))
qqline(resid(accurcay_models$acc_1_h))

summary(accurcay_models$acc_1_h)

```
Linear mixed model fit by maximum likelihood . t-tests use Satterthwaite's method ['lmerModLmerTest']
Formula: h_accuracy_visang ~ (ot1_z + ot2_z) * block + (0 + ot1_z + ot2_z) +      (1 | ssid)
   Data: fixationscreen_only2_lmer

     AIC      BIC   logLik deviance df.resid 
  2686.4   2726.0  -1336.2   2672.4     2100

Scaled residuals: 
    Min      1Q  Median      3Q     Max 
-2.2019 -0.2687 -0.0533  0.1650 19.9560

Random effects:
 Groups   Name        Variance Std.Dev.
 ssid     (Intercept) 0.3487   0.5905  
 Residual             0.1899   0.4357  
Number of obs: 2107, groups:  ssid, 43

Fixed effects:
                Estimate   Std. Error           df t value Pr(>|t|)   
ot1_z          0.0311142    0.0097019 2064.0332461   3.207  0.00136 **
ot2_z         -0.0009764    0.0098278 2064.0580865  -0.099  0.92087   
block          0.0482285    0.0192370 2064.9993309   2.507  0.01225 * 
ot1_z:block    0.0246953    0.0194067 2064.2971262   1.273  0.20333   
ot2_z:block    0.0255152    0.0196523 2064.3885924   1.298  0.19432   
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
            ot1_z  ot2_z  block  ot1_z:
ot2_z        0.054                     
block       -0.078 -0.090              
ot1_z:block -0.123 -0.162  0.029       
ot2_z:block -0.162 -0.194  0.028  0.054

# vertical
```{r}
accurcay_models$acc_1_v <- lmer(v_accuracy_visang ~ (ot1_z + ot2_z) * block+
                              (0+ ot1_z+ot2_z)+ 
                                (1 | ssid), REML = FALSE,
                             data = fixationscreen_only2_lmer)

plot(accurcay_models$acc_1_v)
qqnorm(resid(accurcay_models$acc_1_v))
qqline(resid(accurcay_models$acc_1_v))

emmeans::emmeans(accurcay_models$acc_1_v, pairwise ~ block|ot1_z )

summary(accurcay_models$acc_1_v)

(fixationscreen_only2_lmer) %>%
  ggplot(aes(tNo2, v_accuracy_visang))+
  # geom_smooth(aes(color = ssid), se = F)
 # geom_vline(xintercept = 26)+
  geom_line(aes(y = predict(accurcay_models$acc_1_v, fixationscreen_only2_lmer), colour = subject))+
  facet_grid(~block)

```

Linear mixed model fit by maximum likelihood . t-tests use Satterthwaite's method ['lmerModLmerTest']
Formula: v_accuracy_visang ~ (ot1_z + ot2_z) * block + (0 + ot1_z + ot2_z) +      (1 | ssid)
   Data: fixationscreen_only2_lmer

     AIC      BIC   logLik deviance df.resid 
  2795.3   2834.9  -1390.6   2781.3     2100

Scaled residuals: 
    Min      1Q  Median      3Q     Max 
-4.1827 -0.4861 -0.0329  0.4371 16.6153

Random effects:
 Groups   Name        Variance Std.Dev.
 ssid     (Intercept) 2.0756   1.4407  
 Residual             0.1929   0.4392  
Number of obs: 2107, groups:  ssid, 43

Fixed effects:
               Estimate  Std. Error          df t value Pr(>|t|)   
ot1_z          0.001718    0.009779 2064.007298   0.176  0.86056   
ot2_z          0.002415    0.009906 2064.011559   0.244  0.80743   
block          0.062299    0.019392 2064.177075   3.213  0.00134 **
ot1_z:block    0.054673    0.019561 2064.052790   2.795  0.00524 **
ot2_z:block    0.013280    0.019809 2064.068659   0.670  0.50267   
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Correlation of Fixed Effects:
            ot1_z  ot2_z  block  ot1_z:
ot2_z        0.054                     
block       -0.078 -0.090              
ot1_z:block -0.123 -0.162  0.029       
ot2_z:block -0.162 -0.194  0.028  0.054

$emmeans
ot1_z = -0.00209:
 block  emmean      SE   df lower.CL upper.CL
  -0.5 -0.0311 0.00971 2069  -0.0501  -0.0121
   0.5  0.0311 0.00971 2069   0.0121   0.0502

Degrees-of-freedom method: kenward-roger 
Confidence level used: 0.95

$contrasts
ot1_z = -0.00209:
 contrast   estimate     SE   df t.ratio p.value
 -0.5 - 0.5  -0.0622 0.0194 2069 -3.205  0.0014

Degrees-of-freedom method: kenward-roger

```{r}

# 
# 
# mean(fixationscreen_only2_lmer$accuracy_visang, na.rm = TRUE)
# 
# median(fixationscreen_only2_lmer$accuracy_visang, na.rm = TRUE)
# 
# sd(fixationscreen_only2_lmer$accuracy_visang, na.rm = TRUE)
# min(fixationscreen_only2_lmer$accuracy_visang, na.rm = TRUE)
# max(fixationscreen_only2_lmer$accuracy_visang, na.rm = TRUE)
# 
# 
# 
# mean(fixationscreen_only2_lmer$v_accuracy_visang, na.rm = TRUE)
# 
# median(fixationscreen_only2_lmer$v_accuracy_visang, na.rm = TRUE)
# 
# sd(fixationscreen_only2_lmer$v_accuracy_visang, na.rm = TRUE)
# min(fixationscreen_only2_lmer$v_accuracy_visang, na.rm = TRUE)
# max(fixationscreen_only2_lmer$v_accuracy_visang, na.rm = TRUE)
# 
# 
# mean(fixationscreen_only2_lmer$h_accuracy_visang, na.rm = TRUE)
# 
# median(fixationscreen_only2_lmer$h_accuracy_visang, na.rm = TRUE)
# 
# sd(fixationscreen_only2_lmer$h_accuracy_visang, na.rm = TRUE)
# min(fixationscreen_only2_lmer$h_accuracy_visang, na.rm = TRUE)
# max(fixationscreen_only2_lmer$h_accuracy_visang, na.rm = TRUE)

# Save an object to a file
saveRDS(fixationscreen_only2_lmer, file = "fixationscreen_only2_lmer.rds")
# Restore the object
readRDS(file = "my_data.rds")

fixationscreen_only2_lmer

 tmp.df4_sum_below500 %>%
   subset(cali_order!= 1)%>%
  group_by(ssid, cali_order )%>%
  summarise_at(c('avg_error1','gaze_loss_prop', 'cali_no_resc_agg'), mean, na.rm = TRUE)%>%
   ggplot(aes(avg_error1, gaze_loss_prop))+
   geom_point()+
   facet_grid(~ cali_order)+
   geom_smooth(method = 'lm', se = F)

 tmp.df4_sum_full_stim_gp_leda_beh_self_biopac %>%
   group_by(ssid, screencontent)%>%
   summarise_if(is.numeric, mean, na.rm = TRUE)%>%
   ggplot(aes(Global.Mean, BIO_Global.Mean))+
   geom_point()+
   geom_smooth(method = 'lm', se = F)+ facet_grid(~screencontent)

```

Precision
fixationscreen_only3
model_time_prec

start by finishing fixation

```{r eval=FALSE, include=FALSE}

table(accuracy_dataset_below6s$detection_withw_spursacc)
saveRDS(accuracy_dataset_below6s, file = "accuracy_dataset_below6sjan16.rds")

# not yet
accuracy_dataset_below6s <- accuracy_dataset_below6s %>%
  arrange(ssid, tNo, timerezero)%>%
  mutate(gaze_x_cor_pix_forpreci = if_else(detection1 == "f", gaze_x_cor_pix, NULL))%>%
  mutate(gaze_y_cor_pix_forpreci = if_else(detection1 == "f", gaze_y_cor_pix, NULL))
  # mutate(test = if_else(detection1 == "s", timerezero, NULL))
  # mutate(test2 = if_else(detection_withw_spursacc == "s", timerezero, NULL))

# we need to create a counter for the events so that each fix sacc or loss has a duration

# accuracy_dataset_below6s$test <- duplicated(accuracy_dataset_below6s$detection1)
# accuracy_dataset_below6s$test2 <- accuracy_dataset_below6s$detection1

library(data.table)

accuracy_dataset_below6s<-
accuracy_dataset_below6s %>%
  arrange(ssid, tNo, timerezero)%>%
  group_by(ssid, tNo)%>%
  mutate(event_order = rleid(detection1))%>%
  ungroup()%>%
  group_by(ssid, tNo, detection1, event_order)%>%
  mutate(duplicated_event = !duplicated(event_order))%>%
  ungroup()%>%
  group_by(ssid, tNo)%>%

  mutate(duplicated_event2 = duplicated(event_order))
View(accuracy_dataset_below6s)

# mutate(start = if_else(duplicated_event == TRUE, timerezero, NULL))%>%
#   # fill(start, .direction = "down") %>%
#   mutate(end = if_else(duplicated_event2 == TRUE & lead(duplicated_event2, n=1) == FALSE, timerezero, 
#                if_else(duplicated_event2 == FALSE & lead(duplicated_event2, n=1) == FALSE, start + 0.005, NULL)))%>%
#   ungroup() %>%
#   group_by(ssid, tNo, detection1, event_order) %>%
#   # mutate(end = if_else(duplicated_event == TRUE, timerezero, NULL))%>%
#   fill(start, .direction = "down")%>%
#   fill(end, .direction = "up")%>%
#   mutate(duration = end - start)

# arrangind the ds in order
accuracy_dataset_below6s <- accuracy_dataset_below6s %>%
   arrange(ssid, tNo, timerezero)

accuracy_dataset_below6s$start<- if_else(accuracy_dataset_below6s$duplicated_event == TRUE, accuracy_dataset_below6s$timerezero, NULL)
unique(accuracy_dataset_below6s$start)
table(is.na(accuracy_dataset_below6s$start))

# create end
accuracy_dataset_below6s$end <- 
  if_else(accuracy_dataset_below6s$duplicated_event2 == TRUE & rownames(accuracy_dataset_below6s) == nrow(accuracy_dataset_below6s), accuracy_dataset_below6s$timerezero, 
  if_else(accuracy_dataset_below6s$duplicated_event2 == FALSE & rownames(accuracy_dataset_below6s) == nrow(accuracy_dataset_below6s), accuracy_dataset_below6s$start + 0.005,
  if_else(accuracy_dataset_below6s$duplicated_event2 == TRUE & lead(accuracy_dataset_below6s$duplicated_event2, n = 1) == FALSE, accuracy_dataset_below6s$timerezero,
  if_else(accuracy_dataset_below6s$duplicated_event2 == FALSE & lead(accuracy_dataset_below6s$duplicated_event2, n=1) == FALSE, accuracy_dataset_below6s$start + 0.005, NULL))))

table(is.na(accuracy_dataset_below6s$end))

  # if_else(accuracy_dataset_below6s$duplicated_event2 == TRUE & rownames(accuracy_dataset_below6s) == nrow(accuracy_dataset_below6s), accuracy_dataset_below6s$timerezero, 
  # if_else(accuracy_dataset_below6s$duplicated_event2 == FALSE & rownames(accuracy_dataset_below6s) == nrow(accuracy_dataset_below6s), accuracy_dataset_below6s$start + 0.005, NULL))))

# TEST <- rownames(accuracy_dataset_below6s) == nrow(accuracy_dataset_below6s)
# table(TEST)
# 
# part344 <- subset(accuracy_dataset_below6s, ssid == 344 & tNo == 50 & event_order == 48)
# 
# part344$test <- if_else(rownames(part344) == nrow(part344), TRUE, FALSE)
# 
# part344$test2 <- if_else(part344$duplicated_event2 == TRUE & rownames(part344) == nrow(part344), part344$timerezero, 
#                   if_else(part344$duplicated_event2 == FALSE & rownames(part344) == nrow(part344), part344$start + 0.005, NULL))

table(part344$test)
View(part344)

accuracy_dataset_below6s <- accuracy_dataset_below6s %>%
  arrange(ssid,tNo,timerezero) %>%
  group_by(ssid, tNo, detection1, event_order) %>%
  fill(start, .direction = "down")%>%
  fill(end, .direction = "up")%>%
  mutate(duration = end - start)

unique(accuracy_dataset_below6s$duplicated_event2)

table(is.na(accuracy_dataset_below6s$duration))
table(is.na(accuracy_dataset_below6s$start))
table(is.na(accuracy_dataset_below6s$end))

View(accuracy_dataset_below6s)

max(accuracy_dataset_below6s$duration)
min(accuracy_dataset_below6s$duration)

# natest<- subset(accuracy_dataset_below6s, is.na(duration) == TRUE)
# accuracy_dataset_below6s %>%
#   arrange(ssid, tNo, timerezero)%>%
#   # group_by(ssid, tNo) %>%
#   group_by(ssid, tNo, detection1)%>%
#   fill(end, .direction = "up")

  # mutate(end = if_else(lag(duplicated_event, n = 1) == TRUE, timerezero, NULL))

# accuracy_dataset_below6s%>%
#   ggplot(aes(duration))+
#   geom_histogram(bins = 300)+
#   xlim(0,.01)+
#   facet_grid(~detection1)+
#   geom_vline(xintercept = .005, size = 1, linetype = "dashed", alpha = .5)

# now lets cmpute the average duration of events
saveRDS(accuracy_dataset_below6s, "accuracy_dataset_below6sjan16withevents.rds")

accuracy_dataset_below6s %>%
  group_by(ssid, tNo, detection1)%>%
  summarise_at(c('duration'), mean, na.rm = TRUE)%>%
  ggplot(aes(duration))+
  geom_density(aes(fill = detection1), alpha = .5)
  facet_grid(~detection1)

  table(accuracy_dataset_below6s$detection1 == "f")

  table(is.na(accuracy_dataset_below6s$gaze_x_cor_pix), is.na(accuracy_dataset_below6s$gaze_y_cor_pix))
  unique(accuracy_dataset_below6s$detection1)

  # table(is.na(accuracy_dataset_below6s$detection1))

# eliminate implausbe fixations (< 80ms = 0.08) and saccades( < 12ms = .012)

  saveRDS(  accuracy_dataset_below6s, "  accuracy_dataset_below6sjan16withevents.rds")

accuracy_dataset_below6s<-  readRDS(file = "  accuracy_dataset_below6sjan16withevents.rds")

   accuracy_dataset_below6s$detection2<- if_else(is.na(accuracy_dataset_below6s$detection1) == TRUE,
                                                 "loss",  accuracy_dataset_below6s$detection1)

   table( accuracy_dataset_below6s$detection2)

accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
  group_by(ssid, tNo, detection2, event_order)%>%
    mutate(fix_validity = if_else(detection2 == "f" & duration > .08, TRUE, FALSE))%>%
    mutate(sacc_validity = if_else(detection2 == "s", duration > .012, TRUE,
                                        FALSE))%>%
    mutate(new_dur = if_else(fix_validity == TRUE & detection2 == "f", duration,
                             if_else(sacc_validity == TRUE & detection2 == "s", duration,
                                    if_else(detection2 == "loss", duration,  NULL))))

# nee detectin ignoring small fix or saccades
accuracy_dataset_below6s$detection3<- if_else(accuracy_dataset_below6s$fix_validity == TRUE & accuracy_dataset_below6s$detection2 == "f", accuracy_dataset_below6s$detection2,
                                              if_else(accuracy_dataset_below6s$sacc_validity == TRUE & 
                                                        accuracy_dataset_below6s$detection2 == "s", accuracy_dataset_below6s$detection2, "loss"))

# this shousld result in less fixation and less saccades

table(accuracy_dataset_below6s$detection1)
table(accuracy_dataset_below6s$detection2)

table(accuracy_dataset_below6s$detection3)

# new event 3 that matches the new detection since the old fixations that were deleted will cause the order not to match

accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
  arrange(ssid, tNo, timerezero)%>%
  group_by(ssid, tNo,)%>%
  mutate(event_order_new = rleid(detection3))

unique(accuracy_dataset_below6s$event_order_new)

```

  # ungroup()%>%
  # group_by(ssid, tNo, detection1, event_order)%>%
  # mutate(duplicated_event = !duplicated(event_order))%>%
  # ungroup()%>%
  # group_by(ssid, tNo)%>%

```{r}

# compute amplitute of sacadesaccade_less3
accuracy_dataset_below6s$start

# create a new event order for this new detection

accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
  arrange(ssid, tNo,timerezero)%>%
  group_by(ssid, tNo,detection3, event_order_new)%>%
  mutate(sacc_posstart_x = if_else(detection3 == "s" & start == timerezero, gaze_x_cor_pix, NULL))%>%
 mutate(sacc_posend_x = if_else(detection3 == "s" & end == timerezero, gaze_x_cor_pix, NULL))%>%
    mutate(sacc_posstart_y = if_else(detection3 == "s" & start == timerezero, gaze_y_cor_pix, NULL))%>%
 mutate(sacc_posend_y = if_else(detection3 == "s" & end == timerezero, gaze_y_cor_pix, NULL))

accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
   arrange(ssid, tNo,timerezero)%>%
  group_by(ssid, tNo,detection3, event_order)%>%
 fill(sacc_posstart_x, .direction = "down")%>%
  fill(sacc_posend_x, .direction = "up")%>%
   fill(sacc_posstart_y, .direction = "down")%>%
  fill(sacc_posend_y, .direction = "up")

accuracy_dataset_below6s %>%
  subset(detection3 == "s")%>%
  arrange(ssid, tNo, timerezero)

  saveRDS(accuracy_dataset_below6s, "accuracy_dataset_below6sjan16witheventdur.rds")

# compute saccade amplitude displacement in pitagoean
accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
  arrange(ssid, tNo, timerezero)%>%
  group_by(ssid, tNo, detection3, event_order_new)%>%
  mutate(sac_amp = sqrt((sacc_posstart_x - sacc_posend_x)^2 +(sacc_posstart_y - sacc_posend_y)^2))%>%
  mutate(sac_amp_visang = pixtoAng(hw = 52, d = 65, r = 1920, sac_amp))%>%
  mutate(sac_peak = mean(int_velocity))

#backup
  saveRDS(accuracy_dataset_below6s, "accuracy_dataset_below6sjan16witheventdur.rds")

accuracy_dataset_below6s %>%
  subset(detection3 == "s")%>%
   group_by(ssid, tNo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(sac_amp_visang, sac_peak))+
  geom_point()+
  geom_smooth(aes(group = ssid),method =  'lm', se = F)
  facet_grid(~detection3)

  accuracy_dataset_below6s %>%
  subset(detection3 == "s")%>%
   group_by(tNo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(sac_amp_visang, new_dur))+
  geom_point()+
  geom_smooth(,method =  'lm', se = F)
  facet_grid(~detection3)

accuracy_dataset_below6s$Event<- if_else(accuracy_dataset_below6s$detection2 == "f", "Fixation",
                                         if_else(accuracy_dataset_below6s$detection2 == "s", "Saccade", "Loss"))

acc_plots$parsing<- accuracy_dataset_below6s%>%  
group_by(ssid, tNo,detection2, Event)%>%
    summarise_at(c('new_dur'), max, na.rm = TRUE)%>%
  ggplot(aes(new_dur, fill = Event))+
  geom_histogram(aes(y=..density..),bins = 300, alpha=0.5, 
                position="identity")+
  geom_density(alpha = .2)+
  # geom_vline(xintercept = .1, linetype = "dashed")+
  p$graphstyle+
  xlab("Duration (s)")+
  ylab("Density")+
  scale_color_brewer(palette = "Dark2")+

  # summarise_at(c('Duration (s)')*1000, min, na.rm = TRUE)+
    theme(legend.position = c(0.6, 0.6))

 library(patchwork)

accuracy_dataset_below6s

acc_plots$loss<-  accuracy_dataset_below6s%>%  
group_by(ssid, tNo,detection2, Event)%>%
    summarise_at(c('gaze_loss_prop'), max, na.rm = TRUE)%>%
  ggplot(aes(gaze_loss_prop))+
  geom_histogram(aes(y=..density..),bins = 300, 
                position="identity")+
  # geom_density(alpha = .2)+
  # geom_vline(xintercept = .1, linetype = "dashed")+
  p$graphstyle+
  xlab("Loss")+
  ylab("Density")+
  scale_color_brewer(palette = "Dark2")

acc_plots$loss

acc_plots$loss<- acc_plots$loss+
  scale_x_continuous(limits=c(0,1), breaks = c(0,.5,1))

scale_y_continuous(limits=c(0,40), breaks = c(0,20,40))

acc_plots$loss

  # summarise_at(c('Duration (s)')*1000, min, na.rm = TRUE)+
    theme(legend.position = c(0.6, 0.6))

    library(patchwork)

acc_patch<- (acc_plots$accuracy | acc_plots$precision+theme(axis.title.y = element_blank())) /(acc_plots$loss|acc_plots$parsing+theme(axis.title.y = element_blank()))

acc_patch<- acc_patch+plot_annotation(tag_levels = 'A')
acc_patch

ggsave("acc_patch.tiff", acc_patch, device = "tiff", dpi = 800, height = 7, width = 10)  
#

```

saveRDS(accuracy_dataset_below6s, "accuracy_dataset_below6s.Rds")

```{r}

View(accuracy_dataset_below6s)

accuracy_dataset_below6s$timerezero

#store gazepoints for precision calculations

accuracy_dataset_below6s$gaze_x_cor_pix_for_prec<- if_else(accuracy_dataset_below6s$detection3 == "f", accuracy_dataset_below6s$gaze_x_cor_pix, NULL)

accuracy_dataset_below6s$gaze_y_cor_pix_for_prec<- if_else(accuracy_dataset_below6s$detection3 == "f", accuracy_dataset_below6s$gaze_y_cor_pix, NULL)

# check how parising is happening
 accuracy_dataset_below6s %>%
   subset(ssid == 304 & tNo == 16 )%>%
   ggplot(aes(timerezero, gaze_x_cor_pix_for_prec))+
   geom_line()+
   geom_line(aes(y = gaze_x_cor_pix), color = "green", linetype = "dotted")+
   geom_line(aes(y = int_velocity), color = 'red', alpha = .5)+
   geom_line(aes(y = gaze_y_cor_pix_for_prec), color = "blue")+
    geom_line(aes(y=gaze_y_cor_pix), color = "blue", linetype = "dotted")
   # geom_hline(aes(yintercept = threshold_velocity))+
   geom_vline(aes(xintercept = test))

```

Now compute precision
```{r}
 accuracy_dataset_below6s <- accuracy_dataset_below6s %>%
  arrange(ssid, tNo, timerezero)%>%
  group_by(ssid, tNo) %>%
  mutate(gaze_x_cor_pix_for_prec_lead = lead(gaze_x_cor_pix_for_prec, n = 1)) %>%
  mutate(gaze_x_cor_pix_for_prec_dif = gaze_x_cor_pix_for_prec_lead  - gaze_x_cor_pix_for_prec)%>%
  mutate(gaze_y_cor_pix_for_prec_lead= lead(gaze_y_cor_pix_for_prec, n = 1)) %>%
  mutate(gaze_y_cor_pix_for_prec_dif = gaze_y_cor_pix_for_prec_lead-gaze_y_cor_pix_for_prec) %>%
  mutate(v_precision_pix = sqrt(mean(gaze_y_cor_pix_for_prec_dif ^2, na.rm = TRUE))) %>%
  mutate(h_precision_pix = sqrt(mean(gaze_x_cor_pix_for_prec_dif ^2, na.rm = TRUE))) %>%

  mutate(gaze_cor_pix_euclidean_int_dif = sqrt((gaze_x_cor_pix_for_prec_dif)^2 +(gaze_y_cor_pix_for_prec_dif)^2))%>%
  mutate(precision_eucl_pix = sqrt(mean(gaze_cor_pix_euclidean_int_dif ^2, na.rm = TRUE)))%>%
  mutate(precision_avg_pix = (v_precision_pix + h_precision_pix)/2)%>%

  mutate(sd_h_precision_pix = sd(gaze_x_cor_pix_for_prec, na.rm = TRUE)) %>%
    mutate(sd_v_precision_pix = sd(gaze_y_cor_pix_for_prec, na.rm = TRUE)) %>%
    mutate(sd_precision_avg_pix = (sd_v_precision_pix + sd_h_precision_pix) / 2)

mean(accuracy_dataset_below6s$v_precision_pix, na.rm = TRUE) 
mean(accuracy_dataset_below6s$h_precision_pix, na.rm = TRUE)

mean(accuracy_dataset_below6s$precision_avg_pix, na.rm = TRUE) 
mean(accuracy_dataset_below6s$precision_eucl_pix, na.rm = TRUE)

mean(accuracy_dataset_below6s$sd_h_precision_pix, na.rm = TRUE) 
mean(accuracy_dataset_below6s$sd_v_precision_pix, na.rm = TRUE)

mean(accuracy_dataset_below6s$sd_h_precision_pix, na.rm = TRUE)

accuracy_dataset_below6s%>%
  group_by(ssid, tNo)%>%
  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
  ggplot(aes(precision_eucl_pix))+
  geom_histogram()+
  geom_vline(xintercept = 40)

accuracy_dataset_below6s%>%
  group_by(ssid, tNo)%>%
  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
  ggplot(aes(precision_avg_pix))+
  geom_histogram()+
  geom_vline(xintercept = 40)

accuracy_dataset_below6s%>%
  group_by(ssid, tNo)%>%
  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
  ggplot(aes(sd_precision_avg_pix))+
  geom_histogram()+
  geom_vline(xintercept = 40)

# conversions to degres

accuracy_dataset_below6s$precision_visang<- NULL
 accuracy_dataset_below6s <-  accuracy_dataset_below6s %>%
   arrange(ssid, tNo, timerezero)%>%
  group_by(ssid, tNo) %>%
   mutate(v_precision_visang = pixtoAng(hw = 32.5, d = 65 , r = 1200, v_precision_pix))%>%
   mutate(h_precision_visang = pixtoAng(hw = 52, d = 65 , r = 1920, h_precision_pix))%>% 
    mutate(avg_precision_visang = pixtoAng(hw = 52, d = 65 , r = 1920,precision_avg_pix ))%>%
    mutate(eucl_precision_visang = pixtoAng(hw = 52, d = 65 , r = 1920, precision_eucl_pix))%>%
    mutate(sd_v_precision_visang = pixtoAng(hw = 32.5, d = 65 , r = 1200, sd_v_precision_pix))%>%
     mutate(sd_h_precision_visang = pixtoAng(hw = 52, d = 65 , r = 1920, sd_h_precision_pix))%>%
     mutate(sd_avg_precision_visang = pixtoAng(hw = 32.5, d = 65 , r = 1200, sd_precision_avg_pix))

saveRDS(accuracy_dataset_below6s, file = "accuracy_dataset_below6sjan16eventdurprecis.rds")

#expeted ranges
accuracy_dataset_below6s%>%
  group_by(ssid, tNo)%>%
  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
  ggplot(aes(eucl_precision_visang))+
  geom_histogram()+
  geom_vline(xintercept = .5)

acc_plots$precision<- accuracy_dataset_below6s %>%
  group_by(ssid, tNo)%>%
  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
  ggplot(aes(avg_precision_visang))+
  geom_histogram(aes(y=..density..), 
                position="identity")+
  # geom_histogram()+
  geom_vline(xintercept = .5, linetype = "dashed", color = "red", size = 1.5)+
  p$graphstyle+
  xlab("Precision (deg)")+
  ylab("Density")

acc_plots$precision

accuracy_dataset_below6s%>%
  group_by(ssid, tNo)%>%
  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
  ggplot(aes(sd_avg_precision_visang))+
  geom_histogram()+
  geom_vline(xintercept = .5)

accuracy_dataset_below6s %>%
    subset(detection3 == "f")%>%
  group_by(ssid, tNo)%>%
  mutate(losstest = n())
  summarise_if(is.numeric, mean, na.rm =TRUE)%>%

  ggplot(aes(gaze_loss_prop, new_dur))+
  geom_point()

# mutate(sd_eucl_precision_pix = sqrt())

# sd( (accuracy_dataset_below6s$new_dur  accuracy_dataset_below6s$duration)

  mutate(precision_pix = (h_precision_pix + v_precision_pix)/2) %>%
  mutate(v_precision_visang = pixtoAng(hw = 27.8, d = 62.45, r = 1080, stimsize = v_precision_pix)) %>%
  mutate(h_precision_visang = pixtoAng(hw = 51, d = 62.45, r = 1920, stimsize = h_precision_pix)) %>%
  mutate(precision_visang = (h_precision_visang + v_precision_visang)/2)

```

Precision analyses

```{r}

fixationscreen_only3<-

  View(accuracy_dataset_below6s)

test<- subset(accuracy_dataset_below6s, detection3 == "f")

fixationscreen_only3<- accuracy_dataset_below6s%>%
  subset(detection3 == "f")%>%
  group_by(ssid, tNo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

View(fixationscreen_only3)

unique(fixationscreen_only3$ssid)
fixationscreen_only3$ssid<- as.numeric(as.character(fixationscreen_only3$ssid))

fixationscreen_only3_lmer<- fixationscreen_only3
unique(fixationscreen_only3_lmer$ssid)

fixationscreen_only3_lmer$tNo2<- if_else(as.double(fixationscreen_only3_lmer$tNo)< 25, as.double(fixationscreen_only3_lmer$tNo), fixationscreen_only3_lmer$tNo - 24)

unique(fixationscreen_only3_lmer$tNo2)

#polynomial
fixationscreen_only3_lmer$ot1<- poly(fixationscreen_only3_lmer$tNo2, degree = 1, raw =FALSE)[,1]

# fixationscreen_only3_lmer$ot1[1,]
fixationscreen_only3_lmer$ot2<- poly(fixationscreen_only3_lmer$tNo2, degree = 2, raw =FALSE)[,2]

fixationscreen_only3_lmer$ot1_z<- scale(fixationscreen_only3_lmer$ot1, center = TRUE, scale = TRUE)[,1]
fixationscreen_only3_lmer$ot2_z<- scale(fixationscreen_only3_lmer$ot2, center = TRUE, scale = TRUE)[,1]

fixationscreen_only3_lmer%>%
  ggplot(aes(tNo, ot1_z))+
  geom_point()+
  geom_point(aes(y = ot2_z))

# fixationscreen_only3_lmer$spli_trial<- as.factor(fixationscreen_only3_lmer$spli_trial)
fixationscreen_only3_lmer$block<- if_else(fixationscreen_only3_lmer$tNo <25, -.5, +.5)

fixationscreen_only3_lmer$subject<- as.factor(as.character(fixationscreen_only3_lmer$ssid))
fixationscreen_only3

precision_models<- list()
library(lmerTest)

mean(fixationscreen_only3_lmer$avg_precision_visang, na.rm = TRUE) # 0.2719884
median(fixationscreen_only3_lmer$avg_precision_visang, na.rm = TRUE)# 0.2440743
sd(fixationscreen_only3_lmer$avg_precision_visang, na.rm = TRUE) #0.1080971
range(fixationscreen_only3_lmer$avg_precision_visang, na.rm = TRUE) #0.1065232 0.7233320

# vertical

mean(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE) # 0.3044482
median(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE)# 0.2632572
sd(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE) # 0.1335215
range(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE) #0.1120570 0.9538436

# horizontal

mean(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE) # 0.2484294
median(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE)#  0.2296711
sd(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE) # 0.09180471
range(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE) #0.09097805 0.60289107

fixationscreen_only3_lmer$ssid<- as.factor(as.character(fixationscreen_only3_lmer$ssid))

precision_models$prec_1 <- lmer(avg_precision_visang ~ (ot1_z + ot2_z) * block+
                              (0+ ot1_z+ot2_z)+ (1 | ssid), REML = FALSE,
                             data = fixationscreen_only3_lmer)

summary(precision_models$prec_1)

# fit data
(fixationscreen_only3_lmer) %>%
  ggplot(aes(tNo2, precision_visang))+
  # geom_smooth(aes(color = ssid), se = F)
 # geom_vline(xintercept = 26)+
  geom_line(aes(y = predict(precision_models$prec_1, fixationscreen_only3_lmer), colour = subject))+
  facet_grid(~block)

```

Linear mixed model fit by maximum likelihood . t-tests use Satterthwaite's method [lmerModLmerTest]
Formula: avg_precision_visang ~ (ot1_z + ot2_z) * block + (0 + ot1_z +      ot2_z) + (1 | ssid)
   Data: fixationscreen_only3_lmer

     AIC      BIC   logLik deviance df.resid 
 -6321.0  -6281.4   3167.5  -6335.0     2097

Scaled residuals: 
    Min      1Q  Median      3Q     Max 
-3.9049 -0.5446 -0.0864  0.4553  5.7883

Random effects:
 Groups   Name        Variance Std.Dev.
 ssid     (Intercept) 0.082648 0.28749 
 Residual             0.002479 0.04979 
Number of obs: 2104, groups:  ssid, 43

Fixed effects:
                Estimate   Std. Error           df t value Pr(>|t|)   
ot1_z          0.0007986    0.0011108 2061.0024024   0.719  0.47227   
ot2_z          0.0009260    0.0011245 2061.0040815   0.823  0.41033   
block          0.0065649    0.0022007 2061.0587841   2.983  0.00289 **
ot1_z:block    0.0014579    0.0022219 2061.0173472   0.656  0.51179   
ot2_z:block    0.0023842    0.0022486 2061.0224616   1.060  0.28914

# real data

(fixationscreen_only3_lmer) %>%
  ggplot(aes(tNo2, precision_visang))+
  # geom_line(aes(colour = subject))+
  geom_smooth(aes(color = subject), se = F)+
 # geom_vline(xintercept = 26)+
  #geom_line(aes(y = predict(precision_models$prec_1, fixationscreen_only3_lmer), colour = subject))+
  facet_grid(~spli_trial)

emmeans::emmeans(accurcay_models$prec_1, pairwise ~  block | ot2_z)
```{r}

#vertical precision

mean(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE)
median(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE)
sd(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE)
min(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE)
max(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE)

#horizontal precision

mean(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE)
median(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE)
sd(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE)
min(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE)
max(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE)

# vertical precision

precision_models$v_prec_1 <- lmer(v_precision_visang ~ (ot1_z + ot2_z) * block+
                              (0+ ot1_z+ot2_z)+ (1 | ssid), REML = FALSE,
                             data = fixationscreen_only3_lmer)

plot(precision_models$v_prec_1)
qqnorm(resid(precision_models$v_prec_1))

summary(precision_models$v_prec_1)

```
Linear mixed model fit by maximum likelihood . t-tests use Satterthwaite's method [lmerModLmerTest]
Formula: v_precision_visang ~ (ot1_z + ot2_z) * block + (0 + ot1_z + ot2_z) +      (1 | ssid)
   Data: fixationscreen_only3_lmer

     AIC      BIC   logLik deviance df.resid 
 -5217.6  -5178.1   2615.8  -5231.6     2097

Scaled residuals: 
    Min      1Q  Median      3Q     Max 
-3.8675 -0.4922 -0.0646  0.3834  6.5967

Random effects:
 Groups   Name        Variance Std.Dev.
 ssid     (Intercept) 0.105332 0.32455 
 Residual             0.004213 0.06491 
Number of obs: 2104, groups:  ssid, 43

Fixed effects:
                Estimate   Std. Error           df t value Pr(>|t|)   
ot1_z          0.0007272    0.0014480 2061.0035161   0.502  0.61558   
ot2_z          0.0009723    0.0014659 2061.0057547   0.663  0.50722   
block          0.0076593    0.0028688 2061.0786467   2.670  0.00765 **
ot1_z:block    0.0020506    0.0028965 2061.0234389   0.708  0.47906   
ot2_z:block    0.0031637    0.0029314 2061.0302560   1.079  0.28059   
---
```{r}
# horizontal precision

precision_models$h_prec_1 <- lmer(h_precision_visang ~ (ot1_z + ot2_z) * block+
                              (0+ ot1_z+ot2_z)+ (1 | ssid), REML = FALSE,
                             data = fixationscreen_only3_lmer)

plot(precision_models$h_prec_1)
qqnorm(resid(precision_models$h_prec_1))

summary(precision_models$h_prec_1)

# fit data
(fixationscreen_only3_lmer) %>%
  ggplot(aes(tNo2, h_precision_visang))+
  # geom_smooth(aes(color = ssid), se = F)
 # geom_vline(xintercept = 26)+
  geom_line(aes(y = predict(precision_models$h_prec_1, fixationscreen_only3_lmer), colour = subject))+
  facet_grid(~spli_trial)

# real data

(fixationscreen_only3_lmer) %>%
  ggplot(aes(tNo2, h_precision_visang))+
  # geom_line(aes(colour = subject))+
  geom_smooth(aes(color = subject), se = F)+
 # geom_vline(xintercept = 26)+
  #geom_line(aes(y = predict(precision_models$prec_1, fixationscreen_only3_lmer), colour = subject))+
  facet_grid(~spli_trial)

saveRDS(fixationscreen_only3_lmer, "fixationscreen_only3_lmer_precision.rds")

saveRDS(accuracy_dataset_below6s, "accuracy_dataset_below6sjan16eventdurprecis.rds")
```

Heart rate variability

ALL WE NEED IS bounce

hr variability metrics to use
mean RMSSD

rr interval

```{r}

unique(accuracy_dataset_below6s$ssid)
library(readr)

read_plus_hrv <- function(flnm) {
  data.table::fread(flnm, select = c("ssid", "time", 'hr', "hrv", "hrp", "status", "tNo",  "Condition", "screencontent", "stim")) %>% 
    mutate(filename = flnm)
}

# now read them
library(purrr)
library(data.table)
library(dplyr)

# read all clean data for repixeling

Restperiod <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_plus_hrv(.))

# keep only rest period

Restperiod1 <- subset(Restperiod, tNo == -7)

Restperiod1 %>%
  subset(ssid == 609)%>%
  ggplot(aes(time, hrp))+
  geom_line()

Restperiod1 <- select(Restperiod1, c(ssid, time, hrp))
Restperiod2<- select()
# df_dat <- split(Restperiod1, Restperiod1$ssid)

# Split dataframe by city
split_df <- split(Restperiod1[,3], list(Restperiod1$ssid))
Restperiod1$time

# Write out separate CSV for each city
for (ssid in names(split_df)) {
  # if (ssid == split_df[[ssid]]) {
  # }
    write_csv(split_df[[ssid]], paste0(ssid, "rest_hp.txt"), row.names = FALSE, col.names = FALSE, quote = FALSE)
  }

split_df[["344"]][,3]

lapply(names(SPLIT.DATA), function(nm) 
   write.csv(SPLIT.DATA[[nm]], paste0(nm, ".csv"), row.names = FALSE, quote = FALSE))

View(Restperiod1)

# unique(tmp.df4_full$ssid)
# tmp.df4_full<-  read_csv("_tmp.df4_full.csv")

hr<- subset(tmp.df4_full, is.na(hrp) == FALSE)

# rm(tmp.df4_full)
View(Restperiod)

# exclude 341 hr from biopac

```

Plotting Preferences

```{r}

p<- list()

sf = 1

p$graphstyle <-  theme(#base plot theme

  # axis
  axis.line.y = element_line(colour = "gray40", size = 0.5, lineend=0),
  axis.line.x = element_line(colour = 'gray40', size = 0.5, lineend=0),
  axis.ticks.x = element_line(colour = 'gray40', size = 0.5, lineend=0),
  strip.text.x = element_text(size = 11*(sf+1.5),  colour = "black"),
  strip.text.y = element_text(size = 11*(sf+1.5),  colour = "black"),

  #axis text

  axis.text.x = element_text(size = 16*(sf+.5), family = "sans", colour = "black", hjust =1.2), #angle = 45
  axis.text.y = element_text(size = 16*(sf+.5), family = "sans", colour = "black"),

  # titles
    plot.title = element_text(size = 16*(sf+1.5), hjust = .5),

  axis.title.y=element_text(size = 16*(sf+1), margin=margin(0,5,0,0)),
  axis.title.x=element_text(size = 16*(sf+1), margin=margin(0,5,0,0)),

  #ticks
    #axis.ticks = element_blank(),

  # panel
  panel.border = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_rect(fill="transparent"),

  # legend
  legend.position = "none",
  # legend.direction =,
  text=element_text(size = 16, family = "sans"),

  # strip shades (reco rectagles)
  strip.background = element_blank())

```

```{r}

# 605 and 606 look the same

# gp heart rate
max(Restperiod1$hrp)
gp_heartpulse <-  Restperiod1 %>%
  subset(ssid == 339)%>%
  ggplot(aes(time - min(time), hrp/4740))+
  geom_line()+
    xlim(0,120)+
  theme_classic()+
  ylab("Pulse (AU)")+
  xlab("Time (s)")+
  p$graphstyle+
ggtitle("HP GPB")

```

# biopac heart rate

```{r}
# 120% .004s

rest_ss335_bio<- read.delim("335_IAPS_Physio_v3_rest.txt", skip = 40)

max(rest_ss335_bio$X2.73285)

nrow(rest_ss335_bio)
rest_ss335_bio$time<- seq(1,239725)

rest_ss335_bio$time_ms<- rest_ss335_bio$time/2000

# merge(rest_ss335_bio, as.data.frame(rest_ss335))

rest_ss335_bio%>%
  ggplot(aes(time_ms,X0.116638.1))+
  geom_line()+
    xlim(0,120)+
  theme_classic()

ss335_ecg_bioplot<- rest_ss335_bio%>%
  ggplot(aes(time_ms,X0.116638.1))+
  geom_line()+
    xlim(0,120)+
  theme_classic()+
  ylab("ECG (uv)")+
  xlab("Time (s)")+
  p$graphstyle+
  ggtitle("ECG MP160")

ss335_ecg_bioplot
gp_heartpulse

pulseechpatch<- gp_heartpulse+ss335_ecg_bioplot +plot_annotation(tag_levels = 'A')
pulseechpatch

ggsave("pulseechpatc.tiff", device = "tiff", dpi = 800, width = 12, height = 5)
```

Import parsed hrv from gazepoint

```{r}

library(readxl)
GP_HRVanalysys <- read_excel("GP_HRVanalysys.xlsx")
View(GP_HRVanalysys)

# Import the IBIS and artifact freefreeny

read_plus_ibi <- function(flnm) {
  data.table::fread(flnm) %>% 
    mutate(filename = flnm)
}

# now read
cleanIBI_gp <-
  list.files(pattern = "*.txt", 
             full.names = T) %>% 
  map_df(~read_plus_ibi(.))

cleanIBI_gp<- cleanIBI_gp%>%
  rename(IBI_clean = V1)

cleanIBI_gp$ssid<- substr(cleanIBI_gp$filename, 13,15)

# pointcare plots
cleanIBI_gp%>%
  # subset(ssid == 335)%>%
  group_by(ssid)%>%
  mutate(IBI_clean_z = scale(IBI_clean,center = TRUE)[,1])%>%
  ggplot(aes(IBI_clean_z, lead(IBI_clean_z)+IBI_clean_z))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)
  facet_grid(~ssid)

  # distribution of IBI lenghts
  unique(cleanIBI_gp$ssid)
unique(Restperiod1$ssid)

time<- subset(Restperiod1, is.na(ssid) == FALSE & ssid != 341)

nrow(time)
nrow(cleanIBI_gp)

cleanIBI_gp$time<- Restperiod1$time

cleanIBI_gp %>%
  # subset(ssid == 335)%>%
  group_by(ssid)%>%

  # mutate(IBI_clean_z = scale(IBI_clean,center = TRUE)[,1])%>%
  ggplot(aes(IBI_clean))+
  geom_histogram()

cleanIBI_gp %>%
  # subset(ssid == 335)%>%
  group_by(ssid)%>%
    mutate(time == 1:n())%>%
  subset(ssid == 335)%>%
  # mutate(IBI_clean_z = scale(IBI_clean,center = TRUE)[,1])%>%
  ggplot(aes(time, IBI_clean))+
  geom_point()

```
# data from biopac

```{r}

GP_HRVanalysys$MEANHR
mean(GP_HRVanalysys$RMMSSD, na.rm = TRUE)

# import biopac
BIO_HRVanalysys <- read_excel("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Validation/BIO_HRVanalysys.xlsx")

View(BIO_HRVanalysys)
View(BIO_HRVanalysys)
BIO_HRVanalysys$ssid
GP_HRVanalysys$ssid

GP_HRVanalysys$ssid<- as.character(GP_HRVanalysys$ssid)
BIO_HRVanalysys$ssid<- as.character(BIO_HRVanalysys$ssid)

combined_bio_GP_HRV<- left_join(GP_HRVanalysys, BIO_HRVanalysys, by = "ssid")

View(combined_bio_GP_HRV)
# GP_HRVanalysys$

# r to R
combined_bio_GP_HRV%>%
  subset(ssid!= 608)%>%
ggplot(aes(MEANRR.x, MEANRR.y, color = ssid))+
  geom_point()+
  geom_smooth(method = "lm", se = F)

combined_bio_GP_HRV_no601 <- subset(combined_bio_GP_HRV, ssid != 601)

cor.test(subset(combined_bio_GP_HRV, ssid!= 605)$MEANRR.x, subset(combined_bio_GP_HRV, ssid!= 605)$MEANRR.y, method = "kendal") # 0.9789474 T = 188, p-value < 0.00000000000000022

cor.test(subset(combined_bio_GP_HRV, ssid!= 605 & ssid!= 608)$MEANRR.x, subset(combined_bio_GP_HRV, ssid!= 605 & ssid!= 608)$MEANRR.y, method = "kendal")

# T = 169, p-value = 0.000000000000003775
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#       tau 
# 0.9766082

cor.test(subset(combined_bio_GP_HRV)$MEANRR.x, subset(combined_bio_GP_HRV)$MEANRR.y, method = "kendal")

# T = 199, p-value = 0.000000000002767
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#       tau 
# 0.8952381

```

# rMSSD
```{r}
combined_bio_GP_HRV %>%
  subset(ssid!= 608 & ssid!= 605)%>%
ggplot(aes(SDNN.x, SDNN.y, color = ssid))+
  geom_point()+
  geom_smooth(method = "lm", se = F)

cor.test(subset(combined_bio_GP_HRV, ssid!= 605 & ssid!= 608)$SDNN.x, subset(combined_bio_GP_HRV, ssid!= 605 & ssid!= 608)$SDNN.y, method = "kendal")

# 
# 	Kendall's rank correlation tau
# 
# data:  subset(combined_bio_GP_HRV, ssid != 605 & ssid != 608)$SDNN.x and subset(combined_bio_GP_HRV, ssid != 605 & ssid != 608)$SDNN.y
# T = 148, p-value = 0.000001521
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#       tau 
# 0.7309942

cor.test(subset(combined_bio_GP_HRV)$SDNN.x, subset(combined_bio_GP_HRV)$SDNN.y, method = "kendal")

# data:  subset(combined_bio_GP_HRV)$SDNN.x and subset(combined_bio_GP_HRV)$SDNN.y
# T = 169, p-value = 0.00004489
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#       tau 
# 0.6095238

```

PNN50

```{r}
combined_bio_GP_HRV %>%
  subset(ssid!= 608)%>%
ggplot(aes(pNN50.x, pNN50.y, color = ssid))+
  geom_point()+
  geom_smooth(method = "lm", se = F)

cor.test(subset(combined_bio_GP_HRV, ssid!= 608)$pNN50.x, subset(combined_bio_GP_HRV, ssid!= 608)$pNN50.y, method = "kendal")

```
data:  subset(combined_bio_GP_HRV, ssid != 608)$pNN50.x and subset(combined_bio_GP_HRV, ssid != 608)$pNN50.y
z = 3.7951, p-value = 0.0001476
alternative hypothesis: true tau is not equal to 0
sample estimates:
      tau 
0.6357085

nn50

```{r}

combined_bio_GP_HRV %>%
  # subset(ssid!= 608)%>%
ggplot(aes(NN50.x, NN50.y, color = ssid))+
  geom_point()+
  geom_smooth(method = "lm", se = F)

cor.test(subset(combined_bio_GP_HRV)$NN50.x, subset(combined_bio_GP_HRV)$NN50.y, method = "kendal")

```

RMSSD
```{r}
combined_bio_GP_HRV %>%
  subset( ssid!= 608)%>%
ggplot(aes(RMMSSD.x, RMMSSD.y, color = ssid))+
  geom_point()+
  geom_smooth(method = "lm", se = F)

cor.test(subset(combined_bio_GP_HRV, ssid!= 608)$RMMSSD.x, subset(combined_bio_GP_HRV, ssid!= 608)$RMMSSD.y, method = "kendal")

# Kendall's rank correlation tau
# 
# data:  subset(combined_bio_GP_HRV, ssid != 608)$RMMSSD.x and subset(combined_bio_GP_HRV, ssid != 608)$RMMSSD.y
# T = 153, p-value = 0.00007322
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#       tau 
# 0.6105263

cor.test(subset(combined_bio_GP_HRV)$RMMSSD.x, subset(combined_bio_GP_HRV)$RMMSSD.y, method = "kendal")

# Kendall's rank correlation tau
# 
# data:  subset(combined_bio_GP_HRV)$RMMSSD.x and subset(combined_bio_GP_HRV)$RMMSSD.y
# T = 173, p-value = 0.00001127
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#      tau 
# 0.647619

```

```{r}
# r to R
combined_bio_GP_HRV%>%
ggplot(aes(MEANHR.x, MEANHR.y, color = ssid))+
  geom_point()+
  geom_smooth(method = "lm", se = F)

```
FRequency measures
Of the frequency-domain methods, data related to the amount of low frequency (LF) heartbeats is often used (0.04 to 0.15 Hz) as a measure of sympathetic nervous system activity. Measurements of high-frequency (HF; 0.15 Hz to 0.4 Hz) and very-low-frequency (VLF) are also used

```{r}
# low frequency
combined_bio_GP_HRV%>%
  subset(ssid!= 601)%>%
ggplot(aes(lfperce.x, lfperce.y, color = ssid))+
  geom_point()+
  geom_smooth(method = "lm", se = F)
  # xlim(0,200)

cor.test(subset(combined_bio_GP_HRV, ssid != 601)$lfperce.x, subset(combined_bio_GP_HRV, ssid != 601)$lfperce.y, method = "kendal")

# Kendall's rank correlation tau
# 
# data:  subset(combined_bio_GP_HRV, ssid != 601)$lfperce.x and subset(combined_bio_GP_HRV, ssid != 601)$lfperce.y
# T = 163, p-value = 0.000001342
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#       tau 
# 0.7157895

cor.test(subset(combined_bio_GP_HRV)$lfperce.x, subset(combined_bio_GP_HRV)$lfperce.y, method = "kendal")

# Kendall's rank correlation tau
# 
# data:  subset(combined_bio_GP_HRV)$lfperce.x and subset(combined_bio_GP_HRV)$lfperce.y
# T = 171, p-value = 0.00002292
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#       tau 
# 0.6285714

```

# vlf

```{r}
combined_bio_GP_HRV %>%
    subset(ssid!= 601)%>%
ggplot(aes(vlfperc.x, vlfperc.y, color = ssid))+
  geom_point()+
  geom_smooth(method = "lm", se = F)

cor.test(subset(combined_bio_GP_HRV, ssid != 601)$vlfperc.x, subset(combined_bio_GP_HRV, ssid != 601)$vlfperc.y, method = "kendal")

cor.test(subset(combined_bio_GP_HRV, ssid != 601)$vlfpower.x, subset(combined_bio_GP_HRV, ssid != 601)$vlfpower.y, method = "kendal")
cor.test(subset(combined_bio_GP_HRV, ssid != 601)$lfnu.x, subset(combined_bio_GP_HRV, ssid != 601)$lfnu.y, method = "kendal")

cor.test(subset(combined_bio_GP_HRV, ssid != 601)$pNN50.x, subset(combined_bio_GP_HRV, ssid != 601)$pNN50.y, method = "kendal")

# Kendall's rank correlation tau
# 
# data:  subset(combined_bio_GP_HRV, ssid != 601)$vlfperc.x and subset(combined_bio_GP_HRV, ssid != 601)$vlfperc.y
# T = 163, p-value = 0.000001342
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#       tau 
# 0.7157895

cor.test(subset(combined_bio_GP_HRV)$vlfperc.x, subset(combined_bio_GP_HRV)$vlfperc.y, method = "kendal")

# Kendall's rank correlation tau
# 
# data:  subset(combined_bio_GP_HRV)$vlfperc.x and subset(combined_bio_GP_HRV)$vlfperc.y
# T = 174, p-value = 0.000007786
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#       tau 
# 0.6571429

# hf
combined_bio_GP_HRV%>%
  # subset(ssid!= 601)%>%
ggplot(aes(hfperent.x, hfperent.y, color = ssid))+
  geom_point()+
  geom_smooth(method = "lm", se = F)

cor.test(subset(combined_bio_GP_HRV, ssid != 601)$hfperent.x, subset(combined_bio_GP_HRV, ssid!= 601)$hfperent.y, method = "kendal")
# Kendall's rank correlation tau
# 
# data:  subset(combined_bio_GP_HRV, ssid != 601)$hfperent.x and subset(combined_bio_GP_HRV, ssid != 601)$hfperent.y
# T = 159, p-value = 0.000007745
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#       tau 
# 0.6736842

cor.test(subset(combined_bio_GP_HRV)$hfperent.x, subset(combined_bio_GP_HRV)$hfperent.y, method = "kendal")

# Kendall's rank correlation tau
# 
# data:  subset(combined_bio_GP_HRV)$hfperent.x and subset(combined_bio_GP_HRV)$hfperent.y
# T = 171, p-value = 0.00002292
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#       tau 
# 0.6285714

combined_bio_GP_HRV$group <- if_else(combined_bio_GP_HRV$ssid< 400, "NT", "CLIN")

combined_bio_GP_HRV%>%
  group_by(group)%>%
  ggplot(aes(group, RMMSSD.x))+
  geom_jitter(width = .3)+
  geom_boxplot()

combined_bio_GP_HRV%>%
  group_by(group)%>%
  ggplot(aes(group, RMMSSD.x))+
  geom_jitter(width = .3)+
  geom_boxplot()

combined_bio_GP_HRV%>%
  group_by(group)%>%
  ggplot(aes(group, RMMSSD.y))+
  geom_jitter(width = .3)+
  geom_boxplot()

####

combined_bio_GP_HRV%>%
  group_by(group)%>%
  ggplot(aes(group, MEANRR.x))+
  geom_jitter(width = .3)+
  geom_boxplot()

combined_bio_GP_HRV%>%
  group_by(group)%>%
  ggplot(aes(group, MEANRR.y))+
  geom_jitter(width = .3)+
  geom_boxplot()

# frequency

combined_bio_GP_HRV%>%
  group_by(group)%>%
  ggplot(aes(group, lfperce.x))+
  geom_jitter(width = .3)+
  geom_boxplot()

combined_bio_GP_HRV%>%
  group_by(group)%>%
  ggplot(aes(group, lfperce.y))+
  geom_jitter(width = .3)+
  geom_boxplot()

combined_bio_GP_HRV%>%
  group_by(group)%>%
  ggplot(aes(group, hfperent.x))+
  geom_jitter(width = .3)+
  geom_boxplot()

combined_bio_GP_HRV%>%
  group_by(group)%>%
  ggplot(aes(group, hfperent.y))+
  geom_jitter(width = .3)+
  geom_boxplot()

combined_bio_GP_HRV%>%
    subset(ssid!= 608)%>%
ggplot(aes(hfpower.x, hfpower.y, color = ssid))+
  geom_point()+
  geom_smooth(method = "lm", se = F)

```

HF power

```{r}

combined_bio_GP_HRV%>%
    subset(ssid!= 608)%>%
ggplot(aes(hfpower.x, hfpower.y, color = ssid))+
  geom_point()+
  geom_smooth(method = "lm", se = F)

cor.test(subset(combined_bio_GP_HRV, ssid != 608)$hfpower.x, subset(combined_bio_GP_HRV, ssid!= 608)$hfpower.y, method = "kendal")

```
Kendall's rank correlation tau

data:  subset(combined_bio_GP_HRV, ssid != 601)$hfpower.x and subset(combined_bio_GP_HRV, ssid != 601)$hfpower.y
T = 169, p-value = 0.00000005841
alternative hypothesis: true tau is not equal to 0
sample estimates:
      tau 
0.7789474

LF power

```{r}
combined_bio_GP_HRV%>%
    subset(ssid!= 608 & ssid!= 342)%>%
ggplot(aes(lfpower.x, lfpower.y, color = ssid))+
  geom_point()+
  geom_smooth(method = "lm", se = F)

cor.test(subset(combined_bio_GP_HRV)$hfpower.x, subset(combined_bio_GP_HRV)$hfpower.y, method = "kendal")

cor.test(subset(combined_bio_GP_HRV, ssid !=608& ssid!= 342)$hfpower.x, subset(combined_bio_GP_HRV, ssid !=608& ssid!= 342)$hfpower.y, method = "kendal")

```

# correlations

```{r}

cor.test(GP_HRVanalysys$MEANRR.x,BIO_HRVanalysys$MEANRR.x)

```

```{r}
# IBI data to compare from biopac

read_plus_ibi_bio <- function(flnm) {
  data.table::fread(flnm) %>% 
    mutate(filename = flnm)
}

# now read
cleanIBI_bio <-
  list.files(pattern = "*.txt", 
             full.names = T) %>% 
  map_df(~read_plus_ibi_bio(.))

cleanIBI_bio<- cleanIBI_bio%>%
  rename(IBI_clean = V1)

cleanIBI_bio$ssid<- substr(cleanIBI_bio$filename, 13,15)

# pointcare plots

cleanIBI_gp$IBI_clean_next<- lead(cleanIBI_gp$IBI_clean)

poitcare_gp<- cleanIBI_gp%>%
  # subset(ssid == 335)%>%
  group_by(ssid)%>%
  # mutate(IBI_clean_z = scale(IBI_clean,center = TRUE)[,1])%>%
  ggplot(aes(IBI_clean, IBI_clean_next,  color = ssid))+
  geom_point(alpha = .3)+
  geom_smooth(method = 'lm', se = F)+
  # facet_grid(~ssid)+
  xlab("RR[n] (ms)")+
  ylab("RR[n+1] (ms)")+
    p$graphstyle
  # ggtitle("GP3 Gazepoint")+
  p$graphstyle

poitcare_gp

poitcare_gp <- poitcare_gp +
  scale_y_continuous(limits = c(400, 1600), breaks = c(400, 1000, 1600))+
   scale_x_continuous(limits = c(300, 1600), breaks = c(400, 1000, 1600))

scale_x_continuous(limits = c(500, 1300), breaks = c(500, 900, 1300))

poitcare_gp

```

```{r}

  # cleanIBI_bio$ssid<- a

cleanIBI_bio$IBI_clean_next<- lead(cleanIBI_bio$IBI_clean)
pointcare_bio<-  cleanIBI_bio %>%
    # subset(ssid == 335)%>%
  subset(ssid != 341)%>%
  group_by(ssid)%>%
  # mutate(IBI_clean_z = scale(IBI_clean,center = TRUE)[,1])%>%
  ggplot(aes(IBI_clean, IBI_clean_next,  color = ssid))+
  geom_point(alpha = .3)+
  geom_smooth(method = 'lm', se = F)+
  # facet_grid(~ssid)+
  xlab("RR[n] (ms)")+
  ylab("RR[n+1] (ms)")+
    p$graphstyle
  ggtitle("MP150 BIOPAC")

pointcare_bio<- pointcare_bio+
  scale_y_continuous(limits = c(500, 1300), breaks = c(500, 900, 1300))+
 scale_x_continuous(limits = c(500, 1300), breaks = c(500, 900, 1300))

pointcare<- poitcare_gp+ pointcare_bio+ plot_annotation(tag_levels = 'A')

```

cleanIBI_gp$group <- if_else(cleanIBI_gp$ssid< 400, 1, 2)

  cleanIBI_gp %>%
  # subset(ssid != 341)%>%
  group_by(ssid, group)%>%
  # mutate(IBI_clean_z = scale(IBI_clean,center = TRUE)[,1])%>%
  ggplot(aes(IBI_clean, lead(IBI_clean)+IBI_clean,  color = as.factor(group)))+

  geom_smooth(method = 'lm', se = F)

  facet_grid(~ssid)

```

db_parsed_summarised_fix1.2$tNo2<- if_else(as.double(db_parsed_summarised_fix1.2$tNo)< 25, as.double(db_parsed_summarised_fix1.2$tNo), db_parsed_summarised_fix1.2$tNo - 24)

unique(fixationscreen_only3_lmer$tNo2)

#polynomial
unique(db_parsed_summarised_fix1.2$screencontent)

db_parsed_summarised_fix1.2$ot1<- poly(db_parsed_summarised_fix1.2$tNo2, degree = 1, raw =FALSE)

db_parsed_summarised_fix1.2$ot2<- poly(db_parsed_summarised_fix1.2$tNo2, degree = 2, raw =FALSE)[,2]

db_parsed_summarised_fix1.2$ot1_z<- scale(db_parsed_summarised_fix1.2$ot1, center = TRUE, scale = TRUE)
db_parsed_summarised_fix1.2$ot2_z<- scale(db_parsed_summarised_fix1.2$ot2, center = TRUE, scale = TRUE)

db_parsed_summarised_fix1.2$block<- if_else(db_parsed_summarised_fix1.2$tNo < 25, -.5, +.5)

db_parsed_summarised_fix1.2$subject<- as.factor(as.character(db_parsed_summarised_fix1.2$ssid))

precision_models$prec_stim <- lmer(RMS ~ (ot1_z + ot2_z) * block+
                              (0+ ot1_z+ot2_z)+ (1 | ssid), REML = FALSE,
                             data = subset(db_parsed_summarised_fix1.2,as.numeric(mean_fix_dur) < 3000))

summary(precision_models$prec_stim)

db_parsed_summarised_fix1.2 <- subset(db_parsed_summarised_fix, ssid <500 & tNo> 0)

db_parsed_summarised_fix1.2

 #precision correlation with calibratin accuracy

unique(tmp.df4_sum_below500_1.2$cali_order)
unique(fixationscreen_only2_lmer$tNo)
fixationscreen_only3_lmer$ssid<- as.character(fixationscreen_only3_lmer$subject)

tmp.df4_sum_below500_1.2$ssid<- as.character(tmp.df4_sum_below500_1.2$ssid)

fixationscreen_only3_lmer$cali_order<- as.character(if_else(fixationscreen_only3_lmer$tNo < 24, 2, 3))

tmp.df4_sum_below500_1.2_select<- select(tmp.df4_sum_below500_1.2, c(ssid, cali_order, avg_error1, cali_no_resc_agg))

fixationscreen_only3_lmer<- left_join(fixationscreen_only3_lmer, tmp.df4_sum_below500_1.2_select)

fixationscreen_only3_lmer %>%
  group_by(ssid, cali_order)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(avg_error1, precision_visang))+
  geom_point()+
geom_smooth(method = 'lm', se = F)+
  facet_grid(~cali_order)

fixationscreen_only2_lmer_1.2<- fixationscreen_only2_lmer%>%
  group_by(ssid, cali_order)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

ggplot(aes(avg_error1, precisi))+
  geom_point()+
geom_smooth(method = 'lm', se = F)+
  facet_grid(~cali_order)

cor.test(subset(fixationscreen_only2_lmer_1.2, cali_order == 2)$avg_error1, subset(fixationscreen_only2_lmer_1.2, cali_order == 2)$h_accuracy_visang)

cor.test(subset(fixationscreen_only2_lmer_1.2, cali_order == 3)$avg_error1, subset(fixationscreen_only2_lmer_1.2, cali_order == 3)$h_accuracy_visang)

# Save an object to a file
saveRDS(fixationscreen_only3_lmer, file = "fixationscreen_only3_lmer.rds")
# Restore the object
readRDS(file = "my_data.rds"

```{r}

View(fixationscreen_only1$)

summary(model_time_acc)

fixationscreen_only2_lmer

options(scipen = 999)

accurcay_models<- list()

 #accuracy correlation with calibratin accuracy

unique(tmp.df4_sum_below500_1.2$cali_order)
unique(fixationscreen_only2_lmer$tNo)
fixationscreen_only2_lmer$ssid<- as.character(fixationscreen_only2_lmer$ssid)

tmp.df4_sum_below500_1.2$ssid<- as.character(tmp.df4_sum_below500_1.2$ssid)

fixationscreen_only2_lmer$cali_order<- as.character(if_else(fixationscreen_only2_lmer$tNo < 24, 2, 3))

tmp.df4_sum_below500_1.2_select<- select(tmp.df4_sum_below500_1.2, c(ssid, cali_order, avg_error1, cali_no_resc_agg))

fixationscreen_only2_lmer<- left_join(fixationscreen_only2_lmer, tmp.df4_sum_below500_1.2_select)

fixationscreen_only2_lmer %>%
  group_by(ssid, cali_order)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(avg_error1, v_accuracy_visang))+
  geom_point()+
geom_smooth(method = 'lm', se = F)+
  facet_grid(~cali_order)

fixationscreen_only2_lmer_1.2<- fixationscreen_only2_lmer%>%
  group_by(ssid, cali_order)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

ggplot(aes(avg_error1, precisi))+
  geom_point()+
geom_smooth(method = 'lm', se = F)+
  facet_grid(~cali_order)

cor.test(subset(fixationscreen_only2_lmer_1.2, cali_order == 2)$avg_error1, subset(fixationscreen_only2_lmer_1.2, cali_order == 2)$h_accuracy_visang)

cor.test(subset(fixationscreen_only2_lmer_1.2, cali_order == 3)$avg_error1, subset(fixationscreen_only2_lmer_1.2, cali_order == 3)$h_accuracy_visang)

#neither vertical or horizontal or global reach significance

```

fixationscreen_only2$spli_trial %>%
  ggplot(aes(tNo,accuracy ))+
  geom_point()
  #stat_summary(geom = 'pointrange')+
  geom_vline(xintercept = 24)

#

cor.test(subset(tmp.df4_sum_below500_1.2, cali_order == 2)$cali_no_resc_agg, subset(tmp.df4_sum_below500_1.2, cali_order == 2)$gaze_loss_prop)

cor.test(subset(tmp.df4_sum_below500_1.2, cali_order == 3)$cali_no_resc_agg, subset(tmp.df4_sum_below500_1.2, cali_order == 3)$gaze_loss_prop)

Pupil analysis

```{r}
readRDS(file = "db_full6new_304_up_500less.rds")

db_full4new_stim_pupil$ssid
db_full4new_stim_pupil$subject
View(db_full6new_304_up)

db_full6new_304_up_500less<- subset(db_full6new_304_up, subject< 500 & tNo > 0)

db_full4new_stim_pupil$BIO_Global.Mean

db_full6new_304_up_500less$Bio_Mean_HR_z

unique(db_full6new_304_up_500less$screencontent)

db_full6new_304_up_500less$Bio_Mean_HR_z<- scale(db_full6new_304_up_500less$Bio_Mean_HR, center = TRUE, scale = TRUE)
db_full6new_304_up_500less$BIO_Global.Mean_z<- scale(db_full6new_304_up_500less$BIO_Global.Mean, center = TRUE, scale = TRUE)
db_full6new_304_up_500less$pup_basCor_z<- scale(db_full6new_304_up_500less$pup_basCor, center = TRUE, scale = TRUE)

db_full6new_304_up_500less$hr_interp<- scale(db_full6new_304_up_500less$hr_interp, center = TRUE, scale = TRUE)

# Pupil

```

```
```{r}

summary(lmer(arousal ~  pup_basCor_z + BIO_Global.Mean_z + Bio_Mean_HR_z +ArousalMean+ (1 | stimIAPS) +(1 | ssid), REML = FALSE,
                      data = subset(db_full6new_304_up_500less)))

summary(lmer(pup_basCor_z ~  ArousalMean + (1 | stimIAPS)  +(1 | ssid), REML = FALSE,
                      data = db_full6new_304_up_500less))

cognitivepupil$pup_arous_brigh <- lmer(pup_basCor ~  arousal_c +  BRIGHTNESSc +(1 | stimIAPS)  +(1 | ssid), REML = FALSE,
                      data = db_full6new_304_up_500less)
summary(cognitivepupil$pup_arous_brigh)

MuMIn::r.squaredGLMM(cognitivepupil$pup_arous_brigh)

library(lmerTest)

cognitivepupil$pup_arous_1 <- lmer(pup_basCor ~  arousal_c +( 1| stimIAPS)  +(1 | ssid), REML = FALSE,
                      data = db_full6new_304_up_500less)

library(readr)
library(tidyverse)
cognitivepupil$pup_arous_1bri <- lmer(pup_basCor ~  BRIGHTNESSc +( 1| stimIAPS)  +(1 | ssid), REML = FALSE,
                      data = db_full6new_304_up_500less)

MuMIn::r.squaredGLMM(cognitivepupil$pup_arous_1)
MuMIn::r.squaredGLMM(cognitivepupil$pup_arous_1bri) # 20

db_full6new_304_up_500less$fit_pup_arou_bright<- 
  predict(cognitivepupil$pup_arous_brigh, type = c("response"), terms = "BRIGHTNESSc")
?predict

pupil_plots<- list()

write_csv(db_full6new_304_up_500less, "Pupil_data_db_full6new_304_up_500less.csv")

pupil_plots$brightness<-  db_full6new_304_up_500less %>%
  #subset(!is.na(Alexithymia))%>%
  group_by(ssid,stimIAPS) %>%
  summarise_at(c("arousal_c", "TASc","BRIGHTNESSc", "pup_basCor", "fit_pup_arou_bright"), mean, na.rm = TRUE)%>%
  ggplot(aes(BRIGHTNESSc, pup_basCor, color = ssid))+
  geom_point(alpha = .3)+
  geom_smooth(aes(group = ssid), method = 'lm', se = F)+
  stat_smooth (geom="line", method = 'lm', alpha = .8, size = 1.5, color = "gray30")+
    ylab('Pupilary change (z)')+
  xlab('Brightness (z)')+
  p$graphstyle
    scale_color_brewer(palette = "Dark2")

pupil_plots$brightness<- pupil_plots$brightness+
  scale_y_continuous(limits = c(-12,4), breaks = c(-12,-4, 4))+
  scale_x_continuous(limits = c(-2.5,2), breaks = c(-2.5,-0, 2))

library(dplyr)

pupil_plots$arousalpup<-  db_full6new_304_up_500less %>%
  #subset(!is.na(Alexithymia))%>%
  group_by(ssid,stimIAPS) %>%
  summarise_at(c("arousal", "TASc", "pup_basCor", "fit_pup_arou_bright"), mean, na.rm = TRUE)%>%
  ggplot(aes(pup_basCor, arousal, color = ssid))+
  geom_point(alpha = .3)+
  geom_smooth(aes(group = ssid), method = 'lm', se = F)+
  stat_smooth (geom="line", method = 'lm', alpha = .8, size = 1.5, color = "gray30")+
    ylab('Pupilary change (z)')+
  xlab('Self reported arousal (z)')+
  p$graphstyle
  scale_color_brewer(palette = "Dark2")

pupil_plots$arousalpup

pupil_plots$arousalpup<- pupil_plots$arousalpup+
  scale_y_continuous(limits = c(-10,10), breaks = c(-10,0, 10))+
  scale_x_continuous(limits = c(-12,6), breaks = c(-12,6))

pupil_plots$arousalpup
# Save an object to a file
saveRDS(db_full6new_304_up_500less, file = "db_full6new_304_up_500less.rds")
# Restore the object

library(patchwork)
library(ggplot2)

patchpup<- pupil_plots$arousalpup+ pupil_plots$brightness+theme(axis.title.y = element_blank())
patchpup<- patchpup+plot_annotation(tag_levels = 'A')

ggsave("patchpup.tiff", patchpup, device = 'tiff', width = 10, height = 6, dpi = 800)
```

Quick check Hr pulse

```
```{r}

unique(one$ssid)

one1<- subset(one, ssid == 336)

# pp340 <- subset(tmp.df4_full, tNo = -7 & ssid == 340)

one1 %>%
  ggplot(aes(time - min(time), hrp))+
  geom_line()+
  xlim(0,30)

hrclass<-  kmeans(one1$hrp, 2, nstart = 25)

one1$hrclass<- hrclass$cluster

one1$time2hr<- if_else(one1$hrclass == 2, one1$time - min(one1$time), NULL)

stats::fil
one1 %>%
  ggplot(aes(time-min(time), stats::filter(hrp, 1)))+
  geom_line()+
  geom_vline(aes(xintercept = time2hr), alpha = .05, color = "red")+
  xlim(50, 80)+ theme_classic()

```

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

@@
 
-Compute proportions outside the sccreen
-repixe
+Compute proportions outside the screen
 
@@
 
-```{r}
-colnames(X_tmp_df4_full$trackloss)
-
+```{r eval=FALSE, include=FALSE}
 range(tmp.df2$gaze_x_cor, na.rm = TRUE)
@@
 range(tmp.df, na.rm = TRUE)
-
-```
+tmp.df2$y_outside<-NULL
+
+```
+
 # rezeroing times by trial, by participants
@@
 min(tmp.df3$timerezero, na.rm = TRUE)
-max(tmp.df3$timerezero, na.rm = TRUE)
+max(tmp.df3$timerezero, na.rm = TRUE) # max shoudl be around 120s for 2 mnutes
 natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)
@@
 
-Calibration analysis
+writing for ledalab
 
@@
 
-# fucntion to read all calibration files into one big dataframe
-read_cali <- function(flnm) {
+tmp.df3<- tmp.df3%>%
+  arrange(ssid, tNo,time)
+# gsr baseline wil be the 1 second before tial start
+# gsr to microsiemnes 1/J3*100000
+
+options(scipen = 999)
+
+tmp.df3$gsr_ms <- 1/tmp.df3$gsr*100000
+unique(tmp.df3$ssid)
+max(tmp.df3$gsr_ms)
+min(tmp.df3$gsr_ms)
+
+# gsr for leda
+colnames(tmp.df3)
+db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49 ))
+db_GSR$tNo<- NULL
+colnames(db_GSR)
+
+unique(db_GSR$Condition)
+
+db_GSR$Condition2<- if_else(db_GSR$Condition == 'Rest', 'Rest', 'IAPS')
+unique(db_GSR$Condition2)
+db_GSR$split_column<- paste0(db_GSR$Condition2,paste(db_GSR$ssid))
+unique(db_GSR$split_column)
+  (sprintf("writing for ledlab"))
+
+split_column<- unique(db_GSR$split_column)
+
+split_gsr = split(db_GSR, list(db_GSR$split_column))
+
+    for (ssid in names(split_gsr)) {
+      write_tsv(split_gsr[[ssid]][,c("time","gsr_ms", "trigger")], paste0("gpgsr_", paste0(ssid),".txt"), col_names = FALSE)
+    }
+
+```
+
+# baselining gsr
+```{r}
+# use ms to baseline
+tmp.df3_backup<- tmp.df3
+
+tmp.df3$gsr_bas<- if_else(tmp.df3$timerezero3 >= -3 & tmp.df3$timerezero3 < 0, tmp.df3$gsr_ms, NULL)
+# true if baseline within window
+tmp.df3$gsr_bastrue<- if_else(tmp.df3$timerezero3 >= -3 & tmp.df3$timerezero3 < 0, TRUE, FALSE)
+
+# create baseline median
+tmp.df3$gsr_bas_mean<- NULL
+
+tmp.df3<- tmp.df3%>%
+  arrange(ssid, tNo,time)%>%
+  group_by(ssid, tNo, gsr_bastrue)%>%
+  mutate(gsr_bas_median = median(gsr_bas))
+
+# fill the baseline mean
+tmp.df3<- tmp.df3%>%
+  # arrange(time)%>%
+  group_by(ssid, tNo)%>%
+  fill(gsr_bas_median)
+
+# fill up to complete
+unique(tmp.df3$gsrv)
+
+tmp.df3<- tmp.df3%>%
+  # arrange(time)%>%
+  group_by(ssid, tNo)%>%
+  fill(gsr_bas_median, .direction = 'up')
+
+# do baseline correction
+# 
+tmp.df3<- tmp.df3%>%
+  # arrange(time)%>%
+  group_by(ssid, tNo)%>%
+  mutate(gsr_basCor = gsr_ms - gsr_bas_median)
+
+# rest baselining
+tmp.df3<- tmp.df3%>%
+  # arrange(time)%>%
+  group_by(ssid, Condition)%>%
+  mutate(gsr_restmedian = median(gsr_ms))
+
+tmp.df3$gsr_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$gsr_ms- tmp.df3$gsr_restmedian, tmp.df3$gsr_basCor)
+
+# plot diagnosis
+ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
+  # stat_summary(geom = 'line', fun.data = 'mean')+
+    geom_smooth()+
+    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
+    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
+
+ ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
+  # stat_summary(geom = 'line', fun.data = 'mean')+
+    geom_smooth()+
+    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
+    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2) 
+  # tmp.df_norest$tNo<- as.factor(tmp.df_norest$tNo)
+
+ggplot(subset(tmp.df3, tmp.df3$screencontent == 'stim') , aes(x = timerezero3, y= gsr_basCor, olour = as.factor(ssid)))+
+    geom_smooth(aes())+
+    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
+    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
+
+tmp.df3_backup<- tmp.df3
+# gsr respone
+tmp.df3$gsr_resp_Log<- if_else(tmp.df3$timerezero3 > 1,TRUE, FALSE)
+unique(tmp.df3$gsr_resp_Log)
+
+tmp.df3 <- tmp.df3 %>%
+    group_by(ssid, tNo, gsr_resp_Log )%>%
+    mutate(gsr_response =   max(gsr_basCor))
+
+# gsr response for every bit
+unique(tmp.df3$screencontent)
+
+tmp.df3<- tmp.df3%>%
+  # arrange(time)%>%
+  group_by(ssid, tNo, screencontent)%>%
+  mutate(gsr_response_scrcont =   max(gsr_basCor))
+
+tmp.df3$gsr_response <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)
+
+tmp.df3<-
+  tmp.df3%>%
+  arrange(ssid, tNo,time)%>%
+  group_by(ssid, tNo)%>%
+    fill(gsr_response)
+
+tmp.df3<-
+  tmp.df3%>%
+  arrange(ssid, tNo,time)%>%
+  group_by(ssid, tNo)%>%
+    fill(gsr_response,  .direction = c('up'))
+
+unique(tmp.df3$gsr_response )
+
+tmp.df3_backup<- tmp.df3
+```
+
+#baseline and clean pupil
+
+```{r}
+library(gazer)
+
+min(tmp.df3$pupil, na.rm = TRUE)
+max(tmp.df3$pupil, na.rm = TRUE)
+
+tmp.df3$pupil<- if_else(tmp.df3$pupil> 7.2, tmp.df3$pupil, NULL)
+
+tmp.df3$pupil<- if_else(tmp.df3$pupil< 45, tmp.df3$pupil, NULL)
+
+tmp.df3_backup <- tmp.df3
+
+# note that smothing and interpolating is order dependednt so order by ssid, trial and time
+tmp.df3<- tmp.df3 %>%
+  arrange(ssid, trialUnq,tNo, time)%>%
+  group_by(ssid, trialUnq,tNo,screencontent) %>%
+  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=100, fillforward=100, hz=150))
+
+min(tmp.df3$extendpupil, na.rm = TRUE)
+max(tmp.df3$pupil, na.rm = TRUE)
+
+# let's check
+
+ggplot(subset(tmp.df3, tmp.df3$tNo == 3), aes(x = timerezero3, y= extendpupil , colour = as.factor(ssid)))+
+      geom_line()
+  # geom_line(aes(y = extendpupil), linetype = 'dashed', colour = 'red')
+
+# Smooth and Interpolate
+tmp.df3$subject<- tmp.df3$ssid
+tmp.df3$trial = tmp.df3$trialUnq
+
+# min(pup_extend$pupil, na.rm = TRUE)
+tmp.df3$extendpupil
+# ?smooth_interpolate_pupil
+
+# library(gazer)
+
+?smooth_interpolate_pupil
+
+# vert order dependent
+tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
+                                    extendblinks=TRUE, step.first= 'smooth',
+                                    maxgap=Inf, 
+                                    filter = 'moving',
+                                    type="linear", hz=150, n = 30)
+
+# tmp.df3<- tmp.df3 %>%
+#   group_by(ssid, trialUnq,tNo,screencontent) %>%
+#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
+#                                     extendblinks=TRUE, 
+#                            step.first= 'smooth',
+#                                     maxgap=10, 
+#                                     filter = 'moving',
+#                                     type="linear", hz=20, n = 10)
+# 
+# 
+# tmp.df3<-
+#   tmp.df3%>%
+#   arrange(ssid,tNo,time)
+#   # group_by(ssid, tNo, timerezero3)%>%
+# 
+# tmp.df3te<- tmp.df3 %>%
+#   group_by(ssid, Condition,tNo,screencontent) %>%
+#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
+#                                     extendblinks=TRUE, 
+#                            step.first= 'smooth',
+#                                     maxgap=Inf, 
+#                                     filter = 'moving',
+#                                     type="linear", hz=100, n = 5)
+
+min(tmp.df3$pup_interp, na.rm = TRUE)
+max(tmp.df3$pup_interp, na.rm = TRUE)
+
+subset(tmp.df3, tNo == 20 & ssid == 347)%>%
+ggplot(aes(x = timerezero3, y= pup_interp))+
+  geom_line()+
+   geom_line(aes(y = extendpupil), color = 'red')+
+  geom_line(aes(y = pupil), colour = 'gray')
+  # facet_grid(~Condition)
+
+subset(tmp.df3, tNo == -7 & ssid == 350)%>%
+ggplot(aes(x = timerezero3, y= pupil))+
+  geom_line()
+
+subset(tmp.df3, tNo == 1)%>%
+ggplot(aes(x = timerezero3, y= pup_interp))+
+  geom_line()+
+   geom_line(aes(y = extendpupil), color = 'red')+
+  # geom_line(aes(y = pup_interp), colour = 'gray')+
+    facet_grid(~ssid)
+  # facet_grid(~Condition)
+```
+
+# create baseline pupil mean
+```{r}
+tmp.df3backup<- tmp.df3
+tmp.df3$pup_bas<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, tmp.df3$pup_interp, NULL)
+# true if bseline if baseline within widnown
+tmp.df3$pup_bastrue<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, TRUE, FALSE)
+
+tmp.df3<- tmp.df3%>%
+  # arrange(time)%>%
+  group_by(ssid, tNo, pup_bastrue)%>%
+  mutate(pup_bas_med = median(pup_bas))
+
+# fill the baseline mean pupil
+tmp.df3<- tmp.df3%>%
+  # arrange(time)%>%
+  group_by(ssid,tNo)%>%
+  fill(pup_bas_med)
+
+# fill up to complete pupil
+tmp.df3<- tmp.df3%>%
+  # arrange(time)%>%
+  group_by(ssid, tNo)%>%
+  fill(pup_bas_med, .direction = 'up')
+
+# do baseline correction
+tmp.df3<- tmp.df3%>%
+  arrange(ssid, tNo, time)%>% # pay attentipn to order
+  group_by(ssid, tNo)%>%
+  mutate(pup_basCor = pup_interp - pup_bas_med)
+
+# we only one the median for rest
+tmp.df3<- tmp.df3%>%
+  group_by(Condition)%>%
+  mutate(pupilrest = median(pup_interp))
+
+tmp.df3$pup_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$pup_interp-tmp.df3$pupilrest, tmp.df3$pup_basCor)
+
+# MAD removal
+library(gazer)
+max_pup<-tmp.df3 %>%
+  dplyr::group_by(subject, trial) %>%
+  dplyr::mutate(speed=speed_pupil(pup_interp,time)) %>%
+  dplyr::mutate(MAD=calc_mad(speed))
+  # dplyr::filter(speed < MAD)
+
+tmp.df3<- max_pup
+
+# instead of deleting, nus put NA
+tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)
+
+tmp.df3$pup_interp_mad<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_interp, NULL)
+# tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)
+
+ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
+    # geom_smooth(se = F)+
+  geom_line()+
+    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
+    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
+```
+unique(tmp.df3$ssid)
+
+```{r}
+ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
+    geom_smooth(se = T)+
+    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
+    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
+
+```
+
+```{r}
+colnames(tmp.df3)
+table(is.na(tmp.df3$gsr_ms))
+table(is.na(tmp.df3$hr))
+
+# heart rate
+
+min(tmp.df3$hr, na.rm = TRUE)
+max(tmp.df3$hr, na.rm = TRUE)
+
+tmp.df3$hrv<- as.double(tmp.df3$hrv)
+tmp.df3$hrv2<- if_else(is.na(tmp.df3$hrv) == TRUE, 999,tmp.df3$hrv)
+
+tmp.df3$hr_clean<- tmp.df3$hr
+tmp.df3$hr_clean<- as.double(tmp.df3$hr_clean)
+
+tmp.df3$hr_clean<- if_else(tmp.df3$hrv2 >0,  tmp.df3$hr_clean, NULL)
+
+tmp.df3$hr_clean<- if_else(tmp.df3$hr_clean > 40 & tmp.df3$hr_clean< 120, tmp.df3$hr_clean, NULL)
+
+table(is.na(tmp.df3$hr_clean))
+# interpolate, only 2 seconds 
+library(zoo)
+
+tmp.df3<- tmp.df3%>%
+  arrange(ssid,tNo, time)
+
+# tmp.df3$hr_interp =
+
+tmp.df3<- tmp.df3%>%
+  # arrange(ssid, time, tNo)%>%
+  group_by(ssid, tNo,screencontent)%>%
+  mutate(hr_interp = na.approx(hr_clean, na.rm=FALSE, maxgap =400))
+
+  min(tmp.df3$hr, na.rm = TRUE)
+ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 352) , aes(x = timerezero3, y= hr_interp))+
+    # geom_smooth(se = F)+
+  geom_line()+
+  geom_line(aes(y = hr_clean), linetype = 'dashed', colour = 'green', size = 0.3)+
+   geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
+    # geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
+    # geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
+    # geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
+    # geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
+
+# na.approx(object, x = index(object), xout, ..., na.rm = TRUE, maxgap = Inf, along)
+# z <- na.spline(zoo(y, x), maxgap = 2)
+
+```
+
+```{r}
+tmp.df3 <- tmp.df3 %>%
+    group_by(ssid, tNo, gsr_resp_Log, screencontent)%>%
+    mutate(gsr_response_bycond =   max(gsr_basCor))
+
+# tmp.df3$gsr_response_bycond <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)
+
+colnames(tmp.df3)
+# tmp.df4<- select(tmp.df3, c(1:3,10:22,27:30,33:37,44,46,47,51,53:56,60))
+
+tmp.df4<- select(tmp.df3, c("session_id", "event_id", "ssid", "subject", "text", "trial","trialUnq", "tNo","trigger", "Condition" ,"screencontent","stim",
+                            "time", "timerezero", "timerezero2", "timerezero3", "status","filename",
+                            "left_gaze_x_cor_pix","right_gaze_x_cor_pix","left_gaze_y_cor_pix","right_gaze_y_cor_pix",  "gaze_x_cor_pix",  "gaze_y_cor_pix",
+                            "pupil", "pup_interp_mad", "extendpupil","pup_basCor",
+                            "hr", "hrv", "hrp", "hr_clean", 'hr_interp', 
+                            'gsr_ms', 'gsr_basCor', 'gsr_response', 'gsr_response_bycond', 
+                            "distance"))
+head(tmp.df4)
+
+# calculate trackloss
+unique(tmp.df4$status)
+
+tmp.df4$trackloss<- if_else(is.na(tmp.df4$gaze_x_cor_pix) == TRUE, 0, 
+                         if_else(is.na(tmp.df4$gaze_y_cor_pix) == TRUE, 0, 1))
+unique(tmp.df4$trackloss)
+
+# tmp.df4$trackloss<- if_else(tmp.df4$status> 0, 1, 0)
+
+tmp.df4$hr_trackloss<- if_else(is.na(tmp.df4$hr_clean) == TRUE, 0, 1) # 1 means valid, 0 missing
+
+tmp.df4 <- tmp.df4%>%
+  group_by(ssid, tNo, trialUnq, text)%>%
+  mutate(gaze_valid_prop = sum(trackloss)/n())%>%
+  mutate(gaze_loss_prop = 1 - gaze_valid_prop)%>%
+  mutate(hr_valid_prop = sum(hr_trackloss)/n())%>%
+  mutate(hr_loss_prop = 1 - hr_valid_prop)
+
+# check to see this is right
+ggplot(subset(tmp.df4, tmp.df3$ssid == 353) , aes(x = tNo, y= hr_valid_prop))+
+    # geom_smooth(se = F)+
+  geom_line()+
+  geom_line(aes(y = hr_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
+   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
+
+ggplot(subset(tmp.df4, tmp.df3$ssid == 354) , aes(x = tNo, y= gaze_valid_prop))+
+    # geom_smooth(se = F)+
+  geom_line()+
+  geom_line(aes(y = gaze_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
+   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
+
+colnames(tmp.df4)
+write_csv(tmp.df4, 'interodata_clean_gp.csv')
+
+# tmp.df4<- read_csv('intero_tsdata_clean.csv')
+
+tmp.df4<- tmp.df4%>%
+  arrange(ssid, time, tNo)
+
+unique(tmp.df4$trigger)
+
+# why
+
+tmp.df4$trigger2<- tmp.df4$trigger
+
+tmp.df4$trigger2<- if_else(tmp.df4$trigger>99, tmp.df4$trigger, as.double(tmp.df4$tNo))
+
+unique(tmp.df4$trigger2)
+
+# \why?
+tmp.df4<- tmp.df4%>%
+  group_by(ssid, tNo, text)%>%
+  mutate(stdev_gaze_x = sd(gaze_x_cor_pix, na.rm = TRUE))%>%
+  mutate(stdev_gaze_y = sd(gaze_y_cor_pix, na.rm = TRUE))
+
+tmp.df4$sdev_gazesum<- tmp.df4$stdev_gaze_x+ tmp.df4$stdev_gaze_y
+
+# summarise
+tmp.df4_sum<- tmp.df4%>%
+  arrange(ssid, time, tNo)%>%
+  group_by(ssid, subject, trial, Condition, screencontent, tNo, stim, trialUnq,text)%>%
+  summarise_at(c('pup_basCor', 'gsr_response','gsr_response_bycond', 'gsr_basCor', 'hr_interp', 'hr_clean', 'time', 'gaze_loss_prop', 'gaze_valid_prop', 'hr_valid_prop', 'hr_loss_prop', 'timerezero3', 'sdev_gazesum', 'stdev_gaze_x', 'stdev_gaze_y'), mean, na.rm = TRUE)
+
+tmp.df4_sum$trigger<-if_else(tmp.df4_sum$screencontent == 'fixation', 100,
+                          if_else(tmp.df4_sum$screencontent == 'ValenceResp', 101,
+                             if_else(tmp.df4_sum$screencontent == 'IntResp', 102, as.double(tmp.df4_sum$tNo))))
+
+unique(tmp.df4_sum$trigger)
+
+unique(tmp.df4_sum$trigger)
+tmp.df4_sum<- tmp.df4_sum%>%
+  arrange(time, tNo, ssid)
+
+write_csv(tmp.df4_sum, 'intero_aggdata_clean.csv')
+
+write_csv(tmp.df4_sum, 'intero_aggdata_clean_3046_355.csv')
+# 
+# head(tmp.df4_sum)
+# unique(tmp.df4_sum$tNo)
+
+ggplot(tmp.df4_sum, aes(tNo, gaze_valid_prop, colour = as.factor(ssid)))+
+  geom_point()+
+  geom_line()
+
+ggplot(subset(tmp.df4_sum, tmp.df4_sum$screencontent == 'stim'), aes(tNo, gaze_valid_prop, colour = as.factor(ssid)))+
+  geom_point()+
+  geom_line()
+
+ggplot(subset(tmp.df4_sum, tmp.df4_sum$screencontent == 'stim'), aes(gaze_valid_prop, colour = as.factor(ssid)))+
+# geom_density()+
+  geom_histogram()
+  # geom_line()
+
+```
+
+# for gaze parsing
+
+```{r}
+
+(sprintf("preparing for gazepath"))
+
+colnames(tmp.df4)
+
+  for_gazepath<- select(tmp.df4, c(2:15,17:26, 39:40,42:43))
+
+  for_gazepath$screencontent[for_gazepath$screencontent == 'rest1']<- 'fixation'
+  for_gazepath<- for_gazepath%>%
+    arrange(ssid, time, tNo)
+
+  colnames(for_gazepath)
+
+  for_gazepath<- subset(for_gazepath, is.na(for_gazepath$time) == FALSE)
+   # View(for_gazepath)
+
+  for_gazepath$split_column<- paste0(for_gazepath$ssid, paste0(for_gazepath$screencontent))
+  splitcol<- unique(for_gazepath$split_column)
+  splitcol
+  # ssid<- unique(for_gazepath$ssid)
+  # ssid
+  split_df = split(for_gazepath, list(for_gazepath$split_column))
+
+  (sprintf("writing for gazepath"))
+  # ssid = split(for_gazepath, list(for_gazepath$ssid))
+  # for (ssid in names(split_df)) {
+    for (splitcol in names(split_df)) {
+      # message( split_df[splitcol])
+      write_csv(split_df[[splitcol]], paste0('gp_',paste0(splitcol),".csv"))
+    }
+
+```
+process gazepath and ledalab
+```{r}
+library(gazepath)
+GUI()
+
+```
+
+# Import Ledalab
+Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 105 .01 2])
+```{r}
+read_leda <- function(flnm) {
   data.table::fread(flnm) %>% 
@@
 # now read them
-db_cali <-
+db_leda <-
+  list.files(pattern = "*.txt", 
+             full.names = T) %>% 
+  map_df(~read_leda(.))
+
+db_leda$trigger<- as.numeric(db_leda$Event.NID)
+unique(db_leda$trigger)
+db_leda$ssid<- as.numeric(substr(db_leda$filename, 13,15))
+colnames(tmp.df4_sum)
+colnames(db_leda)
+nrow(tmp.df4_sum)
+nrow(db_leda)
+colnames(tmp.df4_sum)
+tmp.df4_sum2<- subset(tmp.df4_sum,tmp.df4_sum$tNo != -7)
+tmp.df4_sum2<- tmp.df4_sum2%>%
+  arrange(ssid, time, tNo)%>%
+  group_by(ssid)%>%
+  mutate(order = 1:224)
+
+db_leda2<- subset(db_leda, db_leda$trigger != -7)
+db_leda2<- db_leda2%>%
+  arrange(ssid, Event.Nr)%>%
+  group_by(ssid)%>%
+  mutate(order = 1:224)
+
+tmp.df4_sum_fullt<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
+tmp.df4_sum_full_backup<- tmp.df4_sum_full
+
+tmp.df4_sum_full<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
+
+# tmp.df4_sum_full<- bind_cols(tmp.df4_sum, db_leda)
+
+tmp.df4_sum_full<- tmp.df4_sum_full%>%
+  arrange(ssid, tNo)
+```
+
+read parsed data
+```{r}
+read_parsed <- function(flnm) {
+    read_csv(flnm) %>%
+        mutate(filename = flnm)
+}
+
+db_parsed <- list.files(pattern = "*.csv", 
+               full.names = T) %>% 
+    map_df(~read_parsed(.))
+
+# return content between spaces
+# pu things in the correct order
+# library(stringr)
+db_parsed$screencontent<- str_extract(db_parsed$trialUnq, "(?<=\\s)(.*)(?=\\s)")
+unique(db_parsed$screencontent)
+db_parsed$screencontent[db_parsed$screencontent == 'rest1']<- 'fixation'
+
+db_parsed$screencontent_no<- if_else(db_parsed$screencontent == 'fixation', 1,
+                                      if_else(db_parsed$screencontent == 'stim', 2,
+                                              if_else(db_parsed$screencontent == 'ValenceResp', 3,
+                                                      if_else(db_parsed$screencontent == 'IntResp', 4, NULL))))
+
+db_parsed$tNo<- as.numeric(substr(db_parsed$trialUnq, 1,2))
+unique(db_parsed$screencontent_no)
+db_parsed$ssid<- substr(db_parsed$Participant, 4,6)
+
+db_parsed<- db_parsed%>%
+  arrange(ssid, tNo, screencontent_no)
+
+ggplot(db_parsed, aes(mean_x, mean_y))+
+  geom_point()+
+  facet_grid(ssid~screencontent)
+
+unique(db_parsed$tNo)
+# db_parsed$tNo<- if_else(db_parsed$tNo > -1, db_parsed$tNo-1, db_parsed$tNo )
+
+db_parsed<-db_parsed%>%
+  group_by(ssid, tNo, screencontent,Value)%>%
+  mutate(mean_fix_dur = mean(Duration))%>%
+  mutate(mean_POGsdSacAmp = mean(POGsdSacAmp))%>%
+  mutate(fix_count = sum(Value == 'f'))%>%
+  mutate(sac_count = sum(Value == 's'))
+
+# this might be needed for tempoal analisys
+write_csv(db_parsed, 'db_parsed.csv')
+
+db_parsed_summarised<- db_parsed%>%
+  group_by(ssid, tNo,screencontent, trialUnq, screencontent_no, Value)%>%
+  summarise_at(c('fix_count', 'sac_count', 'mean_fix_dur', 'mean_POGsdSacAmp', 'RMS'), mean, na.rm = TRUE)
+
+colnames(db_parsed_summarised)
+db_parsed_summarised_fix<- subset(db_parsed_summarised, db_parsed_summarised$Value == 'f')
+db_parsed_summarised_fix$sac_count<- NULL
+db_parsed_summarised_fix$POGsd<- db_parsed_summarised_fix$mean_POGsdSacAmp
+db_parsed_summarised_fix$mean_POGsdSacAmp<- NULL
+db_parsed_summarised_fix$Value<-NULL
+db_parsed_summarised_sac<- subset(db_parsed_summarised, db_parsed_summarised$Value == 's')
+db_parsed_summarised_sac$fix_count<- NULL
+db_parsed_summarised_sac$mean_sac_dur<-  db_parsed_summarised_sac$mean_fix_dur
+db_parsed_summarised_sac$SacAmp<- db_parsed_summarised_sac$mean_POGsdSacAmp
+db_parsed_summarised_sac$mean_POGsdSacAmp<- NULL
+db_parsed_summarised_sac$mean_fix_dur<- NULL
+db_parsed_summarised_sac$RMS<- NULL
+db_parsed_summarised_sac$Value<- NULL
+View(db_parsed_summarised_sac)
+View(db_parsed_summarised_fix)
+db_parsed_summarised_sac$Value<- NULL
+db_parsed_summarised_fix$Value<- NULL
+db_parsed_summarised_sac$RMS<- NULL
+
+View(db_parsed)
+
+colnames(db_parsed_summarised_fix)
+colnames(db_parsed_summarised_sac)
+
+db_parsed_summarised2<- left_join(db_parsed_summarised_fix,db_parsed_summarised_sac, by = (c('ssid', 'tNo', 'screencontent', "screencontent_no", "trialUnq")))
+
+db_parsed_summarised2<- db_parsed_summarised2%>%
+  arrange(ssid, tNo, screencontent_no)
+# View(db_parsed_summarised2)
+write_csv(db_parsed_summarised2, 'db_parsed_summarised.csv')
+
+db_parsed_summarised2$ssid<- as.numeric(db_parsed_summarised2$ssid)
+db_parsed_summarised2
+tmp.df4_sum_full<- left_join(tmp.df4_sum_full,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))
+rm(tmp.df4_sum_fullt)
+testna<- subset(tmp.df4_sum_fullt, is.na(tmp.df4_sum_fullt$mean_fix_dur) == TRUE)
+
+tmp.df4_sum_fullt
+```
+
+Behavioral data
+
+```{r}
+colnames(X309_2019_Dec_11_1807_01)
+library(data.table) 
+library(purrr)
+
+read_plus_beh <- function(flnm, select = c("condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
+                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt")) {
+  read.csv(flnm) %>% 
+    mutate(filename = flnm)
+}
+
+# now read them
+db_beh <-
   list.files(pattern = "*.csv",
              full.names = T) %>%
-  map_df(~read_cali(.))
-
-# view the dataset
-View(db_cali)
-unique(db_cali$filename)
-
-# select needed columns
-db_cali$ssid <- substring(db_cali$filename, 5,7)
-db_cali$valid_points <- sub(".*_", "", db_cali$text)
-db_cali$valid_points <- if_else(grepl('valid', db_cali$text), db_cali$valid_points, NULL)
-unique(db_cali$valid_points)
-
-db_cali$avg_error <- sub(".*_", "", db_cali$text)
-db_cali$avg_error <- if_else(grepl('AvgError', db_cali$text), db_cali$avg_error, NULL)
-db_cali$cali_no <- substring(db_cali$text, 23, 24)
-db_cali$cali_no <- if_else(grepl('valid', db_cali$text), db_cali$cali_no, NULL)
-db_cali$cali_no<- as.numeric(sub("_", "",db_cali$cali_no))
-
-install.packages("useful")
-
-library(useful)
-db_cali<- db_cali%>%
-  fill(cali_no)%>%
-  fill(valid_points)%>%
-  fill(avg_error, .direction = 'up')
-
-#find the duplicate rows (some trigger messages were sent twice)
-db_cali<- db_cali %>%
-  arrange(ssid)%>%
-  group_by(ssid)%>%
-  mutate(isduplicate = duplicated(avg_error))
-
-db_cali1 <- subset(db_cali, isduplicate == FALSE)
-
-db_cali1 <- select(db_cali1, c(ssid, cali_no, valid_points, avg_error))
-
-# create a order for the calibration
-db_cali1$x = row.names(db_cali1)
-db_cali1$cali_order <- ave(db_cali1$x,                 # Create numbering variable
-                       db_cali1$ssid,
-                       FUN = seq_along)
-```
-
-# FUNCTION TO CONVERT PIXELS TO DEGREES OF VISUAL ANGLE
-
-```{r}
-
-pixtoAng<- function(hw,d,r,stimsize){
-  #hw - height/width of the monitor(cm) - depending on the axis
-  #d - distance of the participant from the monitor (cm)
-  #r - vertical/horizontal resolution of the screen (px)
-  #stimsize - size of the stimulus on the screen (px)
-  deg_per_px = rad2deg(atan2(0.5*hw, d))/(0.5*r)
-  visAng <- stimsize * deg_per_px
-  return (visAng)
-}
-#pixtoAng - hw - height/width of the screen in cm - use height for vertical acc/prec, and width for horizontal; d - distance of the participants to the screen (we used an average distance from the logbook); r = height/width of the screen in pixels; stimsize - basically, what you wish to convert from pixels to degrees of visual angle
-
-```
-
-```{r}
-library(ggplot2)
-
-db_cali1$avg_error1<- as.numeric(as.character(db_cali1$avg_error))
-
-db_cali1 %>%
-  subset(ssid!= 610)%>%
-ggplot(aes(x = cali_order, avg_error1))+
-  geom_line(aes(group = ssid))
-
-db_cali1 %>%
-  subset(ssid!= 610)%>%
-ggplot(aes(x = cali_order, cali_no, color = ssid))+
-  geom_line(aes(group = ssid))
-
-db_cali1<- db_cali1%>%
-  group_by(ssid)%>%
-  mutate(cali_no_resc =  cali_no - lag(cali_no))%>%
-  mutate(cali_no_resc = if_else(!is.na(cali_no_resc), cali_no_resc, cali_no))
-
-db_cali1 %>%
-  subset(ssid!= 610)%>%
-ggplot(aes(x = cali_order, cali_no_resc, colour = ssid))+
-  geom_line(aes(group = ssid))
-
-#how many calibrations does it take until accepting
-library(lmerTest)
-
-cali_models<- list()
-db_cali1$ssid<- as.character(db_cali1$ssid)
-
-db_cali1$cali_order <- as.numeric(as.character(db_cali1$cali_order))
-db_cali1$cali_order_z<- scale(db_cali1$cali_order, center = TRUE, scale = TRUE)
-
-cali_models$cali_toaccept<- glmer(cali_no_resc ~ (1| ssid),
-                                  family = "poisson", data = db_cali1)
-
-summary(cali_models$cali_toaccept)
-
-summary(glm(cali_no_resc ~ cali_order_z, data = db_cali1))
-
-summary(cali_models$cali_toaccept)
-
-db_cali2<- subset(db_cali1, ssid < 500)
-mean(subset(db_cali2, cali_order == 1)$cali_no_resc, na.rm = TRUE)
-sd(subset(db_cali2, cali_order == 1)$cali_no_resc, na.rm = TRUE)
-
-# AVG cali
-mean(db_cali1$cali_no_resc, na.rm = TRUE)
-
-sd(db_cali1$cali_no_resc)
-
-(mean(db_cali1$avg_error1, na.rm = TRUE)) #43.40358
-(median(db_cali1$avg_error1, na.rm = TRUE)) #40.13
-
-install.packages("rCAT")
-library(rCAT)
-
-# height and widrh of the sreen in pixes and cm
-# H = 32.5 cm (108 Pixels) W = (52)  1920Pix by 1200, distance 63 - 65
-
-pixtoAng(52, 65, 1920, 43.40358) # 0.9849095
-pixtoAng(52, 65, 1920, 40.13) # 0.9849095
-
-db_cali1$avg_error1_visang<- pixtoAng(52, 65, 1920, db_cali1$avg_error1)
-
-mean(db_cali1$avg_error1_visang)
-sd(db_cali1$avg_error1_visang)
-range(db_cali1$avg_error1_visang)
-
-db_cali2_id<- db_cali2%>%
-  group_by(ssid)%>%
-  summarise_at(c("avg_error"), mean, na.rm = TRUE)
-
-db_cali2$Participant<- db_cali2$ssid
-
-db_cali2_id$avg_error<- NULL
-db_cali2$Participant<- NULL
-
-db_cali2<- left_join(db_cali2, db_cali2_id)
-
-db_cali2$Participant<- as.character(db_cali2$Participant)
-db_cali2%>%
-  ggplot(aes(cali_order, avg_error1))+
-  geom_line(aes(group = Participant, colour = Participant))+
-  stat_summary(aes(geom = "line"))+
-  geom_smooth()
-
-```
-
-Trackloss
-
-data = (tmp.df4_sum)
-
-```{r}
-# get average loss
-mean(tmp.df4_sum$gaze_loss_prop)*100
-sd(tmp.df4_sum$gaze_loss_prop)*100
-range(accuracy_dataset$gaze_loss_prop)*100
-
-range(accuracy_dataset)*100
-range(db_cali1$cali_no_resc)
-
-tmp.df4_sum %>%
-  subset(ssid < 500)%>%
-  group_by(screencontent)%>%
-  summarise_at(c('gaze_loss_prop'), mean, na.rm = TRUE)
-
-# store only neurotypicals
-
-tmp.df4_sum_below500 <- tmp.df4_sum %>%
-  subset(ssid < 500)
-
-#plot loss overtime
-tmp.df4_sum_below500%>%
-  ggplot(aes(tNo, gaze_loss_prop))+
-  stat_summary(geom = 'pointrange')+
-  geom_vline(xintercept = 26)
-
-#merge calibration information
-db_cali2_summ<- db_cali2 %>%
-  group_by(ssid)%>%
-  mutate(avg_error_agg = mean(avg_error1, na.rm = TRUE), cali_no_resc_agg = mean(cali_no_resc, na.rm = TRUE))
-
-# Save an object to a file
-saveRDS(db_cali2_summ, file = "db_cali2_summ.rds")
-# Restore the object
-accuracy_dataset_below6s<- readRDS(file = "accuracy_dataset_below6s.rds")
-
-View(db_cali2_summ)
-
-tmp.df4_sum_below500$cali_order<- if_else(tmp.df4_sum_below500$tNo < 0,1, if_else(tmp.df4_sum_below500$tNo > 0 & tmp.df4_sum_below500$tNo< 26, 2, 3))
-
-unique(tmp.df4_sum_below500$cali_order)
-
-#merge
-
-tmp.df4_sum_below500$cali_order<- as.character(tmp.df4_sum_below500$cali_order)
-tmp.df4_sum_below500 <- left_join(tmp.df4_sum_below500, db_cali2_summ)
-
-max(tmp.df4_sum_below500$ssid)
-View(tmp.df4_sum_below500)
-
-# just create one trackloss per trial for all screens
-tmp.df4_sum_below500 %>%
-  group_by(ssid)%>%
-  summarise_if(is.numeric, mean, na.r = TRUE)%>%
-  ggplot(aes(avg_error_agg, gaze_loss_prop))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-  facet_grid(~cali_order)
-
- unique(tmp.df4_sum_below500$cali_order)
-
-# mixed models
-
-calibration_lmerdata <-  tmp.df4_sum_below500 %>%
-  group_by(ssid, tNo )%>%
-  summarise_at(c('avg_error_agg','gaze_loss_prop', 'cali_no_resc_agg'), mean, na.rm = TRUE)
-
-nrow(calibration_lmerdata)
-
-loss_lmermodels<- list()
-
-calibration_lmerdata$ot1<- poly(calibration_lmerdata$tNo, degree = 1, raw = FALSE)
-calibration_lmerdata$ot2<- poly(calibration_lmerdata$tNo, degree = 2, raw = FALSE)[,2]
-
-View(calibration_lmerdata)
-calibration_lmerdata%>%
-ggplot(aes(tNo, ot1))+
-  geom_line()+
-  geom_line(aes(y = ot2))
-
-cor.test(calibration_lmerdata$ot1,calibration_lmerdata$ot2 )
-
-calibration_lmerdata1<- subset(calibration_lmerdata, ssid> 303 & tNo > 0 & tNo < 26)
-
-calibration_lmerdata1$ot1<- poly(calibration_lmerdata1$tNo, degree = 1, raw = FALSE)
-calibration_lmerdata1$ot2<- poly(calibration_lmerdata1$tNo, degree = 2, raw = FALSE)[,2]
+  map_df(~read_plus_beh(.))
+
+db328$condition<-db328$ï..condition
+
+db328 <-select(db328, c("condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
+                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
+
+db328$ssid<- 328
+
+db328$filename<- db328$ssid
+
+# files <- list.files(pattern = ".csv")
+# temp <- do.call(rbind,lapply(files, read.csv), header = TRUE)
+
+#install.packages("data.table", repos = "https://cran.rstudio.com")
+library(data.table)
+
+# Read all the files and create a FileName column to store filenames
+db_beh <- rbindlist(sapply(files, fread, simplify = FALSE),
+                use.names = TRUE, idcol = "filename")
+db_beh$condition <- db_beh$ï..condition
+
+db_beh<- select(db_beh, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
+                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
+
+db328<- select(db328, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
+                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
 
 # 
-loss_lmermodels$poly1<- glmer(gaze_loss_prop ~ ot1 + ot2 + (1 + ot1 + ot2 | ssid),
-                             family = "binomial",
-                             data = calibration_lmerdata1)
-
-summary(loss_lmermodels$poly1)
-
-loss_lmermodels$poly2<- glmer(gaze_loss_prop ~ tNo+ (1  | ssid),
-                             family = "binomial",
-                             data = calibration_lmerdata1)
-
-summary(loss_lmermodels$poly2)
-
-calibration_lmerdata$gaze_loss_prop
-
-(calibration_lmerdata1)%>%
-  ggplot(aes(tNo, gaze_loss_prop))+
-  #geom_smooth(aes(color = ssid), se = F)
-  #stat_summary(geom = 'pointrange')
- # geom_vline(xintercept = 26)+
-  geom_line(aes(y = predict(loss_lmermodels$poly1), colour = ssid))
-
-# second part
-
-calibration_lmerdata2<- subset(calibration_lmerdata, ssid> 303 & tNo > 25)
-
-calibration_lmerdata2$ot1<- poly(calibration_lmerdata2$tNo, degree = 1, raw = FALSE)
-calibration_lmerdata2$ot2<- poly(calibration_lmerdata2$tNo, degree = 2, raw = FALSE)[,2]
-
-# lmer models on loss
-
-calibration_lmerdata2$avg_error_agg_z<- scale(calibration_lmerdata2$avg_error_agg, center = TRUE, scale = TRUE)
-
-loss_lmermodels$poly2.1<- glmer(gaze_loss_prop ~ (ot1 + ot2)+ avg_error_agg_z+ (1 + ot1 + ot2 | ssid),
-                             family = "binomial",
-                             data = calibration_lmerdata2)
-
-summary(loss_lmermodels$poly2.1)
-
-loss_lmermodels$poly2.2<- glmer(gaze_loss_prop ~ tNo+ (1  | ssid),
-                             family = "binomial",
-                             data = calibration_lmerdata2)
-
-summary(loss_lmermodels$poly2.2)
-
-calibration_lmerdata$gaze_loss_prop
-
-(calibration_lmerdata2)%>%
-  ggplot(aes(tNo, gaze_loss_prop))+
-  geom_smooth(aes(color = ssid), se = F)
-  #stat_summary(geom = 'pointrange')
- # geom_vline(xintercept = 26)+
-  geom_line(aes(y = predict(loss_lmermodels$poly2.1), colour = ssid))
-
-#combine both
-calibration_lmerdata3$part <- subset(calibration_lmerdata, ssid> 303 & tNo > 0)
-
-calibration_lmerdata3$ot1<- poly(calibration_lmerdata3$tNo2, degree = 1, raw = FALSE)
-calibration_lmerdata3$ot2<- poly(calibration_lmerdata3$tNo2, degree = 2, raw = FALSE)[,2]
-
-#fir full model excluding pratice
-
-calibration_lmerdata3
-calibration_lmerdata3$part<- if_else(calibration_lmerdata3$tNo< 25, -.05, .05)
-
-calibration_lmerdata3$ot1_z<- scale(calibration_lmerdata3$ot1, center = TRUE)
-
-calibration_lmerdata3$ot2_z<- scale(calibration_lmerdata3$ot2, center = TRUE)
-
-loss_lmermodels$poly3.1 <- glmer(gaze_loss_prop ~ (ot1_z + ot2_z) * part +(1 + ot1_z + ot2_z | ssid),
-                             family = 'quasi_binomial',
-                             data = calibration_lmerdata3)
-
-loss_lmermodels$poly3.1 <- lmer(log1p(gaze_loss_prop+.5) ~ (ot1_z + ot2_z) * part +   (0 + ot1_z + ot2_z  | ssid)+(1 | ssid),
-                             REML = FALSE,
-                             data = calibration_lmerdata3)
-
-loss_lmermodels$poly3.1 <- lmer(log1p(gaze_loss_prop+.5) ~ (ot1 + ot2) * part +   (0 + ot1 + ot2  | ssid)+(1 | ssid),
-                             REML = FALSE,
-                             data = calibration_lmerdata3)
-
-summary(loss_lmermodels$poly3.1)
-
-anova(loss_lmermodels$poly3.1)
-library(sjstats)
-library(sjPlot)
-
-tab_model(loss_lmermodels$poly3.1)
-
-relgrad <- with(loss_lmermodels$poly3.1@optinfo$derivs,solve(Hessian,gradient))
- max(abs(relgrad))
- #[1] 1.152891e-05
-
-emmeans::emmeans(loss_lmermodels$poly3.1, pairwise~ part | ot2_z )
-
-loss_lmermodels$poly3.1_rand1 <- lmer(log1p(gaze_loss_prop+.5) ~(1 | ssid),
-                             REML = FALSE,
-                             data = calibration_lmerdata3)
-
-summary(loss_lmermodels$poly3.1_rand1)
-
-loss_lmermodels$poly3.1_rand2 <- lmer(log1p(gaze_loss_prop+.5) ~( | ssid),
-                             REML = FALSE,
-                             data = calibration_lmerdata3)
-
-s
-
-# check ID
-
-library(psych)
-library(sjstats)
-library(psycho)
-psycho::analyze(loss_lmermodels$poly3.1)
-psych
-library(MuMIn)
-r.squaredGLMM(loss_lmermodels$poly3.1)
-r.squaredGLMM(loss_lmermodels$poly3.2)
-#what if we incorporate calibration values
-
-calibration_lmerdata3$avg_error_agg_z <- scale(calibration_lmerdata3$avg_error_agg, center = TRUE, scale = TRUE)
-
-3$avg_error_agg_z <- scale(calibration_lmerdata3$avg_error_agg, center = TRUE, scale = TRUE)
-
-unique(calibration_lmerdata3$ssid)
-loss_lmermodels$poly3.2 <- lmer(log1p(gaze_loss_prop+.5) ~ (ot1_z + ot2_z) * part + avg_error_agg_z +   (0 + ot1_z + ot2_z  | ssid)+(1 | ssid),
-                             REML = FALSE,
-                             data = calibration_lmerdata3)
-
-summary(loss_lmermodels$poly3.2)
-
-anova(loss_lmermodels$poly3.2, loss_lmermodels$poly3.1)
-
-calibration_lmerdata3$tNo2<- if_else(as.double(calibration_lmerdata3$tNo)< 26, as.double(calibration_lmerdata3$tNo), calibration_lmerdata3$tNo-25)
-
-(calibration_lmerdata3)%>%
-  ggplot(aes(tNo2, gaze_loss_prop))+
-  #geom_smooth(aes(color = ssid), se = F)
-  #stat_summary(geom = 'pointrange')
- # geom_vline(xintercept = 26)+
-  geom_line(aes(y = predict(loss_lmermodels$poly3.1), colour = ssid))+
-    facet_grid(~part)
-
-(calibration_lmerdata3)%>%
-  ggplot(aes(tNo2, gaze_loss_prop))+
-  geom_line(aes(group = ssid,color = ssid))+
- # geom_smooth(aes(color = ssid), se = F)+
-    facet_grid(~part)
-
-# Save an object to a file
-saveRDS(calibration_lmerdata3, file = "calibration_lmerdata3.rds")
-# Restore the object
-readRDS(file = "my_data.rds")
-
-# is calibraton related to loss acc etc
-calibration_lmerdata3$avg_error_agg_z<- as.factor(as.character(calibration_lmerdata3$part))
- %>%
-  group_by(ssid, part)%>%
-  summarise_at(c(avg_error1_visang))
-
-calibration_lmerdata3$avg_error_agg_z+5
-
-tmp.df4_sum_below500_1.2<- tmp.df4_sum_below500 %>%
-   subset(cali_order!= 1)%>%
-  group_by(ssid, cali_order )%>%
-  summarise_at(c('avg_error1','gaze_loss_prop', 'cali_no_resc_agg'), mean, na.rm = TRUE)
-
- nrow(tmp.df4_sum_below500_1.2)
-
- #avg error
-cor.test(subset(tmp.df4_sum_below500_1.2, cali_order == 2)$avg_error1, subset(tmp.df4_sum_below500_1.2, cali_order == 2)$gaze_loss_prop)
-
-cor.test(subset(tmp.df4_sum_below500_1.2, cali_order == 3)$avg_error1, subset(tmp.df4_sum_below500_1.2, cali_order == 3)$gaze_loss_prop)
-
-cor.test(subset(tmp.df4_sum_below500_1.2, cali_order == 2)$cali_no_resc_agg, subset(tmp.df4_sum_below500_1.2, cali_order == 2)$gaze_loss_prop)
-
-cor.test(subset(tmp.df4_sum_below500_1.2, cali_order == 3)$cali_no_resc_agg, subset(tmp.df4_sum_below500_1.2, cali_order == 3)$gaze_loss_prop)
-
-tmp.df4_sum_below500_1.2%>%
-ggplot(aes(cali_no_resc_agg, gaze_loss_prop))+
-  geom_point()+
-geom_smooth(method = 'lm', se = F)+
-  facet_grid(~cali_order)
-
-   ggplot(aes(avg_error1, gaze_loss_prop))+
-   geom_point()+
-   facet_grid(~ cali_order)+
-   geom_smooth(method = 'lm', se = F)
-
-```
-
-Accuracy
-
-let's workout a few concepts
-, speed velocity and aceleration
-
-Velocity =
-
-Velocity is a physical vector quantity; both magnitude and direction are needed to define it.
-The scalar absolute value (magnitude) of velocity is called speed, being a coherent derived unit whose quantity is measured in the SI (metric system) as metres per second (m/s) or as the SI base unit of (m???s???1).
-velocity = delta space/ delta time
-
-Speed =  speed  = distance/ time
-
-acceleration is the rate of change of the velocity of an object with respect to time.
-Accelerations are vector quantities (in that they have magnitude and direction).[1][2] acceleration = delta velocity/ delta time
-
-For example, EyeLink (SR Research Ltd., Ontario, Canada) uses a velocity threshold of 35 deg/s and an acceleration threshold of 8000 deg/s 2 as default values, although these thresholds can be altered manually
-
-Let's compute accuracy
-
-ACCURACY FINAL CALCULATION
-STEP 1: Calculate ABSOLUTE horizontal and vertical distance for EACH SAMPLE
-STEP 2: Detect sample outliers using the median + 3 * MAD (rely only on the positive side!)
-STEP 3: Remove outliers (horizontal outliers should be removed ONLY when calculating horizontal accuracy and the same for vertical outliers)
-STEP 4: Mean horizontal and vertical distance (accuracy) for each participant, condition, trials
-STEP 5: Calculate overall accuracy using Pitagorean theorem
-STEP 6: Remove outliers in the same way as the previous (see step 2)
-STEP 7: Mean accuracy per participant, condition and trial
-
-```{r}
-
-accuracy_dataset$y_coord<- 600
-accuracy_dataset$x_coord
-
-unique(accuracy_dataset$screencontent)
-unique(accuracy_dataset$distance)
-#Calculate accuracy again
-library(rCAT)
-# remember to ignore the last few seconds later
-
-accuracy_dataset$distance
-accuracy_dataset$y_coord
-accuracy_dataset$x_coord
-
-setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Validation")
-
-accuracy_dataset <- readRDS("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Validation/accuracy_datasetjan16.rds")
-
-# rm(accuracy_datasetjan16)
-
-accuracy_dataset_below6s<- subset(accuracy_dataset, timerezero< 6)
-
-max(accuracy_dataset_below6s$timerezero)
-# STEP 1: Calculate ABSOLUTE horizontal and vertical distance for EACH SAMPLE
-library(tidyverse)
-
-accuracy_dataset_below6s <- accuracy_dataset_below6s %>%
-  arrange(ssid, tNo, time) %>%
-  group_by(ssid, tNo) %>%
-  mutate(v_accuracy_dif = abs(y_coord - gaze_y_cor_pix)) %>%
-  # mutate(v_accuracy = mean(v_accuracy_dif, na.rm = TRUE)) %>%
-  mutate(h_accuracy_dif = abs(x_coord - gaze_x_cor_pix )) %>%
-  # STEP 2: Detect sample outliers using the median + 3 * MAD (rely only on the positive side!)
-  mutate(v_accuracy_dif_median = median(v_accuracy_dif, na.rm = TRUE),
-                                        h_accuracy_dif_median = median(h_accuracy_dif, na.rm = TRUE),
-                                        v_accuracy_dif_mad = mad(v_accuracy_dif, na.rm = TRUE),
-                                        h_accuracy_dif_mad = mad(h_accuracy_dif, na.rm = TRUE))%>%
-  mutate(v_accuracy_dif_outlier = if_else(v_accuracy_dif > (v_accuracy_dif_median + (3*v_accuracy_dif_mad)), TRUE, FALSE))%>%
-  mutate(h_accuracy_dif_outlier = if_else(h_accuracy_dif > (h_accuracy_dif_median + (3*h_accuracy_dif_mad)), TRUE, FALSE))%>%
-  mutate(both_acc_dif_outlier = if_else(v_accuracy_dif_outlier == TRUE & h_accuracy_dif_outlier == TRUE, TRUE, FALSE))%>%
-  # create new difference columns where we don't have outliers
-  mutate(v_accuracy_dif_nooutl = if_else(v_accuracy_dif_outlier == FALSE, v_accuracy_dif, NULL))%>%
-  mutate(h_accuracy_dif_nooutl = if_else(h_accuracy_dif_outlier == FALSE, h_accuracy_dif, NULL))
-
-```
-
-```{r}
-
-# STEP 4: Mean horizontal and vertical distance (accuracy) for each participant, condition, trials
-library(rCAT)
-
-accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
-  group_by(ssid, tNo) %>%
-  mutate(v_accuracy = mean(v_accuracy_dif_nooutl, na.rm = TRUE)) %>%
-  mutate(h_accuracy = mean(h_accuracy_dif_nooutl, na.rm = TRUE)) %>%
-  mutate(avg_accuracy = (v_accuracy + h_accuracy)/2) %>%
-  mutate(v_accuracy_visang = pixtoAng(hw = 32, d = 65, r = 1200, stimsize = v_accuracy)) %>%
-  mutate(h_accuracy_visang = pixtoAng(hw = 52, d = 65, r = 1920, stimsize = h_accuracy))
-
-accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
-  group_by(ssid, tNo) %>%
-  mutate(avg_accuracy_visang = (v_accuracy_visang + h_accuracy_visang)/2)
-
-accuracy_dataset_below6s %>%
-  group_by(ssid,tNo)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(v_accuracy_visang))+
-  geom_histogram(bins = 300)+
-  geom_vline(xintercept = 1.4, color = 'red')
-
-```
-
-```{r}
-
-# STEP 5: Calculate overall accuracy using Pitagorean theorem
-accuracy_dataset_below6s<- accuracy_dataset_below6s%>%
-    arrange(ssid, tNo, time) %>%
-  group_by(ssid, tNo) %>%
-    mutate(accuracy_dif_pt = sqrt((x_coord - gaze_x_cor_pix)^2+ (x_coord - gaze_x_cor_pix)^2)) %>%
-   mutate(accuracy_dif_pt_median = median(accuracy_dif_pt, na.rm = TRUE),accuracy_dif_pt_mad = mad(accuracy_dif_pt, na.rm = TRUE))%>%
-  # check outliers
-   mutate(accuracy_dif_pt_outlier = if_else(accuracy_dif_pt > (accuracy_dif_pt_median + (3*accuracy_dif_pt_mad)), TRUE, FALSE))%>%
-   mutate(accuracy_dif_pt_nooutl = if_else(accuracy_dif_pt_outlier == FALSE, accuracy_dif_pt, NULL))
-
-# mean accuracy
-accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
-  group_by(ssid, tNo) %>%
-  mutate(accuracy_pt = mean(accuracy_dif_pt_nooutl, na.rm = TRUE)) %>%
-  mutate(avg_accuracy_visang_pt = pixtoAng(hw = 52, d = 65, r = 1920, stimsize = accuracy_pt))
-
-# report
-mean(accuracy_dataset_below6s$avg_accuracy_visang_pt, na.rm = TRUE) #0.770
-sd(accuracy_dataset_below6s$avg_accuracy_visang_pt, na.rm = TRUE) #0.70
-median(accuracy_dataset_below6s$avg_accuracy_visang_pt, na.rm = TRUE) # 0.6382099
-
-# mean(accuracy_dataset_below6s$avg_accuracy_visang, na.rm = TRUE)#.93
-range(accuracy_dataset_below6s$avg_accuracy_visang_pt, na.rm = TRUE) # 0.2335924 13.5357490
-)
-# vertical
-mean(accuracy_dataset_below6s$v_accuracy_visang, na.rm = TRUE) # 1.327067
-median(accuracy_dataset_below6s$v_accuracy_visang, na.rm = TRUE) #1.17
-sd(accuracy_dataset_below6s$v_accuracy_visang, na.rm = TRUE) # 0.725
-
-range(accuracy_dataset_below6s$v_accuracy_visang, na.rm = TRUE) # 0.276907 9.500563
-
-# horizontal
-
-mean(accuracy_dataset_below6s$h_accuracy_visang, na.rm = TRUE) #0.5448298
-median(accuracy_dataset_below6s$h_accuracy_visang, na.rm = TRUE) #.451
-sd(accuracy_dataset_below6s$h_accuracy_visang, na.rm = TRUE) # 0.4966967
-
-range(accuracy_dataset_below6s$accuracy_visang, na.rm = TRUE) #0.3019886 6.3431213
-
-acc_plots<- list()
-
-acc_plots$accuracy<- accuracy_dataset_below6s %>%
-  group_by(ssid,tNo)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(avg_accuracy_visang_pt))+
-  geom_histogram(bins = 300)+
-  geom_vline(xintercept = 1, color = 'red', linetype = "dashed", size =1.5)+p$graphstyle+
-  xlab("Accuracy (deg)")+
-  ylab("Density")
-
-acc_plots$accuracy<- acc_plots$accuracy+
-  scale_x_continuous(limits = c(0,10), breaks = c(0, 5, 10))
-
-acc_plots$accuracy
-saveRDS(accuracy_dataset_below6s, file = "accuracy_dataset_below6sJan16.rds")
-
-```
-
-fixation detection
-
-fixations
-
-# to detect fixations and saccades we should
-compute velocity and degre of displacement by participant and trial
-compute peak velcoicties as well
-compute the median and sd by trial and parocipant
-
-saccades will have occured if at least 3 consecutive samples break 6* sd of the median belocity
-
-```{r}
-
-# unique(fixationscreen_only1$screencontent)
-
-# we need to compute velocity so that we can exclude samples that are likelly saccades
-# exclude samples where people clearly where not looking at the center
-# compute accuracy and precision
-
-View(accuracy_dataset)
-
-#Original calculation with the squaring
-
-accuracy_dataset_below6s
-
-# velocity
-unique(accuracy_dataset_below6s$screencontent)
-accuracy_dataset_below6s$distance
-
-# max(accuracy_dataset_below6s$timerezero )
-
-accuracy_dataset_below6s <-
-
-  accuracy_dataset_below6s %>%
-  arrange(ssid, tNo, timerezero)%>%
-  group_by(ssid, tNo)%>%
-  mutate(intdist_pix =  sqrt((gaze_x_cor_pix - lag(gaze_x_cor_pix))^2 +(gaze_y_cor_pix - lag(gaze_y_cor_pix))^2)) %>%
-  mutate(inttimediff =  (timerezero)-  lag(timerezero))%>% #If time is calculated this way, it will create a mismatch between inter-sample times and inter-sample distance
-  mutate(intdist_visang =  pixtoAng(hw =52, d= 65, r=1920, stimsize= intdist_pix)) %>%
-  mutate(int_velocity = intdist_visang/inttimediff)%>%
-  mutate(median_velocity = median(int_velocity, na.rm = TRUE,
-                                  mad_velocity = mad(int_velocity, na.rm = TRUE)))%>%
-  mutate(threshold_velocity = median_velocity+ (6*mad_velocity))%>%
-  mutate(peak_velocity = max(int_velocity, na.rm = TRUE))%>%
-  mutate(avg_velocity = mean(int_velocity, na.rm = TRUE))
-
-accuracy_dataset_below6s %>%
-  group_by(ssid, trialUnq)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(threshold_velocity))+
-  geom_histogram(bins = 300)
-
-accuracy_dataset_below6s
-
-accuracy_dataset_below6s %>%
-  group_by(ssid, trialUnq)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(peak_velocity, threshold_velocity))+
-  geom_point()+
-  geom_smooth(method = 'lm', se = F)
-
-```
-
-```{r}
-
-# accuracy_dataset<- accuracy_dataset %>%
-#   group_by(ssid, trialUnq)%>%
-#   mutate(median_velocity = median(int_velocity, na.rm = TRUE))%>% # I think his needs to be positive(absolute other wise the median will be screwed)
-#   mutate(mad_velocity = mad(int_velocity, na.rm = TRUE))%>% 
-#   mutate(threshold_velocity = median_velocity + (6* mad_velocity))
-
-# mutate(threshold_velocity = median_velocity + (6* mad_velocity)) %>%
-
-# create a boolean vector for fixationdetcation
-
-accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
-  arrange(ssid, tNo, timerezero)%>%
-  group_by(ssid, tNo)%>%
-  mutate(detection = if_else(abs(int_velocity)> threshold_velocity, "s", "f"))
-
-accuracy_dataset_below6s$detection
-
-# test<-
-# accuracy_dataset_below6s %>%
-#   subset(ssid == 309 &tNo == 2)%>%
-#   mutate(timesaccade = if_else(detection == "s", timerezero, NULL))
-
-accuracy_dataset_below6s %>%
-  subset(ssid == 309 &tNo == 2)%>%
-  mutate(timesaccade = if_else(detection == "s", timerezero, NULL))%>%
-  ggplot(aes(x = timerezero, y = abs(int_velocity)))+
-  geom_line()+
-  geom_line(aes(y =gaze_y_cor_pix ), color = "red")+
-  geom_line(aes(y =gaze_x_cor_pix ), color = "green")+
-  geom_line(aes(y = threshold_velocity) , linetype = "dashed", size = 1, color = "gray")+
-    ylim(0, 1000)+
-  geom_vline(aes(xintercept = timesaccade), alpha  = .3)
-
-  geom_hline(yintercept = -35, linetype = "dashed", size = 1, color = "gray")
-unique(accuracy_dataset_below6s$threshold_velocity)
-
-```
-
-```{r}
-# now find a pattern "s - f - s" and if e two saccades slit by only a few fixatiojs (up to 3) then remove the the fixations as they are likelly saccades"
-# pattern 1 "s-f-s"
-table(test2$detection)
-accuracy_dataset_below6s$new<-NULL
-accuracy_dataset_below6s$new = ifelse(accuracy_dataset_below6s$detection == "f" & 
-                            lag(accuracy_dataset_below6s$detection, n = 1) == "s" & 
-                                lead(accuracy_dataset_below6s$detection, n = 1) == "s", TRUE, FALSE)
-
-r = c("s", "f", "s")
-library(zoo)
-test<- which(rollapply(accuracy_dataset_below6s$detection,length(r),identical,r))+0:(length(r)-1)
-View(test)
-test
-# 
-# test
-test2<- accuracy_dataset_below6s[12:20,]
-
-View(test2)
-
-# pattern 2 "s-f-f-s"
-accuracy_dataset_below6s$new1<-NULL
-
-accuracy_dataset_below6s <- accuracy_dataset_below6s %>% 
- mutate(new1 = ifelse(detection == "f" & 
-                       lead(detection, n = 1) == "f" &
-                            lag(detection, n = 1) == "s" & 
-                                lead(detection, n = 2) == "s", TRUE, FALSE))
-
-r1 = c("s", "f", "f", "s")
-test3<- which(rollapply(accuracy_dataset_below6s$detection,length(r1),identical,r1))+0:(length(r1)-1)
-
-test3
-
-test4<- accuracy_dataset_below6s[304514 :304530,]
-View(test4)
-
-# accuracy_dataset_below6s$new1[accuracy_dataset_below6s$new1 == TRUE
-
-# if_else(accuracy_dataset_below6s$new1 == TRUE, row.names(accuracy_dataset_below6s))
-
-View(test2)
-# 
-test3<- subset(accuracy_dataset_below6s[290310:290328,])
-
-# # pattern 3 "s-f-f-"f" s"
-
-accuracy_dataset_below6s$new2<-NULL
-
-accuracy_dataset_below6s<- accuracy_dataset_below6s %>% 
- mutate(new2 = ifelse(detection == "f" & 
-                        lead(detection, n = 1) == "f" &
-                        lead(detection, n = 2) == "f" &
-                        lead(detection, n = 3) == "s" &
-                            lag(detection, n = 1) == "s", TRUE, FALSE))
-
-# r1 = c("s", "f", "f", "s")
-
-# r2 = c("s", "f", "f", "f", "s")
-# 
-# test1.1 <- which(rollapply(accuracy_dataset_below6s$detection,length(r1),identical,r1))+0:(length(r1)-1)
-
-accuracy_dataset_below6s[which(accuracy_dataset_below6s$new1 == TRUE)+1, 'new1'] <- TRUE
-
-accuracy_dataset_below6s[which(accuracy_dataset_below6s$new2 == TRUE)+1, 'new2'] <- TRUE
-accuracy_dataset_below6s[which(accuracy_dataset_below6s$new2 == TRUE)+1, 'new2'] <- TRUE
-
-# accuracy_dataset_below6s$neW2<- NULL
-
-#mark fixations that need to be changed to saccades
-accuracy_dataset_below6s$fixation_tosacade<- (rowSums(accuracy_dataset_below6s[,startsWith(names(accuracy_dataset_below6s),"new")]=="TRUE") >= 1)
-
-table(accuracy_dataset_below6s$fixation_tosacade)
-
-# unique(subset(accuracy_dataset_below6s, fixation_tosacade == TRUE )$new)
-
-# replace spurious fixations when a sacade is taling pplace
-
-accuracy_dataset_below6s<- accuracy_dataset_below6s%>%
-  mutate(detection1 = if_else(fixation_tosacade == TRUE, "s", detection))
-
-# accuracy_dataset_below6s$sac_time <- if_else(accuracy_dataset_below6s$detection1 == "s", accuracy_dataset_below6s$timerezero, NULL)
-# accuracy_dataset_below6s$sac_time <- NULL
-
-# delete spurious saccades
-
-# create start of a saccade
-
-accuracy_dataset_below6s$start_sacc<- NULL
-accuracy_dataset_below6s$end_sacc<- NULL
-
-# accuracy_dataset_below6s$start_sacc <- if_else(is.na(accuracy_dataset_below6s$sac_time) == FALSE & is.na(lag(accuracy_dataset_below6s$sac_time, n = 1) == TRUE),accuracy_dataset_below6s$sac_time, NULL)
-
-# accuracy_dataset_below6s$end_sacc <- if_else(is.na(accuracy_dataset_below6s$sac_time) == FALSE & is.na(lead(accuracy_dataset_below6s$sac_time, n = 1) == TRUE),accuracy_dataset_below6s$sac_time, NULL)
-# 
-# max(accuracy_dataset_below6s$sac_time, na.rm = TRUE)
-
-# #get rid os start of old spurios saccades
-# accuracy_dataset_below6s$start_sacc <- if_else(accuracy_dataset_below6s$sacc_dur > 0, accuracy_dataset_below6s$start_sacc, NULL)
-# accuracy_dataset_below6s$end_sacc <- if_else(accuracy_dataset_below6s$sacc_dur > 0, accuracy_dataset_below6s$end_sacc, NULL)
-
-# accuracy_dataset_below6s <- accuracy_dataset_below6s%>%
-#   arrange(ssid, tNo, timerezero)%>%
-#   group_by(ssid, tNo)%>%
-#   fill(end_sacc, .direction = "up")%>%
-#   fill(start_sacc, .direction = "updown")%>%
-#   mutate(sacc_dur = end_sacc - start_sacc)%>%
-#   mutate(detection_withw_spursacc = if_else(sacc_dur == 0, "f", detection1))
-#     
-accuracy_dataset_below6s $detection_withw_spursacc<- NULL
-
-accuracy_dataset_below6s %>%
-subset(ssid == 309 & tNo == 2)%>%
-  ggplot(aes(timerezero, abs(int_velocity)))+
-  geom_line()+
-  geom_point(aes(y = gaze_y_cor_pix))+
-  geom_point(aes(y = gaze_x_cor_pix))+
-  geom_line(aes(y = threshold_velocity), size = 1.5)
-  # geom_vline(aes(xintercept = start_sacc), color = 'green')
-  geom_vline(aes(xintercept = end_sacc), color = 'red')
-
-  # annotate("rect", xmin = start_sacc, xmax = end_sacc)
-
-# delete single sacades
-rle(accuracy_dataset_below6s$detection1)
-
-accuracy_dataset_below6s$saccade_less3 <- rle(accuracy_dataset_below6s$detection1)
-
-accuracy_dataset_below6s <- accuracy_dataset_below6s %>%
-  group_by(ssid, tNo, detection1, event_order) %>%
-  mutate(keepF = if_else(detection1 == 'f' & n() >= 12, TRUE, FALSE)) %>%
-  mutate(keepS = if_else(detection1 == 's' & n() >= 3, TRUE, FALSE)) %>%
-
-# create a conter based on saca start
-
-saveRDS(accuracy_dataset_below6s, file = "accuracy_dataset_below6sjan16.rds")
-
-testsacc<- accuracy_dataset_below6s%>%
-subset(ssid == 309 & tNo == 2)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)
-
-  # geom_vline(aes(xintercept = start_sacc), color = "red", size = 2, alpha = .03) +
-  # geom_vline(aes(xintercept = end_sacc), color = "green", linetype = "dotted", alpha = .03) +
-  ylim(0,1000)
-
-mean(accuracy_dataset_below6s$end_sacc - accuracy_dataset_below6s$start_sacc, na.rm = TRUE)
-min(accuracy_dataset_below6s$end_sacc - accuracy_dataset_below6s$start_sacc, na.rm = TRUE)
-max(accuracy_dataset_below6s$end_sacc - accuracy_dataset_below6s$start_sacc, na.rm = TRUE)
-
-accuracy_dataset_below6s %>%
-  subset(ssid == 309 & tNo == 2)%>%
-  ggplot(aes(timerezero, abs(int_velocity)))+
-  geom_line()+
-  geom_line(aes(y = intdist_visang_vert))+
-  geom_point(aes(y = gaze_y_cor_pix))+
-  # geom_point(aes(y = gaze_x_cor_pix))+
-  # geom_line(aes(y = threshold_velocity), size = 1.5)+
-  # geom_vline(aes(xintercept = sac_time), alpha = .03)+
-
-  geom_vline(aes(xintercept = start_sacc), color = "green", size = 2, alpha = .3)+
-  geom_vline(aes(xintercept = end_sacc), color = "red", size = 2, linetype = "dotted", alpha = .3) 
-  ylim(0,100)+
-  xlim(.6,2)
-
-max(accuracy_dataset_below6s$timerezero3)
-
-min(accuracy_dataset_below6s$timerezero)
-```
-
-Timecourse models for accuracy
-
-```{r}
-
-unique(accuracy_dataset_below6s$screencontent)
-unique(accuracy_dataset_below6s$tNo)
-unique(accuracy_dataset_below6s$ssid)
-
-fixationscreen_only2<- accuracy_dataset_below6s%>%
-  group_by(ssid, tNo)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)
-
-fixationscreen_only2$ssid<- as.numeric(as.character(fixationscreen_only2$ssid))
-
-# fixationscreen_only2$ssid< 500
-# fixationscreen_only2_lmer <- fixationscreen_only2  %>%
-#   subset(tNo>0 & as.numeric(ssid, na.rm = TRUE) < 500)
-
-fixationscreen_only2_lmer<- fixationscreen_only2
-fixationscreen_only2_lmer$tNo2<- if_else(as.double(fixationscreen_only2_lmer$tNo)< 25, as.double(fixationscreen_only2_lmer$tNo), fixationscreen_only2_lmer$tNo - 24)
-
-unique(fixationscreen_only2_lmer$tNo2)
-
-#polynomial
-fixationscreen_only2_lmer$ot1<- poly(fixationscreen_only2_lmer$tNo2, degree = 1, raw =FALSE)[,1]
-fixationscreen_only2_lmer$ot2<- poly(fixationscreen_only2_lmer$tNo2, degree = 2, raw =FALSE)[,2]
-fixationscreen_only2_lmer$ot1_z<- scale(fixationscreen_only2_lmer$ot1, center = TRUE, scale = TRUE)[,1]
-fixationscreen_only2_lmer$ot2_z<- scale(fixationscreen_only2_lmer$ot2, center = TRUE, scale = TRUE)[,1]
-
-fixationscreen_only2_lmer%>%
-  ggplot(aes(tNo2, ot1_z))+
-  geom_line()+
-  geom_line(aes(y = ot2_z))
-
-fixationscreen_only2_lmer$block<- if_else(fixationscreen_only2_lmer$tNo< 25, -.5, +.5)
-
-fixationscreen_only2_lmer$subject<- as.factor(as.character(fixationscreen_only2_lmer$ssid))                                          
-# models
-
-accurcay_models$acc_1<- lmer(avg_accuracy_visang_pt ~ (ot1_z + ot2_z) * block+
-                              (0+ ot1_z+ot2_z)+ (1 | subject), REML = FALSE,
-                             data = fixationscreen_only2_lmer)
-
-summary(accurcay_models$acc_1)
-
-anova(accurcay_models$acc_1)
-
-```
-Fixed effects:
-               Estimate  Std. Error          df t value Pr(>|t|)   
-ot1_z          0.044002    0.013721 2064.033249   3.207  0.00136 **
-ot2_z         -0.001381    0.013899 2064.058090  -0.099  0.92087   
-block          0.068205    0.027205 2064.999334   2.507  0.01225 * 
-ot1_z:block    0.034924    0.027445 2064.297130   1.273  0.20333   
-ot2_z:block    0.036084    0.027793 2064.388596   1.298  0.19432   
----
-Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-
-Correlation of Fixed Effects:
-            ot1_z  ot2_z  block  ot1_z:
-ot2_z        0.054                     
-block       -0.078 -0.090              
-ot1_z:block -0.123 -0.162  0.029       
-ot2_z:block -0.162 -0.194  0.028  0.054
-
-```{r}
-
-unique(fixationscreen_only2_lmer$ssid)
-
-plot(accurcay_models$acc_1)
-qqnorm(resid(accurcay_models$acc_1)) 
-qqline(resid(accurcay_models$acc_1))
-
-fixationscreen_only2_lmer$subject<- as.factor(as.character(fixationscreen_only2_lmer$ssid))
-
-accurcay_models$acc_1_notstand <- lmer(accuracy_visang ~ (ot1_z + ot2_z) * block+
-                              (0+ ot1_z+ot2_z)+ (1 | subject), REML = FALSE,
-                             data = fixationscreen_only2_lmer)
-
-summary(accurcay_models$acc_1_notstand)
-# uniq
-
-(fixationscreen_only2_lmer) %>%
-  ggplot(aes(tNo2, accuracy_visang))+
-  # geom_smooth(aes(color = ssid), se = F)
- # geom_vline(xintercept = 26)+
-  geom_line(aes(y = predict(accurcay_models$acc_1, fixationscreen_only2_lmer), colour = subject))+
-  facet_grid(~block)
-
-```
-
-```{r}
-
-# horizontal
-accurcay_models$acc_1_h <- lmer(h_accuracy_visang ~ (ot1_z + ot2_z) * block+
-                              (0+ ot1_z+ot2_z)+ 
-                                (1 | ssid), REML = FALSE,
-                             data = fixationscreen_only2_lmer)
-
-plot(accurcay_models$acc_1_h)
-qqnorm(resid(accurcay_models$acc_1_h))
-qqline(resid(accurcay_models$acc_1_h))
-
-summary(accurcay_models$acc_1_h)
-
-```
-Linear mixed model fit by maximum likelihood . t-tests use Satterthwaite's method ['lmerModLmerTest']
-Formula: h_accuracy_visang ~ (ot1_z + ot2_z) * block + (0 + ot1_z + ot2_z) +      (1 | ssid)
-   Data: fixationscreen_only2_lmer
-
-     AIC      BIC   logLik deviance df.resid 
-  2686.4   2726.0  -1336.2   2672.4     2100
-
-Scaled residuals: 
-    Min      1Q  Median      3Q     Max 
--2.2019 -0.2687 -0.0533  0.1650 19.9560
-
-Random effects:
- Groups   Name        Variance Std.Dev.
- ssid     (Intercept) 0.3487   0.5905  
- Residual             0.1899   0.4357  
-Number of obs: 2107, groups:  ssid, 43
-
-Fixed effects:
-                Estimate   Std. Error           df t value Pr(>|t|)   
-ot1_z          0.0311142    0.0097019 2064.0332461   3.207  0.00136 **
-ot2_z         -0.0009764    0.0098278 2064.0580865  -0.099  0.92087   
-block          0.0482285    0.0192370 2064.9993309   2.507  0.01225 * 
-ot1_z:block    0.0246953    0.0194067 2064.2971262   1.273  0.20333   
-ot2_z:block    0.0255152    0.0196523 2064.3885924   1.298  0.19432   
----
-Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-
-Correlation of Fixed Effects:
-            ot1_z  ot2_z  block  ot1_z:
-ot2_z        0.054                     
-block       -0.078 -0.090              
-ot1_z:block -0.123 -0.162  0.029       
-ot2_z:block -0.162 -0.194  0.028  0.054
-
-# vertical
-```{r}
-accurcay_models$acc_1_v <- lmer(v_accuracy_visang ~ (ot1_z + ot2_z) * block+
-                              (0+ ot1_z+ot2_z)+ 
-                                (1 | ssid), REML = FALSE,
-                             data = fixationscreen_only2_lmer)
-
-plot(accurcay_models$acc_1_v)
-qqnorm(resid(accurcay_models$acc_1_v))
-qqline(resid(accurcay_models$acc_1_v))
-
-emmeans::emmeans(accurcay_models$acc_1_v, pairwise ~ block|ot1_z )
-
-summary(accurcay_models$acc_1_v)
-
-(fixationscreen_only2_lmer) %>%
-  ggplot(aes(tNo2, v_accuracy_visang))+
-  # geom_smooth(aes(color = ssid), se = F)
- # geom_vline(xintercept = 26)+
-  geom_line(aes(y = predict(accurcay_models$acc_1_v, fixationscreen_only2_lmer), colour = subject))+
-  facet_grid(~block)
-
-```
-
-Linear mixed model fit by maximum likelihood . t-tests use Satterthwaite's method ['lmerModLmerTest']
-Formula: v_accuracy_visang ~ (ot1_z + ot2_z) * block + (0 + ot1_z + ot2_z) +      (1 | ssid)
-   Data: fixationscreen_only2_lmer
-
-     AIC      BIC   logLik deviance df.resid 
-  2795.3   2834.9  -1390.6   2781.3     2100
-
-Scaled residuals: 
-    Min      1Q  Median      3Q     Max 
--4.1827 -0.4861 -0.0329  0.4371 16.6153
-
-Random effects:
- Groups   Name        Variance Std.Dev.
- ssid     (Intercept) 2.0756   1.4407  
- Residual             0.1929   0.4392  
-Number of obs: 2107, groups:  ssid, 43
-
-Fixed effects:
-               Estimate  Std. Error          df t value Pr(>|t|)   
-ot1_z          0.001718    0.009779 2064.007298   0.176  0.86056   
-ot2_z          0.002415    0.009906 2064.011559   0.244  0.80743   
-block          0.062299    0.019392 2064.177075   3.213  0.00134 **
-ot1_z:block    0.054673    0.019561 2064.052790   2.795  0.00524 **
-ot2_z:block    0.013280    0.019809 2064.068659   0.670  0.50267   
----
-Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-
-Correlation of Fixed Effects:
-            ot1_z  ot2_z  block  ot1_z:
-ot2_z        0.054                     
-block       -0.078 -0.090              
-ot1_z:block -0.123 -0.162  0.029       
-ot2_z:block -0.162 -0.194  0.028  0.054
-
-$emmeans
-ot1_z = -0.00209:
- block  emmean      SE   df lower.CL upper.CL
-  -0.5 -0.0311 0.00971 2069  -0.0501  -0.0121
-   0.5  0.0311 0.00971 2069   0.0121   0.0502
-
-Degrees-of-freedom method: kenward-roger 
-Confidence level used: 0.95
-
-$contrasts
-ot1_z = -0.00209:
- contrast   estimate     SE   df t.ratio p.value
- -0.5 - 0.5  -0.0622 0.0194 2069 -3.205  0.0014
-
-Degrees-of-freedom method: kenward-roger
-
-```{r}
-
-# 
-# 
-# mean(fixationscreen_only2_lmer$accuracy_visang, na.rm = TRUE)
-# 
-# median(fixationscreen_only2_lmer$accuracy_visang, na.rm = TRUE)
-# 
-# sd(fixationscreen_only2_lmer$accuracy_visang, na.rm = TRUE)
-# min(fixationscreen_only2_lmer$accuracy_visang, na.rm = TRUE)
-# max(fixationscreen_only2_lmer$accuracy_visang, na.rm = TRUE)
+# db304<- rbindlist(sapply(files, fread, simplify = FALSE),
+#                 use.names = TRUE, idcol = "filename")
 # 
@@
 # 
-# mean(fixationscreen_only2_lmer$v_accuracy_visang, na.rm = TRUE)
+# db304<- select(db304, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
+#                                      "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
+
+# db304$ssid<- 304
+colnames(db_beh)
+# db_beh<- bind_rows(db_beh, db304)
+db_beh$ssid<- substr(db_beh$filename, 3,5)
+
+# for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i]))
+
+View(db_beh)
+
+colnames(db_beh)
+
+db_beh2<- db_beh
+db328$filename<- as.character(db328$filename)
+db328$ssid<- as.character(db328$ssid)
+
+db328$ssid <- 328
+
+db_beh2<- bind_rows(db_beh2, db328)
+
+unique(db_beh2$ssid)
+# create one column for arousl and RT
+
+db_beh2$valence<- if_else(is.na(db_beh2$self_valence_4.response) == FALSE, db_beh2$self_valence_4.response,
+                          if_else(is.na(db_beh2$self_valence_2.response) == FALSE, db_beh2$self_valence_2.response, NULL))
+
+db_beh2$Self_intensity_3.response<- as.double(db_beh2$Self_intensity_3.response)                      
+db_beh2$arousal<- if_else(is.na(db_beh2$Self_intensity_2.response) == FALSE, as.numeric(db_beh2$Self_intensity_2.response),
+                          if_else(is.na(db_beh2$Self_intensity_3.response) == FALSE,
+                                  as.numeric(db_beh2$Self_intensity_3.response), NULL))
+
+db_beh2$valence_rt<- if_else(is.na(db_beh2$self_valence_4.rt) == FALSE, db_beh2$self_valence_4.rt,
+                          if_else(is.na(db_beh2$self_valence_2.rt) == FALSE, db_beh2$self_valence_2.rt, NULL))
+
+db_beh2$arousal_rt<- if_else(is.na(db_beh2$Self_intensity_2.rt) == FALSE, db_beh2$Self_intensity_2.rt,
+                          if_else(is.na(db_beh2$Self_intensity_3.rt) == FALSE, db_beh2$Self_intensity_3.rt, NULL))
+
+db_beh2$trialsPract.thisTrialN<- db_beh2$trialsPract.thisTrialN - 6
+
+db_beh2$trialIAPS.thisTrialN<-db_beh2$trialIAPS.thisTrialN +1 
+db_beh2$tNo<- if_else(is.na(db_beh2$Self_intensity_2.response) == FALSE, db_beh2$trialsPract.thisTrialN, db_beh2$trialIAPS.thisTrialN)
+unique(db_beh2$tNo)
+db_beh2<- subset(db_beh2, is.na(db_beh2$tNo) == FALSE)
+
+db_beh2<- db_beh2%>%
+  arrange(ssid, tNo)
+
+ggplot(db_beh2, aes(tNo, valence, colour = ssid))+
+  geom_point()+
+  geom_line()
+
+ggplot(db_beh2, aes(x = tNo, y = valence_rt))+
+  geom_point()+
+  geom_line()
+
+ggplot(db_beh2, aes(x = valence, y = ValenceMean))+
+  geom_point()+
+  geom_smooth(method = lm, se = T)
+
+ggplot(db_beh2, aes(x = arousal, y = ArousalMean))+
+  geom_point()+
+  geom_smooth(method = lm, se = T)
+
+colnames(db_beh2)
+db_beh2$triggeracq<- db_beh2$trigger
+unique(db_beh2$ssid)
+
+db_beh3<- select(db_beh2, c(2:7, 18:23))
+
+# db_beh3<- subset(db_beh3, is.na(db_beh3$condition) == FALSE)
+
+colnames(db_beh3)
+colnames(db_beh3_301_309)
+db_beh3$trigger<-NULL
+db_beh3_301_309$triggeracq<- NULL
+
+db_beh3_301_309$condition[db_beh3_301_309$condition == "Example Stimuli"]<- "Practice"
+db_beh3$condition[db_beh3$condition == "Example Stimuli"]<- "Practice"
+
+db_beh3$triggeracq<- NULL
+
+library(readr)
+db_beh300 <-  read_csv("300-309 beh/tmp.df4300_sum_full.csv")
+View(tmp_df4300_sum_full)
+
+db_beh300 <- subset(db_beh300, db_beh300$condition != "Rest")
+colnames(db_beh300)
+
+db_beh300$ssid<- 300
+
+db_beh300<- select(db_beh300, c("condition", "stimIAPS","stimDescription","ValenceMean", "ArousalMean", "ssid", "valence","arousal","valence_rt","arousal_rt", "tNo"))
+
+db_beh3$ssid<- as.numeric(db_beh3$ssid)
+db_beh_all<- bind_rows(db_beh3, db_beh300)
+db_beh_all<- bind_rows(db_beh_all, db_beh3_301_309)
+# db_beh4<- db_beh3
+
+unique(db_beh_all$ssid)
+
+str(tmp.df4_sum)
+str(db_beh_all)
+tmp.df4_sum$ssid<- as.numeric(tmp.df4_sum$ssid)
+
+db_beh3$ssid<- as.numeric(db_beh3$ssid)
+# rm(tmp.df4_sum_full_t)
+
+tmp.df4_sum_full<- left_join(tmp.df4_sum, db_beh_all, by = c('ssid', 'tNo'))
+
+tmp.df4_sum_full<- tmp.df4_sum_full%>%
+  arrange(ssid, tNo, time)
+
+# self reports
+
+db_selfrep <- read_csv("intero_selrep.csv")
+View(intero_selrep)
+tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_selfrep, by = 'ssid')
+
+unique(tmp.df4_sum_full$ssid)
+# colnames(tmp_df4300_sum_full)
+# colnames(tmp.df4_sum_full)
 # 
-# median(fixationscreen_only2_lmer$v_accuracy_visang, na.rm = TRUE)
-# 
-# sd(fixationscreen_only2_lmer$v_accuracy_visang, na.rm = TRUE)
-# min(fixationscreen_only2_lmer$v_accuracy_visang, na.rm = TRUE)
-# max(fixationscreen_only2_lmer$v_accuracy_visang, na.rm = TRUE)
-# 
-# 
-# mean(fixationscreen_only2_lmer$h_accuracy_visang, na.rm = TRUE)
-# 
-# median(fixationscreen_only2_lmer$h_accuracy_visang, na.rm = TRUE)
-# 
-# sd(fixationscreen_only2_lmer$h_accuracy_visang, na.rm = TRUE)
-# min(fixationscreen_only2_lmer$h_accuracy_visang, na.rm = TRUE)
-# max(fixationscreen_only2_lmer$h_accuracy_visang, na.rm = TRUE)
-
-# Save an object to a file
-saveRDS(fixationscreen_only2_lmer, file = "fixationscreen_only2_lmer.rds")
-# Restore the object
-readRDS(file = "my_data.rds")
-
-fixationscreen_only2_lmer
-
- tmp.df4_sum_below500 %>%
-   subset(cali_order!= 1)%>%
-  group_by(ssid, cali_order )%>%
-  summarise_at(c('avg_error1','gaze_loss_prop', 'cali_no_resc_agg'), mean, na.rm = TRUE)%>%
-   ggplot(aes(avg_error1, gaze_loss_prop))+
-   geom_point()+
-   facet_grid(~ cali_order)+
-   geom_smooth(method = 'lm', se = F)
-
- tmp.df4_sum_full_stim_gp_leda_beh_self_biopac %>%
-   group_by(ssid, screencontent)%>%
-   summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-   ggplot(aes(Global.Mean, BIO_Global.Mean))+
-   geom_point()+
-   geom_smooth(method = 'lm', se = F)+ facet_grid(~screencontent)
-
-```
-
-Precision
-fixationscreen_only3
-model_time_prec
-
-start by finishing fixation
-
-```{r eval=FALSE, include=FALSE}
-
-table(accuracy_dataset_below6s$detection_withw_spursacc)
-saveRDS(accuracy_dataset_below6s, file = "accuracy_dataset_below6sjan16.rds")
-
-# not yet
-accuracy_dataset_below6s <- accuracy_dataset_below6s %>%
-  arrange(ssid, tNo, timerezero)%>%
-  mutate(gaze_x_cor_pix_forpreci = if_else(detection1 == "f", gaze_x_cor_pix, NULL))%>%
-  mutate(gaze_y_cor_pix_forpreci = if_else(detection1 == "f", gaze_y_cor_pix, NULL))
-  # mutate(test = if_else(detection1 == "s", timerezero, NULL))
-  # mutate(test2 = if_else(detection_withw_spursacc == "s", timerezero, NULL))
-
-# we need to create a counter for the events so that each fix sacc or loss has a duration
-
-# accuracy_dataset_below6s$test <- duplicated(accuracy_dataset_below6s$detection1)
-# accuracy_dataset_below6s$test2 <- accuracy_dataset_below6s$detection1
-
-library(data.table)
-
-accuracy_dataset_below6s<-
-accuracy_dataset_below6s %>%
-  arrange(ssid, tNo, timerezero)%>%
-  group_by(ssid, tNo)%>%
-  mutate(event_order = rleid(detection1))%>%
-  ungroup()%>%
-  group_by(ssid, tNo, detection1, event_order)%>%
-  mutate(duplicated_event = !duplicated(event_order))%>%
-  ungroup()%>%
-  group_by(ssid, tNo)%>%
-
-  mutate(duplicated_event2 = duplicated(event_order))
-View(accuracy_dataset_below6s)
-
-# mutate(start = if_else(duplicated_event == TRUE, timerezero, NULL))%>%
-#   # fill(start, .direction = "down") %>%
-#   mutate(end = if_else(duplicated_event2 == TRUE & lead(duplicated_event2, n=1) == FALSE, timerezero, 
-#                if_else(duplicated_event2 == FALSE & lead(duplicated_event2, n=1) == FALSE, start + 0.005, NULL)))%>%
-#   ungroup() %>%
-#   group_by(ssid, tNo, detection1, event_order) %>%
-#   # mutate(end = if_else(duplicated_event == TRUE, timerezero, NULL))%>%
-#   fill(start, .direction = "down")%>%
-#   fill(end, .direction = "up")%>%
-#   mutate(duration = end - start)
-
-# arrangind the ds in order
-accuracy_dataset_below6s <- accuracy_dataset_below6s %>%
-   arrange(ssid, tNo, timerezero)
-
-accuracy_dataset_below6s$start<- if_else(accuracy_dataset_below6s$duplicated_event == TRUE, accuracy_dataset_below6s$timerezero, NULL)
-unique(accuracy_dataset_below6s$start)
-table(is.na(accuracy_dataset_below6s$start))
-
-# create end
-accuracy_dataset_below6s$end <- 
-  if_else(accuracy_dataset_below6s$duplicated_event2 == TRUE & rownames(accuracy_dataset_below6s) == nrow(accuracy_dataset_below6s), accuracy_dataset_below6s$timerezero, 
-  if_else(accuracy_dataset_below6s$duplicated_event2 == FALSE & rownames(accuracy_dataset_below6s) == nrow(accuracy_dataset_below6s), accuracy_dataset_below6s$start + 0.005,
-  if_else(accuracy_dataset_below6s$duplicated_event2 == TRUE & lead(accuracy_dataset_below6s$duplicated_event2, n = 1) == FALSE, accuracy_dataset_below6s$timerezero,
-  if_else(accuracy_dataset_below6s$duplicated_event2 == FALSE & lead(accuracy_dataset_below6s$duplicated_event2, n=1) == FALSE, accuracy_dataset_below6s$start + 0.005, NULL))))
-
-table(is.na(accuracy_dataset_below6s$end))
-
-  # if_else(accuracy_dataset_below6s$duplicated_event2 == TRUE & rownames(accuracy_dataset_below6s) == nrow(accuracy_dataset_below6s), accuracy_dataset_below6s$timerezero, 
-  # if_else(accuracy_dataset_below6s$duplicated_event2 == FALSE & rownames(accuracy_dataset_below6s) == nrow(accuracy_dataset_below6s), accuracy_dataset_below6s$start + 0.005, NULL))))
-
-# TEST <- rownames(accuracy_dataset_below6s) == nrow(accuracy_dataset_below6s)
-# table(TEST)
-# 
-# part344 <- subset(accuracy_dataset_below6s, ssid == 344 & tNo == 50 & event_order == 48)
-# 
-# part344$test <- if_else(rownames(part344) == nrow(part344), TRUE, FALSE)
-# 
-# part344$test2 <- if_else(part344$duplicated_event2 == TRUE & rownames(part344) == nrow(part344), part344$timerezero, 
-#                   if_else(part344$duplicated_event2 == FALSE & rownames(part344) == nrow(part344), part344$start + 0.005, NULL))
-
-table(part344$test)
-View(part344)
-
-accuracy_dataset_below6s <- accuracy_dataset_below6s %>%
-  arrange(ssid,tNo,timerezero) %>%
-  group_by(ssid, tNo, detection1, event_order) %>%
-  fill(start, .direction = "down")%>%
-  fill(end, .direction = "up")%>%
-  mutate(duration = end - start)
-
-unique(accuracy_dataset_below6s$duplicated_event2)
-
-table(is.na(accuracy_dataset_below6s$duration))
-table(is.na(accuracy_dataset_below6s$start))
-table(is.na(accuracy_dataset_below6s$end))
-
-View(accuracy_dataset_below6s)
-
-max(accuracy_dataset_below6s$duration)
-min(accuracy_dataset_below6s$duration)
-
-# natest<- subset(accuracy_dataset_below6s, is.na(duration) == TRUE)
-# accuracy_dataset_below6s %>%
-#   arrange(ssid, tNo, timerezero)%>%
-#   # group_by(ssid, tNo) %>%
-#   group_by(ssid, tNo, detection1)%>%
-#   fill(end, .direction = "up")
-
-  # mutate(end = if_else(lag(duplicated_event, n = 1) == TRUE, timerezero, NULL))
-
-# accuracy_dataset_below6s%>%
-#   ggplot(aes(duration))+
-#   geom_histogram(bins = 300)+
-#   xlim(0,.01)+
-#   facet_grid(~detection1)+
-#   geom_vline(xintercept = .005, size = 1, linetype = "dashed", alpha = .5)
-
-# now lets cmpute the average duration of events
-saveRDS(accuracy_dataset_below6s, "accuracy_dataset_below6sjan16withevents.rds")
-
-accuracy_dataset_below6s %>%
-  group_by(ssid, tNo, detection1)%>%
-  summarise_at(c('duration'), mean, na.rm = TRUE)%>%
-  ggplot(aes(duration))+
-  geom_density(aes(fill = detection1), alpha = .5)
-  facet_grid(~detection1)
-
-  table(accuracy_dataset_below6s$detection1 == "f")
-
-  table(is.na(accuracy_dataset_below6s$gaze_x_cor_pix), is.na(accuracy_dataset_below6s$gaze_y_cor_pix))
-  unique(accuracy_dataset_below6s$detection1)
-
-  # table(is.na(accuracy_dataset_below6s$detection1))
-
-# eliminate implausbe fixations (< 80ms = 0.08) and saccades( < 12ms = .012)
-
-  saveRDS(  accuracy_dataset_below6s, "  accuracy_dataset_below6sjan16withevents.rds")
-
-accuracy_dataset_below6s<-  readRDS(file = "  accuracy_dataset_below6sjan16withevents.rds")
-
-   accuracy_dataset_below6s$detection2<- if_else(is.na(accuracy_dataset_below6s$detection1) == TRUE,
-                                                 "loss",  accuracy_dataset_below6s$detection1)
-
-   table( accuracy_dataset_below6s$detection2)
-
-accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
-  group_by(ssid, tNo, detection2, event_order)%>%
-    mutate(fix_validity = if_else(detection2 == "f" & duration > .08, TRUE, FALSE))%>%
-    mutate(sacc_validity = if_else(detection2 == "s", duration > .012, TRUE,
-                                        FALSE))%>%
-    mutate(new_dur = if_else(fix_validity == TRUE & detection2 == "f", duration,
-                             if_else(sacc_validity == TRUE & detection2 == "s", duration,
-                                    if_else(detection2 == "loss", duration,  NULL))))
-
-# nee detectin ignoring small fix or saccades
-accuracy_dataset_below6s$detection3<- if_else(accuracy_dataset_below6s$fix_validity == TRUE & accuracy_dataset_below6s$detection2 == "f", accuracy_dataset_below6s$detection2,
-                                              if_else(accuracy_dataset_below6s$sacc_validity == TRUE & 
-                                                        accuracy_dataset_below6s$detection2 == "s", accuracy_dataset_below6s$detection2, "loss"))
-
-# this shousld result in less fixation and less saccades
-
-table(accuracy_dataset_below6s$detection1)
-table(accuracy_dataset_below6s$detection2)
-
-table(accuracy_dataset_below6s$detection3)
-
-# new event 3 that matches the new detection since the old fixations that were deleted will cause the order not to match
-
-accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
-  arrange(ssid, tNo, timerezero)%>%
-  group_by(ssid, tNo,)%>%
-  mutate(event_order_new = rleid(detection3))
-
-unique(accuracy_dataset_below6s$event_order_new)
-
-```
-
-  # ungroup()%>%
-  # group_by(ssid, tNo, detection1, event_order)%>%
-  # mutate(duplicated_event = !duplicated(event_order))%>%
-  # ungroup()%>%
-  # group_by(ssid, tNo)%>%
-
+# tmp.df4_sum_full<- tmp.df4_sum_full[,1:54]
+# tmp.df4_sum_full<- bind_rows(tmp.df4_sum_full, tmp_df4300_sum_full)
+
+# db_selfrep <- read_csv("~/Documents/InteroStudy/data/Bio/Dec12/db_selfrep.csv")
+
+# db_selfrep$ssid<- as.numeric(db_selfrep$ssid)
+
+# tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_selfrep, by = 'ssid' )
+
+View(tmp.df4_sum_full)
+write_csv(tmp.df4_sum_full, 'intero_data_full.csv')
+
+# tmp.df4_sum_full<- tmp.df4_sum_full%>%
+#   arrange(ssid, tNo, screencontent_no)
+```
+
+check
 ```{r}
 
-# compute amplitute of sacadesaccade_less3
-accuracy_dataset_below6s$start
-
-# create a new event order for this new detection
-
-accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
-  arrange(ssid, tNo,timerezero)%>%
-  group_by(ssid, tNo,detection3, event_order_new)%>%
-  mutate(sacc_posstart_x = if_else(detection3 == "s" & start == timerezero, gaze_x_cor_pix, NULL))%>%
- mutate(sacc_posend_x = if_else(detection3 == "s" & end == timerezero, gaze_x_cor_pix, NULL))%>%
-    mutate(sacc_posstart_y = if_else(detection3 == "s" & start == timerezero, gaze_y_cor_pix, NULL))%>%
- mutate(sacc_posend_y = if_else(detection3 == "s" & end == timerezero, gaze_y_cor_pix, NULL))
-
-accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
-   arrange(ssid, tNo,timerezero)%>%
-  group_by(ssid, tNo,detection3, event_order)%>%
- fill(sacc_posstart_x, .direction = "down")%>%
-  fill(sacc_posend_x, .direction = "up")%>%
-   fill(sacc_posstart_y, .direction = "down")%>%
-  fill(sacc_posend_y, .direction = "up")
-
-accuracy_dataset_below6s %>%
-  subset(detection3 == "s")%>%
-  arrange(ssid, tNo, timerezero)
-
-  saveRDS(accuracy_dataset_below6s, "accuracy_dataset_below6sjan16witheventdur.rds")
-
-# compute saccade amplitude displacement in pitagoean
-accuracy_dataset_below6s<- accuracy_dataset_below6s %>%
-  arrange(ssid, tNo, timerezero)%>%
-  group_by(ssid, tNo, detection3, event_order_new)%>%
-  mutate(sac_amp = sqrt((sacc_posstart_x - sacc_posend_x)^2 +(sacc_posstart_y - sacc_posend_y)^2))%>%
-  mutate(sac_amp_visang = pixtoAng(hw = 52, d = 65, r = 1920, sac_amp))%>%
-  mutate(sac_peak = mean(int_velocity))
-
-#backup
-  saveRDS(accuracy_dataset_below6s, "accuracy_dataset_below6sjan16witheventdur.rds")
-
-accuracy_dataset_below6s %>%
-  subset(detection3 == "s")%>%
-   group_by(ssid, tNo)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(sac_amp_visang, sac_peak))+
-  geom_point()+
-  geom_smooth(aes(group = ssid),method =  'lm', se = F)
-  facet_grid(~detection3)
-
-  accuracy_dataset_below6s %>%
-  subset(detection3 == "s")%>%
-   group_by(tNo)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(sac_amp_visang, new_dur))+
-  geom_point()+
-  geom_smooth(,method =  'lm', se = F)
-  facet_grid(~detection3)
-
-accuracy_dataset_below6s$Event<- if_else(accuracy_dataset_below6s$detection2 == "f", "Fixation",
-                                         if_else(accuracy_dataset_below6s$detection2 == "s", "Saccade", "Loss"))
-
-acc_plots$parsing<- accuracy_dataset_below6s%>%  
-group_by(ssid, tNo,detection2, Event)%>%
-    summarise_at(c('new_dur'), max, na.rm = TRUE)%>%
-  ggplot(aes(new_dur, fill = Event))+
-  geom_histogram(aes(y=..density..),bins = 300, alpha=0.5, 
-                position="identity")+
-  geom_density(alpha = .2)+
-  # geom_vline(xintercept = .1, linetype = "dashed")+
-  p$graphstyle+
-  xlab("Duration (s)")+
-  ylab("Density")+
-  scale_color_brewer(palette = "Dark2")+
-
-  # summarise_at(c('Duration (s)')*1000, min, na.rm = TRUE)+
-    theme(legend.position = c(0.6, 0.6))
-
- library(patchwork)
-
-accuracy_dataset_below6s
-
-acc_plots$loss<-  accuracy_dataset_below6s%>%  
-group_by(ssid, tNo,detection2, Event)%>%
-    summarise_at(c('gaze_loss_prop'), max, na.rm = TRUE)%>%
-  ggplot(aes(gaze_loss_prop))+
-  geom_histogram(aes(y=..density..),bins = 300, 
-                position="identity")+
-  # geom_density(alpha = .2)+
-  # geom_vline(xintercept = .1, linetype = "dashed")+
-  p$graphstyle+
-  xlab("Loss")+
-  ylab("Density")+
-  scale_color_brewer(palette = "Dark2")
-
-acc_plots$loss
-
-acc_plots$loss<- acc_plots$loss+
-  scale_x_continuous(limits=c(0,1), breaks = c(0,.5,1))
-
-scale_y_continuous(limits=c(0,40), breaks = c(0,20,40))
-
-acc_plots$loss
-
-  # summarise_at(c('Duration (s)')*1000, min, na.rm = TRUE)+
-    theme(legend.position = c(0.6, 0.6))
-
-    library(patchwork)
-
-acc_patch<- (acc_plots$accuracy | acc_plots$precision+theme(axis.title.y = element_blank())) /(acc_plots$loss|acc_plots$parsing+theme(axis.title.y = element_blank()))
-
-acc_patch<- acc_patch+plot_annotation(tag_levels = 'A')
-acc_patch
-
-ggsave("acc_patch.tiff", acc_patch, device = "tiff", dpi = 800, height = 7, width = 10)  
-#
-
-```
-
-saveRDS(accuracy_dataset_below6s, "accuracy_dataset_below6s.Rds")
+View(tmp.df4_sum_full)
+
+tmp.df4_sum_full_stim<- subset( tmp.df4_sum_full,  tmp.df4_sum_full$screencontent == 'stim')
+
+levels(as.factor(tmp.df4_sum_full_stim$Event.Name))
+tmp.df4_sum_full_stim<- subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$gaze_valid_prop> .85)
+colnames(tmp.df4_sum_full_stim)
+
+# is objective arousal and self report arousal correated
+tmp.df4_sum_full_stim$ValenceMean_cat<- if_else(tmp.df4_sum_full_stim$ValenceMean > 4, 'pos', 'neg')
+
+ggplot(tmp.df4_sum_full_stim, aes(arousal, log1p(TTP.AmpSum)), color = as.factor(ssid))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+  facet_grid(~ValenceMean_cat)
+ggplot(tmp.df4_sum_full_stim, aes(arousal, log1p(TTP.AmpSum), color = as.factor(ssid)))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+   facet_grid(~ValenceMean_cat)
+  # facet_grid(~ssid) # for some subjects
+
+color = as.factor(ssid)
+ggplot(tmp.df4_sum_full_stim, aes(arousal, pup_basCor))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+   facet_grid(~ValenceMean_cat)
+  # facet_grid(~ssid)
+color = as.factor(ssid)
+ggplot(tmp.df4_sum_full_stim, aes(arousal, hr))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+   facet_grid(~ValenceMean_cat)
+
+ggplot(tmp.df4_sum_full_stim, aes(arousal, hr))+
+         geom_point()+
+  geom_smooth(method= 'lm')
+
+ggplot(tmp.df4_sum_full_stim, aes(arousal, pup_basCor))+
+         geom_point()+
+  geom_smooth(method= 'lm')
+
+# do our physio signals corelate with one another
+
+ggplot(tmp.df4_sum_full_stim, aes(gsr_basCor, hr, color = as.factor(ssid)))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+   facet_grid(~ValenceMean_cat)
+
+ggplot(subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$CDA.AmpSum > 0), aes(TTP.AmpSum, hr))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+   facet_grid(~ValenceMean_cat)
+
+ggplot(tmp.df4_sum_full_stim, aes(gsr_basCor, pup_basCor))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+   facet_grid(~ValenceMean_cat)
+ colour = as.factor(ssid)
+ggplot(tmp.df4_sum_full_stim, aes(hr, pup_basCor))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+   facet_grid(~ValenceMean_cat)
+
+ggplot(tmp.df4_sum_full_stim, aes(arousal, log1p(CDA.PhasicMax)), color = as.factor(ssid))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+   facet_grid(~ValenceMean_cat)
+
+# okay arousal on gaze
+
+# is there and affect of arousal on number of fxation and saccadescolor = as.factor(ssid)
+library(tibble)
+
+is_outlier <- function(x) {
+  return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))
+}
+
+ggplot(tmp.df4_sum_full_stim, aes(CDA.PhasicMax, fix_count))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+   facet_grid(~ValenceMean_cat)
+
+ggplot(tmp.df4_sum_full_stim, aes(CDA.PhasicMax, sac_count))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+   facet_grid(~ValenceMean_cat)
+
+ggplot(tmp.df4_sum_full_stim, aes(ValenceMean_cat, sac_count))+
+  # geom_jitter()+
+  stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2)
+    # geom_boxplot()
+  # geom_text(aes(label=ssid),hjust=0, vjust=0)
+
+ggplot( tmp.df4_sum_full_stim, aes(IAS, cor_arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+  # stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2)+
+    # geom_boxplot()+
+  # geom_text(aes(label=ssid),hjust=0, vjust=0)
+
+ggplot(tmp.df4_sum_full_stim, aes(ValenceMean_cat, fix_count))+
+  # geom_jitter()+
+  stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2) 
+    # geom_boxplot()+
+  # geom_text(aes(label=ssid),hjust=0, vjust=0)
+
+ggplot(tmp.df4_sum_full_stim, aes(ValenceMean_cat, mean_sac_dur))+
+  # geom_jitter()+
+  stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2)
+    # geom_boxplot()
+  # geom_text(aes(label=ssid),hjust=0, vjust=0)
+
+ggplot(tmp.df4_sum_full_stim, aes(ValenceMean_cat, mean_fix_dur))+
+  # geom_jitter()+
+  stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2)
+  geom_boxplot()
+  # geom_text(aes(label=ssid),hjust=0, vjust=0)
+
+ggplot(tmp.df4_sum_full_stim, aes(CDA.PhasicMax, fix_count, color = as.factor(ssid)))+
+         geom_point()+
+  geom_smooth(method= 'lm')
+  # facet_grid(~ssid)+
+    # geom_text(aes(label=ssid),hjust=0, vjust=0)
+
+ggplot(subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$mean_fix_dur < 6000), aes(TTP.AmpSum, mean_fix_dur))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+   facet_grid(~ValenceMean_cat)
+
+ggplot(subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$mean_fix_dur < 6000 & tmp.df4_sum_full_stim$CDA.AmpSum>0 ), aes(CDA.PhasicMax, mean_fix_dur))+
+         geom_point()+
+  geom_smooth(method= 'lm')+
+   facet_grid(~ValenceMean_cat)
+
+ggplot(tmp.df4_sum_full_stim, aes(TAS, IAS))+
+         geom_point()+
+  geom_smooth(method= 'lm')
+
+p<- list()
+library(lmerTest)
+
+tmp.df4_sum_full_stim$TAS_c<- scale(tmp.df4_sum_full_stim$TAS, center = TRUE,scale = TRUE)
+tmp.df4_sum_full_stim$IAS_c<- scale(tmp.df4_sum_full_stim$IAS, center = TRUE, scale = TRUE)
+tmp.df4_sum_full_stim$arousal_c<- scale(tmp.df4_sum_full_stim$arousal, center = TRUE,scale = TRUE)
+
+tmp.df4_sum_full_stim<- tmp.df4_sum_full_stim%>%
+  group_by(ssid)%>%
+  mutate(cor_arousal = cor(arousal_c, hr))
+tmp.df4_sum_full_stim<- tmp.df4_sum_full_stim%>%
+  # mutate(ssid = as.factor(ssid))%>%
+  mutate(stim = as.factor(stim))
+tmp.df4_sum_full_stim$ssid<- as.factor(tmp.df4_sum_full_stim$ssid)
+
+tmp.df4_sum_full_stim$valence_c<- scale(tmp.df4_sum_full_stim$valence, center = TRUE, scale = TRUE)
+tmp.df4_sum_full_stim$TTP.AmpSum<- scale(tmp.df4_sum_full_stim$TTP.AmpSum,center = TRUE, scale = TRUE)
+
+# test soe models
+tmp.df4_sum_full_stimagg<- (tmp.df4_sum_full_stim%>%
+              group_by(ssid)%>%
+              summarise_at(c('IAS_c', 'TAS_c', 'AQ','cor_arousal', 'fix_count'), mean, na.rm = TRUE))
+
+ggplot(tmp.df4_sum_full_stimagg, aes(TAS_c, cor_arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+ggplot(tmp.df4_sum_full_stimagg, aes(IAS_c, cor_arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+# tmp.df4_sum_full_stimagg<- subset(tmp.df4_sum_full_stimagg, is.na(tmp.df4_sum_full_stimagg$IAS_c) == FALSE)
+
+p$a<- glmer(fix_count ~ 1 + IAS_c * CDA.ISCR *ValenceMean_cat + (1 | ssid ),
+           family = poisson(), data = tmp.df4_sum_full_stim)
+
+summary(p$a)
+
+p$a1<- lmer(mean_fix_dur ~ 1 + IAS_c * (arousal_c + hr) * ValenceMean_cat + (1 | ssid ),
+           REML = FALSE, data = tmp.df4_sum_full_stim)
+
+summary(p$a1)
+
+p$a1<- lmer(mean_fix_dur ~ 1 + IAS_c * + hr * ValenceMean_cat + (1 | ssid ),
+           REML = FALSE, data = tmp.df4_sum_full_stim)
+
+summary(p$a1)
+
+p$a2<- lmer(mean_fix_dur ~ 1 + IAS_c * (arousal_c + TTP.AmpSum) + (1 | ssid ),
+           REML = FALSE, data = tmp.df4_sum_full_stim)
+
+summary(p$a2)
+
+p$a2<- lmer(mean_fix_dur ~ 1 + cor_arousal * hr + (1 | ssid ),
+           REML = FALSE, data = tmp.df4_sum_full_stim)
+
+tmp.df4_sum_full_stim$hr_c<- scale(tmp.df4_sum_full_stim$hr, center = TRUE, scale = TRUE)
+
+p$a3<- glmer(sac_count ~ 1 + IAS_c * hr * ValenceMean_cat  + (1 | ssid ),
+           family = poisson(), data = tmp.df4_sum_full_stim)
+
+summary(p$a3)
+# p$a2<- lmer(mean_fix_dur ~ 1 + cor_arousal * ( hr)+ (1 | ssid ),
+#            REML = FALSE, data = tmp.df4_sum_full_stim)
+p$a4<- lmer(gsr_basCor ~ 1 + IAS_c * arousal_c + (1 | ssid ),
+           REML = FALSE, data = tmp.df4_sum_full_stim)
+
+summary(p$a4)
+
+       tmp.df4_sum_full_stim_cor<- tmp.df4_sum_full_stim%>%
+  group_by(ssid, TAS, IAS, AQ, `DASS Total`)%>%
+  summarise(cor_arousal_self = cor(arousal,  log1p(CDA.PhasicMax)))
+
+ggplot(tmp.df4_sum_full_stim_cor, aes(`DASS Total`, cor_arousal_self))+
+         geom_point()+
+  geom_smooth(method= 'lm')
+
+cor(tmp.df4_sum_full_stim_cor$cor_arousal_self, tmp.df4_sum_full_stim_cor$TAS,  use = 'complete')
+cor(tmp.df4_sum_full_stim_cor$cor_arousal_self, tmp.df4_sum_full_stim_cor$IAS,  use = 'complete')
+cor(tmp.df4_sum_full_stim_cor$TAS, tmp.df4_sum_full_stim_cor$IAS,  use = 'complete')
+
+tmp.df4_sum_full_stim_cor [1:8,]%>%
+  summarise(cor2 = cor(cor_arousal_self, TAS, use = 'complete'))
+
+ggplot(tmp.df4_sum_full_stim, aes(arousal_c, log1p(mean_fix_dur)))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+```
+
+IMPORT BIOPAC
 
 ```{r}
-
-View(accuracy_dataset_below6s)
-
-accuracy_dataset_below6s$timerezero
-
-#store gazepoints for precision calculations
-
-accuracy_dataset_below6s$gaze_x_cor_pix_for_prec<- if_else(accuracy_dataset_below6s$detection3 == "f", accuracy_dataset_below6s$gaze_x_cor_pix, NULL)
-
-accuracy_dataset_below6s$gaze_y_cor_pix_for_prec<- if_else(accuracy_dataset_below6s$detection3 == "f", accuracy_dataset_below6s$gaze_y_cor_pix, NULL)
-
-# check how parising is happening
- accuracy_dataset_below6s %>%
-   subset(ssid == 304 & tNo == 16 )%>%
-   ggplot(aes(timerezero, gaze_x_cor_pix_for_prec))+
-   geom_line()+
-   geom_line(aes(y = gaze_x_cor_pix), color = "green", linetype = "dotted")+
-   geom_line(aes(y = int_velocity), color = 'red', alpha = .5)+
-   geom_line(aes(y = gaze_y_cor_pix_for_prec), color = "blue")+
-    geom_line(aes(y=gaze_y_cor_pix), color = "blue", linetype = "dotted")
-   # geom_hline(aes(yintercept = threshold_velocity))+
-   geom_vline(aes(xintercept = test))
-
-```
-
-Now compute precision
+colnames(tmp.df4_sum_full)
+
+# import
+read_leda_bio <- function(flnm) {
+  data.table::fread(flnm) %>% 
+    mutate(filename = flnm)
+}
+
+# now read them
+db_leda_bio <-
+  list.files(pattern = "*.txt", 
+             full.names = T) %>% 
+  map_df(~read_leda_bio(.))
+
+db_leda_bio$trigger<- as.numeric(db_leda_bio$Event.NID)
+db_leda_bio$ssid<- as.numeric(substr(db_leda_bio$filename, 3,5))
+
+colnames(tmp.df4_sum_full)
+unique(tmp.df4_sum_full$trigger)
+
+tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full, tmp.df4_sum_full$ssid>303)
+# tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full_bio, tmp.df4_sum_full_bio$trigger!= -7)
+
+levels(as.factor(tmp.df4_sum_full_bio$ssid))
+unique(tmp.df4_sum_full_bio$trigger)
+levels(as.factor(db_leda_bio$ssid))
+
+db_leda_bio$ssid<- as.factor(db_leda_bio$ssid)
+db_leda_bio$trigger<- as.factor(db_leda_bio$trigger)
+db_leda_bio$order<- db_leda_bio$Event.Nr
+tmp.df4_sum_full_bio$ssid<- as.factor(tmp.df4_sum_full_bio$ssid)
+tmp.df4_sum_full_bio$trigger<- as.factor(tmp.df4_sum_full_bio$trigger)
+
+colnames(tmp.df4_sum_full_bio)
+
+unique(db_leda_bio$trigger)
+unique(db_leda_bio$Event.Name)
+unique(tmp.df4_sum_full_bio$trigger)
+unique(tmp.df4_sum_full_bio$Event.Name)
+
+tmp.df4_sum_full_bio%>%
+  arrange(ssid, tNo, order)
+db_leda_bio<- db_leda_bio%>%
+  arrange(ssid, order)
+
+tmp.df4_sum_full_bio$trigger<- tmp.df4_sum_full_bio$tNo
+tmp.df4_sum_full_bio$trigger<- if_else(tmp.df4_sum_full_bio$screencontent == 'fixation', 100,
+                                       if_else(tmp.df4_sum_full_bio$screencontent == 'ValenceResp', 101,
+                                               if_else(tmp.df4_sum_full_bio$screencontent == 'IntResp', 102, tmp.df4_sum_full_bio$tNo)))
+
+unique(tmp.df4_sum_full_bio$trigger)
+
+tmp.df4_sum_full_biot<-left_join(tmp.df4_sum_full_bio, db_leda_bio, by = c("order", "ssid", "trigger"))
+(db_leda_bio$trigger)
+
+nrow(tmp.df4_sum_full_bio)
+nrow(db_leda_bio)
+
+tmp.df4_sum_full<- tmp.df4_sum_full%>%
+  arrange(ssid, tNo)
+
+ggplot(tmp.df4_sum_full_biot, aes(CDA.PhasicMax.x, CDA.PhasicMax.y))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+ggplot(tmp.df4_sum_full_biot, aes(TTP.AmpSum.x, TTP.AmpSum.y))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+tmp.df4_sum_full_biot
+ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308), aes(TTP.AmpSum.y, arousal, colour = ssid))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = T)
+
+ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308), aes(TTP.AmpSum.y, arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = T)
+ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308 & tmp.df4_sum_full_biot$TTP.AmpSum.y> 0), aes( TTP.AmpSum.y, arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = T)
+tmp.df4_sum_full_biot1 <-subset(tmp.df4_sum_full_biot, tmp\.df4_sum_full_biot$ssid != 308)
+
+cor(tmp.df4_sum_full_biot1$arousal, tmp.df4_sum_full_biot1$Global.Mean.y, use = 'complete.obs')
+```
+
+import biopac heart rate
 ```{r}
- accuracy_dataset_below6s <- accuracy_dataset_below6s %>%
-  arrange(ssid, tNo, timerezero)%>%
-  group_by(ssid, tNo) %>%
-  mutate(gaze_x_cor_pix_for_prec_lead = lead(gaze_x_cor_pix_for_prec, n = 1)) %>%
-  mutate(gaze_x_cor_pix_for_prec_dif = gaze_x_cor_pix_for_prec_lead  - gaze_x_cor_pix_for_prec)%>%
-  mutate(gaze_y_cor_pix_for_prec_lead= lead(gaze_y_cor_pix_for_prec, n = 1)) %>%
-  mutate(gaze_y_cor_pix_for_prec_dif = gaze_y_cor_pix_for_prec_lead-gaze_y_cor_pix_for_prec) %>%
-  mutate(v_precision_pix = sqrt(mean(gaze_y_cor_pix_for_prec_dif ^2, na.rm = TRUE))) %>%
-  mutate(h_precision_pix = sqrt(mean(gaze_x_cor_pix_for_prec_dif ^2, na.rm = TRUE))) %>%
-
-  mutate(gaze_cor_pix_euclidean_int_dif = sqrt((gaze_x_cor_pix_for_prec_dif)^2 +(gaze_y_cor_pix_for_prec_dif)^2))%>%
-  mutate(precision_eucl_pix = sqrt(mean(gaze_cor_pix_euclidean_int_dif ^2, na.rm = TRUE)))%>%
-  mutate(precision_avg_pix = (v_precision_pix + h_precision_pix)/2)%>%
-
-  mutate(sd_h_precision_pix = sd(gaze_x_cor_pix_for_prec, na.rm = TRUE)) %>%
-    mutate(sd_v_precision_pix = sd(gaze_y_cor_pix_for_prec, na.rm = TRUE)) %>%
-    mutate(sd_precision_avg_pix = (sd_v_precision_pix + sd_h_precision_pix) / 2)
-
-mean(accuracy_dataset_below6s$v_precision_pix, na.rm = TRUE) 
-mean(accuracy_dataset_below6s$h_precision_pix, na.rm = TRUE)
-
-mean(accuracy_dataset_below6s$precision_avg_pix, na.rm = TRUE) 
-mean(accuracy_dataset_below6s$precision_eucl_pix, na.rm = TRUE)
-
-mean(accuracy_dataset_below6s$sd_h_precision_pix, na.rm = TRUE) 
-mean(accuracy_dataset_below6s$sd_v_precision_pix, na.rm = TRUE)
-
-mean(accuracy_dataset_below6s$sd_h_precision_pix, na.rm = TRUE)
-
-accuracy_dataset_below6s%>%
-  group_by(ssid, tNo)%>%
-  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
-  ggplot(aes(precision_eucl_pix))+
-  geom_histogram()+
-  geom_vline(xintercept = 40)
-
-accuracy_dataset_below6s%>%
-  group_by(ssid, tNo)%>%
-  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
-  ggplot(aes(precision_avg_pix))+
-  geom_histogram()+
-  geom_vline(xintercept = 40)
-
-accuracy_dataset_below6s%>%
-  group_by(ssid, tNo)%>%
-  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
-  ggplot(aes(sd_precision_avg_pix))+
-  geom_histogram()+
-  geom_vline(xintercept = 40)
-
-# conversions to degres
-
-accuracy_dataset_below6s$precision_visang<- NULL
- accuracy_dataset_below6s <-  accuracy_dataset_below6s %>%
-   arrange(ssid, tNo, timerezero)%>%
-  group_by(ssid, tNo) %>%
-   mutate(v_precision_visang = pixtoAng(hw = 32.5, d = 65 , r = 1200, v_precision_pix))%>%
-   mutate(h_precision_visang = pixtoAng(hw = 52, d = 65 , r = 1920, h_precision_pix))%>% 
-    mutate(avg_precision_visang = pixtoAng(hw = 52, d = 65 , r = 1920,precision_avg_pix ))%>%
-    mutate(eucl_precision_visang = pixtoAng(hw = 52, d = 65 , r = 1920, precision_eucl_pix))%>%
-    mutate(sd_v_precision_visang = pixtoAng(hw = 32.5, d = 65 , r = 1200, sd_v_precision_pix))%>%
-     mutate(sd_h_precision_visang = pixtoAng(hw = 52, d = 65 , r = 1920, sd_h_precision_pix))%>%
-     mutate(sd_avg_precision_visang = pixtoAng(hw = 32.5, d = 65 , r = 1200, sd_precision_avg_pix))
-
-saveRDS(accuracy_dataset_below6s, file = "accuracy_dataset_below6sjan16eventdurprecis.rds")
-
-#expeted ranges
-accuracy_dataset_below6s%>%
-  group_by(ssid, tNo)%>%
-  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
-  ggplot(aes(eucl_precision_visang))+
-  geom_histogram()+
-  geom_vline(xintercept = .5)
-
-acc_plots$precision<- accuracy_dataset_below6s %>%
-  group_by(ssid, tNo)%>%
-  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
-  ggplot(aes(avg_precision_visang))+
-  geom_histogram(aes(y=..density..), 
-                position="identity")+
-  # geom_histogram()+
-  geom_vline(xintercept = .5, linetype = "dashed", color = "red", size = 1.5)+
-  p$graphstyle+
-  xlab("Precision (deg)")+
-  ylab("Density")
-
-acc_plots$precision
-
-accuracy_dataset_below6s%>%
-  group_by(ssid, tNo)%>%
-  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
-  ggplot(aes(sd_avg_precision_visang))+
-  geom_histogram()+
-  geom_vline(xintercept = .5)
-
-accuracy_dataset_below6s %>%
-    subset(detection3 == "f")%>%
-  group_by(ssid, tNo)%>%
-  mutate(losstest = n())
-  summarise_if(is.numeric, mean, na.rm =TRUE)%>%
-
-  ggplot(aes(gaze_loss_prop, new_dur))+
-  geom_point()
-
-# mutate(sd_eucl_precision_pix = sqrt())
-
-# sd( (accuracy_dataset_below6s$new_dur  accuracy_dataset_below6s$duration)
-
-  mutate(precision_pix = (h_precision_pix + v_precision_pix)/2) %>%
-  mutate(v_precision_visang = pixtoAng(hw = 27.8, d = 62.45, r = 1080, stimsize = v_precision_pix)) %>%
-  mutate(h_precision_visang = pixtoAng(hw = 51, d = 62.45, r = 1920, stimsize = h_precision_pix)) %>%
-  mutate(precision_visang = (h_precision_visang + v_precision_visang)/2)
-
-```
-
-Precision analyses
-
-```{r}
-
-fixationscreen_only3<-
-
-  View(accuracy_dataset_below6s)
-
-test<- subset(accuracy_dataset_below6s, detection3 == "f")
-
-fixationscreen_only3<- accuracy_dataset_below6s%>%
-  subset(detection3 == "f")%>%
-  group_by(ssid, tNo)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)
-
-View(fixationscreen_only3)
-
-unique(fixationscreen_only3$ssid)
-fixationscreen_only3$ssid<- as.numeric(as.character(fixationscreen_only3$ssid))
-
-fixationscreen_only3_lmer<- fixationscreen_only3
-unique(fixationscreen_only3_lmer$ssid)
-
-fixationscreen_only3_lmer$tNo2<- if_else(as.double(fixationscreen_only3_lmer$tNo)< 25, as.double(fixationscreen_only3_lmer$tNo), fixationscreen_only3_lmer$tNo - 24)
-
-unique(fixationscreen_only3_lmer$tNo2)
-
-#polynomial
-fixationscreen_only3_lmer$ot1<- poly(fixationscreen_only3_lmer$tNo2, degree = 1, raw =FALSE)[,1]
-
-# fixationscreen_only3_lmer$ot1[1,]
-fixationscreen_only3_lmer$ot2<- poly(fixationscreen_only3_lmer$tNo2, degree = 2, raw =FALSE)[,2]
-
-fixationscreen_only3_lmer$ot1_z<- scale(fixationscreen_only3_lmer$ot1, center = TRUE, scale = TRUE)[,1]
-fixationscreen_only3_lmer$ot2_z<- scale(fixationscreen_only3_lmer$ot2, center = TRUE, scale = TRUE)[,1]
-
-fixationscreen_only3_lmer%>%
-  ggplot(aes(tNo, ot1_z))+
-  geom_point()+
-  geom_point(aes(y = ot2_z))
-
-# fixationscreen_only3_lmer$spli_trial<- as.factor(fixationscreen_only3_lmer$spli_trial)
-fixationscreen_only3_lmer$block<- if_else(fixationscreen_only3_lmer$tNo <25, -.5, +.5)
-
-fixationscreen_only3_lmer$subject<- as.factor(as.character(fixationscreen_only3_lmer$ssid))
-fixationscreen_only3
-
-precision_models<- list()
-library(lmerTest)
-
-mean(fixationscreen_only3_lmer$avg_precision_visang, na.rm = TRUE) # 0.2719884
-median(fixationscreen_only3_lmer$avg_precision_visang, na.rm = TRUE)# 0.2440743
-sd(fixationscreen_only3_lmer$avg_precision_visang, na.rm = TRUE) #0.1080971
-range(fixationscreen_only3_lmer$avg_precision_visang, na.rm = TRUE) #0.1065232 0.7233320
-
-# vertical
-
-mean(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE) # 0.3044482
-median(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE)# 0.2632572
-sd(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE) # 0.1335215
-range(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE) #0.1120570 0.9538436
-
-# horizontal
-
-mean(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE) # 0.2484294
-median(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE)#  0.2296711
-sd(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE) # 0.09180471
-range(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE) #0.09097805 0.60289107
-
-fixationscreen_only3_lmer$ssid<- as.factor(as.character(fixationscreen_only3_lmer$ssid))
-
-precision_models$prec_1 <- lmer(avg_precision_visang ~ (ot1_z + ot2_z) * block+
-                              (0+ ot1_z+ot2_z)+ (1 | ssid), REML = FALSE,
-                             data = fixationscreen_only3_lmer)
-
-summary(precision_models$prec_1)
-
-# fit data
-(fixationscreen_only3_lmer) %>%
-  ggplot(aes(tNo2, precision_visang))+
-  # geom_smooth(aes(color = ssid), se = F)
- # geom_vline(xintercept = 26)+
-  geom_line(aes(y = predict(precision_models$prec_1, fixationscreen_only3_lmer), colour = subject))+
-  facet_grid(~block)
-
-```
-
-Linear mixed model fit by maximum likelihood . t-tests use Satterthwaite's method [lmerModLmerTest]
-Formula: avg_precision_visang ~ (ot1_z + ot2_z) * block + (0 + ot1_z +      ot2_z) + (1 | ssid)
-   Data: fixationscreen_only3_lmer
-
-     AIC      BIC   logLik deviance df.resid 
- -6321.0  -6281.4   3167.5  -6335.0     2097
-
-Scaled residuals: 
-    Min      1Q  Median      3Q     Max 
--3.9049 -0.5446 -0.0864  0.4553  5.7883
-
-Random effects:
- Groups   Name        Variance Std.Dev.
- ssid     (Intercept) 0.082648 0.28749 
- Residual             0.002479 0.04979 
-Number of obs: 2104, groups:  ssid, 43
-
-Fixed effects:
-                Estimate   Std. Error           df t value Pr(>|t|)   
-ot1_z          0.0007986    0.0011108 2061.0024024   0.719  0.47227   
-ot2_z          0.0009260    0.0011245 2061.0040815   0.823  0.41033   
-block          0.0065649    0.0022007 2061.0587841   2.983  0.00289 **
-ot1_z:block    0.0014579    0.0022219 2061.0173472   0.656  0.51179   
-ot2_z:block    0.0023842    0.0022486 2061.0224616   1.060  0.28914
-
-# real data
-
-(fixationscreen_only3_lmer) %>%
-  ggplot(aes(tNo2, precision_visang))+
-  # geom_line(aes(colour = subject))+
-  geom_smooth(aes(color = subject), se = F)+
- # geom_vline(xintercept = 26)+
-  #geom_line(aes(y = predict(precision_models$prec_1, fixationscreen_only3_lmer), colour = subject))+
-  facet_grid(~spli_trial)
-
-emmeans::emmeans(accurcay_models$prec_1, pairwise ~  block | ot2_z)
-```{r}
-
-#vertical precision
-
-mean(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE)
-median(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE)
-sd(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE)
-min(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE)
-max(fixationscreen_only3_lmer$v_precision_visang, na.rm = TRUE)
-
-#horizontal precision
-
-mean(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE)
-median(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE)
-sd(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE)
-min(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE)
-max(fixationscreen_only3_lmer$h_precision_visang, na.rm = TRUE)
-
-# vertical precision
-
-precision_models$v_prec_1 <- lmer(v_precision_visang ~ (ot1_z + ot2_z) * block+
-                              (0+ ot1_z+ot2_z)+ (1 | ssid), REML = FALSE,
-                             data = fixationscreen_only3_lmer)
-
-plot(precision_models$v_prec_1)
-qqnorm(resid(precision_models$v_prec_1))
-
-summary(precision_models$v_prec_1)
-
-```
-Linear mixed model fit by maximum likelihood . t-tests use Satterthwaite's method [lmerModLmerTest]
-Formula: v_precision_visang ~ (ot1_z + ot2_z) * block + (0 + ot1_z + ot2_z) +      (1 | ssid)
-   Data: fixationscreen_only3_lmer
-
-     AIC      BIC   logLik deviance df.resid 
- -5217.6  -5178.1   2615.8  -5231.6     2097
-
-Scaled residuals: 
-    Min      1Q  Median      3Q     Max 
--3.8675 -0.4922 -0.0646  0.3834  6.5967
-
-Random effects:
- Groups   Name        Variance Std.Dev.
- ssid     (Intercept) 0.105332 0.32455 
- Residual             0.004213 0.06491 
-Number of obs: 2104, groups:  ssid, 43
-
-Fixed effects:
-                Estimate   Std. Error           df t value Pr(>|t|)   
-ot1_z          0.0007272    0.0014480 2061.0035161   0.502  0.61558   
-ot2_z          0.0009723    0.0014659 2061.0057547   0.663  0.50722   
-block          0.0076593    0.0028688 2061.0786467   2.670  0.00765 **
-ot1_z:block    0.0020506    0.0028965 2061.0234389   0.708  0.47906   
-ot2_z:block    0.0031637    0.0029314 2061.0302560   1.079  0.28059   
----
-```{r}
-# horizontal precision
-
-precision_models$h_prec_1 <- lmer(h_precision_visang ~ (ot1_z + ot2_z) * block+
-                              (0+ ot1_z+ot2_z)+ (1 | ssid), REML = FALSE,
-                             data = fixationscreen_only3_lmer)
-
-plot(precision_models$h_prec_1)
-qqnorm(resid(precision_models$h_prec_1))
-
-summary(precision_models$h_prec_1)
-
-# fit data
-(fixationscreen_only3_lmer) %>%
-  ggplot(aes(tNo2, h_precision_visang))+
-  # geom_smooth(aes(color = ssid), se = F)
- # geom_vline(xintercept = 26)+
-  geom_line(aes(y = predict(precision_models$h_prec_1, fixationscreen_only3_lmer), colour = subject))+
-  facet_grid(~spli_trial)
-
-# real data
-
-(fixationscreen_only3_lmer) %>%
-  ggplot(aes(tNo2, h_precision_visang))+
-  # geom_line(aes(colour = subject))+
-  geom_smooth(aes(color = subject), se = F)+
- # geom_vline(xintercept = 26)+
-  #geom_line(aes(y = predict(precision_models$prec_1, fixationscreen_only3_lmer), colour = subject))+
-  facet_grid(~spli_trial)
-
-saveRDS(fixationscreen_only3_lmer, "fixationscreen_only3_lmer_precision.rds")
-
-saveRDS(accuracy_dataset_below6s, "accuracy_dataset_below6sjan16eventdurprecis.rds")
-```
-
-Heart rate variability
-
-ALL WE NEED IS bounce
-
-hr variability metrics to use
-mean RMSSD
-
-rr interval
-
-```{r}
-
-unique(accuracy_dataset_below6s$ssid)
-library(readr)
-
-read_plus_hrv <- function(flnm) {
-  data.table::fread(flnm, select = c("ssid", "time", 'hr', "hrv", "hrp", "status", "tNo",  "Condition", "screencontent", "stim")) %>% 
+nrow(tmp.df4_sum_full_bio)
+
+colnames(tmp.df4_sum_full_bio)
+unique(tmp.df4_sum_full_bio$ssid)
+
+unique(db_biohr$filename)
+
+# import
+read_biohr <- function(flnm) {
+  data.table::fread(flnm) %>% 
     mutate(filename = flnm)
@@
 # now read them
-library(purrr)
-library(data.table)
-library(dplyr)
-
-# read all clean data for repixeling
-
-Restperiod <-
+db_biohr <-
   list.files(pattern = "*.csv", 
              full.names = T) %>% 
-  map_df(~read_plus_hrv(.))
-
-# keep only rest period
-
-Restperiod1 <- subset(Restperiod, tNo == -7)
-
-Restperiod1 %>%
-  subset(ssid == 609)%>%
-  ggplot(aes(time, hrp))+
-  geom_line()
-
-Restperiod1 <- select(Restperiod1, c(ssid, time, hrp))
-Restperiod2<- select()
-# df_dat <- split(Restperiod1, Restperiod1$ssid)
-
-# Split dataframe by city
-split_df <- split(Restperiod1[,3], list(Restperiod1$ssid))
-Restperiod1$time
-
-# Write out separate CSV for each city
-for (ssid in names(split_df)) {
-  # if (ssid == split_df[[ssid]]) {
-  # }
-    write_csv(split_df[[ssid]], paste0(ssid, "rest_hp.txt"), row.names = FALSE, col.names = FALSE, quote = FALSE)
-  }
-
-split_df[["344"]][,3]
-
-lapply(names(SPLIT.DATA), function(nm) 
-   write.csv(SPLIT.DATA[[nm]], paste0(nm, ".csv"), row.names = FALSE, quote = FALSE))
-
-View(Restperiod1)
-
-# unique(tmp.df4_full$ssid)
-# tmp.df4_full<-  read_csv("_tmp.df4_full.csv")
-
-hr<- subset(tmp.df4_full, is.na(hrp) == FALSE)
-
-# rm(tmp.df4_full)
-View(Restperiod)
-
-# exclude 341 hr from biopac
-
-```
-
-Plotting Preferences
-
-```{r}
-
-p<- list()
-
-sf = 1
-
-p$graphstyle <-  theme(#base plot theme
-
-  # axis
-  axis.line.y = element_line(colour = "gray40", size = 0.5, lineend=0),
-  axis.line.x = element_line(colour = 'gray40', size = 0.5, lineend=0),
-  axis.ticks.x = element_line(colour = 'gray40', size = 0.5, lineend=0),
-  strip.text.x = element_text(size = 11*(sf+1.5),  colour = "black"),
-  strip.text.y = element_text(size = 11*(sf+1.5),  colour = "black"),
-
-  #axis text
-
-  axis.text.x = element_text(size = 16*(sf+.5), family = "sans", colour = "black", hjust =1.2), #angle = 45
-  axis.text.y = element_text(size = 16*(sf+.5), family = "sans", colour = "black"),
-
-  # titles
-    plot.title = element_text(size = 16*(sf+1.5), hjust = .5),
-
-  axis.title.y=element_text(size = 16*(sf+1), margin=margin(0,5,0,0)),
-  axis.title.x=element_text(size = 16*(sf+1), margin=margin(0,5,0,0)),
-
-  #ticks
-    #axis.ticks = element_blank(),
-
-  # panel
-  panel.border = element_blank(),
-  panel.grid.major = element_blank(),
-  panel.grid.minor = element_blank(),
-  panel.background = element_rect(fill="transparent"),
-
-  # legend
-  legend.position = "none",
-  # legend.direction =,
-  text=element_text(size = 16, family = "sans"),
-
-  # strip shades (reco rectagles)
-  strip.background = element_blank())
-
-```
-
-```{r}
-
-# 605 and 606 look the same
-
-# gp heart rate
-max(Restperiod1$hrp)
-gp_heartpulse <-  Restperiod1 %>%
-  subset(ssid == 339)%>%
-  ggplot(aes(time - min(time), hrp/4740))+
-  geom_line()+
-    xlim(0,120)+
-  theme_classic()+
-  ylab("Pulse (AU)")+
-  xlab("Time (s)")+
-  p$graphstyle+
-ggtitle("HP GPB")
-
-```
-
-# biopac heart rate
-
-```{r}
-# 120% .004s
-
-rest_ss335_bio<- read.delim("335_IAPS_Physio_v3_rest.txt", skip = 40)
-
-max(rest_ss335_bio$X2.73285)
-
-nrow(rest_ss335_bio)
-rest_ss335_bio$time<- seq(1,239725)
-
-rest_ss335_bio$time_ms<- rest_ss335_bio$time/2000
-
-# merge(rest_ss335_bio, as.data.frame(rest_ss335))
-
-rest_ss335_bio%>%
-  ggplot(aes(time_ms,X0.116638.1))+
-  geom_line()+
-    xlim(0,120)+
-  theme_classic()
-
-ss335_ecg_bioplot<- rest_ss335_bio%>%
-  ggplot(aes(time_ms,X0.116638.1))+
-  geom_line()+
-    xlim(0,120)+
-  theme_classic()+
-  ylab("ECG (uv)")+
-  xlab("Time (s)")+
-  p$graphstyle+
-  ggtitle("ECG MP160")
-
-ss335_ecg_bioplot
-gp_heartpulse
-
-pulseechpatch<- gp_heartpulse+ss335_ecg_bioplot +plot_annotation(tag_levels = 'A')
-pulseechpatch
-
-ggsave("pulseechpatc.tiff", device = "tiff", dpi = 800, width = 12, height = 5)
-```
-
-Import parsed hrv from gazepoint
-
-```{r}
-
-library(readxl)
-GP_HRVanalysys <- read_excel("GP_HRVanalysys.xlsx")
-View(GP_HRVanalysys)
-
-# Import the IBIS and artifact freefreeny
-
-read_plus_ibi <- function(flnm) {
-  data.table::fread(flnm) %>% 
-    mutate(filename = flnm)
-}
-
-# now read
-cleanIBI_gp <-
-  list.files(pattern = "*.txt", 
-             full.names = T) %>% 
-  map_df(~read_plus_ibi(.))
-
-cleanIBI_gp<- cleanIBI_gp%>%
-  rename(IBI_clean = V1)
-
-cleanIBI_gp$ssid<- substr(cleanIBI_gp$filename, 13,15)
-
-# pointcare plots
-cleanIBI_gp%>%
-  # subset(ssid == 335)%>%
-  group_by(ssid)%>%
-  mutate(IBI_clean_z = scale(IBI_clean,center = TRUE)[,1])%>%
-  ggplot(aes(IBI_clean_z, lead(IBI_clean_z)+IBI_clean_z))+
-  geom_point()+
-  geom_smooth(method = 'lm', se = F)
-  facet_grid(~ssid)
-
-  # distribution of IBI lenghts
-  unique(cleanIBI_gp$ssid)
-unique(Restperiod1$ssid)
-
-time<- subset(Restperiod1, is.na(ssid) == FALSE & ssid != 341)
-
-nrow(time)
-nrow(cleanIBI_gp)
-
-cleanIBI_gp$time<- Restperiod1$time
-
-cleanIBI_gp %>%
-  # subset(ssid == 335)%>%
-  group_by(ssid)%>%
-
-  # mutate(IBI_clean_z = scale(IBI_clean,center = TRUE)[,1])%>%
-  ggplot(aes(IBI_clean))+
-  geom_histogram()
-
-cleanIBI_gp %>%
-  # subset(ssid == 335)%>%
-  group_by(ssid)%>%
-    mutate(time == 1:n())%>%
-  subset(ssid == 335)%>%
-  # mutate(IBI_clean_z = scale(IBI_clean,center = TRUE)[,1])%>%
-  ggplot(aes(time, IBI_clean))+
-  geom_point()
-
-```
-# data from biopac
-
-```{r}
-
-GP_HRVanalysys$MEANHR
-mean(GP_HRVanalysys$RMMSSD, na.rm = TRUE)
-
-# import biopac
-BIO_HRVanalysys <- read_excel("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Validation/BIO_HRVanalysys.xlsx")
-
-View(BIO_HRVanalysys)
-View(BIO_HRVanalysys)
-BIO_HRVanalysys$ssid
-GP_HRVanalysys$ssid
-
-GP_HRVanalysys$ssid<- as.character(GP_HRVanalysys$ssid)
-BIO_HRVanalysys$ssid<- as.character(BIO_HRVanalysys$ssid)
-
-combined_bio_GP_HRV<- left_join(GP_HRVanalysys, BIO_HRVanalysys, by = "ssid")
-
-View(combined_bio_GP_HRV)
-# GP_HRVanalysys$
-
-# r to R
-combined_bio_GP_HRV%>%
-  subset(ssid!= 608)%>%
-ggplot(aes(MEANRR.x, MEANRR.y, color = ssid))+
-  geom_point()+
-  geom_smooth(method = "lm", se = F)
-
-combined_bio_GP_HRV_no601 <- subset(combined_bio_GP_HRV, ssid != 601)
-
-cor.test(subset(combined_bio_GP_HRV, ssid!= 605)$MEANRR.x, subset(combined_bio_GP_HRV, ssid!= 605)$MEANRR.y, method = "kendal") # 0.9789474 T = 188, p-value < 0.00000000000000022
-
-cor.test(subset(combined_bio_GP_HRV, ssid!= 605 & ssid!= 608)$MEANRR.x, subset(combined_bio_GP_HRV, ssid!= 605 & ssid!= 608)$MEANRR.y, method = "kendal")
-
-# T = 169, p-value = 0.000000000000003775
-# alternative hypothesis: true tau is not equal to 0
-# sample estimates:
-#       tau 
-# 0.9766082
-
-cor.test(subset(combined_bio_GP_HRV)$MEANRR.x, subset(combined_bio_GP_HRV)$MEANRR.y, method = "kendal")
-
-# T = 199, p-value = 0.000000000002767
-# alternative hypothesis: true tau is not equal to 0
-# sample estimates:
-#       tau 
-# 0.8952381
-
-```
-
-# rMSSD
-```{r}
-combined_bio_GP_HRV %>%
-  subset(ssid!= 608 & ssid!= 605)%>%
-ggplot(aes(SDNN.x, SDNN.y, color = ssid))+
-  geom_point()+
-  geom_smooth(method = "lm", se = F)
-
-cor.test(subset(combined_bio_GP_HRV, ssid!= 605 & ssid!= 608)$SDNN.x, subset(combined_bio_GP_HRV, ssid!= 605 & ssid!= 608)$SDNN.y, method = "kendal")
-
-# 
-# 	Kendall's rank correlation tau
-# 
-# data:  subset(combined_bio_GP_HRV, ssid != 605 & ssid != 608)$SDNN.x and subset(combined_bio_GP_HRV, ssid != 605 & ssid != 608)$SDNN.y
-# T = 148, p-value = 0.000001521
-# alternative hypothesis: true tau is not equal to 0
-# sample estimates:
-#       tau 
-# 0.7309942
-
-cor.test(subset(combined_bio_GP_HRV)$SDNN.x, subset(combined_bio_GP_HRV)$SDNN.y, method = "kendal")
-
-# data:  subset(combined_bio_GP_HRV)$SDNN.x and subset(combined_bio_GP_HRV)$SDNN.y
-# T = 169, p-value = 0.00004489
-# alternative hypothesis: true tau is not equal to 0
-# sample estimates:
-#       tau 
-# 0.6095238
-
-```
-
-PNN50
-
-```{r}
-combined_bio_GP_HRV %>%
-  subset(ssid!= 608)%>%
-ggplot(aes(pNN50.x, pNN50.y, color = ssid))+
-  geom_point()+
-  geom_smooth(method = "lm", se = F)
-
-cor.test(subset(combined_bio_GP_HRV, ssid!= 608)$pNN50.x, subset(combined_bio_GP_HRV, ssid!= 608)$pNN50.y, method = "kendal")
-
-```
-data:  subset(combined_bio_GP_HRV, ssid != 608)$pNN50.x and subset(combined_bio_GP_HRV, ssid != 608)$pNN50.y
-z = 3.7951, p-value = 0.0001476
-alternative hypothesis: true tau is not equal to 0
-sample estimates:
-      tau 
-0.6357085
-
-nn50
-
-```{r}
-
-combined_bio_GP_HRV %>%
-  # subset(ssid!= 608)%>%
-ggplot(aes(NN50.x, NN50.y, color = ssid))+
-  geom_point()+
-  geom_smooth(method = "lm", se = F)
-
-cor.test(subset(combined_bio_GP_HRV)$NN50.x, subset(combined_bio_GP_HRV)$NN50.y, method = "kendal")
-
-```
-
-RMSSD
-```{r}
-combined_bio_GP_HRV %>%
-  subset( ssid!= 608)%>%
-ggplot(aes(RMMSSD.x, RMMSSD.y, color = ssid))+
-  geom_point()+
-  geom_smooth(method = "lm", se = F)
-
-cor.test(subset(combined_bio_GP_HRV, ssid!= 608)$RMMSSD.x, subset(combined_bio_GP_HRV, ssid!= 608)$RMMSSD.y, method = "kendal")
-
-# Kendall's rank correlation tau
-# 
-# data:  subset(combined_bio_GP_HRV, ssid != 608)$RMMSSD.x and subset(combined_bio_GP_HRV, ssid != 608)$RMMSSD.y
-# T = 153, p-value = 0.00007322
-# alternative hypothesis: true tau is not equal to 0
-# sample estimates:
-#       tau 
-# 0.6105263
-
-cor.test(subset(combined_bio_GP_HRV)$RMMSSD.x, subset(combined_bio_GP_HRV)$RMMSSD.y, method = "kendal")
-
-# Kendall's rank correlation tau
-# 
-# data:  subset(combined_bio_GP_HRV)$RMMSSD.x and subset(combined_bio_GP_HRV)$RMMSSD.y
-# T = 173, p-value = 0.00001127
-# alternative hypothesis: true tau is not equal to 0
-# sample estimates:
-#      tau 
-# 0.647619
-
-```
-
-```{r}
-# r to R
-combined_bio_GP_HRV%>%
-ggplot(aes(MEANHR.x, MEANHR.y, color = ssid))+
-  geom_point()+
-  geom_smooth(method = "lm", se = F)
-
-```
-FRequency measures
-Of the frequency-domain methods, data related to the amount of low frequency (LF) heartbeats is often used (0.04 to 0.15 Hz) as a measure of sympathetic nervous system activity.
-Measurements of high-frequency (HF; 0.15 Hz to 0.4 Hz) and very-low-frequency (VLF) are also used
-
-```{r}
-# low frequency
-combined_bio_GP_HRV%>%
-  subset(ssid!= 601)%>%
-ggplot(aes(lfperce.x, lfperce.y, color = ssid))+
-  geom_point()+
-  geom_smooth(method = "lm", se = F)
-  # xlim(0,200)
-
-cor.test(subset(combined_bio_GP_HRV, ssid != 601)$lfperce.x, subset(combined_bio_GP_HRV, ssid != 601)$lfperce.y, method = "kendal")
-
-# Kendall's rank correlation tau
-# 
-# data:  subset(combined_bio_GP_HRV, ssid != 601)$lfperce.x and subset(combined_bio_GP_HRV, ssid != 601)$lfperce.y
-# T = 163, p-value = 0.000001342
-# alternative hypothesis: true tau is not equal to 0
-# sample estimates:
-#       tau 
-# 0.7157895
-
-cor.test(subset(combined_bio_GP_HRV)$lfperce.x, subset(combined_bio_GP_HRV)$lfperce.y, method = "kendal")
-
-# Kendall's rank correlation tau
-# 
-# data:  subset(combined_bio_GP_HRV)$lfperce.x and subset(combined_bio_GP_HRV)$lfperce.y
-# T = 171, p-value = 0.00002292
-# alternative hypothesis: true tau is not equal to 0
-# sample estimates:
-#       tau 
-# 0.6285714
-
-```
-
-# vlf
-
-```{r}
-combined_bio_GP_HRV %>%
-    subset(ssid!= 601)%>%
-ggplot(aes(vlfperc.x, vlfperc.y, color = ssid))+
-  geom_point()+
-  geom_smooth(method = "lm", se = F)
-
-cor.test(subset(combined_bio_GP_HRV, ssid != 601)$vlfperc.x, subset(combined_bio_GP_HRV, ssid != 601)$vlfperc.y, method = "kendal")
-
-cor.test(subset(combined_bio_GP_HRV, ssid != 601)$vlfpower.x, subset(combined_bio_GP_HRV, ssid != 601)$vlfpower.y, method = "kendal")
-cor.test(subset(combined_bio_GP_HRV, ssid != 601)$lfnu.x, subset(combined_bio_GP_HRV, ssid != 601)$lfnu.y, method = "kendal")
-
-cor.test(subset(combined_bio_GP_HRV, ssid != 601)$pNN50.x, subset(combined_bio_GP_HRV, ssid != 601)$pNN50.y, method = "kendal")
-
-# Kendall's rank correlation tau
-# 
-# data:  subset(combined_bio_GP_HRV, ssid != 601)$vlfperc.x and subset(combined_bio_GP_HRV, ssid != 601)$vlfperc.y
-# T = 163, p-value = 0.000001342
-# alternative hypothesis: true tau is not equal to 0
-# sample estimates:
-#       tau 
-# 0.7157895
-
-cor.test(subset(combined_bio_GP_HRV)$vlfperc.x, subset(combined_bio_GP_HRV)$vlfperc.y, method = "kendal")
-
-# Kendall's rank correlation tau
-# 
-# data:  subset(combined_bio_GP_HRV)$vlfperc.x and subset(combined_bio_GP_HRV)$vlfperc.y
-# T = 174, p-value = 0.000007786
-# alternative hypothesis: true tau is not equal to 0
-# sample estimates:
-#       tau 
-# 0.6571429
-
-# hf
-combined_bio_GP_HRV%>%
-  # subset(ssid!= 601)%>%
-ggplot(aes(hfperent.x, hfperent.y, color = ssid))+
-  geom_point()+
-  geom_smooth(method = "lm", se = F)
-
-cor.test(subset(combined_bio_GP_HRV, ssid != 601)$hfperent.x, subset(combined_bio_GP_HRV, ssid!= 601)$hfperent.y, method = "kendal")
-# Kendall's rank correlation tau
-# 
-# data:  subset(combined_bio_GP_HRV, ssid != 601)$hfperent.x and subset(combined_bio_GP_HRV, ssid != 601)$hfperent.y
-# T = 159, p-value = 0.000007745
-# alternative hypothesis: true tau is not equal to 0
-# sample estimates:
-#       tau 
-# 0.6736842
-
-cor.test(subset(combined_bio_GP_HRV)$hfperent.x, subset(combined_bio_GP_HRV)$hfperent.y, method = "kendal")
-
-# Kendall's rank correlation tau
-# 
-# data:  subset(combined_bio_GP_HRV)$hfperent.x and subset(combined_bio_GP_HRV)$hfperent.y
-# T = 171, p-value = 0.00002292
-# alternative hypothesis: true tau is not equal to 0
-# sample estimates:
-#       tau 
-# 0.6285714
-
-combined_bio_GP_HRV$group <- if_else(combined_bio_GP_HRV$ssid< 400, "NT", "CLIN")
-
-combined_bio_GP_HRV%>%
-  group_by(group)%>%
-  ggplot(aes(group, RMMSSD.x))+
-  geom_jitter(width = .3)+
-  geom_boxplot()
-
-combined_bio_GP_HRV%>%
-  group_by(group)%>%
-  ggplot(aes(group, RMMSSD.x))+
-  geom_jitter(width = .3)+
-  geom_boxplot()
-
-combined_bio_GP_HRV%>%
-  group_by(group)%>%
-  ggplot(aes(group, RMMSSD.y))+
-  geom_jitter(width = .3)+
-  geom_boxplot()
-
-####
-
-combined_bio_GP_HRV%>%
-  group_by(group)%>%
-  ggplot(aes(group, MEANRR.x))+
-  geom_jitter(width = .3)+
-  geom_boxplot()
-
-combined_bio_GP_HRV%>%
-  group_by(group)%>%
-  ggplot(aes(group, MEANRR.y))+
-  geom_jitter(width = .3)+
-  geom_boxplot()
-
-# frequency
-
-combined_bio_GP_HRV%>%
-  group_by(group)%>%
-  ggplot(aes(group, lfperce.x))+
-  geom_jitter(width = .3)+
-  geom_boxplot()
-
-combined_bio_GP_HRV%>%
-  group_by(group)%>%
-  ggplot(aes(group, lfperce.y))+
-  geom_jitter(width = .3)+
-  geom_boxplot()
-
-combined_bio_GP_HRV%>%
-  group_by(group)%>%
-  ggplot(aes(group, hfperent.x))+
-  geom_jitter(width = .3)+
-  geom_boxplot()
-
-combined_bio_GP_HRV%>%
-  group_by(group)%>%
-  ggplot(aes(group, hfperent.y))+
-  geom_jitter(width = .3)+
-  geom_boxplot()
-
-combined_bio_GP_HRV%>%
-    subset(ssid!= 608)%>%
-ggplot(aes(hfpower.x, hfpower.y, color = ssid))+
-  geom_point()+
-  geom_smooth(method = "lm", se = F)
-
-```
-
-HF power
-
-```{r}
-
-combined_bio_GP_HRV%>%
-    subset(ssid!= 608)%>%
-ggplot(aes(hfpower.x, hfpower.y, color = ssid))+
-  geom_point()+
-  geom_smooth(method = "lm", se = F)
-
-cor.test(subset(combined_bio_GP_HRV, ssid != 608)$hfpower.x, subset(combined_bio_GP_HRV, ssid!= 608)$hfpower.y, method = "kendal")
-
-```
-Kendall's rank correlation tau
-
-data:  subset(combined_bio_GP_HRV, ssid != 601)$hfpower.x and subset(combined_bio_GP_HRV, ssid != 601)$hfpower.y
-T = 169, p-value = 0.00000005841
-alternative hypothesis: true tau is not equal to 0
-sample estimates:
-      tau 
-0.7789474
-
-LF power
-
-```{r}
-combined_bio_GP_HRV%>%
-    subset(ssid!= 608 & ssid!= 342)%>%
-ggplot(aes(lfpower.x, lfpower.y, color = ssid))+
-  geom_point()+
-  geom_smooth(method = "lm", se = F)
-
-cor.test(subset(combined_bio_GP_HRV)$hfpower.x, subset(combined_bio_GP_HRV)$hfpower.y, method = "kendal")
-
-cor.test(subset(combined_bio_GP_HRV, ssid !=608& ssid!= 342)$hfpower.x, subset(combined_bio_GP_HRV, ssid !=608& ssid!= 342)$hfpower.y, method = "kendal")
-
-```
-
-# correlations
-
-```{r}
-
-cor.test(GP_HRVanalysys$MEANRR.x,BIO_HRVanalysys$MEANRR.x)
-
-```
-
-```{r}
-# IBI data to compare from biopac
-
-read_plus_ibi_bio <- function(flnm) {
-  data.table::fread(flnm) %>% 
-    mutate(filename = flnm)
-}
-
-# now read
-cleanIBI_bio <-
-  list.files(pattern = "*.txt", 
-             full.names = T) %>% 
-  map_df(~read_plus_ibi_bio(.))
-
-cleanIBI_bio<- cleanIBI_bio%>%
-  rename(IBI_clean = V1)
-
-cleanIBI_bio$ssid<- substr(cleanIBI_bio$filename, 13,15)
-
-# pointcare plots
-
-cleanIBI_gp$IBI_clean_next<- lead(cleanIBI_gp$IBI_clean)
-
-poitcare_gp<- cleanIBI_gp%>%
-  # subset(ssid == 335)%>%
-  group_by(ssid)%>%
-  # mutate(IBI_clean_z = scale(IBI_clean,center = TRUE)[,1])%>%
-  ggplot(aes(IBI_clean, IBI_clean_next,  color = ssid))+
-  geom_point(alpha = .3)+
-  geom_smooth(method = 'lm', se = F)+
-  # facet_grid(~ssid)+
-  xlab("RR[n] (ms)")+
-  ylab("RR[n+1] (ms)")+
-    p$graphstyle
-  # ggtitle("GP3 Gazepoint")+
-  p$graphstyle
-
-poitcare_gp
-
-poitcare_gp <- poitcare_gp +
-  scale_y_continuous(limits = c(400, 1600), breaks = c(400, 1000, 1600))+
-   scale_x_continuous(limits = c(300, 1600), breaks = c(400, 1000, 1600))
-
-scale_x_continuous(limits = c(500, 1300), breaks = c(500, 900, 1300))
-
-poitcare_gp
-
-```
-
-```{r}
-
-  # cleanIBI_bio$ssid<- a
-
-cleanIBI_bio$IBI_clean_next<- lead(cleanIBI_bio$IBI_clean)
-pointcare_bio<-  cleanIBI_bio %>%
-    # subset(ssid == 335)%>%
-  subset(ssid != 341)%>%
-  group_by(ssid)%>%
-  # mutate(IBI_clean_z = scale(IBI_clean,center = TRUE)[,1])%>%
-  ggplot(aes(IBI_clean, IBI_clean_next,  color = ssid))+
-  geom_point(alpha = .3)+
-  geom_smooth(method = 'lm', se = F)+
-  # facet_grid(~ssid)+
-  xlab("RR[n] (ms)")+
-  ylab("RR[n+1] (ms)")+
-    p$graphstyle
-  ggtitle("MP150 BIOPAC")
-
-pointcare_bio<- pointcare_bio+
-  scale_y_continuous(limits = c(500, 1300), breaks = c(500, 900, 1300))+
- scale_x_continuous(limits = c(500, 1300), breaks = c(500, 900, 1300))
-
-pointcare<- poitcare_gp+ pointcare_bio+ plot_annotation(tag_levels = 'A')
-
-```
-
-cleanIBI_gp$group <- if_else(cleanIBI_gp$ssid< 400, 1, 2)
-
-  cleanIBI_gp %>%
-  # subset(ssid != 341)%>%
-  group_by(ssid, group)%>%
-  # mutate(IBI_clean_z = scale(IBI_clean,center = TRUE)[,1])%>%
-  ggplot(aes(IBI_clean, lead(IBI_clean)+IBI_clean,  color = as.factor(group)))+
-
-  geom_smooth(method = 'lm', se = F)
-
-  facet_grid(~ssid)
-
-```
-
-db_parsed_summarised_fix1.2$tNo2<- if_else(as.double(db_parsed_summarised_fix1.2$tNo)< 25, as.double(db_parsed_summarised_fix1.2$tNo), db_parsed_summarised_fix1.2$tNo - 24)
-
-unique(fixationscreen_only3_lmer$tNo2)
-
-#polynomial
-unique(db_parsed_summarised_fix1.2$screencontent)
-
-db_parsed_summarised_fix1.2$ot1<- poly(db_parsed_summarised_fix1.2$tNo2, degree = 1, raw =FALSE)
-
-db_parsed_summarised_fix1.2$ot2<- poly(db_parsed_summarised_fix1.2$tNo2, degree = 2, raw =FALSE)[,2]
-
-db_parsed_summarised_fix1.2$ot1_z<- scale(db_parsed_summarised_fix1.2$ot1, center = TRUE, scale = TRUE)
-db_parsed_summarised_fix1.2$ot2_z<- scale(db_parsed_summarised_fix1.2$ot2, center = TRUE, scale = TRUE)
-
-db_parsed_summarised_fix1.2$block<- if_else(db_parsed_summarised_fix1.2$tNo < 25, -.5, +.5)
-
-db_parsed_summarised_fix1.2$subject<- as.factor(as.character(db_parsed_summarised_fix1.2$ssid))
-
-precision_models$prec_stim <- lmer(RMS ~ (ot1_z + ot2_z) * block+
-                              (0+ ot1_z+ot2_z)+ (1 | ssid), REML = FALSE,
-                             data = subset(db_parsed_summarised_fix1.2,as.numeric(mean_fix_dur) < 3000))
-
-summary(precision_models$prec_stim)
-
-db_parsed_summarised_fix1.2 <- subset(db_parsed_summarised_fix, ssid <500 & tNo> 0)
-
-db_parsed_summarised_fix1.2
-
- #precision correlation with calibratin accuracy
-
-unique(tmp.df4_sum_below500_1.2$cali_order)
-unique(fixationscreen_only2_lmer$tNo)
-fixationscreen_only3_lmer$ssid<- as.character(fixationscreen_only3_lmer$subject)
-
-tmp.df4_sum_below500_1.2$ssid<- as.character(tmp.df4_sum_below500_1.2$ssid)
-
-fixationscreen_only3_lmer$cali_order<- as.character(if_else(fixationscreen_only3_lmer$tNo < 24, 2, 3))
-
-tmp.df4_sum_below500_1.2_select<- select(tmp.df4_sum_below500_1.2, c(ssid, cali_order, avg_error1, cali_no_resc_agg))
-
-fixationscreen_only3_lmer<- left_join(fixationscreen_only3_lmer, tmp.df4_sum_below500_1.2_select)
-
-fixationscreen_only3_lmer %>%
-  group_by(ssid, cali_order)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(avg_error1, precision_visang))+
-  geom_point()+
-geom_smooth(method = 'lm', se = F)+
-  facet_grid(~cali_order)
-
-fixationscreen_only2_lmer_1.2<- fixationscreen_only2_lmer%>%
-  group_by(ssid, cali_order)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)
-
-ggplot(aes(avg_error1, precisi))+
-  geom_point()+
-geom_smooth(method = 'lm', se = F)+
-  facet_grid(~cali_order)
-
-cor.test(subset(fixationscreen_only2_lmer_1.2, cali_order == 2)$avg_error1, subset(fixationscreen_only2_lmer_1.2, cali_order == 2)$h_accuracy_visang)
-
-cor.test(subset(fixationscreen_only2_lmer_1.2, cali_order == 3)$avg_error1, subset(fixationscreen_only2_lmer_1.2, cali_order == 3)$h_accuracy_visang)
-
-# Save an object to a file
-saveRDS(fixationscreen_only3_lmer, file = "fixationscreen_only3_lmer.rds")
-# Restore the object
-readRDS(file = "my_data.rds"
-
-```{r}
-
-View(fixationscreen_only1$)
-
-summary(model_time_acc)
-
-fixationscreen_only2_lmer
-
-options(scipen = 999)
-
-accurcay_models<- list()
-
- #accuracy correlation with calibratin accuracy
-
-unique(tmp.df4_sum_below500_1.2$cali_order)
-unique(fixationscreen_only2_lmer$tNo)
-fixationscreen_only2_lmer$ssid<- as.character(fixationscreen_only2_lmer$ssid)
-
-tmp.df4_sum_below500_1.2$ssid<- as.character(tmp.df4_sum_below500_1.2$ssid)
-
-fixationscreen_only2_lmer$cali_order<- as.character(if_else(fixationscreen_only2_lmer$tNo < 24, 2, 3))
-
-tmp.df4_sum_below500_1.2_select<- select(tmp.df4_sum_below500_1.2, c(ssid, cali_order, avg_error1, cali_no_resc_agg))
-
-fixationscreen_only2_lmer<- left_join(fixationscreen_only2_lmer, tmp.df4_sum_below500_1.2_select)
-
-fixationscreen_only2_lmer %>%
-  group_by(ssid, cali_order)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(avg_error1, v_accuracy_visang))+
-  geom_point()+
-geom_smooth(method = 'lm', se = F)+
-  facet_grid(~cali_order)
-
-fixationscreen_only2_lmer_1.2<- fixationscreen_only2_lmer%>%
-  group_by(ssid, cali_order)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)
-
-ggplot(aes(avg_error1, precisi))+
-  geom_point()+
-geom_smooth(method = 'lm', se = F)+
-  facet_grid(~cali_order)
-
-cor.test(subset(fixationscreen_only2_lmer_1.2, cali_order == 2)$avg_error1, subset(fixationscreen_only2_lmer_1.2, cali_order == 2)$h_accuracy_visang)
-
-cor.test(subset(fixationscreen_only2_lmer_1.2, cali_order == 3)$avg_error1, subset(fixationscreen_only2_lmer_1.2, cali_order == 3)$h_accuracy_visang)
-
-#neither vertical or horizontal or global reach significance
-
-```
-
-fixationscreen_only2$spli_trial %>%
-  ggplot(aes(tNo,accuracy ))+
-  geom_point()
-  #stat_summary(geom = 'pointrange')+
-  geom_vline(xintercept = 24)
-
-#
-
-cor.test(subset(tmp.df4_sum_below500_1.2, cali_order == 2)$cali_no_resc_agg, subset(tmp.df4_sum_below500_1.2, cali_order == 2)$gaze_loss_prop)
-
-cor.test(subset(tmp.df4_sum_below500_1.2, cali_order == 3)$cali_no_resc_agg, subset(tmp.df4_sum_below500_1.2, cali_order == 3)$gaze_loss_prop)
-
-Pupil analysis
-
-```{r}
-readRDS(file = "db_full6new_304_up_500less.rds")
-
-db_full4new_stim_pupil$ssid
-db_full4new_stim_pupil$subject
-View(db_full6new_304_up)
-
-db_full6new_304_up_500less<- subset(db_full6new_304_up, subject< 500 & tNo > 0)
-
-db_full4new_stim_pupil$BIO_Global.Mean
-
-db_full6new_304_up_500less$Bio_Mean_HR_z
-
-unique(db_full6new_304_up_500less$screencontent)
-
-db_full6new_304_up_500less$Bio_Mean_HR_z<- scale(db_full6new_304_up_500less$Bio_Mean_HR, center = TRUE, scale = TRUE)
-db_full6new_304_up_500less$BIO_Global.Mean_z<- scale(db_full6new_304_up_500less$BIO_Global.Mean, center = TRUE, scale = TRUE)
-db_full6new_304_up_500less$pup_basCor_z<- scale(db_full6new_304_up_500less$pup_basCor, center = TRUE, scale = TRUE)
-
-db_full6new_304_up_500less$hr_interp<- scale(db_full6new_304_up_500less$hr_interp, center = TRUE, scale = TRUE)
-
-# Pupil
-
-```
-
-```
-```{r}
-
-summary(lmer(arousal ~  pup_basCor_z + BIO_Global.Mean_z + Bio_Mean_HR_z +ArousalMean+ (1 | stimIAPS) +(1 | ssid), REML = FALSE,
-                      data = subset(db_full6new_304_up_500less)))
-
-summary(lmer(pup_basCor_z ~  ArousalMean + (1 | stimIAPS)  +(1 | ssid), REML = FALSE,
-                      data = db_full6new_304_up_500less))
-
-cognitivepupil$pup_arous_brigh <- lmer(pup_basCor ~  arousal_c +  BRIGHTNESSc +(1 | stimIAPS)  +(1 | ssid), REML = FALSE,
-                      data = db_full6new_304_up_500less)
-summary(cognitivepupil$pup_arous_brigh)
-
-MuMIn::r.squaredGLMM(cognitivepupil$pup_arous_brigh)
-
-library(lmerTest)
-
-cognitivepupil$pup_arous_1 <- lmer(pup_basCor ~  arousal_c +( 1| stimIAPS)  +(1 | ssid), REML = FALSE,
-                      data = db_full6new_304_up_500less)
-
-library(readr)
-library(tidyverse)
-cognitivepupil$pup_arous_1bri <- lmer(pup_basCor ~  BRIGHTNESSc +( 1| stimIAPS)  +(1 | ssid), REML = FALSE,
-                      data = db_full6new_304_up_500less)
-
-MuMIn::r.squaredGLMM(cognitivepupil$pup_arous_1)
-MuMIn::r.squaredGLMM(cognitivepupil$pup_arous_1bri) # 20
-
-db_full6new_304_up_500less$fit_pup_arou_bright<- 
-  predict(cognitivepupil$pup_arous_brigh, type = c("response"), terms = "BRIGHTNESSc")
-?predict
-
-pupil_plots<- list()
-
-write_csv(db_full6new_304_up_500less, "Pupil_data_db_full6new_304_up_500less.csv")
-
-pupil_plots$brightness<-  db_full6new_304_up_500less %>%
-  #subset(!is.na(Alexithymia))%>%
-  group_by(ssid,stimIAPS) %>%
-  summarise_at(c("arousal_c", "TASc","BRIGHTNESSc", "pup_basCor", "fit_pup_arou_bright"), mean, na.rm = TRUE)%>%
-  ggplot(aes(BRIGHTNESSc, pup_basCor, color = ssid))+
-  geom_point(alpha = .3)+
-  geom_smooth(aes(group = ssid), method = 'lm', se = F)+
-  stat_smooth (geom="line", method = 'lm', alpha = .8, size = 1.5, color = "gray30")+
-    ylab('Pupilary change (z)')+
-  xlab('Brightness (z)')+
-  p$graphstyle
-    scale_color_brewer(palette = "Dark2")
-
-pupil_plots$brightness<- pupil_plots$brightness+
-  scale_y_continuous(limits = c(-12,4), breaks = c(-12,-4, 4))+
-  scale_x_continuous(limits = c(-2.5,2), breaks = c(-2.5,-0, 2))
-
-library(dplyr)
-
-pupil_plots$arousalpup<-  db_full6new_304_up_500less %>%
-  #subset(!is.na(Alexithymia))%>%
-  group_by(ssid,stimIAPS) %>%
-  summarise_at(c("arousal", "TASc", "pup_basCor", "fit_pup_arou_bright"), mean, na.rm = TRUE)%>%
-  ggplot(aes(pup_basCor, arousal, color = ssid))+
-  geom_point(alpha = .3)+
-  geom_smooth(aes(group = ssid), method = 'lm', se = F)+
-  stat_smooth (geom="line", method = 'lm', alpha = .8, size = 1.5, color = "gray30")+
-    ylab('Pupilary change (z)')+
-  xlab('Self reported arousal (z)')+
-  p$graphstyle
-  scale_color_brewer(palette = "Dark2")
-
-pupil_plots$arousalpup
-
-pupil_plots$arousalpup<- pupil_plots$arousalpup+
-  scale_y_continuous(limits = c(-10,10), breaks = c(-10,0, 10))+
-  scale_x_continuous(limits = c(-12,6), breaks = c(-12,6))
-
-pupil_plots$arousalpup
-# Save an object to a file
-saveRDS(db_full6new_304_up_500less, file = "db_full6new_304_up_500less.rds")
-# Restore the object
-
-library(patchwork)
-library(ggplot2)
-
-patchpup<- pupil_plots$arousalpup+ pupil_plots$brightness+theme(axis.title.y = element_blank())
-patchpup<- patchpup+plot_annotation(tag_levels = 'A')
-
-ggsave("patchpup.tiff", patchpup, device = 'tiff', width = 10, height = 6, dpi = 800)
-```
-
-Quick check Hr pulse
-
-```
-```{r}
-
-unique(one$ssid)
-
-one1<- subset(one, ssid == 336)
-
-# pp340 <- subset(tmp.df4_full, tNo = -7 & ssid == 340)
-
-one1 %>%
-  ggplot(aes(time - min(time), hrp))+
-  geom_line()+
-  xlim(0,30)
-
-hrclass<-  kmeans(one1$hrp, 2, nstart = 25)
-
-one1$hrclass<- hrclass$cluster
-
-one1$time2hr<- if_else(one1$hrclass == 2, one1$time - min(one1$time), NULL)
-
-stats::fil
-one1 %>%
-  ggplot(aes(time-min(time), stats::filter(hrp, 1)))+
-  geom_line()+
-  geom_vline(aes(xintercept = time2hr), alpha = .05, color = "red")+
-  xlim(50, 80)+ theme_classic()
-
-```
+  map_df(~read_biohr(.))
+
+db_biohr$ssid<- substr(db_biohr$filename, 6,8)
+db_biohr$order<- db_biohr$Order
+
+db_biohr$Order<- NULL
+db_biohr$filename<- NULL
+db_biohr$trigger<- as.factor(as.character(db_biohr$trigger))
+unique(tmp.df4_sum_full_bio$ssid)
+unique(db_biohr$ssid)
+tmp.df4_sum_full_bio$trigger<- as.factor(as.character(tmp.df4_sum_full_bio$trigger))
+
+db_biohr$ssid<- as.factor(as.character(db_biohr$ssid))
+tmp.df4_sum_full_bio_hr<- left_join(tmp.df4_sum_full_biot, db_biohr, by = c('ssid', 'order', 'trigger'))
+
+ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(hr, HR_BIO))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(CDA.PhasicMax.x, CDA.PhasicMax.y))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+tmp.df4_sum_full_bio_hr_stim<- subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent != 'fixation')
+
+cor(tmp.df4_sum_full_bio_hr_stim$hr, tmp.df4_sum_full_bio_hr_stim$HR_BIO, use = 'complete')
+
+# tmp.df4_sum_full_bio_hr_stim_1<- subset(tmp.df4_sum_full_bio_hr_stim, tmp.df4_sum_full_bio_hr_stim$HR_BIO> 50)
+
+tmp.df4_sum_full_bio_hr_stim$valence_cat<- if_else(tmp.df4_sum_full_bio_hr_stim$valence >0, 'pos',
+                                                  if_else(tmp.df4_sum_full_bio_hr_stim$valence < 0, 'neg', 'neutral'))
+
+unique(tmp.df4_sum_full_bio_hr_stim$screencontent)
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+  # facet_grid(~valence_cat)
+
+cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$arousal, use = 'complete')
+cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$valence, use = 'complete')
+
+tmp.df4_sum_full_bio_hr_stim%>%
+      group_by(ssid, IAS)%>%
+      summarise(corr = cor(HR_BIO, arousal, use = 'complete'))%>%
+  summarise(new = cor(corr, IAS))
+  # summarise_at(c('TAS'), mean)
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  facet_grid(~valence_cat)
+
+tmp.df4_sum_full_bio_hr_stim%>%
+group_by(valence_cat)%>%
+  summarise(corr = cor(HR_BIO, arousal, use = 'complete'))
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, valence))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  facet_grid(~valence_cat)
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, ValenceMean))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+  # facet_grid(~valence_cat)
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, mean_sac_dur))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  facet_grid(~valence_cat)
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, pup_basCor))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  facet_grid(~valence_cat)
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, Global.Mean.y))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, TAS))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, `DASS Anxiety`))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+```

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

@@
 colnames(tmp.df3)
-db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49 ))
+db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49,51 ))
 db_GSR$tNo<- NULL
@@
 
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021")
+
     for (ssid in names(split_gsr)) {
@@
 tmp.df3<- tmp.df3%>%
-  arrange(ssid, tNo,time)%>%
+  arrange(ssid, time,tNo)%>%
   group_by(ssid, tNo, gsr_bastrue)%>%
@@
 tmp.df3<- tmp.df3 %>%
-  arrange(ssid, trialUnq,tNo, time)%>%
+  arrange(ssid, time,tNo)%>%
   group_by(ssid, trialUnq,tNo,screencontent) %>%
@@
 # vert order dependent
-tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
+tmp.df3 <- gazer::smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                     extendblinks=TRUE, step.first= 'smooth',
@@
   geom_line()+
-   geom_line(aes(y = extendpupil), color = 'red')+
+   # geom_line(aes(y = extendpupil), color = 'red')+
   # geom_line(aes(y = pup_interp), colour = 'gray')+
@@
     geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
+
+ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
+    # geom_smooth(se = F)+
+  geom_line()+
+    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
+    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)+
+  xlim(-3,3)
+
+subset(tmp.df3, tNo == 10)%>%
+  group_by(ssid, tNo)%>%
+  mutate(pupil_z = pup_interp_mad - mean(pup_interp_mad))%>%
+ggplot(aes(x = timerezero3, y= pupil_z))+
+    # geom_smooth(se = F)+
+  geom_smooth()+
+    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
+    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
+    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)+
+  xlim(-6,15)
 ```

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

@@
 
+# preparation
 subset(tmp.df3, tNo == 10)%>%
   group_by(ssid, tNo)%>%
-  mutate(pupil_z = pup_interp_mad - mean(pup_interp_mad))%>%
+  mutate(pupil_z = pup_interp_mad - mean(pup_interp_mad, na.rm = TRUE))%>%
+  ungroup()%>%
 ggplot(aes(x = timerezero3, y= pupil_z))+
     # geom_smooth(se = F)+
-  geom_smooth()+
+  stat_summary(fun = mean, geom = 'line')+
     geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
@@
     geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)+
-  xlim(-6,15)
+  xlim(-3,15)
 ```
@@
 ```{r}
+# rest period
 ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
@@
 tmp.df3<- tmp.df3%>%
-  arrange(ssid,tNo, time)
+  arrange(ssid, time,tNo)
 

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

@@
 
-tmp.df4 <- tmp.df4%>%
+tmp.df4 <- tmp.df4 %>%
   group_by(ssid, tNo, trialUnq, text)%>%
@@
 colnames(tmp.df4)
-write_csv(tmp.df4, 'interodata_clean_gp.csv')
+write_csv(tmp.df4, 'interodata_clean_gp_346_355.csv')
 

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

@@
 
+  setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/346_355")
+
   (sprintf("writing for gazepath"))
@@
 ```
+
 process gazepath and ledalab
+
+gazepath settings
+
+left eye x coord: left_gaze_x_cor_pix
+left eye y coord: left_gaze_y_cor_pix
+
+didtance: distance (mm)
+
+right eye x coord: right_gaze__cor_pix
+right eye y coord: right_gaze_x_cor_pix
+didtance: distance (mm)
+
+trial index: trialnq
+
+sample rate: 150
+screen resolution height (pix): 1200
+screen resolution width (pix): 1920
+
+stimuli height (px): 768
+stimuli width (px): 1024
+variables to keep: trial unq
+
 ```{r}
+
+install.packages('gazepath')
 library(gazepath)

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

@@
 
+203
+270
+
 ```{r}
 
-install.packages('gazepath')
+# install.packages('gazepath')
 library(gazepath)
@@
 Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 105 .01 2])
+
 ```{r}

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

@@
 
-# Import Ledalab
-Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 105 .01 2])
-
-```{r}
-read_leda <- function(flnm) {
-  data.table::fread(flnm) %>% 
-    mutate(filename = flnm)
-}
-
-# now read them
-db_leda <-
-  list.files(pattern = "*.txt", 
-             full.names = T) %>% 
-  map_df(~read_leda(.))
-
-db_leda$trigger<- as.numeric(db_leda$Event.NID)
-unique(db_leda$trigger)
-db_leda$ssid<- as.numeric(substr(db_leda$filename, 13,15))
-colnames(tmp.df4_sum)
-colnames(db_leda)
-nrow(tmp.df4_sum)
-nrow(db_leda)
-colnames(tmp.df4_sum)
-tmp.df4_sum2<- subset(tmp.df4_sum,tmp.df4_sum$tNo != -7)
-tmp.df4_sum2<- tmp.df4_sum2%>%
-  arrange(ssid, time, tNo)%>%
-  group_by(ssid)%>%
-  mutate(order = 1:224)
-
-db_leda2<- subset(db_leda, db_leda$trigger != -7)
-db_leda2<- db_leda2%>%
-  arrange(ssid, Event.Nr)%>%
-  group_by(ssid)%>%
-  mutate(order = 1:224)
-
-tmp.df4_sum_fullt<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
-tmp.df4_sum_full_backup<- tmp.df4_sum_full
-
-tmp.df4_sum_full<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
-
-# tmp.df4_sum_full<- bind_cols(tmp.df4_sum, db_leda)
-
-tmp.df4_sum_full<- tmp.df4_sum_full%>%
-  arrange(ssid, tNo)
-```
-
 read parsed data
@@
 # return content between spaces
-# pu things in the correct order
-# library(stringr)
+# put things in the correct order
+library(stringr)
+
 db_parsed$screencontent<- str_extract(db_parsed$trialUnq, "(?<=\\s)(.*)(?=\\s)")
@@
 write_csv(db_parsed, 'db_parsed.csv')
+write_csv(db_parsed, 'db_parsed_346_355.csv')
 
@@
 write_csv(db_parsed_summarised2, 'db_parsed_summarised.csv')
+write_csv(db_parsed_summarised2, 'db_parsed_summarised_346_355.csv')
 
@@
 db_parsed_summarised2
-tmp.df4_sum_full<- left_join(tmp.df4_sum_full,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))
-rm(tmp.df4_sum_fullt)
-testna<- subset(tmp.df4_sum_fullt, is.na(tmp.df4_sum_fullt$mean_fix_dur) == TRUE)
-
-tmp.df4_sum_fullt
+
+# merge parsed with eyetracking data
+# tmp.df4_sum_full<- left_join(tmp.df4_sum_full,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent")) #original
+
+tmp.df4_sum_full<- left_join(tmp.df4_sum,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))
+
+# rm(tmp.df4_sum_fullt)
+# testna<- subset(tmp.df4_sum_fullt, is.na(tmp.df4_sum_fullt$mean_fix_dur) == TRUE)
+# 
+# tmp.df4_sum_fullt
 ```
@@
 ```{r}
-colnames(X309_2019_Dec_11_1807_01)
+# colnames(X309_2019_Dec_11_1807_01)
 library(data.table) 
@@
 
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/IAPSBehav/346_355")
 # now read them
@@
 
-db328$condition<-db328$ï..condition
+# problem file
+# db328$condition<-db328$ï..condition
 
@@
 
-# files <- list.files(pattern = ".csv")
-# temp <- do.call(rbind,lapply(files, read.csv), header = TRUE)
+files <- list.files(pattern = ".csv")
+files
+temp <- do.call(rbind,lapply(files, read.csv), header = TRUE)
 
@@
 
+# Import Ledalab
+Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 105 .01 2])
+
+etwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021")
+
+SC column = 2
+Event marker column 3
+sampling rate 150hz
+
+```{r}
+read_leda <- function(flnm) {
+  data.table::fread(flnm) %>% 
+    mutate(filename = flnm)
+}
+
+# now read them
+db_leda <-
+  list.files(pattern = "*.txt", 
+             full.names = T) %>% 
+  map_df(~read_leda(.))
+
+db_leda$trigger<- as.numeric(db_leda$Event.NID)
+unique(db_leda$trigger)
+db_leda$ssid<- as.numeric(substr(db_leda$filename, 13,15))
+colnames(tmp.df4_sum)
+colnames(db_leda)
+nrow(tmp.df4_sum)
+nrow(db_leda)
+colnames(tmp.df4_sum)
+tmp.df4_sum2<- subset(tmp.df4_sum,tmp.df4_sum$tNo != -7)
+tmp.df4_sum2<- tmp.df4_sum2%>%
+  arrange(ssid, time, tNo)%>%
+  group_by(ssid)%>%
+  mutate(order = 1:224)
+
+db_leda2<- subset(db_leda, db_leda$trigger != -7)
+db_leda2<- db_leda2%>%
+  arrange(ssid, Event.Nr)%>%
+  group_by(ssid)%>%
+  mutate(order = 1:224)
+
+tmp.df4_sum_fullt<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
+tmp.df4_sum_full_backup<- tmp.df4_sum_full
+
+tmp.df4_sum_full<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
+
+# tmp.df4_sum_full<- bind_cols(tmp.df4_sum, db_leda)
+
+tmp.df4_sum_full<- tmp.df4_sum_full%>%
+  arrange(ssid, tNo)
+```
+
 check

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

@@
 db_beh2<- db_beh
+
+# problem
 db328$filename<- as.character(db328$filename)
@@
 unique(db_beh2$ssid)
+
 # create one column for arousl and RT
@@
 colnames(db_beh2)
+
 db_beh2$triggeracq<- db_beh2$trigger
@@
 colnames(db_beh3)
+
 colnames(db_beh3_301_309)
+
 db_beh3$trigger<-NULL
@@
 db_beh3_301_309$condition[db_beh3_301_309$condition == "Example Stimuli"]<- "Practice"
+
 db_beh3$condition[db_beh3$condition == "Example Stimuli"]<- "Practice"
 
-db_beh3$triggeracq<- NULL
+# db_beh3$triggeracq<- NULL
 
@@
 
-db_beh3$ssid<- as.numeric(db_beh3$ssid)
+db_beh3$ssid <- as.numeric(db_beh3$ssid)
 # rm(tmp.df4_sum_full_t)
@@
 tmp.df4_sum_full<- left_join(tmp.df4_sum, db_beh_all, by = c('ssid', 'tNo'))
+tmp.df4_sum_full$ssid<- as.numeric(tmp.df4_sum_full$ssid)
+
+tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_beh3, by = c('ssid', 'tNo'))
 

### 2021-08-21 Experiment 2.Rmd
Update Experiment 2.Rmd
quest

@@
 
+```
+
 # self reports
+- New Tas is already scored
+- score AQ, etc using https://xavierrg.shinyapps.io/datacleaning
+
+gorilla codes
+
+STAI:: 5nzr
+AQ:7uqw
+STAIS: 8rfo
+Demog: 8zto
+BVAQ: 83b1
+BPQ: bbc4
+DASS: chif
+IQ: esh8
+IAS: jvi8
+TAS:pdlt
+demog_meantal health: v2gn
+
+consent: 8nsp
+
+```{r}
 
@@
 Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 105 .01 2])
+
+Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','biopac','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2])
 

### 2021-08-21 Questionnaires_scoring2021.Rmd
quest

---
title: "Scoring_questionnaires2021"
author: "Helio"
date: "21/08/2021"
output: html_document
---

AQ_50

```{r}
# Traditional scoring

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/data_exp_11458-v9 (2)/Select")

library(readr)

db_quest_checkAQ<- read_csv("data_exp_11458-v8_questionnaire-7uqw.csv")
View(db_quest_checkAQ)

library(tidyverse)
colnames(db_quest_checkAQ)

db_quest_checkAQ<- db_quest_checkAQ%>%
  select(c(16,31:130))

db_quest_checkAQ_1<- db_quest_checkAQ%>%
select(seq(1, 101, 2))

# create a prefix for AQ items
# https://it.unt.edu/sites/default/files/paste_jds_jun2013.pdf - some nice tips here
prefix<- "AQ_"

AQ_counter<- seq(1,50)

aq_labels<-paste(prefix, AQ_counter, sep = "")
# generate odd numbers to match the columns we wnt to keep
names<- c("completion_code", aq_labels)

# rename dataset
names(db_quest_checkAQ_1)<- names

db_quest_checkAQ_2<- db_quest_checkAQ_1 %>%
#   mutate_at(c('TAS_4', 'TAS_5', 'TAS_10', 'TAS_18', 'TAS_19'), 
#             funs(recode(., "1=5; 2=4; 3=3; 4=2; 5 =1")))%>%
# #    2, 4, 5, 6, 7, 9, 12, 13, 16, 18,
# # 19, 20, 21, 22, 23, 26, 33, 35, 39, 41, 42, 43, 45, 46
  mutate_at(c("AQ_2", "AQ_4", "AQ_5", "AQ_6", "AQ_7", "AQ_9", "AQ_12", "AQ_13", "AQ_16", "AQ_18",
                 "AQ_19","AQ_20", "AQ_21", "AQ_22", "AQ_23", "AQ_26", "AQ_33", "AQ_35", "AQ_39", "AQ_41",
                 "AQ_42",
                 "AQ_43", "AQ_45", "AQ_46"), 
            funs(ifelse(. <= 2, 1, 0)))%>%
            # funs(recode(., "1=1; 2=1; 3=0; 4=0")))%>%
   mutate_at(c("AQ_1", "AQ_3", "AQ_8", "AQ_10", "AQ_11", "AQ_14", "AQ_15", "AQ_17", "AQ_24", "AQ_25",
                 "AQ_27","AQ_28", "AQ_29", "AQ_30", "AQ_31", "AQ_32", "AQ_34", "AQ_36", "AQ_37", "AQ_38",
                 "AQ_40",
                 "AQ_44", "AQ_47", "AQ_48", "AQ_49", "AQ_50"), 
             funs(ifelse(. > 2, 1, 0)))
             # funs(recode(., "1=0; 2=0; 3=1; 4=1")))

db_quest_checkAQ_2%>%
  # mutate(DIF = TAS_1 + TAS_3 + TAS_6 + TAS_7 + TAS_9 + TAS_13+ TAS_14)%>%
  # mutate(EOT = TAS_8+TAS_15+TAS_16+TAS_20+TAS_5+TAS_10+TAS_18+TAS_19)%>%
  # mutate(DDF = TAS_2+TAS_11+TAS_12+TAS_17+TAS_4)%>%
  mutate(SS = AQ_1+ AQ_11+ AQ_13 + AQ_15+ AQ_22 + AQ_36 + AQ_44 + AQ_45 + AQ_47 + AQ_48)%>%
  mutate(AS = AQ_2+ AQ_4 + AQ_10+AQ_16+AQ_25+AQ_32+AQ_34+AQ_37+AQ_43+AQ_46)%>%
  mutate(ATD = AQ_5+AQ_6+AQ_9+AQ_12+AQ_19+ AQ_23+AQ_28+AQ_29+AQ_30+AQ_49)%>%
  mutate(COM = AQ_7+AQ_17+AQ_18+AQ_26+AQ_27+AQ_31+AQ_33+AQ_35+AQ_38+AQ_39)%>%
  mutate(IMAG = AQ_3+AQ_8+AQ_14+AQ_20+AQ_21+ AQ_24+AQ_40+AQ_41+AQ_42+AQ_50)%>%
  # mutate(TAS_Total = DIF + DDF + EOT)%>%
  mutate(AQ_Total = SS + AS +ATD + COM + IMAG)%>%
  select(c(completion_code, AQ_Total))
  ggplot(aes(TAS_Total, AQ_Total))+
  geom_point()+
  facet_grid(~Dataset)

```

this confirms that Lucys scoring is correct

### 2021-08-21 Questionnaires_scoring2021.Rmd
Update Questionnaires_scoring2021.Rmd

@@
 
+gorilla codes
+
+STAI:: 5nzr
+AQ:7uqw
+STAIS: 8rfo
+Demog: 8zto
+BVAQ: 83b1
+BPQ: bbc4
+DASS: chif
+IQ: esh8
+IAS: jvi8
+TAS:pdlt
+demog_meantal health: v2gn
+
 AQ_50
+
+quick check that Lucys scoring are correct
 
@@
 
-this confirms that Lucys scoring is correct
+this confirms that Lucy scoring is correct
+also checked a few examples of TAS seem correct. but should note one inconsistency in the first participant (300)
+
+AQ_50
+
+```{r}
+
+# 345_356
+read_selfrep <- function(flnm) {
+    read_csv(flnm) %>%
+        mutate(filename = flnm)
+}
+
+db_AQ <- list.files(pattern = "*.csv", 
+               full.names = T) %>% 
+    map_df(~read_selfrep(.))
+
+db_AQ<- subset(db_AQ, db_AQ$`Event Index`== 1)
+
+View(db_AQ)
+
+library(tidyverse)
+colnames(db_AQ)
+
+db_AQ1<- db_AQ%>%
+  select(c(16,33:132))
+
+colnames(db_AQ1)
+
+db_AQ2<- db_AQ1%>%
+select(seq(1, 101, 2))
+
+# create a prefix for AQ items
+# https://it.unt.edu/sites/default/files/paste_jds_jun2013.pdf - some nice tips here
+prefix<- "AQ_"
+
+AQ_counter<- seq(1,50)
+
+aq_labels<-paste(prefix, AQ_counter, sep = "")
+# generate odd numbers to match the columns we wnt to keep
+names<- c("completion_code", aq_labels)
+
+# rename dataset
+names(db_AQ2)<- names
+
+db_AQ3<- db_AQ2 %>%
+#   mutate_at(c('TAS_4', 'TAS_5', 'TAS_10', 'TAS_18', 'TAS_19'), 
+#             funs(recode(., "1=5; 2=4; 3=3; 4=2; 5 =1")))%>%
+# #    2, 4, 5, 6, 7, 9, 12, 13, 16, 18,
+# # 19, 20, 21, 22, 23, 26, 33, 35, 39, 41, 42, 43, 45, 46
+  mutate_at(c("AQ_2", "AQ_4", "AQ_5", "AQ_6", "AQ_7", "AQ_9", "AQ_12", "AQ_13", "AQ_16", "AQ_18",
+                 "AQ_19","AQ_20", "AQ_21", "AQ_22", "AQ_23", "AQ_26", "AQ_33", "AQ_35", "AQ_39", "AQ_41",
+                 "AQ_42",
+                 "AQ_43", "AQ_45", "AQ_46"), 
+            funs(ifelse(. <= 2, 1, 0)))%>%
+            # funs(recode(., "1=1; 2=1; 3=0; 4=0")))%>%
+   mutate_at(c("AQ_1", "AQ_3", "AQ_8", "AQ_10", "AQ_11", "AQ_14", "AQ_15", "AQ_17", "AQ_24", "AQ_25",
+                 "AQ_27","AQ_28", "AQ_29", "AQ_30", "AQ_31", "AQ_32", "AQ_34", "AQ_36", "AQ_37", "AQ_38",
+                 "AQ_40",
+                 "AQ_44", "AQ_47", "AQ_48", "AQ_49", "AQ_50"), 
+             funs(ifelse(. > 2, 1, 0)))
+             # funs(recode(., "1=0; 2=0; 3=1; 4=1")))
+
+db_AQ4<- db_AQ3%>%
+  # mutate(DIF = TAS_1 + TAS_3 + TAS_6 + TAS_7 + TAS_9 + TAS_13+ TAS_14)%>%
+  # mutate(EOT = TAS_8+TAS_15+TAS_16+TAS_20+TAS_5+TAS_10+TAS_18+TAS_19)%>%
+  # mutate(DDF = TAS_2+TAS_11+TAS_12+TAS_17+TAS_4)%>%
+  mutate(SS = AQ_1+ AQ_11+ AQ_13 + AQ_15+ AQ_22 + AQ_36 + AQ_44 + AQ_45 + AQ_47 + AQ_48)%>%
+  mutate(AS = AQ_2+ AQ_4 + AQ_10+AQ_16+AQ_25+AQ_32+AQ_34+AQ_37+AQ_43+AQ_46)%>%
+  mutate(ATD = AQ_5+AQ_6+AQ_9+AQ_12+AQ_19+ AQ_23+AQ_28+AQ_29+AQ_30+AQ_49)%>%
+  mutate(COM = AQ_7+AQ_17+AQ_18+AQ_26+AQ_27+AQ_31+AQ_33+AQ_35+AQ_38+AQ_39)%>%
+  mutate(IMAG = AQ_3+AQ_8+AQ_14+AQ_20+AQ_21+ AQ_24+AQ_40+AQ_41+AQ_42+AQ_50)%>%
+  # mutate(TAS_Total = DIF + DDF + EOT)%>%
+  mutate(AQ = SS + AS +ATD + COM + IMAG)%>%
+  select(c(completion_code, AQ))
+
+```
+
+TAS-28
+
+```{r}
+
+read_selfrep <- function(flnm) {
+    readxl::read_xlsx(flnm) %>%
+        mutate(filename = flnm)
+}
+
+db_TAS <- list.files(pattern = "*-pdlt.xlsx", 
+               full.names = T) %>% 
+    map_df(~read_selfrep(.))
+
+db_TAS<- subset(db_TAS, db_TAS$`Event Index`== 1)
+
+View(db_TAS)
+
+library(tidyverse)
+colnames(db_TAS)
+
+db_TAS1<- db_TAS%>%
+  select(c(16,33:71))
+
+colnames(db_TAS1)
+
+db_TAS2<- db_TAS1%>%
+select(c(1,seq(2, 40, 2)))
+
+db_TAS2
+# note the gorilal tas labels have a zero, like 01 instead of 1
+?recode
+db_TAS3<- db_TAS2 %>%
+  mutate_at(c('TAS_04', 'TAS_05', 'TAS_10', 'TAS_18', 'TAS_19'), 
+            funs(car::recode(., "1=5; 2=4; 3=3; 4=2; 5 =1")))%>%
+  mutate(DIF = TAS_01 + TAS_03 + TAS_06 + TAS_07 + TAS_09 + TAS_13+ TAS_14)%>%
+  mutate(EOT = TAS_08+TAS_15+TAS_16+TAS_20+TAS_05+TAS_10+TAS_18+TAS_19)%>%
+  mutate(DDF = TAS_02+TAS_11+TAS_12+TAS_17+TAS_04)%>%
+  mutate(TAS = DIF + DDF + EOT)
+
+db_TAS3$completion_code<- db_TAS3$`Participant Completion Code`
+
+db_TAS4<- select(db_TAS3, c(completion_code, TAS))
+
+```
+
+DASS: chif
+
+# Function that scores DASS-21 and all subscales. DASS-21 is a 21-item scale
+# (0-3 likert) measuring the participant's levels of depression, anxiety, and 
+# stress. DASS is based on a dimensional understanding of these factors - 
+# each of the 21 items is mapped to one of the three factors.
+# Dependencies: tidyverse, 03_scoring_helpers.R
+
+subscales need to be multiplied by 2
+
+```{r}
+read_selfrep <- function(flnm) {
+    read_csv(flnm) %>%
+        mutate(filename = flnm)
+}
+
+db_DASS <- list.files(pattern = "*-chif.csv", 
+               full.names = T) %>% 
+    map_df(~read_selfrep(.))
+
+db_DASS<- subset(db_DASS, db_DASS$`Event Index`== 1)
+
+score_DASS <- function(df) {
+  DASS_data <- as_tibble(df) %>% # Building this df to make debugging easier
+    select("Participant Private ID", DASS_01:DASS_21)
+
+  DASS_score <- tibble(
+    "Participant Private ID" = DASS_data$`Participant Private ID`,
+    DASS_score_total =         sumvars(.df = DASS_data,
+                                       DASS_01:DASS_21),
+
+    # Depression subscale is items 3, 5, 10, 13, 16, 17, and 21
+    DASS_subscale_depression = sumvars(.df = DASS_data,
+                                       DASS_03, DASS_05, DASS_10, DASS_13,
+                                       DASS_16, DASS_17, DASS_21),
+
+    # Anxiety subscale is items 2, 4, 7, 9, 15, 19, and 20
+    DASS_subscale_anxiety =    sumvars(.df = DASS_data,
+                                       DASS_02, DASS_04, DASS_07, DASS_09,
+                                       DASS_15, DASS_19, DASS_20),
+
+    # Stress subsccale is items 1, 6, 8, 11, 12, 14, and 18
+    DASS_subscale_stress =     sumvars(.df = DASS_data,
+                                       DASS_01, DASS_06, DASS_08, DASS_11,
+                                       DASS_12, DASS_14, DASS_18)
+  )
+  return(DASS_score)
+}
+
+```

### 2021-08-21 Questionnaires_scoring2021.Rmd
Update Questionnaires_scoring2021.Rmd

@@
 
-score_DASS <- function(df) {
-  DASS_data <- as_tibble(df) %>% # Building this df to make debugging easier
-    select("Participant Private ID", DASS_01:DASS_21)
+colnames(db_DASS)
+db_DASS1<- db_DASS%>%
+  select(c(12,13,16,33:73))
 
-  DASS_score <- tibble(
-    "Participant Private ID" = DASS_data$`Participant Private ID`,
-    DASS_score_total =         sumvars(.df = DASS_data,
-                                       DASS_01:DASS_21),
+colnames(db_DASS1)
 
+db_DASS2<- db_DASS1%>%
+select(c(1:3,seq(4, 44, 2)))
+
+db_DASS2$DASS_08<- db_DASS2$STAI_08
+
+db_DASS2$STAI_08<- NULL
+
+db_DASS3 <- db_DASS2 %>%
+  # mutate(DASS_score_total =         rowsum(
+  #                                      DASS_01:DASS_21))
+  #   
     # Depression subscale is items 3, 5, 10, 13, 16, 17, and 21
-    DASS_subscale_depression = sumvars(.df = DASS_data,
-                                       DASS_03, DASS_05, DASS_10, DASS_13,
-                                       DASS_16, DASS_17, DASS_21),
-
+    mutate(DASSDepression = 2*(DASS_03+ DASS_05+ DASS_10+ DASS_13+
+                                       DASS_16+ DASS_17+ DASS_21),
     # Anxiety subscale is items 2, 4, 7, 9, 15, 19, and 20
-    DASS_subscale_anxiety =    sumvars(.df = DASS_data,
-                                       DASS_02, DASS_04, DASS_07, DASS_09,
-                                       DASS_15, DASS_19, DASS_20),
+    DASSAnxiety =    2*(DASS_02+ DASS_04+ DASS_07+ DASS_09+
+                                       DASS_15+ DASS_19+ DASS_20),
 
     # Stress subsccale is items 1, 6, 8, 11, 12, 14, and 18
-    DASS_subscale_stress =     sumvars(.df = DASS_data,
-                                       DASS_01, DASS_06, DASS_08, DASS_11,
-                                       DASS_12, DASS_14, DASS_18)
-  )
-  return(DASS_score)
-}
+    # on gorilla DAS_08 is islabeled STAI_08
+    DASSStress =     2*(DASS_01+ DASS_06+ DASS_08+ DASS_11+
+                                       DASS_12+ DASS_14+ DASS_18)
+    )%>%
+  mutate(DASSTotal = DASSDepression+DASSAnxiety+DASSStress)
+
+colnames(db_DASS3)
+db_DASS3$completion_code<- db_DASS3$`Participant Completion Code`
+
+db_DASS4<- select(db_DASS3, c(1:2,29,25:28))
 
 ```
+
+IAS: jvi8
+working well om the app
+https://xavierrg.shinyapps.io/datacleaning/
+```{r}
+library(readr)
+db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/345_346_IAS_2021-08-21.csv")
+View(db_IAS)
+
+```
+
+BVAQ: 83b1
+BPQ: bbc4
+
+# Function that scores the Body Perception Questionnaire (BPQ) 
+# (Cabrera et al., 2018) and all subscales
+# Dependencies: 03_scoring_helpers.R, tidyverse
+
+score_BPQ <- function(df){
+
+  # Create a new temporary df to store the BPQ data 
+  BPQ_data <- as_tibble(df) %>%
+    select("Participant Private ID", 
+           BAI_01:BAI_26, ANSR_01:ANSR_20, HHI_01:HHI_28) %>%
+    # Recode factors into numerics
+    mutate_at(.vars = vars(BAI_01:HHI_28), 
+              .funs = recode(Never = 1, 
+                             Mild = 2, 
+                             Moderate = 3, 
+                             Severe = 4, 
+                             Debilitating = 5))
+
+  print(BPQ_data)
+
+  # Construct final scores
+  BPQ_score <- tibble(
+    "Participant Private ID" = BPQ_data$`Participant Private ID`,
+
+    # Body awareness image
+    BAI_score = sumvars(.df = BPQ_data, 
+                        BAI_01:BAI_26) / 26,
+
+    # Autonomic nervous system response
+    ANSR_score = sumvars(.df = BPQ_data,
+                         ANSR_01:ANSR_20) / 20,
+
+    # Health history inventory
+    HHI_score = sumvars(.df = BPQ_data,
+                        HHI_01:HHI_28) / 28
+  )
+
+  return(BPQ_score)
+
+}

### 2021-08-23 Questionnaires_scoring2021.Rmd
Update Questionnaires_scoring2021.Rmd

@@
 https://xavierrg.shinyapps.io/datacleaning/
-```{r}
+```{r eval=FALSE, include=FALSE}
 library(readr)
@@
 
-BVAQ: 83b1
 BPQ: bbc4
@@
 # Dependencies: 03_scoring_helpers.R, tidyverse
+```{r}
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ")
 
-score_BPQ <- function(df){
+# read the files
+read_selfrep <- function(flnm) {
+    read_csv(flnm) %>%
+        mutate(filename = flnm)
+}
 
+db_BPQ <- list.files(pattern = "*-bbc4.csv", 
+               full.names = T) %>% 
+    map_df(~read_selfrep(.))
+
+# eliminate empty rows
+db_BPQ<- subset(db_BPQ, db_BPQ$`Event Index`== 1)
+
+db_BPQ$completion_code<- db_BPQ$`Participant Completion Code`
+
+# store names for BPQ columns
+bpq_names<- names(db_BPQ %>%
+
+# score_BPQ <- function(df){
   # Create a new temporary df to store the BPQ data 
-  BPQ_data <- as_tibble(df) %>%
-    select("Participant Private ID", 
-           BAI_01:BAI_26, ANSR_01:ANSR_20, HHI_01:HHI_28) %>%
+  # BPQ_data <- as_tibble(df) %>%
+    select("Participant Private ID","completion_code", 
+           BAI_01:BAI_26, ANSR_01:ANSR_20, HHI_01:HHI_28)%>%
+  # drop anything with quantised or text
+  select(-contains("text"))%>%
+  select(-contains("quantised")))
+
+bpq_names
+
+# use the quantised columns as the response siunce they have a number rather than a string
+
+db_BPQ1<- db_BPQ %>%
+
+# score_BPQ <- function(df){
+  # Create a new temporary df to store the BPQ data 
+  # BPQ_data <- as_tibble(df) %>%
+    select("Participant Private ID","completion_code", 
+           BAI_01:`BAI_26-quantised`, ANSR_01:`ANSR_20-quantised`, HHI_01:`HHI_28-quantised`)%>%
+  # drop anything with quantised or text
+  # library(dplyr) 
+  select(-contains("text")) %>%
+  # select(-contains("quantised"))%>%
+
+  # select the quantised to use as the coded variable
+  select(c(1:2, contains("quantised")))
+
+# score
+# assign new names replacing quantised column names with BPQ only item names
+names(db_BPQ1)<- bpq_names
+
+colnames(db_BPQ1)
+# do the actual scoring, only on the BPQ part - bpdy awareness
+db_BPQ2<- db_BPQ1%>%
     # Recode factors into numerics
-    mutate_at(.vars = vars(BAI_01:HHI_28), 
-              .funs = recode(Never = 1, 
-                             Mild = 2, 
-                             Moderate = 3, 
-                             Severe = 4, 
-                             Debilitating = 5))
+    # mutate_at(vars(BAI_01:HHI_28), 
+    #           funs(car::recode("Never" = 1, 
+    #                          "Occasionally" = 2, 
+    #                          "Sometimes" = 3, 
+    #                          "Usually" = 4, 
+    #                          "Always" = 5)))
+  select(c(1:28))%>%
+   mutate(BPQ = rowSums(.[ 3:28]))
 
-  print(BPQ_data)
+  #   # Autonomic nervous system response
+  #   ANSR_score = sumvars(.df = BPQ_data,
+  #                        ANSR_01:ANSR_20) / 20,
+  #   
+  #   # Health history inventory
+  #   HHI_score = sumvars(.df = BPQ_data,
+  #                       HHI_01:HHI_28) / 28
+  # )
+  #
 
-  # Construct final scores
-  BPQ_score <- tibble(
-    "Participant Private ID" = BPQ_data$`Participant Private ID`,
+db_BPQ2
+db_BPQ3<- select(db_BPQ2, 1,2,29)
+```
 
-    # Body awareness image
-    BAI_score = sumvars(.df = BPQ_data, 
-                        BAI_01:BAI_26) / 26,
+BVAQ: 83b1
+https://www.psychologicabelgica.com/articles/10.5334/pb.302/print/
+sum ramnge 40-200
 
-    # Autonomic nervous system response
-    ANSR_score = sumvars(.df = BPQ_data,
-                         ANSR_01:ANSR_20) / 20,
+```{r}
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1")
+read_selfrep <- function(flnm) {
+    readxl::read_xlsx(flnm) %>%
+        mutate(filename = flnm)
+}
 
-    # Health history inventory
-    HHI_score = sumvars(.df = BPQ_data,
-                        HHI_01:HHI_28) / 28
-  )
+db_BVAQ <- list.files(pattern = "*-83b1.xlsx", 
+               full.names = T) %>% 
+    map_df(~read_selfrep(.))
 
-  return(BPQ_score)
+# eliminate empty rows
+db_BVAQ<- subset(db_BVAQ, db_BVAQ$`Event Index`== 1)
 
+db_BVAQ$completion_code<- db_BVAQ$`Participant Completion Code`
+
+View(db_BVAQ)
+
+db_BVAQ1<- db_BVAQ %>%
+   select( -contains("quantised"))%>%
+   select(c("Participant Private ID","completion_code",BVAQ_01:BVAQ_40))
+
+db_BVAQ1<- db_BVAQ1%>%
+   mutate(BVAQ = rowSums(.[ 3:42]))
+
+db_BVAQ3<- select(db_BVAQ1, c(1,2,43))
+```
+
+demographics
+8zto- age
+8nsp - vision
+v2gn = mental health
+
+```{r}
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn")
+
+read_selfrep <- function(flnm) {
+    readxl::read_xlsx(flnm) %>%
+        mutate(filename = flnm)
 }
+
+db_age <- list.files(pattern = "*-8zto.xlsx", 
+               full.names = T) %>% 
+    map_df(~read_selfrep(.))
+
+db_vision <- list.files(pattern = "*-8nsp.xlsx", 
+               full.names = T) %>% 
+    map_df(~read_selfrep(.))
+db_mhealth <- list.files(pattern = "*-v2gn.xlsx", 
+               full.names = T) %>% 
+    map_df(~read_selfrep(.))
+
+colnames(db_mhealth)
+# db_mhealth<- subset(db_mhealth, -2:12,14:15,17:26)
+
+bind (db_mhealth, db_vision, db_age, by = `Participant Private ID`)
+
+colnames(db_age)
+db_age$age_response_specific
+db_age$gender_response
+db_age$`gender_response-quantised`
+# db_age$`AgeResponse-text`
+db_age1<- select(db_age, c(1,13,16,36,37,41))
+
+colnames(db_mhealth)
+
+db_mhealth$ASD
+db_mhealth$`ASD-text`
+db_mhealth$clinical_diagnosis
+db_mhealth$mental_health
+db_mhealth$`mental_health-text`
+db_mhealth$medication
+db_mhealth1<- select(db_mhealth, c(1,13,16, 33,34,37:38,40))
+
+colnames(db_vision)
+db_vision$EyesightResponse
+db_vision1<- select(db_vision, c(1,13,16, 33,34,36:37))
+
+db_demog<- left_join(db_vision1, db_mhealth1,db_age1, by = c("Participant Private ID",
+                                                   "Participant Completion Code"))%>%
+  subset(!is.na(`Participant Private ID`))
+
+db_demog$completion_code <- db_demog$`Participant Completion Code`
+
+```
+
+IQ
+IQ: esh8
+```{r}
+IQ: esh8
+
+```

### 2021-08-23 Questionnaires_scoring2021.Rmd
Update Questionnaires_scoring2021.Rmd

@@
 }
+library(readxl)
+db_BPQ <- read_excel("data_exp_11458-v9_questionnaire-bbc4.xlsx")
+View(data_exp_11458_v9_questionnaire_bbc4)
 
@@
 IQ: esh8
+
+345 to 356 need to be scores separatelly
+
+Lucy: https://docs.google.com/spreadsheets/d/1P9x7oHxpUTanb412czfgYqR_stPJ3fHzwYiItANpfO8/edit#gid=277478937
 ```{r}
-IQ: esh8
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8")
+
+read_selfrep <- function(flnm) {
+    readxl::read_xlsx(flnm) %>%
+        mutate(filename = flnm)
+}
+
+db_IQ <- list.files(pattern = "*-esh8.xlsx", 
+               full.names = T) %>% 
+    map_df(~read_selfrep(.))
+
+colnames(db_IQ)
+
+db_IQ1<- select(db_IQ, c(1,13,16, 37,45:48))
+
+db_IQ2<- subset(db_IQ1, !is.na(Response))
+View(db_IQ2)
+
+db_IQ3 <- db_IQ2%>%
+  group_by(`Participant Private ID`, `Participant Completion Code`)%>%
+  summarise_if(is.numeric, sum, na.rm = TRUE)
+
+db_IQ3$Matrix_Total<- db_IQ3$Correct
+db_IQ3$completion_code<- db_IQ3$`Participant Completion Code`
+
+colnames(db_IQ3)
+db_IQ4<- select(db_IQ3,c(1,7,6))
 
 ```
+
+Merge all into one self report
+
+```{r}
+db_demog$`Participant Completion Code`<- NULL
+
+db_demog$completion_code<- db_demog$`Participant Completion Code`
+
+left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS, by = "completion_code")
+
+db_DASS4$`Participant Public ID`<-NULL
+
+db_demog$`Event Index.x`<-NULL
+db_DASS4$`Participant Private ID`<- NULL
+db_AQ4$`Participant Private ID`<- NULL
+
+db_BVAQ3$`Participant Private ID`<- NULL
+db_IQ4$`Participant Private ID`<- NULL
+db_BPQ3$`Participant Private ID`<- NULL
+
+db_BPQ3
+
+left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3, by = "completion_code")
+
+db_self_rep<- Reduce(merge, list(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS))
+
+# db_IAS$
+```

### 2021-08-24 Questionnaires_scoring2021.Rmd
c

@@
 ```{r}
-
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/AQ")
 # 345_356
-read_selfrep <- function(flnm) {
-    read_csv(flnm) %>%
+read_selfrep1 <- function(flnm) {
+    read_excel(flnm) %>%
         mutate(filename = flnm)
@@
 
-db_AQ <- list.files(pattern = "*.csv", 
+db_AQ <- list.files(pattern = "*.xlsx", 
                full.names = T) %>% 
-    map_df(~read_selfrep(.))
+    map_df(~read_selfrep1(.))
+
+db_AQ <- read_excel("data_exp_11458-v9_questionnaire-7uqw-4489770.xlsx")
 
@@
 
-db_AQ4<- db_AQ3%>%
+db_AQ4<- db_AQ3 %>%
   # mutate(DIF = TAS_1 + TAS_3 + TAS_6 + TAS_7 + TAS_9 + TAS_13+ TAS_14)%>%
@@
 
+library(readxl)
+db_TAS <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/TAS/data_exp_11458-v9_questionnaire-pdlt-4489770.xlsx")
+
 db_TAS<- subset(db_TAS, db_TAS$`Event Index`== 1)
 
-View(db_TAS)
+# View(db_TAS)
 
@@
 db_TAS1<- db_TAS%>%
-  select(c(16,33:71))
+  select(c(16,32:71))
 
@@
 
-db_TAS2
+colnames(db_TAS2)
 # note the gorilal tas labels have a zero, like 01 instead of 1
 ?recode
+
 db_TAS3<- db_TAS2 %>%
@@
 
+library(readr)
+db_DASS <- read_xlsx("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")
+
+("Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")
+
 db_DASS<- subset(db_DASS, db_DASS$`Event Index`== 1)
@@
 db_DASS1<- db_DASS%>%
-  select(c(12,13,16,33:73))
+  select(c(12,13,16,32:74))
 
@@
 db_DASS4<- select(db_DASS3, c(1:2,29,25:28))
+db_DASS4
 
@@
 View(db_IAS)
+
+library(readr)
+db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/All_scores_IAS350_2021-08-23.csv")
+db_IAS
 
@@
 View(data_exp_11458_v9_questionnaire_bbc4)
+
+library(readxl)
+# db_BPQ <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ/data_exp_11458-v9_questionnaire-bbc4-4489770.xlsx")
 
@@
 db_BPQ3<- select(db_BPQ2, 1,2,29)
+db_BPQ3
 ```
@@
 
+library(readxl)
+# db_BVAQ <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1/data_exp_11458-v9_questionnaire-83b1-4489770.xlsx")
+
 # eliminate empty rows
@@
 db_BVAQ3<- select(db_BVAQ1, c(1,2,43))
+
+db_BVAQ3
 ```
@@
 
+# db_age <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-8zto-4489770.xlsx")
+
 db_vision <- list.files(pattern = "*-8nsp.xlsx", 
@@
     map_df(~read_selfrep(.))
+
+library(readxl)
+
+# db_vision <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-8nsp-4489770.xlsx")
+
 db_mhealth <- list.files(pattern = "*-v2gn.xlsx", 
@@
 
+library(readxl)
+# db_mhealth <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-v2gn-4489770.xlsx")
+
 colnames(db_mhealth)
@@
 
-bind (db_mhealth, db_vision, db_age, by = `Participant Private ID`)
+# bind (db_mhealth, db_vision, db_age, by = `Participant Private ID`)
 
@@
 # db_age$`AgeResponse-text`
-db_age1<- select(db_age, c(1,13,16,36,37,41))
+db_age1<- select(db_age, c(1,13,16,35,36))
 
@@
 
+library(readxl)
+# db_IQ <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8/data_exp_60620-v2_task-esh8.xlsx")
+
 db_IQ <- list.files(pattern = "*-esh8.xlsx", 
@@
 
-db_IQ1<- select(db_IQ, c(1,13,16, 37,45:48))
+db_IQ1<- select(db_IQ, c(1,13,16, 37,40:44))
 
@@
 colnames(db_IQ3)
-db_IQ4<- select(db_IQ3,c(1,7,6))
+db_IQ4<- select(db_IQ3,c(1,9,8))
 
@@
 
-left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS, by = "completion_code")
+# left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS, by = "completion_code")
 
@@
 db_BPQ3
+# 
+# left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3, by = "completion_code")
 
-left_join(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3, by = "completion_code")
+db_self_rep <- Reduce(merge, list(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS))
 
-db_self_rep<- Reduce(merge, list(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS))
+db_self_rep <- cbind(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS)
+
+db_self_rep
+write_csv(db_self_rep, "db_self_rep_345_356.csv")
+
+write_csv(db_self_rep, "db_self_rep_350.csv")
 
@@
 ```
+
+merge 
+```{r}
+
+db_self_rep
+library(readr)
+db_self_rep_350_1 <- read_csv("db_self_rep_350.1.csv")
+# View(db_self_rep_350_1)
+
+db_self_rep$`Event Index.x`<- NULL
+db_self_rep$`Event Index.y`<-NULL
+db_self_rep_350_1$`Event Index.y`<- NULL
+
+db_self_rep_345_356<- bind_rows(db_self_rep,db_self_rep_350_1)
+colnames(db_self_rep_345_356)
+
+db_self_rep_345_356<- db_self_rep_345_356[,c(1:22)]
+
+write_csv(db_self_rep, "db_self_rep_345_356_final.csv")
+```

### 2021-08-24 Questionnaires_scoring2021.Rmd
345_356 self reports

@@
 
-db_demog<- left_join(db_vision1, db_mhealth1,db_age1, by = c("Participant Private ID",
+# note this is ignoring the last
+db_demog <- left_join(db_vision1, db_mhealth1,db_age1, by = c("Participant Private ID",
+                                                   "Participant Completion Code"))%>%
+
+db_demog <- left_join(db_vision1, db_mhealth1,db_age1, by = c("Participant Private ID",
                                                    "Participant Completion Code"))%>%
@@
 
+```{r}
+# STAI_T:: 5nzr
+
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_T_5nzr")
+
+# STAIS: 8rfo
+
+read_selfrep <- function(flnm) {
+    readxl::read_xlsx(flnm) %>%
+        mutate(filename = flnm)
+}
+
+library(readxl)
+db_STAI_S <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_S_8rfo/data_exp_11458-v9_questionnaire-8rfo_345_356.xlsx")
+
+library(readxl)
+db_STAI_T <- read_excel("data_exp_11458-v9_questionnaire-5nzr_345_356.xlsx")
+
+db_STAI_T
+
+# eliminate empty rows
+db_STAI_T<- subset(db_STAI_T, db_STAI_T$`Event Index`== 1)
+
+db_STAI_T$completion_code<- db_STAI_T$`Participant Completion Code`
+
+# use the quantised columns as the response siunce they have a number rather than a string
+
+colnames(db_STAI_T)
+db_STAI_T1<- db_STAI_T %>%
+    select("Participant Private ID","completion_code", 
+           STAI_01:STAI_20)%>%
+  # drop anything with quantised or text
+  select(-contains("quantised"))
+
+# score
+
+colnames(db_STAI_T1)
+# do the actual scoring, only on the BPQ part - bpdy awareness
+db_STAI_T2<- db_STAI_T1%>%
+   mutate(STAIT = rowSums(.[ 3:22]))
+
+db_STAI_T2
+db_STAI_T3<- select(db_STAI_T2, c(1:2, 23))
+db_STAI_T3
+
+db_STAI_S
+
+# eliminate empty rows
+db_STAI_S <- subset(db_STAI_S, db_STAI_S$`Event Index`== 1)
+
+db_STAI_S$completion_code<- db_STAI_S$`Participant Completion Code`
+
+# use the quantised columns as the response siunce they have a number rather than a string
+
+colnames(db_STAI_S)
+db_STAI_S1<- db_STAI_S %>%
+    select("Participant Private ID","completion_code", 
+           STAIS_01:STAIS_20)%>%
+  # drop anything with quantised or text
+  select(-contains("quantised"))
+
+# score
+
+colnames(db_STAI_S1)
+# do the actual scoring, only on the BPQ part - bpdy awareness
+db_STAI_S2<- db_STAI_S1%>%
+   mutate(STAIS = rowSums(.[ 3:22]))
+
+db_STAI_S2
+db_STAI_S3<- select(db_STAI_S2, c(1:2, 23))
+db_STAI_S3
+
+db_STAI<- left_join(db_STAI_S3, db_STAI_T3)
+
+```
+
 merge 
 ```{r}
-
 db_self_rep
@@
 
-write_csv(db_self_rep, "db_self_rep_345_356_final.csv")
+# library(readxl)
+Interoception_Study_Logbook <- read_excel("Interoception Study Logbook.xlsx")
+View(Interoception_Study_Logbook)
+
+db_self_rep_345_356$completion_code
+Interoception_Study_Logbook$completion_code
+ssid<- select(Interoception_Study_Logbook, c(1:3))
+
+db_self_rep_345_356<- left_join(db_self_rep_345_356,ssid, by = "completion_code")
+write_csv(db_self_rep_345_356, "db_self_rep_345_356_final.csv")
+
+# - CHECK WASI M on the norms
+
+db_age2<- subset(db_age1, !is.na(`Participant Private ID`))
+db_age2
+
+db_self_rep_345_356<- left_join(db_self_rep_345_356,db_age2)
+
+db_self_rep_345_356
+
+colnames(db_self_rep_345_356)
+
+db_self_rep_345_356
+
+db_self_rep_345_356<- left_join(db_self_rep_345_356, db_STAI)
+
 ```

### 2021-08-24 IAPS_PREPROCESSING_2021.Rmd
Create IAPS_PREPROCESSING_2021.Rmd

--- 2021-08-21 Experiment 2.Rmd
@@
 - New Tas is already scored
+- use questionnaire scoring 2021
 - score AQ, etc using https://xavierrg.shinyapps.io/datacleaning
@@
 db_selfrep <- read_csv("intero_selrep.csv")
-View(intero_selrep)
+library(readxl)
+db_selfrep <- read_excel("db_self_rep_345_356_final.xlsx")
+# View(db_self_rep_345_356_final)
+
+db_selfrep$ssid <- as.character(db_selfrep$`Participant No`)
+tmp.df4_sum_full$ssid <- as.character(tmp.df4_sum_full$ssid)
+
 tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_selfrep, by = 'ssid')
@@
 View(tmp.df4_sum_full)
-write_csv(tmp.df4_sum_full, 'intero_data_full.csv')
+write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_345_356.csv')
 
@@
 
-etwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021")
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021")
 

### 2021-08-24 IAPS_PREPROCESSING_2021_1.Rmd
heart rate bio

--- 2021-08-24 IAPS_PREPROCESSING_2021.Rmd
@@
 
-tmp.df4$trigger2<- tmp.df4$trigger
+tmp.df4$trigger2 <- tmp.df4$trigger
 
@@
 unique(tmp.df4$trigger2)
+unique(tmp.df4$trigger)
+unique(tmp.df4$tNo)
 
@@
 
-db_beh2$triggeracq<- db_beh2$trigger
+db_beh2$triggeracq <- db_beh2$trigger
 unique(db_beh2$ssid)
@@
 
+Ledalab('/Users/heliocuve/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2])
+
 SC column = 2
@@
 
+346, 351 - GP gsr data is messed up
+- Note triggers need to be recreated here, never figured out why the digital events don't translate to ledalab
+
 ```{r}
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021/Processed")
+
 read_leda <- function(flnm) {
@@
 unique(db_leda$trigger)
+
 db_leda$ssid<- as.numeric(substr(db_leda$filename, 13,15))
+
 colnames(tmp.df4_sum)
 colnames(db_leda)
+
 nrow(tmp.df4_sum)
 nrow(db_leda)
+
 colnames(tmp.df4_sum)
+
 tmp.df4_sum2<- subset(tmp.df4_sum,tmp.df4_sum$tNo != -7)
+
 tmp.df4_sum2<- tmp.df4_sum2%>%
@@
   group_by(ssid)%>%
-  mutate(order = 1:224)
+  mutate(order = 1:n())
 
 db_leda2<- subset(db_leda, db_leda$trigger != -7)
+
 db_leda2<- db_leda2%>%
@@
   group_by(ssid)%>%
-  mutate(order = 1:224)
-
-tmp.df4_sum_fullt<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
-tmp.df4_sum_full_backup<- tmp.df4_sum_full
+  mutate(order = 1:n())
+
+unique(db_leda2$order)
+
+range(db_leda2$order, na.rm = TRUE)
+
+# tmp.df4_sum_fullt<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
+# tmp.df4_sum_full_backup<- tmp.df4_sum_full
 
@@
   arrange(ssid, tNo)
+
+View(tmp.df4_sum_full)
+
+trigger<- db_leda2 %>%
+  subset(ssid == 348)%>%
+  select(order, Event.NID, trigger,Event.Nr)
 ```
@@
 
-tmp.df4_sum_full_stim<- subset( tmp.df4_sum_full,  tmp.df4_sum_full$screencontent == 'stim')
-
-levels(as.factor(tmp.df4_sum_full_stim$Event.Name))
+# check stiom screen
+tmp.df4_sum_full_stim<- subset(tmp.df4_sum_full,  tmp.df4_sum_full$screencontent == 'stim')
+
+# levels(as.factor(tmp.df4_sum_full_stim$Event.Name))
+
+# exclude trials with very low gaze validity
 tmp.df4_sum_full_stim<- subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$gaze_valid_prop> .85)
 colnames(tmp.df4_sum_full_stim)
+
+colnames(tmp.df4_sum_full)
+
+```
+
+```{r eval=FALSE, include=FALSE}
 
@@
   geom_smooth(method = 'lm')
-
 ```
@@
 ```{r}
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/IAPS/processed/345_456/CDA")
+
 colnames(tmp.df4_sum_full)
@@
 
-db_leda_bio$trigger<- as.numeric(db_leda_bio$Event.NID)
-db_leda_bio$ssid<- as.numeric(substr(db_leda_bio$filename, 3,5))
-
-colnames(tmp.df4_sum_full)
-unique(tmp.df4_sum_full$trigger)
-
-tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full, tmp.df4_sum_full$ssid>303)
-# tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full_bio, tmp.df4_sum_full_bio$trigger!= -7)
-
-levels(as.factor(tmp.df4_sum_full_bio$ssid))
-unique(tmp.df4_sum_full_bio$trigger)
-levels(as.factor(db_leda_bio$ssid))
-
-db_leda_bio$ssid<- as.factor(db_leda_bio$ssid)
-db_leda_bio$trigger<- as.factor(db_leda_bio$trigger)
+write_csv(db_leda_bio, 'db_leda_bio.csv')
+write_csv(db_leda_bio, 'db_leda_bio_345_355_CDA.csv')
+
+# db_leda_bio <- read_csv("db_leda_bio.csv")
+
+colnames(db_leda_bio)
+
+db_leda_bio$BIO_Event.NID<- db_leda_bio$Event.NID
+db_leda_bio$BIO_filename <- db_leda_bio$filename
+
+db_leda_bio$ssid<- as.numeric(substr(db_leda_bio$BIO_filename, 3,5))
+
+unique(db_leda_bio$ssid)
+
+unique(db_leda_bio$trigger)
+
+# subset out rest period
+db_leda_bio<- subset(db_leda_bio, Event.Nr>1)
+
+db_leda_bio<- subset(db_leda_bio, CDA.nSCR!= "NaN")
+range(db_leda_bio$Event.Nr)
+
+# transform NaNs into proper NA
+db_leda_bio[db_leda_bio == "NaN"] <- NA
+
+# move counter to 1
+range(db_leda_bio$Event.Nr-1)
+range(db_leda_bio$Event.Nr)
+trigger$Event.Nr<- NULL
+
+db_leda_bio$order <- db_leda_bio$Event.Nr-1
+db_leda_bio$trigger<- NULL
+
+# merge trigger
+trigger$Event.NID<- NULL
+trigger$ssid<- NULL
+View(db_leda_bio)
+
+db_leda_bio$order
+db_leda_bio<- left_join(db_leda_bio, trigger)
+
+tmp.df4_sum_full
+
+leda_bioames <- colnames(db_leda_bio)
+
+newnames<- c("Event.Nr", paste0("BIO_", paste0(leda_bioames[2:21])))
+
+newnames
+db_leda_bio_backup<- db_leda_bio
+names(db_leda_bio) <- newnames
+
+db_leda_bio
+
+db_leda_bio$ssid <- db_leda_bio$BIO_ssid
+
+db_leda_bio$BIO_ssid<-NULL
+
+db_leda_bio
+
+tmp.df4_sum_full_bio<- left_join(tmp.df4_sum_full,  db_leda_bio)
+
+colnames(tmp.df4_sum_full_bio)
+
+```
+
+```{r eval=FALSE, include=FALSE}
+# stim
+db_leda_bio_stim<-subset(db_leda_bio, db_leda_bio$trigger< 100)
+unique(db_leda_bio_stim$trigger)
+
+colnames(tmp.df4_sum_full_stim_gp_leda_beh_self)
+(unique(tmp.df4_sum_full_stim_gp_leda_beh_self$trigger))
+
+db_leda_bio_stim$ssid<- as.character(db_leda_bio_stim$ssid)
+
+# db_leda_bio_stim$trigger<- as.character(db_leda_bio_stim$trigger)
+
 db_leda_bio$order<- db_leda_bio$Event.Nr
-tmp.df4_sum_full_bio$ssid<- as.factor(tmp.df4_sum_full_bio$ssid)
-tmp.df4_sum_full_bio$trigger<- as.factor(tmp.df4_sum_full_bio$trigger)
-
-colnames(tmp.df4_sum_full_bio)
+
+tmp.df4_sum_full_stim_gp_leda_beh_self$ssid<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$ssid)
+
+tmp.df4_sum_full_stim_gp_leda_beh_self$trigger<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$trigger)
+
+colnames(tmp.df4_sum_full_stim_gp_leda_beh_self)
 
@@
 
-tmp.df4_sum_full_bio%>%
-  arrange(ssid, tNo, order)
-db_leda_bio<- db_leda_bio%>%
-  arrange(ssid, order)
-
-tmp.df4_sum_full_bio$trigger<- tmp.df4_sum_full_bio$tNo
-tmp.df4_sum_full_bio$trigger<- if_else(tmp.df4_sum_full_bio$screencontent == 'fixation', 100,
-                                       if_else(tmp.df4_sum_full_bio$screencontent == 'ValenceResp', 101,
-                                               if_else(tmp.df4_sum_full_bio$screencontent == 'IntResp', 102, tmp.df4_sum_full_bio$tNo)))
+tmp.df4_sum_full_stim_gp_leda_beh_self<- tmp.df4_sum_full_stim_gp_leda_beh_self%>%
+  arrange(ssid, tNo, Event.Nr)
+
+db_leda_bio_stim<- db_leda_bio_stim%>%
+  arrange(ssid, Event.Nr)
+
+#tmp.df4_sum_full_bio$trigger<- tmp.df4_sum_full_bio$tNo
+#tmp.df4_sum_full_bio$trigger<- if_else(tmp.df4_sum_full_bio$screencontent == 'fixation', 100,
+ #                                      if_else(tmp.df4_sum_full_bio$screencontent == 'ValenceResp', 101,
+                                               #if_else(tmp.df4_sum_full_bio$screencontent == #'IntResp', 102, #tmp.df4_sum_full_bio$tNo)))
 
 unique(tmp.df4_sum_full_bio$trigger)
-
-tmp.df4_sum_full_biot<-left_join(tmp.df4_sum_full_bio, db_leda_bio, by = c("order", "ssid", "trigger"))
+tmp.df4_sum_full_stim_gp_leda_beh_self$Event.Nr<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$Event.Nr)
+
+db_leda_bio_stim$Event.Nr<- as.character(db_leda_bio_stim$Event.Nr)
+View(tmp.df4_sum_full_stim_gp_leda_beh_self_biopac)
+
+tmp.df4_sum_full_stim_gp_leda_beh_self_biopac<-left_join(tmp.df4_sum_full_stim_gp_leda_beh_self, db_leda_bio_stim, by = c("Event.Nr", "ssid"))
+
+write_csv(tmp.df4_sum_full_stim_gp_leda_beh_self_biopac, 'tmp.df4_sum_full_stim_gp_leda_beh_self_biopac2.csv')
+
 (db_leda_bio$trigger)
@@
   geom_smooth(method = 'lm', se = T)
-tmp.df4_sum_full_biot1 <-subset(tmp.df4_sum_full_biot, tmp\.df4_sum_full_biot$ssid != 308)
+
+tmp.df4_sum_full_biot1 <-subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308)
 
 cor(tmp.df4_sum_full_biot1$arousal, tmp.df4_sum_full_biot1$Global.Mean.y, use = 'complete.obs')
+
+```
+
+import biopac heart rate
+```{r}
+nrow(tmp.df4_sum_full_bio)
+
+colnames(tmp.df4_sum_full_bio)
+unique(tmp.df4_sum_full_bio$ssid)
+
+# import
+read_biohr <- function(flnm) {
+  data.table::fread(flnm) %>% 
+    mutate(filename = flnm)
+}
+
+# now read them
+
+# old
+db_biohr <-
+  list.files(pattern = "*.csv", 
+             full.names = T) %>% 
+  map_df(~read_biohr(.))
+
+unique(db_biohr$filename)
+
+db_biohr$ssid<- substr(db_biohr$filename, 6,8)
+db_biohr$order<- db_biohr$Order
+
+db_biohr$Order<- NULL
+db_biohr$filename<- NULL
+db_biohr$trigger<- as.factor(as.character(db_biohr$trigger))
+
+unique(db_biohr$ssid)
+
+db_biohr$ssid<- as.factor(as.character(db_biohr$ssid))
+
+```
+
+#HR BIOPAC
+
+```{r}
+library(readxl)
+library(dplyr)
+db_HR_bio <- read_excel("310_IAPS_Physio_HR.xls")
+
+View(db_HR_bio)
+
+nrow(db_HR_bio)
+
+db_HR_bio<- db_HR_bio[6:nrow(db_HR_bio),]
+
+library(data.table)
+library(purrr)
+# import
+read_biohr <- function(flnm) {
+  read_excel(flnm) %>% 
+    mutate(filename = flnm)
+}
+
+# now read them
+db_HR_bionew <-
+  list.files(pattern = "*.xls", 
+             full.names = T) %>% 
+  map_df(~read_biohr(.))
+
+db_HR_bio<- db_HR_bionew
+
+unique(db_HR_bionew$filename)
+
+test<- subset(db_HR_bio, db_HR_bio$filename == "./607_IAPS_Physio_HR.xls")
+
+levels(as.factor(db_HR_bio$filename))
+db_HR_bio$ssid<- substr(db_HR_bio $filename, 3,5)
+
+db_HR_bio$filename<- NULL
+
+db_HR_bio$`Stim-Response Analysis`
+
+db_HR_bio$stim<- if_else(grepl('Stimulus', (db_HR_bio$`Stim-Response Analysis`)) == TRUE, db_HR_bio$`Stim-Response Analysis`, NULL)
+
+library(tidyr)
+
+db_HR_bio<- db_HR_bio%>%
+  group_by(ssid)%>%
+  fill(stim)
+
+levels(as.factor(db_HR_bio$ssid))
+
+#  remove na in the mean heart rate
+
+db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$...2))
+
+db_HR_bio$mhrtext<- is.character(db_HR_bio$...2)
+
+db_HR_bio<- subset(db_HR_bio, !grepl('interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
+
+levels(as.factor(db_HR_bio$ssid))
+
+# loosing participants here
+View(db_HR_bio)
+
+db_HR_bio<- subset(db_HR_bio, !grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
+
+test<- subset(db_HR_bio, grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
+levels(as.factor(db_HR_biotest$ssid))
+
+db_HR_bio<- subset(db_HR_bio, !grepl('Time', db_HR_bio$`Stim-Response Analysis`) == TRUE)
+
+#db_HR_biotest1<- subset(db_HR_biotest, !is.na(db_HR_biotest$stim))
+
+#test<- subset(db_HR_bio, db_HR_bio$ssid == 607)
+
+levels(as.factor(db_HR_bio$ssid))
+
+db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$`Stim-Response Analysis`))
+
+db_HR_bio$...3<- NULL
+db_HR_bio$...4<- NULL
+
+db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$...2))
+
+db_HR_bio<- subset(db_HR_bio, db_HR_bio$...2 != 'Mean(CH 40)')
+db_HR_bio$timestart<- db_HR_bio$`Stim-Response Analysis`
+
+db_HR_bio$Mean_HR<- db_HR_bio$...2
+
+db_HR_bio<- db_HR_bio%>%
+  arrange((as.numeric(timestart)), ssid)
+
+db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$stim))
+
+db_HR_bio$trigger<- substr(db_HR_bio$stim, 10,13)
+
+unique((as.numeric(db_HR_bio$trigger)-128))
+
+db_HR_bio$trigger_200<- if_else(db_HR_bio$trigger> 103, TRUE, FALSE)
+
+db_HR_bio$trigger<- if_else(db_HR_bio$trigger_200 == TRUE, as.numeric(db_HR_bio$trigger)-128, as.numeric(db_HR_bio$trigger))
+
+unique((as.numeric(db_HR_bio$trigger)))
+
+#subset(db_HR_bio, db_HR_bio$ssid!= 328)%>%
+#  group_by(timestart, ssid)%>%
+ # mutate(EventNR= 1:225)
+
+db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger< 100)
+
+db_HR_bio1<- db_HR_bio1%>%
+  arrange(as.numeric(timestart), ssid)
+
+db_HR_bio1<- subset(db_HR_bio1,!is.na(db_HR_bio1$stim))
+
+#tno
+#subset(db_HR_bio1, db_HR_bio1$ssid != 328)%>%
+table(is.na(db_HR_bio1$ssid))
+db_HR_bio1<- db_HR_bio1%>%
+  arrange(as.numeric(timestart), ssid)
+
+db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)
+
+db_HR_bio1no328<- db_HR_bio1no328 %>%
+  group_by(as.numeric(ssid))%>%
+  mutate(tNo = -6:49)
+
+db_HR_bio328<-subset(db_HR_bio1, db_HR_bio1$ssid== 328)
+
+db_HR_bio328<- db_HR_bio328 %>%
+  group_by(as.numeric(ssid))%>%
+  mutate(tNo = -6:24)
+
+db_HR_bio2<- bind_rows(db_HR_bio1no328,db_HR_bio328)
+
+colnames(db_HR_bio2)
+
+levels(as.factor(db_HR_bio1no328$ssid))
+db_HR_bio2$ssid<-db_HR_bio2$`as.numeric(ssid)`
+
+#mereg old and new heart rate
+# now read them
+db_biohr$trigger
+
+db_biohr$tno<-db_biohr$trigger
+db_HR_bio2$trigger
+colnames(db_biohr)
+
+colnames(db_HR_bio2)
+
+db_biohr$Mean_HR<- db_biohr$HR_BIO
+
+db_biohr$timestart<- db_biohr$Time
+
+left_join(db_HR_bio2, db_biohr)
+
+db_HR_bio2<- select(db_HR_bio2, c(timestart,Mean_HR, tNo, ssid))
+
+db_HR_bio2$`as.numeric(ssid)`<- NULL
+
+str((db_HR_bio2))
+str(db_biohrold2)
+db_biohr$tNo<- db_biohr$tno
+db_biohrold2<- db_biohr
+
+db_biohrold2<- select(db_biohr, c(timestart,Mean_HR, tNo, ssid))
+unique(db_biohrold2$tNo)
+
+db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)
+db_biohrold2$timestart<- as.numeric(db_biohrold2$timestart)
+
+db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)
+db_biohrold2$Mean_HR<- as.numeric(db_biohrold2$Mean_HR)
+
+db_HR_bio2$tNo<- as.character(db_HR_bio2$tNo)
+db_biohrold2$tNo<- as.character(db_biohrold2$tNo)
+db_HR_bio2$ssid<- as.character(db_HR_bio2$ssid)
+
+db_biohrold2$ssid<- as.character(db_biohrold2$ssid)
+
+str(db_HR_bio2)
+
+db_biohrold2test<- subset(db_biohrold2, db_biohrold2$tNo != 100)
+db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 101)
+db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 102)
+db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 103)
+db_HR_bio2$subj<- as.factor(db_HR_bio2$ssid)
+db_biohrold2test$subj<- as.factor(db_biohrold2test$ssid)
+db_biohrold2test$ssid<- NULL
+db_HR_bio2$ssid<- NULL
+
+str(db_HR_bio2)
+
+db_HR_bio2<- db_HR_bio2[,1:4]
+
+db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)
+
+db_biohrold2test$Mean_HR<- as.numeric(db_biohrold2test$Mean_HR)
+
+db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)
+
+db_biohrold2test$timestart<- as.numeric(db_biohrold2test$timestart)
+
+db_HR_bio_final<- bind_rows(db_HR_bio2, db_biohrold2test)
+
+db_HR_bio_final$ssid<- db_HR_bio_final$subj
+levels(as.factor(db_HR_bio_final$ssid))
+
+db_HR_bio_final$subj<- NULL
+
+write_csv(db_HR_bio_final, 'db_HR_bio_final_mar5.csv')
+
+db_HR_bio1$tNo<- -6:49
+
+db_HR_bio1$tNo<- if_else(db_HR_bio1$tNo< 0, as.numeric(db_HR_bio1$tNo), as.numeric(db_HR_bio1$tNo+1))
+
+db_HR_bio1$
+
 ```

### 2021-08-24 IAPS_PREPROCESSING_2021_1.Rmd
Update IAPS_PREPROCESSING_2021_1.Rmd

@@
 
-db_parsed$screencontent_no<- if_else(db_parsed$screencontent == 'fixation', 1,
+db_parsed$screencontent_no <- if_else(db_parsed$screencontent == 'fixation', 1,
                                       if_else(db_parsed$screencontent == 'stim', 2,
@@
 # tmp.df4_sum_fullt
+
+tmp.df4_sum_full
 ```
@@
 ```{r}
+
 nrow(tmp.df4_sum_full_bio)
@@
 # now read them
-
 # old
 db_biohr <-
-  list.files(pattern = "*.csv", 
+  list.files(pattern = "*.xls", 
              full.names = T) %>% 
@@
 ```{r}
+setwd("~/OneDrive - Nexus365/InteroStudy2020/Data Collection 2019- 2020/2020/InteroStudyBIOPAC/IAPS/Processed/HR/345_355")
 library(readxl)
 library(dplyr)
-db_HR_bio <- read_excel("310_IAPS_Physio_HR.xls")
-
-View(db_HR_bio)
-
-nrow(db_HR_bio)
-
-db_HR_bio<- db_HR_bio[6:nrow(db_HR_bio),]
+# db_HR_bio <- read_excel("310_IAPS_Physio_HR.xls")
+
+# db_HR_bio<- db_HR_bio[6:nrow(db_HR_bio),]
 
@@
 
-test<- subset(db_HR_bio, db_HR_bio$filename == "./607_IAPS_Physio_HR.xls")
+# test<- subset(db_HR_bio, db_HR_bio$filename == "./607_IAPS_Physio_HR.xls")
 
 levels(as.factor(db_HR_bio$filename))
+
 db_HR_bio$ssid<- substr(db_HR_bio $filename, 3,5)
@@
 
+# 
 db_HR_bio$`Stim-Response Analysis`
 
-db_HR_bio$stim<- if_else(grepl('Stimulus', (db_HR_bio$`Stim-Response Analysis`)) == TRUE, db_HR_bio$`Stim-Response Analysis`, NULL)
+# flag stimulus
+db_HR_bio$stim <- if_else(grepl('Stimulus', (db_HR_bio$`Stim-Response Analysis`)) == TRUE, db_HR_bio$`Stim-Response Analysis`, NULL)
 
@@
 
+db_HR_bio
+
 levels(as.factor(db_HR_bio$ssid))
@@
 db_HR_bio<- subset(db_HR_bio, !grepl('interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
-
-levels(as.factor(db_HR_bio$ssid))
 
@@
 
-test<- subset(db_HR_bio, grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
-levels(as.factor(db_HR_biotest$ssid))
+# test<- subset(db_HR_bio, grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
+# levels(as.factor(db_HR_biotest$ssid))
 
@@
 
-db_HR_bio$trigger<- substr(db_HR_bio$stim, 10,13)
-
+db_HR_bio$trigger <- substr(db_HR_bio$stim, 10,13)
+
+# for soem reason this 
 unique((as.numeric(db_HR_bio$trigger)-128))
@@
 
-db_HR_bio$trigger<- if_else(db_HR_bio$trigger_200 == TRUE, as.numeric(db_HR_bio$trigger)-128, as.numeric(db_HR_bio$trigger))
-
-unique((as.numeric(db_HR_bio$trigger)))
+db_HR_bio$trigger2 <- if_else(db_HR_bio$trigger_200 == TRUE, as.numeric(db_HR_bio$trigger)-128, as.numeric(db_HR_bio$trigger))
+
+unique((as.numeric(db_HR_bio$trigger2)))
 
@@
 
-db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger< 100)
+db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger2< 100)
 
 db_HR_bio1<- db_HR_bio1%>%
-  arrange(as.numeric(timestart), ssid)
+  arrange(ssid, as.numeric(timestart))
 
@@
 table(is.na(db_HR_bio1$ssid))
-db_HR_bio1<- db_HR_bio1%>%
+# 
+# db_HR_bio1<- db_HR_bio1%>%
+#   arrange(as.numeric(timestart), ssid)
+
+# use this
+
+db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)
+db_HR_bio1no328<- subset(db_HR_bio1no328, trigger2> 15 & trigger2<72)
+
+db_HR_bio1no328<- db_HR_bio1no328 %>%
+  arrange(ssid, trigger2)%>%
+  filter(!duplicated(trigger2))
+
+db_HR_bio1no328<- db_HR_bio1no328 %>%
+  group_by(ssid)%>%
+  mutate(tNo = -6:(n()-7)) #56 trials
+
+unique(db_HR_bio1no328$tNo)
+
+range(db_HR_bio1no328$tNo)
+
+table(db_HR_bio1no328$tNo)
+
+# test<- subset(db_HR_bio1no328, tNo>49)
+# 
+# db_HR_bio328<-subset(db_HR_bio1, db_HR_bio1$ssid== 352)
+# 
+# subset(db_HR_bio328, trigger> 15 & trigger<72)
+
+db_HR_bio1no328<- db_HR_bio1no328%>%
   arrange(as.numeric(timestart), ssid)
 
-db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)
-
-db_HR_bio1no328<- db_HR_bio1no328 %>%
-  group_by(as.numeric(ssid))%>%
-  mutate(tNo = -6:49)
-
-db_HR_bio328<-subset(db_HR_bio1, db_HR_bio1$ssid== 328)
-
-db_HR_bio328<- db_HR_bio328 %>%
-  group_by(as.numeric(ssid))%>%
-  mutate(tNo = -6:24)
-
+```
+
+```{r}
+db_HR_bio2<- db_HR_bio328 %>%
+  group_by(ssid)%>%
+  mutate(tNo = -6:(n()-7))
+unique(db_HR_bio328$tNo)
+```
+
+```{r}
 db_HR_bio2<- bind_rows(db_HR_bio1no328,db_HR_bio328)
+db_HR_bio2<-db_HR_bio1no328
 
@@
 levels(as.factor(db_HR_bio1no328$ssid))
-db_HR_bio2$ssid<-db_HR_bio2$`as.numeric(ssid)`
+# db_HR_bio2$ssid<-db_HR_bio2$`as.numeric(ssid)`
 
@@
 # now read them
-db_biohr$trigger
-
-db_biohr$tno<-db_biohr$trigger
-db_HR_bio2$trigger
-colnames(db_biohr)
-
-colnames(db_HR_bio2)
-
-db_biohr$Mean_HR<- db_biohr$HR_BIO
-
-db_biohr$timestart<- db_biohr$Time
-
-left_join(db_HR_bio2, db_biohr)
+# db_biohr$trigger
+# 
+# db_biohr$tno<-db_biohr$trigger
+# db_HR_bio2$trigger
+# colnames(db_biohr)
+# 
+# colnames(db_HR_bio2)
+# 
+# db_biohr$Mean_HR<- db_biohr$HR_BIO
+# 
+# db_biohr$timestart<- db_biohr$Time
+# 
+# 
+# left_join(db_HR_bio2, db_biohr)
 
@@
 
-db_HR_bio2$`as.numeric(ssid)`<- NULL
-
 str((db_HR_bio2))
-str(db_biohrold2)
+# str(db_biohrold2)
 db_biohr$tNo<- db_biohr$tno
@@
 db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)
+
 db_biohrold2$timestart<- as.numeric(db_biohrold2$timestart)
@@
 
-db_biohrold2test<- subset(db_biohrold2, db_biohrold2$tNo != 100)
-db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 101)
-db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 102)
-db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 103)
-db_HR_bio2$subj<- as.factor(db_HR_bio2$ssid)
-db_biohrold2test$subj<- as.factor(db_biohrold2test$ssid)
-db_biohrold2test$ssid<- NULL
-db_HR_bio2$ssid<- NULL
+# db_biohrold2test<- subset(db_biohrold2, db_biohrold2$tNo != 100)
+# db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 101)
+# db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 102)
+# db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 103)
+# db_HR_bio2$subj<- as.factor(db_HR_bio2$ssid)
+# db_biohrold2test$subj<- as.factor(db_biohrold2test$ssid)
+# db_biohrold2test$ssid<- NULL
+# db_HR_bio2$ssid<- NULL
 
@@
 
+# final
+db_HR_bio_final<- db_HR_bio2
 db_HR_bio_final<- bind_rows(db_HR_bio2, db_biohrold2test)
 
-db_HR_bio_final$ssid<- db_HR_bio_final$subj
+# db_HR_bio_final$ssid<- db_HR_bio_final$subj
 levels(as.factor(db_HR_bio_final$ssid))
@@
 
+write_csv(db_HR_bio_final, 'db_HR_bio_final_346_355.csv')
+
+db_HR_bio_final$tNo
+
+db_HR_bio_final$tNo
+
 db_HR_bio1$tNo<- -6:49
 
-db_HR_bio1$tNo<- if_else(db_HR_bio1$tNo< 0, as.numeric(db_HR_bio1$tNo), as.numeric(db_HR_bio1$tNo+1))
-
-db_HR_bio1$
-
-```
-
-import biopac heart rate
-```{r}
-nrow(tmp.df4_sum_full_bio)
+db_HR_bio_final$tNo<- if_else(as.numeric(db_HR_bio_final$tNo) < 0, as.numeric(db_HR_bio_final$tNo), as.numeric(db_HR_bio_final$tNo)+1)
+
+db_HR_bio_final$BIO
+
+```
+
+merge heart rate
+
+```{r}
+tmp.df4_sum_full_bio$ssid<- as.character(tmp.df4_sum_full_bio$ssid)
+db_HR_bio_final$ssid<- as.character(db_HR_bio_final$ssid)
 
 colnames(tmp.df4_sum_full_bio)
-unique(tmp.df4_sum_full_bio$ssid)
-
-unique(db_biohr$filename)
-
-# import
-read_biohr <- function(flnm) {
-  data.table::fread(flnm) %>% 
-    mutate(filename = flnm)
-}
-
-# now read them
-db_biohr <-
-  list.files(pattern = "*.csv", 
-             full.names = T) %>% 
-  map_df(~read_biohr(.))
-
-db_biohr$ssid<- substr(db_biohr$filename, 6,8)
-db_biohr$order<- db_biohr$Order
-
-db_biohr$Order<- NULL
-db_biohr$filename<- NULL
-db_biohr$trigger<- as.factor(as.character(db_biohr$trigger))
-unique(tmp.df4_sum_full_bio$ssid)
-unique(db_biohr$ssid)
-tmp.df4_sum_full_bio$trigger<- as.factor(as.character(tmp.df4_sum_full_bio$trigger))
-
-db_biohr$ssid<- as.factor(as.character(db_biohr$ssid))
-tmp.df4_sum_full_bio_hr<- left_join(tmp.df4_sum_full_biot, db_biohr, by = c('ssid', 'order', 'trigger'))
-
-ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(hr, HR_BIO))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-
-ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(CDA.PhasicMax.x, CDA.PhasicMax.y))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-tmp.df4_sum_full_bio_hr_stim<- subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent != 'fixation')
-
-cor(tmp.df4_sum_full_bio_hr_stim$hr, tmp.df4_sum_full_bio_hr_stim$HR_BIO, use = 'complete')
-
-# tmp.df4_sum_full_bio_hr_stim_1<- subset(tmp.df4_sum_full_bio_hr_stim, tmp.df4_sum_full_bio_hr_stim$HR_BIO> 50)
-
-tmp.df4_sum_full_bio_hr_stim$valence_cat<- if_else(tmp.df4_sum_full_bio_hr_stim$valence >0, 'pos',
-                                                  if_else(tmp.df4_sum_full_bio_hr_stim$valence < 0, 'neg', 'neutral'))
-
-unique(tmp.df4_sum_full_bio_hr_stim$screencontent)
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-  # facet_grid(~valence_cat)
-
-cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$arousal, use = 'complete')
-cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$valence, use = 'complete')
-
-tmp.df4_sum_full_bio_hr_stim%>%
-      group_by(ssid, IAS)%>%
-      summarise(corr = cor(HR_BIO, arousal, use = 'complete'))%>%
-  summarise(new = cor(corr, IAS))
-  # summarise_at(c('TAS'), mean)
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
-  geom_point()+
-  geom_smooth(method = 'lm')+
-  facet_grid(~valence_cat)
-
-tmp.df4_sum_full_bio_hr_stim%>%
-group_by(valence_cat)%>%
-  summarise(corr = cor(HR_BIO, arousal, use = 'complete'))
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, valence))+
-  geom_point()+
-  geom_smooth(method = 'lm')+
-  facet_grid(~valence_cat)
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, ValenceMean))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-  # facet_grid(~valence_cat)
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, mean_sac_dur))+
-  geom_point()+
-  geom_smooth(method = 'lm')+
-  facet_grid(~valence_cat)
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, pup_basCor))+
-  geom_point()+
-  geom_smooth(method = 'lm')+
-  facet_grid(~valence_cat)
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, Global.Mean.y))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, TAS))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, `DASS Anxiety`))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-
-```
+
+tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final, by = c('ssid', 'tNo'))
+
+```
+
+Merge self reports
+
+```{r}
+tmp.df4_sum_full<- left_join(tmp.df4_sum,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))
+
+```

### 2021-08-24 IAPS_PREPROCESSING_2021_1.Rmd
Update IAPS_PREPROCESSING_2021_1.Rmd

@@
 #   arrange(ssid, tNo, screencontent_no)
+
+colnames(tmp.df4_sum_full)
 ```
@@
 
-```{r}
-tmp.df4_sum_full<- left_join(tmp.df4_sum,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))
-
-```
+# add the self report
+```{r}
+
+View(tmp.df4_sum_full_bio_hr)
+
+library(readxl)
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport")
+
+View(db_selfrep)
+db_selfrep <- read_excel("db_self_rep_345_356_final.xlsx")
+
+db_selfrep$ssid <- as.character(db_selfrep$`Participant No`)
+
+tmp.df4_sum_full_bio_hr$ssid <- as.character(tmp.df4_sum_full_bio_hr$ssid)
+
+tmp.df4_sum_full_bio_hr_self <- left_join(tmp.df4_sum_full_bio_hr, db_selfrep, by = 'ssid')
+
+write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_bio_hr_self_345_356.csv')
+
+```
+
+merge parsed data
+```{r}
+tmp.df4_sum_full_bio_hr_self
+db_parsed_summarised2$ssid<- as.character(db_parsed_summarised2$ssid)
+
+tmp.df4_sum_full_bio_hr_self_parsed <- left_join(tmp.df4_sum_full_bio_hr_self, db_parsed_summarised2, 
+                             by = c("ssid", "trialUnq", "tNo", "screencontent"))
+
+# tmp.df4_sum_full<- left_join(tmp.df4_sum,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))
+
+# save the timecourse data and the aggregated data
+
+tmp.df4_sum_full_bio_hr_self_parsed
+write_csv(tmp.df4_sum_full_bio_hr_self_parsed, 'tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv')
+write_csv(tmp.df4, 'tmp.df4_timeseries_345_356.csv')
+```

### 2021-08-24 IAPS_PREPROCESSING_2021_1.Rmd
t

@@
 # \why?
+unique(tmp.df4$text)
+
 tmp.df4<- tmp.df4%>%
@@
 write_csv(tmp.df4, 'tmp.df4_timeseries_345_356.csv')
-```
+
+tmp.df4_sum_full_bio_hr_self_parsed$screencontent_no
+
+tmp.df4_sum_full_bio_hr_self_parsed$TAS
+tmp.df4_sum_full_bio_hr_self_parsed %>%
+  subset(screencontent_no>2)%>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric,mean, na.rm = TRUE)%>%
+  ggplot(aes(Age,sdev_gazesum))+
+  geom_point()+
+  geom_smooth(method = lm, se = F)
+
+```

### 2021-08-24 Paper_Analyses_subj_obje_arousal.Rmd
t

@@
 ```{r}
+db_full4new$screencontent_no
+db_full4new %>%
+  subset(screencontent_no ==4)%>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric, mean,na.rm = TRUE)%>%
+  ggplot(aes(TAS, fix_count))+
+  geom_point()+
+  geom_smooth(method = lm, se = F)+
+  ggpubr::stat_cor()
+
+db_full4new %>%
+  subset(screencontent_no > 2)%>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric, mean,na.rm = TRUE)%>%
+  ggplot(aes(TAS, fix_count))+
+  geom_point()+
+  geom_smooth(method = lm, se = F)+
+  ggpubr::stat_cor()
+
+```
+
+```{r}
+
 options(contrasts = c("contr.sum","contr.poly"))

### 2021-08-25 IAPS_PREPROCESSING_2021_1.Rmd
fixed import biopac

@@
 
-unique(db_leda_bio$trigger)
+# unique(db_leda_bio$trigger)
 
@@
 range(db_leda_bio$Event.Nr-1)
-range(db_leda_bio$Event.Nr)
-trigger$Event.Nr<- NULL
+# range(db_leda_bio$Event.Nr)
+# trigger$Event.Nr<- NULL
 
 db_leda_bio$order <- db_leda_bio$Event.Nr-1
-db_leda_bio$trigger<- NULL
+# db_leda_bio$trigger<- NULL
 
@@
 db_leda_bio$order
+# db_345_355$order
+
+trigger<- db_345_355 %>%
+  group_by(order,trigger, tNo)%>%
+  summarise_at(c('ssid'), mean, na.rm = TRUE)
+  # select(db_345_355, c(trigger, tNo, order))
+
+  trigger$ssid<- NULL
+
   db_leda_bio<- left_join(db_leda_bio, trigger)
@@
 
-newnames<- c("Event.Nr", paste0("BIO_", paste0(leda_bioames[2:21])))
+leda_bioames
+newnames<- c("Event.Nr", paste0("BIO_", paste(leda_bioames[2:16])),"BIO_Event.NID","BIO_filename"  ,"ssid","order","trigger")
 
 newnames
+
 db_leda_bio_backup<- db_leda_bio
+
+colnames(db_leda_bio_backup)
+
 names(db_leda_bio) <- newnames
 
+colnames(db_leda_bio)
+
+# db_leda_bio$ssid <- db_leda_bio$BIO_ssid
+
+# db_leda_bio$BIO_ssid<-NULL
+
 db_leda_bio
 
-db_leda_bio$ssid <- db_leda_bio$BIO_ssid
-
-db_leda_bio$BIO_ssid<-NULL
-
-db_leda_bio
-
-tmp.df4_sum_full_bio<- left_join(tmp.df4_sum_full,  db_leda_bio)
+db_leda_bio$ssid<- as.character(db_leda_bio$ssid)
+
+# db_leda_bio$order<- db_leda_bio$BIO_order
+
+unique(tmp.df4_sum_full$Event.Nr)
+
+db_leda_bio$BIO_Event.NID<- NULL
+db_leda_bio$BIO_filename<- NULL
+
+tmp.df4_sum_full_bio<- left_join(tmp.df4_sum_full,  db_leda_bio, by = c("ssid", "order"))
 
@@
 
+write_csv(db_leda_bio, "db_leda_bio_346_347_ledagsr.csv")
+
+write_csv(db_leda_bio, "db_leda_bio_346_355_ledagsr.csv")
 ```

### 2021-08-25 Paper_Analyses_subj_obje_arousal.Rmd
fixed import biopac

@@
 ```{r}
+# even though it says no pratice I actually kept the pratice
+db_full4new_stim_screen_pupil_nopract$tNo
+
+library(readr)
+db_345_355 <- read_csv("tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv")
+View(db_345_355)
+
+colnames(db_full4new_stim_screen_pupil_nopract)
+
 participants_demog <- db_full4new_stim_screen_pupil_nopract %>%

### 2021-08-25 IAPS_PREPROCESSING_2021_1.Rmd
fixing missing behavioural data in 245_355

@@
 tmp.df4_sum_full_bio_hr_self_parsed
+
+# merge behavioural data
+db_beh3$ssid<- as.character(db_beh3$ssid)
+db_beh3$tNo <- as.character(db_beh3$tNo)
+tmp.df4_sum_full_bio_hr_self_parsed$tNo<- as.character(tmp.df4_sum_full_bio_hr_self_parsed$tNo)
+# tmp.df4_sum_full<-
+
+tmp.df4_sum_full_bio_hr_self_parsed<- left_join(tmp.df4_sum_full_bio_hr_self_parsed, db_beh3, by = c('ssid', 'tNo'))
+
+View(db_beh3)
+tmp.df4_sum_full<- tmp.df4_sum_full%>%
+  arrange(ssid, tNo, time)
+
+tmp.df4_sum_full_bio_hr_self_parsed$screencontent_no
+
+tmp.df4_sum_full_bio_hr_self_parsed$TAS
+# tmp.df4_sum_full_bio_hr_self_parsed<- tmp.df4_sum_full_bio_hr_self_parsed %>%
+#   subset(screencontent_no>2)%>%
+#   group_by(ssid)%>%
+#   summarise_if(is.numeric,mean, na.rm = TRUE)%>%
+#   ggplot(aes(Age,sdev_gazesum))+
+#   geom_point()+
+#   geom_smooth(method = lm, se = F)
+
+colnames(tmp.df4_sum_full_bio_hr_self_parsed)
+
+tmp.df4_sum_full_bio_hr_self_parsed$Age<- tmp.df4_sum_full_bio_hr_self_parsed$age_response_specific
+tmp.df4_sum_full_bio_hr_self_parsed$gender<- substr(tmp.df4_sum_full_bio_hr_self_parsed$gender_response,1,1)
+
+tmp.df4_sum_full_bio_hr_self_parsed$BIO_filename<- NULL
+tmp.df4_sum_full_bio_hr_self_parsed$`Participant Completion Code`<- NULL
+tmp.df4_sum_full_bio_hr_self_parsed$`Participant Private ID`<- NULL
+
+tmp.df4_sum_full_bio_hr_self_parsed$`Participant No`<- NULL
+tmp.df4_sum_full_bio_hr_self_parsed$age_response_specific<- NULL
+tmp.df4_sum_full_bio_hr_self_parsed$Event.NID<- NULL
+tmp.df4_sum_full_bio_hr_self_parsed$`Event Index`<- NULL
+tmp.df4_sum_full_bio_hr_self_parsed$gender_response<- NULL
+
+tmp.df4_sum_full_bio_hr_self_parsed$`Person testing`<- NULL
+tmp.df4_sum_full_bio_hr_self_parsed$Event.Nr.x<- NULL
+tmp.df4_sum_full_bio_hr_self_parsed$filename.x<- NULL
+tmp.df4_sum_full_bio_hr_self_parsed$filename.y<- NULL
+
+tmp.df4_sum_full_bio_hr_self_parsed
+
+tmp.df4_sum_full_bio_hr_self_parsed<- tmp.df4_sum_full_bio_hr_self_parsed%>%
+  rename(IAS = IAS_score)%>%
+  rename(ASD_self = ASD)
+
+tmp.df4_sum_full_bio_hr_self_parsed1<- select(tmp.df4_sum_full_bio_hr_self_parsed,)
+
 write_csv(tmp.df4_sum_full_bio_hr_self_parsed, 'tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv')
 write_csv(tmp.df4, 'tmp.df4_timeseries_345_356.csv')
-
-tmp.df4_sum_full_bio_hr_self_parsed$screencontent_no
-
-tmp.df4_sum_full_bio_hr_self_parsed$TAS
-tmp.df4_sum_full_bio_hr_self_parsed %>%
-  subset(screencontent_no>2)%>%
-  group_by(ssid)%>%
-  summarise_if(is.numeric,mean, na.rm = TRUE)%>%
-  ggplot(aes(Age,sdev_gazesum))+
-  geom_point()+
-  geom_smooth(method = lm, se = F)
-
-```
+```

### 2021-08-25 Paper_Analyses_subj_obje_arousal.Rmd
fixing missing behavioural data in 245_355

@@
 
+colnames(db_345_355)
+
+# db_345_355_1<- select(db_345_355, c(1:41, )
 colnames(db_full4new_stim_screen_pupil_nopract)
 
+db_345_355_stim<- subset(db_345_355, db_345_355$screencontent == "stim")
+
+db_full4new_stim_screen_pupil_nopract$ssid<- as.character(db_full4new_stim_screen_pupil_nopract$ssid)
+db_345_355_stim$ssid<- as.character(db_345_355_stim$ssid)
+db_345_355_stim$tNo<- as.character(db_345_355_stim$tNo)
+
+colnames(db_full4new_stim_screen_pupil_nopract)
+colnames(db_345_355_stim)
+
+install.packages("gtools")
+?gtools::smartbind()
+
+# binf only common columns
+
+outersect <- function(x, y) {
+  sort(c(setdiff(x, y),
+         setdiff(y, x)))
+}
+
+common_cols
+
+oposite_columns<- outersect(colnames(db_full4new_stim_screen_pupil_nopract), colnames(db_345_355_stim$age_response_specific))
+
+common_cols
+oposite_columns
+rbind(
+  db_full4new_stim_screen_pupil_nopract[common_cols], 
+  db_345_355_stim[common_cols]
+)
+
+colnames(db_full4new_stim_screen_pupil_nopract)
+colnames(db_345_355_stim)
+
+db_full4new_stim_screen_pupil_nopract
+db_345_355_stim$gender_response
+
+db_345_355_stim<- db_345_355_stim %>% 
+  rename(Age = age_response_specific)%>%
+  rename(Gender = gender_response)
+db_345_355_stim$Age<- age_response_specific
+
+db_full4new_stim_screen_pupil_nopract<- bind_rows(db_full4new_stim_screen_pupil_nopract, db_345_355_stim)
+```
+
+```{r}
+unique(db_full4new_stim_screen_pupil_nopract$Group)
+db_full4new_stim_screen_pupil_nopract$Group<- if_else(as.numeric(db_full4new_stim_screen_pupil_nopract$ssid) < 500, "NT",                                               if_else(as.numeric(db_full4new_stim_screen_pupil_nopract$ssid) > 700,"NT", "ASD"))
+
+db_full4new_stim_screen_pupil_nopract$Group_t<- NULL
+
+unique(db_full4new_stim_screen_pupil_nopract$Group_t)
+
+# db_full4new_stim_screen_pupil_nopract$grou
+
+db_full4new_stim_screen_pupil_nopract$Gender<- substr(db_full4new_stim_screen_pupil_nopract$Gender, 1,1)
 participants_demog <- db_full4new_stim_screen_pupil_nopract %>%
@@
   group_by(ssid, Gender)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)
+  summarise_at(c("Age","WASIM", "TAS", "AQ", "IAS", "DASSTotal"), mean, na.rm = TRUE)
 

### 2021-08-27 Paper_Analyses_subj_obje_arousal.Rmd
pupil with updated (345_355)

@@
 ```{r}
+
+library(readr)
+library(tidyverse)
+db_345_355_stim$Group<- if_else(as.numeric(db_345_355_stim$ssid)<500,"NT", "ASD")
 # even though it says no pratice I actually kept the pratice
@@
 
-library(readr)
 db_345_355 <- read_csv("tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv")
@@
 colnames(db_345_355)
+db_345_355<- db_345_355 %>%
+  rename(Gender = gender)%>%
+  rename(menalHealth = mental_health)
 
@@
 db_full4new_stim_screen_pupil_nopract<- bind_rows(db_full4new_stim_screen_pupil_nopract, db_345_355_stim)
+
+db_full4new_stim_screen_pupil_nopract%>%
+  subset(Group == "NT")%>%
+  group_by(ssid)%>%
+  mutate(cor = cor(arousal, pup_basCor, use = "complete"))%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ungroup()%>%
+  ggplot(aes(TAS, cor))+
+  geom_point(aes(color = ssid))+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()
+
+db_full4new_stim_screen_pupil_nopract_backup$Mean_HR
+table(is.na(db_full4new_stim_screen_pupil_nopract$Mean_HR))
+
+db_full4new_stim_screen_pupil_nopract$Mean_HR %>%
+  subset(Group == "NT")%>%
+  subset(ssid_num>304)%>%
+  subset(ssid!= "344")%>%
+  subset(ssid!= "900")%>%
+  group_by(ssid)%>%
+  mutate(BIO_CDA.AmpSum_z = scale(BIO_CDA.AmpSum, center = TRUE, scale = TRUE)[,1])%>%
+  mutate(cor = cor(arousal, pup_basCor, use = "complete"))%>%
+  mutate(cor2 = cor(arousal, BIO_CDA.AmpSum_z, use = "complete"))%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ungroup()%>%
+  ggplot(aes(TAS, Mean_HR))+
+  geom_point(aes(color = ssid))+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()
+
 ```
@@
 unique(db_full4new_stim_screen_pupil_nopract$Group)
-db_full4new_stim_screen_pupil_nopract$Group<- if_else(as.numeric(db_full4new_stim_screen_pupil_nopract$ssid) < 500, "NT",                                               if_else(as.numeric(db_full4new_stim_screen_pupil_nopract$ssid) > 700,"NT", "ASD"))
 
@@
 
-db_full4new_stim_screen_pupil_nopract$Gender<- substr(db_full4new_stim_screen_pupil_nopract$Gender, 1,1)
-participants_demog <- db_full4new_stim_screen_pupil_nopract %>%
+# db_full4new_stim_screen_pupil_nopract$Gender<- substr(db_full4new_stim_screen_pupil_nopract$Gender, 1,1)
+
+db_full4new_stim_screen_pupil_nopract_update<- bind_rows(db_full4new_stim_screen_pupil_nopract,
+                                                         db_345_355_stim)
+
+db_full4new_stim_screen_pupil_nopract_update$Group<- if_else(as.numeric(db_full4new_stim_screen_pupil_nopract_update$ssid) < 500, "NT",                                               if_else(as.numeric(db_full4new_stim_screen_pupil_nopract_update$ssid) > 700,"NT", "ASD"))
+
+participants_demog <- db_full4new_stim_screen_pupil_nopract_update %>%
   subset(Group == "NT")%>%
@@
 
-# gender
+unique(participants_demog$ssid)
 table(participants_demog$Gender)
@@
 library(lmerTest)
-
+db_345_355_stim$stim
+View(db_full4new_stim_screen_pupil_nopract)
+unique(db_full4new_stim_screen_pupil_nopract$trialUnq)
+db_full4new_stim_screen_pupil_nopract$ssid
+unique(db_full4new_stim_screen_pupil_nopract$trialUnq.x)
+
+db_full4new_stim_screen_pupil_nopract_backup<- db_full4new_stim_screen_pupil_nopract
+
+db_full4new_stim_screen_pupil_nopract <- db_full4new_stim_screen_pupil_nopract_update
+
+# db_full4new_stim_screen_pupil_nopract$stimIAPS<- subs
 unique(db_full4new_stim_screen_pupil_nopract$stimIAPS)
-unique(substr(db_full4new_stim_screen_pupil_nopract$stimIAPS, 1,8))
+unique(db_full4new_stim_screen_pupil_nopract_backup$stimIAPS)
+unique(substr(db_full4new_stim_screen_pupil_nopract_backup$stimIAPS, 1,8))
+
+db_full4new_stim_screen_pupil_nopract$stimIAPS[db_full4new_stim_screen_pupil_nopract$stimIAPS== "2900.1.jpg"]<- "2900.jpg1.jpg"
+
+db_full4new_stim_screen_pupil_nopract$stimIAPS[db_full4new_stim_screen_pupil_nopract$stimIAPS== "2345.1.jpg"]<- "2345.jpg1.jpg"
+
+unique(db_full4new_stim_screen_pupil_nopract$stimIAPS)
+unique(db_full4new_stim_screen_pupil_nopract_backup$stimIAPS)
+
 db_full4new_stim_screen_pupil_nopract$Label<- substr(db_full4new_stim_screen_pupil_nopract$stimIAPS, 1,8)
-
-db_full4new_stim_screen_pupil_nopract<- left_join(db_full4new_stim_screen_pupil_nopract, imageJ_IAPS, by = "Label")
-
+unique(db_full4new_stim_screen_pupil_nopract$Label)
+table(is.na(db_full4new_stim_screen_pupil_nopract$stimIAPS))
+
+table(is.na(db_full4new_stim_screen_pupil_nopract$Label))
+unique(imageJ_IAPS$Label)
+
+imageJ_IAPS_names<- colnames(imageJ_IAPS)
+imageJ_IAPS_names<- imageJ_IAPS_names[3:14]
+imageJ_IAPS_names
+db_full4new_stim_screen_pupil_nopract
+db_full4new_stim_screen_pupil_nopract_test <- dplyr::left_join(db_full4new_stim_screen_pupil_nopract, imageJ_IAPS, by = "Label")
+
+table(is.na(db_full4new_stim_screen_pupil_nopract_test$Mean.y))
+
+db_full4new_stim_screen_pupil_nopract<- db_full4new_stim_screen_pupil_nopract[,!(names(db_full4new_stim_screen_pupil_nopract) %in% imageJ_IAPS_names)]
+
+db_full4new_stim_screen_pupil_nopract$Mean_gray_z<- NULL
+
+# megre IAPS data
+
+db_full4new_stim_screen_pupil_nopract <- left_join(db_full4new_stim_screen_pupil_nopract, imageJ_IAPS, by = "Label")
+
+table(is.na(db_full4new_stim_screen_pupil_nopract$Mean))
+# test<- subset(db_full4new_stim_screen_pupil_nopract, is.na(Mean))
 nrow(db_full4new_stim_screen_pupil_nopract)
 # rows = 2858
+
+unique(db_full4new_stim_screen_pupil_nopract$ssid)
 
@@
 
+table(is.na(db_full4new_stim_screen_pupil_nopract$arousal))
+table(is.na(db_full4new_stim_screen_pupil_nopract$ArousalMean))
+table(is.na(db_full4new_stim_screen_pupil_nopract$Group))
+
+db_full4new_stim_screen_pupil_nopract<- db_full4new_stim_screen_pupil_nopract%>%
+  ungroup()%>%
+  mutate(arousal_c = scale(arousal, center = TRUE, scale = TRUE)[,1],
+         valence_c = scale(valence, center = TRUE, scale = TRUE)[,1])
+
 pupil_arousal_findings$pupil_from_arousal <- lmer(pup_basCor ~ arousal_c*Mean_gray_z  +(1 +Mean_gray_z | ssid) + (0+arousal_c| ssid), REML = FALSE,
                       data = subset(db_full4new_stim_screen_pupil_nopract, 
-                                    pupil_outlier == FALSE & ssid_num< 500 & 
-                                    arousal_outler == FALSE))
+                                    # pupil_outlier == FALSE & 
+                                     Group == "NT"
+                                    # arousal_outler == FALSE
+                                    ))
 
@@
 
-  ggplot(aes(arousal_c, Mean_gray_z, color = ground_valence_lab))+
-  geom_point()+
+  db_full4new_stim_screen_pupil_nopract %>%
+    subset(ssid < 500)%>%
+  # subset(Group == "NT")%>%
+  group_by(ssid, Group)%>%
+  mutate(cor_ar_pup = cor(arousal, pup_basCor, use = "complete"))%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(TAS,cor_ar_pup, color = Group))+
+  geom_point()+
+    geom_smooth(method = lm, se = F)+
     ggpubr::stat_cor()
+  geom_hline(yintercept = -.75)+
+  geom_hline(yintercept = -.90)
 
@@
 
+db_full4new_stim_screen_pupil_nopract$arousal_outler
+db_full4new_stim_screen_pupil_nopract$pupil_outlier
+
+# flag potential outliers
+
+db_full4new_stim_screen_pupil_nopract<- db_full4new_stim_screen_pupil_nopract %>%
+  group_by(stimIAPS) %>%
+  mutate(arousal_outler = if_else(arousal > (median(arousal, na.rm = TRUE) + 
+                                               (4*mad(arousal, na.rm = TRUE))), TRUE,
+         if_else(arousal < (median(arousal, na.rm = TRUE) - 
+                              (4*mad(arousal, na.rm = TRUE))), TRUE, FALSE)))%>%
+  group_by(ssid)%>%
+   mutate(pupil_outlier = if_else(pup_basCor > (median(pup_basCor, na.rm = TRUE) 
+                                                + (3*mad(pup_basCor, na.rm = TRUE))), TRUE,
+         if_else(pup_basCor < (median(pup_basCor, na.rm = TRUE) - 
+                                 (3*mad(pup_basCor, na.rm = TRUE))), TRUE, FALSE)))
+
+# fit pupil response froma rousal and valence
 pupil_arousal_findings$pupil_from_ar_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
@@
                                                     (1 + Mean_gray_z | ssid)+
-                                                    (0+ valence_c* arousal_c | ssid),
+                                                    (0+ valence_c | ssid),
                                                   REML = FALSE,
-                      data = subset(db_full4new_stim_screen_pupil_nopract, 
-                                    pupil_outlier == FALSE & ssid_num< 500 & 
-                                      arousal_outler == FALSE))
-unique(db_full4new_stim_screen_pupil_nopract$tNo)
-
-unique(db_full4new_stim_screen_pupil_nopract$ssid)
+                      data = db_full4new_stim_screen_pupil_nopract%>%
+                         subset(Group == "NT")%>%
+                        subset(pupil_outlier == FALSE)%>%
+                        subset(arousal_outler == FALSE))
+
+# unique(db_full4new_stim_screen_pupil_nopract$tNo)
+# 
+# unique(db_full4new_stim_screen_pupil_nopract$ssid)
+
 relgrad <- with(pupil_arousal_findings$pupil_from_ar_vale@optinfo$derivs,solve(Hessian,gradient))
@@
 
-# car::vif(pupil_arousal_findings$pupil_from_ar_vale) #curoff 4
-
-plots_paper$interaction_ar_vl <- interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale , pred = arousal_c, modx = valence_c, plot.points = TRUE)
-
+car::vif(pupil_arousal_findings$pupil_from_ar_vale) #curoff 4
+# valence_c           arousal_c         Mean_gray_z valence_c:arousal_c 
+#            1.876902            1.801054            1.004734            1.080785
+
+plots_paper$interaction_ar_vl <- interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale , pred = arousal_c, modx = valence_c)
+
+plots_paper$interaction_ar_vl 
 interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_val_gaze , pred = valence_c , modx = arousal_c)
@@
 
+```
+
+```{r eval=FALSE, include=FALSE}
 # lassomodels$firt
@@
 
-Linear mixed model fit by maximum likelihood . t-tests use Satterthwaite's method ['lmerModLmerTest']
-Formula: pup_basCor ~ (valence_c * arousal_c) + Mean_gray_z + (1 + Mean_gray_z |  
-    ssid) + (0 + valence_c * arousal_c | ssid)
-   Data: subset(db_full4new_stim_screen_pupil_nopract, pupil_outlier ==      FALSE & ssid_num < 500 & arousal_outler == FALSE)
-
-     AIC      BIC   logLik deviance df.resid 
-  8493.9   8579.2  -4231.9   8463.9     2170
-
-Scaled residuals: 
-    Min      1Q  Median      3Q     Max 
--3.6141 -0.5987  0.0067  0.5952  3.6796
-
-Random effects:
- Groups   Name                Variance Std.Dev. Corr       
- ssid     (Intercept)         0.78415  0.8855              
-          Mean_gray_z         0.13611  0.3689   0.55       
- ssid.1   valence_c           0.04233  0.2057              
-          arousal_c           0.02296  0.1515    0.89      
-          valence_c:arousal_c 0.01700  0.1604   -0.19  0.01
- Residual                     2.57999  1.6062              
-Number of obs: 2185, groups:  ssid, 43
-
-Fixed effects:
-                    Estimate Std. Error       df t value             Pr(>|t|)    
-(Intercept)         -0.66764    0.14166 44.77819  -4.713          0.000023962 ***
-valence_c            0.08546    0.06557 28.33677   1.603              0.20294    
-arousal_c            0.44137    0.06445 22.53213   6.848          0.000000619 ***
-Mean_gray_z         -0.96311    0.06622 43.35750 -14.544 < 0.0000000000000002 ***
-valence_c:arousal_c  0.15461    0.04434 24.37046   3.487              0.00187 ** 
----
-Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
-
-Correlation of Fixed Effects:
-            (Intr) vlnc_c arsl_c Mn_gr_
-valence_c   -0.042                     
-arousal_c   -0.031  0.746              
-Mean_gray_z  0.453 -0.013  0.028       
-vlnc_c:rsl_  0.147 -0.267 -0.128  0.035
-
 same analyses as above but regress brightness out of pupil
@@
 pupil_arousal_findings$pupil_from_brightness <- lmer(pup_basCor ~ 
-                                                    Mean  +
+                                                    Mean_gray_z  +
                                                     (1  | ssid),
@@
 
-                      data = subset(db_full4new_stim_screen_pupil_nopract, 
-                                    # pupil_outlier == FALSE & ssid_num< 500 & 
-                                      # arousal_outler == FALSE
-                                    ))
+                      data = db_full4new_stim_screen_pupil_nopract, na.action=na.exclude)
 
@@
 db_full4new_stim_screen_pupil_nopract$pup_resid <- resid(pupil_arousal_findings$pupil_from_brightness)
-
-db_full4new_stim_screen_pupil_nopract$pup_resid_lm <-
-resid(pupil_arousal_findings$pupil_from_brightness_lm)
+?resid
+db_full4new_stim_screen_pupil_nopract$pup_resid_lm <- resid(pupil_arousal_findings$pupil_from_brightness_lm,
+                                                            na.action=na.exclude)
 
@@
 
-# strong correlation, in this case this is good, because it means there is a large ammount of unexplain ed variane not acconted for by the predictor
+# strong correlation, in this case this is good, because it means there is a large amount of unexplained variance not acconted for by the predictor
 
@@
 ```
+
 interaction plot
@@
                                                 REML = FALSE,
-                      data = subset(db_full4new_stim_screen_pupil_nopract, 
-                                    pupil_outlier == FALSE & ssid_num<500 & 
-                                      arousal_outler == FALSE))
+                      data = db_full4new_stim_screen_pupil_nopract%>%
+                         subset(Group == "NT")%>%
+                        subset(pupil_outlier == FALSE)%>%
+                        subset(arousal_outler == FALSE))
 summary(pupil_arousal_findings$arousal_from_pup)
+
 anova(pupil_arousal_findings$arousal_from_pup)
@@
 
-db_full4new_stim_subset<- db_full4new_stim_screen_pupil_nopract[,c(1:4,6:7,12:13,16,21:27, 31:56,80:81,84:96,98:114,116:124)]
+# new folks 
+library(readr)
+tmp_df4_timeseries_345_356 <- read_csv("tmp.df4_timeseries_345_356.csv")
+View(tmp_df4_timeseries_345_356)
+
+colnames(tmp.df4_full_stim_downs_jun2021)
+colnames(tmp_df4_timeseries_345_356)
+# downsample to 60 bins
+
+# create bins
+# install.packages("OneR")
+# install.packages("OneR")
+library(OneR)
+
+?bin
+unique(tmp_df4_timeseries_345_356$screencontent)
+tmp_df4_timeseries_345_356_stim <- subset(tmp_df4_timeseries_345_356, tmp_df4_timeseries_345_356$screencontent == "stim")
+
+tmp_df4_timeseries_345_356_stim$timebin <- OneR::bin(tmp_df4_timeseries_345_356_stim$timerezero3, nbin = 60)
+
+# dowsample by averaging?
+colnames(tmp_df4_timeseries_345_356_stim)
+
+tmp_df4_timeseries_345_356_stim_downs <- tmp_df4_timeseries_345_356_stim %>%
+  group_by(ssid, tNo, timebin, trial,trialUnq)%>%
+  summarise_at(c('timerezero3','pup_basCor', 'gaze_x_cor_pix', 'gaze_y_cor_pix'), 
+               mean, na.rm = TRUE)
+
+?saveRDS
+saveRDS(tmp_df4_timeseries_345_356_stim_downs, "tmp_df4_timeseries_345_356_stim_downs.rds")
+
+# merge pupil series with behavioural data
+colnames(db_full4new_stim_screen_pupil_nopract)
+cname_db_full4new_stim_subset<- colnames(db_full4new_stim_subset)
+
+db_full4new_stim_subset_backup<-db_full4new_stim_subset
+
+# db_full4new_stim_subset<- db_full4new_stim_screen_pupil_nopract[,c(1:4,6:7,12:13,16,21:27, 31:56,80:81,84:96,98:114,116:124)]
+db_full4new_stim_subset<- db_full4new_stim_screen_pupil_nopract[,c(cname_db_full4new_stim_subset)]
+
+View(db_full4new_stim_subset)
 
@@
 
-tmp.df4_full_stim_downs_jun2021$tNo<- as.numeric(tmp.df4_full_stim_downs_jun2021$tNo)
+# temp backup
+tmp.df4_full_stim_downs_jun2021_backup<- tmp.df4_full_stim_downs_jun2021
+tmp_df4_timeseries_345_356_stim_downs_backup<- tmp_df4_timeseries_345_356_stim_downs
+
+tmp_df4_timeseries_345_356_stim_downs$ssid<- as.character(tmp_df4_timeseries_345_356_stim_downs$ssid)
+
+tmp_df4_timeseries_345_356_stim_downs$tNo<- as.character(tmp_df4_timeseries_345_356_stim_downs$tNo)
+
+unique(tmp.df4_full_stim_downs_jun2021$timebin)
+unique(tmp_df4_timeseries_345_356_stim_downs$timebin)
+
+# bind old and new data
+tmp.df4_full_stim_downs_jun2021 <- bind_rows(tmp.df4_full_stim_downs_jun2021,tmp_df4_timeseries_345_356_stim_downs)
+
+tmp.df4_full_stim_downs_jun2021$tNo<- as.character(tmp.df4_full_stim_downs_jun2021$tNo)
+db_full4new_stim_subset$tNo<- as.character(db_full4new_stim_subset$tNo)
+
+# backup[]
+tmp.df4_full_stim_downs_jun2021_60bins_backup<- tmp.df4_full_stim_downs_jun2021_60bins
 
@@
 # create a dataframe version where we downsample to60 and not to 30
+
 tmp.df4_full_stim_downs_jun2021_60bins$Label<- substr(tmp.df4_full_stim_downs_jun2021_60bins$stimIAPS, 1,8)
 
-tmp.df4_full_stim_downs_jun2021_60bins<- left_join(tmp.df4_full_stim_downs_jun2021_60bins, imageJ_IAPS, by = "Label")
+tmp.df4_full_stim_downs_jun2021_60bins$Label2<- substr(tmp.df4_full_stim_downs_jun2021_60bins$stimIAPS, 1,4)
+imageJ_IAPS$Label2<- substr(imageJ_IAPS$Label, 1,4)
+
+unique(imageJ_IAPS$Label2)
+unique(tmp.df4_full_stim_downs_jun2021_60bins$Label2)
+
+# backup
+tmp.df4_full_stim_downs_jun2021_60bins_backup<- tmp.df4_full_stim_downs_jun2021_60bins
+
+tmp.df4_full_stim_downs_jun2021_60bins<- left_join(tmp.df4_full_stim_downs_jun2021_60bins, imageJ_IAPS, by = "Label2")
 
@@
 nrow(tmp.df4_full_stim_downs_jun2021_60bins)
-# 172168 good
+# 172168 good+
+# 205703 (with new)
 
@@
 Quick check that things make sense
-```{r}
-
+30 s timebins
+```{r eval=FALSE, include=FALSE}
+unique(tmp.df4_full_stim_downs_jun2021_with_beh$timebin2)
 # group_by(stimIAPS)%>%
@@
 
-```{r}
+60 bins
+```{r}
+
+ground_arousal_lab
+
 tmp.df4_full_stim_downs_jun2021_60bins %>%
@@
 ```
-
+abs
 ```{r}
@@
 
+  valenc and arousla plots  
 ```{r}
@@
 # create number s for time bins
+
+unique(tmp.df4_full_stim_downs_jun2021_60bins$ssid)
+
 tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins%>%
@@
                       data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
-                                    ssid_num< 500 &
+                                    Group == "NT" &
                                     timebin_no == nbins[b]))
@@
 View(timecourse_60bin_result_df)
+
 plots_timecourse$eff_size_pup_amp <-   timecourse_60bin_result_df[1:56,] %>% 
@@
 
+30hz
 ```{r}
@@
                       data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
-                                    !is.na(pup_vel_smooth)&
-                                      ssid_num< 500 &
+                                    !is.na(pup_velocity)&
+                                     Group == "NT" &
                                     timebin_no == nbins[b]))
@@
 plots_paper$pupil_correlation <-   db_full4new_stim_screen_pupil_nopract %>%
-    subset(ssid_num<500)%>%
+  subset(Group == "NT")%>%
+    # subset(ssid_num<500)%>%
   subset(pupil_outlier == FALSE & arousal_outler == FALSE)%>%
@@
 
-```
-
 ```{r}

### 2021-08-27 IAPS_PREPROCESSING_2021_1.Rmd
Update IAPS_PREPROCESSING_2021_1.Rmd

@@
 
-db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger2< 100)
-
-db_HR_bio1<- db_HR_bio1%>%
+# this will delete fixation and stuff so no
+# db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger2< 100)
+
+db_HR_bio1<- db_HR_bio%>%
   arrange(ssid, as.numeric(timestart))
@@
 db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)
-db_HR_bio1no328<- subset(db_HR_bio1no328, trigger2> 15 & trigger2<72)
-
-db_HR_bio1no328<- db_HR_bio1no328 %>%
-  arrange(ssid, trigger2)%>%
-  filter(!duplicated(trigger2))
-
-db_HR_bio1no328<- db_HR_bio1no328 %>%
+
+db_HR_bio1no328$trigger2
+db_HR_bio1no328<- subset(db_HR_bio1no328, trigger2> 15 & trigger2<106)
+
+db_HR_bio1no328$trigger<- db_HR_bio1no328$tNo
+# db_HR_bio1no328
+
+# db_HR_bio1no328<- db_HR_bio1no328 %>%
+#   arrange(ssid, trigger2)%>%
+#   filter(!duplicated(trigger2))
+
+View(trigger)
+db_HR_bio1no328<- db_HR_bio1no328$t %>%
   group_by(ssid)%>%
@@
 
-tmp.df4_sum_full_bio_hr_self_parsed1<- select(tmp.df4_sum_full_bio_hr_self_parsed,)
+# tmp.df4_sum_full_bio_hr_self_parsed1<- select(tmp.df4_sum_full_bio_hr_self_parsed,)
 

### 2021-08-31 IAPS_PREPROCESSING_2021_1.Rmd
fixed ssid 352 and 353
fixed an issue where artifact digital signals were sent as stim, resulting in an error that mad it hard to create trial numbers on the fly during pre-pocessing. 352 had an extra trial 70 and 353 had a trigger 99 which didn't actually exist in the data

@@
 unique(db_HR_bionew$filename)
+nrow(db_HR_bionew)
 
@@
 # this will delete fixation and stuff so no
-# db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger2< 100)
+db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger2> 15)
 
@@
 # use this
-
+table(db_HR_bio1$ssid!= 328)
 db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)
@@
 db_HR_bio1no328<- db_HR_bio1no328%>%
-  arrange(as.numeric(timestart), ssid)
-
-```
-
-```{r}
-db_HR_bio2<- db_HR_bio328 %>%
+  arrange(ssid,as.numeric(timestart))
+
+```
+
+```{r}
+# db_HR_bio2<-
+
+unique(db_HR_bio1no328$stim)
+db_HR_bio1no328<- db_HR_bio1no328 %>%
   group_by(ssid)%>%
   mutate(tNo = -6:(n()-7))
-unique(db_HR_bio328$tNo)
-```
-
-```{r}
-db_HR_bio2<- bind_rows(db_HR_bio1no328,db_HR_bio328)
+
+unique(db_HR_bio1no328$tNo)
+```
+
+```{r}
+View(db_HR_bio1no328)
+
+unique(db_HR_bio1no328$ssid)
+unique(db_HR_bio328$ssid)
+# db_HR_bio2<- bind_rows(db_HR_bio1no328,db_HR_bio328)
 db_HR_bio2<-db_HR_bio1no328
@@
 
-db_HR_bio2<- select(db_HR_bio2, c(timestart,Mean_HR, tNo, ssid))
-
-str((db_HR_bio2))
+colnames(db_HR_bio2)
+db_HR_bio2<- select(db_HR_bio2, c(timestart,Mean_HR, tNo, ssid,trigger2,trigger_200, trigger,stim,mhrtext))
+
+# store only fixation screens
+
+# create screecontr.treatment()
+unique(db_HR_bio2$trigger)
+unique(db_HR_bio2$trigger2)
+
+db_HR_bio2$screen_content<- if_else(db_HR_bio2$trigger == 100, "Rest",
+                                    if_else(db_HR_bio2$trigger == 101, "fixation",
+                                    if_else(db_HR_bio2$trigger == 102, "valence",
+                                    if_else(db_HR_bio2$trigger == 103, "arousal",
+                                    "stim"))))
+
+unique(db_HR_bio2$trigger)
+
+db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)
+db_HR_bio2.1<- db_HR_bio2 %>%
+  group_by(ssid)%>%
+  arrange(ssid, timestart)%>%
+  group_by(ssid,screen_content)%>%
+  # arrange(ssid, timestart)%>%
+  mutate(tNo =  1:n())
+   arrange(timestart,ssid)
+  # subset(trigger == 100)
+
+unique(db_HR_bio2.1$tNo)
+
+unique(db_HR_bio2.1$tNo-8)
+table(db_HR_bio2.1$tNo)
+
+db_HR_bio2.1$tNo2<- if_else(db_HR_bio2.1$screen_content == "Rest", -7,
+                           as.numeric(as.character(db_HR_bio2.1$tNo)))
+
+db_HR_bio2.1$tNo3<- if_else(db_HR_bio2.1$tNo2 >0 &  db_HR_bio2.1$tNo2< 7, db_HR_bio2.1$tNo2-7,
+                          if_else(db_HR_bio2.1$tNo2  >6, db_HR_bio2.1$tNo2-6, db_HR_bio2.1$tNo2))
+
+table(db_HR_bio2.1$tNo3)
+test352<- subset(db_HR_bio2.1, ssid == 352)
+test353<- subset(db_HR_bio2.1, ssid == 353)
+table(test352$tNo3)
+
+write_csv(test352, "test352.csv")
+
+# fixed the issue was trial 15 is supposed to be trigger 23 but we also had a 70, that can be seen on the psychopy data files
+write_csv(test353, "test353.csv")
+
+# on 353 the issue was a 99 trigger bveing loaded as a stim
+
+# export 352 and 353 and corect manually, they seems ot have an extra trigger
+
+db_352 <- read_csv("352_Biohr_fixed.csv")
+db_353 <- read_csv("353_Biohr_fixed.csv")
+unique(db_352$ssid)
+db_352
+nrow(db_353)
+
+# new dataset withouth the problem ssids
+db_HR_bio2.2<- subset(db_HR_bio2.1, ssid != "352")
+db_HR_bio2.2<- subset(db_HR_bio2.2, ssid != "353")
+
+nrow(db_HR_bio2.2)
+
+unique(db_HR_bio2.2$ssid)
+
+db_352_353<- bind_rows(db_352, db_353)
+
+nrow(db_352_353)
+
+db_HR_bio2.2$ssid<- as.character(db_HR_bio2.2$ssid)
+db_352_353$ssid<- as.character(db_352_353$ssid)
+
+db_352_353$trigger <- as.character(db_352_353$trigger)
+
+nrow(db_HR_bio2.2)
+# nrow(db_HR_bio2.1) 2021 result should be less than this
+
+nrow(db_352_353)
+
+db_HR_bio2.3<- bind_rows(db_HR_bio2.2,db_352_353)
+nrow(db_HR_bio2.3)
+# order
+
+db_HR_bio2.3.1<- db_HR_bio2.3 %>%
+  group_by(ssid)%>%
+  arrange(ssid, timestart) %>%
+  group_by(ssid,screen_content)%>%
+  # arrange(ssid, timestart)%>%
+  mutate(tNo =  1:n())
+   # arrange(timestart,ssid)
+  # subset(ssid == 353)
+
+table(db_HR_bio2.3.1$tNo)
+
+# test<- subset(db_HR_bio2.3.1, ssid == "353")
+
+unique(db_HR_bio2.3.1$tNo)
+
+db_HR_bio2.3.1$tNo2<- if_else(db_HR_bio2.3.1$screen_content == "Rest", -7,
+                           as.numeric(as.character(db_HR_bio2.3.1$tNo)))
+
+db_HR_bio2.3.1$tNo3<- if_else(db_HR_bio2.3.1$tNo2 >0 &  db_HR_bio2.3.1$tNo2< 7, db_HR_bio2.3.1$tNo2-7,
+                          if_else(db_HR_bio2.3.1$tNo2  >6, db_HR_bio2.3.1$tNo2-6, db_HR_bio2.3.1$tNo2))
+
+unique(db_HR_bio2.3.1$tNo3)
+```
+
+```{r}
+unique(db_HR_bio2.3.1$screen_content)
+table(is.na(db_HR_bio2.3.1$screen_content))
+
+str((db_HR_bio2.3.1))
 # str(db_biohrold2)
@@
 
+View(db_biohrold2)
 db_biohrold2$timestart<- as.numeric(db_biohrold2$timestart)
 
+# View(db_HR_bio2)
 db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)
-db_biohrold2$Mean_HR<- as.numeric(db_biohrold2$Mean_HR)
+# db_biohrold2$Mean_HR<- as.numeric(db_biohrold2$Mean_HR)
 
 db_HR_bio2$tNo<- as.character(db_HR_bio2$tNo)
+
 db_biohrold2$tNo<- as.character(db_biohrold2$tNo)
@@
 db_HR_bio2<- db_HR_bio2[,1:4]
-
 db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)
@@
 # final
-db_HR_bio_final<- db_HR_bio2
-db_HR_bio_final<- bind_rows(db_HR_bio2, db_biohrold2test)
+colnames(db_HR_bio_final)
+db_HR_bio2.3.1
+colnames(db_HR_bio2.3.1)
+
+unique(db_HR_bio2.3.1$tNo)
+db_HR_bio2.3.1
+db_HR_bio2.3.2<-select()
+db_HR_bio_final<- select(db_HR_bio2.3.1, c(1,12))
+
+# db_HR_bio_final<- bind_rows(db_HR_bio2, db_biohrold2test)
+
+View(db_HR_bio_final)
 
@@
 
-write_csv(db_HR_bio_final, 'db_HR_bio_final_346_355.csv')
+write_csv(db_HR_bio_final, 'db_HR_bio_final_346_355_withfix.csv')
 

### 2021-09-01 IAPS_PREPROCESSING_2021_1.Rmd
1

@@
 db_HR_bio2.3.1
-db_HR_bio2.3.2<-select()
-db_HR_bio_final<- select(db_HR_bio2.3.1, c(1,12))
+# db_HR_bio2.3.2<-select()
+db_HR_bio_final<- select(db_HR_bio2.3.1, c(1:12))
 
@@
 
-tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final, by = c('ssid', 'tNo'))
+unique(tmp.df4_sum_full_bio$tNo)
+tmp.df4_sum_full_bio$tNo3<- tmp.df4_sum_full_bio$tNo
+tmp.df4_sum_full_bio1<- tmp.df4_sum_full_bio
+tmp.df4_sum_full_bio1$tNo<-NULL
+
+unique(tmp.df4_sum_full_bio$screencontent)
+unique(db_HR_bio_final$screen_content)
+
+tmp.df4_sum_full_bio$screen_content<- if_else(tmp.df4_sum_full_bio$screencontent == "ValenceResp", "valence",
+                                              if_else(tmp.df4_sum_full_bio$screencontent == "IntResp", "arousal", tmp.df4_sum_full_bio$screencontent))
+
+tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final, by = c('ssid', 'tNo', 'screen_content'))
+
+unique(tmp.df4_sum_full_bio_hr$tNo)
 

### 2021-09-01 Paper_Analyses_subj_obje_arousal.Rmd
1

@@
 db_345_355_stim<- subset(db_345_355, db_345_355$screencontent == "stim")
+
+# behavioural data
+db_345_355
+db_f
 
@@
 
+  db_full4new_stim_screen_pupil_nopract$screencontent
+
+  table(is.na(  db_full4new_stim_screen_pupil_nopract$pup_basCor ))
+  unique(  db_full4new_stim_screen_pupil_nopract$ssid)
+
   db_full4new_stim_screen_pupil_nopract %>%
-    subset(ssid < 500)%>%
+    # subset(ssid_num < 343)%>%
   # subset(Group == "NT")%>%
-  group_by(ssid, Group)%>%
+  group_by(ssid)%>%
   mutate(cor_ar_pup = cor(arousal, pup_basCor, use = "complete"))%>%
   summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(TAS,cor_ar_pup, color = Group))+
+  ggplot(aes(TAS,cor_ar_pup))+
   geom_point()+
@@
 # fit pupil response froma rousal and valence
+
+table(is.na(db_full4new_stim_screen_pupil_nopract$valence_c))
 pupil_arousal_findings$pupil_from_ar_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
@@
 plots_paper$interaction_ar_vl
+
+db_full4new_stim_screen_pupil_nopract_nt<- subset(db_full4new_stim_screen_pupil_nopract, Group == "NT")
+
+db_full4new_stim_screen_pupil_nopract_nt%>%
+  group_by(stimIAPS)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(arousal_c, valence_c))+
+  geom_point()+
+  ggpubr::stat_cor()
+
+cor.test(db_full4new_stim_screen_pupil_nopract_nt$valence, db_full4new_stim_screen_pupil_nopract_nt$arousal_c)
+car::scatter3d(db_full4new_stim_screen_pupil_nopract_nt$arousal_c, 
+          db_full4new_stim_screen_pupil_nopract_nt$pup_basCor, 
+          db_full4new_stim_screen_pupil_nopract_nt$valence_c,
+          fit = "smooth"
+          # point = FALSE,
+
+          # surface = FALSE,
+          # point.col = ""
+          )
+```
+
+quick check of TAS
+
+```{r}
+
+db_full4new_stim_screen_pupil_nopract$TASc<- scale(db_full4new_stim_screen_pupil_nopract$TAS, center = TRUE, scale = TRUE)[,1]
+
+db_full4new_stim_screen_pupil_nopract<- db_full4new_stim_screen_pupil_nopract%>%
+  ungroup()%>%
+  mutate(arousal_c = scale(arousal, center = TRUE, scale = TRUE)[,1],
+         valence_c = scale(valence, center = TRUE, scale = TRUE)[,1])
+
+pupil_arousal_findings$pupil_from_ar_vale_TAS <- lmer(pup_basCor ~ (valence_c* arousal_c)*TASc +
+                                                    Mean_gray_z  +
+                                                    (1 + Mean_gray_z | ssid)+
+                                                    (0+ arousal_c | ssid),
+                                                  REML = FALSE,
+                      data = db_full4new_stim_screen_pupil_nopract%>%
+                         subset(Group == "NT"))
+                        subset(pupil_outlier == FALSE)%>%
+                        subset(arousal_outler == FALSE))
+
+summary(pupil_arousal_findings$pupil_from_ar_vale_TAS)
+
+interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale_TAS, pred = TASc, modx = arousal_c)
+interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale_TAS, pred = TASc, modx = arousal_c, mod2= valence_c)
+
 ```
@@
 # with arousal as DV
-pupil_arousal_findings$arousal_from_pup <- lmer(arousal_c ~ valence_c*pup_basCor  + (1| stimIAPS)+
-                                                 # (1 | ssid),
-                                                  (0 +valence_c+pup_basCor | ssid),
+pupil_arousal_findings$arousal_from_pup <- lmer(arousal ~ valence_c*pup_basCor  + 
+                                                  (1| stimIAPS)+
+                                                 # (1 | stimIAPS)+
+                                                  (1  | ssid),
                                                 REML = FALSE,
@@
 
-pupil_arousal_findings$valence_from_pup <- lmer(valence_c ~ arousal_c*pup_basCor  + (1| stimIAPS)+
+pupil_arousal_findings$valence_from_pup <- lmer(valence ~ arousal_c*pup_basCor  + (1| stimIAPS)+
                                                  # (1 | ssid),
-                                                  (0 +arousal_c +pup_basCor | ssid),
+                                                  (0 +arousal_c | ssid),
                                                 REML = FALSE,
                       data = subset(db_full4new_stim_screen_pupil_nopract, 
-                                    pupil_outlier == FALSE & ssid_num<500 & 
-                                      arousal_outler == FALSE))
+                                    Group == "NT"))
 summary(pupil_arousal_findings$valence_from_pup)
@@
 
+unique(tmp.df4_full_stim_downs_jun2021$timebin)
 # new folks 
 library(readr)
+
 tmp_df4_timeseries_345_356 <- read_csv("tmp.df4_timeseries_345_356.csv")
@@
 
-# match types of merging variables
+```
+
+# match types of merging variables (this is 30-hz)
+
+```{r}
+
+unique(tmp.df4_full_stim_downs_jun2021_with_beh2$timebin2)
+
+unique(tmp.df4_full_stim_downs_jun2021_with_behnew$timebin2)
 tmp.df4_full_stim_downs_jun2021_with_beh2$ssid<- as.character(tmp.df4_full_stim_downs_jun2021_with_beh2$ssid)
@@
 # temp backup
+
+tmp.df4_full_stim_downs_jun2021
 tmp.df4_full_stim_downs_jun2021_backup<- tmp.df4_full_stim_downs_jun2021
+
+unique(tmp.df4_full_stim_downs_jun2021$timebin)
+
 tmp_df4_timeseries_345_356_stim_downs_backup<- tmp_df4_timeseries_345_356_stim_downs
@@
 
+tmp.df4_full_stim_downs_jun2021$ssid<- as.character(tmp.df4_full_stim_downs_jun2021$ssid)
+tmp.df4_full_stim_downs_jun2021$tNo<- as.character(tmp.df4_full_stim_downs_jun2021$tNo)
 # bind old and new data
+# nrow(tmp.df4_full_stim_downs_jun2021)+ nrow(tmp_df4_timeseries_345_356_stim_downs) = 205703
+
+tmp.df4_full_stim_downs_jun2021$tNo<- as.character(tmp.df4_full_stim_downs_jun2021$tNo)
+
 tmp.df4_full_stim_downs_jun2021 <- bind_rows(tmp.df4_full_stim_downs_jun2021,tmp_df4_timeseries_345_356_stim_downs)
 
-tmp.df4_full_stim_downs_jun2021$tNo<- as.character(tmp.df4_full_stim_downs_jun2021$tNo)
+# tmp.df4_full_stim_downs_jun2021
+table(is.na(tmp_df4_timeseries_345_356_stim_downs$pup_basCor))
+# 355
+table(is.na(tmp.df4_full_stim_downs_jun2021$pup_basCor))
+
+# backup[]
+tmp.df4_full_stim_downs_jun2021_60bins_backup2<- tmp.df4_full_stim_downs_jun2021_60bins
+
+unique(db_full4new_stim_subset$ssid)
+
+unique(tmp.df4_full_stim_downs_jun2021$ssid)
+unique(db_full4new_stim_subset$ssid)
+
+unique(tmp.df4_full_stim_downs_jun2021$tNo)
+unique(db_full4new_stim_subset$tNo)
+
+unique(tmp.df4_full_stim_downs_jun2021$trial)
+unique(db_full4new_stim_subset$trial)
+
+tmp.df4_full_stim_downs_jun2021_60bins
+
+table(is.na(db_full4new_stim_subset$arousal))
+
+db_full4new_stim_subset
 db_full4new_stim_subset$tNo<- as.character(db_full4new_stim_subset$tNo)
 
-# backup[]
-tmp.df4_full_stim_downs_jun2021_60bins_backup<- tmp.df4_full_stim_downs_jun2021_60bins
-
-tmp.df4_full_stim_downs_jun2021_60bins<- left_join(tmp.df4_full_stim_downs_jun2021, db_full4new_stim_subset, by = c("ssid", "tNo", "trial"))
+# try see if arranging things solve the issue
+tmp.df4_full_stim_downs_jun2021<- tmp.df4_full_stim_downs_jun2021%>%
+  arrange(ssid, tNo, timerezero3)
+
+db_full4new_stim_subset<- db_full4new_stim_subset%>%
+  arrange(ssid, tNo)
+
+db_full4new_stim_subset_valis<- subset( db_full4new_stim_subset, gaze_valid_prop>.80)
+
+tmp.df4_full_stim_downs_jun2021_.1 <- left_join(tmp.df4_full_stim_downs_jun2021, db_full4new_stim_subset$gaze_valid_prop, by = c("ssid", "tNo", "trial"))
+
+table(is.na(db_full4new_stim_subset_valis$gaze_valid_prop))
+tmp.df4_full_stim_downs_jun2021_.1 <- left_join(db_full4new_stim_subset_valis,tmp.df4_full_stim_downs_jun2021,  by = c("ssid", "tNo", "trial"))
+
+table(is.na(tmp.df4_full_stim_downs_jun2021_.1$arousal))
+nrow(tmp.df4_full_stim_downs_jun2021_.1)
+nrow(tmp.df4_full_stim_downs_jun2021)
+
+nrow(db_full4new_stim_subset)
+nrow(test)
+nrow(tmp.df4_full_stim_downs_jun2021_60bins)
+unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
+
+View(db_full4new_stim_subset)
+table(is.na(db_full4new_stim_subset$arousal))
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal))
+
+table(is.na(test$arousal))
+table(is.na(test$arousal))
+
+test1<- subset(test, is.na(arousal))
+
+test2<- subset(test, !is.na(arousal))
+table(test2$ssid)
 
@@
 
-tmp.df4_full_stim_downs_jun2021_60bins$Label<- substr(tmp.df4_full_stim_downs_jun2021_60bins$stimIAPS, 1,8)
-
-tmp.df4_full_stim_downs_jun2021_60bins$Label2<- substr(tmp.df4_full_stim_downs_jun2021_60bins$stimIAPS, 1,4)
+tmp.df4_full_stim_downs_jun2021_.1$Label<- substr(tmp.df4_full_stim_downs_jun2021_.1$stimIAPS, 1,8)
+
+tmp.df4_full_stim_downs_jun2021_.1$Label2<- substr(tmp.df4_full_stim_downs_jun2021_.1$stimIAPS, 1,4)
 imageJ_IAPS$Label2<- substr(imageJ_IAPS$Label, 1,4)
@@
 unique(imageJ_IAPS$Label2)
-unique(tmp.df4_full_stim_downs_jun2021_60bins$Label2)
+unique(tmp.df4_full_stim_downs_jun2021_.1$Label2)
 
 # backup
-tmp.df4_full_stim_downs_jun2021_60bins_backup<- tmp.df4_full_stim_downs_jun2021_60bins
-
-tmp.df4_full_stim_downs_jun2021_60bins<- left_join(tmp.df4_full_stim_downs_jun2021_60bins, imageJ_IAPS, by = "Label2")
+tmp.df4_full_stim_downs_jun2021_60bins_backup<- tmp.df4_full_stim_downs_jun2021_.1
+
+tmp.df4_full_stim_downs_jun2021_60bins<- left_join(tmp.df4_full_stim_downs_jun2021_.1, imageJ_IAPS, by = "Label2")
 
@@
 
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$valence))
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$pup_basCor))
+
+as.factor(tmp.df4_full_stim_downs_jun2021_60bins$timebin)
 ```
@@
 # group_by(stimIAPS)%>%
+
 tmp.df4_full_stim_downs_jun2021_with_beh<- tmp.df4_full_stim_downs_jun2021_with_beh %>%
@@
 
-# higher sample rate]
+# higher sample rate
+
+tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_valence2
 
@@
 
+tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins%>%
+  ungroup()%>%
+  mutate(mediansplit_ground_valence = if_else(ValenceMean >=
+                                                  median(ValenceMean,
+                                                         na.rm = TRUE), "More positive", "More negative"))%>%
+  mutate(mediansplit_ground_arousal = if_else(ArousalMean >=
+                                                  median(ArousalMean,
+                                                         na.rm = TRUE), "High", "Low"))%>%
+    mutate(mediansplit_sample_valence2 = if_else(arousal >=
+                                                  median(arousal,
+                                                         na.rm = TRUE), "More positive", "More negative"))%>%
+  mutate(mediansplit_sample_arousal2 = if_else(valence >=
+                                                  median(valence,
+                                                         na.rm = TRUE), "High", "Low"))
+
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$timebin))
 ground_arousal_lab
@@
   ggplot(aes(x = timerezero3, y = pup_basCor))+
-  stat_smooth(aes(group= ground_arousal_lab, color = ground_arousal_lab), fun = mean,geom = "line",
+  stat_smooth(aes(group= mediansplit_ground_arousal, color = mediansplit_ground_arousal), fun = mean,geom = "line",
                se = F, alpha = .1, size = 1.5)+
-  stat_smooth(aes(group=ground_arousal_lab, color = ground_arousal_lab), size = 3)+  
+  stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
 theme_classic()+
@@
   xlim(0,6)+
-   facet_grid(~mediansplit_self_valence)
+   facet_grid(~mediansplit_ground_valence)
+
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_arousal2))
+
+mediansplit_sample_arousal2
+
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$Group))
+
+tmp.df4_full_stim_downs_jun2021_60bins %>%
+  subset(Group == "NT")%>%
+  # subset(!is.na(mediansplit_sample_arousal2))%>%
+  ggplot(aes(x = timerezero3, y = pup_basCor))+
+  stat_smooth(aes(group= mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), fun = mean,geom = "line",
+               se = F, alpha = .1, size = 1.5)+
+  stat_smooth(aes(group=mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), size = 3)+  
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")+
+  xlim(0,6)+
+   facet_grid(~mediansplit_sample_valence2)
 
@@
 # unique(tmp.df4_full_stim_downs_jun2021_60bins$)
-
+table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_c))
 for (b in 1:length(nbins)) {
@@
   ggplot(aes(timebins, Estimate_ar_vl))+
-  geom_line(size = 1)
-  geom_line(aes(y = t_vl), linetype = "dashed", size = 1)+
-  geom_line(aes(y = t_br), linetype = "dotted", size = 1)+
-  geom_line(aes(y = t_ar), linetype = "dotdash", size = 1, color = "red")
+  # geom_line(size = 1)
+  # geom_line(aes(y = t_vl), linetype = "dashed", size = 1)+
+  # geom_line(aes(y = t_br), linetype = "dotted", size = 1)+
+  # geom_line(aes(y = t_ar), linetype = "dotdash", size = 1, color = "red")
+  #
 
@@
 timecourse_60bin_result_df %>%
-  mutate(test=rollapply(p_ar, width=3, max, align="left", fill=NA, na.rm=TRUE))%>%
+  mutate(test=rollapply(p_ar, width=3, max, align="left", fill=NA, na.rm=TRUE))
+
+View(timecourse_60bin_result_df)
 
@@
 
-tmp.df4_full_stim_downs_jun2021_60bins%>%
-  subset(ssid == 331 & tNo ==40)%>%
+tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins%>%
+  # subset(ssid == 331 & tNo ==40)%>%
   group_by(ssid, tNo)%>%
   arrange(ssid,tNo, timerezero3)%>%
-  mutate(pup_vel_smooth = zoo::rollmean(pup_velocity, k = 3, fill = NA))%>%
+  mutate(pup_vel_smooth = zoo::rollmean(pup_velocity, k = 3, fill = NA))
    ggplot(aes(timerezero3, pup_velocity))+
@@
 
-paste0(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_arousal2)
+# paste0(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_arousal2)
 
@@
 
-pupiul velocity and speed might better caprure arousal dynamics because the temporal dynamics are less adffected by a susrtauned effect of brighetenss.
-whereas amplitude is p[robably strongly affected by brighteness which restricts variability in input from a arousal componenets
+SCR
+```{r}
+
+db_full4new_stim_screen_pupil_nopract_nt<- subset(db_full4new_stim_screen_pupil_nopract, Group == "NT")
+
+db_full4new_stim_screen_pupil_nopract_nt_304<- subset(db_full4new_stim_screen_pupil_nopract_nt, ssid_num>303)
+
+db_full4new_stim_screen_pupil_nopract_nt_304
+
+db_full4new_stim_screen_pupil_nopract_nt_304<- db_full4new_stim_screen_pupil_nopract_nt_304%>%
+  ungroup%>%
+  mutate(valence_c = scale(valence, center = TRUE, scale = TRUE)[,1])%>%
+  mutate(arousal_c = scale(arousal, center = TRUE, scale = TRUE)[,1])%>%
+  mutate(TASc = scale(TAS, center = TRUE, scale = TRUE)[,1])
+
+# models
+table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304$BIO_CDA.SCR))
+
+pupil_arousal_findings$arousal_scr <- lmer(log(BIO_CDA.SCR+.1) ~ arousal_c*valence_c +
+                                             (1|ssid) + (1|stimIAPS),
+                        REML = FALSE,
+                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304))
+
+summary(pupil_arousal_findings$arousal_scr)
+
+interactions::interact_plot(pupil_arousal_findings$arousal_scr, pred = arousal_c, modx = valence_c)
+
+# arousal_BIO_CDA.AmpSum
+pupil_arousal_findings$arousal_BIO_CDA.AmpSum <- lmer(log(BIO_CDA.AmpSum+.1) ~ arousal_c*valence_c +
+                                             (1|ssid) + (1|stimIAPS),
+                        REML = FALSE,
+                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304))
+
+summary(pupil_arousal_findings$arousal_BIO_CDA.AmpSum)
+
+interactions::interact_plot(pupil_arousal_findings$arousal_BIO_CDA.AmpSum, pred = arousal_c, modx = valence_c)
+
+# BIO_CDA.ISCR
+pupil_arousal_findings$BIO_CDA.ISCR <- lmer(log(BIO_CDA.ISCR+.1) ~ arousal_c*valence_c +
+                                             (1+valence_c|ssid) + (1|stimIAPS),
+                        REML = FALSE,
+                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304))
+
+summary(pupil_arousal_findings$BIO_CDA.ISCR)
+
+interactions::interact_plot(pupil_arousal_findings$BIO_CDA.ISCR, pred = arousal_c, modx = valence_c)
+
+# alexithymia
+table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304$gsr_response))
+pupil_arousal_findings$BIO_CDA.ISCR_TAS <- lmer(log(BIO_CDA.AmpSum +.1) ~ arousal_c+
+                                             (1|ssid) + (1|stimIAPS),
+                        REML = FALSE,
+                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304$gsr_basCor))
+summary(pupil_arousal_findings$BIO_CDA.ISCR_TAS)
+```
+
+Heart rate
+
+```{r}
+
+# keep stim and and fixation
+unique(db_full6new$screencontent)
+unique(db_full6new$screencontent_no)
+colnames(db_full6new)
+
+# 345:355
+library(readr)
+library(readr)
+ # read_csv("tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv")
+View(tmp_df4_sum_full_bio_hr_self_parsed_345_356)
+
+db_HR_bio_final_346_355_withfix <-  read_csv("tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv")
+View(db_HR_bio_final_346_355_withfix)
+
+db_HR_bio_final_346_355_withfix$screencontent<- db_HR_bio_final_346_355_withfix$screen_content
+db_HR_bio_final_346_355_withfix<- subset(db_HR_bio_final_346_355_withfix, tNo > -7)
+
+db_HR_bio_final_346_355_withfix$screencontent_no<- if_else(db_HR_bio_final_346_355_withfix$screen_content == "fixation", 1,
+                                                           if_else(db_HR_bio_final_346_355_withfix$screen_content == "stim", 2,
+                                                                   if_else(db_HR_bio_final_346_355_withfix$screen_content == "valence", 3, 4)))
+
+db_HR_bio_final_346_355_withfix_stim <- subset(db_HR_bio_final_346_355_withfix, screencontent_no<3)
+
+# 
+db_HR_bio_final_346_355_withfix_stim$tNo<- db_HR_bio_final_346_355_withfix_stim$tNo3
+unique(db_HR_bio_final_346_355_withfix$tNo)
+unique(db_HR_bio_final_346_355_withfix$tNo)
+
+db_HR_bio_final_346_355_withfix_stim$tNo2<-NULL
+
+db_HR_bio_final_346_355_withfix_stim$tNo3<- NULL
+
+unique(db_HR_bio_final_346_355_withfix$screencontent)
+unique(db_full6new_hr_fix_stim$screencontent)
+# db_HR_bio_final_346_355_withfix$screencontent_no<-
+
+colnames(db_full6new)
+
+db_full6new_hr_fix_stim <- subset(db_full6new, screencontent_no <3)
+
+View(db_full6new_hr_fix_stim)
+# fixation"    "stim" 
+colnames(db_full6new_hr_fix_stim)
+colnames(db_HR_bio_final_346_355_withfix_stim)
+
+db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR<- db_HR_bio_final_346_355_withfix_stim$Mean_HR
+
+# keep controls
+unique(db_full6new_hr_fix_stim$ssid)
+db_full6new_hr_fix_stim$ssid_num <- as.numeric(as.character(db_full6new_hr_fix_stim$ssid))
+
+db_full6new_hr_fix_stim_nt<- subset(db_full6new_hr_fix_stim, Group == "NT")
+unique(db_full6new_hr_fix_stim_nt$ssid_num)
+
+db_full6new_hr_fix_stim_nt<- subset(db_full6new_hr_fix_stim, ssid_num> 303)
+unique(db_full6new_hr_fix_stim_nt$ssid)
+colnames(db_full6new_hr_fix_stim_nt)
+# HR differences
+db_full6new_hr_fix_stim_nt$Bio_Mean_HR_fix<- if_else(db_full6new_hr_fix_stim_nt$screencontent_no ==1, db_full6new_hr_fix_stim_nt$Bio_Mean_HR, NULL)
+
+db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR_fix<- if_else(db_HR_bio_final_346_355_withfix_stim$screencontent_no ==1, db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR, NULL)
+
+View(db_full6new_hr_fix_stim_nt)
+View(db_HR_bio_final_346_355_withfix_stim)
+
+db_HR_bio_final_346_355_withfix_stim$Mean_HR<- NULL
+
+db_HR_bio_final_346_355_withfix_stim$ssid<- as.character(db_HR_bio_final_346_355_withfix_stim$ssid)
+
+db_HR_bio_final_346_355_withfix_stim$tNo <- db_HR_bio_final_346_355_withfix_stim$tNo3.x
+unique(db_HR_bio_final_346_355_withfix_stim$tNo)
+
+db_HR_bio_final_346_355_withfix_stim$tNo <- as.character(db_HR_bio_final_346_355_withfix_stim$tNo)
+db_HR_bio_final_346_355_withfix_stim$trigger <- as.character(db_HR_bio_final_346_355_withfix_stim$trigger)
+
+db_full6new_hr_fix_stim_nt$trigger<- as.character(db_full6new_hr_fix_stim_nt$trigger)
+db_full6new_hr_fix_stim_nt$trigger.x<- NULL
+
+# db_HR_bio_final_346_355_withfix_stim$trig <- as.character(db_HR_bio_final_346_355_withfix_stim$tNo)
+
+db_HR_bio_final_346_355_withfix_stim$triger<- NULL
+db_HR_bio_final_346_355_withfix_stim$trigger.x<- NULL
+
+db_HR_bio_final_346_355_withfix_stim$trigger.y<- NULL
+db_HR_bio_final_346_355_withfix_stim$trigger2<- NULL
+db_HR_bio_final_346_355_withfix_stim$trigger_200<- NULL
+
+nrow(db_full6new_hr_fix_stim_nt)+ nrow(db_HR_bio_final_346_355_withfix_stim)
+# 6895
+# nrow(bind_rows(db_full6new_hr_fix_stim_nt, db_HR_bio_final_346_355_withfix_stim))
+db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR_fix
+db_full6new_hr_fix_stim_nt1<- bind_rows(db_full6new_hr_fix_stim_nt,
+                                        db_HR_bio_final_346_355_withfix_stim)
+
+library(dplyr)
+library(tidyverse)
+
+db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1 %>%
+  group_by(ssid, tNo) %>%
+  arrange(ssid, tNo,screencontent_no)%>%
+  fill(Bio_Mean_HR_fix, .direction = "down")%>%
+  subset(screencontent_no == 2)
+
+View(db_full6new_hr_fix_stim_nt1.1)
+
+db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1 %>%
+  mutate(Bio_Mean_HR_dif = Bio_Mean_HR - Bio_Mean_HR_fix)
+
+# 2 1
+stim - fix
+
+db_full6new_hr_fix_stim_nt1.1%>%
+  ggplot(aes(Bio_Mean_HR_dif))+
+  geom_histogram()
+
+?scatter3d
+
+db_full6new_hr_fix_stim_nt1.1%>%
+  subset(!is.na(pup_basCor))%>%
+   subset(!is.na(BIO_CDA.PhasicMax))%>%
+  subset(!is.na(Bio_Mean_HR_dif))
+
+db_full6new_hr_fix_stim_nt1<- db_full6new_hr_fix_stim_nt1%>%
+  group_by(ssid)%>%
+  mutate(BIO_CDA.PhasicMax_z= scale(BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])
+
+scatter3d(x = db_full6new_hr_fix_stim_nt1$pup_basCor, 
+          y = db_full6new_hr_fix_stim_nt1$BIO_CDA.PhasicMax_z, 
+          z = db_full6new_hr_fix_stim_nt1$Bio_Mean_HR_dif, 
+          fit = "smooth",
+
+          surface = FALSE,
+          point.col = "blue",
+          # point
+          groups = as.factor(db_full6new_hr_fix_stim_nt1$mediansplit_ground_arousal),
+          ellipsoid = TRUE)
+
+cor(db_full6new_hr_fix_stim_nt1[,c("pup_basCor", "BIO_CDA.PhasicMax_z","Bio_Mean_HR_dif")], use = "complete")
+
+db_full6new_hr_fix_stim_nt1%>%
+  group_by(ssid,mediansplit_ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(pup_basCor,BIO_CDA.PhasicMax_z, color= mediansplit_ground_valence))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  ylim(0,.4)+
+  ggpubr::stat_cor()
+
+db_full6new_hr_fix_stim_nt1%>%
+  # group_by(ssid)%>%
+  # mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif))
+  group_by(ssid,mediansplit_ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(pup_basCor,Bio_Mean_HR_dif_z, color= mediansplit_ground_valence))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  # ylim(-7,2)+
+  ggpubr::stat_cor()
+
+db_full6new_hr_fix_stim_nt1%>%
+  subset(!is.na(mediansplit_ground_valence))%>%
+  # group_by(ssid)%>%
+  # mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif))
+  group_by(ssid,mediansplit_ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(BIO_CDA.PhasicMax_z,Bio_Mean_HR_dif, color= mediansplit_ground_valence))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  # ylim(-7,2)+
+  ggpubr::stat_cor()+
+  facet_grid(~mediansplit_ground_valence)
+
+```
+
+```{r}
+
+db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif_outl <- if_else(abs(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif)>                                                   (median(abs(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif),na.rm = TRUE) +                                                               (4*(sd(abs(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif), na.rm = TRUE)))), "outlier", "not outlier")
+
+db_full6new_hr_fix_stim_nt1.1%>%
+  ggplot(aes(Bio_Mean_HR_dif))+
+  geom_histogram()+
+  facet_grid(~Bio_Mean_HR_dif_outl)
+
+```
+
+```{r}
+db_full6new_hr_fix_stim_nt1.1 %>%
+    subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
+  subset(ssid_num<500)%>%
+  group_by(ssid)%>%
+  mutate(Bio_Mean_HR_dif_ssid = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
+  group_by(ssid)%>%
+  # mutate(Bio_Mean_HR_dif_stim = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(TAS, Bio_Mean_HR_dif))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()
+
+db_full6new_hr_fix_stim_nt1.1 %>%
+    subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
+  subset(ssid_num<500)%>%
+  # group_by(ssid)%>%
+  mutate(Bio_Mean_HR_dif = abs(Bio_Mean_HR_dif))%>%
+  group_by(ssid, stimIAPS)%>%
+  mutate(Bio_Mean_HR_dif_stim = abs(Bio_Mean_HR_dif))%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(TASc, Bio_Mean_HR_dif))+
+
+  # geom_point()
+
+  geom_smooth(aes(group = stimIAPS, y =Bio_Mean_HR_dif_stim), method=lm, se=FALSE, colour = "gray40", alpha = .01,linetype="dashed", size = .2 )+
+  geom_smooth( method=lm, se=FALSE, linetype="dashed",
+             color="darkred", size = 2)+
+  stat_summary(geom = 'pointrange', pch = 1)+
+    ggpubr::stat_cor()+
+
+  # geom_point()+
+  # stat_summary(aes(group =ssid, y = Bio_Mean_HR_dif),method = "line",alpha = .1)+
+  # ggpubr::stat_cor()+
+  p$graphstyle+
+  xlab("Alexithymia (Z)")+
+  ylab("HR difference")+
+p$graphstyle
+
+db_full6new_hr_fix_stim_nt1$TASc<- scale(db_full6new_hr_fix_stim_nt1$TAS, center = TRUE, scale = TRUE)
+
+hr_bio <- lmer(Bio_Mean_HR_dif ~ TASc * arousal_c + 
+                 (1|ssid) + 
+                 (1| stimIAPS),
+     REML = FALSE,
+     data = subset(db_full6new_hr_fix_stim_nt1.1, 
+                   Bio_Mean_HR_dif_outl == "not outlier"))
+
+interactions::interact_plot(hr_bio, pred = arousal_c, modx = TASc)
+
+summary(hr_bio)
+
+subset(db_full6new_hr_fix_stim_nt1, Bio_Mean_HR_dif_outl == "not outlier")
+
+```

### 2021-09-01 Paper_Analyses_subj_obje_arousal.Rmd
found an issue of missing heart rate data
almost all new neurotypicals 345-355 are misising practice heart rate data, and some clinical folks (606) are missing hr because their ecg was inverted wrongly

@@
 
+unique(db_full4new_stim_screen_pupil_nopract_nt$screencontent)
 db_full4new_stim_screen_pupil_nopract_nt_304<- subset(db_full4new_stim_screen_pupil_nopract_nt, ssid_num>303)
@@
 
+# phasic
+unique(db_full4new_stim_screen_pupil_nopract_nt_304$ssid)
+
+pupil_arousal_findings$BIO_CDA.PhasicMax <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c * valence_c + (1|ssid),
+                        REML = FALSE,
+                        data = db_full4new_stim_screen_pupil_nopract_nt_304)
+
+summary(pupil_arousal_findings$BIO_CDA.PhasicMax)
+anova(pupil_arousal_findings$arousal_phas_max)
+interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred = arousal_c, modx = valence_c)
+
+interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred =valence_c , modx =  arousal_c)
+
+# Global
+unique(db_full4new_stim_screen_pupil_nopract_nt_304$ssid)
+
+pupil_arousal_findings$BIO_Global.Mean <- lmer(log1p(BIO_Global.Mean+.1) ~ arousal_c * valence_c + (1|ssid)+ (1|stimIAPS),
+                        REML = FALSE,
+                        data = db_full4new_stim_screen_pupil_nopract_nt_304)
+
+# TTP
+table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304$BIO_TTP.AmpSum))
+pupil_arousal_findings$BIO_TTP.AmpSum <- lmer(log1p(BIO_TTP.AmpSum+.1) ~ arousal_c * valence_c + (1|ssid)+ (1|stimIAPS),
+                        REML = FALSE,
+                        data = db_full4new_stim_screen_pupil_nopract_nt_304)
+
+summary(pupil_arousal_findings$BIO_TTP.AmpSum)
+
+anova(pupil_arousal_findings$arousal_phas_max)
+interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred = arousal_c, modx = valence_c)
+
+interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred =valence_c , modx =  arousal_c)
+
 # alexithymia
-table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304$gsr_response))
+table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304$BIO_CDA.PhasicMax))
+interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred = arousal_c, modx = valence_c)
 pupil_arousal_findings$BIO_CDA.ISCR_TAS <- lmer(log(BIO_CDA.AmpSum +.1) ~ arousal_c+
@@
 summary(pupil_arousal_findings$BIO_CDA.ISCR_TAS)
+
+# table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304
+
+# collapsed
 ```
@@
 db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR_fix
+
+colnames(db_HR_bio_final_346_355_withfix_stim)
+as.factor(db_HR_bio_final_346_355_withfix_stim$stimIAPS)
+db_full6new_hr_fix_stim_nt$stimIAPS
+
+db_HR_bio_final_346_355_withfix_stim
+
+as.factor(db_HR_bio_final_346_355_withfix_stim$stim.x)
+as.factor(db_HR_bio_final_346_355_withfix_stim$stim.y)
+db_HR_bio_final_346_355_withfix_stim$stim.y<- NULL
+
+unique(db_HR_bio_final_346_355_withfix_stim$screencontent)
+unique(db_full6new_hr_fix_stim_nt$screencontent)
+unique(db_full6new_hr_fix_stim_nt$screencontent.y)
+
+db_full6new_hr_fix_stim_nt$screencontent.x<- NULL
+db_full6new_hr_fix_stim_nt$screencontent.y<- NULL
+
+unique(db_full6new_hr_fix_stim_nt$trialUnq.x)
+unique(db_full6new_hr_fix_stim_nt$trialUnq.y)
+
+db_full6new_hr_fix_stim_nt$trialUnq<- db_full6new_hr_fix_stim_nt$trialUnq.x
+db_full6new_hr_fix_stim_nt$trialUnq.y<- NULL
+db_full6new_hr_fix_stim_nt$trialUnq.x<- NULL
+
+db_HR_bio_final_346_355_withfix_stim$stim<- db_HR_bio_final_346_355_withfix_stim$stim.x
+db_HR_bio_final_346_355_withfix_stim$stim<- db_HR_bio_final_346_355_withfix_stim$stim.x
+
+# bind heartrate old and new
+
 db_full6new_hr_fix_stim_nt1<- bind_rows(db_full6new_hr_fix_stim_nt,
@@
 
+table(is.na(db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR))
+table(is.na(db_full6new_hr_fix_stim_nt$Bio_Mean_HR))
+
 library(dplyr)
@@
 
+table(is.na(db_full6new_hr_fix_stim_nt1$Bio_Mean_HR))
+
+test<- subset(db_full6new_hr_fix_stim_nt1, is.na(Bio_Mean_HR))
+
+unique(test$ssid)
+# 606
+
 db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1 %>%
-  group_by(ssid, tNo) %>%
-  arrange(ssid, tNo,screencontent_no)%>%
+  # mutate()
+  group_by(as.numeric(ssid_num), as.numeric(tNo)) %>%
+  arrange(ssid_num, as.numeric(tNo),as.numeric(screencontent_no))%>%
+  # select(ssid, tNo,screencontent_no, Bio_Mean_HR,Bio_Mean_HR_fix)
   fill(Bio_Mean_HR_fix, .direction = "down")%>%
@@
 ```{r}
+
+unique(db_full6new_hr_fix_stim_nt1.1$screencontent_no)
+
+test<- subset(db_full6new_hr_fix_stim_nt1.1, is.na(Bio_Mean_HR_dif))
 
@@
 
+# model
+
+table(is.na(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif))
+Bio_Mean_HR_dif_outl
+
 hr_bio <- lmer(Bio_Mean_HR_dif ~ TASc * arousal_c + 

### 2021-09-01 IAPS_PREPROCESSING_2021_1.Rmd
fix missing pratice in heart rate data of ssid 346-355
The issue was cause dby merging final heart rate with the full dataset using thw wrong tno variable

@@
 
+table(is.na(db_HR_bio_final$Mean_HR))
+
 # db_HR_bio_final<- bind_rows(db_HR_bio2, db_biohrold2test)
@@
 
+unique(tmp.df4_sum_full_bio$screen_content)
+
 tmp.df4_sum_full_bio$screen_content<- if_else(tmp.df4_sum_full_bio$screencontent == "ValenceResp", "valence",
@@
 
-tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final, by = c('ssid', 'tNo', 'screen_content'))
+db_HR_bio_final
+
+table(is.na(tmp.df4_sum_full_bio_hr$Mean_HR))
+
+test<- subset(tmp.df4_sum_full_bio_hr, is.na(Mean_HR))
+
+db_HR_bio_final_norest<- subset(db_HR_bio_final, screen_content!= "Rest")
+
+unique(tmp.df4_sum_full_bio$tNo)
+
+unique(db_HR_bio_final_norest$tNo)
+
+# remeber to do this otherwise tno will be matchjing wrong data
+db_HR_bio_final_norest$tNo<- db_HR_bio_final_norest$tNo3
+
+tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final_norest, by = c('ssid', 'tNo', 'screen_content'))
 
 unique(tmp.df4_sum_full_bio_hr$tNo)
+
+table(is.na(tmp.df4_sum_full_bio_hr$Mean_HR))
 
@@
 
+unique(tmp.df4_sum_full_bio_hr_self$ssid)
+table(is.na(tmp.df4_sum_full_bio_hr_self$Mean_HR))
 tmp.df4_sum_full_bio_hr_self <- left_join(tmp.df4_sum_full_bio_hr, db_selfrep, by = 'ssid')

### 2021-09-01 IAPS_PREPROCESSING_2021_1.Rmd
HR analysyes
started the actual HR models

@@
 unique(tmp.df4_sum_full_bio_hr_self$ssid)
+table(is.na(tmp.df4_sum_full_bio_hr$Mean_HR))
+
+tmp.df4_sum_full_bio_hr_self <- left_join(tmp.df4_sum_full_bio_hr, db_selfrep, by = 'ssid')
 table(is.na(tmp.df4_sum_full_bio_hr_self$Mean_HR))
-tmp.df4_sum_full_bio_hr_self <- left_join(tmp.df4_sum_full_bio_hr, db_selfrep, by = 'ssid')
-
 write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_bio_hr_self_345_356.csv')
@@
 # tmp.df4_sum_full<-
+
+tmp.df4_sum_full_bio_hr_self_parsed
+table(is.na(tmp.df4_sum_full_bio_hr_self_parsed$Mean_HR))
 

### 2021-09-01 Paper_Analyses_subj_obje_arousal.Rmd
HR analysyes
started the actual HR models

@@
 
+# tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv
 db_HR_bio_final_346_355_withfix <-  read_csv("tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv")
@@
 # 
-db_HR_bio_final_346_355_withfix_stim$tNo<- db_HR_bio_final_346_355_withfix_stim$tNo3
+# db_HR_bio_final_346_355_withfix_stim$tNo<- db_HR_bio_final_346_355_withfix_stim$tNo3
 unique(db_HR_bio_final_346_355_withfix$tNo)
@@
 
+db_HR_bio_final_346_355_withfix_stim$ssid_num<- as.numeric(db_HR_bio_final_346_355_withfix_stim$ssid)
 # keep controls
@@
 
+table(is.na(db_full6new_hr_fix_stim))
+
+db_full6new_hr_fix_stim$Group<- if_else(db_full6new_hr_fix_stim$ssid_num< 500, "NT",
+                                        if_else(db_full6new_hr_fix_stim$ssid_num>700, "NT",
+                                                "ASC"))
+
+table(is.na(db_full6new_hr_fix_stim$Group))
+
 db_full6new_hr_fix_stim_nt<- subset(db_full6new_hr_fix_stim, Group == "NT")
@@
 
-db_full6new_hr_fix_stim_nt<- subset(db_full6new_hr_fix_stim, ssid_num> 303)
+# attention
+db_full6new_hr_fix_stim_nt<- subset(db_full6new_hr_fix_stim_nt, ssid_num> 303)
 unique(db_full6new_hr_fix_stim_nt$ssid)
 colnames(db_full6new_hr_fix_stim_nt)
+
 # HR differences
@@
 
-db_HR_bio_final_346_355_withfix_stim$triger<- NULL
+# db_HR_bio_final_346_355_withfix_stim$triger<- NULL
 db_HR_bio_final_346_355_withfix_stim$trigger.x<- NULL
@@
 db_HR_bio_final_346_355_withfix_stim$stim<- db_HR_bio_final_346_355_withfix_stim$stim.x
-db_HR_bio_final_346_355_withfix_stim$stim<- db_HR_bio_final_346_355_withfix_stim$stim.x
+# db_HR_bio_final_346_355_withfix_stim$stim<- db_HR_bio_final_346_355_withfix_stim$stim.x
 
 # bind heartrate old and new
+table(is.na(db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR))
+table(is.na(db_full6new_hr_fix_stim_nt$Bio_Mean_HR))
+test<- subset(db_full6new_hr_fix_stim_nt, is.na(Bio_Mean_HR))
+test1<- subset(db_HR_bio_final_346_355_withfix_stim, is.na(Bio_Mean_HR))
 
@@
 
-table(is.na(db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR))
-table(is.na(db_full6new_hr_fix_stim_nt$Bio_Mean_HR))
+unique(db_full6new_hr_fix_stim_nt$Group)
+
+# 346 missing praticdata - it was processed wrongly
+# 347 missing
 
@@
 # 606
+
+# 348 to 355 are missing pratice
 
@@
 
+# 2 1
+# stim - fix
 db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1 %>%
   mutate(Bio_Mean_HR_dif = Bio_Mean_HR - Bio_Mean_HR_fix)
-
-# 2 1
-stim - fix
 
@@
 
-scatter3d(x = db_full6new_hr_fix_stim_nt1$pup_basCor, 
-          y = db_full6new_hr_fix_stim_nt1$BIO_CDA.PhasicMax_z, 
-          z = db_full6new_hr_fix_stim_nt1$Bio_Mean_HR_dif, 
+car::scatter3d(x = db_full6new_hr_fix_stim_nt1.1$pup_basCor, 
+          y = db_full6new_hr_fix_stim_nt1.1$BIO_CDA.PhasicMax_z, 
+          z = db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif, 
           fit = "smooth",
@@
           # point
-          groups = as.factor(db_full6new_hr_fix_stim_nt1$mediansplit_ground_arousal),
+          groups = as.factor(db_full6new_hr_fix_stim_nt1.1$mediansplit_ground_arousal),
           ellipsoid = TRUE)
@@
 
+unique(test$ssid)
+
 db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif_outl <- if_else(abs(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif)>                                                   (median(abs(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif),na.rm = TRUE) +                                                               (4*(sd(abs(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif), na.rm = TRUE)))), "outlier", "not outlier")
@@
 ```{r}
+
+db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1%>%
+  ungroup()%>%
+  mutate(arousal_c = scale(arousal, center = TRUE, scale = TRUE)[,1],
+         valence_c = scale(valence, center = TRUE, scale = TRUE)[,1])
+
 db_full6new_hr_fix_stim_nt1.1 %>%
-    subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
-  subset(ssid_num<500)%>%
+    # subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
+  # subset(ssid_num<500)%>%
   group_by(ssid)%>%
@@
     subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
-  subset(ssid_num<500)%>%
+  # subset(ssid_num<500)%>%
   # group_by(ssid)%>%
@@
 
-subset(db_full6new_hr_fix_stim_nt1, Bio_Mean_HR_dif_outl == "not outlier")
-
-```
+# create more variables ground and self
+db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1%>%
+  ungroup()%>%
+  mutate(mediansplit_ground_valence = if_else(ValenceMean >=
+                                                  median(ValenceMean,
+                                                         na.rm = TRUE), "More positive", "More negative"))%>%
+  mutate(mediansplit_ground_arousal = if_else(ArousalMean >=
+                                                  median(ArousalMean,
+                                                         na.rm = TRUE), "High", "Low"))%>%
+    mutate(mediansplit_sample_valence2 = if_else(valence >=
+                                                  median(valence,
+                                                         na.rm = TRUE), "More positive", "More negative"))%>%
+  mutate(mediansplit_sample_arousal2 = if_else(arousal >=
+                                                  median(arousal,
+                                                         na.rm = TRUE), "High", "Low"))
+
+db_full6new_hr_fix_stim_nt1.1%>%
+  subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
+  subset(!is.na(mediansplit_ground_valence))%>%
+  group_by(ssid,mediansplit_ground_arousal, mediansplit_ground_valence,)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(mediansplit_ground_arousal, Bio_Mean_HR_dif))+
+  geom_jitter(alpha = .2, width = .2)+
+   geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
+  stat_summary(geom = 'pointrange')+
+  # stat_smooth(aes(group = ssid), se = F, method = 'lm', alpha = .2)+
+    facet_grid(~mediansplit_ground_valence)
+
+```
+
+```{r}
+db_full6new_hr_fix_stim_nt1.1%>%
+  subset(!is.na(mediansplit_ground_valence))%>%
+  subset(Bio_Mean_HR_dif_outl== "not outlier")%>%
+  group_by(ssid, mediansplit_ground_arousal,mediansplit_ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(mediansplit_ground_arousal, Bio_Mean_HR_dif, fill = mediansplit_ground_valence))+
+  geom_jitter(alpha = .2, width = .2)+
+   geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
+  stat_summary(geom = 'pointrange')+
+  stat_summary(aes(group = ssid), geom = 'line', alpha = .2)+
+
+  facet_grid(~mediansplit_ground_valence)+
+     ggpubr::stat_compare_means()+
+  # p$graphstyle+
+  scale_fill_brewer(palette = "Dark2")
+
+```
+
+Models
+
+```{r}
+table(is.na(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif))
+test3<- subset(db_full6new_hr_fix_stim_nt1.1, is.na(Bio_Mean_HR_dif))
+test4<- subset(db_full6new_hr_fix_stim_nt1.1, !is.na(Bio_Mean_HR_dif))
+unique(test4$ssid)
+
+db_full6new_hr_fix_stim_nt1.1$ssid<- as.factor(as.character(db_full6new_hr_fix_stim_nt1.1$ssid))
+
+db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1%>%
+  ungroup()%>%
+  mutate(arousal_c = scale(arousal, center = TRUE, scale = TRUE)[,1],
+         valence_c = scale(valence, center = TRUE, scale = TRUE)[,1])
+
+unique(db_full6new_hr_fix_stim_nt1$Group)
+# test - analyse just positive
+summary(hr_dif_models$arousal_val)
+
+hr_dif_models$arousal_val <- lmer(Bio_Mean_HR_dif ~   valence_c+
+                                        + (1 | ssid) + 
+                                    (1|stimIAPS),
+                                        # (1|mediansplit_sample_arousal2),
+     REML = FALSE,
+     data = subset(db_full6new_hr_fix_stim_nt1.1, 
+                   # mediansplit_ground_valence == "More negative" &
+                     Bio_Mean_HR_dif_outl == "not outlier"))
+
+summary(hr_dif_models$arousal_val)
+
+summary(hr_dif_models$arousal_AR)
+
+View(db_full6new_hr_fix_stim_nt1.1)
+
+hr_outlier<- subset(db_full6new_hr_fix_stim_nt1.1, 
+                   # mediansplit_ground_valence == "More negative" &
+                     Bio_Mean_HR_dif_outl != "not outlier")
+
+hr_dif_models$arousal_AR <- lmer(Bio_Mean_HR_dif ~   arousal_c+
+                                        + (1 | ssid) + 
+                                    (1|stimIAPS),
+                                        # (1|mediansplit_sample_arousal2),
+     REML = FALSE,
+     data = subset(db_full6new_hr_fix_stim_nt1.1, 
+                   # mediansplit_ground_valence == "More negative" &
+                     Bio_Mean_HR_dif_outl == "not outlier"))
+
+summary(hr_dif_models$arousal_AR)
+
+unique(db_full6new_hr_fix_stim_nt1$ssid)
+
+summary(hr_dif_models$valfrom_hr)
+
+unique(db_full6new_hr_fix_stim_nt1.1$ssid)
+
+hr_dif_models$valfrom_hr <- lmer(arousal_c ~   Bio_Mean_HR_dif* valence_c+
+                                        + (1 | ssid) + (1|stimIAPS),
+                                        # (1|mediansplit_sample_arousal2),
+     REML = FALSE,
+     data = subset(db_full6new_hr_fix_stim_nt1.1, 
+                   # mediansplit_ground_valence == "More positive" &
+                   Bio_Mean_HR_dif_outl == "not outlier"))
+# arousal_c
+summary(hr_dif_models$valfrom_hr)
+
+# arousal * valence
+
+hr_dif_models$hr_dif_ar_vl <- lmer(Bio_Mean_HR_dif~arousal_c   * valence_c+
+                                        + (1 | ssid),
+                                     # (1|stimIAPS),
+                                        # (1|mediansplit_sample_arousal2),
+     REML = FALSE,
+     data = subset(db_full6new_hr_fix_stim_nt1.1, 
+                   # mediansplit_ground_valence == "More positive" &
+                   Bio_Mean_HR_dif_outl == "not outlier" & !is.na(Bio_Mean_HR_dif)))
+# arousal_c
+summary(hr_dif_models$hr_dif_ar_vl)
+
+```

### 2021-09-01 Paper_Analyses_subj_obje_arousal.Rmd
HR visualisations

@@
 ```
+
+correlaation between the multiple signals
+
+```{r}
+table(is.na(db_full6new_hr_fix_stim_nt1.1$BIO_C))
+db_full6new_hr_fix_stim_nt1.1$pup_basCor
+db_full6new_hr_fix_stim_nt1.1$TTP.nSCR
+db_full6new_hr_fix_stim_nt1.1$CDA.nSCR
+db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif
+
+# 
+library(tidyverse)
+library(ggplot2)
+db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1 %>%
+  group_by(ssid)%>%
+  mutate(BIO_CDA.PhasicMax_z = scale(BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
+  mutate(BIO_CDA.SCR_z = scale(BIO_CDA.SCR, center = TRUE, scale = TRUE)[,1])%>%
+  mutate(BIO_CDA.ISCR_z = scale(BIO_CDA.ISCR, center = TRUE, scale = TRUE)[,1])%>%
+  mutate(BIO_TTP.AmpSum_z = scale(BIO_TTP.AmpSum, center = TRUE, scale = TRUE)[,1])%>%
+  mutate(BIO_CDA.AmpSum_z = scale(BIO_CDA.AmpSum, center = TRUE, scale = TRUE)[,1])%>%
+  mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1])
+
+car::scatter3d(x = db_full6new_hr_fix_stim_nt1.1$pup_basCor, 
+          y = db_full6new_hr_fix_stim_nt1.1$BIO_CDA.PhasicMax_z, 
+          z = db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif, 
+          fit = "smooth",
+
+          surface = TRUE,
+          point.col = "blue")
+          # point
+db_full6new_hr_fix_stim_nt1.1%>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(BIO_CDA.PhasicMax_z, pup_basCor))+
+  geom_point()+
+  geom_smooth(method = lm, se = F)+
+  ggpubr::stat_cor()
+
+db_full6new_hr_fix_stim_nt1.1%>%
+  group_by(ssid)%>%
+  mutate(cor_pup_scr = cor(BIO_CDA.PhasicMax_z, pup_basCor, use = "complete"))%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(cor_pup_scr))+
+  geom_histogram()
+
+db_full6new_hr_fix_stim_nt1.1 %>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(BIO_CDA.SCR_z, Bio_Mean_HR_dif_z))+
+  geom_point()+
+  geom_smooth(method = lm, se = F)+
+  ggpubr::stat_cor()
+
+db_full6new_hr_fix_stim_nt1.1 %>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(BIO_CDA.SCR_z, Bio_Mean_HR))+
+  geom_point()+
+  geom_smooth(method = lm, se = F)+
+  ggpubr::stat_cor()
+
+db_full6new_hr_fix_stim_nt1.1 %>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(pup_basCor, Bio_Mean_HR))+
+  geom_point()+
+  # xlim()
+  geom_smooth(method = lm, se = F)+
+  ggpubr::stat_cor()
+```

### 2021-09-01 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 
+table(is.na(db_full4new_stim_screen_pupil_nopract$Group))
+
+table(db_full4new_stim_screen_pupil_nopract$Group)
+
+ db_full4new_stim_screen_pupil_nopract %>%
+   subset(Group == "NT")%>%
+  subset(pupil_outlier == FALSE)%>%
+  subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
+  subset(!is.na(Alexithymia))%>%
+  # subset(ssid_num<500)%>%
+    # group_by(ssid,Alexithymia, is_valence_high)%>%
+   group_by(ssid,Alexithymia, mediansplit_sample_valence2,mediansplit_sample_arousal2)%>%
+    mutate(cortest = cor(arousal_c, pup_basCor, use = "complete"))%>%
+    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+        ggplot(aes(mediansplit_sample_valence2, cortest, color = mediansplit_sample_valence2))+
+           geom_bar(stat="summary", fun.y = "mean", alpha = .4)+
+
+    geom_jitter(width = .1, alpha = .1)+
+        stat_summary( geom = 'pointrange')+
+          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
+    ylab("R pupil vs self report arousal")+
+  theme_classic()+
+  geom_hline(yintercept = .2, linetype = 'dashed', alpha = .2)+
+   # ggpubr::stat_compare_means(paired = TRUE)+
+  ggpubr::stat_compare_means()
+  facet_grid(~mediansplit_sample_arousal2)
+
 ```
@@
 
+db_full4new_stim_screen_pupil_nopract$valence_abs<- abs(db_full4new_stim_screen_pupil_nopract$valence)
+db_full4new_stim_screen_pupil_nopract$valence_abs_c<- scale(db_full4new_stim_screen_pupil_nopract$valence_abs, center = TRUE,scale = TRUE)[,1]
+
 pupil_arousal_findings$pupil_from_ar_vale_TAS <- lmer(pup_basCor ~ (valence_c* arousal_c)*TASc +
@@
 
+# abs
+pupil_arousal_findings$pupil_from_vale__tas_abs <- lmer(pup_basCor ~ valence_abs_c* TASc +
+                                                    Mean_gray_z  +
+                                                    (1 + Mean_gray_z | ssid)+
+                                                    (0+ arousal_c | ssid),
+                                                  REML = FALSE,
+                      data = db_full4new_stim_screen_pupil_nopract%>%
+                         subset(Group == "NT"))
+
+db_full4new_stim_screen_pupil_nopract$arousal_abs<- abs(db_full4new_stim_screen_pupil_nopract$arousal)
+db_full4new_stim_screen_pupil_nopract$arousal_abs_c<- scale(db_full4new_stim_screen_pupil_nopract$arousal_abs, center = TRUE,scale = TRUE)[,1]
+
+pupil_arousal_findings$pupil_from_ar__tas_abs <- lmer(pup_basCor ~ arousal_abs_c* TASc +
+                                                    Mean_gray_z  +
+                                                    (1 + Mean_gray_z | ssid)+
+                                                    (0+ arousal_c | ssid),
+                                                  REML = FALSE,
+                      data = db_full4new_stim_screen_pupil_nopract%>%
+                         subset(Group == "NT"))
+
+summary(pupil_arousal_findings$pupil_from_ar__tas_abs)
+
+cor.test(db_full4new_stim_screen_pupil_nopract$valence_abs_c, abs(db_full4new_stim_screen_pupil_nopract$arousal))
 ```
@@
   subset(!is.na(ground_arousal_lab))%>%
-  ggplot(aes(x = timerezero3, y = pup_basCor))+
-  stat_smooth(aes(group= mediansplit_ground_arousal, color = mediansplit_ground_arousal), fun = mean,geom = "line",
-               se = F, alpha = .1, size = 1.5)+
-  stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
+  ggplot(aes(x = timerezero3, y = pup_basCor,color = mediansplit_ground_arousal, linetype = mediansplit_ground_valence))+
+
+ # stat_summary(aes(group= mediansplit_ground_arousal, color = mediansplit_ground_arousal, linetype = mediansplit_ground_valence), fun = mean,geom = "line", size = 1.5)
+ #  
+  # stat_smooth(aes(group= mediansplit_ground_arousal), fun = mean,geom = "line",
+  #              se = F, alpha = 1, size = 1.5)+
+  stat_smooth(size=1.5, method = "loess", level = 0.95, 
+    fullrange = TRUE, se = FALSE) + 
+  # stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
 theme_classic()+
@@
   xlim(0,6)+
+   labs(color  = "mediansplit_ground_arousal", linetype = "mediansplit_ground_valence")
    facet_grid(~mediansplit_ground_valence)
+
+```
 
@@
    facet_grid(~mediansplit_sample_valence2)
-
-```
 
@@
 hr_dif_models$hr_dif_ar_vl <- lmer(Bio_Mean_HR_dif~arousal_c   * valence_c+
-                                        + (1 | ssid),
-                                     # (1|stimIAPS),
+                                        + (1 | ssid)+
+                                     (1|stimIAPS),
                                         # (1|mediansplit_sample_arousal2),
@@
 summary(hr_dif_models$hr_dif_ar_vl)
+
+db_full6new_hr_fix_stim_nt1.1%>%
+  subset(Bio_Mean_HR_dif_outl == "not outlier" & !is.na(Bio_Mean_HR_dif))%>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(valence_c, Bio_Mean_HR_dif))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  xlim(-.4,.6)+
+  ggpubr::stat_cor()
+
+db_full6new_hr_fix_stim_nt1.1%>%
+  subset(Bio_Mean_HR_dif_outl == "not outlier" & !is.na(Bio_Mean_HR_dif))%>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(valence_c, Bio_Mean_HR_dif))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  xlim(-.4,.6)
+  ggpubr::stat_cor()
 
@@
   summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(pup_basCor, Bio_Mean_HR))+
+  ggplot(aes(pup_basCor, Bio_Mean_HR_dif))+
   geom_point()+
@@
   geom_smooth(method = lm, se = F)+
+  # geom_smooth(aes(group = ssid),method = lm, se = F)
   ggpubr::stat_cor()
-```
+
+inter_bio<- lmer(pup_basCor~Bio_Mean_HR_dif +BIO_CDA.PhasicMax_z + (1|ssid)+ (1|stimIAPS), 
+                 REML = FALSE,
+                 data = db_full6new_hr_fix_stim_nt1.1)
+
+summary(inter_bio)
+
+inter_bio1<- lmer(Bio_Mean_HR_dif~ pup_basCor +BIO_CDA.PhasicMax_z + (1|ssid)+ (1|stimIAPS), 
+                 REML = FALSE,
+                 data = db_full6new_hr_fix_stim_nt1.1)
+
+summary(inter_bio1)
+
+inter_bio2<- lmer(log1p(BIO_CDA.PhasicMax+.1)~ Bio_Mean_HR_dif + pup_basCor + (1|ssid)+ 
+                    (1|stimIAPS), 
+                 REML = FALSE,
+                 data = db_full6new_hr_fix_stim_nt1.1)
+
+summary(inter_bio2)
+
+# cluster based on bio, pupil angsr_selfrep_matrixthen take these clusters and compare arousal valence
+```

### 2021-09-02 Paper_Analyses_subj_obje_arousal.Rmd
started clustering

@@
   mutate(arousal_c = scale(arousal, center = TRUE, scale = TRUE)[,1],
-         valence_c = scale(valence, center = TRUE, scale = TRUE)[,1])
+         valence_c = scale(valence, center = TRUE, scale = TRUE)[,1])%>%
+  mutate(Bio_Mean_HR_dif_c= scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1])
 
@@
 
-hr_dif_models$valfrom_hr <- lmer(arousal_c ~   Bio_Mean_HR_dif* valence_c+
+hr_dif_models$valfrom_hr <- lmer(arousal_c ~   Bio_Mean_HR_dif_c* valence_c+
+                                         (1 | ssid) + (1|stimIAPS),
+                                        # (1|mediansplit_sample_arousal2),
+     REML = FALSE,
+     data = subset(db_full6new_hr_fix_stim_nt1.1, 
+                   # mediansplit_ground_valence == "More positive" &
+                   Bio_Mean_HR_dif_outl == "not outlier"))
+# arousal_c
+summary(hr_dif_models$valfrom_hr)
+
+hr_dif_models$valfrom_hr_ar <- lmer(valence_c ~   Bio_Mean_HR_dif_c * arousal_c+
                                         + (1 | ssid) + (1|stimIAPS),
@@
 # arousal_c
-summary(hr_dif_models$valfrom_hr)
+summary(hr_dif_models$valfrom_hr_ar)
 
@@
 
-hr_dif_models$hr_dif_ar_vl <- lmer(Bio_Mean_HR_dif~arousal_c   * valence_c+
+hr_dif_models$hr_dif_ar_vl <- lmer(Bio_Mean_HR_dif~arousal_c   + valence_c+
                                         + (1 | ssid)+
@@
 
+sjPlot::tab_model(inter_bio2)
+
+table(is.na(db_full6new_hr_fix_stim_nt1.1$BIO_CDA.PhasicMax))
+table(is.na(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif))
+table(is.na(db_full6new_hr_fix_stim_nt1.1$pup_basCor))
+
+test<- subset(db_full6new_hr_fix_stim_nt1.1, is.na(Bio_Mean_HR_dif))
+test<- subset(db_full6new_hr_fix_stim_nt1.1, is.na(pup_basCor))
+
+```
+
 # cluster based on bio, pupil angsr_selfrep_matrixthen take these clusters and compare arousal valence
-```
+
+Let's crate some sort of data driven  parceling of the data
+option one, use a clustering algorithm that receives 3 inputs: pupil, heart rate and SCR and spits clusters,
+
+and then we can compare these clusters on ground truth arousal and valence
+- decisions to make: do we average the responses per participant and cluster at a trial level - this ignores individual variability
+- what do we do with teh nested nature of teh data, one participant has multiple trials, if we don't accout for this, the cluster will treat data from different participants the same way.
+
+If create cluster on a ndividual level- then the issue is different participants will end up with different clusters and clusters for one person are not translaable.
+
+The PCA type we did in newyork - barycentric?
+
+Let's start with an aggregated case, ignore subjects
+
+```{r}
+
+clustering<- db_full6new_hr_fix_stim_nt1.1%>%
+  subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
+  select(
+                    c(Bio_Mean_HR_dif, pup_basCor, BIO_CDA.PhasicMax, BIO_CDA.ISCR, BIO_TTP.AmpSum,
+                      BIO_CDA.SCR, arousal, valence, ArousalMean, ValenceMean, stimIAPS, tNo, TAS, AQ, Age,
+                      gender, ssid, stimDescription))
+
+clustering$stimIAPS2<- substr(clustering$stimIAPS, 1,4)
+unique(clustering$stimIAPS)
+
+clustering<- subset(clustering, !is.na(stimIAPS2))
+
+unique(clustering$stimIAPS2)
+
+clusterin
+clustering[clustering == "NaN"]<- NA
+
+# create logarithims for SCR
+
+clustering<- clustering%>%
+  mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
+   mutate(log_BIO_CDA.ISCR = log1p(BIO_CDA.ISCR+.1))%>%
+  mutate(log_BIO_TTP.AmpSum = log1p(BIO_TTP.AmpSum+.1))%>%
+  mutate(log_BIO_CDA.SCR = log1p(BIO_CDA.SCR+.1))%>%
+  group_by(ssid)%>%
+  # mutate(log_Bio_Mean_HR_dif_z = scale(log_Bio_Mean_HR_dif, center  = TRUE, scale= TRUE))%>%
+  # mutate(pup_basCor_z = scale(pup_basCor, center  = TRUE, scale= TRUE))%>%
+  mutate(log_Bio_CDA.PhasicMax_z = scale(log_BIO_CDA.PhasicMax, center  = TRUE, scale= TRUE))%>%
+  mutate(log_Bio_CDA.ISCR_z = scale(log_BIO_CDA.ISCR, center  = TRUE, scale= TRUE))%>%
+  mutate(log_Bio_TTP.AmpSum_z = scale(log_BIO_TTP.AmpSum, center  = TRUE, scale= TRUE))%>%
+  mutate(log_Bio_CDA.SCR_z = scale(log_BIO_CDA.SCR, center  = TRUE, scale= TRUE))
+
+# aggregate for clustering first
+clustering_agg <- clustering%>%
+  group_by(stimIAPS2, stimDescription)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)
+
+clustering_agg<- clustering_agg%>%
+  mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif, center  = TRUE, scale= TRUE))%>%
+  mutate(pup_basCor_z = scale(pup_basCor, center  = TRUE, scale= TRUE))
+  # mutate(BIO_CDA.PhasicMax_z = scale(BIO_CDA.PhasicMax, center  = TRUE, scale= TRUE))%>%
+  #  mutate(BIO_CDA.ISCR_z = scale(BIO_CDA.ISCR, center  = TRUE, scale= TRUE))%>%
+  # mutate(BIO_TTP.AmpSum_z = scale(BIO_TTP.AmpSum, center  = TRUE, scale= TRUE))%>%
+  # mutate(BIO_CDA.SCR_z = scale(BIO_CDA.SCR, center  = TRUE, scale= TRUE))
+
+write_csv(clustering_agg, "clustering_agg.csv")
+
+# kmeans clustering
+
+```
+
+```{r}
+library(readr)
+clustering_agg_JASP <- read_csv("clustering_agg_JASP.csv")
+View(clustering_agg_JASP)
+
+stomdescr<- select(clustering_agg, c(stimIAPS2, stimDescription))
+clustering_agg_JASP$stimIAPS2<- as.character(clustering_agg_JASP$stimIAPS2)
+
+left_join(clustering_agg_JASP, stomdescr)%>%
+  ggplot(aes( arousal, valence, color = as.factor(clusters)))+
+  geom_text(aes(label = stimDescription))+
+  facet_grid(~ as.factor(clusters))
+
+left_join(clustering_agg_JASP, stomdescr)%>%
+  ggplot(aes( as.factor(clusters), valence))+
+  geom_jitter(width = .2)+
+  stat_summary(geom  = 'pointrange')
+
+left_join(clustering_agg_JASP, stomdescr)%>%
+  ggplot(aes( as.factor(clusters), abs(arousal)))+
+  geom_jitter(width = .2)+
+  stat_summary(geom  = 'pointrange')
+
+  geom_text(aes(label = stimDescription))+
+  facet_grid(~ as.factor(clusters))
+
+```
+
+Kmeans random initialisation trap
+- what happens if we have a bad ramdon inistialisation fior centroids (center of mass)?
+The selection can ditacte the outcome.
+
+Solution? K-means++ (happens in the background)
+
+steps
+1 - choose the number of k clusters
+2 - select k points and random (centroids) don't need to be in the data
+3 - assign each data point the the closest centroid
+4 - compute and lace new centroids for each cluster
+5 - Reassign each data point to the new closest centroid, if any reassignment take place go back to 4 other wise convergence
+
+Find how the right number of clusters
+- look at the within cluster summ of squares (distance between the point and the centroid) like in regression if numerator sum of sqyares is bigger than error, we tend to have significant results.
+we want the modelwith the smalles within sum of squares (elbow method) - looks like a screeplot

### 2021-09-02 Paper_Analyses_subj_obje_arousal.Rmd
Kmeans, finding K and visualising pca
a few lines to find the optimal k using the elbow method and to visualise the result because we have more than 2 variables the approach relies on pca projecting. A remaining problem has to do with what do do with repeated data within subject as the above was done on aggregated data

@@
 clustering_agg<- clustering_agg%>%
+  ungroup()%>%
   mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif, center  = TRUE, scale= TRUE))%>%
@@
 
+View(clustering_agg)
+
 write_csv(clustering_agg, "clustering_agg.csv")
@@
 Kmeans random initialisation trap
-- what happens if we have a bad ramdon inistialisation fior centroids (center of mass)?
+- what happens if we have a bad ramdon initialization fior centroids (center of mass)?
 The selection can ditacte the outcome.
@@
 we want the modelwith the smalles within sum of squares (elbow method) - looks like a screeplot
+
+note for clustering methods, because the solution is not known we don't typically have crossvalidation, but can asses stability, etc
+
+regular k means on aggregaed data
+
+```{r}
+# K-Means Clustering
+
+# Importing the dataset
+
+clustering_agg<- subset(clustering_agg, !is.na(stimDescription))
+colnames(clustering_agg)
+clust_dataset = clustering_agg[c(20,24,25)]
+
+# Feature Scaling
+# training_set = scale(training_set)
+# test_set = scale(test_set)
+
+# Using the elbow method to find the optimal number of clusters
+set.seed(6)
+wcss = vector()
+for (i in 1:10) wcss[i] = sum(kmeans(clust_dataset, i)$withinss)
+plot(1:10,
+     wcss,
+     type = 'b',
+     main = paste('The Elbow Method'),
+     xlab = 'Number of clusters',
+     ylab = 'WCSS')
+
+# Fitting K-Means to the dataset
+set.seed(29)
+kmeans = kmeans(x = clust_dataset, centers = 3)
+y_kmeans = kmeans$cluster
+
+# Visualising the clusters
+# install.packages("cluster")
+library(cluster)
+
+clusplot(clust_dataset,
+         y_kmeans,
+         lines = 0,
+         shade = TRUE,
+         color = TRUE,
+         labels = 2,
+         plotchar = FALSE,
+         span = TRUE,
+         main = paste('Clusters of customers'),
+         xlab = 'Annual Income',
+         ylab = 'Spending Score')
+
+clustering_agg$y_kmeans<- y_kmeans
+
+clustering_agg%>%
+  ggplot(aes(as.factor(y_kmeans), ArousalMean))+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+clustering_agg%>%
+  ggplot(aes(as.factor(y_kmeans), ValenceMean))+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+clustering_agg%>%
+  ggplot(aes(as.factor(y_kmeans), valence))+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+clustering_agg%>%
+  ggplot(aes(as.factor(y_kmeans), arousal))+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+?car::scatter3d
+View(clustering_agg)
+clustering_agg$y_kmeans<- as.factor(as.character(clustering_agg$y_kmeans))
+car::scatter3d(clustering_agg$log_Bio_CDA.PhasicMax_z, 
+          clustering_agg$Bio_Mean_HR_dif_z, 
+          clustering_agg$pup_basCor_z,
+          fit = "smooth",
+          # point = FALSE,
+          ellipsoid = TRUE,
+          surface = FALSE,
+          groups = clustering_agg$y_kmeans,
+          point.col = clustering_agg$y_kmeans
+          )
+
+# install.packages("scatterplot3d") # Install
+library("scatterplot3d") # load
+
+scatterplot3d(clustering_agg[,c(20,24,25)],pch = 16, color = clustering_agg$y_kmeans, type="h")
+text(clustering_agg$stimDescription, labels = clustering_agg$stimDescription,
+     cex= 0.7, col = "steelblue")
+
+require(ggplot2)
+data("iris")
+
+pca_res <- prcomp(clustering_agg[,c(20,24,25)], center = TRUE, scale. = TRUE)
+plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg$y_kmeans)
+
+ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels)) +
+  geom_point()+
+  geom_text(aes(label= clustering_agg$stimDescription))
+
+summary(pca_res)
+```

### 2021-09-02 Paper_Analyses_subj_obje_arousal.Rmd
kmeans on unnagregted data
this includes multiple trials p[er subject the result overall is similar to the aggregated data but the same stimuli can endup beogn assigned to multiple clusters, becauyse every opccurence of the same stimuli is treated as indeopendent

@@
 # aggregate for clustering first
+
+clustering$AlexGroup<- if_else(clustering$TAS> median(clustering$TAS, na.rm = TRUE), "High", "Low")
+
 clustering_agg <- clustering%>%
   group_by(stimIAPS2, stimDescription)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)
+
+clustering_agg2 <- clustering%>%
+  group_by(stimIAPS2, stimDescription,AlexGroup)%>%
   summarise_if(is.numeric, mean, na.rm = TRUE)
@@
 
+clustering_agg2<- clustering_agg2%>%
+  ungroup()%>%
+  mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif, center  = TRUE, scale= TRUE))%>%
+  mutate(pup_basCor_z = scale(pup_basCor, center  = TRUE, scale= TRUE))
+
 View(clustering_agg)
@@
 clustering_agg<- subset(clustering_agg, !is.na(stimDescription))
+
+clustering_agg$AlexGroup<- if_else(clustering_agg$TAS> median(clustering_agg$TAS, na.rm = TRUE), "High", "Low")
 colnames(clustering_agg)
@@
 ```
+
+Let's do on the unnagregates data
+
+```{r}
+colnames(clustering_agg)
+colnames(clustering)
+
+clustering2<- subset(clustering, !is.na(stimDescription))
+
+# K-Means Clustering
+
+colnames(clustering2)
+clust2_dataset = clustering2[c(24,2,1,7:11,18,19)]
+
+# Feature Scaling
+# training_set = scale(training_set)
+# test_set = scale(test_set)
+
+# Using the elbow method to find the optimal number of clusters
+set.seed(6)
+wcss2 = vector()
+View(clust2_dataset)
+clust2_dataset_nona<- na.omit(clust2_dataset)
+
+for (i in 1:10) wcss2[i] = sum(kmeans(clust2_dataset_nona[,c(1:3)], i)$withinss)
+plot(1:10,
+     wcss,
+     type = 'b',
+     main = paste('The Elbow Method'),
+     xlab = 'Number of clusters',
+     ylab = 'WCSS')
+
+# Fitting K-Means to the dataset
+set.seed(29)
+kmeans2 = kmeans(x = clust2_dataset_nona[,c(1:3)], centers = 3)
+y_kmeans2 = kmeans2$cluster
+
+# Visualising the clusters
+# install.packages("cluster")
+library(cluster)
+
+clusplot(clust_dataset,
+         y_kmeans,
+         lines = 0,
+         shade = TRUE,
+         color = TRUE,
+         labels = 2,
+         plotchar = FALSE,
+         span = TRUE,
+         main = paste('Clusters of customers'),
+         xlab = 'Annual Income',
+         ylab = 'Spending Score')
+
+clust2_dataset_nona$y_kmeans2 <- y_kmeans2
+
+clust2_dataset_nona%>%
+  ggplot(aes(as.factor(y_kmeans2), ArousalMean))+
+  # geom_point()+
+  stat_summary(geom = 'pointrange')
+
+clust2_dataset_nona%>%
+  ggplot(aes(as.factor(y_kmeans2), ValenceMean))+
+  # geom_point()+
+  stat_summary(geom = 'pointrange')
+
+clustering_agg%>%
+  ggplot(aes(as.factor(y_kmeans), valence))+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+clustering_agg%>%
+  ggplot(aes(as.factor(y_kmeans), arousal))+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+?car::scatter3d
+View(clustering_agg)
+
+clust2_dataset_nona$y_kmeans2<- as.factor(as.character(clust2_dataset_nona$y_kmeans2))
+car::scatter3d(clust2_dataset_nona$log_Bio_CDA.PhasicMax_z, 
+          clust2_dataset_nona$Bio_Mean_HR_dif, 
+          clust2_dataset_nona$pup_basCor,
+          fit = "smooth",
+          # point = FALSE,
+          # ellipsoid = TRUE,
+          surface = FALSE,
+          # groups = clust2_dataset_nona$y_kmeans2,
+          point.col = clust2_dataset_nona$y_kmeans2
+          )
+
+# install.packages("scatterplot3d") # Install
+library("scatterplot3d") # load
+
+scatterplot3d(clustering_agg[,c(20,24,25)],pch = 16, color = clustering_agg$y_kmeans, type="h")
+text(clustering_agg$stimDescription, labels = clustering_agg$stimDescription,
+     cex= 0.7, col = "steelblue")
+
+require(ggplot2)
+data("iris")
+
+pca_res2 <- prcomp(clust2_dataset_nona[,c(1:3)])
+plot_data2 <- cbind(as.data.frame(pca_res2$x[, 1:2]), labels = clust2_dataset_nona$y_kmeans2)
+
+ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels)) +
+  # geom_point()
+  geom_text(aes(label= clust2_dataset_nona$stimDescription))
+
+summary(pca_res2)
+```

### 2021-09-02 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 clustering_agg$y_kmeans<- as.factor(as.character(clustering_agg$y_kmeans))
+
+clustering_agg2$y_kmeans<- as.factor(as.character(clustering_agg2$y_kmeans))
+
 car::scatter3d(clustering_agg$log_Bio_CDA.PhasicMax_z, 
@@
           point.col = clustering_agg$y_kmeans
+          )
+
+clustering_agg2$AlexGroup<-as.factor(clustering_agg2$AlexGroup)
+clustering_agg2<- subset(clustering_agg2, !is.na(stimDescription))
+car::scatter3d(clustering_agg2$log_Bio_CDA.PhasicMax_z, 
+          clustering_agg2$Bio_Mean_HR_dif_z, 
+          clustering_agg2$pup_basCor_z,
+          fit = "smooth",
+          # point = FALSE,
+          ellipsoid = TRUE,
+          surface = FALSE,
+          groups = clustering_agg2$AlexGroup
+          # point.col = clustering_agg2$y_kmeans
           )

### 2021-09-02 Paper_Analyses_subj_obje_arousal.Rmd
plotting clusters vs ratings

@@
 
+?clusplot
 clusplot(clust_dataset,
          y_kmeans,
-         lines = 0,
+         lines = 2,
          shade = TRUE,
          color = TRUE,
-         labels = 2,
+         labels = 1,
          plotchar = FALSE,
-         span = TRUE,
-         main = paste('Clusters of customers'),
-         xlab = 'Annual Income',
-         ylab = 'Spending Score')
-
+         span = TRUE
+         # label = 
+         # main = paste('Clusters of customers'),
+         # xlab = 'Annual Income',
+         # ylab = 'Spending Score'
+         )
+
+```
+
+a few visualisations
+```{r}
 clustering_agg$y_kmeans<- y_kmeans
-
-clustering_agg%>%
-  ggplot(aes(as.factor(y_kmeans), ArousalMean))+
-  geom_point()+
-  stat_summary(geom = 'pointrange')
-
-clustering_agg%>%
-  ggplot(aes(as.factor(y_kmeans), ValenceMean))+
-  geom_point()+
-  stat_summary(geom = 'pointrange')
-
-clustering_agg%>%
-  ggplot(aes(as.factor(y_kmeans), valence))+
-  geom_point()+
-  stat_summary(geom = 'pointrange')
-
-clustering_agg%>%
-  ggplot(aes(as.factor(y_kmeans), arousal))+
-  geom_point()+
-  stat_summary(geom = 'pointrange')
 
@@
 require(ggplot2)
-data("iris")
+# data("iris")
 
@@
 
+clustering_agg$cluster_interpreted<- ifelse(clustering_agg$y_kmeans == 1, "mixed",
+                                            ifelse(clustering_agg$y_kmeans == 2, "highlyarousing_aitated", "calmish"))
 summary(pca_res)
+
+# tsne plot
+install.packages("tsne")
+library(tsne)
+
+?tsne
+
+# install.packages("Rtsne")
+require(Rtsne)
+# install.packages("M3C")
+# library(M3C)
+tsne(clustering_agg[,c(20,24,25)])
+
+# cluster vs ground arousal means
+library(tidyverse)
+clustering_agg%>%
+  ggplot(aes(as.factor(y_kmeans), ArousalMean))+
+  # geom_point()+
+  stat_summary(geom = 'pointrange')+
+  ggpubr::stat_compare_means()
+
+clustering_agg %>%
+  ggplot(aes(cluster_interpreted, ArousalMean))+
+  # geom_point()+
+  stat_summary(geom = 'pointrange')+
+    ggpubr::stat_compare_means()
+
+# cluster vs valence ground
+
+# Visualize: Specify the comparisons you want
+my_comparisons <- list( c("1", "2"), c("1", "3"), c("2", "3") )
+my_comparisons <- list( c("mixed", "highlyarousing_aitated"), c("mixed", "calmish"), c("highlyarousing_aitated", "calmish") )
+clustering_agg$cluster_interpreted
+library(ggpubr)
+ggboxplot(clustering_agg, x = "cluster_interpreted", y = "ArousalMean",
+          color = "cluster_interpreted", palette = "jco")+
+  geom_jitter(width = .1, alpha = .2)+
+  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
+  stat_compare_means(label.y = 9)     # Add global p-value
+
+clustering_agg %>%
+  ggplot(aes(as.factor(y_kmeans), ValenceMean))+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+clustering_agg%>%
+  ggplot(aes(cluster_interpreted, ValenceMean))+
+  # geom_point()+
+  stat_summary(geom = 'pointrange')+
+    ggpubr::stat_compare_means()
+
+ggboxplot(clustering_agg, x = "cluster_interpreted", y = "ValenceMean",
+          color = "cluster_interpreted", palette = "jco")+
+  geom_jitter(width = .1, alpha = .2)+
+  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
+  stat_compare_means(label.y = 9)
+
+```
+
+```{r}
+
+# based ins ample
+clustering_agg %>%
+  ggplot(aes(as.factor(y_kmeans), valence))+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+clustering_agg %>%
+  ggplot(aes(cluster_interpreted, valence))+
+  # geom_point()+
+  stat_summary(geom = 'pointrange')+
+    ggpubr::stat_compare_means()
+
+clustering_agg%>%
+  ggplot(aes(as.factor(y_kmeans), arousal))+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+clustering_agg%>%
+  ggplot(aes(cluster_interpreted, arousal))+
+  # geom_point()+
+  stat_summary(geom = 'pointrange')+
+  ggpubr::stat_compare_means()
+
+cluster_stim<- select(clustering_agg, c(stimIAPS2,y_kmeans, cluster_interpreted, stimDescription))
+
+# plot(test)
 ```
@@
 
+?clusplot
 clusplot(clust_dataset,
@@
          plotchar = FALSE,
-         span = TRUE,
-         main = paste('Clusters of customers'),
-         xlab = 'Annual Income',
-         ylab = 'Spending Score')
+         span = TRUE
+         # main = paste('Clusters of customers'),
+         # xlab = 'Annual Income',
+         # ylab = 'Spending Score'
+         )
 

### 2021-09-04 Paper_Analyses_subj_obje_arousal.Rmd
main ideas of the paper are down
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 
-tmp.df4_full_stim_downs_jun2021_60bins %>%
+tmp.df4_full_stim_downs_jun2021_60bins_no_na<- subset(tmp.df4_full_stim_downs_jun2021_60bins, !is.na(stimDescription))
+nrow(tmp.df4_full_stim_downs_jun2021_60bins_no_na)
+
+nrow(tmp.df4_full_stim_downs_jun2021_60bins)
+
+tmp.df4_full_stim_downs_jun2021_60bins_no_na$stimIAPS2<- substr(tmp.df4_full_stim_downs_jun2021_60bins_no_na$stimIAPS, 1,4)
+
+left_join(tmp.df4_full_stim_downs_jun2021_60bins_no_na, cluster_stim)%>%
+# tmp.df4_full_stim_downs_jun2021_60bins %>%
   subset(!is.na(ground_arousal_lab))%>%
@@
 
+tmp.df4_full_stim_downs_jun2021_60bins_no_na<- left_join(tmp.df4_full_stim_downs_jun2021_60bins_no_na, cluster_stim)
+# plot with clusters
+# left_join(tmp.df4_full_stim_downs_jun2021_60bins_no_na, cluster_stim)%>%
+# tmp.df4_full_stim_downs_jun2021_60bins %>%
+  # subset(!is.na(ground_arousal_lab))%>%
+tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
+  ggplot(aes(x = timerezero3, y = pup_basCor,color = cluster_interpreted, linetype = cluster_interpreted))+
+
+ # stat_summary(aes(group= mediansplit_ground_arousal, color = mediansplit_ground_arousal, linetype = mediansplit_ground_valence), fun = mean,geom = "line", size = 1.5)
+ #  
+  # stat_smooth(aes(group= mediansplit_ground_arousal), fun = mean,geom = "line",
+  #              se = F, alpha = 1, size = 1.5)+
+  stat_smooth(size=1.5, method = "loess", level = 0.95, 
+    fullrange = TRUE, se = FALSE) + 
+  # stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
+theme_classic()+
+  ylab("Pupil size (z)")+
+  xlab("Time (s)")+
+  # p$graphstyle+
+  scale_color_brewer(palette = "Dark2")+
+  xlim(0,6)
+   labs(color  = "mediansplit_ground_arousal", linetype = "mediansplit_ground_valence")
+   # facet_grid(~mediansplit_ground_valence)
+
 ```
@@
 View(timecourse_60bin_result_df)
+
+timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_br_adj_TRUE == TRUE]
+
+timecourse_60bin_result_df %>%
+  group_by(p_br_adj_TRUE)%>%
+  summarise_at(c("Estimate_br"), mean, na.rm = TRUE)
+  mutate(mean_effsize = Estimate_br)
+
+  #  arousal
+
+  timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_adj_TRUE == TRUE]
+
+ timecourse_60bin_result_df %>%
+  group_by(p_ar_adj_TRUE)%>%
+  summarise_at(c("Estimate_ar"), mean, na.rm = TRUE)
+
+ # ar and val;
+   timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_vl_adj_TRUE == TRUE]
+
+ timecourse_60bin_result_df %>%
+  group_by(p_ar_vl_adj_TRUE)%>%
+  summarise_at(c("Estimate_ar_vl"), median, na.rm = TRUE)
+
+ # valence
+  # ar and val;
+   timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_vl_adj_TRUE == TRUE]
+
+ timecourse_60bin_result_df %>%
+  group_by(p_vl_adj_TRUE)%>%
+  summarise_at(c("Estimate_vl"), median, na.rm = TRUE)
 
@@
 
-pupil_arousal_findings$BIO_CDA.PhasicMax <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c * valence_c + (1|ssid),
+db_full4new_stim_screen_pupil_nopract_nt_304$arousal_abs<- abs(db_full4new_stim_screen_pupil_nopract_nt_304$arousal)
+
+db_full4new_stim_screen_pupil_nopract_nt_304$arousal_abs_z<- scale(db_full4new_stim_screen_pupil_nopract_nt_304$arousal_abs, center = TRUE,scale = TRUE)
+
+pupil_arousal_findings$BIO_CDA.PhasicMax <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c * valence_c + (1|ssid) + (1|stimIAPS),
                         REML = FALSE,
@@
 
+#
+
+pupil_arousal_findings$BIO_CDA.PhasicMax_ar <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c + (1|ssid),
+                        REML = FALSE,
+                        data = db_full4new_stim_screen_pupil_nopract_nt_304)
+
 interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred =valence_c , modx =  arousal_c)
+
+summary(pupil_arousal_findings$BIO_CDA.PhasicMax_ar)
+pupil_arousal_findings$BIO_CDA.PhasicMax_vl <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ valence_c + (1|ssid) + (1|stimIAPS),
+                        REML = FALSE,
+                        data = db_full4new_stim_screen_pupil_nopract_nt_304)
+
+interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred =valence_c , modx =  arousal_c)
+
+summary(pupil_arousal_findings$BIO_CDA.PhasicMax_vl)
+
+# deal with colinearity by swicthing predictor to dv
+
+db_full4new_stim_screen_pupil_nopract_nt_304$log1p_BIO_CDA.PhasicMax <- log1p(db_full4new_stim_screen_pupil_nopract_nt_304$BIO_CDA.PhasicMax+.1)
+
+db_full4new_stim_screen_pupil_nopract_nt_304$log1p_BIO_CDA.PhasicMax_z<- scale(db_full4new_stim_screen_pupil_nopract_nt_304$log1p_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1]
+
+pupil_arousal_findings$ar_BIO_CDA.PhasicMax <- lmer(arousal_c ~ valence_c +log1p_BIO_CDA.PhasicMax_z+ (1|ssid)+(1|stimIAPS),
+                        REML = FALSE,
+                        data = db_full4new_stim_screen_pupil_nopract_nt_304)
+
+summary(pupil_arousal_findings$ar_BIO_CDA.PhasicMax)
+
+pupil_arousal_findings$ar_BIO_CDA.PhasicMax <- lmer( valence_c~ arousal_c+log1p_BIO_CDA.PhasicMax_z+ (1|ssid)+(1|stimIAPS),
+                        REML = FALSE,
+                        data = db_full4new_stim_screen_pupil_nopract_nt_304)
+
+summary(pupil_arousal_findings$ar_BIO_CDA.PhasicMax)
 
@@
      REML = FALSE,
-     data = subset(db_full6new_hr_fix_stim_nt1.1, 
+     data = subset(db_full6new_hr_fix_stim_nt1.11, 
                    # mediansplit_ground_valence == "More negative" &
@@
 unique(db_full6new_hr_fix_stim_nt1.1$ssid)
+
+db_full6new_hr_fix_stim_nt1.11<- subset(db_full6new_hr_fix_stim_nt1.1, !is.na(stimDescription))
 
@@
      REML = FALSE,
-     data = subset(db_full6new_hr_fix_stim_nt1.1, 
+     data = subset(db_full6new_hr_fix_stim_nt1.11, 
                    # mediansplit_ground_valence == "More positive" &
@@
 
-hr_dif_models$hr_dif_ar_vl <- lmer(Bio_Mean_HR_dif~arousal_c   + valence_c+
+db_full6new_hr_fix_stim_nt1.1$arousal_abs<- abs(db_full6new_hr_fix_stim_nt1.1$arousal)
+db_full6new_hr_fix_stim_nt1.1$arousal_abs_z<- scale(db_full6new_hr_fix_stim_nt1.1$arousal_abs, center = TRUE,scale = TRUE)
+
+table(is.na(db_full6new_hr_fix_stim_nt1.1$stimDescription))
+hr_dif_models$hr_dif_ar_vl <- lmer(Bio_Mean_HR_dif~arousal_c   * valence_c+
                                         + (1 | ssid)+
@@
 
+# abs
+hr_dif_models$hr_dif_arabs_vl <- lmer(Bio_Mean_HR_dif~arousal_abs_z   * valence_c+
+                                        + (1 | ssid)+
+                                     (1|stimIAPS),
+                                        # (1|mediansplit_sample_arousal2),
+     REML = FALSE,
+     data = subset(db_full6new_hr_fix_stim_nt1.11, 
+                   # mediansplit_ground_valence == "More positive" &
+                   Bio_Mean_HR_dif_outl == "not outlier" & !is.na(Bio_Mean_HR_dif)))
+# arousal_c
+summary(hr_dif_models$hr_dif_arabs_vl)
+
 db_full6new_hr_fix_stim_nt1.1%>%
@@
   ggpubr::stat_cor()
+
+  db_full6new_hr_fix_stim_nt1.11%>%
+    subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+    group_by(stimIAPS)%>%
+    mutate(mean_hr_dif = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
+    ggplot(aes(valence_c, mean_hr_dif))+
+    # geom_point()+
+    stat_summary(aes(y = Bio_Mean_HR_dif),geom = 'pointrange')+
+    geom_smooth(method = 'lm', se = F)+
+    p$graphstyle
+
+    db_full6new_hr_fix_stim_nt1.11%>%
+    subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+    group_by(stimIAPS)%>%
+    mutate(mean_hr_dif = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
+    ggplot(aes(arousal_abs_z, mean_hr_dif))+
+    # geom_point()+
+    stat_summary(aes(y = Bio_Mean_HR_dif),geom = 'pointrange')+
+    geom_smooth(method = 'lm', se = F)
 
@@
           fit = "smooth",
-          # point = FALSE,
-          ellipsoid = TRUE,
-          surface = FALSE,
+          point = FALSE,
+          # ellipsoid = TRUE,
+          # surface = FALSE,
           groups = clustering_agg$y_kmeans,
@@
 library(ggpubr)
+
 ggboxplot(clustering_agg, x = "cluster_interpreted", y = "ArousalMean",
@@
 
+tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
+  group_by(ssid, cluster_interpreted)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  mutate(arousal2 = abs(arousal))%>%
+  subset(arousal> -9)%>%
+  ggboxplot(x = "cluster_interpreted", y = "valence",
+          color = "cluster_interpreted", palette = "jco")+
+  geom_jitter(width = .1, alpha = .2)+
+    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
+  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
+  stat_compare_means(label.y = 9)
+
+options(scipen = 999)
+tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
+  group_by(ssid, cluster_interpreted)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  mutate(arousal2 = abs(arousal))%>%
+  subset(arousal> -9)%>%
+  ggboxplot(x = "cluster_interpreted", y = "arousal",
+          color = "cluster_interpreted", palette = "jco")+
+  geom_jitter(width = .1, alpha = .2)+
+    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
+  stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
+  stat_compare_means(label.y = 9)
+
 ```
@@
 
-Let's do on the unnagregates data
+use the clusters ti fit mixed models
+
+```{r}
+View(clustering)
+
+table(is.na(clustering$stimDescription))
+table(is.na(clustering2$stimDescription))
+
+clustering2
+
+clustering3<- left_join(clustering2, cluster_stim)
+
+cluster_lmers<- list()
+clustering3$stimIAPS2<- as.factor(as.character(clustering3$stimIAPS2))
+
+clustering3$ssid<- as.factor(as.character(clustering3$ssid))
+clustering3
+
+library(lmerTest)
+
+clustering3$arousal
+
+cluster_lmers$arousal <- lmer(arousal ~ cluster_interpreted + 
+                               (1 | ssid)+
+                               (1|stimIAPS2),
+                             REML = FALSE,
+                             data = clustering3)
+
+summary(cluster_lmers$arousal)
+
+anova(cluster_lmers$arousal)
+
+emmeans::emmeans(cluster_lmers$arousal, pairwise~cluster_interpreted)
+
+# valence
+cluster_lmers$valence <- lmer(valence ~ cluster_interpreted + 
+                               (1 | ssid)+
+                               (1|stimIAPS2),
+                             REML = FALSE,
+                             data = clustering3)
+
+summary(cluster_lmers$valence)
+emmeans::emmeans(cluster_lmers$valence, pairwise~cluster_interpreted)
+
+```
+
+Let's do on the unnagregated data
 

### 2021-09-04 Figures.Rmd
First patch plot
made the plots and patchwork for the first big panel including a power point with some additional edits

---
title: "Figures"
author: "Helio"
date: "04/09/2021"
output: html_document
---

interaction plot

```{r}
sf = 1 # scaling factor to make it easier to change sizes of everything, in which case change here

p$graphstyle_int <-  theme(#base plot theme

  # axis lines
  axis.line.y = element_line(color="black", size = 1.5),
  axis.line.x = element_line(color="black", size = 1,5),

  axis.title.y=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
  axis.title.x=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),

  # text
  strip.text.x = element_text(size = 12*(sf+.5),  colour = "black"),
  strip.text.y = element_text(size = 12*(sf+.5),  colour = "black"),

  text=element_text(size = 14, family = "sans"),
  axis.text.x = element_text(size = 14*(sf+.5), family = "sans", colour = "black",),
  axis.text.y = element_text(size = 14*(sf+.5), family = "sans", colour = "black"),

  # panel
  panel.grid.major = element_blank(),
  panel.background = element_blank(),
  # panel.background = element_rect(fill="transparent"),
  # panel.border = element_rect(fill="transparent"),
  # strip shades (reco rectagles)
   # strip.background = element_blank(),

  # legend
  legend.position = "top",
  legend.key = element_rect(colour = "transparent", fill="transparent"),
  #legend.direction = "horizontal",

  legend.text = element_text(size = 10*(sf+.3)),
  # legend.title = element_text(size = 10*(sf+.3)),
  # legend line tends to be really small in print so adjust here
  legend.key.height = unit(.5, "cm"),
  legend.key.width = unit(2, "cm"),

  #legend.text = element_text(size = 10*sf),
  # legend.title=element_blank(),
  #legend.text = element_blank(),
  #axis.ticks = element_blank(),
)

```

Pupil
- arousalx valence effect

```{r}

plots_paper$interaction_ar_vl <- interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale , pred = arousal_c, modx = valence_c,
                            line.thickness = 2)

# ?interactions::interact_plot()
plots_paper$interaction_ar_vl<- plots_paper$interaction_ar_vl +
  theme_classic()+
  p$graphstyle_int+
  xlab("Subjective arousal (z)")+
  ylab("Pupil change (z)")+
  scale_y_continuous(breaks = c(-1,0,1))

library(interactions)

plots_paper$interaction_ar_vl<- plots_paper$interaction_ar_vl +   scale_y_continuous(breaks = c(-1.5,-1,-.5,0,.5), limits = c(-2,.5))

plots_paper$interaction_ar_vl <- plots_paper$interaction_ar_vl +
   theme_classic()+
   p$graphstyle_int
   # change leged title
   guides(linetype=guide_legend(title="New Legend Title"), fill = guide_legend(title="New Legend Title"))

plots_paper$interaction_ar_vl

# plots_paper[["interaction_ar_vl"]][["data"]]%>%
#   ggplot(aes(arousal_c, pup_basCor, linetype = modx_group))+
#   stat_summary(aes(fill = modx_group), geom = 'line', size = 2)+
#   p$graphstyle_int

```

Illustration to show that pupil tracks arousal better for more positive emotions
- check how this looks with clusters

```{r}

symnum.args <- list(cutpoints = c(0, 0.0001, 0.001, 0.01, 0.05, 1), symbols = c("****", "***", "**", "*", "ns"))

db_full4new_stim_screen_pupil_nopract
plots_paper$pupil_correlation <- db_full4new_stim_screen_pupil_nopract %>%
  subset(!is.na(mediansplit_sample_valence2))%>%
   subset(Group == "NT")%>%
  # subset(pupil_outlier == FALSE)%>%
  # subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  # subset(!is.na(Alexithymia))%>%
  # subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid, mediansplit_sample_valence2)%>%
    mutate(cortest = cor(arousal_c, pup_basCor, use = "complete"))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_sample_valence2, cortest, fill = mediansplit_sample_valence2, 
                   color = mediansplit_sample_valence2))+
           geom_bar(aes(linetype = mediansplit_sample_valence2), 
                    stat="summary", fun.y = "mean", alpha = .3, width = .5, size = 2)+
    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange', color = "black")+
          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .3)+
    ylab("R pupil vs self report arousal")+
  theme_classic()+
  geom_hline(yintercept = 0, linetype = 'dashed', alpha = .2)+
   # ggpubr::stat_compare_means(paired = TRUE)+
  ggpubr::stat_compare_means(method = 't.test',
                             symnum.args = symnum.args)+
   ylab(expression("Pupil vs subjective arousal ("*rho * ")"))+
   xlab("Subjective valence")

 plots_paper$pupil_correlation<- plots_paper$pupil_correlation+ p$graphstyle+
    scale_fill_brewer(palette = "Dark2")+
     scale_color_brewer(palette = "Dark2")

plots_paper$pupil_correlation

# try with cluster]

db_full4new_stim_screen_pupil_nopract$stimIAPS2<- substring(db_full4new_stim_screen_pupil_nopract$stimIAPS,1,4)
left_join(db_full4new_stim_screen_pupil_nopract, cluster_stim)%>%
  subset(!is.na(mediansplit_sample_valence2))%>%
   subset(Group == "NT")%>%
  # subset(pupil_outlier == FALSE)%>%
  # subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  # subset(!is.na(Alexithymia))%>%
  # subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid, cluster_interpreted)%>%
    mutate(cortest = cor(arousal_c, pup_basCor, use = "complete"))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(cluster_interpreted, cortest, fill = cluster_interpreted, 
                   color = cluster_interpreted))+
           geom_bar(aes(linetype = cluster_interpreted), 
                    stat="summary", fun.y = "mean", alpha = .4, width = .5, size = 2)+
    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange')+
          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .1)+
    ylab("R pupil vs self report arousal")+
  theme_classic()+
  geom_hline(yintercept = 0, linetype = 'dashed', alpha = .2)+
   # ggpubr::stat_compare_means(paired = TRUE)+
  ggpubr::stat_compare_means(method = 't.test',
                             symnum.args = symnum.args)+
   ylab("R - pupil vs subjective arousal")+
   xlab("Subjective valence")

```

<!-- timecourse of pupil based on self reports -->

```{r}
# left_join(tmp.df4_full_stim_downs_jun2021_60bins_no_na, cluster_stim)%>%
# tmp.df4_full_stim_downs_jun2021_60bins %>%

tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
  ungroup()%>%
  mutate(mediansplit_ground_valence = if_else(ValenceMean >=
                                                  median(ValenceMean,
                                                         na.rm = TRUE), "More positive", "More negative"))%>%
  mutate(mediansplit_ground_arousal = if_else(ArousalMean >=
                                                  median(ArousalMean,
                                                         na.rm = TRUE), "High", "Low"))%>%
    mutate(mediansplit_sample_valence2 = if_else(valence >=
                                                  median(valence,
                                                         na.rm = TRUE), "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(arousal >=
                                                  median(arousal,
                                                         na.rm = TRUE), "High", "Low"))

unique(tmp.df4_full_stim_downs_jun2021_60bins_no_na$ssid)

tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
  subset(Group == "NT")%>%
  ggplot(aes(x = timerezero3, y = pup_basCor,
             color = mediansplit_sample_arousal2, 
             linetype = mediansplit_sample_valence2))+
  geom_smooth()+
  # stat_smooth(size=1.5, method = "loess", level = 0.95, 
  #   fullrange = TRUE) + 
  # stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)
   # labs(color  = "mediansplit_ground_arousal", linetype = "mediansplit_ground_valence")

tmp.df4_full_stim_downs_jun2021_60bins_no_na<- tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
group_by(ssid) %>%
  mutate(pp_arousal_outler = if_else(arousal > (median(arousal, na.rm = TRUE) + 
                                               (4*mad(arousal, na.rm = TRUE))), TRUE,
         if_else(arousal < (median(arousal, na.rm = TRUE) - 
                              (4*mad(arousal, na.rm = TRUE))), TRUE, FALSE)))%>%
   mutate(pupil_outlier = if_else(pup_basCor > (median(pup_basCor, na.rm = TRUE) 
                                                + (3*mad(pup_basCor, na.rm = TRUE))), TRUE,
         if_else(pup_basCor < (median(pup_basCor, na.rm = TRUE) - 
                                 (3*mad(pup_basCor, na.rm = TRUE))), TRUE, FALSE)))

unique(tmp.df4_full_stim_downs_jun2021_60bins_no_na$mediansplit_sample_arousal2)

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins_no_na$mediansplit_sample_arousal2))

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins_no_na$mediansplit_sample_valence2))

tmp.df4_full_stim_downs_jun2021_60bins_no_na$Arpisal_newlab<- if_else(tmp.df4_full_stim_downs_jun2021_60bins_no_na$mediansplit_sample_arousal2 == "High", "Agitated", "Calm")

plots_paper$pupil_course<- tmp.df4_full_stim_downs_jun2021_60bins_no_na %>%
  subset(is.na(mediansplit_sample_arousal2) == FALSE)%>%
  subset(Group == "NT")%>%
  subset(pp_arousal_outler == FALSE)%>%
  subset(pupil_outlier == FALSE)%>%

  ggplot(aes(x = timerezero3, y = pup_basCor, color = Arpisal_newlab, linetype = mediansplit_sample_valence2)) +
  # aes(group = ssid),
  geom_smooth()+
  # stat_smooth(size=1.5, method = "loess", level = 0.95, 
  #   fullrange = TRUE) + 
  # stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
# theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  p$graphstyle+
   # scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   labs(color  = "Subjective valence", linetype = "Subjective arousal")

plots_paper$pupil_course<- plots_paper$pupil_course+
    guides(color=guide_legend(nrow=2, byrow=TRUE))

plots_paper$pupil_course
#   
#   tmp.df4_full_stim_downs_jun2021_60bins_no_na %>%
#   subset(is.na(mediansplit_sample_arousal2) == FALSE)%>%
#   subset(Group == "NT")%>%
#   subset(pp_arousal_outler == FALSE)%>%
#   subset(pupil_outlier == FALSE)%>%
#   
#   ggplot(aes(x = timerezero3, y = pup_basCor, color = mediansplit_ground_arousal, linetype = mediansplit_ground_valence)) +
#   # aes(group = ssid),
#   geom_smooth(se = F)+
#   # stat_smooth(size=1.5, method = "loess", level = 0.95, 
#   #   fullrange = TRUE) + 
#   # stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
# # theme_classic()+
#   ylab("Pupil size (z)")+
#   xlab("Time (s)")+
#   # p$graphstyle+
#   # scale_color_brewer(palette = "Dark2")+
#   xlim(0,6)
#   facet_grid(mediansplit_sample_arousal2~mediansplit_)
#    
#   
#   
#     tmp.df4_full_stim_downs_jun2021_60bins_no_na %>%
#   subset(is.na(mediansplit_sample_arousal2) == FALSE)%>%
#   subset(Group == "NT")%>%
#   subset(pp_arousal_outler == FALSE)%>%
#   subset(pupil_outlier == FALSE)%>%
#   
#   ggplot(aes(x = timerezero3, y = pup_basCor, color = mediansplit_sample_arousal2, linetype = mediansplit_ground_valence)) +
#   # aes(group = ssid),
#   geom_smooth(se = F)+
#   # stat_smooth(size=1.5, method = "loess", level = 0.95, 
#   #   fullrange = TRUE) + 
#   # stat_smooth(aes(group=mediansplit_ground_arousal, color = mediansplit_ground_arousal), size = 3)+  
# # theme_classic()+
#   ylab("Pupil size (z)")+
#   xlab("Time (s)")+
#   # p$graphstyle+
#   # scale_color_brewer(palette = "Dark2")+
#   xlim(0,6)
#   facet_grid(mediansplit_sample_arousal2~mediansplit_)

```

timecourse stats plots
```{r}
require(RColorBrewer) # make color friendly plots
require(tidyverse)

brewer.pal(4, "Dark2") # gives the exact names of pallets
  # "#1B9E77" "#D95F02" "#7570B3" "#E7298A"
  # timecourse_60bin_result_df$
  # Estimate_ar, Estimate_ar_vl,Estimate_br. Estimate_v

plots_timecourse <- list()

#  let's use the order arousal, valence, arousal x valence brightness
View(timecourse_60bin_result_df)

plots_timecourse$eff_size_pup_amp <-   timecourse_60bin_result_df[1:56,] %>% 
  select("timebins","Estimate_ar", "Estimate_vl", "Estimate_br", "Estimate_ar_vl") %>% 
  pivot_longer(-timebins, names_to = "variable", values_to = "Estimate")%>%
    subset(!is.na(Estimate))%>%
  #change the order of the coloring variable here and the name of legends
  mutate(variable = factor(variable, c("Estimate_ar", "Estimate_vl","Estimate_ar_vl",  "Estimate_br"), labels = c("arousal", "valence", "arousal x valence", "brightness")))%>%
  ggplot(aes(timebins, Estimate, group = variable, color= variable))+
  geom_line(aes(linetype = variable), size = 1)+

  scale_color_brewer(palette = "Dark2")+
    # scale_color_manual(values=c("#1B9E77", "#D95F02", "#7570B3", "#E7298A"))+
  # use hom correction for significance

    # brighteness
    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_br_adj_TRUE == TRUE]

    annotate(geom = 'rect', # use annotate instead of geom_rect, as it is more flexible
             xmin = .16, # got these values from the data-frame. need to fidn a way to automate this
                xmax = 6,
                ymin = -2.03+(sf*.3), # if I ever need to change this, use the scaling factor sf
                ymax = -2+.1+.01+(sf*.3),
                fill =  "#E7298A" , alpha = .5)+

      annotate("text", 
                x = (1+5.4)/2,
                y = ((-2) +(-2+.1))/2+(sf*.3),
                label = "brightness") +

    # arousal

    # timecourse_60bin_result_df$p_ar_adj
    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_adj_TRUE == TRUE]
     annotate(geom = 'rect', xmin = 1,
                xmax = 6,
                ymin = -2.03+.1+.1+.1+.1+(sf*.3),
                ymax = -2+.1+.1+.1+.1+.1+.01+(sf*.3),
                fill = "#1B9E77", alpha = .5)+
        annotate("text", 
                  x = (1+5.4)/2,
                y = ((-2+.1+.1+.1+.1) +(-2+.1+.1+.1+.1+.1))/2+(sf*.3),
                 label = "arousal") +

    # arousal-valence
   # timecourse_60bin_result_df$p_ar_vl_adj
    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_vl_adj_TRUE == TRUE]
       annotate(geom = 'rect', 
                xmin = 1,
                xmax = 3.30,
                ymin = -2.03+.1+.1+(sf*.3),
                ymax = -2+.1+.1+.1+.01+(sf*.3),

                fill ="#7570B3", alpha = .5, label = "text")+
    annotate("text", 
                x = (1+3.30)/2,
                y = ((-2+.1+.1) +(-2+.1+.1+.1))/2+(sf*.3),
                label = "arousal x valence") +
        xlab("Time (s)")+
    ylab("Effect size")+
    xlab("Time (s)")+
    ylab("Effect size")+
  xlim(0,6)

plots_timecourse$eff_size_pup_amp 
# need to rename the label legends

# Edit legend title and labels
plots_timecourse$eff_size_pup_amp <- plots_timecourse$eff_size_pup_amp + 
  p$graphstyle +
    guides(colour = guide_legend(override.aes = list(size=2)))+ #the line size of the legend tends to be smaller in print
  scale_x_continuous(limits = c(0,6), breaks = c(0,2,4,6))+
  scale_y_continuous(limits = c(-2,.7), breaks = c(-1, -0.5, 0,0.5))

plots_timecourse$eff_size_pup_amp<- plots_timecourse$eff_size_pup_amp+
  guides(color=guide_legend(nrow=2,byrow=TRUE))
# plots_timecourse$eff_size_pup_velocity
plots_timecourse$eff_size_pup_amp
```
SCR and heart rate
```{r}
plots_paper$interaction_SCR<-

interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred = arousal_c, modx = valence_c,line.thickness = 2)

plots_paper$interaction_SCR

plots_paper$interaction_SCR <- plots_paper$interaction_SCR +   scale_y_continuous(breaks = c(.4,.45, .5, .55), limits = c(.4,.58))

plots_paper$interaction_SCR

plots_paper$interaction_SCR<- plots_paper$interaction_SCR +
# plots_paper$interaction_ar_vl +
  theme_classic()+
  p$graphstyle_int+
  xlab("Subjective arousal (z)")+
  ylab("Phasic SCR (log)")

# scale_y_continuous(breaks = c(-1,0,1))

  plots_paper$interaction_SCR+

```

```{r}
  install.packages("expression")

plots_paper$bio_HR <- 
db_full6new_hr_fix_stim_nt1.11%>%
    subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
    group_by(stimIAPS)%>%
    mutate(mean_hr_dif = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
    ggplot(aes(valence_c, mean_hr_dif))+
    # geom_point()+
    geom_smooth(method = 'lm', se = F)+
    stat_summary(aes(y = Bio_Mean_HR_dif),geom = 'pointrange')+

  xlab("Subjective valence (z)")+
  ylab(expression(Delta*" heart rate (bpm)"))
    p$graphstyle+ylim(-4,1)
  # ggpubr::stat_cor()

plots_paper$bio_HR
  # scale_y_continuous(breaks = c(-4,-3,-2,1))

```

pacthwork

```{r}
library(patchwork)

plot_patch1<-
(plots_paper$interaction_ar_vl +
plots_paper$pupil_correlation +
plots_paper$pupil_course +
plots_timecourse$eff_size_pup_amp+
  plots_paper$interaction_SCR+
  plots_paper$bio_HR)+
  plot_layout(nrow = 3)+
  plot_annotation(tag_levels = "A")

plot_patch1

ggsave("patch_plot1.png", plot_patch1, device = "png", width = 15,height = 15, dpi = 800)
ggsave("patch_plot1.tiff", plot_patch1, device = "tiff", width = 15,height = 15, dpi = 800)
```

### 2021-09-04 Paper_Analyses_subj_obje_arousal.Rmd
First patch plot
made the plots and patchwork for the first big panel including a power point with some additional edits

@@
 
- db_full4new_stim_screen_pupil_nopract %>%
+# unique(db_full4new_stim_screen_pupil_nopract$ssid)
+plots_paper$pupil_correlation <- db_full4new_stim_screen_pupil_nopract %>%
    subset(Group == "NT")%>%
@@
   theme_classic()+
-  geom_hline(yintercept = .2, linetype = 'dashed', alpha = .2)+
+  geom_hline(yintercept = 0, linetype = 'dashed', alpha = .2)+
    # ggpubr::stat_compare_means(paired = TRUE)+
   ggpubr::stat_compare_means()
-  facet_grid(~mediansplit_sample_arousal2)
-
+  # facet_grid(~mediansplit_sample_arousal2)
+
+  plots_paper$pupil_correlation+ p$graphstyle
 ```

### 2021-09-04 Figures.Rmd
done plots - to do
match the pca tsne colos to the colors of JASP

@@
 ```
+
+```{r}
+
+p$graphstyle_tsne <-  theme(#base plot theme
+
+  # axis lines
+  # axis.line.y = element_line(color="black", size = 1.5),
+  # axis.line.x = element_line(color="black", size = 1,5),
+
+  axis.title.y=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
+  axis.title.x=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
+
+  # text
+  strip.text.x = element_text(size = 12*(sf+.5),  colour = "black"),
+  strip.text.y = element_text(size = 12*(sf+.5),  colour = "black"),
+
+  text=element_text(size = 14, family = "sans"),
+  axis.text.x = element_text(size = 14*(sf+.5), family = "sans", colour = "black",),
+  axis.text.y = element_text(size = 14*(sf+.5), family = "sans", colour = "black"),
+
+  # panel
+  panel.grid.major = element_blank(),
+   panel.border = element_rect(colour = "black", fill=NA, size=5),
+  panel.background = element_blank(),
+  # panel.background = element_rect(fill="transparent"),
+  # panel.border = element_rect(fill="black"),
+  # strip shades (reco rectagles)
+   # strip.background = element_blank(),
+
+  # legend
+  legend.position = "top",
+  legend.key = element_rect(colour = "transparent", fill="transparent"),
+  #legend.direction = "horizontal",
+
+  legend.text = element_text(size = 10*(sf+.3)),
+  # legend.title = element_text(size = 10*(sf+.3)),
+  # legend line tends to be really small in print so adjust here
+  legend.key.height = unit(.5, "cm"),
+  legend.key.width = unit(2, "cm"),
+
+  #legend.text = element_text(size = 10*sf),
+  # legend.title=element_blank(),
+  #legend.text = element_blank(),
+  #axis.ticks = element_blank(),
+)
+
+pca_res <- prcomp(clustering_agg[,c(20,24,25)], center = TRUE, scale. = TRUE)
+plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg$y_kmeans)
+stat_el
+# plot_data$
+plots_paper$PCA_clust <- ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels, fill = labels)) +
+  geom_point(size = 2, alpha = .6)+
+  geom_text(aes(label= clustering_agg$stimDescription), alpha = .4)+
+  stat_ellipse(aes(fill = labels))+
+  ylab("Componet 2")+
+  xlab("Component 1")+
+  p$graphstyle+
+  scale_color_brewer(palette = "Dark2")+
+  scale_fill_brewer(palette = "Dark2")+
+
+theme(axis.text.y   = element_text(size=14),
+        axis.text.x   = element_text(size=14),
+        axis.title.y  = element_text(size=14),
+        axis.title.x  = element_text(size=14),
+        panel.background = element_blank(),
+        panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_rect(colour = "black", fill=NA, size=3)
+  )
+
+ggsave("PCA_clust.tiff", plots_paper$PCA_clust , device = "tiff", width = 10, height = 7, dpi = 800)
+
+```

### 2021-09-04 Paper_Analyses_subj_obje_arousal.Rmd
done plots - to do
match the pca tsne colos to the colors of JASP

@@
 
+test$Distances
 ```
@@
 
-ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels)) +
-  geom_point()+
-  geom_text(aes(label= clustering_agg$stimDescription))
+# plot_data$
+ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels, fill = labels)) +
+  geom_point(size = 2, alpha = .4)+
+  geom_text(aes(label= clustering_agg$stimDescription))+
+  stat_ellipse()+
+  ylab("Componet 2")+
+  xlab("Component 1")+
+  p$graphstyle+
+  theme()
+```
 

### 2021-09-05 Figures.Rmd
newplots

--- 2021-09-04 Figures.Rmd
@@
 ```
+
+```{r}
+
+p$graphstyle_tsne <-  theme(#base plot theme
+
+  # axis lines
+  # axis.line.y = element_line(color="black", size = 1.5),
+  # axis.line.x = element_line(color="black", size = 1,5),
+
+  axis.title.y=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
+  axis.title.x=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
+
+  # text
+  strip.text.x = element_text(size = 12*(sf+.5),  colour = "black"),
+  strip.text.y = element_text(size = 12*(sf+.5),  colour = "black"),
+
+  text=element_text(size = 14, family = "sans"),
+  axis.text.x = element_text(size = 14*(sf+.5), family = "sans", colour = "black",),
+  axis.text.y = element_text(size = 14*(sf+.5), family = "sans", colour = "black"),
+
+  # panel
+  panel.grid.major = element_blank(),
+   panel.border = element_rect(colour = "black", fill=NA, size=5),
+  panel.background = element_blank(),
+  # panel.background = element_rect(fill="transparent"),
+  # panel.border = element_rect(fill="black"),
+  # strip shades (reco rectagles)
+   # strip.background = element_blank(),
+
+  # legend
+  legend.position = "top",
+  legend.key = element_rect(colour = "transparent", fill="transparent"),
+  #legend.direction = "horizontal",
+
+  legend.text = element_text(size = 10*(sf+.3)),
+  # legend.title = element_text(size = 10*(sf+.3)),
+  # legend line tends to be really small in print so adjust here
+  legend.key.height = unit(.5, "cm"),
+  legend.key.width = unit(2, "cm"),
+
+  #legend.text = element_text(size = 10*sf),
+  # legend.title=element_blank(),
+  #legend.text = element_blank(),
+  #axis.ticks = element_blank(),
+)
+?stat_ellipse
+
+clustering_agg
+clustering_agg$cluster_interpreted<- NULL
+clustering_agg$AlexGroup<-NULL
+clustering_agg$y_kmeans<-NULL
+
+clustering_agg_JASPtest$stimIAPS2<- as.character(clustering_agg_JASPtest$stimIAPS2)
+clust_stim2<- select(clustering_agg_JASPtest, c(stimIAPS2,clusters, stimDescription))
+
+test<- left_join(clustering_agg,clust_stim2)
+
+colnames(clustering_agg_JASPtest)
+clustering_agg_JASPtest<- subset(clustering_agg_JASPtest, !is.na(clustering_agg_JASPtest$clusters))
+pca_res <- prcomp(clustering_agg_JASPtest[,c(24,23,19)], center = TRUE, scale. = FALSE)
+plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg_JASPtest$clusters)
+plot_data$labels<- factor(plot_data$labels)
+# stat_el
+# plot_data$
+plots_paper$PCA_clust
+
+plot_data%>%
+  subset(!is.na(labels))%>%
+   # subset(!is.na(cluster))%>%
+  ggplot( aes(x = PC1, y = PC2, colour = labels)) +
+  geom_point(size = 1, alpha = .8)+
+  # geom_text(aes(label= test$stimDescription), alpha = .7, size = 5)+
+  # stat_ellipse()+
+  # stat_ellipse(aes(x = PC1,y=PC2,
+  #                  lty=labels,
+  #                  fill=labels, 
+  #                  color=labels),
+  #   geom="polygon",
+  #   alpha=0.2, 
+  #   size = 1.5)+
+  # scale_fill_manual(values=c("red","green","blue"))+
+    # scale_color_manual(values=c("red","green","blue"))+
+  # scale_linetype_manual(values=c(1,2,3))+
+  ylab("Componet 2")+
+  xlab("Component 1")+
+  p$graphstyle +
+
+theme(
+  # axis.text.y   = element_text(size=14),
+        # axis.text.x   = element_text(size=14),
+        # axis.title.y  = element_text(size=14),
+        # axis.title.x  = element_text(size=14),
+        panel.background = element_blank(),
+        panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black"),
+        panel.border = element_rect(colour = "black", fill=NA, size=3)
+  )
+
+plots_paper$PCA_clust
+ggsave("PCA_clust.tiff", plots_paper$PCA_clust , device = "tiff", width = 10, height = 7, dpi = 800)
+
+```
+
+```{r}
+
+clust_stim2
+clustering_new <- left_join(clustering, clust_stim2, by = c("stimIAPS2", "stimDescription"))
+
+clustering_new$Cluster<- clustering_new$clusters
+
+unique(tmp.df4_full_stim_downs_jun2021_60bins_no_na1$ssid)
+clustering_new %>%
+  subset(!is.na(Cluster))%>%
+  # subset(ssid_num>303)%>%^
+  group_by(ssid, Cluster)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # mutate(arousal2 = abs(arousal))%>%
+  subset(arousal> -9)%>%
+  ggboxplot(x = "Cluster", y = "arousal",
+          color = "Cluster")+
+  geom_jitter(width = .1, alpha = .2)+
+    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
+  xlab("Cluster")+
+  ylab("Subjective arousal \n (calm - agitated)")+
+  p$graphstyle+ theme(legend.position = "none")
+  # stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
+  # stat_compare_means(label.y = 9)
+plots_paper$arousal_clust
+# valence cluster
+
+plots_paper$valence_clust<- tmp.df4_full_stim_downs_jun2021_60bins_no_na %>%
+  group_by(ssid, Cluster)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  mutate(arousal2 = abs(arousal))%>%
+  subset(arousal> -9)%>%
+  ggboxplot(x = "Cluster", y = "valence",
+          color = "Cluster")+
+  geom_jitter(width = .1, alpha = .2)+
+    stat_summary(aes(group =ssid), geom =  'line', alpha = .2, size = .1)+
+  xlab("Cluster")+
+  ylab("Subjective valence \n (negative - positive)")+
+  p$graphstyle+ theme(legend.position = "none")
+  # stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
+  # stat_compare_means(label.y = 9)
+
+plots_paper$valence_clust
+
+clust_subjective<- plots_paper$valence_clust+plots_paper$arousal_clust+
+  plot_layout(ncol = 2)+plot_annotation(tag_levels = "A")
+
+clust_subjective
+
+ggsave("clust_subjective.tiff", clust_subjective, device = "tiff", width = 10, height = 5, dpi = 800)
+```

### 2021-09-05 Paper_Analyses_subj_obje_arousal.Rmd
newplots

--- 2021-09-04 Paper_Analyses_subj_obje_arousal.Rmd
@@
 colnames(clustering_agg)
-clust_dataset = clustering_agg[c(20,24,25)]
+clust_dataset = clustering_agg[c(25,24,20)]
 
@@
 # Using the elbow method to find the optimal number of clusters
-set.seed(6)
+set.seed(1)
 wcss = vector()
@@
 # Fitting K-Means to the dataset
-set.seed(29)
+set.seed(1)
 kmeans = kmeans(x = clust_dataset, centers = 3)
@@
 ?clusplot
+
+clust_dataset
+y_kmeans
 clusplot(clust_dataset,
@@
 
-pca_res <- prcomp(clustering_agg[,c(20,24,25)], center = TRUE, scale. = TRUE)
+clust_dataset
+
+clustering_agg%>%
+  subset(y_kmeans == 3)%>%
+  select(c(stimDescription))
+
+clustering_agg_JASPtest%>%
+   subset(clusters == 3)%>%
+  select(c(stimDescription))
+
+clustering_agg_bonkers <- subset(clustering_agg, stimIAPS2 != "9926")
+
+pca_res <- prcomp(clustering_agg_bonkers[1:55,c(25,24,20)], center = TRUE, scale. = TRUE)
+pca_res <- prcomp(clustering_agg_JASPtest[,c(24,23,19)], center = TRUE, scale. = FALSE)
 plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg$y_kmeans)
 
-ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels)) +
-  geom_point()+
-  geom_text(aes(label= clustering_agg$stimDescription))
+# plot_data$
+ggplot(plot_data, aes(x = PC1, y = PC2, colour = labels, fill = labels)) +
+  geom_point(size = 2, alpha = .4)+
+  # geom_text(aes(label= clustering_agg$stimDescription))+
+  stat_ellipse(show.legend = TRUE)+
+  ylab("Componet 2")+
+  xlab("Component 1")+
+  # scale_color_manual(values = c("red", "green", "blue"))+
+  p$graphstyle+
+  theme()
+
+?scale_color_manual
+scale_color_brewer(breaks=c("1","5","10","50","100"), palette = "Set1")
+```
 
@@
 
-tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
+tmp.df4_full_stim_downs_jun2021_60bins_no_na %>%
   group_by(ssid, cluster_interpreted)%>%
@@
 options(scipen = 999)
+
+```{r}
 tmp.df4_full_stim_downs_jun2021_60bins_no_na%>%
@@
 cluster_lmers<- list()
-clustering3$stimIAPS2<- as.factor(as.character(clustering3$stimIAPS2))
-
-clustering3$ssid<- as.factor(as.character(clustering3$ssid))
+clustering_new$stimIAPS2<- as.factor(as.character(clustering_new$stimIAPS2))
+
+clustering_new$ssid<- as.factor(as.character(clustering_new$ssid))
 clustering3
@@
 clustering3$arousal
-
-cluster_lmers$arousal <- lmer(arousal ~ cluster_interpreted + 
+clustering_new$Cluster<- as.factor(clustering_new$Cluster)
+cluster_lmers$arousal <- lmer(arousal ~ Cluster + 
+                               (1 | ssid)+
+                               (1|stimIAPS2),
+                             REML = FALSE,
+                             data = clustering_new)
+
+summary(cluster_lmers$arousal)
+
+anova(cluster_lmers$arousal)
+
+emmeans::emmeans(cluster_lmers$arousal, pairwise~Cluster)
+
+# valence
+cluster_lmers$valence <- lmer(valence ~ Cluster + 
+                               (1 | ssid)+
+                               (1|stimIAPS2),
+                             REML = FALSE,
+                             data = clustering_new)
+
+summary(cluster_lmers$valence)
+emmeans::emmeans(cluster_lmers$valence, pairwise~Cluster)
+
+cluster_lmers$pup_clust <- lmer(pup_basCor ~ cluster_interpreted + 
                                (1 | ssid)+
@@
 
-summary(cluster_lmers$arousal)
-
-anova(cluster_lmers$arousal)
-
-emmeans::emmeans(cluster_lmers$arousal, pairwise~cluster_interpreted)
-
-# valence
-cluster_lmers$valence <- lmer(valence ~ cluster_interpreted + 
+cluster_lmers$pup_clust1 <- lmer(pup_basCor ~ y_kmeans + 
                                (1 | ssid)+
@@
 
-summary(cluster_lmers$valence)
-emmeans::emmeans(cluster_lmers$valence, pairwise~cluster_interpreted)
+summary(cluster_lmers$pup_clust1)
+
+emmeans::emmeans(cluster_lmers$pup_clust1, pairwise~y_kmeans, adjust = "bonf")
+
+table(is.na(clustering3$Bio_Mean_HR_dif))
+cluster_lmers$hrdif_clust2 <- lmer(Bio_Mean_HR_dif ~ y_kmeans + 
+                               (1 | ssid),
+                               # <!-- (1|stimIAPS2), -->
+                             REML = FALSE,
+                             data = clustering3)
+
+                             summary(cluster_lmers$pup_clust1)
+
+emmeans::emmeans(cluster_lmers$hrdif_clust2, pairwise~y_kmeans, adjust = "bonf")
+summary(cluster_lmers$hrdif_clust2)
+
+cluster_lmers$scr_clust2 <- lmer(log_BIO_CDA.PhasicMax ~ y_kmeans + 
+                               (1 | ssid)+
+                               (1|stimIAPS),
+                             REML = FALSE,
+                             data = clustering3)
+
+                             summary(cluster_lmers$scr_clust2)
+
+emmeans::emmeans(cluster_lmers$scr_clust2, pairwise~y_kmeans, adjust = "bonf")
+summary(cluster_lmers$hrdif_clust2)
 

### 2021-09-07 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@
 
+summary(pupil_arousal_findings$pupil_from_ar_vale)
 plots_paper$interaction_ar_vl <- interactions::interact_plot(pupil_arousal_findings$pupil_from_ar_vale , pred = arousal_c, modx = valence_c)
@@
   plots_paper$pupil_correlation+ p$graphstyle
+
+summary(lmer(pup_basCor ~ (valence_c) +
+                                                    Mean_gray_z  +
+                                                    (1 + Mean_gray_z | ssid)+
+                                                    (0+ valence_c | ssid),
+                                                  REML = FALSE,
+                      data = db_full4new_stim_screen_pupil_nopract%>%
+                         subset(Group == "NT")%>%
+                        subset(pupil_outlier == FALSE)%>%
+                        subset(arousal_outler == FALSE)))
+
+summary(lmer(pup_basCor ~ (arousal_c) +
+                                                    Mean_gray_z  +
+                                                    (1 + Mean_gray_z | ssid)+
+                                                    (0+ valence_c | ssid),
+                                                  REML = FALSE,
+                      data = db_full4new_stim_screen_pupil_nopract%>%
+                         subset(Group == "NT")%>%
+                        subset(pupil_outlier == FALSE)%>%
+                        subset(arousal_outler == FALSE)))
+
+summary(lmer(pup_basCor ~ (arousal_c+valence_c)
+                                                      +
+                                                    (1 + Mean_gray_z | ssid)+
+                                                    (0+ valence_c | ssid),
+                                                  REML = FALSE,
+                      data = db_full4new_stim_screen_pupil_nopract%>%
+                         subset(Group == "NT")%>%
+                        subset(pupil_outlier == FALSE)%>%
+                        subset(arousal_outler == FALSE)))
+
+macthed_test$stimIAPS2<- as.character(macthed_test$stimIAPS2)
+test_matchedM<- left_join( macthed_test, db_full4new_stim_screen_pupil_nopract,by = "stimIAPS2")
+
+matchedPupiltest <- lmer(pup_basCor ~ (arousal_c*valence_c)
+                                                      +
+                                                    (1 + Mean_gray_z | ssid)+
+                                                    (0+ valence_c | ssid),
+                                                  REML = FALSE,
+                      data = test_matchedM%>%
+                         subset(Group == "NT"))
+
+matchedPupiltest
+
+interactions::interact_plot(matchedPupiltest , pred =arousal_c  , modx =  valence_c)
+
+```
+
+swicth predictirs
+
+```{r}
+unique(db_full4new_stim_screen_pupil_nopract$ssid)
+
+library(lmerTest)
+pupil_arousal_findings$ar_from_val_pup <- lmer(arousal_c ~ valence_c*pup_basCor +
+                                                    Mean_gray_z  +
+                                                    (1 | ssid)+
+                                                    (1|stimIAPS),
+                                                  REML = FALSE,
+                      data = db_full4new_stim_screen_pupil_nopract%>%
+                        subset(Group == "NT"))
+                        # subset(pupil_outlier == FALSE)%>%
+                        # subset(arousal_outler == FALSE))
+
+summary(pupil_arousal_findings$ar_from_val_pup)
+
+interactions::interact_plot(pupil_arousal_findings$ar_from_val_pup, pred = valence_c, modx =  pup_basCor)
+
 ```
@@
 
+test<- subset(db_full4new_stim_screen_pupil_nopract, 
+                                    Group == "NT")
+
+cor.test(test$arousal_c, test$valence_c)
+?rmcorr::rmcorr
+plot(rmcorr::rmcorr(participant = "stimIAPS2", measure1 = "arousal_c", measure2 = "valence_c", data = test))
+
+plot(rmcorr::rmcorr(participant = "ssid", measure1 = "arousal_c", measure2 = "valence_c", data = test))
+
+db_full4new_stim_screen_pupil_nopract%>%
+  ggplot(aes(arousal_c, valence_c))+
+  geom_point()
+
+# pollu
+db_full4new_stim_screen_pupil_nopract$valence_c_sq<- db_full4new_stim_screen_pupil_nopract$valence**2
+polyyrelation<- lmer(arousal_c ~ valence_c+valence_c_sq+ (1|ssid) + (1|stimIAPS),
+                     REML = FALSE,
+                     data = db_full4new_stim_screen_pupil_nopract)
 ```
@@
 
-tmp.df4_full_stim_downs_jun2021_60bins%>%
+tmp.df4_full_stim_downs_jun2021_60bins %>%
   subset(!is.na(ground_valence_2))%>%
@@
 
-#
-
+# macthed test
+
+```
+
+```{r}
+unique(db_full4new_stim_screen_pupil_nopract_nt_304$ssid)
+
+db_full4new_stim_screen_pupil_nopract_nt_304$stimIAPS2<- as.character(substr(db_full4new_stim_screen_pupil_nopract_nt_304$stimIAPS, 1,4))
+
+nrow(db_full4new_stim_screen_pupil_nopract_nt_304)
+nrow(testmatched_scr)
+testmatched_scr<- left_join(macthed_test, db_full4new_stim_screen_pupil_nopract_nt_304, by = "stimIAPS2")
+
+testmcthedscr <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c * valence_c + (1|ssid) + (1|stimIAPS),
+                        REML = FALSE,
+                        data = testmatched_scr)
+
+summary(testmcthedscr)
+
+anova(pupil_arousal_findings$arousal_phas_max)
+
+interactions::interact_plot(testmcthedscr, pred = arousal_c, modx = valence_c)
+
+```
+
+```
 pupil_arousal_findings$BIO_CDA.PhasicMax_ar <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c + (1|ssid),
@@
 summary(pupil_arousal_findings$BIO_CDA.PhasicMax_vl)
+
+```
+
+semi matched dataset
+```
 
@@
 
+library(ggplot2)
+library(reshape2)
+library(data.table)
+library(tidyr)
+library(tidyverse)
+?gather
+
+db_full6new_hr_fix_stim_nt1.1 %>%
+  mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
+  subset(ssid!= "347")%>%
+  group_by(ssid)%>%
+  mutate(Bio_Mean_HR_dif = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1],
+         pup_basCor = scale(pup_basCor, center = TRUE, scale = TRUE)[,1],
+         log_BIO_CDA.PhasicMax = scale(log_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
+  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"))%>%
+  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"))%>%
+  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"))%>%
+  select(c(ssid, cor_hr_pup, cor_hr_scr, cor_pup_scr))%>%
+  gather(key, value, -ssid)%>%
+  group_by(ssid, key, value)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(key, value))+
+  geom_jitter(width = .1, alpha = .1)+
+  geom_line(aes(group = ssid), se = F)+
+  stat_summary(geom = 'pointrange')
+
 ```
@@
 View(clustering_agg_JASP)
+
+clustering_agg_JASP$valence_median_split<- if_else(clustering_agg_JASP$valence > median(clustering_agg_JASP$valence,na.rm = TRUE), "positive", "negative")
+
+clustering_agg_JASP$ValenceMean_median_split <- if_else(clustering_agg_JASP$ValenceMean > median(clustering_agg_JASP$ValenceMean,na.rm = TRUE), "positive", "negative")
+
+clustering_agg_JASP%>%
+  mutate(abs_ar  = abs(arousal))%>%
+  # ggplot(aes(valence_median_split, arousal))+
+  ggpubr::ggboxplot(x = "valence_median_split", y = "abs_ar")+
+  geom_point()
+
+clustering_agg_JASP%>%
+  mutate(abs_ar = abs(clustering_agg_JASP))
+  # ggplot(aes(valence_median_split, arousal))+
+  ggpubr::ggboxplot(x = "ValenceMean_median_split", y = "ArousalMean")+
+  geom_point()+
+  stat_summary(geom = 'pointrange')
+
+write_csv(clustering_agg_JASP, "clustering_agg_JASP_newtomatch.csv")
+
+library(readxl)
+macthed_test <- read_excel("macthed_test.xlsx")
+View(macthed_test)
+
+macthed_test%>%
+  # ggplot(aes(valence_median_split, arousal))+
+  ggpubr::ggboxplot(x = "ValenceMean_median_split", y = "ArousalMean")+
+  # geom_point()+
+  stat_summary(geom = 'pointrange')
+```
 
@@
 
-pca_res <- prcomp(clustering_agg_bonkers[1:55,c(25,24,20)], center = TRUE, scale. = TRUE)
-pca_res <- prcomp(clustering_agg_JASPtest[,c(24,23,19)], center = TRUE, scale. = FALSE)
+pca_res <- prcomp(clustering_agg[,c(25,24,20)], center = TRUE, scale. = TRUE)
+pca_res <- prcomp(clustering_agg_JASPtest[,c(24,23,19)], center = TRUE, scale. = TRUE)
 plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg$y_kmeans)
@@
   geom_point(size = 2, alpha = .4)+
-  # geom_text(aes(label= clustering_agg$stimDescription))+
+  geom_text(aes(label= clustering_agg$stimDescription))+
   stat_ellipse(show.legend = TRUE)+
@@
                                (1 | ssid)+
-                               (1|stimIAPS2),
+                               (1|stimIAPS),
                              REML = FALSE,
@@
 emmeans::emmeans(cluster_lmers$valence, pairwise~Cluster)
+
+clustering_new_agg<- clustering_new%>%
+  subset(!is.na(Cluster))%>%
+  group_by(ssid, Cluster)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)
+clustering_new_agg$Cluster<- factor(clustering_new_agg$Cluster)
+
+clustering_new_agg
+clusr_ar<- afex::aov_ez(id = "ssid",
+             data = clustering_new_agg,
+             dv = "arousal",
+             within = "Cluster",
+             between = NULL)
+
+clustering_new_agg%>%
+  ggplot(aes(Cluster, arousal))+
+  geom_jitter(width = .2)+
+  geom_boxplot()
+emmeans::emmeans(clusr_ar, pairwise~Cluster, adjust = "bonf")
+
+clusr_vl<- afex::aov_ez(id = "ssid",
+             data = clustering_new_agg,
+             dv = "valence",
+             within = "Cluster",
+             between = NULL)
+
+emmeans::emmeans(clusr_vl, pairwise~Cluster, adjust = "bonf")
 

### 2021-09-07 Figures.Rmd
a few new updates
- plots, checks

@@
 interaction plot
+
+https://uc-r.github.io/kmeans_clustering
 
@@
 clustering_agg_JASPtest<- subset(clustering_agg_JASPtest, !is.na(clustering_agg_JASPtest$clusters))
-pca_res <- prcomp(clustering_agg_JASPtest[,c(24,23,19)], center = TRUE, scale. = FALSE)
+pca_res <- prcomp(clustering_agg_JASPtest[,c(24,23,19)], center = TRUE, scale. = TRUE)
 plot_data <- cbind(as.data.frame(pca_res$x[, 1:2]), labels = clustering_agg_JASPtest$clusters)
@@
   # geom_text(aes(label= test$stimDescription), alpha = .7, size = 5)+
-  # stat_ellipse()+
+  stat_ellipse()+
   # stat_ellipse(aes(x = PC1,y=PC2,
@@
 unique(tmp.df4_full_stim_downs_jun2021_60bins_no_na1$ssid)
-clustering_new %>%
+plots_paper$arousal_clust<- clustering_new %>%
   subset(!is.na(Cluster))%>%
@@
 
-plots_paper$valence_clust<- tmp.df4_full_stim_downs_jun2021_60bins_no_na %>%
+plots_paper$valence_clust<- clustering_new %>%
+  subset(!is.na(Cluster))%>%
   group_by(ssid, Cluster)%>%
+
   summarise_if(is.numeric, mean, na.rm = TRUE)%>%
@@
 ```
+
+```{r}
+tsne::tsne()
+
+```
+
+Phasic responses reveal limited cross correlations across physiological signals
+```{r}
+
+correlation_plot<- db_full6new_hr_fix_stim_nt1.1 %>%
+  mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
+  subset(ssid!= "347")%>%
+  subset(!is.na(mediansplit_ground_valence))%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+  group_by(ssid)%>%
+  mutate(Bio_Mean_HR_dif = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1],
+         pup_basCor = scale(pup_basCor, center = TRUE, scale = TRUE)[,1],
+         log_BIO_CDA.PhasicMax = scale(log_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
+  group_by(ssid, mediansplit_ground_valence)%>%
+  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"))%>%
+  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"))%>%
+  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"))%>%
+  select(c(ssid, mediansplit_ground_valence,cor_hr_pup, cor_hr_scr, cor_pup_scr))%>%
+  gather(key, value, -ssid,-mediansplit_ground_valence)%>%
+  group_by(ssid,mediansplit_ground_valence, key, value)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(key, value, color = key))+
+  geom_hline(yintercept = 0, size = 1.5, linetype = "dashed", alpha = .5)+
+  geom_line(aes(group = ssid), se = F, color = "black", alpha = .2)+
+  geom_jitter(width = .1, alpha = .5)+
+
+  stat_summary(geom = 'pointrange', color = "black")+
+    facet_grid(~mediansplit_ground_valence)+
+
+  p$graphstyle+
+  ylab("Correlation")+
+  scale_x_discrete(
+        labels=c("HR vs. Pupil", "HR vs. SCR", "Pupil vs. SCR"))+
+  theme(axis.title.x = element_blank(), axis.text.x = element_text( 
+                           size=14, angle=45), legend.position = "none")+
+  scale_color_brewer(palette = "Dark2")
+  # ggpubr::ggviolin(aes(x = "key", y = "value"))
+
+  # subset(db_full6new_hr_fix_stim_nt1.1, Bio_Mean_HR_dif )
+
+  correlation_plot
+
+  db_full6new_hr_fix_stim_nt1.1
+
+  ?cut
+  db_full6new_hr_fix_stim_nt1.1$valeence_groun_3cat<- cut(db_full6new_hr_fix_stim_nt1.1$ValenceMean, breaks = 3, labels = c("negative", "mid", "positive"))
+
+  db_full6new_hr_fix_stim_nt1.1 %>%
+  mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
+  subset(ssid!= "347")%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+    subset(!is.na(valeence_groun_3cat))%>%
+  group_by(ssid)%>%
+  mutate(Bio_Mean_HR_dif = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1],
+         pup_basCor = scale(pup_basCor, center = TRUE, scale = TRUE)[,1],
+         log_BIO_CDA.PhasicMax = scale(log_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
+    group_by(ssid, valeence_groun_3cat)%>%
+  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"))%>%
+  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"))%>%
+  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"))%>%
+  select(c(ssid,valeence_groun_3cat, cor_hr_pup, cor_hr_scr, cor_pup_scr))%>%
+  gather(key, value, -ssid, - valeence_groun_3cat)%>%
+  group_by(ssid, key, value, valeence_groun_3cat)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(valeence_groun_3cat, value, color = valeence_groun_3cat))+
+  geom_hline(yintercept = 0, size = 1.5, linetype = "dashed", alpha = .5)+
+    geom_hline(yintercept = .2, size = 1.5, linetype = "dashed", alpha = .5)+
+    geom_hline(yintercept = -.2, size = 1.5, linetype = "dashed", alpha = .5)+
+  geom_line(aes(group = ssid), se = F, color = "black", alpha = .2)+
+  geom_jitter(width = .1, alpha = .5)+
+
+  stat_summary(geom = 'pointrange', color = "black")+
+    facet_grid(~key)+
+
+  p$graphstyle+
+  ylab("Correlation")+
+  scale_x_discrete(
+        labels=c("HR vs. Pupil", "HR vs. SCR", "Pupil vs. SCR"))+
+  theme(axis.title.x = element_blank(), axis.text.x = element_text( 
+                           size=14, angle=45))+
+  scale_color_brewer(palette = "Dark2")
+
+```
+
+```{r}
+ggsav
+
+ hr_rmmcorr<- db_full6new_hr_fix_stim_nt1.1 %>%
+  # mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
+  subset(ssid!= "347")%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")
+plot(rmcorr::rmcorr(participant = "ssid", measure1 = "Bio_Mean_HR_dif", measure2 = "pup_basCor", data = hr_rmmcorr))
+
+plot(rmcorr::rmcorr(participant = "ssid", measure1 = "log_BIO_CDA.PhasicMax_z", measure2 = "pup_basCor", data = hr_rmmcorr))
+
+hr_rmmcorr<- hr_rmmcorr%>%
+  group_by(ssid)%>%
+  mutate(log_BIO_CDA.PhasicMax_z= scale(log_BIO_CDA.PhasicMax, center =TRUE, scale = TRUE))
+
+plot(rmcorr::rmcorr(participant = "ssid", measure1 = "log_BIO_CDA.PhasicMax_z", measure2 = "Bio_Mean_HR_dif", data = hr_rmmcorr))
+
+correlation_plot
+
+scater_pupil_HR<- db_full6new_hr_fix_stim_nt1.1 %>%
+  subset(!is.na(stimDescription))%>%
+  subset(!is.na(mediansplit_ground_valence))%>%
+  group_by(stimIAPS,mediansplit_ground_valence, stimDescription)%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(Bio_Mean_HR_dif, pup_basCor))+
+  geom_point(aes(color = mediansplit_ground_valence), size = 2, alpha = .6)+
+  geom_text(aes(label = stimDescription,olor = mediansplit_ground_valence), alpha = .3)+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()+
+  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
+  # xlab("Average heart rate difference")+
+  ylab("Average pupil change (au)")+
+  p$graphstyle
+
+scater_pupil_HR
+
+db_full6new_hr_fix_stim_nt1.1 %>%
+  subset(!is.na(stimDescription))%>%
+  subset(!is.na(mediansplit_ground_valence))%>%
+  group_by(stimIAPS, stimDescription,mediansplit_ground_valence)%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(Bio_Mean_HR_dif, pup_basCor, color = mediansplit_ground_valence))+
+  geom_point(size = 2, alpha = .6)+
+  geom_text(aes(label = stimDescription), alpha = .3)+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()+
+  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
+  # facet_grid(~mediansplit_ground_valence)+
+  # xlab("Average heart rate difference")+
+  ylab("Average pupil change (au)")+
+  p$graphstyle
+
+db_full6new_hr_fix_stim_nt1.1$log_BIO_CDA.PhasicMax_z<- scale(db_full6new_hr_fix_stim_nt1.1$log_BIO_CDA.PhasicMax, center =  TRUE,scale = TRUE)[,1]
+
+db_full6new_hr_fix_stim_nt1.1 %>%
+  subset(!is.na(stimDescription))%>%
+  subset(!is.na(mediansplit_ground_valence))%>%
+  group_by(stimIAPS, stimDescription,mediansplit_ground_valence)%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax_z, color = mediansplit_ground_valence))+
+  geom_point(size = 2, alpha = .6)+
+  geom_text(aes(label = stimDescription), alpha = .3)+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()+
+  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
+  # facet_grid(~mediansplit_ground_valence)+
+  # xlab("Average heart rate difference")+
+  ylab("Average pupil change (au)")+
+  p$graphstyle
+
+db_full6new_hr_fix_stim_nt1.1$stimIAPS2<- as.factor(substr(db_full6new_hr_fix_stim_nt1.1$stimIAPS, 1,4))
+
+macthed_test$matched<- "matched"
+
+macthed_test$stimIAPS2<- as.factor(macthed_test$stimIAPS2)
+
+# mac
+testmatched_hr_stim<- left_join(macthed_test,db_full6new_hr_fix_stim_nt1.1,  by = c("stimIAPS2"))
+
+testmatched_hr_stim %>%
+  subset(!is.na(mediansplit_ground_valence))%>%
+  subset(!is.na(matched))%>%
+  group_by(stimIAPS, stimDescription,mediansplit_ground_valence)%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ungroup()%>%
+  mutate(log_BIO_CDA.PhasicMax_z = scale(log_BIO_CDA.PhasicMax), pup_basCor_z = scale(pup_basCor))%>%
+  ggplot(aes(Bio_Mean_HR_dif, pup_basCor, color = mediansplit_ground_valence))+
+  geom_point(size = 2, alpha = .6)+
+  geom_text(aes(label = stimDescription), alpha = .3)+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()+
+  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
+  # facet_grid(~mediansplit_ground_valence)+
+  # xlab("Average heart rate difference")+
+  ylab("Average pupil change (au)")+
+  p$graphstyle
+
+testmatched_hr_stim %>%
+  subset(!is.na(mediansplit_ground_valence))%>%
+  subset(!is.na(matched))%>%
+  group_by(stimIAPS, stimDescription,mediansplit_ground_valence)%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ungroup()%>%
+  mutate(log_BIO_CDA.PhasicMax_z = scale(log_BIO_CDA.PhasicMax), pup_basCor_z = scale(pup_basCor))%>%
+  ggplot(aes(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax_z, color = mediansplit_ground_valence))+
+  geom_point(size = 2, alpha = .6)+
+  geom_text(aes(label = stimDescription), alpha = .3)+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()+
+  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
+  # facet_grid(~mediansplit_ground_valence)+
+  # xlab("Average heart rate difference")+
+  ylab("Average pupil change (au)")+
+  p$graphstyle
+
+testmatched_hr_stim %>%
+  subset(!is.na(mediansplit_ground_valence))%>%
+  subset(!is.na(matched))%>%
+  group_by(stimIAPS, stimDescription,mediansplit_ground_valence)%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ungroup()%>%
+  mutate(log_BIO_CDA.PhasicMax_z = scale(log_BIO_CDA.PhasicMax), pup_basCor_z = scale(pup_basCor))%>%
+  ggplot(aes(pup_basCor_z, log_BIO_CDA.PhasicMax_z, color = mediansplit_ground_valence))+
+  geom_point(size = 2, alpha = .6)+
+  geom_text(aes(label = stimDescription), alpha = .3)+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()+
+  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
+  # facet_grid(~mediansplit_ground_valence)+
+  # xlab("Average heart rate difference")+
+  ylab("Average pupil change (au)")+
+  p$graphstyle
+
+library(patchwork)
+patch_correlations <- correlation_plot+scater_pupil_HR+
+   plot_layout(ncol = 2)+plot_annotation(tag_levels = "A")
+patch_correlations
+ggsave("patch_correlations.tiff", patch_correlations, device = "tiff", width = 12, height = 5, dpi = 800)
+```

### 2021-09-07 Paper_Analyses_subj_obje_arousal.Rmd
a few new updates
- plots, checks

@@
 db_full4new_stim_screen_pupil_nopract$valence_c_sq<- db_full4new_stim_screen_pupil_nopract$valence**2
-polyyrelation<- lmer(arousal_c ~ valence_c+valence_c_sq+ (1|ssid) + (1|stimIAPS),
+polyyrelation <- lmer(arousal_c ~ valence_c+valence_c_sq+ (1|ssid) + (1|stimIAPS),
                      REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract)
+
+summary(polyyrelation)
+
+polyyrelation1 <- lmer(arousal_c ~ valence_c + (1|ssid) + (1|stimIAPS),
+                     REML = FALSE,
+                     data = db_full4new_stim_screen_pupil_nopract)
+
+polyyrelation3 <- lmer(arousal_c ~ valence_c_sq+ (1|ssid) + (1|stimIAPS),
+                     REML = FALSE,
+                     data = subset(db_full4new_stim_screen_pupil_nopract, )
+
+summary(polyyrelation)
+summary(polyyrelation)
+
+MuMIn::r.squaredGLMM(polyyrelation)
+MuMIn::r.squaredGLMM(polyyrelation1)
+MuMIn::r.squaredGLMM(polyyrelation3)
+
+anova(polyyrelation3, polyyrelation, polyyrelation1)
+
+db_full4new_stim_screen_pupil_nopract%>%
+  subset(Group == "NT")%>%
+  mutate(ssid= as.numeric(ssid))%>%
+  subset(ssid = 20)%>%
+  ggplot(aes(valence_c, arousal_c, color = ssid))+
+  geom_point()+
+  stat_ellipse()+
+  stat_smooth()
+
 ```
@@
 nrow(testmatched_scr)
-testmatched_scr<- left_join(macthed_test, db_full4new_stim_screen_pupil_nopract_nt_304, by = "stimIAPS2")
+testmatched_scr<- right_join(macthed_test, db_full4new_stim_screen_pupil_nopract_nt_304, by = "stimIAPS2")
 
@@
                  REML = FALSE,
-                 data = db_full6new_hr_fix_stim_nt1.1)
+                 data = subset(db_full6new_hr_fix_stim_nt1.1, Bio_Mean_HR_dif_outl!= "outlier"))
 
 summary(inter_bio1)
+# MuMin::
 
@@
                  REML = FALSE,
-                 data = db_full6new_hr_fix_stim_nt1.1)
-
+                 data = subset(db_full6new_hr_fix_stim_nt1.1, Bio_Mean_HR_dif_outl!= "outlier"))
+
+db_full6new_hr_fix_stim_nt1.1$log_BIO_CDA.PhasicMax<- log1p(db_full6new_hr_fix_stim_nt1.1$BIO_CDA.PhasicMax+.1)
 summary(inter_bio2)
@@
 ?gather
+
+unique(db_full6new_hr_fix_stim_nt1.1$ssid)
 
@@
   geom_line(aes(group = ssid), se = F)+
-  stat_summary(geom = 'pointrange')
+  stat_summary(geom = 'pointrange')+
+  geom_hline(yintercept = 0, size = 1.5, linetype = "dashed")+
+  p$graphstyle
+
+db_full6new_hr_fix_stim_nt1.1 %>%
+  mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
+  subset(!is.na(stimIAPS))%>%
+  group_by(stimIAPS)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ungroup()%>%
+  # group_by(stimIAPS)%>%
+  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"))%>%
+  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"))%>%
+  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"))%>%
+  select(c(stimIAPS, cor_hr_pup, cor_hr_scr, cor_pup_scr))%>%
+  gather(key, value, -stimIAPS)%>%
+  group_by(stimIAPS, key, value)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(key, value))+
+  geom_hline(yintercept = 0, size = 1.5, linetype = "dashed")+
+  geom_jitter(width = .1, alpha = .1)+
+  geom_line(aes(group = stimIAPS), se = F)+
+  stat_summary(geom = 'pointrange')+
+  # ggpubr::stat_compare_means(paired = FALSE)+
+  p$graphstyle
+
+db_full6new_hr_fix_stim_nt1.1 %>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(Bio_Mean_HR_dif, pup_basCor))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()
+
+db_full6new_hr_fix_stim_nt1.1 %>%
+  group_by(ssid)%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(Bio_Mean_HR_dif, pup_basCor))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()
+
+db_full6new_hr_fix_stim_nt1.1 %>%
+  group_by(stimIAPS)%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(Bio_Mean_HR_dif, pup_basCor))+
+  geom_point()+
+  geom_smooth(method = 'lm', se = F)+
+  ggpubr::stat_cor()
 

### 2021-09-09 Figures.Rmd
graphical updates

@@
   xlab("Subjective valence (z)")+
-  ylab(expression(Delta*" heart rate (bpm)"))
-    p$graphstyle+ylim(-4,1)
-  # ggpubr::stat_cor()
+  ylab(expression(Delta*" heart rate (bpm)"))+
+    # p$graphstyle+ylim(-4,1)+
+  ggpubr::stat_cor(label.y = -1)
 
@@
 ```
+
+supplemental
+
+unique(db_full4new_stim_screen_pupil_nopract$ssid)
+
+```{r}
+
+fix_dur_byval<-
+db_full4new_stim_screen_pupil_nopract %>%
+  subset(pp_arousal_outler== FALSE)%>%
+  subset(Group == "NT")%>%
+  subset(pupil_outlier == FALSE)%>%
+  subset(!is.na(Alexithymia))%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
+  group_by(ssid, mediansplit_ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
+  ggplot(aes(mediansplit_ground_valence, mean_fix_dur))+
+  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
+      geom_jitter(width = .1, alpha=.2)+
+  stat_summary(geom = 'pointrange',  size = 1, colour = "Black") +
+  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
+  geom_line(aes(group = ssid), alpha = .1)+
+  p$graphstyle+
+  xlab("Valence")+
+  ylab("Average fixation duration (ms)")+
+  # ylab("Baseline corrected pupil")+
+
+  scale_color_brewer(palette = "Dark2")+
+   scale_fill_brewer(palette = "Dark2")+
+  ggpubr::stat_compare_means(method = "t.test", paired =  TRUE)
+  # facet_grid(~mediansplit_ground_valence)+
+  # ylim(-3.3,1.3)
+
+? ggpubr::stat_compare_means
+fix_dur_byval
+
+fix_dur_byval<-
+db_full4new_stim_screen_pupil_nopract %>%
+  subset(pp_arousal_outler== FALSE)%>%
+  subset(Group == "NT")%>%
+  subset(pupil_outlier == FALSE)%>%
+  subset(!is.na(Alexithymia))%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
+  group_by(ssid, mediansplit_ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
+  ggplot(aes(mediansplit_ground_valence, mean_fix_dur))+
+  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
+      geom_jitter(width = .1, alpha=.2)+
+  stat_summary(geom = 'pointrange', alpha = .1, size = 1, colour = "Black") +
+  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
+  geom_line(aes(group = ssid), alpha = .1)+
+  p$graphstyle+
+  xlab("Valence")+
+  ylab("Average fixation duration (ms)")+
+  # ylab("Baseline corrected pupil")+
+
+  scale_color_brewer(palette = "Dark2")+
+   scale_fill_brewer(palette = "Dark2")+
+  ggpubr::stat_compare_means(method = "t.test", paired =  TRUE)
+  # facet_grid(~mediansplit_ground_valence)+
+
+fix_dur_count<- db_full4new_stim_screen_pupil_nopract %>%
+  subset(pp_arousal_outler== FALSE)%>%
+  subset(Group == "NT")%>%
+  subset(pupil_outlier == FALSE)%>%
+  subset(!is.na(Alexithymia))%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
+  group_by(ssid, mediansplit_ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
+  ggplot(aes(mediansplit_ground_valence, fix_count))+
+  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
+      geom_jitter(width = .1, alpha=.2)+
+  stat_summary(geom = 'pointrange', size = 1, colour = "Black") +
+  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
+  geom_line(aes(group = ssid), alpha = .1)+
+  p$graphstyle+
+  xlab("Valence")+
+  ylab("Average fixation count")+
+  # ylab("Baseline corrected pupil")+
+
+  scale_color_brewer(palette = "Dark2")+
+   scale_fill_brewer(palette = "Dark2")+
+  ggpubr::stat_compare_means(method = "t.test", paired =  TRUE)
+
+# data loss
+loss_dur_byval<- db_full4new_stim_screen_pupil_nopract %>%
+  subset(pp_arousal_outler== FALSE)%>%
+  subset(Group == "NT")%>%
+  subset(pupil_outlier == FALSE)%>%
+  subset(!is.na(Alexithymia))%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
+  group_by(ssid, mediansplit_ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
+  ggplot(aes(mediansplit_ground_valence, 1-gaze_valid_prop))+
+  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
+      geom_jitter(width = .1, alpha=.2)+
+  stat_summary(geom = 'pointrange', size = 1, colour = "Black") +
+  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
+  geom_line(aes(group = ssid), alpha = .1)+
+  p$graphstyle+
+  xlab("Valence")+
+  ylab("Average gaze loss (prop)")+
+  # ylab("Baseline corrected pupil")+
+
+  scale_color_brewer(palette = "Dark2")+
+   scale_fill_brewer(palette = "Dark2")+
+  ggpubr::stat_compare_means(method = "t.test", paired =  TRUE)
+
+gaze_control <- fix_dur_byval+fix_dur_count+
+loss_dur_byval
+
+ggsave("gaze_control.tiff",gaze_control, device = "tiff", width = 12, height = 6, dpi = 800)
+```

### 2021-09-09 Paper_Analyses_subj_obje_arousal.Rmd
graphical updates

@@
 
+db_full6new$bio_cda.n
 db_full6new_hr_fix_stim <- subset(db_full6new, screencontent_no <3)
@@
 
+db_full6new_hr_fix_stim$bio_cda.n
 db_full6new_hr_fix_stim_nt<- subset(db_full6new_hr_fix_stim, Group == "NT")
@@
 
+table(is.na(db_HR_bio_final_346_355_withfix_stim$BIO_CDA.nSCR))
+
+unique(db_HR_bio_final_346_355_withfix_stim$ssid)
 db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR_fix<- if_else(db_HR_bio_final_346_355_withfix_stim$screencontent_no ==1, db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR, NULL)
@@
 
+db_full6new_hr_fix_stim_nt$bio_cda.
 db_full6new_hr_fix_stim_nt1<- bind_rows(db_full6new_hr_fix_stim_nt,
@@
 # 348 to 355 are missing pratice
-
+table(is.na(db_full6new_hr_fix_stim_nt1$BIO_CDA.nSCR))
 db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1 %>%
@@
 # 2 1
-# stim - fix
+# stim - fix = positive stim> neg stim<
 db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1 %>%
@@
 
+table(is.na(db_full6new_hr_fix_stim_nt1.1$BIO_CDA.nSCR))
 inter_bio2<- lmer(log1p(BIO_CDA.PhasicMax+.1)~ Bio_Mean_HR_dif + pup_basCor + (1|ssid)+ 
@@
                  REML = FALSE,
-                 data = subset(db_full6new_hr_fix_stim_nt1.1, Bio_Mean_HR_dif_outl!= "outlier"))
+                 data = subset(db_full6new_hr_fix_stim_nt1.1$BIO_CDA.nSCR, Bio_Mean_HR_dif_outl!= "outlier"))
 
@@
 
+clustering3$
 cluster_lmers$scr_clust2 <- lmer(log_BIO_CDA.PhasicMax ~ y_kmeans + 

### 2021-09-09 Figures.Rmd
links

--- 2021-09-07 Figures.Rmd
@@
 ```
+
+supplemental
+
+unique(db_full4new_stim_screen_pupil_nopract$ssid)
+
+```{r}
+
+fix_dur_byval<-
+db_full4new_stim_screen_pupil_nopract %>%
+  subset(pp_arousal_outler== FALSE)%>%
+  subset(Group == "NT")%>%
+  subset(pupil_outlier == FALSE)%>%
+  subset(!is.na(Alexithymia))%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
+  group_by(ssid, mediansplit_ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
+  ggplot(aes(mediansplit_ground_valence, mean_fix_dur))+
+  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
+      geom_jitter(width = .1, alpha=.2)+
+  stat_summary(geom = 'pointrange',  size = 1, colour = "Black") +
+  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
+  geom_line(aes(group = ssid), alpha = .1)+
+  p$graphstyle+
+  theme(axis.text.x = element_text(size = 14, angle = 45), axis.title.x = element_blank())+
+  xlab("Valence")+
+  ylab("Average fixation duration (ms)")+
+  # ylab("Baseline corrected pupil")+
+
+  scale_color_brewer(palette = "Dark2")+
+   scale_fill_brewer(palette = "Dark2")+
+  ggpubr::stat_compare_means(method = "t.test", paired =  TRUE)
+  # facet_grid(~mediansplit_ground_valence)+
+  # ylim(-3.3,1.3)
+
+? ggpubr::stat_compare_means
+fix_dur_byval
+
+fix_dur_byval<-
+db_full4new_stim_screen_pupil_nopract %>%
+  subset(pp_arousal_outler== FALSE)%>%
+  subset(Group == "NT")%>%
+  subset(pupil_outlier == FALSE)%>%
+  subset(!is.na(Alexithymia))%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
+  group_by(ssid, mediansplit_ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
+  ggplot(aes(mediansplit_ground_valence, mean_fix_dur))+
+  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
+      geom_jitter(width = .1, alpha=.2)+
+  stat_summary(geom = 'pointrange', alpha = .1, size = 1, colour = "Black") +
+  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
+  geom_line(aes(group = ssid), alpha = .1)+
+  p$graphstyle+
+  theme(axis.text.x = element_text(size = 14, angle = 45), axis.title.x = element_blank())+
+  xlab("Valence")+
+  ylab("Average fixation duration (ms)")+
+  # ylab("Baseline corrected pupil")+
+
+  scale_color_brewer(palette = "Dark2")+
+   scale_fill_brewer(palette = "Dark2")+
+  ggpubr::stat_compare_means(method = "t.test", paired =  TRUE)
+  # facet_grid(~mediansplit_ground_valence)+
+
+fix_dur_count<- db_full4new_stim_screen_pupil_nopract %>%
+  subset(pp_arousal_outler== FALSE)%>%
+  subset(Group == "NT")%>%
+  subset(pupil_outlier == FALSE)%>%
+  subset(!is.na(Alexithymia))%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
+  group_by(ssid, mediansplit_ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
+  ggplot(aes(mediansplit_ground_valence, fix_count))+
+  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
+      geom_jitter(width = .1, alpha=.2)+
+  stat_summary(geom = 'pointrange', size = 1, colour = "Black") +
+  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
+  geom_line(aes(group = ssid), alpha = .1)+
+  p$graphstyle+
+    theme(axis.text.x = element_text(size = 14, angle = 45), axis.title.x = element_blank())+
+  xlab("Valence")+
+  ylab("Average fixation count")+
+  # ylab("Baseline corrected pupil")+
+
+  scale_color_brewer(palette = "Dark2")+
+   scale_fill_brewer(palette = "Dark2")+
+  ggpubr::stat_compare_means(method = "t.test", paired =  TRUE)
+
+# data loss
+loss_dur_byval<- db_full4new_stim_screen_pupil_nopract %>%
+  subset(pp_arousal_outler== FALSE)%>%
+  subset(Group == "NT")%>%
+  subset(pupil_outlier == FALSE)%>%
+  subset(!is.na(Alexithymia))%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
+  group_by(ssid, mediansplit_ground_valence)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # group_by(mediansplit_ground_valence)%>%
+  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
+  ggplot(aes(mediansplit_ground_valence, 1-gaze_valid_prop))+
+  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
+      geom_jitter(width = .1, alpha=.2)+
+  stat_summary(geom = 'pointrange', size = 1, colour = "Black") +
+  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
+  geom_line(aes(group = ssid), alpha = .1)+
+  p$graphstyle+
+  theme(axis.text.x = element_text(size = 14, angle = 45), axis.title.x = element_blank())+
+  xlab("Valence")+
+  ylab("Average gaze loss (prop)")+
+  # ylab("Baseline corrected pupil")+
+
+  scale_color_brewer(palette = "Dark2")+
+   scale_fill_brewer(palette = "Dark2")+
+  ggpubr::stat_compare_means(method = "t.test", paired =  TRUE)
+
+library(patchwork)
+gaze_control <- fix_dur_byval+fix_dur_count+
+loss_dur_byval
+
+https://lvdmaaten.github.io/tsne/
+
+ggsave("gaze_control.tiff",gaze_control, device = "tiff", width = 13, height = 6, dpi = 800)
+https://www.r-bloggers.com/2017/09/multi-dimensional-reduction-and-visualisation-with-t-sne/
+  https://cran.r-project.org/web/packages/Rtsne/Rtsne.pdf
+https://uc-r.github.io/kmeans_clustering
+```
+
+3dplots
+```{r}
+clustering_agg_JASP
+clustering_agg_JASPtest
+
+clustering_agg_noflood$log_Bio_CDA.PhasicMax_z<- scale(clustering_agg_noflood$log_BIO_CDA.PhasicMax)
+
+clustering_agg_noflood$Bio_Mean_HR_dif_z<- scale(clustering_agg_noflood$Bio_Mean_HR_dif)
+
+clustering_agg_noflood$pup_basCor_z<- scale(clustering_agg_noflood$pup_basCor)
+
+clustering_agg_noflood<- subset(clustering_agg, stimDescription != "Flood")
+car::scatter3d(clustering_agg_noflood$log_Bio_CDA.PhasicMax_z, 
+          clustering_agg_noflood$Bio_Mean_HR_dif_z, 
+          clustering_agg_noflood$pup_basCor_z,
+          fit = "smooth",
+          point = FALSE,
+          ellipsoid = TRUE,
+          surface = FALSE,
+          groups = clustering_agg_noflood$y_kmeans,
+          point.col = clustering_agg_noflood$y_kmeans
+          )
+
+car::scatter3d(clustering_agg_noflood$log_Bio_CDA.PhasicMax_z, 
+          clustering_agg_noflood$Bio_Mean_HR_dif_z, 
+          clustering_agg_noflood$pup_basCor_z,
+          fit = "smooth",
+          point = FALSE,
+          # ellipsoid = TRUE,
+          surface = FALSE,
+          groups = clustering_agg_noflood$y_kmeans,
+          point.col = clustering_agg_noflood$y_kmeans
+          )
+
+# clustering_agg_JASP$clusters<- as.factor(clustering_agg_JASP$clusters)
+
+clustering_agg_JASPtest$HR<-clustering_agg_JASPtest$Bio_Mean_HR_dif
+clustering_agg_JASPtest$SCR<-clustering_agg_JASPtest$log_Bio_CDA.PhasicMax_z
+clustering_agg_JASPtest$Pupil<-clustering_agg_JASPtest$pup_basCor_z
+
+SCR<- clustering_agg_JASPtest$SCR
+HR<- clustering_agg_JASPtest$HR
+Pupil<- clustering_agg_JASPtest$Pupil
+Cluster<- clustering_agg_JASPtest$clusters
+
+car::scatter3d(SCR, 
+          HR, 
+          Pupil,
+          # fit = "smooth",
+          point = TRUE,
+          ellipsoid = TRUE,
+          surface = FALSE,
+          groups = Cluster,
+          point.col = Cluster
+          )
+
+car::scatter3d(clustering_agg_JASPtest$log_Bio_CDA.PhasicMax_z, 
+          clustering_agg_JASPtest$Bio_Mean_HR_dif, 
+          clustering_agg_JASPtest$pup_basCor,
+          fit = "smooth",
+          point = TRUE,
+          # ellipsoid = TRUE,
+          # surface = FALSE,
+          groups = Cluster,
+          point.col = Cluster
+          )
+
+car::scatter3d(SCR, 
+          HR, 
+          Pupil,
+          fit = "smooth",
+          point = TRUE,
+          ellipsoid = TRUE,
+          surface = FALSE,
+          groups = Cluster,
+          point.col = Cluster
+          )
+?car::scatter3d
+car::scatter3d(SCR, 
+          HR, 
+          Pupil,
+          fit = "smooth",
+          point = TRUE,
+          # ellipsoid = TRUE,
+          surface = FALSE,
+          groups = Cluster,
+          point.col = Cluster
+          )
+```

### 2021-09-09 Paper_Analyses_subj_obje_arousal.Rmd
links

@@
 
-db_full4new_stim_screen_pupil_nopract%>%
+db_full4new_stim_screen_pupil_nopract %>%
   subset(Group == "NT")%>%
@@
 summary(pupil_arousal_findings$BIO_CDA.PhasicMax)
+
+sjplot::tab_model(pupil_arousal_findings$BIO_CDA.PhasicMax)
 anova(pupil_arousal_findings$arousal_phas_max)
@@
 
+unique(db_full6new_hr_fix_stim_nt1.1$ssid)
+db_full6new_hr_fix_stim_nt1.1
 car::scatter3d(x = db_full6new_hr_fix_stim_nt1.1$pup_basCor, 
@@
 colnames(clustering_agg)
-clust_dataset = clustering_agg[c(25,24,20)]
+clust_dataset = clustering_agg_noflood[c(25,24,20)]
 
@@
 # Fitting K-Means to the dataset
-set.seed(1)
+set.seed(25)
 kmeans = kmeans(x = clust_dataset, centers = 3)
@@
 ```{r}
-clustering_agg$y_kmeans<- y_kmeans
+clustering_agg_noflood$y_kmeans<- y_kmeans
 
@@
 View(clustering_agg)
-clustering_agg$y_kmeans<- as.factor(as.character(clustering_agg$y_kmeans))
+clustering_agg_noflood$y_kmeans<- as.factor(as.character(clustering_agg_noflood$y_kmeans))
 
@@
           fit = "smooth",
-          point = FALSE,
+          point = TRUE,
           # ellipsoid = TRUE,
-          # surface = FALSE,
+          surface = FALSE,
           groups = clustering_agg$y_kmeans,

### 2021-09-14 IAPS_PREPROCESSING_2021_1_56_357_611_616.Rmd
idk

--- 2021-09-01 IAPS_PREPROCESSING_2021_1.Rmd
@@
 
-hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021"
+hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021/346_357_611_616"
+
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021/346_357_611_616")
 
@@
   }
-   f = 30
+   # f = 30
   for (f in 1:length(hdfFilesList)) {
@@
 
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/Step1_GpExtractor_Output/346-355")
+# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/Step1_GpExtractor_Output/346-355")
+
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/Step1_GpExtractor_Output/356_357_611_616")
 
@@
 
+tmp.df2$ssid[tmp.df2$ssid == 311] <- 611
+tmp.df2$ssid[tmp.df2$ssid == 312] <- 357
+unique(tmp.df2$ssid)
+
 table(is.na(tmp.df2$ssid))
@@
 
+unique(tmp.df2$ssid)
+
+unique(db_beh2$ssid)
+
 ```
@@
 
-range(tmp.df, na.rm = TRUE)
+# range(tmp.df, na.rm = TRUE)
 tmp.df2$y_outside<-NULL
@@
 max(tmp.df3$timerezero, na.rm = TRUE) # max shoudl be around 120s for 2 mnutes
-natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)
+# natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)
 
@@
 
+# rest
 ggplot(subset(tmp.df3, tmp.df3$tNo == -7) , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
@@
 
+tmp.df3$gsr_ms[tmp.df3$gsr_ms == "Inf"]<-NA
+
 # gsr for leda
 colnames(tmp.df3)
-db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49,51 ))
+db_GSR_backup<- db_GSR
+db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49,51,52 ))
 db_GSR$tNo<- NULL
+colnames(db_GSR_backup)
+# unique(db_GSR_backup$trigger)
 colnames(db_GSR)
@@
 setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021")
+
+# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/Step1_GpExtractor_Output/356_357_611_616")
 
@@
 # plot diagnosis
+# takes a bit - 
 ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
@@
 
+# plotting rest
  ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
@@
 
+ # just stim
 ggplot(subset(tmp.df3, tmp.df3$screencontent == 'stim') , aes(x = timerezero3, y= gsr_basCor, olour = as.factor(ssid)))+
@@
 
+range(tmp.df3$gsr_basCor)
 tmp.df3 <- tmp.df3 %>%
     group_by(ssid, tNo, gsr_resp_Log )%>%
-    mutate(gsr_response =   max(gsr_basCor))
-
+    mutate(gsr_response = max(gsr_basCor, na.rm = TRUE))
+
+range(tmp.df3$gsr_response, na.rm = TRUE)
+unique(tmp.df3$gsr_response, na.rm = TRUE)
+
+tmp.df3$gsr_response[tmp.df3$gsr_response == "-Inf"]<- NA
 # gsr response for every bit
@@
 
-# note that smothing and interpolating is order dependednt so order by ssid, trial and time
+# note that smothing and interpolating is order dependent so order by ssid, trial and time
 tmp.df3<- tmp.df3 %>%
@@
 tmp.df3$subject<- tmp.df3$ssid
-tmp.df3$trial = tmp.df3$trialUnq
+tmp.df3$trial <- tmp.df3$trialUnq
 
@@
 
-subset(tmp.df3, tNo == 20 & ssid == 347)%>%
+subset(tmp.df3, tNo == 20 & ssid == 357)%>%
 ggplot(aes(x = timerezero3, y= pup_interp))+
@@
 
-subset(tmp.df3, tNo == -7 & ssid == 350)%>%
+subset(tmp.df3, tNo == -7 & ssid == 357)%>%
 ggplot(aes(x = timerezero3, y= pupil))+
@@
 
+range(max_pup$MAD)
+range(max_pup$speed)
+table(is.infinite(max_pup$MAD))
+tmp.df3_backup<- tmp.df3
+
 tmp.df3<- max_pup
@@
 
-ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
+  subset(tmp.df3,  tNo == 10 & ssid == 357)%>%
+ggplot(aes(x = timerezero3, y= pup_basCor))+
     # geom_smooth(se = F)+
   geom_line()+
+    geom_line(aes(y =pup_interp_mad), color = "red")+
     geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
@@
 tmp.df3<- tmp.df3%>%
-  # arrange(ssid, time, tNo)%>%
+  arrange(ssid, time, tNo)%>%
   group_by(ssid, tNo,screencontent)%>%
@@
   min(tmp.df3$hr, na.rm = TRUE)
-ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 352) , aes(x = timerezero3, y= hr_interp))+
+ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 611) , aes(x = timerezero3, y= hr_interp))+
     # geom_smooth(se = F)+
@@
 # check to see this is right
-ggplot(subset(tmp.df4, tmp.df3$ssid == 353) , aes(x = tNo, y= hr_valid_prop))+
+ggplot(subset(tmp.df4, tmp.df3$ssid == 615) , aes(x = tNo, y= hr_valid_prop))+
     # geom_smooth(se = F)+
@@
 
-ggplot(subset(tmp.df4, tmp.df3$ssid == 354) , aes(x = tNo, y= gaze_valid_prop))+
+ggplot(subset(tmp.df4, tmp.df3$ssid == 356) , aes(x = tNo, y= gaze_valid_prop))+
     # geom_smooth(se = F)+
@@
 colnames(tmp.df4)
-write_csv(tmp.df4, 'interodata_clean_gp_346_355.csv')
+# write_csv(tmp.df4, 'interodata_clean_gp_346_355.csv')
+
+write_csv(tmp.df4, 'interodata_clean_gp_356_357_611_616.csv')
 
@@
 unique(tmp.df4$tNo)
+unique(tmp.df4$ssid)
 
@@
 
-write_csv(tmp.df4_sum, 'intero_aggdata_clean.csv')
-
-write_csv(tmp.df4_sum, 'intero_aggdata_clean_3046_355.csv')
+# write_csv(tmp.df4_sum, 'intero_aggdata_clean.csv')
+
+# write_csv(tmp.df4_sum, 'intero_aggdata_clean_3046_355.csv')
+write_csv(tmp.df4_sum, 'interodata_clean_gp_356_357_611_616.csv')
+
+# interodata_clean_gp_356_357_611_616.csv
 # 
@@
   geom_line()
+
+# 616 seesm to have vey poor data fr eyetracking - exclude
 
@@
 
+  for_gazepath<- subset(for_gazepath, ssid!= 616)
+
   for_gazepath$screencontent[for_gazepath$screencontent == 'rest1']<- 'fixation'
@@
   colnames(for_gazepath)
+  unique(for_gazepath$ssid)
 
@@
 
-  setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/346_355")
+  # setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/346_355")
+
+  setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/356_357_611_615")
 
@@
 
-right eye x coord: right_gaze__cor_pix
-right eye y coord: right_gaze_x_cor_pix
+right eye x coord: right_gaze_x_cor_pix
+right eye y coord: right_gaze_y_cor_pix
 didtance: distance (mm)
@@
 ```{r}
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/356_357_611_615")
+
 read_parsed <- function(flnm) {
@@
 
+db_parsed_backup<- db_parsed
+
 db_parsed <- list.files(pattern = "*.csv", 
@@
 db_parsed$ssid<- substr(db_parsed$Participant, 4,6)
+unique(db_parsed$ssid)
 
@@
 # this might be needed for tempoal analisys
-write_csv(db_parsed, 'db_parsed.csv')
-write_csv(db_parsed, 'db_parsed_346_355.csv')
+# write_csv(db_parsed, 'db_parsed.csv')
+# write_csv(db_parsed, 'db_parsed_346_355.csv')
+write_csv(db_parsed, 'db_parsed_356_357_611_615.csv')
 
@@
 
-View(db_parsed)
+# View(db_parsed)
 
@@
 # View(db_parsed_summarised2)
-write_csv(db_parsed_summarised2, 'db_parsed_summarised.csv')
-write_csv(db_parsed_summarised2, 'db_parsed_summarised_346_355.csv')
+# write_csv(db_parsed_summarised2, 'db_parsed_summarised.csv')
+# write_csv(db_parsed_summarised2, 'db_parsed_summarised_346_355.csv')
+write_csv(db_parsed_summarised2, 'db_parsed_summarised_356_357_611_615.csv')
 
@@
 # tmp.df4_sum_full<- left_join(tmp.df4_sum_full,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent")) #original
+
+unique(tmp.df4_sum$ssid)
+tmp.df4_sum_full_backup<- tmp.df4_sum_full
 
@@
 tmp.df4_sum_full
+
+tmp.df4_sum_full<- tmp.df4_sum_full%>%
+  arrange(ssid, tNo, screencontent_no)
+tmp.df4_sum_full
 ```
@@
 library(purrr)
+
+# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/IAPSBehav/346_355")
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/IAPSBehav/356_357_611_616")
 
@@
 
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/IAPSBehav/346_355")
 # now read them
+db_beh_backup<- db_beh
+
 db_beh <-
@@
 
+unique(db_beh$filename)
+
+```
+
 # problem file
+
 # db328$condition<-db328$ï..condition
@@
 
+```{r}
+
 db_beh<- select(db_beh, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
@@
 
-db328<- select(db328, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
-                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
-
-# 
+# db328<- select(db328, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
+#                                      "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
+
 # db304<- rbindlist(sapply(files, fread, simplify = FALSE),
@@
 
-# problem
+```
+
+# problem file
 db328$filename<- as.character(db328$filename)
@@
 db_beh2<- bind_rows(db_beh2, db328)
+
+```{r}
 
@@
 unique(db_beh2$tNo)
+
 db_beh2<- subset(db_beh2, is.na(db_beh2$tNo) == FALSE)
@@
 
-colnames(db_beh3_301_309)
+# colnames(db_beh3_301_309)
 
 db_beh3$trigger<-NULL
-db_beh3_301_309$triggeracq<- NULL
-
-db_beh3_301_309$condition[db_beh3_301_309$condition == "Example Stimuli"]<- "Practice"
+# db_beh3_301_309$triggeracq<- NULL
+
+# db_beh3_301_309$condition[db_beh3_301_309$condition == "Example Stimuli"]<- "Practice"
 
@@
 
+```
+Probem file
 # db_beh3$triggeracq<- NULL
@@
 library(readr)
-db_beh300 <-  read_csv("300-309 beh/tmp.df4300_sum_full.csv")
-View(tmp_df4300_sum_full)
-
-db_beh300 <- subset(db_beh300, db_beh300$condition != "Rest")
-colnames(db_beh300)
+
+# db_beh300 <-  read_csv("300-309 beh/tmp.df4300_sum_full.csv")
+# View(tmp_df4300_sum_full)
+
+# db_beh300 <- subset(db_beh300, db_beh300$condition != "Rest")
+# colnames(db_beh300)
 
@@
 db_beh300<- select(db_beh300, c("condition", "stimIAPS","stimDescription","ValenceMean", "ArousalMean", "ssid", "valence","arousal","valence_rt","arousal_rt", "tNo"))
+
+```{r}
 
@@
 
-db_beh3$ssid <- as.numeric(db_beh3$ssid)
 # rm(tmp.df4_sum_full_t)
@@
 
+```
+
+```{r}
+db_beh3$ssid <- as.numeric(db_beh3$ssid)
+
+tmp.df4_sum_full_backup_before_beh<- tmp.df4_sum_full
+
 tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_beh3, by = c('ssid', 'tNo'))
@@
 
+unique(tmp.df4_sum_full$ssid)
+
+tmp.df4_sum_full
 ```
@@
 STAI:: 5nzr
-AQ:7uqw
+AQ:
 STAIS: 8rfo
@@
 library(readxl)
+db_selfrep_backup<- db_selfrep
 db_selfrep <- read_excel("db_self_rep_345_356_final.xlsx")
+
+library(readr)
+
+db_selfrep <- read_csv("db_self_rep_356_357_611_616_final.csv")
+View(db_selfrep)
 # View(db_self_rep_345_356_final)
+colnames(db_selfrep)
 
 db_selfrep$ssid <- as.character(db_selfrep$`Participant No`)
+
 tmp.df4_sum_full$ssid <- as.character(tmp.df4_sum_full$ssid)
+
+unique(db_selfrep$ssid )
+
+tmp.df4_sum_full_backup_before_selfrep<- tmp.df4_sum_full
+db_selfrep$`Participant Private ID.x.x`<- NULL
 
@@
 write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_345_356.csv')
-
+write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_356_357_611_616.csv')
 # tmp.df4_sum_full<- tmp.df4_sum_full%>%
 #   arrange(ssid, tNo, screencontent_no)
-
+unique(tmp.df4_sum_full$ssid)
 colnames(tmp.df4_sum_full)
+
+db_selfrep
 ```
@@
 
+>> Ledalab('/Users/heliocuve/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021/3052_356/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2])
+
+>> Ledalab('/Users/heliocuve/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/356_457_611_616/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2])
+
+>> Ledalab('/Users/heliocuve/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/ledalab-349/', 'open','biopac','downsample', 200, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2]
+
 ```{r}
 setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021/Processed")
+
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/356_457_611_616/Processed")
 
@@
 # now read them
+
+db_leda_backup<- db_leda
+
 db_leda <-
@@
 db_leda$ssid<- as.numeric(substr(db_leda$filename, 13,15))
-
+unique(db_leda$ssid)
 colnames(tmp.df4_sum)
@@
 colnames(tmp.df4_sum)
+
+tmp.df4_sum2_backup<- tmp.df4_sum2
 
@@
 
+db_leda2_backup<- db_leda2
+
 db_leda2<- subset(db_leda, db_leda$trigger != -7)
@@
 
+nrow(tmp.df4_sum2)
 tmp.df4_sum_full<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
-
+nrow(tmp.df4_sum_full)
 # tmp.df4_sum_full<- bind_cols(tmp.df4_sum, db_leda)
+unique(tmp.df4_sum_full$ssid)
 
@@
 
-trigger<- db_leda2 %>%
-  subset(ssid == 348)%>%
-  select(order, Event.NID, trigger,Event.Nr)
+# trigger<- db_leda2 %>%
+#   subset(ssid == 348)%>%
+#   select(order, Event.NID, trigger,Event.Nr)
 ```
@@
 # check stiom screen
+tmp.df4_sum_full_stim_baclup<- tmp.df4_sum_full_stim
+
 tmp.df4_sum_full_stim<- subset(tmp.df4_sum_full,  tmp.df4_sum_full$screencontent == 'stim')
@@
 # is objective arousal and self report arousal correated
+tmp.df4_sum_full_stim
 tmp.df4_sum_full_stim$ValenceMean_cat<- if_else(tmp.df4_sum_full_stim$ValenceMean > 4, 'pos', 'neg')
@@
 
-```{r}
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/IAPS/processed/345_456/CDA")
+>> Ledalab('/Users/heliocuve/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/ledalab-349/', 'open','biopac','downsample', 200, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2]
+
+```{r}
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/IAPS/processed/356_357_611_616/CDABIO")
 
@@
 # now read them
+
+db_leda_bio_backup<- db_leda_bio
+
 db_leda_bio <-
@@
 
+view(db_leda_bio)
+
 write_csv(db_leda_bio, 'db_leda_bio.csv')
 write_csv(db_leda_bio, 'db_leda_bio_345_355_CDA.csv')
+write_csv(db_leda_bio, 'db_leda_bio_356_357_611_616 CDA.csv')
 
@@
 
+View(trigger)
+
   trigger$ssid<- NULL
+
+  nrow(db_leda_bio)
+
+  db_leda_bio_beforetrig<- db_leda_bio
 
@@
 
-db_leda_bio_backup<- db_leda_bio
+db_leda_bio_backup_beforename<- db_leda_bio
 
@@
 
-db_leda_bio$BIO_Event.NID<- NULL
-db_leda_bio$BIO_filename<- NULL
+db_leda_bio$BIO_Event.NID <- NULL
+db_leda_bio$BIO_filename <- NULL
+
+nrow(tmp.df4_sum_full)
+nrow(db_leda_bio)
+
+tmp.df4_sum_full_bio_backup<- tmp.df4_sum_full_bio
+tmp.df4_sum_full$ssid<- as.character(tmp.df4_sum_full$ssid)
 
@@
 setwd("~/OneDrive - Nexus365/InteroStudy2020/Data Collection 2019- 2020/2020/InteroStudyBIOPAC/IAPS/Processed/HR/345_355")
+
+setwd("~/OneDrive - Nexus365/InteroStudy2020/Data Collection 2019- 2020/2020/InteroStudyBIOPAC/IAPS/Processed/HR/356_357_611_616")
 library(readxl)
@@
 # now read them
+db_HR_bionew_backup<- db_HR_bionew
+
 db_HR_bionew <-
@@
 
-db_HR_bio<- db_HR_bionew
+db_HR_bio_backup<- db_HR_bio
 
@@
 
+# db_HR_bionew<- subset(db_HR_bionew,db_HR_bionew$`Stim-Response Analysis`!= "Stimulus 100")
+db_HR_bio<- db_HR_bionew
 # test<- subset(db_HR_bio, db_HR_bio$filename == "./607_IAPS_Physio_HR.xls")
@@
 db_HR_bio$ssid<- substr(db_HR_bio $filename, 3,5)
-
+unique(db_HR_bio$ssid)
 db_HR_bio$filename<- NULL
@@
 #  remove na in the mean heart rate
-
+# db_HR_bio$
 db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$...2))
@@
 
+unique(db_HR_bio$ssid)
 # test<- subset(db_HR_bio, grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
@@
 db_HR_bio<- subset(db_HR_bio, db_HR_bio$...2 != 'Mean(CH 40)')
+
 db_HR_bio$timestart<- db_HR_bio$`Stim-Response Analysis`
@@
 db_HR_bio<- db_HR_bio%>%
-  arrange((as.numeric(timestart)), ssid)
+  arrange(ssid,(as.numeric(timestart)))
 
@@
 db_HR_bio$trigger_200<- if_else(db_HR_bio$trigger> 103, TRUE, FALSE)
+table(db_HR_bio$trigger_200)
 
@@
 
-#subset(db_HR_bio, db_HR_bio$ssid!= 328)%>%
+# subset(db_HR_bio, db_HR_bio$ssid== 357)%>%
 #  group_by(timestart, ssid)%>%
- # mutate(EventNR= 1:225)
+# mutate(EventNR= 1:224)
 
@@
 # use this
-table(db_HR_bio1$ssid!= 328)
+# table(db_HR_bio1$ssid!= 328)
 db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)
@@
 
-db_HR_bio1no328$trigger<- db_HR_bio1no328$tNo
+unique(db_HR_bio1no328$tNo)
+# db_HR_bio1no328$trigger<- db_HR_bio1no328$tNo
 # db_HR_bio1no328
@@
 View(trigger)
-db_HR_bio1no328<- db_HR_bio1no328$t %>%
+
+db_HR_bio1no328<- db_HR_bio1no328 %>%
   group_by(ssid)%>%
@@
 
+```
+
 unique(db_HR_bio1no328$tNo)
@@
 
+View(db_HR_bio1no328)
 table(db_HR_bio1no328$tNo)
@@
 
+```{r}
+
 db_HR_bio1no328<- db_HR_bio1no328%>%
@@
 unique(db_HR_bio1no328$tNo)
+
+# unique(db_HR_bio2$tNo)
+
 ```
@@
 # db_HR_bio2<- bind_rows(db_HR_bio1no328,db_HR_bio328)
+db_HR_bio2_backup <- db_HR_bio2
+
 db_HR_bio2<-db_HR_bio1no328
@@
 colnames(db_HR_bio2)
+
 db_HR_bio2<- select(db_HR_bio2, c(timestart,Mean_HR, tNo, ssid,trigger2,trigger_200, trigger,stim,mhrtext))
@@
 db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)
+
+db_HR_bio2.1_backup<- db_HR_bio2.1
+
 db_HR_bio2.1<- db_HR_bio2 %>%
@@
   mutate(tNo =  1:n())
-   arrange(timestart,ssid)
+   # arrange(timestart,ssid)
   # subset(trigger == 100)
@@
 
-unique(db_HR_bio2.1$tNo-8)
+unique(db_HR_bio2.1_backup$tNo)
+
+table(db_HR_bio2.1$ssid)
+# 
+# test<- subset(db_HR_bio2.1, ssid == "357")
+# 
+# test$timestart
+# sort(as.numeric(substr(test$stim, 10,12)))
+# 
+# arrange(as.numeric(unique(test$stim)))
+# 
+# unique(db_HR_bio2.1$tNo-8)
 table(db_HR_bio2.1$tNo)
@@
 table(db_HR_bio2.1$tNo3)
-test352<- subset(db_HR_bio2.1, ssid == 352)
+table(db_HR_bio2.1_backup$tNo3)
+
+test352<- subset(db_HR_bio2.1, ssid == 356)
 test353<- subset(db_HR_bio2.1, ssid == 353)
@@
 
+```
+
+```{r}
 db_352 <- read_csv("352_Biohr_fixed.csv")
@@
 
-db_HR_bio2.3<- bind_rows(db_HR_bio2.2,db_352_353)
-nrow(db_HR_bio2.3)
+# db_HR_bio2.3<- bind_rows(db_HR_bio2.2,db_352_353)
+# nrow(db_HR_bio2.3)
+
+db_HR_bio2.3<- db_HR_bio2.2
+
 # order
@@
 table(db_HR_bio2.3.1$tNo)
-
+table(db_HR_bio2.3.1$ssid)
 # test<- subset(db_HR_bio2.3.1, ssid == "353")
@@
 str((db_HR_bio2.3.1))
+
 # str(db_biohrold2)
@@
 
+```
+
+```{r}
 # final
@@
 
+write_csv(db_HR_bio_final, 'db_HR_bio_final_356_357_611_616_withfix.csv')
+
 db_HR_bio_final$tNo
@@
 
-db_HR_bio1$tNo<- -6:49
-
-db_HR_bio_final$tNo<- if_else(as.numeric(db_HR_bio_final$tNo) < 0, as.numeric(db_HR_bio_final$tNo), as.numeric(db_HR_bio_final$tNo)+1)
-
-db_HR_bio_final$BIO
+# db_HR_bio1$tNo<- -6:49
+
+# db_HR_bio_final$tNo<- if_else(as.numeric(db_HR_bio_final$tNo) < 0, as.numeric(db_HR_bio_final$tNo), as.numeric(db_HR_bio_final$tNo)+1)
+# 
+# View(db_HR_bio_final)
+# db_HR_bio_final$BIO
 
@@
 tmp.df4_sum_full_bio$tNo3<- tmp.df4_sum_full_bio$tNo
+
+tmp.df4_sum_full_bio1_backup<- tmp.df4_sum_full_bio1
+
 tmp.df4_sum_full_bio1<- tmp.df4_sum_full_bio
@@
 
-table(is.na(tmp.df4_sum_full_bio_hr$Mean_HR))
-
-test<- subset(tmp.df4_sum_full_bio_hr, is.na(Mean_HR))
+# table(is.na(tmp.df4_sum_full_bio_hr$Mean_HR))
+# 
+# test<- subset(tmp.df4_sum_full_bio_hr, is.na(Mean_HR))
 
@@
 # remeber to do this otherwise tno will be matchjing wrong data
-db_HR_bio_final_norest$tNo<- db_HR_bio_final_norest$tNo3
-
+db_HR_bio_final_norest$tNo <- db_HR_bio_final_norest$tNo3
+
+tmp.df4_sum_full_bio_hr_backlup<- tmp.df4_sum_full_bio_hr
+
+nrow(tmp.df4_sum_full_bio)
 tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final_norest, by = c('ssid', 'tNo', 'screen_content'))
@@
 unique(tmp.df4_sum_full_bio_hr$tNo)
+unique(tmp.df4_sum_full_bio_hr$ssid)
 
@@
 View(db_selfrep)
-db_selfrep <- read_excel("db_self_rep_345_356_final.xlsx")
+db_selfrep_backup<- db_selfrep
+
+# db_selfrep <- read_excel("db_self_rep_345_356_final.xlsx")
+
+db_selfrep <- read_csv("db_self_rep_356_357_611_616_final.csv")
 
@@
 table(is.na(tmp.df4_sum_full_bio_hr$Mean_HR))
+
+tmp.df4_sum_full_bio_hr_backlup
+tmp.df4_sum_full_bio_hr_self_backup<- tmp.df4_sum_full_bio_hr_self
 
@@
 write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_bio_hr_self_345_356.csv')
+write_csv(tmp.df4_sum_full_bio_hr_self, 'tmp.df4_sum_full_bio_hr_self_356_357_611_616.csv')
 
@@
 tmp.df4_sum_full_bio_hr_self
+unique(db_parsed_summarised2$ssid)
+
 db_parsed_summarised2$ssid<- as.character(db_parsed_summarised2$ssid)
-
-tmp.df4_sum_full_bio_hr_self_parsed <- left_join(tmp.df4_sum_full_bio_hr_self, db_parsed_summarised2, 
+tmp.df4_sum_full_bio_hr_self_parsed_backup<- tmp.df4_sum_full_bio_hr_self_parsed
+
+tmp.df4_sum_full_bio_hr_self_parsed <- left_join(tmp.df4_sum_full_bio_hr_self, 
+                                                 db_parsed_summarised2, 
                              by = c("ssid", "trialUnq", "tNo", "screencontent"))
@@
 db_beh3$tNo <- as.character(db_beh3$tNo)
+
 tmp.df4_sum_full_bio_hr_self_parsed$tNo<- as.character(tmp.df4_sum_full_bio_hr_self_parsed$tNo)
@@
 
+tmp.df4_sum_full_bio_hr_self_parsed_beforebehav_backup<- tmp.df4_sum_full_bio_hr_self_parsed
+
+unique(db_beh3$ssid)
+
 tmp.df4_sum_full_bio_hr_self_parsed<- left_join(tmp.df4_sum_full_bio_hr_self_parsed, db_beh3, by = c('ssid', 'tNo'))
@@
 View(db_beh3)
+
 tmp.df4_sum_full<- tmp.df4_sum_full%>%
@@
 
-tmp.df4_sum_full_bio_hr_self_parsed<- tmp.df4_sum_full_bio_hr_self_parsed%>%
-  rename(IAS = IAS_score)%>%
-  rename(ASD_self = ASD)
+tmp.df4_sum_full_bio_hr_self_parsed<- tmp.df4_sum_full_bio_hr_self_parsed %>%
+  # rename(IAS = IAS_score)%>%
+  rename(ASD_self = `ASD-text`)
 
@@
 write_csv(tmp.df4, 'tmp.df4_timeseries_345_356.csv')
-```
+
+write_csv(tmp.df4_sum_full_bio_hr_self_parsed, 'tmp.df4_sum_full_bio_hr_self_parsed_356_357_611_616.csv')
+write_csv(tmp.df4, 'tmp.df4_timeseries_356_357_611_616.csv')
+```

### 2021-11-10 Paper_Analyses_subj_obje_arousal.Rmd
back to it
Today the goal is to run inferential PCAS and maybe BADIA

@@
 ```{r}
+unique(db_full4new_stim_screen_pupil_nopract$ssid)
 
@@
 tmp_df4_timeseries_345_356 <- read_csv("tmp.df4_timeseries_345_356.csv")
+
+unique(tmp_df4_timeseries_345_356$ssid)
 View(tmp_df4_timeseries_345_356)
@@
 
+colnames(db_HR_bio_final_346_355_withfix)
+
 # tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv
@@
 table(is.na(db_full6new_hr_fix_stim_nt1$BIO_CDA.nSCR))
+
 db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1 %>%
@@
 
+```
+
+```{r}
+
 db_full6new_hr_fix_stim_nt1.1 %>%
@@
   # group_by(ssid)%>%
-  mutate(Bio_Mean_HR_dif = abs(Bio_Mean_HR_dif))%>%
+  # mutate(Bio_Mean_HR_dif = abs(Bio_Mean_HR_dif))%>%
   group_by(ssid, stimIAPS)%>%
-  mutate(Bio_Mean_HR_dif_stim = abs(Bio_Mean_HR_dif))%>%
+  # mutate(Bio_Mean_HR_dif_stim = abs(Bio_Mean_HR_dif))%>%
   summarise_if(is.numeric, mean, na.rm = TRUE)%>%
@@
 
-  geom_smooth(aes(group = stimIAPS, y =Bio_Mean_HR_dif_stim), method=lm, se=FALSE, colour = "gray40", alpha = .01,linetype="dashed", size = .2 )+
+  geom_smooth(aes(group = stimIAPS, y =Bio_Mean_HR_dif), method=lm, se=FALSE, colour = "gray40", alpha = .01,linetype="dashed", size = .2 )+
   geom_smooth( method=lm, se=FALSE, linetype="dashed",
@@
   stat_summary(geom = 'pointrange', pch = 1)+
-    ggpubr::stat_cor()+
+    # ggpubr::stat_cor()+
 
@@
 p$graphstyle
+
+```
 

### 2021-11-10 Paper_Analyses_subj_obje_arousal.Rmd
Inferential PCA start

@@
                      REML = FALSE,
-                     data = subset(db_full4new_stim_screen_pupil_nopract, )
+                     data = subset(db_full4new_stim_screen_pupil_nopract ))
 
@@
 
-# macthed test
-
 ```
@@
 - decisions to make: do we average the responses per participant and cluster at a trial level - this ignores individual variability
-- what do we do with teh nested nature of teh data, one participant has multiple trials, if we don't accout for this, the cluster will treat data from different participants the same way.
-
-If create cluster on a ndividual level- then the issue is different participants will end up with different clusters and clusters for one person are not translaable.
+- what do we do with the nested nature of teh data, one participant has multiple trials, if we don't accout for this, the cluster will treat data from different participants the same way.
+
+If we create cluster on a individual level- then the issue is different participants will end up with different clusters and clusters for one person are not translatable.
 
@@
   facet_grid(~ as.factor(clusters))
-
-```
 
@@
 
-clustering3$
+View(clustering3)
 cluster_lmers$scr_clust2 <- lmer(log_BIO_CDA.PhasicMax ~ y_kmeans + 
@@
 
+View(clustering)
 clustering2<- subset(clustering, !is.na(stimDescription))
@@
 
+View(clustering2)
 colnames(clustering2)
@@
 ```
+
+PCA and barycentric
+
+```{r}
+
+```

### 2021-11-15 Paper_Analyses_subj_obje_arousal.Rmd
initial commit on BADIA

@@
 
+View(clustering)
+
 clustering$stimIAPS2<- substr(clustering$stimIAPS, 1,4)
@@
 library(readr)
+View(clustering_agg_JASP)
 clustering_agg_JASP <- read_csv("clustering_agg_JASP.csv")
@@
 clustering3<- left_join(clustering2, cluster_stim)
+nrow(clustering2)
+nrow(clustering3)
 
@@
 clustering_new$ssid<- as.factor(as.character(clustering_new$ssid))
-clustering3
+View(clustering_new)
 
@@
 
-```
+clustering
+clustering_agg
+clustering_agg_JASP
+clustering_agg2
+clustering
+
+clustering_new
+# clustering3 has problems
+
+# 1 dcast stim to columns
+
+colnames(clustering_new)
+colnames(clustering)
+
+db_forBADA1<- data.table::dcast(setDT(db_full6new_hr_fix_stim_select2_NT_no_outl_5), 
+                    ssid + TAS+AQ+Group ~ stimIAPS2, value.var = c('pup_basCor',
+                'Bio_Mean_HR_dif', 'log1p_BIO_CDA.PhasicMax', 'arousal', 'valence'))
+
+library(data.table)
+colnames(clustering_new)
+library(tidyverse)
+
+clustering_new_pre_PCA<- select(clustering_new, c(ssid, TAS, AQ, stimIAPS2, 
+                                                  pup_basCor,Bio_Mean_HR_dif,
+                                                  log_BIO_CDA.PhasicMax, arousal,
+                                                  valence))
+db_forPCA<- data.table::dcast(setDT(clustering_new_pre_PCA), 
+                    ssid + TAS+AQ ~ stimIAPS2, value.var = c('pup_basCor',
+                'Bio_Mean_HR_dif', 'log_BIO_CDA.PhasicMax', 'arousal', 'valence'))
+
+```

### 2021-11-15 Paper_Analyses_subj_obje_arousal.Rmd
filter out missigngness

@@
 ```{r}
+library(tidyverse)
+db_full6new_hr_fix_stim_nt1.1
 
@@
                       BIO_CDA.SCR, arousal, valence, ArousalMean, ValenceMean, stimIAPS, tNo, TAS, AQ, Age,
-                      gender, ssid, stimDescription))
+                      gender, ssid, stimDescription, fix_count, mean_fix_dur))
 
@@
 
-clustering_new_pre_PCA<- select(clustering_new, c(ssid, TAS, AQ, stimIAPS2, 
+# clustering_new$=
+# clustering
+clustering_new_pre_PCA<- select(clustering, c(ssid, TAS, AQ, stimIAPS2,
+                                              stimDescription, 
                                                   pup_basCor,Bio_Mean_HR_dif,
                                                   log_BIO_CDA.PhasicMax, arousal,
-                                                  valence))
+                                                  valence, fix_count, mean_fix_dur))
+
+clustering_new_pre_PCA
+
+clustering_new_pre_PCA$stim_descr<- paste0(clustering_new_pre_PCA$stimIAPS2, 
+                                           paste0(clustering_new_pre_PCA$stimDescription))
+
+clustering_new_pre_PCA$stim_descr
+
+clustering_new_pre_PCA
 db_forPCA<- data.table::dcast(setDT(clustering_new_pre_PCA), 
-                    ssid + TAS+AQ ~ stimIAPS2, value.var = c('pup_basCor',
-                'Bio_Mean_HR_dif', 'log_BIO_CDA.PhasicMax', 'arousal', 'valence'))
-
-```
+                    ssid + TAS+AQ ~ stim_descr, value.var = c('pup_basCor',
+                'Bio_Mean_HR_dif', 'log_BIO_CDA.PhasicMax', 'arousal', 'valence', 
+                'fix_count', 'mean_fix_dur'))
+
+View(db_forPCA)
+colnames(db_forPCA)
+
+# 
+# start with just physio stuff
+
+all.data<- db_forPCA
+
+# count NAS on the important variables
+# pupufirst(
+
+colnames(all.data[,61: (61+56)])
+all.data$per_ssid_pupil_loss_perc <- (rowSums(is.na(all.data[,4:60]))/56)*100 # pupil
+# rowSums(is.na(all.data[,4:60]))
+all.data$per_ssid_hr_loss_perc<-  (rowSums(is.na(all.data[,61: (61+56)]))/56)*100 # heart rate
+all.data$per_ssid_scr_loss_perc<- (rowSums(is.na(all.data[,(61+56):(61+56+56)]))/56)*100 # scr
+
+# columns
+
+cols_belowmissingthresh <- which(colSums(is.na(all.data))/nrow(all.data) < .8)
+  # all.data%>%
+colSums(is.na(all.data))/nrow(all.data)
+
+ncol(all.data)
+# select columsn that don't have a a lot of missingness
+all.data1<- all.data%>%
+  select(cols_belowmissingthresh)
+
+all.data$TAS_mediansplit<- if_else(all.data$TAS> median(all.data$TAS), "High", "Low")
+all.data$AQ_mediansplit<- if_else(all.data$AQ> median(all.data$AQ), "High", "Low")
+ # design
+var.design_asd <- as.factor(all.data$Group)
+var.design_aq <- as.factor(all.data$AQ_mediansplit)
+var.design_tas <- as.factor(all.data$TAS_mediansplit)
+colnames(all.data)
+
+var.data <- all.data[,c(6:172)]
+
+var.PCA.inf_asd <-InPosition::epPCA.inference.battery(var.data, 
+                                       scale = FALSE, 
+                                       center = FALSE, 
+                                       DESIGN = var.design_asd, 
+                                       make_design_nominal = TRUE, 
+                                       graphs = TRUE, k = 0, 
+                                       test.iters = 1000, 
+                                       constrained = FALSE, 
+                                       critical.value = 2)
+
+```

### 2021-11-15 Paper_Analyses_subj_obje_arousal.Rmd
initialise PCA with inference

@@
 
-all.data$TAS_mediansplit<- if_else(all.data$TAS> median(all.data$TAS), "High", "Low")
-all.data$AQ_mediansplit<- if_else(all.data$AQ> median(all.data$AQ), "High", "Low")
+View(all.data1)
+
+# exclude peope with more han 50% missign data
+
+all.data1$per_ssid_pupil_loss_perc
+
+all.data2<- subset(all.data1,
+                   per_ssid_pupil_loss_perc< 24)
+
+# now mean wise inputation based on each variable
+all.data2
+
+colnames(all.data2)
+# pupil row-wise inputation
+k <- which(is.na(all.data2[, c(1,4:59)]), arr.ind=TRUE)
+k
+all.data3<- all.data2
+all.data3pup<- all.data2[, c(1,4:59)]
+
+all.data3pup[k] <- rowMeans(all.data3pup[, 2:57], na.rm=TRUE)[k[,1]]
+
+# HR
+all.data3_hr<- all.data3[,c(1,60:115)]
+k <- which(is.na(all.data3_hr[, 1:57]), arr.ind=TRUE)
+k
+
+all.data3_hr[k] <- rowMeans(all.data3_hr[, 2:57], na.rm=TRUE)[k[,1]]
+
+# SCR
+colnames(all.data3)
+all.data3_scr<- all.data3[,c(1,116:171)]
+k_scr <- which(is.na(all.data3_scr[, 1:57]), arr.ind=TRUE)
+k_scr
+
+all.data3_scr[k_scr] <- rowMeans(all.data3_scr[, 2:57], na.rm=TRUE)[k_scr[,1]]
+
+# merge()
+all.data3_forPCA<- all.data3[,1:3]
+
+all.data3_forPCA<- left_join(all.data3_forPCA, all.data3pup)
+all.data3_forPCA<- left_join(all.data3_forPCA, all.data3_hr)
+all.data3_forPCA<- left_join(all.data3_forPCA, all.data3_scr)
+
  # design
-var.design_asd <- as.factor(all.data$Group)
-var.design_aq <- as.factor(all.data$AQ_mediansplit)
-var.design_tas <- as.factor(all.data$TAS_mediansplit)
-colnames(all.data)
-
-var.data <- all.data[,c(6:172)]
-
-var.PCA.inf_asd <-InPosition::epPCA.inference.battery(var.data, 
-                                       scale = FALSE, 
-                                       center = FALSE, 
-                                       DESIGN = var.design_asd, 
-                                       make_design_nominal = TRUE, 
+# var.design_asd <- as.factor(all.data$Group)
+
+colnames(all.data3_forPCA)
+
+var.data <- all.data3_forPCA[,c(4:171)]
+
+library(TInPosition)
+library(prettyGraphs)
+
+# inferential PCA
+var.PCA.scr_hr_pup <-InPosition::epPCA.inference.battery(var.data, 
+                                       scale = TRUE, 
+                                       center = TRUE, 
+                                       # DESIGN = var.design_asd, 
+                                       # make_design_nominal = TRUE, 
                                        graphs = TRUE, k = 0, 
@@
 
-```
+# includValenceMean_median_split
+colnames(all.data3)
+
+all.data3_val<- all.data3[,c(1,228:283)]
+
+all.data3_val
+k_val <- which(is.na(all.data3_val[, c(1:57)]), arr.ind=TRUE)
+k_val
+all.data3_val[k_val] <- rowMeans(all.data3_val[, 2:57], na.rm=TRUE)[k_val[,1]]
+
+all.data3_forPCA_withval<- left_join(all.data3_forPCA, all.data3_val)
+
+# subjective arousal
+
+all.data3_ar<- all.data3[,c(1,172:227)]
+
+all.data3_ar
+k_ar <- which(is.na(all.data3_ar[, c(1:57)]), arr.ind=TRUE)
+k_ar
+all.data3_ar[k_ar] <- rowMeans(all.data3_ar[, 2:57], na.rm=TRUE)[k_ar[,1]]
+
+all.data3_forPCA_withar<- left_join(all.data3_forPCA, all.data3_ar)
+
+library(InPosition)
+var.PCA.scr_hr_pup_val <-InPosition::epPCA.inference.battery(all.data3_forPCA_withval[,4:226], 
+                                       scale = TRUE, 
+                                       center = TRUE, 
+                                       # DESIGN = var.design_asd, 
+                                       # make_design_nominal = TRUE, 
+                                       graphs = TRUE, k = 0, 
+                                       test.iters = 1000, 
+                                       constrained = FALSE, 
+                                       critical.value = 2)
+
+# with self arousal
+var.PCA.scr_hr_pup_ar <-InPosition::epPCA.inference.battery(all.data3_forPCA_withar[,4:227], 
+                                       scale = TRUE, 
+                                       center = TRUE, 
+                                       # DESIGN = var.design_asd, 
+                                       # make_design_nominal = TRUE, 
+                                       graphs = TRUE, k = 0, 
+                                       test.iters = 1000, 
+                                       constrained = FALSE, 
+                                       critical.value = 2)
+
+```

### 2021-11-25 Paper_Analyses_subj_obje_arousal.Rmd
First take on MFA
initialised MFA analysis and so far things match the inferential PCAs, but we need a principle way to decide on data structure

@@
 
+View(db_full6new_hr_fix_stim_select2_NT_no_outl_5)
 db_forBADA1<- data.table::dcast(setDT(db_full6new_hr_fix_stim_select2_NT_no_outl_5), 
@@
 # clustering
+View(clustering)
 clustering_new_pre_PCA<- select(clustering, c(ssid, TAS, AQ, stimIAPS2,
@@
                                                   valence, fix_count, mean_fix_dur))
+View(clustering_new_pre_PCA)
 
@@
 
-```
+View(all.data3_forPCA_withar)
+
+View(clustering_new_pre_PCA)
+```
+
+Multiple factor analysys
+
+- consider aggregating  (average per stim)
+- PCA on arousal arousal and valence
+
+```{r}
+
+library(factoextra)
+library(FactoMineR)
+
+clustering_new_pre_PCA
+colnames(clustering_new_pre_PCA)
+
+clustering_new_pre_PCA_2<- clustering_new_pre_PCA[, c(1,5:10,12)]
+colnames(clustering_new_pre_PCA_2)
+
+MFA(base, group, type = rep("s",length(group)), ind.sup = NULL, 
+    name.group = NULL, num.group.sup = NULL, graph = TRUE)
+
+res.mfa <- MFA(wine, 
+               group = c(2, 5, 3, 10, 9, 2), 
+               type = c("n", "s", "s", "s", "s", "s"),
+               name.group = c("origin","odor","visual",
+                              "odor.after.shaking", "taste","overall"),
+               num.group.sup = c(1, 6),
+               graph = FALSE)
+
+clustering_new_pre_PCA_2
+
+View(clustering_new_pre_PCA_2)
+
+clustering_new_pre_PCA_2$ssid<- as.factor(clustering_new_pre_PCA_2$ssid)
+?MFA
+
+clustering_new_pre_PCA_2$stimDescription
+res.mfa <- MFA(clustering_new_pre_PCA_2, 
+               group = c(2, 1, 1, 1, 2, 1), 
+               type = c("n", "s", "s", "s", "s", "s"),
+               name.group = c("pp_stim","pupil","HR","SCR", "ar_val","fix"),
+               num.group.sup = c(1,2),
+               graph = TRUE)
+
+print(res.mfa)
+
+clustering_new_pre_PCA_2print(res.mfa)
+
+```
+```{r}
+library("factoextra")
+eig.val <- get_eigenvalue(res.mfa)
+head(eig.val)
+
+install.packages("MExPosition")
+# ExPosition::FA
+
+TExPosition::
+# InPosition::
+# TExPosition::
+
+```
+
+the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
+```{r}
+fviz_screeplot(res.mfa)
+
+```
+
+The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables.
+This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the
+
+```{r}
+
+group <- get_mfa_var(res.mfa, "group")
+group
+
+```
+
+The different components can be accessed as follow:
+```{r}
+# Coordinates of groups
+head(group$coord)
+# Cos2: quality of representation on the factore map
+head(group$cos2)
+# Contributions to the  dimensions
+head(group$contrib)
+
+```
+
+To plot the groups of variables, type this:
+
+```{r}
+fviz_mfa_var(res.mfa, "group")
+
+```
+
+red color = active groups of variables
+green color = supplementary groups of variables
+The plot above illustrates the correlation between groups and dimensions.
+The coordinates of the four active groups on the first dimension are almost identical.
+This means that they contribute similarly to the first dimension.
+Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.
+
+To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
+```{r}
+# Contribution to the first dimension
+fviz_contrib(res.mfa, "group", axes = 1)
+# Contribution to the second dimension
+fviz_contrib(res.mfa, "group", axes = 2)
+
+```
+Quantitative variables
+The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables.
+This function returns a list containing the coordinates, the cos2 and the contribution of variables:
+```{r}
+quanti.var <- get_mfa_var(res.mfa, "quanti.var")
+quanti.var
+
+```
+```{r}
+# Coordinates
+head(quanti.var$coord)
+# Cos2: quality on the factore map
+head(quanti.var$cos2)
+# Contributions to the dimensions
+head(quanti.var$contrib)
+
+```
+Correlation between quantitative variables and dimensions.
+The R code below plots quantitative variables colored by groups.
+The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
+Supplementary quantitative variables are in dashed arrow and violet color.
+We use repel = TRUE, to avoid text overlapping.
+
+```{r}
+fviz_mfa_var(res.mfa, "quanti.var", palette = "jco", 
+             col.var.sup = "violet", repel = TRUE)
+
+```
+
+To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”).
+We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
+```{r}
+fviz_mfa_var(res.mfa, "quanti.var", palette = "jco", 
+             col.var.sup = "violet", repel = TRUE,
+             geom = c("point", "text"), legend = "bottom")
+
+```
+
+```{r}
+fviz_contrib(res.mfa, choice = "quanti.var", axes = 1, top = 20,
+             palette = "jco")
+
+```
+Graph of individuals
+
+```{r}
+# To get the results for individuals, type this:
+
+ind <- get_mfa_ind(res.mfa)
+ind
+
+```
+To plot individuals, use the function fviz_mfa_ind() [in factoextra].
+By default, individuals are colored in blue.
+However, like variables, it’s also possible to color individuals by their cos2 values:
+
+```{r}
+fviz_mfa_ind(res.mfa, col.ind = "cos2", 
+             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+             repel = FALSE)
+
+fviz_mfa_ind(res.mfa, 
+             habillage = "Label", # color by groups 
+             palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+             addEllipses = TRUE, ellipse.type = "confidence", 
+             repel = TRUE # Avoid text overlapping
+             )
+
+```
+```{r}
+
+clustering_new_pre_PCA_2
+
+fviz_mfa_ind(res.mfa, 
+             habillage = "stimDescription", # color by groups 
+             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+             addEllipses = TRUE, ellipse.type = "confidence", 
+             repel = TRUE # Avoid text overlapping
+             )
+
+fviz_mfa_ind(res.mfa, 
+             habillage = "ssid", # color by groups 
+             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+             addEllipses = TRUE, ellipse.type = "confidence", 
+             repel = TRUE # Avoid text overlapping
+             )
+
+```
+
+Aggregate one average per stim
+
+```{r}
+
+library(factoextra)
+library(FactoMineR)
+
+colnames(clustering_agg_JASPtest)
+
+clustering_agg_JASP_PCA_2<- clustering_agg_JASPtest [, c(1,27, 2:4)]
+colnames(clustering_agg_JASP_PCA_2)
+
+clustering_agg_JASP_PCA_2$stimIAPS2<- as.factor(clustering_agg_JASP_PCA_2$stimIAPS2)
+
+clustering_agg_JASP_PCA_2$stimDescription<- as.factor(clustering_agg_JASP_PCA_2$stimDescription)
+
+res.mfa_agg <- MFA(wine, 
+               group = c(2, 5, 3, 10, 9, 2), 
+               type = c("n", "s", "s", "s", "s", "s"),
+               name.group = c("origin","odor","visual",
+                              "odor.after.shaking", "taste","overall"),
+               num.group.sup = c(1, 6),
+               graph = FALSE)
+
+colnames(clustering_agg_JASP_PCA_2)
+res.mfa_agg <- MFA(clustering_agg_JASP_PCA_2, 
+               group = c(2, 1, 1, 1), 
+               type = c("n", "s", "s", "s"),
+               name.group = c("stim_desc","HR","pupil","SCR"),
+               num.group.sup = c(1,2),
+               graph = TRUE)
+
+print(res.mfa_agg)
+
+```
+```{r}
+library("factoextra")
+eig.val_agg <- get_eigenvalue(res.mfa_agg)
+head(eig.val_agg)
+
+```
+
+the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
+```{r}
+fviz_screeplot(res.mfa_agg)
+
+```
+
+The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables.
+This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the
+
+```{r}
+
+group_agg <- get_mfa_var(res.mfa_agg, "group")
+group_agg
+
+```
+
+The different components can be accessed as follow:
+```{r}
+# Coordinates of groups
+head(group_agg$coord)
+# Cos2: quality of representation on the factore map
+head(group_agg$cos2)
+# Contributions to the  dimensions
+head(group_agg$contrib)
+
+```
+
+To plot the groups of variables, type this:
+
+```{r}
+fviz_mfa_var(res.mfa_agg, "group")
+
+```
+
+red color = active groups of variables
+green color = supplementary groups of variables
+The plot above illustrates the correlation between groups and dimensions.
+The coordinates of the four active groups on the first dimension are almost identical.
+This means that they contribute similarly to the first dimension.
+Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.
+
+To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
+```{r}
+# Contribution to the first dimension
+fviz_contrib(res.mfa_agg, "group", axes = 1)
+# Contribution to the second dimension
+fviz_contrib(res.mfa_agg, "group", axes = 2)
+
+```
+Quantitative variables
+The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables.
+This function returns a list containing the coordinates, the cos2 and the contribution of variables:
+```{r}
+quanti.var_agg <- get_mfa_var(res.mfa_agg, "quanti.var")
+quanti.var_agg
+
+```
+
+```{r}
+# Coordinates
+head(quanti.var_agg$coord)
+# Cos2: quality on the factore map
+head(quanti.var_agg$cos2)
+# Contributions to the dimensions
+head(quanti.var_agg$contrib)
+
+```
+Correlation between quantitative variables and dimensions.
+The R code below plots quantitative variables colored by groups.
+The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
+Supplementary quantitative variables are in dashed arrow and violet color.
+We use repel = TRUE, to avoid text overlapping.
+
+```{r}
+fviz_mfa_var(res.mfa_agg, "quanti.var", palette = "jco", 
+             col.var.sup = "violet", repel = TRUE)
+
+```
+
+To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”).
+We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
+```{r}
+fviz_mfa_var(res.mfa_agg, "quanti.var", palette = "jco", 
+             col.var.sup = "violet", repel = TRUE,
+             geom = c("point", "text"), legend = "bottom")
+
+```
+
+```{r}
+fviz_contrib(res.mfa_agg, choice = "quanti.var", axes = 1, top = 20,
+             palette = "jco")
+fviz_contrib(res.mfa_agg, choice = "quanti.var", axes = 2, top = 20,
+             palette = "jco")
+
+```
+Graph of individuals
+
+```{r}
+# To get the results for individuals, type this:
+
+ind_agg <- get_mfa_ind(res.mfa_agg)
+ind_agg
+
+```
+To plot individuals, use the function fviz_mfa_ind() [in factoextra].
+By default, individuals are colored in blue.
+However, like variables, it’s also possible to color individuals by their cos2 values:
+
+```{r}
+fviz_mfa_ind(res.mfa_agg, col.ind = "cos2", 
+             # gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+             repel = TRUE)
+clust2_dataset$stimDescription
+pp_stim
+fviz_mfa_ind(res.mfa_agg, 
+             habillage = "stimDescription", # color by groups 
+             palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+             addEllipses = TRUE, ellipse.type = "confidence", 
+             repel = TRUE # Avoid text overlapping
+             )
+
+```
+
+```{r}
+
+clustering_new_pre_PCA_2
+
+fviz_mfa_ind(res.mfa_agg, 
+             habillage = "stimIAPS2", # color by groups 
+             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+             addEllipses = TRUE, ellipse.type = "confidence", 
+             repel = TRUE # Avoid text overlapping
+             )
+
+```
+
+Graph of partial individuals
+The results for individuals obtained from the analysis performed with a single group are named partial individuals.
+In other words, an individual considered from the point of view of a single group is called partial individual.
+
+In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual.
+That is, the individual viewed by all groups of variables.
+
+For a given individual, there are as many partial points as groups of variables.
+
+The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:
+
+```{r}
+fviz_mfa_ind(res.mfa_agg, partial = "all") 
+# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:
+
+fviz_mfa_ind(res.mfa, partial = c("1DAM", "1VAU", "2ING"))
+
+```
+
+Graph of partial axes
+The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).
+
+```{r}
+fviz_mfa_axes(res.mfa_agg)
+
+```
+
+```{r}
+data(wine)
+View(wine)
+
+View(clustering_new_pre_PCA_2)
+
+```
+
+colnames
+
+```{r}
+db_forPCA
+colnames(db_forPCA)
+library(tidyverse)
+data3_forPCA_withar
+all.data3_forPCA_withar$TAS_split<- if_else(all.data3_forPCA_withar$TAS > 
+                                          median(all.data3_forPCA_withar$TAS, na.rm = TRUE), "High", "Low")
+colnames(all.data3_forPCA_withar)
+db_forPCA_MFA<- all.data3_forPCA_withar[, c(1,228, 4:171)]
+
+colnames(db_forPCA_MFA)
+
+db_forPCA_MFA
+
+db_forPCA_MFA$ssid<- as.factor(db_forPCA_MFA$ssid)
+
+colnames(db_forPCA_MFA)
+
+db_forPCA_MFA$arousal_9561SickKitty<- NULL
+res.mfa_dcast <- MFA(db_forPCA_MFA, 
+               group = c(2, 56, 56, 56), 
+               type = c("n", "s", "s", "s"),
+               name.group = c("pp_gr","pupil","HR","SCR"),
+               num.group.sup = c(1,2),
+               graph = TRUE)
+
+print(res.mfa_dcast)
+
+```
+
+here
+
+```{r}
+library("factoextra")
+# res.mfa_dcast <- get_eigenvalue(res.mfa_dcast)
+# head(res.mfa_dcast)
+
+```
+
+the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
+```{r}
+fviz_screeplot(res.mfa_dcast)
+
+```
+
+The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables.
+This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the
+
+```{r}
+
+group_dcast <- get_mfa_var(res.mfa_dcast, "group")
+group_dcast
+
+```
+
+The different components can be accessed as follow:
+```{r}
+# Coordinates of groups
+head(group_dcast$coord)
+# Cos2: quality of representation on the factore map
+head(group_dcast$cos2)
+# Contributions to the  dimensions
+head(group_dcast$contrib)
+
+```
+
+To plot the groups of variables, type this:
+
+```{r}
+fviz_mfa_var(res.mfa_dcast, "group")
+
+```
+
+red color = active groups of variables
+green color = supplementary groups of variables
+The plot above illustrates the correlation between groups and dimensions.
+The coordinates of the four active groups on the first dimension are almost identical.
+This means that they contribute similarly to the first dimension.
+Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.
+
+To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
+```{r}
+# Contribution to the first dimension
+fviz_contrib(res.mfa_dcast, "group", axes = 1)
+# Contribution to the second dimension
+fviz_contrib(res.mfa_dcast, "group", axes = 2)
+
+```
+Quantitative variables
+The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables.
+This function returns a list containing the coordinates, the cos2 and the contribution of variables:
+```{r}
+quanti.var_dcast <- get_mfa_var(res.mfa_dcast, "quanti.var")
+quanti.var_dcast
+
+```
+
+```{r}
+# Coordinates
+head(quanti.var_dcast$coord)
+# Cos2: quality on the factore map
+head(quanti.var_dcast$cos2)
+# Contributions to the dimensions
+head(quanti.var_dcast$contrib)
+
+```
+Correlation between quantitative variables and dimensions.
+The R code below plots quantitative variables colored by groups.
+The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
+Supplementary quantitative variables are in dashed arrow and violet color.
+We use repel = TRUE, to avoid text overlapping.
+
+```{r}
+fviz_mfa_var(res.mfa_dcast, "quanti.var", palette = "jco", 
+             col.var.sup = "violet", repel = TRUE)
+
+```
+
+To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”).
+We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
+```{r}
+fviz_mfa_var(res.mfa_dcast, "quanti.var", palette = "jco", 
+             col.var.sup = "violet", repel = TRUE,
+             geom = c("point", "text"), legend = "bottom")
+
+```
+
+```{r}
+fviz_contrib(res.mfa_dcast, choice = "quanti.var", axes = 1, top = 20,
+             palette = "jco")
+fviz_contrib(res.mfa_agg, choice = "quanti.var", axes = 2, top = 20,
+             palette = "jco")
+
+```
+Graph of individuals
+
+```{r}
+# To get the results for individuals, type this:
+
+ind_dcast <- get_mfa_ind(res.mfa_dcast)
+ind_dcast
+
+```
+To plot individuals, use the function fviz_mfa_ind() [in factoextra].
+By default, individuals are colored in blue.
+However, like variables, it’s also possible to color individuals by their cos2 values:
+
+```{r}
+fviz_mfa_ind(res.mfa_dcast, col.ind = "cos2", 
+             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+             repel = TRUE)
+clust2_dataset$stimDescription
+pp_stim
+fviz_mfa_ind(res.mfa_dcast, 
+             habillage = "TAS_split", # color by groups 
+             palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+             addEllipses = TRUE, ellipse.type = "confidence", 
+             repel = TRUE # Avoid text overlapping
+             )
+
+```
+
+```{r}
+
+clustering_new_pre_PCA_2
+
+fviz_mfa_ind(res.mfa_dcast, 
+             habillage = "stimIAPS2", # color by groups 
+             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+             addEllipses = TRUE, ellipse.type = "confidence", 
+             repel = TRUE # Avoid text overlapping
+             )
+
+```
+
+Graph of partial individuals
+The results for individuals obtained from the analysis performed with a single group are named partial individuals.
+In other words, an individual considered from the point of view of a single group is called partial individual.
+
+In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual.
+That is, the individual viewed by all groups of variables.
+
+For a given individual, there are as many partial points as groups of variables.
+
+The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:
+
+```{r}
+fviz_mfa_ind(res.mfa_dcast, partial = "all") 
+# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:
+
+```
+
+Graph of partial axes
+The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).
+
+```{r}
+fviz_mfa_axes(res.mfa_dcast)
+
+```
+
+<!-- neg, neutra positive -->
+
+```{r}
+data(wine)
+View(wine)
+
+View(clustering_new_pre_PCA_2)
+?cut
+clustering_new_pre_PCA_2$valence_split<- cut(clustering_new_pre_PCA_2$valence, 3,
+                                             labels = c("neg", "mid", "positive"))
+
+clustering_new_pre_PCA_2_agg_by_val<- clustering_new_pre_PCA_2%>%
+  group_by(ssid,valence_split)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)
+
+View(clustering_new_pre_PCA_2_agg_by_val)
+
+colnames(clustering_new_pre_PCA_2_agg_by_val)
+clustering_new_pre_PCA_2_agg_by_val_sel<- clustering_new_pre_PCA_2_agg_by_val[, c(1:7)]
+
+# dcast
+library(data.table)
+clustering_new_pre_PCA_2_agg_by_val_sel_dcast<- data.table::dcast(setDT(clustering_new_pre_PCA_2_agg_by_val_sel), 
+                    ssid ~ valence_split, value.var = c('pup_basCor',
+                'Bio_Mean_HR_dif', 'log_BIO_CDA.PhasicMax', "arousal", "valence"))
+
+clustering_new_pre_PCA_2_agg_by_val_sel_dcast
+
+clustering_new_pre_PCA_2_agg_by_val_sel_dcast$pup_basCor_NA<- NULL
+
+clustering_new_pre_PCA_2_agg_by_val_sel_dcast$Bio_Mean_HR_dif_NA<- NULL
+clustering_new_pre_PCA_2_agg_by_val_sel_dcast$log_BIO_CDA.PhasicMax_NA<- NULL
+
+clustering_new_pre_PCA_2_agg_by_val_sel_dcast$valence_NA<- NULL
+clustering_new_pre_PCA_2_agg_by_val_sel_dcast$arousal_NA<- NULL
+clustering_new_pre_PCA_2_agg_by_val_sel_dcast
+View(clustering_new_pre_PCA_2_agg_by_val_sel_dcast)
+
+namesrepl<- colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast)
+
+namesrepl<- c("ssid", "p_neg", "p_mid" ,"p_pos", "HR_neg" , "HR_mid",
+                  "HR_pos","SCR_neg", "SCR_mid", "SCR_pos")
+
+clustering_new_pre_PCA_2_agg_by_val_sel_dcast2<- clustering_new_pre_PCA_2_agg_by_val_sel_dcast
+names(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)<- namesrepl
+
+```
+
+MFA agg by val
+
+```{r}
+colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
+res.mfa_agg_byval <- MFA(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2, 
+               group = c(1, 3, 3, 3), 
+               type = c("n", "s", "s", "s"),
+               name.group = c("ssid","pupil","HR","SCR"),
+               num.group.sup = c(1),
+               graph = TRUE)
+
+print(res.mfa_agg_byval)
+
+```
+
+```{r}
+library("factoextra")
+eif_vyval <- get_eigenvalue(res.mfa_agg_byval)
+head(eif_vyval)
+
+```
+
+the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
+```{r}
+fviz_screeplot(res.mfa_agg_byval)
+
+```
+
+The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables.
+This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the
+
+```{r}
+
+group_vybal <- get_mfa_var(res.mfa_agg_byval, "group")
+group_vybal
+
+```
+
+The different components can be accessed as follow:
+```{r}
+# Coordinates of groups
+head(group_vybal$coord)
+# Cos2: quality of representation on the factore map
+head(group_vybal$cos2)
+# Contributions to the  dimensions
+head(group_vybal$contrib)
+
+```
+
+To plot the groups of variables, type this:
+
+```{r}
+fviz_mfa_var(res.mfa_agg_byval, "group")
+
+```
+
+red color = active groups of variables
+green color = supplementary groups of variables
+The plot above illustrates the correlation between groups and dimensions.
+The coordinates of the four active groups on the first dimension are almost identical.
+This means that they contribute similarly to the first dimension.
+Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.
+
+To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
+```{r}
+# Contribution to the first dimension
+fviz_contrib(res.mfa_agg_byval, "group", axes = 1)
+# Contribution to the second dimension
+fviz_contrib(res.mfa_agg_byval, "group", axes = 2)
+
+```
+Quantitative variables
+The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables.
+This function returns a list containing the coordinates, the cos2 and the contribution of variables:
+```{r}
+quanti.var_agg_by_val <- get_mfa_var(res.mfa_agg_byval, "quanti.var")
+quanti.var_agg_by_val
+
+```
+
+```{r}
+# Coordinates
+head(quanti.var_agg_by_val$coord)
+# Cos2: quality on the factore map
+head(quanti.var_agg_by_val$cos2)
+# Contributions to the dimensions
+head(quanti.var_agg_by_val$contrib)
+
+```
+Correlation between quantitative variables and dimensions.
+The R code below plots quantitative variables colored by groups.
+The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
+Supplementary quantitative variables are in dashed arrow and violet color.
+We use repel = TRUE, to avoid text overlapping.
+
+```{r}
+fviz_mfa_var(res.mfa_agg_byval, "quanti.var", palette = "jco", 
+             col.var.sup = "violet", repel = TRUE)
+
+```
+
+Correlation between quantitative variables and dimensions.
+The R code below plots quantitative variables colored by groups.
+The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
+Supplementary quantitative variables are in dashed arrow and violet color.
+We use repel = TRUE, to avoid text overlapping.
+
+```{r}
+fviz_mfa_var(res.mfa_dcast, "quanti.var", palette = "jco", 
+             col.var.sup = "violet", repel = TRUE)
+
+```
+
+To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”).
+We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
+```{r}
+fviz_mfa_var(res.mfa_agg_byval, "quanti.var", palette = "jco", 
+             col.var.sup = "violet", repel = TRUE,
+             geom = c("point", "text"), legend = "bottom")
+
+```
+
+```{r}
+fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 1, top = 20,
+             palette = "jco")
+fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 2, top = 20,
+             palette = "jco")
+
+```
+Graph of individuals
+
+```{r}
+# To get the results for individuals, type this:
+
+ind_agg_byval <- get_mfa_ind(res.mfa_agg_byval)
+ind_agg_byval
+
+```
+To plot individuals, use the function fviz_mfa_ind() [in factoextra].
+By default, individuals are colored in blue.
+However, like variables, it’s also possible to color individuals by their cos2 values:
+
+```{r}
+fviz_mfa_ind(res.mfa_agg_byval, col.ind = "cos2", 
+             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+             repel = TRUE)
+
+fviz_mfa_ind(res.mfa_agg_byval, 
+             habillage = "ssid", # color by groups
+             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+             addEllipses = TRUE, ellipse.type = "confidence", 
+             repel = TRUE # Avoid text overlapping
+             )
+
+```
+
+```{r}
+
+clustering_new_pre_PCA_2
+
+fviz_mfa_ind(res.mfa_agg_byval, 
+             # habillage = "stimIAPS2", # color by groups 
+             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+             addEllipses = TRUE, ellipse.type = "confidence", 
+             repel = TRUE # Avoid text overlapping
+             )
+
+```
+
+Graph of partial individuals
+The results for individuals obtained from the analysis performed with a single group are named partial individuals.
+In other words, an individual considered from the point of view of a single group is called partial individual.
+
+In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual.
+That is, the individual viewed by all groups of variables.
+
+For a given individual, there are as many partial points as groups of variables.
+
+The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:
+
+```{r}
+fviz_mfa_ind(res.mfa_agg_byval, partial = "all") 
+# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:
+
+```
+
+Graph of partial axes
+The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).
+
+```{r}
+fviz_mfa_axes(res.mfa_agg_byval)
+
+```
+
+with valence
+clustering_new_pre_PCA_2_agg_by_val_sel_dcast
+
+```{r}
+colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
+res.mfa_agg_byval <- MFA(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2, 
+               group = c(1, 3, 3, 3), 
+               type = c("n", "s", "s", "s"),
+               name.group = c("ssid","pupil","HR","SCR"),
+               num.group.sup = c(1),
+               graph = TRUE)
+
+print(res.mfa_agg_byval)
+
+```
+
+```{r}
+library("factoextra")
+eif_vyval <- get_eigenvalue(res.mfa_agg_byval)
+head(eif_vyval)
+
+```
+
+the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
+```{r}
+fviz_screeplot(res.mfa_agg_byval)
+
+```
+
+The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables.
+This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the
+
+```{r}
+
+group_vybal <- get_mfa_var(res.mfa_agg_byval, "group")
+group_vybal
+
+```
+
+The different components can be accessed as follow:
+```{r}
+# Coordinates of groups
+head(group_vybal$coord)
+# Cos2: quality of representation on the factore map
+head(group_vybal$cos2)
+# Contributions to the  dimensions
+head(group_vybal$contrib)
+
+```
+
+To plot the groups of variables, type this:
+
+```{r}
+fviz_mfa_var(res.mfa_agg_byval, "group")
+
+```
+
+red color = active groups of variables
+green color = supplementary groups of variables
+The plot above illustrates the correlation between groups and dimensions.
+The coordinates of the four active groups on the first dimension are almost identical.
+This means that they contribute similarly to the first dimension.
+Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.
+
+To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
+```{r}
+# Contribution to the first dimension
+fviz_contrib(res.mfa_agg_byval, "group", axes = 1)
+# Contribution to the second dimension
+fviz_contrib(res.mfa_agg_byval, "group", axes = 2)
+
+```
+Quantitative variables
+The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables.
+This function returns a list containing the coordinates, the cos2 and the contribution of variables:
+```{r}
+quanti.var_agg_by_val <- get_mfa_var(res.mfa_agg_byval, "quanti.var")
+quanti.var_agg_by_val
+
+```
+
+```{r}
+# Coordinates
+head(quanti.var_agg_by_val$coord)
+# Cos2: quality on the factore map
+head(quanti.var_agg_by_val$cos2)
+# Contributions to the dimensions
+head(quanti.var_agg_by_val$contrib)
+
+```
+Correlation between quantitative variables and dimensions.
+The R code below plots quantitative variables colored by groups.
+The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
+Supplementary quantitative variables are in dashed arrow and violet color.
+We use repel = TRUE, to avoid text overlapping.
+
+```{r}
+fviz_mfa_var(res.mfa_agg_byval, "quanti.var", palette = "jco", 
+             col.var.sup = "violet", repel = TRUE)
+
+```
+
+Correlation between quantitative variables and dimensions.
+The R code below plots quantitative variables colored by groups.
+The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
+Supplementary quantitative variables are in dashed arrow and violet color.
+We use repel = TRUE, to avoid text overlapping.
+
+```{r}
+fviz_mfa_var(res.mfa_dcast, "quanti.var", palette = "jco", 
+             col.var.sup = "violet", repel = TRUE)
+
+```
+
+To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”).
+We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
+```{r}
+fviz_mfa_var(res.mfa_agg_byval, "quanti.var", palette = "jco", 
+             col.var.sup = "violet", repel = TRUE,
+             geom = c("point", "text"), legend = "bottom")
+
+```
+
+```{r}
+fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 1, top = 20,
+             palette = "jco")
+fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 2, top = 20,
+             palette = "jco")
+
+```
+Graph of individuals
+
+```{r}
+# To get the results for individuals, type this:
+
+ind_agg_byval <- get_mfa_ind(res.mfa_agg_byval)
+ind_agg_byval
+
+```
+To plot individuals, use the function fviz_mfa_ind() [in factoextra].
+By default, individuals are colored in blue.
+However, like variables, it’s also possible to color individuals by their cos2 values:
+
+```{r}
+fviz_mfa_ind(res.mfa_agg_byval, col.ind = "cos2", 
+             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+             repel = TRUE)
+
+fviz_mfa_ind(res.mfa_agg_byval, 
+             habillage = "ssid", # color by groups
+             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+             addEllipses = TRUE, ellipse.type = "confidence", 
+             repel = TRUE # Avoid text overlapping
+             )
+
+```
+
+```{r}
+
+clustering_new_pre_PCA_2
+
+fviz_mfa_ind(res.mfa_agg_byval, 
+             # habillage = "stimIAPS2", # color by groups 
+             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+             addEllipses = TRUE, ellipse.type = "confidence", 
+             repel = TRUE # Avoid text overlapping
+             )
+
+```
+
+Graph of partial individuals
+The results for individuals obtained from the analysis performed with a single group are named partial individuals.
+In other words, an individual considered from the point of view of a single group is called partial individual.
+
+In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual.
+That is, the individual viewed by all groups of variables.
+
+For a given individual, there are as many partial points as groups of variables.
+
+The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:
+
+```{r}
+fviz_mfa_ind(res.mfa_agg_byval, partial = "all") 
+# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:
+
+```
+
+Graph of partial axes
+The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).
+
+```{r}
+fviz_mfa_axes(res.mfa_agg_byval)
+
+```

### 2021-11-25 Paper_Analyses_subj_obje_arousal.Rmd
MFA2.1

@@
 namesrepl<- c("ssid", "p_neg", "p_mid" ,"p_pos", "HR_neg" , "HR_mid",
-                  "HR_pos","SCR_neg", "SCR_mid", "SCR_pos")
+                  "HR_pos","SCR_neg", "SCR_mid", "SCR_pos", "ar_neg","ar_mid", "ar_pos",
+              "vl_neg","vl_mid", "vl_pos")
 
@@
 
+clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$pcscoremaybe <- res.mfa_agg_byval[["global.pca"]][["ind"]][["cos2"]][,1]
+
+clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar<- (clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar_neg+clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar_mid+
+  clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar_pos)/3
+
+# cor.test(res.mfa_agg_byval[["global.pca"]][["ind"]][["cos2"]][,3],
+#          clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar)
+
 ```
@@
 ```{r}
+
 colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
-res.mfa_agg_byval <- MFA(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2, 
-               group = c(1, 3, 3, 3), 
-               type = c("n", "s", "s", "s"),
-               name.group = c("ssid","pupil","HR","SCR"),
+res.mfa_agg_byval2 <- MFA(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2, 
+               group = c(1, 3, 3, 3,3,3), 
+               type = c("n", "s", "s", "s","s", "s"),
+               name.group = c("ssid","pupil","HR","SCR", "AR", "VL"),
                num.group.sup = c(1),
@@
 
-print(res.mfa_agg_byval)
+print(res.mfa_agg_byval2)
 
@@
 library("factoextra")
-eif_vyval <- get_eigenvalue(res.mfa_agg_byval)
-head(eif_vyval)
+eif_vyval2 <- get_eigenvalue(res.mfa_agg_byval2)
+head(eif_vyval2)
 
@@
 ```{r}
-fviz_screeplot(res.mfa_agg_byval)
+fviz_screeplot(res.mfa_agg_byval2)
 
@@
 
-group_vybal <- get_mfa_var(res.mfa_agg_byval, "group")
-group_vybal
+group_vybal2 <- get_mfa_var(res.mfa_agg_byval2, "group")
+group_vybal2
 
@@
 # Coordinates of groups
-head(group_vybal$coord)
+head(group_vybal2$coord)
 # Cos2: quality of representation on the factore map
-head(group_vybal$cos2)
+head(group_vybal2$cos2)
 # Contributions to the  dimensions
-head(group_vybal$contrib)
+head(group_vybal2$contrib)
 
@@
 ```{r}
-fviz_mfa_var(res.mfa_agg_byval, "group")
+fviz_mfa_var(res.mfa_agg_byval2, "group")
 
@@
 # Contribution to the first dimension
-fviz_contrib(res.mfa_agg_byval, "group", axes = 1)
+fviz_contrib(res.mfa_agg_byval2, "group", axes = 1)
 # Contribution to the second dimension
-fviz_contrib(res.mfa_agg_byval, "group", axes = 2)
+fviz_contrib(res.mfa_agg_byval2, "group", axes = 2)
 
@@
 ```{r}
-quanti.var_agg_by_val <- get_mfa_var(res.mfa_agg_byval, "quanti.var")
-quanti.var_agg_by_val
+quanti.var_agg_by_val2 <- get_mfa_var(res.mfa_agg_byval2, "quanti.var")
+quanti.var_agg_by_val2
 
@@
 # Coordinates
-head(quanti.var_agg_by_val$coord)
+head(quanti.var_agg_by_val2$coord)
 # Cos2: quality on the factore map
-head(quanti.var_agg_by_val$cos2)
+head(quanti.var_agg_by_val2$cos2)
 # Contributions to the dimensions
-head(quanti.var_agg_by_val$contrib)
+head(quanti.var_agg_by_val2$contrib)
 
@@
 ```{r}
-fviz_mfa_var(res.mfa_agg_byval, "quanti.var", palette = "jco", 
+fviz_mfa_var(res.mfa_agg_byval2, "quanti.var", palette = "jco", 
              col.var.sup = "violet", repel = TRUE)
@@
 ```{r}
-fviz_mfa_var(res.mfa_dcast, "quanti.var", palette = "jco", 
+fviz_mfa_var(res.mfa_agg_byval2, "quanti.var", palette = "jco", 
              col.var.sup = "violet", repel = TRUE)
@@
 ```{r}
-fviz_mfa_var(res.mfa_agg_byval, "quanti.var", palette = "jco", 
+fviz_mfa_var(res.mfa_agg_byval2, "quanti.var", palette = "jco", 
              col.var.sup = "violet", repel = TRUE,
@@
 ```{r}
-fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 1, top = 20,
+fviz_contrib(res.mfa_agg_byval2, choice = "quanti.var", axes = 1, top = 20,
              palette = "jco")
@@
 
-ind_agg_byval <- get_mfa_ind(res.mfa_agg_byval)
-ind_agg_byval
+ind_agg_byval2 <- get_mfa_ind(res.mfa_agg_byval2)
+ind_agg_byval2
 
@@
 ```{r}
-fviz_mfa_ind(res.mfa_agg_byval, col.ind = "cos2", 
+fviz_mfa_ind(res.mfa_agg_byval2, col.ind = "cos2", 
              gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
@@
 
-fviz_mfa_ind(res.mfa_agg_byval, 
+fviz_mfa_ind(res.mfa_agg_byval2, 
              habillage = "ssid", # color by groups
@@
 
-fviz_mfa_ind(res.mfa_agg_byval, 
+fviz_mfa_ind(res.mfa_agg_byval2, 
              # habillage = "stimIAPS2", # color by groups 
@@
 ```{r}
-fviz_mfa_ind(res.mfa_agg_byval, partial = "all") 
+fviz_mfa_ind(res.mfa_agg_byval2, partial = "all") 
 # If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:
@@
 ```{r}
-fviz_mfa_axes(res.mfa_agg_byval)
-
-```
+fviz_mfa_axes(res.mfa_agg_byval2)
+
+```

### 2021-12-08 Paper_Analyses_subj_obje_arousal.Rmd
Quick check on MFA and entropy for MI

@@
 fviz_mfa_axes(res.mfa_agg_byval2)
-
-```
+fviz_mfa_axes()
+
+```
+
+Mutual information
+
+```{r}
+install.packages("infotheo")
+library(infotheo)
+
+mutinformation(X, Y, method="emp")
+?mutinformation
+mutinformation(clustering_new_pre_PCA_2$arousal, clustering_new_pre_PCA_2$pup_basCor, 
+               method="mm")
+
+install.packages("entropy")
+
+entropy::mi.plugin(clustering_new_pre_PCA_2[,c(3,6)])
+```

### 2022-02-02 Subj_Obj_Ar_Bayes_Prev.Rmd
Initial stab at bayes prevalence
Try and estimate bayes prevalence

---
title: "Subj_Arousal_bayes_prevalence"
author: "Helio"
date: "02/02/2022"
output: html_document
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)

Subj_Arousal_bayes_prevalence
pupil_arousal_findings$pupil_from_ar_slope_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
                                                    Mean_gray_z  +
                                                    (1  | ssid)+
                                                    (0+ arousal_c | ssid),
                                                  REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT")%>%
                        subset(pupil_outlier == FALSE)%>%
                        subset(arousal_outler == FALSE))

summary(pupil_arousal_findings$pupil_from_ar_slope_vale)

```

```{r cars}
summary(cars)
```

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2022-02-02 Subj_Obj_Ar_Bayes_Prev.Rmd
adapted robins fucntions to do lm
adapted the functions to do lm instead of t.tests and do prevalence testing for multiple terms

@@
 
-summary(pupil_arousal_findings$pupil_from_ar_slope_vale)
+# remeber this does contain pratice, juts a leftover of an old name not to break code
+# db_full4new_stim_screen_pupil_nopract_no_outl$tNo
+
+# 1st we need to conduct the test within each participant and store the p value
+
+# let's do lm or lmer
+# stoe just the data we need
+db_full4new_stim_screen_pupil_nopract_no_outl<- db_full4new_stim_screen_pupil_nopract%>%
+                         subset(Group == "NT")%>%
+                        subset(pupil_outlier == FALSE)%>%
+                        subset(arousal_outler == FALSE)
+
+# 2.  LEVEL 1
+#
+
+# 2.1. Within-participant statistical test
+# This loop performs within-participant statistical test. Here, a t-test for
+# non-zero mean which is the simplest statistical test. In general, any
+# statistical test can be used at Level 1.
+Nsub = length(unique(db_full4new_stim_screen_pupil_nopract_no_outl$subject))
+
+subject_id<- unique(db_full4new_stim_screen_pupil_nopract_no_outl$subject)
+
+# p <- vector(mode="numeric",length=Nsub) #original
+# instead for our case create a matrix
+p <- matrix(data = NA, nrow = Nsub, ncol = 6) #
+
+# t
+# si = 1
+# rm(si)
+
+# p <- vector(mode="numeric",length=Nsub) # 
+# for( si in 1:Nsub ){
+#   t = t.test(rawdat[,si], mu=0)
+#   p[si] = t[3]
+# }
+
+# test
+# lmoutputtest<- summary(lm(pup_basCor ~ (valence_c* arousal_c) + Mean_gray_z,
+#    data = subset(db_full4new_stim_screen_pupil_nopract_no_outl,subject == 320)))
+# 
+# lmoutputtest
+# lmoutputtest[["coefficients"]][,4]
+
+# this fucntion fits a multiple regression per individual and returns the summary
+# then we stoe the p valus for each term in a matrix yo ue in level 2
+
+db_full4new_stim_screen_pupil_nopract_no_outl$pup_resid
+
+estimate <- matrix(data = NA, nrow = Nsub, ncol = 6) #
+
+for(si in 1:Nsub ){
+  t = summary(lm(pup_basCor ~ (valence_c* arousal_c) + Mean_gray_z,
+  data = subset(db_full4new_stim_screen_pupil_nopract_no_outl,
+                subject == subject_id[si])))
+  estimate[si,1:5] = t(matrix(t[["coefficients"]][,1])) 
+  estimate[si,6] = subject_id[si]  
+  # the first t transposes the data, not we need to change si to row
+  }
+
+  colnames(estimate)<- c("Intercept", "valence_c", "arousal_c", "Mean_gray_z", "valence:arousal", "sid")
+  # names(matrix(t(t[["coefficients"]])))
+  View(estimate)
+
+# save estimates and se
+
+# instead for our case create a matrix
+se <- matrix(data = NA, nrow = Nsub, ncol = 6) #
+
+for(si in 1:Nsub ){
+  t = summary(lm(pup_basCor ~ (valence_c* arousal_c) + Mean_gray_z,
+  data = subset(db_full4new_stim_screen_pupil_nopract_no_outl,
+                subject == subject_id[si])))
+  se[si,1:5] = t(matrix(t[["coefficients"]][,2])) 
+  se[si,6] = subject_id[si]  
+  # the first t transposes the data, not we need to change si to row
+  }
+
+  colnames(se)<- c("Intercept", "valence_c", "arousal_c", "Mean_gray_z", "valence:arousal", "sid")
+
+View(se)
+
+t$coefficients[,4]
+
+# now p values
+p <- matrix(data = NA, nrow = Nsub, ncol = 6) #
+
+for(si in 1:Nsub ){
+  t = summary(lm(pup_basCor ~ (valence_c* arousal_c) + Mean_gray_z,
+  data = subset(db_full4new_stim_screen_pupil_nopract_no_outl,
+                subject == subject_id[si])))
+  p[si,1:5] = t(matrix(t[["coefficients"]][,4])) 
+    p[si,6] = subject_id[si]  
+  # the first t transposes the data, not we need to change si to row
+  }
+
+  colnames(p)<- c("Intercept", "valence_c", "arousal_c", "Mean_gray_z", "valence:arousal", "sid")
+  # names(matrix(t(t[["coefficients"]])))
+  View(p)
+
+```
+
+```{r}
+
+# p holds p-values of test for each participant
+alpha = 0.05  
+indsig = p<alpha
+
+# the binary variable indsig indicates whether the within-participant
+# t-test is, or not, significant for each participant (1 entry for each
+# participant)
+
+# 2.2. Loading within-participant statistical test.
+# You can also load your own within-participant statistical test results here.
+# Load binary results into binary indsig vector with one entry per participant. 
+# See also example_csv.R for an example.
+
+#
+# 3.  LEVEL 2
+#
+
+# Bayesian prevalence inference is performed with three numbers: 
+# k, the number of significant participants (e.g. sum of binary indicator
+# variable)
+# n, the number of participants in the sample
+# alpha, the false positive rate
+n <- Nsub
+# table(indsig)
+
+# lets start with valence
+k_2 <- sum(indsig[,2])
+table(indsig[,2])
+
+?binom.test
+binom.test(k_2, 55, 0.05, alternative="two.sided",  )
+
+# plot posterior distribution of population prevalence
+# install.packages("HDInterval")
+library(HDInterval) # this package is needed
+xvals <- seq(0, 1, .01)
+bayesprev_posterior()
+pdf_2 <- bayesprev_posterior(xvals, k_2, n) # function needed
+pdf_2
+
+plot(xvals, pdf_2, type ="l", xlab = expression(gamma), 
+     ylab ="Posterior density", lwd=3)
+
+# Add the MAP estimate as a point
+# MAP = Maximum
+
+xmap = bayesprev_map(k_2, n)
+pmap = bayesprev_posterior(xmap, k_2, n)
+points(xmap, pmap, cex =2, col= "red", pch=16)
+
+# Add the .95 lower bound as a vertical line
+xbound = bayesprev_bound(0.95, k_2, n)
+pbound = bayesprev_posterior(xbound, k_2, n)
+lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)
+
+# Add the 0.96 HPDI
+int = bayesprev_hpdi(0.96, k_2, n)
+i1 = int[1]
+i2 = int[2]
+h1 = bayesprev_posterior(i1, k_2, n)
+h2 = bayesprev_posterior(i2, k_2, n)
+lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
+
+# try arosual
+
+```
+
+```{r}
+k_3 <- sum(indsig[,3])
+k_3
+# k_3/55 (20%)
+12/55
+
+binom.test(k_3, 55, 0.05, alternative="two.sided") 
+# plot posterior distribution of population prevalence
+# install.packages("HDInterval")
+library(HDInterval) # this package is needed
+xvals <- seq(0, 1, .01)
+pdf_3 <- bayesprev_posterior(xvals, k_3, n) # function needed
+pdf_3
+
+plot(xvals, pdf_3, type ="l", xlab = expression(gamma), 
+     ylab ="Posterior density", lwd=3)
+
+# Add the MAP estimate as a point
+# MAP = Maximum
+
+xmap = bayesprev_map(k_3, n)
+pmap = bayesprev_posterior(xmap, k_3, n)
+points(xmap, pmap, cex =2, col= "red", pch=16)
+
+# Add the .95 lower bound as a vertical line
+xbound = bayesprev_bound(0.95, k_3, n)
+pbound = bayesprev_posterior(xbound, k_3, n)
+lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)
+
+# Add the 0.96 HPDI
+int = bayesprev_hpdi(0.96, k_3, n)
+i1 = int[1]
+i2 = int[2]
+h1 = bayesprev_posterior(i1, k_3, n)
+h2 = bayesprev_posterior(i2, k_3, n)
+lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
+
+```
+
+brighteness
+```{r}
+k_4 <- sum(indsig[,4])
+k_4/55
+
+# plot posterior distribution of population prevalence
+
+xvals <- seq(0, 1, .01)
+pdf_4 <- bayesprev_posterior(xvals, k_4, n) # function needed
+pdf_4
+
+plot(xvals, pdf_4, type ="l", xlab = expression(gamma), 
+     ylab ="Posterior density", lwd=3)
+
+# Add the MAP estimate as a point
+# MAP = Maximum
+
+xmap = bayesprev_map(k_4, n)
+pmap = bayesprev_posterior(xmap, k_4, n)
+points(xmap, pmap, cex =2, col= "red", pch=16)
+
+# Add the .95 lower bound as a vertical line
+xbound = bayesprev_bound(0.95, k_4, n)
+pbound = bayesprev_posterior(xbound, k_4, n)
+lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)
+
+# Add the 0.96 HPDI
+int = bayesprev_hpdi(0.96, k_4, n)
+i1 = int[1]
+i2 = int[2]
+h1 = bayesprev_posterior(i1, k_4, n)
+h2 = bayesprev_posterior(i2, k_4, n)
+lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
+
+# is the p value just a bonomial test on the counts of significants and non significant results?
+```
+
+<!-- interaction -->
+
+<!-- arousal valence-->
+
+```{r}
+k_5 <- sum(indsig[,5])
+
+# plot posterior distribution of population prevalence
+
+xvals <- seq(0, 1, .01)
+pdf_5 <- bayesprev_posterior(xvals, k_5, n) # function needed
+pdf_5
+
+plot(xvals, pdf_5, type ="l", xlab = expression(gamma), 
+     ylab ="Posterior density", lwd=3)
+
+# Add the MAP estimate as a point
+# MAP = Maximum
+
+xmap = bayesprev_map(k_5, n)
+pmap = bayesprev_posterior(xmap, k_5, n)
+points(xmap, pmap, cex =2, col= "red", pch=16)
+
+# Add the .95 lower bound as a vertical line
+xbound = bayesprev_bound(0.95, k_5, n)
+pbound = bayesprev_posterior(xbound, k_5, n)
+lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)
+
+# Add the 0.96 HPDI
+int = bayesprev_hpdi(0.96, k_5, n)
+i1 = int[1]
+i2 = int[2]
+h1 = bayesprev_posterior(i1, k_5, n)
+h2 = bayesprev_posterior(i2, k_5, n)
+lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
+
+```
+
+```{r}
+#    Load the nonlinear equation solver
+   library(nleqslv)
+ #  Load the required functions from the current working directory
+source("bayesprev.R")
+
+  # load the data
+  sigdat = p
+    # read.csv("example_data.csv", header =FALSE);
+
+  alpha = 0.05                       #   this specifies the alpha value used for the within-unit tests
+  Ntests = nrow(sigdat);        #   number of tests (e.g. participants)
+  Nsigtests_3 = sum(sigdat[,3]);    #   number of significant tests
+
+  # Plot the posterior  pdf for the population prevalence proportion
+
+  xvals <- seq(0, 1, .01)
+  pdf_3.1 <- bayesprev_posterior(xvals, Nsigtests_3, Ntests)
+  plot(xvals, pdf_3.1, type ="l", xlab = expression(gamma), ylab ="Posterior density", lwd=3)
+
+  # 0.95 lower bound for the population prevalence proportion
+
+  b = bayesprev_bound(0.05, Nsigtests_3, Ntests)
+  print(b)
+
+  # MAP maximum a posteriori [MAP estimate of the population prevalence proportion
+
+  m = bayesprev_map(Nsigtests_3, Ntests)
+  print(m)
+
+  # 96% HPDI for the population prevalence proportion highest posterior density intervals (HPDIs)
+
+  int = bayesprev_hpdi(0.96, Nsigtests_3, Ntests)
+  print(int)
+
+  # Example of possible Bayesian prevalence analyses on a common plot.
+
+  xvals <- seq(0, 1, .01)
+  pdf_3.1 <- bayesprev_posterior(xvals, Nsigtests_3, Ntests)
+  plot(xvals, pdf_3.1, type ="l", xlab = expression(gamma), ylab ="Posterior density", lwd=3)
+
+  # Add the MAP estimate as a point
+
+  xmap = bayesprev_map(Nsigtests_3, Ntests)
+  pmap = bayesprev_posterior(xmap, Nsigtests_3, Ntests)
+  points(xmap, pmap, cex =2, col= "red", pch=16)
+
+  # Add the .95 lower bound as a vertical line
+
+  xbound = bayesprev_bound(0.05, Nsigtests_3, Ntests)
+  pbound = bayesprev_posterior(xbound, Nsigtests_3, Ntests)
+  lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)
+
+  # Add the 0.96 HPDI
+
+  int = bayesprev_hpdi(0.96, Nsigtests_3, Ntests)
+  i1 = int[1]
+  i2 = int[2]
+  h1 = bayesprev_posterior(i1, Nsigtests_3, Ntests)
+  h2 = bayesprev_posterior(i2, Nsigtests_3, Ntests)
+  lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
+
+```
+
+valence
+```{r}
+
+```
+
+```{r}
+
+range(db_full4new_stim_screen_pupil_nopract_no_outl$pup_basCor)
+?plot()
+  plot(db_full4new_stim_screen_pupil_nopract_no_outl$pup_basCor, 
+       type ="l", xlab = expression(gamma), ylab ="Posterior density", lwd=3)
+
+testdensity<-density(db_full4new_stim_screen_pupil_nopract_no_outl$pup_basCor, n = 55)
+
+db_full4new_stim_screen_pupil_nopract_no_outl<- db_full4new_stim_screen_pupil_nopract_no_outl%>%
+  group_by(ssid)%>%
+  mutate(testdensity_x = density(pup_basCor, n = 1)$x,
+         testdensity_y = density(pup_basCor, n = 1)$y)
+
+db_full4new_stim_screen_pupil_nopract_no_outl%>%
+  subset(ssid == 300)%>%
+  # group_by(ssid)%>%
+  mutate(testdensity_x = density(pup_basCor)$x,
+         testdensity_y = density(pup_basCor)$y)
+testdensity$x
+testdensity$y
+
+?density
+testdensity
+nrow(db_full4new_stim_screen_pupil_nopract_no_outl)
+
+db_full4new_stim_screen_pupil_nopract_no_outl%>%
+    subset(subject>303)%>%
+    group_by(ssid)%>%
+    mutate(density_1= density(pup_basCor))
+
+install.packages('scales')
+
+scales::rescale(0)
+db_full4new_stim_screen_pupil_nopract_no_outl%>%
+  group_by(ssid)%>%
+  mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE))%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  mutate(rescaled_y = scales::rescale_max(testdensity_y, to = c(0,.4)))%>%
+  ggplot(aes(x = pup_basCor))+
+  stat_function(fun=dgamma, args=list(shape=1, scale=.5))+
+  # geom_density()+
+  geom_jitter(aes( x = pup_basCor_mean, y = rescaled_y),
+              width = .1, height = 0)
+  # stat_function(fun=dgamma, args=list(shape=1, scale=.5))
+  geom_jitter()
+  stat_summary(geom = "pointrange")
+
+testdensity$data.name
+
+ c(density(db_full4new_stim_screen_pupil_nopract_no_outl$ssid,n=n)$x, density(bar,n=n)$x)
 

### 2022-02-02 Paper_Analyses_subj_obje_arousal.Rmd
initial stab at the timeseries application

@@
                         subset(arousal_outler == FALSE))
+
+# fit pupil response froma arousal slope
+
+table(is.na(db_full4new_stim_screen_pupil_nopract$valence_c))
+library(lmerTest)
+library(tidyverse)
+pupil_arousal_findings$pupil_from_ar_slope_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
+                                                    Mean_gray_z  +
+                                                    (1  | ssid)+
+                                                    (0+ arousal_c | ssid),
+                                                  REML = FALSE,
+                      data = db_full4new_stim_screen_pupil_nopract%>%
+                         subset(Group == "NT")%>%
+                        subset(pupil_outlier == FALSE)%>%
+                        subset(arousal_outler == FALSE))
+
+summary(pupil_arousal_findings$pupil_from_ar_slope_vale)
 

### 2022-02-03 Paper_Analyses_subj_obje_arousal.Rmd
timeseries bayes prevalence on pupil
added a way to visualise the bayesian prevalence on the timeseries of pupil data

@@
 
-table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_arousal2))
-
-mediansplit_sample_arousal2
-
-table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$Group))
-
-tmp.df4_full_stim_downs_jun2021_60bins %>%
-  subset(Group == "NT")%>%
-  # subset(!is.na(mediansplit_sample_arousal2))%>%
-  ggplot(aes(x = timerezero3, y = pup_basCor))+
-  stat_smooth(aes(group= mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), fun = mean,geom = "line",
-               se = F, alpha = .1, size = 1.5)+
-  stat_smooth(aes(group=mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), size = 3)+  
-theme_classic()+
-  ylab("Pupil size (z)")+
-  xlab("Time (s)")+
-  # p$graphstyle+
-  scale_color_brewer(palette = "Dark2")+
-  xlim(0,6)+
-   facet_grid(~mediansplit_sample_valence2)
-
 ```{r}
@@
 # unique(tmp.df4_full_stim_downs_jun2021_60bins$)
+
 table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_c))

### 2022-02-03 Subj_Obj_Ar_Bayes_Prev1.Rmd
timeseries bayes prevalence on pupil
added a way to visualise the bayesian prevalence on the timeseries of pupil data

---
title: "Subj_Arousal_bayes_prevalence"
author: "Helio"
date: "02/02/2022"
output: html_document
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)

Subj_Arousal_bayes_prevalence
pupil_arousal_findings$pupil_from_ar_slope_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
                                                    Mean_gray_z  +
                                                    (1  | ssid)+
                                                    (0+ arousal_c | ssid),
                                                  REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT")%>%
                        subset(pupil_outlier == FALSE)%>%
                        subset(arousal_outler == FALSE))

# remeber this does contain pratice, juts a leftover of an old name not to break code
# db_full4new_stim_screen_pupil_nopract_no_outl$tNo

# 1st we need to conduct the test within each participant and store the p value

# let's do lm or lmer
# stoe just the data we need
db_full4new_stim_screen_pupil_nopract_no_outl<- db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT")%>%
                        subset(pupil_outlier == FALSE)%>%
                        subset(arousal_outler == FALSE)

# 2.  LEVEL 1
#

# 2.1. Within-participant statistical test
# This loop performs within-participant statistical test. Here, a t-test for
# non-zero mean which is the simplest statistical test. In general, any
# statistical test can be used at Level 1.
Nsub = length(unique(db_full4new_stim_screen_pupil_nopract_no_outl$subject))

subject_id<- unique(db_full4new_stim_screen_pupil_nopract_no_outl$subject)

# p <- vector(mode="numeric",length=Nsub) #original
# instead for our case create a matrix
p <- matrix(data = NA, nrow = Nsub, ncol = 6) #

# t
# si = 1
# rm(si)

# p <- vector(mode="numeric",length=Nsub) # 
# for( si in 1:Nsub ){
#   t = t.test(rawdat[,si], mu=0)
#   p[si] = t[3]
# }

# test
# lmoutputtest<- summary(lm(pup_basCor ~ (valence_c* arousal_c) + Mean_gray_z,
#    data = subset(db_full4new_stim_screen_pupil_nopract_no_outl,subject == 320)))
# 
# lmoutputtest
# lmoutputtest[["coefficients"]][,4]

# this fucntion fits a multiple regression per individual and returns the summary
# then we stoe the p valus for each term in a matrix yo ue in level 2

db_full4new_stim_screen_pupil_nopract_no_outl$pup_resid

estimate <- matrix(data = NA, nrow = Nsub, ncol = 6) #

for(si in 1:Nsub ){
  t = summary(lm(pup_basCor ~ (valence_c* arousal_c) + Mean_gray_z,
  data = subset(db_full4new_stim_screen_pupil_nopract_no_outl,
                subject == subject_id[si])))
  estimate[si,1:5] = t(matrix(t[["coefficients"]][,1])) 
  estimate[si,6] = subject_id[si]  
  # the first t transposes the data, not we need to change si to row
  }

  colnames(estimate)<- c("Intercept", "valence_c", "arousal_c", "Mean_gray_z", "valence:arousal", "sid")
  # names(matrix(t(t[["coefficients"]])))
  View(estimate)

# save estimates and se

# instead for our case create a matrix
se <- matrix(data = NA, nrow = Nsub, ncol = 6) #

for(si in 1:Nsub ){
  t = summary(lm(pup_basCor ~ (valence_c* arousal_c) + Mean_gray_z,
  data = subset(db_full4new_stim_screen_pupil_nopract_no_outl,
                subject == subject_id[si])))
  se[si,1:5] = t(matrix(t[["coefficients"]][,2])) 
  se[si,6] = subject_id[si]  
  # the first t transposes the data, not we need to change si to row
  }

  colnames(se)<- c("Intercept", "valence_c", "arousal_c", "Mean_gray_z", "valence:arousal", "sid")

View(se)

t$coefficients[,4]

# now p values
p <- matrix(data = NA, nrow = Nsub, ncol = 6) #

for(si in 1:Nsub ){
  t = summary(lm(pup_basCor ~ (valence_c* arousal_c) + Mean_gray_z,
  data = subset(db_full4new_stim_screen_pupil_nopract_no_outl,
                subject == subject_id[si])))
  p[si,1:5] = t(matrix(t[["coefficients"]][,4])) 
    p[si,6] = subject_id[si]  
  # the first t transposes the data, not we need to change si to row
  }

  colnames(p)<- c("Intercept", "valence_c", "arousal_c", "Mean_gray_z", "valence:arousal", "sid")
  # names(matrix(t(t[["coefficients"]])))
  View(p)
```

```{r}

# p holds p-values of test for each participant
alpha = 0.05  
indsig = p<alpha

# the binary variable indsig indicates whether the within-participant
# t-test is, or not, significant for each participant (1 entry for each
# participant)

# 2.2. Loading within-participant statistical test.
# You can also load your own within-participant statistical test results here.
# Load binary results into binary indsig vector with one entry per participant. 
# See also example_csv.R for an example.

#
# 3.  LEVEL 2
#

# Bayesian prevalence inference is performed with three numbers: 
# k, the number of significant participants (e.g. sum of binary indicator
# variable)
# n, the number of participants in the sample
# alpha, the false positive rate
n <- Nsub
# table(indsig)

# lets start with valence
k_2 <- sum(indsig[,2])
table(indsig[,2])

?binom.test
binom.test(k_2, 55, 0.05, alternative="two.sided",  )

# plot posterior distribution of population prevalence
# install.packages("HDInterval")
library(HDInterval) # this package is needed
xvals <- seq(0, 1, .01)
bayesprev_posterior()
pdf_2 <- bayesprev_posterior(xvals, k_2, n) # function needed
pdf_2

plot(xvals, pdf_2, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

# Add the MAP estimate as a point
# MAP = Maximum

xmap = bayesprev_map(k_2, n)
pmap = bayesprev_posterior(xmap, k_2, n)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_2, n)
pbound = bayesprev_posterior(xbound, k_2, n)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_2, n)
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_2, n)
h2 = bayesprev_posterior(i2, k_2, n)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

# try arosual

```

```{r}
k_3 <- sum(indsig[,3])
k_3
# k_3/55 (20%)
12/55

binom.test(k_3, 55, 0.05, alternative="two.sided") 
# plot posterior distribution of population prevalence
# install.packages("HDInterval")
library(HDInterval) # this package is needed
xvals <- seq(0, 1, .01)
pdf_3 <- bayesprev_posterior(xvals, k_3, n) # function needed
pdf_3

plot(xvals, pdf_3, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

# Add the MAP estimate as a point
# MAP = Maximum

xmap = bayesprev_map(k_3, n)
pmap = bayesprev_posterior(xmap, k_3, n)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_3, n)
pbound = bayesprev_posterior(xbound, k_3, n)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_3, n)
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_3, n)
h2 = bayesprev_posterior(i2, k_3, n)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

```

brighteness
```{r}
k_4 <- sum(indsig[,4])
k_4/55

# plot posterior distribution of population prevalence

xvals <- seq(0, 1, .01)
pdf_4 <- bayesprev_posterior(xvals, k_4, n) # function needed
pdf_4

plot(xvals, pdf_4, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

# Add the MAP estimate as a point
# MAP = Maximum

xmap = bayesprev_map(k_4, n)
pmap = bayesprev_posterior(xmap, k_4, n)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_4, n)
pbound = bayesprev_posterior(xbound, k_4, n)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_4, n)
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_4, n)
h2 = bayesprev_posterior(i2, k_4, n)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

# is the p value just a bonomial test on the counts of significants and non significant results?
```

<!-- interaction -->

<!-- arousal valence-->

```{r}
k_5 <- sum(indsig[,5])

# plot posterior distribution of population prevalence

xvals <- seq(0, 1, .01)
pdf_5 <- bayesprev_posterior(xvals, k_5, n) # function needed
pdf_5

plot(xvals, pdf_5, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

# Add the MAP estimate as a point
# MAP = Maximum

xmap = bayesprev_map(k_5, n)
pmap = bayesprev_posterior(xmap, k_5, n)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_5, n)
pbound = bayesprev_posterior(xbound, k_5, n)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_5, n)
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_5, n)
h2 = bayesprev_posterior(i2, k_5, n)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

```

Now Level 2 test

```{r}
#    Load the nonlinear equation solver
   library(nleqslv)
 #  Load the required functions from the current working directory
source("bayesprev.R")

  # load the data
  sigdat = p
    # read.csv("example_data.csv", header =FALSE);

  alpha = 0.05                       #   this specifies the alpha value used for the within-unit tests
  Ntests = nrow(sigdat);        #   number of tests (e.g. participants)
  Nsigtests_3 = sum(sigdat[,3]);    #   number of significant tests

  # Plot the posterior  pdf for the population prevalence proportion

  xvals <- seq(0, 1, .01)
  pdf_3.1 <- bayesprev_posterior(xvals, Nsigtests_3, Ntests)
  plot(xvals, pdf_3.1, type ="l", xlab = expression(gamma), ylab ="Posterior density", lwd=3)

  # 0.95 lower bound for the population prevalence proportion

  b = bayesprev_bound(0.05, Nsigtests_3, Ntests)
  print(b)

  # MAP maximum a posteriori [MAP estimate of the population prevalence proportion

  m = bayesprev_map(Nsigtests_3, Ntests)
  print(m)

  # 96% HPDI for the population prevalence proportion highest posterior density intervals (HPDIs)

  int = bayesprev_hpdi(0.96, Nsigtests_3, Ntests)
  print(int)

  # Example of possible Bayesian prevalence analyses on a common plot.

  xvals <- seq(0, 1, .01)
  pdf_3.1 <- bayesprev_posterior(xvals, Nsigtests_3, Ntests)
  plot(xvals, pdf_3.1, type ="l", xlab = expression(gamma), ylab ="Posterior density", lwd=3)

  # Add the MAP estimate as a point

  xmap = bayesprev_map(Nsigtests_3, Ntests)
  pmap = bayesprev_posterior(xmap, Nsigtests_3, Ntests)
  points(xmap, pmap, cex =2, col= "red", pch=16)

  # Add the .95 lower bound as a vertical line

  xbound = bayesprev_bound(0.05, Nsigtests_3, Ntests)
  pbound = bayesprev_posterior(xbound, Nsigtests_3, Ntests)
  lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

  # Add the 0.96 HPDI

  int = bayesprev_hpdi(0.96, Nsigtests_3, Ntests)
  i1 = int[1]
  i2 = int[2]
  h1 = bayesprev_posterior(i1, Nsigtests_3, Ntests)
  h2 = bayesprev_posterior(i2, Nsigtests_3, Ntests)
  lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

```

```{r}

range(db_full4new_stim_screen_pupil_nopract_no_outl$pup_basCor)
?plot()
  plot(db_full4new_stim_screen_pupil_nopract_no_outl$pup_basCor, 
       type ="l", xlab = expression(gamma), ylab ="Posterior density", lwd=3)

testdensity<-density(db_full4new_stim_screen_pupil_nopract_no_outl$pup_basCor, n = 55)

db_full4new_stim_screen_pupil_nopract_no_outl<- db_full4new_stim_screen_pupil_nopract_no_outl%>%
  group_by(ssid)%>%
  mutate(testdensity_x = density(pup_basCor, n = 1)$x,
         testdensity_y = density(pup_basCor, n = 1)$y)

db_full4new_stim_screen_pupil_nopract_no_outl%>%
  subset(ssid == 300)%>%
  # group_by(ssid)%>%
  mutate(testdensity_x = density(pup_basCor)$x,
         testdensity_y = density(pup_basCor)$y)
testdensity$x
testdensity$y

?density
testdensity
nrow(db_full4new_stim_screen_pupil_nopract_no_outl)

db_full4new_stim_screen_pupil_nopract_no_outl%>%
    subset(subject>303)%>%
    group_by(ssid)%>%
    mutate(density_1= density(pup_basCor))

install.packages('scales')

scales::rescale(0)

bind_bayes1 <- left_join(as.data.frame(p), as.data.frame(estimate), by = "sid")
bind_bayes2 <- left_join(as.data.frame(bind_bayes1), as.data.frame(se), by = "sid")
bind_bayes2

bind_test<- bind_cols(p, estimate, se)

db_full4new_stim_screen_pupil_nopract_no_outl%>%
  group_by(ssid)%>%
  mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  mutate(rescaled_y = scales::rescale_max(testdensity_y, to = c(0,.4)))%>%
  ggplot(aes(x = pup_basCor))+
  # stat_function(fun=dgamma, args=list(shape=1, scale=.5))+
  geom_jitter(aes( x = pup_basCor_mean, y = rescaled_y),
              width = .1, height = 0)

bind_bayes2$xdensity<- testdensity[["x"]]
bind_bayes2$ydensity<- testdensity[["y"]]

testgensity

bind_bayes2 %>%

  group_by(sid)%>%
  # mutate(testdensity_x = density(arousal_c.x, n = 2)$x,
  #        testdensity_y = density(arousal_c.x, n = 2)$y)%>%

  ggplot(aes(x = arousal_c.x))+
   # stat_function(fun=dgamma, args=list(shape=1))
  geom_density() +
  geom_point(aes(x = xdensity, y =ydensity))

bind_bayes2%>%
  ggplot(aes(as.numeric(as.factor(as.integer(sid))), arousal_c.y, color = arousal_c.x<.05))+
  geom_point()+
  geom_pointrange(aes(ymin = arousal_c.y- arousal_c, ymax = arousal_c.y+ arousal_c ))

bind_bayes2%>%
  ggplot(aes(as.numeric(as.factor(as.integer(sid))), valence_c.y, color = valence_c.x<.05))+
  geom_point()+
  geom_pointrange(aes(ymin = valence_c.y- valence_c, ymax = valence_c.y+ valence_c ))

bind_bayes2%>%
  ggplot(aes(as.numeric(as.factor(as.integer(sid))), `valence:arousal.y` , 
             color = `valence:arousal.x` <.05))+
  geom_point()+
  geom_pointrange(aes(ymin = `valence:arousal.y` - `valence:arousal`, 
                      ymax = `valence:arousal.y` + `valence:arousal` ))

```

Try with the timecourse now.
start with only one predictor - arousal

then plot the effect size in terms of a heatmap

```{r}

tmp.df4_full_stim_downs_jun2021_60bins_NT<- subset(tmp.df4_full_stim_downs_jun2021_60bins,
                                    Group == "NT")

b = 1

subject_id2<- unique(tmp.df4_full_stim_downs_jun2021_60bins_NT$ssid)
s = 1

b = 1

testtimecourseforbayprev<-   subset(tmp.df4_full_stim_downs_jun2021_60bins_NT,
                                    ssid =  subject_id[s],
                                    timebin_no == nbins[b])

unique(testtimecourseforbayprev$timebin_no)

tmp.df4_full_stim_downs_jun2021_60bins_NT%>%
  group_by(ssid, timebin_no)%>%
  summarise_at(c("pup_basCor"), mean, na.rm = TRUE)

# try and figure out how many timebins per participant we need to cerate to hold data
tmp.df4_full_stim_downs_jun2021_60bins_NT%>%
  subset(timebin_no<56)%>%
  group_by(ssid, timebin_no)%>%
  summarise_at(c("pup_basCor"), mean, na.rm = TRUE) %>%
    group_by(ssid)%>%
  mutate(n_timebin = n())
  # total of 3025 rows
  #  summarise_at(c("pup_basCor", "n_timebin"), mean, na.rm = TRUE)

tmp.df4_full_stim_downs_jun2021_60bins_NT_55<- tmp.df4_full_stim_downs_jun2021_60bins_NT%>%
  subset(timebin_no<56)

# create the dataset to hold participant, timebin code, statistics for each timebin
# seems like the majority have 55

nsubj_2 = 55
n_bins_2 = 55

timecourse_60bin_result_df_for_bp <-timecourse_60bin_result_df <- data.frame(
  ssid = rep(NA, nsubj_2*n_bins_2),
  timebins= rep(NA, nsubj_2*n_bins_2), 
                                       Estimate_ar= rep(NA, nsubj_2*n_bins_2), 
                                       se_ar= rep(NA, nsubj_2*n_bins_2), 
                                       t_ar=rep(NA, nsubj_2*n_bins_2), 
                                       p_ar=rep(NA, nsubj_2*n_bins_2)
                                       # Estimate_vl= rep(NA, nsubj_2*n_bins_2), 
                                       # t_vl=rep(NA, nsubj_2*n_bins_2), 
                                       # p_vl=rep(NA, nsubj_2*n_bins_2),
                                       # Estimate_br= rep(NA, nsubj_2*n_bins_2), 
                                       # t_br= rep(NA, nsubj_2*n_bins_2), 
                                       # p_br= rep(NA, nsubj_2*n_bins_2),
                                       # Estimate_ar_vl= rep(NA, nsubj_2*n_bins_2), 
                                       # t_ar_vl= rep(NA, nsubj_2*n_bins_2), 
                                       # p_ar_vl= rep(NA, nsubj_2*n_bins_2),
                                       # cov= as.character(rep(NA, nsubj_2*n_bins_2)
                                                         )
timecourse_60bin_result_df_for_bp

# now fit level 1 within individual tests
0 = 1 # remember to always rezero it
s=2
b = 3
# nbins

n_bins_3<- unique(tmp.df4_full_stim_downs_jun2021_60bins_NT_55$timebin_no)
subject_id_3<- unique(tmp.df4_full_stim_downs_jun2021_60bins_NT_55$ssid)

s = 1
b = 2

for (s in 1:length(subject_id2)) {
  for (b in 1:length(n_bins_3)) {

    message(sprintf("$$$$$RUNING ssid %s timebin %i", subject_id2[s], n_bins_3[b]))
        lm_bin_pup  <- lm(pup_basCor ~ arousal_c,
                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins_NT_55,
                                    ssid ==  subject_id2[s] &
                                    timebin_no == n_bins_3[b]))
        # save the summary    
        lm_bin_pup_summary<- summary(lm_bin_pup)

        # store statistics for particiapnt and timebin
        timecourse_60bin_result_df_for_bp[i,1]<- subject_id[s] #ssid 
        timecourse_60bin_result_df_for_bp[i,2]<- n_bins_3[b] #timebin
          # timecourse_60bin_result_df[b,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
            timecourse_60bin_result_df_for_bp[i,3] <- lm_bin_pup_summary$coefficients[2] #estimate, note to avoid intercept start on 2 for estimate, then 4 for se, the 6 for t and so on
            timecourse_60bin_result_df_for_bp[i,4] <- lm_bin_pup_summary$coefficients[4] #se
            timecourse_60bin_result_df_for_bp[i,5] <- lm_bin_pup_summary$coefficients[6] #t
             timecourse_60bin_result_df_for_bp[i,6] <- lm_bin_pup_summary$coefficients[8] #p

       i = i+1
     # b = b+1
  }

  }

timecourse_60bin_result_df_for_bp<- timecourse_60bin_result_df_for_bp[442:nrow(timecourse_60bin_result_df_for_bp),]

# heatmap

library(viridis)
install.packages('hrbrthemes')

library(hrbrthemes)
timecourse_60bin_result_df_for_bp%>%
  ggplot(aes(y = as.factor(as.numeric(ssid)), x = timebins))+
  geom_tile(aes(fill = Estimate_ar))+
  scale_fill_viridis(discrete=FALSE) 
  theme_ipsum()
  theme_classic()

  ?p.adjust
  timecourse_60bin_result_df_for_bp$p_ar_adjust<- p.adjust(timecourse_60bin_result_df_for_bp$p_ar,
                                                           method = "holm", n = 55)

timecourse_60bin_result_df_for_bp<-  timecourse_60bin_result_df_for_bp%>%
    group_by(ssid)%>%
    mutate(p_adjusted = p.adjust(p_ar, method = "holm", n = n()))

timecourse_60bin_result_df_for_bp %>%
  ggplot(aes(y = as.factor(as.numeric(ssid)), x = timebins/10))+
  geom_tile(aes(fill = p_adjusted))+
  scale_fill_viridis(discrete=FALSE) +
  # theme_ipsum()
  theme_classic()

timecourse_60bin_result_df_for_bp %>%
  ggplot(aes(x = timebins/10, y = t_ar))+
  stat_summary(geom = "line", size = 2)+
  stat_summary( geom = "errorbar", mult = 1) 
  stat_summary()

  geom_tile(aes(fill = p_adjusted))+
  scale_fill_viridis(discrete=FALSE) +
  # theme_ipsum()
  theme_classic()

  timecourse_60bin_result_df_for_bp %>%
  ggplot(aes(x = timebins/10, y = t_ar))+
  stat_summary(geom = "line", size = 2)+
  stat_summary( geom = "errorbar", mult = 1) 
  stat_summary()

  geom_tile(aes(fill = p_adjusted))+
  scale_fill_viridis(discrete=FALSE) +
  # theme_ipsum()
  theme_classic()

  #########
  p

  # flag max
  timecourse_60bin_result_df_for_bp<- timecourse_60bin_result_df_for_bp%>%
    group_by(ssid)%>%
   mutate(max_T =  max(t_ar))

  # new t = 3.5

timecourse_60bin_result_df_for_bp%>%
  group_by(ssid)%>%
  summarize_if(is.numeric, min, na.rm = TRUE)%>%
  ggplot(aes(x = as.factor(as.numeric(ssid)), y = p_adjusted))+
  geom_point(size = 2, color = "blue")+
  geom_segment( aes(x=as.factor(as.numeric(ssid)), xend=as.factor(as.numeric(ssid)), 
                    y=0, yend=p_adjusted),color = "blue")+
  geom_hline(yintercept = .05, linetype = "dashed")+
  geom_hline(yintercept = .1, linetype = "dashed", color = "red")+
  coord_flip()+
  theme_bw()

timecourse_60bin_result_df_for_bp_minp<- timecourse_60bin_result_df_for_bp%>%
  group_by(ssid)%>%
  summarize_at(c("p_adjusted"), min, na.rm = TRUE)%>%
  mutate(indsign = p_adjusted<.05)

View(timecourse_60bin_result_df_for_bp_minp)

##############################

# test prevalence

# step 2 - count significance

# p holds p-values of test for each participant
alpha = 0.05

# the binary variable indsig indicates whether the within-participant
# t-test is, or not, significant for each participant (1 entry for each
# participant)

# 2.2. Loading within-participant statistical test.
# You can also load your own within-participant statistical test results here.
# Load binary results into binary indsig vector with one entry per participant. 
# See also example_csv.R for an example.

#
# 3.  LEVEL 2
#

# Bayesian prevalence inference is performed with three numbers: 
# k, the number of significant participants (e.g. sum of binary indicator
# variable)
# n, the number of participants in the sample
# alpha, the false positive rate

unique(timecourse_60bin_result_df_for_bp_minp$ssid)
n <- nrow(timecourse_60bin_result_df_for_bp_minp)
# table(indsig)

# lets start with valence
k_3_pupilts <- sum(timecourse_60bin_result_df_for_bp_minp$indsign)

# ?binom.test - added by helio - is the number0f significant particpants significant against chance
binom.test(k_3_pupilts, n, 0.05, alternative="two.sided")  #pp-value = 0.01932

# plot posterior distribution of population prevalence
# install.packages("HDInterval")
library(HDInterval) # this package is needed
xvals <- seq(0, 1, .01)

# bayesprev_posterior()
pdf_3_pupts <- bayesprev_posterior(xvals, k_3_pupilts, n) # function needed
pdf_3_pupts

plot(xvals, pdf_3_pupts, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

# Add the MAP estimate as a point
# MAP = Maximum

xmap = bayesprev_map(k_3_pupilts, n)
pmap = bayesprev_posterior(xmap, k_3_pupilts, n)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_3_pupilts, n)
pbound = bayesprev_posterior(xbound, k_3_pupilts, n)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_3_pupilts, n)
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_3_pupilts, n)
h2 = bayesprev_posterior(i2, k_3_pupilts, n)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

# try arosual

# get prevalenc for the timeseries
# for ech bin do the count
# we need xmap - center pf the MAP on x axis
# and k - # k, the number of significant participants (e.g. sum of binary indicator
# variable)

# create a dataframe fro timebins

timecourse_60bin_forprevalence <-timecourse_60bin_result_df <- data.frame(
  # ssid = rep(NA, n_bins_2), # we just need bins not sids
  timebins= rep(NA, n_bins_2), 
  k_tb= rep(NA, n_bins_2), 
  xmap = rep(NA, n_bins_2),
  pmap = rep(NA, n_bins_2),
  # Add the .95 lower bound as a vertical line
xbound = rep(NA, n_bins_2),
  # bayesprev_bound(0.95, k_3_pupilts, n)
pbound = rep(NA, n_bins_2),
  # bayesprev_posterior(xbound, k_3_pupilts, n)
    # bayesprev_posterior(xmap, k_3_pupilts, n)
t = rep(NA, n_bins_2))

# create the k in advance

timecourse_60bin_result_df_for_bp<- timecourse_60bin_result_df_for_bp %>%
  group_by(timebins)%>%
  mutate(k_3_pupilts = sum(p_adjusted<alpha),
        xmap = bayesprev_map(k_3_pupilts, n()),
        pmap = bayesprev_posterior(xmap, k_3_pupilts, n()),
        i1 = bayesprev_hpdi(0.96, k_3_pupilts, n)[1],
         i2 = bayesprev_hpdi(0.96, k_3_pupilts, n)[2],
        )

  for (b in 1:length(n_bins_3)) {
    # for (s in 1:length(subject_id2)) {

    message(sprintf("$$$$$RUNING timebin %i", n_bins_3[b]))

    timecourse_60bin_forprevalence[i,1]<- n_bins_3[b] #timebin
    timecourse_60bin_forprevalence[i,2]<- sum(timecourse_60bin_result_df_for_bp$indsign)

        lm_bin_pup  <- lm(pup_basCor ~ arousal_c,
                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins_NT_55,
                                    ssid ==  subject_id2[s] &
                                    timebin_no == n_bins_3[b]))
        # save the summary    
        lm_bin_pup_summary<- summary(lm_bin_pup)

        # store statistics for particiapnt and timebin
        timecourse_60bin_result_df_for_bp[i,1]<- subject_id[s] #ssid 
        timecourse_60bin_result_df_for_bp[i,2]<- n_bins_3[b] #timebin
          # timecourse_60bin_result_df[b,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
            timecourse_60bin_result_df_for_bp[i,3] <- lm_bin_pup_summary$coefficients[2] #estimate, note to avoid intercept start on 2 for estimate, then 4 for se, the 6 for t and so on
            timecourse_60bin_result_df_for_bp[i,4] <- lm_bin_pup_summary$coefficients[4] #se
            timecourse_60bin_result_df_for_bp[i,5] <- lm_bin_pup_summary$coefficients[6] #t
             timecourse_60bin_result_df_for_bp[i,6] <- lm_bin_pup_summary$coefficients[8] #p

       i = i+1
     # b = b+1
  }

  }

timecourse_60bin_result_df_for_bp%>%
  group_by(timebins)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(timebins, t_ar))+
  geom_line(color = "blue")+
  geom_line(aes(y = xmap, size = 2))+
   # scale_y_continuous(
   #  "mpg (US)",
   #  sec.axis = sec_axis(~ . * 1.20, name = "mpg (UK)")
  )

timecourse_60bin_result_df_for_bp%>%
  group_by(timebins)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(timebins, xmap))+
  geom_line(color = "blue", size = 2)+
   # geom_line(aes(y = pmap),color = "blue", linetype = "dashed")+
   # geom_line(aes(y = xbound),color = "red", linetype = "dashed")+
    geom_line(aes(y = i1),color = "blue", linetype = "dashed")+
          geom_line(aes(y = i2),color = "blue", linetype = "dashed")+
  stat_summary(aes(fun.ymin=i1, fun.ymax=i2), geom="ribbon", alpha=0.8) +
  theme_bw()

  geom_line(aes(y = xmap, size = 2))+

```

p.adjust(.05, method = "bonferroni", 55)

timecourse_60bin_result_df_for_bp$p_adjusted_count<- timecourse_60bin_result_df_for_bp$p_adjusted< alpha

timecourse_60bin_result_df_for_bp

  # p holds p-values of test for each participant
alpha = 0.05  
indsig = p<alpha

# the binary variable indsig indicates whether the within-participant
# t-test is, or not, significant for each participant (1 entry for each
# participant)

# 2.2. Loading within-participant statistical test.
# You can also load your own within-participant statistical test results here.
# Load binary results into binary indsig vector with one entry per participant. 
# See also example_csv.R for an example.

#
# 3.  LEVEL 2
#

# Bayesian prevalence inference is performed with three numbers: 
# k, the number of significant participants (e.g. sum of binary indicator
# variable)
# n, the number of participants in the sample
# alpha, the false positive rate
n <- Nsub
# table(indsig)

# lets start with valence
k_2 <- sum(indsig[,2])
table(indsig[,2])

?binom.test
binom.test(k_2, 55, 0.05, alternative="two.sided",  )

# plot posterior distribution of population prevalence
# install.packages("HDInterval")
library(HDInterval) # this package is needed
xvals <- seq(0, 1, .01)
bayesprev_posterior()
pdf_2 <- bayesprev_posterior(xvals, k_2, n) # function needed
pdf_2

plot(xvals, pdf_2, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

# Add the MAP estimate as a point
# MAP = Maximum

xmap = bayesprev_map(k_2, n)
pmap = bayesprev_posterior(xmap, k_2, n)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_2, n)
pbound = bayesprev_posterior(xbound, k_2, n)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_2, n)
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_2, n)
h2 = bayesprev_posterior(i2, k_2, n)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

```

do just scr prevalence

```{r}

 # remeber this does contain pratice, juts a leftover of an old name not to break code

# 1st we need to conduct the test within each participant and store the p value

# get the data w need

# unique(db_full4new_stim_screen_pupil_nopract_nt_304$tNo)
db_full4new_stim_screen_pupil_nopract_nt_304

# 2.  LEVEL 1
#

# 2.1. Within-participant statistical test
# This loop performs within-participant statistical test. Here, a t-test for
# non-zero mean which is the simplest statistical test. In general, any
# statistical test can be used at Level 1.
Nsub_scr = length(unique(db_full4new_stim_screen_pupil_nopract_nt_304$subject))

subject_id_scr<- unique(db_full4new_stim_screen_pupil_nopract_nt_304$subject)

# p <- vector(mode="numeric",length=Nsub) #original
# instead for our case create a matrix
p_scr <- matrix(data = NA, nrow = Nsub_scr, ncol = 5) #
e_scr <- matrix(data = NA, nrow = Nsub_scr, ncol = 5) #for estimate
se_scr <- matrix(data = NA, nrow = Nsub_scr, ncol = 5) #for se
tval_scr <- matrix(data = NA, nrow = Nsub_scr, ncol = 5) #for t value

si = 1
# estimate = effect size when centered
for(si in 1:Nsub_scr ){
  t_scr = summary(lm(log1p(BIO_CDA.PhasicMax+.1)  ~ (valence_c* arousal_c),
  data = subset(db_full4new_stim_screen_pupil_nopract_nt_304,
                subject == subject_id_scr[si])))
  e_scr[si,1:4] = t(matrix(t_scr[["coefficients"]][,1])) 
  e_scr[si,5] = subject_id_scr[si]  
  # the first t transposes the data, not we need to change si to row
  }

  colnames(e_scr)<- c("Intercept", "valence_c", "arousal_c",  "valence:arousal", "sid")
  # names(matrix(t(t[["coefficients"]])))
  View(e_scr)

# s se
  for(si in 1:Nsub_scr ){
  t_scr = summary(lm(log1p(BIO_CDA.PhasicMax+.1)  ~ (valence_c* arousal_c),
  data = subset(db_full4new_stim_screen_pupil_nopract_nt_304,
                subject == subject_id_scr[si])))
  se_scr[si,1:4] = t(matrix(t_scr[["coefficients"]][,2])) 
  se_scr[si,5] = subject_id_scr[si]  
  # the first t transposes the data, not we need to change si to row
  }

  colnames(se_scr)<- c("Intercept", "valence_c", "arousal_c",  "valence:arousal", "sid")
  View(se_scr)

t$coefficients[,4]

# now p values
  for(si in 1:Nsub_scr ){
  t_scr = summary(lm(log1p(BIO_CDA.PhasicMax+.1)  ~ (valence_c* arousal_c),
  data = subset(db_full4new_stim_screen_pupil_nopract_nt_304,
                subject == subject_id_scr[si])))
  p_scr[si,1:4] = t(matrix(t_scr[["coefficients"]][,4])) 
  p_scr[si,5] = subject_id_scr[si]  
  # the first t transposes the data, not we need to change si to row
  }

  colnames(p_scr)<- c("Intercept", "valence_c", "arousal_c",  "valence:arousal", "sid")
  View(p_scr)

  # t values

    for(si in 1:Nsub_scr ){
  t_scr = summary(lm(log1p(BIO_CDA.PhasicMax+.1)  ~ (valence_c* arousal_c),
  data = subset(db_full4new_stim_screen_pupil_nopract_nt_304,
                subject == subject_id_scr[si])))
  tval_scr[si,1:4] = t(matrix(t_scr[["coefficients"]][,3])) 
  tval_scr[si,5] = subject_id_scr[si]  
  # the first t transposes the data, not we need to change si to row
  }

  colnames(tval_scr)<- c("Intercept", "valence_c", "arousal_c",  "valence:arousal", "sid")
  View(tval_scr)

```

step 2 - count significance
```{r}

# p holds p-values of test for each participant
alpha = 0.05  
indsig_scr = p_scr <alpha
View(indsig_scr)

# the binary variable indsig indicates whether the within-participant
# t-test is, or not, significant for each participant (1 entry for each
# participant)

# 2.2. Loading within-participant statistical test.
# You can also load your own within-participant statistical test results here.
# Load binary results into binary indsig vector with one entry per participant. 
# See also example_csv.R for an example.

#
# 3.  LEVEL 2
#

# Bayesian prevalence inference is performed with three numbers: 
# k, the number of significant participants (e.g. sum of binary indicator
# variable)
# n, the number of participants in the sample
# alpha, the false positive rate
n <- Nsub_scr
# table(indsig)

# lets start with valence
k_2_scr <- sum(indsig_scr[,2])

# ?binom.test - added by helio - is the number0f significant particpants significant against chance
binom.test(k_2_scr, n, 0.05, alternative="two.sided")  #p-value = 0.04107

# plot posterior distribution of population prevalence
# install.packages("HDInterval")
library(HDInterval) # this package is needed
xvals <- seq(0, 1, .01)

# bayesprev_posterior()
pdf_2_scr <- bayesprev_posterior(xvals, k_2_scr, n) # function needed
pdf_2_scr

plot(xvals, pdf_2_scr, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

# Add the MAP estimate as a point
# MAP = Maximum

xmap = bayesprev_map(k_2_scr, n)
pmap = bayesprev_posterior(xmap, k_2_scr, n)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_2_scr, n)
pbound = bayesprev_posterior(xbound, k_2_scr, n)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_2_scr, n)
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_2_scr, n)
h2 = bayesprev_posterior(i2, k_2_scr, n)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

# try arosual

```

arousal scr

```{r}

k_3_scr <- sum(indsig_scr[,3])

# ?binom.test - added by helio - is the number0f significant particpants significant against chance
binom.test(k_3_scr, n, 0.05, alternative="two.sided")  #p-value = 0.04107

# plot posterior distribution of population prevalence
# install.packages("HDInterval")
library(HDInterval) # this package is needed
xvals <- seq(0, 1, .01)

# bayesprev_posterior()
pdf_3_scr <- bayesprev_posterior(xvals, k_3_scr, n) # function needed
pdf_3_scr

plot(xvals, pdf_3_scr, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

# Add the MAP estimate as a point
# MAP = Maximum

xmap = bayesprev_map(k_3_scr, n)
pmap = bayesprev_posterior(xmap, k_3_scr, n)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_3_scr, n)
pbound = bayesprev_posterior(xbound, k_3_scr, n)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_3_scr, n)
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_3_scr, n)
h2 = bayesprev_posterior(i2, k_3_scr, n)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

```

do the sigend test the hard oway

```{r}
?lm
p_scr <- matrix(data = NA, nrow = Nsub_scr, ncol = 5) #
e_scr <- matrix(data = NA, nrow = Nsub_scr, ncol = 5) #for estimate
se_scr <- matrix(data = NA, nrow = Nsub_scr, ncol = 5) #for se
tval_scr <- matrix(data = NA, nrow = Nsub_scr, ncol = 5) #for t value

si = 1
# estimate = effect size when centered
for(si in 1:Nsub_scr ){
  t_scr = summary(lm(log1p(BIO_CDA.PhasicMax+.1)  ~ (valence_c* arousal_c),
  data = subset(db_full4new_stim_screen_pupil_nopract_nt_304,
                subject == subject_id_scr[si])))
  e_scr[si,1:4] = t(matrix(t_scr[["coefficients"]][,1])) 
  e_scr[si,5] = subject_id_scr[si]  
  # the first t transposes the data, not we need to change si to row
  }

  colnames(e_scr)<- c("Intercept", "valence_c", "arousal_c",  "valence:arousal", "sid")
  # names(matrix(t(t[["coefficients"]])))
  View(e_scr)

# s se
  for(si in 1:Nsub_scr ){
  t_scr = summary(lm(log1p(BIO_CDA.PhasicMax+.1)  ~ (valence_c* arousal_c),
  data = subset(db_full4new_stim_screen_pupil_nopract_nt_304,
                subject == subject_id_scr[si])))
  se_scr[si,1:4] = t(matrix(t_scr[["coefficients"]][,2])) 
  se_scr[si,5] = subject_id_scr[si]  
  # the first t transposes the data, not we need to change si to row
  }

  colnames(se_scr)<- c("Intercept", "valence_c", "arousal_c",  "valence:arousal", "sid")
  View(se_scr)

t$coefficients[,4]

# now p values
  for(si in 1:Nsub_scr ){
  t_scr = summary(lm(log1p(BIO_CDA.PhasicMax+.1)  ~ (valence_c* arousal_c),
  data = subset(db_full4new_stim_screen_pupil_nopract_nt_304,
                subject == subject_id_scr[si])))
  p_scr[si,1:4] = t(matrix(t_scr[["coefficients"]][,4])) 
  p_scr[si,5] = subject_id_scr[si]  
  # the first t transposes the data, not we need to change si to row
  }

  colnames(p_scr)<- c("Intercept_p", "valence_c_p", "arousal_c_p",  "valence:arousal_p", "sid")
  View(p_scr)

  # t values

    for(si in 1:Nsub_scr ){
  t_scr = summary(lm(log1p(BIO_CDA.PhasicMax+.1)  ~ (valence_c* arousal_c),
  data = subset(db_full4new_stim_screen_pupil_nopract_nt_304,
                subject == subject_id_scr[si])))
  tval_scr[si,1:4] = t(matrix(t_scr[["coefficients"]][,3])) 
  tval_scr[si,5] = subject_id_scr[si]  
  # the first t transposes the data, not we need to change si to row
  }

  colnames(tval_scr)<- c("Intercept_p", "valence_c_p", "arousal_c_p",  "valence:arousal_p", "sid")
  View(tval_scr)

e_scr
tval_scr
# colnames(tval_scr)<- paste(colnames(tval_scr),"pval")
tval_scr<- as.data.frame(tval_scr)

# tval_scr$`sid pval`<- "sid"

e_p_scr<- left_join(as.data.frame(e_scr), as.data.frame(p_scr))
View(e_p_scr)

e_p_scr$valence_c_p_onetail<- e_p_scr$valence_c_p/2
e_p_scr$valence_c_p_onetail_indsig <- e_p_scr$valence_c_p_onetail<alpha

sum(e_p_scr$valence_c_p_onetail_indsig)

# do the same for pupil
```

```{r}

k_4_scr <- sum(indsig_scr[,4])
k_4_scr
# ?binom.test - added by helio - is the number0f significant particpants significant against chance
binom.test(k_4_scr, n, 0.05, alternative="two.sided")  #p-value = 0.04107

# plot posterior distribution of population prevalence
# install.packages("HDInterval")
library(HDInterval) # this package is needed
xvals <- seq(0, 1, .01)

# bayesprev_posterior()
pdf_4_scr <- bayesprev_posterior(xvals, k_4_scr, n) # function needed
pdf_4_scr

plot(xvals, pdf_4_scr, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

# Add the MAP estimate as a point
# MAP = Maximum

xmap = bayesprev_map(k_4_scr, n)
pmap = bayesprev_posterior(xmap, k_4_scr, n)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_4_scr, n)
pbound = bayesprev_posterior(xbound, k_4_scr, n)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_4_scr, n)
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_4_scr, n)
h2 = bayesprev_posterior(i2, k_4_scr, n)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

```

```{r}
k_3 <- sum(indsig[,3])
k_3
# k_3/55 (20%)
12/55

binom.test(k_3, 55, 0.05, alternative="two.sided") 
# plot posterior distribution of population prevalence
# install.packages("HDInterval")
library(HDInterval) # this package is needed
xvals <- seq(0, 1, .01)
pdf_3 <- bayesprev_posterior(xvals, k_3, n) # function needed
pdf_3

plot(xvals, pdf_3, type ="l", xlab = expression(gamma), 
     ylab ="Posterior density", lwd=3)

# Add the MAP estimate as a point
# MAP = Maximum

xmap = bayesprev_map(k_3, n)
pmap = bayesprev_posterior(xmap, k_3, n)
points(xmap, pmap, cex =2, col= "red", pch=16)

# Add the .95 lower bound as a vertical line
xbound = bayesprev_bound(0.95, k_3, n)
pbound = bayesprev_posterior(xbound, k_3, n)
lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)

# Add the 0.96 HPDI
int = bayesprev_hpdi(0.96, k_3, n)
i1 = int[1]
i2 = int[2]
h1 = bayesprev_posterior(i1, k_3, n)
h2 = bayesprev_posterior(i2, k_3, n)
lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)

```

### 2022-02-07 Figures.Rmd
07 Jan return

@@
 
+tmp.df4_full_stim_downs_jun2021_60bins_no_na$newlab<- paste0(tmp.df4_full_stim_downs_jun2021_60bins_no_na$Arpisal_newlab, paste0(tmp.df4_full_stim_downs_jun2021_60bins_no_na$mediansplit_sample_valence2))
+
+unique(tmp.df4_full_stim_downs_jun2021_60bins_no_na$newlab)
 plots_paper$pupil_course<- tmp.df4_full_stim_downs_jun2021_60bins_no_na %>%
@@
 
-  ggplot(aes(x = timerezero3, y = pup_basCor, color = Arpisal_newlab, linetype = mediansplit_sample_valence2)) +
+  ggplot(aes(x = timerezero3, y = pup_basCor, color = newlab, linetype = newlab)) +
   # aes(group = ssid),
@@
   p$graphstyle+
-   # scale_color_brewer(palette = "Dark2")+
+   scale_color_brewer(palette = "Dark2")+
   xlim(0,6)+
@@
 
+# newlab
 plots_paper$pupil_course<- plots_paper$pupil_course+
@@
   ylab(expression(Delta*" heart rate (bpm)"))+
-    # p$graphstyle+ylim(-4,1)+
-  ggpubr::stat_cor(label.y = -1)
+    p$graphstyle
+  # ggpubr::stat_cor(label.y = -1)
 
@@
 
-plot_patch1<-
-(plots_paper$interaction_ar_vl +
+plot_patch1<- (plots_paper$interaction_ar_vl +
 plots_paper$pupil_correlation +
@@
 
+library(ggpubr)
 unique(tmp.df4_full_stim_downs_jun2021_60bins_no_na1$ssid)
@@
   ylab("Subjective arousal \n (calm - agitated)")+
-  p$graphstyle+ theme(legend.position = "none")
+  p$graphstyle+ theme(legend.position = "none")+
+  scale_y_continuous(breaks = c(-6, -4, 0, 4))
   # stat_compare_means(comparisons = my_comparisons)+ # Add pairwise comparisons p-value
@@
 https://uc-r.github.io/kmeans_clustering
+https://sciwheel.com/work/item/5365248/resources/12059185/pdf
 ```

### 2022-02-07 Old scripts/IAPS_PREPROCESSING.Rmd
07 Jan return

--- 2021-08-19 intero_study_preprocessing.Rmd
@@
 ---
-title: "Preprocing and mergind datasets"
-author: "Helio Cuve"
-date: "24/01/2020"
-output:
-  word_document: default
-  html_document: default
+title: "IAPS_Preprocessing"
+author: '@H Cuve'
+date: "12/12/2019"
+output: html_document
 ---
-
-# Loading rdhf5 
-```{r}
-if (!requireNamespace("BiocManager", quietly = TRUE))
-    install.packages("BiocManager")
-BiocManager::install(version = "3.10")
-
-BiocManager::install("rhdf5")
-library(rhdf5)
-
-```
 
@@
 list necessary package install them if not already and load them
-```{r}
+```{r eval=FALSE, include=FALSE}
 # devtools::install_github("dmirman/gazer")
 
-list.of.packages <- c("ggplot2", "data.table", 'readr', "c", 'tidyverse', "gazer", 'lmerTest')
+list.of.packages <- c("ggplot2", "data.table", 'readr', "rhdf5", 'tidyverse', "gazer", 'lmerTest')
 new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
-
-# if(length(new.packages)) install.packages(new.packages)
+if(length(new.packages)) install.packages(new.packages)
 lapply(list.of.packages, require, character.only = TRUE)
-# lapply(new.packages, require, character.only = TRUE)
-
-# install.packages('devtools')
-
-remotes::install_github("dmirman/gazer")
-library(gazer)
-library(dplyr)
-
-# setting a workspace
-
-#change approproatelly
-
-setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020")
-# hdf5FilesPath<- "~/Desktop/University Work/Research_Project/Data Analysis January 2020/Data Analysis Jan 2020"
-setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020")
-hdf5FilesPath<- "D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020"
-
-setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Step1_GpExtractor_Output")
-
-# 2021 data
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021")
+lapply(new.packages, require, character.only = TRUE)
+
+# setwd("~/Documents/Intero Study/data/Bio/Dec12")
 hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021"
@@
 
-# gp extractor function
+# gp extractor fucntion
 takes gp files and returns a clean files with messages parsed and deletes unnecessary stuff
-
-Starting from 322 we have gsr v and hr v. and Pulse is around the 30
 
@@
 gp.extractor(hdf5FilesPath)
-
 gp.extractor = function(hdf5FilesPath) {
@@
   }
-   # f = 7
+  # f = 1
   for (f in 1:length(hdfFilesList)) {
@@
     tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent')
-
-    # Fixing 228
-    # session 1 = IAPS
-    nrow(tmp.events)
-    # tmp.events<- subset(tmp.events, tmp.events$session_id == 1)
-
     tmp.eyetr  = h5read(hdfFilesList[f], '/data_collection/events/eyetracker/BinocularEyeSampleEvent')
-
-    # tmp.eyetr<- subset(tmp.eyetr, tmp.eyetr$session_id == 1)
 
@@
 
-Problem files
-```{r}
-# 355  - did not finish IAPS
-# adjust below manually
-
-gp.extractor = function(hdf5FilesPath) {
-
-  setwd(hdf5FilesPath)
-
-  hdfFilesList = list.files(hdf5FilesPath, pattern = "\\.hdf5$")
-  hdfFilesList
-  if (length(hdfFilesList) == 0){
-
-    return(message('No HDF5 files found in the directory provided.'))
-  }
-   f = 10# adjust here to the index for the probematic file
-  for (f in 1:length(hdfFilesList)) {
-
-    message(sprintf("Extracting file %i / %i - %s", f, length(hdfFilesList), hdfFilesList[f]))
-
-    #ATTTENTIONNN  note this sometimes fails because we are using a notebook 
-    # Extract Events from hdf5, in that case run it from command
-    tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent')
-
-    # Fixing 228
-    # session 1 = IAPS
-    nrow(tmp.events)
-    # tmp.events<- subset(tmp.events, tmp.events$session_id == 1)
-
-    tmp.eyetr  = h5read(hdfFilesList[f], '/data_collection/events/eyetracker/BinocularEyeSampleEvent')
-
-    # tmp.eyetr<- subset(tmp.eyetr, tmp.eyetr$session_id == 1)
-
-    # tmp.events<- tmp.events[245:nrow(tmp.events), ]
-
-    # problem file
-    # tmp.events
-
-    # Get subejct id from Events
-    ssid = sapply(strsplit(grep('SubjJID', tmp.events$text, value = TRUE), split = ": "), "[", 2)
-    date = sapply(strsplit(grep('DATE', tmp.events$text, value = TRUE), split = ": "), "[", 2)
-    session = sapply(strsplit(grep('Session:', tmp.events$text, value = TRUE), split = ":"), "[", 2)
-    cali<- subset(tmp.events, grepl('Cali', tmp.events$text) == TRUE)
-
-    # Create DF for trials data
-    tmp.df = data.frame(matrix(ncol = ncol(tmp.eyetr)))
-    names(tmp.df) = names(tmp.eyetr)
-    colnames(tmp.df)
-
-    # Prepare Events, keep only start/end messages
-    phrases = c('tStart', 'tEnd')
-    tmp.events_backup<- tmp.events
-    # tmp.events<-  tmp.events_backup
-    tmp.events = subset(tmp.events, grepl(paste(phrases, collapse = "|"), tmp.events$text))
-
-    # Create start/end references
-    tmp.events$tStart   = NA
-    tmp.events$tEnd     = NA
-
-    # Trial number extraction 
-    tmp.events$tNo      = NA
-    tmp.df$tNo          = NA
-    tmp.df$Condition    = NA
-
-    # Space for subject id
-    tmp.df$ssid         = NA
-    tmp.df$text<-NA
-
-    for (l in 1:nrow(tmp.events)) {
-      # sub(".*_", "", tmp.events)
-
-      # sub("[^_]*/_", "", tmp.events$text)
-      # ([^\/]+$)
-      # remove everything upto to _
-      # as.numeric(strsplit(tmp.events$text[l], split = '_')[[1]][3])
-      # "Extracting file %i / %i - %s", f, length(hdfFilesList), hdfFilesList[f])
-
-      message(sprintf("Grabing start messages %s", tmp.events$text[l]))
-
-      if ((grepl('tStart', tmp.events$text[l])) == TRUE) {
-        tmp.events$tStart[l] = tmp.events$time[l]
-
-        if ((grepl('tEnd', tmp.events$text[l+1])) == TRUE){
-          tmp.events$tEnd[l] = tmp.events$time[l+1]
-        }
-
-        else {
-          message('trial start/end structure not valid')
-        }
-      }
-
-    }
-    message(sprintf("done grabbing messages"))
-    # readline(prompt="Press [enter] to continue")
-
-    tmp.events$tNo<- as.numeric(as.character(gsub(".*_","",tmp.events$text)))
-
-    # tmp.events$tNo[is.na(tmp.events$tNo) == TRUE]<- -7
-
-    # tmp.events$screencontent = strsplit(tmp.events$text, split = '_')[[1]][2]
-    # readline(prompt="Press [enter] to continue")
-     message(sprintf("making screencontent"))
-    tmp.events$screencontent<- if_else(grepl('fixation', tmp.events$text), 'fixation',
-                                       if_else(grepl('Valence', tmp.events$text), 'ValenceResp',
-                                               if_else(grepl('rest', tmp.events$text), 'rest1', 
-                                                       if_else(grepl('IntResp', tmp.events$text), 'IntResp','stim'))))
-
-    unique(tmp.events$screencontent)
-
-    # first let's do condition
-
-    tmp.events$Condition<- if_else(grepl('IAPS', tmp.events$text), 'IAPS',
-                                   if_else(grepl('Example', tmp.events$text), 'Practice',
-                                           if_else(grepl('rest', tmp.events$text), 'Rest', NULL)))
-    tmp.events$stim<- if_else(tmp.events$Condition == 'IAPS', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text),
-                              if_else(tmp.events$Condition == 'Practice', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text), 'REST'))
-
-    # substitute periods
-    tmp.events$stim<- gsub('\\.', '.jpg', tmp.events$stim)
-    # tmp.events$tNo<- as.numeric(tmp.events$tNo)
-    tmp.events$tNo<- if_else(tmp.events$Condition == 'Practice', (tmp.events$tNo)-6,
-                             if_else(tmp.events$Condition == 'Rest',-7, tmp.events$tNo))
-    # tmp.events$tNo<- tmp.events$tNo1
-    tmp.events$tNo<- if_else(tmp.events$tNo> -1, tmp.events$tNo+1, tmp.events$tNo) # avoid zeros
-
-    tmp.events1 = subset(tmp.events, grepl('tStart',tmp.events$text))
-    tmp.events1$tNo1<- NULL
-    tmp.events1$tNo2<- NULL
-
-    # tmp.eyetr_backup<- tmp.eyetr
-    # tmp.df_backup<- tmp.df
-    # tmp.df<- tmp.df_backup
-    colnames(tmp.df)
-    # rm(tmp.raw.trial)
-    # colnames(tmp.raw.trial)
-    colnames(tmp.df)
-    colnames(tmp.events1)
-    colnames(tmp.eyetr)
-    tmp.df$screencontent<- NA
-    tmp.df$stim<- NA
-    # e=10
-    tmp.events1$tEnd<- if_else(tmp.events1$tNo == -7, tmp.events1$tStart+120, tmp.events1$tEnd)
-    message(sprintf("subsetting eyetracking data"))
-    e=1
-    for(e in 1:nrow(tmp.events1)) {
-
-      # Subset the EyeTracking data based on start/end
-      tmp.raw.trial = subset(tmp.eyetr, tmp.eyetr$time >= tmp.events1$tStart[e] & tmp.eyetr$time <= tmp.events1$tEnd[e])
-
-      tmp.raw.trial$tNo = tmp.events1$tNo[e]
-
-      tmp.raw.trial$Condition = tmp.events1$Condition[e]
-      tmp.raw.trial$screencontent = tmp.events1$screencontent[e]
-      tmp.raw.trial$stim = tmp.events1$stim[e]
-      # tmp.raw.trial$stim = tmp.events1$[e]
-      tmp.raw.trial$ssid = ssid
-      tmp.raw.trial$text = tmp.events1$text[e]
-       message(sprintf("binding tmp.df"))
-      tmp.df= rbind(tmp.raw.trial, tmp.df)
-    }
-     message(sprintf("done binding"))
-
-    # Add ssid
-    # tmp.df$ssID = ssid[e]
-    tmp.df<- tmp.df%>%
-      arrange(time)
-
-    # Save file
-    name = sprintf("ss%s_GPdata",ssid)
-    message(sprintf("saving data"))
-
-    write_csv(tmp.df, paste(name,".csv"))
-    # write_csv(tmp.df, "test.csv")
-    # write calibration cali
-    name2 = sprintf("ss%s_GPdata_cali", ssid)
-    write_csv(cali, paste(name2,".csv"))
-
-  }
-
-  # write_csv(tmp.df, 'tmpdf_extracted.csv')
-
-  message("Processing Completed.")
-  tmp.df
-}
-
-# tmp_full<- gp.extractor(hdf5FilesPath)
-
-```
-
 now cleaning
@@
 # function to read all the csvs into one dataframe
-
 rm(tmp_full)
@@
   data.table::fread(flnm, select = c("session_id","event_id", "time", "left_gaze_x", "left_gaze_y","right_gaze_x", "right_gaze_y","left_pupil_measure1",
-                                     "right_pupil_measure1","gsr", "gsrv", 'hr', "hrv", "hrp", "status", "tNo",  "Condition", "screencontent", "stim", "ssid", "text")) %>% 
+                                     "right_pupil_measure1","gsr", 'hr',"status", "tNo",  "Condition", "screencontent", "stim", "ssid", "text")) %>% 
     mutate(filename = flnm)
@@
 # now read them
-setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Step1_GpExtractor_Output")
 
@@
   map_df(~read_plus(.))
-# rm(db_beh)
+rm(db_beh)
 
 tmp.df2$ssid<- substr(tmp.df2$filename, 5,7)
-
 unique(tmp.df2$ssid)
@@
 tmp.df3<- tmp.df2
-
 # tmp.df3<- tmp.df2
@@
 
-head(tmp.df3)
-
 # make zeros
 tmp.df3$zero<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, NULL)
-
 # fill in the zeros
@@
   fill(zero)
-
-unique(tmp.df3$zero)
-
 # rezero
@@
 min(tmp.df3$timerezero, na.rm = TRUE)
-
 natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)
-
 # let's check to see if it looks fine
@@
 
+# ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS'), aes(timerezero, gsr, colour = as.factor(ssid)))+
+#   geom_line()
+
   # create a new time rezero where before stim start is negative
@@
 
-    # fill down
     tmp.df3<- tmp.df3%>%
@@
 
-# fill up
    tmp.df3<- tmp.df3%>%
@@
 unique(tmp.df3$ssid)
-
-#tmp.df3<- subset(tmp.df3, is.na(tmp.df3$ssid) == FALSE)
+tmp.df3<- subset(tmp.df3, is.na(tmp.df3$ssid) == FALSE)
 
@@
 
-ggplot(subset(tmp.df3, tmp.df3$tNo == -7) , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
+ggplot(subset(tmp.df3, tmp.df3$tNo == -1) , aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
   # geom_point()
@@
 triggers
-
 ```{r}
 unique(tmp.df3$tNo)
-
 natest<- subset(tmp.df3, is.na(tmp.df3$tNo) == TRUE)
@@
 
-tmp.df3$intercept_time<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, 
+tmp.df3$intercept_time<- if_else
+(tmp.df3$firststart == FALSE, tmp.df3$time, 
                           if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$time,
                                   NULL))
-
 # takes a bit with a group - so don't run
-# ggplot(tmp.df3, aes(time, gsr))+
-#   geom_line()+
-#   geom_vline(aes(xintercept = intercept_time))
-
-# should trigger be this or should I create a unique code for this based on the images
-
+ggplot(tmp.df3, aes(time, gsr))+
+  geom_line()+
+  geom_vline(aes(xintercept = intercept_time))
+
+# should trigger be this or should I create a uoque code for this based on the images
 unique(tmp.df3$tNo)
@@
                           if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$trigger, 0))
-unique(tmp.df3$trigger)
-
 tmp.df3$trigger <- if_else(tmp.df3$screencontent == 'fixation' &tmp.df3$firststart == FALSE, 100,
@@
 unique(tmp.df3$trigger)
-
 tmp.df3$trigger<- if_else(tmp.df3$firststart == TRUE, 0, tmp.df3$trigger)
@@
 # gsr to microsiemnes 1/J3*100000
-
 options(scipen = 999)
@@
 colnames(tmp.df3)
-db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49 ))
+db_GSR<- select(tmp.df3, c(3,  17, 47, 46 ))
 db_GSR$tNo<- NULL
@@
 
-unique(db_GSR$Condition)
 db_GSR$Condition2<- if_else(db_GSR$Condition == 'Rest', 'Rest', 'IAPS')
@@
     }
-
 ```
@@
 
-# create baseline median
-tmp.df3$gsr_bas_mean<- NULL
-
+# create bseline median
 tmp.df3<- tmp.df3%>%
@@
   group_by(ssid, tNo, gsr_bastrue)%>%
-  mutate(gsr_bas_median = median(gsr_bas))
+  mutate(gsr_bas_mean = median(gsr_bas))
 
@@
   group_by(ssid, tNo)%>%
-  fill(gsr_bas_median)
+  fill(gsr_bas_mean)
 
 # fill up to complete
-unique(tmp.df3$gsrv)
-
 tmp.df3<- tmp.df3%>%
@@
   group_by(ssid, tNo)%>%
-  fill(gsr_bas_median, .direction = 'up')
+  fill(gsr_bas_mean, .direction = 'up')
 
 # do baseline correction
-# 
 tmp.df3<- tmp.df3%>%
@@
   group_by(ssid, tNo)%>%
-  mutate(gsr_basCor = gsr_ms - gsr_bas_median)
+  mutate(gsr_basCor = gsr_ms - gsr_bas_mean)
 
@@
   group_by(ssid, Condition)%>%
-  mutate(gsr_restmedian = median(gsr_ms))
-
-tmp.df3$gsr_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$gsr_ms- tmp.df3$gsr_restmedian, tmp.df3$gsr_basCor)
+  mutate(gsr_restmean = median(gsr_ms))
+
+tmp.df3$gsr_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$gsr_ms- tmp.df3$gsr_restmean, tmp.df3$gsr_basCor)
 
@@
 
-# gsr respone
-tmp.df3$gsr_resp_Log<- if_else(tmp.df3$timerezero3 > 1,TRUE, FALSE)
-unique(tmp.df3$gsr_resp_Log)
-
-tmp.df3 <- tmp.df3 %>%
-    group_by(ssid, tNo, gsr_resp_Log )%>%
-    mutate(gsr_response =   max(gsr_basCor))
-
-# gsr response for every bit
-unique(tmp.df3$screencontent)
-tmp.df3<- tmp.df3%>%
-  # arrange(time)%>%
-  group_by(ssid, tNo, screencontent)%>%
-  mutate(gsr_response_scrcont =   max(gsr_basCor))
-
-tmp.df3$gsr_response <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)
-
-tmp.df3<-
-  tmp.df3%>%
-  arrange(time)%>%
-  group_by(ssid, tNo)%>%
-    fill(gsr_response)
-
-tmp.df3<-
-  tmp.df3%>%
-  arrange(time)%>%
-  group_by(ssid, tNo)%>%
-    fill(gsr_response,  .direction = c('up'))
-
-unique(tmp.df3$gsr_response )
-
 ```
@@
 library(gazer)
+
+tmp.df3$pupil<- if_else(tmp.df3$pupil> 7.2, tmp.df3$pupil, NULL)
 min(tmp.df3$pupil, na.rm = TRUE)
-max(tmp.df3$pupil, na.rm = TRUE)
-
-tmp.df3$pupil<- if_else(tmp.df3$pupil> 7.2, tmp.df3$pupil, NULL)
-
-tmp.df3$pupil<- if_else(tmp.df3$pupil< 45, tmp.df3$pupil, NULL)
 
@@
 min(tmp.df3$extendpupil, na.rm = TRUE)
-max(tmp.df3$pupil, na.rm = TRUE)
 
@@
 
-ggplot(subset(tmp.df3, tmp.df3$tNo == 3), aes(x = timerezero3, y= extendpupil , colour = as.factor(ssid)))+
+ggplot(subset(tmp.df3, tmp.df3$tNo == -3), aes(x = timerezero3, y= extendpupil , colour = as.factor(ssid)))+
       geom_line()
@@
 tmp.df3$extendpupil
-# ?smooth_interpolate_pupil
+?smooth_interpolate_pupil
 
 library(gazer)
-
 tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
@@
 
-min(tmp.df3$pup_interp, na.rm = TRUE)
-max(tmp.df3$pup_interp, na.rm = TRUE)
-
-ggplot(subset(tmp.df3, tmp.df3$tNo == 10 & tmp.df3$ssid == 320) , aes(x = timerezero3, y= pup_interp, colour = as.factor(ssid)))+
-  geom_line()+
-  geom_line(aes(y = pupil), colour = 'gray')
+# tmp.df3<-test
+
+min(tmp.df3$pup_interp)
+max(tmp.df3$pup_interp)
+
+ggplot(subset(tmp.df3, tmp.df3$tNo == -4 & tmp.df3$ssid == 309) , aes(x = timerezero3, y= pup_interp, colour = as.factor(ssid)))+
+  geom_line()
   # facet_grid(~Condition)
@@
   # arrange(time)%>%
-  group_by(ssid, tNo, pup_bastrue)%>%
+  group_by(tNo, pup_bastrue)%>%
   mutate(pup_bas_med = median(pup_bas))
@@
   # arrange(time)%>%
-  group_by(ssid,tNo)%>%
+  group_by(tNo)%>%
   fill(pup_bas_med)
@@
   # arrange(time)%>%
-  group_by(ssid, tNo)%>%
+  group_by(tNo)%>%
   fill(pup_bas_med, .direction = 'up')
@@
 tmp.df3<- tmp.df3%>%
-  arrange(time)%>%
-  group_by(ssid, tNo)%>%
+  # arranÇge(time)%>%
+  group_by(tNo)%>%
   mutate(pup_basCor = pup_interp - pup_bas_med)
@@
 # MAD removal
-max_pup<-tmp.df3 %>%
+tmp.df3<-tmp.df3 %>%
   dplyr::group_by(subject, trial) %>%
   dplyr::mutate(speed=speed_pupil(pup_interp,time)) %>%
-  dplyr::mutate(MAD=calc_mad(speed))
-  # dplyr::filter(speed < MAD)
-
-tmp.df3<- max_pup
-
-# instead of deleting, nus put NA
-tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)
-
-tmp.df3$pup_interp_mad<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_interp, NULL)
-# tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)
-
-ggplot(subset(tmp.df3, tmp.df3$tNo == 5 & tmp.df3$ssid == 900) , aes(x = timerezero3, y= pup_basCor))+
-    # geom_smooth(se = F)+
-  geom_line()+
+  dplyr::mutate(MAD=calc_mad(speed))%>%
+  dplyr::filter(speed < MAD)
+
+tmp.df3
+
+ggplot(subset(tmp.df3, tmp.df3$tNo == -3), aes(x = timerezero3, y = pup_basCor, colour = as.factor(ssid)))+
+  geom_line()
+
+ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
+    geom_smooth(se = F)+
     geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
@@
 
-# heart rate
-
 min(tmp.df3$hr, na.rm = TRUE)
 max(tmp.df3$hr, na.rm = TRUE)
-tmp.df3$hrv<- as.double(tmp.df3$hrv)
-tmp.df3$hrv2<- if_else(is.na(tmp.df3$hrv) == TRUE, 999,tmp.df3$hrv)
-
-tmp.df3$hr_clean<- tmp.df3$hr
-tmp.df3$hr_clean<- as.double(tmp.df3$hr_clean)
-
-tmp.df3$hr_clean<- if_else(tmp.df3$hrv2 >0,  tmp.df3$hr_clean, NULL)
-
-tmp.df3$hr_clean<- if_else(tmp.df3$hr_clean > 40 & tmp.df3$hr_clean< 120, tmp.df3$hr_clean, NULL)
-
-table(is.na(tmp.df3$hr_clean))
-# interpolate, only 2 seconds 
-library(zoo)
-tmp.df3<- tmp.df3%>%
-  arrange(ssid, time, tNo)
-
-# tmp.df3$hr_interp =
-
-tmp.df3<- tmp.df3%>%
-  # arrange(ssid, time, tNo)%>%
-  group_by(ssid, tNo,screencontent)%>%
-  mutate(hr_interp = na.approx(hr_clean, na.rm=FALSE, maxgap =400))
-
-  min(tmp.df3$hr, na.rm = TRUE)
-ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 320) , aes(x = timerezero3, y= hr_interp))+
-    # geom_smooth(se = F)+
-  geom_line()+
-  geom_line(aes(y = hr_clean), linetype = 'dashed', colour = 'green', size = 0.3)+
-   geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
-    # geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
-    # geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
-    # geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
-    # geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
-
-# na.approx(object, x = index(object), xout, ..., na.rm = TRUE, maxgap = Inf, along)
-# z <- na.spline(zoo(y, x), maxgap = 2)
-
-tmp.df3 <- tmp.df3 %>%
-    group_by(ssid, tNo, gsr_resp_Log, screencontent)%>%
-    mutate(gsr_response_bycond =   max(gsr_basCor))
-
-# tmp.df3$gsr_response_bycond <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)
+
+tmp.df3$hr<- if_else(tmp.df3$hr > 40 & tmp.df3$hr< 120, tmp.df3$hr, NULL)
 
 colnames(tmp.df3)
-# tmp.df4<- select(tmp.df3, c(1:3,10:22,27:30,33:37,44,46,47,51,53:56,60))
-
-tmp.df4<- select(tmp.df3, c("session_id", "event_id", "ssid", "subject", "text", "trial","trialUnq", "tNo","trigger", "Condition" ,"screencontent","stim",
-                            "time", "timerezero", "timerezero2", "timerezero3", "status","filename",
-                            "left_gaze_x_cor_pix","right_gaze_x_cor_pix","left_gaze_y_cor_pix","right_gaze_y_cor_pix",  "gaze_x_cor_pix",  "gaze_y_cor_pix",
-                            "pupil", "pup_interp_mad", "extendpupil","pup_basCor",
-                            "hr", "hrv", "hrp", "hr_clean", 'hr_interp', 
-                            'gsr_ms', 'gsr_basCor', 'gsr_response', 'gsr_response_bycond', 
-                            "distance"))
+tmp.df4<- select(tmp.df3, c(1:3,11:19,24:27,33:37,44,46,47,51,53:56,60))
 head(tmp.df4)
 
-# calculate trackloss
-unique(tmp.df4$status)
-
-tmp.df4$trackloss<- if_else(is.na(tmp.df4$gaze_x_cor_pix) == TRUE, 0, 
-                         if_else(is.na(tmp.df4$gaze_y_cor_pix) == TRUE, 0, 1))
-unique(tmp.df4$trackloss)
-
-# tmp.df4$trackloss<- if_else(tmp.df4$status> 0, 1, 0)
-
-tmp.df4$hr_trackloss<- if_else(is.na(tmp.df4$hr_clean) == TRUE, 0, 1) # 1 means valid, 0 missing
-
+tmp.df4$trackloss<- if_else(tmp.df4$status> 0, 1, 0)
+tmp.df4$hr_na<- if_else(is.na(tmp.df4$hr) == TRUE, TRUE, FALSE)
+tmp.df4$hr_na<- if_else(tmp.df4$hr_na == TRUE, 1, 0)
 tmp.df4 <- tmp.df4%>%
   group_by(ssid, tNo, trialUnq, text)%>%
-  mutate(gaze_valid_prop = sum(trackloss)/n())%>%
-  mutate(gaze_loss_prop = 1 - gaze_valid_prop)%>%
-  mutate(hr_valid_prop = sum(hr_trackloss)/n())%>%
-  mutate(hr_loss_prop = 1 - hr_valid_prop)
-
-# check to see this is right
-ggplot(subset(tmp.df4, tmp.df3$ssid == 324) , aes(x = tNo, y= hr_valid_prop))+
-    # geom_smooth(se = F)+
-  geom_line()+
-  geom_line(aes(y = hr_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
-   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
-
-ggplot(subset(tmp.df4, tmp.df3$ssid == 324) , aes(x = tNo, y= gaze_valid_prop))+
-    # geom_smooth(se = F)+
-  geom_line()+
-  geom_line(aes(y = gaze_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
-   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
+  mutate(gaze_loss_prop = sum(trackloss)/n())%>%
+  mutate(gaze_valid_prop = 1 - gaze_loss_prop)%>%
+  mutate(hr_na_prop = sum(hr_na)/n())
 
 colnames(tmp.df4)
-write_csv(tmp.df4, 'interodata_clean_gp.csv')
-
-# tmp.df4<- read_csv('intero_tsdata_clean.csv')
-
+write_csv(tmp.df4, 'intero_tsdata_clean.csv')
+
+tmp.df4<- read_csv('intero_tsdata_clean.csv')
 tmp.df4<- tmp.df4%>%
-  arrange(ssid, time, tNo)
-
+  arrange(ssid, time, tNo )
 unique(tmp.df4$trigger)
-
-# why
-
 tmp.df4$trigger2<- tmp.df4$trigger
 
-tmp.df4$trigger2<- if_else(tmp.df4$trigger>99, tmp.df4$trigger, as.double(tmp.df4$tNo))
-
+tmp.df4$trigger2<- if_else(tmp.df4$trigger>99, tmp.df4$trigger, tmp.df4$tNo)
 unique(tmp.df4$trigger2)
-
-tmp.df4<- tmp.df4%>%
-  group_by(ssid, tNo, text)%>%
-  mutate(stdev_gaze_x = sd(gaze_x_cor_pix, na.rm = TRUE))%>%
-  mutate(stdev_gaze_y = sd(gaze_y_cor_pix, na.rm = TRUE))
-
-tmp.df4$sdev_gazesum<- tmp.df4$stdev_gaze_x+ tmp.df4$stdev_gaze_y
-
-# summarise
 tmp.df4_sum<- tmp.df4%>%
@@
   group_by(ssid, subject, trial, Condition, screencontent, tNo, stim, trialUnq,text)%>%
-  summarise_at(c('pup_basCor', 'gsr_response','gsr_response_bycond', 'gsr_basCor', 'hr_interp', 'hr_clean', 'time', 'gaze_loss_prop', 'gaze_valid_prop', 'hr_valid_prop', 'hr_loss_prop', 'timerezero3', 'sdev_gazesum', 'stdev_gaze_x', 'stdev_gaze_y'), mean, na.rm = TRUE)
+  summarise_at(c('hr', 'pup_basCor', 'gsr_basCor', 'hr', 'time', 'gaze_loss_prop', 'gaze_valid_prop', 'hr_na_prop', 'timerezero3'), mean, na.rm = TRUE)
 
@@
                           if_else(tmp.df4_sum$screencontent == 'ValenceResp', 101,
-                             if_else(tmp.df4_sum$screencontent == 'IntResp', 102, as.double(tmp.df4_sum$tNo))))
+                             if_else(tmp.df4_sum$screencontent == 'IntResp', 102, tmp.df4_sum$tNo)))
 
@@
 unique(tmp.df4_sum$trigger)
+
+write_csv(tmp.df4_sum, 'intero_aggdata_clean.csv')
+
 tmp.df4_sum<- tmp.df4_sum%>%
@@
 
-write_csv(tmp.df4_sum, 'intero_aggdata_clean.csv')
-
 head(tmp.df4_sum)
@@
   geom_line()
-
-ggplot(subset(tmp.df4_sum, tmp.df4_sum$screencontent == 'stim'), aes(gaze_valid_prop, colour = as.factor(ssid)))+
-# geom_density()+
-  geom_histogram()
-  # geom_line()
-
-# for gaze parsing
 
@@
 
-  for_gazepath<- select(tmp.df4, c(2:15,17:26, 39:40,42:43))
+  for_gazepath<- select(tmp.df4, c(1:3,5:22, 29,33:34))
 
@@
 # Import Ledalab
-Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 105 .01 2])
 ```{r}
@@
 colnames(X309_2019_Dec_11_1807_01)
-library(data.table) 
-library(purrr)
 
@@
 
-db328$condition<-db328$ï..condition
-
-db328 <-select(db328, c("condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
-                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
-
-db328$ssid<- 328
-
-db328$filename<- db328$ssid
-
-# files <- list.files(pattern = ".csv")
-# temp <- do.call(rbind,lapply(files, read.csv), header = TRUE)
+library(data.table)  
+files <- list.files(pattern = ".csv")
+temp <- do.call(rbind,lapply(files, read.csv), header = TRUE)
 
@@
                 use.names = TRUE, idcol = "filename")
-db_beh$condition <- db_beh$ï..condition
 
@@
 
-db328<- select(db328, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
+files <- list.files(pattern = ".csv")
+db304<- rbindlist(sapply(files, fread, simplify = FALSE),
+                use.names = TRUE, idcol = "filename")
+
+db304<- select(db304, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
                                      "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
-
-# 
-# db304<- rbindlist(sapply(files, fread, simplify = FALSE),
-#                 use.names = TRUE, idcol = "filename")
-# 
-# 
-# 
-# db304<- select(db304, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
-#                                      "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
 
@@
 colnames(db_beh)
-# db_beh<- bind_rows(db_beh, db304)
-db_beh$ssid<- substr(db_beh$filename, 3,5)
+db_beh<- bind_rows(db_beh, db304)
+db_beh$ssid<- substr(db_beh$filename, 1,3)
 
@@
 db_beh2<- db_beh
-db328$filename<- as.character(db328$filename)
-db328$ssid<- as.character(db328$ssid)
-
-db328$ssid <- 328
-
-db_beh2<- bind_rows(db_beh2, db328)
-
-unique(db_beh2$ssid)
+
 # create one column for arousl and RT
@@
 db_beh2$Self_intensity_3.response<- as.double(db_beh2$Self_intensity_3.response)                      
-db_beh2$arousal<- if_else(is.na(db_beh2$Self_intensity_2.response) == FALSE, as.numeric(db_beh2$Self_intensity_2.response),
+db_beh2$arousal<- if_else(is.na(db_beh2$Self_intensity_2.response) == FALSE, db_beh2$Self_intensity_2.response,
                           if_else(is.na(db_beh2$Self_intensity_3.response) == FALSE,
-                                  as.numeric(db_beh2$Self_intensity_3.response), NULL))
+                                  db_beh2$Self_intensity_3.response, NULL))
 
@@
 db_beh2$trialsPract.thisTrialN<- db_beh2$trialsPract.thisTrialN - 6
-
 db_beh2$trialIAPS.thisTrialN<-db_beh2$trialIAPS.thisTrialN +1 
@@
 ggplot(db_beh2, aes(x = tNo, y = valence_rt))+
-  geom_point()+
   geom_line()
@@
 db_beh2$triggeracq<- db_beh2$trigger
-unique(db_beh2$ssid)
-
-db_beh3<- select(db_beh2, c(2:7, 18:23))
+db_beh3<- select(db_beh2, c(2:6, 18:24))
 
@@
 colnames(db_beh3)
-colnames(db_beh3_301_309)
-db_beh3$trigger<-NULL
-db_beh3_301_309$triggeracq<- NULL
-
-db_beh3_301_309$condition[db_beh3_301_309$condition == "Example Stimuli"]<- "Practice"
-db_beh3$condition[db_beh3$condition == "Example Stimuli"]<- "Practice"
-
-db_beh3$triggeracq<- NULL
-
-library(readr)
-db_beh300 <-  read_csv("300-309 beh/tmp.df4300_sum_full.csv")
-View(tmp_df4300_sum_full)
-
-db_beh300 <- subset(db_beh300, db_beh300$condition != "Rest")
-colnames(db_beh300)
-
-db_beh300$ssid<- 300
-
-db_beh300<- select(db_beh300, c("condition", "stimIAPS","stimDescription","ValenceMean", "ArousalMean", "ssid", "valence","arousal","valence_rt","arousal_rt", "tNo"))
-
+colnames(tmp.df4_sum_full)
 db_beh3$ssid<- as.numeric(db_beh3$ssid)
-db_beh_all<- bind_rows(db_beh3, db_beh300)
-db_beh_all<- bind_rows(db_beh_all, db_beh3_301_309)
-# db_beh4<- db_beh3
-
-unique(db_beh_all$ssid)
-
-str(tmp.df4_sum)
-str(db_beh_all)
-tmp.df4_sum$ssid<- as.numeric(tmp.df4_sum$ssid)
-
-db_beh3$ssid<- as.numeric(db_beh3$ssid)
-# rm(tmp.df4_sum_full_t)
-
-tmp.df4_sum_full<- left_join(tmp.df4_sum, db_beh_all, by = c('ssid', 'tNo'))
-
-tmp.df4_sum_full<- tmp.df4_sum_full%>%
-  arrange(ssid, tNo, time)
-
-# self reports
-
-db_selfrep <- read_csv("intero_selrep.csv")
-View(intero_selrep)
-tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_selfrep, by = 'ssid')
+rm(tmp.df4_sum_full_t)
+
+tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_beh3, by = c('ssid', 'tNo'))
 
 unique(tmp.df4_sum_full$ssid)
-# colnames(tmp_df4300_sum_full)
-# colnames(tmp.df4_sum_full)
-# 
-# tmp.df4_sum_full<- tmp.df4_sum_full[,1:54]
-# tmp.df4_sum_full<- bind_rows(tmp.df4_sum_full, tmp_df4300_sum_full)
-
-# db_selfrep <- read_csv("~/Documents/InteroStudy/data/Bio/Dec12/db_selfrep.csv")
-
-# db_selfrep$ssid<- as.numeric(db_selfrep$ssid)
-
-# tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_selfrep, by = 'ssid' )
+colnames(tmp_df4300_sum_full)
+colnames(tmp.df4_sum_full)
+
+tmp.df4_sum_full<- tmp.df4_sum_full[,1:54]
+tmp.df4_sum_full<- bind_rows(tmp.df4_sum_full, tmp_df4300_sum_full)
+
+db_selfrep <- read_csv("~/Documents/InteroStudy/data/Bio/Dec12/db_selfrep.csv")
+
+db_selfrep$ssid<- as.numeric(db_selfrep$ssid)
+
+tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_selfrep, by = 'ssid' )
 
@@
 
-# tmp.df4_sum_full<- tmp.df4_sum_full%>%
-#   arrange(ssid, tNo, screencontent_no)
+tmp.df4_sum_full<- tmp.df4_sum_full%>%
+  arrange(ssid, tNo, screencontent_no)
 ```
@@
 View(tmp.df4_sum_full)
-
 tmp.df4_sum_full_stim<- subset( tmp.df4_sum_full,  tmp.df4_sum_full$screencontent == 'stim')
@@
 
-import biopac heart rate
+import biopac hear rate
 ```{r}

### 2022-02-07 Old scripts/pupil_arousal_datarmd.Rmd
07 Jan return

@@
   summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(arousal_c, BIO_CDA.PhasicMax_z, color =mediansplit_sample_valence2))+
+  ggplot(aes(arousal_c, BIO_CDA.PhasicMax_z))+
   geom_point()+
@@
 
-pupil_arousal_findings$arousal_scr <- lmer(BIO_CDA.PhasicMax_z ~ valence_c +(1|ssid),
+pupil_arousal_findings$arousal_scr <- lmer(BIO_CDA.PhasicMax_z ~ valence_c + (1|ssid),
                         REML = FALSE,

### 2022-02-07 Paper_Analyses_subj_obje_arousal.Rmd
07 Jan return

@@
 # create and empty dataframe for the timecourse analyses
+
+timecourse_60bin_result_df_bp<- timecourse_60bin_result_df
+
 timecourse_60bin_result_df <- data.frame(timebins= rep(NA, 60), 
@@
 db_full6new_hr_fix_stim_nt1.1
-
+View(clustering)
 clustering<- db_full6new_hr_fix_stim_nt1.1%>%
@@
 View(db_full6new_hr_fix_stim_select2_NT_no_outl_5)
+View(db_forBADA1)
 db_forBADA1<- data.table::dcast(setDT(db_full6new_hr_fix_stim_select2_NT_no_outl_5), 
@@
                 'Bio_Mean_HR_dif', 'log1p_BIO_CDA.PhasicMax', 'arousal', 'valence'))
+
+View(db_forBADA)
 
@@
 
+View(all.data3_forPCA)
 var.data <- all.data3_forPCA[,c(4:171)]
@@
 
+View(var.data)
 # inferential PCA
@@
 
+# mySpca <- spca(obj, ask=FALSE, type=1, scannf=FALSE)
+# install.packages("adegenet")
+library(adegenet)
+# install.packages('spdep')
+install.packages("sf")
+library(spdep)
+
+mySpca <- spca(obj, ask=FALSE, type=1, scannf=FALSE)
+?spca
+mySpca <- spca(var.data, ask=FALSE, type=1, scannf=FALSE)
+
+install.packages("cpca")
+
+?cpca::cpc()
+
+var.data$sid <- all.data3_forPCA$ssid
+require("plyr")
+require("abind")
+
+daply(var.data, "sid", function(x) cov(x[, -ncol(x)]))
+C <- aperm(C, c(2, 3, 1)) # put the 1st dimension to the end
+dim(C)
+dimnames(C)
+
+mod <- cpc(C)
+str(mod)
+
+round(mod$CPC, 2)
+
+pca::cpc(var.data, method = "stepwise", k = 2)
+
+```
+
 all.data3_val<- all.data3[,c(1,228:283)]
@@
 library(InPosition)
+
+```{r}
 var.PCA.scr_hr_pup_val <-InPosition::epPCA.inference.battery(all.data3_forPCA_withval[,4:226], 
@@
                                        critical.value = 2)
+
+View(clustering_new_pre_PCA)
+
+# start by creating a cluster within self reports
+?cut
+clustering_new_pre_PCA$arousal_3cat <- cut(clustering_new_pre_PCA$arousal, 3, labels = c("low", "mid", "high"))
+
+colnames(clustering_new_pre_PCA)
+
+var.design_ar = as.factor(clustering_new_pre_PCA$arousal_3cat)
+
+library(prettyGraphs)
+library(InPosition)
+
+View(clustering_new_pre_PCA)
+clustering_new_pre_PCA[,6:8]
+
+clustering_new_pre_PCA1<- subset(clustering_new_pre_PCA,
+                                 !is.na(pup_basCor))
+
+var.design_ar = as.factor(clustering_new_pre_PCA1$arousal_3cat)
+ table(is.na(var.design_ar))
+
+ clustering_new_pre_PCA2<- subset(clustering_new_pre_PCA1, !is.na(arousal_3cat))
+
+ var.design_ar<- c(clustering_new_pre_PCA2$arousal_3cat)
+
+ clustering_new_pre_PCA2$arousal_3cat <- cut(clustering_new_pre_PCA2$arousal, 2,
+                                            labels = c("low", "high"))
+
+# ExPosition:
+ ?TInPosition::tepBADA.inference.battery
+var.bada.ar_physio <- TInPosition::tepBADA.inference.battery(clustering_new_pre_PCA2[,6:8], 
+                                                       scale = FALSE, 
+                                                       center = FALSE, 
+                                                       # DESIGN = factor( clustering_new_pre_PCA2$arousal_3cat ),
+                                                        DESIGN = factor(var.design_ar ),
+                                                       make_design_nominal = TRUE,
+                                                       group.masses = NULL, 
+                                                       weights = NULL, 
+                                                       graphs = TRUE, 
+                                                       k = 2, 
+                                                       test.iters = 100, 
+                                                       critical.value = 2)
+
+var.bada.ar_physio[["Fixed.Data"]][["TExPosition.Data"]][["fii"]][,1]
+
+clustering_new_pre_PCA2$test_pc1<-var.bada.ar_physio[["Fixed.Data"]][["TExPosition.Data"]][["fii"]][,1]
+
+library(tidyverse)
+
+clustering_new_pre_PCA2%>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  # subset(arousal> -6)%>%
+  ggplot(aes(valence, test_pc1 ))+
+  geom_point()+
+  ggpubr::stat_cor()+
+  geom_smooth(method = 'lm')
+  xlim(-6,3.2)
+
+  # get ground truth data
+clustering_new_pre_PCA2
+
+colnames(db_full4new_stim_screen_pupil_nopract)
+
+stimIapsval<- db_full4new_stim_screen_pupil_nopract %>%
+  group_by(stimIAPS2)%>%
+  summarise_at(c("ValenceMean", "ArousalMean"), mean, na.rm = TRUE)
+
+clustering_new_pre_PCA3 <- left_join(clustering_new_pre_PCA2, stimIapsval)
+
+clustering_new_pre_PCA3$arousal_3cat_ground<- cut(clustering_new_pre_PCA3$ArousalMean,3, labels = 
+                                                    c("low", "mid", "high"))
+
+#
+
+var.design_ar_2<- factor(clustering_new_pre_PCA3$arousal_3cat_ground )
+
+table(is.na( var.design_ar_2))
+# sum(var.design_ar_2)
+# TExPosition::tepBADA()
+var.bada.ar_physio2 <- TInPosition::tepBADA.inference.battery(clustering_new_pre_PCA3[,6:8], 
+                                                       scale = TRUE, 
+                                                       center = TRUE, 
+                                                       # DESIGN = factor( clustering_new_pre_PCA2$arousal_3cat ),
+                                                        DESIGN = var.design_ar_2,
+                                                       make_design_nominal = TRUE,
+                                                       group.masses = NULL, 
+                                                       weights = NULL, 
+                                                       graphs = TRUE, 
+                                                       k = 2, 
+                                                       test.iters = 100, 
+                                                       critical.value = 2)
+
+# do with valence
+
+clustering_new_pre_PCA3$arousal_3cat<- cut(clustering_new_pre_PCA3$valence,3, labels = 
+                                                    c("neg", "mid", "pos"))
+
+#
+
+var.design_ar_2<- factor(clustering_new_pre_PCA3$arousal_3cat_ground )
+
+table(is.na( var.design_ar_2))
+# sum(var.design_ar_2)
+# TExPosition::tepBADA()
+var.bada.vl_physio3 <- TInPosition::tepBADA.inference.battery(clustering_new_pre_PCA3[,6:8], 
+                                                       scale = TRUE, 
+                                                       center = TRUE, 
+                                                       # DESIGN = factor( clustering_new_pre_PCA2$arousal_3cat ),
+                                                        DESIGN = factor(clustering_new_pre_PCA3$arousal_3cat),
+                                                       make_design_nominal = TRUE,
+                                                       group.masses = NULL, 
+                                                       weights = NULL, 
+                                                       graphs = TRUE, 
+                                                       k = 2, 
+                                                       test.iters = 100, 
+                                                       critical.value = 2)
+
+clustering_new_pre_PCA3$vall_3_gr<- cut(clustering_new_pre_PCA3$ValenceMean,3, labels = 
+                                                    c("neg", "mid", "pos"))
+
+table(is.na( var.design_ar_2))
+# sum(var.design_ar_2)
+# TExPosition::tepBADA()
+var.bada.vlgr_physio4 <- TInPosition::tepBADA.inference.battery(clustering_new_pre_PCA3[,6:8], 
+                                                       scale = TRUE, 
+                                                       center = TRUE, 
+                                                       # DESIGN = factor( clustering_new_pre_PCA2$arousal_3cat ),
+                                                        DESIGN = factor(clustering_new_pre_PCA3$vall_3_gr),
+                                                       make_design_nominal = TRUE,
+                                                       group.masses = NULL, 
+                                                       weights = NULL, 
+                                                       graphs = TRUE, 
+                                                       k = 2, 
+                                                       test.iters = 100, 
+                                                       critical.value = 2)
+
+# MFA
+
+res.mfa <- MFA(clustering_new_pre_PCA_2, 
+               group = c(2, 1, 1, 1), 
+               type = c("n", "s", "s", "s"),
+               name.group = c("pp_stim","pupil","HR","SCR"),
+               # num.group.sup = c(1,2),
+               graph = TRUE)
+
+colnames(clustering_new_pre_PCA3)
+
+clustering_new_pre_PCA3$arousal_3cat<- cut(clustering_new_pre_PCA3$arousal,3, labels = 
+                                                    c("low", "mid", "high"))
+c<-FactoMineR::MFA(clustering_new_pre_PCA3[,c(1,14,6:8)], 
+               group = c(2, 1, 1, 1), 
+               type = c("n", "s", "s", "s"),
+               name.group = c("pp_stim","pupil","HR","SCR"),
+               num.group.sup = c(1,2),
+               graph = TRUE)
+
+?FactoMineR::MFA
+FactoMineR::MFA(clustering_new_pre_PCA3[,c(1,4,6:8,9,10)], 
+               group = c(2, 1, 1, 1,1,1), 
+               type = c("n", "s", "s", "s", "s", "s"),
+               name.group = c("pp_stim","pupil","HR","SCR", "arousal", "valence"),
+               num.group.sup = c(1,2),
+               graph = TRUE)
+
+# valence and arousal are creatign a strign compoent one maybe vecause of thir correlatipn
+# so below I am droping one to see if we have more coherence
+# ?
+FactoMineR::MFA(clustering_new_pre_PCA3[,c(1,4,6:8,9)], 
+               group = c(2, 1, 1, 1,1), 
+               type = c("n", "s", "s", "s", "s"),
+               name.group = c("pp_stim","pupil","HR","SCR", "arousal"),
+               num.group.sup = c(1,2),
+               ind.sup = c(1,2),
+               graph = TRUE)
+
+# include 
+colnames(clustering_new_pre_PCA3)
+unique(clustering_new_pre_PCA3$stimDescription)
+
+clustering_new_pre_PCA3.1<- clustering_new_pre_PCA3[,c(1,4,6,7,8,9,10)]
+res.mfa_bio_vs_self<- FactoMineR::MFA(clustering_new_pre_PCA3.1, 
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+               # "s", "s", "s"
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+```
+
+```{r}
+# use stim as indicator
+colnames(clustering_new_pre_PCA3)
+clustering_new_pre_PCA3.1<- clustering_new_pre_PCA3[,c(1,5,6,7,8,9,10)]
+
+res.mfa_bio_vs_self2<- FactoMineR::MFA(clustering_new_pre_PCA3.1[,2:7], 
+               group = c(1, 3, 2), 
+               type = c("n", "s", "s"),
+               # "s", "s", "s"
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+# now z score within participant
+clustering_new_pre_PCA3.1.scale<- clustering_new_pre_PCA3.1%>%
+  group_by(ssid)%>%
+  mutate_if(is.numeric, scale)
+
+clustering_new_pre_PCA3.1.scale$stim_descr
+res.mfa_bio_vs_self2_scale<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale[,2:7], 
+               group = c(1, 3, 2), 
+               type = c("n", "s", "s"),
+               # "s", "s", "s"
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+# Now try HMFA
+
+library(FactoMineR)
+??HMFA
+
+H_n<- clustering_new_pre_PCA3.1.scale%>%
+  group_by(ssid)%>%
+  mutate(n = n())%>%
+  summarise_at(c("n"), mean, na.rm = TRUE)
+
+H_n.1<- H_n$n
+
+as.list(H_n.1)
+c(H_n.1)
+
+hierar<- list(c(H_n.1))
+
+View(wine)
+FactoMineR::HMFA(clustering_new_pre_PCA3.1.scale[,2:7],
+                 H = hierar, 
+               # group = c(1, 3, 2), 
+               type = c("n", "s", "s",  "s", "s",  "s"),
+               # "s", "s", "s"
+               name.group = c("pp_stim","auton","subj"),
+               # num.group.sup = c(1),
+                 # ncp = 
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+# okay try and aggregate  response per stimuli
+
+clustering_new_pre_PCA3.1.scale_agg_bystim<- clustering_new_pre_PCA3.1%>%
+  group_by(stimDescription)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)
+
+clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg<- clustering_new_pre_PCA3.1.scale_agg_bystim%>%
+  mutate_if(is.numeric, scale)
+
+res.mfa_bio_vs_self2_scale_aggbystim<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bystim, 
+               group = c(1, 3, 2), 
+               type = c("n", "s", "s"),
+               # "s", "s", "s"
+               name.group = c("stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+```
+
+```{r}
+res.mfa_bio_vs_self2_scale_afteraggbystim<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg, 
+               group = c(1, 3, 2), 
+               type = c("n", "s", "s"),
+               # "s", "s", "s"
+               name.group = c("stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+```
+
+# agg by pp
+
+```{r}
+clustering_new_pre_PCA3.1.scale_agg_bysid<- clustering_new_pre_PCA3.1%>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)
+
+clustering_new_pre_PCA3.1.scale_aft_agg_bysid<- clustering_new_pre_PCA3.1.scale_agg_bysid%>%
+  mutate_if(is.numeric, scale)
+
+ FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bysid, 
+               group = c(1, 3, 2), 
+               type = c("n", "s", "s"),
+               # "s", "s", "s"
+               name.group = c("stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+```
+
+# now keep participant just cast pupil etc
+clustering_new_pre_PCA3.1.scale
+
+# dcast
+
+library(data.table)
+
+colnames(clustering_new_pre_PCA3.1.scale)
+clustering_new_pre_PCA3.1.scale$pup_basCor<- clustering_new_pre_PCA3.1.scale$pup_basCor[,1]
+
+clustering_new_pre_PCA3.1.scale$Bio_Mean_HR_dif<- clustering_new_pre_PCA3.1.scale$Bio_Mean_HR_dif[,1]
+
+clustering_new_pre_PCA3.1.scale$log_BIO_CDA.PhasicMax<- clustering_new_pre_PCA3.1.scale$log_BIO_CDA.PhasicMax[,1]
+
+clustering_new_pre_PCA3.1.scale$arousal<- clustering_new_pre_PCA3.1.scale$arousal[,1]
+
+clustering_new_pre_PCA3.1.scale$valence<- clustering_new_pre_PCA3.1.scale$valence[,1]
+
+clustering_new_pre_PCA3.1.scale_dcast<- data.table::dcast(setDT(clustering_new_pre_PCA3.1.scale), 
+                    ssid  ~ stimDescription, 
+                    value.var = c('pup_basCor',
+                'Bio_Mean_HR_dif', 'log_BIO_CDA.PhasicMax', 'arousal','valence'), fun.aggregate = mean)
+
+colnames(clustering_new_pre_PCA3.1.scale_dcast)
+
+res.mfadcast <- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_dcast[,
+                                                                      2:ncol(clustering_new_pre_PCA3.1.scale_dcast)], 
+               group = c(52, 52, 52, 52, 52), 
+               type = c("s", "s", "s", "s", "s"),
+               # "s", "s", "s"
+               name.group = c("pup","hr", "scr", "ar", "vl"),
+               # num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+53-2 #pupil
+
+```
 
@@
 
+View(clustering_new_pre_PCA_2)
 clustering_new_pre_PCA_2$stimDescription
+colnames(clustering_new_pre_PCA_2)
+
+res.mfa <- MFA(wine, 
+               group = c(2, 5, 3, 10, 9, 2), 
+               type = c("n", "s", "s", "s", "s", "s"),
+               name.group = c("origin","odor","visual",
+                              "odor.after.shaking", "taste","overall"),
+               num.group.sup = c(1, 6),
+               graph = FALSE)
+
 res.mfa <- MFA(clustering_new_pre_PCA_2, 
-               group = c(2, 1, 1, 1, 2, 1), 
-               type = c("n", "s", "s", "s", "s", "s"),
-               name.group = c("pp_stim","pupil","HR","SCR", "ar_val","fix"),
-               num.group.sup = c(1,2),
+               group = c(2, 1, 1, 1), 
+               type = c("n", "s", "s", "s"),
+               name.group = c("pp_stim","pupil","HR","SCR"),
+               # num.group.sup = c(1,2),
                graph = TRUE)
@@
 ```
+
 ```{r}
@@
 ```{r}
+library(FactoMineR)
+library(factoextra)
+??fviz_screeplot
 fviz_screeplot(res.mfa)
@@
              )
+
+testget<-get_mfa(
+  res.mfa,
+  element = c("ind"))
+
+clustering_new_pre_PCA3$getindaxis<- testget[["coord"]][,1]
+clustering_new_pre_PCA3$getindaxis2<- testget[["coord"]][,2]
+
+clustering_new_pre_PCA3%>%
+  group_by(ssid)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(arousal, getindaxis))+
+  geom_point()+
+  ggpubr::stat_cor()+
+  xlim(-,3.3)
+
+clustering_new_pre_PCA3%>%
+  group_by(ssid, arousal_3cat)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(arousal, getindaxis2))+
+  geom_point()+
+  ggpubr::stat_cor()+
+  facet_grid(~arousal_3cat)
+  # xlim(-,3.3)
 

### 2022-02-07 Questionnaires_scoring2021.Rmd
07 Jan return

--- 2021-08-24 Questionnaires_scoring2021.Rmd
@@
 
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/data_exp_11458-v9 (2)/Select")
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport")
 
@@
 
+hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
 ```{r}
@@
 read_selfrep1 <- function(flnm) {
-    read_excel(flnm) %>%
+    read_csv(flnm) %>%
         mutate(filename = flnm)
@@
 
-db_AQ <- list.files(pattern = "*.xlsx", 
+# lvevkz = 356
+db_aq_356<- subset(db_AQ, `Participant Completion Code` == "lvevkz")
+
+db_AQ_backup<- db_AQ
+
+db_AQ <- list.files(pattern = "*.csv", 
                full.names = T) %>% 
@@
 
-db_AQ <- read_excel("data_exp_11458-v9_questionnaire-7uqw-4489770.xlsx")
+# db_AQ <- read_excel("data_exp_11458-v9_questionnaire-7uqw-4489770.xlsx")
+
+unique(db_AQ$`Participant Completion Code`)
+unique(db_AQ$`Participant Public ID`)
 
@@
 colnames(db_AQ)
+colnames(db_aq_356)
+
+db_AQ<- bind_rows(db_AQ, db_aq_356)
+
+colnames(db_AQ)
+
+db_AQ$completion_code<- db_AQ$`Participant Completion Code`
 
 db_AQ1<- db_AQ%>%
-  select(c(16,33:132))
+  select(c(18,34:133))
 
@@
 
+# selecting quqntised
 db_AQ2<- db_AQ1%>%
 select(seq(1, 101, 2))
+
+colnames(db_AQ2)
 
@@
 aq_labels<-paste(prefix, AQ_counter, sep = "")
+
 # generate odd numbers to match the columns we wnt to keep
@@
 
+db_AQ4
+
 ```
@@
 ```{r}
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/TAS/356_557_611_616")
 
 read_selfrep <- function(flnm) {
-    readxl::read_xlsx(flnm) %>%
+    read_csv(flnm) %>%
         mutate(filename = flnm)
@@
 
+db_TAS_backup<- db_TAS
+db_TAS_356<- subset(db_TAS, `Participant Completion Code` == "lvevkz")
+
+db_TAS <- list.files(pattern = "*.csv", 
+               full.names = T) %>% 
+    map_df(~read_selfrep(.))
+
 library(readxl)
-db_TAS <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/TAS/data_exp_11458-v9_questionnaire-pdlt-4489770.xlsx")
+# db_TAS <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/TAS/data_exp_11458-v9_questionnaire-pdlt-4489770.xlsx")
 
@@
 colnames(db_TAS)
+colnames(db_TAS_356)
+db_TAS<- bind_rows(db_TAS, db_TAS_356)
 
@@
 
+hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
+db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
+
 ```{r}
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/DASS/356_357_611_616")
+
 read_selfrep <- function(flnm) {
@@
 }
+
+db_DASS_backup<- db_DASS
+unique(db_DASS$`Participant Completion Code`)
+db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
 
@@
 library(readr)
-db_DASS <- read_xlsx("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")
 
-("Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")
+# db_DASS <- read_xlsx("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")
+# 
+# ("Short format/DASS/data_exp_11458-v9_questionnaire-chif-4489770.xlsx")
 
@@
 
+db_DASS<-  bind_rows(db_DASS, db_DASS_356)
+
 colnames(db_DASS)
+
 db_DASS1<- db_DASS%>%
-  select(c(12,13,16,32:74))
+  select(c(14,15,18,34:74))
 
 colnames(db_DASS1)
+db_DASS1$`Repeat Key`<- NULL
+
+db_DASS1$completi
 
@@
 select(c(1:3,seq(4, 44, 2)))
+colnames(db_DASS2)
 
@@
 
-db_DASS4<- select(db_DASS3, c(1:2,29,25:28))
+db_DASS4<- select(db_DASS3, c(1:2,29,25:29))
 db_DASS4
@@
 https://xavierrg.shinyapps.io/datacleaning/
+
+hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
+db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
 ```{r eval=FALSE, include=FALSE}
@@
 
+db_TAS_backup$`Participant Private ID`[db_TAS_backup$`Participant Completion Code` == "lvevkz"]
+
+db_IAS_356<- subset(db_IAS, db_IAS$`Participant Private ID` == 4520106)
+db_IAS_backup<- db_IAS
+
+# library(readr)
+db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/356_357_611_616/356_357_611_616All_scores_ias_2021-09-13.csv")
+View(db_IAS)
 ```
@@
 # Dependencies: 03_scoring_helpers.R, tidyverse
+
+hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
+db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
 ```{r}
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ")
+# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ")
+
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ/356_357_611_616")
 
@@
 library(readxl)
-db_BPQ <- read_excel("data_exp_11458-v9_questionnaire-bbc4.xlsx")
-View(data_exp_11458_v9_questionnaire_bbc4)
+# db_BPQ <- read_excel("data_exp_11458-v9_questionnaire-bbc4.xlsx")
+# View(data_exp_11458_v9_questionnaire_bbc4)
 
@@
 # db_BPQ <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ/data_exp_11458-v9_questionnaire-bbc4-4489770.xlsx")
+
+db_BPQ_backup<- db_BPQ
+db_BPQ_356<- subset(db_BPQ, db_BPQ$completion_code == "lvevkz")
 
@@
 db_BPQ$completion_code<- db_BPQ$`Participant Completion Code`
+
+db_BPQ_356$`Event Index`<- as.character(db_BPQ_356$`Event Index`)
+db_BPQ<- bind_rows(db_BPQ, db_BPQ_356)
 
@@
 
+hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
+db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
+
 ```{r}
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1")
+# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1")
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1/356_357_611_616")
+
 read_selfrep <- function(flnm) {
-    readxl::read_xlsx(flnm) %>%
+    read_csv(flnm) %>%
         mutate(filename = flnm)
@@
 
-db_BVAQ <- list.files(pattern = "*-83b1.xlsx", 
+db_BVAQ_backup<- db_BVAQ
+
+db_BVAQ_356<- subset(db_BVAQ, db_BVAQ$completion_code == "lvevkz")
+
+db_BVAQ <- list.files(pattern = "*-83b1.csv", 
                full.names = T) %>% 
@@
 
+db_BVAQ<- bind_rows(db_BVAQ, db_BVAQ_356)
+
 db_BVAQ1<- db_BVAQ %>%
@@
    select(c("Participant Private ID","completion_code",BVAQ_01:BVAQ_40))
+
+colnames(db_BVAQ1)
 
@@
 
+hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
+db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
+
 ```{r}
@@
 
-db_age <- list.files(pattern = "*-8zto.xlsx", 
+read_selfrep <- function(flnm) {
+    read_csv(flnm) %>%
+        mutate(filename = flnm)
+}
+
+db_age_backup<- db_age
+
+db_age_356<- subset(db_age, db_age$`Participant Completion Code` == "lvevkz")
+
+db_age <- list.files(pattern = "*-8zto.csv", 
                full.names = T) %>% 
@@
 
+db_age<- bind_rows(db_age, db_age_356)
+
 # db_age <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-8zto-4489770.xlsx")
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/vision8nsp")
 
-db_vision <- list.files(pattern = "*-8nsp.xlsx", 
+db_vision_backup<- db_vision
+db_vision_356<- subset(db_vision, db_vision$`Participant Completion Code` == "lvevkz")
+
+db_vision <- list.files(pattern = "*-8nsp.csv", 
                full.names = T) %>% 
@@
 
-library(readxl)
+db_vision<- bind_rows(db_vision, db_vision_356)
 
 # db_vision <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/data_exp_11458-v9_questionnaire-8nsp-4489770.xlsx")
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn/vision8nsp")
+db_mhealth_backup<- db_mhealth
 
-db_mhealth <- list.files(pattern = "*-v2gn.xlsx", 
+db_mhealth_356<- subset(db_mhealth,db_mhealth$`Participant Completion Code` == "lvevkz")
+
+db_mhealth <- list.files(pattern = "*-v2gn.csv", 
                full.names = T) %>% 
     map_df(~read_selfrep(.))
+
+db_mhealth$`mental_health-text`<- as.character(db_mhealth$`mental_health-text`)
+db_mhealth<- bind_rows(db_mhealth, db_mhealth_356)
 
@@
 db_age1<- select(db_age, c(1,13,16,35,36))
+db_age1<- subset(db_age1, db_age1$`Event Index` == 1)
+db_vision1<- subset(db_vision, db_vision$`Event Index` == 1)
+db_mhealth1<- subset(db_mhealth, db_mhealth$`Event Index` == 1)
 
@@
 
+colnames(db_mhealth1)
+
 colnames(db_vision)
@@
 
-db_demog<- left_join(db_vision1, db_mhealth1,db_age1, by = c("Participant Private ID",
-                                                   "Participant Completion Code"))%>%
-  subset(!is.na(`Participant Private ID`))
+colnames(db_vision1)
+
+# db_age1<- select(db_age, c(1,13,16,35,36))
+db_age1<- subset(db_age1, db_age1$`Event Index` == 1)
+db_vision1<- subset(db_vision1, db_vision1$`Event Index` == 1)
+db_mhealth1<- subset(db_mhealth1, db_mhealth1$`Event Index` == 1)
+
+# note this is ignoring the last
+db_demog <- left_join(db_vision1, db_mhealth1, by = c("Participant Private ID",
+                                                   "Participant Completion Code"))
+
+db_demog <- left_join(db_demog,db_age1, by = c("Participant Private ID",
+                                                   "Participant Completion Code"))
 
@@
 Lucy: https://docs.google.com/spreadsheets/d/1P9x7oHxpUTanb412czfgYqR_stPJ3fHzwYiItANpfO8/edit#gid=277478937
+
+hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
+db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
 ```{r}
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8")
+# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8")
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IQ_esh8/356_357_611_616")
 
 read_selfrep <- function(flnm) {
-    readxl::read_xlsx(flnm) %>%
+    read_csv(flnm) %>%
         mutate(filename = flnm)
@@
 
-db_IQ <- list.files(pattern = "*-esh8.xlsx", 
+db_IQ_backup<- db_IQ
+
+db_IQ_356<- subset(db_IQ, db_IQ$`Participant Completion Code` =="lvevkz" )
+colnames(db_IQ1)
+db_IQ <- list.files(pattern = "*-esh8.csv", 
                full.names = T) %>% 
@@
 colnames(db_IQ)
-
-db_IQ1<- select(db_IQ, c(1,13,16, 37,40:44))
+iqnames<- colnames(db_IQ1)
+# db_IQ1<- select(db_IQ, c(1,12,15, 35,38:44))
+db_IQ1<- select(db_IQ, iqnames)
 
@@
 colnames(db_IQ3)
-db_IQ4<- select(db_IQ3,c(1,9,8))
+db_IQ4<- select(db_IQ3,c(1,7,6))
 
@@
 ```{r}
+
+db_demog$completion_code <- db_demog$`Participant Completion Code`
 db_demog$`Participant Completion Code`<- NULL
-
-db_demog$completion_code<- db_demog$`Participant Completion Code`
 
@@
 
-db_self_rep <- Reduce(merge, list(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS))
+db_self_rep_backup<- db_self_rep
 
-db_self_rep <- cbind(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS)
+db_AQ4
+# db_demog has priovate and code
+db_code_private<- select(db_demog, c(completion_code, `Participant Private ID`))
+db_IAS<- left_join(db_IAS,db_code_private, by = "completion_code")
+
+# merge all side by side based on a comoon column
+db_self_rep_temp<- left_join(db_demog, db_DASS4, by = "completion_code")
+db_self_rep_temp<- left_join(db_self_rep_temp, db_TAS4, by = "completion_code")
+db_self_rep_temp<- left_join(db_self_rep_temp, db_AQ4, by = "completion_code")
+db_self_rep_temp<- left_join(db_self_rep_temp, db_BVAQ3, by = "completion_code")
+
+db_self_rep_temp<- left_join(db_self_rep_temp, db_IQ4, by = "completion_code")
+
+db_self_rep_temp<- left_join(db_self_rep_temp, db_BPQ3, by = "completion_code")
+db_self_rep_temp<- left_join(db_self_rep_temp, db_IAS, by = "completion_code")
+
+# db_self_rep <- Reduce(merge, list(db_demog$completion_code,db_DASS4,db_TAS4$completion_code, db_AQ4$completion_code, db_BVAQ3$completion_code, db_IQ4$completion_code, db_BPQ3,db_IAS$`Participant Private ID`))
+
+db_demog
+# db_self_rep <- cbind(db_demog,db_DASS4,db_TAS4, db_AQ4, db_BVAQ3, db_IQ4, db_BPQ3,db_IAS)
+db_self_rep_backup<- db_self_rep
+db_self_rep<- db_self_rep_temp
 
 db_self_rep
-write_csv(db_self_rep, "db_self_rep_345_356.csv")
+# write_csv(db_self_rep, "db_self_rep_345_356.csv")
 
-write_csv(db_self_rep, "db_self_rep_350.csv")
+# write_csv(db_self_rep, "db_self_rep_350.csv")
+
+write_csv(db_self_rep, "db_self_rep_356_367_611_616.csv")
 
@@
 
+hcqzar		mobile	Samsung SM-G950F	Android 9 are the same person = 357
+db_DASS_356<- subset(db_DASS, `Participant Completion Code`== "lvevkz")
+```{r}
+# STAI_T:: 5nzr
+
+# setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_T_5nzr")
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_T_5nzr/356_356_611_616")
+
+# STAIS: 8rfo
+
+read_selfrep <- function(flnm) {
+    readxl::read_xlsx(flnm) %>%
+        mutate(filename = flnm)
+}
+
+read_selfrep <- function(flnm) {
+    read_csv(flnm) %>%
+        mutate(filename = flnm)
+}
+
+library(readxl)
+db_STAI_T <- read_excel("data_exp_11458-v9_questionnaire-5nzr_345_356.xlsx")
+
+db_STAI_T_backup<- db_STAI_T
+
+db_STAI_T_356<- subset(db_STAI_T, db_STAI_T$completion_code == "lvevkz")
+
+db_STAI_T<- list.files(pattern = "*-5nzr.csv", 
+               full.names = T) %>% 
+    map_df(~read_selfrep(.))
+
+db_STAI_T_356$`Event Index`<- as.character(db_STAI_T_356$`Event Index`)
+
+db_STAI_T<- bind_rows(db_STAI_T, db_STAI_T_356)
+
+# eliminate empty rows
+db_STAI_T<- subset(db_STAI_T, db_STAI_T$`Event Index`== 1)
+
+db_STAI_T$completion_code<- db_STAI_T$`Participant Completion Code`
+
+# use the quantised columns as the response siunce they have a number rather than a string
+
+colnames(db_STAI_T)
+db_STAI_T1<- db_STAI_T %>%
+    select("Participant Private ID","completion_code", 
+           STAI_01:STAI_20)%>%
+  # drop anything with quantised or text
+  select(-contains("quantised"))
+
+# score
+
+colnames(db_STAI_T1)
+# do the actual scoring, only on the BPQ part - bpdy awareness
+db_STAI_T2<- db_STAI_T1%>%
+   mutate(STAIT = rowSums(.[ 3:22]))
+
+colnames(db_STAI_T2)
+db_STAI_T3<- select(db_STAI_T2, c(1:2, 23))
+db_STAI_T3
+
+library(readxl)
+# db_STAI_S <- read_excel("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_S_8rfo/data_exp_11458-v9_questionnaire-8rfo_345_356.xlsx")
+setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/STAI_S_8rfo/356_357_611_616")
+
+db_STAI_S_backup<- db_STAI_S
+
+db_STAI_S_546<- subset(db_STAI_S, db_STAI_S$completion_code == "lvevkz")
+
+db_STAI_S<- list.files(pattern = "*-8rfo.csv", 
+               full.names = T) %>% 
+    map_df(~read_selfrep(.))
+
+db_STAI_S_546$`Event Index`<- as.character(db_STAI_S_546$`Event Index`)
+
+db_STAI_S<- bind_rows(db_STAI_S, db_STAI_S_546)
+
+# eliminate empty rows
+db_STAI_S <- subset(db_STAI_S, db_STAI_S$`Event Index`== 1)
+
+db_STAI_S$completion_code<- db_STAI_S$`Participant Completion Code`
+
+# use the quantised columns as the response siunce they have a number rather than a string
+
+colnames(db_STAI_S)
+
+db_STAI_S1<- db_STAI_S %>%
+    select("Participant Private ID","completion_code", 
+           STAIS_01:STAIS_20)%>%
+  # drop anything with quantised or text
+  select(-contains("quantised"))
+
+# score
+
+colnames(db_STAI_S1)
+# do the actual scoring, only on the BPQ part - bpdy awareness
+db_STAI_S2<- db_STAI_S1%>%
+   mutate(STAIS = rowSums(.[ 3:22]))
+
+colnames(db_STAI_S2)
+
+db_STAI_S3<- select(db_STAI_S2, c(1:2, 23))
+colnames(db_STAI_S3)
+
+db_STAI<- left_join(db_STAI_S3, db_STAI_T3)
+
+```
+
 merge 
 ```{r}
-
 db_self_rep
 library(readr)
-db_self_rep_350_1 <- read_csv("db_self_rep_350.1.csv")
+# db_self_rep_350_1 <- read_csv("db_self_rep_350.1.csv")
 # View(db_self_rep_350_1)
@@
 
-db_self_rep_345_356<- bind_rows(db_self_rep,db_self_rep_350_1)
+# db_self_rep_345_356<- bind_rows(db_self_rep,db_self_rep_350_1)
+colnames(db_self_rep)
+
+db_self_rep_345_356<- db_self_rep[,c(1:25)]
+
+# library(readxl)
+Interoception_Study_Logbook <- read_excel("Interoception Study Logbook.xlsx")
+
+library(readxl)
+Interoception_Study_Logbook <- read_excel("Interoception Study Logbook _with456_357_611_616.xlsx")
+# View(Interoception_Study_Logbook_with456_357_611_616)
+View(Interoception_Study_Logbook)
+
+db_self_rep_345_356$completion_code
+
+Interoception_Study_Logbook$completion_code
+
+ssid<- select(Interoception_Study_Logbook, c(1:3))
+ssid$completion_code<- ssid$`Completion Code`
+
+db_self_rep_345_356<- left_join(db_self_rep_345_356,ssid, by = "completion_code")
+# write_csv(db_self_rep_345_356, "db_self_rep_345_356_final.csv")
+write_csv(db_self_rep_345_356, "db_self_rep_356_357_611_616_final.csv")
+```
+
+# - CHECK WASI M on the norms
+
+db_age2<- subset(db_age1, !is.na(`Participant Private ID`))
+db_age2
+
+db_self_rep_345_356<- left_join(db_self_rep_345_356,db_age2)
+
+db_self_rep_345_356
+
 colnames(db_self_rep_345_356)
 
-db_self_rep_345_356<- db_self_rep_345_356[,c(1:22)]
+db_self_rep_345_356
 
-write_csv(db_self_rep, "db_self_rep_345_356_final.csv")
+db_self_rep_345_356<- left_join(db_self_rep_345_356, db_STAI)
+
 ```

### 2022-02-08 Paper_Analyses_subj_obje_arousal.Rmd
recover  accidentally discarded changes

@@
 
+clustering_new_pre_PCA3$AR
 clustering_new_pre_PCA3.1<- clustering_new_pre_PCA3[,c(1,4,6,7,8,9,10)]
@@
 colnames(clustering_new_pre_PCA3)
-clustering_new_pre_PCA3.1<- clustering_new_pre_PCA3[,c(1,5,6,7,8,9,10)]
-
-res.mfa_bio_vs_self2<- FactoMineR::MFA(clustering_new_pre_PCA3.1[,2:7], 
-               group = c(1, 3, 2), 
+
+clustering_new_pre_PCA3$val_cut_iaps<- cut(clustering_new_pre_PCA3$ValenceMean, 3, labels = 
+                                             c("neg", "mid", "pos"))
+
+clustering_new_pre_PCA3$aro_cut_iaps<- cut(clustering_new_pre_PCA3$ArousalMean, 3, labels = 
+                                             c("low", "mid", "high"))
+clustering_new_pre_PCA3.1<- clustering_new_pre_PCA3[,c(1,5,22,23,6,7,8,9,10)]
+colnames(clustering_new_pre_PCA3.1)
+
+res.mfa_bio_vs_self2<- FactoMineR::MFA(clustering_new_pre_PCA3.1[,1:9], 
+               group = c(4, 3, 2), 
                type = c("n", "s", "s"),
@@
 clustering_new_pre_PCA3.1.scale$stim_descr
+
+clustering_new_pre_PCA3.1.scale
 res.mfa_bio_vs_self2_scale<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale[,2:7], 
@@
                graph = TRUE)
+
+dimdesc(res.mfa_bio_vs_self2_scale)
+
+TInPosition::
+```
+
+```{r}
+# get_eigenvalue(res.mfa): Extract the eigenvalues/variances retained by each dimension (axis)
+eig.val_bui_self_scl <- get_eigenvalue(res.mfa_bio_vs_self2_scale)
+head(eig.val_bui_self_scl)
+
+# The function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
+
+fviz_screeplot(res.mfa_bio_vs_self2_scale)
+
+group_bio_self_scl <- get_mfa_var(res.mfa_bio_vs_self2_scale, "group")
+group_bio_self_scl
+
+# Coordinates of groups
+options(scipen = 999)
+head(group_bio_self_scl$coord)
+
+#    Dim.1      Dim.2      Dim.3     Dim.4        Dim.5
+# auton 0.5042850 0.98835343 0.85875961 0.4433362 0.0008990348
+# subj  0.6790127 0.00720065 0.01629939 0.3014437 0.2019402875
+
+head(group_bio_self_scl$cos2) 
+# Cos2: quality of representation on the factore map
+
+#        Dim.1         Dim.2        Dim.3      Dim.4           Dim.5
+# auton 0.09726538 0.37362051551 0.2820651231 0.07517484 0.0000003091428
+# subj  0.44230732 0.00004974068 0.0002548654 0.08717275 0.0391213886164
+
+# Contributions to the  dimensions
+head(group_bio_self_scl$contrib)
+
+#          Dim.1      Dim.2     Dim.3   Dim.4      Dim.5
+# auton 42.61692 99.2767194 98.137338 59.5258  0.4432251
+# subj  57.38308  0.7232806  1.862662 40.4742 99.5567749
+
+# draw a bar plot of groups contribution to the dimensions
+
+# Contribution to the first dimension
+fviz_contrib(res.mfa_bio_vs_self2_scale, "group", axes = 1)
+# Contribution to the second dimension
+fviz_contrib(res.mfa_bio_vs_self2_scale, "group", axes = 2)
+# basically they are contibuting to separate dimensions
+
+# is this improved if we dropping pupil?
+
+# res.mfa_bio_vs_self2_scale_nopup<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale[,c(2, 4,6:7)], 
+#                group = c(1, 1, 2), 
+#                type = c("n", "s", "s"),
+#                # "s", "s", "s"
+#                name.group = c("pp_stim","auton","subj"),
+#                num.group.sup = c(1),
+#                # ind.sup = c(1,2),
+#                graph = TRUE)
+# 
+# 
+# # Contribution to the first dimension
+# fviz_contrib(res.mfa_bio_vs_self2_scale_nopup, "group", axes = 1)
+# # Contribution to the second dimension
+# fviz_contrib(res.mfa_bio_vs_self2_scale_nopup, "group", axes = 2)
+# basically they are contibuting to separate dimensions
+
+#
+# is this improved if we dropping pupil? almost but not really
+
+# head(res.mfa_bio_vs_self2_scale_nopup$global.pca)
+
+?dimdesc
+probabchecl<- dimdesc(res.mfa_bio_vs_self2_scale, axes = 1:2, proba = .05)
+
+```
+
+quantitative variables
+```{r}
+quanti.var_bio_vs_self2_scale <- get_mfa_var(res.mfa_bio_vs_self2_scale, "quanti.var")
+quanti.var_bio_vs_self2_scale
+
+# Correlation between quantitative variables and dimensions.
+# corrwlation circle
+
+??factoextra::fviz_mfa_var
+
+res.mfa_bio_vs_self2_scale
+fviz_mfa_var(res.mfa_bio_vs_self2_scale, 
+             "quanti.var", 
+             palette = "jco", 
+             col.var.sup = "violet", 
+             repel = TRUE,
+              addEllipses = TRUE,
+             legend = "bottom",
+              gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+             col.var = "contrib" )
+
+fviz_mfa_var(res.mfa_bio_vs_self2_scale, "quanti.var", col.var = "contrib", 
+             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
+             col.var.sup = "violet", repel = TRUE,
+             geom = c("point", "text"))
+
+# Contributions to dimension 1
+fviz_contrib(res.mfa_bio_vs_self2_scale, choice = "quanti.var", axes = 1, top = 20,
+             palette = "jco")
+
+fviz_contrib(res.mfa_bio_vs_self2_scale, choice = "quanti.var", axes = 2, top = 20,
+             palette = "jco")
+
+```
+Graph of individuals  = rows
+```{r}
+fviz_mfa_ind(res.mfa_bio_vs_self2_scale, col.ind = "cos2", 
+             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
+             repel = TRUE)
+
+clustering_new_pre_PCA3.1.scale$stimDescription
+??fviz_mfa_ind
+fviz_mfa_ind(res.mfa_bio_vs_self2, 
+             habillage = "aro_cut_iaps", # color by groups 
+             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+
+             ellipse.type = "confidence", 
+             # geom = c("point"),
+             alpha.ind = .2,
+             addEllipses = TRUE, 
+             repel = TRUE # Avoid text overlapping
+             )
+
+fviz_mfa_ind(res.mfa_bio_vs_self2, 
+             habillage = "stimDescription", # color by groups 
+             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+
+             ellipse.type = "confidence", 
+             # geom = c("point"),
+             alpha.ind = .2,
+             addEllipses = TRUE, 
+             repel = TRUE # Avoid text overlapping
+             )
+
+fviz_mfa_ind(res.mfa_bio_vs_self2, 
+             habillage = "ssid", # color by groups 
+             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+
+             ellipse.type = "confidence", 
+             # geom = c("point"),
+             alpha.ind = .0,
+             addEllipses = TRUE, 
+             repel = TRUE # Avoid text overlapping
+             )
+
+```
+
+```{r}
+fviz_ellipses(res.mfa_bio_vs_self2, c("val_cut_iaps"), repel = TRUE)
+
+```
+
+# Graph of partial individuals
+The results for individuals obtained from the analysis performed with a single group are named partial individuals.
+In other words, an individual considered from the point of view of a single group is called partial individual.
+
+In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual.
+That is, the individual viewed by all groups of variables.
+
+For a given individual, there are as many partial points as groups of variables.
+
+The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:
+```{r}
+
+fviz_mfa_ind(res.mfa_bio_vs_self2, partial = "all")
+
+fviz_mfa_ind(res.mfa, 
+             partial = c("1neg", "1pos"))
+
+fviz_mfa_axes(res.mfa)
+
+# install.packages()
+
+install.packages("MExPosition")
+```
 
@@
 
+```{r}
+
 clustering_new_pre_PCA3.1.scale_agg_bystim<- clustering_new_pre_PCA3.1%>%
@@
                graph = TRUE)
+
+```
+Agg within participant by neg pos etc (using normative data)
+With and without selfreports
+
+```{r}
+?cut
+#create valence categories based ion self reports (IAPS validation)
+clustering_new_pre_PCA3_val_vat<- clustering_new_pre_PCA3%>%
+  mutate(valence_iaps_cat = cut(ValenceMean,3, labels = c("neg", "mid", "pos")))
+
+# scale within subject
+# aggregate by subject and
+
+View(clustering_new_pre_PCA3_val_vat)
+# clustering_new_pre_PCA3_val_vat%>%
+#   group_by(ssid)%>%
+#   mutate_if(is.numeric, scale)
+
+clustering_new_pre_PCA3_val_vat_agg<- clustering_new_pre_PCA3_val_vat%>%
+  group_by(ssid, valence_iaps_cat)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)
+
+library(factoextra)
+library(FactoMineR)
+
+colnames(clustering_new_pre_PCA3_val_vat_agg)
+clustering_new_pre_PCA3_val_vat_agg[,c(2,5,6,7,8,9)]
+
+FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_agg[,c(1,2,5,6,7,8,9)], 
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+               # "s", "s", "s"
+               name.group = c("ss_id_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+# scale
+clustering_new_pre_PCA3_val_vat_agg_scale<- clustering_new_pre_PCA3_val_vat_agg[,c(1,2,5,6,7,8,9)]
+
+clustering_new_pre_PCA3_val_vat_agg_scale%>%
+   # group_by(ssid)%>%
+  mutate_if(is.numeric, scale)
+
+clustering_new_pre_PCA3_val_vat_scale_then_agg<- clustering_new_pre_PCA3_val_vat%>%
+  group_by(ssid)%>%
+  mutate_if(is.numeric, scale)%>%
+  group_by(ssid, valence_iaps_cat)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)
+
+clustering_new_pre_PCA3_val_vat_scale_then_agg1<- clustering_new_pre_PCA3_val_vat_scale_then_agg[,c(1:2, 5:9)]
+
+?FactoMineR::MFA
+res.mfa_val_cat_scal<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_scale_then_agg1,
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+               name.group = c("ss_id_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+fviz_mfa_ind(res.mfa_val_cat_scal, 
+             habillage = "valence_iaps_cat", # color by groups 
+             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+             addEllipses = TRUE, 
+             ellipse.type = "confidence", 
+             repel = TRUE # Avoid text overlapping
+             )
+
+# we can sorta see that while things allign relativelly well on sujective dimension, they don't allugn very well on the autonomic dimension
 
@@
 
-here
-
 ```{r}
@@
 colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
+
+View(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
 res.mfa_agg_byval <- MFA(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2, 

### 2022-02-08 Paper_Analyses_subj_obje_arousal.Rmd
bootstrap for PCA/MFA
began the fucntions to do boostrap tests to ases stability of PCA/MFA results.

we could do a regular test like the probaility of more extreme values (eigen bectors.values) to the observed ones, but not sure this is appropriate.

A common option in papers is to compute confidence intervals around the estimate, to check if the values are above a certain treshold, e,g  5% 95% for eigenvalue of 1

@@
 clustering_new_pre_PCA3.1.scale
-res.mfa_bio_vs_self2_scale<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale[,2:7], 
+
+res.mfa_bio_vs_self2_scale <- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale[,2:7], 
                group = c(1, 3, 2), 
@@
 
-TInPosition::
+# validation
+# -	Some idea, get p values for factorminer – dimensions, and correklations
+# -	Stability of firt 2 dimensions by resampling
+
+res.mfa_bio_vs_self2_k2<- FactoMineR::MFA(clustering_new_pre_PCA3.1[,1:9], 
+               group = c(4, 3, 2), 
+               type = c("n", "s", "s"),
+              ind.sup = c(1),
+              ncp = 2,
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+# 
+# quanti
+
+# randomly resample withouth replacement
+
+?FactoMineR::simule()
+
+clustering_new_pre_PCA3.1$stimDescription<- as.factor(clustering_new_pre_PCA3.1$stimDescription)
+
+clustering_new_pre_PCA3.1$ssid_stim<- paste0(clustering_new_pre_PCA3.1$ssid,
+                                             paste0(clustering_new_pre_PCA3.1$stimDescription))
+
+clustering_new_pre_PCA3.1$ssid_stim<- as.factor(clustering_new_pre_PCA3.1$ssid_stim)
+
+unique(clustering_new_pre_PCA3.1$ssid)
+
+# this will simulkate 61 times (we can assum that 51 paticipants)
+
+testsim$simul
+
+# clustering_new_pre_PCA3.1$stimDescription
+
+val_cutlabels<- clustering_new_pre_PCA3.1%>%
+  group_by(stimDescription,val_cut_iaps) %>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  select(c("stimDescription", "val_cut_iaps"))
+
+testsim<- FactoMineR::simule(clustering_new_pre_PCA3.1[,c(2,5:9)], 1)
+# then fit pca store the
+testsim_withlabels <- left_join(testsim$simul, val_cutlabels)
+View(testsim_withlabels)
+# then do it again a 100 times
+
+# correlation between variable and dimension
+
+res.mfa_bio_vs_self2_k2[["quanti.var"]][["coord"]]
+
+res.mfa_bio_vs_self2_k2$eig[1:2,]
+
+# https://declaredesign.org/r/fabricatr/reference/resample_data.html
+
+resample_data(clustered_survey, N = 5, ID_labels = "clusters")
+
+unique(clustering_new_pre_PCA3.1$ssid)
+clustering_new_pre_PCA3.1[,c(1,2,5:9)]
+
+testres<- resample_data(clustering_new_pre_PCA3.1 [,c(1,2,5:9)], N = 51, ID_labels = "ssid")
+
+# resample_data(clustering_new_pre_PCA3.1[,c(1,2,5:9)], N = 51, 
+#               ID_labels = c("ssid","stimDescription")) this can throw errior fu to unbalances
+
+# pca
+resampled_temp
+# create emopty dataframe
+resamp_1st<- data.frame(matrix(NA, nrow = 1, ncol = 9))
+colnames(resamp_1st)<- names(resampled_temp)
+
+# create emoty  storage rame for eigenvakues
+eigen_first<- as.data.frame(eugentest)
+eigen_first[,]<- NA
+
+# eigen_first<- as.data.frame(eigen_first)
+
+# create empty storage for correlations
+cor_first<- as.data.frame(cortest)
+cor_first[,]<- NA
+# cor_first<- as.data.frame(cor_first)
+
+# now store group results/partials
+
+partials_first <- res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]]
+partials_first[,]<- NA
+partials_first
+
+i = 1
+
+# for i in 1:100
+# set.seed(ran)
+
+for (i in 1:1500) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+  resampled_temp<-  resample_data(clustering_new_pre_PCA3.1 [,c(1,2,3, 5:9)], N = 51, ID_labels = "ssid")
+  resampled_temp$sim_no = i
+
+# run PCA on the resampled data
+# ?list
+    message(sprintf("$$$$$fitting PCA %i", i))
+mfa.res_res <- FactoMineR::MFA(resampled_temp[,1:8], 
+               group = c(3, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+  message(sprintf("$$$$$storing PCA %i", i))
+eugentest<- as.data.frame(mfa.res_res$eig[1:2,])
+eugentest$sim_no<- i
+
+cortest<- as.data.frame(mfa.res_res$quanti.var$cor)
+cortest$sim_no = i
+
+partials_first<- as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)
+partials_first$sim_no = i
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+resamp_1st<- (bind_rows(resamp_1st, resampled_temp))
+eigen_first<- bind_rows(eigen_first, eugentest)
+cor_first<- bind_rows(cor_first, cortest)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+View(resamp_1st)
+View(eigen_first)
+View(cor_first)
+
+# resamp_1st%>%
+#   subset(ssid!= NA)%>%
+
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
+    subset(!is.na(eigenvalue))%>%
+  ggplot(aes(eigenvalue))+
+  geom_histogram(alpha = .2)+
+  facet_grid(~component)+
+  geom_vline(xintercept = res.mfa_bio_vs_self2_k2$eig[1], linetype= "dashed")+
+    geom_vline(xintercept = res.mfa_bio_vs_self2_k2$eig[2], linetype = "dotted")+
+  theme_classic()
+
+# check component 1
+?quantile
+quantile(eigen_first$eigenvalue,.95, na.rm = TRUE)
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
+    subset(!is.na(eigenvalue) & component == "comp 1" )%>%
+  mutate(perc_5 = quantile(eigenvalue,.05, na.rm = TRUE),
+         perc_95 = quantile(eigenvalue,.95,, na.rm = TRUE))%>%
+  ggplot(aes(eigenvalue))+
+  geom_histogram(alpha = .2)+
+    geom_density()+
+  # facet_grid(~component)+
+  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1],y = 10,size = 2, color = "red")+
+  # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), ymin = 10, ymax = 12 ))
+    geom_vline(aes(xintercept = perc_5), linetype = "dotted")+
+  geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
+  theme_classic()
+
+# dimension 2
+
+quantile(eigen_first$eigenvalue,.95, na.rm = TRUE)
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
+    subset(!is.na(eigenvalue) & component == "comp 2" )%>%
+  mutate(perc_5 = quantile(eigenvalue,.05, na.rm = TRUE),
+         perc_95 = quantile(eigenvalue,.95, na.rm = TRUE))%>%
+  ggplot(aes(eigenvalue))+
+  geom_histogram(alpha = .2)+
+    geom_density()+
+  # facet_grid(~component)+
+  geom_point(x = res.mfa_bio_vs_self2_k2$eig[2],y = 10,size = 2, color = "red")+
+  # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), ymin = 10, ymax = 12 ))
+    geom_vline(aes(xintercept = perc_5), linetype = "dotted")+
+  geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
+  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = 10))
+  theme_classic()
+
+```
+
+```{r}
+
+# first dimension is significant
+
+# same thing as above with variance
+quantile(eigen_first$`percentage of variance`,.95, na.rm = TRUE)
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
+    subset(!is.na(`percentage of variance`) & component == "comp 1" )%>%
+  mutate(perc_5 = quantile(`percentage of variance`,.05, na.rm = TRUE),
+         perc_95 = quantile(`percentage of variance`,.95,, na.rm = TRUE))%>%
+  ggplot(aes(`percentage of variance`))+
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+
+  # facet_grid(~component)+
+      geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = .3,ymin = .2, ymax = .4), color = "gray30")+
+  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1,2],y = .3,size = 3, color = "red")+
+
+    # geom_vline(aes(xintercept = perc_5), linetype = "dotted")+
+  # geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
+  theme_classic()
+
+# compute a direct test
+# we can check the probability of getting a vakue equal to or more extreme than our test
+
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
+    subset(!is.na(`percentage of variance`) & component == "comp 1" )%>%
+  mutate(extreme_eigen_log = eigenvalue>= res.mfa_bio_vs_self2_k2$eig[1])%>%
+  mutate(extreme_eigen_log_prob = (sum(extreme_eigen_log))/n()) %>%
+  summarise_at(c("extreme_eigen_log_prob"), mean, na.rm = TRUE)
+
+# about 50%
+
+# one main difference is that tests checl whether the intervak incldues a ceain value (like zero for eigen vectors or 1 for eigen valkues)
+# so not sure if the test abopve is appropriate withouth correcting for reversals
+
+```
+
+```{r}
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
+    subset(!is.na(eigenvalue) & component == "comp 1" )%>%
+  ggplot(aes(`percentage of variance` ))+
+  geom_histogram(alpha = .2)+
+  # facet_grid(~component)+
+  geom_vline(xintercept = res.mfa_bio_vs_self2_k2$eig[1,2], linetype= "dashed")+
+    # geom_vline(xintercept = res.mfa_bio_vs_self2_k2$eig[2], linetype = "dotted")+
+  theme_classic()
+
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
+    subset(!is.na(eigenvalue) & component == "comp 1" )%>%
+  ggplot(aes(`percentage of variance` ))+
+  geom_histogram(alpha = .2)+
+  # facet_grid(~component)+
+  geom_vline(xintercept = res.mfa_bio_vs_self2_k2$eig[1,2], linetype= "dashed")+
+    # geom_vline(xintercept = res.mfa_bio_vs_self2_k2$eig[2], linetype = "dotted")+
+  theme_classic()
+
+# let's gp to variables
+
+cor_first %>%
+  mutate(variable = as.factor(substr(rownames(cor_first), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  subset(variable == "arousa"|variable == "valenc")%>%
+  # select(c("arousal", "valence"))%>%
+  ggplot(aes(Dim.1))+
+  geom_histogram(alpha = .2)+
+  facet_grid(~variable)+
+  geom_vline(xintercept = .75)+
+    # geom_vline(xintercept = res.mfa_bio_vs_self2_k2$eig[2], linetype = "dotted")+
+  theme_classic()
+
+cor_first %>%
+  mutate(variable = as.factor(substr(rownames(cor_first), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  subset(variable != "arousa"|variable != "valenc")%>%
+  # select(c("arousal", "valence"))%>%
+  ggplot(aes(Dim.2))+
+  geom_histogram(alpha = .2)+
+  facet_grid(~variable)+
+  geom_vline(xintercept = .58)+
+    # geom_vline(xintercept = res.mfa_bio_vs_self2_k2$eig[2], linetype = "dotted")+
+  theme_classic()
+
+ res.mfa_bio_vs_self2_k2$quanti.var$cor
+
+```
+
+unique(as.character(testres$ssid))
+
+mean(testres$pup_basCor)
+mean(clustering_new_pre_PCA3.1$pup_basCor)
+
+testres%>%
+  ggplot(aes(valence, arousal))+
+  geom_point()+
+  ggpubr::stat_cor()
+
+clustering_new_pre_PCA3.1%>%
+  ggplot(aes(valence, arousal))+
+  geom_point()+
+  ggpubr::stat_cor()
+
+# okay this fucntion seems to work
 ```
@@
 View(wine)
-FactoMineR::HMFA(clustering_new_pre_PCA3.1.scale[,2:7],
-                 H = hierar, 
-               # group = c(1, 3, 2), 
-               type = c("n", "s", "s",  "s", "s",  "s"),
-               # "s", "s", "s"
-               name.group = c("pp_stim","auton","subj"),
-               # num.group.sup = c(1),
-                 # ncp = 
-               # ind.sup = c(1,2),
-               graph = TRUE)
-
-# okay try and aggregate  response per stimuli
 
@@
                graph = TRUE)
+
+?FactoMineR::MFA
+View(res.mfa_val_cat_scal)
+
+# force k = 2
+
+res.mfa_val_cat_scal_k2<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_scale_then_agg1,
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+               name.group = c("ss_id_stim","auton","subj"),
+               num.group.sup = c(1),
+               ncp = 2,
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+res.mfa_val_cat_scal_k2$eig
+
+```
+
+```{r}
 

### 2022-02-08 resample_data.R

@@ -1,0 +1,362 @@
+
+
+#' Resample data, including hierarchical data
+#'
+#' This function allows you to resample any data frame. The default mode
+#' performs a single resample of size \code{N} with replacement. Users can
+#' also specify more complex resampling strategies to resample hierarchical
+#' data.
+#'
+#' @param data A data.frame, usually provided by the user.
+#' @param N The number of sample observations to return. If \code{N} is a single
+#' scalar and no labels are provided, \code{N} will specify the number of unit
+#' observations to resample. If \code{N} is named, or if the \code{ID_labels}
+#' argument is specified (in which case, both \code{N} and \code{ID_labels}
+#' should be the same length), then the units resampled will be values of the
+#' levels resampled (this is useful for, e.g., cluster resampling). If \code{N}
+#' is the constant \code{ALL} for any level, all units of this level will be
+#' transparently passed through to the next level of resampling.
+#' @param ID_labels A character vector of the variables that indicate the data
+#' hierarchy, from highest to lowest (i.e., from cities to citizens).
+#' @param unique_labels A boolean, defaulting to FALSE. If TRUE, fabricatr will
+#' created an extra data frame column depicting a unique version of the ID_label
+#' variable resampled on, called <ID_label>_unique.
+#'
+#' @return A data.frame
+#'
+#' @examples
+#'
+#' # Resample a dataset of size N without any hierarchy
+#' baseline_survey <- fabricate(N = 50, Y_pre = rnorm(N))
+#' bootstrapped_data <- resample_data(baseline_survey)
+#'
+#' # Specify a fixed number of observations to return
+#' baseline_survey <- fabricate(N = 50, Y_pre = rnorm(N))
+#' bootstrapped_data <- resample_data(baseline_survey, N = 100)
+#'
+#' # Resample by a single level of a hierarchical dataset (e.g. resampling
+#' # clusters of observations): N specifies a number of clusters to return
+#'
+#' clustered_survey <- fabricate(
+#'   clusters = add_level(N=25),
+#'   cities = add_level(N=round(runif(25, 1, 5)),
+#'                      population=runif(n = N, min=50000, max=1000000))
+#' )
+#'
+#' cluster_resample <- resample_data(clustered_survey, N = 5, ID_labels = "clusters")
+#'
+#' # Alternatively, pass the level to resample as a name:
+#' cluster_resample_2 <- resample_data(clustered_survey, N=c(clusters = 5))
+#'
[…]

### 2022-02-09 Paper_Analyses_subj_obje_arousal.Rmd
started reshuffling for null hypothesis testing
one approach to test significance of esimates is to destroy the relational structure in the data e.g. via reshufling of variables (within the respective hierarquies like subject). this creates a null distribution against which we can test our observed estimates

--- 2022-02-08 Paper_Analyses_subj_obje_arousal.Rmd
@@
 
+```
+
 # MFA
 
+```{r}
 res.mfa <- MFA(clustering_new_pre_PCA_2, 
@@
 
-TInPosition::
-```
+# validation
+# -	Some idea, get p values for factorminer – dimensions, and correklations
+# -	Stability of firt 2 dimensions by resampling
+
+res.mfa_bio_vs_self2_k2<- FactoMineR::MFA(clustering_new_pre_PCA3.1[,1:9], 
+               group = c(4, 3, 2), 
+               type = c("n", "s", "s"),
+              ind.sup = c(1),
+              ncp = 2,
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+# 
+# quanti
+
+# randomly resample withouth replacement
+
+?FactoMineR::simule()
+
+clustering_new_pre_PCA3.1$stimDescription<- as.factor(clustering_new_pre_PCA3.1$stimDescription)
+
+clustering_new_pre_PCA3.1$ssid_stim<- paste0(clustering_new_pre_PCA3.1$ssid,
+                                             paste0(clustering_new_pre_PCA3.1$stimDescription))
+
+clustering_new_pre_PCA3.1$ssid_stim<- as.factor(clustering_new_pre_PCA3.1$ssid_stim)
+
+unique(clustering_new_pre_PCA3.1$ssid)
+
+# this will simulkate 61 times (we can assum that 51 paticipants)
+
+testsim$simul
+
+# clustering_new_pre_PCA3.1$stimDescription
+
+val_cutlabels<- clustering_new_pre_PCA3.1%>%
+  group_by(stimDescription,val_cut_iaps) %>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  select(c("stimDescription", "val_cut_iaps"))
+
+testsim<- FactoMineR::simule(clustering_new_pre_PCA3.1[,c(2,5:9)], 1)
+# then fit pca store the
+testsim_withlabels <- left_join(testsim$simul, val_cutlabels)
+View(testsim_withlabels)
+# then do it again a 100 times
+
+# correlation between variable and dimension
+
+res.mfa_bio_vs_self2_k2[["quanti.var"]][["coord"]]
+
+res.mfa_bio_vs_self2_k2$eig[1:2,]
+
+# https://declaredesign.org/r/fabricatr/reference/resample_data.html
+
+resample_data(clustered_survey, N = 5, ID_labels = "clusters")
+
+unique(clustering_new_pre_PCA3.1$ssid)
+clustering_new_pre_PCA3.1[,c(1,2,5:9)]
+
+testres<- resample_data(clustering_new_pre_PCA3.1 [,c(1,2,5:9)], N = 51, ID_labels = "ssid")
+
+# resample_data(clustering_new_pre_PCA3.1[,c(1,2,5:9)], N = 51, 
+#               ID_labels = c("ssid","stimDescription")) this can throw errior fu to unbalances
+
+# pca
+resampled_temp
+# create emopty dataframe
+resamp_1st<- data.frame(matrix(NA, nrow = 1, ncol = 9))
+colnames(resamp_1st)<- names(resampled_temp)
+
+# create emoty  storage rame for eigenvakues
+eigen_first<- as.data.frame(eugentest)
+eigen_first[,]<- NA
+
+# eigen_first<- as.data.frame(eigen_first)
+
+# create empty storage for correlations
+cor_first<- as.data.frame(cortest)
+cor_first[,]<- NA
+# cor_first<- as.data.frame(cor_first)
+
+# now store group results/partials
+
+res.mfa_bio_vs_self2_k2$group$correlation
+partials_first <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first[,]<- NA
+partials_first
+partials_first$sim_no<- NA
+
+# i = 1
+
+# for i in 1:100
+# set.seed(ran)
+# i = 20
+
+unique(resampled_temp_test$ssid)
+nrow(resampled_temp_test)
+
+ mean(resampled_temp_test$pup_basCor) #0.6710218
+
+ table(resampled_temp_test$ssid)
+
+ View(resampled_temp_test)
+
+ clustering_new_pre_PCA3.1%>%
+   subset(ssid == 1)
+
+resampled_temp_test<- resampled_temp_test %>%
+  group_by(ssid, stimDescription, val_cut_iaps)%>%
+  mutate(dupe = n()>1)
+
+table(resampled_temp_test$dupe)
+
+ install.packages("fabricatr")
+ ??fabricatr::resample_data
+ View(resampled_temp_test)
+ unique(resampled_temp_test$val_cut_iaps_unique)
+ clustering_new_pre_PCA3.1$ssid<- as.character(clustering_new_pre_PCA3.1$ssid)
+
+ table(resampled_temp_test$val_cut_iaps)
+
+ for (i in 1:1000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+  resampled_temp_test<- fabricatr::resample_data(clustering_new_pre_PCA3.1 [,c(1,2,3, 5:9)], 
+                                  N = c(51,55),
+                                  ID_labels = c("ssid", "stimDescription"),
+                                  unique_labels = TRUE)
+  resampled_temp$sim_no = i
+
+# run PCA on the resampled data
+# ?list
+    message(sprintf("$$$$$fitting PCA %i", i))
+mfa.res_res <- FactoMineR::MFA(resampled_temp[,1:8], 
+               group = c(3, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+  message(sprintf("$$$$$storing PCA %i", i))
+eugentest<- as.data.frame(mfa.res_res$eig[1:2,])
+eugentest$sim_no<- i
+
+cortest<- as.data.frame(mfa.res_res$quanti.var$cor)
+cortest$sim_no = i
+
+partials_temp<- as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)
+partials_temp$sim_no = i
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st<- (bind_rows(resamp_1st, resampled_temp))
+eigen_first<- bind_rows(eigen_first, eugentest)
+cor_first<- bind_rows(cor_first, cortest)
+partials_first<- bind_rows(partials_first, partials_temp)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+View(resamp_1st)
+View(eigen_first)
+View(cor_first)
+
+resamp_1st_N30_withrepl<- resamp_1st
+eigen_first_N30_withrepl<- eigen_first
+cor_first_N40_withrepl<- cor_first
+
+partials_first_n30_withrepl<- cor_first
+
+# sample a 100?
+
+for (i in 1:1500) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+  resampled_temp<-  resample_data(clustering_new_pre_PCA3.1 [,c(1,2,3, 5:9)], 
+                                  N = 80, ID_labels = "ssid")
+  resampled_temp$sim_no = i
+
+# run PCA on the resampled data
+# ?list
+    message(sprintf("$$$$$fitting PCA %i", i))
+mfa.res_res <- FactoMineR::MFA(resampled_temp[,1:8], 
+               group = c(3, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+  message(sprintf("$$$$$storing PCA %i", i))
+eugentest<- as.data.frame(mfa.res_res$eig[1:2,])
+eugentest$sim_no<- i
+
+cortest<- as.data.frame(mfa.res_res$quanti.var$cor)
+cortest$sim_no = i
+
+partials_temp<- as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)
+partials_temp$sim_no = i
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st<- (bind_rows(resamp_1st, resampled_temp))
+eigen_first<- bind_rows(eigen_first, eugentest)
+cor_first<- bind_rows(cor_first, cortest)
+partials_first<- bind_rows(partials_first, partials_temp)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+# check if all particiants ocur equally in the old sample
+table(resamp_1st_N30_withrepl$ssid)
+table(resamp_1st$ssid)
+
+resamp_1st_N80_withrepl<- resamp_1st
+eigen_first_N80_withrepl<- eigen_first
+cor_first_N80_withrepl<- cor_first
+
+partials_first_n40_withrepl<- partials_first
+
+resamp_1st_N80_withrepl
+
+table(resamp_1st_N30_withrepl$ssid)
+
+```
+
+##################################################################
+# resample hierarquically, use lower n for subject and valence
+##################################################################
+
+```{r}
+View(resampled_temptest)
+colnames(resamp_1st)
+colnames(resampled_temp_test)
+ # create emopty dataframe
+resamp_1st<- data.frame(matrix(NA, nrow = 1, ncol = 13))
+# cnames_resamp<- names(resampled_temp)
+# colnames(resamp_1st)<- names(resampled_temp)
+colnames(resamp_1st)<- cnames_resamp
+colnames(resamp_1st)
+# create emoty  storage rame for eigenvakues
+eigen_first<- as.data.frame(eugentest)
+eigen_first[,]<- NA
+
+# eigen_first<- as.data.frame(eigen_first)
+
+# create empty storage for correlations
+cor_first<- as.data.frame(cortest)
+cor_first[,]<- NA
+# cor_first<- as.data.frame(cor_first)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first[,]<- NA
+partials_first
+partials_first$sim_no<- NA
+
+# hierarquical clustering
+clustering_new_pre_PCA3.1$ssid<- as.character(clustering_new_pre_PCA3.1$ssid)
+clustering_new_pre_PCA3.1$stimDescription<- as.character(clustering_new_pre_PCA3.1$stimDescription)
+# having clusters as factors causes a subscript oput of bound error
+
+# think we need to store groups
+
+groups_first<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first[,]<- NA
+groups_first
+groups_first$sim_no<- NA
+
+clustering_new_pre_PCA3.1 [,c(1,2,3, 5:9)]
+
+unique(substr(resampled_temp_test$stimDescription_unique,1,6))
+unique(substr(resampled_temp_test$stimDescription_unique,7,30))
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+for (i in 1:1000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+  resampled_temp<- fabricatr::resample_data(clustering_new_pre_PCA3.1 [,c(1,2,3, 5:9)], 
+                                  N = c(51,51),
+                                  ID_labels = c("ssid", "stimDescription"),
+                                  unique_labels = TRUE)
+  resampled_temp$sim_no = i
+  resampled_temp$ssid_new <- as.factor(substr(resampled_temp$stimDescription_unique,1,6))
+  resampled_temp$newstim <- substr(resampled_temp$stimDescription_unique,7,30)
+  # resampled_temp$stimDescription<- as.factor(resampled_temp$stimDescription)
+
+# run PCA on the resampled data
+# ?list
+    message(sprintf("$$$$$fitting PCA %i", i))
+    mfa.res_res <- FactoMineR::MFA(resampled_temp[,c(12,2:8)], 
+               group = c(3, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest<- as.data.frame(mfa.res_res$eig[1:2,])
+eugentest$sim_no<- i
+
+cortest<- as.data.frame(mfa.res_res$quanti.var$cor)
+cortest$sim_no = i
+
+partials_temp<- as.data.frame(mfa.res_res$partial.axes$cor)
+partials_temp$sim_no = i
+
+# groups
+group_temp<- as.data.frame(mfa.res_res$group$cos2)
+group_temp$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st<- (bind_rows(resamp_1st, resampled_temp))
+eigen_first<- bind_rows(eigen_first, eugentest)
+cor_first<- bind_rows(cor_first, cortest)
+partials_first<- bind_rows(partials_first, partials_temp)
+groups_first<- bind_rows(groups_first, group_temp)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+resamp_1st
+View(resamp_1st)
+
+resamp_1st
+
+resamp_1st_1000boot_hier<- resamp_1st
+eigen_first_1000boot_hier<-eigen_first
+cor_first_100boot_hier<- cor_first
+
+partials_first_100boot_hier<-partials_first
+group_first_100boot_hier<-groups_first
+
+resamp_1st%>%
+  subset(sim_no == 11)
+resamp_1st%>%
+  subset(sim_no == 15)
+
+table(resamp_1st$ssid)
+table(resampled_temp_test$ssid)
+```
+Visualisations
+
+```{r}
+
+# check component eigenvalues
+# quantile(eigenvalue,.05, na.rm = TRUE)
+View(eigen_first)
+
+eigen_first$eigenvalue
+
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
+  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
+  ggplot(aes(eigenvalue))+
+  geom_histogram(alpha = .2)+
+    geom_density()+
+  # facet_grid(~component)+
+    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = 1, linetype = "dashed")+
+  ggtitle("distribution of boostraped eigen values for component  1 
+          red dot = observed eigenvalue, boostrapped 95%CI")+
+  annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")
+
+table(eigen_first$eigenvalue>1)
+
+t.testsample1<- eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )
+
+t.test(1.14, mu = mean(t.testsample1$eigenvalue))
+
+# boostrap ratio
+# proposed by abdi for factir scores
+mean(t.testsample1$eigenvalue, na.rm = TRUE)/(sd(t.testsample1$eigenvalue,na.rm = TRUE))
+
+```
+
+```{r}
+# check eigen vectors (correlations
+
+# checpartials_first_n40_withrepl
+
+# check groups
+
+# binom.test(eigen_first$eigenvalue>1)
+
+# calculate the diffeence betwee true eufgenvalye abd boostrap eigenvakue
+# and check if it includes zero?
+
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(eigen_d = (mean(eigenvalue))- res.mfa_bio_vs_self2_k2$eig[1])%>%
+   mutate(eigen_d2 = eigenvalue- res.mfa_bio_vs_self2_k2$eig[1])%>%
+
+  mutate(perc_5 = quantile(eigen_d2,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigen_d2,.975, na.rm = TRUE))%>% #create 95% to descrive interval around the observed estimate
+  ggplot(aes(eigen_d2))+
+  geom_histogram(alpha = .2)+
+    geom_density()+
+  # facet_grid(~component)+
+    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  # geom_point(aes(x = eigen_d,y = 10,size = 2), color = "red")+
+
+  theme_classic()+
+    ggtitle("distribution of observed eigenvalue - boot eigenvalues for component  1")+
+  annotate("text", x = 0, y = 20, label = "95%CI")
+
+```
+  # geom_vline(xintercept = 1, linetype = "dashed")
+
+table(eigen_first$eigenvalue>1)
+
+# boot::boot()
+
+```{r}
+
+t.test_sample<- eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(eigen_d = (mean(eigenvalue))- res.mfa_bio_vs_self2_k2$eig[1])%>%
+   mutate(eigen_d2 = eigenvalue- res.mfa_bio_vs_self2_k2$eig[1])
+t.test(t.test_sample$eigen_d2)
+
+# technially a t test is calculated as the differnce between current mean and pipulation mean devied by population variance, since we often don't have population variance we estimate it from the sample
+
+# will this give us a t?
+(res.mfa_bio_vs_self2_k2$eig[1]- (mean(t.test_sample$eigenvalue, na.rm = TRUE)))/ 
+  (sd(t.test_sample$eigenvalue))
+
+mean(t.test_sample$eigen_d2)/  (sd(t.test_sample$eigenvalue))
+
+resamp_1st%>%
+  subset(sim_no = 1)%>%
+  subset(is.na(ssid) == FALSE)%>%
+  subset(ssid ==  306)
+
+?fabricatr::fabricate()
+
+library(fabricatr)
+
+# ),
+  # pollution = rnorm(N, mean = 5))
+fabricatr::fabricate(
+  stim = add_level(N = 3),
+  id = add_level(N = 30),
+  Var1 = runif(N, 2, 10),
+  Var2 = runif(N, -5, 6),
+  Var2 = runif(N, .2, 2),
+  Var4 = runif(N, -10, 10),
+  Var5 = runif(N, -10, 10)
+))%>%
+  arrange(stim)
+
+fabricate(
+  primary_schools = add_level(N = 3, 
+                              var1 = runif(N, 0, 10)),
+  students = link_levels(N = 30,
+                          by=join(var1, rho = 0.5)))
+
+```
+
+```{r}
+
+# dimension 2
+
+quantile(eigen_first$eigenvalue,.95, na.rm = TRUE)
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
+    subset(!is.na(eigenvalue) & component == "comp 2" )%>%
+  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE),
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
+  ggplot(aes(eigenvalue))+
+  geom_histogram(alpha = .2)+
+    geom_density()+
+   geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_bio_vs_self2_k2$eig[2],y = 10,size = 2, color = "red")+
+  # geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
+  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = 10))+
+  theme_classic()
+
+```
+
+  # first dimension is significant
+
+```{r}
+
+ # same thing as above with variance
+# quantile(eigen_first$`percentage of variance`,.95, na.rm = TRUE)
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
+  subset(!is.na(`percentage of variance`) & component == "comp 1" )%>%
+  mutate(perc_5 = quantile(`percentage of variance`,.025, na.rm = TRUE),
+         perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE))%>%
+  ggplot(aes(`percentage of variance`))+
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = .3), color = "gray30")+
+  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1,2],y = .3,size = 3, color = "red")+
+
+    # geom_vline(aes(xintercept = perc_5), linetype = "dotted")+
+  # geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
+  theme_classic()
+
+```
+
+```{r}
+# let's go to variable correlations with dimenstions
+
+cor_first %>%
+  mutate(variable = as.factor(substr(rownames(cor_first), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  # subset(variable == "arousa"|variable == "valenc")%>%
+  # select(c("arousal", "valence"))%>%
+  ggplot(aes(Dim.1)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+cor_first %>%
+  mutate(variable = as.factor(substr(rownames(cor_first), 1,6)))%>%
+    subset(!is.na(Dim.2)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.2,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.2,.975, na.rm = TRUE))%>%
+  # subset(variable == "arousa"|variable == "valenc")%>%
+  # select(c("arousal", "valence"))%>%
+  ggplot(aes(Dim.2)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+   geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+```
+
+<!-- partials -->
+
+The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).
+```{r}
+View(partials_first)
+
+partials_first%>%
+  mutate(dimension = as.factor(substr(rownames(partials_first), 1,4)),
+         group = as.factor(substr(rownames(partials_first), 5,9)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(dimension, group)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  ggplot(aes(Dim.1)) +
+  geom_histogram(bins = 500)+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =10 ), color = "gray30")+
+  facet_grid(dimension~group)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+  ylim(0,100)
+
+```
+graph of groups
+```{r}
+View(groups_first)
+?gather
+
+# we sgoudl probably store cos2 rather than correlatiopn
+# their cos2 values corresponding to their quality of representation on the factor map
+groups_first%>%
+  mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+
+  gather(dimension, value_dimenion, -group, -sim_no) %>%
+  # -perc_5,-perc_95, 
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
+
+  ggplot(aes(value_dimenion, color = group)) +
+  geom_histogram(bins = 500)+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =10 ), color = "gray30")+
+  facet_grid(dimension~group)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+  ylim(0,100)
+
+```
+
+Do we get the same patterns when loking at paticipants and stimuli searatelly
 
@@
 ??HMFA
-
+```{r}
 H_n<- clustering_new_pre_PCA3.1.scale%>%
@@
 
-H_n.1<- H_n$n
-
-as.list(H_n.1)
-c(H_n.1)
-
-hierar<- list(c(H_n.1))
-
-View(wine)
-FactoMineR::HMFA(clustering_new_pre_PCA3.1.scale[,2:7],
-                 H = hierar, 
-               # group = c(1, 3, 2), 
-               type = c("n", "s", "s",  "s", "s",  "s"),
-               # "s", "s", "s"
-               name.group = c("pp_stim","auton","subj"),
-               # num.group.sup = c(1),
-                 # ncp = 
-               # ind.sup = c(1,2),
-               graph = TRUE)
-
-# okay try and aggregate  response per stimuli
+```
 
@@
 
+########################################
+
+one approach for significance is to create random shuffling that destroys the relational aspect of the data,
+e.g. by resshugling the values betwen variabels per participant.
+e.g. go to participant one, resgule the order of puopil values for  trials, fo th scr fo the same and so on
+
+```{r}
+
+clustering_new_pre_PCA3.1_copy<- clustering_new_pre_PCA3.1
+colnames(clustering_new_pre_PCA3.1)
+
+?sample
+
+# this is slow so need to figure  a better way to to this but for now
+clustering_new_pre_PCA3.1_copy %>%
+  subset(ssid == 304 &val_cut_iaps == "mid" & aro_cut_iaps == "low" )%>%
+  group_by(ssid)%>%
+  transform(pup_basCor = sample(pup_basCor, replace = F),
+            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = F),
+            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = F),
+            arousal = sample(arousal, replace = F),
+            valence = sample(valence, replace = F))
+
+```
+
+```{r}
+
+colnames(resampled_temp_reshuf)
+ # create emopty dataframe
+resamp_1st_reshuf<- data.frame(matrix(NA, nrow = 1, ncol = 9))
+cnames_resamp_reshufl<- names(resampled_temp_reshuf)
+
+colnames(resamp_1st_reshuf)<- cnames_resamp_reshufl
+colnames(resamp_1st_reshuf)
+# create emoty  storage rame for eigenvakues
+eigen_first_reshuf<- as.data.frame(eugentest)
+eigen_first_reshuf[,]<- NA
+
+# eigen_first_reshuf<- as.data.frame(eigen_first_reshuf)
+
+# create empty storage for correlations
+cor_first_reshuf<- as.data.frame(cortest)
+cor_first_reshuf[,]<- NA
+# cor_first_reshuf<- as.data.frame(cor_first_reshuf)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first_reshuf <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first_reshuf[,]<- NA
+partials_first_reshuf
+partials_first_reshuf$sim_no<- NA
+
+# hierarquical clustering
+clustering_new_pre_PCA3.1$ssid<- as.character(clustering_new_pre_PCA3.1$ssid)
+clustering_new_pre_PCA3.1$stimDescription<- as.character(clustering_new_pre_PCA3.1$stimDescription)
+# having clusters as factors causes a subscript oput of bound error
+
+# think we need to store groups
+
+groups_first_reshuf<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first_reshuf[,]<- NA
+groups_first_reshuf
+groups_first_reshuf$sim_no<- NA
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+
+for (i in 1:1000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+
+resampled_temp_reshuf<-    clustering_new_pre_PCA3.1_copy[,c(1,2,3, 5:9)] %>%
+  group_by(ssid)%>%
+  transform(pup_basCor = 
+              sample(pup_basCor, replace = F),
+            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = F),
+            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = F),
+            arousal = sample(arousal, replace = F),
+            valence = sample(valence, replace = F))
+
+  resampled_temp_reshuf$sim_no = i
+  # resampled_temp_reshuf$ssid_new <- as.factor(substr(resampled_temp_reshuf$stimDescription_unique,1,6))
+  # resampled_temp_reshuf$newstim <- substr(resampled_temp_reshuf$stimDescription_unique,7,30)
+  # resampled_temp_reshuf$stimDescription<- as.factor(resampled_temp_reshuf$stimDescription)
+
+# run PCA on the resampled data
+# ?list
+    message(sprintf("$$$$$fitting PCA %i", i))
+    mfa.res_reshuf <- FactoMineR::MFA(resampled_temp_reshuf[,c(1:8)], 
+               group = c(3, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest_reshufl<- as.data.frame(mfa.res_reshuf$eig[1:2,])
+eugentest_reshufl$sim_no<- i
+
+cortest_reshufl<- as.data.frame(mfa.res_reshuf$quanti.var$cor)
+cortest_reshufl$sim_no = i
+
+partials_temp_reshuf<- as.data.frame(mfa.res_reshuf$partial.axes$cor)
+partials_temp_reshuf$sim_no = i
+
+# groups
+group_temp_reshuf<- as.data.frame(mfa.res_reshuf$group$cos2)
+group_temp_reshuf$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st_reshuf<- (bind_rows(resamp_1st_reshuf, resampled_temp_reshuf))
+eigen_first_reshuf<- bind_rows(eigen_first_reshuf, eugentest_reshufl)
+cor_first_reshuf<- bind_rows(cor_first_reshuf, cortest_reshufl)
+partials_first_reshuf<- bind_rows(partials_first_reshuf, partials_temp_reshuf)
+groups_first_reshuf<- bind_rows(groups_first_reshuf, group_temp_reshuf)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+```
+
 # agg by pp
@@
 
- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bysid, 
+res.mfa_agg_bysubj <- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bysid, 
                group = c(1, 3, 2), 
@@
                # "s", "s", "s"
-               name.group = c("stim","auton","subj"),
+               name.group = c("sid","auton","subj"),
                num.group.sup = c(1),
@@
                graph = TRUE)
+
+```
+
+boostrap subjct results
+
+```{r}
+
+factoextra::fviz_eig(res.mfa_agg_bysubj)
+factoextra::fviz_mfa_group(res.mfa_agg_bysubj)
+
+res.mfa_bio_vs_self2_k2$eig
+res.mfa_agg_bysubj$eig
+res.mfa_agg_bysubj$quanti.var$cor
+res.mfa_agg_bysubj$group$cos2
+
+```
+
+```{r}
+colnames(resampled_temp_bysubj)
+resamp_1st_bysubj<- data.frame(matrix(NA, nrow = 1, ncol = 8))
+
+# cnames_resamp_subj<- names(resampled_temp_bysubj)
+colnames(resamp_1st_bysubj)<- cnames_resamp_subj
+colnames(resamp_1st_bysubj)
+# create emoty  storage rame for eigenvakues
+eigen_first_bysubj<- as.data.frame(eugentest)
+eigen_first_bysubj[,]<- NA
+
+# eigen_first<- as.data.frame(eigen_first)
+
+# create empty storage for correlations
+cor_first_bysubj<- as.data.frame(cortest)
+cor_first_bysubj[,]<- NA
+# cor_first<- as.data.frame(cor_first)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first_bysubj <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first_bysubj[,]<- NA
+partials_first_bysubj
+partials_first_bysubj$sim_no<- NA
+
+# hierarquical clustering
+clustering_new_pre_PCA3.1.scale_agg_bysid$ssid<- as.character(clustering_new_pre_PCA3.1.scale_agg_bysid$ssid)
+# clustering_new_pre_PCA3.1.scale_agg_bysid$stimDescription<- as.character(clustering_new_pre_PCA3.1.scale_agg_bysid$stimDescription)
+
+# think we need to store groups
+
+groups_first_bysubj<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first_bysubj[,]<- NA
+groups_first_bysubj
+groups_first_bysubj$sim_no<- NA
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+colnames(clustering_new_pre_PCA3.1.scale_agg_bysid)
+
+for (i in 1:1000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+
+  resampled_temp_bysubj<- fabricatr::resample_data(clustering_new_pre_PCA3.1.scale_agg_bysid, 
+                                  N = c(51),
+                                  ID_labels = c("ssid"),
+                                  unique_labels = TRUE)
+  # View(resampled_temp_bysubj)
+  resampled_temp_bysubj$sim_no = i
+  # resampled_temp_bysubj$ssid_new <- as.factor(substr(resampled_temp_bysubj$stimDescription_unique,1,6))
+  # resampled_temp_bysubj$newstim <- substr(resampled_temp_bysubj$stimDescription_unique,7,30)
+  # resampled_temp_bysubj$stimDescription<- as.factor(resampled_temp_bysubj$stimDescription)
+
+# run PCA on the resampled data
+  # colnames(resampled_temp_bysubj)
+    message(sprintf("$$$$$fitting PCA %i", i))
+    mfa.res_bysubj <- FactoMineR::MFA(resampled_temp_bysubj[,1:6], 
+               group = c(1, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("sid","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest_bysubj<- as.data.frame(mfa.res_bysubj$eig[1:2,])
+eugentest_bysubj$sim_no<- i
+
+cortest_bysubj<- as.data.frame(mfa.res_bysubj$quanti.var$cor)
+cortest_bysubj$sim_no = i
+
+partials_temp_bysubj<- as.data.frame(mfa.res_bysubj$partial.axes$cor)
+partials_temp_bysubj$sim_no = i
+
+# groups
+group_temp_bysubj<- as.data.frame(mfa.res_bysubj$group$cos2)
+group_temp_bysubj$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st_bysubj<- (bind_rows(resamp_1st_bysubj, resampled_temp_bysubj))
+eigen_first_bysubj<- bind_rows(eigen_first_bysubj, eugentest_bysubj)
+cor_first_bysubj<- bind_rows(cor_first_bysubj, cortest_bysubj)
+partials_first_bysubj<- bind_rows(partials_first_bysubj, partials_temp_bysubj)
+groups_first_bysubj<- bind_rows(groups_first_bysubj, group_temp_bysubj)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+resamp_1st_bysubj
+View(resamp_1st_bysubj)
+
+resamp_1st_bysubj
+
+resamp_1st_bysubj%>%
+  subset(sim_no == 11)
+
+```
+
+visualise boostrap CIs for agg by subjec
+
+```{r}
+eigen_first_bysubj%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bysubj), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
+  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
+  ggplot(aes(eigenvalue))+
+  geom_histogram(alpha = .2)+
+    geom_density()+
+  # facet_grid(~component)+
+    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_agg_bysubj$eig[1],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = 1, linetype = "dashed")
+  # ggtitle("distribution of boostraped eigen values for component  1 
+          # red dot = observed eigenvalue, boostrapped 95%CI")+
+  # annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")
+
+eigen_first_bysubj%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bysubj), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
+  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
+  ggplot(aes(eigenvalue))+
+  geom_histogram(alpha = .2)+
+    geom_density()+
+  # facet_grid(~component)+
+    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_agg_bysubj$eig[2],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = 1, linetype = "dashed")
+
+```
+
+variables and dimension corelations
+```{r}
+cor_first_bysubj %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  # subset(variable == "arousa"|variable == "valenc")%>%
+  # select(c("arousal", "valence"))%>%
+  ggplot(aes(Dim.1)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
 
@@
 
+?FactoMineR::MFA
+View(res.mfa_val_cat_scal)
+
+# force k = 2
+
+res.mfa_val_cat_scal_k2<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_scale_then_agg1,
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+               name.group = c("ss_id_stim","auton","subj"),
+               num.group.sup = c(1),
+               ncp = 2,
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+res.mfa_val_cat_scal_k2$eig
+
+```
+
+```{r}
+
 fviz_mfa_ind(res.mfa_val_cat_scal, 
@@
 
-```
-
-# now keep participant just cast pupil etc
-clustering_new_pre_PCA3.1.scale
-
-# dcast
-
-library(data.table)
-
-colnames(clustering_new_pre_PCA3.1.scale)
-clustering_new_pre_PCA3.1.scale$pup_basCor<- clustering_new_pre_PCA3.1.scale$pup_basCor[,1]
-
-clustering_new_pre_PCA3.1.scale$Bio_Mean_HR_dif<- clustering_new_pre_PCA3.1.scale$Bio_Mean_HR_dif[,1]
-
-clustering_new_pre_PCA3.1.scale$log_BIO_CDA.PhasicMax<- clustering_new_pre_PCA3.1.scale$log_BIO_CDA.PhasicMax[,1]
-
-clustering_new_pre_PCA3.1.scale$arousal<- clustering_new_pre_PCA3.1.scale$arousal[,1]
-
-clustering_new_pre_PCA3.1.scale$valence<- clustering_new_pre_PCA3.1.scale$valence[,1]
-
-clustering_new_pre_PCA3.1.scale_dcast<- data.table::dcast(setDT(clustering_new_pre_PCA3.1.scale), 
-                    ssid  ~ stimDescription, 
-                    value.var = c('pup_basCor',
-                'Bio_Mean_HR_dif', 'log_BIO_CDA.PhasicMax', 'arousal','valence'), fun.aggregate = mean)
-
-colnames(clustering_new_pre_PCA3.1.scale_dcast)
-
-res.mfadcast <- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_dcast[,
-                                                                      2:ncol(clustering_new_pre_PCA3.1.scale_dcast)], 
-               group = c(52, 52, 52, 52, 52), 
-               type = c("s", "s", "s", "s", "s"),
-               # "s", "s", "s"
-               name.group = c("pup","hr", "scr", "ar", "vl"),
-               # num.group.sup = c(1),
-               # ind.sup = c(1,2),
-               graph = TRUE)
-
-53-2 #pupil
-
-```
-
-# with self arousal
-var.PCA.scr_hr_pup_ar <-InPosition::epPCA.inference.battery(all.data3_forPCA_withar[,4:227], 
-                                       scale = TRUE, 
-                                       center = TRUE, 
-                                       # DESIGN = var.design_asd, 
-                                       # make_design_nominal = TRUE, 
-                                       graphs = TRUE, k = 0, 
-                                       test.iters = 1000, 
-                                       constrained = FALSE, 
-                                       critical.value = 2)
-
-View(all.data3_forPCA_withar)
-
-View(clustering_new_pre_PCA)
-```
-
-Multiple factor analysys
-
-- consider aggregating  (average per stim)
-- PCA on arousal arousal and valence
-
-```{r}
-
-library(factoextra)
-library(FactoMineR)
-
-clustering_new_pre_PCA
-colnames(clustering_new_pre_PCA)
-
-clustering_new_pre_PCA_2<- clustering_new_pre_PCA[, c(1,5:10,12)]
-colnames(clustering_new_pre_PCA_2)
-
-MFA(base, group, type = rep("s",length(group)), ind.sup = NULL, 
-    name.group = NULL, num.group.sup = NULL, graph = TRUE)
-
-res.mfa <- MFA(wine, 
-               group = c(2, 5, 3, 10, 9, 2), 
-               type = c("n", "s", "s", "s", "s", "s"),
-               name.group = c("origin","odor","visual",
-                              "odor.after.shaking", "taste","overall"),
-               num.group.sup = c(1, 6),
-               graph = FALSE)
-
-clustering_new_pre_PCA_2
-
-View(clustering_new_pre_PCA_2)
-
-clustering_new_pre_PCA_2$ssid<- as.factor(clustering_new_pre_PCA_2$ssid)
-?MFA
-
-View(clustering_new_pre_PCA_2)
-clustering_new_pre_PCA_2$stimDescription
-colnames(clustering_new_pre_PCA_2)
-
-res.mfa <- MFA(wine, 
-               group = c(2, 5, 3, 10, 9, 2), 
-               type = c("n", "s", "s", "s", "s", "s"),
-               name.group = c("origin","odor","visual",
-                              "odor.after.shaking", "taste","overall"),
-               num.group.sup = c(1, 6),
-               graph = FALSE)
-
-res.mfa <- MFA(clustering_new_pre_PCA_2, 
-               group = c(2, 1, 1, 1), 
-               type = c("n", "s", "s", "s"),
-               name.group = c("pp_stim","pupil","HR","SCR"),
-               # num.group.sup = c(1,2),
-               graph = TRUE)
-
-print(res.mfa)
-
-clustering_new_pre_PCA_2print(res.mfa)
-
-```
-
-```{r}
-library("factoextra")
-eig.val <- get_eigenvalue(res.mfa)
-head(eig.val)
-
-install.packages("MExPosition")
-# ExPosition::FA
-
-TExPosition::
-# InPosition::
-# TExPosition::
-
-```
-
-the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
-```{r}
-library(FactoMineR)
-library(factoextra)
-??fviz_screeplot
-fviz_screeplot(res.mfa)
-
-```
-
-The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables.
-This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the
-
-```{r}
-
-group <- get_mfa_var(res.mfa, "group")
-group
-
-```
-
-The different components can be accessed as follow:
-```{r}
-# Coordinates of groups
-head(group$coord)
-# Cos2: quality of representation on the factore map
-head(group$cos2)
-# Contributions to the  dimensions
-head(group$contrib)
-
-```
-
-To plot the groups of variables, type this:
-
-```{r}
-fviz_mfa_var(res.mfa, "group")
-
-```
-
-red color = active groups of variables
-green color = supplementary groups of variables
-The plot above illustrates the correlation between groups and dimensions.
-The coordinates of the four active groups on the first dimension are almost identical.
-This means that they contribute similarly to the first dimension.
-Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.
-
-To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
-```{r}
-# Contribution to the first dimension
-fviz_contrib(res.mfa, "group", axes = 1)
-# Contribution to the second dimension
-fviz_contrib(res.mfa, "group", axes = 2)
-
-```
-Quantitative variables
-The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables.
-This function returns a list containing the coordinates, the cos2 and the contribution of variables:
-```{r}
-quanti.var <- get_mfa_var(res.mfa, "quanti.var")
-quanti.var
-
-```
-
-```{r}
-# Coordinates
-head(quanti.var$coord)
-# Cos2: quality on the factore map
-head(quanti.var$cos2)
-# Contributions to the dimensions
-head(quanti.var$contrib)
-
-```
-Correlation between quantitative variables and dimensions.
-The R code below plots quantitative variables colored by groups.
-The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
-Supplementary quantitative variables are in dashed arrow and violet color.
-We use repel = TRUE, to avoid text overlapping.
-
-```{r}
-fviz_mfa_var(res.mfa, "quanti.var", palette = "jco", 
-             col.var.sup = "violet", repel = TRUE)
-
-```
-
-To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”).
-We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
-```{r}
-fviz_mfa_var(res.mfa, "quanti.var", palette = "jco", 
-             col.var.sup = "violet", repel = TRUE,
-             geom = c("point", "text"), legend = "bottom")
-
-```
-
-```{r}
-fviz_contrib(res.mfa, choice = "quanti.var", axes = 1, top = 20,
-             palette = "jco")
-
-```
-Graph of individuals
-
-```{r}
-# To get the results for individuals, type this:
-
-ind <- get_mfa_ind(res.mfa)
-ind
-
-```
-To plot individuals, use the function fviz_mfa_ind() [in factoextra].
-By default, individuals are colored in blue.
-However, like variables, it’s also possible to color individuals by their cos2 values:
-
-```{r}
-fviz_mfa_ind(res.mfa, col.ind = "cos2", 
-             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-             repel = FALSE)
-
-fviz_mfa_ind(res.mfa, 
-             habillage = "Label", # color by groups 
-             palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-```
-
-```{r}
-
-clustering_new_pre_PCA_2
-
-fviz_mfa_ind(res.mfa, 
-             habillage = "stimDescription", # color by groups 
-             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-fviz_mfa_ind(res.mfa, 
-             habillage = "ssid", # color by groups 
-             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-testget<-get_mfa(
-  res.mfa,
-  element = c("ind"))
-
-clustering_new_pre_PCA3$getindaxis<- testget[["coord"]][,1]
-clustering_new_pre_PCA3$getindaxis2<- testget[["coord"]][,2]
-
-clustering_new_pre_PCA3%>%
-  group_by(ssid)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(arousal, getindaxis))+
-  geom_point()+
-  ggpubr::stat_cor()+
-  xlim(-,3.3)
-
-clustering_new_pre_PCA3%>%
-  group_by(ssid, arousal_3cat)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
-  ggplot(aes(arousal, getindaxis2))+
-  geom_point()+
-  ggpubr::stat_cor()+
-  facet_grid(~arousal_3cat)
-  # xlim(-,3.3)
-
-```
-
-Aggregate one average per stim
-
-```{r}
-
-library(factoextra)
-library(FactoMineR)
-
-colnames(clustering_agg_JASPtest)
-
-clustering_agg_JASP_PCA_2<- clustering_agg_JASPtest [, c(1,27, 2:4)]
-colnames(clustering_agg_JASP_PCA_2)
-
-clustering_agg_JASP_PCA_2$stimIAPS2<- as.factor(clustering_agg_JASP_PCA_2$stimIAPS2)
-
-clustering_agg_JASP_PCA_2$stimDescription<- as.factor(clustering_agg_JASP_PCA_2$stimDescription)
-
-res.mfa_agg <- MFA(wine, 
-               group = c(2, 5, 3, 10, 9, 2), 
-               type = c("n", "s", "s", "s", "s", "s"),
-               name.group = c("origin","odor","visual",
-                              "odor.after.shaking", "taste","overall"),
-               num.group.sup = c(1, 6),
-               graph = FALSE)
-
-colnames(clustering_agg_JASP_PCA_2)
-res.mfa_agg <- MFA(clustering_agg_JASP_PCA_2, 
-               group = c(2, 1, 1, 1), 
-               type = c("n", "s", "s", "s"),
-               name.group = c("stim_desc","HR","pupil","SCR"),
-               num.group.sup = c(1,2),
-               graph = TRUE)
-
-print(res.mfa_agg)
-
-```
-
-```{r}
-library("factoextra")
-eig.val_agg <- get_eigenvalue(res.mfa_agg)
-head(eig.val_agg)
-
-```
-
-the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
-```{r}
-fviz_screeplot(res.mfa_agg)
-
-```
-
-The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables.
-This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the
-
-```{r}
-
-group_agg <- get_mfa_var(res.mfa_agg, "group")
-group_agg
-
-```
-
-The different components can be accessed as follow:
-```{r}
-# Coordinates of groups
-head(group_agg$coord)
-# Cos2: quality of representation on the factore map
-head(group_agg$cos2)
-# Contributions to the  dimensions
-head(group_agg$contrib)
-
-```
-
-To plot the groups of variables, type this:
-
-```{r}
-fviz_mfa_var(res.mfa_agg, "group")
-
-```
-
-red color = active groups of variables
-green color = supplementary groups of variables
-The plot above illustrates the correlation between groups and dimensions.
-The coordinates of the four active groups on the first dimension are almost identical.
-This means that they contribute similarly to the first dimension.
-Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.
-
-To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
-```{r}
-# Contribution to the first dimension
-fviz_contrib(res.mfa_agg, "group", axes = 1)
-# Contribution to the second dimension
-fviz_contrib(res.mfa_agg, "group", axes = 2)
-
-```
-Quantitative variables
-The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables.
-This function returns a list containing the coordinates, the cos2 and the contribution of variables:
-```{r}
-quanti.var_agg <- get_mfa_var(res.mfa_agg, "quanti.var")
-quanti.var_agg
-
-```
-
-```{r}
-# Coordinates
-head(quanti.var_agg$coord)
-# Cos2: quality on the factore map
-head(quanti.var_agg$cos2)
-# Contributions to the dimensions
-head(quanti.var_agg$contrib)
-
-```
-Correlation between quantitative variables and dimensions.
-The R code below plots quantitative variables colored by groups.
-The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
-Supplementary quantitative variables are in dashed arrow and violet color.
-We use repel = TRUE, to avoid text overlapping.
-
-```{r}
-fviz_mfa_var(res.mfa_agg, "quanti.var", palette = "jco", 
-             col.var.sup = "violet", repel = TRUE)
-
-```
-
-To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”).
-We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
-```{r}
-fviz_mfa_var(res.mfa_agg, "quanti.var", palette = "jco", 
-             col.var.sup = "violet", repel = TRUE,
-             geom = c("point", "text"), legend = "bottom")
-
-```
-
-```{r}
-fviz_contrib(res.mfa_agg, choice = "quanti.var", axes = 1, top = 20,
-             palette = "jco")
-fviz_contrib(res.mfa_agg, choice = "quanti.var", axes = 2, top = 20,
-             palette = "jco")
-
-```
-Graph of individuals
-
-```{r}
-# To get the results for individuals, type this:
-
-ind_agg <- get_mfa_ind(res.mfa_agg)
-ind_agg
-
-```
-To plot individuals, use the function fviz_mfa_ind() [in factoextra].
-By default, individuals are colored in blue.
-However, like variables, it’s also possible to color individuals by their cos2 values:
-
-```{r}
-fviz_mfa_ind(res.mfa_agg, col.ind = "cos2", 
-             # gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-             repel = TRUE)
-clust2_dataset$stimDescription
-pp_stim
-fviz_mfa_ind(res.mfa_agg, 
-             habillage = "stimDescription", # color by groups 
-             palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-```
-
-```{r}
-
-clustering_new_pre_PCA_2
-
-fviz_mfa_ind(res.mfa_agg, 
-             habillage = "stimIAPS2", # color by groups 
-             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-```
-
-Graph of partial individuals
-The results for individuals obtained from the analysis performed with a single group are named partial individuals.
-In other words, an individual considered from the point of view of a single group is called partial individual.
-
-In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual.
-That is, the individual viewed by all groups of variables.
-
-For a given individual, there are as many partial points as groups of variables.
-
-The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:
-
-```{r}
-fviz_mfa_ind(res.mfa_agg, partial = "all") 
-# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:
-
-fviz_mfa_ind(res.mfa, partial = c("1DAM", "1VAU", "2ING"))
-
-```
-
-Graph of partial axes
-The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).
-
-```{r}
-fviz_mfa_axes(res.mfa_agg)
-
-```
-
-```{r}
-data(wine)
-View(wine)
-
-View(clustering_new_pre_PCA_2)
-
-```
-
-colnames
-
-```{r}
-db_forPCA
-colnames(db_forPCA)
-library(tidyverse)
-data3_forPCA_withar
-all.data3_forPCA_withar$TAS_split<- if_else(all.data3_forPCA_withar$TAS > 
-                                          median(all.data3_forPCA_withar$TAS, na.rm = TRUE), "High", "Low")
-colnames(all.data3_forPCA_withar)
-db_forPCA_MFA<- all.data3_forPCA_withar[, c(1,228, 4:171)]
-
-colnames(db_forPCA_MFA)
-
-db_forPCA_MFA
-
-db_forPCA_MFA$ssid<- as.factor(db_forPCA_MFA$ssid)
-
-colnames(db_forPCA_MFA)
-
-db_forPCA_MFA$arousal_9561SickKitty<- NULL
-res.mfa_dcast <- MFA(db_forPCA_MFA, 
-               group = c(2, 56, 56, 56), 
-               type = c("n", "s", "s", "s"),
-               name.group = c("pp_gr","pupil","HR","SCR"),
-               num.group.sup = c(1,2),
-               graph = TRUE)
-
-print(res.mfa_dcast)
-
-```
-
-```{r}
-library("factoextra")
-# res.mfa_dcast <- get_eigenvalue(res.mfa_dcast)
-# head(res.mfa_dcast)
-
-```
-
-the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
-```{r}
-fviz_screeplot(res.mfa_dcast)
-
-```
-
-The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables.
-This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the
-
-```{r}
-
-group_dcast <- get_mfa_var(res.mfa_dcast, "group")
-group_dcast
-
-```
-
-The different components can be accessed as follow:
-```{r}
-# Coordinates of groups
-head(group_dcast$coord)
-# Cos2: quality of representation on the factore map
-head(group_dcast$cos2)
-# Contributions to the  dimensions
-head(group_dcast$contrib)
-
-```
-
-To plot the groups of variables, type this:
-
-```{r}
-fviz_mfa_var(res.mfa_dcast, "group")
-
-```
-
-red color = active groups of variables
-green color = supplementary groups of variables
-The plot above illustrates the correlation between groups and dimensions.
-The coordinates of the four active groups on the first dimension are almost identical.
-This means that they contribute similarly to the first dimension.
-Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.
-
-To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
-```{r}
-# Contribution to the first dimension
-fviz_contrib(res.mfa_dcast, "group", axes = 1)
-# Contribution to the second dimension
-fviz_contrib(res.mfa_dcast, "group", axes = 2)
-
-```
-Quantitative variables
-The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables.
-This function returns a list containing the coordinates, the cos2 and the contribution of variables:
-```{r}
-quanti.var_dcast <- get_mfa_var(res.mfa_dcast, "quanti.var")
-quanti.var_dcast
-
-```
-
-```{r}
-# Coordinates
-head(quanti.var_dcast$coord)
-# Cos2: quality on the factore map
-head(quanti.var_dcast$cos2)
-# Contributions to the dimensions
-head(quanti.var_dcast$contrib)
-
-```
-Correlation between quantitative variables and dimensions.
-The R code below plots quantitative variables colored by groups.
-The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
-Supplementary quantitative variables are in dashed arrow and violet color.
-We use repel = TRUE, to avoid text overlapping.
-
-```{r}
-fviz_mfa_var(res.mfa_dcast, "quanti.var", palette = "jco", 
-             col.var.sup = "violet", repel = TRUE)
-
-```
-
-To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”).
-We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
-```{r}
-fviz_mfa_var(res.mfa_dcast, "quanti.var", palette = "jco", 
-             col.var.sup = "violet", repel = TRUE,
-             geom = c("point", "text"), legend = "bottom")
-
-```
-
-```{r}
-fviz_contrib(res.mfa_dcast, choice = "quanti.var", axes = 1, top = 20,
-             palette = "jco")
-fviz_contrib(res.mfa_agg, choice = "quanti.var", axes = 2, top = 20,
-             palette = "jco")
-
-```
-Graph of individuals
-
-```{r}
-# To get the results for individuals, type this:
-
-ind_dcast <- get_mfa_ind(res.mfa_dcast)
-ind_dcast
-
-```
-To plot individuals, use the function fviz_mfa_ind() [in factoextra].
-By default, individuals are colored in blue.
-However, like variables, it’s also possible to color individuals by their cos2 values:
-
-```{r}
-fviz_mfa_ind(res.mfa_dcast, col.ind = "cos2", 
-             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-             repel = TRUE)
-clust2_dataset$stimDescription
-pp_stim
-fviz_mfa_ind(res.mfa_dcast, 
-             habillage = "TAS_split", # color by groups 
-             palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-```
-
-```{r}
-
-clustering_new_pre_PCA_2
-
-fviz_mfa_ind(res.mfa_dcast, 
-             habillage = "stimIAPS2", # color by groups 
-             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-```
-
-Graph of partial individuals
-The results for individuals obtained from the analysis performed with a single group are named partial individuals.
-In other words, an individual considered from the point of view of a single group is called partial individual.
-
-In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual.
-That is, the individual viewed by all groups of variables.
-
-For a given individual, there are as many partial points as groups of variables.
-
-The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:
-
-```{r}
-fviz_mfa_ind(res.mfa_dcast, partial = "all") 
-# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:
-
-```
-
-Graph of partial axes
-The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).
-
-```{r}
-fviz_mfa_axes(res.mfa_dcast)
-
-```
-
-<!-- neg, neutra positive -->
-
-```{r}
-data(wine)
-View(wine)
-
-View(clustering_new_pre_PCA_2)
-?cut
-clustering_new_pre_PCA_2$valence_split<- cut(clustering_new_pre_PCA_2$valence, 3,
-                                             labels = c("neg", "mid", "positive"))
-
-clustering_new_pre_PCA_2_agg_by_val<- clustering_new_pre_PCA_2%>%
-  group_by(ssid,valence_split)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)
-
-View(clustering_new_pre_PCA_2_agg_by_val)
-
-colnames(clustering_new_pre_PCA_2_agg_by_val)
-clustering_new_pre_PCA_2_agg_by_val_sel<- clustering_new_pre_PCA_2_agg_by_val[, c(1:7)]
-
-# dcast
-library(data.table)
-clustering_new_pre_PCA_2_agg_by_val_sel_dcast<- data.table::dcast(setDT(clustering_new_pre_PCA_2_agg_by_val_sel), 
-                    ssid ~ valence_split, value.var = c('pup_basCor',
-                'Bio_Mean_HR_dif', 'log_BIO_CDA.PhasicMax', "arousal", "valence"))
-
-clustering_new_pre_PCA_2_agg_by_val_sel_dcast
-
-clustering_new_pre_PCA_2_agg_by_val_sel_dcast$pup_basCor_NA<- NULL
-
-clustering_new_pre_PCA_2_agg_by_val_sel_dcast$Bio_Mean_HR_dif_NA<- NULL
-clustering_new_pre_PCA_2_agg_by_val_sel_dcast$log_BIO_CDA.PhasicMax_NA<- NULL
-
-clustering_new_pre_PCA_2_agg_by_val_sel_dcast$valence_NA<- NULL
-clustering_new_pre_PCA_2_agg_by_val_sel_dcast$arousal_NA<- NULL
-clustering_new_pre_PCA_2_agg_by_val_sel_dcast
-View(clustering_new_pre_PCA_2_agg_by_val_sel_dcast)
-
-namesrepl<- colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast)
-
-namesrepl<- c("ssid", "p_neg", "p_mid" ,"p_pos", "HR_neg" , "HR_mid",
-                  "HR_pos","SCR_neg", "SCR_mid", "SCR_pos", "ar_neg","ar_mid", "ar_pos",
-              "vl_neg","vl_mid", "vl_pos")
-
-clustering_new_pre_PCA_2_agg_by_val_sel_dcast2<- clustering_new_pre_PCA_2_agg_by_val_sel_dcast
-names(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)<- namesrepl
-
-```
-
-MFA agg by val
-
-```{r}
-colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
-
-View(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
-res.mfa_agg_byval <- MFA(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2, 
-               group = c(1, 3, 3, 3), 
-               type = c("n", "s", "s", "s"),
-               name.group = c("ssid","pupil","HR","SCR"),
-               num.group.sup = c(1),
-               graph = TRUE)
-
-print(res.mfa_agg_byval)
-
-clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$pcscoremaybe <- res.mfa_agg_byval[["global.pca"]][["ind"]][["cos2"]][,1]
-
-clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar<- (clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar_neg+clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar_mid+
-  clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar_pos)/3
-
-# cor.test(res.mfa_agg_byval[["global.pca"]][["ind"]][["cos2"]][,3],
-#          clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar)
-
-```
-
-```{r}
-library("factoextra")
-eif_vyval <- get_eigenvalue(res.mfa_agg_byval)
-head(eif_vyval)
-
-```
-
-the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
-```{r}
-fviz_screeplot(res.mfa_agg_byval)
-
-```
-
-The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables.
-This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the
-
-```{r}
-
-group_vybal <- get_mfa_var(res.mfa_agg_byval, "group")
-group_vybal
-
-```
-
-The different components can be accessed as follow:
-```{r}
-# Coordinates of groups
-head(group_vybal$coord)
-# Cos2: quality of representation on the factore map
-head(group_vybal$cos2)
-# Contributions to the  dimensions
-head(group_vybal$contrib)
-
-```
-
-To plot the groups of variables, type this:
-
-```{r}
-fviz_mfa_var(res.mfa_agg_byval, "group")
-
-```
-
-red color = active groups of variables
-green color = supplementary groups of variables
-The plot above illustrates the correlation between groups and dimensions.
-The coordinates of the four active groups on the first dimension are almost identical.
-This means that they contribute similarly to the first dimension.
-Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.
-
-To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
-```{r}
-# Contribution to the first dimension
-fviz_contrib(res.mfa_agg_byval, "group", axes = 1)
-# Contribution to the second dimension
-fviz_contrib(res.mfa_agg_byval, "group", axes = 2)
-
-```
-Quantitative variables
-The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables.
-This function returns a list containing the coordinates, the cos2 and the contribution of variables:
-```{r}
-quanti.var_agg_by_val <- get_mfa_var(res.mfa_agg_byval, "quanti.var")
-quanti.var_agg_by_val
-
-```
-
-```{r}
-# Coordinates
-head(quanti.var_agg_by_val$coord)
-# Cos2: quality on the factore map
-head(quanti.var_agg_by_val$cos2)
-# Contributions to the dimensions
-head(quanti.var_agg_by_val$contrib)
-
-```
-Correlation between quantitative variables and dimensions.
-The R code below plots quantitative variables colored by groups.
-The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
-Supplementary quantitative variables are in dashed arrow and violet color.
-We use repel = TRUE, to avoid text overlapping.
-
-```{r}
-fviz_mfa_var(res.mfa_agg_byval, "quanti.var", palette = "jco", 
-             col.var.sup = "violet", repel = TRUE)
-
-```
-
-Correlation between quantitative variables and dimensions.
-The R code below plots quantitative variables colored by groups.
-The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
-Supplementary quantitative variables are in dashed arrow and violet color.
-We use repel = TRUE, to avoid text overlapping.
-
-```{r}
-fviz_mfa_var(res.mfa_dcast, "quanti.var", palette = "jco", 
-             col.var.sup = "violet", repel = TRUE)
-
-```
-
-To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”).
-We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
-```{r}
-fviz_mfa_var(res.mfa_agg_byval, "quanti.var", palette = "jco", 
-             col.var.sup = "violet", repel = TRUE,
-             geom = c("point", "text"), legend = "bottom")
-
-```
-
-```{r}
-fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 1, top = 20,
-             palette = "jco")
-fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 2, top = 20,
-             palette = "jco")
-
-```
-Graph of individuals
-
-```{r}
-# To get the results for individuals, type this:
-
-ind_agg_byval <- get_mfa_ind(res.mfa_agg_byval)
-ind_agg_byval
-
-```
-To plot individuals, use the function fviz_mfa_ind() [in factoextra].
-By default, individuals are colored in blue.
-However, like variables, it’s also possible to color individuals by their cos2 values:
-
-```{r}
-fviz_mfa_ind(res.mfa_agg_byval, col.ind = "cos2", 
-             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-             repel = TRUE)
-
-fviz_mfa_ind(res.mfa_agg_byval, 
-             habillage = "ssid", # color by groups
-             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-```
-
-```{r}
-
-clustering_new_pre_PCA_2
-
-fviz_mfa_ind(res.mfa_agg_byval, 
-             # habillage = "stimIAPS2", # color by groups 
-             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-```
-
-Graph of partial individuals
-The results for individuals obtained from the analysis performed with a single group are named partial individuals.
-In other words, an individual considered from the point of view of a single group is called partial individual.
-
-In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual.
-That is, the individual viewed by all groups of variables.
-
-For a given individual, there are as many partial points as groups of variables.
-
-The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:
-
-```{r}
-fviz_mfa_ind(res.mfa_agg_byval, partial = "all") 
-# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:
-
-```
-
-Graph of partial axes
-The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).
-
-```{r}
-fviz_mfa_axes(res.mfa_agg_byval)
-
-```
-
-with valence
-clustering_new_pre_PCA_2_agg_by_val_sel_dcast
-
-```{r}
-
-colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
-res.mfa_agg_byval2 <- MFA(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2, 
-               group = c(1, 3, 3, 3,3,3), 
-               type = c("n", "s", "s", "s","s", "s"),
-               name.group = c("ssid","pupil","HR","SCR", "AR", "VL"),
-               num.group.sup = c(1),
-               graph = TRUE)
-
-print(res.mfa_agg_byval2)
-
-```
-
-```{r}
-library("factoextra")
-eif_vyval2 <- get_eigenvalue(res.mfa_agg_byval2)
-head(eif_vyval2)
-
-```
-
-the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
-```{r}
-fviz_screeplot(res.mfa_agg_byval2)
-
-```
-
-The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables.
-This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the
-
-```{r}
-
-group_vybal2 <- get_mfa_var(res.mfa_agg_byval2, "group")
-group_vybal2
-
-```
-
-The different components can be accessed as follow:
-```{r}
-# Coordinates of groups
-head(group_vybal2$coord)
-# Cos2: quality of representation on the factore map
-head(group_vybal2$cos2)
-# Contributions to the  dimensions
-head(group_vybal2$contrib)
-
-```
-
-To plot the groups of variables, type this:
-
-```{r}
-fviz_mfa_var(res.mfa_agg_byval2, "group")
-
-```
-
-red color = active groups of variables
-green color = supplementary groups of variables
-The plot above illustrates the correlation between groups and dimensions.
-The coordinates of the four active groups on the first dimension are almost identical.
-This means that they contribute similarly to the first dimension.
-Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.
-
-To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
-```{r}
-# Contribution to the first dimension
-fviz_contrib(res.mfa_agg_byval2, "group", axes = 1)
-# Contribution to the second dimension
-fviz_contrib(res.mfa_agg_byval2, "group", axes = 2)
-
-```
-Quantitative variables
-The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables.
-This function returns a list containing the coordinates, the cos2 and the contribution of variables:
-```{r}
-quanti.var_agg_by_val2 <- get_mfa_var(res.mfa_agg_byval2, "quanti.var")
-quanti.var_agg_by_val2
-
-```
-
-```{r}
-# Coordinates
-head(quanti.var_agg_by_val2$coord)
-# Cos2: quality on the factore map
-head(quanti.var_agg_by_val2$cos2)
-# Contributions to the dimensions
-head(quanti.var_agg_by_val2$contrib)
-
-```
-Correlation between quantitative variables and dimensions.
-The R code below plots quantitative variables colored by groups.
-The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
-Supplementary quantitative variables are in dashed arrow and violet color.
-We use repel = TRUE, to avoid text overlapping.
-
-```{r}
-fviz_mfa_var(res.mfa_agg_byval2, "quanti.var", palette = "jco", 
-             col.var.sup = "violet", repel = TRUE)
-
-```
-
-Correlation between quantitative variables and dimensions.
-The R code below plots quantitative variables colored by groups.
-The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette).
-Supplementary quantitative variables are in dashed arrow and violet color.
-We use repel = TRUE, to avoid text overlapping.
-
-```{r}
-fviz_mfa_var(res.mfa_agg_byval2, "quanti.var", palette = "jco", 
-             col.var.sup = "violet", repel = TRUE)
-
-```
-
-To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”).
-We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
-```{r}
-fviz_mfa_var(res.mfa_agg_byval2, "quanti.var", palette = "jco", 
-             col.var.sup = "violet", repel = TRUE,
-             geom = c("point", "text"), legend = "bottom")
-
-```
-
-```{r}
-fviz_contrib(res.mfa_agg_byval2, choice = "quanti.var", axes = 1, top = 20,
-             palette = "jco")
-fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 2, top = 20,
-             palette = "jco")
-
-```
-Graph of individuals
-
-```{r}
-# To get the results for individuals, type this:
-
-ind_agg_byval2 <- get_mfa_ind(res.mfa_agg_byval2)
-ind_agg_byval2
-
-```
-To plot individuals, use the function fviz_mfa_ind() [in factoextra].
-By default, individuals are colored in blue.
-However, like variables, it’s also possible to color individuals by their cos2 values:
-
-```{r}
-fviz_mfa_ind(res.mfa_agg_byval2, col.ind = "cos2", 
-             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
-             repel = TRUE)
-
-fviz_mfa_ind(res.mfa_agg_byval2, 
-             habillage = "ssid", # color by groups
-             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-```
-
-```{r}
-
-clustering_new_pre_PCA_2
-
-fviz_mfa_ind(res.mfa_agg_byval2, 
-             # habillage = "stimIAPS2", # color by groups 
-             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-```
-
-Graph of partial individuals
-The results for individuals obtained from the analysis performed with a single group are named partial individuals.
-In other words, an individual considered from the point of view of a single group is called partial individual.
-
-In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual.
-That is, the individual viewed by all groups of variables.
-
-For a given individual, there are as many partial points as groups of variables.
-
-The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:
-
-```{r}
-fviz_mfa_ind(res.mfa_agg_byval2, partial = "all") 
-# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:
-
-```
-
-Graph of partial axes
-The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).
-
-```{r}
-fviz_mfa_axes(res.mfa_agg_byval2)
-fviz_mfa_axes()
-
-```
-
-Mutual information
-
-```{r}
-install.packages("infotheo")
-library(infotheo)
-
-mutinformation(X, Y, method="emp")
-?mutinformation
-mutinformation(clustering_new_pre_PCA_2$arousal, clustering_new_pre_PCA_2$pup_basCor, 
-               method="mm")
-
-install.packages("entropy")
-
-entropy::mi.plugin(clustering_new_pre_PCA_2[,c(3,6)])
-```
+save.image("subjobjPCAfeb9.RData")
+```

### 2022-02-09 resample_data.R

@@ -348,15 +348,3 @@ uniquify_vector <- function(vector, indices) {
                            ave(vector[indices], indices, FUN=seq_along),
                            sep="_"))
 }
-© 2022 GitHub, Inc.
-Terms
-Privacy
-Security
-Status
-Docs
-Contact GitHub
-Pricing
-API
-Training
-Blog
-About

### 2022-02-10 Paper_Analyses_subj_obje_arousal.Rmd
last push of simulations for the day

@@
 colnames(resampled_temp_test)
+
  # create emopty dataframe
@@
 #################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
-for (i in 1:1000) {
+for (i in 1:5000) {
   message(sprintf("$$$$$RUNING sim %i", i))
@@
 clustering_new_pre_PCA3.1.scale_agg_bystim<- clustering_new_pre_PCA3.1%>%
-  group_by(stimDescription)%>%
+  group_by(stimDescription,val_cut_iaps)%>%
   summarise_if(is.numeric, mean, na.rm = TRUE)
@@
 clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg<- clustering_new_pre_PCA3.1.scale_agg_bystim%>%
+  ungroup()%>%
   mutate_if(is.numeric, scale)
+
+clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$val_cut_iaps
 
@@
   group_by(ssid)%>%
-  transform(pup_basCor = sample(pup_basCor, replace = F),
-            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = F),
-            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = F),
+  transform(pup_basCor = sample(pup_basCor, replace = TRUE),
+            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = TRUE),
+            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = TRUE),
             arousal = sample(arousal, replace = F),
@@
 
-for (i in 1:1000) {
+for (i in 1:10000) {
   message(sprintf("$$$$$RUNING sim %i", i))
 
-resampled_temp_reshuf<-    clustering_new_pre_PCA3.1_copy[,c(1,2,3, 5:9)] %>%
+# changed below to replace treue - shuflle with replacement
+  # https://stats.stackexchange.com/questions/104040/resampling-simulation-methods-monte-carlo-bootstrapping-jackknifing-cross?rq=1
+  # See the question on permutation vs bootstrapping - "The permutation test is best for testing hypotheses and bootstrapping is best for estimating confidence intervals".
+resampled_temp_reshuf <-    clustering_new_pre_PCA3.1_copy[,c(1,2,3, 5:9)] %>%
   group_by(ssid)%>%
   transform(pup_basCor = 
-              sample(pup_basCor, replace = F),
-            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = F),
-            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = F),
-            arousal = sample(arousal, replace = F),
-            valence = sample(valence, replace = F))
+              sample(pup_basCor, replace = TRUE),
+            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = TRUE),
+            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = TRUE),
+            arousal = sample(arousal, replace = TRUE),
+            valence = sample(valence, replace = TRUE))
 
@@
 
+visualise resshufled null data
+
+```{r}
+
+eigen_first_reshuf%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_reshuf), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
+  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
+  ggplot(aes(eigenvalue))+
+  geom_histogram(bins = 500, alpha = .2)+
+    geom_density(alpha = .3)+
+  # facet_grid(~component)+
+    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(aes(xintercept = perc_5, linetype = "dashed"))+
+  geom_vline(aes(xintercept = perc_95, linetype = "dashed"))+
+  ggtitle("distribution of boostraped eigen values for component  1 
+          red dot = observed eigenvalue, boostrapped 95%CI")+
+  annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")+
+  ylim(0,10)
+
+table(eigen_first$eigenvalue>1)
+
+t.testsample1_reshudle<- eigen_first_reshuf%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )
+
+t.testsample1_reshudle$eigen_extreme <- t.testsample1_reshudle$eigenvalue>= res.mfa_bio_vs_self2_k2$eig[1]
+table(t.testsample1_reshudle$eigen_extreme)
+
+?binom.test
+binom.test(c(0,1000))
+
+# let's do component 2
+
+t.testsample1_reshudledim2<- eigen_first_reshuf%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 2" )
+
+t.testsample1_reshudledim2$eigen_extreme <- t.testsample1_reshudledim2$eigenvalue>= res.mfa_bio_vs_self2_k2$eig[2]
+table(t.testsample1_reshudle$eigen_extreme)
+
+eigen_first_reshuf%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_reshuf), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
+  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
+  ggplot(aes(eigenvalue))+
+  geom_histogram(bins = 500, alpha = .2)+
+    geom_density(alpha = .3)+
+  # facet_grid(~component)+
+    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_bio_vs_self2_k2$eig[2],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(aes(xintercept = perc_5, linetype = "dashed"))+
+  geom_vline(aes(xintercept = perc_95, linetype = "dashed"))
+  # ggtitle("distribution of boostraped eigen values for component  1 
+  #         red dot = observed eigenvalue, boostrapped 95%CI")+
+  # annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")
+  # ylim(0,10)
+
+```
+cor reshudl
+
+```{r}
+cor_first_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  # subset(variable == "arousa"|variable == "valenc")%>%
+  # select(c("arousal", "valence"))%>%
+  ggplot(aes(Dim.1)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+cor_first_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  subset(variable == "valenc")%>%
+  mutate(valenc_cor_extreme_d1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[5,1]),
+         valenc_cor_extreme_d2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[5,2]))%>%
+  mutate(prob_extree_vl_d1 = (sum(valenc_cor_extreme_d1)/n()),
+         prob_extree_val_d2 = (sum(valenc_cor_extreme_d2)/n()))
+# p 0.019	0.532
+
+cor_first_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  subset(variable == "arousa")%>%
+  mutate(arous_cor_extreme_d1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[4,1]),
+         arous_cor_extreme_d2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[4,2]))%>%
+  mutate(prob_extree_vl_d1 = (sum(arous_cor_extreme_d1)/n()),
+         prob_extree_val_d2 = (sum(arous_cor_extreme_d2)/n()))
+#  p 0.532; 0.019
+
+```
+
+```{r}
+
+cor_first_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  subset(variable == "pup_ba")%>%
+  mutate(pup_cor_extreme_d1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[1,1]),
+         pup_cor_extreme_d2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[1,2]))%>%
+  mutate(prob_extree_puup_d1 = (sum(pup_cor_extreme_d1))/n(),
+         prob_extree_puup_d2 = (sum(pup_cor_extreme_d2))/n())
+
+```
+# not significant
+
+# scr
+
+```{r}
+cor_first_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  subset(variable == "Bio_Me")%>%
+  mutate(hr_cor_extreme_d1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[2,1]),
+         hr_cor_extreme_d2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[2,2]))%>%
+  mutate(prob_extree_hr_d1 = (sum(hr_cor_extreme_d1))/n(),
+         prob_extree_hr_d2 = (sum(hr_cor_extreme_d2))/n())
+# p< .016 d1 p> ,05 d2
+
+cor_first_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  subset(variable == "log_BI")%>%
+  mutate(scr_cor_extreme_Dim.1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[3,1]),
+         scr_cor_extreme_Dim.2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[3,2]))%>%
+  mutate(prob_extree_scr_dim1 = (sum(scr_cor_extreme_Dim.1))/n(),
+         prob_extree_scr_dim2 = (sum(scr_cor_extreme_Dim.2))/n())
+
+# cor nor significant in any dimension p > p05
+
+```
+
+```{r}
+
+partials_first_reshuf%>%
+  mutate(dimension = as.factor(substr(rownames(partials_first_reshuf), 1,4)),
+         group = as.factor(substr(rownames(partials_first_reshuf), 5,9)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(dimension, group)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  ggplot(aes(Dim.1)) +
+  geom_histogram(bins = 500)+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+  geom_density(alpha=.2) +
+  facet_grid(dimension~group)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+partials_first_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(partials_first_reshuf), 1,8))) %>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+
+  subset(variable == "log_BI")%>%
+  mutate(scr_cor_extreme_Dim.1 = Dim.1>= abs(mfa.res_reshuf$quanti.var$cor[3,1]),
+         scr_cor_extreme_Dim.2 = Dim.2>= abs(mfa.res_reshuf$quanti.var$cor[3,2]))%>%
+  mutate(prob_extree_scr_dim1 = (sum(scr_cor_extreme_Dim.1))/n(),
+         prob_extree_scr_dim2 = (sum(scr_cor_extreme_Dim.2))/n())
+
+```
+
+```{r}
+
+groups_first_reshuf<- groups_first_reshuf%>%
+  mutate(group = as.factor(substr(rownames(groups_first_reshuf), 1,4)))
+
+group_cordf<- as.data.frame(res.mfa_bio_vs_self2_k2$group$correlation)
+group_cordf$group<-as.factor(substr(rownames(group_cordf), 1,4))
+
+groups_first_reshuf<- left_join(groups_first_reshuf, group_cordf, by = "group")
+
+# groups_first_reshuf%>%
+#   mutate(group = as.factor(substr(rownames(groups_first_reshuf), 1,4))) %>%
+#     subset(!is.na(Dim.1)) %>%
+#   # create interval per variable
+
+View(groups_first_reshuf)
+groups_first_reshuf%>%
+  gather(dimension, value_dimenion, -group, -sim_no, -Dim.1.y, -Dim.2.y) %>%
+  # -perc_5,-perc_95, 
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
+
+  ggplot(aes(value_dimenion)) +
+  geom_histogram(bins = 500)+
+  geom_vline(aes(xintercept = Dim.1.y), linetype = "dashed", color = "red")+
+   geom_vline(aes(xintercept = Dim.2.y),  linetype = "dashed", color = "blue")+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+  geom_density(alpha=.2) +
+  facet_grid(dimension~group)+
+
+  theme_classic()
+
+res.mfa_bio_vs_self2_k2$group$correlation
+
+```
 # agg by pp
@@
 # run PCA on the resampled data
-  # colnames(resampled_temp_bysubj)
-    message(sprintf("$$$$$fitting PCA %i", i))
+  colnames(resampled_temp_bysubj)
+    # message(sprintf("$$$$$fitting PCA %i", i))
     mfa.res_bysubj <- FactoMineR::MFA(resampled_temp_bysubj[,1:6], 
@@
 
-```
+cor_first_bysubj %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj), 1,6)))%>%
+    subset(!is.na(Dim.2)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  # subset(variable == "arousa"|variable == "valenc")%>%
+  # select(c("arousal", "valence"))%>%
+  ggplot(aes(Dim.2)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+```
+much less conistent
+
+```{r}
+groups_first_bysubj%>%
+  gather(dimension, value_dimenion, -group, -sim_no) %>%
+  # -perc_5,-perc_95, 
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
+
+  ggplot(aes(value_dimenion)) +
+  geom_histogram(bins = 500)+
+  geom_vline(aes(xintercept = Dim.1.y), linetype = "dashed", color = "red")+
+   geom_vline(aes(xintercept = Dim.2.y),  linetype = "dashed", color = "blue")+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+  geom_density(alpha=.2) +
+  facet_grid(dimension~group)+
+  theme_classic()
+
+```
+
+resample agg by sbj
+
+```{r}
+colnames(resamp_1st_bysubj_reshuf)
+ # create emopty dataframe
+resamp_1st_bysubj_reshuf<- data.frame(matrix(NA, nrow = 1, ncol = 7))
+cnames_resamp_bysubj_reshuf<- names(resampled_temp_bysubj_reshuf)
+
+colnames(resamp_1st_bysubj_reshuf)<- cnames_resamp_bysubj_reshuf
+colnames(resamp_1st_bysubj_reshuf)
+# create emoty  storage rame for eigenvakues
+eigen_first_bysubj_reshuf<- as.data.frame(eugentest)
+eigen_first_bysubj_reshuf[,]<- NA
+
+# eigen_first_bysubj_reshuf<- as.data.frame(eigen_first_bysubj_reshuf)
+
+# create empty storage for correlations
+cor_first_bysubj_reshuf<- as.data.frame(cortest)
+cor_first_bysubj_reshuf[,]<- NA
+# cor_first_bysubj_reshuf<- as.data.frame(cor_first_bysubj_reshuf)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first_bysubj_reshuf <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first_bysubj_reshuf[,]<- NA
+partials_first_bysubj_reshuf
+partials_first_bysubj_reshuf$sim_no<- NA
+
+# hierarquical clustering
+clustering_new_pre_PCA3.1$ssid <- as.character(clustering_new_pre_PCA3.1$ssid)
+clustering_new_pre_PCA3.1$stimDescription<- as.character(clustering_new_pre_PCA3.1$stimDescription)
+# having clusters as factors causes a subscript oput of bound error
+
+# think we need to store groups
+
+groups_first_bysubj_reshuf<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first_bysubj_reshuf[,]<- NA
+groups_first_bysubj_reshuf
+groups_first_bysubj_reshuf$sim_no<- NA
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+
+for (i in 1:1000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+  # changed below to replace treue - shuflle with replacement
+  # https://stats.stackexchange.com/questions/104040/resampling-simulation-methods-monte-carlo-bootstrapping-jackknifing-cross?rq=1
+  # See the question on permutation vs bootstrapping - "The permutation test is best for testing hypotheses and bootstrapping is best for estimating confidence intervals".
+resampled_temp_bysubj_reshuf <- clustering_new_pre_PCA3.1.scale_agg_bysid %>%
+  # group_by(ssid)%>%
+  transform(pup_basCor = 
+              sample(pup_basCor, replace = TRUE),
+            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = TRUE),
+            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = TRUE),
+            arousal = sample(arousal, replace = TRUE),
+            valence = sample(valence, replace = TRUE))
+
+  resampled_temp_bysubj_reshuf$sim_no = i
+
+# run PCA on the resampled data
+# ?list
+  colnames(resampled_temp_bysubj_reshuf)
+    message(sprintf("$$$$$fitting PCA %i", i))
+    mfa.res_bysubj_reshuf <- FactoMineR::MFA(resampled_temp_bysubj_reshuf[,c(1:6)], 
+               group = c(1, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest_bysubj_reshufl<- as.data.frame(mfa.res_bysubj_reshuf$eig[1:2,])
+eugentest_bysubj_reshufl$sim_no<- i
+
+cortest_bysubj_reshufl<- as.data.frame(mfa.res_bysubj_reshuf$quanti.var$cor)
+cortest_bysubj_reshufl$sim_no = i
+
+partials_temp_bysubj_reshuf<- as.data.frame(mfa.res_bysubj_reshuf$partial.axes$cor)
+partials_temp_bysubj_reshuf$sim_no = i
+
+# groups
+group_temp_bysubj_reshuf<- as.data.frame(mfa.res_bysubj_reshuf$group$cos2)
+group_temp_bysubj_reshuf$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st_bysubj_reshuf<- (bind_rows(resamp_1st_bysubj_reshuf, resampled_temp_bysubj_reshuf))
+eigen_first_bysubj_reshuf<- bind_rows(eigen_first_bysubj_reshuf, eugentest_bysubj_reshufl)
+cor_first_bysubj_reshuf<- bind_rows(cor_first_bysubj_reshuf, cortest_bysubj_reshufl)
+partials_first_bysubj_reshuf<- bind_rows(partials_first_bysubj_reshuf, partials_temp_bysubj_reshuf)
+groups_first_bysubj_reshuf<- bind_rows(groups_first_bysubj_reshuf, group_temp_bysubj_reshuf)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+save.image("subjobjPCAfeb9.RData")
+
+```
+
+visualise resshufled null data
+
+```{r}
+
+eigen_first_bysubj_reshuf%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_reshuf), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the
+  ggplot(aes(eigenvalue))+
+  geom_histogram(bins = 500, alpha = .2)+
+    geom_density(alpha = .3)+
+  # facet_grid(~component)+
+    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_agg_bysubj$eig[1],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = res.mfa_agg_bysubj$eig[1], linetype = "dashed")
+
+# no significant
+
+# dimension 2
+eigen_first_bysubj_reshuf%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_reshuf), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the
+  ggplot(aes(eigenvalue))+
+  geom_histogram(bins = 500, alpha = .2)+
+    geom_density(alpha = .3)+
+  # facet_grid(~component)+
+    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_agg_bysubj$eig[2],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = res.mfa_agg_bysubj$eig[2], linetype = "dashed")
+# also not significant
+
+table(eigen_first$eigenvalue>1)
+
+eigen_first_bysubj_reshuf%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>%
+  mutate(extreme_eigen_count = eigenvalue>= res.mfa_agg_bysubj$eig[1])%>%
+  mutate(extreme_eigen_count_prob = (sum(extreme_eigen_count))/n())
+
+# p value 0.702 as we can see in the graph
+
+```
+
+```{r}
+
+res.mfa_agg_bysubj$quanti.var$cor
+
+cor_first_bysubj_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_reshuf), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  group_by(variable)%>%
+  ggplot(aes(Dim.1)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   # geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  theme_classic()
+
+cor_first_bysubj_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_reshuf), 1,6)))%>%
+  subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  subset(variable == "Bio_Me")%>%
+  mutate(hr_cor_extreme_d1 = abs(Dim.1)>= abs(mfa.res_bysubj_reshuf$quanti.var$cor[2,1]),
+         hr_cor_extreme_d2 = abs(Dim.2)>= abs(mfa.res_bysubj_reshuf$quanti.var$cor[2,2]))%>%
+  mutate(prob_extree_hr_d1 = (sum(hr_cor_extreme_d1))/n(),
+         prob_extree_hr_d2 = (sum(hr_cor_extreme_d2))/n())
+
+```
+
+PARTIALS
+
+```{r}
+# res.mfa_agg_bysubj$partial.axes$cor
+partials_first_bysubj_reshuf %>%
+  mutate(dimension = as.factor(substr(rownames(partials_first_bysubj_reshuf), 1,4)),
+         group = as.factor(substr(rownames(partials_first_reshuf), 5,9)))%>%
+    subset(!is.na(Dim.1)) %>%
+  group_by(dimension, group)%>%
+
+  ggplot(aes(Dim.1)) +
+  geom_histogram(bins = 500)+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+  geom_density(alpha=.2) +
+  facet_grid(dimension~group)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+```
+
+groups
+variables and dimension corelations
+
+```{r}
+
+cor_first_bysubj_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_reshuf), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+  ggplot(aes(Dim.1)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+
+  facet_grid(~variable)+
+  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+```
+
 Agg within participant by neg pos etc (using normative data)
@@
 
-```{r}
+start with bootsrap to estimate CIS
+```{r}
+
+clustering_new_pre_PCA3_val_vat_agg_scale # this is the one I need
+colnames(clustering_new_pre_PCA3_val_vat_agg_scale)
+
+res.mfa_agg_bysubj_cat_val<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_agg_scale, 
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("sid","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+colnames(resampled_temp_bysubj_cat_val)
+resamp_1st_bysubj_cat_val<- data.frame(matrix(NA, nrow = 1, ncol = 12))
+
+# cnames_resamp_subj<- names(resampled_temp_bysubj_cat_val)
+colnames(resamp_1st_bysubj_cat_val)<- cnames_resamp_subj
+colnames(resamp_1st_bysubj_cat_val)
+# create emoty  storage rame for eigenvakues
+eigen_first_bysubj_cat_val<- as.data.frame(eugentest)
+eigen_first_bysubj_cat_val[,]<- NA
+
+# eigen_first<- as.data.frame(eigen_first)
+
+# create empty storage for correlations
+cor_first_bysubj_cat_val<- as.data.frame(cortest)
+cor_first_bysubj_cat_val[,]<- NA
+# cor_first<- as.data.frame(cor_first)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first_bysubj_cat_val <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first_bysubj_cat_val[,]<- NA
+partials_first_bysubj_cat_val
+partials_first_bysubj_cat_val$sim_no<- NA
+
+# hierarquical clustering
+clustering_new_pre_PCA3.1.scale_agg_bysid$ssid<- as.character(clustering_new_pre_PCA3.1.scale_agg_bysid$ssid)
+# clustering_new_pre_PCA3.1.scale_agg_bysid$stimDescription<- as.character(clustering_new_pre_PCA3.1.scale_agg_bysid$stimDescription)
+
+# think we need to store groups
+
+groups_first_bysubj_cat_val<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first_bysubj_cat_val[,]<- NA
+groups_first_bysubj_cat_val
+groups_first_bysubj_cat_val$sim_no<- NA
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+colnames(clustering_new_pre_PCA3.1.scale_agg_bysid)
+library(fabricatr)
+
+clustering_new_pre_PCA3_val_vat_agg_scale$valence_iaps_cat<- as.character(clustering_new_pre_PCA3_val_vat_agg_scale$valence_iaps_cat)
+
+clustering_new_pre_PCA3_val_vat_agg_scale$ssid<- as.character(clustering_new_pre_PCA3_val_vat_agg_scale$ssid)
+nrow(clustering_new_pre_PCA3_val_vat_agg_scale)
+
+for (i in 1:1000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+
+  resampled_temp_bysubj_cat_val<- fabricatr::resample_data(clustering_new_pre_PCA3_val_vat_agg_scale, 
+                                  N = c(51,3),
+                                  ID_labels = c("ssid", "valence_iaps_cat"),
+                                  unique_labels = TRUE)
+  # View(resampled_temp_bysubj_cat_val)
+  resampled_temp_bysubj_cat_val$sim_no = i
+  resampled_temp_bysubj_cat_val$ssid_new <- as.factor(substr(resampled_temp_bysubj_cat_val$valence_iaps_cat_unique,1,6))
+  resampled_temp_bysubj_cat_val$newstim <- substr(resampled_temp_bysubj_cat_val$valence_iaps_cat_unique,7,9)
+
+# run PCA on the resampled data
+  # colnames(resampled_temp_bysubj_cat_val)
+    message(sprintf("$$$$$fitting PCA %i", i))
+    # colnames(resampled_temp_bysubj_cat_val[,c(11,12,3:7)])
+    mfa.res_bysubj_cat_val <- FactoMineR::MFA(resampled_temp_bysubj_cat_val[,c(11,12,3:7)], 
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("sid","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest_bysubj_cat_val<- as.data.frame(mfa.res_bysubj_cat_val$eig[1:2,])
+eugentest_bysubj_cat_val$sim_no<- i
+
+cortest_bysubj_cat_val<- as.data.frame(mfa.res_bysubj_cat_val$quanti.var$cor)
+cortest_bysubj_cat_val$sim_no = i
+
+partials_temp_bysubj_cat_val<- as.data.frame(mfa.res_bysubj_cat_val$partial.axes$cor)
+partials_temp_bysubj_cat_val$sim_no = i
+
+# groups
+group_temp_bysubj_cat_val<- as.data.frame(mfa.res_bysubj_cat_val$group$cos2)
+group_temp_bysubj_cat_val$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st_bysubj_cat_val<- (bind_rows(resamp_1st_bysubj_cat_val, resampled_temp_bysubj_cat_val))
+eigen_first_bysubj_cat_val<- bind_rows(eigen_first_bysubj_cat_val, eugentest_bysubj_cat_val)
+cor_first_bysubj_cat_val<- bind_rows(cor_first_bysubj_cat_val, cortest_bysubj_cat_val)
+partials_first_bysubj_cat_val<- bind_rows(partials_first_bysubj_cat_val, partials_temp_bysubj_cat_val)
+groups_first_bysubj_cat_val<- bind_rows(groups_first_bysubj_cat_val, group_temp_bysubj_cat_val)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+resamp_1st_bysubj
+View(resamp_1st_bysubj)
+
+resamp_1st_bysubj
+
+resamp_1st_bysubj%>%
+  subset(sim_no == 11)
+
+```
+
+Visualization of bootsrap for data agregate within particpant and neg mid anpos
+
+```{r}
+eigen_first_bysubj_cat_val%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bysubj_cat_val), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
+  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
+  ggplot(aes(eigenvalue))+
+  geom_histogram(alpha = .2)+
+    geom_density()+
+  # facet_grid(~component)+
+    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_agg_bysubj$eig[1],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = 1, linetype = "dashed")
+  # ggtitle("distribution of boostraped eigen values for component  1 
+          # red dot = observed eigenvalue, boostrapped 95%CI")+
+  # annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")
+
+eigen_first_bysubj_cat_val%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bysubj_cat_val), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
+  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
+  ggplot(aes(eigenvalue))+
+  geom_histogram(alpha = .2)+
+    geom_density()+
+  # facet_grid(~component)+
+    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_agg_bysubj$eig[2],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = 1, linetype = "dashed")
+
+```
+
+variables and dimension corelations
+```{r}
+cor_first_bysubj_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_cat_val), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  # subset(variable == "arousa"|variable == "valenc")%>%
+  # select(c("arousal", "valence"))%>%
+  ggplot(aes(Dim.1)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+cor_first_bysubj_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_cat_val), 1,6)))%>%
+    subset(!is.na(Dim.2)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  # subset(variable == "arousa"|variable == "valenc")%>%
+  # select(c("arousal", "valence"))%>%
+  ggplot(aes(Dim.2)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+# much less conistent
+
+clustering_new_pre_PCA3.1.scale_agg_bystim
+# FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_agg[
+clustering_new_pre_PCA3_val_vat_scale_then_agg1
+
+clustering_new_pre_PCA3_val_vat_agg_scale
+
+```
+
+resample for significance testing
+
+```{r}
+colnames(resamp_1st_bysubj_reshuf_cat_val)
+ # create emopty dataframe
+resamp_1st_bysubj_reshuf_cat_val<- data.frame(matrix(NA, nrow = 1, ncol = 8))
+cnames_resamp_bysubj_reshuf_cat_val<- names(resampled_temp_bysubj_reshuf_cat_val)
+
+colnames(resamp_1st_bysubj_reshuf_cat_val)<- cnames_resamp_bysubj_reshuf_cat_val
+colnames(resamp_1st_bysubj_reshuf_cat_val)
+# create emoty  storage rame for eigenvakues
+eigen_first_bysubj_reshuf_cat_val<- as.data.frame(eugentest)
+eigen_first_bysubj_reshuf_cat_val[,]<- NA
+
+# eigen_first_bysubj_reshuf_cat_val<- as.data.frame(eigen_first_bysubj_reshuf_cat_val)
+
+# create empty storage for correlations
+cor_first_bysubj_reshuf_cat_val<- as.data.frame(cortest)
+cor_first_bysubj_reshuf_cat_val[,]<- NA
+# cor_first_bysubj_reshuf_cat_val<- as.data.frame(cor_first_bysubj_reshuf_cat_val)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first_bysubj_reshuf_cat_val <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first_bysubj_reshuf_cat_val[,]<- NA
+partials_first_bysubj_reshuf_cat_val
+partials_first_bysubj_reshuf_cat_val$sim_no<- NA
+
+# think we need to store groups
+
+groups_first_bysubj_reshuf_cat_val<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first_bysubj_reshuf_cat_val[,]<- NA
+groups_first_bysubj_reshuf_cat_val
+groups_first_bysubj_reshuf_cat_val$sim_no<- NA
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+?sample
+
+# permutations should be withouth replacement
+for (i in 1:1000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+  # changed below to replace treue - shuflle with replacement
+  # https://stats.stackexchange.com/questions/104040/resampling-simulation-methods-monte-carlo-bootstrapping-jackknifing-cross?rq=1
+  # See the question on permutation vs bootstrapping - "The permutation test is best for testing hypotheses and bootstrapping is best for estimating confidence intervals".
+  colnames(clustering_new_pre_PCA3_val_vat_agg_scale)
+resampled_temp_bysubj_reshuf_cat_val <- clustering_new_pre_PCA3_val_vat_agg_scale %>%
+  group_by(ssid)%>%
+  transform(pup_basCor = 
+              sample(pup_basCor, replace = FALSE),
+            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = FALSE),
+            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = FALSE),
+            arousal = sample(arousal, replace = FALSE),
+            valence = sample(valence, replace = FALSE))
+
+  resampled_temp_bysubj_reshuf_cat_val$sim_no = i
+
+# run PCA on the resampled data
+# ?list
+  # colnames(resampled_temp_bysubj_reshuf_cat_val)
+    message(sprintf("$$$$$fitting PCA %i", i))
+    mfa.res_bysubj_reshuf_cat_val <- FactoMineR::MFA(resampled_temp_bysubj_reshuf_cat_val[,c(1:7)], 
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest_bysubj_reshuf_cat_vall<- as.data.frame(mfa.res_bysubj_reshuf_cat_val$eig[1:2,])
+eugentest_bysubj_reshuf_cat_vall$sim_no<- i
+
+cortest_bysubj_reshuf_cat_vall<- as.data.frame(mfa.res_bysubj_reshuf_cat_val$quanti.var$cor)
+cortest_bysubj_reshuf_cat_vall$sim_no = i
+
+partials_temp_bysubj_reshuf_cat_val<- as.data.frame(mfa.res_bysubj_reshuf_cat_val$partial.axes$cor)
+partials_temp_bysubj_reshuf_cat_val$sim_no = i
+
+# groups
+group_temp_bysubj_reshuf_cat_val<- as.data.frame(mfa.res_bysubj_reshuf_cat_val$group$cos2)
+group_temp_bysubj_reshuf_cat_val$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st_bysubj_reshuf_cat_val<- (bind_rows(resamp_1st_bysubj_reshuf_cat_val, resampled_temp_bysubj_reshuf_cat_val))
+eigen_first_bysubj_reshuf_cat_val<- bind_rows(eigen_first_bysubj_reshuf_cat_val, eugentest_bysubj_reshuf_cat_vall)
+cor_first_bysubj_reshuf_cat_val<- bind_rows(cor_first_bysubj_reshuf_cat_val, cortest_bysubj_reshuf_cat_vall)
+partials_first_bysubj_reshuf_cat_val<- bind_rows(partials_first_bysubj_reshuf_cat_val, partials_temp_bysubj_reshuf_cat_val)
+groups_first_bysubj_reshuf_cat_val<- bind_rows(groups_first_bysubj_reshuf_cat_val, group_temp_bysubj_reshuf_cat_val)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+save.image("subjobjPCAfeb9.RData")
+
+```
+
+<!-- visualisae permutation tests -->
+
+```{r}
+eigen_first_bysubj_reshuf_cat_val%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bysubj_reshuf_cat_val), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the
+  ggplot(aes(eigenvalue))+
+  geom_histogram(bins = 500, alpha = .2)+
+    geom_density(alpha = .3)+
+  # facet_grid(~component)+
+    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_agg_bysubj_cat_val$eig[1],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = res.mfa_agg_bysubj$eig[1], linetype = "dashed")
+
+# no significant
+
+# dimension 2
+eigen_first_bysubj_reshuf_cat_val%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bysubj_reshuf_cat_val), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the
+  ggplot(aes(eigenvalue))+
+  geom_histogram(bins = 500, alpha = .2)+
+    geom_density(alpha = .3)+
+  # facet_grid(~component)+
+    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_agg_bysubj_cat_val$eig[2],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = res.mfa_agg_bysubj$eig[2], linetype = "dashed")
+# also not significant
+
+table(eigen_first$eigenvalue>1)
+
+eigen_first_bysubj_reshuf_cat_val%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>%
+  mutate(extreme_eigen_count = eigenvalue>= res.mfa_agg_bysubj_cat_val$eig[1])%>%
+  mutate(extreme_eigen_count_prob = (sum(extreme_eigen_count))/n())
+
+eigen_first_bysubj_reshuf_cat_val%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 2" )%>%
+  mutate(extreme_eigen_count = eigenvalue>= res.mfa_agg_bysubj_cat_val$eig[2])%>%
+  mutate(extreme_eigen_count_prob = (sum(extreme_eigen_count))/n())
+
+```
+
+correlation btween variables and dimensions
+
+```{r}
+res.mfa_agg_bysubj$quanti.var$cor
+
+cor_first_bysubj_reshuf_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_reshuf_cat_val), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  group_by(variable)%>%
+  ggplot(aes(Dim.1)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   # geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  theme_classic()
+
+cor_first_bysubj_reshuf_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_reshuf_cat_val), 1,6)))%>%
+  subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  subset(variable == "Bio_Me")%>%
+  mutate(hr_cor_extreme_d1 = abs(Dim.1)>= abs(mfa.res_bysubj_reshuf_cat_val$quanti.var$cor[2,1]),
+         hr_cor_extreme_d2 = abs(Dim.2)>= abs(mfa.res_bysubj_reshuf_cat_val$quanti.var$cor[2,2]))%>%
+  mutate(prob_extree_hr_d1 = (sum(hr_cor_extreme_d1))/n(),
+         prob_extree_hr_d2 = (sum(hr_cor_extreme_d2))/n())
+
+```
+
+```{r}
+res.mfa_agg_bysubj_cat_val$group$correlation
+groups_first_bysubj_cat_val%>%
+  mutate(group = as.factor(substr(rownames(groups_first_bysubj_cat_val), 1,4)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+
+  gather(dimension, value_dimenion, -group, -sim_no) %>%
+  # -perc_5,-perc_95, 
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
+
+  ggplot(aes(value_dimenion, color = group)) +
+  geom_histogram(bins = 500)+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =10 ), color = "gray30")+
+  facet_grid(dimension~group)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+  ylim(0,100)
+
+```
+
+<!-- agg by stim -->
+
+```{r}
+colnames(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg)
+
+res.mfa_agg_stim<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg, 
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+               # "s", "s", "s"
+               name.group = c("stim_cat","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+```
+
+boostrap
+```{r}
+
+clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg # this is the one I need
+colnames(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg)
+
+colnames(resampled_temp_bystim_cat_val)
+resamp_1st_bystim_cat_val<- data.frame(matrix(NA, nrow = 1, ncol = 10))
+
+cnames_resamp_subj<- names(resampled_temp_bystim_cat_val)
+colnames(resamp_1st_bystim_cat_val)<- cnames_resamp_subj
+colnames(resamp_1st_bystim_cat_val)
+# create emoty  storage rame for eigenvakues
+eigen_first_bystim_cat_val<- as.data.frame(eugentest)
+eigen_first_bystim_cat_val[,]<- NA
+
+# eigen_first<- as.data.frame(eigen_first)
+
+# create empty storage for correlations
+cor_first_bystim_cat_val<- as.data.frame(cortest)
+cor_first_bystim_cat_val[,]<- NA
+# cor_first<- as.data.frame(cor_first)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first_bystim_cat_val <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first_bystim_cat_val[,]<- NA
+partials_first_bystim_cat_val
+partials_first_bystim_cat_val$sim_no<- NA
+
+# hierarquical clustering
+clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$stimDescription <- as.character(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$stimDescription)
+clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$val_cut_iaps <- as.character(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$val_cut_iaps)
+
+# think we need to store groups
+
+groups_first_bystim_cat_val<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first_bystim_cat_val[,]<- NA
+groups_first_bystim_cat_val
+groups_first_bystim_cat_val$sim_no<- NA
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+
+library(fabricatr)
+
+for (i in 1:1000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+
+  resampled_temp_bystim_cat_val<- fabricatr::resample_data(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg, 
+                                  N = c(53),
+                                  ID_labels = c("stimDescription"),
+                                  unique_labels = TRUE)
+  # View(resampled_temp_bystim_cat_val)
+  resampled_temp_bystim_cat_val$sim_no = i
+  resampled_temp_bystim_cat_val$stimDescription_new <- as.factor(substr(resampled_temp_bystim_cat_val$stimDescription_unique,1,3))
+
+# run PCA on the resampled data
+  # colnames(resampled_temp_bystim_cat_val)
+    message(sprintf("$$$$$fitting PCA %i", i))
+    # colnames(resampled_temp_bystim_cat_val[,c(10,2:7)])
+    mfa.res_bystim_cat_val <- FactoMineR::MFA(resampled_temp_bystim_cat_val[,c(10,2:7)], 
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("stimid_cat","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest_bystim_cat_val<- as.data.frame(mfa.res_bystim_cat_val$eig[1:2,])
+eugentest_bystim_cat_val$sim_no<- i
+
+cortest_bystim_cat_val<- as.data.frame(mfa.res_bystim_cat_val$quanti.var$cor)
+cortest_bystim_cat_val$sim_no = i
+
+partials_temp_bystim_cat_val<- as.data.frame(mfa.res_bystim_cat_val$partial.axes$cor)
+partials_temp_bystim_cat_val$sim_no = i
+
+# groups
+group_temp_bystim_cat_val<- as.data.frame(mfa.res_bystim_cat_val$group$cos2)
+group_temp_bystim_cat_val$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st_bystim_cat_val<- (bind_rows(resamp_1st_bystim_cat_val, resampled_temp_bystim_cat_val))
+eigen_first_bystim_cat_val<- bind_rows(eigen_first_bystim_cat_val, eugentest_bystim_cat_val)
+cor_first_bystim_cat_val<- bind_rows(cor_first_bystim_cat_val, cortest_bystim_cat_val)
+partials_first_bystim_cat_val<- bind_rows(partials_first_bystim_cat_val, partials_temp_bystim_cat_val)
+groups_first_bystim_cat_val<- bind_rows(groups_first_bystim_cat_val, group_temp_bystim_cat_val)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+#################################
+# note i have not checked the rsults from above
+
+```
+
+visualise CIS boots
+
+```{r}
+eigen_first_bystim_cat_val%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bystim_cat_val), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
+  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
+  ggplot(aes(eigenvalue))+
+  geom_histogram(alpha = .2)+
+    geom_density()+
+  # facet_grid(~component)+
+    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_agg_stim$eig[1],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = 1, linetype = "dashed")
+  # ggtitle("distribution of boostraped eigen values for component  1 
+          # red dot = observed eigenvalue, boostrapped 95%CI")+
+  # annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")
+
+eigen_first_bystim_cat_val%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bystim_cat_val), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
+  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
+  ggplot(aes(eigenvalue))+
+  geom_histogram(alpha = .2)+
+    geom_density()+
+  # facet_grid(~component)+
+    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_agg_stim$eig[2],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = 1, linetype = "dashed")
+
+```
+
+correlation variables dimensions
+
+```{r}
+cor_first_bystim_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bystim_cat_val), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  # subset(variable == "arousa"|variable == "valenc")%>%
+  # select(c("arousal", "valence"))%>%
+  ggplot(aes(Dim.1)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+cor_first_bystim_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bystim_cat_val), 1,6)))%>%
+    subset(!is.na(Dim.2)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  # subset(variable == "arousa"|variable == "valenc")%>%
+  # select(c("arousal", "valence"))%>%
+  ggplot(aes(Dim.2)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+```
+
+groups
+
+```{r}
+groups_first_bystim_cat_val%>%
+  mutate(group = as.factor(substr(rownames(groups_first_bystim_cat_val), 1,4)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+
+  gather(dimension, value_dimenion, -group, -sim_no) %>%
+  # -perc_5,-perc_95, 
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
+
+  ggplot(aes(value_dimenion, color = group)) +
+  geom_histogram(bins = 500)+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =10 ), color = "gray30")+
+  facet_grid(dimension~group)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+```
+
+resdshufle stim
+```{r}
+colnames(resampled_temp_bystimj_reshuf)
+# create emopty dataframe
+resamp_1st_bystimj_reshuf<- data.frame(matrix(NA, nrow = 1, ncol = 8))
+cnames_resamp_bystimj_reshuf<- names(resampled_temp_bystimj_reshuf)
+
+colnames(resamp_1st_bystimj_reshuf)<- cnames_resamp_bystimj_reshuf
+colnames(resamp_1st_bystimj_reshuf)
+# create emoty  storage rame for eigenvakues
+eigen_first_bystimj_reshuf<- as.data.frame(eugentest)
+eigen_first_bystimj_reshuf[,]<- NA
+
+# eigen_first_bystimj_reshuf<- as.data.frame(eigen_first_bystimj_reshuf)
+
+# create empty storage for correlations
+cor_first_bystimj_reshuf<- as.data.frame(cortest)
+cor_first_bystimj_reshuf[,]<- NA
+# cor_first_bystimj_reshuf<- as.data.frame(cor_first_bystimj_reshuf)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first_bystimj_reshuf <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first_bystimj_reshuf[,]<- NA
+partials_first_bystimj_reshuf
+partials_first_bystimj_reshuf$sim_no<- NA
+
+clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$stimDescription<- as.character(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$stimDescription)
+# having clusters as factors causes a subscript oput of bound error
+
+# think we need to store groups
+
+groups_first_bystimj_reshuf<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first_bystimj_reshuf[,]<- NA
+groups_first_bystimj_reshuf
+groups_first_bystimj_reshuf$sim_no<- NA
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+
+for (i in 1:1000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+  # changed below to replace treue - shuflle with replacement
+  # https://stats.stackexchange.com/questions/104040/resampling-simulation-methods-monte-carlo-bootstrapping-jackknifing-cross?rq=1
+  # See the question on permutation vs bootstrapping - "The permutation test is best for testing hypotheses and bootstrapping is best for estimating confidence intervals".
+resampled_temp_bystimj_reshuf <- clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg %>%
+  # group_by(ssid)%>%
+  transform(pup_basCor = 
+            sample(pup_basCor, replace = FALSE),
+            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = FALSE),
+            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = FALSE),
+            arousal = sample(arousal, replace = FALSE),
+            valence = sample(valence, replace = FALSE))
+
+# View(resampled_temp_bystimj_reshuf)
+  resampled_temp_bystimj_reshuf$sim_no = i
+
+# run PCA on the resampled data
+# ?list
+  # colnames(resampled_temp_bystimj_reshuf)
+    message(sprintf("$$$$$fitting PCA %i", i))
+    mfa.res_bystimj_reshuf <- FactoMineR::MFA(resampled_temp_bystimj_reshuf[,c(1:7)], 
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("stim_cat","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest_bystimj_reshufl<- as.data.frame(mfa.res_bystimj_reshuf$eig[1:2,])
+eugentest_bystimj_reshufl$sim_no<- i
+
+cortest_bystimj_reshufl<- as.data.frame(mfa.res_bystimj_reshuf$quanti.var$cor)
+cortest_bystimj_reshufl$sim_no = i
+
+partials_temp_bystimj_reshuf<- as.data.frame(mfa.res_bystimj_reshuf$partial.axes$cor)
+partials_temp_bystimj_reshuf$sim_no = i
+
+# groups
+group_temp_bystimj_reshuf<- as.data.frame(mfa.res_bystimj_reshuf$group$cos2)
+group_temp_bystimj_reshuf$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st_bystimj_reshuf<- (bind_rows(resamp_1st_bystimj_reshuf, resampled_temp_bystimj_reshuf))
+eigen_first_bystimj_reshuf<- bind_rows(eigen_first_bystimj_reshuf, eugentest_bystimj_reshufl)
+cor_first_bystimj_reshuf<- bind_rows(cor_first_bystimj_reshuf, cortest_bystimj_reshufl)
+partials_first_bystimj_reshuf<- bind_rows(partials_first_bystimj_reshuf, partials_temp_bystimj_reshuf)
+groups_first_bystimj_reshuf<- bind_rows(groups_first_bystimj_reshuf, group_temp_bystimj_reshuf)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+save.image("subjobjPCAfeb9.RData")
+
+```
+
+visualise pernuation on stim MFA
+
+```{r}
+eigen_first_bystimj_reshuf %>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bystimj_reshuf), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the
+  ggplot(aes(eigenvalue))+
+  geom_histogram(bins = 500, alpha = .2)+
+    geom_density(alpha = .3)+
+  # facet_grid(~component)+
+    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_agg_stim$eig[1],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = res.mfa_agg_stim$eig[1], linetype = "dashed")
+
+# no significant
+
+# dimension 2
+eigen_first_bystimj_reshuf %>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bystimj_reshuf), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the
+  ggplot(aes(eigenvalue))+
+  geom_histogram(bins = 500, alpha = .2)+
+    geom_density(alpha = .3)+
+  # facet_grid(~component)+
+    # geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
+  geom_point(x = res.mfa_agg_stim$eig[2],y = 10,size = 2, color = "red")+
+
+  theme_classic()+
+  geom_vline(xintercept = res.mfa_agg_stim$eig[2], linetype = "dashed")
+# not significant
+
+table(eigen_first$eigenvalue>1)
+
+eigen_first_bystimj_reshuf%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 1" )%>%
+  mutate(extreme_eigen_count = eigenvalue>= res.mfa_agg_stim$eig[1])%>%
+  mutate(extreme_eigen_count_prob = (sum(extreme_eigen_count))/n())
+
+eigen_first_bystimj_reshuf%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue) & component == "comp 2" )%>%
+  mutate(extreme_eigen_count = eigenvalue>= res.mfa_agg_stim$eig[2])%>%
+  mutate(extreme_eigen_count_prob = (sum(extreme_eigen_count))/n())
+
+```
+
+significance variable and dimensions
+
+```{r}
+
+res.mfa_agg_stim$quanti.var$cor
+cor_first_bystim_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bystim_cat_val), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  group_by(variable)%>%
+  ggplot(aes(Dim.1)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   # geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  theme_classic()
+
+cor_first_bysubj_reshuf_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_reshuf_cat_val), 1,6)))%>%
+  subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  subset(variable == "Bio_Me")%>%
+  mutate(hr_cor_extreme_d1 = abs(Dim.1)>= abs(mfa.res_bysubj_reshuf_cat_val$quanti.var$cor[2,1]),
+         hr_cor_extreme_d2 = abs(Dim.2)>= abs(mfa.res_bysubj_reshuf_cat_val$quanti.var$cor[2,2]))%>%
+  mutate(prob_extree_hr_d1 = (sum(hr_cor_extreme_d1))/n(),
+         prob_extree_hr_d2 = (sum(hr_cor_extreme_d2))/n())
+
+```
+
+groups
+```{r}
+res.mfa_agg_bysubj_cat_val$group$correlation
+groups_first_bystim_cat_val%>%
+  mutate(group = as.factor(substr(rownames(groups_first_bystim_cat_val), 1,4)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+
+  gather(dimension, value_dimenion, -group, -sim_no) %>%
+  # -perc_5,-perc_95, 
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
+
+  ggplot(aes(value_dimenion, color = group)) +
+  geom_histogram(bins = 500)+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+  geom_density(alpha=.2) +
+   # geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =10 ), color = "gray30")+
+  facet_grid(dimension~group)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+```
+
+```{r}
+
+```
+
 ?cut
@@
 
+clustering_new_pre_PCA3.1.scale_agg_bystim
 FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_agg[,c(1,2,5,6,7,8,9)], 
@@
 # force k = 2
+# res.mfa_bio_vs_self2_k2
 

### 2022-02-10 Paper_Analyses_subj_obje_arousal1.Rmd
finished boorstrap and resampling tests

--- 2022-02-09 Paper_Analyses_subj_obje_arousal.Rmd
@@
 
+```
+
 #
+
+```{r}
 # quanti
@@
   mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
-  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+   # gather(dimension, value_dimenion, -group, -sim_no) %>%
+  group_by(component)%>%
+  # subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
   mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
-         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
+  ungroup()%>%
+  mutate(eig_obs_dim = if_else(component == "comp 1", 
+                               res.mfa_bio_vs_self2_k2$eig[1],
+                               res.mfa_bio_vs_self2_k2$eig[2])) %>% #create 95% to descrive interval around the observed estimate
+  # also store observed eige for each dimensions
   # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
   ggplot(aes(eigenvalue))+
-  geom_histogram(alpha = .2)+
-    geom_density()+
+  geom_histogram(aes(y=..density..), alpha = .3) +  # scale histogram y
+  geom_density(col = "red", alpha = .001)+
   # facet_grid(~component)+
-    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
-  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1],y = 10,size = 2, color = "red")+
+  geom_errorbar(aes(xmin = perc_5, xmax=perc_95, y = 1), color = "gray30")+
+  geom_point(aes(x = eig_obs_dim, y = 1),size = 2, color = "red", alpha = .3)+
 
   theme_classic()+
-  geom_vline(xintercept = 1, linetype = "dashed")+
-  ggtitle("distribution of boostraped eigen values for component  1 
-          red dot = observed eigenvalue, boostrapped 95%CI")+
-  annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")
-
-table(eigen_first$eigenvalue>1)
-
-t.testsample1<- eigen_first%>%
-  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
-  subset(!is.na(eigenvalue) & component == "comp 1" )
-
-t.test(1.14, mu = mean(t.testsample1$eigenvalue))
-
-# boostrap ratio
-# proposed by abdi for factir scores
-mean(t.testsample1$eigenvalue, na.rm = TRUE)/(sd(t.testsample1$eigenvalue,na.rm = TRUE))
-
-```
-
-```{r}
-# check eigen vectors (correlations
-
-# checpartials_first_n40_withrepl
-
-# check groups
-
-# binom.test(eigen_first$eigenvalue>1)
+  geom_vline(aes(xintercept = perc_5), linetype = "dashed")+
+    geom_vline(aes(xintercept = perc_95), linetype = "dashed")+
+
+  geom_hline(yintercept = 0, linetype = "dashed")+
+  facet_grid(~component)+
+  ggtitle("distribution of boostraped eigen values for components 
+          red dot = observed eigenvalue, boostrapped 95%CI")
+  # annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")
+
+```
+
+use this in the resampling bit
+```{r}
 
@@
 ```
-  # geom_vline(xintercept = 1, linetype = "dashed")
-
-table(eigen_first$eigenvalue>1)
-
-# boot::boot()
-
-```{r}
-
-t.test_sample<- eigen_first%>%
-  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
-  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
-  mutate(eigen_d = (mean(eigenvalue))- res.mfa_bio_vs_self2_k2$eig[1])%>%
-   mutate(eigen_d2 = eigenvalue- res.mfa_bio_vs_self2_k2$eig[1])
-t.test(t.test_sample$eigen_d2)
-
-# technially a t test is calculated as the differnce between current mean and pipulation mean devied by population variance, since we often don't have population variance we estimate it from the sample
-
-# will this give us a t?
-(res.mfa_bio_vs_self2_k2$eig[1]- (mean(t.test_sample$eigenvalue, na.rm = TRUE)))/ 
-  (sd(t.test_sample$eigenvalue))
-
-mean(t.test_sample$eigen_d2)/  (sd(t.test_sample$eigenvalue))
-
-resamp_1st%>%
-  subset(sim_no = 1)%>%
-  subset(is.na(ssid) == FALSE)%>%
-  subset(ssid ==  306)
-
-?fabricatr::fabricate()
-
-library(fabricatr)
-
-# ),
-  # pollution = rnorm(N, mean = 5))
-fabricatr::fabricate(
-  stim = add_level(N = 3),
-  id = add_level(N = 30),
-  Var1 = runif(N, 2, 10),
-  Var2 = runif(N, -5, 6),
-  Var2 = runif(N, .2, 2),
-  Var4 = runif(N, -10, 10),
-  Var5 = runif(N, -10, 10)
-))%>%
-  arrange(stim)
-
-fabricate(
-  primary_schools = add_level(N = 3, 
-                              var1 = runif(N, 0, 10)),
-  students = link_levels(N = 30,
-                          by=join(var1, rho = 0.5)))
-
-```
-
-```{r}
-
-# dimension 2
-
-quantile(eigen_first$eigenvalue,.95, na.rm = TRUE)
-eigen_first%>%
-  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
-    subset(!is.na(eigenvalue) & component == "comp 2" )%>%
-  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE),
-         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
-  ggplot(aes(eigenvalue))+
-  geom_histogram(alpha = .2)+
-    geom_density()+
-   geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
-  geom_point(x = res.mfa_bio_vs_self2_k2$eig[2],y = 10,size = 2, color = "red")+
-  # geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
-  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = 10))+
-  theme_classic()
-
-```
-
-  # first dimension is significant
 
@@
 # quantile(eigen_first$`percentage of variance`,.95, na.rm = TRUE)
-eigen_first%>%
-  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
-  subset(!is.na(`percentage of variance`) & component == "comp 1" )%>%
+
+eigen_first %>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  # gather(dimension, value_dimenion, -group, -sim_no) %>%
+  group_by(component)%>%
+  # subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
   mutate(perc_5 = quantile(`percentage of variance`,.025, na.rm = TRUE), 
          perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE))%>%
+  ungroup()%>%
+  mutate(perc_obs_dim = if_else(component == "comp 1", 
+                               res.mfa_bio_vs_self2_k2$eig[1,2],
+                               res.mfa_bio_vs_self2_k2$eig[2,2])) %>% #
   ggplot(aes(`percentage of variance`))+
@@
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = .3), color = "gray30")+
-  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1,2],y = .3,size = 3, color = "red")+
-
-    # geom_vline(aes(xintercept = perc_5), linetype = "dotted")+
-  # geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
+  geom_point(aes(x = perc_obs_dim,y = .3),size = 3, color = "red")+
+  facet_grid(~component)+
+
+    geom_vline(aes(xintercept = perc_5), linetype = "dotted")+
+  geom_vline(aes(xintercept = perc_95), linetype = "dotted")+
   theme_classic()
@@
 
-cor_first %>%
+cor.test_obsmfa<- as.data.frame(res.mfa_bio_vs_self2_k2$quanti.var$cor) %>%
+   mutate(variable = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$quanti.var$cor)), 1,6)))%>%
+ gather(dimension, value_dimenion, -variable)
+
+cor_first1<- cor_first %>%
   mutate(variable = as.factor(substr(rownames(cor_first), 1,6)))%>%
-    subset(!is.na(Dim.1)) %>%
-  # create interval per variable
-  group_by(variable)%>%
-   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
-         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
-  # subset(variable == "arousa"|variable == "valenc")%>%
-  # select(c("arousal", "valence"))%>%
-  ggplot(aes(Dim.1)) +
+    gather(dimension, value_dimenion, -variable, -sim_no) %>%
+  group_by(variable,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))
+
+left_join(cor_first1, cor.test_obsmfa, by = c("variable", "dimension")) %>%
+  ggplot(aes(value_dimenion.x)) +
   geom_histogram(aes(y=..density..), alpha=0.5,
@@
   geom_density(alpha=.2) +
-   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
-  facet_grid(~variable)+
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-2 ), color = "gray30")+
+  facet_grid(~dimension)+
+  geom_point(aes(x = value_dimenion.y, y = -2))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+  facet_grid(variable~dimension)+
   # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
-  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+
   theme_classic()
 
-cor_first %>%
-  mutate(variable = as.factor(substr(rownames(cor_first), 1,6)))%>%
-    subset(!is.na(Dim.2)) %>%
-  # create interval per variable
-  group_by(variable)%>%
-   mutate(perc_5 = quantile(Dim.2,.025, na.rm = TRUE),
-         perc_95 = quantile(Dim.2,.975, na.rm = TRUE))%>%
-  # subset(variable == "arousa"|variable == "valenc")%>%
-  # select(c("arousal", "valence"))%>%
-  ggplot(aes(Dim.2)) +
+```
+
+<!-- partials -->
+
+The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).
+```{r}
+View(partials_first)
+
+res.mfa_bio_vs_self2_k2$partial.axes$cor
+
+partials_first_1_obs<- as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor) %>%
+   mutate(dimension_partial = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)), 1,4)),
+           group = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)), 5,9)))%>%
+ gather(dimension, value_dimenion,-group,-dimension_partial)
+
+partials_first_1boot<- partials_first%>%
+  mutate(dimension_partial = as.factor(substr(rownames(partials_first), 1,4)),
+         group = as.factor(substr(rownames(partials_first), 5,9)))%>%
+   gather(dimension, value_dimenion, -group, -sim_no, -dimension_partial) %>%
+   group_by(dimension_partial,dimension,group)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))
+
+left_join(partials_first_1boot,partials_first_1_obs,by = c("dimension_partial", "group", "dimension")) %>%
+  group_by(dimension_partial,dimension, group)%>%
+  subset(dimension_partial == "Dim1")%>%
+   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  ggplot(aes(value_dimenion.x)) +
   geom_histogram(aes(y=..density..), alpha=0.5,
@@
   geom_density(alpha=.2) +
-   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
-  facet_grid(~variable)+
-  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
-   geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .1, size = 1)+
-  theme_classic()
-
-```
-
-<!-- partials -->
-
-The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).
-```{r}
-View(partials_first)
-
-partials_first%>%
-  mutate(dimension = as.factor(substr(rownames(partials_first), 1,4)),
-         group = as.factor(substr(rownames(partials_first), 5,9)))%>%
-    subset(!is.na(Dim.1)) %>%
-  # create interval per variable
-  group_by(dimension, group)%>%
-   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
-         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
-  ggplot(aes(Dim.1)) +
-  geom_histogram(bins = 500)+
-  # geom_histogram(aes(y=..density..), alpha=0.5,
-  #                position="identity")+
+  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-5 ), color = "gray30")+
+  geom_point(aes(x = value_dimenion.y, y = -5))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+
+  facet_grid(dimension~group)+
+
+  geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .5)+
+  theme_classic()+
+  ggtitle("partial to dimension 1")
+
+left_join(partials_first_1boot,partials_first_1_obs,by = c("dimension_partial", "group", "dimension")) %>%
+  group_by(dimension_partial,dimension, group)%>%
+  subset(dimension_partial == "Dim2")%>%
+   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
   geom_density(alpha=.2) +
-   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =10 ), color = "gray30")+
+  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-5 ), color = "gray30")+
+  geom_point(aes(x = value_dimenion.y, y = -5))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+
+  facet_grid(dimension~group)+
+
+  geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .5)+
+  theme_classic()+
+  ggtitle("partial to dimension 2")
+
+```
+graph of groups
+```{r}
+View(groups_first)
+?gather
+
+groups_first_obs<- as.data.frame(res.mfa_bio_vs_self2_k2$group$correlation) %>%
+   mutate(group = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$group$correlation)), 1,4)))%>%
+ gather(dimension, value_dimenion_obs,-group)
+
+res.mfa_bio_vs_self2_k2$group$correlation
+
+# we sgoudl probably store cos2 rather than correlatiopn
+# their cos2 values corresponding to their quality of representation on the factor map
+groups_first_1boot<- groups_first%>%
+  mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
+  gather(dimension, value_dimenion,-group,-sim_no)%>%
+  # -perc_5,-perc_95, 
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))
+
+?boot::boot.ci
+boot::boot.ci(groups_first_1boot$value_dimenion, type = "bca")[1]
+?bootBCa
+bootBCa(.5, groups_first_1boot$value_dimenion, n = 2600)[1]
+left_join(groups_first_1boot, groups_first_obs,by = c("group", "dimension"))%>%
+
+  ggplot(aes(value_dimenion)) +
+   geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-3 ), color = "gray30")+
+   geom_point(aes(x = value_dimenion_obs, y = -3))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+
   facet_grid(dimension~group)+
@@
   theme_classic()
-  ylim(0,100)
-
-```
-graph of groups
-```{r}
-View(groups_first)
-?gather
-
-# we sgoudl probably store cos2 rather than correlatiopn
-# their cos2 values corresponding to their quality of representation on the factor map
-groups_first%>%
+
+  # bootsrap confidence intervals don't include point estimate
+# seems like a consequnce of resampling a biased statistocs
+# https://stats.stackexchange.com/questions/388931/bootstrap-confidence-intervals-do-not-include-the-observed-mean-can-this-be
+
+# try plooting with corrected bca
+# ?bca
+# groups_first_1boot_CIcorrected<- groups_first%>%
+#   mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
+#   gather(dimension, value_dimenion,-group,-sim_no)%>%
+#   # -perc_5,-perc_95, 
+#    group_by(group,dimension)%>%
+#   subset(!is.na(value_dimenion))%>%
+#    mutate(perc_5 = bca(value_dimenion)[1],
+#          perc_95 = bca(value_dimenion)[2])
+
+groups_first_1boot_CIcorrected2<- groups_first%>%
   mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
-    subset(!is.na(Dim.1)) %>%
-  # create interval per variable
-
-  gather(dimension, value_dimenion, -group, -sim_no) %>%
-  # -perc_5,-perc_95, 
-   group_by(group,dimension)%>%
-   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
-         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
-
-  ggplot(aes(value_dimenion, color = group)) +
-  geom_histogram(bins = 500)+
-  # geom_histogram(aes(y=..density..), alpha=0.5,
-  #                position="identity")+
+  gather(dimension, value_dimenion,-group,-sim_no)
+
+left_join(groups_first_1boot_CIcorrected2, groups_first_obs,by = c("group", "dimension"))%>%
+  subset(!is.na(value_dimenion))%>%
+  group_by(dimension,group)%>%
+   mutate(perc_5 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 2600)[1],
+         perc_95 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 2600)[2])%>%
+   ggplot(aes(value_dimenion)) +
+   geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
   geom_density(alpha=.2) +
-   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =10 ), color = "gray30")+
+
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-3 ), color = "gray30")+
+   geom_point(aes(x = value_dimenion_obs, y = -3))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+
   facet_grid(dimension~group)+
@@
   theme_classic()
-  ylim(0,100)
+
+```
+
+```{r}
+install.packages("coxed")
+library(coxed)
+
+bcatest<- partials_first_1boot%>%
+  subset(!is.na(value_dimenion))
+
+bcatest<- !is.na(bcatest)
+
+bca(bcatest$value_dimenion)[1]
 
@@
 fviz_mfa_var(res.mfa_bio_vs_self2_scale, 
-             "quanti.var", 
+             # "quanti.var", 
              palette = "jco", 
@@
 
-```{r}
-
-clustering_new_pre_PCA3.1_copy<- clustering_new_pre_PCA3.1
-colnames(clustering_new_pre_PCA3.1)
-
-?sample
-
-# this is slow so need to figure  a better way to to this but for now
-clustering_new_pre_PCA3.1_copy %>%
-  subset(ssid == 304 &val_cut_iaps == "mid" & aro_cut_iaps == "low" )%>%
-  group_by(ssid)%>%
-  transform(pup_basCor = sample(pup_basCor, replace = F),
-            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = F),
-            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = F),
-            arousal = sample(arousal, replace = F),
-            valence = sample(valence, replace = F))
-
-```
-
-```{r}
-
-colnames(resampled_temp_reshuf)
- # create emopty dataframe
-resamp_1st_reshuf<- data.frame(matrix(NA, nrow = 1, ncol = 9))
-cnames_resamp_reshufl<- names(resampled_temp_reshuf)
-
-colnames(resamp_1st_reshuf)<- cnames_resamp_reshufl
-colnames(resamp_1st_reshuf)
-# create emoty  storage rame for eigenvakues
-eigen_first_reshuf<- as.data.frame(eugentest)
-eigen_first_reshuf[,]<- NA
-
-# eigen_first_reshuf<- as.data.frame(eigen_first_reshuf)
-
-# create empty storage for correlations
-cor_first_reshuf<- as.data.frame(cortest)
-cor_first_reshuf[,]<- NA
-# cor_first_reshuf<- as.data.frame(cor_first_reshuf)
-
-# now store group results/partials
-
-# res.mfa_bio_vs_self2_k2$group$correlation
-partials_first_reshuf <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
-partials_first_reshuf[,]<- NA
-partials_first_reshuf
-partials_first_reshuf$sim_no<- NA
-
-# hierarquical clustering
-clustering_new_pre_PCA3.1$ssid<- as.character(clustering_new_pre_PCA3.1$ssid)
-clustering_new_pre_PCA3.1$stimDescription<- as.character(clustering_new_pre_PCA3.1$stimDescription)
-# having clusters as factors causes a subscript oput of bound error
-
-# think we need to store groups
-
-groups_first_reshuf<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
-# res.mfa_bio_vs_self2_k2$group$correlation
-
-groups_first_reshuf[,]<- NA
-groups_first_reshuf
-groups_first_reshuf$sim_no<- NA
-
-#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
-
-for (i in 1:1000) {
-  message(sprintf("$$$$$RUNING sim %i", i))
-
-resampled_temp_reshuf<-    clustering_new_pre_PCA3.1_copy[,c(1,2,3, 5:9)] %>%
-  group_by(ssid)%>%
-  transform(pup_basCor = 
-              sample(pup_basCor, replace = F),
-            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = F),
-            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = F),
-            arousal = sample(arousal, replace = F),
-            valence = sample(valence, replace = F))
-
-  resampled_temp_reshuf$sim_no = i
-  # resampled_temp_reshuf$ssid_new <- as.factor(substr(resampled_temp_reshuf$stimDescription_unique,1,6))
-  # resampled_temp_reshuf$newstim <- substr(resampled_temp_reshuf$stimDescription_unique,7,30)
-  # resampled_temp_reshuf$stimDescription<- as.factor(resampled_temp_reshuf$stimDescription)
-
-# run PCA on the resampled data
-# ?list
-    message(sprintf("$$$$$fitting PCA %i", i))
-    mfa.res_reshuf <- FactoMineR::MFA(resampled_temp_reshuf[,c(1:8)], 
-               group = c(3, 3, 2), 
-               type = c("n", "s", "s"),
-              # ind.sup = c(1),
-              ncp = 2,
-               name.group = c("pp_stim","auton","subj"),
-               num.group.sup = c(1),
-               # ind.sup = c(1,2),
-               graph = FALSE)
-
-# store the eigen values
-message(sprintf("$$$$$storing PCA %i", i))
-eugentest_reshufl<- as.data.frame(mfa.res_reshuf$eig[1:2,])
-eugentest_reshufl$sim_no<- i
-
-cortest_reshufl<- as.data.frame(mfa.res_reshuf$quanti.var$cor)
-cortest_reshufl$sim_no = i
-
-partials_temp_reshuf<- as.data.frame(mfa.res_reshuf$partial.axes$cor)
-partials_temp_reshuf$sim_no = i
-
-# groups
-group_temp_reshuf<- as.data.frame(mfa.res_reshuf$group$cos2)
-group_temp_reshuf$sim_no = i
-
-# update the initial d=frames
-  message(sprintf("$$$$$upating dataframes %i", i))
-  resamp_1st_reshuf<- (bind_rows(resamp_1st_reshuf, resampled_temp_reshuf))
-eigen_first_reshuf<- bind_rows(eigen_first_reshuf, eugentest_reshufl)
-cor_first_reshuf<- bind_rows(cor_first_reshuf, cortest_reshufl)
-partials_first_reshuf<- bind_rows(partials_first_reshuf, partials_temp_reshuf)
-groups_first_reshuf<- bind_rows(groups_first_reshuf, group_temp_reshuf)
-  message(sprintf("$$$$$completed iteration%i", i))
-}
-
-```
+to see the reshufllfing for the hierarqucal data see separate script - paper_analyses_subj1
 
@@
 
-# cnames_resamp_subj<- names(resampled_temp_bysubj)
+cnames_resamp_subj<- names(resampled_temp_bysubj)
 colnames(resamp_1st_bysubj)<- cnames_resamp_subj
@@
 
-for (i in 1:1000) {
+for (i in 1:5000) {
   message(sprintf("$$$$$RUNING sim %i", i))
@@
 
-```{r}
-eigen_first_bysubj%>%
-  mutate(component =as.factor(substr(rownames(eigen_first_bysubj), 1,6)))%>% #retrieve names for components
-  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+   # gather(dimension, value_dimenion, -group, -sim_no) %>%
+  group_by(component)%>%
+  # subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
   mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
-         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
+  ungroup()%>%
+  mutate(eig_obs_dim = if_else(component == "comp 1", 
+                               res.mfa_bio_vs_self2_k2$eig[1],
+                               res.mfa_bio_vs_self2_k2$eig[2])) %>% #create 95% to descrive interval around the observed estimate
+  # also store observed eige for each dimensions
   # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
   ggplot(aes(eigenvalue))+
-  geom_histogram(alpha = .2)+
-    geom_density()+
+  geom_histogram(aes(y=..density..), alpha = .3) +  # scale histogram y
+  geom_density(col = "red", alpha = .001)+
   # facet_grid(~component)+
-    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
-  geom_point(x = res.mfa_agg_bysubj$eig[1],y = 10,size = 2, color = "red")+
+  geom_errorbar(aes(xmin = perc_5, xmax=perc_95, y = 1), color = "gray30")+
+  geom_point(aes(x = eig_obs_dim, y = 1),size = 2, color = "red", alpha = .3)+
 
   theme_classic()+
-  geom_vline(xintercept = 1, linetype = "dashed")
-  # ggtitle("distribution of boostraped eigen values for component  1 
-          # red dot = observed eigenvalue, boostrapped 95%CI")+
+  geom_vline(aes(xintercept = perc_5), linetype = "dashed")+
+    geom_vline(aes(xintercept = perc_95), linetype = "dashed")+
+
+  geom_hline(yintercept = 0, linetype = "dashed")+
+  facet_grid(~component)+
+  ggtitle("distribution of boostraped eigen values for components 
+          red dot = observed eigenvalue, boostrapped 95%CI")
   # annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")
 
+```{r}
+
 eigen_first_bysubj%>%
-  mutate(component =as.factor(substr(rownames(eigen_first_bysubj), 1,6)))%>% #retrieve names for components
-  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+   # gather(dimension, value_dimenion, -group, -sim_no) %>%
+  group_by(component)%>%
+  # subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
   mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
-         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
+  ungroup()%>%
+  mutate(eig_obs_dim = if_else(component == "comp 1", 
+                              res.mfa_agg_bysubj$eig[1],
+                              res.mfa_agg_bysubj$eig[2])) %>% #create 95% to descrive interval around the observed estimate
+  # also store observed eige for each dimensions
   # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
   ggplot(aes(eigenvalue))+
-  geom_histogram(alpha = .2)+
-    geom_density()+
+  geom_histogram(aes(y=..density..), alpha = .3) +  # scale histogram y
+  geom_density(col = "red", alpha = .001)+
   # facet_grid(~component)+
-    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
-  geom_point(x = res.mfa_agg_bysubj$eig[2],y = 10,size = 2, color = "red")+
+  geom_errorbar(aes(xmin = perc_5, xmax=perc_95, y = 1), color = "gray30")+
+  geom_point(aes(x = eig_obs_dim, y = 1),size = 2, color = "red", alpha = .3)+
 
   theme_classic()+
-  geom_vline(xintercept = 1, linetype = "dashed")
-
-```
-
+  geom_vline(aes(xintercept = perc_5), linetype = "dashed")+
+    geom_vline(aes(xintercept = perc_95), linetype = "dashed")+
+
+  geom_hline(yintercept = 0, linetype = "dashed")+
+  facet_grid(~component)
+  # annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")
+
+```
+
+res.mfa_agg_bysubj
 variables and dimension corelations
 ```{r}
-cor_first_bysubj %>%
-  mutate(variable = as.factor(substr(rownames(cor_first_bysubj), 1,6)))%>%
+res.mfa_agg_bysubj
+cor.test_obsmfa_bysubj<- as.data.frame(res.mfa_agg_bysubj$quanti.var$cor) %>%
+   mutate(variable = as.factor(substr(rownames(as.data.frame(res.mfa_agg_bysubj$quanti.var$cor)), 1,6)))%>%
+ gather(dimension, value_dimenion, -variable)
+
+cor_first_bysubj1<- cor_first_bysubj %>%
+  mutate(variable = as.factor(substr(rownames(cor_first), 1,6)))%>%
+    gather(dimension, value_dimenion, -variable, -sim_no) %>%
+  group_by(variable,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))
+
+left_join(cor_first_bysubj1, cor.test_obsmfa_bysubj, by = c("variable", "dimension")) %>%
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-2 ), color = "gray30")+
+  facet_grid(~dimension)+
+  geom_point(aes(x = value_dimenion.y, y = -2))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+  facet_grid(variable~dimension)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+
+  theme_classic()
+
+```
+much less consistent
+
+groups_first_obs<- as.data.frame(res.mfa_bio_vs_self2_k2$group$correlation) %>%
+   mutate(group = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$group$correlation)), 1,4)))%>%
+ gather(dimension, value_dimenion_obs,-group)
+
+res.mfa_bio_vs_self2_k2$group$correlation
+
+# we sgoudl probably store cos2 rather than correlatiopn
+# their cos2 values corresponding to their quality of representation on the factor map
+groups_first_1boot<- groups_first%>%
+  mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
+  gather(dimension, value_dimenion,-group,-sim_no)%>%
+  # -perc_5,-perc_95, 
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))
+
+?boot::boot.ci
+boot::boot.ci(groups_first_1boot$value_dimenion, type = "bca")[1]
+?bootBCa
+bootBCa(.5, groups_first_1boot$value_dimenion, n = 2600)[1]
+left_join(groups_first_1boot, groups_first_obs,by = c("group", "dimension"))%>%
+
+  ggplot(aes(value_dimenion)) +
+   geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-3 ), color = "gray30")+
+   geom_point(aes(x = value_dimenion_obs, y = -3))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+
+  facet_grid(dimension~group)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+```{r}
+
+groups_first_bysubj_obs<- as.data.frame(res.mfa_agg_bysubj$group$correlation) %>%
+   mutate(group = as.factor(substr(rownames(as.data.frame(res.mfa_agg_bysubj$group$correlation)), 1,4)))%>%
+ gather(dimension, value_dimenion_obs,-group)
+
+groups_first_bysubj_boot<- groups_first_bysubj%>%
+  mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
+  gather(dimension, value_dimenion,-group,-sim_no)
+  # -perc_5,-perc_95,
+
+left_join(groups_first_bysubj_boot, groups_first_bysubj_obs,by = c("group", "dimension"))%>%
+    group_by(group,dimension)%>%
+   mutate(perc_5 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 51)[1],
+         perc_95 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 51)[2])%>%
+
+  ggplot(aes(value_dimenion)) +
+   geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-1 ), color = "gray30")+
+   geom_point(aes(x = value_dimenion_obs, y = -1))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+
+  facet_grid(dimension~group)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+```
+
+resample agg by sbj
+
+```{r}
+colnames(resamp_1st_bysubj_reshuf)
+ # create emopty dataframe
+resamp_1st_bysubj_reshuf<- data.frame(matrix(NA, nrow = 1, ncol = 7))
+cnames_resamp_bysubj_reshuf<- names(resampled_temp_bysubj_reshuf)
+
+colnames(resamp_1st_bysubj_reshuf)<- cnames_resamp_bysubj_reshuf
+colnames(resamp_1st_bysubj_reshuf)
+# create emoty  storage rame for eigenvakues
+eigen_first_bysubj_reshuf<- as.data.frame(eugentest)
+eigen_first_bysubj_reshuf[,]<- NA
+
+# eigen_first_bysubj_reshuf<- as.data.frame(eigen_first_bysubj_reshuf)
+
+# create empty storage for correlations
+cor_first_bysubj_reshuf<- as.data.frame(cortest)
+cor_first_bysubj_reshuf[,]<- NA
+# cor_first_bysubj_reshuf<- as.data.frame(cor_first_bysubj_reshuf)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first_bysubj_reshuf <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first_bysubj_reshuf[,]<- NA
+partials_first_bysubj_reshuf
+partials_first_bysubj_reshuf$sim_no<- NA
+
+# hierarquical clustering
+clustering_new_pre_PCA3.1$ssid <- as.character(clustering_new_pre_PCA3.1$ssid)
+clustering_new_pre_PCA3.1$stimDescription<- as.character(clustering_new_pre_PCA3.1$stimDescription)
+# having clusters as factors causes a subscript oput of bound error
+
+# think we need to store groups
+
+groups_first_bysubj_reshuf<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first_bysubj_reshuf[,]<- NA
+groups_first_bysubj_reshuf
+groups_first_bysubj_reshuf$sim_no<- NA
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+
+for (i in 1:10000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+  # changed below to replace treue - shuflle with replacement
+  # https://stats.stackexchange.com/questions/104040/resampling-simulation-methods-monte-carlo-bootstrapping-jackknifing-cross?rq=1
+  # See the question on permutation vs bootstrapping - "The permutation test is best for testing hypotheses and bootstrapping is best for estimating confidence intervals".
+resampled_temp_bysubj_reshuf <- clustering_new_pre_PCA3.1.scale_agg_bysid %>%
+  # group_by(ssid)%>%
+  transform(pup_basCor = 
+              sample(pup_basCor, replace = FALSE),
+            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = FALSE),
+            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = FALSE),
+            arousal = sample(arousal, replace = FALSE),
+            valence = sample(valence, replace = FALSE))
+
+  resampled_temp_bysubj_reshuf$sim_no = i
+
+# run PCA on the resampled data
+# ?list
+  colnames(resampled_temp_bysubj_reshuf)
+    message(sprintf("$$$$$fitting PCA %i", i))
+    mfa.res_bysubj_reshuf <- FactoMineR::MFA(resampled_temp_bysubj_reshuf[,c(1:6)], 
+               group = c(1, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest_bysubj_reshufl<- as.data.frame(mfa.res_bysubj_reshuf$eig[1:2,])
+eugentest_bysubj_reshufl$sim_no<- i
+
+cortest_bysubj_reshufl<- as.data.frame(mfa.res_bysubj_reshuf$quanti.var$cor)
+cortest_bysubj_reshufl$sim_no = i
+
+partials_temp_bysubj_reshuf<- as.data.frame(mfa.res_bysubj_reshuf$partial.axes$cor)
+partials_temp_bysubj_reshuf$sim_no = i
+
+# groups
+group_temp_bysubj_reshuf<- as.data.frame(mfa.res_bysubj_reshuf$group$cos2)
+group_temp_bysubj_reshuf$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st_bysubj_reshuf<- (bind_rows(resamp_1st_bysubj_reshuf, resampled_temp_bysubj_reshuf))
+eigen_first_bysubj_reshuf<- bind_rows(eigen_first_bysubj_reshuf, eugentest_bysubj_reshufl)
+cor_first_bysubj_reshuf<- bind_rows(cor_first_bysubj_reshuf, cortest_bysubj_reshufl)
+partials_first_bysubj_reshuf<- bind_rows(partials_first_bysubj_reshuf, partials_temp_bysubj_reshuf)
+groups_first_bysubj_reshuf<- bind_rows(groups_first_bysubj_reshuf, group_temp_bysubj_reshuf)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+save.image("subjobjPCAfeb9.RData")
+
+```
+
+visualise resshufled null data
+
+```{r}
+
+eigen_first_bysubj_reshuf%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bysubj_reshuf), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue))%>% #select only component 1 and remove nas I introduced in the dataframe
+  group_by(component)%>%
+   mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
+  ungroup()%>%
+    group_by(component)%>%
+  mutate(eig_obs_dim = if_else(component == "comp 1", 
+                               res.mfa_agg_bysubj$eig[1],
+                               res.mfa_agg_bysubj$eig[2])) %>% #store observed to visualise ion the null
+  mutate(prob = paste(((sum(eigenvalue>=eig_obs_dim))/n())*100, paste0("%"))) %>%
+  ggplot(aes(eigenvalue))+
+  geom_histogram(aes(y=..density..),bins = 500, alpha = .3) +  # scale histogram y
+  geom_density(col = "red", alpha = .001)+
+  # facet_grid(~component)+
+    geom_vline(aes(xintercept = eig_obs_dim),size = 2, color = "red", linetype = "dashed", alpha = .3)+
+  geom_point(aes(x = eig_obs_dim, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+
+  theme_classic()+
+
+  # annotate(aes(text, label = prob))
+
+  theme_classic()+
+  facet_grid(~component)
+
+# component 1 is significant
+
+```
+
+```{r}
+
+colnames(cor_first_reshuf)
+cor_first_bysubj_reshuf1<- cor_first_bysubj_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_reshuf), 1,6)))%>%
+    gather(dimension, value_dimenion, -variable, -sim_no) %>%
+  group_by(variable,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
+  subset(!is.na(value_dimenion))
+
+# this mighgt have to do with the wrong test
+left_join(cor_first_bysubj_reshuf1, cor.test_obsmfa_bysubj, by = c("variable", "dimension")) %>%
+  group_by(variable,dimension)%>%
+     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
+   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
+  # the line above computes the probability that the correlation is more extreme (in magnitutde) thn the observed one
+
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+  # geom_point(aes(x = value_dimenion.y, y = -2))+
+    # geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+  facet_grid(variable~dimension)+
+   geom_vline(aes(xintercept = value_dimenion.y),size = 2, color = "red", linetype = "dashed", alpha = .3)+
+  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+
+  theme_classic()
+
+```
+
+```{r}
+partials_first_1_bysubj_obs<- as.data.frame(res.mfa_agg_bysubj$partial.axes$cor) %>%
+   mutate(dimension_partial = as.factor(substr(rownames(as.data.frame(res.mfa_agg_bysubj$partial.axes$cor)), 1,4)),
+           group = as.factor(substr(rownames(as.data.frame(res.mfa_agg_bysubj$partial.axes$cor)), 5,9)))%>%
+ gather(dimension, value_dimenion,-group,-dimension_partial)
+
+partials_first_bysubj_reshuf
+
+partials_first_bysubj_reshuf_1<- partials_first_bysubj_reshuf %>%
+  mutate(dimension_partial = as.factor(substr(rownames(partials_first_bysubj_reshuf), 1,4)),
+         group = as.factor(substr(rownames(partials_first_bysubj_reshuf), 5,9)))%>%
+   gather(dimension, value_dimenion, -group, -sim_no, -dimension_partial) %>%
+   group_by(dimension_partial,dimension,group)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
+  subset(!is.na(value_dimenion))
+
+left_join(partials_first_bysubj_reshuf_1,partials_first_1_bysubj_obs,by = c("dimension_partial", "group", "dimension")) %>%
+  group_by(dimension_partial,dimension, group)%>%
+   subset(!is.na(value_dimenion.x))%>%
+   # group_by(variable,dimension)%>%
+     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
+   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
+  subset(dimension_partial == "Dim1")%>%
+   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-1 ), color = "gray30")+
+  geom_vline(aes(xintercept = value_dimenion.y),size = 2, color = "red", linetype = "dashed", alpha = .3)+
+  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+  facet_grid(dimension~group)+
+
+  theme_classic()+
+  ggtitle("partial to dimension 1")
+
+left_join(partials_first_bysubj_reshuf_1,partials_first_1_bysubj_obs,by = c("dimension_partial", "group", "dimension")) %>%
+  group_by(dimension_partial,dimension, group)%>%
+     subset(!is.na(value_dimenion.x))%>%
+   # group_by(variable,dimension)%>%
+     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
+   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
+  subset(dimension_partial == "Dim2")%>%
+   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-1 ), color = "gray30")+
+  geom_vline(aes(xintercept = value_dimenion.y),size = 2, color = "red", linetype = "dashed", alpha = .3)+
+  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+  facet_grid(dimension~group)+
+
+  theme_classic()+
+  ggtitle("partial to dimension 2")
+
+```
+
+groups
+variables and dimension corelations
+
+```{r}
+
+cor_first_bysubj_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_reshuf), 1,6)))%>%
+    subset(!is.na(Dim.1)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+  ggplot(aes(Dim.1)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+
+  facet_grid(~variable)+
+  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+groups_first_bysubj_reshuf
+groups_first_bysubj_reshuf<- groups_first_bysubj_reshuf%>%
+  mutate(group = as.factor(substr(rownames(groups_first_reshuf), 1,4)))
+
+group_cordf_bysubj<- as.data.frame(res.mfa_agg_bysubj$group$correlation)
+group_cordf_bysubj$group<-as.factor(substr(rownames(group_cordf_bysubj), 1,4))
+
+group_cordf_bysubj1<- group_cordf_bysubj%>%
+gather(dimension, value_dimenion, - group)
+
+# View(groups_first_reshuf)
+groups_first_bysubj_reshuf1<- groups_first_bysubj_reshuf %>%
+  gather(dimension, value_dimenion, -group, -sim_no) %>%
+  subset(!is.na(value_dimenion))
+
+ left_join(groups_first_bysubj_reshuf1, group_cordf_bysubj1, c("group", "dimension"))%>%
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion.x,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion.x,.975, na.rm = TRUE))%>%
+     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
+   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
+
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(bins = 500)+
+
+  geom_density(alpha=.2) +
+  facet_grid(dimension~group)+
+     geom_vline(aes(xintercept = value_dimenion.y), linetype = "dashed", color = "red")+
+   # geom_vline(aes(xintercept = Dim.2.y),  linetype = "dashed", color = "blue")+
+  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+
+  theme_classic()
+
+res.mfa_bio_vs_self2_k2$group$correlation
+
+```
+
+Agg within participant by neg pos etc (using normative data)
+With and without selfreports
+```{r}
+clustering_new_pre_PCA3_val_vat_agg_scale
+```
+
+start with bootsrap to estimate CIS
+```{r}
+
+clustering_new_pre_PCA3_val_vat_agg_scale # this is the one I need
+colnames(clustering_new_pre_PCA3_val_vat_agg_scale)
+
+res.mfa_agg_bysubj_cat_val<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_agg_scale, 
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("sid","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = TRUE)
+
+colnames(resampled_temp_bysubj_cat_val)
+resamp_1st_bysubj_cat_val<- data.frame(matrix(NA, nrow = 1, ncol = 12))
+
+ cnames_resamp_subj1<- names(resampled_temp_bysubj_cat_val)
+colnames(resamp_1st_bysubj_cat_val)<- cnames_resamp_subj1
+colnames(resamp_1st_bysubj_cat_val)
+# create emoty  storage rame for eigenvakues
+eigen_first_bysubj_cat_val<- as.data.frame(eugentest)
+eigen_first_bysubj_cat_val[,]<- NA
+
+# eigen_first<- as.data.frame(eigen_first)
+
+# create empty storage for correlations
+cor_first_bysubj_cat_val<- as.data.frame(cortest)
+cor_first_bysubj_cat_val[,]<- NA
+# cor_first<- as.data.frame(cor_first)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first_bysubj_cat_val <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first_bysubj_cat_val[,]<- NA
+partials_first_bysubj_cat_val
+partials_first_bysubj_cat_val$sim_no<- NA
+
+# hierarquical clustering
+clustering_new_pre_PCA3.1.scale_agg_bysid$ssid<- as.character(clustering_new_pre_PCA3.1.scale_agg_bysid$ssid)
+# clustering_new_pre_PCA3.1.scale_agg_bysid$stimDescription<- as.character(clustering_new_pre_PCA3.1.scale_agg_bysid$stimDescription)
+
+# think we need to store groups
+
+groups_first_bysubj_cat_val<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first_bysubj_cat_val[,]<- NA
+groups_first_bysubj_cat_val
+groups_first_bysubj_cat_val$sim_no<- NA
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+colnames(clustering_new_pre_PCA3.1.scale_agg_bysid)
+library(fabricatr)
+
+clustering_new_pre_PCA3_val_vat_agg_scale$valence_iaps_cat<- as.character(clustering_new_pre_PCA3_val_vat_agg_scale$valence_iaps_cat)
+
+clustering_new_pre_PCA3_val_vat_agg_scale$ssid<- as.character(clustering_new_pre_PCA3_val_vat_agg_scale$ssid)
+nrow(clustering_new_pre_PCA3_val_vat_agg_scale)
+
+for (i in 1:5000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+
+  resampled_temp_bysubj_cat_val<- fabricatr::resample_data(clustering_new_pre_PCA3_val_vat_agg_scale, 
+                                  N = c(51,3),
+                                  ID_labels = c("ssid", "valence_iaps_cat"),
+                                  unique_labels = TRUE)
+  # View(resampled_temp_bysubj_cat_val)
+  resampled_temp_bysubj_cat_val$sim_no = i
+  resampled_temp_bysubj_cat_val$ssid_new <- as.factor(substr(resampled_temp_bysubj_cat_val$valence_iaps_cat_unique,1,6))
+  resampled_temp_bysubj_cat_val$newstim <- substr(resampled_temp_bysubj_cat_val$valence_iaps_cat_unique,7,9)
+
+# run PCA on the resampled data
+  # colnames(resampled_temp_bysubj_cat_val)
+    message(sprintf("$$$$$fitting PCA %i", i))
+    # colnames(resampled_temp_bysubj_cat_val[,c(11,12,3:7)])
+    mfa.res_bysubj_cat_val <- FactoMineR::MFA(resampled_temp_bysubj_cat_val[,c(11,12,3:7)], 
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("sid","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest_bysubj_cat_val<- as.data.frame(mfa.res_bysubj_cat_val$eig[1:2,])
+eugentest_bysubj_cat_val$sim_no<- i
+
+cortest_bysubj_cat_val<- as.data.frame(mfa.res_bysubj_cat_val$quanti.var$cor)
+cortest_bysubj_cat_val$sim_no = i
+
+partials_temp_bysubj_cat_val<- as.data.frame(mfa.res_bysubj_cat_val$partial.axes$cor)
+partials_temp_bysubj_cat_val$sim_no = i
+
+# groups
+group_temp_bysubj_cat_val<- as.data.frame(mfa.res_bysubj_cat_val$group$cos2)
+group_temp_bysubj_cat_val$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st_bysubj_cat_val<- (bind_rows(resamp_1st_bysubj_cat_val, resampled_temp_bysubj_cat_val))
+eigen_first_bysubj_cat_val<- bind_rows(eigen_first_bysubj_cat_val, eugentest_bysubj_cat_val)
+cor_first_bysubj_cat_val<- bind_rows(cor_first_bysubj_cat_val, cortest_bysubj_cat_val)
+partials_first_bysubj_cat_val<- bind_rows(partials_first_bysubj_cat_val, partials_temp_bysubj_cat_val)
+groups_first_bysubj_cat_val<- bind_rows(groups_first_bysubj_cat_val, group_temp_bysubj_cat_val)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+resamp_1st_bysubj
+View(resamp_1st_bysubj)
+
+resamp_1st_bysubj
+
+resamp_1st_bysubj%>%
+  subset(sim_no == 11)
+
+```
+
+Visualization of bootsrap for data agregate within particpant and neg mid anpos
+
+```{r}
+
+eigen_first_bysubj_cat_val%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+   # gather(dimension, value_dimenion, -group, -sim_no) %>%
+  group_by(component)%>%
+  # subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
+  ungroup()%>%
+  mutate(eig_obs_dim = if_else(component == "comp 1", 
+                              res.mfa_agg_bysubj_cat_val$eig[1],
+                              res.mfa_agg_bysubj_cat_val$eig[2])) %>% #create 95% to descrive interval around the observed estimate
+  # also store observed eige for each dimensions
+  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
+  ggplot(aes(eigenvalue))+
+  geom_histogram(aes(y=..density..), alpha = .3) +  # scale histogram y
+  geom_density(col = "red", alpha = .001)+
+  # facet_grid(~component)+
+  geom_errorbar(aes(xmin = perc_5, xmax=perc_95, y = 1), color = "gray30")+
+  geom_point(aes(x = eig_obs_dim, y = 1),size = 2, color = "red", alpha = .3)+
+
+  theme_classic()+
+  geom_vline(aes(xintercept = perc_5), linetype = "dashed")+
+    geom_vline(aes(xintercept = perc_95), linetype = "dashed")+
+
+  geom_hline(yintercept = 0, linetype = "dashed")+
+  facet_grid(~component)
+
+```
+
+variables and dimension correlations
+
+```{r}
+cor.test_obsmfa_bysubj_cat_val<- as.data.frame(res.mfa_agg_bysubj_cat_val$quanti.var$cor) %>%
+   mutate(variable = as.factor(substr(rownames(as.data.frame(res.mfa_agg_bysubj_cat_val$quanti.var$cor)), 1,6)))%>%
+ gather(dimension, value_dimenion, -variable)
+
+cor_first_bysubj_cat_val1<- cor_first_bysubj_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_cat_val), 1,6)))%>%
+    gather(dimension, value_dimenion, -variable, -sim_no) %>%
+  group_by(variable,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))
+
+left_join(cor_first_bysubj_cat_val1, cor.test_obsmfa_bysubj_cat_val, by = c("variable", "dimension")) %>%
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-2 ), color = "gray30")+
+  facet_grid(~dimension)+
+  geom_point(aes(x = value_dimenion.y, y = -2))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+  facet_grid(variable~dimension)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+
+  theme_classic()
+
+cor_first_bysubj_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_cat_val), 1,6)))%>%
     subset(!is.na(Dim.1)) %>%
@@
 
-```
-Agg within participant by neg pos etc (using normative data)
-With and without selfreports
-
-```{r}
-?cut
-#create valence categories based ion self reports (IAPS validation)
-clustering_new_pre_PCA3_val_vat<- clustering_new_pre_PCA3%>%
-  mutate(valence_iaps_cat = cut(ValenceMean,3, labels = c("neg", "mid", "pos")))
-
-# scale within subject
-# aggregate by subject and
-
-View(clustering_new_pre_PCA3_val_vat)
-# clustering_new_pre_PCA3_val_vat%>%
-#   group_by(ssid)%>%
-#   mutate_if(is.numeric, scale)
-
-clustering_new_pre_PCA3_val_vat_agg<- clustering_new_pre_PCA3_val_vat%>%
-  group_by(ssid, valence_iaps_cat)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)
-
-library(factoextra)
-library(FactoMineR)
-
-colnames(clustering_new_pre_PCA3_val_vat_agg)
-clustering_new_pre_PCA3_val_vat_agg[,c(2,5,6,7,8,9)]
-
-FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_agg[,c(1,2,5,6,7,8,9)], 
+cor_first_bysubj_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_cat_val), 1,6)))%>%
+    subset(!is.na(Dim.2)) %>%
+  # create interval per variable
+  group_by(variable)%>%
+   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  # subset(variable == "arousa"|variable == "valenc")%>%
+  # select(c("arousal", "valence"))%>%
+  ggplot(aes(Dim.2)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
+  facet_grid(~variable)+
+  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+# much less conistent
+
+clustering_new_pre_PCA3.1.scale_agg_bystim
+# FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_agg[
+clustering_new_pre_PCA3_val_vat_scale_then_agg1
+
+clustering_new_pre_PCA3_val_vat_agg_scale
+
+```
+
+resample for significance testing
+
+```{r}
+colnames(resamp_1st_bysubj_reshuf_cat_val)
+ # create emopty dataframe
+resamp_1st_bysubj_reshuf_cat_val<- data.frame(matrix(NA, nrow = 1, ncol = 8))
+cnames_resamp_bysubj_reshuf_cat_val<- names(resampled_temp_bysubj_reshuf_cat_val)
+
+colnames(resamp_1st_bysubj_reshuf_cat_val)<- cnames_resamp_bysubj_reshuf_cat_val
+colnames(resamp_1st_bysubj_reshuf_cat_val)
+# create emoty  storage rame for eigenvakues
+eigen_first_bysubj_reshuf_cat_val<- as.data.frame(eugentest)
+eigen_first_bysubj_reshuf_cat_val[,]<- NA
+
+# eigen_first_bysubj_reshuf_cat_val<- as.data.frame(eigen_first_bysubj_reshuf_cat_val)
+
+# create empty storage for correlations
+cor_first_bysubj_reshuf_cat_val<- as.data.frame(cortest)
+cor_first_bysubj_reshuf_cat_val[,]<- NA
+# cor_first_bysubj_reshuf_cat_val<- as.data.frame(cor_first_bysubj_reshuf_cat_val)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first_bysubj_reshuf_cat_val <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first_bysubj_reshuf_cat_val[,]<- NA
+partials_first_bysubj_reshuf_cat_val
+partials_first_bysubj_reshuf_cat_val$sim_no<- NA
+
+# think we need to store groups
+
+groups_first_bysubj_reshuf_cat_val<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first_bysubj_reshuf_cat_val[,]<- NA
+groups_first_bysubj_reshuf_cat_val
+groups_first_bysubj_reshuf_cat_val$sim_no<- NA
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+?sample
+
+# permutations should be withouth replacement
+for (i in 1:5000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+  # changed below to replace treue - shuflle with replacement
+  # https://stats.stackexchange.com/questions/104040/resampling-simulation-methods-monte-carlo-bootstrapping-jackknifing-cross?rq=1
+  # See the question on permutation vs bootstrapping - "The permutation test is best for testing hypotheses and bootstrapping is best for estimating confidence intervals".
+  colnames(clustering_new_pre_PCA3_val_vat_agg_scale)
+resampled_temp_bysubj_reshuf_cat_val <- clustering_new_pre_PCA3_val_vat_agg_scale %>%
+  group_by(ssid)%>%
+  transform(pup_basCor = 
+              sample(pup_basCor, replace = FALSE),
+            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = FALSE),
+            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = FALSE),
+            arousal = sample(arousal, replace = FALSE),
+            valence = sample(valence, replace = FALSE))
+
+  resampled_temp_bysubj_reshuf_cat_val$sim_no = i
+
+# run PCA on the resampled data
+# ?list
+  # colnames(resampled_temp_bysubj_reshuf_cat_val)
+    message(sprintf("$$$$$fitting PCA %i", i))
+    mfa.res_bysubj_reshuf_cat_val <- FactoMineR::MFA(resampled_temp_bysubj_reshuf_cat_val[,c(1:7)], 
+               group = c(2, 3, 2), 
+               type = c("n", "s", "s"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("pp_stim","auton","subj"),
+               num.group.sup = c(1),
+               # ind.sup = c(1,2),
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest_bysubj_reshuf_cat_vall<- as.data.frame(mfa.res_bysubj_reshuf_cat_val$eig[1:2,])
+eugentest_bysubj_reshuf_cat_vall$sim_no<- i
+
+cortest_bysubj_reshuf_cat_vall<- as.data.frame(mfa.res_bysubj_reshuf_cat_val$quanti.var$cor)
+cortest_bysubj_reshuf_cat_vall$sim_no = i
+
+partials_temp_bysubj_reshuf_cat_val<- as.data.frame(mfa.res_bysubj_reshuf_cat_val$partial.axes$cor)
+partials_temp_bysubj_reshuf_cat_val$sim_no = i
+
+# groups
+group_temp_bysubj_reshuf_cat_val<- as.data.frame(mfa.res_bysubj_reshuf_cat_val$group$cos2)
+group_temp_bysubj_reshuf_cat_val$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st_bysubj_reshuf_cat_val<- (bind_rows(resamp_1st_bysubj_reshuf_cat_val, resampled_temp_bysubj_reshuf_cat_val))
+eigen_first_bysubj_reshuf_cat_val<- bind_rows(eigen_first_bysubj_reshuf_cat_val, eugentest_bysubj_reshuf_cat_vall)
+cor_first_bysubj_reshuf_cat_val<- bind_rows(cor_first_bysubj_reshuf_cat_val, cortest_bysubj_reshuf_cat_vall)
+partials_first_bysubj_reshuf_cat_val<- bind_rows(partials_first_bysubj_reshuf_cat_val, partials_temp_bysubj_reshuf_cat_val)
+groups_first_bysubj_reshuf_cat_val<- bind_rows(groups_first_bysubj_reshuf_cat_val, group_temp_bysubj_reshuf_cat_val)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+save.image("subjobjPCAfeb93.RData")
+
+```
+
+<!-- visualisae permutation tests -->
+
+```{r}
+
+eigen_first_bysubj_reshuf_cat_val%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bysubj_reshuf_cat_val), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue))%>% #select only component 1 and remove nas I introduced in the dataframe
+  group_by(component)%>%
+   mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
+  ungroup()%>%
+    group_by(component)%>%
+  mutate(eig_obs_dim = if_else(component == "comp 1", 
+                               res.mfa_agg_bysubj_cat_val$eig[1],#always update these two lines
+                               res.mfa_agg_bysubj_cat_val$eig[2])) %>% #store observed to visualise ion the null
+  mutate(prob = paste(((sum(eigenvalue>=eig_obs_dim))/n())*100, paste0("%"))) %>%
+  ggplot(aes(eigenvalue))+
+  geom_histogram(aes(y=..density..),bins = 500, alpha = .3) +  # scale histogram y
+  geom_density(col = "red", alpha = .001)+
+  # facet_grid(~component)+
+    geom_vline(aes(xintercept = eig_obs_dim),size = 2, color = "red", linetype = "dashed", alpha = .3)+
+  geom_point(aes(x = eig_obs_dim, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+
+  theme_classic()+
+
+  # annotate(aes(text, label = prob))
+
+  theme_classic()+
+  facet_grid(~component)
+
+```
+
+correlation btween variables and dimensions
+
+```{r}
+res.mfa_agg_bysubj$quanti.var$cor
+
+colnames(cor_first_reshuf)
+cor_first_bysubj_reshuf_cat_val1<- cor_first_bysubj_reshuf_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bysubj_reshuf_cat_val), 1,6)))%>%
+    gather(dimension, value_dimenion, -variable, -sim_no) %>%
+  group_by(variable,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
+  subset(!is.na(value_dimenion))
+
+# this mighgt have to do with the wrong test
+left_join(cor_first_bysubj_reshuf_cat_val1, cor.test_obsmfa_bysubj_cat_val, by = c("variable", "dimension")) %>%
+  group_by(variable,dimension)%>%
+     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
+   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
+  # the line above computes the probability that the correlation is more extreme (in magnitutde) thn the observed one
+
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+  # geom_point(aes(x = value_dimenion.y, y = -2))+
+    # geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+  facet_grid(variable~dimension)+
+   geom_vline(aes(xintercept = value_dimenion.y),size = 2, color = "red", linetype = "dashed", alpha = .3)+
+  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+
+  theme_classic()
+
+```
+groups
+
+```{r}
+
+groups_first_bysubj_reshuf_cat_val
+groups_first_bysubj_reshuf_cat_val<- groups_first_bysubj_reshuf_cat_val%>%
+  mutate(group = as.factor(substr(rownames(groups_first_bysubj_reshuf_cat_val), 1,4)))
+
+group_cordf_bysubj_cat_val_obs<- as.data.frame(res.mfa_agg_bysubj_cat_val$group$correlation)
+group_cordf_bysubj_cat_val_obs$group<-as.factor(substr(rownames(group_cordf_bysubj_cat_val_obs), 1,4))
+
+group_cordf_bysubj_cat_val_obs1<- group_cordf_bysubj_cat_val_obs%>%
+gather(dimension, value_dimenion, - group)
+
+# View(groups_first_reshuf)
+groups_first_bysubj_reshuf_cat_val1<- groups_first_bysubj_reshuf_cat_val %>%
+  gather(dimension, value_dimenion, -group, -sim_no) %>%
+  subset(!is.na(value_dimenion))
+
+ left_join(groups_first_bysubj_reshuf_cat_val1, group_cordf_bysubj_cat_val_obs1, c("group", "dimension"))%>%
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion.x,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion.x,.975, na.rm = TRUE))%>%
+     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
+   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
+
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(bins = 500)+
+
+  geom_density(alpha=.2) +
+  facet_grid(dimension~group)+
+     geom_vline(aes(xintercept = value_dimenion.y), linetype = "dashed", color = "red")+
+   # geom_vline(aes(xintercept = Dim.2.y),  linetype = "dashed", color = "blue")+
+  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+
+  theme_classic()
+
+```
+
+<!-- agg by stim -->
+
+```{r}
+colnames(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg)
+
+res.mfa_agg_stim<- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg, 
                group = c(2, 3, 2), 
@@
                # "s", "s", "s"
-               name.group = c("ss_id_stim","auton","subj"),
+               name.group = c("stim_cat","auton","subj"),
                num.group.sup = c(1),
@@
 
-# scale
-clustering_new_pre_PCA3_val_vat_agg_scale<- clustering_new_pre_PCA3_val_vat_agg[,c(1,2,5,6,7,8,9)]
-
-clustering_new_pre_PCA3_val_vat_agg_scale%>%
-   # group_by(ssid)%>%
-  mutate_if(is.numeric, scale)
-
-clustering_new_pre_PCA3_val_vat_scale_then_agg<- clustering_new_pre_PCA3_val_vat%>%
-  group_by(ssid)%>%
-  mutate_if(is.numeric, scale)%>%
-  group_by(ssid, valence_iaps_cat)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)
-
-clustering_new_pre_PCA3_val_vat_scale_then_agg1<- clustering_new_pre_PCA3_val_vat_scale_then_agg[,c(1:2, 5:9)]
-
-?FactoMineR::MFA
-res.mfa_val_cat_scal<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_scale_then_agg1,
+```
+
+boostrap
+```{r}
+
+clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg # this is the one I need
+colnames(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg)
+
+colnames(resampled_temp_bystim_cat_val)
+resamp_1st_bystim_cat_val<- data.frame(matrix(NA, nrow = 1, ncol = 10))
+
+cnames_resamp_subj<- names(resampled_temp_bystim_cat_val)
+colnames(resamp_1st_bystim_cat_val)<- cnames_resamp_subj
+colnames(resamp_1st_bystim_cat_val)
+# create emoty  storage rame for eigenvakues
+eigen_first_bystim_cat_val<- as.data.frame(eugentest)
+eigen_first_bystim_cat_val[,]<- NA
+
+# eigen_first<- as.data.frame(eigen_first)
+
+# create empty storage for correlations
+cor_first_bystim_cat_val<- as.data.frame(cortest)
+cor_first_bystim_cat_val[,]<- NA
+# cor_first<- as.data.frame(cor_first)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first_bystim_cat_val <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first_bystim_cat_val[,]<- NA
+partials_first_bystim_cat_val
+partials_first_bystim_cat_val$sim_no<- NA
+
+# hierarquical clustering
+clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$stimDescription <- as.character(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$stimDescription)
+clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$val_cut_iaps <- as.character(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$val_cut_iaps)
+
+# think we need to store groups
+
+groups_first_bystim_cat_val<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first_bystim_cat_val[,]<- NA
+groups_first_bystim_cat_val
+groups_first_bystim_cat_val$sim_no<- NA
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+
+library(fabricatr)
+
+for (i in 1:5000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+
+  resampled_temp_bystim_cat_val<- fabricatr::resample_data(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg, 
+                                  N = c(53),
+                                  ID_labels = c("stimDescription"),
+                                  unique_labels = TRUE)
+  # View(resampled_temp_bystim_cat_val)
+  resampled_temp_bystim_cat_val$sim_no = i
+  resampled_temp_bystim_cat_val$stimDescription_new <- as.factor(substr(resampled_temp_bystim_cat_val$stimDescription_unique,1,3))
+
+# run PCA on the resampled data
+  # colnames(resampled_temp_bystim_cat_val)
+    message(sprintf("$$$$$fitting PCA %i", i))
+    # colnames(resampled_temp_bystim_cat_val[,c(10,2:7)])
+    mfa.res_bystim_cat_val <- FactoMineR::MFA(resampled_temp_bystim_cat_val[,c(10,2:7)], 
                group = c(2, 3, 2), 
                type = c("n", "s", "s"),
-               name.group = c("ss_id_stim","auton","subj"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("stimid_cat","auton","subj"),
                num.group.sup = c(1),
                # ind.sup = c(1,2),
-               graph = TRUE)
-
-?FactoMineR::MFA
-View(res.mfa_val_cat_scal)
-
-# force k = 2
-
-res.mfa_val_cat_scal_k2<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_scale_then_agg1,
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest_bystim_cat_val<- as.data.frame(mfa.res_bystim_cat_val$eig[1:2,])
+eugentest_bystim_cat_val$sim_no<- i
+
+cortest_bystim_cat_val<- as.data.frame(mfa.res_bystim_cat_val$quanti.var$cor)
+cortest_bystim_cat_val$sim_no = i
+
+partials_temp_bystim_cat_val<- as.data.frame(mfa.res_bystim_cat_val$partial.axes$cor)
+partials_temp_bystim_cat_val$sim_no = i
+
+# groups
+group_temp_bystim_cat_val<- as.data.frame(mfa.res_bystim_cat_val$group$cos2)
+group_temp_bystim_cat_val$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st_bystim_cat_val<- (bind_rows(resamp_1st_bystim_cat_val, resampled_temp_bystim_cat_val))
+eigen_first_bystim_cat_val<- bind_rows(eigen_first_bystim_cat_val, eugentest_bystim_cat_val)
+cor_first_bystim_cat_val<- bind_rows(cor_first_bystim_cat_val, cortest_bystim_cat_val)
+partials_first_bystim_cat_val<- bind_rows(partials_first_bystim_cat_val, partials_temp_bystim_cat_val)
+groups_first_bystim_cat_val<- bind_rows(groups_first_bystim_cat_val, group_temp_bystim_cat_val)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
+
+#################################
+# note i have not checked the rsults from above
+
+```
+
+visualise CIS boots
+
+```{r}
+
+eigen_first_bystim_cat_val%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bystim_cat_val), 1,6)))%>% #retrieve names for components
+   # gather(dimension, value_dimenion, -group, -sim_no) %>%
+  group_by(component)%>%
+  # subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
+  ungroup()%>%
+  mutate(eig_obs_dim = if_else(component == "comp 1", 
+                              res.mfa_agg_stim $eig[1],
+                              res.mfa_agg_stim$eig[2])) %>% #create 95% to descrive interval around the observed estimate
+  # also store observed eige for each dimensions
+  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
+  ggplot(aes(eigenvalue))+
+  geom_histogram(aes(y=..density..), alpha = .3) +  # scale histogram y
+  geom_density(col = "red", alpha = .001)+
+  # facet_grid(~component)+
+  geom_errorbar(aes(xmin = perc_5, xmax=perc_95, y = 1), color = "gray30")+
+  geom_point(aes(x = eig_obs_dim, y = 1),size = 2, color = "red", alpha = .3)+
+
+  theme_classic()+
+  geom_vline(aes(xintercept = perc_5), linetype = "dashed")+
+    geom_vline(aes(xintercept = perc_95), linetype = "dashed")+
+
+  geom_hline(yintercept = 0, linetype = "dashed")+
+  facet_grid(~component)
+  # annotate("text", x = 1
+
+```
+
+correlation variables dimensions
+
+```{r}
+cor.test_obsmfa_bystim_cat_val<- as.data.frame(res.mfa_agg_stim$quanti.var$cor) %>%
+   mutate(variable = as.factor(substr(rownames(as.data.frame(res.mfa_agg_stim$quanti.var$cor)), 1,6)))%>%
+ gather(dimension, value_dimenion, -variable)
+
+cor_first_bystim_cat_val1<- cor_first_bystim_cat_val %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bystim_cat_val), 1,6)))%>%
+    gather(dimension, value_dimenion, -variable, -sim_no) %>%
+  group_by(variable,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))
+
+left_join(cor_first_bystim_cat_val1, cor.test_obsmfa_bystim_cat_val, by = c("variable", "dimension")) %>%
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-2 ), color = "gray30")+
+  facet_grid(~dimension)+
+  geom_point(aes(x = value_dimenion.y, y = -2))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+  facet_grid(variable~dimension)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+
+  theme_classic()
+
+```
+
+groups
+
+```{r}
+
+groups_first_bystim_obs<- as.data.frame(res.mfa_agg_stim$group$correlation) %>%
+   mutate(group = as.factor(substr(rownames(as.data.frame(res.mfa_agg_stim$group$correlation)), 1,4)))%>%
+ gather(dimension, value_dimenion_obs,-group)
+
+groups_first_bystim_cat_val_boot<- groups_first_bystim_cat_val%>%
+  mutate(group = as.factor(substr(rownames(groups_first_bystim_cat_val), 1,4)))%>%
+  gather(dimension, value_dimenion,-group,-sim_no)
+  # -perc_5,-perc_95,
+
+left_join(groups_first_bystim_cat_val_boot, groups_first_bystim_obs,by = c("group", "dimension"))%>%
+    group_by(group,dimension)%>%
+   mutate(perc_5 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 51)[1],
+         perc_95 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 51)[2])%>%
+
+  ggplot(aes(value_dimenion)) +
+   geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-1 ), color = "gray30")+
+   geom_point(aes(x = value_dimenion_obs, y = -1))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+
+  facet_grid(dimension~group)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+```
+
+resdshufle stim
+```{r}
+colnames(resampled_temp_bystimj_reshuf)
+# create emopty dataframe
+resamp_1st_bystimj_reshuf<- data.frame(matrix(NA, nrow = 1, ncol = 8))
+cnames_resamp_bystimj_reshuf<- names(resampled_temp_bystimj_reshuf)
+
+colnames(resamp_1st_bystimj_reshuf)<- cnames_resamp_bystimj_reshuf
+colnames(resamp_1st_bystimj_reshuf)
+# create emoty  storage rame for eigenvakues
+eigen_first_bystimj_reshuf<- as.data.frame(eugentest)
+eigen_first_bystimj_reshuf[,]<- NA
+
+# eigen_first_bystimj_reshuf<- as.data.frame(eigen_first_bystimj_reshuf)
+
+# create empty storage for correlations
+cor_first_bystimj_reshuf<- as.data.frame(cortest)
+cor_first_bystimj_reshuf[,]<- NA
+# cor_first_bystimj_reshuf<- as.data.frame(cor_first_bystimj_reshuf)
+
+# now store group results/partials
+
+# res.mfa_bio_vs_self2_k2$group$correlation
+partials_first_bystimj_reshuf <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
+partials_first_bystimj_reshuf[,]<- NA
+partials_first_bystimj_reshuf
+partials_first_bystimj_reshuf$sim_no<- NA
+
+clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$stimDescription<- as.character(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg$stimDescription)
+# having clusters as factors causes a subscript oput of bound error
+
+# think we need to store groups
+
+groups_first_bystimj_reshuf<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
+# res.mfa_bio_vs_self2_k2$group$correlation
+
+groups_first_bystimj_reshuf[,]<- NA
+groups_first_bystimj_reshuf
+groups_first_bystimj_reshuf$sim_no<- NA
+
+#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
+
+for (i in 1:10000) {
+  message(sprintf("$$$$$RUNING sim %i", i))
+  # changed below to replace treue - shuflle with replacement
+  # https://stats.stackexchange.com/questions/104040/resampling-simulation-methods-monte-carlo-bootstrapping-jackknifing-cross?rq=1
+  # See the question on permutation vs bootstrapping - "The permutation test is best for testing hypotheses and bootstrapping is best for estimating confidence intervals".
+resampled_temp_bystimj_reshuf <- clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg %>%
+  # group_by(ssid)%>%
+  transform(pup_basCor = 
+            sample(pup_basCor, replace = FALSE),
+            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = FALSE),
+            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = FALSE),
+            arousal = sample(arousal, replace = FALSE),
+            valence = sample(valence, replace = FALSE))
+
+# View(resampled_temp_bystimj_reshuf)
+  resampled_temp_bystimj_reshuf$sim_no = i
+
+# run PCA on the resampled data
+# ?list
+  # colnames(resampled_temp_bystimj_reshuf)
+    message(sprintf("$$$$$fitting PCA %i", i))
+    mfa.res_bystimj_reshuf <- FactoMineR::MFA(resampled_temp_bystimj_reshuf[,c(1:7)], 
                group = c(2, 3, 2), 
                type = c("n", "s", "s"),
-               name.group = c("ss_id_stim","auton","subj"),
+              # ind.sup = c(1),
+              ncp = 2,
+               name.group = c("stim_cat","auton","subj"),
                num.group.sup = c(1),
-               ncp = 2,
                # ind.sup = c(1,2),
-               graph = TRUE)
-
-res.mfa_val_cat_scal_k2$eig
-
-```
-
-```{r}
-
-fviz_mfa_ind(res.mfa_val_cat_scal, 
-             habillage = "valence_iaps_cat", # color by groups 
-             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, 
-             ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-# we can sorta see that while things allign relativelly well on sujective dimension, they don't allugn very well on the autonomic dimension
+               graph = FALSE)
+
+# store the eigen values
+message(sprintf("$$$$$storing PCA %i", i))
+eugentest_bystimj_reshufl<- as.data.frame(mfa.res_bystimj_reshuf$eig[1:2,])
+eugentest_bystimj_reshufl$sim_no<- i
+
+cortest_bystimj_reshufl<- as.data.frame(mfa.res_bystimj_reshuf$quanti.var$cor)
+cortest_bystimj_reshufl$sim_no = i
+
+partials_temp_bystimj_reshuf<- as.data.frame(mfa.res_bystimj_reshuf$partial.axes$cor)
+partials_temp_bystimj_reshuf$sim_no = i
+
+# groups
+group_temp_bystimj_reshuf<- as.data.frame(mfa.res_bystimj_reshuf$group$cos2)
+group_temp_bystimj_reshuf$sim_no = i
+
+# update the initial d=frames
+  message(sprintf("$$$$$upating dataframes %i", i))
+  resamp_1st_bystimj_reshuf<- (bind_rows(resamp_1st_bystimj_reshuf, resampled_temp_bystimj_reshuf))
+eigen_first_bystimj_reshuf<- bind_rows(eigen_first_bystimj_reshuf, eugentest_bystimj_reshufl)
+cor_first_bystimj_reshuf<- bind_rows(cor_first_bystimj_reshuf, cortest_bystimj_reshufl)
+partials_first_bystimj_reshuf<- bind_rows(partials_first_bystimj_reshuf, partials_temp_bystimj_reshuf)
+groups_first_bystimj_reshuf<- bind_rows(groups_first_bystimj_reshuf, group_temp_bystimj_reshuf)
+  message(sprintf("$$$$$completed iteration%i", i))
+}
 
 save.image("subjobjPCAfeb9.RData")
-```
+
+```
+
+visualise pernuation on stim MFA
+
+```{r}
+
+eigen_first_bystimj_reshuf%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_bystimj_reshuf), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue))%>% #select only component 1 and remove nas I introduced in the dataframe
+  group_by(component)%>%
+   mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
+  ungroup()%>%
+    group_by(component)%>%
+  mutate(eig_obs_dim = if_else(component == "comp 1", 
+                               res.mfa_agg_stim$eig[1],
+                               res.mfa_agg_stim$eig[2])) %>% #store observed to visualise ion the null
+  mutate(prob = paste(((sum(eigenvalue>=eig_obs_dim))/n())*100, paste0("%"))) %>%
+  ggplot(aes(eigenvalue))+
+  geom_histogram(aes(y=..density..),bins = 500, alpha = .3) +  # scale histogram y
+  geom_density(col = "red", alpha = .001)+
+  # facet_grid(~component)+
+    geom_vline(aes(xintercept = eig_obs_dim),size = 2, color = "red", linetype = "dashed", alpha = .3)+
+  geom_point(aes(x = eig_obs_dim, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+
+  theme_classic()+
+
+  # annotate(aes(text, label = prob))
+
+  theme_classic()+
+  facet_grid(~component)
+
+```
+
+significance variable and dimensions
+
+```{r}
+res.mfa_agg_bysubj$quanti.var$cor
+cor_first_bystimj_reshuf
+
+colnames(cor_first_reshuf)
+cor_first_bystimj_reshuf_cat_val1<- cor_first_bystimj_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_bystimj_reshuf), 1,6)))%>%
+    gather(dimension, value_dimenion, -variable, -sim_no) %>%
+  group_by(variable,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
+  subset(!is.na(value_dimenion))
+
+# this mighgt have to do with the wrong test
+left_join(cor_first_bystimj_reshuf_cat_val1, cor.test_obsmfa_bystim_cat_val, by = c("variable", "dimension")) %>%
+  group_by(variable,dimension)%>%
+     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
+   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
+  # the line above computes the probability that the correlation is more extreme (in magnitutde) thn the observed one
+
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+  # geom_point(aes(x = value_dimenion.y, y = -2))+
+    # geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+  facet_grid(variable~dimension)+
+   geom_vline(aes(xintercept = value_dimenion.y),size = 2, color = "red", linetype = "dashed", alpha = .3)+
+  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+
+  theme_classic()
+
+```
+
+groups
+```{r}
+
+groups_first_bystimj_reshuf
+groups_first_bystimj_reshuf<- groups_first_bystimj_reshuf%>%
+  mutate(group = as.factor(substr(rownames(groups_first_bystimj_reshuf), 1,4)))
+
+group_cordf_bystim_cat_val_obs<- as.data.frame(res.mfa_agg_stim$group$correlation)
+group_cordf_bystim_cat_val_obs$group<-as.factor(substr(rownames(group_cordf_bystim_cat_val_obs), 1,4))
+
+group_cordf_bystim_cat_val_obs1<- group_cordf_bystim_cat_val_obs%>%
+gather(dimension, value_dimenion, - group)
+
+# View(groups_first_reshuf)
+groups_first_bystimj_reshuf1<- groups_first_bystimj_reshuf %>%
+  gather(dimension, value_dimenion, -group, -sim_no) %>%
+  subset(!is.na(value_dimenion))
+
+ left_join(groups_first_bystimj_reshuf1, group_cordf_bystim_cat_val_obs1, c("group", "dimension"))%>%
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion.x,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion.x,.975, na.rm = TRUE))%>%
+     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
+   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
+
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(bins = 500)+
+
+  geom_density(alpha=.2) +
+  facet_grid(dimension~group)+
+     geom_vline(aes(xintercept = value_dimenion.y), linetype = "dashed", color = "red")+
+   # geom_vline(aes(xintercept = Dim.2.y),  linetype = "dashed", color = "blue")+
+  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+
+  theme_classic()
+
+```

### 2022-03-03 FactoShyny.Rmd
tracking latests changes
forgot to track these for a bit

---
title: "Tryfactoshyny"
author: "Helio"
date: "15/02/2022"
output: html_document
---

```{r}
install.packages("Factoshiny")

library(Fact)

View(clustering_new_pre_PCA3.1)

Factoshiny::MFAshiny(clustering_new_pre_PCA3.1)

clustering_new_pre_PCA3.1.scale

clustering_new_pre_PCA3.1.scale$ssid<- as.factor(clustering_new_pre_PCA3.1.scale$ssid)
clustering_new_pre_PCA3.1$ssid<- as.factor(clustering_new_pre_PCA3.1.scale$ssid)
Factoshiny::MFAshiny(clustering_new_pre_PCA3.1.scale)

Factoshiny::MFAshiny(clustering_new_pre_PCA3.1.scale_agg_bystim)

Factoshiny::MFAshiny(clustering_new_pre_PCA3.1.scale_agg_bystim_scaleafteragg)

# just agg by ssid
clustering_new_pre_PCA3.1.scale_agg_bysid
Factoshiny::MFAshiny(clustering_new_pre_PCA3.1.scale_agg_bysid)
clustering_new_pre_PCA3.1.scale_aft_agg_bysid
clustering_new_pre_PCA3.1_copy

# group_by(ssid, val_cut_iaps
         # clustering_new_pre_PCA3.1

clustering_new_pre_PCA_2_agg_by_val_sel$ssid<- as.factor(clustering_new_pre_PCA_2_agg_by_val_sel$ssid)
# clustering_new_pre_PCA_2_agg_by_val_sel
Factoshiny::MFAshiny(clustering_new_pre_PCA_2_agg_by_val_sel1)

clustering_new_pre_PCA_2_agg_by_val_sel1<- clustering_new_pre_PCA_2_agg_by_val_sel%>%
  subset(!is.na(valence_split))
```

### 2022-03-03 Paper_Analyses_subj_obje_arousal.Rmd
tracking latests changes
forgot to track these for a bit

--- 2022-02-09 Paper_Analyses_subj_obje_arousal.Rmd
@@
                                        critical.value = 2)
+InPosition::epCA.inference.battery()
 
@@
   mutate(perc_5 = quantile(`percentage of variance`,.025, na.rm = TRUE),
-         perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE))%>%
+         perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE)) %>%
   ggplot(aes(`percentage of variance`))+
@@
   theme_classic()
+
+eigen_first%>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
+    group_by(component)%>%
+  # subset(!is.na(`percentage of variance`) & component == "comp 1" )%>%
+  mutate(perc_5 = quantile(`percentage of variance`,.025, na.rm = TRUE),
+         perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE))%>%
+  group_by(component)%>%
+  summarise_if(is.numeric, mean)
 
@@
 
+  groups_first
+
+  res.MFA_stim_val_scale$group$contrib
+  res.MFA_stim_val_scale[["ind"]][["coord"]])
+
 ```
@@
 colnames(resamp_1st_reshuf)
+
 # create emoty  storage rame for eigenvakues
-eigen_first_reshuf<- as.data.frame(eugentest)
+eigen_first_reshuf<- as.data.frame(res.mfa_bio_vs_self2_k2$eig)
 eigen_first_reshuf[,]<- NA
@@
 # create empty storage for correlations
-cor_first_reshuf<- as.data.frame(cortest)
+cor_first_reshuf<- as.data.frame(cor_first_reshuf)
 cor_first_reshuf[,]<- NA
@@
 
-for (i in 1:1000) {
+for (i in 1:10000) {
   message(sprintf("$$$$$RUNING sim %i", i))
 
-resampled_temp_reshuf<-    clustering_new_pre_PCA3.1_copy[,c(1,2,3, 5:9)] %>%
+# changed below to replace treue - shuflle with replacement
+  # https://stats.stackexchange.com/questions/104040/resampling-simulation-methods-monte-carlo-bootstrapping-jackknifing-cross?rq=1
+  # See the question on permutation vs bootstrapping - "The permutation test is best for testing hypotheses and bootstrapping is best for estimating confidence intervals".
+resampled_temp_reshuf <-    clustering_new_pre_PCA3.1_copy[,c(1,2,3, 5:9)] %>%
   group_by(ssid)%>%
   transform(pup_basCor = 
-              sample(pup_basCor, replace = F),
-            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = F),
-            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = F),
-            arousal = sample(arousal, replace = F),
-            valence = sample(valence, replace = F))
+              sample(pup_basCor, replace = FALSE),
+            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = FALSE),
+            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = FALSE),
+            arousal = sample(arousal, replace = FALSE),
+            valence = sample(valence, replace = FALSE))
 
@@
 
-```
-
-# agg by pp
-
-```{r}
-clustering_new_pre_PCA3.1.scale_agg_bysid<- clustering_new_pre_PCA3.1%>%
-  group_by(ssid)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)
-
-clustering_new_pre_PCA3.1.scale_aft_agg_bysid<- clustering_new_pre_PCA3.1.scale_agg_bysid%>%
-  mutate_if(is.numeric, scale)
-
-res.mfa_agg_bysubj <- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bysid, 
-               group = c(1, 3, 2), 
-               type = c("n", "s", "s"),
-               # "s", "s", "s"
-               name.group = c("sid","auton","subj"),
-               num.group.sup = c(1),
-               # ind.sup = c(1,2),
-               graph = TRUE)
-
-```
-
-boostrap subjct results
-
-```{r}
-
-factoextra::fviz_eig(res.mfa_agg_bysubj)
-factoextra::fviz_mfa_group(res.mfa_agg_bysubj)
-
-res.mfa_bio_vs_self2_k2$eig
-res.mfa_agg_bysubj$eig
-res.mfa_agg_bysubj$quanti.var$cor
-res.mfa_agg_bysubj$group$cos2
-
-```
-
-```{r}
-colnames(resampled_temp_bysubj)
-resamp_1st_bysubj<- data.frame(matrix(NA, nrow = 1, ncol = 8))
-
-# cnames_resamp_subj<- names(resampled_temp_bysubj)
-colnames(resamp_1st_bysubj)<- cnames_resamp_subj
-colnames(resamp_1st_bysubj)
-# create emoty  storage rame for eigenvakues
-eigen_first_bysubj<- as.data.frame(eugentest)
-eigen_first_bysubj[,]<- NA
-
-# eigen_first<- as.data.frame(eigen_first)
-
-# create empty storage for correlations
-cor_first_bysubj<- as.data.frame(cortest)
-cor_first_bysubj[,]<- NA
-# cor_first<- as.data.frame(cor_first)
-
-# now store group results/partials
-
-# res.mfa_bio_vs_self2_k2$group$correlation
-partials_first_bysubj <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
-partials_first_bysubj[,]<- NA
-partials_first_bysubj
-partials_first_bysubj$sim_no<- NA
-
-# hierarquical clustering
-clustering_new_pre_PCA3.1.scale_agg_bysid$ssid<- as.character(clustering_new_pre_PCA3.1.scale_agg_bysid$ssid)
-# clustering_new_pre_PCA3.1.scale_agg_bysid$stimDescription<- as.character(clustering_new_pre_PCA3.1.scale_agg_bysid$stimDescription)
-
-# think we need to store groups
-
-groups_first_bysubj<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
-# res.mfa_bio_vs_self2_k2$group$correlation
-
-groups_first_bysubj[,]<- NA
-groups_first_bysubj
-groups_first_bysubj$sim_no<- NA
-
-#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
-colnames(clustering_new_pre_PCA3.1.scale_agg_bysid)
-
-for (i in 1:1000) {
-  message(sprintf("$$$$$RUNING sim %i", i))
-
-  resampled_temp_bysubj<- fabricatr::resample_data(clustering_new_pre_PCA3.1.scale_agg_bysid, 
-                                  N = c(51),
-                                  ID_labels = c("ssid"),
-                                  unique_labels = TRUE)
-  # View(resampled_temp_bysubj)
-  resampled_temp_bysubj$sim_no = i
-  # resampled_temp_bysubj$ssid_new <- as.factor(substr(resampled_temp_bysubj$stimDescription_unique,1,6))
-  # resampled_temp_bysubj$newstim <- substr(resampled_temp_bysubj$stimDescription_unique,7,30)
-  # resampled_temp_bysubj$stimDescription<- as.factor(resampled_temp_bysubj$stimDescription)
-
-# run PCA on the resampled data
-  # colnames(resampled_temp_bysubj)
-    message(sprintf("$$$$$fitting PCA %i", i))
-    mfa.res_bysubj <- FactoMineR::MFA(resampled_temp_bysubj[,1:6], 
-               group = c(1, 3, 2), 
-               type = c("n", "s", "s"),
-              # ind.sup = c(1),
-              ncp = 2,
-               name.group = c("sid","auton","subj"),
-               num.group.sup = c(1),
-               # ind.sup = c(1,2),
-               graph = FALSE)
-
-# store the eigen values
-message(sprintf("$$$$$storing PCA %i", i))
-eugentest_bysubj<- as.data.frame(mfa.res_bysubj$eig[1:2,])
-eugentest_bysubj$sim_no<- i
-
-cortest_bysubj<- as.data.frame(mfa.res_bysubj$quanti.var$cor)
-cortest_bysubj$sim_no = i
-
-partials_temp_bysubj<- as.data.frame(mfa.res_bysubj$partial.axes$cor)
-partials_temp_bysubj$sim_no = i
-
-# groups
-group_temp_bysubj<- as.data.frame(mfa.res_bysubj$group$cos2)
-group_temp_bysubj$sim_no = i
-
-# update the initial d=frames
-  message(sprintf("$$$$$upating dataframes %i", i))
-  resamp_1st_bysubj<- (bind_rows(resamp_1st_bysubj, resampled_temp_bysubj))
-eigen_first_bysubj<- bind_rows(eigen_first_bysubj, eugentest_bysubj)
-cor_first_bysubj<- bind_rows(cor_first_bysubj, cortest_bysubj)
-partials_first_bysubj<- bind_rows(partials_first_bysubj, partials_temp_bysubj)
-groups_first_bysubj<- bind_rows(groups_first_bysubj, group_temp_bysubj)
-  message(sprintf("$$$$$completed iteration%i", i))
-}
-
-resamp_1st_bysubj
-View(resamp_1st_bysubj)
-
-resamp_1st_bysubj
-
-resamp_1st_bysubj%>%
-  subset(sim_no == 11)
-
-```
-
-visualise boostrap CIs for agg by subjec
-
-```{r}
-eigen_first_bysubj%>%
-  mutate(component =as.factor(substr(rownames(eigen_first_bysubj), 1,6)))%>% #retrieve names for components
-  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+save(clustering_new_pre_PCA3.1_copy,resampled_temp_reshuf,
+     resamp_1st_reshuf,
+     eigen_first_reshuf,
+     cor_first_reshuf,
+     res.mfa_bio_vs_self2_k2,
+     clustering_new_pre_PCA3.1, file = "resample_hierar.RData")
+
+```
+
+visualise resshufled null data
+
+```{r}
+
+eigen_first_reshuf%>%
+  mutate(component =as.factor(substr(rownames(eigen_first_reshuf), 1,6)))%>% #retrieve names for components
+  subset(!is.na(eigenvalue))%>% #select only component 1 and remove nas I introduced in the dataframe
+  group_by(component)%>%
+
    mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
-         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
-  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
+         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
+  ungroup()%>%
+    group_by(component)%>%
+  mutate(eig_obs_dim = if_else(component == "comp 1", 
+                               res.mfa_bio_vs_self2_k2$eig[1],
+                               res.mfa_bio_vs_self2_k2$eig[2])) %>% #store observed to visualise ion the null
+  mutate(prob = paste(((sum(eigenvalue>=eig_obs_dim))/n())*100, paste0("%"))) %>%
   ggplot(aes(eigenvalue))+
-  geom_histogram(alpha = .2)+
-    geom_density()+
+  geom_histogram(aes(y=..density..),bins = 500, alpha = .3) +  # scale histogram y
+  geom_density(col = "red", alpha = .001)+
   # facet_grid(~component)+
-    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
-  geom_point(x = res.mfa_agg_bysubj$eig[1],y = 10,size = 2, color = "red")+
+    geom_vline(aes(xintercept = eig_obs_dim),size = 2, color = "red", linetype = "dashed", alpha = .3)+
+  geom_point(aes(x = eig_obs_dim, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
 
   theme_classic()+
-  geom_vline(xintercept = 1, linetype = "dashed")
-  # ggtitle("distribution of boostraped eigen values for component  1 
-          # red dot = observed eigenvalue, boostrapped 95%CI")+
-  # annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")
-
-eigen_first_bysubj%>%
-  mutate(component =as.factor(substr(rownames(eigen_first_bysubj), 1,6)))%>% #retrieve names for components
-  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the dataframe
-  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
-         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
-  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
-  ggplot(aes(eigenvalue))+
-  geom_histogram(alpha = .2)+
-    geom_density()+
-  # facet_grid(~component)+
-    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
-  geom_point(x = res.mfa_agg_bysubj$eig[2],y = 10,size = 2, color = "red")+
+
+  # annotate(aes(text, label = prob))
 
   theme_classic()+
-  geom_vline(xintercept = 1, linetype = "dashed")
-
-```
-
-variables and dimension corelations
-```{r}
-cor_first_bysubj %>%
-  mutate(variable = as.factor(substr(rownames(cor_first_bysubj), 1,6)))%>%
-    subset(!is.na(Dim.1)) %>%
-  # create interval per variable
-  group_by(variable)%>%
-   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
-         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
-  # subset(variable == "arousa"|variable == "valenc")%>%
-  # select(c("arousal", "valence"))%>%
-  ggplot(aes(Dim.1)) +
+  facet_grid(~component)
+
+# component 1 is significant
+```
+
+cor reshudl
+
+```{r}
+
+cor.test_obsmfa<- as.data.frame(res.mfa_bio_vs_self2_k2$quanti.var$cor) %>%
+   mutate(variable = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$quanti.var$cor)), 1,6)))%>%
+ gather(dimension, value_dimenion, -variable)
+
+cor.test_obsmfa
+
+colnames(cor_first_reshuf)
+cor_first_reshuf1<- cor_first_reshuf %>%
+  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
+    gather(dimension, value_dimenion, -variable, -sim_no) %>%
+
+  group_by(variable,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
+  subset(!is.na(value_dimenion))
+
+# this mighgt have to do with the wrong test
+left_join(cor_first_reshuf1, cor.test_obsmfa, by = c("variable", "dimension")) %>%
+  group_by(variable,dimension)%>%
+     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
+   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
+  # the line above computes the probability that the correlation is more extreme (in magnitutde) thn the observed one
+
+  ggplot(aes(value_dimenion.x)) +
   geom_histogram(aes(y=..density..), alpha=0.5,
@@
   geom_density(alpha=.2) +
-   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
-  facet_grid(~variable)+
-  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
+  # geom_point(aes(x = value_dimenion.y, y = -2))+
+    # geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+  facet_grid(variable~dimension)+
+   geom_vline(aes(xintercept = value_dimenion.y),size = 2, color = "red", linetype = "dashed", alpha = .3)+
+  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+
+  theme_classic()
+
+```
+
+```{r}
+partials_first_1_obs<- as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor) %>%
+   mutate(dimension_partial = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)), 1,4)),
+           group = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)), 5,9)))%>%
+ gather(dimension, value_dimenion,-group,-dimension_partial)
+
+partials_first_reshuf_1<- partials_first_reshuf %>%
+  mutate(dimension_partial = as.factor(substr(rownames(partials_first_reshuf), 1,4)),
+         group = as.factor(substr(rownames(partials_first_reshuf), 5,9)))%>%
+   gather(dimension, value_dimenion, -group, -sim_no, -dimension_partial) %>%
+   group_by(dimension_partial,dimension,group)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
+  subset(!is.na(value_dimenion))
+
+left_join(partials_first_reshuf_1,partials_first_1_obs,by = c("dimension_partial", "group", "dimension")) %>%
+  group_by(dimension_partial,dimension, group)%>%
+   # group_by(variable,dimension)%>%
+     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
+   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
+  subset(dimension_partial == "Dim1")%>%
+   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-5 ), color = "gray30")+
+  geom_vline(aes(xintercept = value_dimenion.y),size = 2, color = "red", linetype = "dashed", alpha = .3)+
+  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+  facet_grid(dimension~group)+
+
+  theme_classic()+
+  ggtitle("partial to dimension 1")
+
+left_join(partials_first_reshuf_1,partials_first_1_obs,by = c("dimension_partial", "group", "dimension")) %>%
+  group_by(dimension_partial,dimension, group)%>%
+   # group_by(variable,dimension)%>%
+     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
+   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
+  subset(dimension_partial == "Dim2")%>%
+   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
+   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-5 ), color = "gray30")+
+  geom_vline(aes(xintercept = value_dimenion.y),size = 2, color = "red", linetype = "dashed", alpha = .3)+
+  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+  facet_grid(dimension~group)+
+
+  theme_classic()+
+  ggtitle("partial to dimension 2")
+
+```
+
+Groups
+
+groups_first_1boot<- groups_first%>%
+  mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
+  gather(dimension, value_dimenion,-group,-sim_no)%>%
+  # -perc_5,-perc_95, 
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))
+
+?boot::boot.ci
+boot::boot.ci(groups_first_1boot$value_dimenion, type = "bca")[1]
+?bootBCa
+bootBCa(.5, groups_first_1boot$value_dimenion, n = 2600)[1]
+left_join(groups_first_1boot, groups_first_obs,by = c("group", "dimension"))%>%
+
+  ggplot(aes(value_dimenion)) +
+   geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-3 ), color = "gray30")+
+   geom_point(aes(x = value_dimenion_obs, y = -3))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+
+  facet_grid(dimension~group)+
   # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
@@
 
-```
-Agg within participant by neg pos etc (using normative data)
-With and without selfreports
-
-```{r}
-?cut
-#create valence categories based ion self reports (IAPS validation)
-clustering_new_pre_PCA3_val_vat<- clustering_new_pre_PCA3%>%
-  mutate(valence_iaps_cat = cut(ValenceMean,3, labels = c("neg", "mid", "pos")))
-
-# scale within subject
-# aggregate by subject and
-
-View(clustering_new_pre_PCA3_val_vat)
-# clustering_new_pre_PCA3_val_vat%>%
-#   group_by(ssid)%>%
-#   mutate_if(is.numeric, scale)
-
-clustering_new_pre_PCA3_val_vat_agg<- clustering_new_pre_PCA3_val_vat%>%
-  group_by(ssid, valence_iaps_cat)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)
-
-library(factoextra)
-library(FactoMineR)
-
-colnames(clustering_new_pre_PCA3_val_vat_agg)
-clustering_new_pre_PCA3_val_vat_agg[,c(2,5,6,7,8,9)]
-
-FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_agg[,c(1,2,5,6,7,8,9)], 
-               group = c(2, 3, 2), 
-               type = c("n", "s", "s"),
-               # "s", "s", "s"
-               name.group = c("ss_id_stim","auton","subj"),
-               num.group.sup = c(1),
-               # ind.sup = c(1,2),
-               graph = TRUE)
-
-# scale
-clustering_new_pre_PCA3_val_vat_agg_scale<- clustering_new_pre_PCA3_val_vat_agg[,c(1,2,5,6,7,8,9)]
-
-clustering_new_pre_PCA3_val_vat_agg_scale%>%
-   # group_by(ssid)%>%
-  mutate_if(is.numeric, scale)
-
-clustering_new_pre_PCA3_val_vat_scale_then_agg<- clustering_new_pre_PCA3_val_vat%>%
-  group_by(ssid)%>%
-  mutate_if(is.numeric, scale)%>%
-  group_by(ssid, valence_iaps_cat)%>%
-  summarise_if(is.numeric, mean, na.rm = TRUE)
-
-clustering_new_pre_PCA3_val_vat_scale_then_agg1<- clustering_new_pre_PCA3_val_vat_scale_then_agg[,c(1:2, 5:9)]
-
-?FactoMineR::MFA
-res.mfa_val_cat_scal<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_scale_then_agg1,
-               group = c(2, 3, 2), 
-               type = c("n", "s", "s"),
-               name.group = c("ss_id_stim","auton","subj"),
-               num.group.sup = c(1),
-               # ind.sup = c(1,2),
-               graph = TRUE)
-
-?FactoMineR::MFA
-View(res.mfa_val_cat_scal)
-
-# force k = 2
-
-res.mfa_val_cat_scal_k2<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_scale_then_agg1,
-               group = c(2, 3, 2), 
-               type = c("n", "s", "s"),
-               name.group = c("ss_id_stim","auton","subj"),
-               num.group.sup = c(1),
-               ncp = 2,
-               # ind.sup = c(1,2),
-               graph = TRUE)
-
-res.mfa_val_cat_scal_k2$eig
-
-```
-
-```{r}
-
-fviz_mfa_ind(res.mfa_val_cat_scal, 
-             habillage = "valence_iaps_cat", # color by groups 
-             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
-             addEllipses = TRUE, 
-             ellipse.type = "confidence", 
-             repel = TRUE # Avoid text overlapping
-             )
-
-# we can sorta see that while things allign relativelly well on sujective dimension, they don't allugn very well on the autonomic dimension
-
-save.image("subjobjPCAfeb9.RData")
-```
+```{r}
+
+groups_first_reshuf<- groups_first_reshuf%>%
+  mutate(group = as.factor(substr(rownames(groups_first_reshuf), 1,4)))
+
+group_cordf<- as.data.frame(res.mfa_bio_vs_self2_k2$group$correlation)
+group_cordf$group<-as.factor(substr(rownames(group_cordf), 1,4))
+
+group_cordf1<- group_cordf%>%
+gather(dimension, value_dimenion, - group)
+
+groups_first_reshuf1<- left_join(groups_first_reshuf, group_cordf1)
+
+# View(groups_first_reshuf)
+groups_first_reshuf1<- groups_first_reshuf %>%
+  gather(dimension, value_dimenion, -group, -sim_no) %>%
+  subset(!is.na(value_dimenion))
+
+ left_join(groups_first_reshuf1, group_cordf1, c("group", "dimension"))%>%
+   group_by(group,dimension)%>%
+   mutate(perc_5 = quantile(value_dimenion.x,.025, na.rm = TRUE),
+         perc_95 = quantile(value_dimenion.x,.975, na.rm = TRUE))%>%
+     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
+   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
+
+  ggplot(aes(value_dimenion.x)) +
+  geom_histogram(bins = 500)+
+
+  geom_density(alpha=.2) +
+  facet_grid(dimension~group)+
+     geom_vline(aes(xintercept = value_dimenion.y), linetype = "dashed", color = "red")+
+   # geom_vline(aes(xintercept = Dim.2.y),  linetype = "dashed", color = "blue")+
+  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
+  # geom_histogram(aes(y=..density..), alpha=0.5,
+  #                position="identity")+
+
+  theme_classic()
+
+res.mfa_bio_vs_self2_k2$group$correlation
+
+```

### 2022-05-25 Paper_Analyses_subj_obje_arousal.Rmd
change of storage location

@@
                                        critical.value = 2)
+
+clustering_new_pre_PCA3.1
+
+colnames(clustering_new_pre_PCA3.1)
+
+library(prettyGraphs)
+
+min(clustering_new_pre_PCA3.1$log_BIO_CDA.PhasicMax, na.rm = TRUE)
+testjustpca <-InPosition::epPCA.inference.battery(clustering_new_pre_PCA3.1[,5:7], 
+                                       scale = TRUE, 
+                                       center = TRUE, 
+                                       # DESIGN = var.design_asd, 
+                                       # make_design_nominal = TRUE, 
+                                       graphs = TRUE, k = 0, 
+                                       test.iters = 1000, 
+                                       constrained = FALSE, 
+                                       critical.value = 2)
+
+?InPosition::epPCA.inference.battery
+
+clustering_new_pre_PCA3.1$pc1<- testjustpca$Fixed.Data$ExPosition.Data$fi[,1]
+clustering_new_pre_PCA3.1$pc2<- testjustpca$Fixed.Data$ExPosition.Data$fi[,2]
+testjustpca$Fixed.Data$ExPosition.Data$fi
+
+library(lmerTest)
+
+summary(lmer(arousal ~ (pc1 + pc2) + (1|ssid) + (1|stimDescription),
+     data = clustering_new_pre_PCA3.1))
+
+write_csv(clustering_new_pre_PCA3.1, "clustering_new_pre_PCA3.1new.csv")
+
 InPosition::epCA.inference.battery()
@@
 colnames(all.data3)
+
+# 
+colnames(clustering_new_pre_PCA_2_agg_by_val_sel)
+
+min(clustering_new_pre_PCA_2_agg_by_val_sel$log_BIO_CDA.PhasicMax)
+testjustpca2 <-InPosition::epPCA.inference.battery(clustering_new_pre_PCA_2_agg_by_val_sel[,3:5], 
+                                       scale = TRUE, 
+                                       center = TRUE, 
+                                       # DESIGN = var.design_asd, 
+                                       # make_design_nominal = TRUE, 
+                                       graphs = TRUE, k = 0, 
+                                       test.iters = 1000, 
+                                       constrained = FALSE, 
+                                       critical.value = 2)
+
+clustering_new_pre_PCA_2_agg_by_val_sel$pc1 <- testjustpca2$Fixed.Data$ExPosition.Data$fi[,1]
+clustering_new_pre_PCA_2_agg_by_val_sel$pc2 <- testjustpca2$Fixed.Data$ExPosition.Data$fi[,2]
+
+library(lmerTest)
+
+summary(lmer(arousal ~ (pc1 + pc2) + (1|ssid),
+     data = clustering_new_pre_PCA_2_agg_by_val_sel))
 

### 2022-05-25 Subj_Obj_Ar_Bayes_Prev.Rmd
change of storage location

@@
   View(p)
-
 ```
@@
 
+Now Level 2 test
+
 ```{r}
@@
 
-valence
-```{r}
-
-```
-
 ```{r}
@@
 scales::rescale(0)
+
+bind_bayes1 <- left_join(as.data.frame(p), as.data.frame(estimate), by = "sid")
+bind_bayes2 <- left_join(as.data.frame(bind_bayes1), as.data.frame(se), by = "sid")
+bind_bayes2
+
+bind_test<- bind_cols(p, estimate, se)
+
 db_full4new_stim_screen_pupil_nopract_no_outl%>%
@@
   ggplot(aes(x = pup_basCor))+
-  stat_function(fun=dgamma, args=list(shape=1, scale=.5))+
-  # geom_density()+
+  # stat_function(fun=dgamma, args=list(shape=1, scale=.5))+
   geom_jitter(aes( x = pup_basCor_mean, y = rescaled_y),
               width = .1, height = 0)
-  # stat_function(fun=dgamma, args=list(shape=1, scale=.5))
-  geom_jitter()
-  stat_summary(geom = "pointrange")
 
-testdensity$data.name
+bind_bayes2$xdensity<- testdensity[["x"]]
+bind_bayes2$ydensity<- testdensity[["y"]]
 
- c(density(db_full4new_stim_screen_pupil_nopract_no_outl$ssid,n=n)$x, density(bar,n=n)$x)
+testgensity
+
+bind_bayes2 %>%
+
+  group_by(sid)%>%
+  # mutate(testdensity_x = density(arousal_c.x, n = 2)$x,
+  #        testdensity_y = density(arousal_c.x, n = 2)$y)%>%
+
+  ggplot(aes(x = arousal_c.x))+
+   # stat_function(fun=dgamma, args=list(shape=1))
+  geom_density() +
+  geom_point(aes(x = xdensity, y =ydensity))
+
+bind_bayes2%>%
+  ggplot(aes(as.numeric(as.factor(as.integer(sid))), arousal_c.y, color = arousal_c.x<.05))+
+  geom_point()+
+  geom_pointrange(aes(ymin = arousal_c.y- arousal_c, ymax = arousal_c.y+ arousal_c ))
+
+bind_bayes2%>%
+  ggplot(aes(as.numeric(as.factor(as.integer(sid))), valence_c.y, color = valence_c.x<.05))+
+  geom_point()+
+  geom_pointrange(aes(ymin = valence_c.y- valence_c, ymax = valence_c.y+ valence_c ))
+
+bind_bayes2%>%
+  ggplot(aes(as.numeric(as.factor(as.integer(sid))), `valence:arousal.y` , 
+             color = `valence:arousal.x` <.05))+
+  geom_point()+
+  geom_pointrange(aes(ymin = `valence:arousal.y` - `valence:arousal`, 
+                      ymax = `valence:arousal.y` + `valence:arousal` ))
 
@@
 
-```{r cars}
-summary(cars)
+Try with the timecourse now.
+start with only one predictor - arousal
+
+then plot the effect size in terms of a heatmap
+
+```{r}
+
+tmp.df4_full_stim_downs_jun2021_60bins_NT<- subset(tmp.df4_full_stim_downs_jun2021_60bins,
+                                    Group == "NT")
+
+b = 1
+
+subject_id2<- unique(tmp.df4_full_stim_downs_jun2021_60bins_NT$ssid)
+s = 1
+
+b = 1
+
+testtimecourseforbayprev<-   subset(tmp.df4_full_stim_downs_jun2021_60bins_NT,
+                                    ssid =  subject_id[s],
+                                    timebin_no == nbins[b])
+
+unique(testtimecourseforbayprev$timebin_no)
+
+tmp.df4_full_stim_downs_jun2021_60bins_NT%>%
+  group_by(ssid, timebin_no)%>%
+  summarise_at(c("pup_basCor"), mean, na.rm = TRUE)
+
+# try and figure out how many timebins per participant we need to cerate to hold data
+tmp.df4_full_stim_downs_jun2021_60bins_NT%>%
+  subset(timebin_no<56)%>%
+  group_by(ssid, timebin_no)%>%
+  summarise_at(c("pup_basCor"), mean, na.rm = TRUE) %>%
+    group_by(ssid)%>%
+  mutate(n_timebin = n())
+  # total of 3025 rows
+  #  summarise_at(c("pup_basCor", "n_timebin"), mean, na.rm = TRUE)
+
+tmp.df4_full_stim_downs_jun2021_60bins_NT_55<- tmp.df4_full_stim_downs_jun2021_60bins_NT%>%
+  subset(timebin_no<56)
+
+# create the dataset to hold participant, timebin code, statistics for each timebin
+# seems like the majority have 55
+
+nsubj_2 = 55
+n_bins_2 = 55
+
+timecourse_60bin_result_df_for_bp <-timecourse_60bin_result_df <- data.frame(
+  ssid = rep(NA, nsubj_2*n_bins_2),
+  timebins= rep(NA, nsubj_2*n_bins_2), 
+                                       Estimate_ar= rep(NA, nsubj_2*n_bins_2), 
+                                       se_ar= rep(NA, nsubj_2*n_bins_2), 
+                                       t_ar=rep(NA, nsubj_2*n_bins_2), 
+                                       p_ar=rep(NA, nsubj_2*n_bins_2)
+                                       # Estimate_vl= rep(NA, nsubj_2*n_bins_2), 
+                                       # t_vl=rep(NA, nsubj_2*n_bins_2), 
+                                       # p_vl=rep(NA, nsubj_2*n_bins_2),
+                                       # Estimate_br= rep(NA, nsubj_2*n_bins_2), 
+                                       # t_br= rep(NA, nsubj_2*n_bins_2), 
+                                       # p_br= rep(NA, nsubj_2*n_bins_2),
+                                       # Estimate_ar_vl= rep(NA, nsubj_2*n_bins_2), 
+                                       # t_ar_vl= rep(NA, nsubj_2*n_bins_2), 
+                                       # p_ar_vl= rep(NA, nsubj_2*n_bins_2),
+                                       # cov= as.character(rep(NA, nsubj_2*n_bins_2)
+                                                         )
+timecourse_60bin_result_df_for_bp
+
+# now fit level 1 within individual tests
+0 = 1 # remember to always rezero it
+s=2
+b = 3
+# nbins
+
+n_bins_3<- unique(tmp.df4_full_stim_downs_jun2021_60bins_NT_55$timebin_no)
+subject_id_3<- unique(tmp.df4_full_stim_downs_jun2021_60bins_NT_55$ssid)
+
+s = 1
+b = 2
+
+for (s in 1:length(subject_id2)) {
+  for (b in 1:length(n_bins_3)) {
+
+    message(sprintf("$$$$$RUNING ssid %s timebin %i", subject_id2[s], n_bins_3[b]))
+        lm_bin_pup  <- lm(pup_basCor ~ arousal_c,
+                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins_NT_55,
+                                    ssid ==  subject_id2[s] &
+                                    timebin_no == n_bins_3[b]))
+        # save the summary    
+        lm_bin_pup_summary<- summary(lm_bin_pup)
+
+        # store statistics for particiapnt and timebin
+        timecourse_60bin_result_df_for_bp[i,1]<- subject_id[s] #ssid 
+        timecourse_60bin_result_df_for_bp[i,2]<- n_bins_3[b] #timebin
+          # timecourse_60bin_result_df[b,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
+            timecourse_60bin_result_df_for_bp[i,3] <- lm_bin_pup_summary$coefficients[2] #estimate, note to avoid intercept start on 2 for estimate, then 4 for se, the 6 for t and so on
+            timecourse_60bin_result_df_for_bp[i,4] <- lm_bin_pup_summary$coefficients[4] #se
+            timecourse_60bin_result_df_for_bp[i,5] <- lm_bin_pup_summary$coefficients[6] #t
+             timecourse_60bin_result_df_for_bp[i,6] <- lm_bin_pup_summary$coefficients[8] #p
+
+       i = i+1
+     # b = b+1
+  }
+
+  }
+
+timecourse_60bin_result_df_for_bp<- timecourse_60bin_result_df_for_bp[442:nrow(timecourse_60bin_result_df_for_bp),]
+
+# heatmap
+
+library(viridis)
+install.packages('hrbrthemes')
+
+library(hrbrthemes)
+timecourse_60bin_result_df_for_bp%>%
+  ggplot(aes(y = as.factor(as.numeric(ssid)), x = timebins))+
+  geom_tile(aes(fill = Estimate_ar))+
+  scale_fill_viridis(discrete=FALSE) 
+  theme_ipsum()
+  theme_classic()
+
+  ?p.adjust
+  timecourse_60bin_result_df_for_bp$p_ar_adjust<- p.adjust(timecourse_60bin_result_df_for_bp$p_ar,
+                                                           method = "bonferroni", n = 55)
+
+timecourse_60bin_result_df_for_bp<-  timecourse_60bin_result_df_for_bp%>%
+    group_by(ssid)%>%
+    mutate(p_adjusted = p.adjust(p_ar, method = "bonferroni", n = n()))
+
+timecourse_60bin_result_df_for_bp %>%
+  ggplot(aes(y = as.factor(as.numeric(ssid)), x = timebins))+
+  geom_tile(aes(fill = p_adjusted))+
+  scale_fill_viridis(discrete=FALSE) +
+  # theme_ipsum()
+  theme_classic()
+
+timecourse_60bin_result_df_for_bp %>%
+  ggplot(aes(x = timebins/10, y = t_ar))+
+  stat_summary(geom = "line", size = 2)+
+  stat_summary( geom = "errorbar", mult = 1) 
+  stat_summary()
+
+  geom_tile(aes(fill = p_adjusted))+
+  scale_fill_viridis(discrete=FALSE) +
+  # theme_ipsum()
+  theme_classic()
+
+  timecourse_60bin_result_df_for_bp %>%
+  ggplot(aes(x = timebins/10, y = t_ar))+
+  stat_summary(geom = "line", size = 2)+
+  stat_summary( geom = "errorbar", mult = 1) 
+  stat_summary()
+
+  geom_tile(aes(fill = p_adjusted))+
+  scale_fill_viridis(discrete=FALSE) +
+  # theme_ipsum()
+  theme_classic()
+
+  # count
+  alpha
+  timecourse_60bin_result_df_for_bp$p_adjusted_count<- 
+    timecourse_60bin_result_df_for_bp$p_adjusted< alpha
+
+   timecourse_60bin_result_df_for_bp$p_count<- 
+    timecourse_60bin_result_df_for_bp$p_ar< alpha
+
+  table(  timecourse_60bin_result_df_for_bp$p_adjusted_count)
+
+  table(  timecourse_60bin_result_df_for_bp$p_count)
+
+# flag max
+  timecourse_60bin_result_df_for_bp<- timecourse_60bin_result_df_for_bp%>%
+    group_by(ssid)%>%
+    # mutate(max_T = if_else(p_adjusted_count == TRUE, max(t_ar), NULL))
+   mutate(max_T =  max(t_ar))
+
+p.adjust(.05, method = "bonferroni", 55)
+
+.05/55
+# 0.0009
+
+# new t = 4.5
+
+timecourse_60bin_result_df_for_bp%>%
+  group_by(ssid)%>%
+  summarize_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(x = as.factor(as.numeric(ssid)), y = t_ar))+
+  geom_point(size = 2, color = "blue")+
+  geom_segment( aes(x=as.factor(as.numeric(ssid)), xend=as.factor(as.numeric(ssid)), 
+                    y=0, yend=t_ar),color = "blue")+
+  geom_hline(yintercept = 3.5, linetype = "dashed")+
+  coord_flip()+
+  theme_bw()
+  geom_line()
+
+  # just p value
+
+  timecourse_60bin_result_df_for_bp%>%
+  group_by(ssid)%>%
+  summarize_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(x = as.factor(as.numeric(ssid)), y = p_ar))+
+  geom_point(size = 2, color = "blue")+
+  geom_segment( aes(x=as.factor(as.numeric(ssid)), xend=as.factor(as.numeric(ssid)), 
+                    y=0, yend=p_ar),color = "blue")+
+  geom_hline(yintercept = .05, linetype = "dashed")+
+  coord_flip()+
+  theme_bw()
+  geom_line()
+
+  # lets for a minute assume the regukar o is fine
+  timecourse_60bin_result_df_for_bp%>%
+    group_by(ssid)
+
+  # alpha, the false positive rate
+n <- Nsub
+
+indsig_ts = timecourse_60bin_result_df_for_bp$p_ar <alpha
+# table(indsig)
+
+# lets start with valence
+k_ar_ts <- sum(indsig_ts)
+table(indsig_ts)
+
+timecourse_60bin_result_df_for_bp%>%
+  group_by(ssid)%>%
+  mutate(p_count_sum_sidsum(p_count))%>%
+  mutate(= k_ar_ts_sid = )
+
+?binom.test
+binom.test(k_ar_ts, 3025, 0.05, alternative="two.sided",  )
+
+# plot posterior distribution of population prevalence
+# install.packages("HDInterval")
+library(HDInterval) # this package is needed
+xvals <- seq(0, 1, .01)
+bayesprev_posterior()
+pdf_2 <- bayesprev_posterior(xvals, k_2, n) # function needed
+pdf_2
+
+plot(xvals, pdf_2, type ="l", xlab = expression(gamma), 
+     ylab ="Posterior density", lwd=3)
+
+# Add the MAP estimate as a point
+# MAP = Maximum
+
+xmap = bayesprev_map(k_2, n)
+pmap = bayesprev_posterior(xmap, k_2, n)
+points(xmap, pmap, cex =2, col= "red", pch=16)
+
+# Add the .95 lower bound as a vertical line
+xbound = bayesprev_bound(0.95, k_2, n)
+pbound = bayesprev_posterior(xbound, k_2, n)
+lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)
+
+# Add the 0.96 HPDI
+int = bayesprev_hpdi(0.96, k_2, n)
+i1 = int[1]
+i2 = int[2]
+h1 = bayesprev_posterior(i1, k_2, n)
+h2 = bayesprev_posterior(i2, k_2, n)
+lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
+
 ```
 
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
+ #save the exact value of time bin
+            # store arousal (2,parameter)            # first number is term(row), second is column
+            timecourse_60bin_result_df[i,2]<-
+            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
+            timecourse_60bin_result_df[i,3]<-
+              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
+            timecourse_60bin_result_df[i,4]<-
+            lmer_bin_pup_summary[["coefficients"]][2,5] # p value
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+            # valence
+
+            timecourse_60bin_result_df[i,5]<-
+            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
+            timecourse_60bin_result_df[i,6]<-
+              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
+            timecourse_60bin_result_df[i,7]<-
+              lmer_bin_pup_summary[["coefficients"]][3,5] # p value
+
+            # brighteness
+
+            timecourse_60bin_result_df[i,8]<-
+            lmer_bin_pup_summary[["coefficients"]][4,1] #estimate
+            timecourse_60bin_result_df[i,9]<-
+              lmer_bin_pup_summary[["coefficients"]][4,4] # t statistic
+            timecourse_60bin_result_df[i,10]<-
+              lmer_bin_pup_summary[["coefficients"]][4,5] # p value
+
+            # interaction arousal x brighteness
+
+            timecourse_60bin_result_df[i,11]<-
+            lmer_bin_pup_summary[["coefficients"]][5,1] #estimate
+            timecourse_60bin_result_df[i,12]<-
+              lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
+            timecourse_60bin_result_df[i,13]<-
+              lmer_bin_pup_summary[["coefficients"]][5,5] # p value

### 2022-05-25 Subj_Obj_Ar_Bayes_Prev1.Rmd
change of storage location

@@
 
-```
-
 do just scr prevalence
@@
 ```
+
+limited coherence
+```{r}
+View(db_full6new_hr_fix_stim_nt1.1)
+db_full6new_hr_fix_stim_nt1.1
+
+# check the proximal distal problem
+# maybe coherecne increases with increasing action potential
+# use norm first and keep stim with high intensity
+
+# use 4.5
+db_full6new_hr_fix_stim_nt1.1 %>%
+  # subset(ArousalMean>6)%>%
+  subset(arousal > 2)%>%
+   mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
+  subset(ssid!= "347")%>%
+  subset(!is.na(mediansplit_ground_valence))%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+  group_by(ssid)%>%
+  mutate(Bio_Mean_HR_dif = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1],
+         pup_basCor = scale(pup_basCor, center = TRUE, scale = TRUE)[,1],
+         log_BIO_CDA.PhasicMax = scale(log_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
+  group_by(ssid)%>%
+  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"))%>%
+  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"))%>%
+  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"))%>%
+  select(c(ssid, mediansplit_ground_valence,cor_hr_pup, cor_hr_scr, cor_pup_scr))%>%
+  gather(key, value, -ssid,-mediansplit_ground_valence)%>%
+  group_by(ssid, key, value)%>%
+  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
+  ggplot(aes(key, value, color = key))+
+  geom_hline(yintercept = 0, size = 1.5, linetype = "dashed", alpha = .5)+
+  geom_line(aes(group = ssid), se = F, color = "black", alpha = .2)+
+  geom_jitter(width = .1, alpha = .5)+
+  stat_summary(geom = 'pointrange', color = "black")+
+    # facet_grid(~mediansplit_ground_valence)+
+  geom_hline(yintercept = .2)
+
+  p$graphstyle
+
+  # ggplot(aes(ArousalMean))+
+  # geom_histogram()
+  # geom_density()
+
+  # intensity thing doesnt work but what abotu bayesian prevalence
+
+  db_full6new_hr_fix_stim_nt1.1_bp<-
+db_full6new_hr_fix_stim_nt1.1 %>%
+   mutate(log_BIO_CDA.PhasicMax = log1p(BIO_CDA.PhasicMax+.1))%>%
+  subset(ssid!= "347")%>%
+  subset(!is.na(mediansplit_ground_valence))%>%
+  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
+
+  mutate(Bio_Mean_HR_dif = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1],
+         pup_basCor = scale(pup_basCor, center = TRUE, scale = TRUE)[,1],
+         log_BIO_CDA.PhasicMax = scale(log_BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])
+
+  # store correlation and ps
+
+  cor.test(db_full6new_hr_fix_stim_nt1.1_bp$pup_basCor, db_full6new_hr_fix_stim_nt1.1_bp$CDA.PhasicMax, use = "complete")$p.value
+
+db_full6new_hr_fix_stim_nt1.1_bp<-  db_full6new_hr_fix_stim_nt1.1_bp%>%
+  group_by(ssid)%>%
+  mutate(cor_hr_pup = cor(Bio_Mean_HR_dif, pup_basCor, use = "complete"),
+         cor_hr_pup_pval = cor.test(Bio_Mean_HR_dif, pup_basCor, use = "complete")$p.value)%>%
+  mutate(cor_hr_scr = cor(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete"),
+         cor_hr_scr_pval = cor.test(Bio_Mean_HR_dif, log_BIO_CDA.PhasicMax, use = "complete")$p.value)%>%
+  mutate(cor_pup_scr = cor(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete"),
+         cor_pup_scr_pval = cor.test(pup_basCor, log_BIO_CDA.PhasicMax, use = "complete")$p.value)
+
+View(db_full6new_hr_fix_stim_nt1.1_bp)
+
+db_full6new_hr_fix_stim_nt1.1_bp2 <- db_full6new_hr_fix_stim_nt1.1_bp %>%
+  group_by(ssid, subject)%>%
+  summarise_at(c("cor_hr_pup", "cor_hr_pup_pval", "cor_hr_scr","cor_hr_scr_pval",
+                 "cor_pup_scr", "cor_pup_scr_pval"), mean, na.rm = TRUE)
+
+?cor
+db_full6new_hr_fix_stim_nt1.1_bp2<- db_full6new_hr_fix_stim_nt1.1_bp2 %>%
+  mutate(indsig_hr_pup = cor_hr_pup_pval<alpha,
+         indsig_hr_scr = cor_hr_scr_pval<alpha,
+         indsig_pup_scr = cor_pup_scr_pval<alpha,
+         # onetailed
+         indsig_hr_pup_1t = (cor_hr_pup_pval/2)<alpha,
+         indsig_hr_scr_1t = (cor_hr_scr_pval)/2<alpha,
+         indsig_pup_scr_1t = (cor_pup_scr_pval)/2<alpha)
+
+sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_pup)
+sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_scr)
+sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_pup_scr)
+
+sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_pup_1t)
+sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_scr_1t)
+sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_pup_scr_1t)
+
+# do bayesian prevalence n the regular
+
+# two-tailed
+k_hr_pup <- sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_pup)
+k_hr_pup/50
+
+# plot posterior distribution of population prevalence
+
+t.test(db_full6new_hr_fix_stim_nt1.1_bp2$cor_hr_pup, 
+       alternative = c("two.sided"))
+# t = 0.94557, df = 49, p-value = 0.349
+
+binom.test(k_hr_pup, 50)
+# number of successes = 6, number of trials = 50, p-value = 0.00000003244
+
+xvals <- seq(0, 1, .01)
+pdf_hr_pup <- bayesprev_posterior(xvals, k_hr_pup, 50) # function needed
+pdf_hr_pup
+
+plot(xvals, pdf_hr_pup, type ="l", xlab = expression(gamma), 
+     ylab ="Posterior density", lwd=3)
+
+# Add the MAP estimate as a point
+# MAP = Maximum
+
+xmap = bayesprev_map(k_hr_pup, 50)
+# 0.07368421
+pmap = bayesprev_posterior(xmap, k_hr_pup, 50)
+points(xmap, pmap, cex =2, col= "red", pch=16)
+
+# Add the .95 lower bound as a vertical line
+xbound = bayesprev_bound(0.95, k_hr_pup, 50)
+pbound = bayesprev_posterior(xbound, k_hr_pup, 50)
+lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)
+
+# Add the 0.96 HPDI
+int = bayesprev_hpdi(0.96, k_hr_pup, 50)
+# 0.08783098 0.34143456
+i1 = int[1]
+i2 = int[2]
+h1 = bayesprev_posterior(i1, k_hr_pup, 50)
+h2 = bayesprev_posterior(i2, k_hr_pup, 50)
+lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
+
+```
+
+# hr scr - 2t
+
+````{r}
+
+# plot posterior distribution of population prevalence
+
+xvals <- seq(0, 1, .01)
+k_hr_scr <- sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_scr)
+# k_hr_pup/50
+
+t.test(db_full6new_hr_fix_stim_nt1.1_bp2$cor_hr_scr, 
+       alternative = c("two.sided"))
+
+binom.test(k_hr_pup, 50)
+binom.test(k_hr_scr, 50, p = 0)
+# number of successes = 7, number of trials = 50, p-value < 0.00000000000000022
+
+pdf_hr_scr <- bayesprev_posterior(xvals, k_hr_scr, 50) # function needed
+pdf_hr_scr
+
+plot(xvals, pdf_hr_scr, type ="l", xlab = expression(gamma), 
+     ylab ="Posterior density", lwd=3)
+
+# Add the MAP estimate as a point
+# MAP = Maximum
+
+xmap = bayesprev_map(k_hr_scr, 50)
+pmap = bayesprev_posterior(xmap, k_hr_scr, 50)
+points(xmap, pmap, cex =2, col= "red", pch=16)
+
+# Add the .95 lower bound as a vertical line
+xbound = bayesprev_bound(0.95, k_hr_scr, 50)
+pbound = bayesprev_posterior(xbound, k_hr_scr, 50)
+lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)
+
+# Add the 0.96 HPDI
+int = bayesprev_hpdi(0.96, k_hr_scr, 50)
+i1 = int[1]
+i2 = int[2]
+h1 = bayesprev_posterior(i1, k_hr_scr, 50)
+h2 = bayesprev_posterior(i2, k_hr_scr, 50)
+lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
+
+# scr pup 22t
+# plot posterior distribution of population prevalence
+
+xvals <- seq(0, 1, .01)
+k_pup_scr <- sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_pup_scr)
+# k_pup_pup/50
+binom.test(k_pup_scr, 50, p = 0.5)
+# number of successes = 7, number of trials = 50, p-value < 0.00000000000000022
+# number of successes = 6, number of trials = 50, p-value = 0.00000003244
+
+pdf_pup_scr <- bayesprev_posterior(xvals, k_pup_scr, 50) # function needed
+pdf_pup_scr
+
+plot(xvals, pdf_pup_scr, type ="l", xlab = expression(gamma), 
+     ylab ="Posterior density", lwd=3)
+
+# Add the MAP estimate as a point
+# MAP = Maximum
+
+xmap = bayesprev_map(k_pup_scr, 50)
+pmap = bayesprev_posterior(xmap, k_pup_scr, 50)
+points(xmap, pmap, cex =2, col= "red", pch=16)
+
+# Add the .95 lower bound as a vertical line
+xbound = bayesprev_bound(0.95, k_pup_scr, 50)
+pbound = bayesprev_posterior(xbound, k_pup_scr, 50)
+lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)
+
+# Add the 0.96 HPDI
+int = bayesprev_hpdi(0.96, k_pup_scr, 50)
+i1 = int[1]
+i2 = int[2]
+h1 = bayesprev_posterior(i1, k_pup_scr, 50)
+h2 = bayesprev_posterior(i2, k_pup_scr, 50)
+lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
+
+# one tailed 
+# hr_pup
+
+k_hr_pup_1t <- sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_pup_1t)
+k_hr_pup_1t/50
+
+# plot posterior distribution of population prevalence
+
+xvals <- seq(0, 1, .01)
+pdf_hr_pup_1t <- bayesprev_posterior(xvals, k_hr_pup_1t, 50) # function needed
+pdf_hr_pup_1t
+
+plot(xvals, pdf_hr_pup_1t, type ="l", xlab = expression(gamma), 
+     ylab ="Posterior density", lwd=3)
+
+# Add the MAP estimate as a point
+# MAP = Maximum
+
+xmap = bayesprev_map(k_hr_pup_1t, 50)
+pmap = bayesprev_posterior(xmap, k_hr_pup_1t, 50)
+points(xmap, pmap, cex =2, col= "red", pch=16)
+
+# Add the .95 lower bound as a vertical line
+xbound = bayesprev_bound(0.95, k_hr_pup_1t, 50)
+pbound = bayesprev_posterior(xbound, k_hr_pup_1t, 50)
+lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)
+
+# Add the 0.96 HPDI
+int = bayesprev_hpdi(0.96, k_hr_pup_1t, 50) #0.02561301 0.24410451
+i1 = int[1]
+i2 = int[2]
+h1 = bayesprev_posterior(i1, k_hr_pup_1t, 50)
+h2 = bayesprev_posterior(i2, k_hr_pup_1t, 50)
+lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
+
+# hr scr_1t - 1t
+
+# plot posterior distribution of population prevalence
+
+xvals <- seq(0, 1, .01)
+k_hr_scr_1t <- sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_hr_scr_1t)
+# k_hr_pup/50
+binom.test(k_hr_scr_1t, 50, p = 0)
+# number of successes = 7, number of trials = 50, p-value < 0.00000000000000022
+
+pdf_hr_scr_1t <- bayesprev_posterior(xvals, k_hr_scr_1t, 50) # function needed
+pdf_hr_scr_1t
+
+plot(xvals, pdf_hr_scr_1t, type ="l", xlab = expression(gamma), 
+     ylab ="Posterior density", lwd=3)
+
+# Add the MAP estimate as a point
+# MAP = Maximum
+
+xmap = bayesprev_map(k_hr_scr_1t, 50)
+pmap = bayesprev_posterior(xmap, k_hr_scr_1t, 50)
+points(xmap, pmap, cex =2, col= "red", pch=16)
+
+# Add the .95 lower bound as a vertical line
+xbound = bayesprev_bound(0.95, k_hr_scr_1t, 50)
+pbound = bayesprev_posterior(xbound, k_hr_scr_1t, 50)
+lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)
+
+# Add the 0.96 HPDI
+int = bayesprev_hpdi(0.96, k_hr_scr_1t, 50) #0.1214375 0.3875048
+i1 = int[1]
+i2 = int[2]
+h1 = bayesprev_posterior(i1, k_hr_scr_1t, 50)
+h2 = bayesprev_posterior(i2, k_hr_scr_1t, 50)
+lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
+
+# scr pup 1t
+# plot posterior distribution of population prevalence
+?t.test
+t.test(db_full6new_hr_fix_stim_nt1.1_bp2$cor_pup_scr, 
+       alternative = c("greater"))
+
+xvals <- seq(0, 1, .01)
+k_pup_scr_1t <- sum(db_full6new_hr_fix_stim_nt1.1_bp2$indsig_pup_scr_1t)
+# number of successes = 12, number of trials = 50, p-value = 0.0003059
+# k_pup_pup/50
+binom.test(k_pup_scr_1t, 50, p = 0.5)
+# number of successes = 7, number of trials = 50, p-value < 0.00000000000000022
+# number of successes = 6, number of trials = 50, p-value = 0.00000003244
+
+pdf_pup_scr_1t <- bayesprev_posterior(xvals, k_pup_scr_1t, 50) # function needed
+pdf_pup_scr_1t
+
+plot(xvals, pdf_pup_scr_1t, type ="l", xlab = expression(gamma), 
+     ylab ="Posterior density", lwd=3)
+
+# Add the MAP estimate as a point
+# MAP = Maximum
+
+xmap = bayesprev_map(k_pup_scr_1t, 50)
+pmap = bayesprev_posterior(xmap, k_pup_scr_1t, 50)
+points(xmap, pmap, cex =2, col= "red", pch=16)
+
+# Add the .95 lower bound as a vertical line
+xbound = bayesprev_bound(0.95, k_pup_scr_1t, 50)
+pbound = bayesprev_posterior(xbound, k_pup_scr_1t, 50)
+lines(c(xbound, xbound), c(0, pbound+0.5), col="blue", lwd=3)
+
+# Add the 0.96 HPDI
+int = bayesprev_hpdi(0.96, k_pup_scr_1t, 50) #0.08783098 0.34143456
+i1 = int[1]
+i2 = int[2]
+h1 = bayesprev_posterior(i1, k_pup_scr_1t, 50)
+h2 = bayesprev_posterior(i2, k_pup_scr_1t, 50)
+lines(c(i1, i2), c(h1, h2), col ="green", lwd=3)
+
+```

### 2022-05-28 PCA figures1.Rmd
MFA figures

---
title: "Figures"
author: "Helio"
date: "15/02/2022"
output: html_document
---

```{r}
library(FactoMineR)
library(factoextra)

newDF <- clustering_new_pre_PCA3.1[,c("ssid","stimDescription","val_cut_iaps","pup_basCor","Bio_Mean_HR_dif","log_BIO_CDA.PhasicMax","arousal","valence")]
newDF2 <- clustering_new_pre_PCA3.1[,c("stimDescription","val_cut_iaps","pup_basCor","Bio_Mean_HR_dif","log_BIO_CDA.PhasicMax","arousal","valence")]
res.MFA<-MFA(newDF,group=c(3,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),num.group.sup=c(1),graph=FALSE)

?plot.MFA

colnames(newDF)
colnames(newDF) <- c("subject", "stimuli", "norm", "pupil", "HR", "SCR", "arousal", "valence")

table(if_else(newDF$norm == "neg", "negative",
                    if_else(newDF$norm == "mid", "mid",
                     if_else(newDF$norm == "pos", "positive", NULL))))

newDF$norm<- if_else(newDF$norm == "neg", "negative",
                    if_else(newDF$norm == "mid", "mid",
                     if_else(newDF$norm == "pos", "positive", NULL)))

table(is.na(newDF$norm))

colnames(newDF)
res.MFA_val<-MFA(newDF,group=c(3,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),num.group.sup=c(1),graph=FALSE)

plot.MFA(res.MFA, choix="ind",lab.par=FALSE,invisible= c('ind','quali'),select='cos2  0.2',habillage='val_cut_iaps',title="Individual factor map")

# drop sid

newDF2_stim_val <- newDF[,c("stimuli","norm","pupil", "HR", "SCR", "arousal", "valence")]
res.MFA_stim_val<-MFA(newDF2_stim_val,group=c(2,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),num.group.sup=c(1),graph=TRUE)

plot.MFA(res.MFA_stim_val)
?plot.MFA

Factoshiny::MFAshiny(newDF2_stim_val)
factoextra::fviz_mfa(res.MFA_stim_val, geom = "point",
                      choix="ind",
                      invisible= c('quali'))

library(FactoMineR)
library(tidyverse)
plot.MFA(res.MFA_stim_val, 
         choix="ind",

         label = "none",

         lab.par=TRUE,
         invisible= c('ind', 'quali'),

         # habillage='norm',
         col.ind = "cos2",
         title="Individual factor map") +
  theme_classic()
  p$graphstyle_int

newDF <- newDF2_stim_val[,c("stimuli","norm","pupil","HR","SCR","arousal","valence")]

sf = 1 # scaling factor to make it easier to change sizes of everything, in which case change here
p<- list()
p$graphstyle_int <-  theme(#base plot theme

  # axis lines
  axis.line.y = element_line(color="black", size = 1.5),
  axis.line.x = element_line(color="black", size = 1,5),

  axis.title.y=element_text(size = 14*(sf+.1), margin=margin(0,5,0,0)),
  axis.title.x=element_text(size = 14*(sf+.1), margin=margin(0,5,0,0)),

  # text
  strip.text.x = element_text(size = 15*(sf+.1),  colour = "black"),
  strip.text.y = element_text(size = 15*(sf+.1),  colour = "black"),

  text=element_text(size = 14),#family = "arial", 
  axis.text.x = element_text(size = 14*(sf+.1),colour = "black"), # family = "arial", 
  axis.text.y = element_text(size = 14*(sf+.1), colour = "black"),#√

  # panel
  # pane
  # panel.grid.major = element_line(colour="black"),
  # panel.background = element_blank(),
  # panel.background = element_rect(fill="black"),
  # panel.border = element_rect(color="black"),
  # strip shades (reco rectagles)
   # strip.background = element_rect(fill="black"),

  # legend
  legend.position = "top",
  legend.key = element_rect(colour = "transparent", fill="transparent"),
  legend.direction = "horizontal",

  legend.text = element_text(size = 10*(sf+.3)),
  # legend.title = element_text(size = 10*(sf+.3)),
  # legend line tends to be really small in print so adjust here
  # legend.key.height = unit(5, "cm"),
  legend.key.width = unit(1, "cm"),
  # lege
  # legen

  # title
  plot.title = element_text(hjust = .5)

  #legend.text = element_text(size = 10*sf),
  # legend.title=element_blank(),
  #legend.text = element_blank(),
  #axis.ticks = element_blank(),
)

newDF2_stim_val %>%
  group

# centering ensures that we don't prioritise specific participants due to their extreme values
# we still capture the covarince within participants
clustering_new_pre_PCA3.1%>%
  group_by(ssid)%>%
  mutate_if(is.numeric, scale)

newDFscale_sid_norm<- newDF%>%
  group_by(subject)%>%
  mutate_if(is.numeric, scale)%>%
  group_by(subject, norm)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

newDFscale_stim<- newDF$subject%>%
  group_by(subject, subject_orig)%>%
  mutate_if(is.numeric, scale)%>%
  group_by(stimuli, norm)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

newDFscale<- newDF%>%
  group_by(subject)%>%
  mutate_if(is.numeric, scale)

colnames(newDFscale)
res.MFA_stim_val<-MFA(newDF2_stim_val,group=c(2,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),num.group.sup=c(1),graph=TRUE)
res.MFA_stim_val_scale<-MFA(newDFscale[,c(2,4:8)],group=c(1,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),num.group.sup=c(1),graph=TRUE)
res.MFA_stim_val_scal2e<-MFA(newDFscale[,3:8],group=c(1,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),num.group.sup=c(1),graph=TRUE)

FactoMineR::MFA(newDFscale[,3:8],group=c(1,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),num.group.sup=c(1),graph=TRUE)

res.MFA_stim_val_scale$group$cos2
Factoshiny::MFAshiny(newDFscale)

colnames(newDFscale_sid_norm)
res.MFA_stim_val_scal2e_sidnorm <-MFA(newDFscale_sid_norm[,1:7],group=c(2,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),
                                      num.group.sup=c(1),graph=TRUE)

# stim plot

res.MFA_stim_val_scal2e_stim <-MFA(newDFscale_stim[,1:7],group=c(2,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),
                                      num.group.sup=c(1),graph=TRUE)

# BADIA

res.MFA_stim_val_scal2e_stim

clustering_new_pre_PCA2

design_notm<- factor(newDFscale_stim$norm)
library(TExPosition)

TInPosition::tepBADA.inference.battery(newDFscale_stim[,3:7], 
                                                       scale = FALSE, 
                                                       center = TRUE, 
                                                       # DESIGN = factor( clustering_new_pre_PCA2$arousal_3cat ),
                                       DESIGN = newDFscale_stim$norm,
                                                       make_design_nominal = TRUE,
                                                       group.masses = NULL, 
                                                       weights = NULL, 
                                                       graphs = TRUE, 
                                                       k = 2, 
                                                       test.iters = 1000, 
                                                       critical.value = 2)

bada_all<- TInPosition::tepBADA.inference.battery(newDFscale[,4:8], 
                                                       scale = FALSE, 
                                                       center = FALSE, 
                                                       # DESIGN = factor( clustering_new_pre_PCA2$arousal_3cat ),
                                       DESIGN = newDFscale$norm,
                                                       make_design_nominal = TRUE,
                                                       group.masses = NULL, 
                                                       weights = NULL, 
                                                       graphs = TRUE, 
                                                       k = 2, 
                                                       test.iters = 1000, 
                                                       critical.value = 2)

# sid

newDFscale_sid<- newDF%>%
  group_by(subject)%>%
  mutate_if(is.numeric, scale, scale = FALSE)%>%
  group_by(subject)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

  mean(newDFscale_sid$HR)

res.MFA_stim_val_scal2e_sid <-MFA(newDFscale_sid[,1:6],group=c(1,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),
                                      num.group.sup=c(1),graph=TRUE)

# get the first two components and do clustering on it

res.MFA_stim_val_scal2e_stim$global.pca

MFAstimtoKmeans <- bind_cols(as.data.frame(res.MFA_stim_val_scal2e_stim[["ind"]][["coord"]]), newDFscale_stim[,c(1:2)])
MFAsidtoKmeans <- bind_cols(as.data.frame(res.MFA_stim_val_scal2e_sidnorm[["ind"]][["coord"]]), newDFscale_sid_norm[,c(1:2)])

MFAsid2toKmeans <- bind_cols(as.data.frame(res.MFA_stim_val_scal2e_sid[["ind"]][["coord"]]), newDFscale_sid[,c(1:2)])

db_full_sum_2$subject<-as.character(db_full_sum_2$ssid)
left_join(MFAsid2toKmeans,db_full_sum_2 )%>%
  ggplot(aes(Dim.1, TASc))+
  geom_point()+
  ggpubr::stat_cor()

left_join(MFAsid2toKmeans,db_full_sum_2 )%>%
  ggplot(aes(Dim.2, TASc))+
  geom_point()+
  ggpubr::stat_cor()

left_join(MFAsid2toKmeans,db_full_sum_2 )%>%
  ggplot(aes(Dim.2, AQc))+
  geom_point()+
  ggpubr::stat_cor()

multilMFAtokmeans<-bind_cols(as.data.frame(res.MFA_stim_val_scale[["ind"]][["coord"]]), newDFscale[,c(1:3,9)])

multilMFAtokmeans$subject
cor.test(MFAstimtoKmeans$Dim.1, MFAstimtoKmeans$Dim.2)
write_csv( MFAsidtoKmeans, "MFAsidtoKmeans.csv")
write_csv( MFAstimtoKmeans, "MFAstimtoKmeans.csv")
write_csv( multilMFAtokmeans, "multilMFAtokmeans.csv")

Factoshiny::MFAshiny(newDFscale_sid_norm)

Factoshiny::MFAshiny(newDFscale_stim)

library(readr)
HCPCshinyvariableand_clusters <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/HCPCshinyvariableand_clusters1.csv")
View(HCPCshinyvariableand_clusters)

HCPCshinyvariableand_clusters<- HCPCshinyvariableand_clusters%>%
 gather(cluster, value, -X1)

write_csv(HCPCshinyvariableand_clusters, "HCPCshinyvariableand_clusters.csv")

HCPCshinyvariableand_clusters$X1<- if_else(HCPCshinyvariableand_clusters$X1 == "norm=positive",
                                           "positive",
                                            if_else(HCPCshinyvariableand_clusters$X1 == "norm=negative", "negative",
                                                     if_else(HCPCshinyvariableand_clusters$X1 == "norm=mid", "mid",HCPCshinyvariableand_clusters$X1)))

HCPCshinyvariableand_clusters$X1<- factor(HCPCshinyvariableand_clusters$X1, levels = c("positive", "mid", "negative", "pupil", "SCR", "HR", "valence", "arousal"))

HCPCshinyvariableand_clusters%>%
  mutate(variable = as.factor(if_else(X1 == "mid", "norm",
                                      if_else(X1 == "negative", "norm",
                                              if_else(X1 == "positive", "norm", "quantitative")))))%>%
  # subset(variable == "norm")%>%

         # HCPCshinyvariableand_clusters %>%
ggplot(aes(cluster,X1,  fill = value))+
    geom_tile()+
  # facet_grid(~variable)+
  theme_classic()+
  # geom_text(aes(label = sig))+
  p$graphstyle+
  scale_fill_viridis_c("inferno")

```

```{r}
plot.MFA(res.MFA_stim_val, 
         choix="ind",
         partial='all',
         lab.par=TRUE,
         invisible= c('ind','quali'),
         select='cos2  0',
         habillage='group',
         title="Individual factor map")+
  theme_classic()
  p$graphstyle_int

  # plot the scaled within a person
mfa_plots$ind1

res.MFA_stim_val_scale
 mfa_plots$ind1 <- plot.MFA(res.MFA_stim_val_scale, 
         choix="ind",
         partial='all',
         label = "norm",
         lab.par=TRUE,
         invisible= c('ind','quali'),
         select='cos2  0',
         habillage='group',
         title="Individual factor map",
         alpha = .2,
         shadowtext = TRUE,
         cex = 1)+
  xlab(paste0("Dimension 1 (",round(mean(res.mfa_bio_vs_self2_scale$eig[1,2], na.rm = TRUE),2),"%[95%CI:",
              paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
                     round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
  ylab(paste0("Dimension 2 (",round(mean(res.mfa_bio_vs_self2_scale$eig[2,2], na.rm = TRUE),2),"%[95%CI:",
              paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
                     round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
  annotate("text", label = paste0("total var: ", round(res.mfa_bio_vs_self2_scale$eig[2,3], 2), "%"), x = 2, y = -1.3, size = 5)+
       scale_color_brewer(palette = "Dark2", labels = c("autonomic", "subjective"))+
  theme_classic()+
  p$graphstyle_int+
   guides(colour = guide_legend(override.aes = list(size=2, stroke=1.5)))

 guides(fill = guide_legend(override.aes = list(linetype = "solid", size = 1) ))

 mfa_plots$ind1
   coord_fixed(ratio = 1)

   # custom plot
 mfa_plots$ind1

 ggsave("indi_factomap.tiff",  mfa_plots$ind1, device = "tiff", width = 10, height = 6, dpi = 800)
```

```{r}
  ?geom_point
ind_inertial<- as.data.frame(res.MFA_stim_val_scale[["quali.var.sup"]][["within.inertia"]])

ind_coord<- as.data.frame(res.MFA_stim_val_scale[["quali.var.sup"]][["coord"]])

ind_inertial%>%
  mutate(stimuli = row.names(ind_inertial))%>%
  ggplot(aes(x = Dim.1, Dim.2))+
  geom_point()

ind_parial_group<-as.data.frame(res.MFA_stim_val_scale[["quali.var.sup"]][["coord.partiel"]])

# strsplit("test.fuck", "[.]")[[1]][1]
ind_parial_group<- ind_parial_group%>%
  mutate(variable = row.names(ind_parial_group))%>%
  mutate(group = if_else(grepl("autonomic",variable), "autonomic", "subjective"))%>%
  group_by(variable)%>%
  mutate(stimuli = strsplit(variable, "[.]")[[1]][1])

ind_coord<- ind_coord%>%
  mutate(stimuli = row.names(ind_coord))

ind_coord%>%
  mutate(stimuli = row.names(ind_coord))%>%
  ggplot(aes(x = Dim.1, Dim.2))+
  # coord_fixed(ratio = 1)+
  geom_point(shape = 0, size = 2)+
  ylim(-1.5,1)+
  geom_line(aes)

ind_coord2_aut<- left_join(ind_coord, subset(ind_parial_group, group == "autonomic"), by = "stimuli")
ind_coord2_aut_subj<- left_join(ind_coord2_aut, subset(ind_parial_group, group != "autonomic"), by = "stimuli")

left_join(ind_coord, ind_parial_group, by = "stimuli")

ind_coord2_aut_subj$Dim.1.x_center<- ind_coord2_aut_subj$Dim.1.x
ind_coord2_aut_subj%>%
    ggplot(aes(x = Dim.1.x, Dim.2.x))+
  # coord_fixed(ratio = 1)+
  geom_point(shape = 0, size = 2)+
   geom_point(aes(Dim.1.y, Dim.2.y), shape = 0, size = 2, color = "red")+
  geom_line(aes(Dim.1.x_center, Dim.2.y))
  scale_color_brewer(palette = "Dark2", direction = -1)

  # ylim(-1.5,1)+
  geom_l(aes(x = Dim.1.x, y = Dim.1.y))

left_join(ind_coord, ind_parial_group, by = "stimuli") %>%

    ggplot(aes(x = Dim.1.x, Dim.2.x))+
  # coord_fixed(ratio = 1)+
  geom_point(shape = 0, size = 2)+
   geom_point(aes(Dim.1.x, Dim.2.y, group = group), shape = 0, size = 2, color = "red")+
  geom_line(aes(Dim.1.x, Dim.2.y, color = group, group = group))
  scale_color_brewer(palette = "Dark2", direction = -1)

  # ylim(-1.5,1)+
  geom_l(aes(x = Dim.1.x, y = Dim.1.y))

  left_join(ind_coord, ind_parial_group, by = "stimuli") %>%
    # subset(group == "autonomic")%>%
      mutate(Dim.2centerx = Dim.2.x)%>%
     mutate(Dim.1centery = Dim.1.y)%>%
 ggplot(aes(x = Dim.1.x, Dim.2.x))+
 # coord_fixed(ratio = 1)+
# geom_point(shape = 7, size = 2, alpha = .5)+
geom_point(aes(Dim.1.y, Dim.2.y, color = group), shape = 0, size = 2)+

geom_line(aes(Dim.1.y, Dim.2.y, group = stimuli), linetype = "dashed", alpha = .3)+
    geom_text(aes(label = stimuli, x = Dim.1.x, y = Dim.2.x))+
    theme_classic()+
    p$graphstyle_int
```

# just norm

```{r}
?plot.MFA

res.MFA_stim_val_scale_norm<-MFA(newDFscale[,3:8],group=c(1,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),num.group.sup=c(1),graph=TRUE)
plot.MFA(res.MFA_stim_val_scale_norm, 
         geom = "point",
         choix="ind",
         partial='all',
         # label = "norm",
         lab.par=TRUE,
         invisible= c('ind', "qua"),
         select='cos2  0',
         habillage='norm',
         title="Individual factor map",
         alpha = .2,
         shadowtext = TRUE)+
  theme_classic()+
  p$graphstyle_int
quartz()

mfa_plots$ind2_cat_val<- plot.MFA(res.MFA_stim_val_scale_norm, 
         choix="ind",
         partial='all',
         label = "norm",
         lab.par=TRUE,
         invisible= c('ind','quali'),
         select='cos2  0',
         habillage='group',
         title="Individual factor map",
         alpha = .2,
         # ellipse= TRUE,
         graph.type = "ggplot",
         cex=2) + #text size
  xlab("Dimension 1")+
   xlab("Dimension 2")+
  ggtitle("factor map")+
    xlab("Dimension 1")+
   ylab("Dimension 2")+
  scale_color_brewer(palette = "Dark2")+
    # scale_fill_brewer(palette = "Dark2")+
  theme_classic()+
  p$graphstyle_int+
  theme(legend.position = "none",
        plot.title = element_blank())

mfa_plots$ind2_cat_val+
  coord_fixed(ratio = 1)

   ggsave("indi_factomap_catval.tiff", mfa_plots$ind2_cat_val, device = "tiff", width = 10, height = 6, dpi = 800)

 mfa_plots$ind2_cat_val<-  mfa_plots$ind2_cat_val +scale_y_continuous(
  labels = scales::number_format(accuracy = 0.1))+ #force two digits in y 
     ylim(-.2,.2)

    ggsave("indi_factomap_catval.tiff", mfa_plots$ind2_cat_val, device = "tiff", width = 7, height = 5, dpi = 800)
```

mfa_plots$ind12<- mfa_plots$ind1+
    annotate("text", label = normtest$norm, x = normtest$Dim.1, y =normtest$Dim.2, size = 5, color = "blue")+
geom_point(aes(x =  normtest$Dim.1, y  = normtest$Dim.2), color = "blue", size = 5, shape = 2)

mfa_plots$ind12

# individuals
library(tidyverse)
newDFscale1<- newDFscale%>%
  subset(subject!= 900)

res.MFA_stim_val_scale_ssid<-MFA(newDFscale[,c(1,4:8)],group=c(1,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),num.group.sup=c(1),graph=TRUE)

```{r}
dev.off()

mfa_plots$ind13_sid<- plot.MFA(res.MFA_stim_val_scale_ssid, 
         choix="ind",
         # geom = c("point"),
         partial='all',
         lab.par=TRUE,
         # label = "subject",
         invisible= c("ind", "quali"),
         select='cos2  0',
         habillage='group',
         title="Individual factor map"
         # alpha = .1
         )+
         # ylim = c(-1,1))

    xlab("Dimension 1")+
   ylab("Dimension 2")+
  scale_color_brewer(palette = "Dark2")+
    # scale_fill_brewer(palette = "Dark2")+
  theme_classic()+
  p$graphstyle_int+
  theme(legend.position = "none",
        plot.title = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank())

  mfa_plots$ind13_sid
    coord_fixed(ratio = 1)
   ggsave("indi_factomap_csid.tiff",   mfa_plots$ind13_sid, device = "tiff", width = 10, height = 6, dpi = 800)

      ggsave("indi_factomap_csid.pdf",   mfa_plots$ind13_sid, device = "pdf", width = 10, height = 6, dpi = 800)

   theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))
mfa_plots$ind13_sid

knitr::plot_crop(indi_factomap_csid.pdf)

```
```{r fig.height = 2, fig.width = 10}
theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))
mfa_plots$ind13_sid
#your plot code
```

patchwork

```{r}
library(patchwork)

mfa_plots$ind1+mfa_plots$ind2_cat_val+ mfa_plots$ind13_sid +
  plot_layout(ncol = 3, widths = c(2,1,1), heights = c(1,1,1))

fviz_mfa_var(res.mfa, "group")

theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))

```

Groups representatin

```{r}
mfa_plots

seq(0,1,.1)
res.MFA_stim_val_scale$group$coord.sup
?  geom_label

View(res.MFA_stim_val_scale)
# considering setting the seize of the size of qualitatie s,aller than the others

test<-bind_rows(as.data.frame(res.MFA_stim_val_scale$group$coord),
          as.data.frame(res.MFA_stim_val_scale$group$coord.sup))%>%
  mutate(group = rownames(bind_rows(as.data.frame(res.MFA_stim_val_scale$group$coord),
          as.data.frame(res.MFA_stim_val_scale$group$coord.sup))))

group_df<- bind_rows(as.data.frame(res.MFA_stim_val_scale$group$coord),
          as.data.frame(res.MFA_stim_val_scale$group$coord.sup))%>%
  mutate(group = rownames(bind_rows(as.data.frame(res.MFA_stim_val_scale$group$coord),
          as.data.frame(res.MFA_stim_val_scale$group$coord.sup))))%>%
  mutate(group = factor(group, levels = c("subjective","autonomic",  "qualitative"),
                        labels = c("subjective","autonomic", "categorical")))

group_df$tyextsize<- if_else(group_df$group == "autonomic", 2,
                             if_else(group_df$group == "subjective", 2, 1))
                             ))

group_df$tyextsize

mfa_plots$groups <- bind_rows(as.data.frame(res.MFA_stim_val_scale$group$coord),
          as.data.frame(res.MFA_stim_val_scale$group$coord.sup))%>%
  mutate(group = rownames(bind_rows(as.data.frame(res.MFA_stim_val_scale$group$coord),
          as.data.frame(res.MFA_stim_val_scale$group$coord.sup))))%>%
  mutate(group = factor(group, levels = c("autonomic", "subjective","qualitative"  ),
                        labels = c("autonomic","subjective","categorical")))%>%
  ggplot(aes(x = seq(0,1,.1), y =seq(0,1,.1)))+
  geom_vline(xintercept = res.mfa_bio_vs_self2_scale$group$coord[1,1], linetype = "dashed")+
  geom_vline(xintercept = res.mfa_bio_vs_self2_scale$group$coord[2,1], linetype = "dashed")+
    geom_hline(yintercept = res.mfa_bio_vs_self2_scale$group$coord[1,2], linetype = "dashed")+
  geom_hline(yintercept = res.mfa_bio_vs_self2_scale$group$coord[2,2], linetype = "dashed")+
  geom_point(aes(x = Dim.1, y = Dim.2, shape = group, fill = group, color = group), size = 8, alpha = .5)+

   # size = tyextsize*8
  geom_text(aes(x = Dim.1, y = Dim.2+.05, label = group, color = group 
               ), size = 8)+
    # annotate("text",label = group x = Dim.1, y = Dim.2))+
  xlim(0,1)+
      theme_classic()+
      xlab("Dimension 1")+
   ylab("Dimension 2")+
  ggtitle("Groups representation")+
  scale_color_brewer(palette = "Dark2", direction = -1)+
    scale_fill_brewer(palette = "Dark2",direction = -1)+
  theme(legend.position = "none",

        # axis.text.x = element_blank(),
        # axis.text.y = element_blank(),
        plot.title = element_text(hjust = .5, size = 16*(sf+.5)))

  # theme(g) = element_blank())

  mfa_plots$groups<- mfa_plots$groups+
    scale_colour_brewer(palette = "Dark2",
                      labels=c("categorical","autonomic","subjective"))+
    scale_fill_brewer(palette = "Dark2",
                      labels=c("categorical","autonomic","subjective"))

  mfa_plots$groups  +p$graphstyle_int
```
```{r}
  mfa_plots$groups<-   mfa_plots$groups+
    # coord_fixed(ratio = 1)+
    p$graphstyle_int+
    theme(legend.title = element_blank())
  # 
  # 
  mfa_plots$groups<- mfa_plots$groups+    
    # p$graphstyle_int+
   guides(
  fill = guide_legend(

    override.aes = aes(label = "")
  )
)

mfa_plots$groups<- mfa_plots$groups+
scale_y_continuous(
  labels = scales::number_format(accuracy = 0.2))
mfa_plots$groups

 ggsave("groups.tiff", mfa_plots$groups, device = "tiff", width = 10, height = 6, dpi = 800)

  ggsave("groups2.tiff", mfa_plots$groups, device = "tiff", width = 10, height = 10, dpi = 800)
    ggsave("groups3.tiff", mfa_plots$groups, device = "tiff", width = 10, height = 8, dpi = 800)

    ggsave("groups5.tiff", mfa_plots$groups, device = "tiff", width = 7, height = 7, dpi = 800)
     ggsave("groups3.tiff", mfa_plots$groups, device = "tiff", width = 7, height = 5, dpi = 800)

     ggsave("groups3.tiff", mfa_plots$groups, device = "tiff", width = 7, height = 7, dpi = 800)
```

```{r}
mfa_plots$cor_circle<- plot.MFA(res.MFA_stim_val_scale, choix="var",habillage='group',title="Correlation circle",
         cex = 2.7) +
    xlim(-1,1)+
  scale_color_brewer(palette = "Dark2", direction = -1)+
  theme_classic()+

      xlab("Dimension 1")+
   ylab("Dimension 2")+
  # ggtitle("Groups representation")+
  scale_color_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+
    p$graphstyle_int+
  theme(legend.position = "none",

        # axis.text.x = element_blank(),
        # axis.text.y = element_blank(),
        plot.title = element_text(hjust = .5, size = 16*(sf+.5)))

mfa_plots$cor_circle+
  theme(plot.margin=unit(c(0,-.4,0,-.5), "null"))
mfa_plots$cor_circle

 ggsave("cor_circle.tiff",   mfa_plots$cor_circle, device = "tiff", width = 10, height = 6, dpi = 800)

```

```{r}
mfa_plots$partial<- plot.MFA(res.MFA_stim_val_scale, choix="axes",habillage='group',cex=1.35,cex.main=1.35,cex.axis=1.35)+
  xlim(-1,1)+
   theme_classic()+
     xlab("Dimension 1")+
   ylab("Dimension 2")+
  # ggtitle("Groups representation")+
  scale_color_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+
    p$graphstyle_int+
  theme(legend.position = "none",

        # axis.text.x = element_blank(),
        # axis.text.y = element_blank(),
        plot.title = element_text(hjust = .5, size = 16*(sf+.5)))

mfa_plots$partial

 ggsave("partial.tiff",   mfa_plots$partial, device = "tiff", width = 10, height = 6, dpi = 800)

circle_partialpatch <- (mfa_plots$cor_circle+theme(axis.text.x = element_blank(),
                                                   axis.title.x = element_blank()))/mfa_plots$partial

 ggsave("circle_partialpatch.tiff",   circle_partialpatch, device = "tiff", width = 5, height = 10, dpi = 800)

```

```{r}

mfa_plots_eigen_value_boot<-
eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
   # gather(dimension, value_dimenion, -group, -sim_no) %>%
  group_by(component)%>%
  # subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
  ungroup()%>%
  mutate(eig_obs_dim = if_else(component == "comp 1", 
                               res.mfa_bio_vs_self2_scale$eig[1],
                               res.mfa_bio_vs_self2_scale$eig[2])) %>% #create 95% to descrive interval around the observed estimate
  mutate(Dimension =  if_else(component == "comp 1", "Dimension 1", "Dimension 2"))%>%
  subset(Dimension == "Dimension 1")%>%
  # also store observed eige for each dimensions
  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
  ggplot(aes(eigenvalue))+
  geom_histogram(aes(y=..density..), alpha = .3) +  # scale histogram y

  geom_errorbar(aes(xmin = perc_5, xmax=perc_95, y = 1), color = "gray30", size = 1.5)+
  geom_point(aes(x = eig_obs_dim, y = 1),size = 3, color = "red", alpha = .3)+

  theme_classic()+
    # geom_vline(aes(xintercept = perc_95),size = 2, linetype = "dashed", alpha = .6)+
    geom_vline(xintercept = 1,size = 2, linetype = "dashed", alpha = .6)+
  # geom_vline(aes(xintercept = perc_5), linetype = "dashed")+
    # geom_vline(aes(xintercept = perc_95), linetype = "dashed")+

  geom_hline(yintercept = 0, linetype = "dashed")+
  # facet_grid(~component)+
  # coord_fixed(ratio = 1)
  ggtitle("distribution of boostraped eigenvalues for\n largest dimension (10000 samples)")+
  annotate("text", label = "95%CI", x = 1.15, y = 2, size = 5*(sf+.8))+
    p$graphstyle_int

mfa_plots_eigen_value_boot

reshufrds<- read_rds("eigen_first_reshuf.Rds")

reshufrds<- as.data.frame(reshufrds)
# install.packages(expres)
mfa_plots$resample<-
reshufrds%>%
  mutate(component =as.factor(substr(rownames(reshufrds), 1,6)))%>% #retrieve names for components
   mutate(Dimension =  if_else(component == "comp 1", "Dimension 1", "Dimension 2"))%>%
  subset(!is.na(eigenvalue))%>% #select only component 1 and remove nas I introduced in the dataframe
  group_by(component)%>%

   mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
  ungroup()%>%
    group_by(component)%>%
  mutate(eig_obs_dim = if_else(component == "comp 1", 
                               res.mfa_bio_vs_self2_scale$eig[1],
                               res.mfa_bio_vs_self2_scale$eig[2])) %>% #store observed to visualise ion the null
  mutate(prob = paste(((sum(eigenvalue>=eig_obs_dim))/n())*100, paste0("%"))) %>%
  subset(Dimension == "Dimension 1")%>%
  ggplot(aes(eigenvalue))+
  geom_histogram(aes(y=..density..),bins = 500, alpha = .3) +  # scale histogram y
  # geom_density(col = "red", alpha = .001)+
  # facet_grid(~component)+
    geom_vline(aes(xintercept = perc_95),size = 2, linetype = "dashed", alpha = .6)+
  geom_point(aes(x = eig_obs_dim, y = 1),size = 3,  color = "red", alpha = .5)+

  theme_classic()+
  ggtitle("null distribution of eigenvalues for\n largest dimension (10000 samples)")+
  annotate("text", label = "p < .001", x = 1.16, y = 3, hjust = .5, color = "red", size = 5*(sf+.8))+
   annotate("text", label = paste0(expression(alpha), " < .05"), x = 1.05, y = 20, hjust = .5, size = 5*(sf+.8), parse = TRUE)+
  p$graphstyle_int

mfa_plots_eigen_value_boot+mfa_plots$resample

mfa_plots$resample

```

```{r}
left_join(cor_first1, cor.test_obsmfa, by = c("variable", "dimension")) %>%
  subset(dimension == "Dim.1")%>%
  ggplot(aes(value_dimenion.x, color = variable)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-2 ))+ #color = "gray30"
  # facet_grid(~dimension)+
  geom_point(aes(x = value_dimenion.y, y = -2))+
    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)
  # facet_grid(~dimension)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+

  theme_classic()

  mfa_plots$cor_var_dimension<-
  mfa_boot_corfirst%>%
  subset(dimension == "Dim.1")%>%
    mutate(measure = factor(measure, levels = c("pupil", "SCR", "HR", "valence", "arousal")))%>%
  ggplot(aes(value_dimenion.x, fill =measure, color = measure)) +
  geom_histogram(aes(y=..density..,fill =measure,color = measure, linetype = measure),alpha=0.2,
                 position="identity")+
  geom_density(aes(fill = measure, linetype = measure), alpha = .1) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-2 , linetype = measure))+ #color = "gray30"
  # facet_grid(~dimension)+
  geom_point(aes(x = value_dimenion.y, y = -2))+
    geom_vline(xintercept = 0,linetype = "dashed", alpha = .5, size = 1)+
    xlim(-1,1)+
    xlab("correlation with largest dimension")+
  # facet_grid(~dimension)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+

  theme_classic()+
  p$graphstyle_int+
    theme(legend.title = element_blank())

    mfa_plots$cor_var_dimension<-mfa_plots$cor_var_dimension+
      guides(colour=guide_legend(nrow=2,byrow=TRUE))

```

groups

```{r}

mfa_plots$group_boot<-

left_join(groups_first_1boot_CIcorrected2, groups_first_obs,by = c("group", "dimension"))%>%
  subset(!is.na(value_dimenion))%>%
  group_by(dimension,group)%>%
   mutate(perc_5 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 2600)[1],
         perc_95 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 2600)[2])%>%

  subset(dimension == "Dim.1")%>%
    mutate(group = if_else(group == "auto", "autonomic", "subjective"))%>%

   ggplot(aes(value_dimenion, color = group)) +

   geom_histogram(aes(y=..density..,fill =group,color = group, linetype = group),alpha=0.2,
                 position="identity")+
  geom_density(aes(fill = group, linetype = group), alpha = .1) +
  #  geom_histogram(aes(y=..density..), alpha=0.5,
  #                position="identity")+
  # geom_density(alpha=.2) +

   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-1, fill =group,color = group, linetype = group))+
    geom_point(aes(x = value_dimenion_obs, y = -1))+
   # geom_point(aes(x = value_dimenion_obs, y = -3))+
       geom_vline(xintercept = 0,linetype = "dashed", alpha = .5, size = 1)+

  # facet_grid(~dimension)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()+
   # xlim(-1,1)+
    xlab("correlation with largest dimension")+
  # facet_grid(~dimension)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+

  theme_classic()+
  p$graphstyle_int+
    theme(legend.title = element_blank())

mfa_plots$patchbootresample <-  (mfa_plots$resample+ mfa_plots_eigen_value_boot +
  mfa_plots$group_boot + mfa_plots$cor_var_dimension)+
  plot_layout(nrow = 2)

ggsave("patch_res_boot.tiff", mfa_plots$patchbootresample,
       device = "tiff",
       width = 10, height = 10, dpi = 800)

```

patchwork

```{r}
?plot_layout
((mfa_plots$ind1 +mfa_plots$ind2_cat_val/mfa_plots$ind13_sid)+ 
    (mfa_plots$groups + mfa_plots$cor_circle / mfa_plots$partial))+
  plot_layout(nrow = 2)+
  plot_annotation(tag_levels = "A")

 # widths = c(2,1,1), heights = c(1,1)

```

```{r}

plot.MFA(res.MFA_stim_val_scale, choix="group",
         cex=2.5,
         cex.main=2.5,
         cex.axis=1.7)+
    theme_classic()+
      xlab("Dimension 1")+
   ylab("Dimension 2")+

  scale_color_brewer(palette = "Dark2", direction = -1)+
    scale_fill_brewer(palette = "Dark2", direction = -1)+
  geom_vline(xintercept = res.mfa_bio_vs_self2_scale$group$coord[1,1], linetype = "dashed")+
  geom_vline(xintercept = res.mfa_bio_vs_self2_scale$group$coord[2,1], linetype = "dashed")+
    geom_hline(yintercept = res.mfa_bio_vs_self2_scale$group$coord[1,2], linetype = "dashed")+
  geom_hline(yintercept = res.mfa_bio_vs_self2_scale$group$coord[2,2], linetype = "dashed")+

  p$graphstyle_int+

```

ssid
```{r}

unique(as.integer(as.factor(newDFscale$subject)))
newDFscale$subject_orig<- newDFscale$subject

newDFscale$subject<- as.factor(as.integer(as.factor(newDFscale$subject)))

newDFscale1<- newDFscale%>% subset(subject!= 49)
res.MFA_stim_val_scale_ssid<-MFA(newDFscale1[,c(1,4:8)],group=c(1,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),num.group.sup=c(1),graph=TRUE)

plot.MFA(res.MFA_stim_val_scale_ssid, 
choix="ind",
         partial='all',
         label = FALSE,
         lab.par=FALSE,
         invisible= c('ind','quali'),
         select='cos2  0',
         habillage='group',
         title="Individual factor map",
         alpha = .2,
         shadowtext = FALSE,
REPEL = TRUE)+
  theme_classic()

  p$graphstyle_int+
    theme(axis.text.x = element_blank(),
        axis.text.y = element_blank()
        )

?factoextra::fviz_mfa_ind

factoextra::fviz_mfa_ind(res.MFA_stim_val_scale_ssid, 
                         choice="quali",
                         axes = c(1,2),
                         geom = "point",
                          habillage= 'none',
                         col.partial = "group",
                         repel = TRUE,
         partial='all',
select.ind = list(name = "subject"),
 alpha.ind = .02
)

```

  p$graphstyle_int

# add the neg pos etc based on their coordiantes

plot.MFA(res.MFA_stim_val, choix="ind",partial='all',lab.par=TRUE,invisible= c('ind','quali'),select='cos2  0',habillage='group',title="Individual factor map")

plot.MFA(res.MFA, choix="var",habillage='group',title="Correlation circle")
plot.MFA(res.MFA, choix="group")
plot.MFA(res.MFA, choix="axes",habillage='group')

```

?factoextra::fviz_mfa_ind
factoextra::fviz_mfa_ind(res.MFA_stim_val, 
                         axes = c(1, 2),
                         geom = c("text"),

                         select.ind = list(name = c("stimuli")),
                         # col.ind = "cos2",
                         habillage = "none",
                         addEllipses = TRUE,
             # gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE # Avoid text overlapping (slow if many points)
             # col.partial = "group"
             )

```

facto

label = "none", # hide individual labels
             habillage = iris$Species, # color by groups
             palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE # Concentration ellipses

fviz_mfa_ind(res.MFA_stim_val,
             geom = "none",
              choix=c("ind"),
               habillage='norm',
         lab.par=FALSE,
         invisible= c('ind'),

         # partial = "all"
         )

fviz_mfa_ind(res.MFA_stim_val, partial = "norm")

```

plot.MFA(res.MFA, 
         choix="ind",
         lab.par=TRUE,
         invisible= c('ind', 'quali'),
         # ellipse = 'val_cut_iaps',
         select='cos2  0.0',
         habillage='val_cut_iaps',
         title="Individual factor map",
         lab.grpe	 = TRUE)+
  theme_classic()
# boolean, if TRUE, the labels of the groups are drawn)

plot.MFA(res.MFA, choix="ind",lab.par=FALSE,invisible= c('ind','quali'),select='cos2  0',habillage='val_cut_iaps',title="Individual factor map")

testplot<- plot.MFA(res.MFA, choix="ind",lab.par=FALSE,invisible= c('ind','quali'),select='cos2  0',habillage='val_cut_iaps',title="Individual factor map")+
  theme_classic()

testplot$data

mfa_plots<- list()

factoextra::fviz_mfa_ind(res.MFA, 
                         choix="ind",

                         title="Individual factor map")
  theme_classic()

  # factor map of indivduals

quartz()
loadfonts(dev="win")
install.packages("extrafont")
library(extrafont)
extrafont::font_import()
plot.MFA(res.MFA, choix="ind",lab.par=FALSE,invisible= c('ind','quali'),select='cos2  0',habillage='val_cut_iaps',title="Individual factor map")+
  theme_classic()+
  p$graphstyle_int

# big lcuster by group
plot.MFA(res.MFA, choix="ind",lab.par=FALSE,invisible= 'quali',select='cos2  0',habillage='val_cut_iaps',title="Individual factor map")

# show that individuals are spread out
plot.MFA(res.MFA, choix="ind",
         lab.par=FALSE,
         invisible= 'quali',
         select='cos2  0',habillage='ssid',title="Individual factor map")

# we can select individuals significanlty contributing to the dimensions

newDF_sid <- clustering_new_pre_PCA3.1[,c("ssid","pup_basCor","Bio_Mean_HR_dif","log_BIO_CDA.PhasicMax","arousal","valence")]
res.MFA_sid<-MFA(newDF_sid,group=c(1,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),num.group.sup=c(1),graph=FALSE)
plot.MFA(res.MFA_sid, choix="ind",lab.par=FALSE,invisible= c('ind','quali'),select='cos2  0.2',
         habillage= 'ssid',
         title="Individual factor map")

?factoextra::fviz_mfa_ind

fviz_mfa_ind(res.MFA_sid, col.ind = "cos2", 
             choix="ind",
             invisible= c('ind','quali'),
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)

plot.MFA(res.MFA, choix="var",habillage='group',title="Correlation circle")
plot.MFA(res.MFA, choix="group")
plot.MFA(res.MFA, choix="axes",habillage='group')

newDF_sid_va <- clustering_new_pre_PCA3.1[,c("ssid","val_cut_iaps","pup_basCor","Bio_Mean_HR_dif","log_BIO_CDA.PhasicMax","arousal","valence")]
res.MFA_sid_val<-MFA(newDF_sid_va,group=c(2,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),num.group.sup=c(1),graph=FALSE)
plot.MFA(res.MFA_sid_val, choix="ind",lab.par=FALSE,invisible= c('ind','quali'),select='cos2  0.2',habillage='val_cut_iaps',title="Individual factor map")

plot.MFA(res.MFA, choix="ind",lab.par=FALSE,invisible= c('ind','quali'),select='cos2  0.2',habillage='val_cut_iaps',title="Individual factor map")
plot.MFA(res.MFA, choix="var",habillage='group',title="Correlation circle")
plot.MFA(res.MFA, choix="group")
plot.MFA(res.MFA, choix="axes",habillage='group')

```

### 2022-12-03 Figures.Rmd
test for Review
recover the power analyses files

@@
 
-  text=element_text(size = 14, family = "sans"),
-  axis.text.x = element_text(size = 14*(sf+.5), family = "sans", colour = "black",),
-  axis.text.y = element_text(size = 14*(sf+.5), family = "sans", colour = "black"),
+  text=element_text(size = 14),
+  axis.text.x = element_text(size = 14*(sf+.5), colour = "black",),
+  axis.text.y = element_text(size = 14*(sf+.5), colour = "black"),
 
@@
    # change leged title
-   guides(linetype=guide_legend(title="New Legend Title"), fill = guide_legend(title="New Legend Title"))
-
-plots_paper$interaction_ar_vl
+   # guides(linetype=guide_legend(title="New Legend Title"), fill = guide_legend(title="New Legend Title"))
+
+plots_paper$interaction_ar_vl <- plots_paper$interaction_ar_vl +
+ guides(title="valence",
+        fill = guide_legend(title="valence"),
+        color = guide_legend(title="valence"),
+        linetype = guide_legend(title="valence"))
 
@@
 
+plots_paper$interaction_ar_vl
 ```
@@
                              symnum.args = symnum.args)+
-   ylab(expression("Pupil vs subjective arousal ("*rho * ")"))+
+   ylab(paste0("Pupil vs subjective \n arousal (cor)"))+
    xlab("Subjective valence")
-
+   0
  plots_paper$pupil_correlation<- plots_paper$pupil_correlation+ p$graphstyle+
@@
 
+```
 # try with cluster]
@@
    xlab("Subjective valence")
+
+plots_paper$interaction_ar_vl<
 
@@
 
+timecourse_60bin_result_df
+
 plots_timecourse$eff_size_pup_amp <-   timecourse_60bin_result_df[1:56,] %>% 
@@
 
+plots_timecourse$eff_size_pup_amp+ p$graphstyle
+
 plots_timecourse$eff_size_pup_amp<- plots_timecourse$eff_size_pup_amp+
@@
   xlab("Subjective arousal (z)")+
-  ylab("Phasic SCR (log)")
+  ylab("Phasic SCR (log)")+
+  guides(title="valence",
+        fill = guide_legend(title="valence"),
+        color = guide_legend(title="valence"),
+        linetype = guide_legend(title="valence"))
 
@@
 
-  plots_paper$interaction_SCR+
+  plots_paper$interaction_SCR
 
@@
 ```{r}
+library(tidyverse)
+
+p$graphstyle <-  theme(#base plot theme
+
+  # axis lines
+  axis.line.y = element_line(color="black"),
+  axis.line.x = element_line(color="black"),
+
+  axis.title.y=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
+  axis.title.x=element_text(size = 16*(sf+.5), margin=margin(0,5,0,0)),
+
+  # text
+  strip.text.x = element_text(size = 12*(sf+.5),  colour = "black"),
+  strip.text.y = element_text(size = 12*(sf+.5),  colour = "black"),
+
+  text=element_text(size = 14),
+  axis.text.x = element_text(size = 14*(sf+.5), colour = "black",),
+  axis.text.y = element_text(size = 14*(sf+.5), colour = "black"),
+
+  # panel
+  panel.grid.major = element_blank(),
+  panel.background = element_blank(),
+  # panel.background = element_rect(fill="transparent"),
+  # panel.border = element_rect(fill="transparent"),
+  # strip shades (reco rectagles)
+   strip.background = element_blank(),
+
+  # legend
+  legend.position = "top",
+  legend.key = element_rect(colour = "transparent", fill="transparent"),
+  #legend.direction = "horizontal",
+
+  legend.text = element_text(size = 10*(sf+.3)),
+  # legend.title = element_text(size = 10*(sf+.3)),
+  # legend line tends to be really small in print so adjust here
+  legend.key.height = unit(.5, "cm"),
+  legend.key.width = unit(2, "cm"),
+
+  #legend.text = element_text(size = 10*sf),
+  legend.title=element_blank(),
+  #legend.text = element_blank(),
+  #axis.ticks = element_blank(),
+)
 library(patchwork)
 
-plot_patch1<- (plots_paper$interaction_ar_vl +
-plots_paper$pupil_correlation +
-plots_paper$pupil_course +
-plots_timecourse$eff_size_pup_amp+
-  plots_paper$interaction_SCR+
-  plots_paper$bio_HR)+
-  plot_layout(nrow = 3)+
-  plot_annotation(tag_levels = "A")
+plot_patch1
+
+plots_paper$pupil_correlation <-plots_paper$pupil_correlation +
+  theme(legend.position = "none")
+fix_dur_byval<-
+fix_dur_byval+theme(legend.position = "none")
+part1<- (plots_paper$interaction_ar_vl |plots_paper$pupil_correlation |plots_timecourse$eff_size_pup_amp)/
+  (plots_paper$interaction_SCR| plots_paper$bio_HR |scater_pupil_HR)
+
+part2<-    (correlation_plot+fix_dur_byval)+plot_layout(ncol = 2, widths = c(3,1))
+
+part3<- (part1/
+part2)
+  # plot_layout(nrow = 3)+
+  plot_annotation(tag_levels = "A", widths = c(2,1,1), heigths = c(1,1,2))
 
@@
 ggsave("patch_plot1.tiff", plot_patch1, device = "tiff", width = 15,height = 15, dpi = 800)
+
+ggsave("part3.tiff", part3, device = "tiff", width = 15,height = 12, dpi = 800)
 ```
@@
   ggpubr::stat_cor()+
-  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
+  xlab(expression("Mean "*Delta*" heart rate (bpm)"))+
   # xlab("Average heart rate difference")+
-  ylab("Average pupil change (au)")+
+  ylab("Mean pupil \n change (au)")+
   p$graphstyle
@@
   # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
-  ggplot(aes(mediansplit_ground_valence, mean_fix_dur))+
+  ggplot(aes(mediansplit_ground_valence, mean_fix_dur, color = mediansplit_ground_valence, fill = mediansplit_ground_valence))+
   # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
@@
   xlab("Valence")+
-  ylab("Average fixation duration (ms)")+
+  ylab(paste0("Mean fixation \n duration (ms)"))+
   # ylab("Baseline corrected pupil")+
@@
 
-? ggpubr::stat_compare_means
+# ? ggpubr::stat_compare_means
 fix_dur_byval

### 2022-12-03 IAPS_PREPROCESSING_2021_1_56_357_611_616.Rmd
test for Review
recover the power analyses files

@@
 write_csv(tmp.df4, 'tmp.df4_timeseries_356_357_611_616.csv')
-```
+
+save.image("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/356_357_611_616_preprocessing.RData")
+```

### 2022-12-03 Old scripts/IAPS_PREPROCESSING_2021.Rmd
test for Review
recover the power analyses files

--- 2021-09-01 IAPS_PREPROCESSING_2021_1.Rmd
@@
 
-tmp.df4$trigger2 <- tmp.df4$trigger
+tmp.df4$trigger2<- tmp.df4$trigger
 
@@
 unique(tmp.df4$trigger2)
-unique(tmp.df4$trigger)
-unique(tmp.df4$tNo)
 
 # \why?
-unique(tmp.df4$text)
-
 tmp.df4<- tmp.df4%>%
@@
 
-db_parsed$screencontent_no <- if_else(db_parsed$screencontent == 'fixation', 1,
+db_parsed$screencontent_no<- if_else(db_parsed$screencontent == 'fixation', 1,
                                       if_else(db_parsed$screencontent == 'stim', 2,
@@
 # tmp.df4_sum_fullt
-
-tmp.df4_sum_full
 ```
@@
 
-db_beh2$triggeracq <- db_beh2$trigger
+db_beh2$triggeracq<- db_beh2$trigger
 unique(db_beh2$ssid)
@@
 #   arrange(ssid, tNo, screencontent_no)
-
-colnames(tmp.df4_sum_full)
 ```
@@
 View(tmp.df4_sum_full)
-
-trigger<- db_leda2 %>%
-  subset(ssid == 348)%>%
-  select(order, Event.NID, trigger,Event.Nr)
 ```
@@
 colnames(tmp.df4_sum_full_stim)
-
-colnames(tmp.df4_sum_full)
 
@@
 
-colnames(db_leda_bio)
-
-db_leda_bio$BIO_Event.NID<- db_leda_bio$Event.NID
-db_leda_bio$BIO_filename <- db_leda_bio$filename
+db_leda_bio$trigger<- as.numeric(db_leda_bio$BIO_Event.NID)
 
@@
 
-# unique(db_leda_bio$trigger)
-
-# subset out rest period
-db_leda_bio<- subset(db_leda_bio, Event.Nr>1)
-
-db_leda_bio<- subset(db_leda_bio, CDA.nSCR!= "NaN")
-range(db_leda_bio$Event.Nr)
-
-# transform NaNs into proper NA
-db_leda_bio[db_leda_bio == "NaN"] <- NA
-
-# move counter to 1
-range(db_leda_bio$Event.Nr-1)
-# range(db_leda_bio$Event.Nr)
-# trigger$Event.Nr<- NULL
-
-db_leda_bio$order <- db_leda_bio$Event.Nr-1
-# db_leda_bio$trigger<- NULL
-
-# merge trigger
-trigger$Event.NID<- NULL
-trigger$ssid<- NULL
-View(db_leda_bio)
-
-db_leda_bio$order
-# db_345_355$order
-
-trigger<- db_345_355 %>%
-  group_by(order,trigger, tNo)%>%
-  summarise_at(c('ssid'), mean, na.rm = TRUE)
-  # select(db_345_355, c(trigger, tNo, order))
-
-  trigger$ssid<- NULL
-
-  db_leda_bio<- left_join(db_leda_bio, trigger)
-
-tmp.df4_sum_full
-
-leda_bioames <- colnames(db_leda_bio)
-
-leda_bioames
-newnames<- c("Event.Nr", paste0("BIO_", paste(leda_bioames[2:16])),"BIO_Event.NID","BIO_filename"  ,"ssid","order","trigger")
-
-newnames
-
-db_leda_bio_backup<- db_leda_bio
-
-colnames(db_leda_bio_backup)
-
-names(db_leda_bio) <- newnames
-
-colnames(db_leda_bio)
-
-# db_leda_bio$ssid <- db_leda_bio$BIO_ssid
-
-# db_leda_bio$BIO_ssid<-NULL
-
-db_leda_bio
-
-db_leda_bio$ssid<- as.character(db_leda_bio$ssid)
-
-# db_leda_bio$order<- db_leda_bio$BIO_order
-
-unique(tmp.df4_sum_full$Event.Nr)
-
-db_leda_bio$BIO_Event.NID<- NULL
-db_leda_bio$BIO_filename<- NULL
-
-tmp.df4_sum_full_bio<- left_join(tmp.df4_sum_full,  db_leda_bio, by = c("ssid", "order"))
-
-colnames(tmp.df4_sum_full_bio)
-
-write_csv(db_leda_bio, "db_leda_bio_346_347_ledagsr.csv")
-
-write_csv(db_leda_bio, "db_leda_bio_346_355_ledagsr.csv")
-```
-
-```{r eval=FALSE, include=FALSE}
-# stim
+unique(db_leda_bio$trigger)
+
 db_leda_bio_stim<-subset(db_leda_bio, db_leda_bio$trigger< 100)
@@
 
+#tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full, tmp.df4_sum_full$ssid>303)
+# tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full_bio, tmp.df4_sum_full_bio$trigger!= -7)
+
+#levels(as.factor(tmp.df4_sum_full_bio$ssid))
+#unique(tmp.df4_sum_full_bio$trigger)
+#levels(as.factor(db_leda_bio$ssid))
+
 db_leda_bio_stim$ssid<- as.character(db_leda_bio_stim$ssid)
 
-# db_leda_bio_stim$trigger<- as.character(db_leda_bio_stim$trigger)
-
-db_leda_bio$order<- db_leda_bio$Event.Nr
-
+db_leda_bio_stim$trigger<- as.character(db_leda_bio_stim$trigger)
+
+#db_leda_bio$order<- db_leda_bio$Event.Nr
 tmp.df4_sum_full_stim_gp_leda_beh_self$ssid<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$ssid)
-
 tmp.df4_sum_full_stim_gp_leda_beh_self$trigger<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$trigger)
@@
 cor(tmp.df4_sum_full_biot1$arousal, tmp.df4_sum_full_biot1$Global.Mean.y, use = 'complete.obs')
-
 ```
@@
 ```{r}
-
 nrow(tmp.df4_sum_full_bio)
@@
 unique(tmp.df4_sum_full_bio$ssid)
+
+unique(db_biohr$filename)
 
@@
 # now read them
-# old
 db_biohr <-
-  list.files(pattern = "*.xls", 
+  list.files(pattern = "*.csv", 
              full.names = T) %>% 
   map_df(~read_biohr(.))
-
-unique(db_biohr$filename)
 
@@
 db_biohr$trigger<- as.factor(as.character(db_biohr$trigger))
-
+unique(tmp.df4_sum_full_bio$ssid)
 unique(db_biohr$ssid)
+tmp.df4_sum_full_bio$trigger<- as.factor(as.character(tmp.df4_sum_full_bio$trigger))
 
 db_biohr$ssid<- as.factor(as.character(db_biohr$ssid))
-
-```
-
-#HR BIOPAC
-
-```{r}
-setwd("~/OneDrive - Nexus365/InteroStudy2020/Data Collection 2019- 2020/2020/InteroStudyBIOPAC/IAPS/Processed/HR/345_355")
-library(readxl)
-library(dplyr)
-# db_HR_bio <- read_excel("310_IAPS_Physio_HR.xls")
-
-# db_HR_bio<- db_HR_bio[6:nrow(db_HR_bio),]
-
-library(data.table)
-library(purrr)
-# import
-read_biohr <- function(flnm) {
-  read_excel(flnm) %>% 
-    mutate(filename = flnm)
-}
-
-# now read them
-db_HR_bionew <-
-  list.files(pattern = "*.xls", 
-             full.names = T) %>% 
-  map_df(~read_biohr(.))
-
-db_HR_bio<- db_HR_bionew
-
-unique(db_HR_bionew$filename)
-nrow(db_HR_bionew)
-
-# test<- subset(db_HR_bio, db_HR_bio$filename == "./607_IAPS_Physio_HR.xls")
-
-levels(as.factor(db_HR_bio$filename))
-
-db_HR_bio$ssid<- substr(db_HR_bio $filename, 3,5)
-
-db_HR_bio$filename<- NULL
-
-# 
-db_HR_bio$`Stim-Response Analysis`
-
-# flag stimulus
-db_HR_bio$stim <- if_else(grepl('Stimulus', (db_HR_bio$`Stim-Response Analysis`)) == TRUE, db_HR_bio$`Stim-Response Analysis`, NULL)
-
-library(tidyr)
-
-db_HR_bio<- db_HR_bio%>%
-  group_by(ssid)%>%
-  fill(stim)
-
-db_HR_bio
-
-levels(as.factor(db_HR_bio$ssid))
-
-#  remove na in the mean heart rate
-
-db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$...2))
-
-db_HR_bio$mhrtext<- is.character(db_HR_bio$...2)
-
-db_HR_bio<- subset(db_HR_bio, !grepl('interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
-
-# loosing participants here
-View(db_HR_bio)
-
-db_HR_bio<- subset(db_HR_bio, !grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
-
-# test<- subset(db_HR_bio, grepl('Interval ', db_HR_bio$`Stim-Response Analysis`) == TRUE)
-# levels(as.factor(db_HR_biotest$ssid))
-
-db_HR_bio<- subset(db_HR_bio, !grepl('Time', db_HR_bio$`Stim-Response Analysis`) == TRUE)
-
-#db_HR_biotest1<- subset(db_HR_biotest, !is.na(db_HR_biotest$stim))
-
-#test<- subset(db_HR_bio, db_HR_bio$ssid == 607)
-
-levels(as.factor(db_HR_bio$ssid))
-
-db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$`Stim-Response Analysis`))
-
-db_HR_bio$...3<- NULL
-db_HR_bio$...4<- NULL
-
-db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$...2))
-
-db_HR_bio<- subset(db_HR_bio, db_HR_bio$...2 != 'Mean(CH 40)')
-db_HR_bio$timestart<- db_HR_bio$`Stim-Response Analysis`
-
-db_HR_bio$Mean_HR<- db_HR_bio$...2
-
-db_HR_bio<- db_HR_bio%>%
-  arrange((as.numeric(timestart)), ssid)
-
-db_HR_bio<- subset(db_HR_bio, !is.na(db_HR_bio$stim))
-
-db_HR_bio$trigger <- substr(db_HR_bio$stim, 10,13)
-
-# for soem reason this 
-unique((as.numeric(db_HR_bio$trigger)-128))
-
-db_HR_bio$trigger_200<- if_else(db_HR_bio$trigger> 103, TRUE, FALSE)
-
-db_HR_bio$trigger2 <- if_else(db_HR_bio$trigger_200 == TRUE, as.numeric(db_HR_bio$trigger)-128, as.numeric(db_HR_bio$trigger))
-
-unique((as.numeric(db_HR_bio$trigger2)))
-
-#subset(db_HR_bio, db_HR_bio$ssid!= 328)%>%
-#  group_by(timestart, ssid)%>%
- # mutate(EventNR= 1:225)
-
-# this will delete fixation and stuff so no
-db_HR_bio1<- subset(db_HR_bio,db_HR_bio$trigger2> 15)
-
-db_HR_bio1<- db_HR_bio%>%
-  arrange(ssid, as.numeric(timestart))
-
-db_HR_bio1<- subset(db_HR_bio1,!is.na(db_HR_bio1$stim))
-
-#tno
-#subset(db_HR_bio1, db_HR_bio1$ssid != 328)%>%
-table(is.na(db_HR_bio1$ssid))
-# 
-# db_HR_bio1<- db_HR_bio1%>%
-#   arrange(as.numeric(timestart), ssid)
-
-# use this
-table(db_HR_bio1$ssid!= 328)
-db_HR_bio1no328<-subset(db_HR_bio1, db_HR_bio1$ssid!= 328)
-
-db_HR_bio1no328$trigger2
-db_HR_bio1no328<- subset(db_HR_bio1no328, trigger2> 15 & trigger2<106)
-
-db_HR_bio1no328$trigger<- db_HR_bio1no328$tNo
-# db_HR_bio1no328
-
-# db_HR_bio1no328<- db_HR_bio1no328 %>%
-#   arrange(ssid, trigger2)%>%
-#   filter(!duplicated(trigger2))
-
-View(trigger)
-db_HR_bio1no328<- db_HR_bio1no328$t %>%
-  group_by(ssid)%>%
-  mutate(tNo =  -6:(n()-7)) #56 trials
-
-unique(db_HR_bio1no328$tNo)
-
-range(db_HR_bio1no328$tNo)
-
-table(db_HR_bio1no328$tNo)
-
-# test<- subset(db_HR_bio1no328, tNo>49)
-# 
-# db_HR_bio328<-subset(db_HR_bio1, db_HR_bio1$ssid== 352)
-# 
-# subset(db_HR_bio328, trigger> 15 & trigger<72)
-
-db_HR_bio1no328<- db_HR_bio1no328%>%
-  arrange(ssid,as.numeric(timestart))
-
-```
-
-```{r}
-# db_HR_bio2<-
-
-unique(db_HR_bio1no328$stim)
-db_HR_bio1no328<- db_HR_bio1no328 %>%
-  group_by(ssid)%>%
-  mutate(tNo = -6:(n()-7))
-
-unique(db_HR_bio1no328$tNo)
-```
-
-```{r}
-View(db_HR_bio1no328)
-
-unique(db_HR_bio1no328$ssid)
-unique(db_HR_bio328$ssid)
-# db_HR_bio2<- bind_rows(db_HR_bio1no328,db_HR_bio328)
-db_HR_bio2<-db_HR_bio1no328
-
-colnames(db_HR_bio2)
-
-levels(as.factor(db_HR_bio1no328$ssid))
-# db_HR_bio2$ssid<-db_HR_bio2$`as.numeric(ssid)`
-
-#mereg old and new heart rate
-# now read them
-# db_biohr$trigger
-# 
-# db_biohr$tno<-db_biohr$trigger
-# db_HR_bio2$trigger
-# colnames(db_biohr)
-# 
-# colnames(db_HR_bio2)
-# 
-# db_biohr$Mean_HR<- db_biohr$HR_BIO
-# 
-# db_biohr$timestart<- db_biohr$Time
-# 
-# 
-# left_join(db_HR_bio2, db_biohr)
-
-colnames(db_HR_bio2)
-db_HR_bio2<- select(db_HR_bio2, c(timestart,Mean_HR, tNo, ssid,trigger2,trigger_200, trigger,stim,mhrtext))
-
-# store only fixation screens
-
-# create screecontr.treatment()
-unique(db_HR_bio2$trigger)
-unique(db_HR_bio2$trigger2)
-
-db_HR_bio2$screen_content<- if_else(db_HR_bio2$trigger == 100, "Rest",
-                                    if_else(db_HR_bio2$trigger == 101, "fixation",
-                                    if_else(db_HR_bio2$trigger == 102, "valence",
-                                    if_else(db_HR_bio2$trigger == 103, "arousal",
-                                    "stim"))))
-
-unique(db_HR_bio2$trigger)
-
-db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)
-db_HR_bio2.1<- db_HR_bio2 %>%
-  group_by(ssid)%>%
-  arrange(ssid, timestart)%>%
-  group_by(ssid,screen_content)%>%
-  # arrange(ssid, timestart)%>%
-  mutate(tNo =  1:n())
-   arrange(timestart,ssid)
-  # subset(trigger == 100)
-
-unique(db_HR_bio2.1$tNo)
-
-unique(db_HR_bio2.1$tNo-8)
-table(db_HR_bio2.1$tNo)
-
-db_HR_bio2.1$tNo2<- if_else(db_HR_bio2.1$screen_content == "Rest", -7,
-                           as.numeric(as.character(db_HR_bio2.1$tNo)))
-
-db_HR_bio2.1$tNo3<- if_else(db_HR_bio2.1$tNo2 >0 &  db_HR_bio2.1$tNo2< 7, db_HR_bio2.1$tNo2-7,
-                          if_else(db_HR_bio2.1$tNo2  >6, db_HR_bio2.1$tNo2-6, db_HR_bio2.1$tNo2))
-
-table(db_HR_bio2.1$tNo3)
-test352<- subset(db_HR_bio2.1, ssid == 352)
-test353<- subset(db_HR_bio2.1, ssid == 353)
-table(test352$tNo3)
-
-write_csv(test352, "test352.csv")
-
-# fixed the issue was trial 15 is supposed to be trigger 23 but we also had a 70, that can be seen on the psychopy data files
-write_csv(test353, "test353.csv")
-
-# on 353 the issue was a 99 trigger bveing loaded as a stim
-
-# export 352 and 353 and corect manually, they seems ot have an extra trigger
-
-db_352 <- read_csv("352_Biohr_fixed.csv")
-db_353 <- read_csv("353_Biohr_fixed.csv")
-unique(db_352$ssid)
-db_352
-nrow(db_353)
-
-# new dataset withouth the problem ssids
-db_HR_bio2.2<- subset(db_HR_bio2.1, ssid != "352")
-db_HR_bio2.2<- subset(db_HR_bio2.2, ssid != "353")
-
-nrow(db_HR_bio2.2)
-
-unique(db_HR_bio2.2$ssid)
-
-db_352_353<- bind_rows(db_352, db_353)
-
-nrow(db_352_353)
-
-db_HR_bio2.2$ssid<- as.character(db_HR_bio2.2$ssid)
-db_352_353$ssid<- as.character(db_352_353$ssid)
-
-db_352_353$trigger <- as.character(db_352_353$trigger)
-
-nrow(db_HR_bio2.2)
-# nrow(db_HR_bio2.1) 2021 result should be less than this
-
-nrow(db_352_353)
-
-db_HR_bio2.3<- bind_rows(db_HR_bio2.2,db_352_353)
-nrow(db_HR_bio2.3)
-# order
-
-db_HR_bio2.3.1<- db_HR_bio2.3 %>%
-  group_by(ssid)%>%
-  arrange(ssid, timestart) %>%
-  group_by(ssid,screen_content)%>%
-  # arrange(ssid, timestart)%>%
-  mutate(tNo =  1:n())
-   # arrange(timestart,ssid)
-  # subset(ssid == 353)
-
-table(db_HR_bio2.3.1$tNo)
-
-# test<- subset(db_HR_bio2.3.1, ssid == "353")
-
-unique(db_HR_bio2.3.1$tNo)
-
-db_HR_bio2.3.1$tNo2<- if_else(db_HR_bio2.3.1$screen_content == "Rest", -7,
-                           as.numeric(as.character(db_HR_bio2.3.1$tNo)))
-
-db_HR_bio2.3.1$tNo3<- if_else(db_HR_bio2.3.1$tNo2 >0 &  db_HR_bio2.3.1$tNo2< 7, db_HR_bio2.3.1$tNo2-7,
-                          if_else(db_HR_bio2.3.1$tNo2  >6, db_HR_bio2.3.1$tNo2-6, db_HR_bio2.3.1$tNo2))
-
-unique(db_HR_bio2.3.1$tNo3)
-```
-
-```{r}
-unique(db_HR_bio2.3.1$screen_content)
-table(is.na(db_HR_bio2.3.1$screen_content))
-
-str((db_HR_bio2.3.1))
-# str(db_biohrold2)
-db_biohr$tNo<- db_biohr$tno
-db_biohrold2<- db_biohr
-
-db_biohrold2<- select(db_biohr, c(timestart,Mean_HR, tNo, ssid))
-unique(db_biohrold2$tNo)
-
-db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)
-
-View(db_biohrold2)
-db_biohrold2$timestart<- as.numeric(db_biohrold2$timestart)
-
-# View(db_HR_bio2)
-db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)
-# db_biohrold2$Mean_HR<- as.numeric(db_biohrold2$Mean_HR)
-
-db_HR_bio2$tNo<- as.character(db_HR_bio2$tNo)
-
-db_biohrold2$tNo<- as.character(db_biohrold2$tNo)
-db_HR_bio2$ssid<- as.character(db_HR_bio2$ssid)
-
-db_biohrold2$ssid<- as.character(db_biohrold2$ssid)
-
-str(db_HR_bio2)
-
-# db_biohrold2test<- subset(db_biohrold2, db_biohrold2$tNo != 100)
-# db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 101)
-# db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 102)
-# db_biohrold2test<- subset(db_biohrold2test, db_biohrold2test$tNo != 103)
-# db_HR_bio2$subj<- as.factor(db_HR_bio2$ssid)
-# db_biohrold2test$subj<- as.factor(db_biohrold2test$ssid)
-# db_biohrold2test$ssid<- NULL
-# db_HR_bio2$ssid<- NULL
-
-str(db_HR_bio2)
-
-db_HR_bio2<- db_HR_bio2[,1:4]
-db_HR_bio2$Mean_HR<- as.numeric(db_HR_bio2$Mean_HR)
-
-db_biohrold2test$Mean_HR<- as.numeric(db_biohrold2test$Mean_HR)
-
-db_HR_bio2$timestart<- as.numeric(db_HR_bio2$timestart)
-
-db_biohrold2test$timestart<- as.numeric(db_biohrold2test$timestart)
-
-# final
-colnames(db_HR_bio_final)
-db_HR_bio2.3.1
-colnames(db_HR_bio2.3.1)
-
-unique(db_HR_bio2.3.1$tNo)
-db_HR_bio2.3.1
-# db_HR_bio2.3.2<-select()
-db_HR_bio_final<- select(db_HR_bio2.3.1, c(1:12))
-
-# db_HR_bio_final<- bind_rows(db_HR_bio2, db_biohrold2test)
-
-View(db_HR_bio_final)
-
-# db_HR_bio_final$ssid<- db_HR_bio_final$subj
-levels(as.factor(db_HR_bio_final$ssid))
-
-db_HR_bio_final$subj<- NULL
-
-write_csv(db_HR_bio_final, 'db_HR_bio_final_mar5.csv')
-
-write_csv(db_HR_bio_final, 'db_HR_bio_final_346_355_withfix.csv')
-
-db_HR_bio_final$tNo
-
-db_HR_bio_final$tNo
-
-db_HR_bio1$tNo<- -6:49
-
-db_HR_bio_final$tNo<- if_else(as.numeric(db_HR_bio_final$tNo) < 0, as.numeric(db_HR_bio_final$tNo), as.numeric(db_HR_bio_final$tNo)+1)
-
-db_HR_bio_final$BIO
-
-```
-
-merge heart rate
-
-```{r}
-tmp.df4_sum_full_bio$ssid<- as.character(tmp.df4_sum_full_bio$ssid)
-db_HR_bio_final$ssid<- as.character(db_HR_bio_final$ssid)
-
-colnames(tmp.df4_sum_full_bio)
-
-unique(tmp.df4_sum_full_bio$tNo)
-tmp.df4_sum_full_bio$tNo3<- tmp.df4_sum_full_bio$tNo
-tmp.df4_sum_full_bio1<- tmp.df4_sum_full_bio
-tmp.df4_sum_full_bio1$tNo<-NULL
-
-unique(tmp.df4_sum_full_bio$screencontent)
-unique(db_HR_bio_final$screen_content)
-
-tmp.df4_sum_full_bio$screen_content<- if_else(tmp.df4_sum_full_bio$screencontent == "ValenceResp", "valence",
-                                              if_else(tmp.df4_sum_full_bio$screencontent == "IntResp", "arousal", tmp.df4_sum_full_bio$screencontent))
-
-tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final, by = c('ssid', 'tNo', 'screen_content'))
-
-unique(tmp.df4_sum_full_bio_hr$tNo)
-
-```
-
-Merge self reports
-
-# add the self report
-```{r}
-
-View(tmp.df4_sum_full_bio_hr)
-
-library(readxl)
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport")
-
-View(db_selfrep)
-db_selfrep <- read_excel("db_self_rep_345_356_final.xlsx")
-
-db_selfrep$ssid <- as.character(db_selfrep$`Participant No`)
-
-tmp.df4_sum_full_bio_hr$ssid <- as.character(tmp.df4_sum_full_bio_hr$ssid)
-
-tmp.df4_sum_full_bio_hr_self <- left_join(tmp.df4_sum_full_bio_hr, db_selfrep, by = 'ssid')
-
-write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_bio_hr_self_345_356.csv')
-
-```
-
-merge parsed data
-```{r}
-tmp.df4_sum_full_bio_hr_self
-db_parsed_summarised2$ssid<- as.character(db_parsed_summarised2$ssid)
-
-tmp.df4_sum_full_bio_hr_self_parsed <- left_join(tmp.df4_sum_full_bio_hr_self, db_parsed_summarised2, 
-                             by = c("ssid", "trialUnq", "tNo", "screencontent"))
-
-# tmp.df4_sum_full<- left_join(tmp.df4_sum,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))
-
-# save the timecourse data and the aggregated data
-
-tmp.df4_sum_full_bio_hr_self_parsed
-
-# merge behavioural data
-db_beh3$ssid<- as.character(db_beh3$ssid)
-db_beh3$tNo <- as.character(db_beh3$tNo)
-tmp.df4_sum_full_bio_hr_self_parsed$tNo<- as.character(tmp.df4_sum_full_bio_hr_self_parsed$tNo)
-# tmp.df4_sum_full<-
-
-tmp.df4_sum_full_bio_hr_self_parsed<- left_join(tmp.df4_sum_full_bio_hr_self_parsed, db_beh3, by = c('ssid', 'tNo'))
-
-View(db_beh3)
-tmp.df4_sum_full<- tmp.df4_sum_full%>%
-  arrange(ssid, tNo, time)
-
-tmp.df4_sum_full_bio_hr_self_parsed$screencontent_no
-
-tmp.df4_sum_full_bio_hr_self_parsed$TAS
-# tmp.df4_sum_full_bio_hr_self_parsed<- tmp.df4_sum_full_bio_hr_self_parsed %>%
-#   subset(screencontent_no>2)%>%
-#   group_by(ssid)%>%
-#   summarise_if(is.numeric,mean, na.rm = TRUE)%>%
-#   ggplot(aes(Age,sdev_gazesum))+
-#   geom_point()+
-#   geom_smooth(method = lm, se = F)
-
-colnames(tmp.df4_sum_full_bio_hr_self_parsed)
-
-tmp.df4_sum_full_bio_hr_self_parsed$Age<- tmp.df4_sum_full_bio_hr_self_parsed$age_response_specific
-tmp.df4_sum_full_bio_hr_self_parsed$gender<- substr(tmp.df4_sum_full_bio_hr_self_parsed$gender_response,1,1)
-
-tmp.df4_sum_full_bio_hr_self_parsed$BIO_filename<- NULL
-tmp.df4_sum_full_bio_hr_self_parsed$`Participant Completion Code`<- NULL
-tmp.df4_sum_full_bio_hr_self_parsed$`Participant Private ID`<- NULL
-
-tmp.df4_sum_full_bio_hr_self_parsed$`Participant No`<- NULL
-tmp.df4_sum_full_bio_hr_self_parsed$age_response_specific<- NULL
-tmp.df4_sum_full_bio_hr_self_parsed$Event.NID<- NULL
-tmp.df4_sum_full_bio_hr_self_parsed$`Event Index`<- NULL
-tmp.df4_sum_full_bio_hr_self_parsed$gender_response<- NULL
-
-tmp.df4_sum_full_bio_hr_self_parsed$`Person testing`<- NULL
-tmp.df4_sum_full_bio_hr_self_parsed$Event.Nr.x<- NULL
-tmp.df4_sum_full_bio_hr_self_parsed$filename.x<- NULL
-tmp.df4_sum_full_bio_hr_self_parsed$filename.y<- NULL
-
-tmp.df4_sum_full_bio_hr_self_parsed
-
-tmp.df4_sum_full_bio_hr_self_parsed<- tmp.df4_sum_full_bio_hr_self_parsed%>%
-  rename(IAS = IAS_score)%>%
-  rename(ASD_self = ASD)
-
-# tmp.df4_sum_full_bio_hr_self_parsed1<- select(tmp.df4_sum_full_bio_hr_self_parsed,)
-
-write_csv(tmp.df4_sum_full_bio_hr_self_parsed, 'tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv')
-write_csv(tmp.df4, 'tmp.df4_timeseries_345_356.csv')
-```
+tmp.df4_sum_full_bio_hr<- left_join(tmp.df4_sum_full_biot, db_biohr, by = c('ssid', 'order', 'trigger'))
+
+ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(hr, HR_BIO))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(CDA.PhasicMax.x, CDA.PhasicMax.y))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+tmp.df4_sum_full_bio_hr_stim<- subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent != 'fixation')
+
+cor(tmp.df4_sum_full_bio_hr_stim$hr, tmp.df4_sum_full_bio_hr_stim$HR_BIO, use = 'complete')
+
+# tmp.df4_sum_full_bio_hr_stim_1<- subset(tmp.df4_sum_full_bio_hr_stim, tmp.df4_sum_full_bio_hr_stim$HR_BIO> 50)
+
+tmp.df4_sum_full_bio_hr_stim$valence_cat<- if_else(tmp.df4_sum_full_bio_hr_stim$valence >0, 'pos',
+                                                  if_else(tmp.df4_sum_full_bio_hr_stim$valence < 0, 'neg', 'neutral'))
+
+unique(tmp.df4_sum_full_bio_hr_stim$screencontent)
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+  # facet_grid(~valence_cat)
+
+cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$arousal, use = 'complete')
+cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$valence, use = 'complete')
+
+tmp.df4_sum_full_bio_hr_stim%>%
+      group_by(ssid, IAS)%>%
+      summarise(corr = cor(HR_BIO, arousal, use = 'complete'))%>%
+  summarise(new = cor(corr, IAS))
+  # summarise_at(c('TAS'), mean)
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  facet_grid(~valence_cat)
+
+tmp.df4_sum_full_bio_hr_stim%>%
+group_by(valence_cat)%>%
+  summarise(corr = cor(HR_BIO, arousal, use = 'complete'))
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, valence))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  facet_grid(~valence_cat)
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, ValenceMean))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+  # facet_grid(~valence_cat)
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, mean_sac_dur))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  facet_grid(~valence_cat)
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, pup_basCor))+
+  geom_point()+
+  geom_smooth(method = 'lm')+
+  facet_grid(~valence_cat)
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, Global.Mean.y))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, TAS))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, `DASS Anxiety`))+
+  geom_point()+
+  geom_smooth(method = 'lm')
+
+```

### 2022-12-03 Old scripts/IAPS_PREPROCESSING_GitSample.Rmd
test for Review
recover the power analyses files

--- 2022-12-03 Old scripts/IAPS_PREPROCESSING_2021.Rmd
@@
 ---
-title: "InteroceptionStudy_GPValidation"
-Author: "Helio Cuve & "
-date: "8 January 2021"
+title: "InteroceptionStudy_GP"
+Author: "Helio Cuve"
+date: "8 January 2020"
 output: html_document
@@
 ```{r}
-# devtools::install_github("dmirman/gazer")
 
@@
 # setting a workspace
-# change approproatelly
 
@@
 ```
-
-Problem files
-```{r}
-# 355  - did not finish IAPS
-# adjust below manually
-
-hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021"
-
-gp.extractor = function(hdf5FilesPath) {
-
-  setwd(hdf5FilesPath)
-  #getwd()
-  hdfFilesList = list.files(hdf5FilesPath, pattern = "\\.hdf5$")
-
-  if (length(hdfFilesList) == 0){
-    hdfFilesList
-
-    return(message('No HDF5 files found in the directory provided.'))
-  }
-   f = 10
-  for (f in 1:length(hdfFilesList)) {
-
-    message(sprintf("Extracting file %i / %i - %s", f, length(hdfFilesList), hdfFilesList[f]))
-
-    #note that some r-studio bug sometimes causes this to fail when runnin from notebook, 
-    # in that case run it directly on command line
-    tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent')
-
-    tmp.eyetr  = h5read(hdfFilesList[f], '/data_collection/events/eyetracker/BinocularEyeSampleEvent')
-
-    # Get subject id from Events
-    ssid = sapply(strsplit(grep('SubjJID', tmp.events$text, value = TRUE), split = ": "), "[", 2)
-    date = sapply(strsplit(grep('DATE', tmp.events$text, value = TRUE), split = ": "), "[", 2)
-    session = sapply(strsplit(grep('Session:', tmp.events$text, value = TRUE), split = ":"), "[", 2)
-    cali<- subset(tmp.events, grepl('Cali', tmp.events$text) == TRUE)
-
-    # Create DF for trials data
-    tmp.df = data.frame(matrix(ncol = ncol(tmp.eyetr)))
-    names(tmp.df) = names(tmp.eyetr)
-    colnames(tmp.df)
-
-    # Prepare Events, keep only start/end messages
-    phrases = c('tStart', 'tEnd')
-    tmp.events_backup<- tmp.events
-    # tmp.events<-  tmp.events_backup
-    tmp.events = subset(tmp.events, grepl(paste(phrases, collapse = "|"), tmp.events$text))
-
-    # Create start/end references
-    tmp.events$tStart   = NA
-    tmp.events$tEnd     = NA
-
-    # Trial number extraction 
-    tmp.events$tNo      = NA
-    tmp.df$tNo          = NA
-    tmp.df$Condition    = NA
-
-    # Space for subject id
-    tmp.df$ssid         = NA
-    tmp.df$text<-NA
-
-    for (l in 1:nrow(tmp.events)) {
-
-      message(sprintf("Grabing start messages %s", tmp.events$text[l]))
-
-      if ((grepl('tStart', tmp.events$text[l])) == TRUE) {
-        tmp.events$tStart[l] = tmp.events$time[l]
-
-        if ((grepl('tEnd', tmp.events$text[l+1])) == TRUE){
-          tmp.events$tEnd[l] = tmp.events$time[l+1]
-        }
-
-        else {
-          message('trial start/end structure not valid')
-        }
-      }
-
-    }
-    message(sprintf("done grabbing messages"))
-    # readline(prompt="Press [enter] to continue")
-
-    tmp.events$tNo<- as.numeric(as.character(gsub(".*_","",tmp.events$text)))
-
-     message(sprintf("making screencontent"))
-
-     tmp.eventsbackup<- tmp.events
-    tmp.events$screencontent<- if_else(grepl('fixation', tmp.events$text), 'fixation',
-                                       if_else(grepl('Valence', tmp.events$text), 'ValenceResp',
-                                               if_else(grepl('rest', tmp.events$text), 'rest1', 
-                                                       if_else(grepl('IntResp', tmp.events$text), 'IntResp','stim'))))
-
-    # unique(tmp.events$screencontent)
-
-    tmp.events$Condition<- if_else(grepl('IAPS', tmp.events$text), 'IAPS',
-                                   if_else(grepl('Example', tmp.events$text), 'Practice',
-                                           if_else(grepl('rest', tmp.events$text), 'Rest', NULL)))
-    tmp.events$stim<- if_else(tmp.events$Condition == 'IAPS', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text),
-                              if_else(tmp.events$Condition == 'Practice', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text), 'REST'))
-
-    # substitute periods
-    tmp.events$stim<- gsub('\\.', '.jpg', tmp.events$stim)
-
-    tmp.events$tNo<- if_else(tmp.events$Condition == 'Practice', (tmp.events$tNo)-6,
-                             if_else(tmp.events$Condition == 'Rest',-7, tmp.events$tNo))
-
-    # create trial number < 0 are practice trials
-    tmp.events$tNo<- if_else(tmp.events$tNo> -1, tmp.events$tNo+1, tmp.events$tNo) # avoid zeros
-
-    tmp.events1 = subset(tmp.events, grepl('tStart',tmp.events$text))
-    # tmp.events1$tNo1<- NULL
-    # tmp.events1$tNo2<- NULL
-
-    tmp.events1<- subset(tmp.events1, is.na(tmp.events1$tNo) == FALSE)
-
-    # colnames(tmp.df)
-    # colnames(tmp.df)
-    # colnames(tmp.events1)
-    # colnames(tmp.eyetr)
-
-    tmp.df$screencontent<- NA
-    tmp.df$stim<- NA
-    tmp.events1$tEnd<- if_else(tmp.events1$tNo == -7, tmp.events1$tStart+120, tmp.events1$tEnd)
-
-    message(sprintf("subsetting eyetracking data"))
-
-    for(e in 1:nrow(tmp.events1)) {
-
-      # Subset the EyeTracking data based on start/end
-      tmp.raw.trial = subset(tmp.eyetr, tmp.eyetr$time >= tmp.events1$tStart[e] & tmp.eyetr$time <= tmp.events1$tEnd[e])
-
-      tmp.raw.trial$tNo = tmp.events1$tNo[e]
-
-      tmp.raw.trial$Condition = tmp.events1$Condition[e]
-      tmp.raw.trial$screencontent = tmp.events1$screencontent[e]
-      tmp.raw.trial$stim = tmp.events1$stim[e]
-      # tmp.raw.trial$stim = tmp.events1$[e]
-      tmp.raw.trial$ssid = ssid
-      tmp.raw.trial$text = tmp.events1$text[e]
-
-      message(sprintf("binding tmp.df"))
-
-      tmp.df= rbind(tmp.raw.trial, tmp.df)
-    }
-     message(sprintf("done binding"))
-
-    # Arrange the dataframe byu time
-    tmp.df<- tmp.df%>%
-      arrange(time)
-
-    # Save file for the task with subject name
-    name = sprintf("ss%s_GPdata",ssid)
-    message(sprintf("saving data"))
-    write_csv(tmp.df, paste(name,".csv"))
-
-    # write calibration file
-    name2 = sprintf("ss%s_GPdata_cali", ssid)
-    write_csv(cali, paste(name2,".csv"))
-
-  }
-
-  message("Processing Completed.")
-  tmp.df
-}
-
-unique(tmp.df$tNo)
-
-```
-
-Now cleaning gaze data and prepare data for ledalab and artifact
-
-```{r, cleaning}
-# function to read all the csvs into one dataframe
-
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/Step1_GpExtractor_Output/346-355")
-
-# rm(tmp_full)
-read_plus <- function(flnm) {
-  data.table::fread(flnm, select = c("session_id","event_id", "time", "left_gaze_x", "left_gaze_y","right_gaze_x", "right_gaze_y","left_pupil_measure1",
-                                     "right_pupil_measure1","gsr", "gsrv", 'hr', "hrv", "hrp", "status", "tNo",  "Condition", "screencontent", "stim", "ssid", "text")) %>% 
-    mutate(filename = flnm)
-}
-
-# read all clean data 
-tmp.df2 <-
-  list.files(pattern = "*.csv", 
-             full.names = T) %>% 
-  map_df(~read_plus(.))
-
-unique(tmp.df2$ssid)
-
-table(is.na(tmp.df2$ssid))
-# tmp.df2$ssid<- substr(tmp.df2$filename, 5,7)
-head(tmp.df2)
-# check we have all participants
-# unique(tmp.df2$ssid)
-tmp.df2<- subset(tmp.df2, !is.na(ssid))
-
-```
-
-#####################################################################################
-# gp preprocessing funtion, checks for losses, averages gaze, pupil and pixelate
-#####################################################################################
-
-```{r, gppreprocessing}
-gp_preprocessing = function(tmp.df2) {
-
-  message(sprintf("step1 lft gaze validity"))
-
-  # transform invalid gaze into NA based on validity codes
-
-  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$status != '20', tmp.df2$left_gaze_x, NULL)
-  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$status != '22', tmp.df2$left_gaze_x_cor, NULL)
-  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$status != '20', tmp.df2$left_gaze_y, NULL)
-  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$left_gaze_y_cor, NULL)
-
-  message(sprintf("step2 right gaze validity"))
-
-  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$status != '2', tmp.df2$right_gaze_x, NULL)
-  #
-  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_x_cor, NULL)
-  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_y, NULL)
-  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_y_cor, NULL)
-
-  # pupil validity
-
-  message(sprintf("step3 pupil validity"))
-  tmp.df2$left_pupil_measure1<- if_else(tmp.df2$status != '20', tmp.df2$left_pupil_measure1, NULL)
-  tmp.df2$left_pupil_measure1<- if_else(tmp.df2$status != '22', tmp.df2$left_pupil_measure1, NULL)
-
-  tmp.df2$right_pupil_measure1<- if_else(tmp.df2$status != '2', tmp.df2$right_pupil_measure1, NULL)
-  tmp.df2$right_pupil_measure1<- if_else(tmp.df2$status != '22', tmp.df2$right_pupil_measure1, NULL)
-  table(is.na(tmp.df2$right_pupil_measure1))
-
-  # check gazepoint out of bounds nd repixelate (1920/2 = 960 by 1200/2 = 600. add half to normalised coordinates from psychopy)
-
-  message(sprintf("step 4 cutting off screen in points and repixelate"))
-
-  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$left_gaze_x_cor >= -960 & tmp.df2$left_gaze_x_cor <= 960, tmp.df2$left_gaze_x_cor, NULL)
-  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$right_gaze_x_cor >= -960 & tmp.df2$right_gaze_x_cor <= 960, tmp.df2$right_gaze_x_cor, NULL)
-
-  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$left_gaze_y_cor >= -600 & tmp.df2$left_gaze_y_cor <= 600, tmp.df2$left_gaze_y_cor, NULL)
-  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$right_gaze_y_cor >= -600 & tmp.df2$right_gaze_y_cor <= 600, tmp.df2$right_gaze_y_cor, NULL)
-
-  tmp.df2$left_gaze_x_cor_pix<- tmp.df2$left_gaze_x_cor+960
-  tmp.df2$right_gaze_x_cor_pix<- tmp.df2$right_gaze_x_cor+960
-
-  tmp.df2$left_gaze_y_cor_pix<- tmp.df2$left_gaze_y_cor+600
-  tmp.df2$right_gaze_y_cor_pix<- tmp.df2$right_gaze_y_cor+600
-
-  # is left or right an NA
-
-  tmp.df2$left_na<- is.na(tmp.df2$left_gaze_x_cor) 
-  tmp.df2$right_na<- is.na(tmp.df2$right_gaze_x_cor)
-  tmp.df2$both_na<- if_else(tmp.df2$left_na == TRUE & tmp.df2$right_na == TRUE, TRUE, FALSE)
-
-  message(sprintf("step5 gaze x  means"))
-
-  tmp.df2$gaze_x_cor<-if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_gaze_x_cor,
-                              if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_gaze_x_cor,
-                                      ((tmp.df2$left_gaze_x_cor + tmp.df2$right_gaze_x_cor)/2)))
-  message(sprintf("step6 gaze y means"))
-
-  tmp.df2$gaze_y_cor<-if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_gaze_y_cor,
-                              if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_gaze_y_cor,
-                                      ((tmp.df2$left_gaze_y_cor + tmp.df2$right_gaze_y_cor)/2)))
-
-  message(sprintf("step6 repixel gaze means"))
-
-  tmp.df2$gaze_x_cor_pix<- tmp.df2$gaze_x_cor + 960
-  min(tmp.df2$gaze_x_cor_pix, na.rm = TRUE)
-
-  tmp.df2$gaze_y_cor_pix<- tmp.df2$gaze_y_cor+600
-  min(tmp.df2$gaze_y_cor_pix, na.rm = TRUE)
-
-  # clean_pupil
-
-  message(sprintf("cleaning pupil"))
-
-  max(tmp.df2$left_pupil_measure1)
-
-  tmp.df2$pupil<- if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_pupil_measure1,
-                          if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_pupil_measure1,
-                                  ((tmp.df2$left_pupil_measure1 + tmp.df2$right_pupil_measure1)/2)))
-
-  # tmp.df2$trackloss<- if_else(tmp.df2$status > 0, TRUE, FALSE)
-  tmp.df2$trialUnq<- paste(tmp.df2$tNo, paste(tmp.df2$screencontent, paste(tmp.df2$stim)))
-  tmp.df2$distance = 630
-
-  # min(tmp.df2$pupil, na.rm = TRUE)
-  # max(tmp.df2$pupil, na.rm = TRUE)
-  # colnames(tmp.df2)
-  tmp.df2<- tmp.df2%>%
-    arrange(time)
-}
-
-tmp.df2<- gp_preprocessing(tmp.df2)
- colnames(tmp.df2)
-
-min(tmp.df2$pupil, na.rm = TRUE)
-max(tmp.df2$gaze_y_cor_pix, na.rm = TRUE)
-
-```
-
-Compute proportions outside the screen
-
-# check gazepoint out of bounds nd repixelate (1920/2 = 960 by 1200/2 = 600. add half to normalised coordinates from psychopy)
-
-  x -960 by 960
-  y -600 by 600
-
-```{r eval=FALSE, include=FALSE}
-range(tmp.df2$gaze_x_cor, na.rm = TRUE)
-
-tmp.df2
-range(tmp.df2$left_gaze_y, na.rm = TRUE)
-
-range(tmp.df2$left_gaze_y, na.rm = TRUE)
-range(tmp.df2$left_gaze_x, na.rm = TRUE)
-tmp.df2$x_outside<- ifelse(tmp.df2$left_gaze_x < -960, TRUE,
-                           ifelse(tmp.df2$left_gaze_x > 960, TRUE, FALSE))
-
-tmp.df2$y_outside<- ifelse(tmp.df2$right_gaze_y < -600, TRUE,
-                           ifelse(tmp.df2$right_gaze_y > 600, TRUE, FALSE))
-
-table(tmp.df2$y_outside)
-137/(185406+137)
-0.0007383733*100
-
-range(tmp.df, na.rm = TRUE)
-tmp.df2$y_outside<-NULL
-
-```
-
-# rezeroing times by trial, by participants
-
-```{r}
-tmp.df3<- tmp.df2
-
-# create start at every screen content
-tmp.df3<- tmp.df3%>% 
-  arrange(ssid, time, tNo)%>%
-  group_by(ssid)%>%
-  mutate(firststart = duplicated(trialUnq))
-
-head(tmp.df3)
-
-# make zero-times
-tmp.df3$zero<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, NULL)
-
-# fill in the zeros
-tmp.df3<- tmp.df3%>%
-  group_by(ssid, Condition, tNo)%>%
-  # group_by(text)%>%
-  fill(zero)
-
-unique(tmp.df3$zero)
-
-# rezero
-tmp.df3<-tmp.df3%>%
-  arrange(ssid, time, tNo)%>%
-  group_by(ssid, tNo)%>%
-  mutate(timerezero = time - zero)
-
-min(tmp.df3$timerezero, na.rm = TRUE)
-max(tmp.df3$timerezero, na.rm = TRUE) # max shoudl be around 120s for 2 mnutes
-natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)
-
-# let's check to see if it looks fine
-ggplot(subset(tmp.df3, tmp.df3$tNo == -1), aes(timerezero, gsr, colour = as.factor(ssid)))+
-  geom_line()
-
-# create a new time rezero where before stim start, time is negative
-
-tmp.df3<- tmp.df3%>%
-  # arrange(time)%>%
-  group_by(ssid, Condition, screencontent)%>%
-  mutate(firststartSTIM = duplicated(tNo))
-
-#this will create a time in the stim start which we can use to do the a second rezeroing
-tmp.df3$zero_stim<- if_else(tmp.df3$firststartSTIM == FALSE & tmp.df3$screencontent == 'stim', tmp.df3$time, NULL)
-
-    # fill down
-tmp.df3<- tmp.df3%>%
-      arrange(time)%>%
-      group_by(tNo, ssid)%>%
-      fill(zero_stim, .direction = c('updown'))
-
-   tmp.df3$timerezero2<- tmp.df3$time-tmp.df3$zero_stim
-
-   # check timerezero2
-     range(tmp.df3$timerezero2, na.rm = TRUE)
-
-# time 3 including rest
-  # simply includes rest as is
-
-tmp.df3$timerezero3<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$timerezero, tmp.df3$timerezero2)
-min(tmp.df3$timerezero3, na.rm = TRUE)
-
-# quick check that everything is fine
-
-ggplot(subset(tmp.df3, tmp.df3$tNo == 27 ) , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
-    geom_smooth()+
-    # geom_()+
-    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
-    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
-
-ggplot(subset(tmp.df3, tmp.df3$tNo == -4) , aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
-  # geom_point()
-      geom_line() +
-    # geom_smooth(aes())+
-    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
-    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
-
-ggplot(subset(tmp.df3, tmp.df3$tNo == -7) , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
-  # geom_point()
-      geom_line() +
-    # geom_smooth(aes())+
-    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
-    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
-
-```
-
-triggers
-
-```{r}
-unique(tmp.df3$tNo)
-
-natest<- subset(tmp.df3, is.na(tmp.df3$tNo) == TRUE)
-tmp.df3<- subset(tmp.df3, is.na(tmp.df3$tNo) == FALSE)
-
-tmp.df3$intercept_time<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, 
-                          if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$time,
-                                  NULL))
-
-# takes a bit with a group - so don't run
-# ggplot(tmp.df3, aes(time, gsr))+
-#   geom_line()+
-#   geom_vline(aes(xintercept = intercept_time))
-
-unique(tmp.df3$tNo)
-
-tmp.df3$trigger<- as.double(tmp.df3$tNo)
-
-tmp.df3$trigger<- if_else(tmp.df3$firststart == FALSE, tmp.df3$trigger, 
-                          if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$trigger, 0))
-unique(tmp.df3$trigger)
-
-tmp.df3$trigger <- if_else(tmp.df3$screencontent == 'fixation' &tmp.df3$firststart == FALSE, 100,
-                          if_else(tmp.df3$screencontent == 'ValenceResp' & tmp.df3$firststart == FALSE, 101,
-                             if_else(tmp.df3$screencontent == 'IntResp' & tmp.df3$firststart == FALSE, 102, tmp.df3$trigger)))
-
-unique(tmp.df3$trigger)
-
-tmp.df3$trigger<- if_else(tmp.df3$firststart == TRUE, 0, tmp.df3$trigger)
-
-unique(tmp.df3$trigger)
-
-```
-
-writing for ledalab
-
-```{r}
-
-tmp.df3<- tmp.df3%>%
-  arrange(ssid, tNo,time)
-# gsr baseline wil be the 1 second before tial start
-# gsr to microsiemnes 1/J3*100000
-
-options(scipen = 999)
-
-tmp.df3$gsr_ms <- 1/tmp.df3$gsr*100000
-unique(tmp.df3$ssid)
-max(tmp.df3$gsr_ms)
-min(tmp.df3$gsr_ms)
-
-# gsr for leda
-colnames(tmp.df3)
-db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49,51 ))
-db_GSR$tNo<- NULL
-colnames(db_GSR)
-
-unique(db_GSR$Condition)
-
-db_GSR$Condition2<- if_else(db_GSR$Condition == 'Rest', 'Rest', 'IAPS')
-unique(db_GSR$Condition2)
-db_GSR$split_column<- paste0(db_GSR$Condition2,paste(db_GSR$ssid))
-unique(db_GSR$split_column)
-  (sprintf("writing for ledlab"))
-
-split_column<- unique(db_GSR$split_column)
-
-split_gsr = split(db_GSR, list(db_GSR$split_column))
-
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021")
-
-    for (ssid in names(split_gsr)) {
-      write_tsv(split_gsr[[ssid]][,c("time","gsr_ms", "trigger")], paste0("gpgsr_", paste0(ssid),".txt"), col_names = FALSE)
-    }
-
-```
-
-# baselining gsr
-```{r}
-# use ms to baseline
-tmp.df3_backup<- tmp.df3
-
-tmp.df3$gsr_bas<- if_else(tmp.df3$timerezero3 >= -3 & tmp.df3$timerezero3 < 0, tmp.df3$gsr_ms, NULL)
-# true if baseline within window
-tmp.df3$gsr_bastrue<- if_else(tmp.df3$timerezero3 >= -3 & tmp.df3$timerezero3 < 0, TRUE, FALSE)
-
-# create baseline median
-tmp.df3$gsr_bas_mean<- NULL
-
-tmp.df3<- tmp.df3%>%
-  arrange(ssid, time,tNo)%>%
-  group_by(ssid, tNo, gsr_bastrue)%>%
-  mutate(gsr_bas_median = median(gsr_bas))
-
-# fill the baseline mean
-tmp.df3<- tmp.df3%>%
-  # arrange(time)%>%
-  group_by(ssid, tNo)%>%
-  fill(gsr_bas_median)
-
-# fill up to complete
-unique(tmp.df3$gsrv)
-
-tmp.df3<- tmp.df3%>%
-  # arrange(time)%>%
-  group_by(ssid, tNo)%>%
-  fill(gsr_bas_median, .direction = 'up')
-
-# do baseline correction
-# 
-tmp.df3<- tmp.df3%>%
-  # arrange(time)%>%
-  group_by(ssid, tNo)%>%
-  mutate(gsr_basCor = gsr_ms - gsr_bas_median)
-
-# rest baselining
-tmp.df3<- tmp.df3%>%
-  # arrange(time)%>%
-  group_by(ssid, Condition)%>%
-  mutate(gsr_restmedian = median(gsr_ms))
-
-tmp.df3$gsr_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$gsr_ms- tmp.df3$gsr_restmedian, tmp.df3$gsr_basCor)
-
-# plot diagnosis
-ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
-  # stat_summary(geom = 'line', fun.data = 'mean')+
-    geom_smooth()+
-    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
-    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
-
- ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
-  # stat_summary(geom = 'line', fun.data = 'mean')+
-    geom_smooth()+
-    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
-    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2) 
-  # tmp.df_norest$tNo<- as.factor(tmp.df_norest$tNo)
-
-ggplot(subset(tmp.df3, tmp.df3$screencontent == 'stim') , aes(x = timerezero3, y= gsr_basCor, olour = as.factor(ssid)))+
-    geom_smooth(aes())+
-    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
-    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
-
-tmp.df3_backup<- tmp.df3
-# gsr respone
-tmp.df3$gsr_resp_Log<- if_else(tmp.df3$timerezero3 > 1,TRUE, FALSE)
-unique(tmp.df3$gsr_resp_Log)
-
-tmp.df3 <- tmp.df3 %>%
-    group_by(ssid, tNo, gsr_resp_Log )%>%
-    mutate(gsr_response =   max(gsr_basCor))
-
-# gsr response for every bit
-unique(tmp.df3$screencontent)
-
-tmp.df3<- tmp.df3%>%
-  # arrange(time)%>%
-  group_by(ssid, tNo, screencontent)%>%
-  mutate(gsr_response_scrcont =   max(gsr_basCor))
-
-tmp.df3$gsr_response <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)
-
-tmp.df3<-
-  tmp.df3%>%
-  arrange(ssid, tNo,time)%>%
-  group_by(ssid, tNo)%>%
-    fill(gsr_response)
-
-tmp.df3<-
-  tmp.df3%>%
-  arrange(ssid, tNo,time)%>%
-  group_by(ssid, tNo)%>%
-    fill(gsr_response,  .direction = c('up'))
-
-unique(tmp.df3$gsr_response )
-
-tmp.df3_backup<- tmp.df3
-```
-
-#baseline and clean pupil
-
-```{r}
-library(gazer)
-
-min(tmp.df3$pupil, na.rm = TRUE)
-max(tmp.df3$pupil, na.rm = TRUE)
-
-tmp.df3$pupil<- if_else(tmp.df3$pupil> 7.2, tmp.df3$pupil, NULL)
-
-tmp.df3$pupil<- if_else(tmp.df3$pupil< 45, tmp.df3$pupil, NULL)
-
-tmp.df3_backup <- tmp.df3
-
-# note that smothing and interpolating is order dependednt so order by ssid, trial and time
-tmp.df3<- tmp.df3 %>%
-  arrange(ssid, time,tNo)%>%
-  group_by(ssid, trialUnq,tNo,screencontent) %>%
-  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=100, fillforward=100, hz=150))
-
-min(tmp.df3$extendpupil, na.rm = TRUE)
-max(tmp.df3$pupil, na.rm = TRUE)
-
-# let's check
-
-ggplot(subset(tmp.df3, tmp.df3$tNo == 3), aes(x = timerezero3, y= extendpupil , colour = as.factor(ssid)))+
-      geom_line()
-  # geom_line(aes(y = extendpupil), linetype = 'dashed', colour = 'red')
-
-# Smooth and Interpolate
-tmp.df3$subject<- tmp.df3$ssid
-tmp.df3$trial = tmp.df3$trialUnq
-
-# min(pup_extend$pupil, na.rm = TRUE)
-tmp.df3$extendpupil
-# ?smooth_interpolate_pupil
-
-# library(gazer)
-
-?smooth_interpolate_pupil
-
-# vert order dependent
-tmp.df3 <- gazer::smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
-                                    extendblinks=TRUE, step.first= 'smooth',
-                                    maxgap=Inf, 
-                                    filter = 'moving',
-                                    type="linear", hz=150, n = 30)
-
-# tmp.df3<- tmp.df3 %>%
-#   group_by(ssid, trialUnq,tNo,screencontent) %>%
-#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
-#                                     extendblinks=TRUE, 
-#                            step.first= 'smooth',
-#                                     maxgap=10, 
-#                                     filter = 'moving',
-#                                     type="linear", hz=20, n = 10)
-# 
-# 
-# tmp.df3<-
-#   tmp.df3%>%
-#   arrange(ssid,tNo,time)
-#   # group_by(ssid, tNo, timerezero3)%>%
-# 
-# tmp.df3te<- tmp.df3 %>%
-#   group_by(ssid, Condition,tNo,screencontent) %>%
-#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
-#                                     extendblinks=TRUE, 
-#                            step.first= 'smooth',
-#                                     maxgap=Inf, 
-#                                     filter = 'moving',
-#                                     type="linear", hz=100, n = 5)
-
-min(tmp.df3$pup_interp, na.rm = TRUE)
-max(tmp.df3$pup_interp, na.rm = TRUE)
-
-subset(tmp.df3, tNo == 20 & ssid == 347)%>%
-ggplot(aes(x = timerezero3, y= pup_interp))+
-  geom_line()+
-   geom_line(aes(y = extendpupil), color = 'red')+
-  geom_line(aes(y = pupil), colour = 'gray')
-  # facet_grid(~Condition)
-
-subset(tmp.df3, tNo == -7 & ssid == 350)%>%
-ggplot(aes(x = timerezero3, y= pupil))+
-  geom_line()
-
-subset(tmp.df3, tNo == 1)%>%
-ggplot(aes(x = timerezero3, y= pup_interp))+
-  geom_line()+
-   # geom_line(aes(y = extendpupil), color = 'red')+
-  # geom_line(aes(y = pup_interp), colour = 'gray')+
-    facet_grid(~ssid)
-  # facet_grid(~Condition)
-```
-
-# create baseline pupil mean
-```{r}
-tmp.df3backup<- tmp.df3
-tmp.df3$pup_bas<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, tmp.df3$pup_interp, NULL)
-# true if bseline if baseline within widnown
-tmp.df3$pup_bastrue<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, TRUE, FALSE)
-
-tmp.df3<- tmp.df3%>%
-  # arrange(time)%>%
-  group_by(ssid, tNo, pup_bastrue)%>%
-  mutate(pup_bas_med = median(pup_bas))
-
-# fill the baseline mean pupil
-tmp.df3<- tmp.df3%>%
-  # arrange(time)%>%
-  group_by(ssid,tNo)%>%
-  fill(pup_bas_med)
-
-# fill up to complete pupil
-tmp.df3<- tmp.df3%>%
-  # arrange(time)%>%
-  group_by(ssid, tNo)%>%
-  fill(pup_bas_med, .direction = 'up')
-
-# do baseline correction
-tmp.df3<- tmp.df3%>%
-  arrange(ssid, tNo, time)%>% # pay attentipn to order
-  group_by(ssid, tNo)%>%
-  mutate(pup_basCor = pup_interp - pup_bas_med)
-
-# we only one the median for rest
-tmp.df3<- tmp.df3%>%
-  group_by(Condition)%>%
-  mutate(pupilrest = median(pup_interp))
-
-tmp.df3$pup_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$pup_interp-tmp.df3$pupilrest, tmp.df3$pup_basCor)
-
-# MAD removal
-library(gazer)
-max_pup<-tmp.df3 %>%
-  dplyr::group_by(subject, trial) %>%
-  dplyr::mutate(speed=speed_pupil(pup_interp,time)) %>%
-  dplyr::mutate(MAD=calc_mad(speed))
-  # dplyr::filter(speed < MAD)
-
-tmp.df3<- max_pup
-
-# instead of deleting, nus put NA
-tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)
-
-tmp.df3$pup_interp_mad<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_interp, NULL)
-# tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)
-
-ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
-    # geom_smooth(se = F)+
-  geom_line()+
-    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
-    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
-
-ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
-    # geom_smooth(se = F)+
-  geom_line()+
-    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
-    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)+
-  xlim(-3,3)
-
-# preparation
-subset(tmp.df3, tNo == 10)%>%
-  group_by(ssid, tNo)%>%
-  mutate(pupil_z = pup_interp_mad - mean(pup_interp_mad, na.rm = TRUE))%>%
-  ungroup()%>%
-ggplot(aes(x = timerezero3, y= pupil_z))+
-    # geom_smooth(se = F)+
-  stat_summary(fun = mean, geom = 'line')+
-    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
-    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)+
-  xlim(-3,15)
-```
-unique(tmp.df3$ssid)
-
-```{r}
-# rest period
-ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
-    geom_smooth(se = T)+
-    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
-    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
-    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
-
-```
-
-```{r}
-colnames(tmp.df3)
-table(is.na(tmp.df3$gsr_ms))
-table(is.na(tmp.df3$hr))
-
-# heart rate
-
-min(tmp.df3$hr, na.rm = TRUE)
-max(tmp.df3$hr, na.rm = TRUE)
-
-tmp.df3$hrv<- as.double(tmp.df3$hrv)
-tmp.df3$hrv2<- if_else(is.na(tmp.df3$hrv) == TRUE, 999,tmp.df3$hrv)
-
-tmp.df3$hr_clean<- tmp.df3$hr
-tmp.df3$hr_clean<- as.double(tmp.df3$hr_clean)
-
-tmp.df3$hr_clean<- if_else(tmp.df3$hrv2 >0,  tmp.df3$hr_clean, NULL)
-
-tmp.df3$hr_clean<- if_else(tmp.df3$hr_clean > 40 & tmp.df3$hr_clean< 120, tmp.df3$hr_clean, NULL)
-
-table(is.na(tmp.df3$hr_clean))
-# interpolate, only 2 seconds 
-library(zoo)
-
-tmp.df3<- tmp.df3%>%
-  arrange(ssid, time,tNo)
-
-# tmp.df3$hr_interp =
-
-tmp.df3<- tmp.df3%>%
-  # arrange(ssid, time, tNo)%>%
-  group_by(ssid, tNo,screencontent)%>%
-  mutate(hr_interp = na.approx(hr_clean, na.rm=FALSE, maxgap =400))
-
-  min(tmp.df3$hr, na.rm = TRUE)
-ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 352) , aes(x = timerezero3, y= hr_interp))+
-    # geom_smooth(se = F)+
-  geom_line()+
-  geom_line(aes(y = hr_clean), linetype = 'dashed', colour = 'green', size = 0.3)+
-   geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
-    # geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
-    # geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
-    # geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
-    # geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)
-
-# na.approx(object, x = index(object), xout, ..., na.rm = TRUE, maxgap = Inf, along)
-# z <- na.spline(zoo(y, x), maxgap = 2)
-
-```
-
-```{r}
-tmp.df3 <- tmp.df3 %>%
-    group_by(ssid, tNo, gsr_resp_Log, screencontent)%>%
-    mutate(gsr_response_bycond =   max(gsr_basCor))
-
-# tmp.df3$gsr_response_bycond <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)
-
-colnames(tmp.df3)
-# tmp.df4<- select(tmp.df3, c(1:3,10:22,27:30,33:37,44,46,47,51,53:56,60))
-
-tmp.df4<- select(tmp.df3, c("session_id", "event_id", "ssid", "subject", "text", "trial","trialUnq", "tNo","trigger", "Condition" ,"screencontent","stim",
-                            "time", "timerezero", "timerezero2", "timerezero3", "status","filename",
-                            "left_gaze_x_cor_pix","right_gaze_x_cor_pix","left_gaze_y_cor_pix","right_gaze_y_cor_pix",  "gaze_x_cor_pix",  "gaze_y_cor_pix",
-                            "pupil", "pup_interp_mad", "extendpupil","pup_basCor",
-                            "hr", "hrv", "hrp", "hr_clean", 'hr_interp', 
-                            'gsr_ms', 'gsr_basCor', 'gsr_response', 'gsr_response_bycond', 
-                            "distance"))
-head(tmp.df4)
-
-# calculate trackloss
-unique(tmp.df4$status)
-
-tmp.df4$trackloss<- if_else(is.na(tmp.df4$gaze_x_cor_pix) == TRUE, 0, 
-                         if_else(is.na(tmp.df4$gaze_y_cor_pix) == TRUE, 0, 1))
-unique(tmp.df4$trackloss)
-
-# tmp.df4$trackloss<- if_else(tmp.df4$status> 0, 1, 0)
-
-tmp.df4$hr_trackloss<- if_else(is.na(tmp.df4$hr_clean) == TRUE, 0, 1) # 1 means valid, 0 missing
-
-tmp.df4 <- tmp.df4 %>%
-  group_by(ssid, tNo, trialUnq, text)%>%
-  mutate(gaze_valid_prop = sum(trackloss)/n())%>%
-  mutate(gaze_loss_prop = 1 - gaze_valid_prop)%>%
-  mutate(hr_valid_prop = sum(hr_trackloss)/n())%>%
-  mutate(hr_loss_prop = 1 - hr_valid_prop)
-
-# check to see this is right
-ggplot(subset(tmp.df4, tmp.df3$ssid == 353) , aes(x = tNo, y= hr_valid_prop))+
-    # geom_smooth(se = F)+
-  geom_line()+
-  geom_line(aes(y = hr_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
-   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
-
-ggplot(subset(tmp.df4, tmp.df3$ssid == 354) , aes(x = tNo, y= gaze_valid_prop))+
-    # geom_smooth(se = F)+
-  geom_line()+
-  geom_line(aes(y = gaze_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
-   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
-
-colnames(tmp.df4)
-write_csv(tmp.df4, 'interodata_clean_gp_346_355.csv')
-
-# tmp.df4<- read_csv('intero_tsdata_clean.csv')
-
-tmp.df4<- tmp.df4%>%
-  arrange(ssid, time, tNo)
-
-unique(tmp.df4$trigger)
-
-# why
-
-tmp.df4$trigger2<- tmp.df4$trigger
-
-tmp.df4$trigger2<- if_else(tmp.df4$trigger>99, tmp.df4$trigger, as.double(tmp.df4$tNo))
-
-unique(tmp.df4$trigger2)
-
-# \why?
-tmp.df4<- tmp.df4%>%
-  group_by(ssid, tNo, text)%>%
-  mutate(stdev_gaze_x = sd(gaze_x_cor_pix, na.rm = TRUE))%>%
-  mutate(stdev_gaze_y = sd(gaze_y_cor_pix, na.rm = TRUE))
-
-tmp.df4$sdev_gazesum<- tmp.df4$stdev_gaze_x+ tmp.df4$stdev_gaze_y
-
-# summarise
-tmp.df4_sum<- tmp.df4%>%
-  arrange(ssid, time, tNo)%>%
-  group_by(ssid, subject, trial, Condition, screencontent, tNo, stim, trialUnq,text)%>%
-  summarise_at(c('pup_basCor', 'gsr_response','gsr_response_bycond', 'gsr_basCor', 'hr_interp', 'hr_clean', 'time', 'gaze_loss_prop', 'gaze_valid_prop', 'hr_valid_prop', 'hr_loss_prop', 'timerezero3', 'sdev_gazesum', 'stdev_gaze_x', 'stdev_gaze_y'), mean, na.rm = TRUE)
-
-tmp.df4_sum$trigger<-if_else(tmp.df4_sum$screencontent == 'fixation', 100,
-                          if_else(tmp.df4_sum$screencontent == 'ValenceResp', 101,
-                             if_else(tmp.df4_sum$screencontent == 'IntResp', 102, as.double(tmp.df4_sum$tNo))))
-
-unique(tmp.df4_sum$trigger)
-
-unique(tmp.df4_sum$trigger)
-tmp.df4_sum<- tmp.df4_sum%>%
-  arrange(time, tNo, ssid)
-
-write_csv(tmp.df4_sum, 'intero_aggdata_clean.csv')
-
-write_csv(tmp.df4_sum, 'intero_aggdata_clean_3046_355.csv')
-# 
-# head(tmp.df4_sum)
-# unique(tmp.df4_sum$tNo)
-
-ggplot(tmp.df4_sum, aes(tNo, gaze_valid_prop, colour = as.factor(ssid)))+
-  geom_point()+
-  geom_line()
-
-ggplot(subset(tmp.df4_sum, tmp.df4_sum$screencontent == 'stim'), aes(tNo, gaze_valid_prop, colour = as.factor(ssid)))+
-  geom_point()+
-  geom_line()
-
-ggplot(subset(tmp.df4_sum, tmp.df4_sum$screencontent == 'stim'), aes(gaze_valid_prop, colour = as.factor(ssid)))+
-# geom_density()+
-  geom_histogram()
-  # geom_line()
-
-```
-
-# for gaze parsing
-
-```{r}
-
-(sprintf("preparing for gazepath"))
-
-colnames(tmp.df4)
-
-  for_gazepath<- select(tmp.df4, c(2:15,17:26, 39:40,42:43))
-
-  for_gazepath$screencontent[for_gazepath$screencontent == 'rest1']<- 'fixation'
-  for_gazepath<- for_gazepath%>%
-    arrange(ssid, time, tNo)
-
-  colnames(for_gazepath)
-
-  for_gazepath<- subset(for_gazepath, is.na(for_gazepath$time) == FALSE)
-   # View(for_gazepath)
-
-  for_gazepath$split_column<- paste0(for_gazepath$ssid, paste0(for_gazepath$screencontent))
-  splitcol<- unique(for_gazepath$split_column)
-  splitcol
-  # ssid<- unique(for_gazepath$ssid)
-  # ssid
-  split_df = split(for_gazepath, list(for_gazepath$split_column))
-
-  setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/346_355")
-
-  (sprintf("writing for gazepath"))
-  # ssid = split(for_gazepath, list(for_gazepath$ssid))
-  # for (ssid in names(split_df)) {
-    for (splitcol in names(split_df)) {
-      # message( split_df[splitcol])
-      write_csv(split_df[[splitcol]], paste0('gp_',paste0(splitcol),".csv"))
-    }
-
-```
-
-process gazepath and ledalab
-
-gazepath settings
-
-left eye x coord: left_gaze_x_cor_pix
-left eye y coord: left_gaze_y_cor_pix
-
-didtance: distance (mm)
-
-right eye x coord: right_gaze__cor_pix
-right eye y coord: right_gaze_x_cor_pix
-didtance: distance (mm)
-
-trial index: trialnq
-
-sample rate: 150
-screen resolution height (pix): 1200
-screen resolution width (pix): 1920
-
-stimuli height (px): 768
-stimuli width (px): 1024
-variables to keep: trial unq
-
-203
-270
-
-```{r}
-
-# install.packages('gazepath')
-library(gazepath)
-GUI()
-
-```
-
-read parsed data
-```{r}
-read_parsed <- function(flnm) {
-    read_csv(flnm) %>%
-        mutate(filename = flnm)
-}
-
-db_parsed <- list.files(pattern = "*.csv", 
-               full.names = T) %>% 
-    map_df(~read_parsed(.))
-
-# return content between spaces
-# put things in the correct order
-library(stringr)
-
-db_parsed$screencontent<- str_extract(db_parsed$trialUnq, "(?<=\\s)(.*)(?=\\s)")
-unique(db_parsed$screencontent)
-db_parsed$screencontent[db_parsed$screencontent == 'rest1']<- 'fixation'
-
-db_parsed$screencontent_no<- if_else(db_parsed$screencontent == 'fixation', 1,
-                                      if_else(db_parsed$screencontent == 'stim', 2,
-                                              if_else(db_parsed$screencontent == 'ValenceResp', 3,
-                                                      if_else(db_parsed$screencontent == 'IntResp', 4, NULL))))
-
-db_parsed$tNo<- as.numeric(substr(db_parsed$trialUnq, 1,2))
-unique(db_parsed$screencontent_no)
-db_parsed$ssid<- substr(db_parsed$Participant, 4,6)
-
-db_parsed<- db_parsed%>%
-  arrange(ssid, tNo, screencontent_no)
-
-ggplot(db_parsed, aes(mean_x, mean_y))+
-  geom_point()+
-  facet_grid(ssid~screencontent)
-
-unique(db_parsed$tNo)
-# db_parsed$tNo<- if_else(db_parsed$tNo > -1, db_parsed$tNo-1, db_parsed$tNo )
-
-db_parsed<-db_parsed%>%
-  group_by(ssid, tNo, screencontent,Value)%>%
-  mutate(mean_fix_dur = mean(Duration))%>%
-  mutate(mean_POGsdSacAmp = mean(POGsdSacAmp))%>%
-  mutate(fix_count = sum(Value == 'f'))%>%
-  mutate(sac_count = sum(Value == 's'))
-
-# this might be needed for tempoal analisys
-write_csv(db_parsed, 'db_parsed.csv')
-write_csv(db_parsed, 'db_parsed_346_355.csv')
-
-db_parsed_summarised<- db_parsed%>%
-  group_by(ssid, tNo,screencontent, trialUnq, screencontent_no, Value)%>%
-  summarise_at(c('fix_count', 'sac_count', 'mean_fix_dur', 'mean_POGsdSacAmp', 'RMS'), mean, na.rm = TRUE)
-
-colnames(db_parsed_summarised)
-db_parsed_summarised_fix<- subset(db_parsed_summarised, db_parsed_summarised$Value == 'f')
-db_parsed_summarised_fix$sac_count<- NULL
-db_parsed_summarised_fix$POGsd<- db_parsed_summarised_fix$mean_POGsdSacAmp
-db_parsed_summarised_fix$mean_POGsdSacAmp<- NULL
-db_parsed_summarised_fix$Value<-NULL
-db_parsed_summarised_sac<- subset(db_parsed_summarised, db_parsed_summarised$Value == 's')
-db_parsed_summarised_sac$fix_count<- NULL
-db_parsed_summarised_sac$mean_sac_dur<-  db_parsed_summarised_sac$mean_fix_dur
-db_parsed_summarised_sac$SacAmp<- db_parsed_summarised_sac$mean_POGsdSacAmp
-db_parsed_summarised_sac$mean_POGsdSacAmp<- NULL
-db_parsed_summarised_sac$mean_fix_dur<- NULL
-db_parsed_summarised_sac$RMS<- NULL
-db_parsed_summarised_sac$Value<- NULL
-View(db_parsed_summarised_sac)
-View(db_parsed_summarised_fix)
-db_parsed_summarised_sac$Value<- NULL
-db_parsed_summarised_fix$Value<- NULL
-db_parsed_summarised_sac$RMS<- NULL
-
-View(db_parsed)
-
-colnames(db_parsed_summarised_fix)
-colnames(db_parsed_summarised_sac)
-
-db_parsed_summarised2<- left_join(db_parsed_summarised_fix,db_parsed_summarised_sac, by = (c('ssid', 'tNo', 'screencontent', "screencontent_no", "trialUnq")))
-
-db_parsed_summarised2<- db_parsed_summarised2%>%
-  arrange(ssid, tNo, screencontent_no)
-# View(db_parsed_summarised2)
-write_csv(db_parsed_summarised2, 'db_parsed_summarised.csv')
-write_csv(db_parsed_summarised2, 'db_parsed_summarised_346_355.csv')
-
-db_parsed_summarised2$ssid<- as.numeric(db_parsed_summarised2$ssid)
-db_parsed_summarised2
-
-# merge parsed with eyetracking data
-# tmp.df4_sum_full<- left_join(tmp.df4_sum_full,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent")) #original
-
-tmp.df4_sum_full<- left_join(tmp.df4_sum,db_parsed_summarised2, by = c("ssid", "trialUnq", "tNo", "screencontent"))
-
-# rm(tmp.df4_sum_fullt)
-# testna<- subset(tmp.df4_sum_fullt, is.na(tmp.df4_sum_fullt$mean_fix_dur) == TRUE)
-# 
-# tmp.df4_sum_fullt
-```
-
-Behavioral data
-
-```{r}
-# colnames(X309_2019_Dec_11_1807_01)
-library(data.table) 
-library(purrr)
-
-read_plus_beh <- function(flnm, select = c("condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
-                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt")) {
-  read.csv(flnm) %>% 
-    mutate(filename = flnm)
-}
-
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/IAPSBehav/346_355")
-# now read them
-db_beh <-
-  list.files(pattern = "*.csv",
-             full.names = T) %>%
-  map_df(~read_plus_beh(.))
-
-# problem file
-# db328$condition<-db328$ï..condition
-
-db328 <-select(db328, c("condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
-                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
-
-db328$ssid<- 328
-
-db328$filename<- db328$ssid
-
-files <- list.files(pattern = ".csv")
-files
-temp <- do.call(rbind,lapply(files, read.csv), header = TRUE)
-
-#install.packages("data.table", repos = "https://cran.rstudio.com")
-library(data.table)
-
-# Read all the files and create a FileName column to store filenames
-db_beh <- rbindlist(sapply(files, fread, simplify = FALSE),
-                use.names = TRUE, idcol = "filename")
-db_beh$condition <- db_beh$ï..condition
-
-db_beh<- select(db_beh, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
-                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
-
-db328<- select(db328, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
-                                     "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
-
-# 
-# db304<- rbindlist(sapply(files, fread, simplify = FALSE),
-#                 use.names = TRUE, idcol = "filename")
-# 
-# 
-# 
-# db304<- select(db304, c("filename", "condition", "stimIAPS","stimDescription", "ValenceMean","ArousalMean","trigger",
-#                                      "trialsPract.thisTrialN","trialIAPS.thisTrialN", "self_valence_4.response","self_valence_2.response","Self_intensity_2.response","Self_intensity_3.response", "self_valence_4.rt", "self_valence_2.rt", "Self_intensity_2.rt", "Self_intensity_3.rt"))
-
-# db304$ssid<- 304
-colnames(db_beh)
-# db_beh<- bind_rows(db_beh, db304)
-db_beh$ssid<- substr(db_beh$filename, 3,5)
-
-# for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i]))
-
-View(db_beh)
-
-colnames(db_beh)
-
-db_beh2<- db_beh
-
-# problem
-db328$filename<- as.character(db328$filename)
-db328$ssid<- as.character(db328$ssid)
-
-db328$ssid <- 328
-
-db_beh2<- bind_rows(db_beh2, db328)
-
-unique(db_beh2$ssid)
-
-# create one column for arousl and RT
-
-db_beh2$valence<- if_else(is.na(db_beh2$self_valence_4.response) == FALSE, db_beh2$self_valence_4.response,
-                          if_else(is.na(db_beh2$self_valence_2.response) == FALSE, db_beh2$self_valence_2.response, NULL))
-
-db_beh2$Self_intensity_3.response<- as.double(db_beh2$Self_intensity_3.response)                      
-db_beh2$arousal<- if_else(is.na(db_beh2$Self_intensity_2.response) == FALSE, as.numeric(db_beh2$Self_intensity_2.response),
-                          if_else(is.na(db_beh2$Self_intensity_3.response) == FALSE,
-                                  as.numeric(db_beh2$Self_intensity_3.response), NULL))
-
-db_beh2$valence_rt<- if_else(is.na(db_beh2$self_valence_4.rt) == FALSE, db_beh2$self_valence_4.rt,
-                          if_else(is.na(db_beh2$self_valence_2.rt) == FALSE, db_beh2$self_valence_2.rt, NULL))
-
-db_beh2$arousal_rt<- if_else(is.na(db_beh2$Self_intensity_2.rt) == FALSE, db_beh2$Self_intensity_2.rt,
-                          if_else(is.na(db_beh2$Self_intensity_3.rt) == FALSE, db_beh2$Self_intensity_3.rt, NULL))
-
-db_beh2$trialsPract.thisTrialN<- db_beh2$trialsPract.thisTrialN - 6
-
-db_beh2$trialIAPS.thisTrialN<-db_beh2$trialIAPS.thisTrialN +1 
-db_beh2$tNo<- if_else(is.na(db_beh2$Self_intensity_2.response) == FALSE, db_beh2$trialsPract.thisTrialN, db_beh2$trialIAPS.thisTrialN)
-unique(db_beh2$tNo)
-db_beh2<- subset(db_beh2, is.na(db_beh2$tNo) == FALSE)
-
-db_beh2<- db_beh2%>%
-  arrange(ssid, tNo)
-
-ggplot(db_beh2, aes(tNo, valence, colour = ssid))+
-  geom_point()+
-  geom_line()
-
-ggplot(db_beh2, aes(x = tNo, y = valence_rt))+
-  geom_point()+
-  geom_line()
-
-ggplot(db_beh2, aes(x = valence, y = ValenceMean))+
-  geom_point()+
-  geom_smooth(method = lm, se = T)
-
-ggplot(db_beh2, aes(x = arousal, y = ArousalMean))+
-  geom_point()+
-  geom_smooth(method = lm, se = T)
-
-colnames(db_beh2)
-
-db_beh2$triggeracq<- db_beh2$trigger
-unique(db_beh2$ssid)
-
-db_beh3<- select(db_beh2, c(2:7, 18:23))
-
-# db_beh3<- subset(db_beh3, is.na(db_beh3$condition) == FALSE)
-
-colnames(db_beh3)
-
-colnames(db_beh3_301_309)
-
-db_beh3$trigger<-NULL
-db_beh3_301_309$triggeracq<- NULL
-
-db_beh3_301_309$condition[db_beh3_301_309$condition == "Example Stimuli"]<- "Practice"
-
-db_beh3$condition[db_beh3$condition == "Example Stimuli"]<- "Practice"
-
-# db_beh3$triggeracq<- NULL
-
-library(readr)
-db_beh300 <-  read_csv("300-309 beh/tmp.df4300_sum_full.csv")
-View(tmp_df4300_sum_full)
-
-db_beh300 <- subset(db_beh300, db_beh300$condition != "Rest")
-colnames(db_beh300)
-
-db_beh300$ssid<- 300
-
-db_beh300<- select(db_beh300, c("condition", "stimIAPS","stimDescription","ValenceMean", "ArousalMean", "ssid", "valence","arousal","valence_rt","arousal_rt", "tNo"))
-
-db_beh3$ssid<- as.numeric(db_beh3$ssid)
-db_beh_all<- bind_rows(db_beh3, db_beh300)
-db_beh_all<- bind_rows(db_beh_all, db_beh3_301_309)
-# db_beh4<- db_beh3
-
-unique(db_beh_all$ssid)
-
-str(tmp.df4_sum)
-str(db_beh_all)
-tmp.df4_sum$ssid<- as.numeric(tmp.df4_sum$ssid)
-
-db_beh3$ssid <- as.numeric(db_beh3$ssid)
-# rm(tmp.df4_sum_full_t)
-
-tmp.df4_sum_full<- left_join(tmp.df4_sum, db_beh_all, by = c('ssid', 'tNo'))
-tmp.df4_sum_full$ssid<- as.numeric(tmp.df4_sum_full$ssid)
-
-tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_beh3, by = c('ssid', 'tNo'))
-
-tmp.df4_sum_full<- tmp.df4_sum_full%>%
-  arrange(ssid, tNo, time)
-
-```
-
-# self reports
-- New Tas is already scored
-- use questionnaire scoring 2021
-- score AQ, etc using https://xavierrg.shinyapps.io/datacleaning
-
-gorilla codes
-
-STAI:: 5nzr
-AQ:7uqw
-STAIS: 8rfo
-Demog: 8zto
-BVAQ: 83b1
-BPQ: bbc4
-DASS: chif
-IQ: esh8
-IAS: jvi8
-TAS:pdlt
-demog_meantal health: v2gn
-
-consent: 8nsp
-
-```{r}
-
-db_selfrep <- read_csv("intero_selrep.csv")
-library(readxl)
-db_selfrep <- read_excel("db_self_rep_345_356_final.xlsx")
-# View(db_self_rep_345_356_final)
-
-db_selfrep$ssid <- as.character(db_selfrep$`Participant No`)
-tmp.df4_sum_full$ssid <- as.character(tmp.df4_sum_full$ssid)
-
-tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_selfrep, by = 'ssid')
-
-unique(tmp.df4_sum_full$ssid)
-# colnames(tmp_df4300_sum_full)
-# colnames(tmp.df4_sum_full)
-# 
-# tmp.df4_sum_full<- tmp.df4_sum_full[,1:54]
-# tmp.df4_sum_full<- bind_rows(tmp.df4_sum_full, tmp_df4300_sum_full)
-
-# db_selfrep <- read_csv("~/Documents/InteroStudy/data/Bio/Dec12/db_selfrep.csv")
-
-# db_selfrep$ssid<- as.numeric(db_selfrep$ssid)
-
-# tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_selfrep, by = 'ssid' )
-
-View(tmp.df4_sum_full)
-write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_345_356.csv')
-
-# tmp.df4_sum_full<- tmp.df4_sum_full%>%
-#   arrange(ssid, tNo, screencontent_no)
-```
-
-# Import Ledalab
-Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 105 .01 2])
-
-Ledalab('/Users/heliocuve/Documents/InteroStudy/EATProcesing/EAT/forLeda/', 'open','biopac','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2])
-
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021")
-
-Ledalab('/Users/heliocuve/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021/', 'open','text3','downsample', 15, 'smooth',{'adapt'}, 'analyze','CDA', 'optimize',3, 'export_era', [1 6 .01 2])
-
-SC column = 2
-Event marker column 3
-sampling rate 150hz
-
-346, 351 - GP gsr data is messed up
-- Note triggers need to be recreated here, never figured out why the digital events don't translate to ledalab
-
-```{r}
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021/Processed")
-
-read_leda <- function(flnm) {
-  data.table::fread(flnm) %>% 
-    mutate(filename = flnm)
-}
-
-# now read them
-db_leda <-
-  list.files(pattern = "*.txt", 
-             full.names = T) %>% 
-  map_df(~read_leda(.))
-
-db_leda$trigger<- as.numeric(db_leda$Event.NID)
-unique(db_leda$trigger)
-
-db_leda$ssid<- as.numeric(substr(db_leda$filename, 13,15))
-
-colnames(tmp.df4_sum)
-colnames(db_leda)
-
-nrow(tmp.df4_sum)
-nrow(db_leda)
-
-colnames(tmp.df4_sum)
-
-tmp.df4_sum2<- subset(tmp.df4_sum,tmp.df4_sum$tNo != -7)
-
-tmp.df4_sum2<- tmp.df4_sum2%>%
-  arrange(ssid, time, tNo)%>%
-  group_by(ssid)%>%
-  mutate(order = 1:n())
-
-db_leda2<- subset(db_leda, db_leda$trigger != -7)
-
-db_leda2<- db_leda2%>%
-  arrange(ssid, Event.Nr)%>%
-  group_by(ssid)%>%
-  mutate(order = 1:n())
-
-unique(db_leda2$order)
-
-range(db_leda2$order, na.rm = TRUE)
-
-# tmp.df4_sum_fullt<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
-# tmp.df4_sum_full_backup<- tmp.df4_sum_full
-
-tmp.df4_sum_full<- left_join(tmp.df4_sum2, db_leda2, by = c("order", "trigger", "ssid"))
-
-# tmp.df4_sum_full<- bind_cols(tmp.df4_sum, db_leda)
-
-tmp.df4_sum_full<- tmp.df4_sum_full%>%
-  arrange(ssid, tNo)
-
-View(tmp.df4_sum_full)
-```
-
-check
-```{r}
-
-View(tmp.df4_sum_full)
-
-# check stiom screen
-tmp.df4_sum_full_stim<- subset(tmp.df4_sum_full,  tmp.df4_sum_full$screencontent == 'stim')
-
-# levels(as.factor(tmp.df4_sum_full_stim$Event.Name))
-
-# exclude trials with very low gaze validity
-tmp.df4_sum_full_stim<- subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$gaze_valid_prop> .85)
-colnames(tmp.df4_sum_full_stim)
-
-```
-
-```{r eval=FALSE, include=FALSE}
-
-# is objective arousal and self report arousal correated
-tmp.df4_sum_full_stim$ValenceMean_cat<- if_else(tmp.df4_sum_full_stim$ValenceMean > 4, 'pos', 'neg')
-
-ggplot(tmp.df4_sum_full_stim, aes(arousal, log1p(TTP.AmpSum)), color = as.factor(ssid))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-  facet_grid(~ValenceMean_cat)
-ggplot(tmp.df4_sum_full_stim, aes(arousal, log1p(TTP.AmpSum), color = as.factor(ssid)))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-   facet_grid(~ValenceMean_cat)
-  # facet_grid(~ssid) # for some subjects
-
-color = as.factor(ssid)
-ggplot(tmp.df4_sum_full_stim, aes(arousal, pup_basCor))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-   facet_grid(~ValenceMean_cat)
-  # facet_grid(~ssid)
-color = as.factor(ssid)
-ggplot(tmp.df4_sum_full_stim, aes(arousal, hr))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-   facet_grid(~ValenceMean_cat)
-
-ggplot(tmp.df4_sum_full_stim, aes(arousal, hr))+
-         geom_point()+
-  geom_smooth(method= 'lm')
-
-ggplot(tmp.df4_sum_full_stim, aes(arousal, pup_basCor))+
-         geom_point()+
-  geom_smooth(method= 'lm')
-
-# do our physio signals corelate with one another
-
-ggplot(tmp.df4_sum_full_stim, aes(gsr_basCor, hr, color = as.factor(ssid)))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-   facet_grid(~ValenceMean_cat)
-
-ggplot(subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$CDA.AmpSum > 0), aes(TTP.AmpSum, hr))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-   facet_grid(~ValenceMean_cat)
-
-ggplot(tmp.df4_sum_full_stim, aes(gsr_basCor, pup_basCor))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-   facet_grid(~ValenceMean_cat)
- colour = as.factor(ssid)
-ggplot(tmp.df4_sum_full_stim, aes(hr, pup_basCor))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-   facet_grid(~ValenceMean_cat)
-
-ggplot(tmp.df4_sum_full_stim, aes(arousal, log1p(CDA.PhasicMax)), color = as.factor(ssid))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-   facet_grid(~ValenceMean_cat)
-
-# okay arousal on gaze
-
-# is there and affect of arousal on number of fxation and saccadescolor = as.factor(ssid)
-library(tibble)
-
-is_outlier <- function(x) {
-  return(x < quantile(x, 0.25) - 1.5 * IQR(x) | x > quantile(x, 0.75) + 1.5 * IQR(x))
-}
-
-ggplot(tmp.df4_sum_full_stim, aes(CDA.PhasicMax, fix_count))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-   facet_grid(~ValenceMean_cat)
-
-ggplot(tmp.df4_sum_full_stim, aes(CDA.PhasicMax, sac_count))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-   facet_grid(~ValenceMean_cat)
-
-ggplot(tmp.df4_sum_full_stim, aes(ValenceMean_cat, sac_count))+
-  # geom_jitter()+
-  stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2)
-    # geom_boxplot()
-  # geom_text(aes(label=ssid),hjust=0, vjust=0)
-
-ggplot( tmp.df4_sum_full_stim, aes(IAS, cor_arousal))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-  # stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2)+
-    # geom_boxplot()+
-  # geom_text(aes(label=ssid),hjust=0, vjust=0)
-
-ggplot(tmp.df4_sum_full_stim, aes(ValenceMean_cat, fix_count))+
-  # geom_jitter()+
-  stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2) 
-    # geom_boxplot()+
-  # geom_text(aes(label=ssid),hjust=0, vjust=0)
-
-ggplot(tmp.df4_sum_full_stim, aes(ValenceMean_cat, mean_sac_dur))+
-  # geom_jitter()+
-  stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2)
-    # geom_boxplot()
-  # geom_text(aes(label=ssid),hjust=0, vjust=0)
-
-ggplot(tmp.df4_sum_full_stim, aes(ValenceMean_cat, mean_fix_dur))+
-  # geom_jitter()+
-  stat_summary( geom = 'pointrange', fun.data = 'mean_se', colour = "red", size = 2)
-  geom_boxplot()
-  # geom_text(aes(label=ssid),hjust=0, vjust=0)
-
-ggplot(tmp.df4_sum_full_stim, aes(CDA.PhasicMax, fix_count, color = as.factor(ssid)))+
-         geom_point()+
-  geom_smooth(method= 'lm')
-  # facet_grid(~ssid)+
-    # geom_text(aes(label=ssid),hjust=0, vjust=0)
-
-ggplot(subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$mean_fix_dur < 6000), aes(TTP.AmpSum, mean_fix_dur))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-   facet_grid(~ValenceMean_cat)
-
-ggplot(subset(tmp.df4_sum_full_stim, tmp.df4_sum_full_stim$mean_fix_dur < 6000 & tmp.df4_sum_full_stim$CDA.AmpSum>0 ), aes(CDA.PhasicMax, mean_fix_dur))+
-         geom_point()+
-  geom_smooth(method= 'lm')+
-   facet_grid(~ValenceMean_cat)
-
-ggplot(tmp.df4_sum_full_stim, aes(TAS, IAS))+
-         geom_point()+
-  geom_smooth(method= 'lm')
-
-p<- list()
-library(lmerTest)
-
-tmp.df4_sum_full_stim$TAS_c<- scale(tmp.df4_sum_full_stim$TAS, center = TRUE,scale = TRUE)
-tmp.df4_sum_full_stim$IAS_c<- scale(tmp.df4_sum_full_stim$IAS, center = TRUE, scale = TRUE)
-tmp.df4_sum_full_stim$arousal_c<- scale(tmp.df4_sum_full_stim$arousal, center = TRUE,scale = TRUE)
-
-tmp.df4_sum_full_stim<- tmp.df4_sum_full_stim%>%
-  group_by(ssid)%>%
-  mutate(cor_arousal = cor(arousal_c, hr))
-tmp.df4_sum_full_stim<- tmp.df4_sum_full_stim%>%
-  # mutate(ssid = as.factor(ssid))%>%
-  mutate(stim = as.factor(stim))
-tmp.df4_sum_full_stim$ssid<- as.factor(tmp.df4_sum_full_stim$ssid)
-
-tmp.df4_sum_full_stim$valence_c<- scale(tmp.df4_sum_full_stim$valence, center = TRUE, scale = TRUE)
-tmp.df4_sum_full_stim$TTP.AmpSum<- scale(tmp.df4_sum_full_stim$TTP.AmpSum,center = TRUE, scale = TRUE)
-
-# test soe models
-tmp.df4_sum_full_stimagg<- (tmp.df4_sum_full_stim%>%
-              group_by(ssid)%>%
-              summarise_at(c('IAS_c', 'TAS_c', 'AQ','cor_arousal', 'fix_count'), mean, na.rm = TRUE))
-
-ggplot(tmp.df4_sum_full_stimagg, aes(TAS_c, cor_arousal))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-
-ggplot(tmp.df4_sum_full_stimagg, aes(IAS_c, cor_arousal))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-
-# tmp.df4_sum_full_stimagg<- subset(tmp.df4_sum_full_stimagg, is.na(tmp.df4_sum_full_stimagg$IAS_c) == FALSE)
-
-p$a<- glmer(fix_count ~ 1 + IAS_c * CDA.ISCR *ValenceMean_cat + (1 | ssid ),
-           family = poisson(), data = tmp.df4_sum_full_stim)
-
-summary(p$a)
-
-p$a1<- lmer(mean_fix_dur ~ 1 + IAS_c * (arousal_c + hr) * ValenceMean_cat + (1 | ssid ),
-           REML = FALSE, data = tmp.df4_sum_full_stim)
-
-summary(p$a1)
-
-p$a1<- lmer(mean_fix_dur ~ 1 + IAS_c * + hr * ValenceMean_cat + (1 | ssid ),
-           REML = FALSE, data = tmp.df4_sum_full_stim)
-
-summary(p$a1)
-
-p$a2<- lmer(mean_fix_dur ~ 1 + IAS_c * (arousal_c + TTP.AmpSum) + (1 | ssid ),
-           REML = FALSE, data = tmp.df4_sum_full_stim)
-
-summary(p$a2)
-
-p$a2<- lmer(mean_fix_dur ~ 1 + cor_arousal * hr + (1 | ssid ),
-           REML = FALSE, data = tmp.df4_sum_full_stim)
-
-tmp.df4_sum_full_stim$hr_c<- scale(tmp.df4_sum_full_stim$hr, center = TRUE, scale = TRUE)
-
-p$a3<- glmer(sac_count ~ 1 + IAS_c * hr * ValenceMean_cat  + (1 | ssid ),
-           family = poisson(), data = tmp.df4_sum_full_stim)
-
-summary(p$a3)
-# p$a2<- lmer(mean_fix_dur ~ 1 + cor_arousal * ( hr)+ (1 | ssid ),
-#            REML = FALSE, data = tmp.df4_sum_full_stim)
-p$a4<- lmer(gsr_basCor ~ 1 + IAS_c * arousal_c + (1 | ssid ),
-           REML = FALSE, data = tmp.df4_sum_full_stim)
-
-summary(p$a4)
-
-       tmp.df4_sum_full_stim_cor<- tmp.df4_sum_full_stim%>%
-  group_by(ssid, TAS, IAS, AQ, `DASS Total`)%>%
-  summarise(cor_arousal_self = cor(arousal,  log1p(CDA.PhasicMax)))
-
-ggplot(tmp.df4_sum_full_stim_cor, aes(`DASS Total`, cor_arousal_self))+
-         geom_point()+
-  geom_smooth(method= 'lm')
-
-cor(tmp.df4_sum_full_stim_cor$cor_arousal_self, tmp.df4_sum_full_stim_cor$TAS,  use = 'complete')
-cor(tmp.df4_sum_full_stim_cor$cor_arousal_self, tmp.df4_sum_full_stim_cor$IAS,  use = 'complete')
-cor(tmp.df4_sum_full_stim_cor$TAS, tmp.df4_sum_full_stim_cor$IAS,  use = 'complete')
-
-tmp.df4_sum_full_stim_cor [1:8,]%>%
-  summarise(cor2 = cor(cor_arousal_self, TAS, use = 'complete'))
-
-ggplot(tmp.df4_sum_full_stim, aes(arousal_c, log1p(mean_fix_dur)))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-```
-
-IMPORT BIOPAC
-
-```{r}
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/IAPS/processed/345_456/CDA")
-
-colnames(tmp.df4_sum_full)
-
-# import
-read_leda_bio <- function(flnm) {
-  data.table::fread(flnm) %>% 
-    mutate(filename = flnm)
-}
-
-# now read them
-db_leda_bio <-
-  list.files(pattern = "*.txt", 
-             full.names = T) %>% 
-  map_df(~read_leda_bio(.))
-
-write_csv(db_leda_bio, 'db_leda_bio.csv')
-write_csv(db_leda_bio, 'db_leda_bio_345_355_CDA.csv')
-
-# db_leda_bio <- read_csv("db_leda_bio.csv")
-
-db_leda_bio$trigger<- as.numeric(db_leda_bio$BIO_Event.NID)
-
-db_leda_bio$ssid<- as.numeric(substr(db_leda_bio$BIO_filename, 3,5))
-
-unique(db_leda_bio$ssid)
-
-unique(db_leda_bio$trigger)
-
-db_leda_bio_stim<-subset(db_leda_bio, db_leda_bio$trigger< 100)
-unique(db_leda_bio_stim$trigger)
-
-colnames(tmp.df4_sum_full_stim_gp_leda_beh_self)
-(unique(tmp.df4_sum_full_stim_gp_leda_beh_self$trigger))
-
-#tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full, tmp.df4_sum_full$ssid>303)
-# tmp.df4_sum_full_bio<- subset(tmp.df4_sum_full_bio, tmp.df4_sum_full_bio$trigger!= -7)
-
-#levels(as.factor(tmp.df4_sum_full_bio$ssid))
-#unique(tmp.df4_sum_full_bio$trigger)
-#levels(as.factor(db_leda_bio$ssid))
-
-db_leda_bio_stim$ssid<- as.character(db_leda_bio_stim$ssid)
-
-db_leda_bio_stim$trigger<- as.character(db_leda_bio_stim$trigger)
-
-#db_leda_bio$order<- db_leda_bio$Event.Nr
-tmp.df4_sum_full_stim_gp_leda_beh_self$ssid<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$ssid)
-tmp.df4_sum_full_stim_gp_leda_beh_self$trigger<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$trigger)
-
-colnames(tmp.df4_sum_full_stim_gp_leda_beh_self)
-
-unique(db_leda_bio$trigger)
-unique(db_leda_bio$Event.Name)
-unique(tmp.df4_sum_full_bio$trigger)
-unique(tmp.df4_sum_full_bio$Event.Name)
-
-tmp.df4_sum_full_stim_gp_leda_beh_self<- tmp.df4_sum_full_stim_gp_leda_beh_self%>%
-  arrange(ssid, tNo, Event.Nr)
-
-db_leda_bio_stim<- db_leda_bio_stim%>%
-  arrange(ssid, Event.Nr)
-
-#tmp.df4_sum_full_bio$trigger<- tmp.df4_sum_full_bio$tNo
-#tmp.df4_sum_full_bio$trigger<- if_else(tmp.df4_sum_full_bio$screencontent == 'fixation', 100,
- #                                      if_else(tmp.df4_sum_full_bio$screencontent == 'ValenceResp', 101,
-                                               #if_else(tmp.df4_sum_full_bio$screencontent == #'IntResp', 102, #tmp.df4_sum_full_bio$tNo)))
-
-unique(tmp.df4_sum_full_bio$trigger)
-tmp.df4_sum_full_stim_gp_leda_beh_self$Event.Nr<- as.character(tmp.df4_sum_full_stim_gp_leda_beh_self$Event.Nr)
-
-db_leda_bio_stim$Event.Nr<- as.character(db_leda_bio_stim$Event.Nr)
-View(tmp.df4_sum_full_stim_gp_leda_beh_self_biopac)
-
-tmp.df4_sum_full_stim_gp_leda_beh_self_biopac<-left_join(tmp.df4_sum_full_stim_gp_leda_beh_self, db_leda_bio_stim, by = c("Event.Nr", "ssid"))
-
-write_csv(tmp.df4_sum_full_stim_gp_leda_beh_self_biopac, 'tmp.df4_sum_full_stim_gp_leda_beh_self_biopac2.csv')
-
-(db_leda_bio$trigger)
-
-nrow(tmp.df4_sum_full_bio)
-nrow(db_leda_bio)
-
-tmp.df4_sum_full<- tmp.df4_sum_full%>%
-  arrange(ssid, tNo)
-
-ggplot(tmp.df4_sum_full_biot, aes(CDA.PhasicMax.x, CDA.PhasicMax.y))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-
-ggplot(tmp.df4_sum_full_biot, aes(TTP.AmpSum.x, TTP.AmpSum.y))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-
-tmp.df4_sum_full_biot
-ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308), aes(TTP.AmpSum.y, arousal, colour = ssid))+
-  geom_point()+
-  geom_smooth(method = 'lm', se = T)
-
-ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308), aes(TTP.AmpSum.y, arousal))+
-  geom_point()+
-  geom_smooth(method = 'lm', se = T)
-ggplot(subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308 & tmp.df4_sum_full_biot$TTP.AmpSum.y> 0), aes( TTP.AmpSum.y, arousal))+
-  geom_point()+
-  geom_smooth(method = 'lm', se = T)
-
-tmp.df4_sum_full_biot1 <-subset(tmp.df4_sum_full_biot, tmp.df4_sum_full_biot$ssid != 308)
-
-cor(tmp.df4_sum_full_biot1$arousal, tmp.df4_sum_full_biot1$Global.Mean.y, use = 'complete.obs')
-```
-
-import biopac heart rate
-```{r}
-nrow(tmp.df4_sum_full_bio)
-
-colnames(tmp.df4_sum_full_bio)
-unique(tmp.df4_sum_full_bio$ssid)
-
-unique(db_biohr$filename)
-
-# import
-read_biohr <- function(flnm) {
-  data.table::fread(flnm) %>% 
-    mutate(filename = flnm)
-}
-
-# now read them
-db_biohr <-
-  list.files(pattern = "*.csv", 
-             full.names = T) %>% 
-  map_df(~read_biohr(.))
-
-db_biohr$ssid<- substr(db_biohr$filename, 6,8)
-db_biohr$order<- db_biohr$Order
-
-db_biohr$Order<- NULL
-db_biohr$filename<- NULL
-db_biohr$trigger<- as.factor(as.character(db_biohr$trigger))
-unique(tmp.df4_sum_full_bio$ssid)
-unique(db_biohr$ssid)
-tmp.df4_sum_full_bio$trigger<- as.factor(as.character(tmp.df4_sum_full_bio$trigger))
-
-db_biohr$ssid<- as.factor(as.character(db_biohr$ssid))
-tmp.df4_sum_full_bio_hr<- left_join(tmp.df4_sum_full_biot, db_biohr, by = c('ssid', 'order', 'trigger'))
-
-ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(hr, HR_BIO))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-
-ggplot(subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent == 'stim'), aes(CDA.PhasicMax.x, CDA.PhasicMax.y))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-tmp.df4_sum_full_bio_hr_stim<- subset(tmp.df4_sum_full_bio_hr, tmp.df4_sum_full_bio_hr$screencontent != 'fixation')
-
-cor(tmp.df4_sum_full_bio_hr_stim$hr, tmp.df4_sum_full_bio_hr_stim$HR_BIO, use = 'complete')
-
-# tmp.df4_sum_full_bio_hr_stim_1<- subset(tmp.df4_sum_full_bio_hr_stim, tmp.df4_sum_full_bio_hr_stim$HR_BIO> 50)
-
-tmp.df4_sum_full_bio_hr_stim$valence_cat<- if_else(tmp.df4_sum_full_bio_hr_stim$valence >0, 'pos',
-                                                  if_else(tmp.df4_sum_full_bio_hr_stim$valence < 0, 'neg', 'neutral'))
-
-unique(tmp.df4_sum_full_bio_hr_stim$screencontent)
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-  # facet_grid(~valence_cat)
-
-cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$arousal, use = 'complete')
-cor(tmp.df4_sum_full_bio_hr_stim$HR_BIO, tmp.df4_sum_full_bio_hr_stim$valence, use = 'complete')
-
-tmp.df4_sum_full_bio_hr_stim%>%
-      group_by(ssid, IAS)%>%
-      summarise(corr = cor(HR_BIO, arousal, use = 'complete'))%>%
-  summarise(new = cor(corr, IAS))
-  # summarise_at(c('TAS'), mean)
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, arousal))+
-  geom_point()+
-  geom_smooth(method = 'lm')+
-  facet_grid(~valence_cat)
-
-tmp.df4_sum_full_bio_hr_stim%>%
-group_by(valence_cat)%>%
-  summarise(corr = cor(HR_BIO, arousal, use = 'complete'))
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, valence))+
-  geom_point()+
-  geom_smooth(method = 'lm')+
-  facet_grid(~valence_cat)
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, ValenceMean))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-  # facet_grid(~valence_cat)
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, mean_sac_dur))+
-  geom_point()+
-  geom_smooth(method = 'lm')+
-  facet_grid(~valence_cat)
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, pup_basCor))+
-  geom_point()+
-  geom_smooth(method = 'lm')+
-  facet_grid(~valence_cat)
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, Global.Mean.y))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, TAS))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-
-ggplot(tmp.df4_sum_full_bio_hr_stim, aes(HR_BIO, `DASS Anxiety`))+
-  geom_point()+
-  geom_smooth(method = 'lm')
-
-```

### 2022-12-03 Old scripts/intero_study_preprocessing.Rmd
test for Review
recover the power analyses files

--- 2021-08-19 intero_study_preprocessing.Rmd
@@
 BiocManager::install("rhdf5")
-library(rhdf5)
 
@@
 
-list.of.packages <- c("ggplot2", "data.table", 'readr', "c", 'tidyverse', "gazer", 'lmerTest')
+list.of.packages <- c("ggplot2", "data.table", 'readr', "rhdf5", 'tidyverse', "gazer", 'lmerTest')
 new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
-
-# if(length(new.packages)) install.packages(new.packages)
+if(length(new.packages)) install.packages(new.packages)
 lapply(list.of.packages, require, character.only = TRUE)
-# lapply(new.packages, require, character.only = TRUE)
-
-# install.packages('devtools')
+lapply(new.packages, require, character.only = TRUE)
+
+install.packages('devtools')
 
@@
 
-# 2021 data
-setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021")
-hdf5FilesPath<- "~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021"
-
 ```
@@
 # gp extractor function
-takes gp files and returns a clean files with messages parsed and deletes unnecessary stuff
-
-Starting from 322 we have gsr v and hr v. and Pulse is around the 30
+takes gp files and returns a clean files with messages parsed and deletes unecessary stuff
+
+Starting from 322 we have gsr v and hr v. And OPulse is around the 30
 
@@
 tmp_full<- gp.extractor(hdf5FilesPath)
-
-```
-
-Problem files
-```{r}
-# 355  - did not finish IAPS
-# adjust below manually
-
-gp.extractor = function(hdf5FilesPath) {
-
-  setwd(hdf5FilesPath)
-
-  hdfFilesList = list.files(hdf5FilesPath, pattern = "\\.hdf5$")
-  hdfFilesList
-  if (length(hdfFilesList) == 0){
-
-    return(message('No HDF5 files found in the directory provided.'))
-  }
-   f = 10# adjust here to the index for the probematic file
-  for (f in 1:length(hdfFilesList)) {
-
-    message(sprintf("Extracting file %i / %i - %s", f, length(hdfFilesList), hdfFilesList[f]))
-
-    #ATTTENTIONNN  note this sometimes fails because we are using a notebook 
-    # Extract Events from hdf5, in that case run it from command
-    tmp.events =h5read(hdfFilesList[f], '/data_collection/events/experiment/MessageEvent')
-
-    # Fixing 228
-    # session 1 = IAPS
-    nrow(tmp.events)
-    # tmp.events<- subset(tmp.events, tmp.events$session_id == 1)
-
-    tmp.eyetr  = h5read(hdfFilesList[f], '/data_collection/events/eyetracker/BinocularEyeSampleEvent')
-
-    # tmp.eyetr<- subset(tmp.eyetr, tmp.eyetr$session_id == 1)
-
-    # tmp.events<- tmp.events[245:nrow(tmp.events), ]
-
-    # problem file
-    # tmp.events
-
-    # Get subejct id from Events
-    ssid = sapply(strsplit(grep('SubjJID', tmp.events$text, value = TRUE), split = ": "), "[", 2)
-    date = sapply(strsplit(grep('DATE', tmp.events$text, value = TRUE), split = ": "), "[", 2)
-    session = sapply(strsplit(grep('Session:', tmp.events$text, value = TRUE), split = ":"), "[", 2)
-    cali<- subset(tmp.events, grepl('Cali', tmp.events$text) == TRUE)
-
-    # Create DF for trials data
-    tmp.df = data.frame(matrix(ncol = ncol(tmp.eyetr)))
-    names(tmp.df) = names(tmp.eyetr)
-    colnames(tmp.df)
-
-    # Prepare Events, keep only start/end messages
-    phrases = c('tStart', 'tEnd')
-    tmp.events_backup<- tmp.events
-    # tmp.events<-  tmp.events_backup
-    tmp.events = subset(tmp.events, grepl(paste(phrases, collapse = "|"), tmp.events$text))
-
-    # Create start/end references
-    tmp.events$tStart   = NA
-    tmp.events$tEnd     = NA
-
-    # Trial number extraction 
-    tmp.events$tNo      = NA
-    tmp.df$tNo          = NA
-    tmp.df$Condition    = NA
-
-    # Space for subject id
-    tmp.df$ssid         = NA
-    tmp.df$text<-NA
-
-    for (l in 1:nrow(tmp.events)) {
-      # sub(".*_", "", tmp.events)
-
-      # sub("[^_]*/_", "", tmp.events$text)
-      # ([^\/]+$)
-      # remove everything upto to _
-      # as.numeric(strsplit(tmp.events$text[l], split = '_')[[1]][3])
-      # "Extracting file %i / %i - %s", f, length(hdfFilesList), hdfFilesList[f])
-
-      message(sprintf("Grabing start messages %s", tmp.events$text[l]))
-
-      if ((grepl('tStart', tmp.events$text[l])) == TRUE) {
-        tmp.events$tStart[l] = tmp.events$time[l]
-
-        if ((grepl('tEnd', tmp.events$text[l+1])) == TRUE){
-          tmp.events$tEnd[l] = tmp.events$time[l+1]
-        }
-
-        else {
-          message('trial start/end structure not valid')
-        }
-      }
-
-    }
-    message(sprintf("done grabbing messages"))
-    # readline(prompt="Press [enter] to continue")
-
-    tmp.events$tNo<- as.numeric(as.character(gsub(".*_","",tmp.events$text)))
-
-    # tmp.events$tNo[is.na(tmp.events$tNo) == TRUE]<- -7
-
-    # tmp.events$screencontent = strsplit(tmp.events$text, split = '_')[[1]][2]
-    # readline(prompt="Press [enter] to continue")
-     message(sprintf("making screencontent"))
-    tmp.events$screencontent<- if_else(grepl('fixation', tmp.events$text), 'fixation',
-                                       if_else(grepl('Valence', tmp.events$text), 'ValenceResp',
-                                               if_else(grepl('rest', tmp.events$text), 'rest1', 
-                                                       if_else(grepl('IntResp', tmp.events$text), 'IntResp','stim'))))
-
-    unique(tmp.events$screencontent)
-
-    # first let's do condition
-
-    tmp.events$Condition<- if_else(grepl('IAPS', tmp.events$text), 'IAPS',
-                                   if_else(grepl('Example', tmp.events$text), 'Practice',
-                                           if_else(grepl('rest', tmp.events$text), 'Rest', NULL)))
-    tmp.events$stim<- if_else(tmp.events$Condition == 'IAPS', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text),
-                              if_else(tmp.events$Condition == 'Practice', sub(".*_ *(.*?) *jpg.*", "\\1", tmp.events$text), 'REST'))
-
-    # substitute periods
-    tmp.events$stim<- gsub('\\.', '.jpg', tmp.events$stim)
-    # tmp.events$tNo<- as.numeric(tmp.events$tNo)
-    tmp.events$tNo<- if_else(tmp.events$Condition == 'Practice', (tmp.events$tNo)-6,
-                             if_else(tmp.events$Condition == 'Rest',-7, tmp.events$tNo))
-    # tmp.events$tNo<- tmp.events$tNo1
-    tmp.events$tNo<- if_else(tmp.events$tNo> -1, tmp.events$tNo+1, tmp.events$tNo) # avoid zeros
-
-    tmp.events1 = subset(tmp.events, grepl('tStart',tmp.events$text))
-    tmp.events1$tNo1<- NULL
-    tmp.events1$tNo2<- NULL
-
-    # tmp.eyetr_backup<- tmp.eyetr
-    # tmp.df_backup<- tmp.df
-    # tmp.df<- tmp.df_backup
-    colnames(tmp.df)
-    # rm(tmp.raw.trial)
-    # colnames(tmp.raw.trial)
-    colnames(tmp.df)
-    colnames(tmp.events1)
-    colnames(tmp.eyetr)
-    tmp.df$screencontent<- NA
-    tmp.df$stim<- NA
-    # e=10
-    tmp.events1$tEnd<- if_else(tmp.events1$tNo == -7, tmp.events1$tStart+120, tmp.events1$tEnd)
-    message(sprintf("subsetting eyetracking data"))
-    e=1
-    for(e in 1:nrow(tmp.events1)) {
-
-      # Subset the EyeTracking data based on start/end
-      tmp.raw.trial = subset(tmp.eyetr, tmp.eyetr$time >= tmp.events1$tStart[e] & tmp.eyetr$time <= tmp.events1$tEnd[e])
-
-      tmp.raw.trial$tNo = tmp.events1$tNo[e]
-
-      tmp.raw.trial$Condition = tmp.events1$Condition[e]
-      tmp.raw.trial$screencontent = tmp.events1$screencontent[e]
-      tmp.raw.trial$stim = tmp.events1$stim[e]
-      # tmp.raw.trial$stim = tmp.events1$[e]
-      tmp.raw.trial$ssid = ssid
-      tmp.raw.trial$text = tmp.events1$text[e]
-       message(sprintf("binding tmp.df"))
-      tmp.df= rbind(tmp.raw.trial, tmp.df)
-    }
-     message(sprintf("done binding"))
-
-    # Add ssid
-    # tmp.df$ssID = ssid[e]
-    tmp.df<- tmp.df%>%
-      arrange(time)
-
-    # Save file
-    name = sprintf("ss%s_GPdata",ssid)
-    message(sprintf("saving data"))
-
-    write_csv(tmp.df, paste(name,".csv"))
-    # write_csv(tmp.df, "test.csv")
-    # write calibration cali
-    name2 = sprintf("ss%s_GPdata_cali", ssid)
-    write_csv(cali, paste(name2,".csv"))
-
-  }
-
-  # write_csv(tmp.df, 'tmpdf_extracted.csv')
-
-  message("Processing Completed.")
-  tmp.df
-}
-
-# tmp_full<- gp.extractor(hdf5FilesPath)
 

### 2022-12-03 PCA figures1.Rmd
test for Review
recover the power analyses files

@@
 
-newDFscale_stim<- newDF$subject%>%
+newDFscale_stim<- newDF%>%
   group_by(subject, subject_orig)%>%
@@
 colnames(newDFscale_sid_norm)
-res.MFA_stim_val_scal2e_sidnorm <-MFA(newDFscale_sid_norm[,1:7],group=c(2,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),
+res.MFA_stim_val_scal2e_sidnorm <-MFA(newDFscale_sid_norm[,1:7],group=c(2,3,2), type=c("n","c","c"),name.group=c("categorical","autonomic","subjective"),
                                       num.group.sup=c(1),graph=TRUE)
@@
 
-res.MFA_stim_val_scal2e_stim <-MFA(newDFscale_stim[,1:7],group=c(2,3,2), type=c("n","c","c"),name.group=c("qualitative","autonomic","subjective"),
+res.MFA_stim_val_scal2e_stim <-MFA(newDFscale_stim[,1:7],group=c(2,3,2), type=c("n","c","c"),name.group=c("categorical","autonomic","subjective"),
                                       num.group.sup=c(1),graph=TRUE)
+
+res.MFA_stim_val_scal2e_sid <-MFA(newDFscale_sid[,1:6],group=c(1,3,2), type=c("n","c","c"),name.group=c("categorical","autonomic","subjective"),
+                                      num.group.sup=c(1),graph=TRUE)
+
+newDFscale_sid
 
@@
  ggsave("cor_circle.tiff",   mfa_plots$cor_circle, device = "tiff", width = 10, height = 6, dpi = 800)
+
+```
+
+Supplementary materials
+
+```{r}
+plot.MFA(res.MFA_stim_val_scal2e_sidnorm)
+
+SM_plots<- list()
+
+SM_plots$sid_by_stimclass <-
+plot.MFA(res.MFA_stim_val_scal2e_sidnorm, 
+         choix="ind",
+         partial='all',
+         label = "norm",
+         lab.par=TRUE,
+         invisible= c('ind','quali'),
+         select='cos2  0',
+         habillage='group',
+         title="Factor map  \n aggregated by participant * stimulus category",
+         alpha = .2,
+         shadowtext = TRUE,
+         cex = 1)+
+  # # xlab(paste0("Dimension 1 (",round(mean(res.mfa_bio_vs_self2_scale$eig[1,2], na.rm = TRUE),2),"%[95%CI:",
+  #             paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
+  #                    round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
+  # ylab(paste0("Dimension 2 (",round(mean(res.mfa_bio_vs_self2_scale$eig[2,2], na.rm = TRUE),2),"%[95%CI:",
+  #             paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
+  #                    round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
+  annotate("text", label = paste0("total var: ", round(res.mfa_bio_vs_self2_scale$eig[2,3], 2), "%"), x = 2, y = -1.3, size = 5)+
+       scale_color_brewer(palette = "Dark2", labels = c("autonomic", "subjective"))+
+  theme_classic()+
+  p$graphstyle_int+
+   guides(colour = guide_legend(override.aes = list(size=2, stroke=1.5)))
+
+SM_plots$stim <- plot.MFA(res.MFA_stim_val_scal2e_stim, 
+         choix="ind",
+         partial='all',
+         label = "norm",
+         lab.par=TRUE,
+         invisible= c('ind','quali'),
+         select='cos2  0',
+         habillage='group',
+         title="Factor map \n aggerated by stimulus id",
+         alpha = .2,
+         shadowtext = TRUE,
+         cex = 1)+
+  # # xlab(paste0("Dimension 1 (",round(mean(res.mfa_bio_vs_self2_scale$eig[1,2], na.rm = TRUE),2),"%[95%CI:",
+  #             paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
+  #                    round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
+  # ylab(paste0("Dimension 2 (",round(mean(res.mfa_bio_vs_self2_scale$eig[2,2], na.rm = TRUE),2),"%[95%CI:",
+  #             paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
+  #                    round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
+  # annotate("text", label = paste0("total var: ", round(res.mfa_bio_vs_self2_scale$eig[2,3], 2), "%"), x = 2, y = -1.3, size = 5)+
+       scale_color_brewer(palette = "Dark2", labels = c("autonomic", "subjective"))+
+  theme_classic()+
+  p$graphstyle_int+
+   guides(colour = guide_legend(override.aes = list(size=2, stroke=1.5)))
+
+SM_plots$sid<- plot.MFA(res.MFA_stim_val_scal2e_sid, 
+         choix="ind",
+         partial='all',
+         label = "norm",
+         lab.par=TRUE,
+         invisible= c('ind','quali'),
+         select='cos2  0',
+         habillage='group',
+         title="Factor map \n aggregated by participant id",
+         alpha = .2,
+         shadowtext = TRUE,
+         cex = 1)+
+  # # xlab(paste0("Dimension 1 (",round(mean(res.mfa_bio_vs_self2_scale$eig[1,2], na.rm = TRUE),2),"%[95%CI:",
+  #             paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
+  #                    round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
+  # ylab(paste0("Dimension 2 (",round(mean(res.mfa_bio_vs_self2_scale$eig[2,2], na.rm = TRUE),2),"%[95%CI:",
+  #             paste0(round(mean(eigen_first1$perc_5[eigen_first1$component == "comp 1"], na.rm = TRUE),2), ",",
+  #                    round(mean(eigen_first1$perc_95[eigen_first1$component == "comp 2"], na.rm = TRUE),2), "])")))+
+  # annotate("text", label = paste0("total var: ", round(res.mfa_bio_vs_self2_scale$eig[2,3], 2), "%"), x = 2, y = -1.3, size = 5)+
+       scale_color_brewer(palette = "Dark2", labels = c("autonomic", "subjective"))+
+  theme_classic()+
+  p$graphstyle_int+
+   guides(colour = guide_legend(override.aes = list(size=2, stroke=1.5)))
+
+# Group representation
+# sid_by_stimclass
+SM_plots$sid_by_stimclas_GR<-  bind_rows(as.data.frame(res.MFA_stim_val_scal2e_sidnorm$group$coord),
+          as.data.frame(res.MFA_stim_val_scal2e_sidnorm$group$coord.sup))%>%
+  mutate(group = rownames(bind_rows(as.data.frame(res.MFA_stim_val_scal2e_sidnorm$group$coord),
+          as.data.frame(res.MFA_stim_val_scal2e_sidnorm$group$coord.sup))))%>%
+  mutate(group = factor(group, levels = c("autonomic", "subjective","categorical"  ),
+                        labels = c("autonomic","subjective","categorical")))%>%
+  ggplot(aes(x = seq(0,1,.1), y =seq(0,1,.1)))+
+  geom_vline(xintercept = res.MFA_stim_val_scal2e_sidnorm$group$coord[1,1], linetype = "dashed")+
+  geom_vline(xintercept = res.MFA_stim_val_scal2e_sidnorm$group$coord[2,1], linetype = "dashed")+
+    geom_hline(yintercept = res.MFA_stim_val_scal2e_sidnorm$group$coord[1,2], linetype = "dashed")+
+  geom_hline(yintercept = res.MFA_stim_val_scal2e_sidnorm$group$coord[2,2], linetype = "dashed")+
+  geom_point(aes(x = Dim.1, y = Dim.2, shape = group, fill = group, color = group), size = 8, alpha = .5)+
+
+   # size = tyextsize*8
+  geom_text(aes(x = Dim.1, y = Dim.2+.05, label = group, color = group 
+               ), size = 8)+
+    # annotate("text",label = group x = Dim.1, y = Dim.2))+
+  xlim(0,1)+
+      theme_classic()+
+      xlab("Dimension 1")+
+   ylab("Dimension 2")+
+  ggtitle("Groups representation")+
+  scale_color_brewer(palette = "Dark2", direction = -1)+
+    scale_fill_brewer(palette = "Dark2",direction = -1)+
+  theme(legend.position = "none",
+
+        # axis.text.x = element_blank(),
+        # axis.text.y = element_blank(),
+        plot.title = element_text(hjust = .5, size = 16*(sf+.5)))
+
+  # theme(g) = element_blank())
+
+SM_plots$sid_by_stimclas_GR<- SM_plots$sid_by_stimclas_GR+
+  p$graphstyle+
+    scale_colour_brewer(palette = "Dark2",
+                      labels=c("categorical","autonomic","subjective"))+
+    scale_fill_brewer(palette = "Dark2",
+                      labels=c("categorical","autonomic","subjective"))+
+   theme(legend.position = "none",
+
+        # axis.text.x = element_blank(),
+        # axis.text.y = element_blank(),
+        plot.title = element_text(hjust = .5, size = 16*(sf+.5)))
+
+# GR forSM_plots$stim <- plot.MFA(res.MFA_stim_val_scal2e_stim,
+
+SM_plots$stim_GR<-  bind_rows(as.data.frame(res.MFA_stim_val_scal2e_stim$group$coord),
+          as.data.frame(res.MFA_stim_val_scal2e_stim$group$coord.sup))%>%
+  mutate(group = rownames(bind_rows(as.data.frame(res.MFA_stim_val_scal2e_stim$group$coord),
+          as.data.frame(res.MFA_stim_val_scal2e_stim$group$coord.sup))))%>%
+  mutate(group = factor(group, levels = c("autonomic", "subjective","categorical"  ),
+                        labels = c("autonomic","subjective","categorical")))%>%
+  ggplot(aes(x = seq(0,1,.1), y =seq(0,1,.1)))+
+  geom_vline(xintercept = res.MFA_stim_val_scal2e_stim$group$coord[1,1], linetype = "dashed")+
+  geom_vline(xintercept = res.MFA_stim_val_scal2e_stim$group$coord[2,1], linetype = "dashed")+
+    geom_hline(yintercept = res.MFA_stim_val_scal2e_stim$group$coord[1,2], linetype = "dashed")+
+  geom_hline(yintercept = res.MFA_stim_val_scal2e_stim$group$coord[2,2], linetype = "dashed")+
+  geom_point(aes(x = Dim.1, y = Dim.2, shape = group, fill = group, color = group), size = 8, alpha = .5)+
+
+   # size = tyextsize*8
+  geom_text(aes(x = Dim.1, y = Dim.2+.05, label = group, color = group 
+               ), size = 8)+
+    # annotate("text",label = group x = Dim.1, y = Dim.2))+
+  xlim(0,1)+
+  ylim(0,1)+
+      theme_classic()+
+      xlab("Dimension 1")+
+   ylab("Dimension 2")+
+  ggtitle("Groups representation")+
+  scale_color_brewer(palette = "Dark2", direction = -1)+
+    scale_fill_brewer(palette = "Dark2",direction = -1)+
+  theme(legend.position = "none",
+
+        # axis.text.x = element_blank(),
+        # axis.text.y = element_blank(),
+        plot.title = element_text(hjust = .5, size = 16*(sf+.5)))
+
+  # theme(g) = element_blank())
+
+SM_plots$stim_GR <- SM_plots$stim_GR +
+  p$graphstyle+
+    scale_colour_brewer(palette = "Dark2",
+                      labels=c("categorical","autonomic","subjective"))+
+    scale_fill_brewer(palette = "Dark2",
+                      labels=c("categorical","autonomic","subjective"))+
+   theme(legend.position = "none",
+
+        # axis.text.x = element_blank(),
+        # axis.text.y = element_blank(),
+        plot.title = element_text(hjust = .5, size = 16*(sf+.5)))
+
+SM_plots$stim_GR
+
+# ssid
+# SM_plots$sid<- plot.MFA(res.MFA_stim_val_scal2e_sid,
+
+SM_plots$ssid_GR<-  bind_rows(as.data.frame(res.MFA_stim_val_scal2e_sid$group$coord),
+          as.data.frame(res.MFA_stim_val_scal2e_sid$group$coord.sup))%>%
+  mutate(group = rownames(bind_rows(as.data.frame(res.MFA_stim_val_scal2e_sid$group$coord),
+          as.data.frame(res.MFA_stim_val_scal2e_sid$group$coord.sup))))%>%
+  mutate(group = factor(group, levels = c("autonomic", "subjective","categorical"  ),
+                        labels = c("autonomic","subjective","categorical")))%>%
+  ggplot(aes(x = seq(0,1,.1), y =seq(0,1,.1)))+
+  geom_vline(xintercept = res.MFA_stim_val_scal2e_sid$group$coord[1,1], linetype = "dashed")+
+  geom_vline(xintercept = res.MFA_stim_val_scal2e_sid$group$coord[2,1], linetype = "dashed")+
+    geom_hline(yintercept = res.MFA_stim_val_scal2e_sid$group$coord[1,2], linetype = "dashed")+
+  geom_hline(yintercept = res.MFA_stim_val_scal2e_sid$group$coord[2,2], linetype = "dashed")+
+  geom_point(aes(x = Dim.1, y = Dim.2, shape = group, fill = group, color = group), size = 8, alpha = .5)+
+
+   # size = tyextsize*8
+  geom_text(aes(x = Dim.1, y = Dim.2-.1, label = group, color = group 
+               ), size = 8)+
+    # annotate("text",label = group x = Dim.1, y = Dim.2))+
+  xlim(0,1)+
+  ylim(0,1)+
+      theme_classic()+
+      xlab("Dimension 1")+
+   ylab("Dimension 2")+
+  ggtitle("Groups representation")+
+  scale_color_brewer(palette = "Dark2", direction = -1)+
+    scale_fill_brewer(palette = "Dark2",direction = -1)+
+  theme(legend.position = "none",
+
+        # axis.text.x = element_blank(),
+        # axis.text.y = element_blank(),
+        plot.title = element_text(hjust = .5, size = 16*(sf+.5)))
+
+  # theme(g) = element_blank())
+
+SM_plots$ssid_GR<- SM_plots$ssid_GR +
+  p$graphstyle+
+    scale_colour_brewer(palette = "Dark2",
+                      labels=c("categorical","autonomic","subjective"))+
+    scale_fill_brewer(palette = "Dark2",
+                      labels=c("categorical","autonomic","subjective"))+
+   theme(legend.position = "none",
+
+        # axis.text.x = element_blank(),
+        # axis.text.y = element_blank(),
+        plot.title = element_text(hjust = .5, size = 16*(sf+.5)))
+
+SM_plots$stim_GR 
+SM_plots$ssid_GR
+
+# correlation circles
+
+SM_plots$cor_circle_sid_stim_cat<- plot.MFA(res.MFA_stim_val_scal2e_sidnorm, choix="var",habillage='group',title="Correlation circle",
+         cex = 2.7) +
+    xlim(-1,1)+
+  scale_color_brewer(palette = "Dark2", direction = -1)+
+  theme_classic()+
+
+      xlab("Dimension 1")+
+   ylab("Dimension 2")+
+  # ggtitle("Groups representation")+
+  scale_color_brewer(palette = "Dark2")+
+    scale_fill_brewer(palette = "Dark2")+
+    p$graphstyle_int+
+  theme(legend.position = "none",
+
+        # axis.text.x = element_blank(),
+        # axis.text.y = element_blank(),
+        plot.title = element_text(hjust = .5, size = 16*(sf+.5)))
+
+ # ggsave("cor_circle.tiff",   mfa_plots$cor_circle, device = "tiff", width = 10, height = 6, dpi = 800)
+
+# cor circle stim
+
+SM_plots$cor_circle_stim<- plot.MFA(res.MFA_stim_val_scal2e_stim, choix="var",habillage='group',title="Correlation circle",
+         cex = 2.7) +
+    xlim(-1,1)+
+  scale_color_brewer(palette = "Dark2", direction = -1)+
+  theme_classic()+
+
+      xlab("Dimension 1")+
+   ylab("Dimension 2")+
+  # ggtitle("Groups representation")+
+  scale_color_brewer(palette = "Dark2")+
+    scale_fill_brewer(palette = "Dark2")+
+    p$graphstyle_int+
+  theme(legend.position = "none",
+
+        # axis.text.x = element_blank(),
+        # axis.text.y = element_blank(),
+        plot.title = element_text(hjust = .5, size = 16*(sf+.5)))
+
+SM_plots$cor_circle_stim
 

### 2022-12-03 Paper_Analyses_subj_obje_arousal1.Rmd
test for Review
recover the power analyses files

@@
 
+View(eigen_first)
+eigen_first1<- eigen_first %>%
+  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>% #retrieve names for components
+  # gather(dimension, value_dimenion, -group, -sim_no) %>%
+  group_by(component)%>%
+  # subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
+  mutate(perc_5 = quantile(`percentage of variance`,.025, na.rm = TRUE), 
+         perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE))
+
 eigen_first %>%
@@
 
+res.mfa_bio_vs_self2_scale$eig[2,3]
 ```
@@
   theme_classic()
+
+mfa_boot_corfirst<- left_join(cor_first1, cor.test_obsmfa, by = c("variable", "dimension"))
+
+mfa_boot_corfirst$measure<- if_else(mfa_boot_corfirst$variable == "log_BI", "SCR",
+        if_else(mfa_boot_corfirst$variable == "Bio_Me", "HR",
+                if_else(mfa_boot_corfirst$variable == "pup_ba", "pupil",
+                if_else(mfa_boot_corfirst$variable == "arousa", "arousal",
+                if_else(mfa_boot_corfirst$variable == "valenc", "valence",NULL)
+                ))))
+
+mfa_boot_corfirst$variable
+left_join(cor_first1, cor.test_obsmfa, by = c("variable", "dimension"))
+
+mfa_boot_corfirst%>%
+  subset(dimension == "Dim.1")%>%
+  ggplot(aes(value_dimenion.x, color = measure)) +
+  geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  # geom_density(alpha=.2) +
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-2 , linetype = measure))+ #color = "gray30"
+  # facet_grid(~dimension)+
+  geom_point(aes(x = value_dimenion.y, y = -2))+
+    geom_vline(xintercept = 0,linetype = "dashed", alpha = .5, size = 1)+
+  # facet_grid(~dimension)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  scale_color_brewer(palette = "Dark2")+
+
+  theme_classic()+
+  p$graphstyle_int
 
@@
 
+library(boot)
+library(rms)
+
+??bootBCa
+
 left_join(groups_first_1boot_CIcorrected2, groups_first_obs,by = c("group", "dimension"))%>%
@@
   facet_grid(dimension~group)+
+  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
+  theme_classic()
+
+left_join(groups_first_1boot_CIcorrected2, groups_first_obs,by = c("group", "dimension"))%>%
+  subset(!is.na(value_dimenion))%>%
+  group_by(dimension,group)%>%
+   mutate(perc_5 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 2600)[1],
+         perc_95 = bootBCa(mean(value_dimenion_obs), value_dimenion, n = 2600)[2])%>%
+   ggplot(aes(value_dimenion, color = group)) +
+   geom_histogram(aes(y=..density..), alpha=0.5,
+                 position="identity")+
+  geom_density(alpha=.2) +
+
+   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-3 ), color = "gray30")+
+   geom_point(aes(x = value_dimenion_obs, y = -3))+
+    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
+
+  facet_grid(~dimension)+
   # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+

### 2022-12-03 Power.Rmd
R2R simr

---
title: "Power simulations"
author: "Helio"
date: '2022-12-03'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

summary(pupil_arousal_findings$pupil_from_arousal)

install.packages("simr")

```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
library(simr)
library(lmerTest)
# Power for predictor 'x', (95% confidence interval):
power_models<- list()

table(is.na(db_full4new_stim_screen_pupil_nopract$arousal_c))
table(is.na(db_full4new_stim_screen_pupil_nopract$pup_basCor))

power_models$pupil <- lmer(pup_basCor ~ arousal_c +(1  | ssid), REML = FALSE,
                      data = subset(db_full4new_stim_screen_pupil_nopract, 
                                    # pupil_outlier == FALSE & 
                                     Group == "NT" & !is.na(pup_basCor) &
                                      !is.na(arousal_c)
                                    # arousal_outler == FALSE
                                    ))

db_full4new_stim_screen_pupil_nopract
power_models$pupil1<- power_models$pupil
fixef(power_models$pupil1)["arousal_c"]<- .4
sim_.4 <- powerSim(power_models$pupil1, nsim = 100)
sim_.4
# Power for predictor 'arousal_c', (95% confidence interval):
#       100.0% (96.38, 100.0)

?powerCurve

curve<- powerCurve(power_models$pupil1, nsim = 100)

plot(curve)

model3 <- extend(power_models$pupil1, along="ssid", n=1)

pc3 <- powerCurve(power_models$pupil1, along="ssid", nsim = 10)

plot(pc3)

extendeddata_along_ssid<- extend(power_models$pupil1, along="ssid", n=100)

pc_extended100 <- powerCurve(extendeddata_along_ssid, along="ssid", nsim = 100)
pc_extended100

plot(pc_extended100)

```
SCR

```{r}
power_models$BIO_CDA.PhasicMax <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c + (1|ssid) + (1|stimIAPS),
                        REML = FALSE,
                        data = subset(db_full4new_stim_screen_pupil_nopract_nt_304,
                                      !is.na(arousal_c)&
                                        !is.na(BIO_CDA.PhasicMax)))

table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304$arousal_c))
table(is.na(db_full4new_stim_screen_pupil_nopract_nt_304$BIO_CDA.PhasicMax))

summary(power_models$BIO_CDA.PhasicMax)
power_models$BIO_CDA.PhasicMax1<- power_models$BIO_CDA.PhasicMax
# 0.01571715 
fixef(power_models$BIO_CDA.PhasicMax1)["arousal_c"]
fixef(power_models$BIO_CDA.PhasicMax1)["arousal_c"] <- .1

summary(power_models$BIO_CDA.PhasicMax)

summary(power_models$BIO_CDA.PhasicMax1)
sim_SCR <- powerSim(power_models$pupil1, nsim = 100)

extendedscr100<- extend(power_models$BIO_CDA.PhasicMax1, along="ssid", n=100)

 pc_scr100<- powerCurve(extendedscr100, along="ssid", nsim = 100)
 plot(pc_scr100)

extendedscr1002<- extend(power_models$BIO_CDA.PhasicMax, along="ssid", n=100)

pc_scr100_2<- powerCurve(extendedscr1002, along="ssid", nsim = 100)

plot(pc_scr100_2)
```

### 2022-12-06 Power.Rmd
PowerRmd

@@
 ```{r}
-power_models$BIO_CDA.PhasicMax <- lmer(log1p(BIO_CDA.PhasicMax+.1) ~ arousal_c + (1|ssid) + (1|stimIAPS),
+power_models$BIO_CDA.PhasicMax <- lmer(BIO_CDA.PhasicMax ~ valence_c + (1|ssid) + (1|stimIAPS),
                         REML = FALSE,
@@
 # 0.01571715 
-fixef(power_models$BIO_CDA.PhasicMax1)["arousal_c"]
-fixef(power_models$BIO_CDA.PhasicMax1)["arousal_c"] <- .1
+fixef(power_models$BIO_CDA.PhasicMax)["valence_c"]
+
+# reverse log to get proper unites wot meaninful effect size
+0.01571715
+
+ex
+
+fixef(power_models$BIO_CDA.PhasicMax1)["valence_c"] <- -.1
 
@@
 summary(power_models$BIO_CDA.PhasicMax1)
-sim_SCR <- powerSim(power_models$pupil1, nsim = 100)
+sim_SCR <- powerSim(power_models$BIO_CDA.PhasicMax1,test = fixed("arousal_c:valence_c", "z"),
+                    nsim = 100)
 
-extendedscr100<- extend(power_models$BIO_CDA.PhasicMax1, along="ssid", n=100)
+# extendedscr100<- extend(power_models$BIO_CDA.PhasicMax1, along="ssid", n=100)
+# extendedscr100_int<- extend(power_models$BIO_CDA.PhasicMax1, along="ssid", n=100)
 
@@
 
-extendedscr1002<- extend(power_models$BIO_CDA.PhasicMax, along="ssid", n=100)
+extendedscr1002<- extend(power_models$BIO_CDA.PhasicMax1, along="ssid", n=100)
 
-pc_scr100_2<- powerCurve(extendedscr1002, along="ssid", nsim = 100)
+# pc_scr100_2<- powerCurve(extendedscr1002, along="ssid", nsim = 100)
 
-plot(pc_scr100_2)
+# extendedscr100_int@call
+pc_scr100_int<- powerCurve(extendedscr1002,
+                           test = fixed("arousal_c:valence_c", "z"),
+                           along="ssid", nsim = 50)
+
+plot(pc_scr100_int)
 ```

### 2022-12-10 Power.Rmd
Update Power.Rmd

@@
 summary(power_models$BIO_CDA.PhasicMax1)
-sim_SCR <- powerSim(power_models$BIO_CDA.PhasicMax1,test = fixed("arousal_c:valence_c", "z"),
+sim_SCR <- powerSim(power_models$BIO_CDA.PhasicMax1,
                     nsim = 100)
@@
 
- pc_scr100<- powerCurve(extendedscr100, along="ssid", nsim = 100)
- plot(pc_scr100)
+# pc_scr100<- powerCurve(extendedscr100, along="ssid", nsim = 100)
+ # plot(pc_scr100)
 
@@
 pc_scr100_int<- powerCurve(extendedscr1002,
-                           test = fixed("arousal_c:valence_c", "z"),
+                           test = fixed("valence_c", "z"),
                            along="ssid", nsim = 50)

### 2023-01-21 Paper_Analyses_subj_obje_arousal.Rmd
missed push
Prep-pub updates

@@
           )
+
+pupil_arousal_findings$pupil_from_ar_vale
+
+library(insight)
+sjPlot::sjp.lmer(pupil_arousal_findings$pupil_from_ar_vale)
+
+# load packages
+devtools::install_cran("sjPlot", force = TRUE, dependencies = TRUE)
+install.packages("sjPlot")
+library(sjPlot)
+library(sjmisc)
+
 ```
@@
 
-Do we get the same patterns when loking at paticipants and stimuli searatelly
+Do we get the same patterns when looking at participants and stimuli separately
 

### 2023-01-31 anonymise.Rmd
push

---
title: "Anonymise"
author: "Helio"
date: "2023-01-21"
output: html_document
---

```{r}
colnames(clustering_new_pre_PCA3.1)
colnames(clustering_new_pre_PCA3)

unique(clustering_new_pre_PCA3.1$ssid)
clustering_new_pre_PCA3.1

table(clustering_new_pre_PCA3.1$ssid)

data_osf<- clustering_new_pre_PCA3[,c(1,4:13,16:17)]

# create a factor variable with original levels
factor_var <- as.factor(as.character(data_osf$ssid))
# create a vector of letters and numbers
letters_and_numbers <- c(letters, 0:9)
# generate unique random strings for each level
random_strings <- lapply(levels(factor_var), function(x) paste(sample(letters_and_numbers, 10, replace = TRUE), collapse = ""))
names(random_strings) <- levels(factor_var)

idsnew<- data.frame(matrix(nrow=50))
idsnew$ssid<- as.vector(unique(data_osf$ssid))
# factor_var

idsnew$ssid_rand<- as.vector(unlist(unlist(random_strings)))
library(tidyverse)
data_osf_v1<- left_join(data_osf,idsnew)%>%
  select(c(15,2:13))

data_osf_v1

saveRDS(data_osf_v1,"data_RDS_v1.RDS", compress = F)

```
